### 2021-12-28 main.tex
init commit

\documentclass{article}

\usepackage[english]{babel}
\usepackage[letterpaper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

\title{Anonymous provision of services via blockchain}
\author{Stanisław Barański}
\date{December 2021}

\providecommand{\keywords}[1]{\textbf{Keywords:} #1}

\begin{document}
\maketitle

\begin{abstract}
Lorem ipsum\ldots
\end{abstract}
\keywords{data privacy, zk-SNARK, blockchain}

\section{Problem statement}
Service providers (SP) like: lawyers, laboratories, auditors, or banks, to provide services, require data that is often associated with user identity. The guarantee of the privacy of the data is based on a trust assumptions and security of IT systems. However, most of the service providers don't need the information of user identity for other reasons than payment, communication, or logistics. It would be desirable if the user could keep its identity private, while service provider still provide its services. This could lead to reduced trust that users have to put on SP and less responsibility borne by SP.

In this paper we propose a protocol for anonymous provision of services via blockchain and cryptography. Specificaly, we use
\begin{enumerate}
    \item \textbf{confidential blockchain} to process payment for a service without revealing a user's identity.
    \item \textbf{zero-knowledge proofs} — to proof the payment for the service without revealing the payment itself.
    \item \textbf{encryption scheme and blockchain} — to asynchronously deliver the results of the made service back to the user.
\end{enumerate}

\section{State of the art}
Verifiable Document Redacting ~\cite{chabanne2017verifiable} is a protocol for erasing confidential information from authenticated images in verifiable manner. In other words, the protocol allows verifying that only the fields that cover personal information has been blacked out from the authenticated image.

\section{Coverage}

Non invasive tests — those which patients can sample themselves: 
\begin{enumerate}
    \item Urine tests
    \item Stool tests
    \item Saliva tests
\end{enumerate}

\section{Solution}

\begin{figure}[htbp]
\centerline{\includegraphics[width=\linewidth]{sequence-flow.png}}
\caption{Sequence flow}
\label{fig:sequence-flow}
\end{figure}

\section{Blockchains}
\paragraph{Monero}
Monero offers out-of-the-box proving/checking confidental transactions. \href{https://www.getmonero.org/resources/user-guides/prove-payment.html}

\paragraph{ZCash}
ZCash offers payment disclosure as a preview feature.
\href{https://garethtdavies.medium.com/an-introduction-to-payment-disclosure-in-zcash-96748c209d49}

\href{https://garethtdavies.medium.com/an-introduction-to-payment-disclosure-in-zcash-96748c209d49}

\section{Applications}
\subsections{Clinical tests}
Bodybuilders, athletes,  weightlifters, cyclists, football and rugby players have to pass anti-doping tests before attending the competition.

Patients willing to check steroid tests, drug tests, venereal diseases — anything that they wouldn't want to share with anyone, have to risk that the data stored in laboratory won't get to unauthorized hands like attacker or malicious worker.

Analysis of urine, saliva, stool, or blood.

\subsections{Lawyer consultations}

People willing to take business action that may be risky or not yet fully legistlated, may be willing to receive the estimation of risks and repercussions of such action.
Such protocol would provide a mechanism for

\bibliographystyle{alpha}
\bibliography{bibliography}

\end{document}

### 2021-12-29 main.tex
update state of the ar

@@
 \section{State of the art}
+
 Verifiable Document Redacting ~\cite{chabanne2017verifiable} is a protocol for erasing confidential information from authenticated images in verifiable manner.
 In other words, the protocol allows verifying that only the fields that cover personal information has been blacked out from the authenticated image.
+This allows users to provide required images without exposing their personal information, and SPs to authenticate the modified images, such that they are sure that only the stated fields have been blacked out and nothing else was touched.
+% In this paper we extend the idea to a whole user-to-service-provider protocol
+
+Authors of the paper~\cite{lin2021efficient} propose a system for Privacy-Preserving Credit Score System.
+Letting banks to calculate creditworthness without learning user private information like registration, hobbies, credit, relationships, and inquiry.
+To achieve this they use Paillier encryption and noninteractive zero-Knowledge schemes (NIZK).
 

### 2021-12-29 main.tex
update problem statement refer to literature

@@
 \end{abstract}
-\keywords{data privacy, zk-SNARK, blockchain}
+\keywords{data privacy, privacy preserving, zk-SNARK, blockchain}
 
@@
 Service providers (SP) like: lawyers, laboratories, auditors, or banks, to provide services, require data that is often associated with user identity.
+
+Providing personal information exposes users to privacy risk, i.e. potential loss of control over personal information ~\cite{smith2011information}.
+
+Such user information can be used then for commercial gains.
+For example, by reselling it to marketers, other businesses or even cybercriminals.
+Which in turn can lead to profiled advertisements, or cryminal activities like identity theft or illegal tracking and surveillance ~\cite{}
+
 The guarantee of the privacy of the data is based on a trust assumptions and security of IT systems.
 However, most of the service providers don't need the information of user identity for other reasons than payment, communication, or logistics.
+
 It would be desirable if the user could keep its identity private, while service provider still provide its services.
@@
 
-In this paper we propose a protocol for anonymous provision of services via blockchain and cryptography. Specificaly, we use
+In this paper we propose a protocol for anonymous provision of services via blockchain and cryptography techniques. Specificaly, we use
 \begin{enumerate}
@@
 \section{Applications}
-\subsections{Clinical tests}
+\subsection{Anonymous clinical tests}
 Bodybuilders, athletes,  weightlifters, cyclists, football and rugby players have to pass anti-doping tests before attending the competition.
@@
 
-\subsections{Lawyer consultations}
+\subsection{Anonymous lawyer consultations}
 
@@
 Such protocol would provide a mechanism for
+
+\subsection{Anonymous financial trustworthiness evaluation}
+
+Evaluating financial trustworthiness is required when user want to, for example issue a credit card, take loan for a home, or rent a car. 
+As defined in~\cite{lin2021efficient}, such a system consist of three parties: (i) users, (ii) credit bureaus, and (iii) creditors.
+Users willing to take a credit, have to provide to the credit bureaus, their financial activities like: new account creation, account balance, credit card utilization, credit inquires, and payment history.
+Such information are then submitted to creditors to compute the user's credit score.
 

### 2021-12-29 main.tex
update state of the art

@@
 
-Such user information can be used then for commercial gains.
-For example, by reselling it to marketers, other businesses or even cybercriminals.
-Which in turn can lead to profiled advertisements, or cryminal activities like identity theft or illegal tracking and surveillance ~\cite{}
+Such user information can be then used deliberately or unintentionally (e.g, by theft) for: insider disclosure, unauthorized access, or commercial gains.
+For example, by reselling it to marketers, finantial institutions, other businesses, government agencies, or even cybercriminals.
+Which in turn can lead to profiled advertisements, or cryminal activities like identity theft or illegal tracking and surveillance~\cite{smith2011information}.
 

### 2022-01-13 main.tex
update application
update

@@
 \title{Anonymous provision of services via blockchain}
+% Anonymous and fair provision of physical services via blockchain
 \author{Stanisław Barański}
@@
 \end{abstract}
-\keywords{data privacy, privacy preserving, zk-SNARK, blockchain}
+\keywords{data privacy, privacy preserving, blockchain, fair-exchange}
 
@@
 Such user information can be then used deliberately or unintentionally (e.g, by theft) for: insider disclosure, unauthorized access, or commercial gains.
-For example, by reselling it to marketers, finantial institutions, other businesses, government agencies, or even cybercriminals.
-Which in turn can lead to profiled advertisements, or cryminal activities like identity theft or illegal tracking and surveillance~\cite{smith2011information}.
+For example, by reselling it to marketers, financial institutions, other businesses, government agencies, or even cybercriminals.
+Which in turn can lead to profiled advertisements, or criminal activities like identity theft or illegal tracking and surveillance~\cite{smith2011information}.
 
@@
 
-\section{State of the art}
-
-Verifiable Document Redacting ~\cite{chabanne2017verifiable} is a protocol for erasing confidential information from authenticated images in verifiable manner.
-In other words, the protocol allows verifying that only the fields that cover personal information has been blacked out from the authenticated image.
-This allows users to provide required images without exposing their personal information, and SPs to authenticate the modified images, such that they are sure that only the stated fields have been blacked out and nothing else was touched.
-% In this paper we extend the idea to a whole user-to-service-provider protocol
-
 Authors of the paper~\cite{lin2021efficient} propose a system for Privacy-Preserving Credit Score System.
@@
 
-\section{Coverage}
+\subsection{Fair-exchange protocols}
 
-Non invasive tests — those which patients can sample themselves: 
+We observe that such protocols for providing services are special case of fair-exchange protocol.
+
+Fair-exchange protocol is a protocol used for performing e-commerce transactions of both digital and physical goods, exchanging documents, or signing contracts, between mutually distrusting parties, while satisfying following conditions:
+\begin{itemize}
+    \item non-repudiation  — any participating party can not deny their actions (e.g. signing, sending, and receiving data). Usually this is achieved by digital signatures.
+    \item fairness — any participating party does not gain any advantage at any step of the exchange protocol.
+    \item timeliness — the protocol eventually terminates for all participants.
+\end{itemize}
+
+There are two main categories of fair-exchange protocols~\cite{kremer2002intensive,duangphasuk2020fair}: those that involve the use of trusted third party (TTP), and those that do not.
+
+\paragraph{Protocols that do not involve use of trusted third party.}
+Protocols that do not involve use of trusted third party, also called "probabilistic" or "gradual" exchange protocols.
+In such protocols~\cite{markowitch1999probabilistic}, items that will be exchanged are first split into parts.
+Then, the parts are exchanged between parties.
+This causes increased communication overhead.
+Moreover the fairness of such protocol is probabilistic, meaning that there is a small chance that the protocol will end up with one party being in advantageous position.
+
+Hence, the great benefit of TTP-less protocol, comes at a cost of increased communication overhead, and unsatisfactory property of uncertain termination.
+
+\paragraph{Protocols that involve the use of trusted third party}
+The most common approach to achieve fair-exhange conditions is by introducing Trusted Third Party (TTP).
+
+TTP can play different role in fair-exchange protocol. Commonly agreed classification~\cite{kremer2002intensive,duangphasuk2020fair} distinguish three roles the TTP can play:
+
 \begin{enumerate}
-    \item Urine tests
-    \item Stool tests
-    \item Saliva tests
+    \item Inline~\cite{coffey1996non}, the TTP act as a authoritative middleman between sender and receiver.
+The obvious consequence of such method is the communication bottleneck and single point of failure.
+These protocols are inefficient and trust-dependent.
+
+    \item Online~\cite{djuric2015feips}, the TTP is involved in each protocol step, but not in each data transmission. Significantly improving the performance compared to inline TTP.
+
+    \item Offline~\cite{hwang2015provable}, the TTP is involved only in case of a dispute between parties.
+This approach is also called "optimistic", because in scenarios where both parties behaves honesty, the TTP is ignored.
+Resulting in high-performance and low trust-dependency.
 \end{enumerate}
 
-\section{Solution}
+Involving online and centralized TTP in each transaction, could cause the communication bottleneck problem. Therefore, the offline TTP is the most favorable approach.
+
+The main idea of the offline TTP model is that the sender sends a ciphertext of his/her own document before obtaining the expect document from opposite party.
+Both parties will then fairly exchange the decryption keys of the ciphertext.
+
+\section{E-commerce transaction protocol}
+
+According to ~\cite{djuric2015feips}, a typical e-commerce process can be illustrated with the diagram on figure ~\ref{fig:ecommerce-transaction-diagram}.
 
 \begin{figure}[htbp]
-\centerline{\includegraphics[width=\linewidth]{sequence-flow.png}}
-\caption{Sequence flow}
-\label{fig:sequence-flow}
+\centerline{\includegraphics[width=.4\linewidth]{ecommerce-process.png}}
+\caption{Diagram illustrating a typical e-commerce transaction process}
+\label{fig:ecommerce-transaction-diagram}
 \end{figure}
 
-\section{Blockchains}
-\paragraph{Monero}
-Monero offers out-of-the-box proving/checking confidental transactions. \href{https://www.getmonero.org/resources/user-guides/prove-payment.html}
+\section{Anonymous fair-exchange}
 
-\paragraph{ZCash}
-ZCash offers payment disclosure as a preview feature.
-\href{https://garethtdavies.medium.com/an-introduction-to-payment-disclosure-in-zcash-96748c209d49}
+An protocol ensures anonymity if no party can make a link between identity and actions taken by another party.
 
-\href{https://garethtdavies.medium.com/an-introduction-to-payment-disclosure-in-zcash-96748c209d49}
+\subsection{State of the art}
+\subsubsection{Anonymity and fair-exchange in e-commerce protocol for physical products delivery}
+
+Authors of ~\cite{birjoveanu2015anonymity} proposed a fair-exchange of physical product and electronic payment protocol that guarantee both customer and merchant anonymity.
+They achieve it by introducing online trusted third party that validate coins and provide fair exchange guarantees.
+
+The anonymity is ensured by assuming the existence of source cabinet (SC) and delivery cabinet (DC), and a trusted delivery agent who take product from a source cabinet and provide it to a destination cabinet.
+Both cabinets provides access to the product by passwords to conceal identity of the customer and the merchant.
+To avoid identity disclosure of customer and merchant, the access to the product is provided by passwords.
+
+Both cabinets are equipment with cameras. Also there should exist the trusted delivery agent (DA) who will deliver items from source cabinet do delivery cabinet.
+
+The protocol works as follows:
+\begingroup
+\renewcommand{\labelenumii}{\arabic{enumii}.}
+\begin{enumerate}
+    \item Both parties agree on the purchase details.
+    \item The customer buys a digital coin from his bank and validates it with the TTP.
+    \item The customer sends to the merchant the purchase order and the digital signature made by TTP on the encrypted coin.
+    \item The merchant post the product to the source cabinet.
+    \item Delivery agent collect the product from source cabinet and post it to delivery cabinet.
+    \item Customer collects the product from delivery cabinet using password.
+    \item The customer checks if the product is actually the ordered one.
+    \begin{itemize}
+    \item[-] if yes 
+        \begin{enumerate}
+        \setcounter{enumii}{7}
+        \item the customer sends the acknowledge to delivery cabinet and decryption key to the merchant.
+        \item The merchant redeem the coins from the bank.
+        \end{enumerate}
+    \item[-] if no
+        \begin{enumerate}
+        \setcounter{enumii}{7}
+        \item the delivery cabinet is equipment with video camera that records the moment when the customer open the package and let the customer to signal the invalidity of the product, and so, sending the encrypted recording to the TTP.
+        \item the dispute is settled via TTP, optionally letting each party to reveal it's identity.
+    \end{enumerate}
+    \end{itemize}
+\end{enumerate}
+\endgroup
+
+Yet, the fair-exchange properties are achieved by strong assumptions. Namely, 
+\begin{itemize}
+    \item the TTP does not misbehave or collude with any party. 
+    \item The customer's and merchant's banks enable confidental transactions and both share commit-buffer where the value is locked until the transaction is finished.   
+    \item All banks mantain a global list of coin's serial numbers to prevent double-spending problem. 
+    \item The source cabinet and delivery cabinet exists, and in both the product access is protected by password.
+    \item Delivery cabinet is equppted with a video camera that records the moment when the customer opens the package, and provide a way to submit the video to TTP in case of a dispute. 
+    \item Delivery agent exist and is trusted. 
+    \item Communication channels between parties provides anonymity.
+\end{itemize}
+
+\subsubsection{Themis} Themis~\cite{meng2019themis} is a fair-exchange protocol, which uses blockchain instead of TTP.
+It provide escrow services for secure exchanging between cryptocurrencies and physical goods.
+
+Authors highlight that a widely-used atomic exchange mechanism HTLC (Hashed Time-lock Contract) is vulnerable to denial of service (DoS) attacks.
+While Multi-Signature Schemes depends on the Trusted Third Party (TTP) making them vulnerable to collusion attacks.
+Such TTP can collude with one party and take the locked funds.
+It can also refuse settling disputes and lock the hosted funds.
+
+Themis is a decentralized system which provides an escrow and dispute resolution serivces. It satisfies following requirements:
+\begin{description}
+    \item[Fairness] Either both seller and buyer obtain all the goods, or they both obtain nothing.
+    \item[Security] The funds are locked until the transaction is completed.
+    \item[Passivity] If no dispute arise, the third-party does not need to involve in the transaction.
+    \item[Correctness] Transactions and disputes are executed according to a priori agreed protocol rules.
+    \item[Dependability] There is no single point of failure vulnerable to DoS attack.
+    \item[Privacy] If the dispute does not arise, the third-party does not know if the transaction completes. If the dispute arises, only the related parties are aware of it.    
+\end{description}
+
+\subsection{A Solution for Secure Certified Electronic Mail Using Blockchain as a Secure Message Board}
+
+\section{Contribution}
+In this paper similarly to by~\cite{birjoveanu2015anonymity}, we propose fully-fledged protocol for anonymous fair-exchange which includes payment processing and physical goods exchange.
+Yet, compared to ~\cite{birjoveanu2015anonymity}, we use decentralized blockchain instead of centralized TTP, and payments using cryptocurrencies, getting rid of strong and unrealistic assumptions on traditional banking.
+
+Additionally, since the services are provided locally, we enable customers to disclose the transaction and start the dispute in law.
+
+Once the package is delivered to the SP, the SP publish POR (Proof-of-recipment) on the blockchain.
+From this point the customer is secured, i.e.
+if the merchant misbehaves, customer can proof to the justice that he paid for the service at a particular point of time, and that SP received the package, but didn't publish results.
+
+Or we can create a smart contract that automatically punish the SP if he doesn't fulfull the agreement in time.
+And the proof to justice is used in case where the content of the service is invalid, something that have to be settled by human.
+
+If merchant misbehaves i.e. does not provide the agreed services, then the customer can create a proof that such incident happened 
+However it provide a proof that such incident happened. In settings where the identity of the party is known, such proof can be used to bring the misbehaving party to the justice.
 
@@
 
+\subsection{Anonymous physical delivery e-commerce}
+% TODO write about
+~\cite{birjoveanu2015anonymity}
+
+% [![](https://mermaid.ink/img/eyJjb2RlIjoic2VxdWVuY2VEaWFncmFtXG4gICAgQ3VzdG9tZXItPj5TbWFydCBDb250cmFjdDogUHJvdmlkZSBkZXRhaWxzLCBsb2NrIGZ1bmRzLlxuXHRhY3RpdmF0ZSBTbWFydCBDb250cmFjdFxuXHRTbWFydCBDb250cmFjdCAtPj4gU21hcnQgQ29udHJhY3Q6IENyZWF0ZSBhZ3JlZW1lbnRcblx0ZGVhY3RpdmF0ZSBTbWFydCBDb250cmFjdFxuXHRhbHQgSWYgc2VydmljZSBwcm92aWRlciBkZWNsaW5lIGFncmVlbWVudFxuXHRTZXJ2aWNlIFByb3ZpZGVyIC0-PiBTbWFydCBDb250cmFjdDogRGVjbGluZVxuXHRTbWFydCBDb250cmFjdCAtPj4gQ3VzdG9tZXI6IFJlZnVuZFxuXHRlbmRcblx0U2VydmljZSBQcm92aWRlciAtPj4gU21hcnQgQ29udHJhY3Q6IEFjY2VwdFxuXHRcblx0YWx0IGRpZ2l0YWwgZG9jdW1lbnRzXG5cdFx0cGFyIGF0b21pYyB0cmFuc2FjdGlvblxuXHRcdEN1c3RvbWVyIC0-PiAgb2ZmLWNoYWluIHN0b3JhZ2U6IFB1Ymxpc2ggZW5jcnlwdGVkIGRvY3VtZW50c1xuXHRcdG9mZi1jaGFpbiBzdG9yYWdlIC0tPj4gQ3VzdG9tZXI6IFByb29mLW9mLURlbGl2ZXJ5IChQT0QpXG5cdFx0ZW5kXG5cdEN1c3RvbWVyIC0-PiBTbWFydCBDb250cmFjdDogUHVibGlzaCBQT0Rcblx0ZWxzZSBwaHlzaWNhbCBkb2N1bWVudHNcblx0XHRwYXIgYXRvbWljIHRyYW5zYWN0aW9uXG5cdFx0Q3VzdG9tZXIgLT4-ICBTZXJ2aWNlIFByb3ZpZGVyOiBQcm92aWRlIGRvY3VtZW50cyBwaHlzaWNhbGx5XG5cdFx0U2VydmljZSBQcm92aWRlciAtPj4gU21hcnQgQ29udHJhY3Q6IFB1Ymxpc2ggUE9EXG5cdFx0ZW5kXG5cdGVuZFxuXHRsb29wIGV4ZWN1dGUgdW50aWwgY3VzdG9tZXIgaXMgc2F0aXNmaWVkIHdpdGggcmVzdWx0c1xuXHRTZXJ2aWNlIFByb3ZpZGVyIC0-PiBTZXJ2aWNlIFByb3ZpZGVyOiBFeGVjdXRlIHNlcnZpY2Vcblx0U2VydmljZSBQcm92aWRlciAtPj4gT2ZmLWNoYWluIHN0b3JhZ2U6IFB1Ymxpc2ggZW5jcnlwdGVkIHJlc3VsdHNcblx0U2VydmljZSBQcm92aWRlciAtPj4gU21hcnQgQ29udHJhY3Q6IFB1Ymxpc2ggUHJvb2Ytb2YtUmVzdWx0c1xuXHRcblx0XG5cdEN1c3RvbWVyIC0-PiBTbWFydCBDb250cmFjdDogR2V0IFByb29mLW9mLVJlc3VsdHNcblx0Q3VzdG9tZXIgLT4-IE9mZi1jaGFpbiBzdG9yYWdlOiBHZXQgcmVzdWx0c1xuXHRDdXN0b21lciAtPj4gQ3VzdG9tZXI6IFZhbGlkYXRlIHJlc3VsdHNcblx0YWx0IHJlc3VsdHMgYXJlIGluY29ycmVjdFxuXHRcdEN1c3RvbWVyIC0-PiBTbWFydCBDb250cmFjdDogU3RhcnQgZGlzcHV0ZSwgcHJvdmlkZSBkZXRhaWxzXG5cdFx0YWx0IFNlcnZpY2UgUHJvdmlkZXIgZGVjbGluZSBhcmd1bWVudHNcblx0XHRcdFNtYXJ0IENvbnRyYWN0IC0-PiBTZXJ2aWNlIFByb3ZpZGVyOiBVbmxvY2sgZnVuZHNcblx0XHRcdG5vdGUgcmlnaHQgb2YgU2VydmljZSBQcm92aWRlcjogU1AgaXMgYWx3YXlzIG9uIGxvc3QgcG9zaXRpb24sIDxicj5iZWNhdXNlIGhlIGNhbiBub3Qgc3VlIGFub255bW91cyBjdXN0b21lci48YnI-IFRoZXJlZm9yZSB0aGUgc2hvdWxkIGJlIHRoZSBob2xkZXIgdGhlIGZ1bmRzIGFzIHNvb24gYXMgcG9zc2libGUuXG5cdFx0XHRDdXN0b21lciAtPj4gUG9saWNlOiBPcGVuIGRpc3B1dGUgYXQgcG9saWNlXG5cdFx0ZW5kXG5cdGVuZFxuXHRlbmRcblx0XG5cbiAgICBcbiAgICAgICAgICAgICIsIm1lcm1haWQiOnsidGhlbWUiOiJkZWZhdWx0In0sInVwZGF0ZUVkaXRvciI6ZmFsc2UsImF1dG9TeW5jIjp0cnVlLCJ1cGRhdGVEaWFncmFtIjpmYWxzZX0)](https://mermaid.live/edit#eyJjb2RlIjoic2VxdWVuY2VEaWFncmFtXG4gICAgQ3VzdG9tZXItPj5TbWFydCBDb250cmFjdDogUHJvdmlkZSBkZXRhaWxzLCBsb2NrIGZ1bmRzLlxuXHRhY3RpdmF0ZSBTbWFydCBDb250cmFjdFxuXHRTbWFydCBDb250cmFjdCAtPj4gU21hcnQgQ29udHJhY3Q6IENyZWF0ZSBhZ3JlZW1lbnRcblx0ZGVhY3RpdmF0ZSBTbWFydCBDb250cmFjdFxuXHRhbHQgSWYgc2VydmljZSBwcm92aWRlciBkZWNsaW5lIGFncmVlbWVudFxuXHRTZXJ2aWNlIFByb3ZpZGVyIC0-PiBTbWFydCBDb250cmFjdDogRGVjbGluZVxuXHRTbWFydCBDb250cmFjdCAtPj4gQ3VzdG9tZXI6IFJlZnVuZFxuXHRlbmRcblx0U2VydmljZSBQcm92aWRlciAtPj4gU21hcnQgQ29udHJhY3Q6IEFjY2VwdFxuXHRcblx0YWx0IGRpZ2l0YWwgZG9jdW1lbnRzXG5cdFx0cGFyIGF0b21pYyB0cmFuc2FjdGlvblxuXHRcdEN1c3RvbWVyIC0-PiAgb2ZmLWNoYWluIHN0b3JhZ2U6IFB1Ymxpc2ggZW5jcnlwdGVkIGRvY3VtZW50c1xuXHRcdG9mZi1jaGFpbiBzdG9yYWdlIC0tPj4gQ3VzdG9tZXI6IFByb29mLW9mLURlbGl2ZXJ5IChQT0QpXG5cdFx0ZW5kXG5cdEN1c3RvbWVyIC0-PiBTbWFydCBDb250cmFjdDogUHVibGlzaCBQT0Rcblx0ZWxzZSBwaHlzaWNhbCBkb2N1bWVudHNcblx0XHRwYXIgYXRvbWljIHRyYW5zYWN0aW9uXG5cdFx0Q3VzdG9tZXIgLT4-ICBTZXJ2aWNlIFByb3ZpZGVyOiBQcm92aWRlIGRvY3VtZW50cyBwaHlzaWNhbGx5XG5cdFx0U2VydmljZSBQcm92aWRlciAtPj4gU21hcnQgQ29udHJhY3Q6IFB1Ymxpc2ggUE9EXG5cdFx0ZW5kXG5cdGVuZFxuXHRsb29wIGV4ZWN1dGUgdW50aWwgY3VzdG9tZXIgaXMgc2F0aXNmaWVkIHdpdGggcmVzdWx0c1xuXHRTZXJ2aWNlIFByb3ZpZGVyIC0-PiBTZXJ2aWNlIFByb3ZpZGVyOiBFeGVjdXRlIHNlcnZpY2Vcblx0U2VydmljZSBQcm92aWRlciAtPj4gT2ZmLWNoYWluIHN0b3JhZ2U6IFB1Ymxpc2ggZW5jcnlwdGVkIHJlc3VsdHNcblx0U2VydmljZSBQcm92aWRlciAtPj4gU21hcnQgQ29udHJhY3Q6IFB1Ymxpc2ggUHJvb2Ytb2YtUmVzdWx0c1xuXHRcblx0XG5cdEN1c3RvbWVyIC0-PiBTbWFydCBDb250cmFjdDogR2V0IFByb29mLW9mLVJlc3VsdHNcblx0Q3VzdG9tZXIgLT4-IE9mZi1jaGFpbiBzdG9yYWdlOiBHZXQgcmVzdWx0c1xuXHRDdXN0b21lciAtPj4gQ3VzdG9tZXI6IFZhbGlkYXRlIHJlc3VsdHNcblx0YWx0IHJlc3VsdHMgYXJlIGluY29ycmVjdFxuXHRcdEN1c3RvbWVyIC0-PiBTbWFydCBDb250cmFjdDogU3RhcnQgZGlzcHV0ZSwgcHJvdmlkZSBkZXRhaWxzXG5cdFx0YWx0IFNlcnZpY2UgUHJvdmlkZXIgZGVjbGluZSBhcmd1bWVudHNcblx0XHRcdFNtYXJ0IENvbnRyYWN0IC0-PiBTZXJ2aWNlIFByb3ZpZGVyOiBVbmxvY2sgZnVuZHNcblx0XHRcdG5vdGUgcmlnaHQgb2YgU2VydmljZSBQcm92aWRlcjogU1AgaXMgYWx3YXlzIG9uIGxvc3QgcG9zaXRpb24sIDxicj5iZWNhdXNlIGhlIGNhbiBub3Qgc3VlIGFub255bW91cyBjdXN0b21lci48YnI-IFRoZXJlZm9yZSB0aGUgc2hvdWxkIGJlIHRoZSBob2xkZXIgdGhlIGZ1bmRzIGFzIHNvb24gYXMgcG9zc2libGUuXG5cdFx0XHRDdXN0b21lciAtPj4gUG9saWNlOiBPcGVuIGRpc3B1dGUgYXQgcG9saWNlXG5cdFx0ZW5kXG5cdGVuZFxuXHRlbmRcblx0XG5cbiAgICBcbiAgICAgICAgICAgICIsIm1lcm1haWQiOiJ7XG4gIFwidGhlbWVcIjogXCJkZWZhdWx0XCJcbn0iLCJ1cGRhdGVFZGl0b3IiOmZhbHNlLCJhdXRvU3luYyI6dHJ1ZSwidXBkYXRlRGlhZ3JhbSI6ZmFsc2V9)
+\begin{figure}[htbp]
+\centerline{\includegraphics[width=\linewidth]{sequence-flow.png}}
+\caption{Sequence flow}
+\label{fig:sequence-flow}
+\end{figure}
+
+\section{Solution protocol}
+
+\section{Blockchains}
+\paragraph{Monero}
+Monero offers out-of-the-box proving/checking confidental transactions. \href{https://www.getmonero.org/resources/user-guides/prove-payment.html}
+
+\paragraph{ZCash}
+ZCash offers payment disclosure as a preview feature.
+\href{https://garethtdavies.medium.com/an-introduction-to-payment-disclosure-in-zcash-96748c209d49}
+
+\href{https://garethtdavies.medium.com/an-introduction-to-payment-disclosure-in-zcash-96748c209d49}
+
+\paragraph{Aleo}
+
+\section{Future work}
+
+Verifiable Document Redacting ~\cite{chabanne2017verifiable} is a protocol for erasing confidential information from authenticated images in verifiable manner.
+In other words, the protocol allows verifying that only the fields that cover personal information has been blacked out from the authenticated image.
+This allows users to provide required images without exposing their personal information, and SPs to authenticate the modified images, such that they are sure that only the stated fields have been blacked out and nothing else was touched.
+
+If such Verifiable Redacted Documents were accepted by other service providers like bank or tax office, national register of the judiciary, then the SP could use the documents provided by the customer to provide wider range of services, without knowing identity of the customer.
+
+% In this paper we extend the idea to a whole user-to-service-provider protocol
+
 \bibliographystyle{alpha}

### 2022-01-30 main.tex
update paper
add anynomous

@@
 \documentclass{article}
-
 \usepackage[english]{babel}
@@
 \begin{abstract}
-Lorem ipsum\ldots
+Service providers like: lawyers, laboratories, auditors, or banks, to provide services, require customers to submit data that is often associated with their personal information.
+This situation expose customers to privacy risk.
+However, most of the service providers use the personal information merely for logistic operations, and could provide services on anonymous data if other means of communication would be possible.
+
+We propose a protocol for local confidential services provision, using blockchain for both contract agreement and anonymous payments.
+
+In case of dispute, we let the parties communicate over blockchain. In case of disagreement, the customer can disclose the whole interaction and proof to the justice misbehaving SP.
+
+We propose three applications for our protocol: (i) anonymous steroid examination, (ii) anonymous legal advice, and (iii) anonymous financial trustworthiness evaluation.
+
 \end{abstract}
@@
 
-In this paper we propose a protocol for anonymous provision of services via blockchain and cryptography techniques. Specificaly, we use
+In this paper we propose a protocol for anonymous provision of services via blockchain and cryptography techniques. Specifically, we use
 \begin{enumerate}
     \item \textbf{confidential blockchain} to process payment for a service without revealing a user's identity.
+    \item \textbf{smart contracts} to process the agreements and disputes in decentralized and trustless manner.
     \item \textbf{zero-knowledge proofs} — to proof the payment for the service without revealing the payment itself.
@@
 
-\section{Anonymous fair-exchange}
+\section{Pseudo-anonymous vs anonymous blockchain}
+In the papers on fair-exchange and anonymity, there's a disagreement on what the anonymity is, the definition is vague, and sometimes overused (wiki leaks), it's rather commonly accepted that Bitcoin and other the like traceable blockchains are not anonymous, rather pseudo-nomous.
+
+What is a anonymity then? We like the definition stated in (huge paper on privacy ), or the more practical in the context of blockchain the definition stated in (swap in Monero).
+
+\section{State of the art}
+
+\subsection{Anonymous fair-exchange}
 
@@
 
-\subsection{State of the art}
-\subsubsection{Anonymity and fair-exchange in e-commerce protocol for physical products delivery}
+\paragraph{Themis} Themis~\cite{meng2019themis} is a fair-exchange protocol, which uses blockchain instead of TTP.
+It provide escrow services for secure exchanging between cryptocurrencies and digital goods.
+
+Authors highlight that a widely-used atomic exchange mechanism HTLC (Hashed Time-lock Contract) is vulnerable to denial of service (DoS) attacks.
+While Multi-Signature Schemes depends on the Trusted Third Party (TTP) making them vulnerable to collusion attacks.
+Such TTP can collude with one party and take the locked funds.
+It can also refuse settling disputes and lock the hosted funds.
+
+Themis is a decentralized system that provides an escrow and dispute resolution. It claims to satisfy following requirements:
+\begin{description}
+    \item[Fairness] Either both seller and buyer obtain all the goods, or they both obtain nothing.
+    \item[Security] The funds are locked until the transaction is completed.
+    \item[Passivity] If no dispute arise, the third-party does not need to involve in the transaction.
+    \item[Correctness] Transactions and disputes are executed according to a priori agreed protocol rules.
+    \item[Dependability] There is no single point of failure vulnerable to DoS attack.
+    \item[Privacy] If the dispute does not arise, the third-party does not know if the transaction completes. If the dispute arises, only the related parties are aware of it.    
+\end{description}
+
+Two parties, say Alice and Bob, can create an escrow by generating 2-of-2 (not 2-of-3 as it is other TTP-based systems) threshold account using Thresh-Key-Gen protocol.
+Alice and Bob generate secret keys $x_A$ and $x_B$ accordingly, the shared account public key becomes $y = g^{x_A+x_B}$; only the access to both Alice's and Bob's secrets grants access to the shared account.
+
+Then, both Alice and Bob, takes their keys, and split them into $n=2t+1$ secret shares using Shamir Secret Shamir protocol, where $n$ is the number of mediators that participate in the decentralized network, and $t+1$ becomes the threshold of sufficient number of mediators that can reconstruct the secret key.
+
+Next, both Alice and Bob, take their key shares, and encrypt each $i$-th key share using public key of $i$-th mediator.
+As a result Alice's secret $x_A$ becomes ${c^A_1, c^A_2,...,c^A_n}$, and Bob's secret $x_B$ becomes ${c^B_1, c^B_2,...,c^B_n}$, where $c_i = E_{M_i}(P_i)$ is the encrypted $i$-th key share using $i$-th mediator public key $M_i$.
+
+Next, both Alice and Bob exchange the sets of encrypted key shares with each other. And send funds to the escrow account.
+
+The escrow is secure as long as $t+1$ of mediators does not collude, which would let them recreate both $x_A$ and $x_B$.
+Also, to ensure that parties are exchanging real key shares, they also send a witnesses generated with Feldman VSS scheme and zero-knowledge proofs to guarantee the consistency between witnesses and key shares.
+
+In case of dispute, the decentralized network of mediators settle the conflict and grand one winning party, the other party secret key, letting him to withdraw the funds.
+
+The honesty of mediators is achieved by the monetary incentivization and reputation system.
+
+\paragraph{A Solution for Secure Certified Electronic Mail Using Blockchain as a Secure Message Board}
+
+The idea of certified mail is simple, neither the sender can deny sending the mail, nor the receiver can deny receiving it.
+As the service is widely used in paper world, achieving it for e-mails haven't meet the agreement across scientific community for over 40 years.
+The main reason was the dependency of TTP.
+Which significantly reduce the performance, security, and robustness of such protocol.
+Those protocols that do not use TTP struggle with high computation and communication overhead.
+
+Authors of ~\cite{hinarejos2019solution} replaced the TTP with blockchain (concretely Bitcoin blockchain as a reference implementation), which can be seen as a secure, verifiable, and decentralized TTP.
+
+The idea behind certified e-mails—and any other fair-exchange protocol—is following
+\begin{enumerate}
+    \item The sender sends encrypted and signed message to the receiver.
+    \item The receiver returns a proof of delivery (a signature) of the encrypted message to the sender.
+    \item The sender publish on blockchain (or TTP in general) a proof of delivery and the decryption key.
+    \item The receiver decrypt the encrypted message using the published decryption key.
+\end{enumerate}
+
+The non-repudiation requirement is achieved by the receiver sending the Proof-of-Delivery prior having access to the decrypted message.
+And the sender publishing the decription key together with the Proof-of-Delivery on blockchain (or TTP) so that the receiver can not deny both receiving the message and having access to decryption key, because it's publicly available.
+
+The protocol also handles confidentiality — the encryption key used to encrypt and then decrypt the message is encrypted using the receiver's public key, so the key is never published in raw form.
+Also, the protocol supports timeliness, meaning that the transaction is always finalized in a finite time.
+
+In this case, the role of Blockchain is to attest the existence of decryption key.
+
+\subsection{Anonymous delivery system for physical goods}
+
+\paragraph{Anonymity and fair-exchange in e-commerce protocol for physical products delivery}
 
@@
 
-\subsubsection{Themis} Themis~\cite{meng2019themis} is a fair-exchange protocol, which uses blockchain instead of TTP.
-It provide escrow services for secure exchanging between cryptocurrencies and physical goods.
+\paragraph{Lelanros} Lelanros~\cite{altawy2017lelantos} is a blockchain-based anonymous physical delivery system.
+The anonymity is achieved by employing ToR's onion routing to connect physical delivery providers.
+The whole route from merchant to customer is split into multiple steps, and each step is undertaken by different randomly selected delivery provider.
+As long as the develiery providers does no collude, mechant can not learn both identity and destination address of the customer.
 
-Authors highlight that a widely-used atomic exchange mechanism HTLC (Hashed Time-lock Contract) is vulnerable to denial of service (DoS) attacks.
-While Multi-Signature Schemes depends on the Trusted Third Party (TTP) making them vulnerable to collusion attacks.
-Such TTP can collude with one party and take the locked funds.
-It can also refuse settling disputes and lock the hosted funds.
+Onchain smart-contract is used to coordinate the whole process and mediate communication between customer and delivery providers.
 
-Themis is a decentralized system which provides an escrow and dispute resolution serivces. It satisfies following requirements:
-\begin{description}
-    \item[Fairness] Either both seller and buyer obtain all the goods, or they both obtain nothing.
-    \item[Security] The funds are locked until the transaction is completed.
-    \item[Passivity] If no dispute arise, the third-party does not need to involve in the transaction.
-    \item[Correctness] Transactions and disputes are executed according to a priori agreed protocol rules.
-    \item[Dependability] There is no single point of failure vulnerable to DoS attack.
-    \item[Privacy] If the dispute does not arise, the third-party does not know if the transaction completes. If the dispute arises, only the related parties are aware of it.    
-\end{description}
+However, the system achieve only pseudo-anonymity or 'weak anonymity'.
 
-\subsection{A Solution for Secure Certified Electronic Mail Using Blockchain as a Secure Message Board}
+\paragraph{Auditable Protocols for Fair Payment and Physical Asset Delivery Based on Smart Contracts}
+Authors of~\cite{wang2019auditable} propose simillar to \cite{altawy2017lelantos} physical asset delivery system to connect merchants, customers and logistic company.
+
+However, the system does not achieve anonymity.
 
@@
 In this paper similarly to by~\cite{birjoveanu2015anonymity}, we propose fully-fledged protocol for anonymous fair-exchange which includes payment processing and physical goods exchange.
-Yet, compared to ~\cite{birjoveanu2015anonymity}, we use decentralized blockchain instead of centralized TTP, and payments using cryptocurrencies, getting rid of strong and unrealistic assumptions on traditional banking.
+Yet, compared to ~\cite{birjoveanu2015anonymity}, we use blockchain instead of centralized TTP.
+Additionally, we use anonymous cryptocurrencies getting rid of strong and unrealistic assumptions on traditional banking.
+
+Although there have been number of protocols achieving fair-exchange over blockchain~\cite{heilman2016blindly, meng2019themis, icete18, barber2012bitter}, only few achieve anonymity~\cite{heilman2016blindly}.
+From these achieving anonymity, non target exchange of psychical goods.
+
+We contribute to the field of anonymous fair-exchange and anonymous physical delivery with following improvements:
+With this paper we propose a protocol that add following contribution to the field of physical delivery, fair-exchange protocols:
+\begin{itemize}
+    \item Strong anonymity — unlike other protocols based on pseudoanonymous traceable blockchains like Bitcoin or Ethereum, we propose a solution based on private blockchain (ZCash) where transactions can not be analyzed and thus linked back to users' identity.
+    \item Practicality — out proposal is practical and ready to deploy
+\end{itemize}
+
+In this paper, we propose a protocol for provisioning local services, that guarantee following requirements:
+\begin{enumerate}
+    \item Anonymous — The customer identity is strongly untraceable (see section~\ref{anonimity-vs-pseudoanonimity}.
+    \item Fair-exchange — the service provider does not receive the payment before it provide the service, in case it provide wrong service, customer can proof this case to the justice.
+    \item Blockchain-based — the protocol does not use TTP, instead it uses decentralized blockchain network.
+    \item Timeliness — the transaction will terminate if it don't meet the timely requirerement
+\end{enumerate}
 
@@
 
-\section{Blockchains}
+\section{confidential Blockchains}
+
+\paragraph{Ethereum}
+
+\paragraph{Aleo}
+
+\paragraph{STARK-net}
+
 \paragraph{Monero}
@@
 \href{https://garethtdavies.medium.com/an-introduction-to-payment-disclosure-in-zcash-96748c209d49}
-
-\paragraph{Aleo}
 

### 2022-02-03 main.tex
update diagram
update paper

--- 2021-12-29 main.tex
@@
 \maketitle
+\keywords{data privacy, privacy preserving, blockchain, fair-exchange}
 
-\begin{abstract}
-Lorem ipsum\ldots
-\end{abstract}
-\keywords{data privacy, privacy preserving, zk-SNARK, blockchain}
+\section{Abstract}
+Service providers like: lawyers, laboratories, auditors, or banks, to provide services, require customers to submit data that is often associated with their personal information.
+This situation expose customers to privacy risk.
+However, most of the service providers use the personal information merely for logistic operations, and could provide services on anonymous data if other means of communication would be possible.
 
-\section{Problem statement}
+We propose a protocol for local confidential services provision, using blockchain for both contract agreement and anonymous payments.
+
+In case of dispute, we let the parties communicate over blockchain. In case of disagreement, the customer can disclose the whole interaction and proof to the justice misbehaving SP.
+
+We propose three applications for our protocol: (i) anonymous steroid examination, (ii) anonymous legal advice, and (iii) anonymous financial trustworthiness evaluation.
+
+\section{Introduction}
 Service providers (SP) like: lawyers, laboratories, auditors, or banks, to provide services, require data that is often associated with user identity.
@@
 Such user information can be then used deliberately or unintentionally (e.g, by theft) for: insider disclosure, unauthorized access, or commercial gains.
-For example, by reselling it to marketers, finantial institutions, other businesses, government agencies, or even cybercriminals.
-Which in turn can lead to profiled advertisements, or cryminal activities like identity theft or illegal tracking and surveillance~\cite{smith2011information}.
+For example, by reselling it to marketers, financial institutions, other businesses, government agencies, or even cybercriminals.
+Which in turn can lead to profiled advertisements, or criminal activities like identity theft or illegal tracking and surveillance~\cite{smith2011information}.
+
+Important individuals like top government, influencers, or celebrities are especially vulnerable to this kind of attacks as exposure of their health records, purchase habits, or legal documents can threaten their reputation, position, or can be used for blackmailing.
 
 The guarantee of the privacy of the data is based on a trust assumptions and security of IT systems.
-However, most of the service providers don't need the information of user identity for other reasons than payment, communication, or logistics.
+However, most of the service providers don't need the personal information for any other reasons than payment, communication, or logistics.
 
@@
 
-In this paper we propose a protocol for anonymous provision of services via blockchain and cryptography techniques. Specificaly, we use
-\begin{enumerate}
-    \item \textbf{confidential blockchain} to process payment for a service without revealing a user's identity.
-    \item \textbf{zero-knowledge proofs} — to proof the payment for the service without revealing the payment itself.
-    \item \textbf{encryption scheme and blockchain} — to asynchronously deliver the results of the made service back to the user.
-\end{enumerate}
+\subsection{Contribution}
+In this paper, we propose a blockchain based anonymity-preserving framework for local services provision.
 
 \section{State of the art}
+\subsection{Anonymity and Fair-Exchange in e-Commerce Protocol for Physical Products Delivery}
 
-Verifiable Document Redacting ~\cite{chabanne2017verifiable} is a protocol for erasing confidential information from authenticated images in verifiable manner.
-In other words, the protocol allows verifying that only the fields that cover personal information has been blacked out from the authenticated image.
-This allows users to provide required images without exposing their personal information, and SPs to authenticate the modified images, such that they are sure that only the stated fields have been blacked out and nothing else was touched.
-% In this paper we extend the idea to a whole user-to-service-provider protocol
+Authors of ~\cite{birjoveanu2015anonymity} proposed a fair-exchange of physical product and electronic payment protocol that guarantee both customer and merchant anonymity.
+They achieve it by introducing online trusted third party that validate coins and provide fair exchange guarantees.
 
-Authors of the paper~\cite{lin2021efficient} propose a system for Privacy-Preserving Credit Score System.
-Letting banks to calculate creditworthness without learning user private information like registration, hobbies, credit, relationships, and inquiry.
-To achieve this they use Paillier encryption and noninteractive zero-Knowledge schemes (NIZK).
+The anonymity is ensured by assuming the existence of source cabinet (SC) and delivery cabinet (DC), and a trusted delivery agent who take product from a source cabinet and provide it to a destination cabinet.
+Both cabinets provides access to the product by passwords to conceal identity of the customer and the merchant.
+To avoid identity disclosure of customer and merchant, the access to the product is provided by passwords.
 
-\section{Coverage}
+Both cabinets are equipment with cameras. Also there should exist the trusted delivery agent (DA) who will deliver items from source cabinet do delivery cabinet.
 
-Non invasive tests — those which patients can sample themselves: 
+The protocol works as follows:
+\begingroup
+\renewcommand{\labelenumii}{\arabic{enumii}.}
 \begin{enumerate}
-    \item Urine tests
-    \item Stool tests
-    \item Saliva tests
+\item Both parties agree on the purchase details.
+\item The customer buys a digital coin from his bank and validates it with the TTP.
+\item The customer sends to the merchant the purchase order and the digital signature made by TTP on the encrypted coin.
+\item The merchant post the product to the source cabinet.
+\item Delivery agent collect the product from source cabinet and post it to delivery cabinet.
+\item Customer collects the product from delivery cabinet using password.
+\item The customer checks if the product is actually the ordered one.
+\begin{itemize}
+\item[-] if yes
+\begin{enumerate}
+\setcounter{enumii}{7}
+\item the customer sends the acknowledge to delivery cabinet and decryption key to the merchant.
+\item The merchant redeem the coins from the bank.
 \end{enumerate}
+\item[-] if no
+\begin{enumerate}
+\setcounter{enumii}{7}
+\item the delivery cabinet is equipment with video camera that records the moment when the customer open the package and let the customer to signal the invalidity of the product, and so, sending the encrypted recording to the TTP.
+\item the dispute is settled via TTP, optionally letting each party to reveal it's identity.
+\end{enumerate}
+\end{itemize}
+\end{enumerate}
+\endgroup
 
-\section{Solution}
+Yet, the fair-exchange properties are achieved by strong assumptions. Namely,
+\begin{itemize}
+\item the TTP does not misbehave or collude with any party.
+\item The customer's and merchant's banks enable confidental transactions and both share commit-buffer where the value is locked until the transaction is finished.
+\item All banks mantain a global list of coin's serial numbers to prevent double-spending problem.
+\item The source cabinet and delivery cabinet exists, and in both the product access is protected by password.
+\item Delivery cabinet is equppted with a video camera that records the moment when the customer opens the package, and provide a way to submit the video to TTP in case of a dispute.
+\item Delivery agent exist and is trusted.
+\item Communication channels between parties provides anonymity.
+\end{itemize}
 
-\begin{figure}[htbp]
-\centerline{\includegraphics[width=\linewidth]{sequence-flow.png}}
-\caption{Sequence flow}
-\label{fig:sequence-flow}
-\end{figure}
+\subsection{Lelantos - A blockchain-based anonymous physical delivery system}
 
-\section{Blockchains}
-\paragraph{Monero}
-Monero offers out-of-the-box proving/checking confidental transactions. \href{https://www.getmonero.org/resources/user-guides/prove-payment.html}
+Lelanros~\cite{altawy2017lelantos} is a blockchain-based anonymous physical delivery system.
+The anonymity is achieved by employing ToR's onion routing to connect physical delivery providers.
+The whole route from merchant to customer is split into multiple steps, and each step is undertaken by different randomly selected delivery provider.
+As long as the develiery providers does no collude, mechant can not learn both identity and destination address of the customer.
 
-\paragraph{ZCash}
-ZCash offers payment disclosure as a preview feature.
-\href{https://garethtdavies.medium.com/an-introduction-to-payment-disclosure-in-zcash-96748c209d49}
+Onchain smart-contract is used to coordinate the whole process and mediate communication between customer and delivery providers.
 
-\href{https://garethtdavies.medium.com/an-introduction-to-payment-disclosure-in-zcash-96748c209d49}
+However, the system achieve only pseudo-anonymity or 'weak anonymity'.
+
+\subsection{Themis - Towards Decentralized Escrow of Cryptocurrencies without Trusted Third Parties}
+
+Themis~\cite{meng2019themis} is a fair-exchange protocol, which uses blockchain instead of TTP. It provide escrow services for secure exchanging between cryptocurrencies and digital goods.
+
+Authors highlight that a widely-used atomic exchange mechanism HTLC (Hashed Time-lock Contract) is vulnerable to denial of service (DoS) attacks.
+While Multi-Signature Schemes depends on the Trusted Third Party (TTP) making them vulnerable to collusion attacks.
+Such TTP can collude with one party and take the locked funds.
+It can also refuse settling disputes and lock the hosted funds.
+
+Themis is a decentralized system that provides an escrow and dispute resolution. It claims to satisfy following requirements:
+\begin{description}
+    \item[Fairness] Either both seller and buyer obtain all the goods, or they both obtain nothing.
+    \item[Security] The funds are locked until the transaction is completed.
+    \item[Passivity] If no dispute arise, the third-party does not need to involve in the transaction.
+    \item[Correctness] Transactions and disputes are executed according to a priori agreed protocol rules.
+    \item[Dependability] There is no single point of failure vulnerable to DoS attack.
+    \item[Privacy] If the dispute does not arise, the third-party does not know if the transaction completes. If the dispute arises, only the related parties are aware of it.    
+\end{description}
+
+Two parties, say Alice and Bob, can create an escrow by generating 2-of-2 (not 2-of-3 as it is other TTP-based systems) threshold account using Thresh-Key-Gen protocol.
+Alice and Bob generate secret keys $x_A$ and $x_B$ accordingly, the shared account public key becomes $y = g^{x_A+x_B}$; only the access to both Alice's and Bob's secrets grants access to the shared account.
+
+Then, both Alice and Bob, takes their keys, and split them into $n=2t+1$ secret shares using Shamir Secret Shamir protocol, where $n$ is the number of mediators that participate in the decentralized network, and $t+1$ becomes the threshold of sufficient number of mediators that can reconstruct the secret key.
+
+Next, both Alice and Bob, take their key shares, and encrypt each $i$-th key share using public key of $i$-th mediator.
+As a result Alice's secret $x_A$ becomes ${c^A_1, c^A_2,...,c^A_n}$, and Bob's secret $x_B$ becomes ${c^B_1, c^B_2,...,c^B_n}$, where $c_i = E_{M_i}(P_i)$ is the encrypted $i$-th key share using $i$-th mediator public key $M_i$.
+
+Next, both Alice and Bob exchange the sets of encrypted key shares with each other. And send funds to the escrow account.
+
+The escrow is secure as long as $t+1$ of mediators does not collude, which would let them recreate both $x_A$ and $x_B$.
+Also, to ensure that parties are exchanging real key shares, they also send a witnesses generated with Feldman VSS scheme and zero-knowledge proofs to guarantee the consistency between witnesses and key shares.
+
+In case of dispute, the decentralized network of mediators settle the conflict and grand one winning party, the other party secret key, letting him to withdraw the funds.
+
+The honesty of mediators is achieved by the monetary incentivization and reputation system.
+
+\subsection{Background}
+\subsection{Dispute resolution system}
+
+[[Themis - Towards Decentralized Escrow of Cryptocurrencies without Trusted Third Parties]] proposed a semi-autonomous decentralised dispute resolution system, which comply with the web3 postulates of decentralised web.
+Themis resolve disputes by set of voluntary anonymous users participating in a voting and deciding which party misbehaved.
+
+Such dispute resolution system might work for straightforward money exchanges.
+However it's hard to realise such decentralised evaluation of quality of heath or legal services when expertise and privacy concerns are taken into an account.
+Therefore, in this protocol we take the more practical approach and resolve disputes using local justice system.
+
+Possible directions toward semi-autonomous decentralised resolution system are discussed in [[anonser/Future Work]].
+
+Unless such expertise service evaluation is possible the evaluation have to be in justice.
+
+\subsection{There is really no need to create an escrow}
+One could assume that the escrow mechanism would make the whole protocol more fair, because the SP would not receive the money until it doesn't provide the services.
+But, in scenario without TTP its the SP who decide if service is provided or not.
+In other words, SP can finish the protocol at any time, sending some arbitrary data and claim that he finished providing the services.
+We could make the customer decide if the service is provided or not, but then the customer could receive the services and lie that he didn't.
+And since the customer is anonymous, there would be no means to open the dispute.
+
+\subsection{Proof to justice}
+In case of dispute customer can proof to the justice (police, court, etc.) evidences that convinces justice about the honesty of customer and misbehaviour of SP.
+Abstracting from the services the SP is providing.
+Customer should be able to proof that: (I) he delivered complete $pkg$ and POD proofs that; (ii) he paid for the transaction $tx$ and payment disclosure proofs that.
+In case the customer is laying, and the SP has indeed delivered the results in time, he can proof: that the results had been published on time and Proof-of-Provision proofs that;
+
+# Proof-of-Delivery
+
+# Payment disclosure
+
+Private cryptocurrencies can hide
+
+# Proof-of-Provision
+Blockchain is global block that time stamps everything that gets to the block.
+Therefore by publishing results on a blockchain, everyone is convinced that the service have been indeed provisioned on time, because the results have been available since the publication of that block.
+
+\subsection{Pseudo-anonymous vs anonymous blockchain}
+
+\subsection{Payment for services}
+Transactions between customers and SP have to be somehow pegged in order to prevent proving one payment for multiple transactions.
+In other words, we need some way to uniquely link particular payment with the transaction it pays for.
+
+Depending for the cryptocurrency the link can be created in different ways. 
+- separate address - each transaction derives new address uniquely associating it with the transaction. Such addresses can be derived using BEP-32 standard. 
+- memo - the payments are send to one SP account, but contain extra field named "memo" which contains a random value generated by SP and included in POD.
+Each payment containing such value in memo is considered to pay for the transaction in question.
+in case of dispute, the connection can be disclosed by revealing the value in POD and  payment's memo.
+
+Both approaches have some advantages and shortcomings, but our protocol can abstract them away by treating them as come unique number called "invoice".
+How it's implemented  depends on the payment blockchain.
+
+\subsection{Message Board}
+Blockchain as a Message Board — proof-of-existence.
+
+\subsection{We could use one blockchain}
+Instead of using two blockchains, one for anonymous payments and one for message board, we could use one blockchain that supports both.
+
+Ufortunately at the time of writing. Monero does not support message board functionallity. Zcash transaction disclosure is experimental feature.
+
+\section{The framework}
+
+\subsection{Overview of the framework}
+\subsubsection{Why we need to first give the items to the merchant then pay}
+
+If we pay first, then mechant can refuse to accept our package, and refuse to give us the Proof-of-Delivery acknowledge.
+In such a case, we are left with proof of payment that we can't really do much about it.
+
+We have to first, go to merchant, give it package with sample, they give us the proof-of-delivery with some random secret, acting like a invoice.
+
+Proof-of-Delivery is something we can use to proof to the justice that we have.
+
+To prove the payment for that invoice, we have to send a message to the mechant with the memo value of the secret. Pegging these two values.
+
+\subsubsection{There is a need to create proof of delivery}
+
+Without the proof of delivery, the customer get's left with just proof of payment, but he has no proof that he indeed brought the sample and other stuff to the merchant.
+
+Merchant has to give the customer either on blockchain or via other means that he accepted the package.
+
+\subsection{Notation}
+\begin{itemize}
+    \item $\mathrm{SP}$ - Service Provider.
+    \item $\mathrm{customer}$ - Customer.
+    \item $\mathrm{pkg}$ - package anonymously delivered by customer to SP. pkg = (materials, )
+    \item $\mathrm{materials}$ - materials used by SP to provide services, can be of any kind: urine, saliva, blood, stool, or health documents, legal documents etc.
+    \item $\mathrm{results}$ - results in binary format, can be either PDF, docx or any format agreed by both parities. 
+    \item $\mathrm{examination}(\mathrm{materials}) : \mathrm{results}$ - actual service provision executed on materials provided by customer and producing results
+    \item $\mathrm{POD}$ - Proof-of-Delivery, a confirmation issued by SP to the customer.
+The POD encompasses delivery time and an address to send funds to.
+POD is signed by SP to guarantee non-...
+.
+POD can be used as a evidence in case of dispute.
+    \item $\mathrm{POP}$ - Proof-of-Provision, an logical proof of the existence of provision results.
+    \item $\mathrm{E}_\mathrm{key}(\cdot)$, $\mathrm{D}_\mathrm{key}(\cdot)$ - symmetric encryption and decryption operators.
+    \item $\mathrm{S}_\mathrm{key}(\cdot)$, $\mathrm{V}_\mathrm{key}(\cdot)$ - digital sign and verify operators.
+    \item $\mathrm{sk}$, $\mathrm{pk}$ - Key pair of secret and public keys accordingly.
+    \item $\mathrm{DH}(\cdot, \cdot)$ - Diffie–Hellman key exchange.
+    \item $CID$ - Content Identifier, a label used to address content in IPFS.
+\end{itemize}
+
+\subsection{Prerequisites}
+Blockchain:
+- Anonymous payments.
+- Invoice mechanism as described in [[Payment for services]].
+- Transaction disclosure as described in [[Proof to justice]].
+
+\subsection{Assumptions}
+Our protocol rely on some assumptions:
+1. SPs accept packages from unknown customers and give them back confirmation of acceptance (to stick with convention we call it Proof-of-Delivery).
+2. SPs accept payment for services via anonymous cryptocurrencies like Monero, Grin or ZCash. 
+3. Justice accepts as a evidence in dispute proof of payment of cryptocurrencies.
+
+\subsection{The protocol}
+\subsubsection{Messages}
+\paragraph{Proof-of-Delivery}
+
+$\mathrm{POD} = (issued-at, pay-invoice-time-limit, provide-results-time-limit, invoice-nonce, signature)$
+
+where:
+\begin{itemize}
+    \item $issued-at$ - time at which the POD is issued
+    \item $pay-invoice-time-limit$ - time limit to pay the invoice 
+    \item $provide-results-time-limit$ - time limit to provide the service results
+    \item $\mathrm{nonce}$ - randomly generated number uniquely identifying the transaction.
+    \item $signature$ - signature proving authenticity of the SP
+\end{itemize}
+moreover
+
+$issued-at < pay-invoice-time-limit < provide-results-time-limit$
+
+\paragraph{Proof-of-Provision}
+$\mathrm{POP} = (\mathrm{cid}, \mathrm{nonce}, signature)$
+
+where:
+\begin{itemize}
+    \item $\mathrm{cid}$ - content identifier.
+    \item $\mathrm{nonce}$ - randomly generated number uniquely identifying the transaction.
+\end{itemize}
+
+\subsubsection{Step 1: deliver package}
+
+They protocol start once the customer delivers package $\mathrm{pkg}$ to SP.
+
+In return, the SP issue an Proof-of-Delivery (POD) confirmation. The confirmation encompasses timestamp, invoice (see section [[Payment for services]]), and signature.
+
+Symbolically:
+$$
+\mathrm{delivery}(\mathrm{pkg}) : \mathrm{POD}
+$$
+
+\subsubsection{Step 2: pay for invoice}
+Having POD, SP can not reject receiving the package. At this point the customer should pay for the invoice according to selected cryptocurrency system (see section [[Payment for services]]).
+
+In return, the customer receives the proof of payment that should be used in case of a dispute.
+
+Symbolically:
+$$
+\mathrm{payment}(\mathrm{POD}.\mathrm{nonce}) : \mathrm{POP}
+$$
+
+\subsubsection{Step 3: provision of service}
+At this point the SP can start the provision of service. If it's suspicious it may decide to wait until the invoice is paid, otherwise start immediately.
+
+Symbolically:
+$$
+\mathrm{examination}(\mathrm{pkg}.\mathrm{materials}) : \mathrm{results}
+$$
+
+\subsubsection{Step 4: publication of results}
+Once the service is finished, some kind of output should be created.
+The output should be encrypted using symmetric key derived using Diffie–Hellman key exchange between customer's public key and SP's secret key, and later decrypted using customer's secret key and SP's public key.
+
+The encrypted results can be then published on content network such as IPFS. As a result, the content identifier (CID) is returned.
+
+Symbolically:
+$$\mathrm{key} = \mathrm{DH}(\mathrm{pkg}.\mathrm{pk}, \mathrm{SP}.\mathrm{sk})$$
+$$\mathrm{cid} = \mathrm{publish}(E_\mathrm{key}(\mathrm{results}))$$
+
+\subsubsection{Step 5: publication of proof-of-provision}
+Now, when the results are published on content addressable network such as IPFS, the SP publish $\mathrm{cid}$ obtained in previous step on a message board doing proof of provision.
+
+Symbolically:
+$$\mathrm{publish}(\mathrm{cid})$$
+
+\subsubsection{Step 6: observe proof-of-provision}
+
+Since the delivery and payment was made the customer observes blockchain for a POP corresponding to his transaction. When it happen,
+
+\subsubsection{Step 7: fetch the results}
+
+\section{Security analysis}
+\subsection{Fairness analysis}
+\subsubsection{Model}
+We consider three positions:
+\begin{itemize}
+    \item Disadvantage (-) position if a party has put any effort or paid money without being able to reclaim it. In other words it has to **risk** its resources.
+    \item Advantage(+) position is when a party would benefit if the transaction would halt at that point. For example, received payment in advance.
+    \item Neutral (•) is a neutral state where the party does not gain or lose anything significant. For example, beggining of the protocol.
+\end{itemize}
+
+We assume that if the protocol goes well each party ends in advantage position. Hence the incentive to accept transactions.
+
+And two dimensions:
+\begin{itemize}
+    \item Normal, in this dimension the parties acts honestly or 
+    \item Dispute, in this dimension one party starts a dispute in justice and according to the local law gets into one of three positions.
+\end{itemize}
+
+% - Disputable (!) position is when a party can proof to the justice the misbehaviour of the other party and (according to the local law) win the dispute.
+
+Motivation:
+At least one party should be motivated either via reward or punishment to move the protocol forward.
+
+The protocol is fair, if at any point of the protocol, each party is either in Disputable or Advantage position. Moreover, at least one party has the motivation and means to move the protocol forward.
+
+\subsubsection{Steps}
+We assume the steps of the protocol to be atomic, there are no intermediate steps, nor the party can revert any step. In other words, it can only move forward.
+
+\subsubsection{Step 1: deliver package}
+    Customer has delivered the package:
+- Following protocol:
+	- Customer has risked its materials but has not paid anything, so we assume he is in neutral position (•).
+One would argue that the customer has put effort of delivering the sample to the merchant, or that the sample is valuable.
+We assume that the sample without personal information is useless and the effort to deliver the package is negligible small.
+	- SP is in neutral position as he didn't put any effort be receiving the package, also the package hasn't any value to the SP (•).
+- Starting a dispute:
+	- The customer lose the case as the SP has still opportunity to publish proof-of-provision within timeframe (-).
+	- The SP win the case for the same reason (•).
+
+Motivation:
+At this point the customer has the motivation to push the protocol forward as he want to receive the service results.
+
+\subsubsection{Step 2: pay for invoice}
+Customer has paid the invoice:
+- Following protocol:
+	- The customer has spend his funds but hasn't received the results. Therefore, he moves to the disadvantage position (-).
+	- The SP has received the payment but hasn't spend his resources yet. Therefore, he moves to advantage position (+).
+- Starting a dispute:
+	- The customer lose the case as the SP has still opportunity to publish proof-of-provision within timeframe (-)
+	- The SP win the case for the same reason (+)
+
+Customer has timeouted $time-to-issue-$, then:
+- Following protocol:
+	- The customer ends up in neutral position, since he didn't spend his funds (•)
+	- The SP ends up in neutral position as he didn't receive the payment, nor spent his resources (•)
+- Starting a dispute:
+	- The customer loses the case as he can not prove the payment before the time limit. Consequently, ends up in disadvantage position (-)
+	- The SP is not charged to the justice due to lack of proofs. Therefore, he ends up in neutral position (-)
+
+Motivation:
+The merchant has the motivation to move the protocol forward, as he don't want to lose the case and get punished.
+
+\subsubsection{Step 3: provision of service}
+
+SP has done the provision of service:
+- Following protocol:
+	- The customer hasn't received the results. Therefore, he remains in disadvantage position (-).
+	- The SP has fullfiled the contract on time (+).
+- Starting a dispute:
+	- The customer lose the case as the SP has still opportunity to publish proof-of-provision within timeframe (-)
+	- The SP win the case for the same reason (+)
+
+SP has timeouted, then:
+- Following protocol:
+	- The customer ends up in disadvantage position (-)
+	- The SP ends up in advantage position as he received the payment (+)
+- Starting a dispute:
+	- The customer wins the case and end up in neutral position (•)
+	- The SP loses the case and end up in disadvantage position (-)
+
+Motivation:
+The SP has the motivation to move the protocol forward, as he don't want to lose the case and get punished.
+
+\subsubsection{Step 4: publication of results}
+
+SP has published results on time:
+- Following protocol:
+	- The customer hasn't received the results. Therefore, he remains in disadvantage position (-).
+	- The SP has fullfiled the contract on time (+).
+- Starting a dispute:
+	- The customer lose the case as the SP has still opportunity to publish proof-of-provision within timeframe (-)
+	- The SP win the case for the same reason (+)
+
+SP has timeouted, then:
+- Following protocol:
+	- The customer ends up in disadvantage position (-)
+	- The SP ends up in advantage position as he received the payment (+)
+- Starting a dispute:
+	- The customer wins the case and end up in neutral position (•)
+	- The SP loses the case and end up in disadvantage position (-)
+
+Motivation:
+The SP has the motivation to move the protocol forward, as he does not want to timeout and expose to losing case.
+
+\subsubsection{Step 5: publication of proof-of-provision}
+
+SP has published proof-of-provision on time:
+- Following protocol:
+	- The customer hasn't received the results. Therefore, he remains in disadvantage position (-).
+	- The SP has fullfiled the contract on time (+).
+- Starting a dispute:
+	- The customer lose the case as the SP can prove the publication of proof-of-provision (-)
+	- The SP win the case as the SP can prove the publication of proof-of-provision (+)
+
+SP has timeouted, then:
+- Following protocol:
+	- The customer ends up in disadvantage position (-)
+	- The SP ends up in advantage position as he received the payment (+)
+- Starting a dispute:
+	- The customer wins the case and end up in neutral position (•)
+	- The SP loses the case and end up in disadvantage position (-)
+
+Motivation:
+The customer wants to receive the results, therefore he move the protocol forward.
+
+\subsubsection{Step 6: retreival of proof-of-provision}
+
+SP has published results on time, then:
+- Follows the protocol:
+	- The customer gets hash of the results but not the results. Therefore, he is still in disadvantage position(-).
+	- The SP position hasn't changed(+).
+- Starts a dispute:
+	- The customer lose the case as the SP can prove the publication of proof-of-provision (-)
+	- The SP win the case as the SP can prove the publication of proof-of-provision (+)
+
+Customer has timeouted, then:
+- Follows the protocol:
+	- The customer ends up in disadvantage position (-)
+	- The SP ends up in advantage position as he received the payment but didn't spend his resources (+)
+- Starts a dispute:
+	- The customer wins the case and end up in neutral position (•)
+	- The SP loses the case and end up in disadvantage position (-)
+
+Motivation:
+The customer wants to receive the results, therefore he move to the protocol forward.
+
+\subsubsection{Step 7: retrieval of results}
+
+SP has published **correct** results on time:
+- Following protocol:
+	- The customer gets the correct results. Therefore, he moves to advantage position (+).
+	- The SP position hasn't changed(+).
+- Starting a dispute:
+	- The customer lose the case as the SP can prove the publication of proof-of-provision (-)
+	- The SP win the case as the SP can prove the publication of proof-of-provision (+)
+
+SP has published **incorrect** results on time:
+- Following protocol:
+	- The customer end up in disadvantage position, as he ends up with incorrect results (-)
+	- The SP ends up in advantage position as he received the payment but didn't spend his resources (+)
+- Starting a dispute:
+	- The customer wins the case and ends up in neutral position (•)
+	- The SP lose the case and end up in disadvantage position (-)
+
+Motivation:
+At this point no party has the motivation to start the case, since everyone  .
+
+See how monero swaps analysis fairness and motivations.
+
+\subsection{Privacy and anonymity analysis}
+
+# Model
+The data can be either:
+- Public(+), 
+- Private(-)
+
+- Plaintext (...)
+- Encrypted (...)
+
+We analisis at each step of the protocol
 
@@
 
+\subsection{Anonymous physical delivery e-commerce}
+% TODO write about
+~\cite{birjoveanu2015anonymity}
+
+\section{Future work}
+
+\subsection{Justice}
+Justice is the one biggest obstacle in achieving system that is complied with web3 manifests.
+
+The possible directions for mitigation of such issue are to either (1) replace Justice with decentralised autonomous organisations (DAO) like proposed in [[Themis - Towards Decentralized Escrow of Cryptocurrencies without Trusted Third Parties]]; or (2) make it impossible to provide incorrect results.
+
+The first approach is more feasible in the near future.
+It would require creating large pool of experts in a field, that in case of dispute, would receive all the proofs (POD, POP, POP, as well as any other proofs significant to the case) that could be queried by the experts in zero-knowledge fashion, i.e., they could ask limited number of questions to the proofs and getting yes/no answers.
+Keeping the case fully confidential.
+The experts would be incentivised to participate in the pool by the system of fees.
+Their honest behaviour would be incentivised by the stake they would have to lock, and punishment they would get by judging incorrectly, where the "correctly" is determined by the quorum of votes.
+
+The second approach is more philosophical and visionary.
+Suppose that the service we are undertaking is fully computable.
+Then, it would be possible by employing proofs of correctness of computations (cite snarks) to enforce that only correct computations (hence correct services) are accepted.
+But to do so the whole service examination would have to be computable, which is hard to achieve in settings where physical materials (like urine) are examined.
+Concretely, the problem canes down to "How to digitally represent urine".
+If we could represent urine, blood, saliva, or any other physical material in binary format, and let the customer to take a sample, discrete it and send it to the SP by himself.
+Then the whole chain of integrity could be ensured.
+Therefore, wrong service provision would be impossible, or — using cryptographic nomenclature — infeasible.
+
+\subsection{Paying with cash}
+Without lose of generality the payment can be made with cash. 
+The customer can exchange the cash with SP together with delivering the package pkg.
+The POD would contain an information that the transaction has been paid with cash; therefore, [[The protocol#Phase 2 pay for invoice]] could be ommited.
+
+%%# Verifable documents
+
+Verifiable Document Redacting ~\cite{chabanne2017verifiable} is a protocol for erasing confidential information from authenticated images in verifiable manner.
+In other words, the protocol allows verifying that only the fields that cover personal information has been blacked out from the authenticated image.
+This allows users to provide required images without exposing their personal information, and SPs to authenticate the modified images, such that they are sure that only the stated fields have been blacked out and nothing else was touched.
+
+If such Verifiable Redacted Documents were accepted by other service providers like bank or tax office, national register of the judiciary, then the SP could use the documents provided by the customer to provide wider range of services, without knowing identity of the customer.%%
+
+\subsection{Conclusions}
+In this paper, we have proposed a privacy- and anonymity- preserving blockchain-based framework for local services provision.
+The framework can be employed by any local service provider to provide services without collecting any personal information.
+The payment is handled by anonymous cryptocurrencies, and the results are published on content based p2p network.
+The dispute can be settled by disclosing proofs to the justice.
+At any stage of the transaction, both parties are either in privelaged situation or can proof to the justice the misbehaviour of the other party.
+
 \bibliographystyle{alpha}

### 2022-02-07 main.tex
update paper

@@
 This situation expose customers to privacy risk.
-However, most of the service providers use the personal information merely for logistic operations, and could provide services on anonymous data if other means of communication would be possible.
+However, most of the service providers use the personal information merely for logistic operations like payments and communication, and could provide services anonymously if other means of logistics would exists.
 
-We propose a protocol for local confidential services provision, using blockchain for both contract agreement and anonymous payments.
+We propose a framework for coordingating local anonymous service provision.
+Our proposal uses blockchain for both anonymous payments and proof-of-existence, and content addressable network (IPFS) for results delivery.
 
-In case of dispute, we let the parties communicate over blockchain. In case of disagreement, the customer can disclose the whole interaction and proof to the justice misbehaving SP.
+In case of dispute, either due to exceeding deadlines or providing incorrect results, the customer can disclose the whole interaction and proof to the justice (police or court) the misbehaviour of the SP.
+
+We analyse the protocol in the context of fairness, privacy, and anonymity.
 
 We propose three applications for our protocol: (i) anonymous steroid examination, (ii) anonymous legal advice, and (iii) anonymous financial trustworthiness evaluation.
+
+We contribute to the field of fair-exchanges by proposing a simple and practical framework that does not rely on centralized trusted-third party, rather on decentralized blockchain and decentralized content addressable networking.
+Also, we support physical materials delivery, which was rarely targeted by other researchers.
 
@@
 
-The guarantee of the privacy of the data is based on a trust assumptions and security of IT systems.
-However, most of the service providers don't need the personal information for any other reasons than payment, communication, or logistics.
+The guarantee of the privacy of the data is often based merely on a trust assumptions and security of IT system.
+However, most of the SP don't need the personal information for any other reasons than payment, or communication, which should be considered secondary compared to primary matter that is service provision.
 
@@
 \subsection{Contribution}
-In this paper, we propose a blockchain based anonymity-preserving framework for local services provision.
+We contribute to the field of fair-exchanges by proposing a simple and practical framework that does not rely on centralized trusted-third party, rather on decentralized blockchain and distributed content addressable networking.
+Also, we support physical materials delivery, which was rarely targeted by other researchers.
 
@@
 \subsubsection{Messages}
+
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=\textwidth]{diagram.png}
+    \caption{Diagram}
+    \label{fig:diagram}
+\end{figure}
+
 \paragraph{Proof-of-Delivery}
-
 $\mathrm{POD} = (issued-at, pay-invoice-time-limit, provide-results-time-limit, invoice-nonce, signature)$
@@
 \begin{itemize}
+\item Neutral (•) position is when a party does not gain or lose anything significant. For example, beggining of the protocol.
 \item Disadvantage (-) position if a party has put any effort or paid money without being able to reclaim it. In other words it has to **risk** its resources.
 \item Advantage(+) position is when a party would benefit if the transaction would halt at that point. For example, received payment in advance.
-    \item Neutral (•) is a neutral state where the party does not gain or lose anything significant. For example, beggining of the protocol.
 \end{itemize}
 
-We assume that if the protocol goes well each party ends in advantage position. Hence the incentive to accept transactions.
+$$\sigma = \{-, •, +\}$$
 
-And two dimensions:
+We call one position *better* than the other if it's more preferable or more advantageous for the party.
+Then, we say that neutral position (•) *is better* than disadvantage position (-), and advantage position (+) is better than neutral position (•).
+The relation is transitive so advantage position (+) is better than disadvantage position (-).
+Formally:
+$$
+\mathrm{is\ better} = \{(-,•), (•,+), (-,+)\}
+$$
+
+There are many actions that each party can take, but we group them together into two categories: 
 \begin{itemize}
-    \item Normal, in this dimension the parties acts honestly or 
-    \item Dispute, in this dimension one party starts a dispute in justice and according to the local law gets into one of three positions.
+    \item Following the protocol — taking the action prescribed by the protocol.
+    \item Not following the protocol — everything that deviates from designed steps of the protocol. For example, sending arbitrary message, skipping some step, repeating step, timing out. 
 \end{itemize}
 
-% - Disputable (!) position is when a party can proof to the justice the misbehaviour of the other party and (according to the local law) win the dispute.
+Moreover, at any step of the protocol the customer can react with two reactions: 
+\begin{itemize}
+    \item Agree — the customer agree with the action and therefore does not start a dispute.
+    \item Start a dispute — the customer does not agree with the action and therefore start a dispute.
+\end{itemize}
+
+Hence, in our analysis we have to consider four different outcomes for each party of the protocol:
+- $\sigma_\mathrm{n}$ — after following the protocol within the timeframe.
+- $\sigma_\mathrm{d}$ — after a dispute where the other party hasn't broken the protocol.
+- $\sigma_\overline{n}$ — after not starting a dispute despite the other party has broken the protocol.
+- $\sigma_\overline{d}$ — after a dispute where the other party has broken the protocol.
+
+After starting a dispute, the protocol terminate. After timing out there is no going back on the normal path.
+
+In our framework, the only party that can start a dispute is the customer. It's because the customer is anonymous, and so the SP does not have any personal information to start a dispute against.
+
+To mitigate this issue, the protocol is designed so that the SP who follows the protocol is always in advantage position, therefore he has no incentivisations to start a dispute.
+
+We say that the protocol achieve fairness if:
+
+$$\forall_{party \in parties}\forall_{\mathrm{step} \in \mathrm{steps}} \mathrm{can\ move\ the\ protocol\ forward\ to\ the\ non-disadvantage\ position}$$
+
+\subsubsection{Assumptions}
+For the analysis purpose we state assumptions listed below. We consider them being rational and realistic.
+
+Assumptions:
+\begin{itemize}
+
+\item Both parties start from neutral position (•).
+\item Both parties, by completing the transaction, end up in advantage positions (+).
+The transaction produces win-win scenario.
+In other words, they have intrinsic motivation to pursue in the transaction.
+\item We assume the steps of the protocol to be atomic, there are no intermediate steps.
+\item Repeating the first step starts new transaction.
+Repeating any other step is considered abnormal and gets ignored.
+For example paying for the invoice twice does not cause any effect on the curse of protocol.
+\item The protocol can go only forward, there is no way of revert any action.
+\item Losing the dispute leads to punishment that is greater than any reward therefore always leads to disadvantage position. Hence, the rational customer won't start a dispute that he will lose.
+\item Winning the dispute leads to neutral position (•)
+\item Both the customer and the SP are rational (selfish).
+They always prefer go from worst position to better position, but also risk temporary worst position in favour for later better position iff it's assured that they won't stuck in worst position.
+\end{itemize}
 
 Motivation:
-At least one party should be motivated either via reward or punishment to move the protocol forward.
+At least one party should be motivated either via reward (better possition) or punishment (worst position) to move the protocol forward.
 
 The protocol is fair, if at any point of the protocol, each party is either in Disputable or Advantage position. Moreover, at least one party has the motivation and means to move the protocol forward.
+
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=\textwidth]{table-of-positions.png}
+    \caption{positions}
+    \label{fig:my_label}
+\end{figure}
 
@@
 \subsubsection{Step 1: deliver package}
+Turn: Customer
+
 Customer has delivered the package:
-- Following protocol:
-	- Customer has risked its materials but has not paid anything, so we assume he is in neutral position (•).
-One would argue that the customer has put effort of delivering the sample to the merchant, or that the sample is valuable.
-We assume that the sample without personal information is useless and the effort to deliver the package is negligible small.
-	- SP is in neutral position as he didn't put any effort be receiving the package, also the package hasn't any value to the SP (•).
+- Agreeable path:
+	- $\sigma_{1, c, \mathrm{n}} = •$ - the customer has risked its materials but has not paid anything, so we assume he is in neutral position (•).
+One would argue that the customer has put effort of delivering the materials to the merchant, or that the sample is valuable.
+We assume that the sample without personal information is useless and the effort to deliver the package is negligible.
+	- $\sigma_{1, s, \mathrm{n}} = •$ - the SP is in neutral position as he didn't put any effort to rece the package, also the package hasn't any value to the SP (•).
 - Starting a dispute:
-	- The customer lose the case as the SP has still opportunity to publish proof-of-provision within timeframe (-).
-	- The SP win the case for the same reason (•).
+	- $\sigma_{1, c, \mathrm{d}} = -$ - the customer lose the case as the SP has still opportunity to publish proof-of-provision within timeframe (-).
+	- $\sigma_{1, s, \mathrm{d}} = •$ - the SP win the case for the same reason (•).
 
-Motivation:
-At this point the customer has the motivation to push the protocol forward as he want to receive the service results.
+Fairness:
+- The customer can follow the protocol and move to the non-disadvantage position $\sigma_{1, c, \mathrm{n}} = •$.
+- The SP can do nothing and end up in non-disadvantage position $\sigma_{1, s, \mathrm{n}} = •$ or $\sigma_{1, s, \mathrm{d}} = •$.
 
 \subsubsection{Step 2: pay for invoice}
+Turn: Customer
+
 Customer has paid the invoice:
-- Following protocol:
-	- The customer has spend his funds but hasn't received the results. Therefore, he moves to the disadvantage position (-).
-	- The SP has received the payment but hasn't spend his resources yet. Therefore, he moves to advantage position (+).
-- Starting a dispute:
-	- The customer lose the case as the SP has still opportunity to publish proof-of-provision within timeframe (-)
-	- The SP win the case for the same reason (+)
+\begin{itemize}
+    \item Following protocol:
+    \begin{itemize}
+	    \item $\sigma_{2, c, \mathrm{n}} = -$ the customer has spend his funds but hasn't received the results. Therefore, he moves to the disadvantage position (-).
+	    \item  $\sigma_{2, s, \mathrm{n}} = +$ the SP has received the payment but hasn't spend his resources yet. Therefore, he moves to advantage position (+).
+    \end{itemize}
+    \item Starting a dispute:
+    \begin{itemize}
+	\item $\sigma_{2, c, \mathrm{d}} = -$ the customer lose the case as the SP has still opportunity to publish proof-of-provision before the deadline (-)
+	\item $\sigma_{2, s, \mathrm{d}} = +$ the SP win the case for the same reason (+)
+	\end{itemize}
+\end{itemize}
 
@@
 - Following protocol:
-	- The customer ends up in neutral position, since he didn't spend his funds (•)
-	- The SP ends up in neutral position as he didn't receive the payment, nor spent his resources (•)
+	- $\sigma_{2, c, \overline{\mathrm{n}}} = •$ - the customer ends up in neutral position, since he didn't spend his funds (•)
+	- $\sigma_{2, s, \overline{\mathrm{n}}} = •$ - The SP ends up in neutral position as he didn't receive the payment, nor spent his resources (•)
 - Starting a dispute:
-	- The customer loses the case as he can not prove the payment before the time limit. Consequently, ends up in disadvantage position (-)
-	- The SP is not charged to the justice due to lack of proofs. Therefore, he ends up in neutral position (-)
+	- $\sigma_{2, c, \overline{\mathrm{d}}} = -$ - the customer loses the case as he can not prove the payment before the time limit. Consequently, ends up in disadvantage position (-)
+	- $\sigma_{2, s, \overline{\mathrm{d}}} = •$ - the SP is not charged to the justice due to lack of proofs. Therefore, he ends up in neutral position (•)
 
-Motivation:
-The merchant has the motivation to move the protocol forward, as he don't want to lose the case and get punished.
+Fairness:
+\begin{itemize}
+    \item The customer can move the protocol forward to the step 3, where if the SP follow the protocol then the customer can push the protocol forward up to the last termination step $\sigma_{7, c, \mathrm{n}} = +$, otherwise if at any step the SP does not follow the protocol the customer can start a dispute which terminates the protocol at non-disadvantage position, i.e., $\sigma_{3, c, \overline{\mathrm{d}}} = •$, $\sigma_{4, c, \overline{\mathrm{d}}} = •$, $\sigma_{5, c, \overline{\mathrm{d}}} = •$.
+    \item The SP can do nothing and end up in non-disadvantage position $\sigma_{2, s, \mathrm{n}} = +$, $\sigma_{2, s, \mathrm{d}} = +$, $\sigma_{2, s, \overline{\mathrm{n}}} = •$, $\sigma_{2, s, \overline{\mathrm{d}}} = •$.
+\end{itemize}
 
@@
 
+\subsubsection{Examples}
+
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=\textwidth]{misbehaving-path.png}
+    \caption{positions}
+    \label{fig:my_label}
+\end{figure}
+
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=\textwidth]{rational-path.png}
+    \caption{rational path}
+    \label{fig:my_label}
+\end{figure}
+
 Motivation:

### 2022-02-09 main.tex
docs: update

@@
 \subsection{Pseudo-anonymous vs anonymous blockchain}
+Privacy is a concept used in almost all kinds of social sciences like philosophy, psychology, sociology, and legal.
+The multidisciplinary nature leads to ambigous definitions.
+Therefore we do not attempt to pick any definion of privacy, rather build on more concrete concept that is anonymity.[[Information Privacy Research]]
+
+Anonymity is a the ability to hide one identity from others.
+More precisely, the unability to correlate actions performed within the sytem to the identity of the user.
+Or we can say, that the system guarantee anonimity if for all observers the actions are equally likely to be associated with any user of the system.
+However, anonimity is a spectrum rather than dichotomous classification.
+One method of quantifying level of anonymity is proposed in [[k-anonymity]].
+It measure the user's anonymity by the number of other users from whom the user can not be distinguished.
+Concreatly, the user is *k*-anonymous if his actions are equaly likely associated with *k*-1 other users.
+The larger *k*, the higher anonimity.
+The cryptocurrencies that natively support anonymous transactions are [[Monero]] (via [[Confidential Transactions]]) and [[ZCash]] (via [[zkSNARK]]s).
+There are also techniques that can be deployed on non-anonymous blockchains, they are so-called mixers [[Tornado Cash]], [[CoinJoin]], cite more..., that literaly gather together "anonimimity set" of users that collude together in order to launder the transactions, in such a way that to the outside observer the likelyhood of the sender of each transaction was equiprobable for any user from the anonimity set.
+
+Some systems guarantee pseudonomity rather than anonimity.
+Pseudonomity, allows uses to hide their real identity behind the pseudonim.
+Despite the whole system is transparent and allows linking actions to one identity, the system is considered anonymous as long as the link between pseudonym and real identity is secret.
+This assumption is hard to satisfy in practice, as the KYC (Know You Customer) and AML (Anti Money Laundering) regulations require users to reveal their real identity on most of the cryptocurrencies exchanges.
+This makes the anonymity of the user dependent on the security of the IT system.
+Moreover, some correlations can be infered merely by the analysis of transactions [[Evaluating user privacy in bitcoin]], [[Structure and anonymity of the bitcoin transaction graph]].
+Examples of pseudonomous blockchains are [[Bitcoin]] and [[Ethereum]].
 

### 2022-02-22 access.tex
update to new format

\documentclass{ieeeaccess}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{textcomp}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}
\history{Date of publication xxxx 00, 0000, date of current version xxxx 00, 0000.}
\doi{10.1109/ACCESS.2017.DOI}

\title{Anonymous provision of local services via blockchain}
\author{\uppercase{Stanis\l{}aw Bara{\'n}ski}\authorrefmark{1}}

\address[1]{Department of Electronic, Telecommunication and Informatics, Gdansk University of Technology, Narutowicza 11/12 Gdansk Poland (e-mail: stanislaw.baranski@pg.edu.pl}

\tfootnote{This paragraph of the first footnote will contain support 
information, including sponsor and financial support acknowledgment. For 
example, ``This work was supported in part by the U.S. Department of 
Commerce under Grant BS123456.''}

\markboth{Bara{\'n}ski : 
Anonymous provision of local services via blockchain}
{Bara{\'n}ski : 
Anonymous provision of local services via blockchain}

\corresp{Corresponding author: Stanislaw Baranski (e-mail: stanislaw.baranski@pg.edu.pl).}

\begin{abstract}
Service providers like: lawyers, laboratories, auditors, or banks, to
provide services, require customers to submit data that is often
associated with their personal information. This situation expose
customers to privacy risk. However, most of the service providers use
the personal information merely for logistic operations like payments
and communication, and could provide services anonymously if other means
of logistics would exists.

We propose a framework for coordingating local anonymous service
provision. Our proposal uses blockchain for both anonymous payments and
proofs of existence (so called Message Board), and content addressable
network (e.g.~IPFS) for results delivery.

The framework can be employed by any local service provider to provide
services without collecting any personal information. Possible
applications for this framework include anonymous clinical drug testing,
steroid testing, parenting testing, anonymous legal advices, or
anonymous financial trustworthiness evaluation.

In case of dispute, either due to exceeding deadlines or providing
incorrect results, the customer can disclose the whole interaction and
prove to the justice (police or court) the misbehaviour of the service
provider.

We analyse the protocol in the context of fairness, and discuss further
extensions to anonymous delivery system, payment with cash, and
decentralized conflict resolution system.

Our framework can potentially enable variety of services that for many
customers base on unacceptable trust assumptions to the SP.
\end{abstract}

\begin{keywords}
Blockchain, anonimity, fair-exchange, physical delivery
\end{keywords}

\titlepgskip=-15pt

\maketitle
\section{Introduction}
Service providers (SP) like: lawyers, laboratories, auditors, or banks,
to provide services, require data that is often associated with user
identity.

Providing personal information exposes users to privacy risk,
i.e.~potential loss of control over personal
information~\cite{smith2011information}.

Such user information can be then used deliberately or unintentionally
(e.g, by theft) for: insider disclosure, unauthorized access, or
commercial gains. For example, by reselling it to marketers, financial
institutions, other businesses, government agencies, or even
cybercriminals. Which in turn can lead to profiled advertisements, or
criminal activities like identity theft or illegal tracking and
surveillance~\cite{smith2011information}.

Important individuals like top government, influencers, or celebrities
are especially vulnerable to this kind of attacks as exposure of their
health records, purchase habits, or legal documents can threaten their
reputation, position, or can be used for blackmailing.

The guarantee of the privacy of the data is often based merely on a
trust assumptions and security of IT system. However, most of the SP
don't need the personal information for any other reasons than payment,
or communication, which should be considered secondary compared to
primary matter that is service provision.

It would be desirable if the user could keep its identity private, while
service provider still provide its services. This could lead to reduced
trust that users have to put on SP and less responsibility borne by SP.

\subsection{Use cases}
\paragraph{Anonymous clinical tests} \label{anonymous-clinical-tests}

Patients willing to take steroid test, drug test, venereal diseases
test, paternity test --- have strong incentive to keep the whole
procedure private. Merely the fact that they took the test --- without
exposing the results --- is suggestive enought to act as a premise in
case of a conflict.

Especially celebrites, politicans and public persona are exposed to this
kind of probems as such precedent can judge their future career.

Currently, they have to risk that their materials and results are stored
securely and keept in private from any any unathorized actor (both
curious employee, and malicious attacker).

Our protocol allows taking such tests anonymously, and therefore getting
rid of the strong trust assumption put on the laboratories and their IT
systems.

\paragraph{Anonymous lawyer consultations} \label{anonymous-lawyer-consultations}

People willing to take business action that may be risky or not yet
fully legistlated, may be willing to receive the rist estimation and
prediction of possible repercussions of such action.

By exposing our identity to the lawer, we trust that he won't use that
information for harmful actions.

Our protocol would allow taking such advices anonymously, and therefore
getting rid of the strong trust assumption put on the laboratories and
their IT systems.

\subsection{Contribution}
We contribute to the field of fair-exchanges by proposing a simple,
practical, and strongly anonymous framework that does not rely on
centralized trusted-third party, but on decentralized blockchain and
distributed content addressable networking.

Also, we support physical materials delivery, which was rarely targeted
by other researchers or based on strong and unpractical assumptions.

Our framework simultanesly provides three main properties:

\begin{itemize}
\item Anonimity:
throughout the whole transaction the customer stays anonymous to all external observers.
\item Fairness:
at each step of the protocol, both parties are incentivised to act accordingly to the protocol; otherwise the misbehaving party ends up in worst position.
\item Dispute resolution: at each step of the protocol the customer can open a dispute win the case iff the SP misbehaved.
\item TTP-less: our protocol does not rely on trusted-third party to conduct transactions in fairly manner. Only in case of dispute the centralized justice is invlolved (the justice decentralisation is discussed in {[}{[}Future Work{]}{]}).
\item Physical materials: our protocol allows providing not only
  digital but also physical materials to the service provider.
\end{itemize}

Some authors have proposed blockchain-based fair-exchange systems that
could be adapted to service provision; however, to our best knowledge we
are the first to propose a system that satisfy all five properties
stated above. Especially anonimity and physical materials delivery, are
properties that were rarely addressed together, and if so, the protocol
based on TTP, and strong and impractial assumptions on banking system
\cite{birjoveanu2015anonymity}, or didn't address the of conflict
between parties \cite{altawy2017lelantos}.

Our framework can potentially enable variety of services that for many
customers base on unacceptable trust assumptions to the SP.

\section{State of the art}\label{state-of-the-art}

\paragraph{Anonymity and Fair-Exchange in e-Commerce Protocol for
Physical Products
Delivery}\label{anonymity-and-fair-exchange-in-e-commerce-protocol-for-physical-products-delivery}

Authors of \cite{birjoveanu2015anonymity} proposed a
fair-exchange of physical product and electronic payment protocol that
guarantee both customer and merchant anonymity. They achieve it by
introducing online trusted third party that validate coins and provide
fair exchange guarantees.

The anonymity is ensured by assuming the existence of source cabinet
(SC) and delivery cabinet (DC), and a trusted delivery agent who take
product from a source cabinet and provide it to a destination cabinet.
Both cabinets provides access to the product by passwords to conceal
identity of the customer and the merchant. To avoid identity disclosure
of customer and merchant, the access to the product is provided by
passwords.

The protocol works as follows: \begingroup
\renewcommand{\labelenumii}{\arabic{enumii}.}

\begin{enumerate}
    \item Both parties agree on the purchase details.
    \item The customer buys a digital coin from his bank and validates it with the TTP.
    \item The customer sends to the merchant the purchase order and the digital signature made by TTP on the encrypted coin.
    \item The merchant post the product to the source cabinet.
    \item Delivery agent collect the product from source cabinet and post it to delivery cabinet.
    \item Customer collects the product from delivery cabinet using password.
    \item The customer checks if the product is actually the ordered one.
    \begin{itemize}
    \item[-] if yes 
        \begin{enumerate}
        \setcounter{enumii}{7}
        \item the customer sends the acknowledge to delivery cabinet and decryption key to the merchant.
        \item The merchant redeem the coins from the bank.
        \end{enumerate}
    \item[-] if no
        \begin{enumerate}
        \setcounter{enumii}{7}
        \item the delivery cabinet is equipment with video camera that records the moment when the customer open the package and let the customer to signal the invalidity of the product, and so, sending the encrypted recording to the TTP. 
        \item the dispute is settled via TTP, optionally letting each party to reveal it's identity.
    \end{enumerate}
    \end{itemize}
\end{enumerate}
\endgroup

Yet, the fair-exchange properties are achieved by strong assumptions.
Namely,

\begin{itemize}
    \item the TTP does not misbehave or collude with any party. 
    \item The customer's and merchant's banks enable confidental transactions and both share commit-buffer where the value is locked until the transaction is finished.   
    \item All banks mantain a global list of coin's serial numbers to prevent double-spending problem. 
    \item The source cabinet and delivery cabinet exists, and in both the product access is protected by password.
    \item Delivery cabinet is equppted with a video camera that records the moment when the customer opens the package, and provide a way to submit the video to TTP in case of a dispute. 
    \item Delivery agent exist and is trusted. 
    \item Communication channels between parties provides anonymity.
\end{itemize}

\paragraph{Themis: Towards decentralized escrow of cryptocurrencies
without trusted third
parties}\label{themis-towards-decentralized-escrow-of-cryptocurrencies-without-trusted-third-parties}

Themis\cite{meng2019themis} is a fair-exchange
protocol, which uses blockchain instead of TTP. It provide escrow
services for secure exchanging between cryptocurrencies and digital
goods.

Authors highlight that a widely-used atomic exchange mechanism HTLC
(Hashed Time-lock Contract) is vulnerable to denial of service (DoS)
attacks. While Multi-Signature Schemes depends on the Trusted Third
Party (TTP) making them vulnerable to collusion attacks. Such TTP can
collude with one party and take the locked funds. It can also refuse
settling disputes and lock the hosted funds.

Themis is a decentralized system that provides an escrow and dispute
resolution. It claims to satisfy following requirements:

\begin{itemize}
    \item Fairness: Either both seller and buyer obtain all the goods, or they both obtain nothing.
    \item Security: The funds are locked until the transaction is completed.
    \item Passivity: If no dispute arise, the third-party does not need to involve in the transaction.
    \item Correctness: Transactions and disputes are executed according to a priori agreed protocol rules.
    \item Dependability: There is no single point of failure vulnerable to DoS attack.
    \item Privacy: If the dispute does not arise, the third-party does not know if the transaction completes. If the dispute arises, only the related parties are aware of it.    
\end{itemize}

Two parties, say Alice and Bob, can create an escrow by generating
2-of-2 (not 2-of-3 as it is other TTP-based systems) threshold account
using Thresh-Key-Gen protocol. Alice and Bob generate secret keys
\(x_A\) and \(x_B\) accordingly, the shared account public key becomes
\(y = g^{x_A+x_B}\); only the access to both Alice's and Bob's secrets
grants access to the shared account.

Then, both Alice and Bob, takes their keys, and split them into
\(n=2t+1\) secret shares using Shamir Secret Shamir protocol, where
\(n\) is the number of mediators that participate in the decentralized
network, and \(t+1\) becomes the threshold of sufficient number of
mediators that can reconstruct the secret key.

Next, both Alice and Bob, take their key shares, and encrypt each
\(i\)-th key share using public key of \(i\)-th mediator. As a result
Alice's secret \(x_A\) becomes \({c^A_1, c^A_2,...,c^A_n}\), and Bob's
secret \(x_B\) becomes \({c^B_1, c^B_2,...,c^B_n}\), where
\(c_i = E_{M_i}(P_i)\) is the encrypted \(i\)-th key share using
\(i\)-th mediator public key \(M_i\).

Next, both Alice and Bob exchange the sets of encrypted key shares with
each other. And send funds to the escrow account.

The escrow is secure as long as \(t+1\) of mediators does not collude,
which would let them recreate both \(x_A\) and \(x_B\). Also, to ensure
that parties are exchanging real key shares, they also send a witnesses
generated with Feldman VSS scheme and zero-knowledge proofs to guarantee
the consistency between witnesses and key shares.

In case of dispute, the decentralized network of mediators settle the
conflict and grand one winning party, the other party secret key,
letting him to withdraw the funds.

The honesty of mediators is achieved by the monetary incentivization and
reputation system.

\paragraph{Lelantos: A blockchain-based anonymous physical delivery
system}\label{lelantos-a-blockchain-based-anonymous-physical-delivery-system}

Lelanros\cite{altawy2017lelantos} is a blockchain-based anonymous
physical delivery system. The anonymity is achieved by employing ToR's
onion routing to connect physical delivery providers. The whole route
from merchant to customer is split into multiple steps, and each step is
undertaken by different randomly selected delivery provider. As long as
the develiery providers does no collude, mechant can not learn both
identity and destination address of the customer.

Onchain smart-contract is used to coordinate the whole process and
mediate communication between customer and delivery providers.

However, the system doesn't achieve full anonimity but pseudonimity (see
section \ref{pseudo-anon}). Also the protocol does not
cover the case of dispute between the customer and the SP.

\section{Background}
\subsection{Dispute resolution system}

Disputes are inevitable part of all human transactions. Whether
intentional or accidental, the system should prevent any behaviour
volatiling rules of agreed contract or local jurisdiction. The rules are
specified by law, and implemented by police.

The vision of smart contract was to replace legal contract with
programmable and autonomous contracts. The specifications of contract
was encompasses in the code, hence the slogan ``code as a law''. Yet,
the blockchain paradigm has its limitations. It can assure the
correctness of data existing on the blockchain. The problem arises on
the contact between blockchain and real world. When we want the smart
contract to make a decision based on some input from outside the
blockchain. We move a lot of trust assumptions on the data providers.
The technique of providing real world data to the blockchain is called
oracle. Oracle provide data based on decentralised network of mediators,
therefore the trust is also decentralised.

Some oracles provide the data like weather, soccer match result, stock
price, train delay, election results, others---and they are the ones we
are interested in---provide the settlement of a submited dispute.

Themis \cite{meng2019themis} besides providing fair-exchange protocol,
also offers a semi-autonomous decentralised dispute resolution system,
which comply with the web3 postulates of decentralised web. Themis
resolve disputes by set of voluntary anonymous mediators participating
in a voting and deciding whether a party misbehaved. The honesty of
mediators is achieved by the monetary incentivization and reputation
system.

Kleros \cite{lesaege2018kleros} is a smart contract deployed on
Ethereum platform that mimics in decentralised and autonomous way how
court works in real life. In Kleros, every process of a dispute like
gathering evidences, selecting jurors, rewarding the winning party is if
automated by a set of smart contracts. Simillar to Themis, the honesty
of the agents voting in a case is achieved by game-theoretical economic
incentives.

Such decentralised, voluntary, and anonymous dispute resolution system
might work for simple contracts violation like eBay seller sending
broken or wrong product, or Airbnb apartment being not adequate to the
photos in the offer. However it's hard to realise such decentralised
evaluation of quality of heath or legal services when expertise and
privacy concerns are taken into an account. Therefore, in our protocol
we take the more conservative approach and resolve disputes using local
justice system (police or court).

Possible directions toward semi-autonomous decentralised resolution
system are discussed in {[}{[}anonser/Future Work{]}{]}.

\subsection{Proof to justice}
In case of dispute the customer can proof to the justice (police, court,
etc.) evidences that convinces the justice about the honesty of customer
and misbehaviour of SP. The reason why the SP can not start a dispute is
that the customer is anonymous, and therefore there is no personal
information to start a dispute aginst. To mitigate this issue the SP is
always in advantaged postition, so that he has no reason to start a
dispute. The idea described firther in {[}{[}Fairness analysis{]}{]}.

Abstracting from the services the SP is providing, in case of dispute
the customer should be able to prove that: (i) he delivered to the SP a
complete (according to the SP requirements) package \(pkg\), and the SP
accepted it; (ii) he paid for the transaction \(tx\).

The first proof called proof-of-delivery (PoD) is a confirmation issued
by the SP to the customer.

\[\mathrm{PoD} = (\mathrm{T}_\mathrm{issue}, \mathrm{T}_\mathrm{pay}, \mathrm{T}_\mathrm{provide}, \mathrm{nonce}, \mathrm{sig}_\mathrm{SP})\]

where:

\begin{itemize}

\item
  \(\mathrm{T}_\mathrm{issue}\) - time at which the PoD is issued.
\item
  \(\mathrm{T}_\mathrm{pay}\) - deadline to pay for the transaction.
\item
  \(\mathrm{T}_\mathrm{provide}\) - deadline to provide the service
  results.
\item
  \(\mathrm{nonce}\) - randomly generated number uniquely identifying
  the transaction.
\item
  \(\mathrm{sig}_\mathrm{SP}\) - the SP's signature guaranteeing
  non-repudiation.
\end{itemize}

also:

\(\mathrm{T}_\mathrm{issue} < \mathrm{T}_\mathrm{pay} < \mathrm{T}_\mathrm{provide}\)

The second proof depend on the cryptocurrency implementation and is
discussed further in section {[}{[}Payment for services{]}{]}.

In case the SP has fulfulled the transaction and provide the results,
but the customer unjustly start a dispute, the SP is secured by the
proof-of-provision (PoP) he's published on the message board
({[}{[}Message Board{]}{]}).

\[\mathrm{PoP} = (\mathrm{cid}, \mathrm{nonce}, \mathrm{sig}_\mathrm{SP})\]

where:

\begin{itemize}

\item
  \(\mathrm{cid}\) - content identifier as specified in {[}{[}Storage
  Network{]}{]}.
\item
  \(\mathrm{nonce}\) - the value uniquely identifying the transaction
  previosuly generated in PoD.
\item
  \(\mathrm{sig}_\mathrm{SP}\) - the SP's signature guaranteeing
  non-repudiation.
\end{itemize}

By publishing the PoP on the blockchain, the SP can not falsify the time
at which the results has been provided, because the block creation time
proves that. Blockchain acts as a global clock that securely timestamps
everything that gets into the block, so the PoP that was included in a
block will be associated with the time when the block has been forged.
Moreover, since the blockchain is public, everyone (including the
justice) can be convinced that the SP indeed provided the results at
that time.

The connection between PoP and the results is made by the content
identifier which uniquely points to the results such that the PoP can
not forge results after the publication.

The content identifier is usually some kind of hash write about ipfs

\subsection{Message Board}\label{message-board}
The proof of provision that we coined for the purpose of this protocol
is generaly called the proof of existence
\cite{proofofexistence, de2016stampery, Chainpoi39}.

The idea behind proof of existence is to certify that some information
has existed at a certain moment of time, in such a way that nobody can
undermine its existence, integrity, and ownership (also called the
nonrepudiation requirement).

We need this functionality for two reasons: 1. Communicate the existence
of the results to the customer to whom the SP have no other
communication medium as the customer stays anonymous. 2. Let the SP to
proof the publication of results within the agreed with customer
deadline. Without such a proof there would be no other means to settle
the conflict between the customer claiming the results have not been
published and the SP claiming the results have been published within the
deadline.

Depending on the context the platform of achieving it is called bulletin
board \cite{achenbach2015improved} or message board
\cite{hinarejos2019solution} or trusted timestamping
\cite{gipp2015decentralized}. In this work we call it Message Board.

Such functionallity is the easiest to achieve by the trusted third party
that authoritatively tells what happend and when.

Bitcoin introduced a way of decentralizing not only the currency system,
but also other similary working centralized trusted third parties
including the Message Board.

We let keep the protocol general enough to let the implementator use any
existing technology to provide Message Board service, with the
assumption that it's decentralised and supports subscribing for the
upcoming proofs from particular address.

\subsection{Pseudo-anonymous vs anonymous blockchain}
Privacy is a concept used in almost all kinds of social sciences like
philosophy, psychology, sociology, and legal. The multidisciplinary
nature leads to ambigous definitions\cite{smith2011information}. For
the purpose of our work we rely on more concrete definitions,
i.e.~confidentality and anonimity.

Confidentality is the ability to hide the details of an action from
others. Or we can say, that the system guarantee confidentality if for
all observers everything they can say about the action is the fact that
it happened and nothing more.

Anonymity is a the ability to hide one identity from others. More
precisely, the unability to correlate actions performed within the sytem
to the identity of the user. Or we can say, that the system guarantee
anonimity if for all observers the actions are equally likely to be
associated with any user of the system. However, anonimity is a spectrum
rather than dichotomous classification. One method of quantifying level
of anonymity is proposed in k-anonymity \cite{sweeney2002k}. It measure
the user's anonymity by the number of other users from whom the user can
not be distinguished. Concreatly, the user is \emph{k}-anonymous if his
actions are equaly likely associated with \emph{k}-1 other users. The
larger \emph{k}, the higher anonimity.

The cryptocurrencies that natively support anonymous transactions are
Monero \cite{van2013cryptonote} (via Bulletproofs
\cite{Bulletpr14, bunz2018bulletproofs}) and ZCash
\cite{sasson2014zerocash} (via zk-SNARK \cite{ben2013snarks}), Grin
\cite{fuchsbauer2019aggregate} (via Mimblewimble \cite{httpsdow19}).

There are also techniques that can be deployed on non-anonymous
blockchains, the so called mixers: Ethereum's Tornado
Cash\cite{pertsev2019tornado}, Bitcoin's Wasabi\cite{WasabiWa56} (uses
CoinJoin \cite{CoinJoin41}) that literaly gather together users into an
``anonimimity set'', which then collude together in order to launder the
transactions, in such a way that to a observer the likelyhood of the
sender of each transaction was equiprobable for any user from the
anonimity set.

Some systems guarantee pseudonomity rather than anonimity. Pseudonomity,
allows uses to hide their real identity behind the pseudonim. Despite
the whole system is transparent and allows linking actions to one
identity, the system is considered anonymous as long as the link between
pseudonym and real identity is secret. This assumption is hard to
satisfy in practice, as the KYC (Know You Customer) and AML (Anti Money
Laundering) regulations require users to reveal their real identity on
most of the cryptocurrencies exchanges. This makes the anonymity of the
user dependent on the security of the IT system. Moreover, some
correlations can be infered merely by the analysis of transactions
\cite{androulaki2013evaluating, ober2013structure}. Most of the
blockchains, including Bitcoin and Ethereum achieve this kind of
pseudonimity.

The relations between these terms are ilustrated in the figure~\ref{fig:anonimity-confidentality}.

\begin{figure}[h!]
\caption{Scenario of path where both the customer and  the SP are behaving correctly}
\centering
\includegraphics[width=9cm]{anonimity-confidentality.png}
\label{fig:anonimity-confidentality}
\end{figure}

People who call tracable and linkable blockchains to be anonymous base
on a strong assumption that the identification is impossible, infeasable
or at least plausably unlikely. We require the system for anonymous
payments to satisfy anonymilty via untraceability or unlinkability. We
don't pay much attention to confidentiality as it doesn't bring much
value to the protocol.

\subsection{Payment for services}
Transactions between customers and SP have to be somehow pegged in order
to prevent proving one payment for multiple transactions. In other
words, we need some way to uniquely link particular payment with the
transaction it pays for.

Depending for the cryptocurrency the link can be created in different
ways:

\begin{itemize}

\item
  separate address --- each transaction derives new address uniquely
  associating it with the transaction. Such addresses can be derived
  using BEP-32 standard.
\item
  memo --- the payments are send to one SP account, but contain extra
  field named ``memo'' which contains a random value generated by SP and
  included in POD. Each payment containing such value in memo is
  considered to pay for the transaction in question. in case of dispute,
  the connection can be disclosed by revealing the value in POD and
  payment's memo.
\end{itemize}

Both approaches have some advantages and disadvantages, but our protocol
can abstract them away by treating them as some randomly genrated unique
number, often called \textit{nonce} (number once). How it is implemented
depends on a particular blockchain.

In case of a dispute there must a way to prove to the justice that the
customer has paid for the transaction. As the proof of transaction is
trivial in transparent and trackable blockchains, it gets more
complicated when it comes to anonymous blockchains. Monero allows
proving and checking payments via dedicated API \cite{Howtopro46}.
ZCash provides mechanism called Payment Disclosure \cite{AnIntrod25},
which at the time of writing is still a experimental feature
\cite{paymentd11}. Proving payments that were made with the usage of
mixers, involve two steps.

\subsection{Storage network}
Once the SP finish its service, he has to provide the results to the
customer. The most natural approach would to be send the results via
email of decidated platform. However, since the customer wants to stay
anonymous, he don't want to expose his email address nor IP address.
Moreover, in case of dispute the SP should be able to prove that the
results have been provided before the deadline.

One approach would be to post the results into a blockchain. Yet,
storing data on a blockchain is very expensive. The most common
workaround
(\cite{shahid2020blockchain, wang2019auditable, chen2017improved, Usageide95})
is to publish the data to the IPFS \cite{benet2014ipfs}---a content
adressable peer-to-peer storage network---and publish to a blockchain
just a content identifier (cid) that uniquely points to the content
stored on the IPFS.

We take the same approach. Once the SP creates the results, he encrypts
them using the previously provided customer's public key; then publish
them into a IPFS network.

To increase anonimity, the customer should use a common techniques to
hide its IP address; for example, use gateway, VPN, proxy, or onion
routing.

\subsection{Separation of concerns}
We could use one blockchain to achieve all of these three roles: (i)
Anonymous payments; (ii) Message Board; (iii) Storage network.

As the Message board could be achieved by most of the blockchanis, the
anonymous payments isn't so prevalent, and provable storage network is a
functionality of a few specialized blockchains.

Instead of searching for one blockchain that solves all the
functionallities, we allow the framework to use separate blockchains for
each of the functionalities. In case a suitable blockchain arises, it
can play more than one role.

At the time of writing, we see following technologies that fulfill the
requrements of each role:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}

\item Anonymous payments: Monero \cite{van2013cryptonote}, ZCash
  \cite{sasson2014zerocash}, Grin \cite{fuchsbauer2019aggregate},
  Tornado Cash \cite{pertsev2019tornado}.
\item Message Board: Stampery \cite{de2016stampery}, Proof of Existence
  \cite{proofofexistence} (Bitcoin blockchain), Chainpoint
  \cite{Chainpoi39} (Bitcoin blockchain), or any other blockchain that
  supports attaching extra data along the transaction.
\item Storage network: IPFS \cite{benet2014ipfs}, Filecoin
  \cite{benetfilecoin} (runs on top of IPFS), or Ethereum's
  Swarm\cite{swarmwhi49}.
\end{enumerate}

\section{The Protocol}

\(\mathrm{SP}\) - Service Provider. \(\mathrm{customer}\) - Customer.
\(\mathrm{pkg}\) - package anonymously delivered by customer to SP.
\(\mathrm{materials}\) - materials used by SP to provide services, can
be of any kind: urine, saliva, blood, stool, or health documents, legal
documents etc. \(\mathrm{results}\) - results in binary format, can be
either PDF, docx or any format agreed by both parities. \(\mathrm{PoD}\)
- Proof-of-Delivery is a confirmation issued by SP to the customer after
the \(pkg\) is accepted by the SP. \(\mathrm{PoP}\) -
Proof-of-Provision, a proof of existence of provisioned results.
\(\mathrm{E}_\mathrm{key}(\cdot)\), \(\mathrm{D}_\mathrm{key}(\cdot)\) -
symmetric encryption and decryption operators.
\(\mathrm{S}_\mathrm{key}(\cdot)\), \(\mathrm{V}_\mathrm{key}(\cdot)\) -
digital sign and verify operators. \(\mathrm{sk}\), \(\mathrm{pk}\) -
Key pair of secret and public keys accordingly.
\(\mathrm{DH}(\cdot, \cdot)\) - Diffie--Hellman key exchange. \(CID\) -
Content Identifier, a label used to address content in IPFS.

\subsection{Prerequisites}

Anonymous payments:

\begin{itemize}

\item
  SPs accept packages from unknown customers and give them back
  confirmation of acceptance (to stick with convention we call it
  Proof-of-Delivery).
\item
  SPs accept payment for services via anonymous cryptocurrencies like
  Monero, Grin or ZCash as described in {[}{[}Payment for
  services{]}{]}.
\item
  Justice accepts as a evidence in dispute proof of payment of
  cryptocurrencies as described in {[}{[}Proof to Justice{]}{]}.
\end{itemize}

\subsection{Protocol description}

\subsection{Messages}\label{messages}

\paragraph{Package}\label{package}

\[\mathrm{pkg} \equiv (\mathrm{materials}, \mathrm{key})\]

where:

\begin{itemize}

\item
  \(\mathrm{materials}\) - are the materials needed to provide the
  service on. For example, sample of urine, blood, stool, saliva; legal
  documents, CDs, mails, photos, bank statement, or any other kind of
  evidence depending on the service.
\item
  \(\mathrm{key}\) - symmetric key used to encrypt and decrypt the
  results.
\end{itemize}

\paragraph{Proof-of-Delivery}\label{proof-of-delivery}

\[\mathrm{PoD} \equiv (\mathrm{T}_\mathrm{issue}, \mathrm{T}_\mathrm{pay}, \mathrm{T}_\mathrm{provide}, \mathrm{nonce}, \mathrm{sig}_\mathrm{SP})\]

where:

\begin{itemize}

\item
  \(\mathrm{T}_\mathrm{issue}\) - time at which the PoD is issued.
\item
  \(\mathrm{T}_\mathrm{pay}\) - deadline to pay for the transaction.
\item
  \(\mathrm{T}_\mathrm{provide}\) - deadline to provide the service
  results.
\item
  \(\mathrm{nonce}\) - randomly generated number uniquely identifying
  the transaction.
\item
  \(\mathrm{sig}_\mathrm{SP}\) - the SP's signature guaranteeing
  non-repudiation.
\end{itemize}

also:

\(\mathrm{T}_\mathrm{issue} < \mathrm{T}_\mathrm{pay} < \mathrm{T}_\mathrm{provide}\)

\paragraph{Proof-of-Provision}\label{proof-of-provision}

\[\mathrm{PoP} \equiv (\mathrm{cid}, \mathrm{nonce}, \mathrm{sig}_\mathrm{SP})\]

where:

\begin{itemize}

\item
  \(\mathrm{cid}\) - content identifier as specified in {[}{[}Storage
  Network{]}{]}.
\item
  \(\mathrm{nonce}\) - the value uniquely identifying the transaction
  previosuly generated in PoD.
\item
  \(\mathrm{sig}_\mathrm{SP}\) - the SP's signature guaranteeing
  non-repudiation.
\end{itemize}

\paragraph{Payment attestation}\label{payment-attestation}

Payment attestation proves that the customer did the payment. Since the
evidences depends on the particular blockchain (see Section
{[}{[}Payment for services{]}{]}). We refer to them symbollicaly as
\(attestation\).

\paragraph{Results}\label{results}

We assume results to be documents in PDF format, but they can be
anything as long as they can be binary encoded and uploaded to IPFS. We
refer to them symbollicaly as \(results\).

\paragraph{Content Identifier (cid)}\label{content-identifier-cid}

Although content identifier (cid) is a term coined by IPFS
\cite{Contenta59}. However, since we our protocol does not depend on
this particular implementation of storage network, we let the cid be any
other identifier that securely and uniquely points to the content.

\subsection{Protocol description}\label{protocol-description}

In this section we describe each step of the protocol. The steps are
shown in the figure ~\ref{fig:diagram}.

\begin{figure}[h!]
\includegraphics[width=9cm]{anonser-diagram.png}
\centering
\caption{Diagram}
\label{fig:diagram}
\end{figure}

\subsubsection{Step 1: Package delivery}\label{step-1-package-delivery}

They protocol start once the customer delivers package \(\mathrm{pkg}\)
to SP.

In return, the SP issue an Proof-of-Delivery (POD) confirmation. The
confirmation encompasses timestamp, invoice (see section {[}{[}Payment
for services{]}{]}), and signature.

Symbolically: \[
\mathrm{delivery}(\mathrm{pkg}) : \mathrm{PoD}
\]

\subsubsection{Step 2: Payment}\label{step-2-payment}

Having POD, SP can not reject receiving the package. At this point the
customer should pay for the invoice according to selected cryptocurrency
system (see section {[}{[}Payment for services{]}{]}).

In return, the customer receives the attestation that should be used in
case of a dispute.

Symbolically: \[
\mathrm{payment}(\mathrm{PoD}.\mathrm{nonce}) : \mathrm{attestation}
\]

\subsubsection{Step 3: Provision of
service}\label{step-3-provision-of-service}

At this point the SP can start the provision of service. If it's
suspicious it may decide to wait until the invoice is paid, otherwise
start immediately.

Symbolically: \[
\mathrm{provision}(\mathrm{pkg}.\mathrm{materials}) : \mathrm{results}
\]

\subsubsection{Step 4: Results
publication}\label{step-4-results-publication}

Once the service is finished, some kind of output should be created. The
output should be encrypted using encryption symmetric key provided in
the first step.

The encrypted results can be then published on content network such as
IPFS. As a result, the content identifier (CID) is returned.

Symbolically: \[
 \mathrm{publish}(E_{\mathrm{pkg}.\mathrm{key}}(\mathrm{results})) : \mathrm{PoP}
\]

\subsubsection{Step 5: Proof of provision
publication}\label{step-5-proof-of-provision-publication}

Now, when the results are published on content addressable network such
as IPFS, the SP publish \(\mathrm{cid}\) obtained in previous step on a
message board doing proof of provision.

Symbolically: \[\mathrm{publish}(\mathrm{cid})\]

\subsubsection{Step 6: Proof-of-provision
notification}\label{step-6-proof-of-provision-notification}

Since the delivery and payment was made the customer observes blockchain
for a POP corresponding to his transaction. When it happen,

Symbolically: \[
\mathrm{pull}(\mathrm{pkg.nonce})
\]

\subsubsection{Step 7: Results download}\label{step-7-results-download}

Symbolically: \[
\mathrm{download}(\mathrm{cid}) : \mathrm{results}
\]

\section{Fairness analysis}
We analyse the fairness of the protocol by representing it as a
interactive non-cooperative game.

\subsubsection{Model}\label{model}

We consider three positions:

\begin{itemize}
\item
  Neutral (•) position is when a party hasn't spend not gain anything of
  significant value (money, time, effort). For example, at beggining of
  the protocol.
\item
  Disadvantage (-) position — when a party has put any effort or paid
  money without being able to reclaim it. In other words it has
  \textbf{risked} its resources. For example, paid for a service in
  advance.
\item
  Advantage(+) position — when a party would benefit if the
  transaction would halt at that point. For example, received payment in
  advance.
\end{itemize}

There are many actions that each party can take, but we group them
together into two categories:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}

\item
  Normal --- taking the action prescribed by the protocol.
\item
  Abnormal --- everything that deviates from designed steps of the
  protocol. For example, sending arbitrary message, skipping some step,
  repeating step, timing out.
\end{enumerate}

Moreover, at any step of the protocol the customer can react with two
reactions:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}

\item
  Agree --- the customer agree with the action and therefore does not
  start a dispute.
\item
  Start a dispute --- the customer does not agree with the action and
  therefore start a dispute.
\end{enumerate}

Therefore, there are two possible actions a party can take at any step
of the protocol and two reactions the customer can take.

Hence, in our analysis we have to consider four different outcomes for
each party of the protocol:

\begin{itemize}

\item
  \(\sigma_\mathrm{n}\) --- after following the protocol within the
  timeframe.
\item
  \(\sigma_\mathrm{d}\) --- after a dispute where the other party hasn't
  broken the protocol.
\item
  \(\sigma_\overline{n}\) --- after not starting a dispute despite the
  other party has broken the protocol.
\item
  \(\sigma_\overline{d}\) --- after a dispute where the other party has
  broken the protocol.
\end{itemize}

The protocol terminate after last step, after starting a dispute, or
after a party hasn't completed it's designated action in time. Therefore
all positions except \(\sigma_\mathrm{n}\) are termination positions.

After starting a dispute, the protocol terminate. After timing out there
is no going back on the normal path.

In our framework, the only party that can start a dispute is the
customer. It's because the customer is anonymous, and so the SP does not
have any personal information to start a dispute against.

To mitigate this issue, the protocol is designed so that the SP who
follows the protocol is always in advantaged position, therefore he has
no incentivisations to start a dispute.

We say that the protocol achieve fairness if:

\begin{align*} 
  \forall_{party \in parties}\forall_{\mathrm{step} \in \mathrm{steps}} \mathrm{can\ move\ the\ protocol\ \\
  to\ the\ non\-disadvantaged\ position} 
\end{align*}

\paragraph{Assumptions}\label{assumptions}

For the analysis purpose we state assumptions listed below. We consider
them being rational and realistic.

Assumptions:

\begin{itemize}

\item
  Both parties start from neutral position (•).
\item
  Both parties, by completing a transaction, end up in advantaged
  positions (+). In other words, they have intrinsic motivation to
  initialise the transaction.
\item
  We assume the steps of the protocol to be atomic, there are no
  intermediate steps.
\item
  Repeating the first step starts new transaction. Repeating any other
  step is considered abnormal and gets ignored. For example paying for
  the invoice twice does not cause any effect on the curse of protocol.
\item
  Once published, the results are avaiable to the customer in the
  content storage. The idea of guaranteeing it cryptographically is
  discussed in {[}{[}Future Work{]}{]}.
\item
  The protocol can go only forward, there is no way of revert any
  action.
\item
  Losing the dispute leads to punishment that is greater than any
  reward, which leads to disadvantaged position. Hence, the rational
  customer won't start a dispute that he is not sure to win.
\item
  Winning the dispute leads to neutral position (•)
\item
  Both the customer and the SP are rational (selfish). They always
  prefer go from worst position to better position, but also risk
  temporary worst position in favour for later better position iff it's
  assured that they won't stuck in worst position.
\end{itemize}

\subsubsection{Steps}\label{steps}

The table in figure~\ref{fig:positions} shows the positions of each party after each possible
action taken.

\begin{figure}[h!]
\includegraphics[width=9cm]{formal-table-of-positions.png}
\centering
\caption{Formal table of positions}
\label{fig:positions}
\end{figure}

Below is the description for each step and rationale of the outcome
position.

\paragraph{Step 1: deliver package}\label{step-1-deliver-package}

Turn: Customer

Customer has delivered the package:

\begin{itemize}
\item
  Agreeable path:

  \begin{itemize}

  \item
    \(\sigma_{1, c, \mathrm{n}} = •\) - the customer has risked its
    materials but has not paid anything, so we assume he is in neutral
    position (•). One would argue that the customer has put effort of
    delivering the materials to the SP, or that the sample is valuable.
    We assume that the sample without personal information is useless
    and the effort to deliver the package is negligible.
  \item
    \(\sigma_{1, s, \mathrm{n}} = •\) - the SP is in neutral position as
    he didn't put any effort to rece the package, also the package
    hasn't any value to the SP (•).
  \end{itemize}
\item
  Starting a dispute:

  \begin{itemize}

  \item
    \(\sigma_{1, c, \mathrm{d}} = -\) - the customer lose the case as
    the SP has still opportunity to publish proof-of-provision within
    timeframe (-).
  \item
    \(\sigma_{1, s, \mathrm{d}} = •\) - the SP win the case for the same
    reason (•).
  \end{itemize}
\end{itemize}

Fairness:

\begin{itemize}

\item
  The customer can follow the protocol and move to the non-disadvantaged
  position \(\sigma_{1, c, \mathrm{n}} = •\).
\item
  The SP can do nothing and end up in non-disadvantaged position
  \(\sigma_{1, s, \mathrm{n}} = •\) or
  \(\sigma_{1, s, \mathrm{d}} = •\).
\end{itemize}

\paragraph{Step 2: pay for invoice}\label{step-2-pay-for-invoice}

Turn: Customer

Customer has paid the invoice:

\begin{itemize}
\item
  Following protocol:

  \begin{itemize}

  \item
    \(\sigma_{2, c, \mathrm{n}} = -\) the customer has spend his funds
    but hasn't received the results. Therefore, he moves to the
    disadvantaged position (-).
  \item
    \(\sigma_{2, s, \mathrm{n}} = +\) the SP has received the payment
    but hasn't spend his resources yet. Therefore, he moves to advantaged
    position (+).
  \end{itemize}
\item
  Starting a dispute:

  \begin{itemize}

  \item
    \(\sigma_{2, c, \mathrm{d}} = -\) the customer lose the case as the
    SP has still opportunity to publish proof-of-provision before the
    deadline (-)
  \item
    \(\sigma_{2, s, \mathrm{d}} = +\) the SP win the case for the same
    reason (+)
  \end{itemize}
\end{itemize}

Customer has timeouted \(time-to-issue-\), then:

\begin{itemize}
\item
  Following protocol:

  \begin{itemize}

  \item
    \(\sigma_{2, c, \overline{\mathrm{n}}} = •\) - the customer ends up
    in neutral position, since he didn't spend his funds (•)
  \item
    \(\sigma_{2, s, \overline{\mathrm{n}}} = •\) - The SP ends up in
    neutral position as he didn't receive the payment, nor spent his
    resources (•)
  \end{itemize}
\item
  Starting a dispute:

  \begin{itemize}

  \item
    \(\sigma_{2, c, \overline{\mathrm{d}}} = -\) - the customer loses
    the case as he can not prove the payment before the time limit.
    Consequently, ends up in disadvantaged position (-)
  \item
    \(\sigma_{2, s, \overline{\mathrm{d}}} = •\) - the SP is not charged
    to the justice due to lack of proofs. Therefore, he ends up in
    neutral position (•)
  \end{itemize}
\end{itemize}

Fairness:

\begin{itemize}

\item
  The customer can move the protocol forward to the step 3, where if the
  SP follow the protocol then the customer can push the protocol forward
  up to the last termination step \(\sigma_{7, c, \mathrm{n}} = +\),
  otherwise if at any step the SP does not follow the protocol the
  customer can start a dispute which terminates the protocol at
  non-disadvantaged position, i.e.,
  \(\sigma_{3, c, \overline{\mathrm{d}}} = •\),
  \(\sigma_{4, c, \overline{\mathrm{d}}} = •\),
  \(\sigma_{5, c, \overline{\mathrm{d}}} = •\).
\item
  The SP can do nothing and end up in non-disadvantaged position
  \(\sigma_{2, s, \mathrm{n}} = +\), \(\sigma_{2, s, \mathrm{d}} = +\),
  \(\sigma_{2, s, \overline{\mathrm{n}}} = •\),
  \(\sigma_{2, s, \overline{\mathrm{d}}} = •\).
\end{itemize}

\paragraph{Step 3: provision of
service}\label{step-3-provision-of-service}

Turn: SP

SP has done the provision of service:

\begin{itemize}
\item
  Following protocol:

  \begin{itemize}

  \item
    \(\sigma_{3, c, \mathrm{n}} = -\) the customer hasn't received the
    results. Therefore, he remains in disadvantaged position (-).
  \item
    \(\sigma_{3, s, \mathrm{n}} = +\) the SP has fullfiled the contract
    on time (+).
  \end{itemize}
\item
  Starting a dispute:

  \begin{itemize}

  \item
    \(\sigma_{3, c, \mathrm{d}} = -\) the customer lose the case as the
    SP has still opportunity to publish proof-of-provision within
    timeframe (-)
  \item
    \(\sigma_{3, s, \mathrm{d}} = +\) the SP win the case for the same
    reason (+)
  \end{itemize}
\end{itemize}

SP has timeouted, then:

\begin{itemize}
\item
  Following protocol:

  \begin{itemize}

  \item
    \(\sigma_{3, c, \overline{\mathrm{n}}} = -\) the customer ends up in
    disadvantaged position (-)
  \item
    \(\sigma_{3, s, \overline{\mathrm{n}}} = +\) the SP ends up in
    advantaged position as he received the payment (+)
  \end{itemize}
\item
  Starting a dispute:

  \begin{itemize}

  \item
    \(\sigma_{3, c, \overline{\mathrm{d}}} = •\) the customer wins the
    case and end up in neutral position (•)
  \item
    \(\sigma_{3, s, \overline{\mathrm{d}}} = -\) the SP loses the case
    and end up in disadvantaged position (-)
  \end{itemize}
\end{itemize}

Fairness:

\begin{itemize}

\item
  The customer can do nothing if the SP follows the protocol, which will
  ultimately put him in advantaged position
  \(\sigma_{7, c, \mathrm{n}} = +\), or in case of the SP not following
  the protocol, the customer can start a dispute and terminate in
  non-disadvantaged position
  \(\sigma_{3, c, \overline{\mathrm{d}}} = •\).
\item
  The SP can follow the protocol and move to the non-disadvantaged
  position \(\sigma_{3, s, \mathrm{n}} = +\), or not follow the protocol
  and also end up at non-disadvantaged position
  \(\sigma_{3, s, \overline{\mathrm{n}}} = +\), but the second option
  puts him at risk of terminating the protocol at
  \(\sigma_{3, s, \overline{\mathrm{n}}} = +\), if the customer is
  rational and starts a dispute.
\end{itemize}

\paragraph{Step 4: publication of
results}\label{step-4-publication-of-results}

Turn: SP

SP has published results on time:

\begin{itemize}
\item
  Following protocol:

  \begin{itemize}

  \item
    \(\sigma_{4, c, \mathrm{n}} = -\) the customer hasn't received the
    results. Therefore, he remains in disadvantaged position (-).
  \item
    \(\sigma_{4, s, \mathrm{n}} = +\) the SP has fullfiled the contract
    on time (+).
  \end{itemize}
\item
  Starting a dispute:

  \begin{itemize}

  \item
    \(\sigma_{4, c, \mathrm{d}} = -\) the customer lose the case as the
    SP has still opportunity to publish proof-of-provision within
    timeframe (-)
  \item
    \(\sigma_{4, s, \mathrm{d}} = +\) the SP win the case for the same
    reason (+)
  \end{itemize}
\end{itemize}

SP has timeouted, then:

\begin{itemize}
\item
  Following protocol:

  \begin{itemize}

  \item
    \(\sigma_{4, c, \overline{\mathrm{n}}} = -\) the customer ends up in
    disadvantaged position (-)
  \item
    \(\sigma_{4, s, \overline{\mathrm{n}}} = +\) the SP ends up in
    advantaged position as he received the payment (+)
  \end{itemize}
\item
  Starting a dispute:

  \begin{itemize}

  \item
    \(\sigma_{4, c, \overline{\mathrm{d}}} = •\) the customer wins the
    case and end up in neutral position (•)
  \item
    \(\sigma_{4, s, \overline{\mathrm{d}}} = -\) the SP loses the case
    and end up in disadvantaged position (-)
  \end{itemize}
\end{itemize}

Fairness:

\begin{itemize}

\item
  The customer can do nothing if the SP follows the protocol, which will
  ultimately put him in advantaged position
  \(\sigma_{7, c, \mathrm{n}} = +\), or in case of the SP not following
  the protocol, the customer can start a dispute and terminate in
  non-disadvantaged position
  \(\sigma_{4, c, \overline{\mathrm{d}}} = •\).
\item
  The SP can follow the protocol and move to the non-disadvantaged
  position \(\sigma_{4, s, \mathrm{n}} = +\), or not follow the protocol
  and also end up at non-disadvantaged position
  \(\sigma_{4, s, \overline{\mathrm{n}}} = +\), but the second option
  puts him at risk of terminating the protocol at
  \(\sigma_{4, s, \overline{\mathrm{n}}} = +\), if the customer is
  rational and starts a dispute.
\end{itemize}

\paragraph{Step 5: publication of
proof-of-provision}\label{step-5-publication-of-proof-of-provision}

Turn: SP

SP has published proof-of-provision on time:

\begin{itemize}
\item
  Following protocol:

  \begin{itemize}

  \item
    \(\sigma_{5, c, \mathrm{n}} = -\) the customer hasn't received the
    results. Therefore, he remains in disadvantaged position (-).
  \item
    \(\sigma_{5, s, \mathrm{n}} = +\) the SP has fullfiled the contract
    on time (+).
  \end{itemize}
\item
  Starting a dispute:

  \begin{itemize}

  \item
    \(\sigma_{5, c, \mathrm{d}} = -\) the customer lose the case as the
    SP can prove the publication of proof-of-provision (-)
  \item
    \(\sigma_{5, s, \mathrm{d}} = +\) the SP win the case as the SP can
    prove the publication of proof-of-provision (+)
  \end{itemize}
\end{itemize}

SP has timeouted, then:

\begin{itemize}
\item
  Following protocol:

  \begin{itemize}

  \item
    \(\sigma_{5, c, \overline{\mathrm{n}}} = -\) the customer ends up in
    disadvantaged position (-)
  \item
    \(\sigma_{5, s, \overline{\mathrm{n}}} = +\) the SP ends up in
    advantaged position as he received the payment (+)
  \end{itemize}
\item
  Starting a dispute:

  \begin{itemize}

  \item
    \(\sigma_{5, c, \overline{\mathrm{d}}} = •\) the customer wins the
    case and end up in neutral position (•)
  \item
    \(\sigma_{5, s, \overline{\mathrm{d}}} = -\) the SP loses the case
    and end up in disadvantaged position (-)
  \end{itemize}
\end{itemize}

Fairness:

\begin{itemize}

\item
  The customer can do nothing if the SP follows the protocol, because it
  will ultimately put him in advantaged position
  \(\sigma_{7, c, \mathrm{n}} = +\), otherwise, in case of the SP not
  following the protocol, the customer can start a dispute and terminate
  in non-disadvantaged position
  \(\sigma_{5, c, \overline{\mathrm{d}}} = •\).
\item
  The SP can follow the protocol and move to the non-disadvantaged
  position \(\sigma_{5, s, \mathrm{n}} = +\), or not follow the protocol
  and also end up at non-disadvantaged position
  \(\sigma_{5, s, \overline{\mathrm{n}}} = +\), but the second option
  puts him at risk of terminating the protocol at
  \(\sigma_{5, s, \overline{\mathrm{n}}} = +\), if the customer is
  rational and starts a dispute.
\end{itemize}

\paragraph{Step 6: pull
proof-of-provision}\label{step-6-pull-proof-of-provision}

Turn: Customer

SP has published results on time, then:

\begin{itemize}
\item
  Follows the protocol:

  \begin{itemize}

  \item
    \(\sigma_{6, c, \mathrm{n}} = -\) the customer gets hash of the
    results but not the results. Therefore, he is still in disadvantaged
    position(-).
  \item
    \(\sigma_{6, s, \mathrm{n}} = +\) the SP position hasn't changed(+).
  \end{itemize}
\item
  Starts a dispute:

  \begin{itemize}

  \item
    \(\sigma_{6, c, \mathrm{d}} = -\) the customer lose the case as the
    SP can prove the publication of proof-of-provision (-)
  \item
    \(\sigma_{6, s, \mathrm{d}} = +\) the SP win the case as the SP can
    prove the publication of proof-of-provision (+)
  \end{itemize}
\end{itemize}

Customer has timeouted, then:

\begin{itemize}
\item
  Follows the protocol:

  \begin{itemize}

  \item
    \(\sigma_{6, c, \overline{\mathrm{n}}} = -\) the customer ends up in
    disadvantaged position (-)
  \item
    \(\sigma_{6, s, \overline{\mathrm{n}}} = +\) the SP ends up in
    advantaged position as he received the payment but didn't spend his
    resources (+)
  \end{itemize}
\item
  Starts a dispute:

  \begin{itemize}

  \item
    \(\sigma_{6, c, \overline{\mathrm{d}}} = •\) the customer wins the
    case and end up in neutral position (•)
  \item
    \(\sigma_{6, s, \overline{\mathrm{d}}} = -\) the SP loses the case
    and end up in disadvantaged position (-)
  \end{itemize}
\end{itemize}

Fairness:

\begin{itemize}

\item
  The customer can follow the protocol to the position
  \(\sigma_{6, c, \mathrm{n}} = -\), which let's him move the protocol
  to non-disadvantaged termination position
  \(\sigma_{7, c, \mathrm{n}} = +\), or in case the SP haven't followed
  the protocol start a dispute and win the case
  \(\sigma_{6, c, \overline{\mathrm{d}}} = •\).
\item
  The SP can do nothing and end up in non-disadvantaged position
  \(\sigma_{6, s, \mathrm{n}} = +\), or
  \(\sigma_{6, s, \overline{\mathrm{n}}} = +\).
\end{itemize}

\paragraph{Step 7: retrieval of
results}\label{step-7-retrieval-of-results}

Turn: Customer

SP has published \textbf{correct} results on time:

\begin{itemize}
\item
  Following protocol:

  \begin{itemize}

  \item
    \(\sigma_{7, c, \mathrm{n}} = +\) the customer gets the correct
    results. Therefore, he moves to advantaged position (+).
  \item
    \(\sigma_{7, s, \mathrm{n}} = +\) the SP position hasn't changed
    (+).
  \end{itemize}
\item
  Starting a dispute:

  \begin{itemize}

  \item
    \(\sigma_{7, c, \mathrm{d}} = -\) the customer lose the case as the
    SP can prove the publication of proof-of-provision (-)
  \item
    \(\sigma_{7, s, \mathrm{d}} = +\) the SP win the case as the SP can
    prove the publication of proof-of-provision (+)
  \end{itemize}
\end{itemize}

SP has published \textbf{incorrect} results on time:

\begin{itemize}
\item
  Following protocol:

  \begin{itemize}

  \item
    \(\sigma_{7, c, \overline{\mathrm{n}}} = -\) customer end up in
    disadvantaged position, as he ends up with incorrect results (-)
  \item
    \(\sigma_{7, c, \overline{\mathrm{n}}} = +\) SP ends up in advantaged
    position as he received the payment but didn't spend his resources
    (+)
  \end{itemize}
\item
  Starting a dispute:

  \begin{itemize}

  \item
    \(\sigma_{7, c, \overline{\mathrm{d}}} = •\) customer wins the case
    and ends up in neutral position (•)
  \item
    \(\sigma_{7, c, \overline{\mathrm{d}}} = -\) SP lose the case and
    end up in disadvantaged position (-)
  \end{itemize}
\end{itemize}

Fairness:

\begin{itemize}

\item
  The customer can follow the protocol to the non-disadvantaged
  termination position \(\sigma_{7, c, \mathrm{n}} = +\), or in case the
  SP haven't followed the protocol start a dispute and win the case
  \(\sigma_{7, c, \overline{\mathrm{d}}} = •\).
\item
  The SP can do nothing and end up in non-disadvantaged position
  \(\sigma_{7, s, \mathrm{n}} = +\).
\end{itemize}

\subsection{Example scenarios}\label{example-scenarios}

The diagram below shows the path of positions when SP try to misbehave
and don't execute service after receiving the payment. The protocol ends
up in neutral to customer and disadvantaged to SP positions.

\begin{figure}[h!]
\includegraphics[width=9cm]{formal-misbehaviour-path.png}
\centering
\caption{Scenario of paths where the SP is misbehaving and the customer starts a dispute}
\label{fig:misbehaviour}
\end{figure}

Ultimately, the rational path for both parties is to follow the protocol
as shown in the diagram below.

\begin{figure}[h!]
\includegraphics[width=9cm]{formal-rational-path.png}
\centering
\caption{Scenario of path where both the customer and  the SP are behaving correctly}
\label{fig:well-behaviour}
\end{figure}

\subsection{Results}\label{results}

With the fairness definition stated in equation, and the assumptions
stated in \ref{assumptions}, our analysis indicate that the protocol
achieve fairness.

\section{Future work}
\subsection{Justice}\label{justice}

Justice is the one biggest obstacle in achieving system that is complied
with web3 manifests.

The possible directions for mitigation of such issue are to either (1)
replace Justice with decentralised autonomous organisations (DAO) like
proposed in Themis\cite{meng2019themis} or
Kleros\cite{lesaege2018kleros}; or (2) make it infeasible to provide
incorrect results.

The first approach is more feasible in the near future. It would require
creating large pool of experts in a field, that in case of dispute,
would receive all the proofs (POD, POP, as well as any other proofs
significant to the case) that could be queried by the experts in
zero-knowledge fashion, i.e., they could ask limited number of questions
to the proofs and getting yes/no answers. Keeping the case fully
confidential. The experts would be incentivised to participate in the
pool by the system of fees. Their honest behaviour would be incentivised
by the stake they would have to lock, and punishment they would get by
judging incorrectly, where the ``correctly'' is determined by the quorum
of votes.

The second approach is more philosophical and visionary. Suppose that
the service we are undertaking is fully computable. Then, it would be
possible by employing proofs of correctness of
computations\cite{ben2013snarks} to enforce that only correct
computations (hence correct services) are accepted. To do so the whole
service examination would have to be computable, which is hard to
achieve in settings where physical materials (like blood) are examined.
Concretely, the problem canes down to ``How to digitally represent
blood''. If we could represent urine, blood, saliva, or any other
physical material in binary format, and let the customer to take a
sample, discrete it and send it to the SP by himself, then the whole
chain of integrity could be ensured. Therefore, wrong service provision
would be infeasible.

\subsection{Cryptographically provable availability of
results}\label{cryptographically-provable-availability-of-results}

Currently, the SP has to publish the results into a p2p content storage
network (IPFS). The problem is that, nothing prevent such SP to publish
the content, receive the content identifier (cid), and immediately after
remove it from from it's local storage. In case of dispute the SP can
upload the content again, proving its availability. The SP has no
motivation to proceed with this kind of misbehaviour, other than puting
the customer in disadvantaged position caused by the lost dispute. We see
possible prevention of this misbehaviour by the usage of Filecoin---an
incentive layer on top of IPFS that guarantee the content availability
via economic incentivisations Filecoin\cite{benetfilecoin}. With the
help of Filecoin, the SP would be obligated to create a Filecoin deal
that guarantee the results availability until the deadline of the
transaction. Moreover, since Filecoin is a blockchain by itself, it
could play both roles of Message Board and Storage Network.

\subsection{Paying with cash}\label{paying-with-cash}

Without lose of generality the payment can be made with cash. The
customer can exchange the cash with SP together with delivering the
package. The PoD would contain an information that the
transaction has been paid with cash; therefore, Steps 1 and 2 could be
merged together and realised in one step. In case of dispute the payment
disclosure would be in included in PoD.

\subsection{Anonymous delivery}\label{anonymous-delivery}

Currently our framework require customer to deliver the \(pkg\) to SP
personally or via trusted person. However the system could be extended
to support anonymous delivery system as proposed in
Lelantos~\cite{altawy2017lelantos}.

\section{Conclusions}
In this paper, we have proposed a anonymity- preserving blockchain-based framework for local services provision. The framework can be employed by any local service provider to provide services without collecting any personal information. The payment is handled by anonymous cryptocurrencies, and the results are published on content based p2p network. The dispute can be settled by disclosing proofs to the justice. At any stage of the transaction, both parties are either in privelaged situation or can proof to the justice the misbehaviour of the other party.

\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
\bibliography{bibliography}
\EOD

\end{document}

\setcounter{page}{0}
\newcommand{\floor}[1]{\left\lfloor #1 \right\rfloor}
\newcommand{\ceil}[1]{\left\lceil #1 \right\rceil}

### 2022-02-22 access.tex
update access tex

@@
 provision. Our proposal uses blockchain for both anonymous payments and
-proofs of existence (so called Message Board), and content addressable
+proofs of existence (so called message board), and content addressable
 network (e.g.~IPFS) for results delivery.
@@
 
-People willing to take business action that may be risky or not yet
-fully legistlated, may be willing to receive the rist estimation and
-prediction of possible repercussions of such action.
-
-By exposing our identity to the lawer, we trust that he won't use that
+People willing to take business action that may be risky or not yet fully legislated, may be willing to receive the risk estimation and prediction of possible repercussions of such action.
+
+By exposing our identity to the lawyer, we trust that he won't use that
 information for harmful actions.
@@
 \item TTP-less: our protocol does not rely on trusted-third party to conduct transactions in fairly manner.
-Only in case of dispute the centralized justice is invlolved (the justice decentralisation is discussed in {[}{[}Future Work{]}{]}).
+Only in case of dispute the centralized justice is invlolved (the justice decentralisation is discussed in section ~\ref{future-work}.
 \item Physical materials: our protocol allows providing not only
@@
 properties that were rarely addressed together, and if so, the protocol
-based on TTP, and strong and impractial assumptions on banking system
-\cite{birjoveanu2015anonymity}, or didn't address the of conflict
-between parties \cite{altawy2017lelantos}.
+based on TTP, and strong and impractial assumptions on banking system~\cite{birjoveanu2015anonymity}, or didn't address the of conflict
+between parties~\cite{altawy2017lelantos}.
 
@@
 
-Authors of \cite{birjoveanu2015anonymity} proposed a
+Authors of~\cite{birjoveanu2015anonymity} proposed a
 fair-exchange of physical product and electronic payment protocol that
@@
 
-Themis\cite{meng2019themis} is a fair-exchange
+Themis~\cite{meng2019themis} is a fair-exchange
 protocol, which uses blockchain instead of TTP. It provide escrow
@@
 
-Lelanros\cite{altawy2017lelantos} is a blockchain-based anonymous
+Lelanros~\cite{altawy2017lelantos} is a blockchain-based anonymous
 physical delivery system. The anonymity is achieved by employing ToR's
@@
 
-Themis \cite{meng2019themis} besides providing fair-exchange protocol,
+Themis~\cite{meng2019themis} besides providing fair-exchange protocol,
 also offers a semi-autonomous decentralised dispute resolution system,
@@
 
-Kleros \cite{lesaege2018kleros} is a smart contract deployed on
+Kleros~\cite{lesaege2018kleros} is a smart contract deployed on
 Ethereum platform that mimics in decentralised and autonomous way how
@@
 Possible directions toward semi-autonomous decentralised resolution
-system are discussed in {[}{[}anonser/Future Work{]}{]}.
-
-\subsection{Proof to justice}
+system are discussed in section ~\ref{future-work}.
+
+\subsection{Proof to justice}\label{proof-of-justice}
 In case of dispute the customer can proof to the justice (police, court,
@@
 that the customer is anonymous, and therefore there is no personal
-information to start a dispute aginst. To mitigate this issue the SP is
+information to start a dispute against. To mitigate this issue the SP is
 always in advantaged postition, so that he has no reason to start a
-dispute. The idea described firther in {[}{[}Fairness analysis{]}{]}.
+dispute. The idea described further in section ~\ref{future-work}.
 
@@
 The second proof depend on the cryptocurrency implementation and is
-discussed further in section {[}{[}Payment for services{]}{]}.
-
-In case the SP has fulfulled the transaction and provide the results,
+discussed further section~\ref{payment-for-services}.
+
+In case the SP has fulfilled the transaction and provide the results,
 but the customer unjustly start a dispute, the SP is secured by the
-proof-of-provision (PoP) he's published on the message board
-({[}{[}Message Board{]}{]}).
+proof of provision (PoP) he has published on the message board (described in section ~\ref{message-board}.
 
@@
 \item
-  \(\mathrm{cid}\) - content identifier as specified in {[}{[}Storage
-  Network{]}{]}.
+  \(\mathrm{cid}\) - content identifier as specified in section ~\ref{storage-network}.
 \item
@@
 Depending on the context the platform of achieving it is called bulletin
-board \cite{achenbach2015improved} or message board
-\cite{hinarejos2019solution} or trusted timestamping
-\cite{gipp2015decentralized}. In this work we call it Message Board.
+board~\cite{achenbach2015improved} or message board~\cite{hinarejos2019solution} or trusted timestamping~\cite{gipp2015decentralized}. In this work we call it message board.
 
@@
 but also other similary working centralized trusted third parties
-including the Message Board.
+including the message board.
 
 We let keep the protocol general enough to let the implementator use any
-existing technology to provide Message Board service, with the
+existing technology to provide message board service, with the
 assumption that it's decentralised and supports subscribing for the
@@
 philosophy, psychology, sociology, and legal. The multidisciplinary
-nature leads to ambigous definitions\cite{smith2011information}. For
+nature leads to ambigous definitions~\cite{smith2011information}. For
 the purpose of our work we rely on more concrete definitions,
@@
 rather than dichotomous classification. One method of quantifying level
-of anonymity is proposed in k-anonymity \cite{sweeney2002k}. It measure
+of anonymity is proposed in \textit{k}-anonymity~\cite{sweeney2002k}. It measure
 the user's anonymity by the number of other users from whom the user can
-not be distinguished. Concreatly, the user is \emph{k}-anonymous if his
-actions are equaly likely associated with \emph{k}-1 other users. The
-larger \emph{k}, the higher anonimity.
+not be distinguished. Concretely, the user is \textit{k}-anonymous if his
+actions are equally likely associated with \textit{k}-1 other users. The
+larger \textit{k}, the higher anonymity.
 
 The cryptocurrencies that natively support anonymous transactions are
-Monero \cite{van2013cryptonote} (via Bulletproofs
-\cite{Bulletpr14, bunz2018bulletproofs}) and ZCash
-\cite{sasson2014zerocash} (via zk-SNARK \cite{ben2013snarks}), Grin
-\cite{fuchsbauer2019aggregate} (via Mimblewimble \cite{httpsdow19}).
+Monero~\cite{van2013cryptonote} (via Bulletproofs~\cite{Bulletpr14, bunz2018bulletproofs}) and ZCash~\cite{sasson2014zerocash} (via zk-SNARK~\cite{ben2013snarks}), Grin~\cite{fuchsbauer2019aggregate} (via Mimblewimble~\cite{httpsdow19}).
 
@@
 CoinJoin \cite{CoinJoin41}) that literaly gather together users into an
-``anonimimity set'', which then collude together in order to launder the
-transactions, in such a way that to a observer the likelyhood of the
+\textit{anonymity set}, which then collude together in order to launder the
+transactions, in such a way that to a observer the likelihood of the
 sender of each transaction was equiprobable for any user from the
-anonimity set.
-
-Some systems guarantee pseudonomity rather than anonimity. Pseudonomity,
+anonymity set.
+
+Some systems guarantee pseudonomity rather than anonymity. Pseudonomity,
 allows uses to hide their real identity behind the pseudonim. Despite
@@
 
-\subsection{Payment for services}
+\subsection{Payment for services}\label{payment-for-services}
 Transactions between customers and SP have to be somehow pegged in order
@@
 
-\subsection{Storage network}
+\subsection{Storage network}\label{storage-network}
 Once the SP finish its service, he has to provide the results to the
@@
 (\cite{shahid2020blockchain, wang2019auditable, chen2017improved, Usageide95})
-is to publish the data to the IPFS \cite{benet2014ipfs}---a content
-adressable peer-to-peer storage network---and publish to a blockchain
+is to publish the data to the IPFS \cite{benet2014ipfs}—a content
+adressable peer-to-peer storage network—and publish to a blockchain
 just a content identifier (cid) that uniquely points to the content
@@
 We could use one blockchain to achieve all of these three roles: (i)
-Anonymous payments; (ii) Message Board; (iii) Storage network.
-
-As the Message board could be achieved by most of the blockchanis, the
+anonymous payments; (ii) message board; (iii) storage network.
+
+As the message board could be achieved by most of the blockchanis, the
 anonymous payments isn't so prevalent, and provable storage network is a
@@
   Tornado Cash \cite{pertsev2019tornado}.
-\item Message Board: Stampery \cite{de2016stampery}, Proof of Existence
+\item Message board: Stampery \cite{de2016stampery}, Proof of Existence
   \cite{proofofexistence} (Bitcoin blockchain), Chainpoint
@@
   SPs accept payment for services via anonymous cryptocurrencies like
-  Monero, Grin or ZCash as described in {[}{[}Payment for
-  services{]}{]}.
+  Monero, Grin or ZCash as described in section ~\ref{payment-for-services}.
 \item
   Justice accepts as a evidence in dispute proof of payment of
-  cryptocurrencies as described in {[}{[}Proof to Justice{]}{]}.
-\end{itemize}
-
-\subsection{Protocol description}
+  cryptocurrencies as described in section~\ref{proof-of-justice}.
+\end{itemize}
 
@@
 
-\[\mathrm{pkg} \equiv (\mathrm{materials}, \mathrm{key})\]
+$$\mathrm{pkg} \equiv (\mathrm{materials}, \mathrm{key})$$
 
@@
 
-\item
-  \(\mathrm{materials}\) - are the materials needed to provide the
+\item $\mathrm{materials}$ - are the materials needed to provide the
   service on. For example, sample of urine, blood, stool, saliva; legal
@@
   evidence depending on the service.
-\item
-  \(\mathrm{key}\) - symmetric key used to encrypt and decrypt the
+\item $\mathrm{key}$ - symmetric key used to encrypt and decrypt the
   results.
@@
 
-\[\mathrm{PoD} \equiv (\mathrm{T}_\mathrm{issue}, \mathrm{T}_\mathrm{pay}, \mathrm{T}_\mathrm{provide}, \mathrm{nonce}, \mathrm{sig}_\mathrm{SP})\]
+$$\mathrm{PoD} \equiv (\mathrm{T}_\mathrm{issue}, \mathrm{T}_\mathrm{pay}, \mathrm{T}_\mathrm{provide}, \mathrm{nonce}, \mathrm{sig}_\mathrm{SP})$$
 
@@
 
-\item
-  \(\mathrm{T}_\mathrm{issue}\) - time at which the PoD is issued.
-\item
-  \(\mathrm{T}_\mathrm{pay}\) - deadline to pay for the transaction.
-\item
-  \(\mathrm{T}_\mathrm{provide}\) - deadline to provide the service
+\item $\mathrm{T}_\mathrm{issue}$ - time at which the PoD is issued.
+\item
+  $\mathrm{T}_\mathrm{pay}$ - deadline to pay for the transaction.
+\item
+  $\mathrm{T}_\mathrm{provide}$ - deadline to provide the service
   results.
-\item
-  \(\mathrm{nonce}\) - randomly generated number uniquely identifying
+\item $\mathrm{nonce}$ - randomly generated number uniquely identifying
   the transaction.
+\item $\mathrm{sig}_\mathrm{SP}$ - the SP's signature guaranteeing
+  non-repudiation.
+\end{itemize}
+
+also:
+
+\(\mathrm{T}_\mathrm{issue} < \mathrm{T}_\mathrm{pay} < \mathrm{T}_\mathrm{provide}\)
+
+\paragraph{Proof-of-Provision}\label{proof-of-provision}
+
+\[\mathrm{PoP} \equiv (\mathrm{cid}, \mathrm{nonce}, \mathrm{sig}_\mathrm{SP})\]
+
+where:
+
+\begin{itemize}
+
+\item
+  \(\mathrm{cid}\) - content identifier as specified in ~\ref{storage-network}.
+\item
+  \(\mathrm{nonce}\) - the value uniquely identifying the transaction
+  previosuly generated in PoD.
 \item
@@
 
-also:
-
-\(\mathrm{T}_\mathrm{issue} < \mathrm{T}_\mathrm{pay} < \mathrm{T}_\mathrm{provide}\)
-
-\paragraph{Proof-of-Provision}\label{proof-of-provision}
-
-\[\mathrm{PoP} \equiv (\mathrm{cid}, \mathrm{nonce}, \mathrm{sig}_\mathrm{SP})\]
-
-where:
-
-\begin{itemize}
-
-\item
-  \(\mathrm{cid}\) - content identifier as specified in {[}{[}Storage
-  Network{]}{]}.
-\item
-  \(\mathrm{nonce}\) - the value uniquely identifying the transaction
-  previosuly generated in PoD.
-\item
-  \(\mathrm{sig}_\mathrm{SP}\) - the SP's signature guaranteeing
-  non-repudiation.
-\end{itemize}
-
 \paragraph{Payment attestation}\label{payment-attestation}
@@
 Payment attestation proves that the customer did the payment. Since the
-evidences depends on the particular blockchain (see Section
-{[}{[}Payment for services{]}{]}). We refer to them symbollicaly as
+evidences depends on the particular blockchain (see section ~\ref{payment-for-services}). We refer to them symbollicaly as
 \(attestation\).
@@
 In return, the SP issue an Proof-of-Delivery (POD) confirmation. The
-confirmation encompasses timestamp, invoice (see section {[}{[}Payment
-for services{]}{]}), and signature.
+confirmation encompasses timestamp, invoice (see section \ref{payment-for-services}), and signature.
 
@@
 customer should pay for the invoice according to selected cryptocurrency
-system (see section {[}{[}Payment for services{]}{]}).
+system (see section~\ref{payment-for-services}).
 
@@
 \item
-  Once published, the results are avaiable to the customer in the
+  Once published, the results are available to the customer in the
   content storage. The idea of guaranteeing it cryptographically is
-  discussed in {[}{[}Future Work{]}{]}.
+  discussed in section ~\ref{future-work}.
 \item
@@
 
-\section{Future work}
+\section{Future work}\label{future-work}
 \subsection{Justice}\label{justice}
 
-Justice is the one biggest obstacle in achieving system that is complied
-with web3 manifests.
+Justice is the one biggest obstacle in achieving system that complies with Web3 postulates~\cite{Web3Wiki71}.
 
@@
 replace Justice with decentralised autonomous organisations (DAO) like
-proposed in Themis\cite{meng2019themis} or
-Kleros\cite{lesaege2018kleros}; or (2) make it infeasible to provide
+proposed in Themis~\cite{meng2019themis} or
+Kleros~\cite{lesaege2018kleros}; or (2) make it infeasible to provide
 incorrect results.
@@
 possible by employing proofs of correctness of
-computations\cite{ben2013snarks} to enforce that only correct
+computations~\cite{ben2013snarks} to enforce that only correct
 computations (hence correct services) are accepted. To do so the whole
@@
 incentive layer on top of IPFS that guarantee the content availability
-via economic incentivisations Filecoin\cite{benetfilecoin}. With the
+via economic incentivisations Filecoin~\cite{benetfilecoin}. With the
 help of Filecoin, the SP would be obligated to create a Filecoin deal
@@
 transaction. Moreover, since Filecoin is a blockchain by itself, it
-could play both roles of Message Board and Storage Network.
+could play both roles of message board and Storage Network.
 

### 2022-02-23 access.tex
update anonimity diagram and protocol description

@@
 \tfootnote{This paragraph of the first footnote will contain support 
-information, including sponsor and financial support acknowledgment. For 
+information, including sponsor and financial support acknowledgement. For 
 example, ``This work was supported in part by the U.S. Department of 
@@
 \begin{abstract}
-Service providers like: lawyers, laboratories, auditors, or banks, to
-provide services, require customers to submit data that is often
-associated with their personal information. This situation expose
-customers to privacy risk. However, most of the service providers use
-the personal information merely for logistic operations like payments
-and communication, and could provide services anonymously if other means
-of logistics would exists.
-
-We propose a framework for coordingating local anonymous service
-provision. Our proposal uses blockchain for both anonymous payments and
-proofs of existence (so called message board), and content addressable
-network (e.g.~IPFS) for results delivery.
-
-The framework can be employed by any local service provider to provide
+Service providers like lawyers, laboratories, auditors, or banks, to
+provide services, require customers to submit data often
+associated with their personal information. This situation exposes
+customers to privacy risks. However, most service providers use personal information merely for logistic operations like payments
+and communication and could provide services anonymously if other means of logistics exist.
+
+We propose a framework for coordinating local anonymous service
+provision. Our proposal uses blockchain for both anonymous payments and proofs of existence (so-called message board) and content-addressable network (e.g.~IPFS) for results delivery.
+
+A local service provider can employ our framework to provide
 services without collecting any personal information. Possible
 applications for this framework include anonymous clinical drug testing,
-steroid testing, parenting testing, anonymous legal advices, or
+steroid testing, parenting testing, anonymous legal advice, or
 anonymous financial trustworthiness evaluation.
@@
 incorrect results, the customer can disclose the whole interaction and
-prove to the justice (police or court) the misbehaviour of the service
+prove to justice (police or court) the misbehaviour of the service
 provider.
 
-We analyse the protocol in the context of fairness, and discuss further
-extensions to anonymous delivery system, payment with cash, and
-decentralized conflict resolution system.
-
-Our framework can potentially enable variety of services that for many
-customers base on unacceptable trust assumptions to the SP.
+We analyse the protocol in the context of fairness and discuss further
+extensions to an anonymous delivery system, payment with cash, and
+decentralised conflict resolution system.
+
+Our framework can enable various services currently based on unacceptable trust assumptions to the SP.
 \end{abstract}
@@
 \begin{keywords}
-Blockchain, anonimity, fair-exchange, physical delivery
+Blockchain, anonymity, fair-exchange, physical delivery
 \end{keywords}
@@
 \section{Introduction}
-Service providers (SP) like: lawyers, laboratories, auditors, or banks,
-to provide services, require data that is often associated with user
+Service providers (SP) like lawyers, laboratories, auditors, or banks,
+to provide services, require data that is often associated with the user
 identity.
 
-Providing personal information exposes users to privacy risk,
-i.e.~potential loss of control over personal
+Providing personal information exposes users to privacy risks,
+i.e. potential loss of control over personal
 information~\cite{smith2011information}.
 
-Such user information can be then used deliberately or unintentionally
-(e.g, by theft) for: insider disclosure, unauthorized access, or
+Such user information can be used deliberately or unintentionally
+(e.g., by theft) for insider disclosure, unauthorised access, or
 commercial gains. For example, by reselling it to marketers, financial
 institutions, other businesses, government agencies, or even
-cybercriminals. Which in turn can lead to profiled advertisements, or
+cybercriminals. Which in turn can lead to profiled advertisements or
 criminal activities like identity theft or illegal tracking and
@@
 
-Important individuals like top government, influencers, or celebrities
-are especially vulnerable to this kind of attacks as exposure of their
+Important individuals like top government, influencers, or celebrities are especially vulnerable to this kind of attack as exposure of their
 health records, purchase habits, or legal documents can threaten their
@@
 trust assumptions and security of IT system. However, most of the SP
-don't need the personal information for any other reasons than payment,
+do not need the personal information for any other reason than payment
 or communication, which should be considered secondary compared to
-primary matter that is service provision.
-
-It would be desirable if the user could keep its identity private, while
-service provider still provide its services. This could lead to reduced
+actual service provision.
+
+It would be desirable for the user to keep its identity private while the service provider still provides its services. This could lead to reduced
 trust that users have to put on SP and less responsibility borne by SP.
@@
 
-Patients willing to take steroid test, drug test, venereal diseases
-test, paternity test --- have strong incentive to keep the whole
-procedure private. Merely the fact that they took the test --- without
-exposing the results --- is suggestive enought to act as a premise in
+Patients willing to take a steroid test, drug tests, venereal diseases
+test, paternity test — have strong incentive to keep the whole
+procedure private. Merely the fact that they took the test — without
+exposing the results — is suggestive enough to act as a premise in
 case of a conflict.
 
-Especially celebrites, politicans and public persona are exposed to this
-kind of probems as such precedent can judge their future career.
+Especially celebrities, politicians and public persona are prone to this kind of problem as such precedent can negatively influence their future career.
 
 Currently, they have to risk that their materials and results are stored
-securely and keept in private from any any unathorized actor (both
+securely and kept in private from any unauthorised actor (both
 curious employee, and malicious attacker).
 
-Our protocol allows taking such tests anonymously, and therefore getting
+Our protocol allows taking such tests anonymously and therefore getting
 rid of the strong trust assumption put on the laboratories and their IT
@@
 practical, and strongly anonymous framework that does not rely on
-centralized trusted-third party, but on decentralized blockchain and
+centralised trusted-third party, but on decentralised blockchain and
 distributed content addressable networking.
@@
 \item TTP-less: our protocol does not rely on trusted-third party to conduct transactions in fairly manner.
-Only in case of dispute the centralized justice is invlolved (the justice decentralisation is discussed in section ~\ref{future-work}.
+Only in case of dispute the centralised justice is invlolved (the justice decentralisation is discussed in section ~\ref{future-work}.
 \item Physical materials: our protocol allows providing not only
@@
     \item The source cabinet and delivery cabinet exists, and in both the product access is protected by password.
-    \item Delivery cabinet is equppted with a video camera that records the moment when the customer opens the package, and provide a way to submit the video to TTP in case of a dispute. 
-    \item Delivery agent exist and is trusted. 
+    \item Delivery cabinet is equipped with a video camera that records the moment when the customer opens the package, and provide a way to submit the video to TTP in case of a dispute. 
+    \item There exists a trusted delivery agent.
     \item Communication channels between parties provides anonymity.
@@
 protocol, which uses blockchain instead of TTP. It provide escrow
-services for secure exchanging between cryptocurrencies and digital
-goods.
-
-Authors highlight that a widely-used atomic exchange mechanism HTLC
-(Hashed Time-lock Contract) is vulnerable to denial of service (DoS)
-attacks. While Multi-Signature Schemes depends on the Trusted Third
-Party (TTP) making them vulnerable to collusion attacks. Such TTP can
-collude with one party and take the locked funds. It can also refuse
-settling disputes and lock the hosted funds.
-
-Themis is a decentralized system that provides an escrow and dispute
-resolution. It claims to satisfy following requirements:
-
-\begin{itemize}
-    \item Fairness: Either both seller and buyer obtain all the goods, or they both obtain nothing.
-    \item Security: The funds are locked until the transaction is completed.
-    \item Passivity: If no dispute arise, the third-party does not need to involve in the transaction.
-    \item Correctness: Transactions and disputes are executed according to a priori agreed protocol rules.
-    \item Dependability: There is no single point of failure vulnerable to DoS attack.
-    \item Privacy: If the dispute does not arise, the third-party does not know if the transaction completes. If the dispute arises, only the related parties are aware of it.    
-\end{itemize}
+services for secure exchanging between cryptocurrencies and digital goods, and decentralised dispute resolution system for resolving conflicts.
 
@@
 \(n=2t+1\) secret shares using Shamir Secret Shamir protocol, where
-\(n\) is the number of mediators that participate in the decentralized
+\(n\) is the number of mediators that participate in the decentralised
 network, and \(t+1\) becomes the threshold of sufficient number of
@@
 Next, both Alice and Bob, take their key shares, and encrypt each
-\(i\)-th key share using public key of \(i\)-th mediator. As a result
+\textit{i}-th key share using public key of \textit{i}-th mediator. As a result
 Alice's secret \(x_A\) becomes \({c^A_1, c^A_2,...,c^A_n}\), and Bob's
@@
 
-In case of dispute, the decentralized network of mediators settle the
+In case of dispute, the decentralised network of mediators settle the
 conflict and grand one winning party, the other party secret key,
@@
 
-The honesty of mediators is achieved by the monetary incentivization and
+The honesty of mediators is achieved by the monetary incentivisation and
 reputation system.
@@
 However, the system doesn't achieve full anonimity but pseudonimity (see
-section \ref{pseudo-anon}). Also the protocol does not
-cover the case of dispute between the customer and the SP.
+section~\ref{pseudo-anon}). Also the protocol does not
+cover the case of dispute between the parties.
 
@@
 in a voting and deciding whether a party misbehaved. The honesty of
-mediators is achieved by the monetary incentivization and reputation
+mediators is achieved by the monetary incentivisation and reputation
 system.
@@
 
-Bitcoin introduced a way of decentralizing not only the currency system,
-but also other similary working centralized trusted third parties
+Bitcoin introduced a way of decentralising not only the currency system,
+but also other similary working centralised trusted third parties
 including the message board.
@@
 \subsection{Pseudo-anonymous vs anonymous blockchain}
-Privacy is a concept used in almost all kinds of social sciences like
-philosophy, psychology, sociology, and legal. The multidisciplinary
-nature leads to ambigous definitions~\cite{smith2011information}. For
-the purpose of our work we rely on more concrete definitions,
-i.e.~confidentality and anonimity.
-
-Confidentality is the ability to hide the details of an action from
-others. Or we can say, that the system guarantee confidentality if for
-all observers everything they can say about the action is the fact that
-it happened and nothing more.
-
-Anonymity is a the ability to hide one identity from others. More
-precisely, the unability to correlate actions performed within the sytem
-to the identity of the user. Or we can say, that the system guarantee
-anonimity if for all observers the actions are equally likely to be
-associated with any user of the system. However, anonimity is a spectrum
-rather than dichotomous classification. One method of quantifying level
-of anonymity is proposed in \textit{k}-anonymity~\cite{sweeney2002k}. It measure
-the user's anonymity by the number of other users from whom the user can
-not be distinguished. Concretely, the user is \textit{k}-anonymous if his
-actions are equally likely associated with \textit{k}-1 other users. The
-larger \textit{k}, the higher anonymity.
-
-The cryptocurrencies that natively support anonymous transactions are
-Monero~\cite{van2013cryptonote} (via Bulletproofs~\cite{Bulletpr14, bunz2018bulletproofs}) and ZCash~\cite{sasson2014zerocash} (via zk-SNARK~\cite{ben2013snarks}), Grin~\cite{fuchsbauer2019aggregate} (via Mimblewimble~\cite{httpsdow19}).
-
-There are also techniques that can be deployed on non-anonymous
-blockchains, the so called mixers: Ethereum's Tornado
-Cash\cite{pertsev2019tornado}, Bitcoin's Wasabi\cite{WasabiWa56} (uses
-CoinJoin \cite{CoinJoin41}) that literaly gather together users into an
-\textit{anonymity set}, which then collude together in order to launder the
-transactions, in such a way that to a observer the likelihood of the
-sender of each transaction was equiprobable for any user from the
-anonymity set.
-
-Some systems guarantee pseudonomity rather than anonymity. Pseudonomity,
-allows uses to hide their real identity behind the pseudonim. Despite
-the whole system is transparent and allows linking actions to one
-identity, the system is considered anonymous as long as the link between
-pseudonym and real identity is secret. This assumption is hard to
-satisfy in practice, as the KYC (Know You Customer) and AML (Anti Money
-Laundering) regulations require users to reveal their real identity on
-most of the cryptocurrencies exchanges. This makes the anonymity of the
-user dependent on the security of the IT system. Moreover, some
-correlations can be infered merely by the analysis of transactions
-\cite{androulaki2013evaluating, ober2013structure}. Most of the
-blockchains, including Bitcoin and Ethereum achieve this kind of
-pseudonimity.
-
-The relations between these terms are ilustrated in the figure~\ref{fig:anonimity-confidentality}.
+
+Privacy is a concept used in almost all kinds of social sciences like philosophy, psychology, sociology, and legal.
+The multidisciplinary nature leads to ambigous definitions~\cite{smith2011information}.
+For the purpose of our work we rely on more concrete definitions, i.e.~confidentality and anonimity.
+
+Confidentality is the ability to hide the details of an action from others.
+Or we can say, that the system guarantee confidentality if for all observers everything they can say about the action is the fact that it happened and nothing more.
+
+Anonymity is a the ability to hide one identity from others.
+More precisely, the unability to correlate actions performed within the sytem to the identity of the user.
+Or we can say, that the system guarantee anonimity if for all observers the actions are equally likely to be associated with any user of the system.
+However, anonimity is a spectrum rather than dichotomous classification.
+One method of quantifying level of anonymity is proposed in \textit{k}-anonymity~\cite{sweeney2002k}.
+It measure the user's anonymity by the number of other users from whom the user can not be distinguished.
+Concretely, the user is \textit{k}-anonymous if his actions are equally likely associated with \textit{k}-1 other users.
+The larger \textit{k}, the higher anonymity.
+
+There are also techniques that can be deployed on non-anonymous blockchains, the so called mixers that literaly gather together users into an \textit{anonymity set}, which then collude together in order to launder the transactions, in such a way that to a observer the likelihood of the sender of each transaction was equiprobable for any user from the anonymity set.
+
+Some systems guarantee pseudonomity rather than anonymity.
+Pseudonomity, allows uses to hide their real identity behind the pseudonim.
+Despite the whole system is transparent and allows linking actions to one identity, the system is considered anonymous as long as the link between pseudonym and real identity is secret.
+This assumption is hard to satisfy in practice, as the KYC (Know You Customer) and AML (Anti Money Laundering) regulations require users to reveal their real identity on most of the cryptocurrencies exchanges.
+This makes the anonymity of the user dependent on the security of the IT system.
+Moreover, some correlations can be infered merely by the analysis of transactions \cite{androulaki2013evaluating, ober2013structure}.
+
+The relations between these terms are ilustrated in the figure~\ref{fig:anonymity-diagram}.
 
 \begin{figure}[h!]
-\caption{Scenario of path where both the customer and  the SP are behaving correctly}
+\caption{}
 \centering
-\includegraphics[width=9cm]{anonimity-confidentality.png}
-\label{fig:anonimity-confidentality}
+\includegraphics[width=9cm]{anonymity-diagram.png}
+\label{fig:anonymity-diagram}
 \end{figure}
 
-People who call tracable and linkable blockchains to be anonymous base
-on a strong assumption that the identification is impossible, infeasable
-or at least plausably unlikely. We require the system for anonymous
-payments to satisfy anonymilty via untraceability or unlinkability. We
-don't pay much attention to confidentiality as it doesn't bring much
-value to the protocol.
+Let us assume the Alice to be the customer willing to keep her identity private (anonymous) and Bob be the public SP.
+Alice controls two blockchain addresses 1 and 2, the connection between her real identity and the first address was compromised, and therefore the identification is possible, the connection between the second pseudonym is still unknown therefore anonymous.
+Alice takes two actions; the first one from the compromised address and the second one from anonymous one.
+The first action is confidential; therefore even though the psudonym has been compromised the action can not be associated with the Alice.
+The second action is transparent, therefore the Alice's anonymity is maintained as long as the connection to the second pseudonym is concealed.
+
+The privacy-preserving blockchains are the ones that maintain anonymity via untraceability and unlikability, not via assumption that the connection between an address and the real identity is concealed.
+
+Blockchains that natively support confidential transactions are
+Monero~\cite{van2013cryptonote} (via Ring Signatures~\cite{cryptoeprint:2015:1098} and Bulletproofs~\cite{Bulletpr14, bunz2018bulletproofs}) and ZCash~\cite{sasson2014zerocash} (via zkSNARK~\cite{ben2013snarks}), Grin~\cite{fuchsbauer2019aggregate} (via Mimblewimble~\cite{httpsdow19}).
+
+Overly techniques that achieve anonymity on top of non-privacy-preserving blockchains are: Ethereum's Tornado Cash\cite{pertsev2019tornado} (via zkSNARK~\cite{groth2016size} and MiMC~\cite{albrecht2016mimc}), Bitcoin's Wasabi\cite{WasabiWa56} (via CoinJoin \cite{CoinJoin41}).
 
@@
 anonymous payments isn't so prevalent, and provable storage network is a
-functionality of a few specialized blockchains.
+functionality of a few specialised blockchains.
 
@@
 
-\subsubsection{Step 1: Package delivery}\label{step-1-package-delivery}
-
-They protocol start once the customer delivers package \(\mathrm{pkg}\)
-to SP.
-
-In return, the SP issue an Proof-of-Delivery (POD) confirmation. The
-confirmation encompasses timestamp, invoice (see section \ref{payment-for-services}), and signature.
+\paragraph{Step 0: Preparation}\label{step-0-preparation}
+
+The customer collects all the $\mathrm{materials}$ required by the SP, generate an encryption $\mathrm{key}$ print it on a paper as a QR code, and pack them together into a package $\mathrm{pkg}$.
+
+\paragraph{Step 1: Package delivery}\label{step-1-package-delivery}
+
+They protocol starts once the customer delivers package $\mathrm{pkg}$ and the SP accepts its content.
+In return, the SP issue a $\mathrm{PoD}$ with agreed upfront payment deadline $\mathrm{T}_\mathrm{pay}$, service provision deadline $\mathrm{T}_\mathrm{provide}$ and current time $\mathrm{T}_\mathrm{issue}$.
+Also, the $\mathrm{PoD}$ consist of randomly generated unique number $\mathrm{nonce}$, which will allow associating all actions related to the transaction throughout the protocol.
+Finally, the digital signature $\mathrm{sig}_\mathrm{SP}$ on the $\mathrm{PoD}$ created with the SP's secret key guarantee non-repudiation.
+
+We assume this step to be fully physical, that is, $\mathrm{pkg}$ consist of physical materials, $\mathrm{PoD}$ is in a form of e.g., QR code printed on paper receipt.
+
+$\mathrm{PoD}$ could be published on a message board (similarly to $\mathrm{PoP}$); however, since the $\mathrm{pkg}$ is delivered personally or via trusted person, the confirmation can be issued in person as well.
+If we would like to hire a courier to deliver our $\mathrm{pkg}$, then the $\mathrm{PoD}$ would have to be published on message board (further extension to anonymous delivery system is discussed in section \ref{future-work}).
 
@@
 
-\subsubsection{Step 2: Payment}\label{step-2-payment}
-
-Having POD, SP can not reject receiving the package. At this point the
-customer should pay for the invoice according to selected cryptocurrency
-system (see section~\ref{payment-for-services}).
-
-In return, the customer receives the attestation that should be used in
-case of a dispute.
+\paragraph{Step 2: Payment}\label{step-2-payment}
+
+Having the PoD issued, the SP can not reject receiving the package. At this point the
+customer should pay for the transaction with agreed upfront cryptocurrency system (see section~\ref{payment-for-services}).
+
+In return, the customer receives the $\mathrm{attestation}$ that should be disclosed in case of a dispute.
 
@@
 
-\subsubsection{Step 3: Provision of
+\paragraph{Step 3: Provision of
 service}\label{step-3-provision-of-service}
@@
 
-\subsubsection{Step 4: Results
+\paragraph{Step 4: Results
 publication}\label{step-4-results-publication}
@@
 
-\subsubsection{Step 5: Proof of provision
+\paragraph{Step 5: Proof of provision
 publication}\label{step-5-proof-of-provision-publication}
@@
 
-\subsubsection{Step 6: Proof-of-provision
+\paragraph{Step 6: Proof-of-provision
 notification}\label{step-6-proof-of-provision-notification}
@@
 
-\subsubsection{Step 7: Results download}\label{step-7-results-download}
+\paragraph{Step 7: Results download}\label{step-7-results-download}
 
@@
 
-\subsubsection{Model}\label{model}
+\subsection{Model}\label{model}
 
@@
   \forall_{party \in parties}\forall_{\mathrm{step} \in \mathrm{steps}} \mathrm{can\ move\ the\ protocol\ \\
-  to\ the\ non\-disadvantaged\ position} 
+  to\ the\ non\ disadvantaged\ position} 
 \end{align*}
 
-\paragraph{Assumptions}\label{assumptions}
+\subsection{Assumptions}\label{assumptions}
 
@@
   Losing the dispute leads to punishment that is greater than any
-  reward, which leads to disadvantaged position. Hence, the rational
+  reward, which leads to disadvantaged position (-). Hence, the rational
   customer won't start a dispute that he is not sure to win.
 \item
-  Winning the dispute leads to neutral position (•)
+  Winning the dispute leads to neutral position (•).
 \item
@@
 
-\subsubsection{Steps}\label{steps}
+\subsection{Steps}\label{steps}
 
@@
 The possible directions for mitigation of such issue are to either (1)
-replace Justice with decentralised autonomous organisations (DAO) like
+replace justice with decentralised autonomous organisations (DAO) like
 proposed in Themis~\cite{meng2019themis} or

### 2022-02-24 access.tex
docs: update

@@
 \usepackage{caption}
+\usepackage[english]{babel}
+\newtheorem{theorem}{Theorem}
+\newtheorem{definition}{Definition}
 \usepackage{textcomp}
@@
 (e.g., by theft) for insider disclosure, unauthorised access, or
-commercial gains. For example, by reselling it to marketers, financial
-institutions, other businesses, government agencies, or even
-cybercriminals. Which in turn can lead to profiled advertisements or
-criminal activities like identity theft or illegal tracking and
-surveillance~\cite{smith2011information}.
-
-Important individuals like top government, influencers, or celebrities are especially vulnerable to this kind of attack as exposure of their
-health records, purchase habits, or legal documents can threaten their
-reputation, position, or can be used for blackmailing.
-
-The guarantee of the privacy of the data is often based merely on a
-trust assumptions and security of IT system. However, most of the SP
-do not need the personal information for any other reason than payment
-or communication, which should be considered secondary compared to
-actual service provision.
-
-It would be desirable for the user to keep its identity private while the service provider still provides its services. This could lead to reduced
-trust that users have to put on SP and less responsibility borne by SP.
-
-\subsection{Use cases}
-\paragraph{Anonymous clinical tests} \label{anonymous-clinical-tests}
-
-Patients willing to take a steroid test, drug tests, venereal diseases
+commercial gains.
+For example, by reselling it to marketers, financial institutions, other businesses, government agencies, or even cybercriminals.
+Which in turn can lead to profiled advertisements or criminal activities like identity theft or illegal tracking and surveillance~\cite{smith2011information}.
+
+Important individuals like top government, influencers, or celebrities are especially vulnerable to this kind of attack as exposure of their health records, purchase habits, or legal documents can threaten their reputation, position, or can be used for blackmailing.
+
+The guarantee of the privacy of the data is often based merely on a trust assumptions and security of IT system.
+However, most of the SP do not need the personal information for any other reason than payment or communication, which should be considered secondary compared to actual service provision.
+
+It would be desirable for the user to keep its identity private while the service provider still provides its services.
+This could lead to reduced trust that users have to put on SP and less responsibility borne by SP.
+
+Example services that would benefit from anonymous services are:
+\begin{itemize}
+    \item Patients willing to take a steroid test, drug tests, venereal diseases
 test, paternity test — have strong incentive to keep the whole
@@
 
-Especially celebrities, politicians and public persona are prone to this kind of problem as such precedent can negatively influence their future career.
-
-Currently, they have to risk that their materials and results are stored
-securely and kept in private from any unauthorised actor (both
-curious employee, and malicious attacker).
+Especially celebrities, politicians and public figures are prone to this kind of problem as such precedent can negatively influence their future career.
+
+Currently, they have to risk that their personal details, materials, and results are stored securely and kept in private from any unauthorised actor (both curious employee, and malicious attacker).
 
@@
 systems.
-
-\paragraph{Anonymous lawyer consultations} \label{anonymous-lawyer-consultations}
-
-People willing to take business action that may be risky or not yet fully legislated, may be willing to receive the risk estimation and prediction of possible repercussions of such action.
+\item People willing to take business action that may be risky or not yet fully legislated, may be willing to receive the risk estimation and prediction of possible repercussions of such action.
 
@@
 Our protocol would allow taking such advices anonymously, and therefore
-getting rid of the strong trust assumption put on the laboratories and
-their IT systems.
-
-\subsection{Contribution}
+getting rid of the strong trust assumption put on the lawyers and their IT systems.
+\end{itemize}
+
+We propose a framework for anonymously provisioning services that require delivery of physical materials.
+A service provider employing our framework can provide services without collecting any personal information from customers.
+
+In case of dispute, either due to exceeding deadlines or providing
+incorrect results, the customer can disclose the whole interaction and
+prove to justice (police or court) the misbehaviour of the service
+provider.
+
+To achieve these objectives we use:
+\begin{itemize}
+    \item Privacy-preserving blockchain, to allow customers anonymously pay for the services.
+    \item Message board blockchain, to achieve fairness, i.e., as a mean for proving that certain actions took place at a certain moment of time without the trusted third party.
+    \item Content-addressable peer-to-peer storage network, to provide results to the customer. 
+    \item Cryptography
+    \begin{itemize}
+        \item Symmetric encryption: to encrypt and decrypt results published on public networks.
+        \item Digital signatures: To achieve authentication and non-repudiation of actions. 
+    \end{itemize}
+
+\end{itemize}
+
+We observe that the issue of anonymous service provision can be seen as a problem of fair-exchange where parties exchange some informations in a fairly manner, i.e., either both parties obtain the goods being exchanged, or they both obtain nothing.
+
+In our case the customer is exchanging with the SP cryptocurrency and materials for the results.
+
 We contribute to the field of fair-exchanges by proposing a simple,
-practical, and strongly anonymous framework that does not rely on
-centralised trusted-third party, but on decentralised blockchain and
-distributed content addressable networking.
-
-Also, we support physical materials delivery, which was rarely targeted
-by other researchers or based on strong and unpractical assumptions.
-
-Our framework simultanesly provides three main properties:
+practical, and anonymous framework that does not rely on centralised trusted-third party, but on decentralised blockchain and
+distributed content-addressable storage network.
+
+Also, we support physical materials delivery, which was rarely targeted by other researchers or based on strong and unpractical assumptions.
+
+Our framework simultaneously provides five main properties:
 
@@
 \item Dispute resolution: at each step of the protocol the customer can open a dispute win the case iff the SP misbehaved.
-\item TTP-less: our protocol does not rely on trusted-third party to conduct transactions in fairly manner.
+\item TTP-less: 
+our protocol does not rely on trusted-third party to conduct transactions in fairly manner.
 Only in case of dispute the centralised justice is invlolved (the justice decentralisation is discussed in section ~\ref{future-work}.
-\item Physical materials: our protocol allows providing not only
-  digital but also physical materials to the service provider.
-\end{itemize}
-
-Some authors have proposed blockchain-based fair-exchange systems that
-could be adapted to service provision; however, to our best knowledge we
+\item Physical materials: our protocol allows providing not only digital but also physical materials to the service provider.
+\end{itemize}
+
+Some authors have proposed blockchain-based fair-exchange systems that could be adapted to service provision; however, to our best knowledge we
 are the first to propose a system that satisfy all five properties
@@
 Next, both Alice and Bob exchange the sets of encrypted key shares with
-each other. And send funds to the escrow account.
+each other, and send funds to the escrow account.
 
@@
 
-However, the system doesn't achieve full anonimity but pseudonimity (see
-section~\ref{pseudo-anon}). Also the protocol does not
-cover the case of dispute between the parties.
+However, since the system uses Ethereum— fully traceable blockchain—its anonymity is achieved as long as the addresses are not identified with the real identities, which we call pseudonymity rather than anonymity (see section~\ref{pseudo-anon}).
+Also, the protocol does not cover the case of dispute between the parties.
 
@@
 
-Disputes are inevitable part of all human transactions. Whether
-intentional or accidental, the system should prevent any behaviour
-volatiling rules of agreed contract or local jurisdiction. The rules are
-specified by law, and implemented by police.
+Disputes are inevitable part of all human transactions.
+Whether intentional or accidental, the system should prevent any behaviour volatiling rules of agreed contract or local jurisdiction.
+The rules are specified by law, and implemented by police.
 
@@
 we take the more conservative approach and resolve disputes using local
-justice system (police or court).
+justice system (police, court, etc.).
 
@@
 
-\subsection{Proof to justice}\label{proof-of-justice}
+\subsection{Proofs to justice}\label{proof-of-justice}
 In case of dispute the customer can proof to the justice (police, court,
@@
 information to start a dispute against. To mitigate this issue the SP is
-always in advantaged postition, so that he has no reason to start a
+always in advantaged position, so that he has no reason to start a
 dispute. The idea described further in section ~\ref{future-work}.
+
+% Unify with what is writen in fiarness analysis
 
@@
 the customer should be able to prove that: (i) he delivered to the SP a
-complete (according to the SP requirements) package \(pkg\), and the SP
-accepted it; (ii) he paid for the transaction \(tx\).
+complete (according to the SP requirements) package, and the SP
+accepted it; (ii) he paid for the transaction.
 
@@
 
-\subsection{Pseudo-anonymous vs anonymous blockchain}
+\subsection{Anonymity, pseudonomity, and confidentality}\label{pseudo-anonymous-vs-anonymous-blockchain}
 
@@
 Anonymity is a the ability to hide one identity from others.
-More precisely, the unability to correlate actions performed within the sytem to the identity of the user.
-Or we can say, that the system guarantee anonimity if for all observers the actions are equally likely to be associated with any user of the system.
-However, anonimity is a spectrum rather than dichotomous classification.
+More precisely, the unability to correlate actions performed within the system with the identity of the user.
+Or we can say, that the system guarantee anonymity if for all observers the actions are equally likely to be associated with any user of the system.
+However, anonymity is a spectrum rather than dichotomous classification.
 One method of quantifying level of anonymity is proposed in \textit{k}-anonymity~\cite{sweeney2002k}.
@@
 
-The privacy-preserving blockchains are the ones that maintain anonymity via untraceability and unlikability, not via assumption that the connection between an address and the real identity is concealed.
+The privacy-preserving blockchains are the ones that maintain anonymity via untraceability and (ideally) unlikability, not via assumption that the connection between an address and the real identity is concealed.
 
@@
 \item
-  separate address --- each transaction derives new address uniquely
+  separate address — each transaction derives new address uniquely
   associating it with the transaction. Such addresses can be derived
-  using BEP-32 standard.
-\item
-  memo --- the payments are send to one SP account, but contain extra
+  using Hierarchical Deterministic Wallets (BIP-32)~\cite{bipsbip089}.
+\item
+  memo — the payments are send to one SP account, but contain extra
   field named ``memo'' which contains a random value generated by SP and
-  included in POD. Each payment containing such value in memo is
-  considered to pay for the transaction in question. in case of dispute,
-  the connection can be disclosed by revealing the value in POD and
-  payment's memo.
+  included in $\mathrm{PoD}$. Each payment containing such value in memo is
+  considered to pay for the transaction in question. In case of a dispute,
+  the connection can be disclosed by revealing the value in $\mathrm{PoD}$ and payment's memo.
 \end{itemize}
@@
 which at the time of writing is still a experimental feature
-\cite{paymentd11}. Proving payments that were made with the usage of
-mixers, involve two steps.
+\cite{paymentd11}.
 
@@
 We take the same approach. Once the SP creates the results, he encrypts
-them using the previously provided customer's public key; then publish
+them using the previously provided encryption key; then publish
 them into a IPFS network.
@@
 
-\(\mathrm{SP}\) - Service Provider. \(\mathrm{customer}\) - Customer.
-\(\mathrm{pkg}\) - package anonymously delivered by customer to SP.
-\(\mathrm{materials}\) - materials used by SP to provide services, can
-be of any kind: urine, saliva, blood, stool, or health documents, legal
-documents etc. \(\mathrm{results}\) - results in binary format, can be
-either PDF, docx or any format agreed by both parities. \(\mathrm{PoD}\)
-- Proof-of-Delivery is a confirmation issued by SP to the customer after
-the \(pkg\) is accepted by the SP. \(\mathrm{PoP}\) -
-Proof-of-Provision, a proof of existence of provisioned results.
-\(\mathrm{E}_\mathrm{key}(\cdot)\), \(\mathrm{D}_\mathrm{key}(\cdot)\) -
-symmetric encryption and decryption operators.
-\(\mathrm{S}_\mathrm{key}(\cdot)\), \(\mathrm{V}_\mathrm{key}(\cdot)\) -
-digital sign and verify operators. \(\mathrm{sk}\), \(\mathrm{pk}\) -
-Key pair of secret and public keys accordingly.
-\(\mathrm{DH}(\cdot, \cdot)\) - Diffie--Hellman key exchange. \(CID\) -
-Content Identifier, a label used to address content in IPFS.
-
 \subsection{Prerequisites}
-
-Anonymous payments:
-
-\begin{itemize}
-
-\item
-  SPs accept packages from unknown customers and give them back
-  confirmation of acceptance (to stick with convention we call it
-  Proof-of-Delivery).
-\item
-  SPs accept payment for services via anonymous cryptocurrencies like
-  Monero, Grin or ZCash as described in section ~\ref{payment-for-services}.
-\item
-  Justice accepts as a evidence in dispute proof of payment of
-  cryptocurrencies as described in section~\ref{proof-of-justice}.
+We do not design our framework with the particular technologies in mind, instead we state requirements that each party of the framework must satisfy to make the whole system to work together.
+The choice of the particular technology for each role is up to the implementer.
+
+\begin{itemize}
+\item There exists common PKI infrastructure:
+    \begin{itemize}
+        \item The customer and the SP have their own key pairs consisting of secret key $\mathrm{sk}(\mathrm{party})$ and public key $\mathrm{pk}(\mathrm{party})$, where $\mathrm{party} \in \{\mathrm{C}, \mathrm{SP}\}$ is the customer or the service provider accordingly.
+        \item Both the customer and the SP can create and verify digital signatures created by the customer $\mathrm{sig}_{\mathrm{sk}(\mathrm{C})}$ and the SP $\mathrm{sig}_{\mathrm{sk}(\mathrm{SP})}$.
+        \item The SP's public key is publicly known.
+    \end{itemize}
+
+\item Both the customer and the SP:
+    \begin{itemize}
+        \item Uses common symmetric encryption $\mathrm{E}_\mathrm{key}(\cdot)$ and decryption $\mathrm{D}_\mathrm{key}(\cdot)$ operations.
+    \end{itemize}
+
+\item The SP:
+    \begin{itemize}
+        \item Accepts packages from unknown customers and give $\mathrm{PoD}$ in return.
+        \item Accepts payments with anonymous cryptocurrencies as described in section~\ref{payment-for-services}.
+    \end{itemize}
+
+\item Justice:
+    \begin{itemize}
+        \item Accepts as a evidence in dispute a $\mathrm{PoD}$, $\mathrm{PoP}$, and payment $\mathrm{attestation}$ as described in section~\ref{proof-of-justice}.
+    \end{itemize}
+
+\item Anonymous payments:
+    \begin{itemize}
+        \item Supports anonymous, i.e., untraceable and (ideally) unlinkable transactions as specified in section~\ref{pseudo-anonymous-vs-anonymous-blockchain}.
+        \item Supports uniquely identifying transaction either via separate address per transaction, memo field, or other similar mechanism as described in section ~\ref{payment-for-services}. 
+    \end{itemize}
+
+\item Message board:
+    \begin{itemize}
+        \item Supports proofs as large as the size of $\mathrm{PoP}$, i.e., sum size of $\mathrm{cid}$, $\mathrm{nonce}$, and $\mathrm{sig}$.
+    \end{itemize}
+
+\item The storage network:
+    \begin{itemize}
+        \item Allows for uniquely content retrieval via $\mathrm{cid}$ (usually a hash of the content).
+        \item Allows for anonymous content retrieval.
+    \end{itemize}
 \end{itemize}
@@
 In this section we describe each step of the protocol. The steps are
-shown in the figure ~\ref{fig:diagram}.
+shown in the figure ~\ref{fig:protocol-diagram}.
 
 \begin{figure}[h!]
-\includegraphics[width=9cm]{anonser-diagram.png}
+\includegraphics[width=9cm]{anonser-protocol.png}
 \centering
 \caption{Diagram}
-\label{fig:diagram}
+\label{fig:protocol-diagram}
 \end{figure}
@@
 The customer collects all the $\mathrm{materials}$ required by the SP, generate an encryption $\mathrm{key}$ print it on a paper as a QR code, and pack them together into a package $\mathrm{pkg}$.
+
+Symbolically: \[
+\mathrm{pkg} \gets (\mathrm{materials}, \mathrm{key})
+\]
 
@@
 Also, the $\mathrm{PoD}$ consist of randomly generated unique number $\mathrm{nonce}$, which will allow associating all actions related to the transaction throughout the protocol.
-Finally, the digital signature $\mathrm{sig}_\mathrm{SP}$ on the $\mathrm{PoD}$ created with the SP's secret key guarantee non-repudiation.
+Finally, the digital signature $\mathrm{sig}_{\mathrm{sk}(\mathrm{SP})}$ on the $\mathrm{PoD}$ created with the SP's secret key $\mathrm{sk}(\mathrm{SP})$ guarantee non-repudiation.
 
@@
 
-Symbolically: \[
-\mathrm{delivery}(\mathrm{pkg}) : \mathrm{PoD}
+Symbolically: 
+\[
+\mathrm{PoD} \gets \mathrm{delivery}(\mathrm{pkg})
+\]
+\[
+(\mathrm{T}_\mathrm{issue}, \mathrm{T}_\mathrm{pay}, \mathrm{T}_\mathrm{provide}, \mathrm{nonce}, \mathrm{sig}_{\mathrm{sk}(\mathrm{SP})}) \equiv \mathrm{PoD}
 \]
@@
 Symbolically: \[
-\mathrm{payment}(\mathrm{PoD}.\mathrm{nonce}) : \mathrm{attestation}
+\mathrm{attestation} \gets \mathrm{payment}(\mathrm{nonce}, \mathrm{sig}_{\mathrm{sk}(\mathrm{C})})
 \]
@@
 service}\label{step-3-provision-of-service}
-
-At this point the SP can start the provision of service. If it's
-suspicious it may decide to wait until the invoice is paid, otherwise
-start immediately.
+Once the transaction is paid the SP start the provision of service.
 
 Symbolically: \[
-\mathrm{provision}(\mathrm{pkg}.\mathrm{materials}) : \mathrm{results}
+\mathrm{results} \gets \mathrm{provision}(\mathrm{materials})
 \]
@@
 \paragraph{Step 4: Results
-publication}\label{step-4-results-publication}
-
-Once the service is finished, some kind of output should be created. The
-output should be encrypted using encryption symmetric key provided in
-the first step.
-
-The encrypted results can be then published on content network such as
-IPFS. As a result, the content identifier (CID) is returned.
-
-Symbolically: \[
- \mathrm{publish}(E_{\mathrm{pkg}.\mathrm{key}}(\mathrm{results})) : \mathrm{PoP}
+upload}\label{step-4-results-upload}
+
+After the service is finished, some kind of output should be created. Next, the output is encrypted using encryption symmetric key $\mathrm{key}$ provided in the first step.
+
+The encrypted results are then uploaded on content addressable network such as IPFS. As a result, the content identifier (cid) is returned.
+
+Symbolically: 
+\[
+\mathrm{cid} \gets \mathrm{upload}(E_{\mathrm{key}}(\mathrm{results}))
 \]
@@
 
-Now, when the results are published on content addressable network such
-as IPFS, the SP publish \(\mathrm{cid}\) obtained in previous step on a
-message board doing proof of provision.
-
-Symbolically: \[\mathrm{publish}(\mathrm{cid})\]
+When the results are published, the SP perform proof of provision by publishing $\mathrm{cid}$ along with $\mathrm{nonce}$ and signature $\mathrm{sig}_\mathrm{SP}$.
+
+Symbolically: 
+\[\mathrm{PoP} \equiv (\mathrm{cid}, \mathrm{nonce}, \mathrm{sig}_{\mathrm{sk}(\mathrm{SP})})\]
+\[\mathrm{publish}(\mathrm{PoP})\]
 
@@
 
-Since the delivery and payment was made the customer observes blockchain
-for a POP corresponding to his transaction. When it happen,
+After delivering the package and paying for the transaction the customer subscribe to the message board and waits until the SP publish the proof of provision.
+The subscription is for the SP public key $\mathrm{pk}(\mathrm{SP}$ and transaction's $\mathrm{nonce}$.
 
 Symbolically: \[
-\mathrm{pull}(\mathrm{pkg.nonce})
+\mathrm{cid} \gets \mathrm{subscribe}(\mathrm{pk}(\mathrm{SP}), \mathrm{nonce})
 \]
@@
 \paragraph{Step 7: Results download}\label{step-7-results-download}
+Having the $\mathrm{cid}$, the customer downloads and decrypts the $\mathrm{results}$.
 
 Symbolically: \[
-\mathrm{download}(\mathrm{cid}) : \mathrm{results}
+\mathrm{results} \gets \mathrm{D}_{\mathrm{key}}(\mathrm{download}(\mathrm{cid}))
 \]
@@
 \section{Fairness analysis}
-We analyse the fairness of the protocol by representing it as a
-interactive non-cooperative game.
+We analyse the fairness of the protocol by representing it as a interactive non-cooperative game.
 
 \subsection{Model}\label{model}
-
 We consider three positions:
@@
 \item
-  Neutral (•) position is when a party hasn't spend not gain anything of
-  significant value (money, time, effort). For example, at beggining of
-  the protocol.
-\item
-  Disadvantage (-) position — when a party has put any effort or paid
-  money without being able to reclaim it. In other words it has
-  \textbf{risked} its resources. For example, paid for a service in
+  Neutral (•) position: when a party hasn't spend nor gain anything of significant value (money, time, effort). For example, at the beginning of the protocol.
+\item
+  Disadvantage (-) position: when a party has put a significant value without receiving an equivalent. For example, paid for a service in
   advance.
 \item
-  Advantage(+) position — when a party would benefit if the
-  transaction would halt at that point. For example, received payment in
-  advance.
-\end{itemize}
-
-There are many actions that each party can take, but we group them
-together into two categories:
+  Advantage(+) position: when a party would benefit if the transaction would halt at that step. For example, the SP has received payment before service provision.
+\end{itemize}
+
+There are many actions that each party can take, but we group them together into two categories:
 
@@
 \item
-  Normal --- taking the action prescribed by the protocol.
-\item
-  Abnormal --- everything that deviates from designed steps of the
-  protocol. For example, sending arbitrary message, skipping some step,
-  repeating step, timing out.
+  Normal: taking the action prescribed by the protocol.
+\item
+  Abnormal: everything that deviates from designed steps of the protocol. For example, sending arbitrary message, skipping some step, repeating step, timing out.
 \end{enumerate}
 
-Moreover, at any step of the protocol the customer can react with two
-reactions:
+Moreover, at any step of the protocol the customer can start a dispute; therefore, another dimension with two positions has to be considered:
 
@@
 \item
-  Agree --- the customer agree with the action and therefore does not
-  start a dispute.
-\item
-  Start a dispute --- the customer does not agree with the action and
-  therefore start a dispute.
+  Agree: the customer agree with the action, and therefore does not start a dispute.
+\item
+  Start a dispute: the customer does not agree with the action and therefore start a dispute.
 \end{enumerate}
 
-Therefore, there are two possible actions a party can take at any step
-of the protocol and two reactions the customer can take.
-
-Hence, in our analysis we have to consider four different outcomes for
-each party of the protocol:
-
-\begin{itemize}
-
-\item
-  \(\sigma_\mathrm{n}\) --- after following the protocol within the
-  timeframe.
-\item
-  \(\sigma_\mathrm{d}\) --- after a dispute where the other party hasn't
-  broken the protocol.
-\item
-  \(\sigma_\overline{n}\) --- after not starting a dispute despite the
-  other party has broken the protocol.
-\item
-  \(\sigma_\overline{d}\) --- after a dispute where the other party has
-  broken the protocol.
+As a result, in our analysis we have to consider four different outcomes for each party of the protocol:
+
+\begin{itemize}
+
+\item
+  $\sigma_\mathrm{n}$: after following the protocol when the other party acted normally.
+\item
+  $\sigma_\mathrm{d}$: after a settled dispute when the other party acted normally.
+\item
+  $\sigma_\overline{n}$: after not starting a dispute despite the other party has acted abnormally.
+\item
+  $\sigma_\overline{d}$: after a settled dispute when the other party has acted abnormally.
 \end{itemize}
@@
 The protocol terminate after last step, after starting a dispute, or
-after a party hasn't completed it's designated action in time. Therefore
-all positions except \(\sigma_\mathrm{n}\) are termination positions.
-
-After starting a dispute, the protocol terminate. After timing out there
-is no going back on the normal path.
-
-In our framework, the only party that can start a dispute is the
-customer. It's because the customer is anonymous, and so the SP does not
-have any personal information to start a dispute against.
-
-To mitigate this issue, the protocol is designed so that the SP who
-follows the protocol is always in advantaged position, therefore he has
-no incentivisations to start a dispute.
-
-We say that the protocol achieve fairness if:
-
-\begin{align*} 
-  \forall_{party \in parties}\forall_{\mathrm{step} \in \mathrm{steps}} \mathrm{can\ move\ the\ protocol\ \\
-  to\ the\ non\ disadvantaged\ position} 
-\end{align*}
+after a party hasn't completed it's designated action in time. Therefore,
+all positions except $\sigma_\mathrm{n}$ are termination positions.
+
+Because the customer is anonymous the SP can not start a dispute---there is no mean to identify the customer.
+To mitigate the issue, we designed the protocol so that the SP who follows the protocol is always in advantage position, therefore he has no reason to start a dispute.
+The customer on the other hand can start a dispute at any time of the protocol, but only the actual misbehaviour of the SP makes him win the case.
+
+\begin{definition}[Fairness] \label{fairness}
+A protocol achieve fariness iff 
+\begin{equation*}
+\begin{split}
+\forall_{party \in parties}\forall_{\mathrm{step} \in \mathrm{steps}} &\mathrm{can\ move}\\
+&\mathrm{to\ the\ non\ disadvantaged\ position} 
+\end{split}
+\end{equation*}
+
+\end{definition}
 
@@
 
-For the analysis purpose we state assumptions listed below. We consider
-them being rational and realistic.
+For the analysis purpose we state plausable assumptions listed below.
 
@@
 \item
-  Both parties, by completing a transaction, end up in advantaged
-  positions (+). In other words, they have intrinsic motivation to
-  initialise the transaction.
+  Both parties, by completing a transaction, end up in advantaged positions (+). In other words, they have intrinsic motivation to initialise and complete the transaction.
 \item
@@
 
-\paragraph{Step 1: deliver package}\label{step-1-deliver-package}
-
-Turn: Customer
+\paragraph{Step 1, customer turn: deliver package}\label{step-1-deliver-package}
 
@@
 
-\paragraph{Step 2: pay for invoice}\label{step-2-pay-for-invoice}
-
-Turn: Customer
+\paragraph{Step 2, customer turn: pay for invoice}\label{step-2-pay-for-invoice}
 
@@
 
-\paragraph{Step 3: provision of
+\paragraph{Step 3, SP turn: provision of
 service}\label{step-3-provision-of-service}
 
-Turn: SP
-
-SP has done the provision of service:
+The SP has done the provision of service:
 
@@
 
-\paragraph{Step 4: publication of
+\paragraph{Step 4, SP turn: publication of
 results}\label{step-4-publication-of-results}
-
-Turn: SP
 
@@
 
-\paragraph{Step 5: publication of
+\paragraph{Step 5, SP turn: publication of
 proof-of-provision}\label{step-5-publication-of-proof-of-provision}
 
-Turn: SP
-
-SP has published proof-of-provision on time:
+The SP has published proof of provision on time:
 
@@
 
-\paragraph{Step 6: pull
+\paragraph{Step 6, customer turn: pull
 proof-of-provision}\label{step-6-pull-proof-of-provision}
-
-Turn: Customer
 
@@
 
-\paragraph{Step 7: retrieval of
+\paragraph{Step 7, customer turn: retrieval of
 results}\label{step-7-retrieval-of-results}
-
-Turn: Customer
 
@@
   \item
-    \(\sigma_{7, c, \overline{\mathrm{d}}} = •\) customer wins the case
-    and ends up in neutral position (•)
-  \item
-    \(\sigma_{7, c, \overline{\mathrm{d}}} = -\) SP lose the case and
-    end up in disadvantaged position (-)
+    \(\sigma_{7, c, \overline{\mathrm{d}}} = •\) customer wins the case and ends up in neutral position (•)
+  \item
+    \(\sigma_{7, c, \overline{\mathrm{d}}} = -\) SP lose the case and end up in disadvantaged position (-)
   \end{itemize}
@@
 \item
-  The customer can follow the protocol to the non-disadvantaged
-  termination position \(\sigma_{7, c, \mathrm{n}} = +\), or in case the
-  SP haven't followed the protocol start a dispute and win the case
-  \(\sigma_{7, c, \overline{\mathrm{d}}} = •\).
-\item
-  The SP can do nothing and end up in non-disadvantaged position
-  \(\sigma_{7, s, \mathrm{n}} = +\).
+  The customer can follow the protocol to the non-disadvantaged termination position \(\sigma_{7, c, \mathrm{n}} = +\), or in case the SP haven't followed the protocol start a dispute and win the case \(\sigma_{7, c, \overline{\mathrm{d}}} = •\).
+\item
+  The SP can do nothing and end up in non-disadvantaged position \(\sigma_{7, s, \mathrm{n}} = +\).
 \end{itemize}
@@
 
-The diagram below shows the path of positions when SP try to misbehave
-and don't execute service after receiving the payment. The protocol ends
-up in neutral to customer and disadvantaged to SP positions.
+The diagram below shows the path of positions when SP try to misbehave and don't execute service after receiving the payment.
+The protocol ends up in neutral to customer and disadvantaged to SP positions.
 
@@
 
-Ultimately, the rational path for both parties is to follow the protocol
-as shown in the diagram below.
+Ultimately, the rational path for both parties is to follow the protocol as shown in the diagram below.
 
@@
 
-With the fairness definition stated in equation, and the assumptions
-stated in \ref{assumptions}, our analysis indicate that the protocol
-achieve fairness.
+With the fairness definition stated in equation, and the assumptions stated in \ref{assumptions}, our analysis indicate that the protocol achieve fairness.
 
@@
 
-The possible directions for mitigation of such issue are to either (1)
-replace justice with decentralised autonomous organisations (DAO) like
-proposed in Themis~\cite{meng2019themis} or
-Kleros~\cite{lesaege2018kleros}; or (2) make it infeasible to provide
-incorrect results.
-
-The first approach is more feasible in the near future. It would require
-creating large pool of experts in a field, that in case of dispute,
-would receive all the proofs (POD, POP, as well as any other proofs
-significant to the case) that could be queried by the experts in
-zero-knowledge fashion, i.e., they could ask limited number of questions
-to the proofs and getting yes/no answers. Keeping the case fully
-confidential. The experts would be incentivised to participate in the
-pool by the system of fees. Their honest behaviour would be incentivised
-by the stake they would have to lock, and punishment they would get by
-judging incorrectly, where the ``correctly'' is determined by the quorum
-of votes.
-
-The second approach is more philosophical and visionary. Suppose that
-the service we are undertaking is fully computable. Then, it would be
-possible by employing proofs of correctness of
-computations~\cite{ben2013snarks} to enforce that only correct
-computations (hence correct services) are accepted. To do so the whole
-service examination would have to be computable, which is hard to
-achieve in settings where physical materials (like blood) are examined.
-Concretely, the problem canes down to ``How to digitally represent
-blood''. If we could represent urine, blood, saliva, or any other
-physical material in binary format, and let the customer to take a
-sample, discrete it and send it to the SP by himself, then the whole
-chain of integrity could be ensured. Therefore, wrong service provision
-would be infeasible.
-
-\subsection{Cryptographically provable availability of
+The possible directions for mitigation of such issue are to either (1) replace justice with decentralised autonomous organisations (DAO) like proposed in Themis~\cite{meng2019themis} or Kleros~\cite{lesaege2018kleros}; or (2) make it infeasible to provide incorrect results.
+
+The first approach is more feasible in the near future.
+It would require creating large pool of experts in a field, that in case of dispute, would receive all the proofs (POD, POP, as well as any other proofs significant to the case) that could be queried by the experts in zero-knowledge fashion, i.e., they could ask limited number of questions to the proofs and getting yes/no answers.
+Keeping the case fully confidential.
+The experts would be incentivised to participate in the pool by the system of fees.
+Their honest behaviour would be incentivised by the stake they would have to lock, and punishment they would get by judging incorrectly, where the ``correctly'' is determined by the quorum of votes.
+
+The second approach is more philosophical and visionary.
+Suppose that the service we are undertaking is fully computable.
+Then, it would be possible by employing proofs of correctness of computations~\cite{ben2013snarks} to enforce that only correct computations (hence correct services) are accepted.
+To do so the whole service examination would have to be computable, which is hard to achieve in settings where physical materials (like blood) are examined.
+Concretely, the problem canes down to ``How to digitally represent blood''.
+If we could represent urine, blood, saliva, or any other physical material in binary format, and let the customer to take a sample, discrete it and send it to the SP by himself, then the whole chain of integrity could be ensured.
+Therefore, wrong service provision would be infeasible.
+
+\subsection{Provable availability of
 results}\label{cryptographically-provable-availability-of-results}
 
-Currently, the SP has to publish the results into a p2p content storage
-network (IPFS). The problem is that, nothing prevent such SP to publish
-the content, receive the content identifier (cid), and immediately after
-remove it from from it's local storage. In case of dispute the SP can
-upload the content again, proving its availability. The SP has no
-motivation to proceed with this kind of misbehaviour, other than puting
-the customer in disadvantaged position caused by the lost dispute. We see
-possible prevention of this misbehaviour by the usage of Filecoin---an
-incentive layer on top of IPFS that guarantee the content availability
-via economic incentivisations Filecoin~\cite{benetfilecoin}. With the
-help of Filecoin, the SP would be obligated to create a Filecoin deal
-that guarantee the results availability until the deadline of the
-transaction. Moreover, since Filecoin is a blockchain by itself, it
-could play both roles of message board and Storage Network.
+Currently, the SP has to publish the results into a p2p content addressable storage network, e.g., IPFS.
+The problem is that, nothing prevent the SP from publishing the results, receiving the cid, publishing $\mathrm{PoP}$, and immediately after removing the results from the local storage.
+In case of dispute the SP can upload the content again, proving its availability.
+The SP has no motivation to proceed with this kind of misbehaviour, other than putting the customer in disadvantaged position caused by the lost dispute.
+We see possible prevention of this misbehaviour by the usage of Filecoin---an incentive layer on top of IPFS that guarantee the content availability via economic incentivisations~\cite{benetfilecoin}.
+With the help of Filecoin, the SP would be obligated to create a deal that guarantee the results availability until the deadline of the transaction.
+Moreover, since Filecoin is a blockchain by itself, it could play both roles of message board and storage network.
 
@@
 
-Without lose of generality the payment can be made with cash. The
-customer can exchange the cash with SP together with delivering the
-package. The PoD would contain an information that the
-transaction has been paid with cash; therefore, Steps 1 and 2 could be
-merged together and realised in one step. In case of dispute the payment
-disclosure would be in included in PoD.
+Without lose of generality the payment can be made with cash.
+The customer can exchange the cash with SP together with delivering the package.
+The $\mathrm{PoD}$ would contain an information that the transaction has been paid with cash; therefore, Steps 1 and 2 could be merged together and realised in one step.
+In case of dispute the payment disclosure would be in included in $\mathrm{PoD}$.
 
@@
 
-Currently our framework require customer to deliver the \(pkg\) to SP
-personally or via trusted person. However the system could be extended
-to support anonymous delivery system as proposed in
-Lelantos~\cite{altawy2017lelantos}.
+We assumed the customer to deliver the package to the SP personally or via trusted person.
+However the system could be extended to support anonymous delivery system as proposed in Lelantos~\cite{altawy2017lelantos}.
 
@@
 The framework can be employed by any local service provider to provide services without collecting any personal information.
-The payment is handled by anonymous cryptocurrencies, and the results are published on content based p2p network.
-The dispute can be settled by disclosing proofs to the justice.
-At any stage of the transaction, both parties are either in privelaged situation or can proof to the justice the misbehaviour of the other party.
+The payment is handled by anonymous cryptocurrencies.
+Proof of delivery and proof of provision are published on message board blockchain.
+The results are published on content addressable p2p network.
+The dispute can be settled by disclosing proofs to justice.
+Assuming the definition~\ref{fairness} we showed that the protocol achieve fairness.
+Finally, we pinpointed further improvements like decentralised dispute resolution, provable  availability of results, paying with cash, and anonymous delivery via courier.
 

### 2022-02-25 access.tex
unify PoD, PoP definitions

@@
 \subsection{Proofs to justice}\label{proof-of-justice}
-In case of dispute the customer can proof to the justice (police, court,
-etc.) evidences that convinces the justice about the honesty of customer
-and misbehaviour of SP. The reason why the SP can not start a dispute is
-that the customer is anonymous, and therefore there is no personal
-information to start a dispute against. To mitigate this issue the SP is
-always in advantaged position, so that he has no reason to start a
-dispute. The idea described further in section ~\ref{future-work}.
-
-% Unify with what is writen in fiarness analysis
-
-Abstracting from the services the SP is providing, in case of dispute
-the customer should be able to prove that: (i) he delivered to the SP a
-complete (according to the SP requirements) package, and the SP
-accepted it; (ii) he paid for the transaction.
-
-The first proof called proof-of-delivery (PoD) is a confirmation issued
-by the SP to the customer.
-
-\[\mathrm{PoD} = (\mathrm{T}_\mathrm{issue}, \mathrm{T}_\mathrm{pay}, \mathrm{T}_\mathrm{provide}, \mathrm{nonce}, \mathrm{sig}_\mathrm{SP})\]
-
-where:
-
-\begin{itemize}
-
-\item
-  \(\mathrm{T}_\mathrm{issue}\) - time at which the PoD is issued.
-\item
-  \(\mathrm{T}_\mathrm{pay}\) - deadline to pay for the transaction.
-\item
-  \(\mathrm{T}_\mathrm{provide}\) - deadline to provide the service
-  results.
-\item
-  \(\mathrm{nonce}\) - randomly generated number uniquely identifying
-  the transaction.
-\item
-  \(\mathrm{sig}_\mathrm{SP}\) - the SP's signature guaranteeing
-  non-repudiation.
-\end{itemize}
-
-also:
-
-\(\mathrm{T}_\mathrm{issue} < \mathrm{T}_\mathrm{pay} < \mathrm{T}_\mathrm{provide}\)
-
-The second proof depend on the cryptocurrency implementation and is
-discussed further section~\ref{payment-for-services}.
-
-In case the SP has fulfilled the transaction and provide the results,
-but the customer unjustly start a dispute, the SP is secured by the
-proof of provision (PoP) he has published on the message board (described in section ~\ref{message-board}.
-
-\[\mathrm{PoP} = (\mathrm{cid}, \mathrm{nonce}, \mathrm{sig}_\mathrm{SP})\]
-
-where:
-
-\begin{itemize}
-
-\item
-  \(\mathrm{cid}\) - content identifier as specified in section ~\ref{storage-network}.
-\item
-  \(\mathrm{nonce}\) - the value uniquely identifying the transaction
-  previosuly generated in PoD.
-\item
-  \(\mathrm{sig}_\mathrm{SP}\) - the SP's signature guaranteeing
-  non-repudiation.
-\end{itemize}
-
-By publishing the PoP on the blockchain, the SP can not falsify the time
+
+In case of dispute the customer can proof to justice (police, court, etc.) convincing evidences for the honesty of the customer and misbehaviour of the SP. 
+Because the customer is anonymous the SP can not start a dispute---there is no mean to identify the customer.
+
+To mitigate the issue, we designed the protocol so that the SP who follows the protocol is always in advantage position, therefore he has no reason to start a dispute.
+The customer on the other hand can start a dispute at any time of the protocol, but only the actual misbehaviour of the SP makes him win the case.
+
+Abstracting from the services the SP is providing, in case of dispute each party should be able to prove its honest behaviour.
+We introduce three proofs that should be disclosed to justice in case of a dispute:
+
+\begin{enumerate}
+    \item Proof-of-delivery ($\mathrm{PoD}$) is a confirmation issued by the SP to the customer that proves that the customer has delivered to the SP a complete (according to the SP requirements) package, and the SP accepted it.
+It consists of: current time; deadline to pay for the transaction; and deadline to provide the service; deadline to provide the service results; randomly generated number uniquely identifying the transaction; and the SP's signature guaranteeing non-repudiation.
+The formal definition of the $\mathrm{PoD}$ is presented in section ~\ref{proof-of-delivery}.
+
+    \item Payment $\mathrm{attestation}$ is confirmation that the customer has paid for the transaction, at a certain time.
+The actual implementation depends on the particular cryptocurrency and is discussed further section~\ref{payment-for-services}.
+
+    \item Proof-of-provision ($\mathrm{PoP}$) is an proof that the SP published the results at a certain time.
+It defend the SP in case the customer unjustly start a dispute after the results has been published.
+It consist of: content identifier as specified in section ~\ref{storage-network}; the value uniquely identifying the transaction previosuly generated in $\mathrm{PoD}$; the SP's signature guaranteeing authentication.
+The connection between $\mathrm{PoP}$ and the results is made by the content identifier which uniquely points to the results such that the $\mathrm{PoP}$ can not forge results after the publication.
+\end{enumerate}
+
+\subsection{Message Board}\label{message-board}
+The proof-of-provision that we coined for the purpose of this protocol
+is generally called the proof-of-existence
+\cite{proofofexistence, de2016stampery, Chainpoi39}.
+
+The idea behind proof-of-existence is to certify that some information
+has existed at a certain moment of time, in such a way that nobody can
+undermine its existence, integrity, and ownership (also called the
+non-repudiation requirement).
+
+We need this functionality for two reasons: (1) Communicate the existence
+of the results to the customer to whom the SP have no other
+communication medium as the customer stays anonymous; (2) let the SP to proof the publication of results within the agreed with customer deadline.
+
+By publishing the $\mathrm{PoP}$ on the blockchain, the SP can not falsify the time
 at which the results has been provided, because the block creation time
 proves that. Blockchain acts as a global clock that securely timestamps
-everything that gets into the block, so the PoP that was included in a
-block will be associated with the time when the block has been forged.
-Moreover, since the blockchain is public, everyone (including the
-justice) can be convinced that the SP indeed provided the results at
-that time.
-
-The connection between PoP and the results is made by the content
-identifier which uniquely points to the results such that the PoP can
-not forge results after the publication.
-
-The content identifier is usually some kind of hash write about ipfs
-
-\subsection{Message Board}\label{message-board}
-The proof of provision that we coined for the purpose of this protocol
-is generaly called the proof of existence
-\cite{proofofexistence, de2016stampery, Chainpoi39}.
-
-The idea behind proof of existence is to certify that some information
-has existed at a certain moment of time, in such a way that nobody can
-undermine its existence, integrity, and ownership (also called the
-nonrepudiation requirement).
-
-We need this functionality for two reasons: 1. Communicate the existence
-of the results to the customer to whom the SP have no other
-communication medium as the customer stays anonymous. 2. Let the SP to
-proof the publication of results within the agreed with customer
-deadline. Without such a proof there would be no other means to settle
-the conflict between the customer claiming the results have not been
-published and the SP claiming the results have been published within the
-deadline.
-
-Depending on the context the platform of achieving it is called bulletin
-board~\cite{achenbach2015improved} or message board~\cite{hinarejos2019solution} or trusted timestamping~\cite{gipp2015decentralized}. In this work we call it message board.
-
-Such functionallity is the easiest to achieve by the trusted third party
-that authoritatively tells what happend and when.
-
-Bitcoin introduced a way of decentralising not only the currency system,
-but also other similary working centralised trusted third parties
-including the message board.
-
-We let keep the protocol general enough to let the implementator use any
+everything that gets into the block, so the $\mathrm{PoP}$ that was included in a
+block will be associated with the time when the block has been created.
+Moreover, since the blockchain is public, everyone (including justice) can be convinced that the SP indeed published the results at that time.
+
+Without such a proof there would be no other means to settle the conflict between the customer claiming the results have not been published and the SP claiming the results have been published within the deadline.
+
+Depending on the context the platform of achieving it is called bulletin board~\cite{achenbach2015improved} or message board~\cite{hinarejos2019solution} or trusted timestamping~\cite{gipp2015decentralized}.
+In this work we call it message board.
+
+% Such functionallity is the easiest to achieve by the trusted third party that authoritatively tells what happened and when.
+
+% Bitcoin introduced a way of decentralising not only the currency system,
+% but also other similary working centralised trusted third parties
+% including the message board.
+
+We let keep the protocol general enough to let the implementer use any
 existing technology to provide message board service, with the
@@
 The multidisciplinary nature leads to ambigous definitions~\cite{smith2011information}.
-For the purpose of our work we rely on more concrete definitions, i.e.~confidentality and anonimity.
+For the purpose of our work we rely on more concrete definitions, i.e.~confidentality and anonymity.
 
@@
 
-There are also techniques that can be deployed on non-anonymous blockchains, the so called mixers that literaly gather together users into an \textit{anonymity set}, which then collude together in order to launder the transactions, in such a way that to a observer the likelihood of the sender of each transaction was equiprobable for any user from the anonymity set.
+There are also techniques that can be deployed on non-anonymous blockchains, the so called mixers that literally gather together users into an \textit{anonymity set}, which then collude together in order to launder the transactions, in such a way that to a observer the likelihood of the sender of each transaction was equiprobable for any user from the anonymity set.
 
 Some systems guarantee pseudonomity rather than anonymity.
-Pseudonomity, allows uses to hide their real identity behind the pseudonim.
+Pseudonomity, allows uses to hide their real identity behind the pseudonym.
 Despite the whole system is transparent and allows linking actions to one identity, the system is considered anonymous as long as the link between pseudonym and real identity is secret.
@@
 \begin{figure}[h!]
-\caption{}
+\caption{Let us assume the Alice to be the customer willing to keep her identity private (anonymous) and Bob be the public SP.
+Alice controls two addresses 1 and 2, the connection between her real identity and the first address was compromised, and therefore the identification is possible, the connection between the second pseudonym is still unknown therefore anonymous.
+Alice takes two actions; the first one from the compromised address and the second one from anonymous one.
+The first action is confidential; therefore even though the psudonym has been compromised the action can not be associated with the Alice.
+The second action is transparent, therefore the Alice's anonymity is maintained as long as the connection to the second pseudonym is concealed.}
 \centering
@@
 \end{figure}
-
-Let us assume the Alice to be the customer willing to keep her identity private (anonymous) and Bob be the public SP.
-Alice controls two blockchain addresses 1 and 2, the connection between her real identity and the first address was compromised, and therefore the identification is possible, the connection between the second pseudonym is still unknown therefore anonymous.
-Alice takes two actions; the first one from the compromised address and the second one from anonymous one.
-The first action is confidential; therefore even though the psudonym has been compromised the action can not be associated with the Alice.
-The second action is transparent, therefore the Alice's anonymity is maintained as long as the connection to the second pseudonym is concealed.
 
@@
 
-\item $\mathrm{materials}$ - are the materials needed to provide the
-  service on. For example, sample of urine, blood, stool, saliva; legal
-  documents, CDs, mails, photos, bank statement, or any other kind of
-  evidence depending on the service.
-\item $\mathrm{key}$ - symmetric key used to encrypt and decrypt the
-  results.
+\item $\mathrm{materials}$ - are the materials needed to provide the service on.
+For example, sample of urine, blood, stool, saliva; legal documents, CDs, mails, photos, bank statement, or any other kind of evidence depending on the service.
+\item $\mathrm{key}$ - symmetric key used to encrypt and decrypt the results.
 \end{itemize}
@@
 \item
-  $\mathrm{T}_\mathrm{provide}$ - deadline to provide the service
-  results.
-\item $\mathrm{nonce}$ - randomly generated number uniquely identifying
-  the transaction.
-\item $\mathrm{sig}_\mathrm{SP}$ - the SP's signature guaranteeing
-  non-repudiation.
+  $\mathrm{T}_\mathrm{provide}$ - deadline to provide the service results.
+\item $\mathrm{nonce}$ - randomly generated number uniquely identifying the transaction.
+\item $\mathrm{sig}_\mathrm{SP}$ - the SP's signature guaranteeing non-repudiation.
 \end{itemize}
@@
 \item
-  \(\mathrm{nonce}\) - the value uniquely identifying the transaction
-  previosuly generated in PoD.
-\item
-  \(\mathrm{sig}_\mathrm{SP}\) - the SP's signature guaranteeing
-  non-repudiation.
+  \(\mathrm{nonce}\) - the value uniquely identifying the transaction previously generated in $\mathrm{PoD}$.
+\item
+  \(\mathrm{sig}_\mathrm{SP}\) - the SP's signature guaranteeing authentication.
 \end{itemize}
@@
 The first approach is more feasible in the near future.
-It would require creating large pool of experts in a field, that in case of dispute, would receive all the proofs (POD, POP, as well as any other proofs significant to the case) that could be queried by the experts in zero-knowledge fashion, i.e., they could ask limited number of questions to the proofs and getting yes/no answers.
+It would require creating large pool of experts in a field, that in case of dispute, would receive all the proofs ($\mathrm{PoD}$, $\mathrm{PoP}$, as well as any other proofs significant to the case) that could be queried by the experts in zero-knowledge fashion, i.e., they could ask limited number of questions to the proofs and getting yes/no answers.
 Keeping the case fully confidential.

### 2022-02-25 access.tex
submit work
update fairness analysis

@@
 \newtheorem{definition}{Definition}
+\usepackage{scalerel}
+\newcommand\sbullet[1][.75]{\mathbin{\ThisStyle{\vcenter{\hbox{%
+  \scalebox{#1}{$\SavedStyle\bullet$}}}}}%
+}
 \usepackage{textcomp}
@@
 
-\title{Anonymous provision of local services via blockchain}
+\title{Anonymous provision of services via blockchain}
 \author{\uppercase{Stanis\l{}aw Bara{\'n}ski}\authorrefmark{1}}
@@
 \begin{itemize}
-    \item Patients willing to take a steroid test, drug tests, venereal diseases
-test, paternity test — have strong incentive to keep the whole
-procedure private. Merely the fact that they took the test — without
-exposing the results — is suggestive enough to act as a premise in
-case of a conflict.
+    \item Patients willing to take a steroid test, drug tests, venereal diseases test, paternity test — have strong incentive to keep the whole procedure private.
+Merely the fact that they took the test — without exposing the results — is suggestive enough to act as a premise in case of a conflict.
 
@@
 
-We observe that the issue of anonymous service provision can be seen as a problem of fair-exchange where parties exchange some informations in a fairly manner, i.e., either both parties obtain the goods being exchanged, or they both obtain nothing.
+We observe that the issue of anonymous service provision can be seen as a problem of fair-exchange where parties exchange some goods in a fairly manner, i.e., either both parties obtain the goods, or they both obtain nothing.
 
@@
 
+\paragraph{Contributions}
 We contribute to the field of fair-exchanges by proposing a simple,
@@
 our protocol does not rely on trusted-third party to conduct transactions in fairly manner.
-Only in case of dispute the centralised justice is invlolved (the justice decentralisation is discussed in section ~\ref{future-work}.
+Only in case of dispute the centralised justice is invlolved (the justice decentralisation is discussed in section ~\ref{sec:future-work}.
 \item Physical materials: our protocol allows providing not only digital but also physical materials to the service provider.
@@
 
-\section{State of the art}\label{state-of-the-art}
-
-\paragraph{Anonymity and Fair-Exchange in e-Commerce Protocol for
-Physical Products
-Delivery}\label{anonymity-and-fair-exchange-in-e-commerce-protocol-for-physical-products-delivery}
+\paragraph{Organisation}
+The remainder of this paper is organized as follows.
+In section~\ref{sec:related-works} we briefly review related works. 
+Section~\ref{sec:background} explains the background related to fair-exchanges, blockchain, anonymity and confidentiality, and storage network. 
+Section~\ref{sec:protocol} describes how the protocol works in details.
+Section~\ref{sec:fairness-analysis} provides an fairness analysis of the proposed protocol.
+Section~\ref{sec:future-work} discuss possible improvements. 
+Finally, section~\ref{sec:conclusion} concludes the paper.
+
+\section{Related Works}\label{sec:related-works}
+
+\paragraph{Anonymity and Fair-Exchange in e-Commerce Protocol for Physical Products Delivery} \label{anonymity-and-fair-exchange-in-e-commerce-protocol-for-physical-products-delivery}
 
@@
 
-\paragraph{Themis: Towards decentralized escrow of cryptocurrencies
-without trusted third
-parties}\label{themis-towards-decentralized-escrow-of-cryptocurrencies-without-trusted-third-parties}
+\paragraph{Themis: Towards decentralized escrow of cryptocurrencies without trusted third parties}\label{themis-towards-decentralized-escrow-of-cryptocurrencies-without-trusted-third-parties}
 
@@
 
-\paragraph{Lelantos: A blockchain-based anonymous physical delivery
-system}\label{lelantos-a-blockchain-based-anonymous-physical-delivery-system}
+\paragraph{Lelantos: A blockchain-based anonymous physical delivery system}\label{lelantos-a-blockchain-based-anonymous-physical-delivery-system}
 
@@
 
-However, since the system uses Ethereum— fully traceable blockchain—its anonymity is achieved as long as the addresses are not identified with the real identities, which we call pseudonymity rather than anonymity (see section~\ref{pseudo-anon}).
+However, since the system uses Ethereum— fully traceable blockchain—its anonymity is achieved as long as the addresses are not identified with the real identities, which we call pseudonymity rather than anonymity (see section~\ref{sec:pseudo-anon}).
 Also, the protocol does not cover the case of dispute between the parties.
 
-\section{Background}
+\section{Background}\label{sec:background}
 \subsection{Dispute resolution system}
@@
 Possible directions toward semi-autonomous decentralised resolution
-system are discussed in section ~\ref{future-work}.
-
-\subsection{Proofs to justice}\label{proof-of-justice}
+system are discussed in section ~\ref{sec:future-work}.
+
+\subsection{Fairness}\label{proof-of-justice}
 
@@
 
-\subsection{Anonymity, pseudonomity, and confidentality}\label{pseudo-anonymous-vs-anonymous-blockchain}
+\subsection{Anonymity, pseudonomity, and confidentality}\label{sec:pseudo-anon}
 
@@
 
-Both approaches have some advantages and disadvantages, but our protocol
-can abstract them away by treating them as some randomly genrated unique
-number, often called \textit{nonce} (number once). How it is implemented
-depends on a particular blockchain.
-
-In case of a dispute there must a way to prove to the justice that the
-customer has paid for the transaction. As the proof of transaction is
-trivial in transparent and trackable blockchains, it gets more
-complicated when it comes to anonymous blockchains. Monero allows
-proving and checking payments via dedicated API \cite{Howtopro46}.
-ZCash provides mechanism called Payment Disclosure \cite{AnIntrod25},
-which at the time of writing is still a experimental feature
+Both approaches have some advantages and disadvantages, but our protocol can abstract them away by treating them as some randomly genrated unique number, often called \textit{nonce} (number once).
+How it is implemented depends on a particular blockchain.
+
+In case of a dispute there must a way to prove to the justice that the customer has paid for the transaction.
+As the proof of transaction is trivial in transparent and trackable blockchains, it gets more complicated when it comes to anonymous blockchains.
+Monero allows proving and checking payments via dedicated API \cite{Howtopro46}.
+ZCash provides mechanism called Payment Disclosure \cite{AnIntrod25}, which at the time of writing is still a experimental feature
 \cite{paymentd11}.
@@
 \subsection{Storage network}\label{storage-network}
-Once the SP finish its service, he has to provide the results to the
-customer. The most natural approach would to be send the results via
-email of decidated platform. However, since the customer wants to stay
-anonymous, he don't want to expose his email address nor IP address.
-Moreover, in case of dispute the SP should be able to prove that the
-results have been provided before the deadline.
-
-One approach would be to post the results into a blockchain. Yet,
-storing data on a blockchain is very expensive. The most common
-workaround
-(\cite{shahid2020blockchain, wang2019auditable, chen2017improved, Usageide95})
-is to publish the data to the IPFS \cite{benet2014ipfs}—a content
-adressable peer-to-peer storage network—and publish to a blockchain
-just a content identifier (cid) that uniquely points to the content
-stored on the IPFS.
-
-We take the same approach. Once the SP creates the results, he encrypts
-them using the previously provided encryption key; then publish
-them into a IPFS network.
-
-To increase anonimity, the customer should use a common techniques to
-hide its IP address; for example, use gateway, VPN, proxy, or onion
-routing.
+Once the SP finish its service, he has to provide the results to the customer.
+The most natural approach would to be send the results via email of decidated platform.
+However, since the customer wants to stay anonymous, he don't want to expose his email address nor IP address.
+Moreover, in case of dispute the SP should be able to prove that the results have been provided before the deadline.
+
+One approach would be to post the results into a blockchain.
+Yet, storing data on a blockchain is very expensive.
+The most common workaround (\cite{shahid2020blockchain, wang2019auditable, chen2017improved, Usageide95}) is to publish the data to the IPFS \cite{benet2014ipfs}—a content adressable peer-to-peer storage network—and publish to a blockchain just a content identifier (cid) that uniquely points to the content stored on the IPFS.
+
+We take the same approach. Once the SP creates the results, he encrypts them using the previously provided encryption key; then publish them into a IPFS network.
+
+To increase anonimity, the customer should use a common techniques to hide its IP address; for example, use gateway, VPN, proxy, or onion routing.
 
 \subsection{Separation of concerns}
-We could use one blockchain to achieve all of these three roles: (i)
-anonymous payments; (ii) message board; (iii) storage network.
-
-As the message board could be achieved by most of the blockchanis, the
-anonymous payments isn't so prevalent, and provable storage network is a
-functionality of a few specialised blockchains.
-
-Instead of searching for one blockchain that solves all the
-functionallities, we allow the framework to use separate blockchains for
-each of the functionalities. In case a suitable blockchain arises, it
-can play more than one role.
-
-At the time of writing, we see following technologies that fulfill the
-requrements of each role:
+We could use one blockchain to achieve all of these three roles: (i) anonymous payments; (ii) message board; (iii) storage network.
+
+As the message board could be achieved by most of the blockchanis, the anonymous payments isn't so prevalent, and provable storage network is a functionality of a few specialised blockchains.
+
+Instead of searching for one blockchain that solves all the functionallities, we allow the framework to use separate blockchains for each of the functionalities.
+In case a suitable blockchain arises, it can play more than one role.
+
+At the time of writing, we see following technologies that fulfill the requrements of each role:
 
@@
 
-\section{The Protocol}
+\section{The Protocol}\label{sec:protocol}
 
@@
     \begin{itemize}
-        \item Supports anonymous, i.e., untraceable and (ideally) unlinkable transactions as specified in section~\ref{pseudo-anonymous-vs-anonymous-blockchain}.
+        \item Supports anonymous, i.e., untraceable and (ideally) unlinkable transactions as specified in section~\ref{sec:pseudo-anon}.
         \item Supports uniquely identifying transaction either via separate address per transaction, memo field, or other similar mechanism as described in section ~\ref{payment-for-services}. 
@@
 $\mathrm{PoD}$ could be published on a message board (similarly to $\mathrm{PoP}$); however, since the $\mathrm{pkg}$ is delivered personally or via trusted person, the confirmation can be issued in person as well.
-If we would like to hire a courier to deliver our $\mathrm{pkg}$, then the $\mathrm{PoD}$ would have to be published on message board (further extension to anonymous delivery system is discussed in section \ref{future-work}).
+If we would like to hire a courier to deliver our $\mathrm{pkg}$, then the $\mathrm{PoD}$ would have to be published on message board (further extension to anonymous delivery system is discussed in section \ref{sec:future-work}).
 
@@
 
-\paragraph{Step 3: Provision of
-service}\label{step-3-provision-of-service}
+\paragraph{Step 3: Provision of service}\label{step-3-provision-of-service} 
 Once the transaction is paid the SP start the provision of service.
@@
 
-\paragraph{Step 4: Results
-upload}\label{step-4-results-upload}
+\paragraph{Step 4: Results upload}\label{step-4-results-upload}
 
@@
 
-\paragraph{Step 5: Proof of provision
-publication}\label{step-5-proof-of-provision-publication}
+\paragraph{Step 5: Proof of provision publication}\label{step-5-proof-of-provision-publication}
 
@@
 
-\paragraph{Step 6: Proof-of-provision
-notification}\label{step-6-proof-of-provision-notification}
+\paragraph{Step 6: Proof-of-provision notification}\label{step-6-proof-of-provision-notification}
 
@@
 
-\paragraph{Step 7: Results download}\label{step-7-results-download}
-Having the $\mathrm{cid}$, the customer downloads and decrypts the $\mathrm{results}$.
+\paragraph{Step 7: Results download}\label{step-7-results-download} Having the $\mathrm{cid}$, the customer downloads and decrypts the $\mathrm{results}$.
 
@@
 
-\section{Fairness analysis}
+\section{Fairness analysis}\label{sec:fairness-analysis}
+
 We analyse the fairness of the protocol by representing it as a interactive non-cooperative game.
@@
 \item
-  We assume the steps of the protocol to be atomic, there are no
-  intermediate steps.
-\item
-  Repeating the first step starts new transaction. Repeating any other
-  step is considered abnormal and gets ignored. For example paying for
-  the invoice twice does not cause any effect on the curse of protocol.
-\item
-  Once published, the results are available to the customer in the
-  content storage. The idea of guaranteeing it cryptographically is
-  discussed in section ~\ref{future-work}.
-\item
-  The protocol can go only forward, there is no way of revert any
-  action.
-\item
-  Losing the dispute leads to punishment that is greater than any
-  reward, which leads to disadvantaged position (-). Hence, the rational
-  customer won't start a dispute that he is not sure to win.
+  We assume the steps of the protocol to be atomic, there are no intermediate steps.
+\item
+  Repeating the first step starts new transaction.
+Repeating any other step is considered abnormal and gets ignored.
+For example paying for the invoice twice does not cause any effect on the curse of protocol.
+\item
+  Once published, the results are available to the customer in the content storage. The idea of guaranteeing it cryptographically is discussed in section ~\ref{future-work}.
+\item
+  The protocol can go only forward, there is no way of revert any action.
+\item
+  Losing the dispute leads to punishment that is greater than any reward, which leads to disadvantaged position (-). Hence, the rational customer won't start a dispute that he is not sure to win.
 \item
@@
 \item
-  Both the customer and the SP are rational (selfish). They always
-  prefer go from worst position to better position, but also risk
-  temporary worst position in favour for later better position iff it's
-  assured that they won't stuck in worst position.
+  Both the customer and the SP are rational (selfish).
+They always prefer go from worst position to better position, but also risk temporary worst position in favour for later better position iff it's assured that they won't stuck in worst position.
 \end{itemize}
@@
 
-The table in figure~\ref{fig:positions} shows the positions of each party after each possible
-action taken.
+The table in figure~\ref{fig:positions} shows the positions of each party after each possible action taken.
 
@@
 \centering
-\caption{Formal table of positions}
+\caption{Table of positions after each step of protocol}
 \label{fig:positions}
@@
 
-Below is the description for each step and rationale of the outcome
-position.
+Below is the description for each step and rationale of the outcome position.
 
@@
   \item
-    \(\sigma_{1, c, \mathrm{n}} = •\) - the customer has risked its
+    \(\sigma_{1, c, \mathrm{n}} = \sbullet\), the customer has risked its
     materials but has not paid anything, so we assume he is in neutral
-    position (•). One would argue that the customer has put effort of
+    position. One would argue that the customer has put effort of
     delivering the materials to the SP, or that the sample is valuable.
@@
   \item
-    \(\sigma_{1, s, \mathrm{n}} = •\) - the SP is in neutral position as
-    he didn't put any effort to rece the package, also the package
-    hasn't any value to the SP (•).
+    \(\sigma_{1, s, \mathrm{n}} = \sbullet\), the SP is in neutral position as he didn't put any effort to hence the package, also the package hasn't any value to the SP.
   \end{itemize}
@@
   \item
-    \(\sigma_{1, c, \mathrm{d}} = -\) - the customer lose the case as
-    the SP has still opportunity to publish proof-of-provision within
-    timeframe (-).
-  \item
-    \(\sigma_{1, s, \mathrm{d}} = •\) - the SP win the case for the same
-    reason (•).
+    \(\sigma_{1, c, \mathrm{d}} = -\), the customer lose the case as the SP has still opportunity to publish proof-of-provision within timeframe.
+  \item
+    \(\sigma_{1, s, \mathrm{d}} = \sbullet\), the SP win the case for the same reason.
   \end{itemize}
@@
   The customer can follow the protocol and move to the non-disadvantaged
-  position \(\sigma_{1, c, \mathrm{n}} = •\).
+  position \(\sigma_{1, c, \mathrm{n}} = \sbullet\).
 \item
   The SP can do nothing and end up in non-disadvantaged position
-  \(\sigma_{1, s, \mathrm{n}} = •\) or
-  \(\sigma_{1, s, \mathrm{d}} = •\).
+  \(\sigma_{1, s, \mathrm{n}} = \sbullet \) or
+  \(\sigma_{1, s, \mathrm{d}} = \sbullet \).
 \end{itemize}
@@
   Following protocol:
-
-  \begin{itemize}
-
-  \item
-    \(\sigma_{2, c, \mathrm{n}} = -\) the customer has spend his funds
-    but hasn't received the results. Therefore, he moves to the
-    disadvantaged position (-).
-  \item
-    \(\sigma_{2, s, \mathrm{n}} = +\) the SP has received the payment
-    but hasn't spend his resources yet. Therefore, he moves to advantaged
-    position (+).
+  \begin{itemize}
+  \item
+    \(\sigma_{2, c, \mathrm{n}} = -\), the customer has spend his funds but hasn't received the results.
+  \item
+    \(\sigma_{2, s, \mathrm{n}} = +\), the SP has received the payment but hasn't spend his resources yet.
   \end{itemize}
@@
   \begin{itemize}
-
-  \item
-    \(\sigma_{2, c, \mathrm{d}} = -\) the customer lose the case as the
-    SP has still opportunity to publish proof-of-provision before the
-    deadline (-)
-  \item
-    \(\sigma_{2, s, \mathrm{d}} = +\) the SP win the case for the same
-    reason (+)
-  \end{itemize}
-\end{itemize}
-
-Customer has timeouted \(time-to-issue-\), then:
+  \item
+    \(\sigma_{2, c, \mathrm{d}} = -\), the customer lose the case as the SP has still opportunity to publish proof-of-provision before the deadline.
+  \item
+    \(\sigma_{2, s, \mathrm{d}} = +\), the SP win the case for the same reason.
+  \end{itemize}
+\end{itemize}
+
+Customer has time outed, then:
 
@@
   Following protocol:
-
-  \begin{itemize}
-
-  \item
-    \(\sigma_{2, c, \overline{\mathrm{n}}} = •\) - the customer ends up
-    in neutral position, since he didn't spend his funds (•)
-  \item
-    \(\sigma_{2, s, \overline{\mathrm{n}}} = •\) - The SP ends up in
-    neutral position as he didn't receive the payment, nor spent his
-    resources (•)
+  \begin{itemize}
+  \item
+    \(\sigma_{2, c, \overline{\mathrm{n}}} = \sbullet\), the customer ends up in neutral position, since he didn't spend his funds.
+  \item
+    \(\sigma_{2, s, \overline{\mathrm{n}}} = \sbullet\), the SP ends up in neutral position as he didn't receive the payment, nor spent his resources.
   \end{itemize}
@@
   \item
-    \(\sigma_{2, c, \overline{\mathrm{d}}} = -\) - the customer loses
-    the case as he can not prove the payment before the time limit.
-    Consequently, ends up in disadvantaged position (-)
-  \item
-    \(\sigma_{2, s, \overline{\mathrm{d}}} = •\) - the SP is not charged
-    to the justice due to lack of proofs. Therefore, he ends up in
-    neutral position (•)
+    \(\sigma_{2, c, \overline{\mathrm{d}}} = -\), the customer loses the case as he can not prove the payment before the time limit.
+  \item
+    \(\sigma_{2, s, \overline{\mathrm{d}}} = \sbullet\), the SP is not charged to the justice due to lack of proofs.
   \end{itemize}
@@
   non-disadvantaged position, i.e.,
-  \(\sigma_{3, c, \overline{\mathrm{d}}} = •\),
-  \(\sigma_{4, c, \overline{\mathrm{d}}} = •\),
-  \(\sigma_{5, c, \overline{\mathrm{d}}} = •\).
+  \(\sigma_{3, c, \overline{\mathrm{d}}} = \sbullet\),
+  \(\sigma_{4, c, \overline{\mathrm{d}}} = \sbullet\),
+  \(\sigma_{5, c, \overline{\mathrm{d}}} = \sbullet\).
 \item
@@
   \(\sigma_{2, s, \mathrm{n}} = +\), \(\sigma_{2, s, \mathrm{d}} = +\),
-  \(\sigma_{2, s, \overline{\mathrm{n}}} = •\),
-  \(\sigma_{2, s, \overline{\mathrm{d}}} = •\).
-\end{itemize}
-
-\paragraph{Step 3, SP turn: provision of
-service}\label{step-3-provision-of-service}
+  \(\sigma_{2, s, \overline{\mathrm{n}}} = \sbullet\),
+  \(\sigma_{2, s, \overline{\mathrm{d}}} = \sbullet\).
+\end{itemize}
+
+\paragraph{Step 3, SP turn: provision of service}\label{step-3-provision-of-service}
 
@@
   \item
-    \(\sigma_{3, c, \mathrm{n}} = -\) the customer hasn't received the
-    results. Therefore, he remains in disadvantaged position (-).
-  \item
-    \(\sigma_{3, s, \mathrm{n}} = +\) the SP has fullfiled the contract
-    on time (+).
+    \(\sigma_{3, c, \mathrm{n}} = -\), the customer hasn't received the
+    results so he remains in disadvantaged position.
+  \item
+    \(\sigma_{3, s, \mathrm{n}} = +\), the SP has fulfilled the contract
+    on time.
   \end{itemize}
@@
   \item
-    \(\sigma_{3, c, \mathrm{d}} = -\) the customer lose the case as the
+    \(\sigma_{3, c, \mathrm{d}} = -\), the customer lose the case as the
     SP has still opportunity to publish proof-of-provision within
-    timeframe (-)
-  \item
-    \(\sigma_{3, s, \mathrm{d}} = +\) the SP win the case for the same
-    reason (+)
+    timeframe.
+  \item
+    \(\sigma_{3, s, \mathrm{d}} = +\), the SP win the case for the same
+    reason.
   \end{itemize}
@@
   \item
-    \(\sigma_{3, c, \overline{\mathrm{n}}} = -\) the customer ends up in
-    disadvantaged position (-)
-  \item
-    \(\sigma_{3, s, \overline{\mathrm{n}}} = +\) the SP ends up in
-    advantaged position as he received the payment (+)
+    \(\sigma_{3, c, \overline{\mathrm{n}}} = -\), the customer ends up in disadvantaged position.
+  \item
+    \(\sigma_{3, s, \overline{\mathrm{n}}} = +\), the SP ends up in
+    advantaged position as he received the payment.
   \end{itemize}
@@
   \item
-    \(\sigma_{3, c, \overline{\mathrm{d}}} = •\) the customer wins the
-    case and end up in neutral position (•)
-  \item
-    \(\sigma_{3, s, \overline{\mathrm{d}}} = -\) the SP loses the case
-    and end up in disadvantaged position (-)
+    \(\sigma_{3, c, \overline{\mathrm{d}}} = •\), the customer wins the case and end up in neutral position.
+  \item
+    \(\sigma_{3, s, \overline{\mathrm{d}}} = -\), the SP loses the case
+    and end up in disadvantaged position.
   \end{itemize}
@@
 
-\paragraph{Step 4, SP turn: publication of
-results}\label{step-4-publication-of-results}
+\paragraph{Step 4, SP turn: publication of results}\label{step-4-publication-of-results}
 
@@
   \item
-    \(\sigma_{4, c, \mathrm{n}} = -\) the customer hasn't received the
-    results. Therefore, he remains in disadvantaged position (-).
-  \item
-    \(\sigma_{4, s, \mathrm{n}} = +\) the SP has fullfiled the contract
-    on time (+).
+    \(\sigma_{4, c, \mathrm{n}} = -\), the customer hasn't received the results so he remains in disadvantaged position.
+  \item
+    \(\sigma_{4, s, \mathrm{n}} = +\), the SP has fulfilled the contract on time.
   \end{itemize}
@@
   \item
-    \(\sigma_{4, c, \mathrm{d}} = -\) the customer lose the case as the
+    \(\sigma_{4, c, \mathrm{d}} = -\), the customer lose the case as the
     SP has still opportunity to publish proof-of-provision within
-    timeframe (-)
-  \item
-    \(\sigma_{4, s, \mathrm{d}} = +\) the SP win the case for the same
-    reason (+)
+    timeframe.
+  \item
+    \(\sigma_{4, s, \mathrm{d}} = +\), the SP win the case for the same
+    reason.
   \end{itemize}
@@
   \item
-    \(\sigma_{4, c, \overline{\mathrm{n}}} = -\) the customer ends up in
-    disadvantaged position (-)
-  \item
-    \(\sigma_{4, s, \overline{\mathrm{n}}} = +\) the SP ends up in
-    advantaged position as he received the payment (+)
+    \(\sigma_{4, c, \overline{\mathrm{n}}} = -\), the customer ends up in
+    disadvantaged position.
+  \item
+    \(\sigma_{4, s, \overline{\mathrm{n}}} = +\), the SP ends up in
+    advantaged position as he received the payment.
   \end{itemize}
@@
   \item
-    \(\sigma_{4, c, \overline{\mathrm{d}}} = •\) the customer wins the
-    case and end up in neutral position (•)
-  \item
-    \(\sigma_{4, s, \overline{\mathrm{d}}} = -\) the SP loses the case
-    and end up in disadvantaged position (-)
+    \(\sigma_{4, c, \overline{\mathrm{d}}} = •\), the customer wins the
+    case and end up in neutral position.
+  \item
+    \(\sigma_{4, s, \overline{\mathrm{d}}} = -\), the SP loses the case
+    and end up in disadvantaged position.
   \end{itemize}
@@
   non-disadvantaged position
-  \(\sigma_{4, c, \overline{\mathrm{d}}} = •\).
+  \(\sigma_{4, c, \overline{\mathrm{d}}} = \sbullet\).
 \item
@@
 
-\paragraph{Step 5, SP turn: publication of
-proof-of-provision}\label{step-5-publication-of-proof-of-provision}
+\paragraph{Step 5, SP turn: publication of proof-of-provision}\label{step-5-publication-of-proof-of-provision}
 
@@
     \(\sigma_{5, c, \mathrm{n}} = -\) the customer hasn't received the
-    results. Therefore, he remains in disadvantaged position (-).
-  \item
-    \(\sigma_{5, s, \mathrm{n}} = +\) the SP has fullfiled the contract
-    on time (+).
+    results. Therefore, he remains in disadvantaged position.
+  \item
+    \(\sigma_{5, s, \mathrm{n}} = +\) the SP has fulfilled the contract
+    on time.
   \end{itemize}
@@
     \(\sigma_{5, c, \mathrm{d}} = -\) the customer lose the case as the
-    SP can prove the publication of proof-of-provision (-)
+    SP can prove the publication of proof-of-provision.
   \item
     \(\sigma_{5, s, \mathrm{d}} = +\) the SP win the case as the SP can
-    prove the publication of proof-of-provision (+)
+    prove the publication of proof-of-provision.
   \end{itemize}
@@
   \item
-    \(\sigma_{5, c, \overline{\mathrm{n}}} = -\) the customer ends up in
-    disadvantaged position (-)
+    \(\sigma_{5, c, \overline{\mathrm{n}}} = -\) the customer ends up in disadvantaged position.
   \item
     \(\sigma_{5, s, \overline{\mathrm{n}}} = +\) the SP ends up in
-    advantaged position as he received the payment (+)
+    advantaged position as he received the payment.
   \end{itemize}
@@
     \(\sigma_{5, c, \overline{\mathrm{d}}} = •\) the customer wins the
-    case and end up in neutral position (•)
+    case and end up in neutral position.
   \item
     \(\sigma_{5, s, \overline{\mathrm{d}}} = -\) the SP loses the case
-    and end up in disadvantaged position (-)
+    and end up in disadvantaged position.
   \end{itemize}
@@
 
-\paragraph{Step 6, customer turn: pull
-proof-of-provision}\label{step-6-pull-proof-of-provision}
+\paragraph{Step 6, customer turn: pull proof-of-provision}\label{step-6-pull-proof-of-provision}
 
@@
     \(\sigma_{6, c, \mathrm{n}} = -\) the customer gets hash of the
-    results but not the results. Therefore, he is still in disadvantaged
-    position(-).
-  \item
-    \(\sigma_{6, s, \mathrm{n}} = +\) the SP position hasn't changed(+).
+    results but not the results yet.
+  \item
+    \(\sigma_{6, s, \mathrm{n}} = +\) the SP position hasn't changed.
   \end{itemize}
@@
     \(\sigma_{6, c, \mathrm{d}} = -\) the customer lose the case as the
-    SP can prove the publication of proof-of-provision (-)
+    SP can prove the publication of proof-of-provision.
   \item
     \(\sigma_{6, s, \mathrm{d}} = +\) the SP win the case as the SP can
-    prove the publication of proof-of-provision (+)
+    prove the publication of proof-of-provision.
   \end{itemize}
@@
     \(\sigma_{6, c, \overline{\mathrm{n}}} = -\) the customer ends up in
-    disadvantaged position (-)
+    disadvantaged position.
   \item
@@
     advantaged position as he received the payment but didn't spend his
-    resources (+)
+    resources.
   \end{itemize}
@@
     \(\sigma_{6, c, \overline{\mathrm{d}}} = •\) the customer wins the
-    case and end up in neutral position (•)
+    case and end up in neutral position.
   \item
     \(\sigma_{6, s, \overline{\mathrm{d}}} = -\) the SP loses the case
-    and end up in disadvantaged position (-)
+    and end up in disadvantaged position.
   \end{itemize}
@@
   the protocol start a dispute and win the case
-  \(\sigma_{6, c, \overline{\mathrm{d}}} = •\).
+  \(\sigma_{6, c, \overline{\mathrm{d}}} = \sbullet\).
 \item
@@
 
-\paragraph{Step 7, customer turn: retrieval of
-results}\label{step-7-retrieval-of-results}
+\paragraph{Step 7, customer turn: retrieval of results}\label{step-7-retrieval-of-results}
 
@@
     \(\sigma_{7, c, \mathrm{n}} = +\) the customer gets the correct
-    results. Therefore, he moves to advantaged position (+).
-  \item
-    \(\sigma_{7, s, \mathrm{n}} = +\) the SP position hasn't changed
-    (+).
+    results. Therefore, he moves to advantaged position.
+  \item
+    \(\sigma_{7, s, \mathrm{n}} = +\) the SP position hasn't changed.
   \end{itemize}
@@
     \(\sigma_{7, c, \mathrm{d}} = -\) the customer lose the case as the
-    SP can prove the publication of proof-of-provision (-)
+    SP can prove the publication of proof-of-provision.
   \item
     \(\sigma_{7, s, \mathrm{d}} = +\) the SP win the case as the SP can
-    prove the publication of proof-of-provision (+)
+    prove the publication of proof-of-provision.
   \end{itemize}
@@
   \item
-    \(\sigma_{7, c, \overline{\mathrm{n}}} = -\) customer end up in
-    disadvantaged position, as he ends up with incorrect results (-)
+    \(\sigma_{7, c, \overline{\mathrm{n}}} = -\) customer end up in disadvantaged position, as he ends up with incorrect results.
   \item
     \(\sigma_{7, c, \overline{\mathrm{n}}} = +\) SP ends up in advantaged
-    position as he received the payment but didn't spend his resources
-    (+)
+    position as he received the payment but didn't spend his resources.
   \end{itemize}
@@
   \item
-    \(\sigma_{7, c, \overline{\mathrm{d}}} = •\) customer wins the case and ends up in neutral position (•)
-  \item
-    \(\sigma_{7, c, \overline{\mathrm{d}}} = -\) SP lose the case and end up in disadvantaged position (-)
+    \(\sigma_{7, c, \overline{\mathrm{d}}} = •\) customer wins the case and ends up in neutral position.
+  \item
+    \(\sigma_{7, c, \overline{\mathrm{d}}} = -\) SP lose the case and end up in disadvantaged position.
   \end{itemize}
@@
 
-\section{Future work}\label{future-work}
+\section{Future work}\label{sec:future-work}
 \subsection{Justice}\label{justice}
@@
 
-\section{Conclusions}
+\section{Conclusions}\label{sec:conclusion}
 In this paper, we have proposed a anonymity- preserving blockchain-based framework for local services provision.

### 2022-03-03 access.tex
szymanski fixes and my patches

@@
 \title{Anonymous provision of services via blockchain}
-\author{\uppercase{Stanis\l{}aw Bara{\'n}ski}\authorrefmark{1}}
-
-\address[1]{Department of Electronic, Telecommunication and Informatics, Gdansk University of Technology, Narutowicza 11/12 Gdansk Poland (e-mail: stanislaw.baranski@pg.edu.pl}
-
-\tfootnote{This paragraph of the first footnote will contain support 
-information, including sponsor and financial support acknowledgement. For 
-example, ``This work was supported in part by the U.S. Department of 
-Commerce under Grant BS123456.''}
-
-\markboth{Bara{\'n}ski : 
+\author{\uppercase{Stanis\l{}aw Bara{\'n}ski}\authorrefmark{1},
+\uppercase{Julian Szyma{\'n}ski\authorrefmark{1} } 
+ }
+
+\address[1]{Department of Electronic, Telecommunication and Informatics, Gdansk University of Technology, Narutowicza 11/12 Gdansk Poland (e-mail: stanislaw.baranski@pg.edu.pl, julian.szymanski@eti.pg.edu.pl}
+
+\tfootnote{The work has been supported partially by the founds of Department of Computer Architecture Faculty of Electronics, Telecommunications and Informatics, Gdańsk University of Technology.}
+
+\markboth{S. Bara{\'n}ski, J. Szyma{\'n}ski : 
 Anonymous provision of local services via blockchain}
-{Bara{\'n}ski : 
+{S. Bara{\'n}ski, J. Szyma{\'n}ski : 
 Anonymous provision of local services via blockchain}
@@
 
-We propose a framework for coordinating local anonymous service
+We propose a protocol for coordinating local anonymous service
 provision. Our proposal uses blockchain for both anonymous payments and proofs of existence (so-called message board) and content-addressable network (e.g.~IPFS) for results delivery.
 
-A local service provider can employ our framework to provide
+A local service provider can employ our protocol to provide
 services without collecting any personal information. Possible
-applications for this framework include anonymous clinical drug testing,
+applications for this protocol include anonymous clinical drug testing,
 steroid testing, parenting testing, anonymous legal advice, or
@@
 incorrect results, the customer can disclose the whole interaction and
-prove to justice (police or court) the misbehaviour of the service
+prove to justice (police or court) the misbehavior of the service
 provider.
 
-We analyse the protocol in the context of fairness and discuss further
+We analyze the protocol in the context of fairness and discuss further
 extensions to an anonymous delivery system, payment with cash, and
-decentralised conflict resolution system.
-
-Our framework can enable various services currently based on unacceptable trust assumptions to the SP.
+decentralized conflict resolution system.
+
+Our protocol can enable various services currently based on unacceptable trust assumptions to the SP.
+%JS to framework czy protocol?
+%SB zmieniłem na protocol, framework jest zbyt abstrakcyjne
 \end{abstract}
@@
 Such user information can be used deliberately or unintentionally
-(e.g., by theft) for insider disclosure, unauthorised access, or
+(e.g., by theft) for insider disclosure, unauthorized access, or
 commercial gains.
@@
 
-The guarantee of the privacy of the data is often based merely on a trust assumptions and security of IT system.
-However, most of the SP do not need the personal information for any other reason than payment or communication, which should be considered secondary compared to actual service provision.
+The guarantee of the privacy of the data is often based merely on trust assumptions and the security of IT system.
+However, most of the SP does not need personal information for any other reason than payment or communication, which should be considered secondary compared to actual service provision.
 
@@
 
-Example services that would benefit from anonymous services are:
-\begin{itemize}
-    \item Patients willing to take a steroid test, drug tests, venereal diseases test, paternity test — have strong incentive to keep the whole procedure private.
+There is some services that would benefit from anonymous services, some examples are:
+\begin{itemize}
+    \item Patients willing to take a 
+    test for drug, venereal diseases, paternity etc.
+have a strong incentive to keep the whole procedure private.
 Merely the fact that they took the test — without exposing the results — is suggestive enough to act as a premise in case of a conflict.
 
-Especially celebrities, politicians and public figures are prone to this kind of problem as such precedent can negatively influence their future career.
-
-Currently, they have to risk that their personal details, materials, and results are stored securely and kept in private from any unauthorised actor (both curious employee, and malicious attacker).
+Especially celebrities, politicians, and public figures are prone to this kind of problem as such precedent can negatively influence their future career.
+
+Currently, they have to risk that their personal details, materials, and results are stored securely and kept in private from any unauthorized actor (both curious employee, and malicious attacker).
 
@@
 systems.
-\item People willing to take business action that may be risky or not yet fully legislated, may be willing to receive the risk estimation and prediction of possible repercussions of such action.
+\item People willing to take business activities that may be risky % or not yet fully legislated, 
+may be willing to receive the risk estimation and prediction of possible personal repercussions of such action.
 
@@
 
-Our protocol would allow taking such advices anonymously, and therefore
+Our protocol would allow taking such advice anonymously, and therefore
 getting rid of the strong trust assumption put on the lawyers and their IT systems.
@@
 
-We propose a framework for anonymously provisioning services that require delivery of physical materials.
-A service provider employing our framework can provide services without collecting any personal information from customers.
+We propose a protocol for anonymously provisioning services that require the delivery of physical materials.
+A service provider employing our protocol can provide services without collecting any personal information from customers.
 
@@
 incorrect results, the customer can disclose the whole interaction and
-prove to justice (police or court) the misbehaviour of the service
+prove to justice (police or court) the misbehavior of the service 
 provider.
+%JS a np automatyczny zwrot środków?
+%SP to wymagałoby wprowadzenie depozytu co bardzo komplikuje cały system. Co więcej miałoby to sens tylko wtedy gdyby użyć "zdecentralizowanych sądów" (Future Work/Justice).
 
@@
     \item Privacy-preserving blockchain, to allow customers anonymously pay for the services.
-    \item Message board blockchain, to achieve fairness, i.e., as a mean for proving that certain actions took place at a certain moment of time without the trusted third party.
+    \item Message board blockchain, to achieve fairness, i.e., as a means for proving that certain actions took place at a certain moment without the trusted third party.
     \item Content-addressable peer-to-peer storage network, to provide results to the customer. 
@@
 
-In our case the customer is exchanging with the SP cryptocurrency and materials for the results.
-
-\paragraph{Contributions}
+In our case, the customer is exchanging with the SP cryptocurrency and materials for the results.
+
+%\paragraph{Contributions}
 We contribute to the field of fair-exchanges by proposing a simple,
-practical, and anonymous framework that does not rely on centralised trusted-third party, but on decentralised blockchain and
+ practical, and anonymous protocol that does not rely on centralized trusted-third party, but on decentralized blockchain and
 distributed content-addressable storage network.
@@
 
-Our framework simultaneously provides five main properties:
-
-\begin{itemize}
-\item Anonimity:
-throughout the whole transaction the customer stays anonymous to all external observers.
+Our protocol simultaneously provides five main properties:
+
+\begin{itemize}
+\item Anonymity:
+throughout the whole transaction, the customer stays anonymous to all external observers.
 \item Fairness:
-at each step of the protocol, both parties are incentivised to act accordingly to the protocol; otherwise the misbehaving party ends up in worst position.
-\item Dispute resolution: at each step of the protocol the customer can open a dispute win the case iff the SP misbehaved.
+at each step of the protocol, both parties are incentivized to act accordingly to the protocol; otherwise, the misbehaving party ends up in the worst position.
+\item Dispute resolution: at each step of the protocol the customer can start a dispute and win the case if and only if the SP misbehaved.
+
 \item TTP-less: 
-our protocol does not rely on trusted-third party to conduct transactions in fairly manner.
-Only in case of dispute the centralised justice is invlolved (the justice decentralisation is discussed in section ~\ref{sec:future-work}.
+our protocol does not rely on a trusted-third party to conduct transactions in fairly manner.
+Only in case of dispute   the centralized justice is involved (the justice decentralization is discussed in section ~\ref{sec:future-work}.
 \item Physical materials: our protocol allows providing not only digital but also physical materials to the service provider.
@@
 Some authors have proposed blockchain-based fair-exchange systems that could be adapted to service provision; however, to our best knowledge we
-are the first to propose a system that satisfy all five properties
-stated above. Especially anonimity and physical materials delivery, are
+are the first to propose a system that satisfies all five properties
+stated above using blockchain technology. Especially anonymity and physical materials delivery, are
 properties that were rarely addressed together, and if so, the protocol
-based on TTP, and strong and impractial assumptions on banking system~\cite{birjoveanu2015anonymity}, or didn't address the of conflict
+based on TTP, and strong and impractical assumptions on banking system~\cite{birjoveanu2015anonymity}, or didn't address the conflict
 between parties~\cite{altawy2017lelantos}.
 
-Our framework can potentially enable variety of services that for many
-customers base on unacceptable trust assumptions to the SP.
-
-\paragraph{Organisation}
+Our protocol can potentially enable a variety of services that for many
+customers based on unacceptable trust assumptions to the SP.
+
+%\paragraph{Organisation}
 The remainder of this paper is organized as follows.
 In section~\ref{sec:related-works} we briefly review related works. 
-Section~\ref{sec:background} explains the background related to fair-exchanges, blockchain, anonymity and confidentiality, and storage network. 
-Section~\ref{sec:protocol} describes how the protocol works in details.
-Section~\ref{sec:fairness-analysis} provides an fairness analysis of the proposed protocol.
+Section~\ref{sec:building-blocks} explains the background related to fair-exchanges, blockchain, anonymity and confidentiality, and storage network. 
+Section~\ref{sec:protocol} describes how the protocol works in detail.
+Section~\ref{sec:fairness-analysis} provides a fairness analysis of the proposed protocol.
 Section~\ref{sec:future-work} discuss possible improvements. 
@@
 
-\paragraph{Anonymity and Fair-Exchange in e-Commerce Protocol for Physical Products Delivery} \label{anonymity-and-fair-exchange-in-e-commerce-protocol-for-physical-products-delivery}
+\subsection{Fair-exchange and blockchain}
+The idea of certified mail is simple, neither the sender can deny sending the mail, nor the receiver can deny receiving it.
+As the service is widely used in paper world, achieving it for e-mails haven't meet the agreement across scientific community for over 40 years.
+The main reason was the dependency of TTP, which significantly reduce the performance, security, and robustness of such protocols.
+The protocols that do not use TTP struggle with high computation and communication overhead.
+
+Authors of ~\cite{hinarejos2019solution} replaced the TTP with blockchain (concretely Bitcoin blockchain as a reference implementation), which acts as a secure, verifiable, and decentralized TTP.
+
+The idea behind certified e-mails—and any other fair-exchange protocol—is following:
+\begin{enumerate}
+    \item The sender sends encrypted and signed message to the receiver.
+    \item The receiver returns a proof of delivery (a signature) of the encrypted message to the sender.
+    \item The sender publish on blockchain (or TTP in general) a proof of delivery and the decryption key.
+    \item The receiver decrypts the encrypted message using the published decryption key.
+\end{enumerate}
+
+The non-repudiation requirement is achieved by the receiver sending the proof of delivery prior having access to the decrypted message.
+And the sender publishing the decription key together with the proof of delivery on blockchain (or TTP) so that the receiver can not deny both receiving the message and having access to decryption key, because it is publicly available.
+
+The protocol also handles confidentiality — the encryption key used to encrypt and then decrypt the message is encrypted using the receiver's public key, so the key is never published in raw form.
+Also, the protocol supports timeliness, meaning that the transaction is always finalized in a finite time.
+
+In this case, the role of Blockchain is to attest the public existence of decryption key at a particular point of time.
+
+\subsection{Fair-exchange, anonymity, and physical products delivery} 
+\label{anonymity-and-fair-exchange-in-e-commerce-protocol-for-physical-products-delivery}
 
 Authors of~\cite{birjoveanu2015anonymity} proposed a
-fair-exchange of physical product and electronic payment protocol that
+fair-exchange of physical products and electronic payment protocol that
 guarantee both customer and merchant anonymity. They achieve it by
-introducing online trusted third party that validate coins and provide
+introducing online trusted third parties that validate coins and provide
 fair exchange guarantees.
 
-The anonymity is ensured by assuming the existence of source cabinet
+The anonymity is ensured by assuming the existence of a source cabinet
 (SC) and delivery cabinet (DC), and a trusted delivery agent who take
-product from a source cabinet and provide it to a destination cabinet.
-Both cabinets provides access to the product by passwords to conceal
-identity of the customer and the merchant. To avoid identity disclosure
-of customer and merchant, the access to the product is provided by
+a product from a source cabinet and provide it to a destination cabinet.
+Both cabinets provide access to the product by passwords to conceal
+the identity of the customer and the merchant. To avoid identity disclosure
+of customers and merchants, the access to the product is provided by
 passwords.
@@
     \item The merchant post the product to the source cabinet.
-    \item Delivery agent collect the product from source cabinet and post it to delivery cabinet.
-    \item Customer collects the product from delivery cabinet using password.
-    \item The customer checks if the product is actually the ordered one.
+    \item Delivery agent collects the product from the source cabinet and posts it to the delivery cabinet.
+    \item Customer collects the product from the delivery cabinet using a password.
+    \item The customer checks if the product is the ordered one.
     \begin{itemize}
@@
         \setcounter{enumii}{7}
-        \item the customer sends the acknowledge to delivery cabinet and decryption key to the merchant.
+        \item the customer sends the acknowledge to the delivery cabinet and decryption key to the merchant.
         \item The merchant redeem the coins from the bank.
@@
         \setcounter{enumii}{7}
-        \item the delivery cabinet is equipment with video camera that records the moment when the customer open the package and let the customer to signal the invalidity of the product, and so, sending the encrypted recording to the TTP.
-        \item the dispute is settled via TTP, optionally letting each party to reveal it's identity.
+        \item the delivery cabinet is equipped with a video camera that records the moment when the customer opens the package and lets the customer signal the invalidity of the product, and so, sending the encrypted recording to the TTP.
+        \item the dispute is settled via TTP, optionally letting each party reveal its identity.
     \end{enumerate}
@@
     \item the TTP does not misbehave or collude with any party. 
-    \item The customer's and merchant's banks enable confidental transactions and both share commit-buffer where the value is locked until the transaction is finished.   
-    \item All banks mantain a global list of coin's serial numbers to prevent double-spending problem. 
-    \item The source cabinet and delivery cabinet exists, and in both the product access is protected by password.
-    \item Delivery cabinet is equipped with a video camera that records the moment when the customer opens the package, and provide a way to submit the video to TTP in case of a dispute. 
+    \item The customer's and merchant's banks enable confidential transactions and both share commit-buffer where the value is locked until the transaction is finished.   
+    \item All banks maintain a global list of coin's serial numbers to prevent double-spending problems. 
+    \item The source cabinet and delivery cabinet exist, and in both the product access is protected by a password.
+    \item Delivery cabinet is equipped with a video camera that records the moment when the customer opens the package and provides a way to submit the video to TTP in case of a dispute. 
     \item There exists a trusted delivery agent.
-    \item Communication channels between parties provides anonymity.
-\end{itemize}
-
-\paragraph{Themis: Towards decentralized escrow of cryptocurrencies without trusted third parties}\label{themis-towards-decentralized-escrow-of-cryptocurrencies-without-trusted-third-parties}
+    \item Communication channels between parties provide anonymity.
+\end{itemize}
+
+\subsection{Fair-exchange, blockchain, and decentralized dispute resolution}
+\label{themis-towards-decentralized-escrow-of-cryptocurrencies-without-trusted-third-parties}
 
 Themis~\cite{meng2019themis} is a fair-exchange
-protocol, which uses blockchain instead of TTP. It provide escrow
-services for secure exchanging between cryptocurrencies and digital goods, and decentralised dispute resolution system for resolving conflicts.
-
-Two parties, say Alice and Bob, can create an escrow by generating
+protocol, which uses blockchain instead of TTP. It provides escrow
+services for secure exchanging between cryptocurrencies and digital goods, and a decentralized dispute resolution system for resolving conflicts.
+
+Two parties say Alice and Bob, can create an escrow by generating
 2-of-2 (not 2-of-3 as it is other TTP-based systems) threshold account
@@
 
-Then, both Alice and Bob, takes their keys, and split them into
+Then, both Alice and Bob, take their keys, and split them into
 \(n=2t+1\) secret shares using Shamir Secret Shamir protocol, where
-\(n\) is the number of mediators that participate in the decentralised
-network, and \(t+1\) becomes the threshold of sufficient number of
+\(n\) is the number of mediators that participate in the decentralized
+network and \(t+1\) becomes the threshold of a sufficient number of
 mediators that can reconstruct the secret key.
@@
 
-In case of dispute, the decentralised network of mediators settle the
+In case of dispute, the decentralized network of mediators settle the
 conflict and grand one winning party, the other party secret key,
-letting him to withdraw the funds.
-
-The honesty of mediators is achieved by the monetary incentivisation and
+letting him withdraw the funds.
+
+The honesty of mediators is achieved by the monetary incentivization and
 reputation system.
 
-\paragraph{Lelantos: A blockchain-based anonymous physical delivery system}\label{lelantos-a-blockchain-based-anonymous-physical-delivery-system}
+\subsection{Blockchain, anonymity, and physical delivery}\label{lelantos-a-blockchain-based-anonymous-physical-delivery-system}
 
@@
 onion routing to connect physical delivery providers. The whole route
-from merchant to customer is split into multiple steps, and each step is
-undertaken by different randomly selected delivery provider. As long as
-the develiery providers does no collude, mechant can not learn both
-identity and destination address of the customer.
+from merchant to a customer is split into multiple steps, and each step is
+undertaken by the different randomly selected delivery providers. As long as
+the delivery providers do not collude, a merchant can not learn both
+the identity and destination address of the customer.
 
 Onchain smart-contract is used to coordinate the whole process and
-mediate communication between customer and delivery providers.
+mediate communication between customers and delivery providers.
 
@@
 
-\section{Background}\label{sec:background}
+%JS moze\section{Building Blocks}
+%SB Dla mnie idealnie.
+\section{Building Blocks}\label{sec:building-blocks}
+%JS bacground czego?  
+%SB To jest takie wprowadzenie i opisanie wszystkich elementów które będą potrzebne do stowrzenia protokołu. Czy Preliminaries będzie ok?
 \subsection{Dispute resolution system}
 
-Disputes are inevitable part of all human transactions.
-Whether intentional or accidental, the system should prevent any behaviour volatiling rules of agreed contract or local jurisdiction.
-The rules are specified by law, and implemented by police.
-
-The vision of smart contract was to replace legal contract with
-programmable and autonomous contracts. The specifications of contract
-was encompasses in the code, hence the slogan ``code as a law''. Yet,
+Disputes are an inevitable part of all human transactions. Whether intentional or accidental, the system should prevent 
+violation of  
+agreed contract rules  or local jurisdiction. The rules are specified by law and implemented by the police.
+
+The vision of smart contracts was to replace the legal contract with
+programmable and autonomous contracts. The specifications of the contract
+were encompassed in the code, hence the slogan ``code as a law''. Yet,
 the blockchain paradigm has its limitations. It can assure the
-correctness of data existing on the blockchain. The problem arises on
-the contact between blockchain and real world. When we want the smart
+correctness of data existing on the blockchain. The problem arises in
+the contact between blockchain and the real world. When we want the smart
 contract to make a decision based on some input from outside the
 blockchain. We move a lot of trust assumptions on the data providers.
-The technique of providing real world data to the blockchain is called
-oracle. Oracle provide data based on decentralised network of mediators,
-therefore the trust is also decentralised.
+The technique of providing real-world data to the blockchain is called
+oracle. Oracle provides data based on a decentralized network of mediators,
+therefore the trust is also decentralized.
 
@@
 price, train delay, election results, others---and they are the ones we
-are interested in---provide the settlement of a submited dispute.
+are interested in---provide the settlement of a submitted dispute.
 
 Themis~\cite{meng2019themis} besides providing fair-exchange protocol,
-also offers a semi-autonomous decentralised dispute resolution system,
-which comply with the web3 postulates of decentralised web. Themis
-resolve disputes by set of voluntary anonymous mediators participating
-in a voting and deciding whether a party misbehaved. The honesty of
-mediators is achieved by the monetary incentivisation and reputation
+also offers a semi-autonomous decentralized dispute resolution system,
+which complies with the web3 postulates of a decentralized web. Themis
+resolve disputes by a set of voluntary anonymous mediators participating
+in voting and deciding whether a party misbehaved. The honesty of
+mediators is achieved by the monetary incentivization and reputation
 system.
@@
 Kleros~\cite{lesaege2018kleros} is a smart contract deployed on
-Ethereum platform that mimics in decentralised and autonomous way how
-court works in real life. In Kleros, every process of a dispute like
-gathering evidences, selecting jurors, rewarding the winning party is if
-automated by a set of smart contracts. Simillar to Themis, the honesty
+Ethereum platform mimics in a decentralized and autonomous way how
+the court works in real life. In Kleros, every process of a dispute like
+gathering evidence, selecting jurors, rewarding the winning party is 
+automated by a set of smart contracts. Similar to Themis, the honesty
 of the agents voting in a case is achieved by game-theoretical economic
@@
 
-In case of dispute the customer can proof to justice (police, court, etc.) convincing evidences for the honesty of the customer and misbehaviour of the SP. 
-Because the customer is anonymous the SP can not start a dispute---there is no mean to identify the customer.
-
-To mitigate the issue, we designed the protocol so that the SP who follows the protocol is always in advantage position, therefore he has no reason to start a dispute.
-The customer on the other hand can start a dispute at any time of the protocol, but only the actual misbehaviour of the SP makes him win the case.
-
-Abstracting from the services the SP is providing, in case of dispute each party should be able to prove its honest behaviour.
+In case of dispute, the customer can prove to justice (police, court, etc.) convincing evidence for the honesty of the customer and misbehavior of the SP. 
+Because the customer is anonymous the SP can not start a dispute---there is no means to identify the customer.
+
+To mitigate the issue, we designed the protocol so that the SP who follows the protocol is always in an advantageous position, therefore he has no reason to start a dispute.
+The customer on the other hand can start a dispute at any time of the protocol, but only the actual misbehavior of the SP makes him win the case.
+
+Abstracting from the services the SP is providing, in case of a dispute each party should be able to prove its honest behavior.
 We introduce three proofs that should be disclosed to justice in case of a dispute:
@@
     \item Proof-of-delivery ($\mathrm{PoD}$) is a confirmation issued by the SP to the customer that proves that the customer has delivered to the SP a complete (according to the SP requirements) package, and the SP accepted it.
-It consists of: current time; deadline to pay for the transaction; and deadline to provide the service; deadline to provide the service results; randomly generated number uniquely identifying the transaction; and the SP's signature guaranteeing non-repudiation.
+It consists of the current time; deadline to pay for the transaction, and the deadline to provide the service; deadline to provide the service results; randomly generated number uniquely identifying the transaction, and the SP's signature guaranteeing non-repudiation.
 The formal definition of the $\mathrm{PoD}$ is presented in section ~\ref{proof-of-delivery}.
@@
 
-    \item Proof-of-provision ($\mathrm{PoP}$) is an proof that the SP published the results at a certain time.
-It defend the SP in case the customer unjustly start a dispute after the results has been published.
-It consist of: content identifier as specified in section ~\ref{storage-network}; the value uniquely identifying the transaction previosuly generated in $\mathrm{PoD}$; the SP's signature guaranteeing authentication.
+    \item Proof-of-provision ($\mathrm{PoP}$) is proof that the SP published the results at a certain time.
+It defends the SP in case the customer unjustly starts a dispute after the results have been published.
+It consists of a content identifier as specified in section ~\ref{storage-network}; the value uniquely identifying the transaction previously generated in $\mathrm{PoD}$; the SP's signature guaranteeing authentication.
 The connection between $\mathrm{PoP}$ and the results is made by the content identifier which uniquely points to the results such that the $\mathrm{PoP}$ can not forge results after the publication.
@@
 The idea behind proof-of-existence is to certify that some information
-has existed at a certain moment of time, in such a way that nobody can
+has existed at a certain moment, in such a way that nobody can
 undermine its existence, integrity, and ownership (also called the
@@
 
-We let keep the protocol general enough to let the implementer use any
+We let keep the protocol general enough to 
+be implemented using any of  
 existing technology to provide message board service, with the
-assumption that it's decentralised and supports subscribing for the
-upcoming proofs from particular address.
+the assumption that it's decentralized and supports subscribing for the
+upcoming proofs from a particular address.
 
@@
 Privacy is a concept used in almost all kinds of social sciences like philosophy, psychology, sociology, and legal.
-The multidisciplinary nature leads to ambigous definitions~\cite{smith2011information}.
-For the purpose of our work we rely on more concrete definitions, i.e.~confidentality and anonymity.
-
-Confidentality is the ability to hide the details of an action from others.
-Or we can say, that the system guarantee confidentality if for all observers everything they can say about the action is the fact that it happened and nothing more.
-
-Anonymity is a the ability to hide one identity from others.
-More precisely, the unability to correlate actions performed within the system with the identity of the user.
-Or we can say, that the system guarantee anonymity if for all observers the actions are equally likely to be associated with any user of the system.
-However, anonymity is a spectrum rather than dichotomous classification.
-One method of quantifying level of anonymity is proposed in \textit{k}-anonymity~\cite{sweeney2002k}.
-It measure the user's anonymity by the number of other users from whom the user can not be distinguished.
+The multidisciplinary nature leads to ambiguous definitions~\cite{smith2011information}.
+For our work we rely on more concrete definitions, i.e.~confidentality, and anonymity.
+
+Confidentiality is the ability to hide the details of action from others.
+Or we can say, that the system guarantees confidentiality if for all observers everything they can say about the action is the fact that it happened and nothing more.
+
+Anonymity is the ability to hide one identity from others.
+More precisely, the inability to correlate actions performed within the system with the identity of the user.
+Or we can say, that the system guarantees anonymity if for all observers the actions are equally likely to be associated with any user of the system.
+However, anonymity is a spectrum rather than a dichotomous classification.
+One method of quantifying the level of anonymity is proposed in \textit{k}-anonymity~\cite{sweeney2002k}.
+It measures the user's anonymity by the number of other users from whom the user can not be distinguished.
 Concretely, the user is \textit{k}-anonymous if his actions are equally likely associated with \textit{k}-1 other users.
@@
 
-There are also techniques that can be deployed on non-anonymous blockchains, the so called mixers that literally gather together users into an \textit{anonymity set}, which then collude together in order to launder the transactions, in such a way that to a observer the likelihood of the sender of each transaction was equiprobable for any user from the anonymity set.
+Some techniques can be deployed on non-anonymous blockchains, the so-called mixers that gather together users into an \textit{anonymity set}, which then collude together to launder the transactions, in such a way that to an observer the likelihood of the sender of each transaction was equiprobable for any user from the anonymity set.
 
 Some systems guarantee pseudonomity rather than anonymity.
-Pseudonomity, allows uses to hide their real identity behind the pseudonym.
-Despite the whole system is transparent and allows linking actions to one identity, the system is considered anonymous as long as the link between pseudonym and real identity is secret.
-This assumption is hard to satisfy in practice, as the KYC (Know You Customer) and AML (Anti Money Laundering) regulations require users to reveal their real identity on most of the cryptocurrencies exchanges.
+Pseudonomity allows users to hide their real identity behind the pseudonym.
+Despite the whole system being transparent and allowing linking actions to one identity, the system is considered anonymous as long as the link between pseudonym and real identity is secret.
+This assumption is hard to satisfy in practice, as the KYC (Know Your Customer) and AML (Anti Money Laundering) regulations require users to reveal their real identity on most of the cryptocurrencies exchanges.
 This makes the anonymity of the user dependent on the security of the IT system.
-Moreover, some correlations can be infered merely by the analysis of transactions \cite{androulaki2013evaluating, ober2013structure}.
-
-The relations between these terms are ilustrated in the figure~\ref{fig:anonymity-diagram}.
+Moreover, some correlations can be inferred merely by the analysis of transactions \cite{androulaki2013evaluating, ober2013structure}.
+
+The relations between these terms are illustrated in the figure~\ref{fig:anonymity-diagram1}.
 
 \begin{figure}[h!]
+\includegraphics[width=9cm]{anonymity-diagram.png}
+\centering
 \caption{Let us assume the Alice to be the customer willing to keep her identity private (anonymous) and Bob be the public SP.
@@
 The second action is transparent, therefore the Alice's anonymity is maintained as long as the connection to the second pseudonym is concealed.}
-\centering
-\includegraphics[width=9cm]{anonymity-diagram.png}
-\label{fig:anonymity-diagram}
+
+\label{fig:anonymity-diagram1}
 \end{figure}
@@
 \subsection{Payment for services}\label{payment-for-services}
-Transactions between customers and SP have to be somehow pegged in order
-to prevent proving one payment for multiple transactions. In other
+Transactions between customers and SP have to be somehow pegged to prevent proving one payment for multiple transactions. In other
 words, we need some way to uniquely link particular payment with the
-transaction it pays for.
-
-Depending for the cryptocurrency the link can be created in different
+the transaction paid for.
+
+Depending on the cryptocurrency the link can be created in different
 ways:
@@
 \item
-  separate address — each transaction derives new address uniquely
+  separate address — each transaction derives a new address uniquely
   associating it with the transaction. Such addresses can be derived
@@
 \item
-  memo — the payments are send to one SP account, but contain extra
+  memo — the payments are sent to one SP account but contain an extra
   field named ``memo'' which contains a random value generated by SP and
-  included in $\mathrm{PoD}$. Each payment containing such value in memo is
+  included in $\mathrm{PoD}$. Each payment containing such value in the memo is
   considered to pay for the transaction in question. In case of a dispute,
-  the connection can be disclosed by revealing the value in $\mathrm{PoD}$ and payment's memo.
-\end{itemize}
-
-Both approaches have some advantages and disadvantages, but our protocol can abstract them away by treating them as some randomly genrated unique number, often called \textit{nonce} (number once).
+  the connection can be disclosed by revealing the value in $\mathrm{PoD}$ and the payment's memo.
+\end{itemize}
+
+Both approaches have some advantages and disadvantages, but our protocol can abstract them away by treating them as some randomly generated unique number, often called \textit{nonce} (number once).
 How it is implemented depends on a particular blockchain.
 
-In case of a dispute there must a way to prove to the justice that the customer has paid for the transaction.
+In case of a dispute, there must be a way to prove to the justice that the customer has paid for the transaction.
 As the proof of transaction is trivial in transparent and trackable blockchains, it gets more complicated when it comes to anonymous blockchains.
 Monero allows proving and checking payments via dedicated API \cite{Howtopro46}.
-ZCash provides mechanism called Payment Disclosure \cite{AnIntrod25}, which at the time of writing is still a experimental feature
+ZCash provides a mechanism called Payment Disclosure \cite{AnIntrod25}, which at the time of writing is still an experimental feature
 \cite{paymentd11}.
@@
 \subsection{Storage network}\label{storage-network}
-Once the SP finish its service, he has to provide the results to the customer.
-The most natural approach would to be send the results via email of decidated platform.
-However, since the customer wants to stay anonymous, he don't want to expose his email address nor IP address.
-Moreover, in case of dispute the SP should be able to prove that the results have been provided before the deadline.
+Once the SP finishes its service, he has to provide the results to the customer.
+The most natural approach would to be send the results via email of the dedicated platform.
+However, since the customer wants to stay anonymous, he doesn't want to expose his email address nor IP address.
+Moreover, in case of dispute, the SP should be able to prove that the results have been provided before the deadline.
 
@@
 Yet, storing data on a blockchain is very expensive.
-The most common workaround (\cite{shahid2020blockchain, wang2019auditable, chen2017improved, Usageide95}) is to publish the data to the IPFS \cite{benet2014ipfs}—a content adressable peer-to-peer storage network—and publish to a blockchain just a content identifier (cid) that uniquely points to the content stored on the IPFS.
-
-We take the same approach. Once the SP creates the results, he encrypts them using the previously provided encryption key; then publish them into a IPFS network.
-
-To increase anonimity, the customer should use a common techniques to hide its IP address; for example, use gateway, VPN, proxy, or onion routing.
+The most common workaround (\cite{shahid2020blockchain, wang2019auditable, chen2017improved, Usageide95}) is to publish the data to the IPFS \cite{benet2014ipfs}—a content addressable peer-to-peer storage network—and publish to a blockchain just a content identifier (cid) that uniquely points to the content stored on the IPFS.
+
+We take the same approach. Once the SP creates the results, he encrypts them using the previously provided encryption key; then publishes them into an IPFS network.
+
+To increase anonymity, the customer should use common techniques to hide its IP address; for example, use gateway, VPN, proxy, or onion routing.
 
@@
 
-As the message board could be achieved by most of the blockchanis, the anonymous payments isn't so prevalent, and provable storage network is a functionality of a few specialised blockchains.
-
-Instead of searching for one blockchain that solves all the functionallities, we allow the framework to use separate blockchains for each of the functionalities.
+As the message board could be achieved by most of the blockchains, anonymous payments aren't so prevalent, and a provable storage network is a functionality of a few specialized blockchains.
+
+Instead of searching for one blockchain that solves all the functionalities, we allow the protocol to use separate blockchains for each of the functionalities.
 In case a suitable blockchain arises, it can play more than one role.
 
-At the time of writing, we see following technologies that fulfill the requrements of each role:
+At the time of writing, we see the following technologies that fulfill the requirements of each role:
 
@@
 
+%%%%%%%%%%% dotad sprawdzone
 \section{The Protocol}\label{sec:protocol}
@@
 \subsection{Prerequisites}
-We do not design our framework with the particular technologies in mind, instead we state requirements that each party of the framework must satisfy to make the whole system to work together.
-The choice of the particular technology for each role is up to the implementer.
+We do not design our protocol with the assumption of usage particular technologies, instead, we define requirements that each party of the protocol must satisfy to make the whole system work together.
+The choice of the particular technology for each role is up to the developer.
 
@@
         \item Supports anonymous, i.e., untraceable and (ideally) unlinkable transactions as specified in section~\ref{sec:pseudo-anon}.
-        \item Supports uniquely identifying transaction either via separate address per transaction, memo field, or other similar mechanism as described in section ~\ref{payment-for-services}. 
+        \item Supports uniquely identifying transaction either via separate address, memo field, or other similar mechanism as described in section ~\ref{payment-for-services}. 
     \end{itemize}
@@
 \subsection{Messages}\label{messages}
-
-\paragraph{Package}\label{package}
+In this section we describe the messages exchanged between the parties of the protocol.
+
+\noindent \textbf
+{Package}\label{package} is a physical container prepared by the customer encompassing all $\mathrm{materials}$ required by the SP to provide the service, and an encryption $\mathrm{key}$ used to encrypt results published on the storage network.
 
@@
 
-\item $\mathrm{materials}$ - are the materials needed to provide the service on.
-For example, sample of urine, blood, stool, saliva; legal documents, CDs, mails, photos, bank statement, or any other kind of evidence depending on the service.
+\item $\mathrm{materials}$ - are the materials required to provide the service on.
+For example: sample of urine, blood, stool, saliva; legal documents, CDs, mails, photos, bank statement, or any other kind of evidence depending on the service.
 \item $\mathrm{key}$ - symmetric key used to encrypt and decrypt the results.
@@
 
-\paragraph{Proof-of-Delivery}\label{proof-of-delivery}
+\noindent \textbf
+{Proof of delivery ($\mathrm{PoD}$)}\label{proof-of-delivery} is  a  confirmation  issued  by the SP to the customer that proves that the customer has delivered to the SP a complete (according to the SP requirements) package, and the SP accepted it.
+
+It is also an agreement between the customer and the SP, as it includes agreed upfront deadlines of actions in the protocol.
+
+We assume the $\mathrm{PoD}$ to be an QR code printed on a paper receipt, but any other form that quarantee integrity, authenticity and non-repudiation can be used instead.
+
+The ($\mathrm{PoD}$ can be then used as a evidence in case of a dispute.
 
@@
 
-\paragraph{Proof-of-Provision}\label{proof-of-provision}
+\noindent \textbf
+{Proof of provision ($\mathrm{PoP}$)}\label{proof-of-provision} is proof that the SP published the results at a certain time.
+It defends the SP in case the customer unjustly starts a dispute after the results have been published.
+The connection between $\mathrm{PoP}$ and the results is made by the content identifier which uniquely points to the results such that the $\mathrm{PoP}$ can not forge results after the publication.
+
+The $\mathrm{PoP}$ is an digital construction published by the SP on a message board.
 
@@
 
-\paragraph{Payment attestation}\label{payment-attestation}
+\noindent \textbf
+{Payment attestation}\label{payment-attestation}
 
@@
 
-\paragraph{Results}\label{results}
+\noindent \textbf
+{Results}\label{results}
 
@@
 
-\paragraph{Content Identifier (cid)}\label{content-identifier-cid}
+\noindent \textbf
+{Content Identifier (cid)}\label{content-identifier-cid}
 
@@
 \centering
-\caption{Diagram}
+\caption{Messages exchanged in protocol.}
 \label{fig:protocol-diagram}
@@
 
-\paragraph{Step 0: Preparation}\label{step-0-preparation}
+\noindent \textbf
+{Step 0.  Preparation}\label{step-0-preparation}
 
@@
 
-\paragraph{Step 1: Package delivery}\label{step-1-package-delivery}
+\noindent \textbf
+{Step 1. Package delivery}\label{step-1-package-delivery}
 
@@
 
-\paragraph{Step 2: Payment}\label{step-2-payment}
+\noindent \textbf
+{Step 2. Payment}\label{step-2-payment}
 
@@
 
-\paragraph{Step 3: Provision of service}\label{step-3-provision-of-service} 
+\noindent \textbf
+{Step 3. Provision of service}\label{step-3-provision-of-service} 
 Once the transaction is paid the SP start the provision of service.
@@
 
-\paragraph{Step 4: Results upload}\label{step-4-results-upload}
+\noindent \textbf
+{Step 4. Results upload}\label{step-4-results-upload}
 
@@
 
-\paragraph{Step 5: Proof of provision publication}\label{step-5-proof-of-provision-publication}
+\noindent \textbf
+{Step 5. Proof of provision publication}\label{step-5-proof-of-provision-publication}
 
@@
 
-\paragraph{Step 6: Proof-of-provision notification}\label{step-6-proof-of-provision-notification}
+\noindent \textbf
+{Step 6. Proof-of-provision notification}\label{step-6-proof-of-provision-notification}
 
@@
 
-\paragraph{Step 7: Results download}\label{step-7-results-download} Having the $\mathrm{cid}$, the customer downloads and decrypts the $\mathrm{results}$.
+\noindent \textbf
+{Step 7. Results download}\label{step-7-results-download} Having the $\mathrm{cid}$, the customer downloads and decrypts the $\mathrm{results}$.
 
@@
 \item
-  Neutral (•) position: when a party hasn't spend nor gain anything of significant value (money, time, effort). For example, at the beginning of the protocol.
-\item
-  Disadvantage (-) position: when a party has put a significant value without receiving an equivalent. For example, paid for a service in
-  advance.
-\item
-  Advantage(+) position: when a party would benefit if the transaction would halt at that step. For example, the SP has received payment before service provision.
+  Neutral position (•): when a party hasn't spend nor gain anything of significant value (money, time, effort). For example, at the beginning of the protocol.
+\item
+  Disadvantaged position (-): when a party has put a significant value without receiving an equivalent. For example, paid for a service in advance.
+\item
+  Advantaged position (+): when a party would benefit if the transaction would halt at that step. For example, the SP has received payment before service provision.
 \end{itemize}
@@
 
-The protocol terminate after last step, after starting a dispute, or
-after a party hasn't completed it's designated action in time. Therefore,
-all positions except $\sigma_\mathrm{n}$ are termination positions.
+The protocol terminate after last step, after starting a dispute, or after a party hasn't completed it's designated action in time.
+Therefore, all positions except $\sigma_\mathrm{n}$ are termination positions.
 
@@
 
-Below is the description for each step and rationale of the outcome position.
-
-\paragraph{Step 1, customer turn: deliver package}\label{step-1-deliver-package}
+Below we give the description for each step and rationale of the outcome position.
+
+\noindent \textbf
+{Step 1. Customer turn: deliver package}\label{step-1-deliver-package}
 
@@
 
-\paragraph{Step 2, customer turn: pay for invoice}\label{step-2-pay-for-invoice}
+\noindent \textbf
+{Step 2. Customer turn: pay for invoice}\label{step-2-pay-for-invoice}
 
@@
 
-\paragraph{Step 3, SP turn: provision of service}\label{step-3-provision-of-service}
+\noindent \textbf
+{Step 3. SP turn: provision of service}\label{step-3-provision-of-service}
 
@@
 
-\paragraph{Step 4, SP turn: publication of results}\label{step-4-publication-of-results}
+\noindent \textbf
+{Step 4. SP turn: publication of results}\label{step-4-publication-of-results}
 
@@
 
-\paragraph{Step 5, SP turn: publication of proof-of-provision}\label{step-5-publication-of-proof-of-provision}
+\noindent \textbf
+{Step 5. SP turn: publication of proof-of-provision}\label{step-5-publication-of-proof-of-provision}
 
@@
 
-\paragraph{Step 6, customer turn: pull proof-of-provision}\label{step-6-pull-proof-of-provision}
+\noindent \textbf
+{Step 6. customer turn: pull proof-of-provision}\label{step-6-pull-proof-of-provision}
 
@@
 
-\paragraph{Step 7, customer turn: retrieval of results}\label{step-7-retrieval-of-results}
+\noindent \textbf
+{Step 7. Customer turn: retrieval of results}\label{step-7-retrieval-of-results}
 
@@
 \section{Conclusions}\label{sec:conclusion}
-In this paper, we have proposed a anonymity- preserving blockchain-based framework for local services provision.
-The framework can be employed by any local service provider to provide services without collecting any personal information.
+In this paper, we have proposed a anonymity- preserving blockchain-based protocol for local services provision.
+The protocol can be employed by any local service provider to provide services without collecting any personal information.
 The payment is handled by anonymous cryptocurrencies.

### 2022-03-04 access.tex
results to result

@@
 \markboth{S. Bara{\'n}ski, J. Szyma{\'n}ski : 
-Anonymous provision of local services via blockchain}
+Anonymous provision of services via blockchain}
 {S. Bara{\'n}ski, J. Szyma{\'n}ski : 
-Anonymous provision of local services via blockchain}
+Anonymous provision of services via blockchain}
 
@@
 
-A local service provider can employ our protocol to provide
+A service provider can employ our protocol to provide
 services without collecting any personal information. Possible
 applications for this protocol include anonymous clinical drug testing,
-steroid testing, parenting testing, anonymous legal advice, or
+steroid, parenting testing, anonymous legal advice, or
 anonymous financial trustworthiness evaluation.
@@
 In case of dispute, either due to exceeding deadlines or providing
-incorrect results, the customer can disclose the whole interaction and
+incorrect result, the customer can disclose the whole interaction and
 prove to justice (police or court) the misbehavior of the service
@@
 \begin{keywords}
-Blockchain, anonymity, fair-exchange, physical delivery
+fair-exchange, blockchain, anonymity,  physical delivery, services
 \end{keywords}
@@
 have a strong incentive to keep the whole procedure private.
-Merely the fact that they took the test — without exposing the results — is suggestive enough to act as a premise in case of a conflict.
+Merely the fact that they took the test without exposing the result is suggestive enough to act as a premise in case of a conflict.
 
@@
 In case of dispute, either due to exceeding deadlines or providing
-incorrect results, the customer can disclose the whole interaction and
+incorrect result, the customer can disclose the whole interaction and
 prove to justice (police or court) the misbehavior of the service 
@@
     \item Message board blockchain, to achieve fairness, i.e., as a means for proving that certain actions took place at a certain moment without the trusted third party.
-    \item Content-addressable peer-to-peer storage network, to provide results to the customer. 
+    \item Content-addressable peer-to-peer storage network, to provide results to customers. 
     \item Cryptography
@@
 
-In our case, the customer is exchanging with the SP cryptocurrency and materials for the results.
+In our case, the customer is exchanging with the SP cryptocurrency and materials for the result of a service.
 
@@
 our protocol does not rely on a trusted-third party to conduct transactions in fairly manner.
-Only in case of dispute   the centralized justice is involved (the justice decentralization is discussed in section ~\ref{sec:future-work}.
+Only in case of dispute   the centralized justice is involved (the justice decentralization is discussed in Section ~\ref{sec:future-work}.
 \item Physical materials: our protocol allows providing not only digital but also physical materials to the service provider.
@@
 The remainder of this paper is organized as follows.
-In section~\ref{sec:related-works} we briefly review related works. 
+In Section~\ref{sec:related-works} we briefly review related works. 
 Section~\ref{sec:building-blocks} explains the background related to fair-exchanges, blockchain, anonymity and confidentiality, and storage network. 
@@
 Section~\ref{sec:future-work} discuss possible improvements. 
-Finally, section~\ref{sec:conclusion} concludes the paper.
+Finally, Section~\ref{sec:conclusion} concludes the paper.
 
@@
 
-The idea behind certified e-mails—and any other fair-exchange protocol—is following:
+The idea behind certified e-mails and any other fair-exchange protocol is following:
 \begin{enumerate}
@@
 
-In this case, the role of Blockchain is to attest the public existence of decryption key at a particular point of time.
+In this case, the role of blockchain is to attest the public existence of decryption key at a particular point of time.
 
@@
 
-However, since the system uses Ethereum— fully traceable blockchain—its anonymity is achieved as long as the addresses are not identified with the real identities, which we call pseudonymity rather than anonymity (see section~\ref{sec:pseudo-anon}).
+However, since the system uses Ethereum— fully traceable blockchain—its anonymity is achieved as long as the addresses are not identified with the real identities, which we call pseudonymity rather than anonymity (see Section~\ref{sec:pseudo-anon}).
 Also, the protocol does not cover the case of dispute between the parties.
@@
 Possible directions toward semi-autonomous decentralised resolution
-system are discussed in section ~\ref{sec:future-work}.
+system are discussed in Section ~\ref{sec:future-work}.
 
@@
     \item Proof-of-delivery ($\mathrm{PoD}$) is a confirmation issued by the SP to the customer that proves that the customer has delivered to the SP a complete (according to the SP requirements) package, and the SP accepted it.
-It consists of the current time; deadline to pay for the transaction, and the deadline to provide the service; deadline to provide the service results; randomly generated number uniquely identifying the transaction, and the SP's signature guaranteeing non-repudiation.
-The formal definition of the $\mathrm{PoD}$ is presented in section ~\ref{proof-of-delivery}.
+It consists of the current time; deadline to pay for the transaction; deadline to provide a result of the service; randomly generated number uniquely identifying the transaction, and the SP's signature guaranteeing non-repudiation.
+The formal definition of the $\mathrm{PoD}$ is presented in Section ~\ref{proof-of-delivery}.
 
     \item Payment $\mathrm{attestation}$ is confirmation that the customer has paid for the transaction, at a certain time.
-The actual implementation depends on the particular cryptocurrency and is discussed further section~\ref{payment-for-services}.
-
-    \item Proof-of-provision ($\mathrm{PoP}$) is proof that the SP published the results at a certain time.
-It defends the SP in case the customer unjustly starts a dispute after the results have been published.
-It consists of a content identifier as specified in section ~\ref{storage-network}; the value uniquely identifying the transaction previously generated in $\mathrm{PoD}$; the SP's signature guaranteeing authentication.
-The connection between $\mathrm{PoP}$ and the results is made by the content identifier which uniquely points to the results such that the $\mathrm{PoP}$ can not forge results after the publication.
+The actual implementation depends on the particular cryptocurrency and is discussed further Section~\ref{payment-for-services}.
+
+    \item Proof of provision ($\mathrm{PoP}$) is proof that the SP published the result at a certain time.
+It defends the SP in case the customer unjustly starts a dispute after the result have been published.
+It consists of a content identifier as specified in Section ~\ref{storage-network}; the value uniquely identifying the transaction previously generated in $\mathrm{PoD}$; the SP's signature guaranteeing authentication.
+The connection between $\mathrm{PoP}$ and the result is made by the content identifier (cid) that uniquely identify the result (it is some kind of a hash of the result) such that the result can not be forged after the $\mathrm{PoP}$ has been published.
 \end{enumerate}
@@
 We need this functionality for two reasons: (1) Communicate the existence
-of the results to the customer to whom the SP have no other
-communication medium as the customer stays anonymous; (2) let the SP to proof the publication of results within the agreed with customer deadline.
+of the result to the customer to whom the SP have no other
+communication medium as the customer stays anonymous; (2) let the SP to proof the publication of the result within the agreed with customer deadline.
 
 By publishing the $\mathrm{PoP}$ on the blockchain, the SP can not falsify the time
-at which the results has been provided, because the block creation time
+at which the result has been provided, because the block creation time
 proves that. Blockchain acts as a global clock that securely timestamps
@@
 block will be associated with the time when the block has been created.
-Moreover, since the blockchain is public, everyone (including justice) can be convinced that the SP indeed published the results at that time.
-
-Without such a proof there would be no other means to settle the conflict between the customer claiming the results have not been published and the SP claiming the results have been published within the deadline.
+Moreover, since the blockchain is public, everyone (including justice) can be convinced that the SP indeed published the result at that time.
+
+Without such a proof there would be no other means to settle the conflict between the customer claiming the result has not been published and the SP claiming the result has been published within the deadline.
 
@@
 
-The relations between these terms are illustrated in the figure~\ref{fig:anonymity-diagram1}.
+The relations between these terms are illustrated in the Figure~\ref{fig:anonymity-diagram1}.
 
@@
 \subsection{Storage network}\label{storage-network}
-Once the SP finishes its service, he has to provide the results to the customer.
-The most natural approach would to be send the results via email of the dedicated platform.
+Once the SP finishes its service, he has to provide the result to the customer.
+The most natural approach would to be send the result via email of the dedicated platform.
 However, since the customer wants to stay anonymous, he doesn't want to expose his email address nor IP address.
-Moreover, in case of dispute, the SP should be able to prove that the results have been provided before the deadline.
-
-One approach would be to post the results into a blockchain.
+Moreover, in case of dispute, the SP should be able to prove that the result has been provided before the deadline.
+
+One approach would be to post the result into a blockchain.
 Yet, storing data on a blockchain is very expensive.
@@
 
-We take the same approach. Once the SP creates the results, he encrypts them using the previously provided encryption key; then publishes them into an IPFS network.
+We take the same approach. Once the SP creates the result, he encrypts it using the previously provided encryption key and uploads it to IPFS network.
 
@@
 
-%%%%%%%%%%% dotad sprawdzone
 \section{The Protocol}\label{sec:protocol}
@@
         \item Accepts packages from unknown customers and give $\mathrm{PoD}$ in return.
-        \item Accepts payments with anonymous cryptocurrencies as described in section~\ref{payment-for-services}.
+        \item Accepts payments with anonymous cryptocurrencies as described in Section~\ref{payment-for-services}.
     \end{itemize}
@@
     \begin{itemize}
-        \item Accepts as a evidence in dispute a $\mathrm{PoD}$, $\mathrm{PoP}$, and payment $\mathrm{attestation}$ as described in section~\ref{proof-of-justice}.
+        \item Accepts as a evidence in dispute a $\mathrm{PoD}$, $\mathrm{PoP}$, and payment $\mathrm{attestation}$ as described in Section~\ref{proof-of-justice}.
     \end{itemize}
@@
     \begin{itemize}
-        \item Supports anonymous, i.e., untraceable and (ideally) unlinkable transactions as specified in section~\ref{sec:pseudo-anon}.
-        \item Supports uniquely identifying transaction either via separate address, memo field, or other similar mechanism as described in section ~\ref{payment-for-services}. 
+        \item Supports anonymous, i.e., untraceable and (ideally) unlinkable transactions as specified in Section~\ref{sec:pseudo-anon}.
+        \item Supports uniquely identifying transaction either via separate address, memo field, or other similar mechanisms as described in Section ~\ref{payment-for-services}. 
     \end{itemize}
@@
 \subsection{Messages}\label{messages}
-In this section we describe the messages exchanged between the parties of the protocol.
-
-\noindent \textbf
-{Package}\label{package} is a physical container prepared by the customer encompassing all $\mathrm{materials}$ required by the SP to provide the service, and an encryption $\mathrm{key}$ used to encrypt results published on the storage network.
+In this section, we describe the messages exchanged between the parties of the protocol.
+
+\noindent \textbf
+{Package}\label{package} is a physical container prepared by the customer encompassing all $\mathrm{materials}$ required by the SP to provide the service, and an encryption $\mathrm{key}$ used to encrypt the result published on the storage network.
 
@@
 
-\item $\mathrm{materials}$ - are the materials required to provide the service on.
-For example: sample of urine, blood, stool, saliva; legal documents, CDs, mails, photos, bank statement, or any other kind of evidence depending on the service.
-\item $\mathrm{key}$ - symmetric key used to encrypt and decrypt the results.
+\item $\mathrm{materials}$ - are the materials required to provide the service.
+For example samples of urine, blood, stool, saliva; legal documents, CDs, emails, photos, bank statements, or any other kind of evidence depending on the service.
+\item $\mathrm{key}$ - symmetric key used to encrypt and decrypt the result.
 \end{itemize}
@@
 
-We assume the $\mathrm{PoD}$ to be an QR code printed on a paper receipt, but any other form that quarantee integrity, authenticity and non-repudiation can be used instead.
-
-The ($\mathrm{PoD}$ can be then used as a evidence in case of a dispute.
+We assume the $\mathrm{PoD}$ to be a QR code printed on a paper receipt, but any other form that guarantees integrity, authenticity, and non-repudiation can be used instead.
+
+The ($\mathrm{PoD}$ can be then used as evidence in case of a dispute.
 
@@
 \item
-  $\mathrm{T}_\mathrm{provide}$ - deadline to provide the service results.
+  $\mathrm{T}_\mathrm{provide}$ - deadline to provide a result of the service.
 \item $\mathrm{nonce}$ - randomly generated number uniquely identifying the transaction.
@@
 also:
-
 \(\mathrm{T}_\mathrm{issue} < \mathrm{T}_\mathrm{pay} < \mathrm{T}_\mathrm{provide}\)
@@
 \noindent \textbf
-{Proof of provision ($\mathrm{PoP}$)}\label{proof-of-provision} is proof that the SP published the results at a certain time.
-It defends the SP in case the customer unjustly starts a dispute after the results have been published.
-The connection between $\mathrm{PoP}$ and the results is made by the content identifier which uniquely points to the results such that the $\mathrm{PoP}$ can not forge results after the publication.
-
-The $\mathrm{PoP}$ is an digital construction published by the SP on a message board.
+{Proof of provision ($\mathrm{PoP}$)}\label{proof-of-provision} is proof that the SP published the result at a certain time.
+It defends the SP in case the customer unjustly starts a dispute after the result has been published.
+The connection between $\mathrm{PoP}$ and the result is made by the content identifier ($(\mathrm{cid}$) that uniquely identify the result (it is some kind of a hash of the result) such that the result can not be forged after the $\mathrm{PoP}$ has been published.
+
+The $\mathrm{PoP}$ is a digital construction published by the SP on the message board.
 
@@
 {Payment attestation}\label{payment-attestation}
-
-Payment attestation proves that the customer did the payment. Since the
-evidences depends on the particular blockchain (see section ~\ref{payment-for-services}). We refer to them symbollicaly as
+proves that the customer did the payment. Since the
+evidence depends on the particular blockchain (see Section ~\ref{payment-for-services}). We refer to them symbolically as
 \(attestation\).
@@
 \noindent \textbf
-{Results}\label{results}
-
-We assume results to be documents in PDF format, but they can be
-anything as long as they can be binary encoded and uploaded to IPFS. We
-refer to them symbollicaly as \(results\).
-
-\noindent \textbf
-{Content Identifier (cid)}\label{content-identifier-cid}
-
-Although content identifier (cid) is a term coined by IPFS
-\cite{Contenta59}. However, since we our protocol does not depend on
-this particular implementation of storage network, we let the cid be any
+{Result}\label{results} is assumed to be document in PDF format, but any other format is allowed as long as it can be binary encoded and uploaded to IPFS. We refer to it symbolically as $result$.
+
+\noindent \textbf
+{Content Identifier (cid)}\label{content-identifier-cid}  is a term coined by IPFS
+\cite{Contenta59}  
+. However, since our protocol does not depend on
+this particular implementation of the storage network, we let the cid be any
 other identifier that securely and uniquely points to the content.
@@
 
-In this section we describe each step of the protocol. The steps are
-shown in the figure ~\ref{fig:protocol-diagram}.
+In this section, we describe each step of the protocol. The steps are
+shown in the Figure ~\ref{fig:protocol-diagram}.
 
@@
 
-The customer collects all the $\mathrm{materials}$ required by the SP, generate an encryption $\mathrm{key}$ print it on a paper as a QR code, and pack them together into a package $\mathrm{pkg}$.
-
-Symbolically: \[
+The customer collects all the $\mathrm{materials}$ required by the SP, generates an encryption $\mathrm{key}$ prints it on a paper as a QR code, and packs them together into a package $\mathrm{pkg}$.
+
+Symbolically: 
+$
 \mathrm{pkg} \gets (\mathrm{materials}, \mathrm{key})
-\]
+$
 
@@
 
-We assume this step to be fully physical, that is, $\mathrm{pkg}$ consist of physical materials, $\mathrm{PoD}$ is in a form of e.g., QR code printed on paper receipt.
-
-$\mathrm{PoD}$ could be published on a message board (similarly to $\mathrm{PoP}$); however, since the $\mathrm{pkg}$ is delivered personally or via trusted person, the confirmation can be issued in person as well.
-If we would like to hire a courier to deliver our $\mathrm{pkg}$, then the $\mathrm{PoD}$ would have to be published on message board (further extension to anonymous delivery system is discussed in section \ref{sec:future-work}).
+We assume this step to be fully physical, that is, $\mathrm{pkg}$ consists of physical materials, $\mathrm{PoD}$ is in a form of e.g., QR code printed on a paper receipt.
+
+$\mathrm{PoD}$ could be published on a message board (similarly to $\mathrm{PoP}$); however, since the $\mathrm{pkg}$ is delivered personally or via a trusted person, the confirmation can be issued in person as well.
+If we would like to hire a courier to deliver our $\mathrm{pkg}$, then the $\mathrm{PoD}$ would have to be published on the message board (further extension to the anonymous delivery system is discussed in Section \ref{sec:future-work}).
 
 Symbolically: 
-\[
+$
 \mathrm{PoD} \gets \mathrm{delivery}(\mathrm{pkg})
-\]
-\[
+$
+
+$
 (\mathrm{T}_\mathrm{issue}, \mathrm{T}_\mathrm{pay}, \mathrm{T}_\mathrm{provide}, \mathrm{nonce}, \mathrm{sig}_{\mathrm{sk}(\mathrm{SP})}) \equiv \mathrm{PoD}
-\]
+$
 
@@
 Having the PoD issued, the SP can not reject receiving the package. At this point the
-customer should pay for the transaction with agreed upfront cryptocurrency system (see section~\ref{payment-for-services}).
+customer should pay for the transaction with an agreed upfront cryptocurrency system (see Section~\ref{payment-for-services}).
 
@@
 
-Symbolically: \[
+Symbolically: 
+$
 \mathrm{attestation} \gets \mathrm{payment}(\mathrm{nonce}, \mathrm{sig}_{\mathrm{sk}(\mathrm{C})})
-\]
+$
 
@@
 {Step 3. Provision of service}\label{step-3-provision-of-service} 
-Once the transaction is paid the SP start the provision of service.
-
-Symbolically: \[
-\mathrm{results} \gets \mathrm{provision}(\mathrm{materials})
-\]
-
-\noindent \textbf
-{Step 4. Results upload}\label{step-4-results-upload}
-
-After the service is finished, some kind of output should be created. Next, the output is encrypted using encryption symmetric key $\mathrm{key}$ provided in the first step.
-
-The encrypted results are then uploaded on content addressable network such as IPFS. As a result, the content identifier (cid) is returned.
+Once the transaction is paid the SP starts the provision of service.
 
 Symbolically: 
-\[
-\mathrm{cid} \gets \mathrm{upload}(E_{\mathrm{key}}(\mathrm{results}))
-\]
+$
+\mathrm{result} \gets \mathrm{provision}(\mathrm{materials})
+$
+
+\noindent \textbf
+{Step 4. Upload result }\label{step-4-results-upload}
+
+After the service is finished, some result should be created. Next, the result is encrypted using encryption symmetric $\mathrm{key}$ provided in the first step.
+
+The encrypted result is then uploaded on the content addressable network such as IPFS. In return the content identifier (cid) is created.
+
+Symbolically: 
+$
+\mathrm{cid} \gets \mathrm{upload}(E_{\mathrm{key}}(\mathrm{result}))
+$
 
@@
 
-When the results are published, the SP perform proof of provision by publishing $\mathrm{cid}$ along with $\mathrm{nonce}$ and signature $\mathrm{sig}_\mathrm{SP}$.
+When the result is published, the SP performs proof of provision by publishing $\mathrm{cid}$ along with $\mathrm{nonce}$ and signature $\mathrm{sig}_\mathrm{SP}$.
 
 Symbolically: 
-\[\mathrm{PoP} \equiv (\mathrm{cid}, \mathrm{nonce}, \mathrm{sig}_{\mathrm{sk}(\mathrm{SP})})\]
-\[\mathrm{publish}(\mathrm{PoP})\]
+$
+\mathrm{PoP} \equiv (\mathrm{cid}, \mathrm{nonce}, \mathrm{sig}_{\mathrm{sk}(\mathrm{SP})})
+$
+
+$
+\mathrm{publish}(\mathrm{PoP})
+$
 
@@
 
-After delivering the package and paying for the transaction the customer subscribe to the message board and waits until the SP publish the proof of provision.
+After delivering the package and paying for the transaction the customer subscribes to the message board and waits until the SP publishes the proof of provision.
 The subscription is for the SP public key $\mathrm{pk}(\mathrm{SP}$ and transaction's $\mathrm{nonce}$.
 
-Symbolically: \[
+Symbolically: 
+$
 \mathrm{cid} \gets \mathrm{subscribe}(\mathrm{pk}(\mathrm{SP}), \mathrm{nonce})
-\]
-
-\noindent \textbf
-{Step 7. Results download}\label{step-7-results-download} Having the $\mathrm{cid}$, the customer downloads and decrypts the $\mathrm{results}$.
-
-Symbolically: \[
-\mathrm{results} \gets \mathrm{D}_{\mathrm{key}}(\mathrm{download}(\mathrm{cid}))
-\]
+$
+
+\noindent \textbf
+{Step 7. Result download}\label{step-7-results-download} 
+Having the $\mathrm{cid}$, the customer downloads and decrypts the $\mathrm{result}$.
+
+Symbolically: 
+$
+\mathrm{result} \gets \mathrm{D}_{\mathrm{key}}(\mathrm{download}(\mathrm{cid}))
+$
 
@@
 
-We analyse the fairness of the protocol by representing it as a interactive non-cooperative game.
+We analyze the fairness of the protocol by representing it as an interactive non-cooperative game.
 
@@
 \item
-  Neutral position (•): when a party hasn't spend nor gain anything of significant value (money, time, effort). For example, at the beginning of the protocol.
+  Neutral position (•): when a party hasn't spent nor gained anything of significant value (money, time, effort). For example, at the beginning of the protocol.
 \item
@@
 
-There are many actions that each party can take, but we group them together into two categories:
+There are many actions that each party can take, but we group them into two categories:
 
@@
 \item
-  Abnormal: everything that deviates from designed steps of the protocol. For example, sending arbitrary message, skipping some step, repeating step, timing out.
+  Abnormal: everything that deviates from the designed steps of the protocol. For example, sending an arbitrary message, skipping some step, repeating step, timing out.
 \end{enumerate}
 
-Moreover, at any step of the protocol the customer can start a dispute; therefore, another dimension with two positions has to be considered:
+Moreover, at any step of the protocol, the customer can start a dispute; therefore, another dimension with two positions has to be considered:
 
@@
 \item
-  Agree: the customer agree with the action, and therefore does not start a dispute.
-\item
-  Start a dispute: the customer does not agree with the action and therefore start a dispute.
+  Agree: the customer agrees with the action and therefore does not start a dispute.
+\item
+  Start a dispute: the customer does not agree with the action and therefore starts a dispute.
 \end{enumerate}
@@
 
-The protocol terminate after last step, after starting a dispute, or after a party hasn't completed it's designated action in time.
+The protocol terminates after the last step, after starting a dispute, or after a party hasn't completed its designated action in time.
 Therefore, all positions except $\sigma_\mathrm{n}$ are termination positions.
 
-Because the customer is anonymous the SP can not start a dispute---there is no mean to identify the customer.
-To mitigate the issue, we designed the protocol so that the SP who follows the protocol is always in advantage position, therefore he has no reason to start a dispute.
-The customer on the other hand can start a dispute at any time of the protocol, but only the actual misbehaviour of the SP makes him win the case.
+Because the customer is anonymous the SP can not start a dispute---there is no means to identify the customer.
+To mitigate the issue, we designed the protocol so that the SP who follows the protocol is always in an advantageous position, therefore he has no reason to start a dispute.
+The customer on the other hand can start a dispute at any time of the protocol, but only the actual misbehavior of the SP makes him win the case.
 
@@
 
-For the analysis purpose we state plausable assumptions listed below.
-
-Assumptions:
-
-\begin{itemize}
-
-\item
-  Both parties start from neutral position (•).
-\item
-  Both parties, by completing a transaction, end up in advantaged positions (+). In other words, they have intrinsic motivation to initialise and complete the transaction.
+Below  we listed
+assumptions we took
+for the analysis purpose.
+
+\begin{itemize}
+
+\item
+  Both parties start from a neutral position (•).
+\item
+  Both parties, by completing a transaction, end up in advantaged positions (+). In other words, they have intrinsic motivation to initialize and complete the transaction.
 \item
@@
 \item
-  Repeating the first step starts new transaction.
+  Repeating the first step starts a new transaction.
 Repeating any other step is considered abnormal and gets ignored.
-For example paying for the invoice twice does not cause any effect on the curse of protocol.
-\item
-  Once published, the results are available to the customer in the content storage. The idea of guaranteeing it cryptographically is discussed in section ~\ref{future-work}.
-\item
-  The protocol can go only forward, there is no way of revert any action.
-\item
-  Losing the dispute leads to punishment that is greater than any reward, which leads to disadvantaged position (-). Hence, the rational customer won't start a dispute that he is not sure to win.
-\item
-  Winning the dispute leads to neutral position (•).
+For example, paying for the invoice twice does not cause any effect on the curse of the protocol.
+\item
+  Once published, the result is available to the customer in the content storage. The idea of guaranteeing it cryptographically is discussed in Section~\ref{sec:future-work}.
+
+\item
+  The protocol can go only forward, there is no way of reverting any action.
+\item
+  Losing the dispute leads to a punishment that is greater than any reward, which leads to a disadvantaged position (-). Hence, the rational customer won't start a dispute that he is not sure to win.
+\item
+  Winning the dispute leads to a neutral position (•).
 \item
   Both the customer and the SP are rational (selfish).
-They always prefer go from worst position to better position, but also risk temporary worst position in favour for later better position iff it's assured that they won't stuck in worst position.
+They always prefer to go from worst position to better position, but also risk temporary worst position in favor of a later better position iff it's assured that they won't be stuck in the worst position.
 \end{itemize}
@@
 
-The table in figure~\ref{fig:positions} shows the positions of each party after each possible action taken.
+Figure~\ref{fig:positions} 
+shows the positions of each party after each possible action taken.
 
@@
 \centering
-\caption{Table of positions after each step of protocol}
+\caption{Positions after each step of protocol}
 \label{fig:positions}
@@
 
-Below we give the description for each step and rationale of the outcome position.
+Below we describe each step and rationale of the outcome position.
 
@@
   \item
-    \(\sigma_{1, s, \mathrm{n}} = \sbullet\), the SP is in neutral position as he didn't put any effort to hence the package, also the package hasn't any value to the SP.
+    \(\sigma_{1, s, \mathrm{n}} = \sbullet\), the SP is in the neutral position as he didn't put any effort to hence the package, also the package hasn't any value to the SP.
   \end{itemize}
@@
   \item
-    \(\sigma_{1, c, \mathrm{d}} = -\), the customer lose the case as the SP has still opportunity to publish proof-of-provision within timeframe.
+    \(\sigma_{1, c, \mathrm{d}} = -\), the customer loses the case as the SP has still an opportunity to publish proof-of-provision within the timeframe.
   \item
@@
 \item
-  The customer can follow the protocol and move to the non-disadvantaged
+  The customer can follow the protocol and move to a non-disadvantaged
   position \(\sigma_{1, c, \mathrm{n}} = \sbullet\).
 \item
-  The SP can do nothing and end up in non-disadvantaged position
+  The SP can do nothing and end up in a non-disadvantaged position
   \(\sigma_{1, s, \mathrm{n}} = \sbullet \) or
@@
   \item
-    \(\sigma_{2, c, \mathrm{n}} = -\), the customer has spend his funds but hasn't received the results.
-  \item
-    \(\sigma_{2, s, \mathrm{n}} = +\), the SP has received the payment but hasn't spend his resources yet.
+    \(\sigma_{2, c, \mathrm{n}} = -\), the customer has spent his funds but hasn't received the result.
+  \item
+    \(\sigma_{2, s, \mathrm{n}} = +\), the SP has received the payment but hasn't spent his resources yet.
   \end{itemize}
@@
   \item
-    \(\sigma_{2, c, \mathrm{d}} = -\), the customer lose the case as the SP has still opportunity to publish proof-of-provision before the deadline.
+    \(\sigma_{2, c, \mathrm{d}} = -\), the customer loses the case as the SP has still an opportunity to publish proof-of-provision before the deadline.
   \item
@@
 
-Customer has time outed, then:
+Customer has timeouted, then:
 
@@
   \item
-    \(\sigma_{2, c, \overline{\mathrm{n}}} = \sbullet\), the customer ends up in neutral position, since he didn't spend his funds.
-  \item
-    \(\sigma_{2, s, \overline{\mathrm{n}}} = \sbullet\), the SP ends up in neutral position as he didn't receive the payment, nor spent his resources.
+    \(\sigma_{2, c, \overline{\mathrm{n}}} = \sbullet\), the customer ends up in a neutral position, since he didn't spend his funds.
+  \item
+    \(\sigma_{2, s, \overline{\mathrm{n}}} = \sbullet\), the SP ends up in a neutral position as he didn't receive the payment, nor spent his resources.
   \end{itemize}
@@
   \item
-    \(\sigma_{2, s, \overline{\mathrm{d}}} = \sbullet\), the SP is not charged to the justice due to lack of proofs.
+    \(\sigma_{2, s, \overline{\mathrm{d}}} = \sbullet\), the SP is not charged to justice due to a lack of proof.
   \end{itemize}
@@
 \item
-  The customer can move the protocol forward to the step 3, where if the
-  SP follow the protocol then the customer can push the protocol forward
+  The customer can move the protocol forward to step 3, where if the
+  SP follows the protocol then the customer can push the protocol forward
   up to the last termination step \(\sigma_{7, c, \mathrm{n}} = +\),
@@
     \(\sigma_{3, c, \mathrm{n}} = -\), the customer hasn't received the
-    results so he remains in disadvantaged position.
+    result so he remains in a disadvantaged position.
   \item
@@
     \(\sigma_{3, c, \mathrm{d}} = -\), the customer lose the case as the
-    SP has still opportunity to publish proof-of-provision within
+    SP has still the opportunity to publish proof-of-provision within
     timeframe.
@@
   \item
-    \(\sigma_{3, c, \overline{\mathrm{n}}} = -\), the customer ends up in disadvantaged position.
-  \item
-    \(\sigma_{3, s, \overline{\mathrm{n}}} = +\), the SP ends up in
+    \(\sigma_{3, c, \overline{\mathrm{n}}} = -\), the customer ends up in a disadvantaged position.
+  \item
+    \(\sigma_{3, s, \overline{\mathrm{n}}} = +\), the SP ends up in a
     advantaged position as he received the payment.
@@
   \item
-    \(\sigma_{3, c, \overline{\mathrm{d}}} = •\), the customer wins the case and end up in neutral position.
+    \(\sigma_{3, c, \overline{\mathrm{d}}} = •\), the customer wins the case and ends up in a neutral position.
   \item
     \(\sigma_{3, s, \overline{\mathrm{d}}} = -\), the SP loses the case
-    and end up in disadvantaged position.
+    and end up in a disadvantaged position.
   \end{itemize}
@@
   The customer can do nothing if the SP follows the protocol, which will
-  ultimately put him in advantaged position
+  ultimately put him in an advantaged position
   \(\sigma_{7, c, \mathrm{n}} = +\), or in case of the SP not following
-  the protocol, the customer can start a dispute and terminate in
+  the protocol, the customer can start a dispute and terminate in a
   non-disadvantaged position
@@
 \item
-  The SP can follow the protocol and move to the non-disadvantaged
+  The SP can follow the protocol and move to a non-disadvantaged
   position \(\sigma_{3, s, \mathrm{n}} = +\), or not follow the protocol
-  and also end up at non-disadvantaged position
+  and also end up at a non-disadvantaged position
   \(\sigma_{3, s, \overline{\mathrm{n}}} = +\), but the second option
@@
 \noindent \textbf
-{Step 4. SP turn: publication of results}\label{step-4-publication-of-results}
-
-SP has published results on time:
+{Step 4. SP turn: upload result}\label{step-4-publication-of-results}
+
+SP has uploaded the result on time:
 
@@
   \item
-    \(\sigma_{4, c, \mathrm{n}} = -\), the customer hasn't received the results so he remains in disadvantaged position.
+    \(\sigma_{4, c, \mathrm{n}} = -\), the customer hasn't received the result so he remains in disadvantaged position.
   \item
@@
     \(\sigma_{4, s, \overline{\mathrm{d}}} = -\), the SP loses the case
-    and end up in disadvantaged position.
+    and end up in a disadvantaged position.
   \end{itemize}
@@
   The customer can do nothing if the SP follows the protocol, which will
-  ultimately put him in advantaged position
+  ultimately put him in an advantaged position
   \(\sigma_{7, c, \mathrm{n}} = +\), or in case of the SP not following
@@
     \(\sigma_{5, c, \mathrm{n}} = -\) the customer hasn't received the
-    results. Therefore, he remains in disadvantaged position.
+    result. Therefore, he remains in a disadvantaged position.
   \item
@@
   \item
-    \(\sigma_{5, c, \overline{\mathrm{n}}} = -\) the customer ends up in disadvantaged position.
+    \(\sigma_{5, c, \overline{\mathrm{n}}} = -\) the customer ends up in a disadvantaged position.
   \item
     \(\sigma_{5, s, \overline{\mathrm{n}}} = +\) the SP ends up in
-    advantaged position as he received the payment.
+    an advantaged position as he received the payment.
   \end{itemize}
@@
     \(\sigma_{5, c, \overline{\mathrm{d}}} = •\) the customer wins the
-    case and end up in neutral position.
+    case and end up in a neutral position.
   \item
     \(\sigma_{5, s, \overline{\mathrm{d}}} = -\) the SP loses the case
-    and end up in disadvantaged position.
+    and end up in a disadvantaged position.
   \end{itemize}
@@
 \item
-  The customer can do nothing if the SP follows the protocol, because it
-  will ultimately put him in advantaged position
+  The customer can do nothing if the SP follows the protocol because it
+  will ultimately put him in an advantaged position
   \(\sigma_{7, c, \mathrm{n}} = +\), otherwise, in case of the SP not
@@
 \noindent \textbf
-{Step 6. customer turn: pull proof-of-provision}\label{step-6-pull-proof-of-provision}
-
-SP has published results on time, then:
+{Step 6. customer turn: pull proof of provision}\label{step-6-pull-proof-of-provision}
+
+SP has uploaded the result on time, then:
 
@@
     \(\sigma_{6, c, \mathrm{n}} = -\) the customer gets hash of the
-    results but not the results yet.
+    result but not the result yet.
   \item
@@
     \(\sigma_{6, c, \overline{\mathrm{d}}} = •\) the customer wins the
-    case and end up in neutral position.
+    case and end up in a neutral position.
   \item
     \(\sigma_{6, s, \overline{\mathrm{d}}} = -\) the SP loses the case
-    and end up in disadvantaged position.
+    and end up in a disadvantaged position.
   \end{itemize}
@@
   \(\sigma_{6, c, \mathrm{n}} = -\), which let's him move the protocol
-  to non-disadvantaged termination position
+  to a non-disadvantaged termination position
   \(\sigma_{7, c, \mathrm{n}} = +\), or in case the SP haven't followed
@@
 \item
-  The SP can do nothing and end up in non-disadvantaged position
+  The SP can do nothing and end up in a non-disadvantaged position
   \(\sigma_{6, s, \mathrm{n}} = +\), or
@@
 \noindent \textbf
-{Step 7. Customer turn: retrieval of results}\label{step-7-retrieval-of-results}
-
-SP has published \textbf{correct} results on time:
+{Step 7. Customer turn: result download}\label{step-7-retrieval-of-results}
+
+SP has published the \textbf{correct} result on time:
 
@@
     \(\sigma_{7, c, \mathrm{n}} = +\) the customer gets the correct
-    results. Therefore, he moves to advantaged position.
+    result. Therefore, he moves to an advantaged position.
   \item
@@
 
-SP has published \textbf{incorrect} results on time:
+SP has published the \textbf{incorrect} result on time:
 
@@
   \item
-    \(\sigma_{7, c, \overline{\mathrm{n}}} = -\) customer end up in disadvantaged position, as he ends up with incorrect results.
+    \(\sigma_{7, c, \overline{\mathrm{n}}} = -\) the customer ends up in a disadvantaged position, as he ends up with incorrect result.
   \item
@@
   \item
-    \(\sigma_{7, c, \overline{\mathrm{d}}} = •\) customer wins the case and ends up in neutral position.
-  \item
-    \(\sigma_{7, c, \overline{\mathrm{d}}} = -\) SP lose the case and end up in disadvantaged position.
+    \(\sigma_{7, c, \overline{\mathrm{d}}} = •\) the customer wins the case and ends up in a neutral position.
+  \item
+    \(\sigma_{7, c, \overline{\mathrm{d}}} = -\) SP loses the case and ends up in a disadvantaged position.
   \end{itemize}
@@
 \item
-  The customer can follow the protocol to the non-disadvantaged termination position \(\sigma_{7, c, \mathrm{n}} = +\), or in case the SP haven't followed the protocol start a dispute and win the case \(\sigma_{7, c, \overline{\mathrm{d}}} = •\).
-\item
-  The SP can do nothing and end up in non-disadvantaged position \(\sigma_{7, s, \mathrm{n}} = +\).
+  The customer can follow the protocol to the non-disadvantaged termination position \(\sigma_{7, c, \mathrm{n}} = +\), or in case the SP hasn't followed the protocol start a dispute and win the case \(\sigma_{7, c, \overline{\mathrm{d}}} = •\).
+\item
+  The SP can do nothing and ends up in a non-disadvantaged position \(\sigma_{7, s, \mathrm{n}} = +\).
 \end{itemize}
@@
 
-The diagram below shows the path of positions when SP try to misbehave and don't execute service after receiving the payment.
-The protocol ends up in neutral to customer and disadvantaged to SP positions.
+The diagram below shows the path of positions when SP tries to misbehave and doesn't execute service after receiving the payment.
+The protocol ends up neutral to customer and disadvantaged to SP positions.
 
@@
 \centering
-\caption{Scenario of path where both the customer and  the SP are behaving correctly}
+\caption{The scenario of path where both the customer and  the SP are behaving correctly}
 \label{fig:well-behaviour}
@@
 
-\subsection{Results}\label{results}
-
-With the fairness definition stated in equation, and the assumptions stated in \ref{assumptions}, our analysis indicate that the protocol achieve fairness.
-
-\section{Future work}\label{sec:future-work}
+%\subsection{Results}\label{results}
+
+With the fairness definition stated in the equation and the assumptions stated in Section \ref{assumptions}, our analysis indicates that the protocol achieves fairness.
+
+\section{Future work}
+\label{sec:future-work}
+
 \subsection{Justice}\label{justice}
 
-Justice is the one biggest obstacle in achieving system that complies with Web3 postulates~\cite{Web3Wiki71}.
-
-The possible directions for mitigation of such issue are to either (1) replace justice with decentralised autonomous organisations (DAO) like proposed in Themis~\cite{meng2019themis} or Kleros~\cite{lesaege2018kleros}; or (2) make it infeasible to provide incorrect results.
-
-The first approach is more feasible in the near future.
-It would require creating large pool of experts in a field, that in case of dispute, would receive all the proofs ($\mathrm{PoD}$, $\mathrm{PoP}$, as well as any other proofs significant to the case) that could be queried by the experts in zero-knowledge fashion, i.e., they could ask limited number of questions to the proofs and getting yes/no answers.
+Justice is the one biggest obstacle in achieving a system that complies with Web3 postulates~\cite{Web3Wiki71}.
+
+The possible directions for mitigation of such issues are to either (1) replace justice with decentralized autonomous organizations (DAO) like proposed in Themis~\cite{meng2019themis} or Kleros~\cite{lesaege2018kleros}; or (2) make it infeasible to provide incorrect result.
+
+The first approach is more feasible shortly.
+It would require creating a large pool of experts in a field, that in case of dispute, would receive all the proofs ($\mathrm{PoD}$, $\mathrm{PoP}$, as well as any other proofs significant to the case) that could be queried by the experts in zero-knowledge fashion, i.e., they could ask a limited number of questions to the proofs and getting yes/no answers.
 Keeping the case fully confidential.
-The experts would be incentivised to participate in the pool by the system of fees.
-Their honest behaviour would be incentivised by the stake they would have to lock, and punishment they would get by judging incorrectly, where the ``correctly'' is determined by the quorum of votes.
+The experts would be incentivized to participate in the pool by the system of fees.
+Their honest behavior would be incentivized by the stake they would have to lock, and punishment they would get by judging incorrectly, where the ``correctly'' is determined by the quorum of votes.
 
@@
 Concretely, the problem canes down to ``How to digitally represent blood''.
-If we could represent urine, blood, saliva, or any other physical material in binary format, and let the customer to take a sample, discrete it and send it to the SP by himself, then the whole chain of integrity could be ensured.
+If we could represent urine, blood, saliva, or any other physical material in binary format, and let the customer take a sample, discrete it, and send it to the SP by himself, then the whole chain of integrity could be ensured.
 Therefore, wrong service provision would be infeasible.
 
-\subsection{Provable availability of
-results}\label{cryptographically-provable-availability-of-results}
-
-Currently, the SP has to publish the results into a p2p content addressable storage network, e.g., IPFS.
-The problem is that, nothing prevent the SP from publishing the results, receiving the cid, publishing $\mathrm{PoP}$, and immediately after removing the results from the local storage.
-In case of dispute the SP can upload the content again, proving its availability.
-The SP has no motivation to proceed with this kind of misbehaviour, other than putting the customer in disadvantaged position caused by the lost dispute.
-We see possible prevention of this misbehaviour by the usage of Filecoin---an incentive layer on top of IPFS that guarantee the content availability via economic incentivisations~\cite{benetfilecoin}.
-With the help of Filecoin, the SP would be obligated to create a deal that guarantee the results availability until the deadline of the transaction.
+\subsection{Provable availability of the
+result}\label{cryptographically-provable-availability-of-results}
+
+Currently, the SP has to publish the result into a peer-to-peer content-addressable storage network, e.g., IPFS.
+The problem is that nothing prevents the SP from publishing the result, receiving the cid, publishing $\mathrm{PoP}$, and immediately after removing the result from the local storage.
+In case of dispute, the SP can upload the content again, proving its availability.
+The SP has no motivation to proceed with this kind of misbehavior, other than putting the customer in a disadvantaged position caused by the lost dispute.
+We see possible prevention of this misbehavior by the usage of Filecoin---an incentive layer on top of IPFS that guarantees the content availability via economic incentivisations~\cite{benetfilecoin}.
+With the help of Filecoin, the SP would be obligated to create a deal that guarantees the result availability until the deadline of the transaction.
 Moreover, since Filecoin is a blockchain by itself, it could play both roles of message board and storage network.
@@
 
-Without lose of generality the payment can be made with cash.
+Without loss of generality, the payment can be made with cash.
 The customer can exchange the cash with SP together with delivering the package.
-The $\mathrm{PoD}$ would contain an information that the transaction has been paid with cash; therefore, Steps 1 and 2 could be merged together and realised in one step.
-In case of dispute the payment disclosure would be in included in $\mathrm{PoD}$.
+The $\mathrm{PoD}$ would contain information that the transaction has been paid with cash; therefore, Steps 1 and 2 could be merged and realized in one step.
+In case of dispute, the payment disclosure would be included in $\mathrm{PoD}$.
 
@@
 
-We assumed the customer to deliver the package to the SP personally or via trusted person.
-However the system could be extended to support anonymous delivery system as proposed in Lelantos~\cite{altawy2017lelantos}.
+We assumed the customer to deliver the package to the SP personally or via a trusted person.
+However, the system could be extended to support an anonymous delivery system as proposed in Lelantos~\cite{altawy2017lelantos}.
 
 \section{Conclusions}\label{sec:conclusion}
-In this paper, we have proposed a anonymity- preserving blockchain-based protocol for local services provision.
-The protocol can be employed by any local service provider to provide services without collecting any personal information.
+In this paper, we have proposed anonymity-preserving blockchain-based protocol for services provision.
+The protocol can be employed to provide services without collecting any personal information.
 The payment is handled by anonymous cryptocurrencies.
-Proof of delivery and proof of provision are published on message board blockchain.
-The results are published on content addressable p2p network.
-The dispute can be settled by disclosing proofs to justice.
-Assuming the definition~\ref{fairness} we showed that the protocol achieve fairness.
-Finally, we pinpointed further improvements like decentralised dispute resolution, provable  availability of results, paying with cash, and anonymous delivery via courier.
+Proof of delivery and proof of provision are published on the message board blockchain.
+The result is published on a content-addressable p2p network.
+The dispute can be settled by disclosing proof to justice.
+Using the definition~\ref{fairness} we showed that the protocol achieves fairness.
+Finally, we pinpointed further improvements like decentralized dispute resolution, provable availability of the result, paying with cash, and anonymous delivery via courier.
 
@@
 \bibliography{bibliography}
+%JS uporządkować bibliografię
 \EOD

### 2022-03-04 access.tex
update abstract

@@
 \begin{abstract}
-Service providers like lawyers, laboratories, auditors, or banks, to
-provide services, require customers to submit data often
-associated with their personal information. This situation exposes
-customers to privacy risks. However, most service providers use personal information merely for logistic operations like payments
-and communication and could provide services anonymously if other means of logistics exist.
-
-We propose a protocol for coordinating local anonymous service
-provision. Our proposal uses blockchain for both anonymous payments and proofs of existence (so-called message board) and content-addressable network (e.g.~IPFS) for results delivery.
-
-A service provider can employ our protocol to provide
-services without collecting any personal information. Possible
-applications for this protocol include anonymous clinical drug testing,
-steroid, parenting testing, anonymous legal advice, or
-anonymous financial trustworthiness evaluation.
-
-In case of dispute, either due to exceeding deadlines or providing
-incorrect result, the customer can disclose the whole interaction and
-prove to justice (police or court) the misbehavior of the service
-provider.
-
-We analyze the protocol in the context of fairness and discuss further
-extensions to an anonymous delivery system, payment with cash, and
-decentralized conflict resolution system.
-
-Our protocol can enable various services currently based on unacceptable trust assumptions to the SP.
-%JS to framework czy protocol?
-%SB zmieniłem na protocol, framework jest zbyt abstrakcyjne
+Service providers like lawyers, laboratories, auditors, or banks, to provide services, require customers to submit data often associated with their personal information.
+This situation exposes customers to privacy risks.
+However, most service providers use personal information merely for logistic operations like payments and communication and could provide services anonymously if other means of logistics exist.
+We propose a protocol for coordinating anonymous service provision.
+Our proposal uses blockchain for both anonymous payments and proofs of existence (so-called message board) and content-addressable network (e.g.~IPFS) for results delivery.
+A service provider can employ our protocol to provide services without collecting personal information.
+Possible applications for this protocol include anonymous clinical drugs, steroids, parenting testing, or anonymous legal advice.
+In case of dispute, either due to exceeding deadlines or providing incorrect results, the customer can disclose the whole interaction and prove to justice (police or court) the misbehaviour of the service provider.
+We analyze the protocol in the context of fairness and discuss further extensions to an anonymous delivery system, payment with cash, and a decentralized conflict resolution system.
+Our protocol may enable various services currently based on unacceptable trust assumptions to the SP.
 \end{abstract}
@@
 \section{Building Blocks}\label{sec:building-blocks}
-%JS bacground czego?  
-%SB To jest takie wprowadzenie i opisanie wszystkich elementów które będą potrzebne do stowrzenia protokołu. Czy Preliminaries będzie ok?
+
 \subsection{Dispute resolution system}
@@
 To do so the whole service examination would have to be computable, which is hard to achieve in settings where physical materials (like blood) are examined.
-Concretely, the problem canes down to ``How to digitally represent blood''.
+Concretely, the problem canes down to ``How to digitally represent blood?''.
 If we could represent urine, blood, saliva, or any other physical material in binary format, and let the customer take a sample, discrete it, and send it to the SP by himself, then the whole chain of integrity could be ensured.
@@
 The customer can exchange the cash with SP together with delivering the package.
-The $\mathrm{PoD}$ would contain information that the transaction has been paid with cash; therefore, Steps 1 and 2 could be merged and realized in one step.
+The $\mathrm{PoD}$ would contain information that the transaction has been paid with cash; therefore, steps one and two could be merged and realized in one step.
 In case of dispute, the payment disclosure would be included in $\mathrm{PoD}$.

### 2022-03-08 access.tex
grammarly fixes

@@
 \begin{keywords}
-fair-exchange, blockchain, anonymity,  physical delivery, services
+Anonymity, blockchain, fair-exchange, physical delivery, privacy, services
 \end{keywords}
@@
 
-Important individuals like top government, influencers, or celebrities are especially vulnerable to this kind of attack as exposure of their health records, purchase habits, or legal documents can threaten their reputation, position, or can be used for blackmailing.
-
-The guarantee of the privacy of the data is often based merely on trust assumptions and the security of IT system.
-However, most of the SP does not need personal information for any other reason than payment or communication, which should be considered secondary compared to actual service provision.
-
-It would be desirable for the user to keep its identity private while the service provider still provides its services.
-This could lead to reduced trust that users have to put on SP and less responsibility borne by SP.
-
-There is some services that would benefit from anonymous services, some examples are:
-\begin{itemize}
-    \item Patients willing to take a 
-    test for drug, venereal diseases, paternity etc.
-have a strong incentive to keep the whole procedure private.
-Merely the fact that they took the test without exposing the result is suggestive enough to act as a premise in case of a conflict.
+Important individuals like top government, influencers, or celebrities are especially vulnerable to this kind of attack as exposure of their health records, purchase habits, or legal documents can threaten their reputation, position or be used for blackmailing.
+
+The privacy guarantee of the data is often based merely on trust assumptions and the security of the IT system.
+However, most SPs do not need personal information for any other reason than payment or communication, which should be considered secondary compared to actual service provision.
+
+It would be desirable for the user to keep its identity private while still receiving the service. This could lead to reduced trust that users have to put on SP and less responsibility borne by SP.
+
+Examples of services that would benefit from the anonymity property are:
+\begin{itemize}
+    \item Patients willing to take a test for drugs, venereal diseases, paternity or steroids have a strong incentive to keep the whole procedure private.
+Merely the fact that they took the test—without exposing the result—is suggestive enough to act as a premise in case of a conflict.
 
@@
 
-Currently, they have to risk that their personal details, materials, and results are stored securely and kept in private from any unauthorized actor (both curious employee, and malicious attacker).
-
-Our protocol allows taking such tests anonymously and therefore getting
-rid of the strong trust assumption put on the laboratories and their IT
+Currently, they have to risk that their personal details, materials, and results are stored securely and kept in private from any unauthorized actor (both curious employee and malicious attacker).
+
+Our protocol allows taking such tests anonymously, therefore eliminating the strong trust assumption put on the laboratories and their IT
 systems.
-\item People willing to take business activities that may be risky % or not yet fully legislated, 
-may be willing to receive the risk estimation and prediction of possible personal repercussions of such action.
-
-By exposing our identity to the lawyer, we trust that he won't use that
+\item People willing to take risky business activities may be willing to receive the risk estimation and prediction of possible personal repercussions of such action.
+
+By exposing our identity to the lawyer, we trust that he will not use that
 information for harmful actions.
 
-Our protocol would allow taking such advice anonymously, and therefore
-getting rid of the strong trust assumption put on the lawyers and their IT systems.
+Our protocol would allow taking such advice anonymously, therefore eliminating the strong trust assumption put on the lawyers and their IT systems.
 \end{itemize}
@@
 
-In case of dispute, either due to exceeding deadlines or providing
-incorrect result, the customer can disclose the whole interaction and
-prove to justice (police or court) the misbehavior of the service 
-provider.
-%JS a np automatyczny zwrot środków?
-%SP to wymagałoby wprowadzenie depozytu co bardzo komplikuje cały system. Co więcej miałoby to sens tylko wtedy gdyby użyć "zdecentralizowanych sądów" (Future Work/Justice).
-
-To achieve these objectives we use:
+In case of dispute, either due to exceeding deadlines or providing an  incorrect result, the customer can disclose the whole interaction and
+prove to justice (police or court) the misbehaviour of the SP.
+
+To achieve these objectives, we use:
 \begin{itemize}
@@
     \item Message board blockchain, to achieve fairness, i.e., as a means for proving that certain actions took place at a certain moment without the trusted third party.
-    \item Content-addressable peer-to-peer storage network, to provide results to customers. 
+    \item Content-addressable peer-to-peer storage network to provide results to customers. 
     \item Cryptography
@@
 
-We observe that the issue of anonymous service provision can be seen as a problem of fair-exchange where parties exchange some goods in a fairly manner, i.e., either both parties obtain the goods, or they both obtain nothing.
-
-In our case, the customer is exchanging with the SP cryptocurrency and materials for the result of a service.
+We observe that the issue of anonymous service provision can be seen as a problem of fair exchange where parties exchange some goods fairly, i.e., either both parties obtain the goods, or they both obtain nothing.
+
+In our case, the customer is exchanging with the SP cryptocurrency and materials for the result of the service.
 
 %\paragraph{Contributions}
-We contribute to the field of fair-exchanges by proposing a simple,
- practical, and anonymous protocol that does not rely on centralized trusted-third party, but on decentralized blockchain and
+We contribute to the field of fair exchanges by proposing a simple, practical, and anonymous protocol that does not rely on the centralized trusted-third party but decentralized blockchain and
 distributed content-addressable storage network.
@@
 at each step of the protocol, both parties are incentivized to act accordingly to the protocol; otherwise, the misbehaving party ends up in the worst position.
-\item Dispute resolution: at each step of the protocol the customer can start a dispute and win the case if and only if the SP misbehaved.
+\item Dispute resolution: at each step of the protocol, the customer can start a dispute and win the case if and only if the SP misbehaved.
 
 \item TTP-less: 
-our protocol does not rely on a trusted-third party to conduct transactions in fairly manner.
-Only in case of dispute   the centralized justice is involved (the justice decentralization is discussed in Section ~\ref{sec:future-work}.
+our protocol does not rely on a trusted third party to conduct transactions fairly.
+Only in case of dispute the centralized justice is involved (the justice decentralization is discussed in section ~\ref{sec:future-work}.
 \item Physical materials: our protocol allows providing not only digital but also physical materials to the service provider.
@@
 
-Some authors have proposed blockchain-based fair-exchange systems that could be adapted to service provision; however, to our best knowledge we
-are the first to propose a system that satisfies all five properties
-stated above using blockchain technology. Especially anonymity and physical materials delivery, are
-properties that were rarely addressed together, and if so, the protocol
-based on TTP, and strong and impractical assumptions on banking system~\cite{birjoveanu2015anonymity}, or didn't address the conflict
+Some authors have proposed blockchain-based fair-exchange systems that could be adapted to service provision; however, to our best knowledge, we are the first to propose a system that satisfies all five properties stated above using blockchain technology.
+Especially anonymity and physical materials delivery were rarely addressed together, and if so, the protocol was based on TTP and strong and impractical assumptions on banking system~\cite{birjoveanu2015anonymity} or did not address the conflict
 between parties~\cite{altawy2017lelantos}.
 
-Our protocol can potentially enable a variety of services that for many
-customers based on unacceptable trust assumptions to the SP.
+Our protocol may enable various services currently based on unacceptable trust assumptions to the SP.
 
@@
 The remainder of this paper is organized as follows.
-In Section~\ref{sec:related-works} we briefly review related works. 
-Section~\ref{sec:building-blocks} explains the background related to fair-exchanges, blockchain, anonymity and confidentiality, and storage network. 
+In section~\ref{sec:related-works} we briefly review related works. 
+Section~\ref{sec:building-blocks} explains the building blocks related to fair exchanges, blockchain, anonymity and confidentiality, and storage network. 
 Section~\ref{sec:protocol} describes how the protocol works in detail.
@@
 Section~\ref{sec:future-work} discuss possible improvements. 
-Finally, Section~\ref{sec:conclusion} concludes the paper.
+Finally, section~\ref{sec:conclusion} concludes the paper.
 
@@
 
-\subsection{Fair-exchange and blockchain}
+\subsection{Fair exchange and blockchain}
 The idea of certified mail is simple, neither the sender can deny sending the mail, nor the receiver can deny receiving it.
-As the service is widely used in paper world, achieving it for e-mails haven't meet the agreement across scientific community for over 40 years.
-The main reason was the dependency of TTP, which significantly reduce the performance, security, and robustness of such protocols.
+As the service is widely used in the paper world, achieving it for e-mails has not yet met the agreement across the scientific community.
+The main reason was the dependency of TTP, which significantly reduced the performance, security, and robustness of such protocols.
 The protocols that do not use TTP struggle with high computation and communication overhead.
 
-Authors of ~\cite{hinarejos2019solution} replaced the TTP with blockchain (concretely Bitcoin blockchain as a reference implementation), which acts as a secure, verifiable, and decentralized TTP.
-
-The idea behind certified e-mails and any other fair-exchange protocol is following:
+Authors of ~\cite{hinarejos2019solution} replaced the TTP with blockchain (concretely Bitcoin blockchain as a reference implementation) that acts as a secure, verifiable, and decentralized TTP.
+
+The idea behind certified e-mails and any other fair exchange protocols is following:
 \begin{enumerate}
@@
     \item The receiver returns a proof of delivery (a signature) of the encrypted message to the sender.
-    \item The sender publish on blockchain (or TTP in general) a proof of delivery and the decryption key.
+    \item The sender publishes proof of delivery and the decryption key on a blockchain (or TTP in general).
     \item The receiver decrypts the encrypted message using the published decryption key.
@@
 
-The non-repudiation requirement is achieved by the receiver sending the proof of delivery prior having access to the decrypted message.
-And the sender publishing the decription key together with the proof of delivery on blockchain (or TTP) so that the receiver can not deny both receiving the message and having access to decryption key, because it is publicly available.
-
-The protocol also handles confidentiality — the encryption key used to encrypt and then decrypt the message is encrypted using the receiver's public key, so the key is never published in raw form.
-Also, the protocol supports timeliness, meaning that the transaction is always finalized in a finite time.
-
-In this case, the role of blockchain is to attest the public existence of decryption key at a particular point of time.
-
-\subsection{Fair-exchange, anonymity, and physical products delivery} 
+The non-repudiation requirement is achieved by the receiver sending the proof of delivery prior to having access to the decrypted message and the sender publishing the decryption key together with the proof of delivery on the blockchain (or TTP) so that the receiver can deny neither receiving the message nor having access to the decryption key—because it is publicly available.
+
+In this case, the role of blockchain is to certify the public existence of the decryption key at a certain time.
+
+\subsection{Fair exchange, anonymity, and physical products delivery} 
 \label{anonymity-and-fair-exchange-in-e-commerce-protocol-for-physical-products-delivery}
@@
 Authors of~\cite{birjoveanu2015anonymity} proposed a
-fair-exchange of physical products and electronic payment protocol that
+fair exchange of physical products and electronic payment protocol that
 guarantee both customer and merchant anonymity. They achieve it by
@@
 
-The anonymity is ensured by assuming the existence of a source cabinet
-(SC) and delivery cabinet (DC), and a trusted delivery agent who take
+The anonymity is ensured by assuming the existence of a source cabinet (SC), delivery cabinet (DC), and a trusted delivery agent who take
 a product from a source cabinet and provide it to a destination cabinet.
 Both cabinets provide access to the product by passwords to conceal
-the identity of the customer and the merchant. To avoid identity disclosure
-of customers and merchants, the access to the product is provided by
-passwords.
+the identity of the customer and the merchant.
 
@@
     \item The customer buys a digital coin from his bank and validates it with the TTP.
-    \item The customer sends to the merchant the purchase order and the digital signature made by TTP on the encrypted coin.
+    \item The customer sends the merchant the purchase order and the digital signature made by TTP on the encrypted coin.
     \item The merchant post the product to the source cabinet.
@@
 
-Yet, the fair-exchange properties are achieved by strong assumptions.
+However, the protocol relies on strong assumptions to achieve fairness.
 Namely,
@@
     \item the TTP does not misbehave or collude with any party. 
-    \item The customer's and merchant's banks enable confidential transactions and both share commit-buffer where the value is locked until the transaction is finished.   
-    \item All banks maintain a global list of coin's serial numbers to prevent double-spending problems. 
-    \item The source cabinet and delivery cabinet exist, and in both the product access is protected by a password.
+    \item The customer's and merchant's banks enable confidential transactions, and both share commit-buffer where the value is locked until the transaction is finished.   
+    \item All banks maintain a global list of coins' serial numbers to prevent double-spending problems. 
+    \item The source cabinet and delivery cabinet exist, and in both, the product access is protected by a password.
     \item Delivery cabinet is equipped with a video camera that records the moment when the customer opens the package and provides a way to submit the video to TTP in case of a dispute. 
@@
 
-Themis~\cite{meng2019themis} is a fair-exchange
-protocol, which uses blockchain instead of TTP. It provides escrow
-services for secure exchanging between cryptocurrencies and digital goods, and a decentralized dispute resolution system for resolving conflicts.
-
-Two parties say Alice and Bob, can create an escrow by generating
+Themis~\cite{meng2019themis} is a fair exchange
+protocol that uses blockchain instead of TTP. It provides an escrow
+service for secure exchanging cryptocurrencies and digital goods. Also, it provides a decentralized dispute resolution system for resolving conflicts.
+
+Two parties say, Alice and Bob, can create an escrow by generating
 2-of-2 (not 2-of-3 as it is other TTP-based systems) threshold account
@@
 
-Then, both Alice and Bob, take their keys, and split them into
+Then, both Alice and Bob take their keys and split them into
 \(n=2t+1\) secret shares using Shamir Secret Shamir protocol, where
 \(n\) is the number of mediators that participate in the decentralized
-network and \(t+1\) becomes the threshold of a sufficient number of
-mediators that can reconstruct the secret key.
+network and \(t+1\) becomes the threshold of a sufficient number of mediators to reconstruct the secret key.
 
@@
 The escrow is secure as long as \(t+1\) of mediators does not collude,
-which would let them recreate both \(x_A\) and \(x_B\). Also, to ensure
-that parties are exchanging real key shares, they also send a witnesses
-generated with Feldman VSS scheme and zero-knowledge proofs to guarantee
-the consistency between witnesses and key shares.
+which would let them recreate both \(x_A\) and \(x_B\). To ensure
+that parties exchange actual key shares, they send witnesses
+generated with the Feldman VSS scheme and zero-knowledge proofs to guarantee the consistency between witnesses and key shares.
 
@@
 
-The honesty of mediators is achieved by the monetary incentivization and
-reputation system.
+The monetary incentivization and reputation system guarantee the honesty of mediators.
 
@@
 Lelanros~\cite{altawy2017lelantos} is a blockchain-based anonymous
-physical delivery system. The anonymity is achieved by employing ToR's
-onion routing to connect physical delivery providers. The whole route
-from merchant to a customer is split into multiple steps, and each step is
-undertaken by the different randomly selected delivery providers. As long as
-the delivery providers do not collude, a merchant can not learn both
-the identity and destination address of the customer.
+physical delivery system.
+The protocol achieves anonymity by employing onion routing (similar to the Tor network) to connect physical delivery providers.
+The whole route from a merchant to a customer is split into multiple steps, and each step is undertaken by the different randomly selected delivery providers.
+As long as the delivery providers do not collude, a merchant neither can learn the identity nor destination address of the customer.
 
@@
 However, since the system uses Ethereum— fully traceable blockchain—its anonymity is achieved as long as the addresses are not identified with the real identities, which we call pseudonymity rather than anonymity (see Section~\ref{sec:pseudo-anon}).
-Also, the protocol does not cover the case of dispute between the parties.
-
-%JS moze\section{Building Blocks}
-%SB Dla mnie idealnie.
+Also, the protocol does not cover the dispute between the parties.
+
 \section{Building Blocks}\label{sec:building-blocks}
-
 \subsection{Dispute resolution system}
 
-Disputes are an inevitable part of all human transactions. Whether intentional or accidental, the system should prevent 
-violation of  
-agreed contract rules  or local jurisdiction. The rules are specified by law and implemented by the police.
+Disputes are an inevitable part of all human transactions.
+Whether intentional or accidental, the system should prevent violation of agreed contract rules or local jurisdiction.
+The rules are specified by law and implemented by the police.
 
 The vision of smart contracts was to replace the legal contract with
-programmable and autonomous contracts. The specifications of the contract
-were encompassed in the code, hence the slogan ``code as a law''. Yet,
-the blockchain paradigm has its limitations. It can assure the
-correctness of data existing on the blockchain. The problem arises in
-the contact between blockchain and the real world. When we want the smart
-contract to make a decision based on some input from outside the
-blockchain. We move a lot of trust assumptions on the data providers.
-The technique of providing real-world data to the blockchain is called
-oracle. Oracle provides data based on a decentralized network of mediators,
-therefore the trust is also decentralized.
+programmable and autonomous contracts. The smart contract code encompasses the contract's specifications, hence the slogan ``code as a law''.
+
+Nevertheless, the blockchain paradigm has its limitations.
+Blockchain can assure the correctness of data existing only on the blockchain—the problem arises in the contact between blockchain and the real world when we want the smart contract to decide based on some input from outside the blockchain.
+The technique of providing real-world data to the blockchain is called oracle.
+Oracle provides data based on a decentralized network of mediators; therefore, the trust is also decentralized.
 
 Some oracles provide the data like weather, soccer match result, stock
-price, train delay, election results, others---and they are the ones we
-are interested in---provide the settlement of a submitted dispute.
-
-Themis~\cite{meng2019themis} besides providing fair-exchange protocol,
-also offers a semi-autonomous decentralized dispute resolution system,
-which complies with the web3 postulates of a decentralized web. Themis
+price, train delay, election results, others—and they are the ones we
+are interested in—provide the settlement of a submitted dispute.
+
+Themis~\cite{meng2019themis} besides providing fair exchange protocol,
+also offers a semi-autonomous decentralized dispute resolution system that complies with the Web3 postulates of a decentralized web. Themis
 resolve disputes by a set of voluntary anonymous mediators participating
@@
 
-Kleros~\cite{lesaege2018kleros} is a smart contract deployed on
-Ethereum platform mimics in a decentralized and autonomous way how
-the court works in real life. In Kleros, every process of a dispute like
-gathering evidence, selecting jurors, rewarding the winning party is 
-automated by a set of smart contracts. Similar to Themis, the honesty
-of the agents voting in a case is achieved by game-theoretical economic
-incentives.
-
-Such decentralised, voluntary, and anonymous dispute resolution system
-might work for simple contracts violation like eBay seller sending
-broken or wrong product, or Airbnb apartment being not adequate to the
-photos in the offer. However it's hard to realise such decentralised
-evaluation of quality of heath or legal services when expertise and
-privacy concerns are taken into an account. Therefore, in our protocol
-we take the more conservative approach and resolve disputes using local
-justice system (police, court, etc.).
-
-Possible directions toward semi-autonomous decentralised resolution
+Kleros~\cite{lesaege2018kleros} is a smart contract deployed on the Ethereum platform that mimics in a decentralized and autonomous way how the court works in real life.
+In Kleros, every process of a dispute like gathering evidence, selecting jurors, rewarding the winning party is automated by a set of smart contracts.
+Like Themis, the honesty of the agents voting in a case is achieved by game-theoretical economic incentives.
+
+Such a decentralized, voluntary, and anonymous dispute resolution system might work for simple contracts violations like an eBay seller sending broken or wrong products or an Airbnb apartment being inadequate to the photos in the offer.
+However, it is hard to realize such decentralized evaluation of heath or legal services quality when expertise and privacy concerns are taken into account.
+Therefore, in our protocol, we take the more conservative approach and resolve disputes using local
+justice system (police or court).
+
+Possible directions toward semi-autonomous decentralized resolution
 system are discussed in Section ~\ref{sec:future-work}.
@@
 
-In case of dispute, the customer can prove to justice (police, court, etc.) convincing evidence for the honesty of the customer and misbehavior of the SP. 
-Because the customer is anonymous the SP can not start a dispute---there is no means to identify the customer.
-
-To mitigate the issue, we designed the protocol so that the SP who follows the protocol is always in an advantageous position, therefore he has no reason to start a dispute.
-The customer on the other hand can start a dispute at any time of the protocol, but only the actual misbehavior of the SP makes him win the case.
-
-Abstracting from the services the SP is providing, in case of a dispute each party should be able to prove its honest behavior.
+In case of dispute, the customer can prove to justice (police or court) convincing evidence for the honesty of the customer and misbehaviour of the SP. 
+Because the customer is anonymous, the SP can not start a dispute---there is no means to identify the customer.
+
+To mitigate the issue, we designed the protocol so that the SP who follows the protocol is always in an advantageous position; therefore, he has no reason to start a dispute.
+On the other hand, the customer can start a dispute at any time of the protocol, but only the actual misbehaviour of the SP makes him win the case.
+
+Abstracting from the services the SP is providing, each party should be able to prove its honest behaviour in case of a dispute.
 We introduce three proofs that should be disclosed to justice in case of a dispute:
@@
     \item Proof-of-delivery ($\mathrm{PoD}$) is a confirmation issued by the SP to the customer that proves that the customer has delivered to the SP a complete (according to the SP requirements) package, and the SP accepted it.
-It consists of the current time; deadline to pay for the transaction; deadline to provide a result of the service; randomly generated number uniquely identifying the transaction, and the SP's signature guaranteeing non-repudiation.
+It consists of the current time, the deadline to pay for the transaction, the deadline to provide a result of the service, randomly generated number uniquely identifying the transaction, and the SP's signature guaranteeing non-repudiation.
 The formal definition of the $\mathrm{PoD}$ is presented in Section ~\ref{proof-of-delivery}.
 
-    \item Payment $\mathrm{attestation}$ is confirmation that the customer has paid for the transaction, at a certain time.
+    \item Payment $\mathrm{attestation}$ is confirmation that the customer has paid for the transaction at a certain time.
 The actual implementation depends on the particular cryptocurrency and is discussed further Section~\ref{payment-for-services}.
@@
     \item Proof of provision ($\mathrm{PoP}$) is proof that the SP published the result at a certain time.
-It defends the SP in case the customer unjustly starts a dispute after the result have been published.
-It consists of a content identifier as specified in Section ~\ref{storage-network}; the value uniquely identifying the transaction previously generated in $\mathrm{PoD}$; the SP's signature guaranteeing authentication.
-The connection between $\mathrm{PoP}$ and the result is made by the content identifier (cid) that uniquely identify the result (it is some kind of a hash of the result) such that the result can not be forged after the $\mathrm{PoP}$ has been published.
+It defends the SP in case the customer unjustly starts a dispute after the result has been published.
+It consists of a content identifier as specified in section ~\ref{storage-network}, the $\mathrm{nonce}$ uniquely identifying the transaction previously generated in $\mathrm{PoD}$, and the SP's signature guaranteeing authentication.
+The connection between $\mathrm{PoP}$ and the result is created by the content identifier ($\mathrm{cid}$) that uniquely identify the result (it is some kind of a hash of the result) such that the result can not be forged after the $\mathrm{PoP}$ has been published.
 \end{enumerate}
@@
 
-By publishing the $\mathrm{PoP}$ on the blockchain, the SP can not falsify the time
-at which the result has been provided, because the block creation time
-proves that. Blockchain acts as a global clock that securely timestamps
-everything that gets into the block, so the $\mathrm{PoP}$ that was included in a
-block will be associated with the time when the block has been created.
+By publishing the $\mathrm{PoP}$ on the blockchain, the SP can not falsify the time at which the result has been provided because the block creation time proves that.
+Blockchain acts as a global clock that securely timestamps everything that gets into the block, so the $\mathrm{PoP}$ that was included in a block will be associated with the time when the block has been created.
 Moreover, since the blockchain is public, everyone (including justice) can be convinced that the SP indeed published the result at that time.
 
-Without such a proof there would be no other means to settle the conflict between the customer claiming the result has not been published and the SP claiming the result has been published within the deadline.
+Without such proof, there would be no other means to settle the conflict between the customer claiming the result has not been published and the SP claiming the result has been published within the deadline.
 
 Depending on the context the platform of achieving it is called bulletin board~\cite{achenbach2015improved} or message board~\cite{hinarejos2019solution} or trusted timestamping~\cite{gipp2015decentralized}.
-In this work we call it message board.
-
-% Such functionallity is the easiest to achieve by the trusted third party that authoritatively tells what happened and when.
-
-% Bitcoin introduced a way of decentralising not only the currency system,
-% but also other similary working centralised trusted third parties
-% including the message board.
-
-We let keep the protocol general enough to 
-be implemented using any of  
-existing technology to provide message board service, with the
-the assumption that it's decentralized and supports subscribing for the
-upcoming proofs from a particular address.
+In this work, we call it a message board.
+
+We keep the protocol general enough to be implemented using any existing technology to provide message board service, assuming it is decentralized and supports subscribing for the upcoming proofs from a particular address.
 
@@
 
-Privacy is a concept used in almost all kinds of social sciences like philosophy, psychology, sociology, and legal.
+Privacy is a concept used in almost all social sciences like philosophy, psychology, sociology, and legal.
 The multidisciplinary nature leads to ambiguous definitions~\cite{smith2011information}.
-For our work we rely on more concrete definitions, i.e.~confidentality, and anonymity.
+For our work, we rely on more concrete definitions, i.e.~confidentality, and anonymity.
 
 Confidentiality is the ability to hide the details of action from others.
-Or we can say, that the system guarantees confidentiality if for all observers everything they can say about the action is the fact that it happened and nothing more.
+Alternatively, we can say that the system guarantees confidentiality if, for all observers, everything they can say about the action is the fact that it happened and nothing more.
 
 Anonymity is the ability to hide one identity from others.
-More precisely, the inability to correlate actions performed within the system with the identity of the user.
-Or we can say, that the system guarantees anonymity if for all observers the actions are equally likely to be associated with any user of the system.
+More precisely, the inability to correlate actions performed within the system with the user's identity.
+Alternatively, we can say that the system guarantees anonymity if, for all observers, the actions are equally likely to be associated with any user of the system.
 However, anonymity is a spectrum rather than a dichotomous classification.
-One method of quantifying the level of anonymity is proposed in \textit{k}-anonymity~\cite{sweeney2002k}.
+One method of quantifying the level of anonymity is \textit{k}-anonymity proposed in~\cite{sweeney2002k}.
 It measures the user's anonymity by the number of other users from whom the user can not be distinguished.
-Concretely, the user is \textit{k}-anonymous if his actions are equally likely associated with \textit{k}-1 other users.
-The larger \textit{k}, the higher anonymity.
-
-Some techniques can be deployed on non-anonymous blockchains, the so-called mixers that gather together users into an \textit{anonymity set}, which then collude together to launder the transactions, in such a way that to an observer the likelihood of the sender of each transaction was equiprobable for any user from the anonymity set.
-
-Some systems guarantee pseudonomity rather than anonymity.
-Pseudonomity allows users to hide their real identity behind the pseudonym.
-Despite the whole system being transparent and allowing linking actions to one identity, the system is considered anonymous as long as the link between pseudonym and real identity is secret.
-This assumption is hard to satisfy in practice, as the KYC (Know Your Customer) and AML (Anti Money Laundering) regulations require users to reveal their real identity on most of the cryptocurrencies exchanges.
-This makes the anonymity of the user dependent on the security of the IT system.
+Concretely, the user is \textit{k}-anonymous if his actions are equally likely associated with \textit{k}-1 other users; the larger \textit{k}, the higher anonymity.
+
+Some anonymity techniques can be deployed on non-anonymous blockchains.
+The so-called mixers gather users into an \textit{anonymity set}, which then collude together to launder transactions in such a way that to an observer, the likelihood of the sender of each transaction is equiprobable for any user from the anonymity set.
+
+Some systems guarantee pseudonymity rather than anonymity.
+Pseudonymity allows users to hide their real identity behind the pseudonym.
+Despite the whole system being transparent and allowing linking actions to pseudonyms, the system is considered anonymous as long as the link between pseudonyms and real identities is secret.
+This assumption is hard to satisfy in practice, as the KYC (Know Your Customer) and AML (Anti Money Laundering) regulations require users to reveal their real identity to cryptocurrencies exchanges, making the user's anonymity dependent on the security of the IT system.
 Moreover, some correlations can be inferred merely by the analysis of transactions \cite{androulaki2013evaluating, ober2013structure}.
 
-The relations between these terms are illustrated in the Figure~\ref{fig:anonymity-diagram1}.
+The figure ~\ref{fig:anonymity-diagram1} ilustrate relations between these terms.
 
@@
 \centering
-\caption{Let us assume the Alice to be the customer willing to keep her identity private (anonymous) and Bob be the public SP.
-Alice controls two addresses 1 and 2, the connection between her real identity and the first address was compromised, and therefore the identification is possible, the connection between the second pseudonym is still unknown therefore anonymous.
-Alice takes two actions; the first one from the compromised address and the second one from anonymous one.
-The first action is confidential; therefore even though the psudonym has been compromised the action can not be associated with the Alice.
-The second action is transparent, therefore the Alice's anonymity is maintained as long as the connection to the second pseudonym is concealed.}
+\caption{Let us assume Alice to be the customer willing to keep her identity anonymous and Bob to be the public SP.
+Alice controls two addresses, 1 and 2; the connection between her real identity and the first address has been compromised, and therefore the identification is possible; the connection between the second pseudonym is still unknown therefore anonymous.
+Alice takes two actions; the first one from the compromised address and the second one from the anonymous one.
+The first action is confidential; therefore, even though the pseudonym has been compromised, the action can not be associated with Alice.
+The second action is transparent; therefore, Alice maintain her anonymity as long as the connection to the second pseudonym is concealed.}
 
@@
 
-The privacy-preserving blockchains are the ones that maintain anonymity via untraceability and (ideally) unlikability, not via assumption that the connection between an address and the real identity is concealed.
-
-Blockchains that natively support confidential transactions are
-Monero~\cite{van2013cryptonote} (via Ring Signatures~\cite{cryptoeprint:2015:1098} and Bulletproofs~\cite{Bulletpr14, bunz2018bulletproofs}) and ZCash~\cite{sasson2014zerocash} (via zkSNARK~\cite{ben2013snarks}), Grin~\cite{fuchsbauer2019aggregate} (via Mimblewimble~\cite{httpsdow19}).
+The privacy-preserving blockchains are the ones that maintain anonymity via untraceability and (ideally) unlikability, not via the assumption that the connection between an address (pseudonym) and the real identity is concealed.
+
+Examples of blockchains that natively support confidential transactions are: Monero~\cite{van2013cryptonote} (via Ring Signatures~\cite{cryptoeprint:2015:1098} and Bulletproofs~\cite{Bulletpr14, bunz2018bulletproofs}), ZCash~\cite{sasson2014zerocash} (via zkSNARK~\cite{ben2013snarks}), and Grin~\cite{fuchsbauer2019aggregate} (via Mimblewimble~\cite{httpsdow19}).
 
@@
 \subsection{Payment for services}\label{payment-for-services}
-Transactions between customers and SP have to be somehow pegged to prevent proving one payment for multiple transactions. In other
-words, we need some way to uniquely link particular payment with the
-the transaction paid for.
-
-Depending on the cryptocurrency the link can be created in different
+Transactions between customers and SPs must be pegged to prevent proving one payment for multiple transactions. In other
+words, we need a mechanism that uniquely associates a payment with the corresponding transaction.
+
+Depending on the cryptocurrency, the link can be created in different
 ways:
@@
   separate address — each transaction derives a new address uniquely
-  associating it with the transaction. Such addresses can be derived
+  associated with the transaction. Such addresses can be derived
   using Hierarchical Deterministic Wallets (BIP-32)~\cite{bipsbip089}.
@@
   memo — the payments are sent to one SP account but contain an extra
-  field named ``memo'' which contains a random value generated by SP and
-  included in $\mathrm{PoD}$. Each payment containing such value in the memo is
-  considered to pay for the transaction in question. In case of a dispute,
-  the connection can be disclosed by revealing the value in $\mathrm{PoD}$ and the payment's memo.
+  field named ``memo'' filled with the unique number provided by the SP in $\mathrm{PoD}$. Each payment containing such value in the memo is
+  considered to pay for the transaction. In case of a dispute, revealing both the payment memo and the $\mathrm{PoD}$ proves the connection.
 \end{itemize}
@@
 Both approaches have some advantages and disadvantages, but our protocol can abstract them away by treating them as some randomly generated unique number, often called \textit{nonce} (number once).
-How it is implemented depends on a particular blockchain.
+The actual implementation depends on a particular blockchain.
 
@@
 Monero allows proving and checking payments via dedicated API \cite{Howtopro46}.
-ZCash provides a mechanism called Payment Disclosure \cite{AnIntrod25}, which at the time of writing is still an experimental feature
-\cite{paymentd11}.
+ZCash provides a mechanism called Payment Disclosure \cite{AnIntrod25}.
 
@@
 Once the SP finishes its service, he has to provide the result to the customer.
-The most natural approach would to be send the result via email of the dedicated platform.
-However, since the customer wants to stay anonymous, he doesn't want to expose his email address nor IP address.
-Moreover, in case of dispute, the SP should be able to prove that the result has been provided before the deadline.
+The most natural approach would be to send the result via e-mail or some dedicated platform.
+However, since the customer wants to stay anonymous, he does not want to expose his e-mail address nor IP address.
+Moreover, the SP should prove that the result has been provided before the deadline, which brings us to the issue of proof of existence discussed in section ~\section{message-board}.
 
 One approach would be to post the result into a blockchain.
-Yet, storing data on a blockchain is very expensive.
-The most common workaround (\cite{shahid2020blockchain, wang2019auditable, chen2017improved, Usageide95}) is to publish the data to the IPFS \cite{benet2014ipfs}—a content addressable peer-to-peer storage network—and publish to a blockchain just a content identifier (cid) that uniquely points to the content stored on the IPFS.
-
-We take the same approach. Once the SP creates the result, he encrypts it using the previously provided encryption key and uploads it to IPFS network.
-
-To increase anonymity, the customer should use common techniques to hide its IP address; for example, use gateway, VPN, proxy, or onion routing.
+However, storing data on a blockchain is very expensive.
+The most common workaround (\cite{shahid2020blockchain, wang2019auditable, chen2017improved, Usageide95}) is to publish the data on a content addressable peer-to-peer storage network like IPFS~\cite{benet2014ipfs}.
+Then, publish on the blockchain just a content identifier ($\mathrm{cid}$) that uniquely points to the content stored on IPFS.
+
+We take the same approach. Once the SP creates the result, he encrypts it using the previously provided encryption key and uploads it to the IPFS network.
+
+To increase anonymity, the customer should use standard techniques to hide its IP address, such as gateway, VPN, proxy, or onion routing.
 
 \subsection{Separation of concerns}
-We could use one blockchain to achieve all of these three roles: (i) anonymous payments; (ii) message board; (iii) storage network.
-
-As the message board could be achieved by most of the blockchains, anonymous payments aren't so prevalent, and a provable storage network is a functionality of a few specialized blockchains.
-
-Instead of searching for one blockchain that solves all the functionalities, we allow the protocol to use separate blockchains for each of the functionalities.
-In case a suitable blockchain arises, it can play more than one role.
-
-At the time of writing, we see the following technologies that fulfill the requirements of each role:
+We could use one blockchain to achieve all of these three roles: (i) anonymous payments, (ii) message board, (iii) storage network.
+
+While most blockchains could provide the message board functionality, anonymous payments are not as prevalent.
+Especially a provable storage network is a functionality of a few specialized blockchains.
+
+Instead of searching for one blockchain that solves all the functionalities, we allow the protocol to use separate blockchains for each role.
+If a suitable blockchain arises, it can play more than one role.
+
+At the time of writing, we see the following technologies that fulfil the requirements of each role:
 
@@
 \subsection{Prerequisites}
-We do not design our protocol with the assumption of usage particular technologies, instead, we define requirements that each party of the protocol must satisfy to make the whole system work together.
+We do not design our protocol with the assumption of using particular technologies; instead, we define requirements that each party must satisfy to make the whole system work together.
 The choice of the particular technology for each role is up to the developer.
@@
 
-\item $\mathrm{materials}$ - are the materials required to provide the service.
-For example samples of urine, blood, stool, saliva; legal documents, CDs, emails, photos, bank statements, or any other kind of evidence depending on the service.
+\item $\mathrm{materials}$ - are the materials required to provide the service, for example, samples of urine, blood, stool, saliva; legal documents, CDs, emails, photos, bank statements, or any other kind of evidence depending on the service.
 \item $\mathrm{key}$ - symmetric key used to encrypt and decrypt the result.
@@
 \noindent \textbf
-{Proof of delivery ($\mathrm{PoD}$)}\label{proof-of-delivery} is a  confirmation issued by the SP to the customer that proves that the customer has delivered to the SP a complete (according to the SP requirements) package, and the SP accepted it.
+{proof of delivery ($\mathrm{PoD}$)}\label{proof-of-delivery} is a  confirmation issued by the SP to the customer that proves that the customer has delivered to the SP a complete (according to the SP requirements) package, and the SP accepted it.
 
@@
 We assume the $\mathrm{PoD}$ to be a QR code printed on a paper receipt, but any other form that guarantees integrity, authenticity, and non-repudiation can be used instead.
-
-The ($\mathrm{PoD}$ can be then used as evidence in case of a dispute.
 
@@
 \noindent \textbf
-{Proof of provision ($\mathrm{PoP}$)}\label{proof-of-provision} is proof that the SP published the result at a certain time.
+{proof of provision ($\mathrm{PoP}$)}\label{proof-of-provision} is proof that the SP published the result at a certain time.
 It defends the SP in case the customer unjustly starts a dispute after the result has been published.
-The connection between $\mathrm{PoP}$ and the result is made by the content identifier ($(\mathrm{cid}$) that uniquely identify the result (it is some kind of a hash of the result) such that the result can not be forged after the $\mathrm{PoP}$ has been published.
+The connection between $\mathrm{PoP}$ and the result is made by the content identifier ($\mathrm{cid}$) that uniquely identify the result (it is some kind of a hash of the result) such that the result can not be forged after the $\mathrm{PoP}$ has been published.
 
@@
 \noindent \textbf
-{Result}\label{results} is assumed to be document in PDF format, but any other format is allowed as long as it can be binary encoded and uploaded to IPFS. We refer to it symbolically as $result$.
-
-\noindent \textbf
-{Content Identifier (cid)}\label{content-identifier-cid}  is a term coined by IPFS
-\cite{Contenta59}  
-. However, since our protocol does not depend on
-this particular implementation of the storage network, we let the cid be any
-other identifier that securely and uniquely points to the content.
+{Result}\label{results} is assumed to be a document in PDF format, but any other format is allowed as long as it can be binary encoded and uploaded to IPFS. We refer to it symbolically as $result$.
+
+\noindent \textbf
+{Content Identifier (cid)}\label{content-identifier-cid}  is a term coined by IPFS~\cite{Contenta59}. However, since our protocol does not depend on
+this particular implementation of the storage network, we let the $\mathrm{cid}$ be any other identifier that securely and uniquely points to the content.
 
@@
 \begin{figure}[h!]
-\includegraphics[width=9cm]{anonser-protocol.png}
+\includegraphics[width=\linewidth]{anonser-protocol.png}
 \centering
@@
 Symbolically: 
-$
+\[
 \mathrm{pkg} \gets (\mathrm{materials}, \mathrm{key})
-$
+\]
 
@@
 
-We assume this step to be fully physical, that is, $\mathrm{pkg}$ consists of physical materials, $\mathrm{PoD}$ is in a form of e.g., QR code printed on a paper receipt.
+We assume this step to be entirely physical, that is, $\mathrm{pkg}$ consists of physical materials, $\mathrm{PoD}$ is in the form of, e.g., QR code printed on a paper receipt.
 
 $\mathrm{PoD}$ could be published on a message board (similarly to $\mathrm{PoP}$); however, since the $\mathrm{pkg}$ is delivered personally or via a trusted person, the confirmation can be issued in person as well.
-If we would like to hire a courier to deliver our $\mathrm{pkg}$, then the $\mathrm{PoD}$ would have to be published on the message board (further extension to the anonymous delivery system is discussed in Section \ref{sec:future-work}).
+If we would like to hire a courier to deliver our $\mathrm{pkg}$, then the $\mathrm{PoD}$ would have to be published on the message board (further extension to the anonymous delivery system is discussed in section \ref{sec:future-work}).
 
 Symbolically: 
-$
+\[
 \mathrm{PoD} \gets \mathrm{delivery}(\mathrm{pkg})
-$
-
-$
+\]
+\[
 (\mathrm{T}_\mathrm{issue}, \mathrm{T}_\mathrm{pay}, \mathrm{T}_\mathrm{provide}, \mathrm{nonce}, \mathrm{sig}_{\mathrm{sk}(\mathrm{SP})}) \equiv \mathrm{PoD}
-$
+\]
 
@@
 Symbolically: 
-$
+\[
 \mathrm{attestation} \gets \mathrm{payment}(\mathrm{nonce}, \mathrm{sig}_{\mathrm{sk}(\mathrm{C})})
-$
+\]
 
@@
 {Step 3. Provision of service}\label{step-3-provision-of-service} 
-Once the transaction is paid the SP starts the provision of service.
+Once the customer has paid for the transaction, the SP starts providing the service.
 
 Symbolically: 
-$
+\[
 \mathrm{result} \gets \mathrm{provision}(\mathrm{materials})
-$
+\]
 
@@
 
-After the service is finished, some result should be created. Next, the result is encrypted using encryption symmetric $\mathrm{key}$ provided in the first step.
-
-The encrypted result is then uploaded on the content addressable network such as IPFS. In return the content identifier (cid) is created.
+After the service is finished, a result should be created. Next, the result is encrypted using encryption symmetric $\mathrm{key}$ provided in the first step.
+
+The encrypted result is then uploaded on the content addressable network such as IPFS. In return the content identifier ($\mathrm{cid}$) is created.
 
 Symbolically: 
-$
+\[
 \mathrm{cid} \gets \mathrm{upload}(E_{\mathrm{key}}(\mathrm{result}))
-$
+\]
 
@@
 Symbolically: 
-$
+\[
 \mathrm{PoP} \equiv (\mathrm{cid}, \mathrm{nonce}, \mathrm{sig}_{\mathrm{sk}(\mathrm{SP})})
-$
-
-$
+\]
+\[
 \mathrm{publish}(\mathrm{PoP})
-$
+\]
 
@@
 
-After delivering the package and paying for the transaction the customer subscribes to the message board and waits until the SP publishes the proof of provision.
+After delivering the package and paying for the transaction, the customer subscribes to the message board and waits until the SP publishes the proof of provision.
 The subscription is for the SP public key $\mathrm{pk}(\mathrm{SP}$ and transaction's $\mathrm{nonce}$.
@@
 Symbolically: 
-$
+\[
 \mathrm{cid} \gets \mathrm{subscribe}(\mathrm{pk}(\mathrm{SP}), \mathrm{nonce})
-$
+\]
 
@@
 Symbolically: 
-$
+\[
 \mathrm{result} \gets \mathrm{D}_{\mathrm{key}}(\mathrm{download}(\mathrm{cid}))
-$
+\]
 
@@
 \begin{itemize}
-\item
-  Neutral position (•): when a party hasn't spent nor gained anything of significant value (money, time, effort). For example, at the beginning of the protocol.
-\item
-  Disadvantaged position (-): when a party has put a significant value without receiving an equivalent. For example, paid for a service in advance.
-\item
-  Advantaged position (+): when a party would benefit if the transaction would halt at that step. For example, the SP has received payment before service provision.
+\item Neutral position (•): when a party has not spent nor gained anything of significant value (money, time, effort). For example, at the beginning of the protocol.
+\item Disadvantaged position (-): when a party has put a significant value without receiving an equivalent. For example, the customer has paid for a service in advance.
+\item Advantaged position (+): when a party would benefit if the transaction would halt at that step. For example, the SP has received payment before service provision.
 \end{itemize}
@@
 
-\item
-  Normal: taking the action prescribed by the protocol.
-\item
-  Abnormal: everything that deviates from the designed steps of the protocol. For example, sending an arbitrary message, skipping some step, repeating step, timing out.
+\item Normal: taking actions prescribed by the protocol.
+\item Abnormal: everything that deviates from the designed steps of the protocol. For example, sending an arbitrary message, skipping or repeating steps, timing out.
 \end{enumerate}
@@
 
-\item
-  Agree: the customer agrees with the action and therefore does not start a dispute.
-\item
-  Start a dispute: the customer does not agree with the action and therefore starts a dispute.
+\item Agree: the customer agrees with the action and therefore does not start a dispute.
+\item Start a dispute: the customer disagrees with the action and therefore starts a dispute.
 \end{enumerate}
 
-As a result, in our analysis we have to consider four different outcomes for each party of the protocol:
+As a result, in our analysis, we have to consider four different outcomes for each party of the protocol:
 
@@
 
-The protocol terminates after the last step, after starting a dispute, or after a party hasn't completed its designated action in time.
+The protocol terminates after the last step, after starting a dispute, or after a party has not completed its designated action in time.
 Therefore, all positions except $\sigma_\mathrm{n}$ are termination positions.
 
-Because the customer is anonymous the SP can not start a dispute---there is no means to identify the customer.
-To mitigate the issue, we designed the protocol so that the SP who follows the protocol is always in an advantageous position, therefore he has no reason to start a dispute.
-The customer on the other hand can start a dispute at any time of the protocol, but only the actual misbehavior of the SP makes him win the case.
+Because the customer is anonymous, the SP can not start a dispute—there is no means to identify the customer.
+To mitigate the issue, we designed the protocol so that the SP who follows the protocol is always in an advantaged position, and therefore he has no reason to start a dispute.
+On the other hand, the customer can start a dispute at any time of the protocol, but only the actual misbehaviour of the SP makes him win the case.
 
@@
 \item
-  Both parties, by completing a transaction, end up in advantaged positions (+). In other words, they have intrinsic motivation to initialize and complete the transaction.
-\item
-  We assume the steps of the protocol to be atomic, there are no intermediate steps.
+  By completing a transaction, both parties end up in advantaged positions (+). In other words, they have intrinsic motivation to initialize and complete the transaction.
+\item
+  We assume the protocol steps to be atomic—there are no intermediate steps.
 \item
@@
 For example, paying for the invoice twice does not cause any effect on the curse of the protocol.
-\item
-  Once published, the result is available to the customer in the content storage. The idea of guaranteeing it cryptographically is discussed in Section~\ref{sec:future-work}.
-
-\item
-  The protocol can go only forward, there is no way of reverting any action.
-\item
-  Losing the dispute leads to a punishment that is greater than any reward, which leads to a disadvantaged position (-). Hence, the rational customer won't start a dispute that he is not sure to win.
+\item Once published, the result is available to the customer on the storage network. The idea of guaranteeing it cryptographically is discussed in Section~\ref{sec:future-work}.
+
+\item The protocol can go only forward—there is no way of reverting any action.
+\item
+  Losing the dispute leads to a punishment greater than any reward, leading to a disadvantaged position (-). Hence, the rational customer will not start a dispute that he is unsure of winning.
 \item
@@
   Both the customer and the SP are rational (selfish).
-They always prefer to go from worst position to better position, but also risk temporary worst position in favor of a later better position iff it's assured that they won't be stuck in the worst position.
+They always prefer to go from the worst position to a better position, but also risk a temporary worst position in favour of a later better position if and only if it is assured that they will not be stuck in the worst position.
 \end{itemize}
@@
     materials but has not paid anything, so we assume he is in neutral
-    position. One would argue that the customer has put effort of
-    delivering the materials to the SP, or that the sample is valuable.
-    We assume that the sample without personal information is useless
-    and the effort to deliver the package is negligible.
-  \item
-    \(\sigma_{1, s, \mathrm{n}} = \sbullet\), the SP is in the neutral position as he didn't put any effort to hence the package, also the package hasn't any value to the SP.
+    position. One would argue that the customer has put effort into
+    delivering the materials to the SP or that the sample is valuable.
+    We assume that the sample without personal information is useless, and the effort to deliver the package is negligible.
+  \item
+    \(\sigma_{1, s, \mathrm{n}} = \sbullet\), the SP is in the neutral position as he did not put any effort also the package has not brought any value to the SP.
   \end{itemize}
@@
   \item
-    \(\sigma_{1, c, \mathrm{d}} = -\), the customer loses the case as the SP has still an opportunity to publish proof-of-provision within the timeframe.
+    \(\sigma_{1, c, \mathrm{d}} = -\), the customer loses the case as the SP has still an opportunity to publish proof of provision within the timeframe.
   \item
@@
 
-Customer has paid the invoice:
+The customer has paid the invoice:
 
@@
   \item
-    \(\sigma_{2, c, \mathrm{n}} = -\), the customer has spent his funds but hasn't received the result.
-  \item
-    \(\sigma_{2, s, \mathrm{n}} = +\), the SP has received the payment but hasn't spent his resources yet.
+    \(\sigma_{2, c, \mathrm{n}} = -\), the customer has spent his funds but has not received the result.
+  \item
+    \(\sigma_{2, s, \mathrm{n}} = +\), the SP has received the payment but has not spent his resources yet.
   \end{itemize}
@@
   \item
-    \(\sigma_{2, c, \mathrm{d}} = -\), the customer loses the case as the SP has still an opportunity to publish proof-of-provision before the deadline.
+    \(\sigma_{2, c, \mathrm{d}} = -\), the customer loses the case as the SP has still an opportunity to publish proof of provision before the deadline.
   \item
@@
 
-Customer has timeouted, then:
+The customer has timeouted, then:
 
@@
   \item
-    \(\sigma_{4, c, \overline{\mathrm{d}}} = •\), the customer wins the
+    \(\sigma_{4, c, \overline{\mathrm{d}}} = \sbullet\), the customer wins the
     case and end up in neutral position.
@@
   \item
-    \(\sigma_{5, c, \overline{\mathrm{d}}} = •\) the customer wins the
+    \(\sigma_{5, c, \overline{\mathrm{d}}} = \sbullet\) the customer wins the
     case and end up in a neutral position.
@@
   in non-disadvantaged position
-  \(\sigma_{5, c, \overline{\mathrm{d}}} = •\).
+  \(\sigma_{5, c, \overline{\mathrm{d}}} = \sbullet\).
 \item
@@
   \item
-    \(\sigma_{6, c, \overline{\mathrm{d}}} = •\) the customer wins the
+    \(\sigma_{6, c, \overline{\mathrm{d}}} = \sbullet\) the customer wins the
     case and end up in a neutral position.
@@
   \item
-    \(\sigma_{7, c, \overline{\mathrm{d}}} = •\) the customer wins the case and ends up in a neutral position.
+    \(\sigma_{7, c, \overline{\mathrm{d}}} = \sbullet\) the customer wins the case and ends up in a neutral position.
   \item
@@
 \item
-  The customer can follow the protocol to the non-disadvantaged termination position \(\sigma_{7, c, \mathrm{n}} = +\), or in case the SP hasn't followed the protocol start a dispute and win the case \(\sigma_{7, c, \overline{\mathrm{d}}} = •\).
+  The customer can follow the protocol to the non-disadvantaged termination position \(\sigma_{7, c, \mathrm{n}} = +\), or in case the SP hasn't followed the protocol start a dispute and win the case \(\sigma_{7, c, \overline{\mathrm{d}}} = \sbullet\).
 \item
@@
 Currently, the SP has to publish the result into a peer-to-peer content-addressable storage network, e.g., IPFS.
-The problem is that nothing prevents the SP from publishing the result, receiving the cid, publishing $\mathrm{PoP}$, and immediately after removing the result from the local storage.
+The problem is that nothing prevents the SP from publishing the result, receiving the $\mathrm{cid}$, publishing $\mathrm{PoP}$, and immediately after removing the result from the local storage.
 In case of dispute, the SP can upload the content again, proving its availability.
@@
 \section{Conclusions}\label{sec:conclusion}
-In this paper, we have proposed anonymity-preserving blockchain-based protocol for services provision.
+In this paper, we have proposed protocol for services provision that simultaneously achieves anonymity, fairness, dispute resolution, TTP-less, and support physical materials.
 The protocol can be employed to provide services without collecting any personal information.
 The payment is handled by anonymous cryptocurrencies.
-Proof of delivery and proof of provision are published on the message board blockchain.
-The result is published on a content-addressable p2p network.
-The dispute can be settled by disclosing proof to justice.
+The protocol achieves fairness by the proof of delivery, payment attestation, and proof of provision published on the message board blockchain.
+The result of the service is published on a content-addressable p2p network.
+The dispute can be settled by disclosing the collected proofs to justice.
 Using the definition~\ref{fairness} we showed that the protocol achieves fairness.
@@
 
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{a1.jpg}}]{Stanis\l{}aw Bara{\'n}ski} received BEng in 2019 and MSc in 2020 in informatics at Gdańsk University of Technology.
+Currently, he is pursuing PhD degree at the Department of Computer Architecture, Faculty of Electronics, Telecommunications and Informatics, Gdansk University of Technology.
+He has published as the first author and presented his work on internet voting via Stellar blockchain and mitigation of content poisoning attacks via blockchain.
+
+His research interests include internet voting, information-centric networking, distributed systems, blockchain, and cryptography.
+
+He likes to develop his ideas right up to the commercialization stage.
+
+\end{IEEEbiography}
+
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{js access.jpg}}]{JULIAN SZYMA{\'N}SKI}  received the PhD degree in 2009 and DSc in 2020 at Gdańsk University of Technology.
+He is currently with the Department of Computer
+Architecture, Faculty of Electronics, Telecommunications and Informatics, Gdansk University of
+Technology. He addresses the problems of knowledge representation, methods of lexical knowledge acquisition, and linguistic data utilization.
+His research results find applications in
+web search engines and systems of automated text
+categorization. He manages research projects for
+processing the information in Wikipedia, where the main goal is to extract and
+structuralize textual knowledge and construct interfaces capable of communicating in natural language. Besides his research in information retrieval
+domain, he was involved in projects related to cognitive science. His mainstream of this research is building semantic memory models that improve
+natural language processing. He also worked on analyzing
+human emotions, by mining EEG signals. His results are implemented in
+the form of brain-machine interfaces for disabled people. He also works
+on analyzing data within the IoT domain and its secure storage on the blockchain. 
+He is involved in project, where acquisition of data from sensors placed in beehives 
+allows one to predict apiary
+development and detect abnormalities.
+
+He was a committee member and reviewer in  many international
+conferences as well as served as guest editor preparing special issues of prestigious journals.
+
+\end{IEEEbiography}
+
 \end{document}

### 2022-03-08 access.tex
update protocol description

@@
 
-The customer has timeouted, then:
+The customer has acted abnormally, then:
 
@@
 
-The SP has done the provision of service:
+The SP has made the provision of service:
 
@@
 
-SP has timeouted, then:
+The SP has acted abnormally, then:
 
@@
 
-SP has uploaded the result on time:
+The SP has uploaded the result on time:
 
@@
 
-SP has uploaded the result on time, then:
+The SP has uploaded the result on time, then:
 
@@
 
-Customer has timeouted, then:
+The customer has acted abnormally, then:
 
@@
 
-SP has published the \textbf{correct} result on time:
+The SP has published the correct result on time:
 
@@
 
-SP has published the \textbf{incorrect} result on time:
+The customer has acted abnormally, then:
 
@@
 
-The diagram below shows the path of positions when SP tries to misbehave and doesn't execute service after receiving the payment.
-The protocol ends up neutral to customer and disadvantaged to SP positions.
+The diagram below shows the path of positions when the SP tries to misbehave and does not execute service after receiving the payment.
+The protocol ends up neutral to the customer and disadvantaged to the SP positions.
 
@@
 
-Justice is the one biggest obstacle in achieving a system that complies with Web3 postulates~\cite{Web3Wiki71}.
-
-The possible directions for mitigation of such issues are to either (1) replace justice with decentralized autonomous organizations (DAO) like proposed in Themis~\cite{meng2019themis} or Kleros~\cite{lesaege2018kleros}; or (2) make it infeasible to provide incorrect result.
-
-The first approach is more feasible shortly.
-It would require creating a large pool of experts in a field, that in case of dispute, would receive all the proofs ($\mathrm{PoD}$, $\mathrm{PoP}$, as well as any other proofs significant to the case) that could be queried by the experts in zero-knowledge fashion, i.e., they could ask a limited number of questions to the proofs and getting yes/no answers.
-Keeping the case fully confidential.
+Justice is the biggest obstacle in achieving a system that complies with Web3 postulates~\cite{Web3Wiki71}.
+
+The possible directions for mitigation of such issues are to either (1) replace justice with decentralized autonomous organizations (DAO) like proposed in Themis~\cite{meng2019themis} or Kleros~\cite{lesaege2018kleros}; or (2) make it infeasible to provide incorrect results.
+
+The first approach is more feasible in the near future.
+It would require creating a large pool of experts in a field that, in case of dispute, would receive all the proofs ($\mathrm{PoD}$, $\mathrm{PoP}$, as well as any other proofs significant to the case) that could be queried by the experts in zero-knowledge fashion, i.e., they could ask a limited number of questions to the proofs and getting yes/no answers.
+The case would be fully confidential as they would not be able to query personal information.
 The experts would be incentivized to participate in the pool by the system of fees.
-Their honest behavior would be incentivized by the stake they would have to lock, and punishment they would get by judging incorrectly, where the ``correctly'' is determined by the quorum of votes.
+They would be incentivized to vote honesty by the stake they would have to lock and reward/punishment they would get by judging correctly/incorrectly, where the ``correctly'' is determined by the quorum of votes.
 
@@
 Then, it would be possible by employing proofs of correctness of computations~\cite{ben2013snarks} to enforce that only correct computations (hence correct services) are accepted.
-To do so the whole service examination would have to be computable, which is hard to achieve in settings where physical materials (like blood) are examined.
-Concretely, the problem canes down to ``How to digitally represent blood?''.
-If we could represent urine, blood, saliva, or any other physical material in binary format, and let the customer take a sample, discrete it, and send it to the SP by himself, then the whole chain of integrity could be ensured.
+It would require the complete service examination to be computable, which is hard to achieve in settings where physical materials (like blood) are examined.
+Concretely, the problem canes down to ``How to represent blood digitally?''.
+If we could represent urine, blood, saliva, or any other physical material in a binary format and let the customer take a sample, discrete it, and send it to the SP by himself, then the whole chain of integrity could be ensured.
 Therefore, wrong service provision would be infeasible.
@@
 In case of dispute, the SP can upload the content again, proving its availability.
-The SP has no motivation to proceed with this kind of misbehavior, other than putting the customer in a disadvantaged position caused by the lost dispute.
-We see possible prevention of this misbehavior by the usage of Filecoin---an incentive layer on top of IPFS that guarantees the content availability via economic incentivisations~\cite{benetfilecoin}.
-With the help of Filecoin, the SP would be obligated to create a deal that guarantees the result availability until the deadline of the transaction.
+The SP has no motivation to proceed with this kind of misbehaviour other than putting the customer in a disadvantaged position caused by the lost dispute.
+We see possible prevention of this misbehaviour by the usage of Filecoin—an incentive layer on top of IPFS that guarantees the content availability via economic incentivisations~\cite{benetfilecoin}.
+With the help of Filecoin, the SP would be obligated to create a deal that guarantees the availability of the result until the deadline of the transaction.
 Moreover, since Filecoin is a blockchain by itself, it could play both roles of message board and storage network.
@@
 \section{Conclusions}\label{sec:conclusion}
-In this paper, we have proposed protocol for services provision that simultaneously achieves anonymity, fairness, dispute resolution, TTP-less, and support physical materials.
+In this paper, we have proposed the protocol for services provision that simultaneously achieves anonymity, fairness, dispute resolution, TTP-less, and support physical materials.
 The protocol can be employed to provide services without collecting any personal information.
@@
 The protocol achieves fairness by the proof of delivery, payment attestation, and proof of provision published on the message board blockchain.
-The result of the service is published on a content-addressable p2p network.
+The result of the service is published on a content-addressable p2p network like IPFS.
 The dispute can be settled by disclosing the collected proofs to justice.

### 2022-03-08 access.tex
update bio

@@
 \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{a1.jpg}}]{Stanis\l{}aw Bara{\'n}ski} received BEng in 2019 and MSc in 2020 in informatics at Gdańsk University of Technology.
-Currently, he is pursuing PhD degree at the Department of Computer Architecture, Faculty of Electronics, Telecommunications and Informatics, Gdansk University of Technology.
-He has published as the first author and presented his work on internet voting via Stellar blockchain and mitigation of content poisoning attacks via blockchain.
-
-His research interests include internet voting, information-centric networking, distributed systems, blockchain, and cryptography.
+Currently, he is a PhD candidate at the Department of Computer Architecture, Faculty of Electronics, Telecommunications and Informatics, Gdansk University of Technology.
+
+His research interests include blockchains and cryptography, especially the issue of blockchain-based internet voting and mitigation of content poisoning attacks via blockchain.
 

### 2022-03-08 access.tex
update conclusions

@@
 \section{Conclusions}\label{sec:conclusion}
-In this paper, we have proposed the protocol for services provision that simultaneously achieves anonymity, fairness, dispute resolution, TTP-less, and support physical materials.
+In this paper, we have proposed the protocol for service provision that simultaneously achieves anonymity, fairness, dispute resolution, TTP-less, and support physical materials.
 The protocol can be employed to provide services without collecting any personal information.
-The payment is handled by anonymous cryptocurrencies.
-The protocol achieves fairness by the proof of delivery, payment attestation, and proof of provision published on the message board blockchain.
+Payments are handled by anonymous cryptocurrencies.
 The result of the service is published on a content-addressable p2p network like IPFS.
 The dispute can be settled by disclosing the collected proofs to justice.
-Using the definition~\ref{fairness} we showed that the protocol achieves fairness.
+Using the definition~\ref{fairness} we showed that the protocol achieves fairness by the proof of delivery, payment attestation, and proof of provision published on the message board blockchain.
 Finally, we pinpointed further improvements like decentralized dispute resolution, provable availability of the result, paying with cash, and anonymous delivery via courier.
@@
 He likes to develop his ideas right up to the commercialization stage.
-
+He is the author of multiple mobile and web applications that have reached success on the market.
+His blockchain-based internet voting project has been funded by the Stellar Community Fund for the most useful Stellar application.
 \end{IEEEbiography}

### 2022-03-08 access.tex
small fixes to paper

@@
 
-Customer has delivered the package:
+The customer has delivered the package:
 
@@
   \item
-    \(\sigma_{1, c, \mathrm{n}} = \sbullet\), the customer has risked its
-    materials but has not paid anything, so we assume he is in neutral
-    position. One would argue that the customer has put effort into
-    delivering the materials to the SP or that the sample is valuable.
+    \(\sigma_{1, c, \mathrm{n}} = \sbullet\), the customer has risked its materials but has not paid anything, so we assume he is in a neutral position.
+One would argue that the customer has put effort into delivering the materials to the SP or that the sample is valuable.
 We assume that the sample without personal information is useless, and the effort to deliver the package is negligible.
@@
 \item
-  The customer can follow the protocol and move to a non-disadvantaged
-  position \(\sigma_{1, c, \mathrm{n}} = \sbullet\).
-\item
-  The SP can do nothing and end up in a non-disadvantaged position
-  \(\sigma_{1, s, \mathrm{n}} = \sbullet \) or
-  \(\sigma_{1, s, \mathrm{d}} = \sbullet \).
+  The customer can follow the protocol and move to a non-disadvantaged position \(\sigma_{1, c, \mathrm{n}} = \sbullet\).
+\item
+  The SP can do nothing and end up in a non-disadvantaged position \(\sigma_{1, s, \mathrm{n}} = \sbullet \) or \(\sigma_{1, s, \mathrm{d}} = \sbullet \).
 \end{itemize}
@@
 He is currently with the Department of Computer
-Architecture, Faculty of Electronics, Telecommunications and Informatics, Gdansk University of
-Technology. He addresses the problems of knowledge representation, methods of lexical knowledge acquisition, and linguistic data utilization.
-His research results find applications in
-web search engines and systems of automated text
-categorization. He manages research projects for
-processing the information in Wikipedia, where the main goal is to extract and
-structuralize textual knowledge and construct interfaces capable of communicating in natural language. Besides his research in information retrieval
-domain, he was involved in projects related to cognitive science. His mainstream of this research is building semantic memory models that improve
-natural language processing. He also worked on analyzing
+Architecture, Faculty of Electronics, Telecommunications and Informatics, Gdansk University of Technology.
+He addresses the problems of knowledge representation, methods of lexical knowledge acquisition, and linguistic data utilization.
+His research results find applications in web search engines and systems of automated text categorization.
+He manages research projects for processing the information in Wikipedia, where the main goal is to extract and structuralize textual knowledge and construct interfaces capable of communicating in natural language.
+Besides his research in information retrieval domain, he was involved in projects related to cognitive science.
+His mainstream of this research is building semantic memory models that improve natural language processing.
+He also worked on analyzing
 human emotions, by mining EEG signals. His results are implemented in
@@
 on analyzing data within the IoT domain and its secure storage on the blockchain. 
-He is involved in project, where acquisition of data from sensors placed in beehives 
-allows one to predict apiary
-development and detect abnormalities.
+He is involved in project, where acquisition of data from sensors placed in beehives  allows one to predict apiary development and detect abnormalities.
 

### 2022-03-08 access.tex
update steps names

@@
 \noindent \textbf
-{Step 5. Proof of provision publication}\label{step-5-proof-of-provision-publication}
+{Step 5. Proof of provision}\label{step-5-proof-of-provision-publication}
 
@@
 \noindent \textbf
-{Step 6. Proof-of-provision notification}\label{step-6-proof-of-provision-notification}
+{Step 6. Pull proof of provision}\label{step-6-proof-of-provision-notification}
 
@@
 
-Figure~\ref{fig:positions} 
-shows the positions of each party after each possible action taken.
+Figure~\ref{fig:positions} shows the positions of each party after each possible action taken.
 
@@
 \noindent \textbf
-{Step 1. Customer turn: deliver package}\label{step-1-deliver-package}
+{Step 1. Customer turn: package delivery}\label{step-1-deliver-package}
 
@@
   \item
-    \(\sigma_{1, s, \mathrm{n}} = \sbullet\), the SP is in the neutral position as he did not put any effort also the package has not brought any value to the SP.
+    \(\sigma_{1, s, \mathrm{n}} = \sbullet\), the SP is in a neutral position as he did not put any effort, and the package has not brought any value to the SP.
   \end{itemize}
@@
 \noindent \textbf
-{Step 2. Customer turn: pay for invoice}\label{step-2-pay-for-invoice}
+{Step 2. Customer turn: payment}\label{step-2-pay-for-invoice}
 
@@
 \noindent \textbf
-{Step 5. SP turn: publication of proof-of-provision}\label{step-5-publication-of-proof-of-provision}
+{Step 5. SP turn: Proof of provision}\label{step-5-publication-of-proof-of-provision}
 
@@
 \noindent \textbf
-{Step 7. Customer turn: result download}\label{step-7-retrieval-of-results}
+{Step 7. Customer turn: download result}\label{step-7-retrieval-of-results}
 

### 2022-03-08 access.tex
update analysis

@@
   \item
-    \(\sigma_{1, c, \mathrm{n}} = \sbullet\), the customer has risked its materials but has not paid anything, so we assume he is in a neutral position.
+    \(\sigma_{1, c, \mathrm{n}} = \sbullet\), the customer has risked its materials but has not paid anything, so we assume he is in the neutral position.
 One would argue that the customer has put effort into delivering the materials to the SP or that the sample is valuable.
@@
 \item
-  The customer can follow the protocol and move to a non-disadvantaged position \(\sigma_{1, c, \mathrm{n}} = \sbullet\).
-\item
-  The SP can do nothing and end up in a non-disadvantaged position \(\sigma_{1, s, \mathrm{n}} = \sbullet \) or \(\sigma_{1, s, \mathrm{d}} = \sbullet \).
+  The customer can follow the protocol and move to the non-disadvantaged position \(\sigma_{1, c, \mathrm{n}} = \sbullet\).
+\item
+  The SP can do nothing and end up in the non-disadvantaged position \(\sigma_{1, s, \mathrm{n}} = \sbullet \) or \(\sigma_{1, s, \mathrm{d}} = \sbullet \).
 \end{itemize}
@@
   \item
-    \(\sigma_{2, c, \overline{\mathrm{n}}} = \sbullet\), the customer ends up in a neutral position, since he didn't spend his funds.
-  \item
-    \(\sigma_{2, s, \overline{\mathrm{n}}} = \sbullet\), the SP ends up in a neutral position as he didn't receive the payment, nor spent his resources.
+    \(\sigma_{2, c, \overline{\mathrm{n}}} = \sbullet\), the customer ends up in the neutral position as he did not spend his funds.
+  \item
+    \(\sigma_{2, s, \overline{\mathrm{n}}} = \sbullet\), the SP ends up in a neutral position as he did not receive the payment, nor spent his resources.
   \end{itemize}
@@
 \item
-  The customer can move the protocol forward to step 3, where if the
-  SP follows the protocol then the customer can push the protocol forward
-  up to the last termination step \(\sigma_{7, c, \mathrm{n}} = +\),
-  otherwise if at any step the SP does not follow the protocol the
-  customer can start a dispute which terminates the protocol at
-  non-disadvantaged position, i.e.,
-  \(\sigma_{3, c, \overline{\mathrm{d}}} = \sbullet\),
-  \(\sigma_{4, c, \overline{\mathrm{d}}} = \sbullet\),
+  The customer can move the protocol forward to step 3, where if the SP follows the protocol then the customer can push the protocol forward up to the last termination step \(\sigma_{7, c, \mathrm{n}} = +\), otherwise if at any step the SP does not follow the protocol the customer can start a dispute which terminates the protocol at the non-disadvantaged position, i.e., \(\sigma_{3, c, \overline{\mathrm{d}}} = \sbullet\), \(\sigma_{4, c, \overline{\mathrm{d}}} = \sbullet\), \(\sigma_{5, c, \overline{\mathrm{d}}} = \sbullet\).
+\item
+  The SP can do nothing and end up in the non-disadvantaged position \(\sigma_{2, s, \mathrm{n}} = +\), \(\sigma_{2, s, \mathrm{d}} = +\), \(\sigma_{2, s, \overline{\mathrm{n}}} = \sbullet\), \(\sigma_{2, s, \overline{\mathrm{d}}} = \sbullet\).
+\end{itemize}
+
+\noindent \textbf
+{Step 3. SP turn: provision of service}\label{step-3-provision-of-service}
+
+The SP has made the provision of service:
+
+\begin{itemize}
+\item
+  Following protocol:
+
+  \begin{itemize}
+
+  \item
+    \(\sigma_{3, c, \mathrm{n}} = -\), the customer has not received the result, so he remains in the disadvantaged position. 
+  \item
+    \(\sigma_{3, s, \mathrm{n}} = +\), the SP has fulfilled the contract on time.
+  \end{itemize}
+\item
+  Starting a dispute:
+
+  \begin{itemize}
+
+  \item
+    \(\sigma_{3, c, \mathrm{d}} = -\), the customer loses the case as the SP has still the opportunity to publish proof of provision within the timeframe. 
+  \item
+    \(\sigma_{3, s, \mathrm{d}} = +\), the SP win the case for the same reason.
+  \end{itemize}
+\end{itemize}
+
+The SP has acted abnormally, then:
+
+\begin{itemize}
+\item
+  Following protocol:
+
+  \begin{itemize}
+
+  \item
+    \(\sigma_{3, c, \overline{\mathrm{n}}} = -\), the customer ends up in a disadvantaged position.
+  \item
+    \(\sigma_{3, s, \overline{\mathrm{n}}} = +\), the SP ends up in the advantaged position as he received the payment. 
+  \end{itemize}
+\item
+  Starting a dispute:
+
+  \begin{itemize}
+
+  \item
+    \(\sigma_{3, c, \overline{\mathrm{d}}} = •\), the customer wins the case and ends up in the neutral position.
+  \item
+    \(\sigma_{3, s, \overline{\mathrm{d}}} = -\), the SP loses the case and ends up in the disadvantaged position. 
+  \end{itemize}
+\end{itemize}
+
+Fairness:
+
+\begin{itemize}
+
+\item
+  The customer can do nothing if the SP follows the protocol, which will ultimately put him in the advantaged position \(\sigma_{7, c, \mathrm{n}} = +\), or in case of the SP not following the protocol, the customer can start a dispute and terminate in the non-disadvantaged position \(\sigma_{3, c, \overline{\mathrm{d}}} = •\).
+\item
+  The SP can follow the protocol and move to the non-disadvantaged position \(\sigma_{3, s, \mathrm{n}} = +\), or not follow the protocol and also end up at the non-disadvantaged position \(\sigma_{3, s, \overline{\mathrm{n}}} = +\), but the second option puts him at risk of terminating the protocol at \(\sigma_{3, s, \overline{\mathrm{n}}} = +\), if the customer is rational and starts a dispute.
+\end{itemize}
+
+\noindent \textbf
+{Step 4. SP turn: upload result}\label{step-4-publication-of-results}
+
+The SP has uploaded the result on time:
+
+\begin{itemize}
+\item
+  Following protocol:
+
+  \begin{itemize}
+
+  \item
+    \(\sigma_{4, c, \mathrm{n}} = -\), the customer has not received the result, so he remains in the disadvantaged position. 
+  \item
+    \(\sigma_{4, s, \mathrm{n}} = +\), the SP has fulfilled the contract on time.
+  \end{itemize}
+\item
+  Starting a dispute:
+
+  \begin{itemize}
+
+  \item
+    \(\sigma_{4, c, \mathrm{d}} = -\), the customer loses the case as the SP has still an opportunity to publish proof of provision within the timeframe. 
+  \item
+    \(\sigma_{4, s, \mathrm{d}} = +\), the SP win the case for the same reason.
+  \end{itemize}
+\end{itemize}
+
+The SP has acted abnormally, then:
+
+\begin{itemize}
+\item
+  Following protocol:
+
+  \begin{itemize}
+
+  \item
+    \(\sigma_{4, c, \overline{\mathrm{n}}} = -\), the customer ends up in the disadvantaged position. 
+  \item
+    \(\sigma_{4, s, \overline{\mathrm{n}}} = +\), the SP ends up in the advantaged position as he received the payment. 
+  \end{itemize}
+\item
+  Starting a dispute:
+
+  \begin{itemize}
+
+  \item
+    \(\sigma_{4, c, \overline{\mathrm{d}}} = \sbullet\), the customer wins the case and ends up in a neutral position. 
+  \item
+    \(\sigma_{4, s, \overline{\mathrm{d}}} = -\), the SP loses the case and ends up in the disadvantaged position. 
+  \end{itemize}
+\end{itemize}
+
+Fairness:
+
+\begin{itemize}
+
+\item
+  The customer can do nothing if the SP follows the protocol, which will ultimately put him in an advantaged position \(\sigma_{7, c, \mathrm{n}} = +\), or in case of the SP not following the protocol, the customer can start a dispute and terminate in the non-disadvantaged position \(\sigma_{4, c, \overline{\mathrm{d}}} = \sbullet\).
+\item
+  The SP can follow the protocol and move to the non-disadvantaged position \(\sigma_{4, s, \mathrm{n}} = +\), or not follow the protocol and also end up at the non-disadvantaged position \(\sigma_{4, s, \overline{\mathrm{n}}} = +\), but the second option puts him at risk of terminating the protocol at \(\sigma_{4, s, \overline{\mathrm{n}}} = +\), if the customer is rational and starts a dispute.
+\end{itemize}
+
+\noindent \textbf
+{Step 5. SP turn: proof of provision}\label{step-5-publication-of-proof-of-provision}
+
+The SP has published proof of provision on time:
+
+\begin{itemize}
+\item
+  Following protocol:
+
+  \begin{itemize}
+
+  \item
+    \(\sigma_{5, c, \mathrm{n}} = -\), the customer has not received the result. Therefore, he remains in the disadvantaged position. 
+  \item
+    \(\sigma_{5, s, \mathrm{n}} = +\), the SP has fulfilled the contract on time.
+  \end{itemize}
+\item
+  Starting a dispute:
+
+  \begin{itemize}
+
+  \item
+    \(\sigma_{5, c, \mathrm{d}} = -\), the customer loses the case as the SP can prove the publication of proof of provision. 
+  \item
+    \(\sigma_{5, s, \mathrm{d}} = +\), the SP win the case for the same reason.
+  \end{itemize}
+\end{itemize}
+
+The SP has acted abnormally, then:
+
+\begin{itemize}
+\item
+  Following protocol:
+
+  \begin{itemize}
+
+  \item
+    \(\sigma_{5, c, \overline{\mathrm{n}}} = -\), the customer ends up in the disadvantaged position.
+  \item
+    \(\sigma_{5, s, \overline{\mathrm{n}}} = +\), the SP ends up in the advantaged position as he received the payment.
+  \end{itemize}
+\item
+  Starting a dispute:
+
+  \begin{itemize}
+
+  \item
+    \(\sigma_{5, c, \overline{\mathrm{d}}} = \sbullet\), the customer wins the case and ends up in the neutral position. 
+  \item
+    \(\sigma_{5, s, \overline{\mathrm{d}}} = -\), the SP loses the case and ends up in the disadvantaged position. 
+  \end{itemize}
+\end{itemize}
+
+Fairness:
+
+\begin{itemize}
+
+\item
+  The customer can do nothing if the SP follows the protocol because it will ultimately put him in the advantaged position \(\sigma_{7, c, \mathrm{n}} = +\); otherwise, in case of the SP not following the protocol, the customer can start a dispute and terminate in the non-disadvantaged position.
   \(\sigma_{5, c, \overline{\mathrm{d}}} = \sbullet\).
 \item
-  The SP can do nothing and end up in non-disadvantaged position
-  \(\sigma_{2, s, \mathrm{n}} = +\), \(\sigma_{2, s, \mathrm{d}} = +\),
-  \(\sigma_{2, s, \overline{\mathrm{n}}} = \sbullet\),
-  \(\sigma_{2, s, \overline{\mathrm{d}}} = \sbullet\).
-\end{itemize}
-
-\noindent \textbf
-{Step 3. SP turn: provision of service}\label{step-3-provision-of-service}
-
-The SP has made the provision of service:
+  The SP can follow the protocol and move to the non-disadvantaged position \(\sigma_{5, s, \mathrm{n}} = +\), or not follow the protocol and also end up at the non-disadvantaged position \(\sigma_{5, s, \overline{\mathrm{n}}} = +\), but the second option puts him at risk of terminating the protocol at \(\sigma_{5, s, \overline{\mathrm{n}}} = +\), if the customer is rational and starts a dispute.
+\end{itemize}
+
+\noindent \textbf
+{Step 6. customer turn: pull proof of provision}\label{step-6-pull-proof-of-provision}
+
+The SP has uploaded the result on time, then:
+
+\begin{itemize}
+\item
+  Follows the protocol:
+
+  \begin{itemize}
+
+  \item
+    \(\sigma_{6, c, \mathrm{n}} = -\), the customer gets a hash of the result but not the result yet.
+  \item
+    \(\sigma_{6, s, \mathrm{n}} = +\), the SP position has not changed.
+  \end{itemize}
+\item
+  Starts a dispute:
+
+  \begin{itemize}
+
+  \item
+    \(\sigma_{6, c, \mathrm{d}} = -\), the customer loses the case as the SP can prove the publication of proof of provision. 
+  \item
+    \(\sigma_{6, s, \mathrm{d}} = +\), the SP win the case for the same reason.
+  \end{itemize}
+\end{itemize}
+
+The customer has acted abnormally, then:
+
+\begin{itemize}
+\item
+  Follows the protocol:
+
+  \begin{itemize}
+
+  \item
+    \(\sigma_{6, c, \overline{\mathrm{n}}} = -\), the customer ends up in the disadvantaged position.
+  \item
+    \(\sigma_{6, s, \overline{\mathrm{n}}} = +\), the SP ends up in the advantaged position as he received the payment but did not spend his resources.
+  \end{itemize}
+\item
+  Starts a dispute:
+
+  \begin{itemize}
+
+  \item
+    \(\sigma_{6, c, \overline{\mathrm{d}}} = \sbullet\), the customer wins the case and ends up in the neutral position.
+  \item
+    \(\sigma_{6, s, \overline{\mathrm{d}}} = -\), the SP loses the case and ends up in the disadvantaged position.
+  \end{itemize}
+\end{itemize}
+
+Fairness:
+
+\begin{itemize}
+
+\item
+  The customer can follow the protocol to the position \(\sigma_{6, c, \mathrm{n}} = -\), which lets him move the protocol to the non-disadvantaged termination position \(\sigma_{7, c, \mathrm{n}} = +\), or in case the SP has not followed the protocol start a dispute and win the case \(\sigma_{6, c, \overline{\mathrm{d}}} = \sbullet\).
+\item
+  The SP can do nothing and end up in a non-disadvantaged position \(\sigma_{6, s, \mathrm{n}} = +\), or \(\sigma_{6, s, \overline{\mathrm{n}}} = +\).
+\end{itemize}
+
+\noindent \textbf
+{Step 7. Customer turn: download result}\label{step-7-retrieval-of-results}
+
+The SP has published the correct result on time:
 
@@
   \item
-    \(\sigma_{3, c, \mathrm{n}} = -\), the customer hasn't received the
-    result so he remains in a disadvantaged position.
-  \item
-    \(\sigma_{3, s, \mathrm{n}} = +\), the SP has fulfilled the contract
-    on time.
+    \(\sigma_{7, c, \mathrm{n}} = +\), the customer gets the correct result. Therefore, he moves to the advantaged position. 
+  \item
+    \(\sigma_{7, s, \mathrm{n}} = +\), the SP position has not changed. 
   \end{itemize}
@@
   \item
-    \(\sigma_{3, c, \mathrm{d}} = -\), the customer lose the case as the
-    SP has still the opportunity to publish proof-of-provision within
-    timeframe.
-  \item
-    \(\sigma_{3, s, \mathrm{d}} = +\), the SP win the case for the same
-    reason.
-  \end{itemize}
-\end{itemize}
-
-The SP has acted abnormally, then:
+    \(\sigma_{7, c, \mathrm{d}} = -\), the customer loses the case as the SP can prove the publication of proof of provision. 
+  \item
+    \(\sigma_{7, s, \mathrm{d}} = +\), the SP win the case for the same reason.
+  \end{itemize}
+\end{itemize}
+
+The customer has acted abnormally, then:
 
@@
   \item
-    \(\sigma_{3, c, \overline{\mathrm{n}}} = -\), the customer ends up in a disadvantaged position.
-  \item
-    \(\sigma_{3, s, \overline{\mathrm{n}}} = +\), the SP ends up in a
-    advantaged position as he received the payment.
+    \(\sigma_{7, c, \overline{\mathrm{n}}} = -\), the customer ends up in a disadvantaged position, as he ends up with the incorrect result.
+  \item
+    \(\sigma_{7, c, \overline{\mathrm{n}}} = +\), the SP ends up in the advantaged position as he received the payment but did not spend his resources.
   \end{itemize}
@@
   \item
-    \(\sigma_{3, c, \overline{\mathrm{d}}} = •\), the customer wins the case and ends up in a neutral position.
-  \item
-    \(\sigma_{3, s, \overline{\mathrm{d}}} = -\), the SP loses the case
-    and end up in a disadvantaged position.
+    \(\sigma_{7, c, \overline{\mathrm{d}}} = \sbullet\), the customer wins the case and ends up in the neutral position.
+  \item
+    \(\sigma_{7, c, \overline{\mathrm{d}}} = -\), the SP loses the case and ends up in the disadvantaged position.
   \end{itemize}
@@
 \item
-  The customer can do nothing if the SP follows the protocol, which will
-  ultimately put him in an advantaged position
-  \(\sigma_{7, c, \mathrm{n}} = +\), or in case of the SP not following
-  the protocol, the customer can start a dispute and terminate in a
-  non-disadvantaged position
-  \(\sigma_{3, c, \overline{\mathrm{d}}} = •\).
-\item
-  The SP can follow the protocol and move to a non-disadvantaged
-  position \(\sigma_{3, s, \mathrm{n}} = +\), or not follow the protocol
-  and also end up at a non-disadvantaged position
-  \(\sigma_{3, s, \overline{\mathrm{n}}} = +\), but the second option
-  puts him at risk of terminating the protocol at
-  \(\sigma_{3, s, \overline{\mathrm{n}}} = +\), if the customer is
-  rational and starts a dispute.
-\end{itemize}
-
-\noindent \textbf
-{Step 4. SP turn: upload result}\label{step-4-publication-of-results}
-
-The SP has uploaded the result on time:
-
-\begin{itemize}
-\item
-  Following protocol:
-
-  \begin{itemize}
-
-  \item
-    \(\sigma_{4, c, \mathrm{n}} = -\), the customer hasn't received the result so he remains in disadvantaged position.
-  \item
-    \(\sigma_{4, s, \mathrm{n}} = +\), the SP has fulfilled the contract on time.
-  \end{itemize}
-\item
-  Starting a dispute:
-
-  \begin{itemize}
-
-  \item
-    \(\sigma_{4, c, \mathrm{d}} = -\), the customer lose the case as the
-    SP has still opportunity to publish proof-of-provision within
-    timeframe.
-  \item
-    \(\sigma_{4, s, \mathrm{d}} = +\), the SP win the case for the same
-    reason.
-  \end{itemize}
-\end{itemize}
-
-The SP has acted abnormally, then:
-
-\begin{itemize}
-\item
-  Following protocol:
-
-  \begin{itemize}
-
-  \item
-    \(\sigma_{4, c, \overline{\mathrm{n}}} = -\), the customer ends up in
-    disadvantaged position.
-  \item
-    \(\sigma_{4, s, \overline{\mathrm{n}}} = +\), the SP ends up in
-    advantaged position as he received the payment.
-  \end{itemize}
-\item
-  Starting a dispute:
-
-  \begin{itemize}
-
-  \item
-    \(\sigma_{4, c, \overline{\mathrm{d}}} = \sbullet\), the customer wins the
-    case and end up in neutral position.
-  \item
-    \(\sigma_{4, s, \overline{\mathrm{d}}} = -\), the SP loses the case
-    and end up in a disadvantaged position.
-  \end{itemize}
-\end{itemize}
-
-Fairness:
-
-\begin{itemize}
-
-\item
-  The customer can do nothing if the SP follows the protocol, which will
-  ultimately put him in an advantaged position
-  \(\sigma_{7, c, \mathrm{n}} = +\), or in case of the SP not following
-  the protocol, the customer can start a dispute and terminate in
-  non-disadvantaged position
-  \(\sigma_{4, c, \overline{\mathrm{d}}} = \sbullet\).
-\item
-  The SP can follow the protocol and move to the non-disadvantaged
-  position \(\sigma_{4, s, \mathrm{n}} = +\), or not follow the protocol
-  and also end up at non-disadvantaged position
-  \(\sigma_{4, s, \overline{\mathrm{n}}} = +\), but the second option
-  puts him at risk of terminating the protocol at
-  \(\sigma_{4, s, \overline{\mathrm{n}}} = +\), if the customer is
-  rational and starts a dispute.
-\end{itemize}
-
-\noindent \textbf
-{Step 5. SP turn: Proof of provision}\label{step-5-publication-of-proof-of-provision}
-
-The SP has published proof of provision on time:
-
-\begin{itemize}
-\item
-  Following protocol:
-
-  \begin{itemize}
-
-  \item
-    \(\sigma_{5, c, \mathrm{n}} = -\) the customer hasn't received the
-    result. Therefore, he remains in a disadvantaged position.
-  \item
-    \(\sigma_{5, s, \mathrm{n}} = +\) the SP has fulfilled the contract
-    on time.
-  \end{itemize}
-\item
-  Starting a dispute:
-
-  \begin{itemize}
-
-  \item
-    \(\sigma_{5, c, \mathrm{d}} = -\) the customer lose the case as the
-    SP can prove the publication of proof-of-provision.
-  \item
-    \(\sigma_{5, s, \mathrm{d}} = +\) the SP win the case as the SP can
-    prove the publication of proof-of-provision.
-  \end{itemize}
-\end{itemize}
-
-The SP has acted abnormally, then:
-
-\begin{itemize}
-\item
-  Following protocol:
-
-  \begin{itemize}
-
-  \item
-    \(\sigma_{5, c, \overline{\mathrm{n}}} = -\) the customer ends up in a disadvantaged position.
-  \item
-    \(\sigma_{5, s, \overline{\mathrm{n}}} = +\) the SP ends up in
-    an advantaged position as he received the payment.
-  \end{itemize}
-\item
-  Starting a dispute:
-
-  \begin{itemize}
-
-  \item
-    \(\sigma_{5, c, \overline{\mathrm{d}}} = \sbullet\) the customer wins the
-    case and end up in a neutral position.
-  \item
-    \(\sigma_{5, s, \overline{\mathrm{d}}} = -\) the SP loses the case
-    and end up in a disadvantaged position.
-  \end{itemize}
-\end{itemize}
-
-Fairness:
-
-\begin{itemize}
-
-\item
-  The customer can do nothing if the SP follows the protocol because it
-  will ultimately put him in an advantaged position
-  \(\sigma_{7, c, \mathrm{n}} = +\), otherwise, in case of the SP not
-  following the protocol, the customer can start a dispute and terminate
-  in non-disadvantaged position
-  \(\sigma_{5, c, \overline{\mathrm{d}}} = \sbullet\).
-\item
-  The SP can follow the protocol and move to the non-disadvantaged
-  position \(\sigma_{5, s, \mathrm{n}} = +\), or not follow the protocol
-  and also end up at non-disadvantaged position
-  \(\sigma_{5, s, \overline{\mathrm{n}}} = +\), but the second option
-  puts him at risk of terminating the protocol at
-  \(\sigma_{5, s, \overline{\mathrm{n}}} = +\), if the customer is
-  rational and starts a dispute.
-\end{itemize}
-
-\noindent \textbf
-{Step 6. customer turn: pull proof of provision}\label{step-6-pull-proof-of-provision}
-
-The SP has uploaded the result on time, then:
-
-\begin{itemize}
-\item
-  Follows the protocol:
-
-  \begin{itemize}
-
-  \item
-    \(\sigma_{6, c, \mathrm{n}} = -\) the customer gets hash of the
-    result but not the result yet.
-  \item
-    \(\sigma_{6, s, \mathrm{n}} = +\) the SP position hasn't changed.
-  \end{itemize}
-\item
-  Starts a dispute:
-
-  \begin{itemize}
-
-  \item
-    \(\sigma_{6, c, \mathrm{d}} = -\) the customer lose the case as the
-    SP can prove the publication of proof-of-provision.
-  \item
-    \(\sigma_{6, s, \mathrm{d}} = +\) the SP win the case as the SP can
-    prove the publication of proof-of-provision.
-  \end{itemize}
-\end{itemize}
-
-The customer has acted abnormally, then:
-
-\begin{itemize}
-\item
-  Follows the protocol:
-
-  \begin{itemize}
-
-  \item
-    \(\sigma_{6, c, \overline{\mathrm{n}}} = -\) the customer ends up in
-    disadvantaged position.
-  \item
-    \(\sigma_{6, s, \overline{\mathrm{n}}} = +\) the SP ends up in
-    advantaged position as he received the payment but didn't spend his
-    resources.
-  \end{itemize}
-\item
-  Starts a dispute:
-
-  \begin{itemize}
-
-  \item
-    \(\sigma_{6, c, \overline{\mathrm{d}}} = \sbullet\) the customer wins the
-    case and end up in a neutral position.
-  \item
-    \(\sigma_{6, s, \overline{\mathrm{d}}} = -\) the SP loses the case
-    and end up in a disadvantaged position.
-  \end{itemize}
-\end{itemize}
-
-Fairness:
-
-\begin{itemize}
-
-\item
-  The customer can follow the protocol to the position
-  \(\sigma_{6, c, \mathrm{n}} = -\), which let's him move the protocol
-  to a non-disadvantaged termination position
-  \(\sigma_{7, c, \mathrm{n}} = +\), or in case the SP haven't followed
-  the protocol start a dispute and win the case
-  \(\sigma_{6, c, \overline{\mathrm{d}}} = \sbullet\).
-\item
-  The SP can do nothing and end up in a non-disadvantaged position
-  \(\sigma_{6, s, \mathrm{n}} = +\), or
-  \(\sigma_{6, s, \overline{\mathrm{n}}} = +\).
-\end{itemize}
-
-\noindent \textbf
-{Step 7. Customer turn: download result}\label{step-7-retrieval-of-results}
-
-The SP has published the correct result on time:
-
-\begin{itemize}
-\item
-  Following protocol:
-
-  \begin{itemize}
-
-  \item
-    \(\sigma_{7, c, \mathrm{n}} = +\) the customer gets the correct
-    result. Therefore, he moves to an advantaged position.
-  \item
-    \(\sigma_{7, s, \mathrm{n}} = +\) the SP position hasn't changed.
-  \end{itemize}
-\item
-  Starting a dispute:
-
-  \begin{itemize}
-
-  \item
-    \(\sigma_{7, c, \mathrm{d}} = -\) the customer lose the case as the
-    SP can prove the publication of proof-of-provision.
-  \item
-    \(\sigma_{7, s, \mathrm{d}} = +\) the SP win the case as the SP can
-    prove the publication of proof-of-provision.
-  \end{itemize}
-\end{itemize}
-
-The customer has acted abnormally, then:
-
-\begin{itemize}
-\item
-  Following protocol:
-
-  \begin{itemize}
-
-  \item
-    \(\sigma_{7, c, \overline{\mathrm{n}}} = -\) the customer ends up in a disadvantaged position, as he ends up with incorrect result.
-  \item
-    \(\sigma_{7, c, \overline{\mathrm{n}}} = +\) SP ends up in advantaged
-    position as he received the payment but didn't spend his resources.
-  \end{itemize}
-\item
-  Starting a dispute:
-
-  \begin{itemize}
-
-  \item
-    \(\sigma_{7, c, \overline{\mathrm{d}}} = \sbullet\) the customer wins the case and ends up in a neutral position.
-  \item
-    \(\sigma_{7, c, \overline{\mathrm{d}}} = -\) SP loses the case and ends up in a disadvantaged position.
-  \end{itemize}
-\end{itemize}
-
-Fairness:
-
-\begin{itemize}
-
-\item
-  The customer can follow the protocol to the non-disadvantaged termination position \(\sigma_{7, c, \mathrm{n}} = +\), or in case the SP hasn't followed the protocol start a dispute and win the case \(\sigma_{7, c, \overline{\mathrm{d}}} = \sbullet\).
-\item
-  The SP can do nothing and ends up in a non-disadvantaged position \(\sigma_{7, s, \mathrm{n}} = +\).
+  The customer can follow the protocol to the non-disadvantaged termination position \(\sigma_{7, c, \mathrm{n}} = +\), or in case the SP has not followed the protocol start a dispute and win the case \(\sigma_{7, c, \overline{\mathrm{d}}} = \sbullet\).
+\item
+  The SP can do nothing and ends up in the non-disadvantaged position \(\sigma_{7, s, \mathrm{n}} = +\).
 \end{itemize}
@@
 
-The diagram below shows the path of positions when the SP tries to misbehave and does not execute service after receiving the payment.
-The protocol ends up neutral to the customer and disadvantaged to the SP positions.
+The figure~\ref{fig:misbehaviour} shows the transitions of positions when the SP tries to misbehave and does not execute service after receiving the payment.
+The customer reacts by starting a dispute, and the protocol ends up neutral to the customer and disadvantaged to the SP positions.
 
@@
 \centering
-\caption{Scenario of paths where the SP is misbehaving and the customer starts a dispute}
+\caption{Transitions of positions where the SP is misbehaving and the customer starts a dispute}
 \label{fig:misbehaviour}
@@
 
-Ultimately, the rational path for both parties is to follow the protocol as shown in the diagram below.
+Ultimately, the rational path for both parties is to follow the protocol as shown in the figure~\ref{fig:rational} below.
 
@@
 \centering
-\caption{The scenario of path where both the customer and  the SP are behaving correctly}
-\label{fig:well-behaviour}
+\caption{Transitions of positions where where both the customer and the SP are behaving correctly}
+\label{fig:rational}
 \end{figure}
@@
 
-With the fairness definition stated in the equation and the assumptions stated in Section \ref{assumptions}, our analysis indicates that the protocol achieves fairness.
+Using the fariness definition~\ref{fairness} and the assumptions stated in section~\ref{assumptions}, our analysis indicates that the protocol achieves fairness.
 

### 2022-03-09 access.tex
proof reading

@@
 \usepackage{amsmath,amssymb,amsfonts}
+
 \usepackage{algorithmic}
@@
 \title{Anonymous provision of services via blockchain}
-\author{\uppercase{Stanis\l{}aw Bara{\'n}ski}\authorrefmark{1},
+\author{\uppercase{Stanis\l{}aw Bara{\'n}ski} \authorrefmark{1},
 \uppercase{Julian Szyma{\'n}ski\authorrefmark{1} } 
@@
 A service provider can employ our protocol to provide services without collecting personal information.
-Possible applications for this protocol include anonymous clinical drugs, steroids, parenting testing, or anonymous legal advice.
+Possible applications for this protocol include anonymous tests for drugs, venereal diseases, paternity, and steroids, or anonymous legal advice.
 In case of dispute, either due to exceeding deadlines or providing incorrect results, the customer can disclose the whole interaction and prove to justice (police or court) the misbehaviour of the service provider.
 We analyze the protocol in the context of fairness and discuss further extensions to an anonymous delivery system, payment with cash, and a decentralized conflict resolution system.
-Our protocol may enable various services currently based on unacceptable trust assumptions to the SP.
+Our protocol may enable various services currently based on unacceptable trust assumptions to the service providers.
 \end{abstract}
@@
 \section{Introduction}
-Service providers (SP) like lawyers, laboratories, auditors, or banks,
+Service providers (SPs) like lawyers, laboratories, auditors, or banks,
 to provide services, require data that is often associated with the user
@@
 
-Providing personal information exposes users to privacy risks,
-i.e. potential loss of control over personal
+Providing personal information exposes users to privacy risks, i.e. potential loss of control over personal
 information~\cite{smith2011information}.
 
-Such user information can be used deliberately or unintentionally
-(e.g., by theft) for insider disclosure, unauthorized access, or
-commercial gains.
+Such personal information can be used deliberately or unintentionally
+(e.g., by theft) for insider disclosure, unauthorized access, or commercial gains.
 For example, by reselling it to marketers, financial institutions, other businesses, government agencies, or even cybercriminals.
@@
 
-Important individuals like top government, influencers, or celebrities are especially vulnerable to this kind of attack as exposure of their health records, purchase habits, or legal documents can threaten their reputation, position or be used for blackmailing.
+Important individuals like influencers, politicians, or celebrities are especially vulnerable to this kind of attack as exposure of their health records, purchase habits, or legal documents can threaten their reputation, position or be used for blackmailing.
 
@@
 
-It would be desirable for the user to keep its identity private while still receiving the service. This could lead to reduced trust that users have to put on SP and less responsibility borne by SP.
+It would be desirable for the user to keep its identity private while still receiving the service. This could lead to reduced trust that users have to put on SPs and less responsibility borne by SPs.
 
@@
 
-Our protocol allows taking such tests anonymously, therefore eliminating the strong trust assumption put on the laboratories and their IT
+Our protocol allows taking such tests anonymously, eliminating the strong trust assumption put on the laboratories and their IT
 systems.
@@
 
-Our protocol would allow taking such advice anonymously, therefore eliminating the strong trust assumption put on the lawyers and their IT systems.
+Our protocol would allow taking such advice anonymously, eliminating the strong trust assumption put on the lawyers and their IT systems.
 \end{itemize}
@@
 \begin{itemize}
-    \item Privacy-preserving blockchain, to allow customers anonymously pay for the services.
-    \item Message board blockchain, to achieve fairness, i.e., as a means for proving that certain actions took place at a certain moment without the trusted third party.
+    \item Privacy-preserving cryptocurrency, to allow customers anonymously pay for the services.
+    \item Message board blockchain, to achieve fairness, i.e., as a means for proving that certain actions took place at a certain moment without the trusted third party (TTP).
     \item Content-addressable peer-to-peer storage network to provide results to customers. 
@@
     \begin{itemize}
-        \item Symmetric encryption: to encrypt and decrypt results published on public networks.
-        \item Digital signatures: To achieve authentication and non-repudiation of actions. 
+        \item Symmetric encryption, to encrypt and decrypt results published on the public networks.
+        \item Digital signatures, to achieve authentication and non-repudiation of actions. 
     \end{itemize}
@@
 %\paragraph{Contributions}
-We contribute to the field of fair exchanges by proposing a simple, practical, and anonymous protocol that does not rely on the centralized trusted-third party but decentralized blockchain and
+We contribute to the field of fair exchanges by proposing a simple, practical, and anonymous protocol that does not rely on the centralized trusted third party but decentralized blockchain and
 distributed content-addressable storage network.
@@
 \begin{itemize}
-\item Anonymity:
-throughout the whole transaction, the customer stays anonymous to all external observers.
+\item Anonymity: the customer stays anonymous to all external observers throughout the transaction.
 \item Fairness:
-at each step of the protocol, both parties are incentivized to act accordingly to the protocol; otherwise, the misbehaving party ends up in the worst position.
+at each step of the protocol, both parties are incentivized to act accordingly to the protocol; otherwise, the misbehaving party ends up in a disadvantaged position.
 \item Dispute resolution: at each step of the protocol, the customer can start a dispute and win the case if and only if the SP misbehaved.
@@
 In section~\ref{sec:related-works} we briefly review related works. 
-Section~\ref{sec:building-blocks} explains the building blocks related to fair exchanges, blockchain, anonymity and confidentiality, and storage network. 
+Section~\ref{sec:building-blocks} explains the building blocks of fair exchanges, blockchain, storage network, anonymity and confidentiality.
 Section~\ref{sec:protocol} describes how the protocol works in detail.
@@
 fair exchange of physical products and electronic payment protocol that
-guarantee both customer and merchant anonymity. They achieve it by
-introducing online trusted third parties that validate coins and provide
+guarantee both customer and merchant anonymity. They achieve it by introducing online TTPs that validate coins and provide
 fair exchange guarantees.
 
-The anonymity is ensured by assuming the existence of a source cabinet (SC), delivery cabinet (DC), and a trusted delivery agent who take
-a product from a source cabinet and provide it to a destination cabinet.
+The anonymity is ensured by assuming the existence of a source cabinet (SC), delivery cabinet (DC), and a trusted delivery agent who take a product from a SC and provide it to a DC.
 Both cabinets provide access to the product by passwords to conceal
@@
     \item The customer sends the merchant the purchase order and the digital signature made by TTP on the encrypted coin.
-    \item The merchant post the product to the source cabinet.
-    \item Delivery agent collects the product from the source cabinet and posts it to the delivery cabinet.
-    \item Customer collects the product from the delivery cabinet using a password.
+    \item The merchant post the product to the SC.
+    \item Delivery agent collects the product from the SC and posts it to the DC.
+    \item Customer collects the product from the DC using a password.
     \item The customer checks if the product is the ordered one.
@@
         \setcounter{enumii}{7}
-        \item the customer sends the acknowledge to the delivery cabinet and decryption key to the merchant.
+        \item the customer sends the acknowledge to the DC and decryption key to the merchant.
         \item The merchant redeem the coins from the bank.
@@
         \setcounter{enumii}{7}
-        \item the delivery cabinet is equipped with a video camera that records the moment when the customer opens the package and lets the customer signal the invalidity of the product, and so, sending the encrypted recording to the TTP.
+        \item the DC is equipped with a video camera that records the moment when the customer opens the package and lets the customer signal the invalidity of the product, and so, sending the encrypted recording to the TTP.
         \item the dispute is settled via TTP, optionally letting each party reveal its identity.
@@
 \begin{itemize}
-    \item the TTP does not misbehave or collude with any party. 
-    \item The customer's and merchant's banks enable confidential transactions, and both share commit-buffer where the value is locked until the transaction is finished.   
-    \item All banks maintain a global list of coins' serial numbers to prevent double-spending problems. 
-    \item The source cabinet and delivery cabinet exist, and in both, the product access is protected by a password.
-    \item Delivery cabinet is equipped with a video camera that records the moment when the customer opens the package and provides a way to submit the video to TTP in case of a dispute. 
-    \item There exists a trusted delivery agent.
-    \item Communication channels between parties provide anonymity.
+    \item the TTP does not misbehave or collude with any party;
+    \item the customer's and merchant's banks enable confidential transactions, and both share commit-buffer where the value is locked until the transaction is finished;
+    \item all banks maintain a global list of coins' serial numbers to prevent double-spending problems;
+    \item the SC and DC exist, and in both, the product access is protected by a password;
+    \item the DC is equipped with a video camera that records the moment when the customer opens the package and provides a way to submit the video to TTP in case of a dispute;
+    \item there exists a trusted delivery agent;
+    \item communication channels between parties provide anonymity.
 \end{itemize}
@@
 
-Themis~\cite{meng2019themis} is a fair exchange
-protocol that uses blockchain instead of TTP. It provides an escrow
-service for secure exchanging cryptocurrencies and digital goods. Also, it provides a decentralized dispute resolution system for resolving conflicts.
+Themis~\cite{meng2019themis} is a fair exchange protocol that uses blockchain instead of TTP.
+It provides an escrow service for the secure exchange of cryptocurrencies and digital goods.
+Also, it provides a decentralized dispute resolution system for resolving conflicts.
 
@@
 
-In case of dispute, the decentralized network of mediators settle the
-conflict and grand one winning party, the other party secret key,
+In case of dispute, the decentralized network of mediators settle the conflict and grand one winning party, the other party secret key,
 letting him withdraw the funds.
@@
 
-However, since the system uses Ethereum— fully traceable blockchain—its anonymity is achieved as long as the addresses are not identified with the real identities, which we call pseudonymity rather than anonymity (see Section~\ref{sec:pseudo-anon}).
-Also, the protocol does not cover the dispute between the parties.
+However, since the system uses Ethereum, it achieves pseudonymity rather than anonymity (see section~\ref{sec:pseudo-anon}). Also, the protocol does not cover disputes between the parties.
 
@@
 Nevertheless, the blockchain paradigm has its limitations.
-Blockchain can assure the correctness of data existing only on the blockchain—the problem arises in the contact between blockchain and the real world when we want the smart contract to decide based on some input from outside the blockchain.
+Blockchain can assure the correctness of data existing only on the blockchain.
+The problem arises in the contact between blockchain and the real world, when we want the smart contract to decide based on some input from outside the blockchain.
 The technique of providing real-world data to the blockchain is called oracle.
@@
 
-Possible directions toward semi-autonomous decentralized resolution
-system are discussed in Section ~\ref{sec:future-work}.
+Possible directions toward semi-autonomous decentralized resolution system are discussed in section ~\ref{sec:future-work}.
 
@@
 
-To mitigate the issue, we designed the protocol so that the SP who follows the protocol is always in an advantageous position; therefore, he has no reason to start a dispute.
+To mitigate the issue, we designed the protocol so that the SP who follows the protocol is always in an advantaged position; therefore, he has no reason to start a dispute.
 On the other hand, the customer can start a dispute at any time of the protocol, but only the actual misbehaviour of the SP makes him win the case.
@@
 \begin{enumerate}
-    \item Proof-of-delivery ($\mathrm{PoD}$) is a confirmation issued by the SP to the customer that proves that the customer has delivered to the SP a complete (according to the SP requirements) package, and the SP accepted it.
+    \item Proof of delivery ($\mathrm{PoD}$) is a confirmation issued by the SP to the customer that proves that the customer has delivered to the SP a complete (according to the SP requirements) package, and the SP accepted it.
 It consists of the current time, the deadline to pay for the transaction, the deadline to provide a result of the service, randomly generated number uniquely identifying the transaction, and the SP's signature guaranteeing non-repudiation.
-The formal definition of the $\mathrm{PoD}$ is presented in Section ~\ref{proof-of-delivery}.
+The formal definition of the $\mathrm{PoD}$ is presented in section ~\ref{proof-of-delivery}.
 
     \item Payment $\mathrm{attestation}$ is confirmation that the customer has paid for the transaction at a certain time.
-The actual implementation depends on the particular cryptocurrency and is discussed further Section~\ref{payment-for-services}.
+The actual implementation depends on the particular cryptocurrency and is discussed further section~\ref{payment-for-services}.
 
@@
 \subsection{Message Board}\label{message-board}
-The proof-of-provision that we coined for the purpose of this protocol
-is generally called the proof-of-existence
+The proof of provision that we coined for the purpose of this protocol is generally called the proof of existence
 \cite{proofofexistence, de2016stampery, Chainpoi39}.
 
-The idea behind proof-of-existence is to certify that some information
+The idea behind proof of existence is to certify that some information
 has existed at a certain moment, in such a way that nobody can
@@
 
-We need this functionality for two reasons: (1) Communicate the existence
-of the result to the customer to whom the SP have no other
-communication medium as the customer stays anonymous; (2) let the SP to proof the publication of the result within the agreed with customer deadline.
+We need this functionality for two reasons: (1) communicate the existence of the result to the customer to whom the SP have no other communication medium as the customer stays anonymous; (2) let the SP to proof the publication of the result within the agreed with customer deadline.
 
@@
 
-Depending on the context the platform of achieving it is called bulletin board~\cite{achenbach2015improved} or message board~\cite{hinarejos2019solution} or trusted timestamping~\cite{gipp2015decentralized}.
+Depending on the context the platform of achieving it is called bulletin board~\cite{achenbach2015improved}, trusted timestamping~\cite{gipp2015decentralized}, or message board~\cite{hinarejos2019solution}.
 In this work, we call it a message board.
@@
 The multidisciplinary nature leads to ambiguous definitions~\cite{smith2011information}.
-For our work, we rely on more concrete definitions, i.e.~confidentality, and anonymity.
-
-Confidentiality is the ability to hide the details of action from others.
+For our work, we rely on more concrete definitions, i.e.~confidentality and anonymity.
+
+Confidentiality is the ability to hide the details of an action from others.
 Alternatively, we can say that the system guarantees confidentiality if, for all observers, everything they can say about the action is the fact that it happened and nothing more.
@@
 Some systems guarantee pseudonymity rather than anonymity.
-Pseudonymity allows users to hide their real identity behind the pseudonym.
+Pseudonymity allows users to hide their real identity behind the pseudonyms.
 Despite the whole system being transparent and allowing linking actions to pseudonyms, the system is considered anonymous as long as the link between pseudonyms and real identities is secret.
@@
 ways:
-
-\begin{itemize}
-
-\item
-  separate address — each transaction derives a new address uniquely
-  associated with the transaction. Such addresses can be derived
-  using Hierarchical Deterministic Wallets (BIP-32)~\cite{bipsbip089}.
-\item
-  memo — the payments are sent to one SP account but contain an extra
-  field named ``memo'' filled with the unique number provided by the SP in $\mathrm{PoD}$. Each payment containing such value in the memo is
-  considered to pay for the transaction. In case of a dispute, revealing both the payment memo and the $\mathrm{PoD}$ proves the connection.
+% continue reading from here
+\begin{itemize}
+
+\item separate address: each transaction derives a new address uniquely associated with the transaction.
+Such addresses can be derived using Hierarchical Deterministic Wallets (BIP-32)~\cite{bipsbip089}.
+\item memo: the payments are sent to one SP account but contain an extra field named ``memo'' filled with the unique number provided by the SP in $\mathrm{PoD}$.
+Each payment containing such value in the memo is considered to pay for the transaction.
+In case of a dispute, revealing both the payment memo and the $\mathrm{PoD}$ proves the connection.
 \end{itemize}

### 2022-03-09 access.tex
docs: update

@@
 \usepackage{amsmath,amssymb,amsfonts}
-
 \usepackage{algorithmic}
@@
 
-\subsection{Fairness}\label{proof-of-justice}
+\subsection{Fairness}\label{fairness}
 
@@
 
-\subsection{Message Board}\label{message-board}
+\subsection{Message Board}\label{sec:message-board}
 The proof of provision that we coined for the purpose of this protocol is generally called the proof of existence
@@
 
-The figure ~\ref{fig:anonymity-diagram1} ilustrate relations between these terms.
+The figure ~\ref{fig:anonymity-diagram} ilustrate relations between these terms.
 
@@
 
-\label{fig:anonymity-diagram1}
+\label{fig:anonymity-diagram}
 \end{figure}
@@
 
-Depending on the cryptocurrency, the link can be created in different
+Depending on a cryptocurrency, the link can be created in different
 ways:
@@
 However, since the customer wants to stay anonymous, he does not want to expose his e-mail address nor IP address.
-Moreover, the SP should prove that the result has been provided before the deadline, which brings us to the issue of proof of existence discussed in section ~\section{message-board}.
+Moreover, the SP should prove that the result has been provided before the deadline, which brings us to the issue of proof of existence discussed in section ~\ref{sec:message-board}.
 
@@
 The most common workaround (\cite{shahid2020blockchain, wang2019auditable, chen2017improved, Usageide95}) is to publish the data on a content addressable peer-to-peer storage network like IPFS~\cite{benet2014ipfs}.
-Then, publish on the blockchain just a content identifier ($\mathrm{cid}$) that uniquely points to the content stored on IPFS.
+Then, publish on the blockchain just the content identifier ($\mathrm{cid}$) that uniquely points to the content stored on IPFS.
 
@@
 
-Instead of searching for one blockchain that solves all the functionalities, we allow the protocol to use separate blockchains for each role.
+Instead of searching for one blockchain that provides all the functionalities, we allow the protocol to use separate blockchains for each role.
 If a suitable blockchain arises, it can play more than one role.
@@
     \begin{itemize}
-        \item The customer and the SP have their own key pairs consisting of secret key $\mathrm{sk}(\mathrm{party})$ and public key $\mathrm{pk}(\mathrm{party})$, where $\mathrm{party} \in \{\mathrm{C}, \mathrm{SP}\}$ is the customer or the service provider accordingly.
+        \item The customer and the SP have their key pairs consisting of secret key $\mathrm{sk}(\mathrm{party})$ and public key $\mathrm{pk}(\mathrm{party})$, where $\mathrm{party} \in \{\mathrm{C}, \mathrm{SP}\}$ is the customer or the service provider accordingly.
         \item Both the customer and the SP can create and verify digital signatures created by the customer $\mathrm{sig}_{\mathrm{sk}(\mathrm{C})}$ and the SP $\mathrm{sig}_{\mathrm{sk}(\mathrm{SP})}$.
-        \item The SP's public key is publicly known.
+        \item The SP's public key $\mathrm{pk}(\mathrm{SP})$ is publicly known.
     \end{itemize}
@@
     \begin{itemize}
-        \item Uses common symmetric encryption $\mathrm{E}_\mathrm{key}(\cdot)$ and decryption $\mathrm{D}_\mathrm{key}(\cdot)$ operations.
+        \item use common symmetric encryption $\mathrm{E}_\mathrm{key}(\cdot)$ and decryption $\mathrm{D}_\mathrm{key}(\cdot)$ operations.
     \end{itemize}
@@
     \begin{itemize}
-        \item Accepts packages from unknown customers and give $\mathrm{PoD}$ in return.
-        \item Accepts payments with anonymous cryptocurrencies as described in Section~\ref{payment-for-services}.
+        \item accepts packages from unknown customers and give $\mathrm{PoD}$ in return.
+        \item accepts payments with anonymous cryptocurrencies as described in section~\ref{payment-for-services}.
     \end{itemize}
@@
     \begin{itemize}
-        \item Accepts as a evidence in dispute a $\mathrm{PoD}$, $\mathrm{PoP}$, and payment $\mathrm{attestation}$ as described in Section~\ref{proof-of-justice}.
+        \item accepts as evidence in a dispute the $\mathrm{PoD}$, $\mathrm{PoP}$, and payment $\mathrm{attestation}$ as described in section~\ref{fairness}.
     \end{itemize}
@@
     \begin{itemize}
-        \item Supports anonymous, i.e., untraceable and (ideally) unlinkable transactions as specified in Section~\ref{sec:pseudo-anon}.
-        \item Supports uniquely identifying transaction either via separate address, memo field, or other similar mechanisms as described in Section ~\ref{payment-for-services}. 
+        \item supports anonymous, i.e., untraceable and (ideally) unlinkable transactions as specified in section~\ref{sec:pseudo-anon}.
+        \item supports uniquely identifying transaction either via separate address, memo field, or other similar mechanisms as described in section ~\ref{payment-for-services}. 
     \end{itemize}
@@
     \begin{itemize}
-        \item Supports proofs as large as the size of $\mathrm{PoP}$, i.e., sum size of $\mathrm{cid}$, $\mathrm{nonce}$, and $\mathrm{sig}$.
+        \item supports proofs as large as the size of $\mathrm{PoP}$, i.e., sum size of $\mathrm{cid}$, $\mathrm{nonce}$, and $\mathrm{sig}$.
     \end{itemize}
@@
     \begin{itemize}
-        \item Allows for uniquely content retrieval via $\mathrm{cid}$ (usually a hash of the content).
-        \item Allows for anonymous content retrieval.
+        \item allows for uniquely content retrieval via $\mathrm{cid}$ (usually a hash of the content).
+        \item allows for anonymous content retrieval.
     \end{itemize}
@@
 
+\vspace{5mm}
+
 \noindent \textbf
@@
 
-\item $\mathrm{materials}$ - are the materials required to provide the service, for example, samples of urine, blood, stool, saliva; legal documents, CDs, emails, photos, bank statements, or any other kind of evidence depending on the service.
+\item $\mathrm{materials}$ - are the materials required to provide the service, for example, samples of urine, blood, stool, saliva; legal documents, CDs, emails, photos, bank statements; or any other kind of evidence depending on the service.
 \item $\mathrm{key}$ - symmetric key used to encrypt and decrypt the result.
@@
 \noindent \textbf
-{proof of delivery ($\mathrm{PoD}$)}\label{proof-of-delivery} is a  confirmation issued by the SP to the customer that proves that the customer has delivered to the SP a complete (according to the SP requirements) package, and the SP accepted it.
+{Proof of delivery ($\mathrm{PoD}$)}\label{proof-of-delivery} is a  confirmation issued by the SP to the customer that proves that the customer has delivered to the SP a complete (according to the SP requirements) package, and the SP accepted it.
 
@@
 
-\item $\mathrm{T}_\mathrm{issue}$ - time at which the PoD is issued.
+\item $\mathrm{T}_\mathrm{issue}$ - time at which the $\mathrm{PoD}$ is issued.
 \item
@@
 \noindent \textbf
-{proof of provision ($\mathrm{PoP}$)}\label{proof-of-provision} is proof that the SP published the result at a certain time.
+{Proof of provision ($\mathrm{PoP}$)}\label{proof-of-provision} is proof that the SP published the result at a certain time.
 It defends the SP in case the customer unjustly starts a dispute after the result has been published.
@@
 \item
-  \(\mathrm{cid}\) - content identifier as specified in ~\ref{storage-network}.
+  \(\mathrm{cid}\) - content identifier as specified in section~\ref{storage-network}.
 \item
@@
 \noindent \textbf
-{Payment attestation}\label{payment-attestation}
-proves that the customer did the payment. Since the
-evidence depends on the particular blockchain (see Section ~\ref{payment-for-services}). We refer to them symbolically as
-\(attestation\).
-
-\noindent \textbf
-{Result}\label{results} is assumed to be a document in PDF format, but any other format is allowed as long as it can be binary encoded and uploaded to IPFS. We refer to it symbolically as $result$.
+{Payment attestation}\label{payment-attestation} proves that the customer did the payment.
+Since the evidence depends on a particular blockchain (see section ~\ref{payment-for-services}), we refer to it symbolically as
+\(\mathrm{attestation}\).
+
+\noindent \textbf
+{Result}\label{results} is assumed to be a document in PDF format, but any other format is allowed as long as it can be binary encoded and uploaded to IPFS.
+We refer to it symbolically as $\mathrm{result}$.
 
@@
 
-In this section, we describe each step of the protocol. The steps are
-shown in the Figure ~\ref{fig:protocol-diagram}.
+In this section, we describe each step of the protocol, also shown in the figure~\ref{fig:protocol-diagram}.
 
@@
 \centering
-\caption{Messages exchanged in protocol.}
+\caption{Messages exchanged in the protocol.}
 \label{fig:protocol-diagram}
@@
 
-The customer collects all the $\mathrm{materials}$ required by the SP, generates an encryption $\mathrm{key}$ prints it on a paper as a QR code, and packs them together into a package $\mathrm{pkg}$.
+The customer collects all the $\mathrm{materials}$ required by the SP, generates an encryption $\mathrm{key}$, prints it on a paper as a QR code, and packs them together into a package $\mathrm{pkg}$.
 
@@
 They protocol starts once the customer delivers package $\mathrm{pkg}$ and the SP accepts its content.
-In return, the SP issue a $\mathrm{PoD}$ with agreed upfront payment deadline $\mathrm{T}_\mathrm{pay}$, service provision deadline $\mathrm{T}_\mathrm{provide}$ and current time $\mathrm{T}_\mathrm{issue}$.
+In return, the SP issue a $\mathrm{PoD}$ with agreed upfront payment deadline $\mathrm{T}_\mathrm{pay}$, service provision deadline $\mathrm{T}_\mathrm{provide}$, and current time $\mathrm{T}_\mathrm{issue}$.
 Also, the $\mathrm{PoD}$ consist of randomly generated unique number $\mathrm{nonce}$, which will allow associating all actions related to the transaction throughout the protocol.
@@
 
-We assume this step to be entirely physical, that is, $\mathrm{pkg}$ consists of physical materials, $\mathrm{PoD}$ is in the form of, e.g., QR code printed on a paper receipt.
-
-$\mathrm{PoD}$ could be published on a message board (similarly to $\mathrm{PoP}$); however, since the $\mathrm{pkg}$ is delivered personally or via a trusted person, the confirmation can be issued in person as well.
+We assume this step to be entirely physical, i.e., $\mathrm{pkg}$ consists of physical materials, $\mathrm{PoD}$ is in the form of, e.g., QR code printed on a paper receipt.
+
+$\mathrm{PoD}$ could be published on a message board (similarly to $\mathrm{PoP}$); however, since the $\mathrm{pkg}$ is delivered personally or via a trusted person, the confirmation can be issued in person.
 If we would like to hire a courier to deliver our $\mathrm{pkg}$, then the $\mathrm{PoD}$ would have to be published on the message board (further extension to the anonymous delivery system is discussed in section \ref{sec:future-work}).
@@
 
-Having the PoD issued, the SP can not reject receiving the package. At this point the
-customer should pay for the transaction with an agreed upfront cryptocurrency system (see Section~\ref{payment-for-services}).
+Having the $\mathrm{PoD}$ issued, the SP can not reject receiving the package. At this point the
+customer should pay for the transaction (identified by $\mathrm{nonce}$ value) with the agreed upfront cryptocurrency blockchain (see section~\ref{payment-for-services}).
 
@@
 After delivering the package and paying for the transaction, the customer subscribes to the message board and waits until the SP publishes the proof of provision.
-The subscription is for the SP public key $\mathrm{pk}(\mathrm{SP}$ and transaction's $\mathrm{nonce}$.
+The subscription is for the SP public key $\mathrm{pk}(\mathrm{SP})$ and transaction's $\mathrm{nonce}$.
 
@@
 
-As a result, in our analysis, we have to consider four different outcomes for each party of the protocol:
-
-\begin{itemize}
-
-\item
-  $\sigma_\mathrm{n}$: after following the protocol when the other party acted normally.
-\item
-  $\sigma_\mathrm{d}$: after a settled dispute when the other party acted normally.
-\item
-  $\sigma_\overline{n}$: after not starting a dispute despite the other party has acted abnormally.
-\item
-  $\sigma_\overline{d}$: after a settled dispute when the other party has acted abnormally.
+As a result, in our analysis, we have to consider four different outcomes for each party of the protocol ($\mathrm{party \in \{c, s}\}$), for each step of the protocol ($\mathrm{step \in 1..7}$):
+
+\begin{itemize}
+
+\item
+  $\mathrm{\sigma_{step,party,n}}$: after following the protocol when the other party acted normally.
+\item
+  $\mathrm{\sigma_{step,party,d}}$: after a settled dispute when the other party acted normally.
+\item
+  $\mathrm{\sigma_{step,party,\overline{n}}}$: after not starting a dispute despite the other party has acted abnormally.
+\item
+  $\mathrm{\sigma_{step,party,\overline{d}}}$: after a settled dispute when the other party has acted abnormally.
 \end{itemize}
@@
 The protocol terminates after the last step, after starting a dispute, or after a party has not completed its designated action in time.
-Therefore, all positions except $\sigma_\mathrm{n}$ are termination positions.
+Therefore, all positions except $\mathrm{\sigma_n}$ are termination positions.
 
@@
 
-\begin{definition}[Fairness] \label{fairness}
+\begin{definition}[Fairness] \label{def:fairness}
 A protocol achieve fariness iff 
@@
 \begin{split}
-\forall_{party \in parties}\forall_{\mathrm{step} \in \mathrm{steps}} &\mathrm{can\ move}\\
-&\mathrm{to\ the\ non\ disadvantaged\ position} 
+\forall_{party \in parties}\forall_{\mathrm{step} \in \mathrm{steps}} &\operatorname{can\ move}\\
+&\operatorname{to\ the\ non-disadvantaged\ position} 
 \end{split}
@@
 
-Below  we listed
-assumptions we took
-for the analysis purpose.
+Below  we listed assumptions we took for the analysis purpose.
 
@@
 \item
-  By completing a transaction, both parties end up in advantaged positions (+). In other words, they have intrinsic motivation to initialize and complete the transaction.
-\item
-  We assume the protocol steps to be atomic—there are no intermediate steps.
+    After completing a transaction, both parties end up in advantaged positions (+). In other words, they have intrinsic motivation to initialize and complete the transaction.
+\item
+    The protocol steps are atomic—there are no intermediate steps.
+\item 
+    The protocol can go only forward—there is no way of reverting any action.
 \item
@@
 For example, paying for the invoice twice does not cause any effect on the curse of the protocol.
-\item Once published, the result is available to the customer on the storage network. The idea of guaranteeing it cryptographically is discussed in Section~\ref{sec:future-work}.
-
-\item The protocol can go only forward—there is no way of reverting any action.
+\item 
+    Once published, the result is available to the customer on the storage network. The idea of guaranteeing it cryptographically is discussed in section~\ref{sec:future-work}.
+
+\item
+    Winning the dispute leads to a neutral position (•).
+
 \item
     Losing the dispute leads to a punishment greater than any reward, leading to a disadvantaged position (-). Hence, the rational customer will not start a dispute that he is unsure of winning.
-\item
-  Winning the dispute leads to a neutral position (•).
 \item
@@
 \begin{itemize}
-\item
-  Agreeable path:
-
-  \begin{itemize}
-
-  \item
-    \(\sigma_{1, c, \mathrm{n}} = \sbullet\), the customer has risked its materials but has not paid anything, so we assume he is in the neutral position.
-One would argue that the customer has put effort into delivering the materials to the SP or that the sample is valuable.
-We assume that the sample without personal information is useless, and the effort to deliver the package is negligible.
-  \item
-    \(\sigma_{1, s, \mathrm{n}} = \sbullet\), the SP is in a neutral position as he did not put any effort, and the package has not brought any value to the SP.
+\item Agreeable path:
+  \begin{itemize}
+  \item
+    \(\operatorname{\sigma_{1, c, n} = \sbullet}\), the customer has risked its materials but has not paid anything, so we assume he is in the neutral position \footnote{One would argue that the customer has put effort into delivering the materials to the SP or that the sample is valuable.
+We assume that the sample without personal information is useless, and the effort to deliver the package is negligible.}.
+  \item
+    \(\operatorname{\sigma_{1, s, n} = \sbullet}\), the SP is in a neutral position as he did not put any effort, and the package has not brought any value to the SP.
   \end{itemize}
@@
   \item
-    \(\sigma_{1, c, \mathrm{d}} = -\), the customer loses the case as the SP has still an opportunity to publish proof of provision within the timeframe.
-  \item
-    \(\sigma_{1, s, \mathrm{d}} = \sbullet\), the SP win the case for the same reason.
+    \(\operatorname{\sigma_{1, c, d} = -}\), the customer loses the case as the SP has still an opportunity to publish proof of provision within the timeframe.
+  \item
+    \(\operatorname{\sigma_{1, s, d} = \sbullet}\), the SP win the case for the same reason.
   \end{itemize}
@@
 \item
-  The customer can follow the protocol and move to the non-disadvantaged position \(\sigma_{1, c, \mathrm{n}} = \sbullet\).
-\item
-  The SP can do nothing and end up in the non-disadvantaged position \(\sigma_{1, s, \mathrm{n}} = \sbullet \) or \(\sigma_{1, s, \mathrm{d}} = \sbullet \).
+  The customer can follow the protocol and move to the non-disadvantaged position \(\operatorname{\sigma_{1, c, n} = \sbullet}\).
+\item
+  The SP can do nothing and end up in the non-disadvantaged position \(\operatorname{\sigma_{1, s, n} = \sbullet}\) or \(\operatorname{\sigma_{1, s, d} = \sbullet}\).
 \end{itemize}
@@
   \item
-    \(\sigma_{2, c, \mathrm{n}} = -\), the customer has spent his funds but has not received the result.
-  \item
-    \(\sigma_{2, s, \mathrm{n}} = +\), the SP has received the payment but has not spent his resources yet.
+    \(\operatorname{\sigma_{2, c, n} = -}\), the customer has spent his funds but has not received the result.
+  \item
+    \(\operatorname{\sigma_{2, s, n} = +}\), the SP has received the payment but has not spent his resources yet.
   \end{itemize}
@@
   \item
-    \(\sigma_{2, c, \mathrm{d}} = -\), the customer loses the case as the SP has still an opportunity to publish proof of provision before the deadline.
-  \item
-    \(\sigma_{2, s, \mathrm{d}} = +\), the SP win the case for the same reason.
+    \(\operatorname{\sigma_{2, c, d} = -}\), the customer loses the case as the SP has still an opportunity to publish proof of provision before the deadline.
+  \item
+    \(\operatorname{\sigma_{2, s, d} = +}\), the SP win the case for the same reason.
   \end{itemize}
@@
   \item
-    \(\sigma_{2, c, \overline{\mathrm{n}}} = \sbullet\), the customer ends up in the neutral position as he did not spend his funds.
-  \item
-    \(\sigma_{2, s, \overline{\mathrm{n}}} = \sbullet\), the SP ends up in a neutral position as he did not receive the payment, nor spent his resources.
+    \(\operatorname{\sigma_{2, c, \overline{n}} = \sbullet}\), the customer ends up in the neutral position as he did not spend his funds.
+  \item
+    \(\operatorname{\sigma_{2, s, \overline{n}} = \sbullet}\), the SP ends up in a neutral position as he did not receive the payment, nor spent his resources.
   \end{itemize}
@@
   \item
-    \(\sigma_{2, c, \overline{\mathrm{d}}} = -\), the customer loses the case as he can not prove the payment before the time limit.
-  \item
-    \(\sigma_{2, s, \overline{\mathrm{d}}} = \sbullet\), the SP is not charged to justice due to a lack of proof.
+    \(\operatorname{\sigma_{2, c, \overline{d}} = -}\), the customer loses the case as he can not prove the payment before the time limit.
+  \item
+    \(\operatorname{\sigma_{2, s, \overline{d}} = \sbullet}\), the SP is not charged to justice due to a lack of proof.
   \end{itemize}
@@
 \item
-  The customer can move the protocol forward to step 3, where if the SP follows the protocol then the customer can push the protocol forward up to the last termination step \(\sigma_{7, c, \mathrm{n}} = +\), otherwise if at any step the SP does not follow the protocol the customer can start a dispute which terminates the protocol at the non-disadvantaged position, i.e., \(\sigma_{3, c, \overline{\mathrm{d}}} = \sbullet\), \(\sigma_{4, c, \overline{\mathrm{d}}} = \sbullet\), \(\sigma_{5, c, \overline{\mathrm{d}}} = \sbullet\).
-\item
-  The SP can do nothing and end up in the non-disadvantaged position \(\sigma_{2, s, \mathrm{n}} = +\), \(\sigma_{2, s, \mathrm{d}} = +\), \(\sigma_{2, s, \overline{\mathrm{n}}} = \sbullet\), \(\sigma_{2, s, \overline{\mathrm{d}}} = \sbullet\).
-\end{itemize}
-
-\noindent \textbf
-{Step 3. SP turn: provision of service}\label{step-3-provision-of-service}
+  The customer can move the protocol forward to step 3, where if the SP follows the protocol then the customer can push the protocol forward up to the last termination step \(\operatorname{\sigma_{7, c, n} = +}\), otherwise if at any step the SP does not follow the protocol the customer can start a dispute which terminates the protocol at the non-disadvantaged position, i.e., \(\operatorname{\sigma_{3, c, \overline{d}} = \sbullet}\), \(\operatorname{\sigma_{4, c, \overline{d}} = \sbullet}\), \(\operatorname{\sigma_{5, c, \overline{d}} = \sbullet}\).
+\item
+  The SP can do nothing and end up in the non-disadvantaged position \(\operatorname{\sigma_{2, s, n} = +}\), \(\operatorname{\sigma_{2, s, d} = +}\), \(\operatorname{\sigma_{2, s, \overline{n}} = \sbullet}\), \(\operatorname{\sigma_{2, s, \overline{d}} = \sbullet}\).
+\end{itemize}
+
+\noindent \textbf
+{Step 3. SP turn: provision of service}
 
@@
   \item
-    \(\sigma_{3, c, \mathrm{n}} = -\), the customer has not received the result, so he remains in the disadvantaged position. 
-  \item
-    \(\sigma_{3, s, \mathrm{n}} = +\), the SP has fulfilled the contract on time.
+    \(\operatorname{\sigma_{3, c, \n} = -}\), the customer has not received the result, so he remains in the disadvantaged position. 
+  \item
+    \(\operatorname{\sigma_{3, s, n} = +}\), the SP has fulfilled the contract on time.
   \end{itemize}
@@
   \item
-    \(\sigma_{3, c, \mathrm{d}} = -\), the customer loses the case as the SP has still the opportunity to publish proof of provision within the timeframe. 
-  \item
-    \(\sigma_{3, s, \mathrm{d}} = +\), the SP win the case for the same reason.
+    \(\operatorname{\sigma_{3, c, d} = -}\), the customer loses the case as the SP has still the opportunity to publish proof of provision within the timeframe. 
+  \item
+    \(\operatorname{\sigma_{3, s, d} = +}\), the SP win the case for the same reason.
   \end{itemize}
@@
   \item
-    \(\sigma_{3, c, \overline{\mathrm{n}}} = -\), the customer ends up in a disadvantaged position.
-  \item
-    \(\sigma_{3, s, \overline{\mathrm{n}}} = +\), the SP ends up in the advantaged position as he received the payment. 
+    \(\operatorname{\sigma_{3, c, \overline{n}} = -}\), the customer ends up in a disadvantaged position.
+  \item
+    \(\operatorname{\sigma_{3, s, \overline{n}} = +}\), the SP ends up in the advantaged position as he received the payment. 
   \end{itemize}
@@
   \item
-    \(\sigma_{3, c, \overline{\mathrm{d}}} = •\), the customer wins the case and ends up in the neutral position.
-  \item
-    \(\sigma_{3, s, \overline{\mathrm{d}}} = -\), the SP loses the case and ends up in the disadvantaged position. 
+    \(\operatorname{\sigma_{3, c, \overline{d}} = \sbullet}\), the customer wins the case and ends up in the neutral position.
+  \item
+    \(\operatorname{\sigma_{3, s, \overline{d}} = -}\), the SP loses the case and ends up in the disadvantaged position. 
   \end{itemize}
@@
 \item
-  The customer can do nothing if the SP follows the protocol, which will ultimately put him in the advantaged position \(\sigma_{7, c, \mathrm{n}} = +\), or in case of the SP not following the protocol, the customer can start a dispute and terminate in the non-disadvantaged position \(\sigma_{3, c, \overline{\mathrm{d}}} = •\).
-\item
-  The SP can follow the protocol and move to the non-disadvantaged position \(\sigma_{3, s, \mathrm{n}} = +\), or not follow the protocol and also end up at the non-disadvantaged position \(\sigma_{3, s, \overline{\mathrm{n}}} = +\), but the second option puts him at risk of terminating the protocol at \(\sigma_{3, s, \overline{\mathrm{n}}} = +\), if the customer is rational and starts a dispute.
+  The customer can do nothing if the SP follows the protocol, which will ultimately put him in the advantaged position \(\operatorname{\sigma_{7, c, n} = +}\), or in case of the SP not following the protocol, the customer can start a dispute and terminate in the non-disadvantaged position \(\operatorname{\sigma_{3, c, \overline{d}} = \sbullet}\).
+\item
+  The SP can follow the protocol and move to the non-disadvantaged position \(\operatorname{\sigma_{3, s, n} = +}\), or not follow the protocol and also end up at the non-disadvantaged position \(\operatorname{\sigma_{3, s, \overline{n}} = +}\), but the second option puts him at risk of terminating the protocol at \(\operatorname{\sigma_{3, s, \overline{n}} = +}\), if the customer is rational and starts a dispute.
 \end{itemize}
@@
   \item
-    \(\sigma_{4, c, \mathrm{n}} = -\), the customer has not received the result, so he remains in the disadvantaged position. 
-  \item
-    \(\sigma_{4, s, \mathrm{n}} = +\), the SP has fulfilled the contract on time.
+    \(\operatorname{\sigma_{4, c, n} = -}\), the customer has not received the result, so he remains in the disadvantaged position. 
+  \item
+    \(\operatorname{\sigma_{4, s, n} = +}\), the SP has fulfilled the contract on time.
   \end{itemize}
@@
   \item
-    \(\sigma_{4, c, \mathrm{d}} = -\), the customer loses the case as the SP has still an opportunity to publish proof of provision within the timeframe. 
-  \item
-    \(\sigma_{4, s, \mathrm{d}} = +\), the SP win the case for the same reason.
+    \(\operatorname{\sigma_{4, c, d} = -}\), the customer loses the case as the SP has still an opportunity to publish proof of provision within the timeframe. 
+  \item
+    \(\operatorname{\sigma_{4, s, d} = +}\), the SP win the case for the same reason.
   \end{itemize}
@@
   \item
-    \(\sigma_{4, c, \overline{\mathrm{n}}} = -\), the customer ends up in the disadvantaged position. 
-  \item
-    \(\sigma_{4, s, \overline{\mathrm{n}}} = +\), the SP ends up in the advantaged position as he received the payment. 
+    \(\operatorname{\sigma_{4, c, \overline{n}} = -}\), the customer ends up in the disadvantaged position. 
+  \item
+    \(\operatorname{\sigma_{4, s, \overline{n}} = +}\), the SP ends up in the advantaged position as he received the payment. 
   \end{itemize}
@@
   \item
-    \(\sigma_{4, c, \overline{\mathrm{d}}} = \sbullet\), the customer wins the case and ends up in a neutral position. 
-  \item
-    \(\sigma_{4, s, \overline{\mathrm{d}}} = -\), the SP loses the case and ends up in the disadvantaged position. 
+    \(\operatorname{\sigma_{4, c, \overline{d}} = \sbullet}\), the customer wins the case and ends up in a neutral position. 
+  \item
+    \(\operatorname{\sigma_{4, s, \overline{d}} = -}\), the SP loses the case and ends up in the disadvantaged position. 
   \end{itemize}
@@
 \item
-  The customer can do nothing if the SP follows the protocol, which will ultimately put him in an advantaged position \(\sigma_{7, c, \mathrm{n}} = +\), or in case of the SP not following the protocol, the customer can start a dispute and terminate in the non-disadvantaged position \(\sigma_{4, c, \overline{\mathrm{d}}} = \sbullet\).
-\item
-  The SP can follow the protocol and move to the non-disadvantaged position \(\sigma_{4, s, \mathrm{n}} = +\), or not follow the protocol and also end up at the non-disadvantaged position \(\sigma_{4, s, \overline{\mathrm{n}}} = +\), but the second option puts him at risk of terminating the protocol at \(\sigma_{4, s, \overline{\mathrm{n}}} = +\), if the customer is rational and starts a dispute.
+  The customer can do nothing if the SP follows the protocol, which will ultimately put him in an advantaged position \(\operatorname{\sigma_{7, c, n} = +}\), or in case of the SP not following the protocol, the customer can start a dispute and terminate in the non-disadvantaged position \(\operatorname{\sigma_{4, c, \overline{d}} = \sbullet}\).
+\item
+  The SP can follow the protocol and move to the non-disadvantaged position \(\operatorname{\sigma_{4, s, n} = +}\), or not follow the protocol and also end up at the non-disadvantaged position \(\operatorname{\sigma_{4, s, \overline{n}} = +}\), but the second option puts him at risk of terminating the protocol at \(\operatorname{\sigma_{4, s, \overline{n}} = +}\), if the customer is rational and starts a dispute.
 \end{itemize}
@@
   \item
-    \(\sigma_{5, c, \mathrm{n}} = -\), the customer has not received the result. Therefore, he remains in the disadvantaged position. 
-  \item
-    \(\sigma_{5, s, \mathrm{n}} = +\), the SP has fulfilled the contract on time.
+    \(\operatorname{\sigma_{5, c, n} = -}\), the customer has not received the result. Therefore, he remains in the disadvantaged position. 
+  \item
+    \(\operatorname{\sigma_{5, s, n} = +}\), the SP has fulfilled the contract on time.
   \end{itemize}
@@
   \item
-    \(\sigma_{5, c, \mathrm{d}} = -\), the customer loses the case as the SP can prove the publication of proof of provision. 
-  \item
-    \(\sigma_{5, s, \mathrm{d}} = +\), the SP win the case for the same reason.
+    \(\operatorname{\sigma_{5, c, d} = -}\), the customer loses the case as the SP can prove the publication of proof of provision. 
+  \item
+    \(\operatorname{\sigma_{5, s, d} = +}\), the SP win the case for the same reason.
   \end{itemize}
@@
   \item
-    \(\sigma_{5, c, \overline{\mathrm{n}}} = -\), the customer ends up in the disadvantaged position.
-  \item
-    \(\sigma_{5, s, \overline{\mathrm{n}}} = +\), the SP ends up in the advantaged position as he received the payment.
+    \(\operatorname{\sigma_{5, c, \overline{n}} = -}\), the customer ends up in the disadvantaged position.
+  \item
+    \(\operatorname{\sigma_{5, s, \overline{n}} = +}\), the SP ends up in the advantaged position as he received the payment.
   \end{itemize}
@@
   \item
-    \(\sigma_{5, c, \overline{\mathrm{d}}} = \sbullet\), the customer wins the case and ends up in the neutral position. 
-  \item
-    \(\sigma_{5, s, \overline{\mathrm{d}}} = -\), the SP loses the case and ends up in the disadvantaged position. 
+    \(\operatorname{\sigma_{5, c, \overline{d}} = \sbullet}\), the customer wins the case and ends up in the neutral position. 
+  \item
+    \(\operatorname{\sigma_{5, s, \overline{d}} = -}\), the SP loses the case and ends up in the disadvantaged position. 
   \end{itemize}
@@
 \item
-  The customer can do nothing if the SP follows the protocol because it will ultimately put him in the advantaged position \(\sigma_{7, c, \mathrm{n}} = +\); otherwise, in case of the SP not following the protocol, the customer can start a dispute and terminate in the non-disadvantaged position.
-  \(\sigma_{5, c, \overline{\mathrm{d}}} = \sbullet\).
-\item
-  The SP can follow the protocol and move to the non-disadvantaged position \(\sigma_{5, s, \mathrm{n}} = +\), or not follow the protocol and also end up at the non-disadvantaged position \(\sigma_{5, s, \overline{\mathrm{n}}} = +\), but the second option puts him at risk of terminating the protocol at \(\sigma_{5, s, \overline{\mathrm{n}}} = +\), if the customer is rational and starts a dispute.
+  The customer can do nothing if the SP follows the protocol because it will ultimately put him in the advantaged position \(\operatorname{\sigma_{7, c, n} = +}\); otherwise, in case of the SP not following the protocol, the customer can start a dispute and terminate in the non-disadvantaged position.
+  \(\operatorname{\sigma_{5, c, \overline{d}} = \sbullet}\).
+\item
+  The SP can follow the protocol and move to the non-disadvantaged position \(\operatorname{\sigma_{5, s, n} = +}\), or not follow the protocol and also end up at the non-disadvantaged position \(\operatorname{\sigma_{5, s, \overline{n}} = +}\), but the second option puts him at risk of terminating the protocol at \(\operatorname{\sigma_{5, s, \overline{n}} = +}\), if the customer is rational and starts a dispute.
 \end{itemize}
@@
   \item
-    \(\sigma_{6, c, \mathrm{n}} = -\), the customer gets a hash of the result but not the result yet.
-  \item
-    \(\sigma_{6, s, \mathrm{n}} = +\), the SP position has not changed.
+    \(\operatorname{\sigma_{6, c, n} = -}\), the customer gets a hash of the result but not the result yet.
+  \item
+    \(\operatorname{\sigma_{6, s, n} = +}\), the SP position has not changed.
   \end{itemize}
@@
   \item
-    \(\sigma_{6, c, \mathrm{d}} = -\), the customer loses the case as the SP can prove the publication of proof of provision. 
-  \item
-    \(\sigma_{6, s, \mathrm{d}} = +\), the SP win the case for the same reason.
+    \(\operatorname{\sigma_{6, c, d} = -}\), the customer loses the case as the SP can prove the publication of proof of provision. 
+  \item
+    \(\operatorname{\sigma_{6, s, d} = +}\), the SP win the case for the same reason.
   \end{itemize}
@@
   \item
-    \(\sigma_{6, c, \overline{\mathrm{n}}} = -\), the customer ends up in the disadvantaged position.
-  \item
-    \(\sigma_{6, s, \overline{\mathrm{n}}} = +\), the SP ends up in the advantaged position as he received the payment but did not spend his resources.
+    \(\operatorname{\sigma_{6, c, \overline{n}} = -}\), the customer ends up in the disadvantaged position.
+  \item
+    \(\operatorname{\sigma_{6, s, \overline{n}} = +}\), the SP ends up in the advantaged position as he received the payment but did not spend his resources.
   \end{itemize}
@@
   \item
-    \(\sigma_{6, c, \overline{\mathrm{d}}} = \sbullet\), the customer wins the case and ends up in the neutral position.
-  \item
-    \(\sigma_{6, s, \overline{\mathrm{d}}} = -\), the SP loses the case and ends up in the disadvantaged position.
+    \(\operatorname{\sigma_{6, c, \overline{d}} = \sbullet}\), the customer wins the case and ends up in the neutral position.
+  \item
+    \(\operatorname{\sigma_{6, s, \overline{d}} = -}\), the SP loses the case and ends up in the disadvantaged position.
   \end{itemize}
@@
 \item
-  The customer can follow the protocol to the position \(\sigma_{6, c, \mathrm{n}} = -\), which lets him move the protocol to the non-disadvantaged termination position \(\sigma_{7, c, \mathrm{n}} = +\), or in case the SP has not followed the protocol start a dispute and win the case \(\sigma_{6, c, \overline{\mathrm{d}}} = \sbullet\).
-\item
-  The SP can do nothing and end up in a non-disadvantaged position \(\sigma_{6, s, \mathrm{n}} = +\), or \(\sigma_{6, s, \overline{\mathrm{n}}} = +\).
+  The customer can follow the protocol to the position \(\operatorname{\sigma_{6, c, n} = -}\), which lets him move the protocol to the non-disadvantaged termination position \(\operatorname{\sigma_{7, c, n} = +}\), or in case the SP has not followed the protocol start a dispute and win the case \(\operatorname{\sigma_{6, c, \overline{d}} = \sbullet}\).
+\item
+  The SP can do nothing and end up in a non-disadvantaged position \(\operatorname{\sigma_{6, s, n} = +}\), or \(\operatorname{\sigma_{6, s, \overline{n}} = +}\).
 \end{itemize}
@@
   \item
-    \(\sigma_{7, c, \mathrm{n}} = +\), the customer gets the correct result. Therefore, he moves to the advantaged position. 
-  \item
-    \(\sigma_{7, s, \mathrm{n}} = +\), the SP position has not changed. 
+    \(\operatorname{\sigma_{7, c, n} = +}\), the customer gets the correct result. Therefore, he moves to the advantaged position. 
+  \item
+    \(\operatorname{\sigma_{7, s, n} = +}\), the SP position has not changed. 
   \end{itemize}
@@
   \item
-    \(\sigma_{7, c, \mathrm{d}} = -\), the customer loses the case as the SP can prove the publication of proof of provision. 
-  \item
-    \(\sigma_{7, s, \mathrm{d}} = +\), the SP win the case for the same reason.
+    \(\operatorname{\sigma_{7, c, d} = -}\), the customer loses the case as the SP can prove the publication of proof of provision. 
+  \item
+    \(\operatorname{\sigma_{7, s, d} = +}\), the SP win the case for the same reason.
   \end{itemize}
@@
   \item
-    \(\sigma_{7, c, \overline{\mathrm{n}}} = -\), the customer ends up in a disadvantaged position, as he ends up with the incorrect result.
-  \item
-    \(\sigma_{7, c, \overline{\mathrm{n}}} = +\), the SP ends up in the advantaged position as he received the payment but did not spend his resources.
+    \(\operatorname{\sigma_{7, c, \overline{n}} = -}\), the customer ends up in a disadvantaged position, as he ends up with the incorrect result.
+  \item
+    \(\operatorname{\sigma_{7, c, \overline{n}} = +}\), the SP ends up in the advantaged position as he received the payment but did not spend his resources.
   \end{itemize}
@@
   \item
-    \(\sigma_{7, c, \overline{\mathrm{d}}} = \sbullet\), the customer wins the case and ends up in the neutral position.
-  \item
-    \(\sigma_{7, c, \overline{\mathrm{d}}} = -\), the SP loses the case and ends up in the disadvantaged position.
+    \(\operatorname{\sigma_{7, c, \overline{d}} = \sbullet}\), the customer wins the case and ends up in the neutral position.
+  \item
+    \(\operatorname{\sigma_{7, c, \overline{d}} = -}\), the SP loses the case and ends up in the disadvantaged position.
   \end{itemize}
@@
 \item
-  The customer can follow the protocol to the non-disadvantaged termination position \(\sigma_{7, c, \mathrm{n}} = +\), or in case the SP has not followed the protocol start a dispute and win the case \(\sigma_{7, c, \overline{\mathrm{d}}} = \sbullet\).
-\item
-  The SP can do nothing and ends up in the non-disadvantaged position \(\sigma_{7, s, \mathrm{n}} = +\).
+  The customer can follow the protocol to the non-disadvantaged termination position \(\operatorname{\sigma_{7, c, n} = +}\), or in case the SP has not followed the protocol start a dispute and win the case \(\operatorname{\sigma_{7, c, \overline{d}} = \sbullet}\).
+\item
+  The SP can do nothing and ends up in the non-disadvantaged position \(\operatorname{\sigma_{7, s, n} = +}\).
 \end{itemize}
@@
 The figure~\ref{fig:misbehaviour} shows the transitions of positions when the SP tries to misbehave and does not execute service after receiving the payment.
-The customer reacts by starting a dispute, and the protocol ends up neutral to the customer and disadvantaged to the SP positions.
+The customer reacts by starting a dispute and the protocol ends up neutral to the customer and disadvantaged to the SP positions.
 
@@
 
-Ultimately, the rational path for both parties is to follow the protocol as shown in the figure~\ref{fig:rational} below.
+Ultimately, the rational path for both parties is to follow the protocol as shown in the figure~\ref{fig:rational}.
 
@@
 
-%\subsection{Results}\label{results}
-
-Using the fariness definition~\ref{fairness} and the assumptions stated in section~\ref{assumptions}, our analysis indicates that the protocol achieves fairness.
+Using the fariness definition~\ref{def:fairness} and the assumptions stated in section~\ref{assumptions}, our analysis indicates that the protocol achieves fairness.
 
@@
 
-The possible directions for mitigation of such issues are to either (1) replace justice with decentralized autonomous organizations (DAO) like proposed in Themis~\cite{meng2019themis} or Kleros~\cite{lesaege2018kleros}; or (2) make it infeasible to provide incorrect results.
+The possible directions for mitigation of such issues are to either (i) replace justice with decentralized autonomous organizations (DAO) like proposed in Themis~\cite{meng2019themis} or Kleros~\cite{lesaege2018kleros}; or (ii) make it infeasible to provide incorrect results.
 
 The first approach is more feasible in the near future.
-It would require creating a large pool of experts in a field that, in case of dispute, would receive all the proofs ($\mathrm{PoD}$, $\mathrm{PoP}$, as well as any other proofs significant to the case) that could be queried by the experts in zero-knowledge fashion, i.e., they could ask a limited number of questions to the proofs and getting yes/no answers.
+It would require creating a large set of experts in a field that, in case of dispute, would receive all the proofs ($\mathrm{PoD}$, $\mathrm{PoP}$, as well as any other proofs significant to the case) that could be queried by the experts in zero-knowledge fashion, i.e., they could ask a limited number of questions to the proofs and getting yes/no answers.
 The case would be fully confidential as they would not be able to query personal information.
@@
 However, the system could be extended to support an anonymous delivery system as proposed in Lelantos~\cite{altawy2017lelantos}.
+One modification to the protocol would be to publish $\mathrm{PoD}$ on the message board, similarly to $\mathrm{PoP}$.
 
@@
 The dispute can be settled by disclosing the collected proofs to justice.
-Using the definition~\ref{fairness} we showed that the protocol achieves fairness by the proof of delivery, payment attestation, and proof of provision published on the message board blockchain.
-Finally, we pinpointed further improvements like decentralized dispute resolution, provable availability of the result, paying with cash, and anonymous delivery via courier.
+Using the definition~\ref{def:fairness} we showed that the protocol achieves fairness by the proof of delivery, payment attestation, and proof of provision published on the message board blockchain.
+Finally, we pinpointed further improvements like decentralized dispute resolution, provable availability of the result, paying with cash, and anonymous package delivery via courier.
 
@@
 \bibliography{bibliography}
-%JS uporządkować bibliografię
 \EOD

### 2022-12-02 paper/access.tex
update paper

--- 2022-03-09 access.tex
@@
 
+\section{Experiments}\label{sec:experiments}
+
+\subsection*{Setup}
+
+We have developed a prototype of our protocol using the following technologies:
+
+\begin{itemize}
+  \item{Anonymous payments} — we use the Monero blockchain \cite{monero-blockchain}.
+  \item{Storage netowork} — we use the Powergate, which is a wrapper around Filecoin and IPFS \cite{ipfs}.
+  \item{Message board} — we use the Ethereum blockchain \cite{ethereum-blockchain}; concretely, Truffle Ganache and Solidity language.
+  \item{Customer and SP} — we create client-side web application (webapp) using React for UI, web3.js for interaction with Ethereum, and crypto-js for encryption.
+We use MetaMask browser extension for signing and submiting transactions to Ethereum's node.
+We use `monerod` and `monero-wallet-cli' command-line tools for interacting with Monero blockchain.
+\end{itemize}
+
+The prototype is available at \url{https://anonser.stan.bar}. The source code is available at \url{https://github.com/stanbar/anonymous-provision-of-services-via-blockchain}.
+
+We developed and tested our prototype in the following environment:
+
+\begin{itemize}
+  \item{OS} — Arch Linux 5.11.8
+  \item{Docker} — 20.10.5
+  \item{CPU} — Intel(R) Core(TM) i7-4790 (8) 4.00~GHz
+  \item{RAM} — 16 GB DDR3
+  \item{Storage} — Samsung PM85 256~GB SSD
+
+  \item{monerod and monero-wallet-cli} — v0.18.1.2-release
+  \item{Powergate} — v0.1.6 // get the version from `docker ps`
+  \item{Ganache} — v7.5.0
+  \item{Solidity} — v0.8.17
+  \item{ReactJS} — v18.0.25
+  \item{web3.js} — v1.8.1
+  \item{crypto-js} — v4.1.1
+\end{itemize}
+
+For simplicity, all components run on one, mentioned above, physical machine; and all processes are managed by Docker.
+
+Moreover, Powergate (storage network) is configured to use local Filecoin and IPFS networks.
+For Ethereum blockchain we use Truffle Ganache, which is a local Ethereum blockchain for development and testing purposes. 
+Monero is configured to use the public stage network.
+
+\subsection*{Experiments}
+
+\paragraph{Preparation}
+
+Both customer and SP create a Monero wallets using `monero-wallet-cli' command-line tool.
+
+Service provider deploys the smart contract using the `truffle migrate --network development` command, which deploys the smart contract to the local Ethereum blockchain.
+The webapp is configured to use the latest deployed smart contract address.
+
+Customer get some testing funds using \url{https://community.rino.io/faucet/stagenet/} faucet service.
+
+Next, the customer enable per-transaction proof generation by setting `set store-tx-info 1` for his wallet.  The proof generation is required to verify the payment in case of dispute.
+
+At this point both the customer and the SP are ready to start the protocol.
+
+\paragraph{Experiment}
+
+Service Provider (SP) and Customer (C) are two different users of our prototype, but for simplicity they use the same machine and the same web application.
+
+Now we describe the experiments we performed to test our protocol.
+
+1. The protocol starts with the Customer opening the webapp and creating new provision. 
+The app generates random ECDSA (secp256k1) client's keypair and random 32 bytes provisionID, then display QR code that encodes both the provisionID and the client's public key. 
+The private key must be stored and provided later for the decryption of the results.
+
+2. The Customer prints the QR code and put it on a package.
+
+3. The Customer delivers his package to the SP either: in person, via trusted party, or delivery agency.
+
+4. The SP opens the app, scans the QR code decoding the provisionID and the client's public key.
+
+5.
+Since (in this experiment) the provision has not been paid in cash, the SP submits a Proof of Delivery transaction to the Ethereum blockchain, indicating that fact setting the `paid` flag to `false`, and `paymentAddress` field with dedicated Monero address using `monero-wallet-cli integrated-address`.
+ If the provision is paid with cash, the SP proceed to the step 8. Otherwise, the SP waits until the Customer pays for the provision.
+
+6. The Customer (using the webapp) check the transaction status on the Ethereum blockchain invoking `getProvision(clientPubKey, provisionID)`.
+
+7. The Customer (using the `monero-wallet-cli transfer`) sends the payment to the designated in the smart contract `paymentAddress` and stores the .
+
+8. The SP starts providing the service and outputs the file `result.pdf`.
+
+9. The SP uploads the file `result.pdf` on the Filecoin and IPFS networks using Powergate. In result, SP gets the content identifier (`cid`), and `dealID`.
+
+10. The SP submits a Proof of Provision transaction to the Ethereum blockchain by invoking `proofOfProvision(clientPubKey, provisionID, cid, dealID)`.
+
+11. Meantime, the Customer subscribes to the Ethereum and waits until the SP publishes the Proof Of Provision.
+ Once the Proof Of Provision is published the Customer downloads the result using either: IPFS network via https://dweb.link/<cid> or Lotus network using `lotus retreive <cid> <minerID>'.
+Then the results are decrypted using previously stored client's private key.
+
 \section{Fairness analysis}\label{sec:fairness-analysis}
@@
 
-Below we describe each step and rationale of the outcome position.
-
-\noindent \textbf
-{Step 1. Customer turn: package delivery}\label{step-1-deliver-package}
-
-The customer has delivered the package:
-
-\begin{itemize}
-\item Agreeable path:
-  \begin{itemize}
-  \item
-    \(\operatorname{\sigma_{1, c, n} = \sbullet}\), the customer has risked its materials but has not paid anything, so we assume he is in the neutral position \footnote{One would argue that the customer has put effort into delivering the materials to the SP or that the sample is valuable.
-We assume that the sample without personal information is useless, and the effort to deliver the package is negligible.}.
-  \item
-    \(\operatorname{\sigma_{1, s, n} = \sbullet}\), the SP is in a neutral position as he did not put any effort, and the package has not brought any value to the SP.
-  \end{itemize}
-\item
-  Starting a dispute:
-
-  \begin{itemize}
-
-  \item
-    \(\operatorname{\sigma_{1, c, d} = -}\), the customer loses the case as the SP has still an opportunity to publish proof of provision within the timeframe.
-  \item
-    \(\operatorname{\sigma_{1, s, d} = \sbullet}\), the SP win the case for the same reason.
-  \end{itemize}
-\end{itemize}
-
-Fairness:
-
-\begin{itemize}
-
-\item
-  The customer can follow the protocol and move to the non-disadvantaged position \(\operatorname{\sigma_{1, c, n} = \sbullet}\).
-\item
-  The SP can do nothing and end up in the non-disadvantaged position \(\operatorname{\sigma_{1, s, n} = \sbullet}\) or \(\operatorname{\sigma_{1, s, d} = \sbullet}\).
-\end{itemize}
-
-\noindent \textbf
-{Step 2. Customer turn: payment}\label{step-2-pay-for-invoice}
-
-The customer has paid the invoice:
-
-\begin{itemize}
-\item
-  Following protocol:
-  \begin{itemize}
-  \item
-    \(\operatorname{\sigma_{2, c, n} = -}\), the customer has spent his funds but has not received the result.
-  \item
-    \(\operatorname{\sigma_{2, s, n} = +}\), the SP has received the payment but has not spent his resources yet.
-  \end{itemize}
-\item
-  Starting a dispute:
-
-  \begin{itemize}
-  \item
-    \(\operatorname{\sigma_{2, c, d} = -}\), the customer loses the case as the SP has still an opportunity to publish proof of provision before the deadline.
-  \item
-    \(\operatorname{\sigma_{2, s, d} = +}\), the SP win the case for the same reason.
-  \end{itemize}
-\end{itemize}
-
-The customer has acted abnormally, then:
-
-\begin{itemize}
-\item
-  Following protocol:
-  \begin{itemize}
-  \item
-    \(\operatorname{\sigma_{2, c, \overline{n}} = \sbullet}\), the customer ends up in the neutral position as he did not spend his funds.
-  \item
-    \(\operatorname{\sigma_{2, s, \overline{n}} = \sbullet}\), the SP ends up in a neutral position as he did not receive the payment, nor spent his resources.
-  \end{itemize}
-\item
-  Starting a dispute:
-
-  \begin{itemize}
-
-  \item
-    \(\operatorname{\sigma_{2, c, \overline{d}} = -}\), the customer loses the case as he can not prove the payment before the time limit.
-  \item
-    \(\operatorname{\sigma_{2, s, \overline{d}} = \sbullet}\), the SP is not charged to justice due to a lack of proof.
-  \end{itemize}
-\end{itemize}
-
-Fairness:
-
-\begin{itemize}
-
-\item
-  The customer can move the protocol forward to step 3, where if the SP follows the protocol then the customer can push the protocol forward up to the last termination step \(\operatorname{\sigma_{7, c, n} = +}\), otherwise if at any step the SP does not follow the protocol the customer can start a dispute which terminates the protocol at the non-disadvantaged position, i.e., \(\operatorname{\sigma_{3, c, \overline{d}} = \sbullet}\), \(\operatorname{\sigma_{4, c, \overline{d}} = \sbullet}\), \(\operatorname{\sigma_{5, c, \overline{d}} = \sbullet}\).
-\item
-  The SP can do nothing and end up in the non-disadvantaged position \(\operatorname{\sigma_{2, s, n} = +}\), \(\operatorname{\sigma_{2, s, d} = +}\), \(\operatorname{\sigma_{2, s, \overline{n}} = \sbullet}\), \(\operatorname{\sigma_{2, s, \overline{d}} = \sbullet}\).
-\end{itemize}
-
-\noindent \textbf
-{Step 3. SP turn: provision of service}
-
-The SP has made the provision of service:
-
-\begin{itemize}
-\item
-  Following protocol:
-
-  \begin{itemize}
-
-  \item
-    \(\operatorname{\sigma_{3, c, \n} = -}\), the customer has not received the result, so he remains in the disadvantaged position. 
-  \item
-    \(\operatorname{\sigma_{3, s, n} = +}\), the SP has fulfilled the contract on time.
-  \end{itemize}
-\item
-  Starting a dispute:
-
-  \begin{itemize}
-
-  \item
-    \(\operatorname{\sigma_{3, c, d} = -}\), the customer loses the case as the SP has still the opportunity to publish proof of provision within the timeframe. 
-  \item
-    \(\operatorname{\sigma_{3, s, d} = +}\), the SP win the case for the same reason.
-  \end{itemize}
-\end{itemize}
-
-The SP has acted abnormally, then:
-
-\begin{itemize}
-\item
-  Following protocol:
-
-  \begin{itemize}
-
-  \item
-    \(\operatorname{\sigma_{3, c, \overline{n}} = -}\), the customer ends up in a disadvantaged position.
-  \item
-    \(\operatorname{\sigma_{3, s, \overline{n}} = +}\), the SP ends up in the advantaged position as he received the payment. 
-  \end{itemize}
-\item
-  Starting a dispute:
-
-  \begin{itemize}
-
-  \item
-    \(\operatorname{\sigma_{3, c, \overline{d}} = \sbullet}\), the customer wins the case and ends up in the neutral position.
-  \item
-    \(\operatorname{\sigma_{3, s, \overline{d}} = -}\), the SP loses the case and ends up in the disadvantaged position. 
-  \end{itemize}
-\end{itemize}
-
-Fairness:
-
-\begin{itemize}
-
-\item
-  The customer can do nothing if the SP follows the protocol, which will ultimately put him in the advantaged position \(\operatorname{\sigma_{7, c, n} = +}\), or in case of the SP not following the protocol, the customer can start a dispute and terminate in the non-disadvantaged position \(\operatorname{\sigma_{3, c, \overline{d}} = \sbullet}\).
-\item
-  The SP can follow the protocol and move to the non-disadvantaged position \(\operatorname{\sigma_{3, s, n} = +}\), or not follow the protocol and also end up at the non-disadvantaged position \(\operatorname{\sigma_{3, s, \overline{n}} = +}\), but the second option puts him at risk of terminating the protocol at \(\operatorname{\sigma_{3, s, \overline{n}} = +}\), if the customer is rational and starts a dispute.
-\end{itemize}
-
-\noindent \textbf
-{Step 4. SP turn: upload result}\label{step-4-publication-of-results}
-
-The SP has uploaded the result on time:
-
-\begin{itemize}
-\item
-  Following protocol:
-
-  \begin{itemize}
-
-  \item
-    \(\operatorname{\sigma_{4, c, n} = -}\), the customer has not received the result, so he remains in the disadvantaged position. 
-  \item
-    \(\operatorname{\sigma_{4, s, n} = +}\), the SP has fulfilled the contract on time.
-  \end{itemize}
-\item
-  Starting a dispute:
-
-  \begin{itemize}
-
-  \item
-    \(\operatorname{\sigma_{4, c, d} = -}\), the customer loses the case as the SP has still an opportunity to publish proof of provision within the timeframe. 
-  \item
-    \(\operatorname{\sigma_{4, s, d} = +}\), the SP win the case for the same reason.
-  \end{itemize}
-\end{itemize}
-
-The SP has acted abnormally, then:
-
-\begin{itemize}
-\item
-  Following protocol:
-
-  \begin{itemize}
-
-  \item
-    \(\operatorname{\sigma_{4, c, \overline{n}} = -}\), the customer ends up in the disadvantaged position. 
-  \item
-    \(\operatorname{\sigma_{4, s, \overline{n}} = +}\), the SP ends up in the advantaged position as he received the payment. 
-  \end{itemize}
-\item
-  Starting a dispute:
-
-  \begin{itemize}
-
-  \item
-    \(\operatorname{\sigma_{4, c, \overline{d}} = \sbullet}\), the customer wins the case and ends up in a neutral position. 
-  \item
-    \(\operatorname{\sigma_{4, s, \overline{d}} = -}\), the SP loses the case and ends up in the disadvantaged position. 
-  \end{itemize}
-\end{itemize}
-
-Fairness:
-
-\begin{itemize}
-
-\item
-  The customer can do nothing if the SP follows the protocol, which will ultimately put him in an advantaged position \(\operatorname{\sigma_{7, c, n} = +}\), or in case of the SP not following the protocol, the customer can start a dispute and terminate in the non-disadvantaged position \(\operatorname{\sigma_{4, c, \overline{d}} = \sbullet}\).
-\item
-  The SP can follow the protocol and move to the non-disadvantaged position \(\operatorname{\sigma_{4, s, n} = +}\), or not follow the protocol and also end up at the non-disadvantaged position \(\operatorname{\sigma_{4, s, \overline{n}} = +}\), but the second option puts him at risk of terminating the protocol at \(\operatorname{\sigma_{4, s, \overline{n}} = +}\), if the customer is rational and starts a dispute.
-\end{itemize}
-
-\noindent \textbf
-{Step 5. SP turn: proof of provision}\label{step-5-publication-of-proof-of-provision}
-
-The SP has published proof of provision on time:
-
-\begin{itemize}
-\item
-  Following protocol:
-
-  \begin{itemize}
-
-  \item
-    \(\operatorname{\sigma_{5, c, n} = -}\), the customer has not received the result. Therefore, he remains in the disadvantaged position. 
-  \item
-    \(\operatorname{\sigma_{5, s, n} = +}\), the SP has fulfilled the contract on time.
-  \end{itemize}
-\item
-  Starting a dispute:
-
-  \begin{itemize}
-
-  \item
-    \(\operatorname{\sigma_{5, c, d} = -}\), the customer loses the case as the SP can prove the publication of proof of provision. 
-  \item
-    \(\operatorname{\sigma_{5, s, d} = +}\), the SP win the case for the same reason.
-  \end{itemize}
-\end{itemize}
-
-The SP has acted abnormally, then:
-
-\begin{itemize}
-\item
-  Following protocol:
-
-  \begin{itemize}
-
-  \item
-    \(\operatorname{\sigma_{5, c, \overline{n}} = -}\), the customer ends up in the disadvantaged position.
-  \item
-    \(\operatorname{\sigma_{5, s, \overline{n}} = +}\), the SP ends up in the advantaged position as he received the payment.
-  \end{itemize}
-\item
-  Starting a dispute:
-
-  \begin{itemize}
-
-  \item
-    \(\operatorname{\sigma_{5, c, \overline{d}} = \sbullet}\), the customer wins the case and ends up in the neutral position. 
-  \item
-    \(\operatorname{\sigma_{5, s, \overline{d}} = -}\), the SP loses the case and ends up in the disadvantaged position. 
-  \end{itemize}
-\end{itemize}
-
-Fairness:
-
-\begin{itemize}
-
-\item
-  The customer can do nothing if the SP follows the protocol because it will ultimately put him in the advantaged position \(\operatorname{\sigma_{7, c, n} = +}\); otherwise, in case of the SP not following the protocol, the customer can start a dispute and terminate in the non-disadvantaged position.
-  \(\operatorname{\sigma_{5, c, \overline{d}} = \sbullet}\).
-\item
-  The SP can follow the protocol and move to the non-disadvantaged position \(\operatorname{\sigma_{5, s, n} = +}\), or not follow the protocol and also end up at the non-disadvantaged position \(\operatorname{\sigma_{5, s, \overline{n}} = +}\), but the second option puts him at risk of terminating the protocol at \(\operatorname{\sigma_{5, s, \overline{n}} = +}\), if the customer is rational and starts a dispute.
-\end{itemize}
-
-\noindent \textbf
-{Step 6. customer turn: pull proof of provision}\label{step-6-pull-proof-of-provision}
-
-The SP has uploaded the result on time, then:
-
-\begin{itemize}
-\item
-  Follows the protocol:
-
-  \begin{itemize}
-
-  \item
-    \(\operatorname{\sigma_{6, c, n} = -}\), the customer gets a hash of the result but not the result yet.
-  \item
-    \(\operatorname{\sigma_{6, s, n} = +}\), the SP position has not changed.
-  \end{itemize}
-\item
-  Starts a dispute:
-
-  \begin{itemize}
-
-  \item
-    \(\operatorname{\sigma_{6, c, d} = -}\), the customer loses the case as the SP can prove the publication of proof of provision. 
-  \item
-    \(\operatorname{\sigma_{6, s, d} = +}\), the SP win the case for the same reason.
-  \end{itemize}
-\end{itemize}
-
-The customer has acted abnormally, then:
-
-\begin{itemize}
-\item
-  Follows the protocol:
-
-  \begin{itemize}
-
-  \item
-    \(\operatorname{\sigma_{6, c, \overline{n}} = -}\), the customer ends up in the disadvantaged position.
-  \item
-    \(\operatorname{\sigma_{6, s, \overline{n}} = +}\), the SP ends up in the advantaged position as he received the payment but did not spend his resources.
-  \end{itemize}
-\item
-  Starts a dispute:
-
-  \begin{itemize}
-
-  \item
-    \(\operatorname{\sigma_{6, c, \overline{d}} = \sbullet}\), the customer wins the case and ends up in the neutral position.
-  \item
-    \(\operatorname{\sigma_{6, s, \overline{d}} = -}\), the SP loses the case and ends up in the disadvantaged position.
-  \end{itemize}
-\end{itemize}
-
-Fairness:
-
-\begin{itemize}
-
-\item
-  The customer can follow the protocol to the position \(\operatorname{\sigma_{6, c, n} = -}\), which lets him move the protocol to the non-disadvantaged termination position \(\operatorname{\sigma_{7, c, n} = +}\), or in case the SP has not followed the protocol start a dispute and win the case \(\operatorname{\sigma_{6, c, \overline{d}} = \sbullet}\).
-\item
-  The SP can do nothing and end up in a non-disadvantaged position \(\operatorname{\sigma_{6, s, n} = +}\), or \(\operatorname{\sigma_{6, s, \overline{n}} = +}\).
-\end{itemize}
-
-\noindent \textbf
-{Step 7. Customer turn: download result}\label{step-7-retrieval-of-results}
-
-The SP has published the correct result on time:
-
-\begin{itemize}
-\item
-  Following protocol:
-
-  \begin{itemize}
-
-  \item
-    \(\operatorname{\sigma_{7, c, n} = +}\), the customer gets the correct result. Therefore, he moves to the advantaged position. 
-  \item
-    \(\operatorname{\sigma_{7, s, n} = +}\), the SP position has not changed. 
-  \end{itemize}
-\item
-  Starting a dispute:
-
-  \begin{itemize}
-
-  \item
-    \(\operatorname{\sigma_{7, c, d} = -}\), the customer loses the case as the SP can prove the publication of proof of provision. 
-  \item
-    \(\operatorname{\sigma_{7, s, d} = +}\), the SP win the case for the same reason.
-  \end{itemize}
-\end{itemize}
-
-The customer has acted abnormally, then:
-
-\begin{itemize}
-\item
-  Following protocol:
-
-  \begin{itemize}
-
-  \item
-    \(\operatorname{\sigma_{7, c, \overline{n}} = -}\), the customer ends up in a disadvantaged position, as he ends up with the incorrect result.
-  \item
-    \(\operatorname{\sigma_{7, c, \overline{n}} = +}\), the SP ends up in the advantaged position as he received the payment but did not spend his resources.
-  \end{itemize}
-\item
-  Starting a dispute:
-
-  \begin{itemize}
-
-  \item
-    \(\operatorname{\sigma_{7, c, \overline{d}} = \sbullet}\), the customer wins the case and ends up in the neutral position.
-  \item
-    \(\operatorname{\sigma_{7, c, \overline{d}} = -}\), the SP loses the case and ends up in the disadvantaged position.
-  \end{itemize}
-\end{itemize}
-
-Fairness:
-
-\begin{itemize}
-
-\item
-  The customer can follow the protocol to the non-disadvantaged termination position \(\operatorname{\sigma_{7, c, n} = +}\), or in case the SP has not followed the protocol start a dispute and win the case \(\operatorname{\sigma_{7, c, \overline{d}} = \sbullet}\).
-\item
-  The SP can do nothing and ends up in the non-disadvantaged position \(\operatorname{\sigma_{7, s, n} = +}\).
-\end{itemize}
+The description of each step and the rationale of the outcome position is given in the appendix in section \ref{sec:proof-of-fairness}.
 
@@
 
+\section*{Appendix A: Proof of fairness}\label{sec:proof-of-fairness}
+Below we describe each step and rationale of the outcome position.
+
+\noindent \textbf
+{Step 1. Customer turn: package delivery}\label{step-1-deliver-package}
+
+The customer has delivered the package:
+
+\begin{itemize}
+\item Agreeable path:
+  \begin{itemize}
+  \item
+    \(\operatorname{\sigma_{1, c, n} = \sbullet}\), the customer has risked its materials but has not paid anything, so we assume he is in the neutral position \footnote{One would argue that the customer has put effort into delivering the materials to the SP or that the sample is valuable.
+We assume that the sample without personal information is useless, and the effort to deliver the package is negligible.}.
+  \item
+    \(\operatorname{\sigma_{1, s, n} = \sbullet}\), the SP is in a neutral position as he did not put any effort, and the package has not brought any value to the SP.
+  \end{itemize}
+\item
+  Starting a dispute:
+
+  \begin{itemize}
+
+  \item
+    \(\operatorname{\sigma_{1, c, d} = -}\), the customer loses the case as the SP has still an opportunity to publish proof of provision within the timeframe.
+  \item
+    \(\operatorname{\sigma_{1, s, d} = \sbullet}\), the SP win the case for the same reason.
+  \end{itemize}
+\end{itemize}
+
+Fairness:
+
+\begin{itemize}
+
+\item
+  The customer can follow the protocol and move to the non-disadvantaged position \(\operatorname{\sigma_{1, c, n} = \sbullet}\).
+\item
+  The SP can do nothing and end up in the non-disadvantaged position \(\operatorname{\sigma_{1, s, n} = \sbullet}\) or \(\operatorname{\sigma_{1, s, d} = \sbullet}\).
+\end{itemize}
+
+\noindent \textbf
+{Step 2. Customer turn: payment}\label{step-2-pay-for-invoice}
+
+The customer has paid the invoice:
+
+\begin{itemize}
+\item
+  Following protocol:
+  \begin{itemize}
+  \item
+    \(\operatorname{\sigma_{2, c, n} = -}\), the customer has spent his funds but has not received the result.
+  \item
+    \(\operatorname{\sigma_{2, s, n} = +}\), the SP has received the payment but has not spent his resources yet.
+  \end{itemize}
+\item
+  Starting a dispute:
+
+  \begin{itemize}
+  \item
+    \(\operatorname{\sigma_{2, c, d} = -}\), the customer loses the case as the SP has still an opportunity to publish proof of provision before the deadline.
+  \item
+    \(\operatorname{\sigma_{2, s, d} = +}\), the SP win the case for the same reason.
+  \end{itemize}
+\end{itemize}
+
+The customer has acted abnormally, then:
+
+\begin{itemize}
+\item
+  Following protocol:
+  \begin{itemize}
+  \item
+    \(\operatorname{\sigma_{2, c, \overline{n}} = \sbullet}\), the customer ends up in the neutral position as he did not spend his funds.
+  \item
+    \(\operatorname{\sigma_{2, s, \overline{n}} = \sbullet}\), the SP ends up in a neutral position as he did not receive the payment, nor spent his resources.
+  \end{itemize}
+\item
+  Starting a dispute:
+
+  \begin{itemize}
+
+  \item
+    \(\operatorname{\sigma_{2, c, \overline{d}} = -}\), the customer loses the case as he can not prove the payment before the time limit.
+  \item
+    \(\operatorname{\sigma_{2, s, \overline{d}} = \sbullet}\), the SP is not charged to justice due to a lack of proof.
+  \end{itemize}
+\end{itemize}
+
+Fairness:
+
+\begin{itemize}
+
+\item
+  The customer can move the protocol forward to step 3, where if the SP follows the protocol then the customer can push the protocol forward up to the last termination step \(\operatorname{\sigma_{7, c, n} = +}\), otherwise if at any step the SP does not follow the protocol the customer can start a dispute which terminates the protocol at the non-disadvantaged position, i.e., \(\operatorname{\sigma_{3, c, \overline{d}} = \sbullet}\), \(\operatorname{\sigma_{4, c, \overline{d}} = \sbullet}\), \(\operatorname{\sigma_{5, c, \overline{d}} = \sbullet}\).
+\item
+  The SP can do nothing and end up in the non-disadvantaged position \(\operatorname{\sigma_{2, s, n} = +}\), \(\operatorname{\sigma_{2, s, d} = +}\), \(\operatorname{\sigma_{2, s, \overline{n}} = \sbullet}\), \(\operatorname{\sigma_{2, s, \overline{d}} = \sbullet}\).
+\end{itemize}
+
+\noindent \textbf
+{Step 3. SP turn: provision of service}
+
+The SP has made the provision of service:
+
+\begin{itemize}
+\item
+  Following protocol:
+
+  \begin{itemize}
+
+  \item
+    \(\operatorname{\sigma_{3, c, \n} = -}\), the customer has not received the result, so he remains in the disadvantaged position. 
+  \item
+    \(\operatorname{\sigma_{3, s, n} = +}\), the SP has fulfilled the contract on time.
+  \end{itemize}
+\item
+  Starting a dispute:
+
+  \begin{itemize}
+
+  \item
+    \(\operatorname{\sigma_{3, c, d} = -}\), the customer loses the case as the SP has still the opportunity to publish proof of provision within the timeframe. 
+  \item
+    \(\operatorname{\sigma_{3, s, d} = +}\), the SP win the case for the same reason.
+  \end{itemize}
+\end{itemize}
+
+The SP has acted abnormally, then:
+
+\begin{itemize}
+\item
+  Following protocol:
+
+  \begin{itemize}
+
+  \item
+    \(\operatorname{\sigma_{3, c, \overline{n}} = -}\), the customer ends up in a disadvantaged position.
+  \item
+    \(\operatorname{\sigma_{3, s, \overline{n}} = +}\), the SP ends up in the advantaged position as he received the payment. 
+  \end{itemize}
+\item
+  Starting a dispute:
+
+  \begin{itemize}
+
+  \item
+    \(\operatorname{\sigma_{3, c, \overline{d}} = \sbullet}\), the customer wins the case and ends up in the neutral position.
+  \item
+    \(\operatorname{\sigma_{3, s, \overline{d}} = -}\), the SP loses the case and ends up in the disadvantaged position. 
+  \end{itemize}
+\end{itemize}
+
+Fairness:
+
+\begin{itemize}
+
+\item
+  The customer can do nothing if the SP follows the protocol, which will ultimately put him in the advantaged position \(\operatorname{\sigma_{7, c, n} = +}\), or in case of the SP not following the protocol, the customer can start a dispute and terminate in the non-disadvantaged position \(\operatorname{\sigma_{3, c, \overline{d}} = \sbullet}\).
+\item
+  The SP can follow the protocol and move to the non-disadvantaged position \(\operatorname{\sigma_{3, s, n} = +}\), or not follow the protocol and also end up at the non-disadvantaged position \(\operatorname{\sigma_{3, s, \overline{n}} = +}\), but the second option puts him at risk of terminating the protocol at \(\operatorname{\sigma_{3, s, \overline{n}} = +}\), if the customer is rational and starts a dispute.
+\end{itemize}
+
+\noindent \textbf
+{Step 4. SP turn: upload result}\label{step-4-publication-of-results}
+
+The SP has uploaded the result on time:
+
+\begin{itemize}
+\item
+  Following protocol:
+
+  \begin{itemize}
+
+  \item
+    \(\operatorname{\sigma_{4, c, n} = -}\), the customer has not received the result, so he remains in the disadvantaged position. 
+  \item
+    \(\operatorname{\sigma_{4, s, n} = +}\), the SP has fulfilled the contract on time.
+  \end{itemize}
+\item
+  Starting a dispute:
+
+  \begin{itemize}
+
+  \item
+    \(\operatorname{\sigma_{4, c, d} = -}\), the customer loses the case as the SP has still an opportunity to publish proof of provision within the timeframe. 
+  \item
+    \(\operatorname{\sigma_{4, s, d} = +}\), the SP win the case for the same reason.
+  \end{itemize}
+\end{itemize}
+
+The SP has acted abnormally, then:
+
+\begin{itemize}
+\item
+  Following protocol:
+
+  \begin{itemize}
+
+  \item
+    \(\operatorname{\sigma_{4, c, \overline{n}} = -}\), the customer ends up in the disadvantaged position. 
+  \item
+    \(\operatorname{\sigma_{4, s, \overline{n}} = +}\), the SP ends up in the advantaged position as he received the payment. 
+  \end{itemize}
+\item
+  Starting a dispute:
+
+  \begin{itemize}
+
+  \item
+    \(\operatorname{\sigma_{4, c, \overline{d}} = \sbullet}\), the customer wins the case and ends up in a neutral position. 
+  \item
+    \(\operatorname{\sigma_{4, s, \overline{d}} = -}\), the SP loses the case and ends up in the disadvantaged position. 
+  \end{itemize}
+\end{itemize}
+
+Fairness:
+
+\begin{itemize}
+
+\item
+  The customer can do nothing if the SP follows the protocol, which will ultimately put him in an advantaged position \(\operatorname{\sigma_{7, c, n} = +}\), or in case of the SP not following the protocol, the customer can start a dispute and terminate in the non-disadvantaged position \(\operatorname{\sigma_{4, c, \overline{d}} = \sbullet}\).
+\item
+  The SP can follow the protocol and move to the non-disadvantaged position \(\operatorname{\sigma_{4, s, n} = +}\), or not follow the protocol and also end up at the non-disadvantaged position \(\operatorname{\sigma_{4, s, \overline{n}} = +}\), but the second option puts him at risk of terminating the protocol at \(\operatorname{\sigma_{4, s, \overline{n}} = +}\), if the customer is rational and starts a dispute.
+\end{itemize}
+
+\noindent \textbf
+{Step 5. SP turn: proof of provision}\label{step-5-publication-of-proof-of-provision}
+
+The SP has published proof of provision on time:
+
+\begin{itemize}
+\item
+  Following protocol:
+
+  \begin{itemize}
+
+  \item
+    \(\operatorname{\sigma_{5, c, n} = -}\), the customer has not received the result. Therefore, he remains in the disadvantaged position. 
+  \item
+    \(\operatorname{\sigma_{5, s, n} = +}\), the SP has fulfilled the contract on time.
+  \end{itemize}
+\item
+  Starting a dispute:
+
+  \begin{itemize}
+
+  \item
+    \(\operatorname{\sigma_{5, c, d} = -}\), the customer loses the case as the SP can prove the publication of proof of provision. 
+  \item
+    \(\operatorname{\sigma_{5, s, d} = +}\), the SP win the case for the same reason.
+  \end{itemize}
+\end{itemize}
+
+The SP has acted abnormally, then:
+
+\begin{itemize}
+\item
+  Following protocol:
+
+  \begin{itemize}
+
+  \item
+    \(\operatorname{\sigma_{5, c, \overline{n}} = -}\), the customer ends up in the disadvantaged position.
+  \item
+    \(\operatorname{\sigma_{5, s, \overline{n}} = +}\), the SP ends up in the advantaged position as he received the payment.
+  \end{itemize}
+\item
+  Starting a dispute:
+
+  \begin{itemize}
+
+  \item
+    \(\operatorname{\sigma_{5, c, \overline{d}} = \sbullet}\), the customer wins the case and ends up in the neutral position. 
+  \item
+    \(\operatorname{\sigma_{5, s, \overline{d}} = -}\), the SP loses the case and ends up in the disadvantaged position. 
+  \end{itemize}
+\end{itemize}
+
+Fairness:
+
+\begin{itemize}
+
+\item
+  The customer can do nothing if the SP follows the protocol because it will ultimately put him in the advantaged position \(\operatorname{\sigma_{7, c, n} = +}\); otherwise, in case of the SP not following the protocol, the customer can start a dispute and terminate in the non-disadvantaged position.
+  \(\operatorname{\sigma_{5, c, \overline{d}} = \sbullet}\).
+\item
+  The SP can follow the protocol and move to the non-disadvantaged position \(\operatorname{\sigma_{5, s, n} = +}\), or not follow the protocol and also end up at the non-disadvantaged position \(\operatorname{\sigma_{5, s, \overline{n}} = +}\), but the second option puts him at risk of terminating the protocol at \(\operatorname{\sigma_{5, s, \overline{n}} = +}\), if the customer is rational and starts a dispute.
+\end{itemize}
+
+\noindent \textbf
+{Step 6. customer turn: pull proof of provision}\label{step-6-pull-proof-of-provision}
+
+The SP has uploaded the result on time, then:
+
+\begin{itemize}
+\item
+  Follows the protocol:
+
+  \begin{itemize}
+
+  \item
+    \(\operatorname{\sigma_{6, c, n} = -}\), the customer gets a hash of the result but not the result yet.
+  \item
+    \(\operatorname{\sigma_{6, s, n} = +}\), the SP position has not changed.
+  \end{itemize}
+\item
+  Starts a dispute:
+
+  \begin{itemize}
+
+  \item
+    \(\operatorname{\sigma_{6, c, d} = -}\), the customer loses the case as the SP can prove the publication of proof of provision. 
+  \item
+    \(\operatorname{\sigma_{6, s, d} = +}\), the SP win the case for the same reason.
+  \end{itemize}
+\end{itemize}
+
+The customer has acted abnormally, then:
+
+\begin{itemize}
+\item
+  Follows the protocol:
+
+  \begin{itemize}
+
+  \item
+    \(\operatorname{\sigma_{6, c, \overline{n}} = -}\), the customer ends up in the disadvantaged position.
+  \item
+    \(\operatorname{\sigma_{6, s, \overline{n}} = +}\), the SP ends up in the advantaged position as he received the payment but did not spend his resources.
+  \end{itemize}
+\item
+  Starts a dispute:
+
+  \begin{itemize}
+
+  \item
+    \(\operatorname{\sigma_{6, c, \overline{d}} = \sbullet}\), the customer wins the case and ends up in the neutral position.
+  \item
+    \(\operatorname{\sigma_{6, s, \overline{d}} = -}\), the SP loses the case and ends up in the disadvantaged position.
+  \end{itemize}
+\end{itemize}
+
+Fairness:
+
+\begin{itemize}
+
+\item
+  The customer can follow the protocol to the position \(\operatorname{\sigma_{6, c, n} = -}\), which lets him move the protocol to the non-disadvantaged termination position \(\operatorname{\sigma_{7, c, n} = +}\), or in case the SP has not followed the protocol start a dispute and win the case \(\operatorname{\sigma_{6, c, \overline{d}} = \sbullet}\).
+\item
+  The SP can do nothing and end up in a non-disadvantaged position \(\operatorname{\sigma_{6, s, n} = +}\), or \(\operatorname{\sigma_{6, s, \overline{n}} = +}\).
+\end{itemize}
+
+\noindent \textbf
+{Step 7. Customer turn: download result}\label{step-7-retrieval-of-results}
+
+The SP has published the correct result on time:
+
+\begin{itemize}
+\item
+  Following protocol:
+
+  \begin{itemize}
+
+  \item
+    \(\operatorname{\sigma_{7, c, n} = +}\), the customer gets the correct result. Therefore, he moves to the advantaged position. 
+  \item
+    \(\operatorname{\sigma_{7, s, n} = +}\), the SP position has not changed. 
+  \end{itemize}
+\item
+  Starting a dispute:
+
+  \begin{itemize}
+
+  \item
+    \(\operatorname{\sigma_{7, c, d} = -}\), the customer loses the case as the SP can prove the publication of proof of provision. 
+  \item
+    \(\operatorname{\sigma_{7, s, d} = +}\), the SP win the case for the same reason.
+  \end{itemize}
+\end{itemize}
+
+The customer has acted abnormally, then:
+
+\begin{itemize}
+\item
+  Following protocol:
+
+  \begin{itemize}
+
+  \item
+    \(\operatorname{\sigma_{7, c, \overline{n}} = -}\), the customer ends up in a disadvantaged position, as he ends up with the incorrect result.
+  \item
+    \(\operatorname{\sigma_{7, c, \overline{n}} = +}\), the SP ends up in the advantaged position as he received the payment but did not spend his resources.
+  \end{itemize}
+\item
+  Starting a dispute:
+
+  \begin{itemize}
+
+  \item
+    \(\operatorname{\sigma_{7, c, \overline{d}} = \sbullet}\), the customer wins the case and ends up in the neutral position.
+  \item
+    \(\operatorname{\sigma_{7, c, \overline{d}} = -}\), the SP loses the case and ends up in the disadvantaged position.
+  \end{itemize}
+\end{itemize}
+
+Fairness:
+
+\begin{itemize}
+
+\item
+  The customer can follow the protocol to the non-disadvantaged termination position \(\operatorname{\sigma_{7, c, n} = +}\), or in case the SP has not followed the protocol start a dispute and win the case \(\operatorname{\sigma_{7, c, \overline{d}} = \sbullet}\).
+\item
+  The SP can do nothing and ends up in the non-disadvantaged position \(\operatorname{\sigma_{7, s, n} = +}\).
+\end{itemize}
+
 \end{document}

### 2022-12-02 paper/access.tex
update paper

@@
 \usepackage{caption}
+\usepackage{url}
+\usepackage{amsmath}
 \usepackage[english]{babel}
@@
 
-Providing personal information exposes users to privacy risks, i.e. potential loss of control over personal
-information~\cite{smith2011information}.
+Providing personal information exposes users to privacy risks, i.e. potential loss of control over personal information~\cite{smithInformationPrivacyResearch2011}.
 
@@
 For example, by reselling it to marketers, financial institutions, other businesses, government agencies, or even cybercriminals.
-Which in turn can lead to profiled advertisements or criminal activities like identity theft or illegal tracking and surveillance~\cite{smith2011information}.
+Which in turn can lead to profiled advertisements or criminal activities like identity theft or illegal tracking and surveillance~\cite{smithInformationPrivacyResearch2011}.
 
@@
 Some authors have proposed blockchain-based fair-exchange systems that could be adapted to service provision; however, to our best knowledge, we are the first to propose a system that satisfies all five properties stated above using blockchain technology.
-Especially anonymity and physical materials delivery were rarely addressed together, and if so, the protocol was based on TTP and strong and impractical assumptions on banking system~\cite{birjoveanu2015anonymity} or did not address the conflict
-between parties~\cite{altawy2017lelantos}.
+Especially anonymity and physical materials delivery were rarely addressed together, and if so, the protocol was based on TTP and strong and impractical assumptions on banking system~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} or did not address the conflict
+between parties~\cite{altawyLelantosBlockchainBasedAnonymous2017}.
 
@@
 
-Authors of ~\cite{hinarejos2019solution} replaced the TTP with blockchain (concretely Bitcoin blockchain as a reference implementation) that acts as a secure, verifiable, and decentralized TTP.
+Authors of ~\cite{hinarejosSolutionSecureCertified2019} replaced the TTP with blockchain (concretely Bitcoin blockchain as a reference implementation) that acts as a secure, verifiable, and decentralized TTP.
 
@@
 
-Authors of~\cite{birjoveanu2015anonymity} proposed a
+Authors of~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} proposed a
 fair exchange of physical products and electronic payment protocol that
@@
 
-Themis~\cite{meng2019themis} is a fair exchange protocol that uses blockchain instead of TTP.
+Themis~\cite{mengThemisDecentralizedEscrow2019} is a fair exchange protocol that uses blockchain instead of TTP.
 It provides an escrow service for the secure exchange of cryptocurrencies and digital goods.
@@
 
-Lelanros~\cite{altawy2017lelantos} is a blockchain-based anonymous
+Lelanros~\cite{altawyLelantosBlockchainBasedAnonymous2017} is a blockchain-based anonymous
 physical delivery system.
@@
 
-Themis~\cite{meng2019themis} besides providing fair exchange protocol,
+Themis~\cite{mengThemisDecentralizedEscrow2019} besides providing fair exchange protocol,
 also offers a semi-autonomous decentralized dispute resolution system that complies with the Web3 postulates of a decentralized web. Themis
@@
 
-Kleros~\cite{lesaege2018kleros} is a smart contract deployed on the Ethereum platform that mimics in a decentralized and autonomous way how the court works in real life.
+Kleros~\cite{bergollaKlerosSociolegalCase2022} is a smart contract deployed on the Ethereum platform that mimics in a decentralized and autonomous way how the court works in real life.
 In Kleros, every process of a dispute like gathering evidence, selecting jurors, rewarding the winning party is automated by a set of smart contracts.
@@
 \subsection{Message Board}\label{sec:message-board}
-The proof of provision that we coined for the purpose of this protocol is generally called the proof of existence
-\cite{proofofexistence, de2016stampery, Chainpoi39}.
+The proof of provision that we coined for the purpose of this protocol is generally called the proof of existence~\cite{ProofExistenceOnline, crespoStamperyBlockchainTimestamping2017, ChainpointBlockchainProof}.
 
@@
 
-Depending on the context the platform of achieving it is called bulletin board~\cite{achenbach2015improved}, trusted timestamping~\cite{gipp2015decentralized}, or message board~\cite{hinarejos2019solution}.
+Depending on the context the platform of achieving it is called bulletin board~\cite{achenbachImprovedCoercionresistantElectronic2015}, trusted timestamping~\cite{gippDecentralizedTrustedTimestamping2015}, or message board~\cite{hinarejosSolutionSecureCertified2019}.
 In this work, we call it a message board.
@@
 Privacy is a concept used in almost all social sciences like philosophy, psychology, sociology, and legal.
-The multidisciplinary nature leads to ambiguous definitions~\cite{smith2011information}.
+The multidisciplinary nature leads to ambiguous definitions~\cite{smithInformationPrivacyResearch2011}.
 For our work, we rely on more concrete definitions, i.e.~confidentality and anonymity.
@@
 However, anonymity is a spectrum rather than a dichotomous classification.
-One method of quantifying the level of anonymity is \textit{k}-anonymity proposed in~\cite{sweeney2002k}.
+One method of quantifying the level of anonymity is \textit{k}-anonymity proposed in~\cite{sweeneyKanonymityModelProtecting2002}.
 It measures the user's anonymity by the number of other users from whom the user can not be distinguished.
@@
 This assumption is hard to satisfy in practice, as the KYC (Know Your Customer) and AML (Anti Money Laundering) regulations require users to reveal their real identity to cryptocurrencies exchanges, making the user's anonymity dependent on the security of the IT system.
-Moreover, some correlations can be inferred merely by the analysis of transactions \cite{androulaki2013evaluating, ober2013structure}.
+Moreover, some correlations can be inferred merely by the analysis of transactions \cite{androulakiEvaluatingUserPrivacy2013, oberStructureAnonymityBitcoin2013}.
 
@@
 
-Examples of blockchains that natively support confidential transactions are: Monero~\cite{van2013cryptonote} (via Ring Signatures~\cite{cryptoeprint:2015:1098} and Bulletproofs~\cite{Bulletpr14, bunz2018bulletproofs}), ZCash~\cite{sasson2014zerocash} (via zkSNARK~\cite{ben2013snarks}), and Grin~\cite{fuchsbauer2019aggregate} (via Mimblewimble~\cite{httpsdow19}).
-
-Overly techniques that achieve anonymity on top of non-privacy-preserving blockchains are: Ethereum's Tornado Cash\cite{pertsev2019tornado} (via zkSNARK~\cite{groth2016size} and MiMC~\cite{albrecht2016mimc}), Bitcoin's Wasabi\cite{WasabiWa56} (via CoinJoin \cite{CoinJoin41}).
+Examples of blockchains that natively support confidential transactions are: Monero~\cite{vansaberhagenCryptoNote2013} (via Ring Signatures~\cite{noetherRingSignatureConfidential2015} and Bulletproofs~\cite{moneroBulletproofsMoneropediaMonero, bunzBulletproofsShortProofs2018}), ZCash~\cite{ben-sassonZerocashDecentralizedAnonymous2014} (via zkSNARK~\cite{ben-sassonSNARKsVerifyingProgram2013}), and Grin~\cite{fuchsbauerAggregateCashSystems2019} (via Mimblewimble~\cite{jedusorMIMBLEWIMBLE2016}).
+
+Overly techniques that achieve anonymity on top of non-privacy-preserving blockchains are: Ethereum's Tornado Cash\cite{pertsevTornadoCashPrivacy2019} (via zkSNARK~\cite{grothSizePairingbasedNoninteractive2016} and MiMC~\cite{albrechtMiMCEfficientEncryption2016}), Bitcoin's Wasabi\footnote{https://wasabiwallet.io/} (via CoinJoin \cite{maxwellCoinJoinBitcoinPrivacy2013}).
 
@@
 \item separate address: each transaction derives a new address uniquely associated with the transaction.
-Such addresses can be derived using Hierarchical Deterministic Wallets (BIP-32)~\cite{bipsbip089}.
+Such addresses can be derived using Hierarchical Deterministic Wallets (BIP-32)\footnote{https://github.com/bitcoin/bips/blob/master/bip-0032.mediawiki}.
 \item memo: the payments are sent to one SP account but contain an extra field named ``memo'' filled with the unique number provided by the SP in $\mathrm{PoD}$.
@@
 As the proof of transaction is trivial in transparent and trackable blockchains, it gets more complicated when it comes to anonymous blockchains.
-Monero allows proving and checking payments via dedicated API \cite{Howtopro46}.
-ZCash provides a mechanism called Payment Disclosure \cite{AnIntrod25}.
+Monero allows proving and checking payments via dedicated API \cite{MoneroHowProve}.
+ZCash provides a mechanism called Payment Disclosure \cite{daviesIntroductionPaymentDisclosure2017}.
 
@@
 However, storing data on a blockchain is very expensive.
-The most common workaround (\cite{shahid2020blockchain, wang2019auditable, chen2017improved, Usageide95}) is to publish the data on a content addressable peer-to-peer storage network like IPFS~\cite{benet2014ipfs}.
+The most common workaround (\cite{shahidBlockchainBasedAgriFoodSupply2020, wangAuditableProtocolsFair2019, chenImprovedP2PFile2017}) is to publish the data on a content addressable peer-to-peer storage network like IPFS~\cite{benetIPFSContentAddressed2014}.
 Then, publish on the blockchain just the content identifier ($\mathrm{cid}$) that uniquely points to the content stored on IPFS.
@@
 
-\item Anonymous payments: Monero \cite{van2013cryptonote}, ZCash
-  \cite{sasson2014zerocash}, Grin \cite{fuchsbauer2019aggregate},
-  Tornado Cash \cite{pertsev2019tornado}.
-\item Message board: Stampery \cite{de2016stampery}, Proof of Existence
-  \cite{proofofexistence} (Bitcoin blockchain), Chainpoint
-  \cite{Chainpoi39} (Bitcoin blockchain), or any other blockchain that
+\item Anonymous payments: Monero \cite{vansaberhagenCryptoNote2013}, ZCash
+  \cite{ben-sassonZerocashDecentralizedAnonymous2014}, Grin \cite{fuchsbauerAggregateCashSystems2019},
+  Tornado Cash \cite{pertsevTornadoCashPrivacy2019}.
+\item Message board: Stampery \cite{crespoStamperyBlockchainTimestamping2017}, Proof of Existence
+  \cite{ProofExistenceOnline} (Bitcoin blockchain), Chainpoint
+  \cite{ChainpointBlockchainProof} (Bitcoin blockchain), or any other blockchain that
   supports attaching extra data along the transaction.
-\item Storage network: IPFS \cite{benet2014ipfs}, Filecoin
-  \cite{benetfilecoin} (runs on top of IPFS), or Ethereum's
-  Swarm\cite{swarmwhi49}.
+\item Storage network: IPFS \cite{benetIPFSContentAddressed2014}, Filecoin
+  \cite{protocollabsFilecoinDecentralizedStorage2017} (runs on top of IPFS), or Ethereum's
+  Swarm\cite{teamSWARMStorageCommunication2021}.
 \end{enumerate}
@@
 \noindent \textbf
-{Content Identifier (cid)}\label{content-identifier-cid}  is a term coined by IPFS~\cite{Contenta59}. However, since our protocol does not depend on
+{Content Identifier (cid)}\label{content-identifier-cid} is a term coined by IPFS\footnote{https://docs.ipfs.tech/concepts/content-addressing}. However, since our protocol does not depend on
 this particular implementation of the storage network, we let the $\mathrm{cid}$ be any other identifier that securely and uniquely points to the content.
@@
 \begin{itemize}
-  \item{Anonymous payments} — we use the Monero blockchain \cite{monero-blockchain}.
-  \item{Storage netowork} — we use the Powergate, which is a wrapper around Filecoin and IPFS \cite{ipfs}.
-  \item{Message board} — we use the Ethereum blockchain \cite{ethereum-blockchain}; concretely, Truffle Ganache and Solidity language.
+  \item{Anonymous payments} — we use the Monero blockchain \cite{noetherRingSignatureConfidential2015}.
+  \item{Storage netowork} — we use the Powergate\footnote{https://github.com/textileio/powergate}, which is a wrapper around Filecoin and IPFS.
+  \item{Message board} — we use the Ethereum blockchain \cite{woodEthereumSecureDecentralised2014}; concretely, Truffle Ganache\footnote{https://trufflesuite.com/ganache/} and Solidity language.
   \item{Customer and SP} — we create client-side web application (webapp) using React for UI, web3.js for interaction with Ethereum, and crypto-js for encryption.
@@
 
-Moreover, Powergate (storage network) is configured to use local Filecoin and IPFS networks.
+Moreover, Powergate is configured to use local Filecoin and IPFS networks.
 For Ethereum blockchain we use Truffle Ganache, which is a local Ethereum blockchain for development and testing purposes. 
@@
 
-1. The protocol starts with the Customer opening the webapp and creating new provision. 
+\begin{itemize}
+  \item 1. The protocol starts with the Customer opening the webapp and creating new provision. 
 The app generates random ECDSA (secp256k1) client's keypair and random 32 bytes provisionID, then display QR code that encodes both the provisionID and the client's public key. 
@@
 
-2. The Customer prints the QR code and put it on a package.
-
-3. The Customer delivers his package to the SP either: in person, via trusted party, or delivery agency.
-
-4. The SP opens the app, scans the QR code decoding the provisionID and the client's public key.
-
-5.
+  \item 2. The Customer prints the QR code and put it on a package.
+
+  \item 3. The Customer delivers his package to the SP either: in person, via trusted party, or delivery agency.
+
+  \item 4. The SP opens the app, scans the QR code decoding the provisionID and the client's public key.
+
+  \item 5.
 Since (in this experiment) the provision has not been paid in cash, the SP submits a Proof of Delivery transaction to the Ethereum blockchain, indicating that fact setting the `paid` flag to `false`, and `paymentAddress` field with dedicated Monero address using `monero-wallet-cli integrated-address`.
@@
 
-6. The Customer (using the webapp) check the transaction status on the Ethereum blockchain invoking `getProvision(clientPubKey, provisionID)`.
-
-7. The Customer (using the `monero-wallet-cli transfer`) sends the payment to the designated in the smart contract `paymentAddress` and stores the .
-
-8. The SP starts providing the service and outputs the file `result.pdf`.
-
-9. The SP uploads the file `result.pdf` on the Filecoin and IPFS networks using Powergate. In result, SP gets the content identifier (`cid`), and `dealID`.
-
-10. The SP submits a Proof of Provision transaction to the Ethereum blockchain by invoking `proofOfProvision(clientPubKey, provisionID, cid, dealID)`.
-
-11. Meantime, the Customer subscribes to the Ethereum and waits until the SP publishes the Proof Of Provision.
+  \item 6. The Customer (using the webapp) check the transaction status on the Ethereum blockchain invoking `getProvision(clientPubKey, provisionID)`.
+
+  \item 7. The Customer (using the `monero-wallet-cli transfer`) sends the payment to the designated in the smart contract `paymentAddress` and stores the .
+
+  \item 8. The SP starts providing the service and outputs the file `result.pdf`.
+
+  \item 9. The SP uploads the file `result.pdf` on the Filecoin and IPFS networks using Powergate. In result, SP gets the content identifier (`cid`), and `dealID`.
+
+  \item 10. The SP submits a Proof of Provision transaction to the Ethereum blockchain by invoking `proofOfProvision(clientPubKey, provisionID, cid, dealID)`.
+
+  \item 11. Meantime, the Customer subscribes to the Ethereum and waits until the SP publishes the Proof Of Provision.
  Once the Proof Of Provision is published the Customer downloads the result using either: IPFS network via https://dweb.link/<cid> or Lotus network using `lotus retreive <cid> <minerID>'.
 Then the results are decrypted using previously stored client's private key.
+
+\end{itemize}
 
@@
 
-Justice is the biggest obstacle in achieving a system that complies with Web3 postulates~\cite{Web3Wiki71}.
-
-The possible directions for mitigation of such issues are to either (i) replace justice with decentralized autonomous organizations (DAO) like proposed in Themis~\cite{meng2019themis} or Kleros~\cite{lesaege2018kleros}; or (ii) make it infeasible to provide incorrect results.
+Justice is the biggest obstacle in achieving a system that complies with Web 3.0 postulates\footnote{https://en.wikipedia.org/wiki/Web3}.
+
+The possible directions for mitigation of such issues are to either (i) replace justice with decentralized autonomous organizations (DAO) like proposed in Themis~\cite{mengThemisDecentralizedEscrow2019} or Kleros~\cite{bergollaKlerosSociolegalCase2022}; or (ii) make it infeasible to provide incorrect results.
 
@@
 Suppose that the service we are undertaking is fully computable.
-Then, it would be possible by employing proofs of correctness of computations~\cite{ben2013snarks} to enforce that only correct computations (hence correct services) are accepted.
+Then, it would be possible by employing proofs of correctness of computations~\cite{ben-sassonSNARKsVerifyingProgram2013} to enforce that only correct computations (hence correct services) are accepted.
 It would require the complete service examination to be computable, which is hard to achieve in settings where physical materials (like blood) are examined.
@@
 The SP has no motivation to proceed with this kind of misbehaviour other than putting the customer in a disadvantaged position caused by the lost dispute.
-We see possible prevention of this misbehaviour by the usage of Filecoin—an incentive layer on top of IPFS that guarantees the content availability via economic incentivisations~\cite{benetfilecoin}.
+We see possible prevention of this misbehaviour by the usage of Filecoin—an incentive layer on top of IPFS that guarantees the content availability via economic incentivisations~\cite{protocollabsFilecoinDecentralizedStorage2017}.
 With the help of Filecoin, the SP would be obligated to create a deal that guarantees the availability of the result until the deadline of the transaction.
@@
 We assumed the customer to deliver the package to the SP personally or via a trusted person.
-However, the system could be extended to support an anonymous delivery system as proposed in Lelantos~\cite{altawy2017lelantos}.
+However, the system could be extended to support an anonymous delivery system as proposed in Lelantos~\cite{altawyLelantosBlockchainBasedAnonymous2017}.
 One modification to the protocol would be to publish $\mathrm{PoD}$ on the message board, similarly to $\mathrm{PoP}$.
@@
 
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{a1.jpg}}]{Stanis\l{}aw Bara{\'n}ski} received BEng in 2019 and MSc in 2020 in informatics at Gdańsk University of Technology.
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{stanislaw.jpg}}]{Stanis\l{}aw Bara{\'n}ski} received BEng in 2019 and MSc in 2020 in informatics at Gdańsk University of Technology.
 Currently, he is a PhD candidate at the Department of Computer Architecture, Faculty of Electronics, Telecommunications and Informatics, Gdansk University of Technology.
@@
 
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{js access.jpg}}]{JULIAN SZYMA{\'N}SKI}  received the PhD degree in 2009 and DSc in 2020 at Gdańsk University of Technology.
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{julina.jpg}}]{JULIAN SZYMA{\'N}SKI}  received the PhD degree in 2009 and DSc in 2020 at Gdańsk University of Technology.
 He is currently with the Department of Computer
@@
   \item
-    \(\operatorname{\sigma_{3, c, \n} = -}\), the customer has not received the result, so he remains in the disadvantaged position. 
+    \(\operatorname{\sigma_{3, c, n} = -}\), the customer has not received the result, so he remains in the disadvantaged position. 
   \item

### 2022-12-04 smartcontracts/truffle-config.js
update ethereum node address

@@ -66,7 +66,7 @@ module.exports = {
     // options below to some value.
     //
     development: {
-      host: "anton.gbaranski.com",     // Localhost (default: none)
+      host: "ethereum.anonser.stan.bar",     // Localhost (default: none)
       port: 8545,            // Standard Ethereum port (default: none)
       network_id: "*",       // Any network (default: none)
     },

### 2022-12-05 paper/access.tex
update paper

@@
 In case of dispute, either due to exceeding deadlines or providing incorrect results, the customer can disclose the whole interaction and prove to justice (police or court) the misbehaviour of the service provider.
-We analyze the protocol in the context of fairness and discuss further extensions to an anonymous delivery system, payment with cash, and a decentralized conflict resolution system.
+We analyze the protocol in the context of fairness and discuss further extensions to an anonymous delivery system, and a decentralized conflict resolution system.
 Our protocol may enable various services currently based on unacceptable trust assumptions to the service providers.
@@
 our protocol does not rely on a trusted third party to conduct transactions fairly.
-Only in case of dispute the centralized justice is involved (the justice decentralization is discussed in section ~\ref{sec:future-work}.
+Only in case of dispute the centralized justice is involved (the justice decentralization is discussed in section ~\ref{sec:discussion}.
 \item Physical materials: our protocol allows providing not only digital but also physical materials to the service provider.
@@
 Section~\ref{sec:fairness-analysis} provides a fairness analysis of the proposed protocol.
-Section~\ref{sec:future-work} discuss possible improvements. 
+Section~\ref{sec:discussion} discuss possible improvements. 
 Finally, section~\ref{sec:conclusion} concludes the paper.
@@
 
-Possible directions toward semi-autonomous decentralized resolution system are discussed in section ~\ref{sec:future-work}.
+Possible directions toward semi-autonomous decentralized resolution system are discussed in section ~\ref{sec:discussion}.
 
@@
 $\mathrm{PoD}$ could be published on a message board (similarly to $\mathrm{PoP}$); however, since the $\mathrm{pkg}$ is delivered personally or via a trusted person, the confirmation can be issued in person.
-If we would like to hire a courier to deliver our $\mathrm{pkg}$, then the $\mathrm{PoD}$ would have to be published on the message board (further extension to the anonymous delivery system is discussed in section \ref{sec:future-work}).
+If we would like to hire a courier to deliver our $\mathrm{pkg}$, then the $\mathrm{PoD}$ would have to be published on the message board (further extension to the anonymous delivery system is discussed in section \ref{sec:discussion}).
 
@@
 \]
-
-\section{Experiments}\label{sec:experiments}
-
-\subsection*{Setup}
-
-We have developed a prototype of our protocol using the following technologies:
-
-\begin{itemize}
-  \item{Anonymous payments} — we use the Monero blockchain \cite{noetherRingSignatureConfidential2015}.
-  \item{Storage netowork} — we use the Powergate\footnote{https://github.com/textileio/powergate}, which is a wrapper around Filecoin and IPFS.
-  \item{Message board} — we use the Ethereum blockchain \cite{woodEthereumSecureDecentralised2014}; concretely, Truffle Ganache\footnote{https://trufflesuite.com/ganache/} and Solidity language.
-  \item{Customer and SP} — we create client-side web application (webapp) using React for UI, web3.js for interaction with Ethereum, and crypto-js for encryption.
-We use MetaMask browser extension for signing and submiting transactions to Ethereum's node.
-We use `monerod` and `monero-wallet-cli' command-line tools for interacting with Monero blockchain.
-\end{itemize}
-
-The prototype is available at \url{https://anonser.stan.bar}. The source code is available at \url{https://github.com/stanbar/anonymous-provision-of-services-via-blockchain}.
-
-We developed and tested our prototype in the following environment:
-
-\begin{itemize}
-  \item{OS} — Arch Linux 5.11.8
-  \item{Docker} — 20.10.5
-  \item{CPU} — Intel(R) Core(TM) i7-4790 (8) 4.00~GHz
-  \item{RAM} — 16 GB DDR3
-  \item{Storage} — Samsung PM85 256~GB SSD
-
-  \item{monerod and monero-wallet-cli} — v0.18.1.2-release
-  \item{Powergate} — v0.1.6 // get the version from `docker ps`
-  \item{Ganache} — v7.5.0
-  \item{Solidity} — v0.8.17
-  \item{ReactJS} — v18.0.25
-  \item{web3.js} — v1.8.1
-  \item{crypto-js} — v4.1.1
-\end{itemize}
-
-For simplicity, all components run on one, mentioned above, physical machine; and all processes are managed by Docker.
-
-Moreover, Powergate is configured to use local Filecoin and IPFS networks.
-For Ethereum blockchain we use Truffle Ganache, which is a local Ethereum blockchain for development and testing purposes. 
-Monero is configured to use the public stage network.
-
-\subsection*{Experiments}
-
-\paragraph{Preparation}
-
-Both customer and SP create a Monero wallets using `monero-wallet-cli' command-line tool.
-
-Service provider deploys the smart contract using the `truffle migrate --network development` command, which deploys the smart contract to the local Ethereum blockchain.
-The webapp is configured to use the latest deployed smart contract address.
-
-Customer get some testing funds using \url{https://community.rino.io/faucet/stagenet/} faucet service.
-
-Next, the customer enable per-transaction proof generation by setting `set store-tx-info 1` for his wallet.  The proof generation is required to verify the payment in case of dispute.
-
-At this point both the customer and the SP are ready to start the protocol.
-
-\paragraph{Experiment}
-
-Service Provider (SP) and Customer (C) are two different users of our prototype, but for simplicity they use the same machine and the same web application.
-
-Now we describe the experiments we performed to test our protocol.
-
-\begin{itemize}
-  \item 1. The protocol starts with the Customer opening the webapp and creating new provision. 
-The app generates random ECDSA (secp256k1) client's keypair and random 32 bytes provisionID, then display QR code that encodes both the provisionID and the client's public key. 
-The private key must be stored and provided later for the decryption of the results.
-
-  \item 2. The Customer prints the QR code and put it on a package.
-
-  \item 3. The Customer delivers his package to the SP either: in person, via trusted party, or delivery agency.
-
-  \item 4. The SP opens the app, scans the QR code decoding the provisionID and the client's public key.
-
-  \item 5.
-Since (in this experiment) the provision has not been paid in cash, the SP submits a Proof of Delivery transaction to the Ethereum blockchain, indicating that fact setting the `paid` flag to `false`, and `paymentAddress` field with dedicated Monero address using `monero-wallet-cli integrated-address`.
- If the provision is paid with cash, the SP proceed to the step 8. Otherwise, the SP waits until the Customer pays for the provision.
-
-  \item 6. The Customer (using the webapp) check the transaction status on the Ethereum blockchain invoking `getProvision(clientPubKey, provisionID)`.
-
-  \item 7. The Customer (using the `monero-wallet-cli transfer`) sends the payment to the designated in the smart contract `paymentAddress` and stores the .
-
-  \item 8. The SP starts providing the service and outputs the file `result.pdf`.
-
-  \item 9. The SP uploads the file `result.pdf` on the Filecoin and IPFS networks using Powergate. In result, SP gets the content identifier (`cid`), and `dealID`.
-
-  \item 10. The SP submits a Proof of Provision transaction to the Ethereum blockchain by invoking `proofOfProvision(clientPubKey, provisionID, cid, dealID)`.
-
-  \item 11. Meantime, the Customer subscribes to the Ethereum and waits until the SP publishes the Proof Of Provision.
- Once the Proof Of Provision is published the Customer downloads the result using either: IPFS network via https://dweb.link/<cid> or Lotus network using `lotus retreive <cid> <minerID>'.
-Then the results are decrypted using previously stored client's private key.
-
-\end{itemize}
-
 \section{Fairness analysis}\label{sec:fairness-analysis}
@@
 \item 
-    Once published, the result is available to the customer on the storage network. The idea of guaranteeing it cryptographically is discussed in section~\ref{sec:future-work}.
+    Once published, the result is available to the customer on the storage network. The idea of guaranteeing it cryptographically is discussed in section~\ref{sec:discussion}.
 
@@
 
-\section{Future work}
-\label{sec:future-work}
+\section{Experiments}\label{sec:experiments}
+
+\subsection*{Setup}
+
+We have developed a prototype of our protocol using the following technologies:
+
+\begin{itemize}
+  \item{Anonymous payments} — we use the Monero blockchain \cite{noetherRingSignatureConfidential2015}.
+  \item{Storage netowork} — we use the Powergate\footnote{https://github.com/textileio/powergate}, which is a wrapper around Filecoin and IPFS.
+  \item{Message board} — we use the Ethereum blockchain \cite{woodEthereumSecureDecentralised2014}; concretely, Truffle Ganache\footnote{https://trufflesuite.com/ganache/} and Solidity language.
+  \item{Customer and SP} — we create client side web application (webapp) using \texttt{React}\footnote{https://reactjs.org} for creating UI, \texttt{web3.js}\footnote{https://web3js.org} for interaction with Ethereum, and \texttt{crypto-js}\footnote{https://github.com/brix/crypto-js} for encryption.
+We use \texttt{MetaMask}\footnote{https://metamask.io} browser extension for signing and submiting transactions to Ethereum's node.
+We use \texttt{monerod}\footnote{https://monerodocs.org/interacting/monerod-reference/} network client and \texttt{monero-wallet-cli}\footnote{https://monerodocs.org/interacting/monero-wallet-cli-reference/} command-line interface for interacting with Monero blockchain.
+\end{itemize}
+
+The prototype is available at \url{https://anonser.stan.bar}. The source code is available at \url{https://github.com/stanbar/anonymous-provision-of-services-via-blockchain}.
+
+We developed and tested our prototype in the following environment:
+
+\begin{itemize}
+  \item{OS} — Arch Linux 5.11.8
+  \item{Docker} — 20.10.5
+  \item{CPU} — Intel(R) Core(TM) i7-4790 (8) 4.00~GHz
+  \item{RAM} — 16 GB DDR3
+  \item{Storage} — Samsung PM85 256~GB SSD
+
+  \item{monerod and monero-wallet-cli} — v0.18.1.2-release
+  \item{Powergate} — v2.6.2-7-gfd1d093-dirty
+  \item{Ganache} — v7.5.0
+  \item{Solidity} — v0.8.17
+  \item{ReactJS} — v18.0.25
+  \item{web3.js} — v1.8.1
+  \item{crypto-js} — v4.1.1
+\end{itemize}
+
+For simplicity, all components run on one, mentioned above, physical machine; and all processes are managed by Docker.
+
+Moreover, Powergate is configured to use local Filecoin and IPFS networks.
+For Ethereum blockchain we use Truffle Ganache, which is a local Ethereum blockchain for development and testing purposes. 
+Monero is configured to use the public stage network.
+We assume service provider offers only one type of service, which is offered for a fixed public price, hence we omit the type of service and price from the protocol.
+
+\subsection*{Preparation}
+
+Both the customer and the SP create a Monero wallets using \texttt{monero-wallet-cli} command-line tool.
+
+Service provider deploys the smart contract using the \texttt{truffle migrate --network development} command, which deploys the smart contract to the Ethereum blockchain.
+The webapp is configured to use the latest deployed smart contract address.
+
+Customer gets some testing Monero funds using \url{https://community.rino.io/faucet/stagenet/} faucet service.
+
+Next, the customer enable per-transaction proof generation (payment \texttt{attestation}) by setting \texttt{set store-tx-info 1} for his wallet.
+The proof generation is required to verify the payment in case of dispute.
+
+At this point both the customer and the SP are ready to start the protocol.
+
+\subsection*{Experiment}
+
+The customer and the SP are two different users of our prototype, but for simplicity they use the same machine and the same web application.
+
+Now we describe the experiments we performed to test our protocol.
+
+\begin{itemize}
+  \item 1. The protocol starts with the customer opening the webapp and creating new provision. 
+The app generates random ECDSA (secp256k1) customer's keypair and random 32 bytes provisionID, then display QR code that encodes both the provisionID and the customer's public key. 
+The customer's private key must be downloaded and provided later for the decryption of the results.
+
+  \item 2. The customer prints the QR code and put it on a package.
+
+  \item 3. The customer delivers his package to the SP either: in person, via trusted party, or delivery agency.
+
+  \item 4. The SP opens the app, scans the QR code decoding the provisionID and the client's public key.
+
+  \item 5.
+Since (in this experiment) the provision has not been paid in cash, the SP submits a Proof of Delivery transaction to the Ethereum blockchain, indicating that fact setting the \texttt{paid} flag to \texttt{false}, and \texttt{paymentAddress} field with dedicated Monero address using \texttt{monero-wallet-cli integrated-address}.
+  Then SP waits until the customer pays for the provision. If the provision would have been paid with cash, the SP would proceed to the step 8.
+
+  \item 6. The customer (using the webapp) check the transaction status on the Ethereum blockchain invoking \texttt{getProvision(customerPubKey, provisionID)}.
+
+  \item 7.
+The customer (using the \texttt{monero-wallet-cli transfer}) sends the payment to the designated in the smart contract \texttt{paymentAddress} and stores the payment attestation (using \texttt{get\_tex\_key <tx-id>}) in case of dispute.
+
+  \item 8. Once SP notice the payment on Monero blockchain it starts providing the service and outputs the file \texttt{result.pdf}.
+
+  \item 9. The SP uploads the file \texttt{result.pdf} on the Filecoin and IPFS networks using Powergate. In result, the SP gets the content identifier \texttt{cid}, and \texttt{dealID}.
+
+  \item 10.
+The SP submits a Proof of Provision transaction to the Ethereum blockchain by invoking \texttt{proofOfProvision} with arguments \texttt{customerPubKey}, \texttt{provisionID}, \texttt{cid}, and \texttt{dealID}.
+
+  \item 11. Meantime, the Customer subscribes to the Ethereum and waits until the SP publishes the Proof Of Provision.
+ Once the Proof Of Provision is published the Customer downloads the result using either: IPFS network via \texttt{https://dweb.link/<cid>} or Lotus network using \texttt{lotus retreive <cid> <minerID>}.
+
+  \item 12.
+Results are then decrypted using previously stored customer's private key.
+If everything is correct, the Customer is satisfied with the service and the protocol ends, otherwise the Customer can initiate a dispute.
+
+\end{itemize}
+
+\subsection*{Results}
+
+Deploying smart contract consumed 1456577 gas.
+Proof of delivery consumed 129649 gas.
+Proof of provision consumed 149130 gas.
+The price of gas at the time of the experiment (03.01.2023) was $0.000000002227 \frac{\mathrm{ETH}}{\mathrm gas}$\footnote{https://etherscan.io/gastracker}, and the price of 1 $\mathrm{ETH}$ was $1261.97 \mathrm{USD}$.
+In result, the cost of 
+1) deploying the smart contract was $0.000000002227 \frac{\mathrm{ETH}}{\mathrm gas} \times 1456577 \mathrm{gas} \times 1261.97 \frac{\mathrm{USD}}{\mathrm{ETH}} = 4.09 \mathrm{USD}$; 
+2) Proof of delivery was $0.000000002227 \frac{\mathrm{ETH}}{\mathrm gas} \times 129649 \mathrm{gas} \times 1261.97 \frac{\mathrm{USD}}{\mathrm{ETH}} = 0.29 \mathrm{USD}$; 
+3) Proof of provision was $0.000000002227 \frac{\mathrm{ETH}}{\mathrm gas} \times 149130 \mathrm{gas} \times 1261.97 \frac{\mathrm{USD}}{\mathrm{ETH}} = 0.33 \mathrm{USD}$.
+
+\section{Discussion}
+\label{sec:discussion}
 
@@
 
-The possible directions for mitigation of such issues are to either (i) replace justice with decentralized autonomous organizations (DAO) like proposed in Themis~\cite{mengThemisDecentralizedEscrow2019} or Kleros~\cite{bergollaKlerosSociolegalCase2022}; or (ii) make it infeasible to provide incorrect results.
+The possible directions for mitigation of such issues are to either (i) replace justice with decentralized autonomous organizations (DAO) like proposed in Themis~\cite{mengThemisDecentralizedEscrow2019}, Kleros~\cite{bergollaKlerosSociolegalCase2022}, or Aragon Court\footnote{https://aragon.org/aragon-court}; or (ii) make it infeasible to provide incorrect results.
 
 The first approach is more feasible in the near future.
-It would require creating a large set of experts in a field that, in case of dispute, would receive all the proofs ($\mathrm{PoD}$, $\mathrm{PoP}$, as well as any other proofs significant to the case) that could be queried by the experts in zero-knowledge fashion, i.e., they could ask a limited number of questions to the proofs and getting yes/no answers.
+It would require creating a large set of experts in a field that, in case of dispute, would receive all the proofs ($\mathrm{PoD}$, $\mathrm{PoP}$, payment $\mathrm{attestation}$ as well as any other proofs significant to the case) that could be queried by the experts in zero-knowledge fashion, i.e., they could ask a limited number of questions to the proofs and getting yes/no answers.
 The case would be fully confidential as they would not be able to query personal information.
@@
 
-The second approach is more philosophical and visionary.
+The second approach is more futuristic.
 Suppose that the service we are undertaking is fully computable.
@@
 
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{julina.jpg}}]{JULIAN SZYMA{\'N}SKI}  received the PhD degree in 2009 and DSc in 2020 at Gdańsk University of Technology.
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{julian.jpg}}]{JULIAN SZYMA{\'N}SKI}  received the PhD degree in 2009 and DSc in 2020 at Gdańsk University of Technology.
 He is currently with the Department of Computer

### 2022-12-07 webapp/src/__tests__/crypto.ts
update crypto algorithms

@@ -34,8 +34,8 @@ it("Encryption works for key derived from ECDH", async () => {
     const msg = new Uint8Array(Array.from({ length: 1000 }, (v, i) => i % 255))
     const msgString = Buffer.from(msg).toString('hex')
 
-    const encrypted = await encrypt(msgString, provisionId, alice.getPrivate('hex'), bob.getPublic().encode('hex', true))
-    const decrypted = await decrypt(encrypted, provisionId, alice.getPrivate('hex'), bob.getPublic().encode('hex', true))
+    const encrypted = encrypt(msgString, alice.getPrivate('hex'), bob.getPublic().encode('hex', true))
+    const decrypted = decrypt(encrypted, alice.getPrivate('hex'), bob.getPublic().encode('hex', true))
     expect(decrypted).toEqual(msgString)
 })
 

### 2022-12-07 webapp/src/crypto/encrypt.ts

@@ -35,23 +35,63 @@ export const deriveKey = (privateKey: string, publicKey: string): Buffer => {
     return key
 }
 
-export const encrypt = async (msg: Uint8Array| string, iv: Uint8Array, privateKey: string, publicKey: string): Promise<string> => {
+export const encrypt = (msg: Uint8Array| string, privateKey: string, publicKey: string): string => {
     const key = deriveKey(privateKey, publicKey)
 
     if (msg instanceof Uint8Array) {
-        msg = Buffer.from(msg.slice(0,16)).toString('hex')
+        msg = Buffer.from(msg).toString('hex')
     }
 
     return CryptoJS.AES.encrypt(msg, key.toString("utf-8")).toString()
 }
 
-export const decrypt = async (msg: Uint8Array | string, iv: Uint8Array, privateKey: string, publicKey: string): Promise<string> => {
+export const encryptU8intArray = (msg: Uint8Array | string, privateKey: string, publicKey: string): Uint8Array => {
     const key = deriveKey(privateKey, publicKey)
 
     if (msg instanceof Uint8Array) {
-        msg = Buffer.from(msg.slice(0,16)).toString('hex')
+        msg = Buffer.from(msg).toString('hex')
+    }
+
+    const ciphertext64 = CryptoJS.AES.encrypt(msg, key.toString("utf-8")).toString()
+    console.log({ciphertext64})
+    const ciphertextWordArray = CryptoJS.enc.Base64.parse(ciphertext64)
+    console.log({ ciphertextWordArray })
+    return convertWordArrayToUint8Array(ciphertextWordArray)
+}
+
+export const decrypt = (msg: Uint8Array | string, privateKey: string, publicKey: string): string => {
+    const key = deriveKey(privateKey, publicKey)
+
+    if (msg instanceof Uint8Array) {
+        msg = Buffer.from(msg).toString('hex')
     }
 
     const decrypted = CryptoJS.AES.decrypt(msg, key.toString("utf8"))
     return decrypted.toString(CryptoJS.enc.Utf8)
 }
+
+
+export const decryptU8intArray = (msg: Uint8Array | string, privateKey: string, publicKey: string): Uint8Array => {
+    const key = deriveKey(privateKey, publicKey)
+
+    if (msg instanceof Uint8Array) {
+        msg = Buffer.from(msg).toString('hex')
+    }
+
[…]

### 2023-01-10 webapp/src/Constants.ts
refactor

@@ -1,4 +1,4 @@
-const requires = (envVar: string| undefined) : string => {
+const requires = (envVar: string | undefined): string => {
     if (!envVar) {
         throw new Error(`${envVar} not set`);
     }

### 2023-01-10 webapp/src/Provision.ts

@@ -38,19 +38,19 @@ export class ProvisionDelivered extends ProvisionBase {
     issueTime: number;
     paymentDeadlineTime: number;
     provisionDeadlineTime: number;
-    paidInCash: boolean;
+    paidWithCash: boolean;
     paymentAddress: string;
 
-    constructor(clientPubKey: string, provisionId: string, issueTime: number, paymentDeadlineTime: number, provisionDeadlineTime: number, paidInCash: boolean, paymentAddress: string) {
+    constructor(clientPubKey: string, provisionId: string, issueTime: number, paymentDeadlineTime: number, provisionDeadlineTime: number, paidWithCash: boolean, paymentAddress: string) {
         super(clientPubKey, provisionId);
         this.issueTime = issueTime;
         this.paymentDeadlineTime = paymentDeadlineTime;
         this.provisionDeadlineTime = provisionDeadlineTime;
-        this.paidInCash = paidInCash;
+        this.paidWithCash = paidWithCash;
         this.paymentAddress = paymentAddress;
     }
     public upgradeToUploaded(cid: string, dealId: number, minerId: string) {
-        return new ProvisionProvisioned(this.clientPubKey, this.provisionId, this.issueTime, this.paymentDeadlineTime, this.provisionDeadlineTime, this.paidInCash, this.paymentAddress, cid, dealId, minerId)
+        return new ProvisionProvisioned(this.clientPubKey, this.provisionId, this.issueTime, this.paymentDeadlineTime, this.provisionDeadlineTime, this.paidWithCash, this.paymentAddress, cid, dealId, minerId)
     }
     public status(): string {
         return "Delivered";

### 2023-01-10 webapp/src/contexts/EthContext/useEth.ts

@@ -3,7 +3,6 @@ import EthContext from "./EthContext";
 import type Web3 from "web3";
 import {Contract} from "web3-eth-contract";
 
-
 interface EthState {
      dispatch: any;
      state: { artifact: object, web3: Web3, accounts: string[], networkID: number, contract: Contract  }

### 2023-01-10 webapp/src/crypto/index.ts

@@ -2,4 +2,4 @@ import { genKeypair } from './keys'
 import { encrypt, decrypt } from './encrypt'
 import rand from 'randombytes'
 
-export {genKeypair, encrypt, decrypt, rand}
+export { genKeypair, encrypt, decrypt, rand }

### 2023-01-10 webapp/src/crypto/keys.ts

@@ -4,6 +4,6 @@ import rand from 'randombytes'
 
 const secp256k1 = new ec('secp256k1');
 
-export const genKeypair = () : ec.KeyPair => {
+export const genKeypair = (): ec.KeyPair => {
     return secp256k1.keyFromPrivate(rand(32))
 }

### 2023-01-10 webapp/src/__tests__/crypto.ts
unify crypto library

@@ -30,13 +30,11 @@ it("ECDH works for secp256k1 compressed", () => {
 it("Encryption works for key derived from ECDH", async () => {
     const alice = secp256k1.keyFromPrivate(rand(32))
     const bob = secp256k1.keyFromPrivate(rand(32))
-    const provisionId = rand(32)
     const msg = new Uint8Array(Array.from({ length: 1000 }, (v, i) => i % 255))
-    const msgString = Buffer.from(msg).toString('hex')
 
-    const encrypted = encrypt(msgString, alice.getPrivate('hex'), bob.getPublic().encode('hex', true))
+    const encrypted = encrypt(msg, alice.getPrivate('hex'), bob.getPublic().encode('hex', true))
     const decrypted = decrypt(encrypted, alice.getPrivate('hex'), bob.getPublic().encode('hex', true))
-    expect(decrypted).toEqual(msgString)
+    expect(decrypted).toEqual(msg)
 })
 
 it("Encryption works with CryptoJS for larger bytes and default values", async () => {
@@ -58,7 +56,7 @@ it("Encryption works for a README.md file with internal encryption", async () =>
     const bob = secp256k1.keyFromPrivate(rand(32))
 
     const file = readFileSync('README.md', null)
-    
+
     const msg = file.toString('hex')
 
     const alicePrivate = alice.getPrivate('hex')

### 2023-01-10 webapp/src/crypto/encrypt.ts

@@ -1,13 +1,12 @@
 import { ec } from 'elliptic'
-import { encrypt as _encrypt, decrypt as _decrypt } from '@futuretense/secret-box'
-import CryptoJS from 'crypto-js';
+import aesjs from 'aes-js';
 
 const secp256k1 = new ec('secp256k1');
 
 const normaliseHex = (hex: string): string => {
     if (hex.startsWith('0x')) {
         return hex.slice(2)
-    } 
+    }
     return hex
 }
 
@@ -15,12 +14,12 @@ export const deriveKey = (privateKey: string, publicKey: string): Buffer => {
     privateKey = normaliseHex(privateKey)
     publicKey = normaliseHex(publicKey)
 
-    if(Buffer.from(privateKey, 'hex').length !== 32) {
+    if (Buffer.from(privateKey, 'hex').length !== 32) {
         const message = `Invalid private key, it should be 32 bytes long, but found ${Buffer.from(privateKey, 'hex').length} ${privateKey}`
         console.error(message)
         throw new Error(message)
     }
-    if(Buffer.from(publicKey, 'hex').length !== 33) {
+    if (Buffer.from(publicKey, 'hex').length !== 33) {
         const message = `Invalid public key, it should be 33 bytes long, but found ${Buffer.from(publicKey, 'hex').length} ${publicKey}`
         console.error(message)
         throw new Error(message)
@@ -29,69 +28,22 @@ export const deriveKey = (privateKey: string, publicKey: string): Buffer => {
     const receiver = secp256k1.keyFromPublic(publicKey, 'hex')
     const derived = secp256k1.keyFromPrivate(privateKey).derive(receiver.getPublic())
     const key = Buffer.from(derived.toString('hex', 32), 'hex')
-    if(key.length !== 32){
+    if (key.length !== 32) {
         throw new Error("Derived key is not 32 bytes long")
     }
     return key
 }
 
-export const encrypt = (msg: Uint8Array| string, privateKey: string, publicKey: string): string => {
+export const encrypt = (msg: Uint8Array | Buffer | number[], privateKey: string, publicKey: string): Uint8Array => {
     const key = deriveKey(privateKey, publicKey)
 
-    if (msg instanceof Uint8Array) {
-        msg = Buffer.from(msg).toString('hex')
-    }
-
[…]

### 2023-01-10 webapp/src/__tests__/crypto.ts
fix crypto tests

@@ -1,9 +1,8 @@
 import { ec } from 'elliptic'
 import rand from 'randombytes'
-import { encrypt, decrypt, deriveKey } from '../crypto/encrypt'
+import { encrypt, decrypt } from '../crypto/encrypt'
 import { readFileSync } from 'fs'
 import { encrypt as _encrypt, decrypt as _decrypt } from '@futuretense/secret-box'
-import CryptoJS from 'crypto-js';
 
 const secp256k1 = new ec('secp256k1');
 
@@ -32,24 +31,17 @@ it("Encryption works for key derived from ECDH", async () => {
     const bob = secp256k1.keyFromPrivate(rand(32))
     const msg = new Uint8Array(Array.from({ length: 1000 }, (v, i) => i % 255))
 
-    const encrypted = encrypt(msg, alice.getPrivate('hex'), bob.getPublic().encode('hex', true))
-    const decrypted = decrypt(encrypted, alice.getPrivate('hex'), bob.getPublic().encode('hex', true))
+    const alicePrivate = alice.getPrivate('hex')
+    const alicePublic = alice.getPublic().encode('hex', true)
+
+    const bobPrivate = bob.getPrivate('hex')
+    const bobPublic = bob.getPublic().encode('hex', true)
+
+    const encrypted = encrypt(msg, alicePrivate, bobPublic)
+    const decrypted = decrypt(encrypted, bobPrivate, alicePublic)
+
     expect(decrypted).toEqual(msg)
 })
-
-it("Encryption works with CryptoJS for larger bytes and default values", async () => {
-    const alice = secp256k1.keyFromPrivate(rand(32))
-    const bob = secp256k1.keyFromPrivate(rand(32))
-    const msg = new Uint8Array(Array.from({ length: 1000 }, (v, i) => i % 255))
-    const msgString = Buffer.from(msg).toString('hex')
-
-    const key = deriveKey(alice.getPrivate('hex'), bob.getPublic().encode('hex', true))
-
-    const encrypted = CryptoJS.AES.encrypt(msgString, key.toString("utf-8")).toString()
-    const decrypted = CryptoJS.AES.decrypt(encrypted, key.toString("utf-8")).toString(CryptoJS.enc.Utf8)
-    expect(decrypted).toEqual(msgString)
-})
-
 
 it("Encryption works for a README.md file with internal encryption", async () => {
[…]

### 2023-01-10 paper/access.tex
add experiment diagrams to paper

@@
 \usepackage{amsmath}
+\usepackage{pdfpages}
 \usepackage[english]{babel}
@@
 
+\begin{figure*}[ht]
+  \begin{center}
+  \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{experiment1.pdf}
+  \end{center}
+\end{figure*}
+\begin{figure*}[ht]
+  \begin{center}
+  \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{experiment2.pdf}
+  \end{center}
+\end{figure*}
+
 \begin{itemize}
@@
 
-  \item 2. The customer prints the QR code and put it on a package.
-
-  \item 3. The customer delivers his package to the SP either: in person, via trusted party, or delivery agency.
-
-  \item 4. The SP opens the app, scans the QR code decoding the provisionID and the client's public key.
-
-  \item 5.
-Since (in this experiment) the provision has not been paid in cash, the SP submits a Proof of Delivery transaction to the Ethereum blockchain, indicating that fact setting the \texttt{paid} flag to \texttt{false}, and \texttt{paymentAddress} field with dedicated Monero address using \texttt{monero-wallet-cli integrated-address}.
-  Then SP waits until the customer pays for the provision. If the provision would have been paid with cash, the SP would proceed to the step 8.
-
-  \item 6. The customer (using the webapp) check the transaction status on the Ethereum blockchain invoking \texttt{getProvision(customerPubKey, provisionID)}.
-
-  \item 7.
-The customer (using the \texttt{monero-wallet-cli transfer}) sends the payment to the designated in the smart contract \texttt{paymentAddress} and stores the payment attestation (using \texttt{get\_tex\_key <tx-id>}) in case of dispute.
-
-  \item 8. Once SP notice the payment on Monero blockchain it starts providing the service and outputs the file \texttt{result.pdf}.
-
-  \item 9. The SP uploads the file \texttt{result.pdf} on the Filecoin and IPFS networks using Powergate. In result, the SP gets the content identifier \texttt{cid}, and \texttt{dealID}.
-
-  \item 10.
+  \item 2. The customer prints the QR code, stick it on a package, and delivers the package to the SP either: in person, via trusted party, or delivery agency.
+
+  \item 3. The SP opens the app, scans the QR code decoding the provisionID and the client's public key.
+
+  \item 4.
+Since (in this experiment) the provision has not been paid in cash, the SP generate unique Monero payment address using $\mathtt{monero-wallet-cli integrated_address}$ command, and submits the proof of delivery to the Ethereum blockchain.
+
+  % monero-wallet-cli --stagenet --wallet-file sp --password "" integrated_address
+  % Random payment ID: <2b6d65d7d48b7896>
+  % Matching integrated address: 5LHmrsVsQM2Q2TgqufX4A5gKPpxy1czHULDyVc84omvnh1nQLVmqXk4VBuy8WnX1AXfKxDx7xuASAc6svkZqGVkL1XkUBWT7QejHymEaYM
+  \item 5. The customer (using the webapp) check the transaction status on the Ethereum blockchain invoking $\mathtt{getProvision(customerPubKey, provisionID)}$.
+  % monero-wallet-cli --stagenet --wallet-file customer --password "" transfer 5LHmrsVsQM2Q2TgqufX4A5gKPpxy1czHULDyVc84omvnh1nQLVmqXk4VBuy8WnX1AXfKxDx7xuASAc6svkZqGVkL1XkUBWT7QejHymEaYM 1
+  % Transaction successfully submitted, transaction <7d89c04de458cfb76a811d5eb325075dec59f7a993c3bf7ce37f9e3a1630af65>
+  % monero-wallet-cli --stagenet --wallet-file customer --password "" get_tx_key 7d89c04de458cfb76a811d5eb325075dec59f7a993c3bf7ce37f9e3a1630af65
+  % Tx key: 1364dc848a752bf52011f4a63d98bcb16091cacd985713b6b5264b3ede6de40f
+
+  \item 6.
+The customer (using the \texttt{monero-wallet-cli transfer}) sends the payment to the designated in the smart contract \texttt{paymentAddress} and stores the payment attestation (using \texttt{monero-wallet-cli get\_tex\_key <tx-id>}) in case of dispute.
+
+  \item 7. Once SP notice the payment on Monero blockchain it starts providing the service and outputs the file \texttt{result.pdf}.
+
+  \item 8.
+The SP uploads the file \texttt{result.pdf} on the Filecoin and IPFS networks using Powergate.
+In result, the SP gets the content identifier \texttt{cid}, and \texttt{dealID} and \texttt{minerID}.
+
+  \item 9.
 The SP submits a Proof of Provision transaction to the Ethereum blockchain by invoking \texttt{proofOfProvision} with arguments \texttt{customerPubKey}, \texttt{provisionID}, \texttt{cid}, and \texttt{dealID}.
 
-  \item 11. Meantime, the Customer subscribes to the Ethereum and waits until the SP publishes the Proof Of Provision.
+  \item 10. Meantime, the Customer subscribes to the Ethereum and waits until the SP publishes the Proof Of Provision.
  Once the Proof Of Provision is published the Customer downloads the result using either: IPFS network via \texttt{https://dweb.link/<cid>} or Lotus network using \texttt{lotus retreive <cid> <minerID>}.
 
-  \item 12.
+  \item 11.
 Results are then decrypted using previously stored customer's private key.

### 2023-01-12 paper/access.tex
add comparision table

@@
 \usepackage[english]{babel}
+\usepackage{xcolor,colortbl}
 \newtheorem{theorem}{Theorem}
@@
 In case of dispute, either due to exceeding deadlines or providing incorrect results, the customer can disclose the whole interaction and prove to justice (police or court) the misbehaviour of the service provider.
-We analyze the protocol in the context of fairness and discuss further extensions to an anonymous delivery system, and a decentralized conflict resolution system.
+We provide the fairness analysis, implementation of the protocol, and discuss further extensions to an anonymous delivery system, and a decentralized conflict resolution system.
 Our protocol may enable various services currently based on unacceptable trust assumptions to the service providers.
@@
 \section{Introduction}
-Service providers (SPs) like lawyers, laboratories, auditors, or banks,
-to provide services, require data that is often associated with the user
-identity.
+Service providers (SPs) like lawyers, laboratories, auditors, or banks, to provide services, require data that is often associated with the user identity.
 
@@
 
-The privacy guarantee of the data is often based merely on trust assumptions and the security of the IT system.
+The privacy guarantee of the personal information is often based merely on trust assumptions and the security of the IT system.
 However, most SPs do not need personal information for any other reason than payment or communication, which should be considered secondary compared to actual service provision.
@@
 
-In case of dispute, either due to exceeding deadlines or providing an  incorrect result, the customer can disclose the whole interaction and
-prove to justice (police or court) the misbehaviour of the SP.
+In case of dispute, either due to exceeding deadlines or providing an incorrect result, the customer can disclose the whole interaction and prove to justice (police or court) the misbehaviour of the SP.
 
@@
         \item Symmetric encryption, to encrypt and decrypt results published on the public networks.
+        \item Public-key cryptography, to derive shared secrets for symmetric encryption.
         \item Digital signatures, to achieve authentication and non-repudiation of actions. 
@@
 
-In our case, the customer is exchanging with the SP cryptocurrency and materials for the result of the service.
+In our case, the customer who wants to use the service, exchanges his materials and cryptocurrencies with the SP for the result of the service.
 
 %\paragraph{Contributions}
-We contribute to the field of fair exchanges by proposing a simple, practical, and anonymous protocol that does not rely on the centralized trusted third party but decentralized blockchain and
+We contribute to the field of fair exchanges by proposing a simple, practical, and anonymous protocol that does not rely on the centralized TTP, but uses decentralized blockchain and
 distributed content-addressable storage network.
@@
 Some authors have proposed blockchain-based fair-exchange systems that could be adapted to service provision; however, to our best knowledge, we are the first to propose a system that satisfies all five properties stated above using blockchain technology.
-Especially anonymity and physical materials delivery were rarely addressed together, and if so, the protocol was based on TTP and strong and impractical assumptions on banking system~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} or did not address the conflict
+Especially anonymity and physical materials delivery were rarely addressed together, and if so, the protocol was based on TTP and impractical assumptions on banking system~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} or did not address the conflict
 between parties~\cite{altawyLelantosBlockchainBasedAnonymous2017}.
@@
 \section{Related Works}\label{sec:related-works}
-
-\subsection{Fair exchange and blockchain}
-The idea of certified mail is simple, neither the sender can deny sending the mail, nor the receiver can deny receiving it.
-As the service is widely used in the paper world, achieving it for e-mails has not yet met the agreement across the scientific community.
-The main reason was the dependency of TTP, which significantly reduced the performance, security, and robustness of such protocols.
-The protocols that do not use TTP struggle with high computation and communication overhead.
-
-Authors of ~\cite{hinarejosSolutionSecureCertified2019} replaced the TTP with blockchain (concretely Bitcoin blockchain as a reference implementation) that acts as a secure, verifiable, and decentralized TTP.
-
-The idea behind certified e-mails and any other fair exchange protocols is following:
-\begin{enumerate}
-    \item The sender sends encrypted and signed message to the receiver.
-    \item The receiver returns a proof of delivery (a signature) of the encrypted message to the sender.
-    \item The sender publishes proof of delivery and the decryption key on a blockchain (or TTP in general).
-    \item The receiver decrypts the encrypted message using the published decryption key.
-\end{enumerate}
-
-The non-repudiation requirement is achieved by the receiver sending the proof of delivery prior to having access to the decrypted message and the sender publishing the decryption key together with the proof of delivery on the blockchain (or TTP) so that the receiver can deny neither receiving the message nor having access to the decryption key—because it is publicly available.
-
-In this case, the role of blockchain is to certify the public existence of the decryption key at a certain time.
+In this section we review related works on fair exchange, anonymous, and physical delivery protocols. Then we outline the main differences between our protocol and the existing ones.
 
@@
 
-Authors of~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} proposed a
-fair exchange of physical products and electronic payment protocol that
-guarantee both customer and merchant anonymity. They achieve it by introducing online TTPs that validate coins and provide
-fair exchange guarantees.
+The most common application of anonymous fair exchange protocols is e-commerce.
+The problem gets even more challenging when physical products are involved.
+Authors of~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} proposed a protocol for fair exchange of physical products and electronic payments, which guarantee both customer and merchant anonymity.
+They achieve it by introducing online TTPs that validate coins and provide fair exchange guarantees.
 
@@
 \begin{itemize}
-    \item the TTP does not misbehave or collude with any party;
+    \item there exists trusted third party (TTP) which does not misbehave or collude with any party;
     \item the customer's and merchant's banks enable confidential transactions, and both share commit-buffer where the value is locked until the transaction is finished;
@@
 
+\subsection{Fair exchange and blockchain}
+
+The issue of TTPs in fair exchange protocols has been solved by the usage of decentralised networks, especially blockchain technology.
+
+The simplest example of blockchain-based fair exchange protocol is certified electronic mail protocol in which neither the sender can deny sending the mail, nor the receiver can deny receiving it.
+As the service is widely used in the paper world, achieving it for e-mails has not yet met the agreement across the scientific community.
+The main problem was the dependency of TTP, which significantly reduced the performance, security, and robustness of such protocols.
+The protocols that do not use TTP struggle with high computation and communication overhead~\cite{hinarejosSolutionSecureCertified2019}.
+
+Authors of ~\cite{hinarejosSolutionSecureCertified2019} replaced the TTP with blockchain (concretely Bitcoin blockchain as a reference implementation) that acts as a secure, verifiable, and decentralized TTP.
+
+The idea behind certified e-mails and any other fair exchange protocols is following:
+\begin{enumerate}
+    \item The sender sends encrypted and signed message to the receiver.
+    \item The receiver returns a proof of delivery (a signature) of the encrypted message to the sender.
+    \item The sender publishes proof of delivery and the decryption key on a blockchain (or TTP in general).
+    \item The receiver decrypts the encrypted message using the published decryption key.
+\end{enumerate}
+
+The non-repudiation requirement is achieved by the receiver sending the proof of delivery prior to having access to the decrypted message and the sender publishing the decryption key together with the proof of delivery on the blockchain (or TTP) so that the receiver can deny neither receiving the message nor having access to the decryption key—because it is publicly available.
+
+In this case, the role of blockchain is to certify the existence of the decryption key at a certain time.
+
 \subsection{Fair-exchange, blockchain, and decentralized dispute resolution}
@@
 
-Lelanros~\cite{altawyLelantosBlockchainBasedAnonymous2017} is a blockchain-based anonymous
+Lelantos~\cite{altawyLelantosBlockchainBasedAnonymous2017} is a blockchain-based anonymous
 physical delivery system.
@@
 However, since the system uses Ethereum, it achieves pseudonymity rather than anonymity (see section~\ref{sec:pseudo-anon}). Also, the protocol does not cover disputes between the parties.
+
+\subsection{Comparision}
+
+We considered only protocols that achieve fair exchange as it is the fundamental feature of such protocols.
+
+Bîrjoveanu, 2015~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} is the closest to our protocol, however it uses TTP and does not consider dispute between parties.
+
+Hinarejos et al., 2019~\cite{hinarejosSolutionSecureCertified2019} is the simplest protocol that replaces TTP with blockchain.
+However, it does not consider anonymity, dispute between parties nor physical material exchange.
+
+Meng et al., 2019~\cite{mengThemisDecentralizedEscrow2019} improves the previous protocol by the crownsource dispute resolution system. However it does not take anonimity into consideration.
+
+Altawy et al., 2017~\cite{altawyLelantosBlockchainBasedAnonymous2017} is a blockchain-based protocol that does not provide dispute resolution, but provides anonymous physical delivery by using onion routing and anonymous blockchain interaction assuming unlinkability between pseudonyms and real identities.
+
+Our notion of anonymity is based on weaker (better) assumption.
+We achieve anonimity by using either cash or privacy-preserving blockchain.
+Moreover, our protocol does not require a customer to submit any transaction to the message board, which may be the weakest link in the anonymity of aforementioned protocols.
+
+Our protocol does not handle the whole proces of delivery system (like courier). We assume that there is a mean to deliver the package securely and anonymously, either via trusted party.
+
+Our protocol does not provide its own dispute resolution mechanism as Themis does.
+However, we assume the existence of an abstract justice, which can be instantiated with either local court or police, or one of the available online dispute resolution services like Themis~\cite{mengThemisDecentralizedEscrow2019}, Kleros, or others~\cite{allenGovernanceBlockchainDispute2019}.
+
+The comparision of the protocols is presented in table~\ref{tab:comparision}.
+
+\begin{table}
+  \newcommand{\YES}{\cellcolor{green!50}Yes}
+  \newcommand{\ID}{\cellcolor{green!25}Identity}
+  \newcommand{\PSEUDO}{\cellcolor{green!25}Pseudonym}
+  \newcommand{\ANON}{\cellcolor{green!50}Anonymity}
+  \newcommand{\NO}{\cellcolor{red!50}No}
+  \newcommand{\TTP}{\cellcolor{red!50}TTP}
+  \newcommand{\BC}{\cellcolor{green!50}Blockchain}
+  \caption{Related work comparision}
+  \label{tab:comparision}
+  \setlength{\tabcolsep}{3pt}
+  \begin{tabular}{|p{38pt}|p{32pt}|p{38pt}|p{35pt}|p{37pt}|p{30pt}|}
+  \hline
+  Protocol & Fair exchange & Anonymity & Dispute resolution & Trust & Physical delivery \\
+  \hline
+  Bîrjoveanu, 2015~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} & \YES & \YES & \NO & \TTP & \YES \\
+  \hline
+  Hinarejos et al., 2019~\cite{hinarejosSolutionSecureCertified2019} & \YES & \NO & \NO & \BC & \NO \\
+  \hline
+  Themis~\cite{mengThemisDecentralizedEscrow2019} & \YES & \NO & \YES & \BC & \NO \\
+  \hline
+  Lelantos~\cite{altawyLelantosBlockchainBasedAnonymous2017} & \YES & \PSEUDO & \NO & \BC & \YES \\
+  \hline
+  This paper & \YES & \YES & \YES & \BC & \YES \\
+  \hline
+
+  \end{tabular}
+\end{table}
 
@@
 \section{The Protocol}\label{sec:protocol}
+In this section we propose an abstract protocol for anonymous service provisioning without any assumptions about the underlying technologies.
+We define the requirements for each role and leave the choice of the technology to the developer.
+Later in the paper (section~\ref{sec:experiments}) we describe our implementation used for conducting experiments.
 
 \subsection{Prerequisites}
-We do not design our protocol with the assumption of using particular technologies; instead, we define requirements that each party must satisfy to make the whole system work together.
-The choice of the particular technology for each role is up to the developer.
-
-\begin{itemize}
-\item There exists common PKI infrastructure:
-    \begin{itemize}
-        \item The customer and the SP have their key pairs consisting of secret key $\mathrm{sk}(\mathrm{party})$ and public key $\mathrm{pk}(\mathrm{party})$, where $\mathrm{party} \in \{\mathrm{C}, \mathrm{SP}\}$ is the customer or the service provider accordingly.
+
+\begin{itemize}
+\item There exists PKI infrastructure:
+    \begin{itemize}
+        \item The customer and the SP have their key pairs consisting of secret key $\mathrm{sk}(\mathrm{party})$ and public key $\mathrm{pk}(\mathrm{party})$, where $\mathrm{party} \in \{\mathrm{C}, \mathrm{SP}\}$ for the customer and the SP.
         \item Both the customer and the SP can create and verify digital signatures created by the customer $\mathrm{sig}_{\mathrm{sk}(\mathrm{C})}$ and the SP $\mathrm{sig}_{\mathrm{sk}(\mathrm{SP})}$.
@@
         \item use common symmetric encryption $\mathrm{E}_\mathrm{key}(\cdot)$ and decryption $\mathrm{D}_\mathrm{key}(\cdot)$ operations.
+        \item have access to anonymous payments blockchain, message board, and storage network.
     \end{itemize}
@@
     \begin{itemize}
-        \item accepts packages from unknown customers and give $\mathrm{PoD}$ in return.
+        \item accepts packages from unknown customers.
         \item accepts payments with anonymous cryptocurrencies as described in section~\ref{payment-for-services}.
@@
 
-\item Anonymous payments:
+\item Anonymous payments blockchain:
     \begin{itemize}
@@
 
-\item Message board:
-    \begin{itemize}
-        \item supports proofs as large as the size of $\mathrm{PoP}$, i.e., sum size of $\mathrm{cid}$, $\mathrm{nonce}$, and $\mathrm{sig}$.
-    \end{itemize}
-
-\item The storage network:
-    \begin{itemize}
-        \item allows for uniquely content retrieval via $\mathrm{cid}$ (usually a hash of the content).
+\item Message Board:
+    \begin{itemize}
+        \item supports transactions of sizes up to $\mathrm{PoD}$ and $\mathrm{PoP}$.
+    \end{itemize}
+
+\item Storage network:
+    \begin{itemize}
+        \item allows for content retrieval via content identifier $\mathrm{cid}$ (usually a hash of the content).
         \item allows for anonymous content retrieval.
+        \item guarantee that the content will be available for the duration of the agreement.
     \end{itemize}
@@
 \noindent \textbf
-{Package}\label{package} is a physical container prepared by the customer encompassing all $\mathrm{materials}$ required by the SP to provide the service, and an encryption $\mathrm{key}$ used to encrypt the result published on the storage network.
-
-$$\mathrm{pkg} \equiv (\mathrm{materials}, \mathrm{key})$$
+{Package}\label{package} is a physical container prepared by the customer encompassing all $\mathrm{materials}$ required by the SP to provide the service, randomly generated provision identifier used to anonymously track the provision throughout the protocol's steps, and the customer's public key $\mathrm{pk(C)}$ used to encrypt the result published on the public storage network.
+
+$$\mathrm{pkg} \equiv (\mathrm{materials}, \mathrm{provisionID}, \mathrm{pk(C)})$$
 
@@
 
-\item $\mathrm{materials}$ - are the materials required to provide the service, for example, samples of urine, blood, stool, saliva; legal documents, CDs, emails, photos, bank statements; or any other kind of evidence depending on the service.
-\item $\mathrm{key}$ - symmetric key used to encrypt and decrypt the result.
-\end{itemize}
-
-\noindent \textbf
-{Proof of delivery ($\mathrm{PoD}$)}\label{proof-of-delivery} is a  confirmation issued by the SP to the customer that proves that the customer has delivered to the SP a complete (according to the SP requirements) package, and the SP accepted it.
-
-It is also an agreement between the customer and the SP, as it includes agreed upfront deadlines of actions in the protocol.
-
-We assume the $\mathrm{PoD}$ to be a QR code printed on a paper receipt, but any other form that guarantees integrity, authenticity, and non-repudiation can be used instead.
-
-$$\mathrm{PoD} \equiv (\mathrm{T}_\mathrm{issue}, \mathrm{T}_\mathrm{pay}, \mathrm{T}_\mathrm{provide}, \mathrm{nonce}, \mathrm{sig}_\mathrm{SP})$$
+\item $\mathrm{materials}$ - are the materials required to provide the service, for example, samples of urine, blood, stool, saliva; legal documents, CDs, emails, photos, bank statements; or any other kind of materials depending on the service.
+\item $\mathrm{provisionID}$ - a randomly generated provision identifier, used to anonymously track the provision throughout the protocol's steps.
+\item $\mathrm{pk(C)}$ - customer's public key used to encrypt the result published on the public storage network.
+\end{itemize}
+
+\noindent \textbf
+{Proof of delivery ($\mathrm{PoD}$)}\label{proof-of-delivery} is an attestation to the fact that the customer has delivered a correct (according to the SP requirements) package to the SP, and the SP has accepted it.
+
+It is also an agreement between the customer and the SP, as it includes agreed upfront deadlines of actions, and a payment method.
+
+$\mathrm{PoD}$ is published on the message board by the SP.
+
+$$\mathrm{PoD} \equiv (\mathrm{T}_\mathrm{issue}, \mathrm{T}_\mathrm{pay}, \mathrm{T}_\mathrm{provide}, \mathrm{address}, \mathrm{provisionID}, \mathrm{pk(C)}, \mathrm{sig}_\mathrm{SP})$$
 
@@
   $\mathrm{T}_\mathrm{provide}$ - deadline to provide a result of the service.
-\item $\mathrm{nonce}$ - randomly generated number uniquely identifying the transaction.
+\item $\mathrm{address}$ - payment address of the SP's anonymous blockchain account.
+\item \(\mathrm{provisionID}\) - the number uniquely identifying the transaction previously generated by the customer.
+\item $\mathrm{pk(C)}$ - customer's public key used to encrypt the result published on the public storage network.
 \item $\mathrm{sig}_\mathrm{SP}$ - the SP's signature guaranteeing non-repudiation.
@@
 {Proof of provision ($\mathrm{PoP}$)}\label{proof-of-provision} is proof that the SP published the result at a certain time.
-It defends the SP in case the customer unjustly starts a dispute after the result has been published.
-The connection between $\mathrm{PoP}$ and the result is made by the content identifier ($\mathrm{cid}$) that uniquely identify the result (it is some kind of a hash of the result) such that the result can not be forged after the $\mathrm{PoP}$ has been published.
+It protects the SP in case the customer unjustly starts a dispute after the result has been published.
+The connection between $\mathrm{PoP}$ and the result is made by the content identifier ($\mathrm{cid}$) uniquely identifing the result such that the result can not be forged after the $\mathrm{PoP}$ has been published.
 
@@
 
-\item
-  \(\mathrm{cid}\) - content identifier as specified in section~\ref{storage-network}.
-\item
-  \(\mathrm{nonce}\) - the value uniquely identifying the transaction previously generated in $\mathrm{PoD}$.
-\item
-  \(\mathrm{sig}_\mathrm{SP}\) - the SP's signature guaranteeing authentication.
+\item $\mathrm{cid}$ - content identifier as specified in section~\ref{storage-network}.
+\item $\mathrm{provisionID}$ - the number uniquely identifying the transaction previously generated by the customer.
+\item $\mathrm{sig}_\mathrm{SP}$ - the SP's signature guaranteeing non-repudiation.
 \end{itemize}
@@
 \noindent \textbf
-{Result}\label{results} is assumed to be a document in PDF format, but any other format is allowed as long as it can be binary encoded and uploaded to IPFS.
+{Result}\label{results} is assumed to be a document in PDF format, but any other format is allowed as long as it can be binary encoded and uploaded to sotrage network.
 We refer to it symbolically as $\mathrm{result}$.
@@
 
-They protocol starts once the customer delivers package $\mathrm{pkg}$ and the SP accepts its content.
+The protocol starts once the customer delivers package $\mathrm{pkg}$ and the SP accepts its content.
 In return, the SP issue a $\mathrm{PoD}$ with agreed upfront payment deadline $\mathrm{T}_\mathrm{pay}$, service provision deadline $\mathrm{T}_\mathrm{provide}$, and current time $\mathrm{T}_\mathrm{issue}$.
@@
 Moreover, since Filecoin is a blockchain by itself, it could play both roles of message board and storage network.
-
-\subsection{Paying with cash}\label{paying-with-cash}
-
-Without loss of generality, the payment can be made with cash.
-The customer can exchange the cash with SP together with delivering the package.
-The $\mathrm{PoD}$ would contain information that the transaction has been paid with cash; therefore, steps one and two could be merged and realized in one step.
-In case of dispute, the payment disclosure would be included in $\mathrm{PoD}$.
 

### 2023-01-14 paper/access.tex
update diagram and protocol steps

@@
 
-\title{Anonymous provision of services via blockchain}
+\title{Privacy-preserving service provisioning using distributed networks}
 \author{\uppercase{Stanis\l{}aw Bara{\'n}ski} \authorrefmark{1},
@@
 \begin{abstract}
-Service providers like lawyers, laboratories, auditors, or banks, to provide services, require customers to submit data often associated with their personal information.
-This situation exposes customers to privacy risks.
+Service providers like lawyers, laboratories, auditors, or banks, to provide services, require customers to submit data often associated with their personal information, exposing their customers to privacy risks.
 However, most service providers use personal information merely for logistic operations like payments and communication and could provide services anonymously if other means of logistics exist.
-We propose a protocol for coordinating anonymous service provision.
-Our proposal uses blockchain for both anonymous payments and proofs of existence (so-called message board) and content-addressable network (e.g.~IPFS) for results delivery.
-A service provider can employ our protocol to provide services without collecting personal information. 
+We propose a anonymous fair exchange protocol for coordinating service provision using blockchain for both anonymous payments and proofs of existence and content-addressable network for results delivery.
+% Less important
+A service provider can employ our protocol to provide services without collecting personal information, enabling services currently based on unacceptable trust assumptions. 
+% Even less important
 Possible applications for this protocol include anonymous tests for drugs, venereal diseases, paternity, and steroids, or anonymous legal advice.
-In case of dispute, either due to exceeding deadlines or providing incorrect results, the customer can disclose the whole interaction and prove to justice (police or court) the misbehaviour of the service provider.
-We provide the fairness analysis, implementation of the protocol, and discuss further extensions to an anonymous delivery system, and a decentralized conflict resolution system.
-Our protocol may enable various services currently based on unacceptable trust assumptions to the service providers.
+We provide the fairness analysis and well as the implementation of the protocol. We discuss further extensions to an anonymous delivery system, and a decentralized conflict resolution system.
 \end{abstract}
@@
 
-By exposing our identity to the lawyer, we trust that he will not use that
-information for harmful actions.
+By exposing our identity we trust that the lawer will not use that information for harmful actions.
 
@@
 The remainder of this paper is organized as follows.
-In section~\ref{sec:related-works} we briefly review related works. 
-Section~\ref{sec:building-blocks} explains the building blocks of fair exchanges, blockchain, storage network, anonymity and confidentiality.
+In section~\ref{sec:related-works} we review related works. 
+Then, in section~\ref{sec:building-blocks} we explain the building blocks of fair exchanges, blockchain, storage network, anonymity and confidentiality.
 Section~\ref{sec:protocol} describes how the protocol works in detail.
@@
 The most common application of anonymous fair exchange protocols is e-commerce.
+The problem is that the customer wants to buy a product from a merchant, but does not want to reveal his identity to the merchant.
 The problem gets even more challenging when physical products are involved.
+
 Authors of~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} proposed a protocol for fair exchange of physical products and electronic payments, which guarantee both customer and merchant anonymity.
@@
 
-However, the protocol relies on strong assumptions to achieve fairness.
-Namely,
-
-\begin{itemize}
-    \item there exists trusted third party (TTP) which does not misbehave or collude with any party;
+However, the protocol relies on strong assumptions, namely:
+
+\begin{itemize}
+    \item there exists trusted third party (TTP) and trusted delivery agent which do not misbehave or collude with any party;
+    \item there exists an anonymous communication channel 
     \item the customer's and merchant's banks enable confidential transactions, and both share commit-buffer where the value is locked until the transaction is finished;
     \item all banks maintain a global list of coins' serial numbers to prevent double-spending problems;
-    \item the SC and DC exist, and in both, the product access is protected by a password;
+    \item the SC and DC exist, and in both, the access is protected by a password;
     \item the DC is equipped with a video camera that records the moment when the customer opens the package and provides a way to submit the video to TTP in case of a dispute;
-    \item there exists a trusted delivery agent;
-    \item communication channels between parties provide anonymity.
 \end{itemize}
@@
 
-Our notion of anonymity is based on weaker (better) assumption.
-We achieve anonimity by using either cash or privacy-preserving blockchain.
+Our protocol achieves stronger anonymity guarantees.
+Namely, we achieve anonimity by using either cash or privacy-preserving blockchains.
 Moreover, our protocol does not require a customer to submit any transaction to the message board, which may be the weakest link in the anonymity of aforementioned protocols.
 
-Our protocol does not handle the whole proces of delivery system (like courier). We assume that there is a mean to deliver the package securely and anonymously, either via trusted party.
-
-Our protocol does not provide its own dispute resolution mechanism as Themis does.
-However, we assume the existence of an abstract justice, which can be instantiated with either local court or police, or one of the available online dispute resolution services like Themis~\cite{mengThemisDecentralizedEscrow2019}, Kleros, or others~\cite{allenGovernanceBlockchainDispute2019}.
+Our protocol does not use its own delivery system. We assume that there is a way to anonymously deliver a package either via SP's drop box, or trusted party.
+
+Also, our protocol does not provide its own dispute resolution mechanism as Themis does.
+However, we assume the existence of an abstract justice which accepts evidences and ., which can be instantiated with either local court or police, or one of the available online dispute resolution services like Themis~\cite{mengThemisDecentralizedEscrow2019}, Kleros~\cite{bergollaKlerosSociolegalCase2022}, Aragon Court\footnote{https://aragon.org/aragon-court}, or others~\cite{allenGovernanceBlockchainDispute2019}.
 
@@
 The vision of smart contracts was to replace the legal contract with
-programmable and autonomous contracts. The smart contract code encompasses the contract's specifications, hence the slogan ``code as a law''.
+programmable and autonomous contracts. The smart contract code encompasses the contract's specifications, hence the slogan \textit{code as a law}.
 
@@
 
-To mitigate the issue, we designed the protocol so that the SP who follows the protocol is always in an advantaged position; therefore, he has no reason to start a dispute.
+To mitigate the issue, we designed the protocol so that the SP who follows the protocol is always in an advantaged position; therefore, she has no reason to start a dispute.
 On the other hand, the customer can start a dispute at any time of the protocol, but only the actual misbehaviour of the SP makes him win the case.
@@
 \subsection{Storage network}\label{storage-network}
-Once the SP finishes its service, he has to provide the result to the customer.
+Once the SP finishes its service, she has to provide the result to the customer.
 The most natural approach would be to send the result via e-mail or some dedicated platform.
-However, since the customer wants to stay anonymous, he does not want to expose his e-mail address nor IP address.
+However, since the customer wants to stay anonymous and so does not want to expose his e-mail address nor IP address.
 Moreover, the SP should prove that the result has been provided before the deadline, which brings us to the issue of proof of existence discussed in section ~\ref{sec:message-board}.
@@
 
-We take the same approach. Once the SP creates the result, he encrypts it using the previously provided encryption key and uploads it to the IPFS network.
+We take the same approach. Once the SP creates the result, she encrypts it using the previously provided encryption key and uploads it to the IPFS network.
+%TODO: write about DHKE encyption
 
@@
 \item Storage network: IPFS \cite{benetIPFSContentAddressed2014}, Filecoin
-  \cite{protocollabsFilecoinDecentralizedStorage2017} (runs on top of IPFS), or Ethereum's
+  \cite{protocollabsFilecoinDecentralizedStorage2017}, or Ethereum's
   Swarm\cite{teamSWARMStorageCommunication2021}.
@@
 
-$$\mathrm{PoD} \equiv (\mathrm{T}_\mathrm{issue}, \mathrm{T}_\mathrm{pay}, \mathrm{T}_\mathrm{provide}, \mathrm{address}, \mathrm{provisionID}, \mathrm{pk(C)}, \mathrm{sig}_\mathrm{SP})$$
+\begin{eqnarray}
+\mathrm{PoD} & \equiv & (\begin{array}[t]{l}\mathrm{T}_\mathrm{issue}, \mathrm{T}_\mathrm{pay}, \mathrm{T}_\mathrm{provide},\\ \mathrm{address}, \mathrm{provisionID}, \mathrm{pk(C)}, \mathrm{sig}_\mathrm{SP} \; )\end{array}
+\end{eqnarray}
+
+% \begin{eqnarray}
+%   \quad L_{\mathrm{H}}(H) & \equiv & (\begin{array}[t]{l}H_{\mathrm{p}}, H_{\mathrm{o}}, H_{\mathrm{c}}, H_{\mathrm{r}}, H_{\mathrm{t}}, H_{\mathrm{e}}, H_{\mathrm{b}}, H_{\mathrm{d}},\\ H_{\mathrm{i}}, H_{\mathrm{l}}, H_{\mathrm{g}}, H_{\mathrm{s}}, H_{\mathrm{x}}, H_{\mathrm{m}}, H_{\mathrm{n}} \; )\end{array} \\
+%   \quad L_{\mathrm{B}}(B) & \equiv & \big( L_{\mathrm{H}}(B_{\mathrm{H}}), \widetilde{L}_{\mathrm{T}}^*(B_{\mathbf{T}}), L_{\mathrm{H}}^*(\hyperlink{ommer_block_headers_B__U}{B_{\mathbf{U}}}) \big)
+%   \end{eqnarray}
 
@@
 \item $\mathrm{address}$ - payment address of the SP's anonymous blockchain account.
-\item \(\mathrm{provisionID}\) - the number uniquely identifying the transaction previously generated by the customer.
+\item $\mathrm{provisionID}$ - the number uniquely identifying the transaction previously generated by the customer.
 \item $\mathrm{pk(C)}$ - customer's public key used to encrypt the result published on the public storage network.
@@
 
-The $\mathrm{PoP}$ is a digital construction published by the SP on the message board.
-
-\[\mathrm{PoP} \equiv (\mathrm{cid}, \mathrm{nonce}, \mathrm{sig}_\mathrm{SP})\]
+$\mathrm{PoP}$ is published on the message board by the SP.
+
+\begin{eqnarray}
+\mathrm{PoP} & \equiv & (\mathrm{cid}, \mathrm{provisionID}, \mathrm{sig}_\mathrm{SP})
+\end{eqnarray}
 
@@
 
-The customer collects all the $\mathrm{materials}$ required by the SP, generates an encryption $\mathrm{key}$, prints it on a paper as a QR code, and packs them together into a package $\mathrm{pkg}$.
+The customer collects all the $\mathrm{materials}$ required by the SP, generates a random $\mathrm{provisionID}$ and a random keypair $(\mathrm{sk(C)},\mathrm{pk(C)})$.
+The $\mathrm{provisionID}$ will be used to associate all actions related to the transaction throughout the protocol.
+The $\mathrm{provisionID}$ and $\mathrm{pk(C)}$ are encoded as a QR code, printed, and sticked to the package $\mathrm{pkg}$.
+The $\mathrm{sk(C)}$ is kept secret and used to decrypt the $\mathrm{result}$ at the end of the protocol.
+
+\noindent \textbf
+{Step 1. Package delivery}\label{step-1-package-delivery}
+
+The protocol starts once the customer delivers package $\mathrm{pkg}$ to the SP and its content gets accepted.
+As a result, $\mathrm{PoD}$ is created with predefined payment deadline $\mathrm{T}_\mathrm{pay}$, service provision deadline $\mathrm{T}_\mathrm{provide}$, and current time $\mathrm{T}_\mathrm{issue}$.
+Also $\mathrm{PoD}$ embodies the information whether the service has been paid in cash or should be paid by the customer using the anonymous blockchain account.
+In the latter case, the SP's payment address is included in the $\mathrm{PoD}$.
+
+The digital signature $\mathrm{sig}_{\mathrm{sk}(\mathrm{SP})}$ on the $\mathrm{PoD}$ created with the SP's secret key $\mathrm{sk}(\mathrm{SP})$ guarantee non-repudiation.
 
@@
 \[
-\mathrm{pkg} \gets (\mathrm{materials}, \mathrm{key})
+\mathrm{PoD \gets delivery(pkg)}
 \]
@@
 \noindent \textbf
-{Step 1. Package delivery}\label{step-1-package-delivery}
-
-The protocol starts once the customer delivers package $\mathrm{pkg}$ and the SP accepts its content.
-In return, the SP issue a $\mathrm{PoD}$ with agreed upfront payment deadline $\mathrm{T}_\mathrm{pay}$, service provision deadline $\mathrm{T}_\mathrm{provide}$, and current time $\mathrm{T}_\mathrm{issue}$.
-Also, the $\mathrm{PoD}$ consist of randomly generated unique number $\mathrm{nonce}$, which will allow associating all actions related to the transaction throughout the protocol.
-Finally, the digital signature $\mathrm{sig}_{\mathrm{sk}(\mathrm{SP})}$ on the $\mathrm{PoD}$ created with the SP's secret key $\mathrm{sk}(\mathrm{SP})$ guarantee non-repudiation.
-
-We assume this step to be entirely physical, i.e., $\mathrm{pkg}$ consists of physical materials, $\mathrm{PoD}$ is in the form of, e.g., QR code printed on a paper receipt.
-
-$\mathrm{PoD}$ could be published on a message board (similarly to $\mathrm{PoP}$); however, since the $\mathrm{pkg}$ is delivered personally or via a trusted person, the confirmation can be issued in person.
-If we would like to hire a courier to deliver our $\mathrm{pkg}$, then the $\mathrm{PoD}$ would have to be published on the message board (further extension to the anonymous delivery system is discussed in section \ref{sec:discussion}).
+{Step 2. Proof of Delivery}\label{step-2-pod}
+
+Then, the $\mathrm{PoD}$ is published on the message board by the SP, commiting to the fact that the package $\mathrm{pkg}$ has been delivered, adn the SP can not reject receiving it.
+If the provision has not been paid in cash, the SP waits for the customer to pay for the service on the specified in the $\mathrm{PoD}$ payment $\mathrm{address}$.
 
@@
 \[
-\mathrm{PoD} \gets \mathrm{delivery}(\mathrm{pkg})
+\mathrm{publish(PoD)}
 \]
-\[
-(\mathrm{T}_\mathrm{issue}, \mathrm{T}_\mathrm{pay}, \mathrm{T}_\mathrm{provide}, \mathrm{nonce}, \mathrm{sig}_{\mathrm{sk}(\mathrm{SP})}) \equiv \mathrm{PoD}
-\]
-
-\noindent \textbf
-{Step 2. Payment}\label{step-2-payment}
-
-Having the $\mathrm{PoD}$ issued, the SP can not reject receiving the package. At this point the
-customer should pay for the transaction (identified by $\mathrm{nonce}$ value) with the agreed upfront cryptocurrency blockchain (see section~\ref{payment-for-services}).
-
-In return, the customer receives the $\mathrm{attestation}$ that should be disclosed in case of a dispute.
+
+\noindent \textbf
+{Step 3. Get Proof of Delivery}\label{step-3-get-pod}
+
+Once the package is delivered and the $\mathrm{PoD}$ is published, the customer can get the $\mathrm{PoD}$ from the message board and (if everything is correct) proceed with the protocol.
 
@@
 \[
-\mathrm{attestation} \gets \mathrm{payment}(\mathrm{nonce}, \mathrm{sig}_{\mathrm{sk}(\mathrm{C})})
+\mathrm{PoD \gets get(provisionID)}
 \]
@@
 \noindent \textbf
-{Step 3. Provision of service}\label{step-3-provision-of-service} 
-Once the customer has paid for the transaction, the SP starts providing the service.
+{Step 4. Payment}\label{step-4-payment}
+
+If the provision has not been paid in cash, the customer should pay for the transaction with the predefined anonymous payment blockchain (see section~\ref{payment-for-services}).
+
+In return, the customer receives the $\mathrm{attestation}$ that should be disclosed in case of a dispute.
 
@@
 \[
-\mathrm{result} \gets \mathrm{provision}(\mathrm{materials})
+\mathrm{attestation \gets payment(address)}
 \]
@@
 \noindent \textbf
-{Step 4. Upload result }\label{step-4-results-upload}
-
-After the service is finished, a result should be created. Next, the result is encrypted using encryption symmetric $\mathrm{key}$ provided in the first step.
-
-The encrypted result is then uploaded on the content addressable network such as IPFS. In return the content identifier ($\mathrm{cid}$) is created.
+{Step 5. Provision of service}\label{step-5-provision-of-service} 
+Once the customer has paid for the transaction either in cash or using the anonymous blockchain, the SP can start providing the service.
 
@@
 \[
-\mathrm{cid} \gets \mathrm{upload}(E_{\mathrm{key}}(\mathrm{result}))
+\mathrm{result \gets provision(materials)}
 \]
@@
 \noindent \textbf
-{Step 5. Proof of provision}\label{step-5-proof-of-provision-publication}
-
-When the result is published, the SP performs proof of provision by publishing $\mathrm{cid}$ along with $\mathrm{nonce}$ and signature $\mathrm{sig}_\mathrm{SP}$.
+{Step 6. Upload result}\label{step-6-upload-result}
+
+After the service is finished, a result should be created. 
+Next, the result is encrypted using shared key derived from the customer's public key $\mathrm{pk(C)}$ and the SP's secret key $\mathrm{sk(S)}$ using Diffie-Hellman key exchange (DHKE) method.
+
+The encrypted result is then uploaded on the content addressable network (such as IPFS). In return the content identifier ($\mathrm{cid}$) is created.
 
@@
 \[
-\mathrm{PoP} \equiv (\mathrm{cid}, \mathrm{nonce}, \mathrm{sig}_{\mathrm{sk}(\mathrm{SP})})
+\mathrm{cid \gets upload(E_{DHKE(sk(SP), pk(C))}(result))}
 \]
-\[
-\mathrm{publish}(\mathrm{PoP})
-\]
-
-\noindent \textbf
-{Step 6. Pull proof of provision}\label{step-6-proof-of-provision-notification}
-
-After delivering the package and paying for the transaction, the customer subscribes to the message board and waits until the SP publishes the proof of provision.
-The subscription is for the SP public key $\mathrm{pk}(\mathrm{SP})$ and transaction's $\mathrm{nonce}$.
+
+\noindent \textbf
+{Step 7. Proof of provision}\label{step-7-proof-of-provision}
+
+When the $\mathrm{result}$ is uploaded, the SP creates and publish on a message board a proof of provision consisting of $\mathrm{cid}$ along with $\mathrm{provisionID}$ and signature $\mathrm{sig}_\mathrm{SP}$.
 
@@
 \[
-\mathrm{cid} \gets \mathrm{subscribe}(\mathrm{pk}(\mathrm{SP}), \mathrm{nonce})
+\mathrm{publish(PoP)}
 \]
@@
 \noindent \textbf
-{Step 7. Result download}\label{step-7-results-download} 
-Having the $\mathrm{cid}$, the customer downloads and decrypts the $\mathrm{result}$.
+{Step 8. Get Proof of Provision}\label{step-8-get-proof-of-provision}
+
+After delivering the package and paying for the transaction, the customer start listening to the message board and waits until the SP publishes the $\mathrm{PoP}$ for the $\mathrm{provisionID}$.
 
@@
 \[
-\mathrm{result} \gets \mathrm{D}_{\mathrm{key}}(\mathrm{download}(\mathrm{cid}))
+\mathrm{cid \gets get(provisionID)}
 \]
+
+\noindent \textbf
+{Step 9. Download result}\label{step-9-download-result} 
+Having the $\mathrm{cid}$, the customer downloads and decrypts the $\mathrm{result}$ using shared key derived from the customer's secret key $\mathrm{sk(C)}$ and the SP's public key $\mathrm{pk(S)}$ using DHKE method.
+The protocol ends.
+
+Symbolically: 
+\[
+\mathrm{result \gets D_{DHKE(sk(C), pk(SP))}(download(cid))}
+\]
+
 \section{Fairness analysis}\label{sec:fairness-analysis}
-
 We analyze the fairness of the protocol by representing it as an interactive non-cooperative game.
 
-\subsection{Model}\label{model}
+\subsection{Model}\label{sec:fairness-model}
 We consider three positions:
@@
 
-As a result, in our analysis, we have to consider four different outcomes for each party of the protocol ($\mathrm{party \in \{c, s}\}$), for each step of the protocol ($\mathrm{step \in 1..7}$):
+As a result, in our analysis, we have to consider four different outcomes for each party of the protocol ($\mathrm{party \in \{c, s}\}$), for each step of the protocol ($\mathrm{step \in 1..9}$):
 
@@
 Because the customer is anonymous, the SP can not start a dispute—there is no means to identify the customer.
-To mitigate the issue, we designed the protocol so that the SP who follows the protocol is always in an advantaged position, and therefore he has no reason to start a dispute.
+To mitigate the issue, we designed the protocol so that the SP who follows the protocol is always in an advantaged position, and therefore has no reason to start a dispute.
 On the other hand, the customer can start a dispute at any time of the protocol, but only the actual misbehaviour of the SP makes him win the case.
@@
 
-The description of each step and the rationale of the outcome position is given in the appendix in section \ref{sec:proof-of-fairness}.
+The description of each step and the rationale of the outcome position is given in the Appendix~\ref{app:proof-of-fairness}.
 
@@
 
-  \item{monerod and monero-wallet-cli} — v0.18.1.2-release
-  \item{Powergate} — v2.6.2-7-gfd1d093-dirty
+  \item{monerod and monero-wallet-cli} — v0.18.1.2
+  \item{Powergate} — v2.6.2
   \item{Ganache} — v7.5.0
@@
   \item 4.
-Since (in this experiment) the provision has not been paid in cash, the SP generate unique Monero payment address using $\mathtt{monero-wallet-cli integrated_address}$ command, and submits the proof of delivery to the Ethereum blockchain.
+Since (in this experiment) the provision has not been paid in cash, the SP generate unique Monero payment address using \texttt{monero-wallet-cli integrated\_address} command, and submits the proof of delivery to the Ethereum blockchain.
 
@@
   % Matching integrated address: 5LHmrsVsQM2Q2TgqufX4A5gKPpxy1czHULDyVc84omvnh1nQLVmqXk4VBuy8WnX1AXfKxDx7xuASAc6svkZqGVkL1XkUBWT7QejHymEaYM
-  \item 5. The customer (using the webapp) check the transaction status on the Ethereum blockchain invoking $\mathtt{getProvision(customerPubKey, provisionID)}$.
+  \item 5. The customer (using the webapp) check the transaction status on the Ethereum blockchain invoking \texttt{getProvision(customerPubKey, provisionID)}.
   % monero-wallet-cli --stagenet --wallet-file customer --password "" transfer 5LHmrsVsQM2Q2TgqufX4A5gKPpxy1czHULDyVc84omvnh1nQLVmqXk4VBuy8WnX1AXfKxDx7xuASAc6svkZqGVkL1XkUBWT7QejHymEaYM 1
@@
 The experts would be incentivized to participate in the pool by the system of fees.
-They would be incentivized to vote honesty by the stake they would have to lock and reward/punishment they would get by judging correctly/incorrectly, where the ``correctly'' is determined by the quorum of votes.
+They would be incentivized to vote honesty by the stake they would have to lock and reward/punishment they would get by judging correctly/incorrectly, where the correctness is determined by the quorum of votes.
 
@@
 
-\section*{Appendix A: Proof of fairness}\label{sec:proof-of-fairness}
+\appendices
+
+\section{Appendix A: Proof of fairness}\label{app:proof-of-fairness}
 Below we describe each step and rationale of the outcome position.
+We use the notation intoruced in Section~\ref{sec:fairness-model} to analise each position in the protocol.
 
@@
   \item
-    \(\operatorname{\sigma_{1, c, n} = \sbullet}\), the customer has risked its materials but has not paid anything, so we assume he is in the neutral position \footnote{One would argue that the customer has put effort into delivering the materials to the SP or that the sample is valuable.
+    \(\operatorname{\sigma_{1, c, n} = \sbullet}\), the customer has risked its materials but has not paid for the transaction, so we assume he is in the neutral position \footnote{One would argue that the customer has put effort into delivering the materials to the SP or that the sample is valuable.
 We assume that the sample without personal information is useless, and the effort to deliver the package is negligible.}.
   \item
-    \(\operatorname{\sigma_{1, s, n} = \sbullet}\), the SP is in a neutral position as he did not put any effort, and the package has not brought any value to the SP.
+    \(\operatorname{\sigma_{1, s, n} = \sbullet}\), the SP is in a neutral position as she did not put any effort, and the package has not brought any value to the SP.
   \end{itemize}
@@
 \item
-  The customer can follow the protocol and move to the non-disadvantaged position \(\operatorname{\sigma_{1, c, n} = \sbullet}\).
-\item
-  The SP can do nothing and end up in the non-disadvantaged position \(\operatorname{\sigma_{1, s, n} = \sbullet}\) or \(\operatorname{\sigma_{1, s, d} = \sbullet}\).
-\end{itemize}
-
-\noindent \textbf
-{Step 2. Customer turn: payment}\label{step-2-pay-for-invoice}
+  The customer can follow the protocol to the non-disadvantaged position \(\operatorname{\sigma_{1, c, n} = \sbullet}\).
+\item
+  The SP can do nothing and always ends up in the non-disadvantaged position.
+\end{itemize}
+
+\noindent \textbf
+{Step 2. SP turn: proof of delivery}\label{step-2-proof-of-delivery}
+
+The SP has published proof of delivery:
+
+\begin{itemize}
+\item
+  Following protocol:
+
+  \begin{itemize}
+
+  \item
+    \(\operatorname{\sigma_{2, c, n} = \sbullet}\), the customer remains in the neutral position as the PoD allows him to pay for the transaction but does not obligate him to anything.
+  \item
+    \(\operatorname{\sigma_{2, s, n} = \sbullet}\), the SP is in a neutral position as she did not put any effort to provide the service, and the package has not brought any value to the SP.
+  \end{itemize}
+\item
+  Starting a dispute:
+
+  \begin{itemize}
+
+  \item
+    \(\operatorname{\sigma_{2, c, d} = -}\), the customer loses the case as the SP didn't receive the payment on time.
+  \item
+    \(\operatorname{\sigma_{2, s, d} = \sbullet}\), the SP win the case for the same reason.
+  \end{itemize}
+\end{itemize}
+
+The SP has acted abnormally, then:
+
+\begin{itemize}
+\item
+  Following protocol:
+
+  \begin{itemize}
+
+  \item
+    \(\operatorname{\sigma_{2, c, \overline{n}} = \sbullet}\), the customer remains in the neutral position as he is not obligated agree with the incorrect $\mathrm{PoD}$.
+  \item
+    \(\operatorname{\sigma_{2, s, \overline{n}} = \sbullet}\), the SP is in a neutral position as she did not put any effort to provide the service, and the package has not brought any value to the SP.
+  \end{itemize}
+\item
+  Starting a dispute:
+
+  \begin{itemize}
+
+  \item
+    \(\operatorname{\sigma_{2, c, \overline{d}} = -}\), the customer loses the case as the SP is not obligated to publish correct $\mathrm{PoD}$.
+  \item
+    \(\operatorname{\sigma_{2, s, \overline{d}} = \sbullet}\), the SP win the case for the same reason.
+  \end{itemize}
+\end{itemize}
+
+Fairness:
+
+\begin{itemize}
+
+\item The customer can do nothing and always ends up in a non-disadvantaged position.
+\item The SP can follow the protocol ends up in the non-disadvantaged position \(\operatorname{\sigma_{2, s, n} = \sbullet}\).
+
+\end{itemize}
+
+\noindent \textbf
+{Step 3. customer turn: get proof of delivery}\label{step-3-get-proof-of-delivery}
+
+The customer has got the PoD, then:
+
+\begin{itemize}
+\item
+  Follows the protocol:
+
+  \begin{itemize}
+
+  \item
+    $\operatorname{\sigma_{3, c, n} = \sbullet}$, the customer has the opportunity to pay for the transaction, but since he didn't put any effort, he is in the neutral position.
+  \item
+    $\operatorname{\sigma_{3, s, n} = \sbullet}$, the SP position has not changed.
+  \end{itemize}
+\item
+  Starts a dispute:
+
+  \begin{itemize}
+
+  \item
+    $\operatorname{\sigma_{3, c, d} = -}$, the customer loses the case as the SP didn't receive the payment on time.
+  \item
+    $\operatorname{\sigma_{3, s, d} = \sbullet}$, the SP win the case for the same reason.
+  \end{itemize}
+\end{itemize}
+
+The customer has acted abnormally, then:
+
+\begin{itemize}
+\item
+  Follows the protocol:
+
+  \begin{itemize}
+
+  \item
+    \(\operatorname{\sigma_{3, c, \overline{n}} = \sbullet}\), the customer can not follow the protocol but since he didn't put any efford he is in the neutral position.
+  \item
+    \(\operatorname{\sigma_{3, s, \overline{n}} = \sbullet}\), the SP position has not changed.
+  \end{itemize}
+\item
+  Starts a dispute:
+
+  \begin{itemize}
+
+  \item
+    \(\operatorname{\sigma_{3, c, \overline{d}} = -}\), the customer loses the case as the SP is not obligated to do anything before the payment is made.
+  \item
+    \(\operatorname{\sigma_{3, s, \overline{d}} = \sbullet}\), the SP wins the case and ends up in the neutral position.
+  \end{itemize}
+\end{itemize}
+
+Fairness:
+
+\begin{itemize}
+
+\item The customer can follow the protocol to the non-disadvantaged position \(\operatorname{\sigma_{3, c, n} = \sbullet}\).
+\item The SP can do nothing and always ends up in a non-disadvantaged position.
+\end{itemize}
+
+\noindent \textbf
+{Step 4. Customer turn: payment}
 
@@
 \noindent \textbf
-{Step 3. SP turn: provision of service}
+{Step 5. SP turn: provision of service}
 
@@
 \noindent \textbf
-{Step 4. SP turn: upload result}\label{step-4-publication-of-results}
+{Step 6. SP turn: upload result}\label{step-6-publication-of-results}
 
@@
 \noindent \textbf
-{Step 5. SP turn: proof of provision}\label{step-5-publication-of-proof-of-provision}
+{Step 7. SP turn: proof of provision}\label{step-7-publication-of-proof-of-provision}
 
@@
 \noindent \textbf
-{Step 6. customer turn: pull proof of provision}\label{step-6-pull-proof-of-provision}
+{Step 8. customer turn: pull proof of provision}\label{step-8-pull-proof-of-provision}
 
@@
 \noindent \textbf
-{Step 7. Customer turn: download result}\label{step-7-retrieval-of-results}
+{Step 9. Customer turn: download result}\label{step-9-retrieval-of-results}
 

### 2023-01-17 paper/access.tex
update protocol steps

@@
 Also $\mathrm{PoD}$ embodies the information whether the service has been paid in cash or should be paid by the customer using the anonymous blockchain account.
-In the latter case, the SP's payment address is included in the $\mathrm{PoD}$.
+In the latter case, the SP's payment $\mathrm{address}$ is included in the $\mathrm{PoD}$.
 
@@
 
-\subsection{Steps}\label{steps}
+\subsection{Steps}\label{sec:steps}
 
@@
 
-\begin{itemize}
-  \item 1. The protocol starts with the customer opening the webapp and creating new provision. 
+\begin{description}
+  \item[0.] The protocol starts with the customer opening the webapp and creating new provision. 
 The app generates random ECDSA (secp256k1) customer's keypair and random 32 bytes provisionID, then display QR code that encodes both the provisionID and the customer's public key. 
@@
 
-  \item 2. The customer prints the QR code, stick it on a package, and delivers the package to the SP either: in person, via trusted party, or delivery agency.
-
-  \item 3. The SP opens the app, scans the QR code decoding the provisionID and the client's public key.
-
-  \item 4.
-Since (in this experiment) the provision has not been paid in cash, the SP generate unique Monero payment address using \texttt{monero-wallet-cli integrated\_address} command, and submits the proof of delivery to the Ethereum blockchain.
+  \item[1.] The customer prints the QR code, stick it on a package, and delivers the package to the SP either: in person, via trusted party, or delivery agency.
+
+  \item[2.1.] The SP opens the app, scans the QR code decoding the provisionID and the client's public key.
+
+  \item[2.2.] Since (in this experiment) the provision has not been paid in cash, the SP generate unique Monero payment address using \texttt{monero-wallet-cli integrated\_address} 
+  \item[2.3.] The SP submits the proof of delivery to the Ethereum blockchain using MetaMask interface.
 
@@
   % Matching integrated address: 5LHmrsVsQM2Q2TgqufX4A5gKPpxy1czHULDyVc84omvnh1nQLVmqXk4VBuy8WnX1AXfKxDx7xuASAc6svkZqGVkL1XkUBWT7QejHymEaYM
-  \item 5. The customer (using the webapp) check the transaction status on the Ethereum blockchain invoking \texttt{getProvision(customerPubKey, provisionID)}.
+  \item[3.] The customer (using the webapp) check the transaction status on the Ethereum blockchain invoking \texttt{getProvision} with arguments \texttt{customerPubKey} and \texttt{provisionID}.
   % monero-wallet-cli --stagenet --wallet-file customer --password "" transfer 5LHmrsVsQM2Q2TgqufX4A5gKPpxy1czHULDyVc84omvnh1nQLVmqXk4VBuy8WnX1AXfKxDx7xuASAc6svkZqGVkL1XkUBWT7QejHymEaYM 1
@@
 
-  \item 6.
-The customer (using the \texttt{monero-wallet-cli transfer}) sends the payment to the designated in the smart contract \texttt{paymentAddress} and stores the payment attestation (using \texttt{monero-wallet-cli get\_tex\_key <tx-id>}) in case of dispute.
-
-  \item 7. Once SP notice the payment on Monero blockchain it starts providing the service and outputs the file \texttt{result.pdf}.
-
-  \item 8.
-The SP uploads the file \texttt{result.pdf} on the Filecoin and IPFS networks using Powergate.
+  \item[4.] The customer (using the \texttt{monero-wallet-cli transfer}) sends the payment to the designated in the smart contract \texttt{paymentAddress} and stores the payment attestation (using \texttt{monero-wallet-cli get\_tex\_key <tx-id>}) in case of dispute.
+
+  \item[5.] Once SP notice the payment on Monero blockchain it starts providing the service and outputs the file \texttt{result.pdf}.
+
+  \item[6.] The SP uploads the file \texttt{result.pdf} on the Filecoin and IPFS networks using Powergate.
 In result, the SP gets the content identifier \texttt{cid}, and \texttt{dealID} and \texttt{minerID}.
 
-  \item 9.
-The SP submits a Proof of Provision transaction to the Ethereum blockchain by invoking \texttt{proofOfProvision} with arguments \texttt{customerPubKey}, \texttt{provisionID}, \texttt{cid}, and \texttt{dealID}.
-
-  \item 10. Meantime, the Customer subscribes to the Ethereum and waits until the SP publishes the Proof Of Provision.
+  \item[7.] The SP submits a Proof of Provision transaction to the Ethereum blockchain by invoking \texttt{proofOfProvision} with arguments \texttt{customer\-PubKey}, \texttt{provisionID}, \texttt{cid}, and \texttt{dealID}.
+
+  \item[8.] Meantime, the Customer subscribes to the Ethereum and waits until the SP publishes the Proof Of Provision.
  Once the Proof Of Provision is published the Customer downloads the result using either: IPFS network via \texttt{https://dweb.link/<cid>} or Lotus network using \texttt{lotus retreive <cid> <minerID>}.
 
-  \item 11.
-Results are then decrypted using previously stored customer's private key.
+  \item[9.] Results are then decrypted using previously stored customer's private key.
 If everything is correct, the Customer is satisfied with the service and the protocol ends, otherwise the Customer can initiate a dispute.
 
-\end{itemize}
-
-\subsection*{Results}
-
+\end{description}
+
+\subsection{Results}
+
+\paragraph{Fariness}
+As showed in Section~\ref{sec:steps} and Appendix~\ref{app:fairness}, the protocol is fair.
+It is achieved by a undeniable hand-shake mechanism in which the SP first publishes $\mathrm{PoD}$ (step 2.) commiting to package delivery and deadlines of the service, and then the customer accepts it by paying for the service or not (step 3.).
+
+Once the payment is made, the SP stays in the advantaged position.
+Since he has agreed on the deadlines of the provision of the service, he is incentivised to provide the serice and publish the resutlts and PoP before the deadline (step 7.); because otherwise the customer—having all the evidences—can initiate a dispute and punish the SP, therefore rational parties will follow the protocol.
+
+Non-repudiation without TTP is achieved by using the blockchain and digital signatures.
+
+\paragraph{Provable Results Availability}
+Content addressable networks such as IPFS can not guarantee the availability of the content.
+However, the Filecoin network, which works as an incentivisation layer on top of IPFS that guarantees the content availability via economic incentivisations~\cite{protocollabsFilecoinDecentralizedStorage2017} can guarantee the availability of the content.
+
+The SP uploads the result on both IPFS and Filecoin networks (via Powergate) making the result available even in case of the SP stop serving the result from his node.
+
+\paragraph{Anonymity}
+We achieved anonymity by using anonymous payment methods such as cash or privacy-preserving payment blockchains (e.g.
+Monero), and decentralised storage networks like IPFS and Filecoin, allowing the customer to interact with the protocol without revealing his identity at any step of the protocol.
+
+\paragraph{Costs}
 Deploying smart contract consumed 1456577 gas.
@@
 In result, the cost of 
-1) deploying the smart contract was $0.000000002227 \frac{\mathrm{ETH}}{\mathrm gas} \times 1456577 \mathrm{gas} \times 1261.97 \frac{\mathrm{USD}}{\mathrm{ETH}} = 4.09 \mathrm{USD}$; 
-2) Proof of delivery was $0.000000002227 \frac{\mathrm{ETH}}{\mathrm gas} \times 129649 \mathrm{gas} \times 1261.97 \frac{\mathrm{USD}}{\mathrm{ETH}} = 0.29 \mathrm{USD}$; 
-3) Proof of provision was $0.000000002227 \frac{\mathrm{ETH}}{\mathrm gas} \times 149130 \mathrm{gas} \times 1261.97 \frac{\mathrm{USD}}{\mathrm{ETH}} = 0.33 \mathrm{USD}$.
+\begin{itemize}
+  \item deploying the smart contract was $0.000000002227 \frac{\mathrm{ETH}}{\mathrm gas} \cdot 1456577 \mathrm{gas} \cdot 1261.97 \frac{\mathrm{USD}}{\mathrm{ETH}} = 4.09 \mathrm{USD}$; 
+  \item Proof of delivery was $0.000000002227 \mathrm{\frac{ETH}{gas}} \cdot 129649 \mathrm{gas} \cdot 1261.97 \frac{\mathrm{USD}}{\mathrm{ETH}} = 0.29 \mathrm{USD}$; 
+  \item Proof of provision was $0.000000002227 \mathrm{\frac{ETH}{gas}} \cdot 149130 \mathrm{gas} \cdot 1261.97 \frac{\mathrm{USD}}{\mathrm{ETH}} = 0.33 \mathrm{USD}$.
+\end{itemize}
 
@@
   \item
-    \(\operatorname{\sigma_{2, s, n} = \sbullet}\), the SP is in a neutral position as she did not put any effort to provide the service, and the package has not brought any value to the SP.
+    \(\operatorname{\sigma_{2, s, n} = \sbullet}\), the SP is in a neutral position because the package has not brought her any value and she did not put any effort to provide the service yet
   \end{itemize}
@@
   \item
-    \(\operatorname{\sigma_{2, c, n} = -}\), the customer has spent his funds but has not received the result.
+    \(\operatorname{\sigma_{2, c, n} = -}\), the customer has spent his funds but has not received the result yet.
   \item

### 2023-01-17 paper/access.tex
update protocol steps

@@
 \usepackage{url}
-\usepackage{amsmath}
+\usepackage{listings}
 \usepackage{pdfpages}
@@
 \usepackage{scalerel}
-\newcommand\sbullet[1][.75]{\mathbin{\ThisStyle{\vcenter{\hbox{%
+
+\newcommand\neutral[1][.75]{\mathbin{\ThisStyle{\vcenter{\hbox{%
   \scalebox{#1}{$\SavedStyle\bullet$}}}}}%
 }
+
+\newcommand{\plus}{+}
+\newcommand{\minus}{-}
+
 \usepackage{textcomp}
@@
 
+% We observe
+We observe that the issue of anonymous service provision can be seen as a problem of fair exchange where parties exchange some goods fairly, i.e., either both parties obtain the goods, or they both obtain nothing.
+
+In our case, the customer who wants to use the service, exchanges his materials and money with the SP for the result of the service.
+
+% Therefore we propose
 We propose a protocol for anonymously provisioning services that require the delivery of physical materials.
@@
 
-In case of dispute, either due to exceeding deadlines or providing an incorrect result, the customer can disclose the whole interaction and prove to justice (police or court) the misbehaviour of the SP.
+In case of dispute, either due to exceeding deadlines or providing an incorrect result, the customer can disclose the whole interaction and prove to justice the misbehaviour of the SP.
 
@@
 \begin{itemize}
-    \item Privacy-preserving cryptocurrency, to allow customers anonymously pay for the services.
-    \item Message board blockchain, to achieve fairness, i.e., as a means for proving that certain actions took place at a certain moment without the trusted third party (TTP).
-    \item Content-addressable peer-to-peer storage network to provide results to customers. 
+    \item Blockchain (aka message board), to achieve fairness, i.e., as a means for proving that certain actions took place at a certain moment without the trusted third party (TTP).
+    \item Anonymous payment methods, like cash or privacy-preserving cryptocurrencies, allowing customers to pay for the services anonymously.
+    \item Content-addressable decentralised storage network (like IPFS) to anonymously provide results to customers. 
+    \item Provable storage network (like Filecoin) to guarantee that the results are available to the customer even in case of the SP deny of service.
     \item Cryptography
@@
         \item Symmetric encryption, to encrypt and decrypt results published on the public networks.
-        \item Public-key cryptography, to derive shared secrets for symmetric encryption.
+        \item Public-key cryptography, and Diffie-Helman key exchange (DHKE) to derive shared secrets for symmetric encryption.
         \item Digital signatures, to achieve authentication and non-repudiation of actions. 
@@
 
-We observe that the issue of anonymous service provision can be seen as a problem of fair exchange where parties exchange some goods fairly, i.e., either both parties obtain the goods, or they both obtain nothing.
-
-In our case, the customer who wants to use the service, exchanges his materials and cryptocurrencies with the SP for the result of the service.
-
 %\paragraph{Contributions}
-We contribute to the field of fair exchanges by proposing a simple, practical, and anonymous protocol that does not rely on the centralized TTP, but uses decentralized blockchain and
+We contribute to the field of fair exchanges by proposing a simple, practical, and anonymous protocol that does not rely on centralized TTP, but uses decentralized blockchain and
 distributed content-addressable storage network.
@@
 \item Anonymity: the customer stays anonymous to all external observers throughout the transaction.
-\item Fairness:
-at each step of the protocol, both parties are incentivized to act accordingly to the protocol; otherwise, the misbehaving party ends up in a disadvantaged position.
+\item Fairness: at each step of the protocol, both parties are incentivized to act accordingly to the protocol; otherwise, the misbehaving party ends up in a disadvantaged position.
 \item Dispute resolution: at each step of the protocol, the customer can start a dispute and win the case if and only if the SP misbehaved.
@@
 our protocol does not rely on a trusted third party to conduct transactions fairly.
-Only in case of dispute the centralized justice is involved (the justice decentralization is discussed in section ~\ref{sec:discussion}.
+Only in case of a dispute, the centralised justice is involved, which can be instantiated either with courts and polices, or blockchain-based dispute resolution mechanisms as discussed in Section~\ref{sec:justice}.
 \item Physical materials: our protocol allows providing not only digital but also physical materials to the service provider.
@@
 
-Some authors have proposed blockchain-based fair-exchange systems that could be adapted to service provision; however, to our best knowledge, we are the first to propose a system that satisfies all five properties stated above using blockchain technology.
-Especially anonymity and physical materials delivery were rarely addressed together, and if so, the protocol was based on TTP and impractical assumptions on banking system~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} or did not address the conflict
-between parties~\cite{altawyLelantosBlockchainBasedAnonymous2017}.
-
-Our protocol may enable various services currently based on unacceptable trust assumptions to the SP.
+Some authors have proposed blockchain-based fair-exchange systems that could be adapted to service provision; however, to our best knowledge, we are the first to propose a system that satisfies all five properties stated above.
+Especially anonymity and physical materials delivery were rarely addressed together, and if so, the protocol was based on TTP and impractical assumptions on banking system~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} or did not address the conflict between parties~\cite{altawyLelantosBlockchainBasedAnonymous2017}.
 
@@
 The vision of smart contracts was to replace the legal contract with
-programmable and autonomous contracts. The smart contract code encompasses the contract's specifications, hence the slogan \textit{code as a law}.
-
-Nevertheless, the blockchain paradigm has its limitations.
+programmable and autonomous contracts.
+The smart contract code encompasses the contract's specifications, hence the slogan \textit{code as a law}.
+Moreover, smart contracts are automatically executed merging together the gap of law and its enforcment by police~\cite{allenGovernanceBlockchainDispute2019}.
+However, the blockchain paradigm has its limitations.
+
 Blockchain can assure the correctness of data existing only on the blockchain.
@@
 
-Possible directions toward semi-autonomous decentralized resolution system are discussed in section ~\ref{sec:discussion}.
+Possible directions toward semi-autonomous decentralized resolution system are discussed in Section~\ref{sec:decentralised-justice}.
 
@@
   \begin{center}
-  \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{experiment1.pdf}
+  \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{anonser-experiment1.pdf}
   \end{center}
@@
   \begin{center}
-  \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{experiment2.pdf}
+  \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{anonser-experiment2.pdf}
   \end{center}
@@
 
-\begin{description}
+\begin{enumerate}
+  \setcounter{enumi}{0}
   \item[0.] The protocol starts with the customer opening the webapp and creating new provision. 
@@
 
-\end{description}
+\end{enumerate}
 
@@
 
-\subsection{Justice}\label{justice}
+\subsection{Justice}\label{sec:decentralised-justice}
 
@@
 
-The possible directions for mitigation of such issues are to either (i) replace justice with decentralized autonomous organizations (DAO) like proposed in Themis~\cite{mengThemisDecentralizedEscrow2019}, Kleros~\cite{bergollaKlerosSociolegalCase2022}, or Aragon Court\footnote{https://aragon.org/aragon-court}; or (ii) make it infeasible to provide incorrect results.
+The possible directions for mitigation of such issues are to either (i) replace local justice with Online Dispute Resolution systems like proposed in Themis~\cite{mengThemisDecentralizedEscrow2019}, Kleros~\cite{bergollaKlerosSociolegalCase2022,gudkovCrowdArbitrationBlockchain2020}, Aragon Court\footnote{Aragon Court, Decentralized Dispute Resolution Protocol, https://aragon.org/aragon-court, (last visited Jan.
+10, 2023)}, LTO Network\footnote{LTO Network, 2019, https://lto.network/, (last visited Jan.
+17, 2023)}, and other blockchain dispute resolution platforms~\cite{allenGovernanceBlockchainDispute2019}; or (ii) make it infeasible to provide incorrect results.
 
@@
   \item
-    \(\operatorname{\sigma_{1, c, n} = \sbullet}\), the customer has risked its materials but has not paid for the transaction, so we assume he is in the neutral position \footnote{One would argue that the customer has put effort into delivering the materials to the SP or that the sample is valuable.
+    \(\operatorname{\sigma_{1, c, n} = \neutral}\), the customer has risked its materials but has not paid for the transaction, so we assume he is in the neutral position \footnote{One would argue that the customer has put effort into delivering the materials to the SP or that the sample is valuable.
 We assume that the sample without personal information is useless, and the effort to deliver the package is negligible.}.
   \item
-    \(\operatorname{\sigma_{1, s, n} = \sbullet}\), the SP is in a neutral position as she did not put any effort, and the package has not brought any value to the SP.
+    \(\operatorname{\sigma_{1, s, n} = \neutral}\), the SP is in a neutral position as she did not put any effort, and the package has not brought any value to the SP.
   \end{itemize}
@@
   \item
-    \(\operatorname{\sigma_{1, s, d} = \sbullet}\), the SP win the case for the same reason.
+    \(\operatorname{\sigma_{1, s, d} = \neutral}\), the SP win the case for the same reason.
   \end{itemize}
@@
 \item
-  The customer can follow the protocol to the non-disadvantaged position \(\operatorname{\sigma_{1, c, n} = \sbullet}\).
+  The customer can follow the protocol to the non-disadvantaged position \(\operatorname{\sigma_{1, c, n} = \neutral}\).
 \item
@@
   \item
-    \(\operatorname{\sigma_{2, c, n} = \sbullet}\), the customer remains in the neutral position as the PoD allows him to pay for the transaction but does not obligate him to anything.
-  \item
-    \(\operatorname{\sigma_{2, s, n} = \sbullet}\), the SP is in a neutral position because the package has not brought her any value and she did not put any effort to provide the service yet
+    \(\operatorname{\sigma_{2, c, n} = \neutral}\), the customer remains in the neutral position as the PoD allows him to pay for the transaction but does not obligate him to anything.
+  \item
+    \(\operatorname{\sigma_{2, s, n} = \neutral}\), the SP is in a neutral position because the package has not brought her any value and she did not put any effort to provide the service yet
   \end{itemize}
@@
   \item
-    \(\operatorname{\sigma_{2, s, d} = \sbullet}\), the SP win the case for the same reason.
+    \(\operatorname{\sigma_{2, s, d} = \neutral}\), the SP win the case for the same reason.
   \end{itemize}
@@
   \item
-    \(\operatorname{\sigma_{2, c, \overline{n}} = \sbullet}\), the customer remains in the neutral position as he is not obligated agree with the incorrect $\mathrm{PoD}$.
-  \item
-    \(\operatorname{\sigma_{2, s, \overline{n}} = \sbullet}\), the SP is in a neutral position as she did not put any effort to provide the service, and the package has not brought any value to the SP.
+    \(\operatorname{\sigma_{2, c, \overline{n}} = \neutral}\), the customer remains in the neutral position as he is not obligated agree with the incorrect $\mathrm{PoD}$.
+  \item
+    \(\operatorname{\sigma_{2, s, \overline{n}} = \neutral}\), the SP is in a neutral position as she did not put any effort to provide the service, and the package has not brought any value to the SP.
   \end{itemize}
@@
   \item
-    \(\operatorname{\sigma_{2, s, \overline{d}} = \sbullet}\), the SP win the case for the same reason.
+    \(\operatorname{\sigma_{2, s, \overline{d}} = \neutral}\), the SP win the case for the same reason.
   \end{itemize}
@@
 \item The customer can do nothing and always ends up in a non-disadvantaged position.
-\item The SP can follow the protocol ends up in the non-disadvantaged position \(\operatorname{\sigma_{2, s, n} = \sbullet}\).
+\item The SP can follow the protocol ends up in the non-disadvantaged position \(\operatorname{\sigma_{2, s, n} = \neutral}\).
 
@@
   \item
-    $\operatorname{\sigma_{3, c, n} = \sbullet}$, the customer has the opportunity to pay for the transaction, but since he didn't put any effort, he is in the neutral position.
-  \item
-    $\operatorname{\sigma_{3, s, n} = \sbullet}$, the SP position has not changed.
+    $\operatorname{\sigma_{3, c, n} = \neutral}$, the customer has the opportunity to pay for the transaction, but since he didn't put any effort, he is in the neutral position.
+  \item
+    $\operatorname{\sigma_{3, s, n} = \neutral}$, the SP position has not changed.
   \end{itemize}
@@
   \item
-    $\operatorname{\sigma_{3, s, d} = \sbullet}$, the SP win the case for the same reason.
+    $\operatorname{\sigma_{3, s, d} = \neutral}$, the SP win the case for the same reason.
   \end{itemize}
@@
   \item
-    \(\operatorname{\sigma_{3, c, \overline{n}} = \sbullet}\), the customer can not follow the protocol but since he didn't put any efford he is in the neutral position.
-  \item
-    \(\operatorname{\sigma_{3, s, \overline{n}} = \sbullet}\), the SP position has not changed.
+    \(\operatorname{\sigma_{3, c, \overline{n}} = \neutral}\), the customer can not follow the protocol but since he didn't put any efford he is in the neutral position.
+  \item
+    \(\operatorname{\sigma_{3, s, \overline{n}} = \neutral}\), the SP position has not changed.
   \end{itemize}
@@
   \item
-    \(\operatorname{\sigma_{3, s, \overline{d}} = \sbullet}\), the SP wins the case and ends up in the neutral position.
+    \(\operatorname{\sigma_{3, s, \overline{d}} = \neutral}\), the SP wins the case and ends up in the neutral position.
   \end{itemize}
@@
 
-\item The customer can follow the protocol to the non-disadvantaged position \(\operatorname{\sigma_{3, c, n} = \sbullet}\).
+\item The customer can follow the protocol to the non-disadvantaged position \(\operatorname{\sigma_{3, c, n} = \neutral}\).
 \item The SP can do nothing and always ends up in a non-disadvantaged position.
@@
   \item
-    \(\operatorname{\sigma_{2, s, d} = +}\), the SP win the case for the same reason.
+    \(\operatorname{\sigma_{2, s, d} = \neutral}\), the SP win the case for the same reason.
   \end{itemize}
@@
   \item
-    \(\operatorname{\sigma_{2, c, \overline{n}} = \sbullet}\), the customer ends up in the neutral position as he did not spend his funds.
-  \item
-    \(\operatorname{\sigma_{2, s, \overline{n}} = \sbullet}\), the SP ends up in a neutral position as he did not receive the payment, nor spent his resources.
+    \(\operatorname{\sigma_{2, c, \overline{n}} = \neutral}\), the customer ends up in the neutral position as he did not spend his funds.
+  \item
+    \(\operatorname{\sigma_{2, s, \overline{n}} = \neutral}\), the SP ends up in a neutral position as he did not receive the payment, nor spent his resources.
   \end{itemize}
@@
   \item
-    \(\operatorname{\sigma_{2, s, \overline{d}} = \sbullet}\), the SP is not charged to justice due to a lack of proof.
+    \(\operatorname{\sigma_{2, s, \overline{d}} = \neutral}\), the SP is not charged to justice due to a lack of proof.
   \end{itemize}
@@
 \item
-  The customer can move the protocol forward to step 3, where if the SP follows the protocol then the customer can push the protocol forward up to the last termination step \(\operatorname{\sigma_{7, c, n} = +}\), otherwise if at any step the SP does not follow the protocol the customer can start a dispute which terminates the protocol at the non-disadvantaged position, i.e., \(\operatorname{\sigma_{3, c, \overline{d}} = \sbullet}\), \(\operatorname{\sigma_{4, c, \overline{d}} = \sbullet}\), \(\operatorname{\sigma_{5, c, \overline{d}} = \sbullet}\).
-\item
-  The SP can do nothing and end up in the non-disadvantaged position \(\operatorname{\sigma_{2, s, n} = +}\), \(\operatorname{\sigma_{2, s, d} = +}\), \(\operatorname{\sigma_{2, s, \overline{n}} = \sbullet}\), \(\operatorname{\sigma_{2, s, \overline{d}} = \sbullet}\).
+  The customer can move the protocol forward to step 3, where if the SP follows the protocol then the customer can push the protocol forward up to the last termination step \(\operatorname{\sigma_{7, c, n} = +}\), otherwise if at any step the SP does not follow the protocol the customer can start a dispute which terminates the protocol at the non-disadvantaged position, i.e., \(\operatorname{\sigma_{3, c, \overline{d}} = \neutral}\), \(\operatorname{\sigma_{4, c, \overline{d}} = \neutral}\), \(\operatorname{\sigma_{5, c, \overline{d}} = \neutral}\).
+\item
+  The SP can do nothing and end up in the non-disadvantaged position \(\operatorname{\sigma_{2, s, n} = +}\), \(\operatorname{\sigma_{2, s, d} = +}\), \(\operatorname{\sigma_{2, s, \overline{n}} = \neutral}\), \(\operatorname{\sigma_{2, s, \overline{d}} = \neutral}\).
 \end{itemize}
@@
   \item
-    \(\operatorname{\sigma_{3, s, d} = +}\), the SP win the case for the same reason.
+    \(\operatorname{\sigma_{3, s, d} = \neutral}\), the SP win the case for the same reason.
   \end{itemize}
@@
   \item
-    \(\operatorname{\sigma_{3, c, \overline{d}} = \sbullet}\), the customer wins the case and ends up in the neutral position.
+    \(\operatorname{\sigma_{3, c, \overline{d}} = \neutral}\), the customer wins the case and ends up in the neutral position.
   \item
@@
 \item
-  The customer can do nothing if the SP follows the protocol, which will ultimately put him in the advantaged position \(\operatorname{\sigma_{7, c, n} = +}\), or in case of the SP not following the protocol, the customer can start a dispute and terminate in the non-disadvantaged position \(\operatorname{\sigma_{3, c, \overline{d}} = \sbullet}\).
+  The customer can do nothing if the SP follows the protocol, which will ultimately put him in the advantaged position \(\operatorname{\sigma_{7, c, n} = +}\), or in case of the SP not following the protocol, the customer can start a dispute and terminate in the non-disadvantaged position \(\operatorname{\sigma_{3, c, \overline{d}} = \neutral}\).
 \item
@@
   \item
-    \(\operatorname{\sigma_{4, s, d} = +}\), the SP win the case for the same reason.
+    \(\operatorname{\sigma_{4, s, d} = \neutral}\), the SP win the case for the same reason.
   \end{itemize}
@@
   \item
-    \(\operatorname{\sigma_{4, c, \overline{d}} = \sbullet}\), the customer wins the case and ends up in a neutral position. 
+    \(\operatorname{\sigma_{4, c, \overline{d}} = \neutral}\), the customer wins the case and ends up in a neutral position. 
   \item
@@
 \item
-  The customer can do nothing if the SP follows the protocol, which will ultimately put him in an advantaged position \(\operatorname{\sigma_{7, c, n} = +}\), or in case of the SP not following the protocol, the customer can start a dispute and terminate in the non-disadvantaged position \(\operatorname{\sigma_{4, c, \overline{d}} = \sbullet}\).
+  The customer can do nothing if the SP follows the protocol, which will ultimately put him in an advantaged position \(\operatorname{\sigma_{7, c, n} = +}\), or in case of the SP not following the protocol, the customer can start a dispute and terminate in the non-disadvantaged position \(\operatorname{\sigma_{4, c, \overline{d}} = \neutral}\).
 \item
@@
   \item
-    \(\operatorname{\sigma_{5, c, \overline{d}} = \sbullet}\), the customer wins the case and ends up in the neutral position. 
+    \(\operatorname{\sigma_{5, c, \overline{d}} = \neutral}\), the customer wins the case and ends up in the neutral position. 
   \item
@@
   The customer can do nothing if the SP follows the protocol because it will ultimately put him in the advantaged position \(\operatorname{\sigma_{7, c, n} = +}\); otherwise, in case of the SP not following the protocol, the customer can start a dispute and terminate in the non-disadvantaged position.
-  \(\operatorname{\sigma_{5, c, \overline{d}} = \sbullet}\).
+  \(\operatorname{\sigma_{5, c, \overline{d}} = \neutral}\).
 \item
@@
   \item
-    \(\operatorname{\sigma_{6, c, \overline{d}} = \sbullet}\), the customer wins the case and ends up in the neutral position.
+    \(\operatorname{\sigma_{6, c, \overline{d}} = \neutral}\), the customer wins the case and ends up in the neutral position.
   \item
@@
 \item
-  The customer can follow the protocol to the position \(\operatorname{\sigma_{6, c, n} = -}\), which lets him move the protocol to the non-disadvantaged termination position \(\operatorname{\sigma_{7, c, n} = +}\), or in case the SP has not followed the protocol start a dispute and win the case \(\operatorname{\sigma_{6, c, \overline{d}} = \sbullet}\).
+  The customer can follow the protocol to the position \(\operatorname{\sigma_{6, c, n} = -}\), which lets him move the protocol to the non-disadvantaged termination position \(\operatorname{\sigma_{7, c, n} = +}\), or in case the SP has not followed the protocol start a dispute and win the case \(\operatorname{\sigma_{6, c, \overline{d}} = \neutral}\).
 \item
@@
   \item
-    \(\operatorname{\sigma_{7, c, \overline{d}} = \sbullet}\), the customer wins the case and ends up in the neutral position.
+    \(\operatorname{\sigma_{7, c, \overline{d}} = \neutral}\), the customer wins the case and ends up in the neutral position.
   \item
@@
 \item
-  The customer can follow the protocol to the non-disadvantaged termination position \(\operatorname{\sigma_{7, c, n} = +}\), or in case the SP has not followed the protocol start a dispute and win the case \(\operatorname{\sigma_{7, c, \overline{d}} = \sbullet}\).
+  The customer can follow the protocol to the non-disadvantaged termination position \(\operatorname{\sigma_{7, c, n} = +}\), or in case the SP has not followed the protocol start a dispute and win the case \(\operatorname{\sigma_{7, c, \overline{d}} = \neutral}\).
 \item
@@
 \end{itemize}
+
+% \section{Appendix B: Smart contract code}\label{appendix-b-smart-contract-code}
+
+% \input{solidity-highlighting.tex}
+% \begin{lstlisting}[language=Solidity]
+% // SPDX-License-Identifier: MIT
+% pragma solidity >=0.4.22 <0.9.0;
+
+% contract AnonSer {
+%     struct Provision {
+%         uint256 issueTime;
+%         uint256 paymentDeadlineTime;
+%         uint256 provisionDeadlineTime;
+%         bool paidInCash;
+%         string paymentAddress;
+%         string cid;
+%         bool exist;
+%         uint256 dealId;
+%         string minerId;
+%     }
+
+%     mapping(bytes => mapping(bytes32 => Provision)) public provisions;
+
+%     address private _owner;
+
+%     event ProofOfDelivery(
+%         bytes indexed clientPubKey,
+%         bytes32 indexed provisionId,
+%         uint256 issueTime,
+%         uint256 paymentDeadlineTime,
+%         uint256 provisionDeadlineTime,
+%         bool paidInCash,
+%         string paymentAddress
+%     );
+
+%     constructor() {
+%         _owner = msg.sender;
+%     }
+
+%     modifier onlyOwner() {
+%         require(
+%             _owner == msg.sender,
+%             "Ownership Assertion: Caller of the function is not the owner."
+%         );
+%         _;
+%     }
+
+%     function proofOfDelivery(
+%         bytes memory clientPubKey,
+%         bytes32 provisionId,
+%         bool paidInCash,
+%         string memory paymentAddress
+%     ) public onlyOwner {
+%         if (provisions[clientPubKey][provisionId].exist) {
+%             revert("Provision already exists");
+%         }
+%         if (paidInCash && bytes(paymentAddress).length > 0) {
+%             revert("Payment address should be empty if paid in cash");
+%         }
+%         if (!paidInCash && bytes(paymentAddress).length == 0) {
+%             revert(
+%                 "Payment address should not be empty if didn't paid in cash"
+%             );
+%         }
+%         Provision memory provision = Provision({
+%             exist: true,
+%             issueTime: block.timestamp,
+%             paymentDeadlineTime: block.timestamp + 1 days,
+%             provisionDeadlineTime: block.timestamp + 8 days,
+%             paidInCash: paidInCash,
+%             paymentAddress: paymentAddress,
+%             dealId: 0,
+%             cid: "",
+%             minerId: ""
+%         });
+%         provisions[clientPubKey][provisionId] = provision;
+%         emit ProofOfDelivery(
+%             clientPubKey,
+%             provisionId,
+%             provision.issueTime,
+%             provision.paymentDeadlineTime,
+%             provision.provisionDeadlineTime,
+%             provision.paidInCash,
+%             provision.paymentAddress
+%         );
+%     }
+
+%     event ProofOfProvision(
+%         bytes indexed clientPubKey,
+%         bytes32 indexed provisionId,
+%         string cid,
+%         uint256 dealId,
+%         string minerId
+%     );
+
+%     function proofOfProvision(
+%         bytes memory clientPubKey,
+%         bytes32 provisionId,
+%         string memory cid,
+%         uint256 dealId,
+%         string memory minerId
+%     ) public onlyOwner {
+%         Provision storage provision = provisions[clientPubKey][provisionId];
+%         if (!provision.exist) {
+%             revert("Provision must be created with proof of delivery first");
+%         }
+
+%         provision.cid = cid;
+%         provision.dealId = dealId;
+%         provision.minerId = minerId;
+%         emit ProofOfProvision(clientPubKey, provisionId, cid, dealId, minerId);
+%     }
+
+%     function getProvision(bytes memory clientPubKey, bytes32 provisionId)
+%         public
+%         view
+%         returns (Provision memory)
+%     {
+%         return provisions[clientPubKey][provisionId];
+%     }
+% }
+% \end{lstlisting}
 

### 2023-01-18 paper/access.tex
Add blockchain-obviousness as a feature Improve "The remainer of this paper" Improve the Dispute resolution system paragraph.
Improve Justice section

Add Self-sovereign identities paragraph

@@
 \item Dispute resolution: at each step of the protocol, the customer can start a dispute and win the case if and only if the SP misbehaved.
-
+\item Blockchain-obvious: the customer using our protocol does not need to interact with the blockchain directly; especially, he does not need to obtain funds and pay for the transaction fees, allowing the use of our protocol for non-technical users.
 \item TTP-less: 
@@
 In section~\ref{sec:related-works} we review related works. 
-Then, in section~\ref{sec:building-blocks} we explain the building blocks of fair exchanges, blockchain, storage network, anonymity and confidentiality.
+Then, in section~\ref{sec:building-blocks} we discuss the concepts of dispute resolution system, self-sorveign identifiers, fairness, message board, anonimity, payment for services, storage network, result availability, anonymity and confidentiality.
 Section~\ref{sec:protocol} describes how the protocol works in detail.
@@
 The technique of providing real-world data to the blockchain is called oracle.
-Oracle provides data based on a decentralized network of mediators; therefore, the trust is also decentralized.
+Oracle provides data based on a decentralized network of mediators; therefore, the trust is also decentralized~\cite{breidenbachChainlinkNextSteps2021}.
 
@@
 
-Justice is the biggest obstacle in achieving a system that complies with Web 3.0 postulates\footnote{https://en.wikipedia.org/wiki/Web3}.
+Centralised justice is the biggest obstacle in achieving a system that complies with Web 3.0 postulates\footnote{https://en.wikipedia.org/wiki/Web3}.
 
@@
 Moreover, since Filecoin is a blockchain by itself, it could play both roles of message board and storage network.
+
+\subsection{Self-sovereign identities}
+Our research in the field showed that some jurisdictions require SPs to associate the diagnosis with the customer personal information.
+For example, in Poland all laboratories performing medical diagnostic tests, and collecting the material (except tests for HIV) are obligated to the unambiguous identification and verification of the identity of the patient from whom the material was collected~\footnote{Regulation of the Minister of Health of March 23, 2006 on quality standards for medical diagnostic and microbiological laboratories, https://isap.sejm.gov.pl/isap.nsf/DocDetails.xsp?id=WDU20060610435}.
+
+This conflicts with the main goal of our protocol, which is to prevent any identification information from being collected.
+
+One promising solution would be to use Self-sovereign identities (SSI)~\cite{muhleSurveyEssentialComponents2018}, especially the verifable claims.
+A trusted authority (e.g., a government) would issue a one-time claim for a customer that would be accepted by the SP as a legitimate personal identificator.
+The SP would associate the diagnosis result with the provided DID.
+The DID itself would not contain any personal information, therefore the SP would learn nothing about the customer identity besides the random-looking identificator.
+The DID could be deanonimised by the collaboration with the government.
+
+However, since SSI is relatively new technology and the government has not yet adopted it, we decided to postpone the discussion of this topic to the future work.
 

### 2023-01-19 paper/access.tex
refactor proof of fairness

@@
 \documentclass{ieeeaccess}
+
 \usepackage{cite}
@@
 \usepackage{graphicx}
+\usepackage{textcomp}
+
 \usepackage{caption}
@@
 
+\newcommand{\plus}{+}
+\newcommand{\minus}{-}
 \newcommand\neutral[1][.75]{\mathbin{\ThisStyle{\vcenter{\hbox{%
@@
 
-\newcommand{\plus}{+}
-\newcommand{\minus}{-}
-
-\usepackage{textcomp}
+\newcommand{\floor}[1]{\left\lfloor #1 \right\rfloor}
+\newcommand{\ceil}[1]{\left\lceil #1 \right\rceil}
+
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 \history{Date of publication xxxx 00, 0000, date of current version xxxx 00, 0000.}
-\doi{10.1109/ACCESS.2017.DOI}
-
-\title{Privacy-preserving service provisioning using distributed networks}
+\doi{10.1109/ACCESS.2022.0122113}
+
+\title{Privacy-preserving physical delivery service provisioning using distributed networks}
 \author{\uppercase{Stanis\l{}aw Bara{\'n}ski} \authorrefmark{1},
@@
 \markboth{S. Bara{\'n}ski, J. Szyma{\'n}ski : 
-Anonymous provision of services via blockchain}
+Privacy-preserving physical delivery service provisioning using distributed networks}
 {S. Bara{\'n}ski, J. Szyma{\'n}ski : 
-Anonymous provision of services via blockchain}
+Privacy-preserving physical delivery service provisioning using distributed networks}
 
@@
 
-\titlepgskip=-15pt
+\titlepgskip=-21pt
 
 \maketitle
+
 \section{Introduction}
+\label{sec:introduction}
 Service providers (SPs) like lawyers, laboratories, auditors, or banks, to provide services, require data that is often associated with the user identity.
@@
     \item Anonymous payment methods, like cash or privacy-preserving cryptocurrencies, allowing customers to pay for the services anonymously.
-    \item Content-addressable decentralised storage network (like IPFS) to anonymously provide results to customers. 
-    \item Provable storage network (like Filecoin) to guarantee that the results are available to the customer even in case of the SP deny of service.
+    \item Content-addressable decentralised storage network (e.g., IPFS) to anonymously provide results to customers together with provable storage netwrok (e.g., Filecoin) to guarantee that the results are available to the customer even in case of the SP deny of service.
     \item Cryptography
@@
 %\paragraph{Contributions}
-We contribute to the field of fair exchanges by proposing a simple, practical, and anonymous protocol that does not rely on centralized TTP, but uses decentralized blockchain and
-distributed content-addressable storage network.
-
-Also, we support physical materials delivery, which was rarely targeted by other researchers or based on strong and unpractical assumptions.
-
-Our protocol simultaneously provides five main properties:
-
-\begin{itemize}
-\item Anonymity: the customer stays anonymous to all external observers throughout the transaction.
-\item Fairness: at each step of the protocol, both parties are incentivized to act accordingly to the protocol; otherwise, the misbehaving party ends up in a disadvantaged position.
-\item Dispute resolution: at each step of the protocol, the customer can start a dispute and win the case if and only if the SP misbehaved.
-\item Blockchain-obvious: the customer using our protocol does not need to interact with the blockchain directly; especially, he does not need to obtain funds and pay for the transaction fees, allowing the use of our protocol for non-technical users.
-\item TTP-less: 
-our protocol does not rely on a trusted third party to conduct transactions fairly.
-Only in case of a dispute, the centralised justice is involved, which can be instantiated either with courts and polices, or blockchain-based dispute resolution mechanisms as discussed in Section~\ref{sec:justice}.
-\item Physical materials: our protocol allows providing not only digital but also physical materials to the service provider.
-\end{itemize}
-
-Some authors have proposed blockchain-based fair-exchange systems that could be adapted to service provision; however, to our best knowledge, we are the first to propose a system that satisfies all five properties stated above.
+We contribute to the state of the art by:
+
+\begin{itemize}
+\item proposing a novel protocol that:
+  \begin{itemize}
+  \item allows \textbf{anonymous} service provision, i.e., the service provider does not need to collect any personal information from the customer.
+  \item achieves \textbf{fairness} by carefully designing the protocol as an interactive non-cooperative game, in which the SP remains in advantageous position, and customer in disadvantageus with the option to start a dispute in case the SP misbehaviour.
+  \item \textbf{does not rely on centralized TTP}, but uses decentralized blockchain and distributed content-addressable storage network.
+  \item abstracts the customers from the blockchain technology used underneath, allowing the use of our protocol for \textbf{non-technical users}.
+  \item allows the \textbf{delivery of physical materials}, which was rarely addressed by other researchers or based on strong and unpractical assumptions.
+  \item guarantees the \textbf{remote availability of the results}, even in case of the SP denial of service.
+  \end{itemize} 
+\item Systemise often misused definitions of anonymity, pseudonymity, linkability, and traceability.
+\item Proposing a framework for analysing fairness analysis in fair-exchange protocols.
+\item Discuss the possible improvements to the protocol witht the use of secure computation, self-sovereign identities, zero-knowledge proofs, and blockchain-based dispute resolution mechanisms.
+\end{itemize}
+
+% Our protocol simultaneously provides five main properties:
+
+% \begin{itemize}
+% \item Anonymity: the customer stays anonymous to all external observers throughout the transaction.
+% \item Fairness: at each step of the protocol, both parties are incentivized to act accordingly to the protocol; otherwise, the misbehaving party ends up in a disadvantaged position.
+% \item Dispute resolution: at each step of the protocol, the customer can start a dispute and win the case if and only if the SP misbehaved.
+% \item Blockchain-obvious: the customer using our protocol does not need to interact with the blockchain directly; especially, he does not need to obtain funds and pay for the transaction fees, allowing the use of our protocol for non-technical users.
+% \item TTP-less: 
+% our protocol does not rely on a trusted third party to conduct transactions fairly.
+Only in case of a dispute, the centralised justice is involved, which can be instantiated either with courts and polices, or blockchain-based dispute resolution mechanisms as discussed in Section~\ref{sec:decentralised-justice}.
+% \item Physical materials: our protocol allows providing not only digital but also physical materials to the service provider.
+% \end{itemize}
+
+Some authors have proposed blockchain-based fair-exchange systems that could be adapted to service provision; however, to our best knowledge, we are the first to propose a system that satisfies all the properties stated above.
 Especially anonymity and physical materials delivery were rarely addressed together, and if so, the protocol was based on TTP and impractical assumptions on banking system~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} or did not address the conflict between parties~\cite{altawyLelantosBlockchainBasedAnonymous2017}.
@@
 In section~\ref{sec:related-works} we review related works. 
-Then, in section~\ref{sec:building-blocks} we discuss the concepts of dispute resolution system, self-sorveign identifiers, fairness, message board, anonimity, payment for services, storage network, result availability, anonymity and confidentiality.
+Then, in section~\ref{sec:building-blocks} we discuss the building blocks of dispute resolution system, blockchain as a message board, fairness, payment for services, storage network, result availability, anonymity and confidentiality.
 Section~\ref{sec:protocol} describes how the protocol works in detail.
 Section~\ref{sec:fairness-analysis} provides a fairness analysis of the proposed protocol.
-Section~\ref{sec:discussion} discuss possible improvements. 
+In Section~\ref{sec:experiments} we present the implementation of the protocol and results of our experiments.
+Section~\ref{sec:discussion} discuss possible improvements in terms of crowd sourced dispute resolution or dispute avoidance, self-sovereign identities (SSI), and anonymous delivery.
 Finally, section~\ref{sec:conclusion} concludes the paper.
@@
 Also, our protocol does not provide its own dispute resolution mechanism as Themis does.
-However, we assume the existence of an abstract justice which accepts evidences and ., which can be instantiated with either local court or police, or one of the available online dispute resolution services like Themis~\cite{mengThemisDecentralizedEscrow2019}, Kleros~\cite{bergollaKlerosSociolegalCase2022}, Aragon Court\footnote{https://aragon.org/aragon-court}, or others~\cite{allenGovernanceBlockchainDispute2019}.
+However, we assume the existence of an abstract justice that accepts evidence and punishes the misbehaving party.
+It can be instantiated with either local court or police, or one of the blockchain
+dispute resolution services like Themis~\cite{mengThemisDecentralizedEscrow2019}, Kleros~\cite{bergollaKlerosSociolegalCase2022,gudkovCrowdArbitrationBlockchain2020}, Aragon Court\footnote{Aragon Court, Decentralized Dispute Resolution Protocol, https://aragon.org/aragon-court, (last visited Jan.
+10, 2023)}, LTO Network\footnote{LTO Network, 2019, https://lto.network/, (last visited Jan.
+17, 2023)}, and other Online Dispute Resolution platforms~\cite{allenGovernanceBlockchainDispute2019}.
 
@@
   \newcommand{\TTP}{\cellcolor{red!50}TTP}
-  \newcommand{\BC}{\cellcolor{green!50}Blockchain}
+  \newcommand{\BC}{\cellcolor{green!50}BC}
   \caption{Related work comparision}
@@
   \setlength{\tabcolsep}{3pt}
-  \begin{tabular}{|p{38pt}|p{32pt}|p{38pt}|p{35pt}|p{37pt}|p{30pt}|}
+  \begin{tabular}{|p{40pt}|p{35pt}|p{40pt}|p{35pt}|p{30pt}|p{30pt}|}
   \hline
@@
 
-Overly techniques that achieve anonymity on top of non-privacy-preserving blockchains are: Ethereum's Tornado Cash\cite{pertsevTornadoCashPrivacy2019} (via zkSNARK~\cite{grothSizePairingbasedNoninteractive2016} and MiMC~\cite{albrechtMiMCEfficientEncryption2016}), Bitcoin's Wasabi\footnote{https://wasabiwallet.io/} (via CoinJoin \cite{maxwellCoinJoinBitcoinPrivacy2013}).
+Overly techniques that achieve anonymity on top of non-privacy-preserving blockchains are: Ethereum's Tornado Cash\cite{pertsevTornadoCashPrivacy2019} (via zkSNARK~\cite{grothSizePairingbasedNoninteractive2016} and MiMC~\cite{albrechtMiMCEfficientEncryption2016}), Bitcoin's Wasabi\footnote{Wasabi Wallet, Open-source, non-custodial Bitcoin Wallet for desktop, \url{https://wasabiwallet.io/}, (last visited Nov.
+28, 2022)} (via CoinJoin \cite{maxwellCoinJoinBitcoinPrivacy2013}).
 
@@
 \item separate address: each transaction derives a new address uniquely associated with the transaction.
-Such addresses can be derived using Hierarchical Deterministic Wallets (BIP-32)\footnote{https://github.com/bitcoin/bips/blob/master/bip-0032.mediawiki}.
+Such addresses can be derived using Hierarchical Deterministic Wallets (BIP-32)\footnote{Bitcoin Improvement Proposals,Hierarchical Deterministic Wallets, \url{https://github.com/bitcoin/bips/blob/master/bip-0032.mediawiki}, (last visited Dec.
+03, 2022)}.
 \item memo: the payments are sent to one SP account but contain an extra field named ``memo'' filled with the unique number provided by the SP in $\mathrm{PoD}$.
@@
 \noindent \textbf
-{Content Identifier (cid)}\label{content-identifier-cid} is a term coined by IPFS\footnote{https://docs.ipfs.tech/concepts/content-addressing}. However, since our protocol does not depend on
-this particular implementation of the storage network, we let the $\mathrm{cid}$ be any other identifier that securely and uniquely points to the content.
+{Content Identifier (cid)}\label{content-identifier-cid} is a term coined by IPFS\footnote{IPFS, Content addressing and CIDs, \url{https://docs.ipfs.tech/concepts/content-addressing}, (last visited Dec.
+01, 2022)}.
+However, since our protocol does not depend on this particular implementation of the storage network, we let the $\mathrm{cid}$ be any other identifier that securely and uniquely points to the content.
 
@@
 {Step 5. Provision of service}\label{step-5-provision-of-service}
+
 Once the customer has paid for the transaction either in cash or using the anonymous blockchain, the SP can start providing the service.
@@
 {Step 9. Download result}\label{step-9-download-result}
+
 Having the $\mathrm{cid}$, the customer downloads and decrypts the $\mathrm{result}$ using shared key derived from the customer's secret key $\mathrm{sk(C)}$ and the SP's public key $\mathrm{pk(S)}$ using DHKE method.
@@
   \item{Anonymous payments} — we use the Monero blockchain \cite{noetherRingSignatureConfidential2015}.
-  \item{Storage netowork} — we use the Powergate\footnote{https://github.com/textileio/powergate}, which is a wrapper around Filecoin and IPFS.
-  \item{Message board} — we use the Ethereum blockchain \cite{woodEthereumSecureDecentralised2014}; concretely, Truffle Ganache\footnote{https://trufflesuite.com/ganache/} and Solidity language.
-  \item{Customer and SP} — we create client side web application (webapp) using \texttt{React}\footnote{https://reactjs.org} for creating UI, \texttt{web3.js}\footnote{https://web3js.org} for interaction with Ethereum, and \texttt{crypto-js}\footnote{https://github.com/brix/crypto-js} for encryption.
-We use \texttt{MetaMask}\footnote{https://metamask.io} browser extension for signing and submiting transactions to Ethereum's node.
-We use \texttt{monerod}\footnote{https://monerodocs.org/interacting/monerod-reference/} network client and \texttt{monero-wallet-cli}\footnote{https://monerodocs.org/interacting/monero-wallet-cli-reference/} command-line interface for interacting with Monero blockchain.
+  \item{Storage netowork} — we use the Powergate\footnote{Powergate, \url{https://github.com/textileio/powergate}, (last visited Dec. 20, 2022)}, which is a wrapper around Filecoin and IPFS.
+  \item{Message board} — we use the Ethereum blockchain \cite{woodEthereumSecureDecentralised2014}; concretely, Truffle Ganache\footnote{Truffle Ganache, \url{https://trufflesuite.com/ganache/}, (last visited Dec.
+20, 2022)} and Solidity language.
+  \item{Customer and SP} — we create client side web application (webapp) using \texttt{React}\footnote{React, A JavaScript library for building user interfaces, \url{https://reactjs.org}, (last visited Dec.
+20, 2022)} for creating UI, and \texttt{web3.js}\footnote{web3.js, A JavaScript library for building on Ethereum, \url{https://web3js.org}, (last visited Dec.
+20, 2022)} for interaction with Ethereum.
+We use \texttt{MetaMask}\footnote{MetaMask, A crypto wallet \& gateway to blockchain apps, \url{https://metamask.io}, (last visited Dec.
+20, 2022)} browser extension for signing and submiting transactions to Ethereum's node.
+We use \texttt{monerod}\footnote{Monero, The Monero daemon \texttt{monerod}, \url{https://monerodocs.org/interacting/monerod-reference/}, (last visited Dec.
+20, 2022)} network client and \texttt{monero-wallet-cli}\footnote{Monero, The CLI client for Monero, \url{https://monerodocs.org/interacting/monero-wallet-cli-reference/}, (last visited Dec.
+20, 2022)} command-line interface for interacting with Monero blockchain.
 \end{itemize}
@@
 \paragraph{Fariness}
-As showed in Section~\ref{sec:steps} and Appendix~\ref{app:fairness}, the protocol is fair.
+As showed in Section~\ref{sec:steps} and Appendix~\ref{app:proof-of-fairness}, the protocol is fair.
 It is achieved by a undeniable hand-shake mechanism in which the SP first publishes $\mathrm{PoD}$ (step 2.) commiting to package delivery and deadlines of the service, and then the customer accepts it by paying for the service or not (step 3.).
@@
 Non-repudiation without TTP is achieved by using the blockchain and digital signatures.
+Blockchain guarantees that each change to the state of the smart contract is visible to everyone and only the SP is allowed to modify its state.
 
 \paragraph{Provable Results Availability}
-Content addressable networks such as IPFS can not guarantee the availability of the content.
-However, the Filecoin network, which works as an incentivisation layer on top of IPFS that guarantees the content availability via economic incentivisations~\cite{protocollabsFilecoinDecentralizedStorage2017} can guarantee the availability of the content.
+Content addressable networks such as IPFS can not guarantee the availability of the content\footnote{Nothing prevents the SP from publishing the result, receiving the $\mathrm{cid}$, publishing $\mathrm{PoP}$, and immediately after removing the result from the local storage.
+In case of dispute, the SP can upload the content again, proving its availability.
+The SP has no motivation to proceed with this kind of misbehaviour other than putting the customer in a disadvantaged position caused by the lost dispute.}.
+However, the Filecoin network, which works as an incentivisation layer on top of IPFS, increases the content availability via economic incentivisations (i.e., punishment in case of lack of proof of storage of the content)~\cite{protocollabsFilecoinDecentralizedStorage2017}.
 
@@
 Proof of provision consumed 149130 gas.
-The price of gas at the time of the experiment (03.01.2023) was $0.000000002227 \frac{\mathrm{ETH}}{\mathrm gas}$\footnote{https://etherscan.io/gastracker}, and the price of 1 $\mathrm{ETH}$ was $1261.97 \mathrm{USD}$.
+The price of gas at the time of the experiment (Jan.
+03, 2023) was $0.000000002227 \frac{\mathrm{ETH}}{\mathrm gas}$\footnote{Etherscan, Ethereum Gas Tracker, \url{https://etherscan.io/gastracker}, (last visited Jan.
+03, 2023)}, and the price of 1 $\mathrm{ETH}$ was $1261.97 \mathrm{USD}$.
 In result, the cost of 
@@
 
-Centralised justice is the biggest obstacle in achieving a system that complies with Web 3.0 postulates\footnote{https://en.wikipedia.org/wiki/Web3}.
-
-The possible directions for mitigation of such issues are to either (i) replace local justice with Online Dispute Resolution systems like proposed in Themis~\cite{mengThemisDecentralizedEscrow2019}, Kleros~\cite{bergollaKlerosSociolegalCase2022,gudkovCrowdArbitrationBlockchain2020}, Aragon Court\footnote{Aragon Court, Decentralized Dispute Resolution Protocol, https://aragon.org/aragon-court, (last visited Jan.
+Centralised justice is the biggest obstacle in achieving a system that complies with Web 3.0 postulates\footnote{Web3, \url{https://en.wikipedia.org/wiki/Web3}, (last visited Jan. 05, 2023)}.
+
+The possible directions for mitigation of such issues are to either (i) replace local justice with blockchain dispute resolution systems like proposed in Themis~\cite{mengThemisDecentralizedEscrow2019}, Kleros~\cite{bergollaKlerosSociolegalCase2022,gudkovCrowdArbitrationBlockchain2020}, Aragon Court\footnote{Aragon Court, Decentralized Dispute Resolution Protocol, https://aragon.org/aragon-court, (last visited Jan.
 10, 2023)}, LTO Network\footnote{LTO Network, 2019, https://lto.network/, (last visited Jan.
-17, 2023)}, and other blockchain dispute resolution platforms~\cite{allenGovernanceBlockchainDispute2019}; or (ii) make it infeasible to provide incorrect results.
+17, 2023)}, and other Online Dispute Resolution platforms~\cite{allenGovernanceBlockchainDispute2019}; or (ii) make it infeasible to provide incorrect results.
 
@@
 Concretely, the problem canes down to ``How to represent blood digitally?''.
-If we could represent urine, blood, saliva, or any other physical material in a binary format and let the customer take a sample, discrete it, and send it to the SP by himself, then the whole chain of integrity could be ensured.
-Therefore, wrong service provision would be infeasible.
-
-\subsection{Provable availability of the
-result}\label{cryptographically-provable-availability-of-results}
-
-Currently, the SP has to publish the result into a peer-to-peer content-addressable storage network, e.g., IPFS.
-The problem is that nothing prevents the SP from publishing the result, receiving the $\mathrm{cid}$, publishing $\mathrm{PoP}$, and immediately after removing the result from the local storage.
-In case of dispute, the SP can upload the content again, proving its availability.
-The SP has no motivation to proceed with this kind of misbehaviour other than putting the customer in a disadvantaged position caused by the lost dispute.
-We see possible prevention of this misbehaviour by the usage of Filecoin—an incentive layer on top of IPFS that guarantees the content availability via economic incentivisations~\cite{protocollabsFilecoinDecentralizedStorage2017}.
-With the help of Filecoin, the SP would be obligated to create a deal that guarantees the availability of the result until the deadline of the transaction.
-Moreover, since Filecoin is a blockchain by itself, it could play both roles of message board and storage network.
+If we could represent urine, blood, saliva, or any other physical material in a binary format and let the customer take a sample, discrete it, and send it to the SP, then the whole chain of integrity could be ensured.
+Therefore, incorrect service provision would be infeasible, and hence, disputes would be avoided.
 
@@
 Our research in the field showed that some jurisdictions require SPs to associate the diagnosis with the customer personal information.
-For example, in Poland all laboratories performing medical diagnostic tests, and collecting the material (except tests for HIV) are obligated to the unambiguous identification and verification of the identity of the patient from whom the material was collected~\footnote{Regulation of the Minister of Health of March 23, 2006 on quality standards for medical diagnostic and microbiological laboratories, https://isap.sejm.gov.pl/isap.nsf/DocDetails.xsp?id=WDU20060610435}.
+For example, in Poland all laboratories performing medical diagnostic tests, and collecting the material (except tests for HIV) are obligated to the unambiguous identification and verification of the identity of the patient from whom the material was collected~\footnote{Regulation of the Minister of Health of March 23, 2006 on quality standards for medical diagnostic and microbiological laboratories, \url{https://isap.sejm.gov.pl/isap.nsf/DocDetails.xsp?id=WDU20060610435}}.
 
@@
 
+\appendices
+
+\section{Proof of fairness}\label{app:proof-of-fairness}
+Below we describe each step and rationale of the outcome position.
+We use the notation introduced in Section~\ref{sec:fairness-model} to analise each position in the protocol and fariness Definition~\ref{def:fairness} to show the fairness of the protocol.
+
+\newcommand{\customer}{customer}
+\renewcommand{\sp}{SP}
+\newcommand{\AgreeablePath}{Agreeable path:}
+\newcommand{\DisputePath}{The customer starts a dispute:}
+\newcommand{\Fairness}{Fairness:}
+\newcommand{\CustomerTurn}[0]{\expandafter\MakeUppercase customer turn:}
+\newcommand{\SPTurn}[0]{\sp{} turn:}
+
+\newcommand{\CanFollowToOne}[2]{The #1 can follow the protocol to the non-disadvantaged position #2}
+\newcommand{\CanDoNothing}[1]{The #1 can do nothing and always end up in the non-disadvantaged position}
+\newcommand{\CanDoAnything}[1]{The #1 can do anything and always end up in the non-disadvantaged position}
+\newcommand{\Pos}[4]{$\operatorname{\sigma_{#1, #2, #3} = #4}$}
+\newcommand{\WinForTheSameReason}[1]{The #1 wins the dispute for the same reason}
+
+\newcommand{\CustomerLosesBeforePayment}{The customer loses the dispute because the SP is not obligated to do anything until the transaction is paid}
+\newcommand{\CustomerLosesBeforePoP}{The customer loses the dispute because the SP still can publish the PoP within the agreed timeframe}
+
+\newcommand{\normal}{n}
+\newcommand{\dispute}{d}
+\newcommand{\abnormal}{\overline{n}}
+\newcommand{\abdispute}{\overline{d}}
+
+\newcommand{\PoD}{$\mathrm{PoD}$}
+\newcommand{\PoP}{$\mathrm{PoP}$}
+
+\newcommand{\RemainsIn}[2]{The #1 remains in the #2 position}
+
+\subsubsection*{Step 1. \CustomerTurn{} Package delivery}\label{step-1-deliver-package}
+
+The protocol starts when the customer correctly execute the first step of the protocol, i.e., deliver the package to the SP.
+
+The case where the customer does not deliver the package is not considered as it is not a part of the protocol.
+
+\begin{itemize}
+\item \AgreeablePath
+  \begin{itemize}
+    \item  \Pos{1}{c}{\normal}{\neutral}, the customer risked his materials but did not pay for the transaction therefore ends up in neutral position\footnote{One would argue that the customer has put effort into delivering the materials to the SP or that the materials are valuable.
+We assume that the materials without personal information is useless, and the effort to deliver the package is negligible.}.
+    \item \Pos{1}{s}{\normal}{\neutral}, the SP ends up in neutral position as she did not spend any resources and the package did not bring her any value.
+  \end{itemize}
+\item \DisputePath
+  \begin{itemize}
+    \item \Pos{1}{c}{\dispute}{\minus}, \CustomerLosesBeforePayment{}.
+    \item \Pos{1}{s}{\dispute}{\neutral}, \WinForTheSameReason{SP}.
+  \end{itemize}
+\end{itemize}
+
+\Fairness
+
+\begin{itemize}
+  \item \CanFollowToOne{customer}{\Pos{1}{c}{n}{\neutral}}
+  \item \CanDoNothing{SP}
+\end{itemize}
+
+\subsubsection*{Step 2. \SPTurn{} Proof of Delivery}\label{step-2-proof-of-delivery}
+
+The SP publishes the PoD, then:
+
+\begin{itemize}
+  \item \AgreeablePath
+    \begin{itemize}
+      \item \Pos{2}{c}{\normal}{\neutral}, the customer remains in the neutral position as the PoD allows him to pay for the transaction but does not obligate him to anything.
+      \item \Pos{2}{s}{\normal}{\neutral}, the SP remains in the neutral position as the package has not brought her any value and she did not spend any resource to provide the service yet.
+    \end{itemize}
+
+  \item \DisputePath
+    \begin{itemize}
+      \item \Pos{2}{c}{\dispute}{\minus}, \CustomerLosesBeforePayment{}.
+      \item \Pos{2}{s}{\dispute}{\neutral}, \WinForTheSameReason{SP}.
+    \end{itemize}
+\end{itemize}
+
+The SP acted abnormally, then:
+
+\begin{itemize}
+\item \AgreeablePath
+  \begin{itemize}
+    \item \Pos{2}{c}{\abnormal}{\neutral}, the customer remains in the neutral position as he is not obligated to agree with the incorrect $\mathrm{PoD}$.
+    \item \Pos{2}{s}{\abnormal}{\neutral}, the SP remains in the neutral position as the package has not brought her any value and she did not spend any resource to provide the service yet.
+  \end{itemize}
+\item \DisputePath
+  \begin{itemize}
+    \item \Pos{2}{c}{\abdispute}{\minus}, \CustomerLosesBeforePayment{}, not even to publish correct $\mathrm{PoD}$.
+    \item \Pos{2}{s}{\abdispute}{\neutral}, \WinForTheSameReason{SP}.
+  \end{itemize}
+\end{itemize}
+
+\Fairness
+
+\begin{itemize}
+  \item \CanDoAnything{SP}.
+  \item The customer can either wait (in case of the SP following the protocol), or abandon the transaction (in case of the SP acting abnormally).
+In both cases the customer ends up in non-disadvantaged position \Pos{2}{c}{\normal}{\neutral} or \Pos{2}{c}{\abnormal}{\neutral}
+\end{itemize}
+
+\subsubsection{Step 3. \CustomerTurn\ Get Proof of Delivery}\label{step-3-get-proof-of-delivery}
+
+The customer got the \PoD, then:
+
+\begin{itemize}
+\item \AgreeablePath
+  \begin{itemize}
+    \item \Pos{3}{c}{\normal}{\neutral}, \RemainsIn{customer}{neutral}.
+    \item \Pos{3}{s}{\normal}{\neutral}, \RemainsIn{SP}{neutral}.
+  \end{itemize}
+\item \DisputePath
+  \begin{itemize}
+    \item \Pos{3}{c}{\dispute}{\minus}, \CustomerLosesBeforePayment{}.
+    \item \Pos{3}{s}{\dispute}{\neutral}, \WinForTheSameReason{SP}.
+  \end{itemize}
+\end{itemize}
+
+The customer acted abnormally, then:
+\begin{itemize}
+\item \AgreeablePath
+  \begin{itemize}
+    \item \Pos{3}{c}{\abnormal}{\neutral}, \RemainsIn{customer}{neutral}.
+    \item \Pos{3}{s}{\abnormal}{\neutral}, \RemainsIn{SP}{neutral}.
+  \end{itemize}
+\item \DisputePath
+  \begin{itemize}
+    \item \Pos{3}{c}{\abdispute}{\minus}, \CustomerLosesBeforePayment{}.
+    \item \Pos{3}{s}{\abdispute}{\neutral}, \WinForTheSameReason{SP}.
+  \end{itemize}
+\end{itemize}
+
+\Fairness
+
+\begin{itemize}
+  \item The customer can follow the protocol to the non-disadvantaged position \Pos{3}{c}{\normal}{\neutral}.
+  \item \CanDoNothing{SP}.
+\end{itemize}
+
+\subsubsection{Step 4. \CustomerTurn{} Payment}
+
+The customer paid the transaction:
+
+\begin{itemize}
+\item \AgreeablePath
+  \begin{itemize}
+    \item \Pos{4}{c}{\normal}{\minus}, the customer paid in advance.
+    \item \Pos{4}{s}{\normal}{\plus}, the SP received the payment, but has not spent his resources yet.
+  \end{itemize}
+\item \DisputePath
+  \begin{itemize}
+    \item \Pos{4}{c}{\dispute}{\minus}, \CustomerLosesBeforePoP{}.
+    \item \Pos{4}{s}{\dispute}{\neutral}, \WinForTheSameReason{SP}.
+  \end{itemize}
+\end{itemize}
+
+The customer acted abnormally, then:
+
+\begin{itemize}
+\item \AgreeablePath
+  \begin{itemize}
+    \item \Pos{4}{c}{\abnormal}{\neutral}, the customer ends up in the neutral position as he did not spend his funds.
+    \item \Pos{4}{s}{\abnormal}{\neutral}, the SP ends up in a neutral position as he did not receive the payment, nor spent his resources.
+  \end{itemize}
+\item \DisputePath
+  \begin{itemize}
+    \item \(\operatorname{\sigma_{2, c, \overline{d}} = -}\), the customer loses the case as he can not prove the payment before the time limit.
+    \item \(\operatorname{\sigma_{2, s, \overline{d}} = \neutral}\), the SP is not charged to justice due to a lack of proof.
+  \end{itemize}
+\end{itemize}
+
+\Fairness
+
+\begin{itemize}
+  \item The customer can move the protocol forward to step 3, where if the SP follows the protocol then the customer can push the protocol forward up to the last termination step \(\operatorname{\sigma_{7, c, n} = +}\), otherwise if at any step the SP does not follow the protocol the customer can start a dispute which terminates the protocol at the non-disadvantaged position, i.e., \(\operatorname{\sigma_{3, c, \overline{d}} = \neutral}\), \(\operatorname{\sigma_{4, c, \overline{d}} = \neutral}\), \(\operatorname{\sigma_{5, c, \overline{d}} = \neutral}\).
+  \item The SP can do nothing and end up in the non-disadvantaged position \(\operatorname{\sigma_{2, s, n} = +}\), \(\operatorname{\sigma_{2, s, d} = +}\), \(\operatorname{\sigma_{2, s, \overline{n}} = \neutral}\), \(\operatorname{\sigma_{2, s, \overline{d}} = \neutral}\).
+\end{itemize}
+
+\subsubsection{Step 5. SP turn: Provision of service}
+
+The SP has made the provision of service:
+
+\begin{itemize}
+\item \AgreeablePath
+  \begin{itemize}
+    \item \(\operatorname{\sigma_{3, c, n} = -}\), the customer has not received the result, so he remains in the disadvantaged position. 
+    \item \(\operatorname{\sigma_{3, s, n} = +}\), the SP has fulfilled the contract on time.
+  \end{itemize}
+\item \DisputePath
+  \begin{itemize}
+    \item \(\operatorname{\sigma_{3, c, d} = -}\), the customer loses the case as the SP has still the opportunity to publish proof of provision within the timeframe. 
+    \item \(\operatorname{\sigma_{3, s, d} = \neutral}\), the SP win the case for the same reason.
+  \end{itemize}
+\end{itemize}
+
+The SP has acted abnormally, then:
+
+\begin{itemize}
+\item \AgreeablePath
+  \begin{itemize}
+    \item \(\operatorname{\sigma_{3, c, \overline{n}} = -}\), the customer ends up in a disadvantaged position.
+    \item \(\operatorname{\sigma_{3, s, \overline{n}} = +}\), the SP ends up in the advantaged position as he received the payment. 
+  \end{itemize}
+\item \DisputePath
+  \begin{itemize}
+    \item \(\operatorname{\sigma_{3, c, \overline{d}} = \neutral}\), the customer wins the case and ends up in the neutral position.
+    \item \(\operatorname{\sigma_{3, s, \overline{d}} = -}\), the SP loses the case and ends up in the disadvantaged position. 
+  \end{itemize}
+\end{itemize}
+
+\Fairness
+
+\begin{itemize}
+  \item The customer can do nothing if the SP follows the protocol, which will ultimately put him in the advantaged position \(\operatorname{\sigma_{7, c, n} = +}\), or in case of the SP not following the protocol, the customer can start a dispute and terminate in the non-disadvantaged position \(\operatorname{\sigma_{3, c, \overline{d}} = \neutral}\).
+  \item The SP can follow the protocol and move to the non-disadvantaged position \(\operatorname{\sigma_{3, s, n} = +}\), or not follow the protocol and also end up at the non-disadvantaged position \(\operatorname{\sigma_{3, s, \overline{n}} = +}\), but the second option puts him at risk of terminating the protocol at \(\operatorname{\sigma_{3, s, \overline{n}} = +}\), if the customer is rational and starts a dispute.
+\end{itemize}
+
+\subsubsection{Step 6. SP turn: Upload result}\label{step-6-publication-of-results}
+
+The SP has uploaded the result on time:
+
+\begin{itemize}
+\item \AgreeablePath
+  \begin{itemize}
+
+  \item
+    \(\operatorname{\sigma_{4, c, n} = -}\), the customer has not received the result, so he remains in the disadvantaged position. 
+  \item
+    \(\operatorname{\sigma_{4, s, n} = +}\), the SP has fulfilled the contract on time.
+  \end{itemize}
+\item \DisputePath
+
+  \begin{itemize}
+
+  \item
+    \(\operatorname{\sigma_{4, c, d} = -}\), the customer loses the case as the SP has still an opportunity to publish proof of provision within the timeframe. 
+  \item
+    \(\operatorname{\sigma_{4, s, d} = \neutral}\), the SP win the case for the same reason.
+  \end{itemize}
+\end{itemize}
+
+The SP has acted abnormally, then:
+
+\begin{itemize}
+\item \AgreeablePath
+  \begin{itemize}
+    \item \(\operatorname{\sigma_{4, c, \overline{n}} = -}\), the customer ends up in the disadvantaged position. 
+    \item \(\operatorname{\sigma_{4, s, \overline{n}} = +}\), the SP ends up in the advantaged position as he received the payment. 
+  \end{itemize}
+\item \DisputePath
+  \begin{itemize}
+    \item \(\operatorname{\sigma_{4, c, \overline{d}} = \neutral}\), the customer wins the case and ends up in a neutral position. 
+    \item \(\operatorname{\sigma_{4, s, \overline{d}} = -}\), the SP loses the case and ends up in the disadvantaged position. 
+  \end{itemize}
+\end{itemize}
+
+\Fairness
+
+\begin{itemize}
+  \item The customer can do nothing if the SP follows the protocol, which will ultimately put him in an advantaged position \(\operatorname{\sigma_{7, c, n} = +}\), or in case of the SP not following the protocol, the customer can start a dispute and terminate in the non-disadvantaged position \(\operatorname{\sigma_{4, c, \overline{d}} = \neutral}\).
+  \item The SP can follow the protocol and move to the non-disadvantaged position \(\operatorname{\sigma_{4, s, n} = +}\), or not follow the protocol and also end up at the non-disadvantaged position \(\operatorname{\sigma_{4, s, \overline{n}} = +}\), but the second option puts him at risk of terminating the protocol at \(\operatorname{\sigma_{4, s, \overline{n}} = +}\), if the customer is rational and starts a dispute.
+\end{itemize}
+
+\subsubsection{Step 7. SP turn: Proof of provision}\label{step-7-publication-of-proof-of-provision}
+
+The SP has published PoP on time:
+
+\begin{itemize}
+  \item \AgreeablePath
+    \begin{itemize}
+      \item \(\operatorname{\sigma_{5, c, n} = -}\), the customer has not received the result. Therefore, he remains in the disadvantaged position. 
+      \item \(\operatorname{\sigma_{5, s, n} = +}\), the SP has fulfilled the contract on time.
+    \end{itemize}
+  \item \DisputePath
+    \begin{itemize}
+      \item \(\operatorname{\sigma_{5, c, d} = -}\), the customer loses the case as the SP can prove the publication of proof of provision. 
+      \item \(\operatorname{\sigma_{5, s, d} = +}\), the SP win the case for the same reason.
+    \end{itemize}
+\end{itemize}
+
+The SP has acted abnormally, then:
+
+\begin{itemize}
+\item \AgreeablePath
+  \begin{itemize}
+    \item \(\operatorname{\sigma_{5, c, \overline{n}} = -}\), the customer ends up in the disadvantaged position.
+    \item \(\operatorname{\sigma_{5, s, \overline{n}} = +}\), the SP ends up in the advantaged position as he received the payment.
+  \end{itemize}
+\item \DisputePath
+  \begin{itemize}
+    \item \(\operatorname{\sigma_{5, c, \overline{d}} = \neutral}\), the customer wins the case and ends up in the neutral position. 
+    \item \(\operatorname{\sigma_{5, s, \overline{d}} = -}\), the SP loses the case and ends up in the disadvantaged position. 
+  \end{itemize}
+\end{itemize}
+
+Fairness:
+
+\begin{itemize}
+  \item The customer can do nothing if the SP follows the protocol because it will ultimately put him in the advantaged position \(\operatorname{\sigma_{7, c, n} = +}\); otherwise, in case of the SP not following the protocol, the customer can start a dispute and terminate in the non-disadvantaged position.
+\(\operatorname{\sigma_{5, c, \overline{d}} = \neutral}\).
+  \item The SP can follow the protocol and move to the non-disadvantaged position \(\operatorname{\sigma_{5, s, n} = +}\), or not follow the protocol and also end up at the non-disadvantaged position \(\operatorname{\sigma_{5, s, \overline{n}} = +}\), but the second option puts him at risk of terminating the protocol at \(\operatorname{\sigma_{5, s, \overline{n}} = +}\), if the customer is rational and starts a dispute.
+\end{itemize}
+
+\subsubsection{Step 8. customer turn: Get Proof of Provision}\label{step-8-pull-proof-of-provision}
+
+The SP has uploaded the result on time, then:
+
+\begin{itemize}
+\item \AgreeablePath
+  \begin{itemize}
+    \item \(\operatorname{\sigma_{6, c, n} = -}\), the customer gets a hash of the result but not the result yet.
+    \item \(\operatorname{\sigma_{6, s, n} = +}\), the SP position has not changed.
+  \end{itemize}
+\item \DisputePath
+
+  \begin{itemize}
+    \item \(\operatorname{\sigma_{6, c, d} = -}\), the customer loses the case as the SP can prove the publication of proof of provision. 
+    \item \(\operatorname{\sigma_{6, s, d} = +}\), the SP win the case for the same reason.
+  \end{itemize}
+\end{itemize}
+
+The customer has acted abnormally, then:
+
+\begin{itemize}
+\item \AgreeablePath
+  \begin{itemize}
+    \item \(\operatorname{\sigma_{6, c, \overline{n}} = -}\), the customer does not have the access to $cid$, and hence, can not get the result from the storage network.
+    \item \(\operatorname{\sigma_{6, s, \overline{n}} = +}\), the SP ends up in the advantaged position as he received the payment but did not spend his resources.
+  \end{itemize}
+\item \DisputePath
+  \begin{itemize}
+    \item \(\operatorname{\sigma_{6, c, \overline{d}} = \neutral}\), the customer wins the case and ends up in the neutral position.
+    \item \(\operatorname{\sigma_{6, s, \overline{d}} = -}\), the SP loses the case and ends up in the disadvantaged position.
+  \end{itemize}
+\end{itemize}
+
+\Fairness
+
+\begin{itemize}
+  \item The customer can follow the protocol to the position \(\operatorname{\sigma_{6, c, n} = -}\), which lets him move the protocol to the non-disadvantaged termination position \(\operatorname{\sigma_{7, c, n} = +}\), or in case the SP has not followed the protocol start a dispute and win the case \(\operatorname{\sigma_{6, c, \overline{d}} = \neutral}\).
+  \item The SP can do nothing and end up in a non-disadvantaged position \(\operatorname{\sigma_{6, s, n} = +}\), or \(\operatorname{\sigma_{6, s, \overline{n}} = +}\).
+\end{itemize}
+
+\subsubsection{Step 9. Customer turn: Download resul}\label{step-9-retrieval-of-results}
+
+The SP has published the correct result on time:
+
+\begin{itemize}
+\item \AgreeablePath
+  \begin{itemize}
+    \item \(\operatorname{\sigma_{7, c, n} = +}\), the customer gets the correct result. Therefore, he moves to the advantaged position. 
+    \item \(\operatorname{\sigma_{7, s, n} = +}\), the SP position has not changed. 
+  \end{itemize}
+\item \DisputePath
+  \begin{itemize}
+    \item \(\operatorname{\sigma_{7, c, d} = -}\), the customer loses the case as the SP can prove the publication of proof of provision. 
+    \item \(\operatorname{\sigma_{7, s, d} = +}\), the SP win the case for the same reason.
+  \end{itemize}
+\end{itemize}
+
+The customer has acted abnormally, then:
+
+\begin{itemize}
+\item \AgreeablePath
+  \begin{itemize}
+    \item \(\operatorname{\sigma_{7, c, \overline{n}} = -}\), the customer ends up in a disadvantaged position, as he ends up with the incorrect result.
+    \item \(\operatorname{\sigma_{7, c, \overline{n}} = +}\), the SP ends up in the advantaged position as he received the payment but did not spend his resources.
+  \end{itemize}
+\item \DisputePath
+
+  \begin{itemize}
+
+  \item
+    \(\operatorname{\sigma_{7, c, \overline{d}} = \neutral}\), the customer wins the case and ends up in the neutral position.
+  \item
+    \(\operatorname{\sigma_{7, c, \overline{d}} = -}\), the SP loses the case and ends up in the disadvantaged position.
+  \end{itemize}
+\end{itemize}
+
+Fairness:
+
+\begin{itemize}
+
+\item
+  The customer can follow the protocol to the non-disadvantaged termination position \(\operatorname{\sigma_{7, c, n} = +}\), or in case the SP has not followed the protocol start a dispute and win the case \(\operatorname{\sigma_{7, c, \overline{d}} = \neutral}\).
+\item
+  The SP can do nothing and ends up in the non-disadvantaged position \(\operatorname{\sigma_{7, s, n} = +}\).
+\end{itemize}
+
 \bibliographystyle{IEEEtran}
@@
 
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{stanislaw.jpg}}]{Stanis\l{}aw Bara{\'n}ski} received BEng in 2019 and MSc in 2020 in informatics at Gdańsk University of Technology.
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{stanislaw.jpg}}]{Stanis\L{}aw Bara{\'n}ski} received BEng in 2019 and MSc in 2020 in informatics at Gdańsk University of Technology.
 Currently, he is a PhD candidate at the Department of Computer Architecture, Faculty of Electronics, Telecommunications and Informatics, Gdansk University of Technology.
 
-His research interests include blockchains and cryptography, especially the issue of blockchain-based internet voting and mitigation of content poisoning attacks via blockchain.
-
-He likes to develop his ideas right up to the commercialization stage.
-He is the author of multiple mobile and web applications that have reached success on the market.
+His research interests include blockchains, applied cryptography, and secure computation; particularly the issue of blockchain-based internet voting, but also other areas that currently depend on trusted third parties.
+
+He likes to validate his ideas in practice, developing them up to the commercialization stage.
+He is the author of multiple software products that have reached success in the market.
 His blockchain-based internet voting project has been funded by the Stellar Community Fund for the most useful Stellar application.
@@
 His mainstream of this research is building semantic memory models that improve natural language processing.
-He also worked on analyzing
-human emotions, by mining EEG signals. His results are implemented in
-the form of brain-machine interfaces for disabled people. He also works
-on analyzing data within the IoT domain and its secure storage on the blockchain. 
+He also worked on analyzing human emotions, by mining EEG signals.
+His results are implemented in the form of brain-machine interfaces for disabled people.
+He also works on analyzing data within the IoT domain and its secure storage on the blockchain.
 He is involved in project, where acquisition of data from sensors placed in beehives  allows one to predict apiary development and detect abnormalities.
@@
 \end{IEEEbiography}
-
-\appendices
-
-\section{Appendix A: Proof of fairness}\label{app:proof-of-fairness}
-Below we describe each step and rationale of the outcome position.
-We use the notation intoruced in Section~\ref{sec:fairness-model} to analise each position in the protocol.
-
-\noindent \textbf
-{Step 1. Customer turn: package delivery}\label{step-1-deliver-package}
-
-The customer has delivered the package:
-
-\begin{itemize}
-\item Agreeable path:
-  \begin{itemize}
-  \item
-    \(\operatorname{\sigma_{1, c, n} = \neutral}\), the customer has risked its materials but has not paid for the transaction, so we assume he is in the neutral position \footnote{One would argue that the customer has put effort into delivering the materials to the SP or that the sample is valuable.
-We assume that the sample without personal information is useless, and the effort to deliver the package is negligible.}.
-  \item
-    \(\operatorname{\sigma_{1, s, n} = \neutral}\), the SP is in a neutral position as she did not put any effort, and the package has not brought any value to the SP.
-  \end{itemize}
-\item
-  Starting a dispute:
-
-  \begin{itemize}
-
-  \item
-    \(\operatorname{\sigma_{1, c, d} = -}\), the customer loses the case as the SP has still an opportunity to publish proof of provision within the timeframe.
-  \item
-    \(\operatorname{\sigma_{1, s, d} = \neutral}\), the SP win the case for the same reason.
-  \end{itemize}
-\end{itemize}
-
-Fairness:
-
-\begin{itemize}
-
-\item
-  The customer can follow the protocol to the non-disadvantaged position \(\operatorname{\sigma_{1, c, n} = \neutral}\).
-\item
-  The SP can do nothing and always ends up in the non-disadvantaged position.
-\end{itemize}
-
-\noindent \textbf
-{Step 2. SP turn: proof of delivery}\label{step-2-proof-of-delivery}
-
-The SP has published proof of delivery:
-
-\begin{itemize}
-\item
-  Following protocol:
-
-  \begin{itemize}
-
-  \item
-    \(\operatorname{\sigma_{2, c, n} = \neutral}\), the customer remains in the neutral position as the PoD allows him to pay for the transaction but does not obligate him to anything.
-  \item
-    \(\operatorname{\sigma_{2, s, n} = \neutral}\), the SP is in a neutral position because the package has not brought her any value and she did not put any effort to provide the service yet
-  \end{itemize}
-\item
-  Starting a dispute:
-
-  \begin{itemize}
-
-  \item
-    \(\operatorname{\sigma_{2, c, d} = -}\), the customer loses the case as the SP didn't receive the payment on time.
-  \item
-    \(\operatorname{\sigma_{2, s, d} = \neutral}\), the SP win the case for the same reason.
-  \end{itemize}
-\end{itemize}
-
-The SP has acted abnormally, then:
-
-\begin{itemize}
-\item
-  Following protocol:
-
-  \begin{itemize}
-
-  \item
-    \(\operatorname{\sigma_{2, c, \overline{n}} = \neutral}\), the customer remains in the neutral position as he is not obligated agree with the incorrect $\mathrm{PoD}$.
-  \item
-    \(\operatorname{\sigma_{2, s, \overline{n}} = \neutral}\), the SP is in a neutral position as she did not put any effort to provide the service, and the package has not brought any value to the SP.
-  \end{itemize}
-\item
-  Starting a dispute:
-
-  \begin{itemize}
-
-  \item
-    \(\operatorname{\sigma_{2, c, \overline{d}} = -}\), the customer loses the case as the SP is not obligated to publish correct $\mathrm{PoD}$.
-  \item
-    \(\operatorname{\sigma_{2, s, \overline{d}} = \neutral}\), the SP win the case for the same reason.
-  \end{itemize}
-\end{itemize}
-
-Fairness:
-
-\begin{itemize}
-
-\item The customer can do nothing and always ends up in a non-disadvantaged position.
-\item The SP can follow the protocol ends up in the non-disadvantaged position \(\operatorname{\sigma_{2, s, n} = \neutral}\).
-
-\end{itemize}
-
-\noindent \textbf
-{Step 3. customer turn: get proof of delivery}\label{step-3-get-proof-of-delivery}
-
-The customer has got the PoD, then:
-
-\begin{itemize}
-\item
-  Follows the protocol:
-
-  \begin{itemize}
-
-  \item
-    $\operatorname{\sigma_{3, c, n} = \neutral}$, the customer has the opportunity to pay for the transaction, but since he didn't put any effort, he is in the neutral position.
-  \item
-    $\operatorname{\sigma_{3, s, n} = \neutral}$, the SP position has not changed.
-  \end{itemize}
-\item
-  Starts a dispute:
-
-  \begin{itemize}
-
-  \item
-    $\operatorname{\sigma_{3, c, d} = -}$, the customer loses the case as the SP didn't receive the payment on time.
-  \item
-    $\operatorname{\sigma_{3, s, d} = \neutral}$, the SP win the case for the same reason.
-  \end{itemize}
-\end{itemize}
-
-The customer has acted abnormally, then:
-
-\begin{itemize}
-\item
-  Follows the protocol:
-
-  \begin{itemize}
-
-  \item
-    \(\operatorname{\sigma_{3, c, \overline{n}} = \neutral}\), the customer can not follow the protocol but since he didn't put any efford he is in the neutral position.
-  \item
-    \(\operatorname{\sigma_{3, s, \overline{n}} = \neutral}\), the SP position has not changed.
-  \end{itemize}
-\item
-  Starts a dispute:
-
-  \begin{itemize}
-
-  \item
-    \(\operatorname{\sigma_{3, c, \overline{d}} = -}\), the customer loses the case as the SP is not obligated to do anything before the payment is made.
-  \item
-    \(\operatorname{\sigma_{3, s, \overline{d}} = \neutral}\), the SP wins the case and ends up in the neutral position.
-  \end{itemize}
-\end{itemize}
-
-Fairness:
-
-\begin{itemize}
-
-\item The customer can follow the protocol to the non-disadvantaged position \(\operatorname{\sigma_{3, c, n} = \neutral}\).
-\item The SP can do nothing and always ends up in a non-disadvantaged position.
-\end{itemize}
-
-\noindent \textbf
-{Step 4. Customer turn: payment}
-
-The customer has paid the invoice:
-
-\begin{itemize}
-\item
-  Following protocol:
-  \begin{itemize}
-  \item
-    \(\operatorname{\sigma_{2, c, n} = -}\), the customer has spent his funds but has not received the result yet.
-  \item
-    \(\operatorname{\sigma_{2, s, n} = +}\), the SP has received the payment but has not spent his resources yet.
-  \end{itemize}
-\item
-  Starting a dispute:
-
-  \begin{itemize}
-  \item
-    \(\operatorname{\sigma_{2, c, d} = -}\), the customer loses the case as the SP has still an opportunity to publish proof of provision before the deadline.
-  \item
-    \(\operatorname{\sigma_{2, s, d} = \neutral}\), the SP win the case for the same reason.
-  \end{itemize}
-\end{itemize}
-
-The customer has acted abnormally, then:
-
-\begin{itemize}
-\item
-  Following protocol:
-  \begin{itemize}
-  \item
-    \(\operatorname{\sigma_{2, c, \overline{n}} = \neutral}\), the customer ends up in the neutral position as he did not spend his funds.
-  \item
-    \(\operatorname{\sigma_{2, s, \overline{n}} = \neutral}\), the SP ends up in a neutral position as he did not receive the payment, nor spent his resources.
-  \end{itemize}
-\item
-  Starting a dispute:
-
-  \begin{itemize}
-
-  \item
-    \(\operatorname{\sigma_{2, c, \overline{d}} = -}\), the customer loses the case as he can not prove the payment before the time limit.
-  \item
-    \(\operatorname{\sigma_{2, s, \overline{d}} = \neutral}\), the SP is not charged to justice due to a lack of proof.
-  \end{itemize}
-\end{itemize}
-
-Fairness:
-
-\begin{itemize}
-
-\item
-  The customer can move the protocol forward to step 3, where if the SP follows the protocol then the customer can push the protocol forward up to the last termination step \(\operatorname{\sigma_{7, c, n} = +}\), otherwise if at any step the SP does not follow the protocol the customer can start a dispute which terminates the protocol at the non-disadvantaged position, i.e., \(\operatorname{\sigma_{3, c, \overline{d}} = \neutral}\), \(\operatorname{\sigma_{4, c, \overline{d}} = \neutral}\), \(\operatorname{\sigma_{5, c, \overline{d}} = \neutral}\).
-\item
-  The SP can do nothing and end up in the non-disadvantaged position \(\operatorname{\sigma_{2, s, n} = +}\), \(\operatorname{\sigma_{2, s, d} = +}\), \(\operatorname{\sigma_{2, s, \overline{n}} = \neutral}\), \(\operatorname{\sigma_{2, s, \overline{d}} = \neutral}\).
-\end{itemize}
-
-\noindent \textbf
-{Step 5. SP turn: provision of service}
-
-The SP has made the provision of service:
-
-\begin{itemize}
-\item
-  Following protocol:
-
-  \begin{itemize}
-
-  \item
-    \(\operatorname{\sigma_{3, c, n} = -}\), the customer has not received the result, so he remains in the disadvantaged position. 
-  \item
-    \(\operatorname{\sigma_{3, s, n} = +}\), the SP has fulfilled the contract on time.
-  \end{itemize}
-\item
-  Starting a dispute:
-
-  \begin{itemize}
-
-  \item
-    \(\operatorname{\sigma_{3, c, d} = -}\), the customer loses the case as the SP has still the opportunity to publish proof of provision within the timeframe. 
-  \item
-    \(\operatorname{\sigma_{3, s, d} = \neutral}\), the SP win the case for the same reason.
-  \end{itemize}
-\end{itemize}
-
-The SP has acted abnormally, then:
-
-\begin{itemize}
-\item
-  Following protocol:
-
-  \begin{itemize}
-
-  \item
-    \(\operatorname{\sigma_{3, c, \overline{n}} = -}\), the customer ends up in a disadvantaged position.
-  \item
-    \(\operatorname{\sigma_{3, s, \overline{n}} = +}\), the SP ends up in the advantaged position as he received the payment. 
-  \end{itemize}
-\item
-  Starting a dispute:
-
-  \begin{itemize}
-
-  \item
-    \(\operatorname{\sigma_{3, c, \overline{d}} = \neutral}\), the customer wins the case and ends up in the neutral position.
-  \item
-    \(\operatorname{\sigma_{3, s, \overline{d}} = -}\), the SP loses the case and ends up in the disadvantaged position. 
-  \end{itemize}
-\end{itemize}
-
-Fairness:
-
-\begin{itemize}
-
-\item
-  The customer can do nothing if the SP follows the protocol, which will ultimately put him in the advantaged position \(\operatorname{\sigma_{7, c, n} = +}\), or in case of the SP not following the protocol, the customer can start a dispute and terminate in the non-disadvantaged position \(\operatorname{\sigma_{3, c, \overline{d}} = \neutral}\).
-\item
-  The SP can follow the protocol and move to the non-disadvantaged position \(\operatorname{\sigma_{3, s, n} = +}\), or not follow the protocol and also end up at the non-disadvantaged position \(\operatorname{\sigma_{3, s, \overline{n}} = +}\), but the second option puts him at risk of terminating the protocol at \(\operatorname{\sigma_{3, s, \overline{n}} = +}\), if the customer is rational and starts a dispute.
-\end{itemize}
-
-\noindent \textbf
-{Step 6. SP turn: upload result}\label{step-6-publication-of-results}
-
-The SP has uploaded the result on time:
-
-\begin{itemize}
-\item
-  Following protocol:
-
-  \begin{itemize}
-
-  \item
-    \(\operatorname{\sigma_{4, c, n} = -}\), the customer has not received the result, so he remains in the disadvantaged position. 
-  \item
-    \(\operatorname{\sigma_{4, s, n} = +}\), the SP has fulfilled the contract on time.
-  \end{itemize}
-\item
-  Starting a dispute:
-
-  \begin{itemize}
-
-  \item
-    \(\operatorname{\sigma_{4, c, d} = -}\), the customer loses the case as the SP has still an opportunity to publish proof of provision within the timeframe. 
-  \item
-    \(\operatorname{\sigma_{4, s, d} = \neutral}\), the SP win the case for the same reason.
-  \end{itemize}
-\end{itemize}
-
-The SP has acted abnormally, then:
-
-\begin{itemize}
-\item
-  Following protocol:
-
-  \begin{itemize}
-
-  \item
-    \(\operatorname{\sigma_{4, c, \overline{n}} = -}\), the customer ends up in the disadvantaged position. 
-  \item
-    \(\operatorname{\sigma_{4, s, \overline{n}} = +}\), the SP ends up in the advantaged position as he received the payment. 
-  \end{itemize}
-\item
-  Starting a dispute:
-
-  \begin{itemize}
-
-  \item
-    \(\operatorname{\sigma_{4, c, \overline{d}} = \neutral}\), the customer wins the case and ends up in a neutral position. 
-  \item
-    \(\operatorname{\sigma_{4, s, \overline{d}} = -}\), the SP loses the case and ends up in the disadvantaged position. 
-  \end{itemize}
-\end{itemize}
-
-Fairness:
-
-\begin{itemize}
-
-\item
-  The customer can do nothing if the SP follows the protocol, which will ultimately put him in an advantaged position \(\operatorname{\sigma_{7, c, n} = +}\), or in case of the SP not following the protocol, the customer can start a dispute and terminate in the non-disadvantaged position \(\operatorname{\sigma_{4, c, \overline{d}} = \neutral}\).
-\item
-  The SP can follow the protocol and move to the non-disadvantaged position \(\operatorname{\sigma_{4, s, n} = +}\), or not follow the protocol and also end up at the non-disadvantaged position \(\operatorname{\sigma_{4, s, \overline{n}} = +}\), but the second option puts him at risk of terminating the protocol at \(\operatorname{\sigma_{4, s, \overline{n}} = +}\), if the customer is rational and starts a dispute.
-\end{itemize}
-
-\noindent \textbf
-{Step 7. SP turn: proof of provision}\label{step-7-publication-of-proof-of-provision}
-
-The SP has published proof of provision on time:
-
-\begin{itemize}
-\item
-  Following protocol:
-
-  \begin{itemize}
-
-  \item
-    \(\operatorname{\sigma_{5, c, n} = -}\), the customer has not received the result. Therefore, he remains in the disadvantaged position. 
-  \item
-    \(\operatorname{\sigma_{5, s, n} = +}\), the SP has fulfilled the contract on time.
-  \end{itemize}
-\item
-  Starting a dispute:
-
-  \begin{itemize}
-
-  \item
-    \(\operatorname{\sigma_{5, c, d} = -}\), the customer loses the case as the SP can prove the publication of proof of provision. 
-  \item
-    \(\operatorname{\sigma_{5, s, d} = +}\), the SP win the case for the same reason.
-  \end{itemize}
-\end{itemize}
-
-The SP has acted abnormally, then:
-
-\begin{itemize}
-\item
-  Following protocol:
-
-  \begin{itemize}
-
-  \item
-    \(\operatorname{\sigma_{5, c, \overline{n}} = -}\), the customer ends up in the disadvantaged position.
-  \item
-    \(\operatorname{\sigma_{5, s, \overline{n}} = +}\), the SP ends up in the advantaged position as he received the payment.
-  \end{itemize}
-\item
-  Starting a dispute:
-
-  \begin{itemize}
-
-  \item
-    \(\operatorname{\sigma_{5, c, \overline{d}} = \neutral}\), the customer wins the case and ends up in the neutral position. 
-  \item
-    \(\operatorname{\sigma_{5, s, \overline{d}} = -}\), the SP loses the case and ends up in the disadvantaged position. 
-  \end{itemize}
-\end{itemize}
-
-Fairness:
-
-\begin{itemize}
-
-\item
-  The customer can do nothing if the SP follows the protocol because it will ultimately put him in the advantaged position \(\operatorname{\sigma_{7, c, n} = +}\); otherwise, in case of the SP not following the protocol, the customer can start a dispute and terminate in the non-disadvantaged position.
-  \(\operatorname{\sigma_{5, c, \overline{d}} = \neutral}\).
-\item
-  The SP can follow the protocol and move to the non-disadvantaged position \(\operatorname{\sigma_{5, s, n} = +}\), or not follow the protocol and also end up at the non-disadvantaged position \(\operatorname{\sigma_{5, s, \overline{n}} = +}\), but the second option puts him at risk of terminating the protocol at \(\operatorname{\sigma_{5, s, \overline{n}} = +}\), if the customer is rational and starts a dispute.
-\end{itemize}
-
-\noindent \textbf
-{Step 8. customer turn: pull proof of provision}\label{step-8-pull-proof-of-provision}
-
-The SP has uploaded the result on time, then:
-
-\begin{itemize}
-\item
-  Follows the protocol:
-
-  \begin{itemize}
-
-  \item
-    \(\operatorname{\sigma_{6, c, n} = -}\), the customer gets a hash of the result but not the result yet.
-  \item
-    \(\operatorname{\sigma_{6, s, n} = +}\), the SP position has not changed.
-  \end{itemize}
-\item
-  Starts a dispute:
-
-  \begin{itemize}
-
-  \item
-    \(\operatorname{\sigma_{6, c, d} = -}\), the customer loses the case as the SP can prove the publication of proof of provision. 
-  \item
-    \(\operatorname{\sigma_{6, s, d} = +}\), the SP win the case for the same reason.
-  \end{itemize}
-\end{itemize}
-
-The customer has acted abnormally, then:
-
-\begin{itemize}
-\item
-  Follows the protocol:
-
-  \begin{itemize}
-
-  \item
-    \(\operatorname{\sigma_{6, c, \overline{n}} = -}\), the customer ends up in the disadvantaged position.
-  \item
-    \(\operatorname{\sigma_{6, s, \overline{n}} = +}\), the SP ends up in the advantaged position as he received the payment but did not spend his resources.
-  \end{itemize}
-\item
-  Starts a dispute:
-
-  \begin{itemize}
-
-  \item
-    \(\operatorname{\sigma_{6, c, \overline{d}} = \neutral}\), the customer wins the case and ends up in the neutral position.
-  \item
-    \(\operatorname{\sigma_{6, s, \overline{d}} = -}\), the SP loses the case and ends up in the disadvantaged position.
-  \end{itemize}
-\end{itemize}
-
-Fairness:
-
-\begin{itemize}
-
-\item
-  The customer can follow the protocol to the position \(\operatorname{\sigma_{6, c, n} = -}\), which lets him move the protocol to the non-disadvantaged termination position \(\operatorname{\sigma_{7, c, n} = +}\), or in case the SP has not followed the protocol start a dispute and win the case \(\operatorname{\sigma_{6, c, \overline{d}} = \neutral}\).
-\item
-  The SP can do nothing and end up in a non-disadvantaged position \(\operatorname{\sigma_{6, s, n} = +}\), or \(\operatorname{\sigma_{6, s, \overline{n}} = +}\).
-\end{itemize}
-
-\noindent \textbf
-{Step 9. Customer turn: download result}\label{step-9-retrieval-of-results}
-
-The SP has published the correct result on time:
-
-\begin{itemize}
-\item
-  Following protocol:
-
-  \begin{itemize}
-
-  \item
-    \(\operatorname{\sigma_{7, c, n} = +}\), the customer gets the correct result. Therefore, he moves to the advantaged position. 
-  \item
-    \(\operatorname{\sigma_{7, s, n} = +}\), the SP position has not changed. 
-  \end{itemize}
-\item
-  Starting a dispute:
-
-  \begin{itemize}
-
-  \item
-    \(\operatorname{\sigma_{7, c, d} = -}\), the customer loses the case as the SP can prove the publication of proof of provision. 
-  \item
-    \(\operatorname{\sigma_{7, s, d} = +}\), the SP win the case for the same reason.
-  \end{itemize}
-\end{itemize}
-
-The customer has acted abnormally, then:
-
-\begin{itemize}
-\item
-  Following protocol:
-
-  \begin{itemize}
-
-  \item
-    \(\operatorname{\sigma_{7, c, \overline{n}} = -}\), the customer ends up in a disadvantaged position, as he ends up with the incorrect result.
-  \item
-    \(\operatorname{\sigma_{7, c, \overline{n}} = +}\), the SP ends up in the advantaged position as he received the payment but did not spend his resources.
-  \end{itemize}
-\item
-  Starting a dispute:
-
-  \begin{itemize}
-
-  \item
-    \(\operatorname{\sigma_{7, c, \overline{d}} = \neutral}\), the customer wins the case and ends up in the neutral position.
-  \item
-    \(\operatorname{\sigma_{7, c, \overline{d}} = -}\), the SP loses the case and ends up in the disadvantaged position.
-  \end{itemize}
-\end{itemize}
-
-Fairness:
-
-\begin{itemize}
-
-\item
-  The customer can follow the protocol to the non-disadvantaged termination position \(\operatorname{\sigma_{7, c, n} = +}\), or in case the SP has not followed the protocol start a dispute and win the case \(\operatorname{\sigma_{7, c, \overline{d}} = \neutral}\).
-\item
-  The SP can do nothing and ends up in the non-disadvantaged position \(\operatorname{\sigma_{7, s, n} = +}\).
-\end{itemize}
 
@@
 \end{document}
-
-\setcounter{page}{0}
-\newcommand{\floor}[1]{\left\lfloor #1 \right\rfloor}
-\newcommand{\ceil}[1]{\left\lceil #1 \right\rceil}

### 2023-01-20 paper/access.tex
update descriptions of abnormal steps

@@
 }
+
+\newcommand{\customer}{customer}
+\renewcommand{\sp}{SP}
+
+\newcommand{\normal}{n}
+\newcommand{\dispute}{d}
+\newcommand{\abnormal}{\overline{n}}
+\newcommand{\abdispute}{\overline{d}}
+
+\newcommand{\PoD}{$\mathrm{PoD}$}
+\newcommand{\PoP}{$\mathrm{PoP}$}
+\newcommand{\cid}{$\mathrm{cid}$}
 
@@
 
-\subsection{Assumptions}\label{assumptions}
+\subsection{Assumptions}\label{sec:assumptions}
 
@@
 
-\begin{itemize}
-
-\item
-    Both parties start from a neutral position (•).
-\item
-    After completing a transaction, both parties end up in advantaged positions (+). In other words, they have intrinsic motivation to initialize and complete the transaction.
-\item
-    The protocol steps are atomic—there are no intermediate steps.
-\item 
-    The protocol can go only forward—there is no way of reverting any action.
-\item
-    Repeating the first step starts a new transaction.
+\begin{enumerate}
+\item Both parties start from a neutral position $\neutral$.
+\item After completing a transaction, both parties end up in advantaged positions (\plus{}). In other words, they have intrinsic motivation to initialize and complete the transaction.
+\item The protocol steps are atomic—there are no intermediate steps.
+\item The protocol can go only forward—there is no way of reverting any action.
+\item Repeating the first step starts a new transaction.
 Repeating any other step is considered abnormal and gets ignored.
 For example, paying for the invoice twice does not cause any effect on the curse of the protocol.
-\item 
-    Once published, the result is available to the customer on the storage network. The idea of guaranteeing it cryptographically is discussed in section~\ref{sec:discussion}.
-
-\item
-    Winning the dispute leads to a neutral position (•).
-
-\item
-    Losing the dispute leads to a punishment greater than any reward, leading to a disadvantaged position (-). Hence, the rational customer will not start a dispute that he is unsure of winning.
-\item
-    Both the customer and the SP are rational (selfish).
-They always prefer to go from the worst position to a better position, but also risk a temporary worst position in favour of a later better position if and only if it is assured that they will not be stuck in the worst position.
-\end{itemize}
+\item Once published, the result is available to the customer on the storage network. The idea of guaranteeing it cryptographically is discussed in section~\ref{sec:discussion}.
+\item Winning the dispute leads to a neutral position ($\neutral$).
+\item Losing the dispute leads to a punishment greater than any reward, leading to a disadvantaged position (\minus{}).
+Hence, the rational customer will not start a dispute that he is unsure of winning.
+\item Both the customer and the SP are rational (selfish).
+They always prefer to go from the worst position (\minus{} or $\neutral${}) to a better position ($\neutral$ or \plus), but also risk a temporary worst position in favour of a later better position if and only if at any time they can get out of the worst position; in particular, at any time the customer can start a dispute and, if the SP has misbehaved, get out of disadvantaged position (\minus) to the neutral position ($\neutral$).
+\end{enumerate}
 
@@
 
-Using the fariness definition~\ref{def:fairness} and the assumptions stated in section~\ref{assumptions}, our analysis indicates that the protocol achieves fairness.
+Using the fariness definition~\ref{def:fairness} and the assumptions stated in Section~\ref{sec:assumptions}, our analysis indicates that the protocol achieves fairness.
 
@@
 
-\newcommand{\customer}{customer}
-\renewcommand{\sp}{SP}
 \newcommand{\AgreeablePath}{Agreeable path:}
-\newcommand{\DisputePath}{The customer starts a dispute:}
+\newcommand{\DisputePath}{The \customer{} starts a dispute:}
 \newcommand{\Fairness}{Fairness:}
-\newcommand{\CustomerTurn}[0]{\expandafter\MakeUppercase customer turn:}
+\newcommand{\CustomerTurn}[0]{\expandafter\MakeUppercase \customer{} turn:}
 \newcommand{\SPTurn}[0]{\sp{} turn:}
@@
 \newcommand{\CanFollowToOne}[2]{The #1 can follow the protocol to the non-disadvantaged position #2}
-\newcommand{\CanDoNothing}[1]{The #1 can do nothing and always end up in the non-disadvantaged position}
-\newcommand{\CanDoAnything}[1]{The #1 can do anything and always end up in the non-disadvantaged position}
+\newcommand{\CanDoNothing}[1]{The #1 can do nothing and always ends up in the non-disadvantaged position}
+\newcommand{\CanDoAnything}[1]{The #1 can do anything and always ends up in the non-disadvantaged position}
 \newcommand{\Pos}[4]{$\operatorname{\sigma_{#1, #2, #3} = #4}$}
 \newcommand{\WinForTheSameReason}[1]{The #1 wins the dispute for the same reason}
+\newcommand{\LoseForTheSameReason}[1]{The #1 loses the dispute for the same reason}
+\newcommand{\ActedAbnormallyThen}[1]{The #1 acted abnormally, then:}
+\newcommand{\CustomerPaidButDidntGetResult}{the customer ends up in a disadvantaged position as he paid in advance but didn't receive the result}
+\newcommand{\SpReceivedThePayment}{the SP ends up in the advantaged position as she received the payment}
 
@@
 \newcommand{\CustomerLosesBeforePoP}{The customer loses the dispute because the SP still can publish the PoP within the agreed timeframe}
-
-\newcommand{\normal}{n}
-\newcommand{\dispute}{d}
-\newcommand{\abnormal}{\overline{n}}
-\newcommand{\abdispute}{\overline{d}}
-
-\newcommand{\PoD}{$\mathrm{PoD}$}
-\newcommand{\PoP}{$\mathrm{PoP}$}
 
@@
 
-The SP acted abnormally, then:
+\ActedAbnormallyThen{\sp}
 
@@
   \item The customer can either wait (in case of the SP following the protocol), or abandon the transaction (in case of the SP acting abnormally).
-In both cases the customer ends up in non-disadvantaged position \Pos{2}{c}{\normal}{\neutral} or \Pos{2}{c}{\abnormal}{\neutral}
-\end{itemize}
-
-\subsubsection{Step 3. \CustomerTurn\ Get Proof of Delivery}\label{step-3-get-proof-of-delivery}
+In both cases the customer ends up in non-disadvantaged position \Pos{2}{c}{\normal}{\neutral} or \Pos{2}{c}{\abnormal}{\neutral}.
+\end{itemize}
+
+\subsubsection*{Step 3. \CustomerTurn{} Get Proof of Delivery}\label{step-3-get-proof-of-delivery}
 
@@
 
-The customer acted abnormally, then:
+\ActedAbnormallyThen{\customer}
+
 \begin{itemize}
@@
 \begin{itemize}
-  \item The customer can follow the protocol to the non-disadvantaged position \Pos{3}{c}{\normal}{\neutral}.
+  \item \CanFollowToOne{customer}{\Pos{3}{c}{\normal}{\neutral}}.
   \item \CanDoNothing{SP}.
@@
 
-\subsubsection{Step 4. \CustomerTurn{} Payment}
-
-The customer paid the transaction:
+\subsubsection*{Step 4. \CustomerTurn{} Payment}
+
+The customer paid the transaction, then:
 
@@
 
-The customer acted abnormally, then:
+\ActedAbnormallyThen{\customer}
 
@@
     \item \Pos{4}{c}{\abnormal}{\neutral}, the customer ends up in the neutral position as he did not spend his funds.
-    \item \Pos{4}{s}{\abnormal}{\neutral}, the SP ends up in a neutral position as he did not receive the payment, nor spent his resources.
+    \item \Pos{4}{s}{\abnormal}{\neutral}, the SP ends up in the neutral position as she neither received the payment nor spent her resources.
   \end{itemize}
@@
   \begin{itemize}
-    \item \(\operatorname{\sigma_{2, c, \overline{d}} = -}\), the customer loses the case as he can not prove the payment before the time limit.
-    \item \(\operatorname{\sigma_{2, s, \overline{d}} = \neutral}\), the SP is not charged to justice due to a lack of proof.
+    \item \Pos{4}{c}{\abdispute}{\minus}, \CustomerLosesBeforePayment{}.
+    \item \Pos{4}{s}{\abdispute}{\neutral}, \WinForTheSameReason{SP}.
   \end{itemize}
@@
 
-\begin{itemize}
-  \item The customer can move the protocol forward to step 3, where if the SP follows the protocol then the customer can push the protocol forward up to the last termination step \(\operatorname{\sigma_{7, c, n} = +}\), otherwise if at any step the SP does not follow the protocol the customer can start a dispute which terminates the protocol at the non-disadvantaged position, i.e., \(\operatorname{\sigma_{3, c, \overline{d}} = \neutral}\), \(\operatorname{\sigma_{4, c, \overline{d}} = \neutral}\), \(\operatorname{\sigma_{5, c, \overline{d}} = \neutral}\).
-  \item The SP can do nothing and end up in the non-disadvantaged position \(\operatorname{\sigma_{2, s, n} = +}\), \(\operatorname{\sigma_{2, s, d} = +}\), \(\operatorname{\sigma_{2, s, \overline{n}} = \neutral}\), \(\operatorname{\sigma_{2, s, \overline{d}} = \neutral}\).
-\end{itemize}
-
-\subsubsection{Step 5. SP turn: Provision of service}
-
-The SP has made the provision of service:
+\newcommand{\CustomerRiskTemporaryDisadvantagedPosition}[1]{The customer, following the 9th assumption described in Section~\ref{sec:assumptions}, risk the temporary disadvantaged position #1 in faviour of a later better position \Pos{9}{s}{\normal}{\plus}; meanwhile being able to get out of the disadvantaged position if the SP misbehave in one of the following steps.}
+
+\begin{itemize}
+  \item \CustomerRiskTemporaryDisadvantagedPosition{\Pos{4}{c}{\normal}{\minus}}.
+  \item \CanDoNothing{SP}.
+\end{itemize}
+
+\subsubsection*{Step 5. \SPTurn{} Provision of service}
+
+The \sp{} did the provision of service, then:
 
@@
   \begin{itemize}
-    \item \(\operatorname{\sigma_{3, c, n} = -}\), the customer has not received the result, so he remains in the disadvantaged position. 
-    \item \(\operatorname{\sigma_{3, s, n} = +}\), the SP has fulfilled the contract on time.
+    \item \Pos{5}{c}{\normal}{\minus}, \RemainsIn{\customer}{disadvantaged} as he did not receive the result.
+    \item \Pos{5}{s}{\normal}{\plus}, \RemainsIn{\sp}{advantaged} as she received the payment.
   \end{itemize}
@@
   \begin{itemize}
-    \item \(\operatorname{\sigma_{3, c, d} = -}\), the customer loses the case as the SP has still the opportunity to publish proof of provision within the timeframe. 
-    \item \(\operatorname{\sigma_{3, s, d} = \neutral}\), the SP win the case for the same reason.
-  \end{itemize}
-\end{itemize}
-
-The SP has acted abnormally, then:
+    \item \Pos{5}{c}{\dispute}{\minus}, \CustomerLosesBeforePoP{}.
+    \item \Pos{5}{s}{\dispute}{\neutral}, \WinForTheSameReason{SP}.
+  \end{itemize}
+\end{itemize}
+
+\ActedAbnormallyThen{\sp}
 
@@
   \begin{itemize}
-    \item \(\operatorname{\sigma_{3, c, \overline{n}} = -}\), the customer ends up in a disadvantaged position.
-    \item \(\operatorname{\sigma_{3, s, \overline{n}} = +}\), the SP ends up in the advantaged position as he received the payment. 
+    \item \Pos{5}{c}{\abnormal}{\minus}, \CustomerPaidButDidntGetResult{}. 
+    \item \Pos{5}{s}{\abnormal}{\plus}, \SpReceivedThePayment{}.
   \end{itemize}
@@
   \begin{itemize}
-    \item \(\operatorname{\sigma_{3, c, \overline{d}} = \neutral}\), the customer wins the case and ends up in the neutral position.
-    \item \(\operatorname{\sigma_{3, s, \overline{d}} = -}\), the SP loses the case and ends up in the disadvantaged position. 
+    \item \Pos{5}{c}{\abdispute}{\neutral} The customer wins the dispute because the SP did not provide the service within the time agreed upon in the \PoD{}, and so the SP will not be able to upload the result and publish the \PoP{} on time.
+    \item \Pos{5}{s}{\abdispute}{\minus}, \LoseForTheSameReason{SP}.
   \end{itemize}
@@
 \Fairness
-
-\begin{itemize}
-  \item The customer can do nothing if the SP follows the protocol, which will ultimately put him in the advantaged position \(\operatorname{\sigma_{7, c, n} = +}\), or in case of the SP not following the protocol, the customer can start a dispute and terminate in the non-disadvantaged position \(\operatorname{\sigma_{3, c, \overline{d}} = \neutral}\).
-  \item The SP can follow the protocol and move to the non-disadvantaged position \(\operatorname{\sigma_{3, s, n} = +}\), or not follow the protocol and also end up at the non-disadvantaged position \(\operatorname{\sigma_{3, s, \overline{n}} = +}\), but the second option puts him at risk of terminating the protocol at \(\operatorname{\sigma_{3, s, \overline{n}} = +}\), if the customer is rational and starts a dispute.
-\end{itemize}
-
-\subsubsection{Step 6. SP turn: Upload result}\label{step-6-publication-of-results}
-
-The SP has uploaded the result on time:
+\newcommand{\SPCanDoBothButFollowIsSafe}[1]{The SP can follow the protocol and move to the advantaged position \Pos{#1}{s}{\normal}{\plus}, or act abnormally (not provide the service) and also move to the advantaged position \Pos{#1}{s}{\abnormal}{\plus}; however, the second option puts her at risk of terminating the protocol at \Pos{#1}{s}{\abdispute}{\minus} if the customer is rational and starts a dispute; hence, the SP should choose the first option}
+
+\begin{itemize}
+  \item \CustomerRiskTemporaryDisadvantagedPosition{\Pos{5}{c}{\normal}{\minus}}.
+  \item \SPCanDoBothButFollowIsSafe{5}.
+\end{itemize}
+
+\subsubsection*{Step 6. \SPTurn{} Upload result}\label{step-6-publication-of-results}
+
+The SP uploaded the result on time, then:
 
@@
   \begin{itemize}
-
-  \item
-    \(\operatorname{\sigma_{4, c, n} = -}\), the customer has not received the result, so he remains in the disadvantaged position. 
-  \item
-    \(\operatorname{\sigma_{4, s, n} = +}\), the SP has fulfilled the contract on time.
+    \item \Pos{6}{c}{\normal}{\minus}, \RemainsIn{\customer}{disadvantaged} as he did not receive the result.
+    \item \Pos{6}{s}{\normal}{\plus}, \RemainsIn{SP}{advantaged} as she received the payment.
   \end{itemize}
 \item \DisputePath
-
-  \begin{itemize}
-
-  \item
-    \(\operatorname{\sigma_{4, c, d} = -}\), the customer loses the case as the SP has still an opportunity to publish proof of provision within the timeframe. 
-  \item
-    \(\operatorname{\sigma_{4, s, d} = \neutral}\), the SP win the case for the same reason.
-  \end{itemize}
-\end{itemize}
-
-The SP has acted abnormally, then:
+  \begin{itemize}
+    \item \Pos{6}{c}{\dispute}{\minus}, \CustomerLosesBeforePoP{}.
+    \item \Pos{6}{s}{\dispute}{\neutral}, \WinForTheSameReason{SP}.
+
+  \end{itemize}
+\end{itemize}
+
+\ActedAbnormallyThen{\sp}
 
@@
   \begin{itemize}
-    \item \(\operatorname{\sigma_{4, c, \overline{n}} = -}\), the customer ends up in the disadvantaged position. 
-    \item \(\operatorname{\sigma_{4, s, \overline{n}} = +}\), the SP ends up in the advantaged position as he received the payment. 
+    \item \Pos{6}{c}{\abnormal}{\minus}, \CustomerPaidButDidntGetResult{}.
+    \item \Pos{6}{s}{\abnormal}{\plus}, \SpReceivedThePayment{}.
   \end{itemize}
@@
   \begin{itemize}
-    \item \(\operatorname{\sigma_{4, c, \overline{d}} = \neutral}\), the customer wins the case and ends up in a neutral position. 
-    \item \(\operatorname{\sigma_{4, s, \overline{d}} = -}\), the SP loses the case and ends up in the disadvantaged position. 
+    \item \Pos{6}{c}{\abdispute}{\neutral}, the customer wins the dispute because the SP did not upload the service within the time agreed upon in the \PoD{}, and so the SP will not be able to publish the \PoP{} on time.
+    \item \Pos{6}{s}{\abdispute}{\minus}, \LoseForTheSameReason{SP}.
   \end{itemize}
@@
 \begin{itemize}
-  \item The customer can do nothing if the SP follows the protocol, which will ultimately put him in an advantaged position \(\operatorname{\sigma_{7, c, n} = +}\), or in case of the SP not following the protocol, the customer can start a dispute and terminate in the non-disadvantaged position \(\operatorname{\sigma_{4, c, \overline{d}} = \neutral}\).
-  \item The SP can follow the protocol and move to the non-disadvantaged position \(\operatorname{\sigma_{4, s, n} = +}\), or not follow the protocol and also end up at the non-disadvantaged position \(\operatorname{\sigma_{4, s, \overline{n}} = +}\), but the second option puts him at risk of terminating the protocol at \(\operatorname{\sigma_{4, s, \overline{n}} = +}\), if the customer is rational and starts a dispute.
-\end{itemize}
-
-\subsubsection{Step 7. SP turn: Proof of provision}\label{step-7-publication-of-proof-of-provision}
-
-The SP has published PoP on time:
+  \item \CustomerRiskTemporaryDisadvantagedPosition{\Pos{6}{c}{\normal}{\minus}}.
+  \item \SPCanDoBothButFollowIsSafe{6}.
+\end{itemize}
+
+\subsubsection*{Step 7. \SPTurn{} Proof of provision}\label{step-7-publication-of-proof-of-provision}
+
+The SP published \PoP{} on time, then:
+
+\newcommand{\CustomerLosesBecauseSPCanProveBeingCorrect}{the \customer{} loses the dispute as the \sp{} has published all evidences to prove her correct behaviour}
 
@@
     \begin{itemize}
-      \item \(\operatorname{\sigma_{5, c, n} = -}\), the customer has not received the result. Therefore, he remains in the disadvantaged position. 
-      \item \(\operatorname{\sigma_{5, s, n} = +}\), the SP has fulfilled the contract on time.
+      \item \Pos{7}{c}{\normal}{\minus}, the customer has not received the result. Therefore, he remains in the disadvantaged position. 
+      \item \Pos{7}{s}{\normal}{\plus}, the SP has published all evidences to prove her correct behaviour, therefore she remains in advantaged position fot the rest of the protocol.
     \end{itemize}
@@
     \begin{itemize}
-      \item \(\operatorname{\sigma_{5, c, d} = -}\), the customer loses the case as the SP can prove the publication of proof of provision. 
-      \item \(\operatorname{\sigma_{5, s, d} = +}\), the SP win the case for the same reason.
-    \end{itemize}
-\end{itemize}
-
-The SP has acted abnormally, then:
+      \item \Pos{7}{c}{\dispute}{\minus}, \CustomerLosesBecauseSPCanProveBeingCorrect{}.
+      \item \Pos{7}{s}{\dispute}{\plus}, \WinForTheSameReason{SP}.
+    \end{itemize}
+\end{itemize}
+
+\ActedAbnormallyThen{\sp}
 
@@
   \begin{itemize}
-    \item \(\operatorname{\sigma_{5, c, \overline{n}} = -}\), the customer ends up in the disadvantaged position.
-    \item \(\operatorname{\sigma_{5, s, \overline{n}} = +}\), the SP ends up in the advantaged position as he received the payment.
+    \item \Pos{7}{c}{\abnormal}{\minus}, \CustomerPaidButDidntGetResult{}.
+    \item \Pos{7}{s}{\abnormal}{\plus}, \SpReceivedThePayment{}.
   \end{itemize}
@@
   \begin{itemize}
-    \item \(\operatorname{\sigma_{5, c, \overline{d}} = \neutral}\), the customer wins the case and ends up in the neutral position. 
-    \item \(\operatorname{\sigma_{5, s, \overline{d}} = -}\), the SP loses the case and ends up in the disadvantaged position. 
-  \end{itemize}
-\end{itemize}
-
-Fairness:
-
-\begin{itemize}
-  \item The customer can do nothing if the SP follows the protocol because it will ultimately put him in the advantaged position \(\operatorname{\sigma_{7, c, n} = +}\); otherwise, in case of the SP not following the protocol, the customer can start a dispute and terminate in the non-disadvantaged position.
-\(\operatorname{\sigma_{5, c, \overline{d}} = \neutral}\).
-  \item The SP can follow the protocol and move to the non-disadvantaged position \(\operatorname{\sigma_{5, s, n} = +}\), or not follow the protocol and also end up at the non-disadvantaged position \(\operatorname{\sigma_{5, s, \overline{n}} = +}\), but the second option puts him at risk of terminating the protocol at \(\operatorname{\sigma_{5, s, \overline{n}} = +}\), if the customer is rational and starts a dispute.
-\end{itemize}
-
-\subsubsection{Step 8. customer turn: Get Proof of Provision}\label{step-8-pull-proof-of-provision}
-
-The SP has uploaded the result on time, then:
+    \item \Pos{7}{c}{\abdispute}{\neutral}, the customer wins the dispute because the SP did not publish the correct \PoP{} on time.
+    \item \Pos{7}{s}{\abdispute}{\minus}, \LoseForTheSameReason{SP}.
+  \end{itemize}
+\end{itemize}
+
+\Fairness
+
+\begin{itemize}
+  \item \CustomerRiskTemporaryDisadvantagedPosition{\Pos{7}{c}{\normal}{\minus}}.
+  \item \SPCanDoBothButFollowIsSafe{7}.
+\end{itemize}
+
+\subsubsection*{Step 8. \CustomerTurn{} Get Proof of Provision}\label{step-8-pull-proof-of-provision}
+
+The customer got the \PoP{}, then:
 
@@
   \begin{itemize}
-    \item \(\operatorname{\sigma_{6, c, n} = -}\), the customer gets a hash of the result but not the result yet.
-    \item \(\operatorname{\sigma_{6, s, n} = +}\), the SP position has not changed.
+    \item \Pos{8}{c}{\normal}{\minus}, the customer gets the \cid{}, but not the result yet.
+    \item \Pos{8}{s}{\normal}{\plus}, \RemainsIn{\sp}{advantaged}.
   \end{itemize}
@@
   \begin{itemize}
-    \item \(\operatorname{\sigma_{6, c, d} = -}\), the customer loses the case as the SP can prove the publication of proof of provision. 
-    \item \(\operatorname{\sigma_{6, s, d} = +}\), the SP win the case for the same reason.
-  \end{itemize}
-\end{itemize}
-
-The customer has acted abnormally, then:
+    \item \Pos{8}{c}{\dispute}{\minus}, \CustomerLosesBecauseSPCanProveBeingCorrect{}.
+    \item \Pos{8}{s}{\dispute}{\plus}, \WinForTheSameReason{SP}.
+  \end{itemize}
+\end{itemize}
+
+\ActedAbnormallyThen{\customer}
 
@@
   \begin{itemize}
-    \item \(\operatorname{\sigma_{6, c, \overline{n}} = -}\), the customer does not have the access to $cid$, and hence, can not get the result from the storage network.
-    \item \(\operatorname{\sigma_{6, s, \overline{n}} = +}\), the SP ends up in the advantaged position as he received the payment but did not spend his resources.
+    \item \Pos{8}{c}{\abnormal}{\minus}, the customer paid for the transaction but does not have the access to $cid$, and hence, can not get the result from the storage network.
+    \item \Pos{8}{s}{\abnormal}{\plus}, \SpReceivedThePayment{}.
   \end{itemize}
@@
   \begin{itemize}
-    \item \(\operatorname{\sigma_{6, c, \overline{d}} = \neutral}\), the customer wins the case and ends up in the neutral position.
-    \item \(\operatorname{\sigma_{6, s, \overline{d}} = -}\), the SP loses the case and ends up in the disadvantaged position.
+    \item \Pos{8}{c}{\abdispute}{\minus}, \CustomerLosesBecauseSPCanProveBeingCorrect{}
+    \item \Pos{8}{s}{\abdispute}{\neutral}, \WinForTheSameReason{SP}.
   \end{itemize}
@@
 \begin{itemize}
-  \item The customer can follow the protocol to the position \(\operatorname{\sigma_{6, c, n} = -}\), which lets him move the protocol to the non-disadvantaged termination position \(\operatorname{\sigma_{7, c, n} = +}\), or in case the SP has not followed the protocol start a dispute and win the case \(\operatorname{\sigma_{6, c, \overline{d}} = \neutral}\).
-  \item The SP can do nothing and end up in a non-disadvantaged position \(\operatorname{\sigma_{6, s, n} = +}\), or \(\operatorname{\sigma_{6, s, \overline{n}} = +}\).
-\end{itemize}
-
-\subsubsection{Step 9. Customer turn: Download resul}\label{step-9-retrieval-of-results}
-
-The SP has published the correct result on time:
+  \item \CustomerRiskTemporaryDisadvantagedPosition{\Pos{8}{c}{\normal}{\minus}}.
+  \item \CanDoNothing{} \Pos{8}{s}{\normal}{\plus} or \Pos{8}{s}{\abnormal}{\plus}.
+\end{itemize}
+
+\subsubsection*{Step 9. \CustomerTurn{} Download result}\label{step-9-retrieval-of-results}
+
+The customer downloaded the result, then:
 
@@
   \begin{itemize}
-    \item \(\operatorname{\sigma_{7, c, n} = +}\), the customer gets the correct result. Therefore, he moves to the advantaged position. 
-    \item \(\operatorname{\sigma_{7, s, n} = +}\), the SP position has not changed. 
+    \item \Pos{9}{c}{\normal}{\plus}, the customer got the result, therefore he terminate the protocol in advantaged position.
+    \item \Pos{9}{s}{\normal}{\plus}, \RemainsIn{\sp}{advantaged}.
   \end{itemize}
@@
   \begin{itemize}
-    \item \(\operatorname{\sigma_{7, c, d} = -}\), the customer loses the case as the SP can prove the publication of proof of provision. 
-    \item \(\operatorname{\sigma_{7, s, d} = +}\), the SP win the case for the same reason.
-  \end{itemize}
-\end{itemize}
-
-The customer has acted abnormally, then:
+    \item \Pos{9}{c}{\dispute}{\minus}, \CustomerLosesBecauseSPCanProveBeingCorrect{}.
+    \item \Pos{9}{s}{\dispute}{\plus}, \WinForTheSameReason{SP}.
+  \end{itemize}
+\end{itemize}
+
+\ActedAbnormallyThen{\customer}
 
@@
   \begin{itemize}
-    \item \(\operatorname{\sigma_{7, c, \overline{n}} = -}\), the customer ends up in a disadvantaged position, as he ends up with the incorrect result.
-    \item \(\operatorname{\sigma_{7, c, \overline{n}} = +}\), the SP ends up in the advantaged position as he received the payment but did not spend his resources.
+    \item \Pos{9}{c}{\abnormal}{\minus},the customer ends up in a disadvantaged position, as he ends up with the incorrect result.
+    \item \Pos{9}{s}{\abnormal}{\plus}, the SP ends up in the advantaged position as he received the payment but did not spend his resources.
   \end{itemize}
 \item \DisputePath
-
-  \begin{itemize}
-
-  \item
-    \(\operatorname{\sigma_{7, c, \overline{d}} = \neutral}\), the customer wins the case and ends up in the neutral position.
-  \item
-    \(\operatorname{\sigma_{7, c, \overline{d}} = -}\), the SP loses the case and ends up in the disadvantaged position.
-  \end{itemize}
-\end{itemize}
-
-Fairness:
-
-\begin{itemize}
-
-\item
-  The customer can follow the protocol to the non-disadvantaged termination position \(\operatorname{\sigma_{7, c, n} = +}\), or in case the SP has not followed the protocol start a dispute and win the case \(\operatorname{\sigma_{7, c, \overline{d}} = \neutral}\).
-\item
-  The SP can do nothing and ends up in the non-disadvantaged position \(\operatorname{\sigma_{7, s, n} = +}\).
+  \begin{itemize}
+    \item \Pos{9}{c}{\abdispute}{\neutral}, the customer wins the case and ends up in the neutral position.
+    \item \Pos{9}{s}{\abdispute}{\minus}, the SP loses the case and ends up in the disadvantaged position.
+  \end{itemize}
+\end{itemize}
+
+\Fairness
+
+\begin{itemize}
+  \item \CanFollowToOne{\customer}{\Pos{9}{c}{\normal}{\plus}}.
+  \item \CanDoNothing{} \Pos{9}{s}{\normal}{\plus} or \Pos{9}{s}{\abnormal}{\plus}. 
 \end{itemize}

### 2023-01-27 paper/access.tex
add results of filecoin

@@
 \end{figure}
-
-Ultimately, the rational path for both parties is to follow the protocol as shown in the figure~\ref{fig:rational}.
+the rational path for both parties is to follow the protocol as shown in the figure~\ref{fig:rational}.
 
@@
 
+\paragraph{Anonymity}
+We achieved anonymity by using anonymous payment methods such as cash or privacy-preserving payment blockchains (e.g.
+Monero), and decentralised storage networks like IPFS and Filecoin, allowing the customer to interact with the protocol without revealing his identity at any step of the protocol.
+
 \paragraph{Provable Results Availability}
@@
 The SP has no motivation to proceed with this kind of misbehaviour other than putting the customer in a disadvantaged position caused by the lost dispute.}.
-However, the Filecoin network, which works as an incentivisation layer on top of IPFS, increases the content availability via economic incentivisations (i.e., punishment in case of lack of proof of storage of the content)~\cite{protocollabsFilecoinDecentralizedStorage2017}.
+However, the Filecoin network, which works as an incentivisation layer on top of IPFS, increases the content availability via economic incentivisations (i.e., punishment in case of lack of proof of storage of the content\footnote{Filecoin, Slashing, \url{https://docs.filecoin.io/storage-provider/rewards/slashing}, (last visited Jan.
+03, 2023)})~\cite{protocollabsFilecoinDecentralizedStorage2017}.
 
@@
 
-\paragraph{Anonymity}
-We achieved anonymity by using anonymous payment methods such as cash or privacy-preserving payment blockchains (e.g.
-Monero), and decentralised storage networks like IPFS and Filecoin, allowing the customer to interact with the protocol without revealing his identity at any step of the protocol.
-
 \paragraph{Costs}
+Deploying smart contract and invoking functions on the Ethereum blockchain costs gas. The cost of gas is proportional to the amount of computation required to execute a transaction.
+
 Deploying smart contract consumed 1456577 gas.
@@
 Proof of provision consumed 149130 gas.
+
+Although our experiment was conducted on testnet, the amount of gas is the same on mainnet.
+
+The cost of gas is denominated in $\mathrm{ETH}$.
 The price of gas at the time of the experiment (Jan.
@@
 03, 2023)}, and the price of 1 $\mathrm{ETH}$ was $1261.97 \mathrm{USD}$.
-In result, the cost of 
+
+In result, the cost of:
 \begin{itemize}
@@
 \end{itemize}
+
+% Storing data in and retreiving data from Filecoin costs FIL cryptocurrency. Interacting with Filecoin is done via deals, which cost some FIL coins. 
+% Deals are made in a free market, where miners compete for the best price.
+
+% Selecting miners is not part of the Filecoin protocol. It is up to the customer to select the miners.
+
+% The list of all miners can be obtained by either quering Filecoin node or by visiting webpages like \url{https://filrep.io}.
+
+% Once we select a miner, we can use the \texttt{lotus} CLI to query it for the price of the deal.
+The price of the deal is determined by the miner and depends on the size of the payload, the duration of the deal, and the miner configuration.
+The price of the deal is denominated in FIL.
+% At the of the experiment (Jan.
+03, 2023) the price for one FIL coin was $5.28 \mathrm{USD}$\footnote{CoinMarketCap, Cryptocurrency Prices, \url{https://coinmarketcap.com/currencies/filecoin/}, (last visited Jan.
+03, 2023)}.
+% Because of the volatilaty of all the deal's parameters, the price is hard to predict.
+However, we can assume that the size of the result document is 1MiB, and the duration of the deal is 180 days (minimal duration), sector size is 256KiB,  and the miner price is .
+
+% Moreover, Filecoin allows publishing deals for free by using reputation based incentivisation layer\footnote{Filecoin, Filecoin Plus Overview, \url{https://docs.filecoin.io/store/filecoin-plus/overview/}, (last visited Jan.
+04, 2023)}.
+
+% Since the price is dynamic 
+% Each miner publishes the 
+% Deals are executed in a free market
 

### 2023-01-30 paper/constants.tex
split the tex into subtexs

\newcommand{\customer}{customer}
\renewcommand{\sp}{SP}

\newcommand{\normal}{n}
\newcommand{\dispute}{d}
\newcommand{\abnormal}{\overline{n}}
\newcommand{\abdispute}{\overline{d}}

\newcommand{\PoD}{$\mathrm{PoD}$}
\newcommand{\PoP}{$\mathrm{PoP}$}
\newcommand{\cid}{$\mathrm{cid}$}

\newcommand{\floor}[1]{\left\lfloor #1 \right\rfloor}
\newcommand{\ceil}[1]{\left\lceil #1 \right\rceil}

\newcommand{\plus}{+}
\newcommand{\minus}{-}
\newcommand\neutral[1][.75]{\mathbin{\ThisStyle{\vcenter{\hbox{%
  \scalebox{#1}{$\SavedStyle\bullet$}}}}}%
}

\newcommand\TITLE{Anonymous provision of privacy-sensitive services using distributed networks}
% \newcommand\TITLE{Privacy-preserving physical delivery service provisioning using distributed networks}
\newcommand\STANLONG{Stanis\l{}aw Bara{\'n}ski}
\newcommand\JULLONG{Julian Szyma{\'n}ski}
\newcommand\STAN{S. Bara{\'n}ski}
\newcommand\JUL{J. Szyma{\'n}ski}

\newcommand\ABSTRACT{%
Service providers like lawyers, laboratories, auditors, or banks, to provide services, require customers to submit data often associated with their personal information.
This information puts suppliers at risk of breaking GDPR, CPAA, or other privacy regulations, and puts customers at risk of privacy violations.

However, most service providers use personal information merely for logistic operations like payments and communication and could provide services anonymously if other means of logistics exist.
We propose an anonymous protocol for coordinating service provision using blockchain for both anonymous payments and proofs of existence and content-addressable network for results delivery.
% Less important
Service providers may use our protocol to provide services without collecting personal information. Enabling provision of services that were previously limited by a high level of trust.
% Even less important
Possible applications for this protocol include anonymous genetic tests, tests for paternity, venereal diseases, HIV, drugs, and steroids, or anonymous legal advice.

Compared to other works, our protocol achieves stronger anonimity by accepting payments in either cash or privacy-preserving blockchains. It supports physical materials, dispute resolution, and does not require customers to submit any transaction to the message board, indicating higher practicality.

We provide the fairness analysis and an implementation of the protocol using Ethereum as a message board, Monero as a privacy-preserving blockchain, and Powergate (IPFS and Filecoin) as a content-addressable network.
We discuss further extensions to an anonymous delivery system, self-sovereign identifiers, and a decentralized conflict resolution system.
%JS tu należałoby dodac kilka słów na temat rozwiazania i jak zostało ono zwalidowane czemu jest lepsze od innych
}

\newcommand\ACKNOWLEDGEMENTS{
The work has been supported partially by the founds of Department of Computer Architecture Faculty of Electronics, Telecommunications and Informatics, Gdańsk University of Technology.
}

\newcommand\LASTVISITED{(last visited Jan. 31, 2023)}

### 2023-01-30 paper/content.tex
split the tex into subtexs

--- 2023-01-27 paper/access.tex
@@
-\documentclass{ieeeaccess}
-
-\usepackage{cite}
-\usepackage{amsmath,amssymb,amsfonts}
-\usepackage{algorithmic}
-\usepackage{graphicx}
-\usepackage{textcomp}
-
-\usepackage{caption}
-\usepackage{url}
-\usepackage{listings}
-\usepackage{pdfpages}
-\usepackage[english]{babel}
-\usepackage{xcolor,colortbl}
-\newtheorem{theorem}{Theorem}
-\newtheorem{definition}{Definition}
-\usepackage{scalerel}
-
-\newcommand{\plus}{+}
-\newcommand{\minus}{-}
-\newcommand\neutral[1][.75]{\mathbin{\ThisStyle{\vcenter{\hbox{%
-  \scalebox{#1}{$\SavedStyle\bullet$}}}}}%
-}
-
-\newcommand{\customer}{customer}
-\renewcommand{\sp}{SP}
-
-\newcommand{\normal}{n}
-\newcommand{\dispute}{d}
-\newcommand{\abnormal}{\overline{n}}
-\newcommand{\abdispute}{\overline{d}}
-
-\newcommand{\PoD}{$\mathrm{PoD}$}
-\newcommand{\PoP}{$\mathrm{PoP}$}
-\newcommand{\cid}{$\mathrm{cid}$}
-
-\newcommand{\floor}[1]{\left\lfloor #1 \right\rfloor}
-\newcommand{\ceil}[1]{\left\lceil #1 \right\rceil}
-
-\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
-    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
-\begin{document}
-\history{Date of publication xxxx 00, 0000, date of current version xxxx 00, 0000.}
-\doi{10.1109/ACCESS.2022.0122113}
-
-\title{Privacy-preserving physical delivery service provisioning using distributed networks}
-\author{\uppercase{Stanis\l{}aw Bara{\'n}ski} \authorrefmark{1},
-\uppercase{Julian Szyma{\'n}ski\authorrefmark{1} } 
- }
-
-\address[1]{Department of Electronic, Telecommunication and Informatics, Gdansk University of Technology, Narutowicza 11/12 Gdansk Poland (e-mail: stanislaw.baranski@pg.edu.pl, julian.szymanski@eti.pg.edu.pl}
-
-\tfootnote{The work has been supported partially by the founds of Department of Computer Architecture Faculty of Electronics, Telecommunications and Informatics, Gdańsk University of Technology.}
-
-\markboth{S. Bara{\'n}ski, J. Szyma{\'n}ski : 
-Privacy-preserving physical delivery service provisioning using distributed networks}
-{S. Bara{\'n}ski, J. Szyma{\'n}ski : 
-Privacy-preserving physical delivery service provisioning using distributed networks}
-
-\corresp{Corresponding author: Stanislaw Baranski (e-mail: stanislaw.baranski@pg.edu.pl).}
-
-\begin{abstract}
-Service providers like lawyers, laboratories, auditors, or banks, to provide services, require customers to submit data often associated with their personal information, exposing their customers to privacy risks.
-However, most service providers use personal information merely for logistic operations like payments and communication and could provide services anonymously if other means of logistics exist.
-We propose a anonymous fair exchange protocol for coordinating service provision using blockchain for both anonymous payments and proofs of existence and content-addressable network for results delivery.
-% Less important
-A service provider can employ our protocol to provide services without collecting personal information, enabling services currently based on unacceptable trust assumptions. 
-% Even less important
-Possible applications for this protocol include anonymous tests for drugs, venereal diseases, paternity, and steroids, or anonymous legal advice.
-We provide the fairness analysis and well as the implementation of the protocol. We discuss further extensions to an anonymous delivery system, and a decentralized conflict resolution system.
-\end{abstract}
-
-\begin{keywords}
-Anonymity, blockchain, fair-exchange, physical delivery, privacy, services
-\end{keywords}
-
-\titlepgskip=-21pt
-
-\maketitle
-
 \section{Introduction}
@@
 Providing personal information exposes users to privacy risks, i.e. potential loss of control over personal information~\cite{smithInformationPrivacyResearch2011}.
-
-Such personal information can be used deliberately or unintentionally
-(e.g., by theft) for insider disclosure, unauthorized access, or commercial gains.
-For example, by reselling it to marketers, financial institutions, other businesses, government agencies, or even cybercriminals.
-Which in turn can lead to profiled advertisements or criminal activities like identity theft or illegal tracking and surveillance~\cite{smithInformationPrivacyResearch2011}.
-
-Important individuals like influencers, politicians, or celebrities are especially vulnerable to this kind of attack as exposure of their health records, purchase habits, or legal documents can threaten their reputation, position or be used for blackmailing.
-
-The privacy guarantee of the personal information is often based merely on trust assumptions and the security of the IT system.
-However, most SPs do not need personal information for any other reason than payment or communication, which should be considered secondary compared to actual service provision.
-
-It would be desirable for the user to keep its identity private while still receiving the service. This could lead to reduced trust that users have to put on SPs and less responsibility borne by SPs.
+%JS co może prowadzic do nieintencjonalnego naruszenia rodo  
+%SP dodałem na dole
+
+Such personal information can be used deliberately or accidently (e.g., by theft) 
+%JS kradzież to chyba inencjonalne
+%SB zmieniłem na accidentaly
+for insider disclosure, unauthorized access, or commercial gains. For example, by reselling it to marketers, financial institutions, other businesses, government agencies, or even cybercriminals. 
+In turn, it can lead to an unintentional violation of the GDPR or CCPA, profiled advertisements or even criminal activities like identity theft or illegal tracking and surveillance~\cite{smithInformationPrivacyResearch2011}.
+
+Public individuals like influencers, politicians, or celebrities are especially vulnerable to this kind of attack as exposure of their health records, purchase habits, or legal documents can threaten their reputation, position or be used for blackmailing.
+
+% SB START emphasise 
+The problem amplifies when personal information is linked to biological materials like DNA, saliva, or blood, or legal documents like contracts, or wills.
+
+In such situations, customers may be reluctant to provide their personal information to the SP and thus resign from the service.
+Both parties are harmed as the client does not receive a diagnosis relevant to their health and the SP loses potential clients.
+Both parties are affected as the client does not receive a diagnosis relevant to their health and the SP loses potential clients.
+% SB END emphasise
+
+The privacy guarantee of personal information is often based merely on trust assumptions and the security of the IT system.
+However, most SPs do not need the personal information for any other reason than payment or communication, which should be considered secondary compared to actual service provision.
+
+It would be desirable for the user to keep his or her identity private while still receiving the service.
+This could lead to reduced trust that users have to put in SPs and less responsibility borne by SPs.
 
@@
 \begin{itemize}
-    \item Patients willing to take a test for drugs, venereal diseases, paternity or steroids have a strong incentive to keep the whole procedure private.
+    \item Patients willing to take a test eg.: for drugs, venereal diseases, paternity or steroids have a strong incentive to keep the whole procedure private.
 Merely the fact that they took the test—without exposing the result—is suggestive enough to act as a premise in case of a conflict.
 
-Especially celebrities, politicians, and public figures are prone to this kind of problem as such precedent can negatively influence their future career.
-
-Currently, they have to risk that their personal details, materials, and results are stored securely and kept in private from any unauthorized actor (both curious employee and malicious attacker).
-
-Our protocol allows taking such tests anonymously, eliminating the strong trust assumption put on the laboratories and their IT
-systems.
+Especially %celebrities, politicians, and %js powtorka
+public figures are prone to this kind of problem as such precedent can negatively influence their future career.
+
+Currently, they have to risk that their personal details, materials, and results are stored securely and kept private from any unauthorized actor (both curious employees and malicious attackers).
+
+Our protocol allows taking such services anonymously, eliminating the strong trust assumption put on the service provider's (e.g., laboratory) IT system.
 \item People willing to take risky business activities may be willing to receive the risk estimation and prediction of possible personal repercussions of such action.
 
-By exposing our identity we trust that the lawer will not use that information for harmful actions.
+By exposing our identity we trust that the lawyer will not use that information for harmful actions.
 
@@
 \end{itemize}
+
+%SB GOAL
+In this work, we research the possibility of providing services without the collection of personal information.
 
@@
 
-% Therefore we propose
-We propose a protocol for anonymously provisioning services that require the delivery of physical materials.
-A service provider employing our protocol can provide services without collecting any personal information from customers.
-
-In case of dispute, either due to exceeding deadlines or providing an incorrect result, the customer can disclose the whole interaction and prove to justice the misbehaviour of the SP.
+Our review of the state of the art indicates that none of the current systems is sufficient to achieve the desired goal.
+Therefore, we propose a protocol for anonymously provisioning services that require the delivery of physical materials.
+In case of dispute, either due to exceeding deadlines or providing an incorrect result, the customer can disclose the whole interaction and prove to justice the misbehavior of the SP.
 
@@
     \item Blockchain (aka message board), to achieve fairness, i.e., as a means for proving that certain actions took place at a certain moment without the trusted third party (TTP).
-    \item Anonymous payment methods, like cash or privacy-preserving cryptocurrencies, allowing customers to pay for the services anonymously.
-    \item Content-addressable decentralised storage network (e.g., IPFS) to anonymously provide results to customers together with provable storage netwrok (e.g., Filecoin) to guarantee that the results are available to the customer even in case of the SP deny of service.
+    \item Anonymous payment methods, like cash or privacy-preserving cryptocurrencies, allow customers to pay for services anonymously.
+    \item Content-addressable decentralized storage network (e.g., IPFS) to anonymously provide results to customers together with a provable storage network (e.g., Filecoin) to guarantee that the results are available to the customer even in case of the SP denial of service.
     \item Cryptography
@@
 %\paragraph{Contributions}
-We contribute to the state of the art by:
-
+%We contribute to the state of the art by:
+The contribution of our paper is:
 \begin{itemize}
@@
   \item allows \textbf{anonymous} service provision, i.e., the service provider does not need to collect any personal information from the customer.
-  \item achieves \textbf{fairness} by carefully designing the protocol as an interactive non-cooperative game, in which the SP remains in advantageous position, and customer in disadvantageus with the option to start a dispute in case the SP misbehaviour.
+  \item achieves \textbf{fairness} by carefully designing the protocol as an interactive non-cooperative game, in which the SP remains in an advantageous position and the customer in a disadvantageous one with the option to start a dispute in case the SP misbehavior.
   \item \textbf{does not rely on centralized TTP}, but uses decentralized blockchain and distributed content-addressable storage network.
@@
 \item Systemise often misused definitions of anonymity, pseudonymity, linkability, and traceability.
-\item Proposing a framework for analysing fairness analysis in fair-exchange protocols.
-\item Discuss the possible improvements to the protocol witht the use of secure computation, self-sovereign identities, zero-knowledge proofs, and blockchain-based dispute resolution mechanisms.
+\item Proposing a framework for analyzing fairness analysis in fair-exchange protocols.
+\item Discuss the possible improvements to the protocol with the use of secure computation, self-sovereign identities, zero-knowledge proofs, and blockchain-based dispute resolution mechanisms.
 \end{itemize}
@@
 %\paragraph{Organisation}
-The remainder of this paper is organized as follows.
+The rest of this paper is organized as follows.
 In section~\ref{sec:related-works} we review related works. 
-Then, in section~\ref{sec:building-blocks} we discuss the building blocks of dispute resolution system, blockchain as a message board, fairness, payment for services, storage network, result availability, anonymity and confidentiality.
+Then, in section~\ref{sec:building-blocks} we discuss the building blocks of a dispute resolution system, blockchain as a message board, fairness, payment for services, storage network, result availability, anonymity, and confidentiality.
 Section~\ref{sec:protocol} describes how the protocol works in detail.
@@
 In Section~\ref{sec:experiments} we present the implementation of the protocol and results of our experiments.
-Section~\ref{sec:discussion} discuss possible improvements in terms of crowd sourced dispute resolution or dispute avoidance, self-sovereign identities (SSI), and anonymous delivery.
+Section~\ref{sec:discussion} discuss possible improvements in terms of crowd-sourced dispute resolution or dispute avoidance, self-sovereign identities (SSI), and anonymous delivery.
 Finally, section~\ref{sec:conclusion} concludes the paper.
@@
 \section{Related Works}\label{sec:related-works}
-In this section we review related works on fair exchange, anonymous, and physical delivery protocols. Then we outline the main differences between our protocol and the existing ones.
+In this section, we review related works on fair exchange, anonymous, and physical delivery protocols. Then we outline the main differences between our protocol and the existing ones.
+
+\subsection{Fair exchange, physical delivery}
+The most common application of fair exchange protocols is e-commerce.
+A typical transaction involves a seller and a buyer, who exchange money for a physical product such as a smartphone.
+To protect themselves, a seller would want to receive the funds prior to sending the product, while a buyer would want to receive the product prior to paying.
+The fairness of the protocol should guarantee that either both parties obtain the goods, or they both obtain nothing.
+
+Authors of~\cite{mohammedalarajFairnessPhysicalProducts2012} proposed an protocol for fair-exchage involving physical materials delivery.
+The protocol assumes the existence of offline~\footnote{\textit{Offline} (also called \textit{optimistic}) TTP compared to \textit{online} TTP is in improvement which assumes the TTP being involved only in the case of a dispute between parties~\cite{rayFairExchangeEcommerce2002}.} TTP that is involved only in the case of a dispute.
+The protocol works as follows:
+\begin{enumerate}
+\item The buyer sends an encrypted payment to the seller along with the proof of validity.
+\item The seller validates the proof which convinces him that the decrypted payment will also be valid.
+\item The seller forwards the physical product to the delivery agent.
+\item The buyer verifies whether the product is the one he ordered.
+\item The buyer creates a proof of delivery and sends it along with the decryption key to the seller.
+\end{enumerate}
+
+However, the protocol relies on strong assumptions, namely, the existence of a trusted third party (TTP) and trusted delivery agent which does not misbehave or collude with any party.
+
+\begin{itemize}
+    \item there exists a trusted third party (TTP) and trusted delivery agent which does not misbehave or collude with any party;
+\end{itemize}
 
@@
 
-The most common application of anonymous fair exchange protocols is e-commerce.
-The problem is that the customer wants to buy a product from a merchant, but does not want to reveal his identity to the merchant.
+In the previous protocol, the identities of both parties are known.
+There are however situations where the customer does not want to reveal his identity to the merchant.
 The problem gets even more challenging when physical products are involved.
 
-Authors of~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} proposed a protocol for fair exchange of physical products and electronic payments, which guarantee both customer and merchant anonymity.
+Authors of~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} proposed a protocol for the fair exchange of physical products and electronic payments, which guarantees both customer and merchant anonymity.
 They achieve it by introducing online TTPs that validate coins and provide fair exchange guarantees.
 
-The anonymity is ensured by assuming the existence of a source cabinet (SC), delivery cabinet (DC), and a trusted delivery agent who take a product from a SC and provide it to a DC.
+The anonymity is ensured by assuming the existence of a source cabinet (SC), delivery cabinet (DC), and a trusted delivery agent who take a product from an SC and provide it to a DC.
 Both cabinets provide access to the product by passwords to conceal
@@
         \setcounter{enumii}{7}
-        \item the customer sends the acknowledge to the DC and decryption key to the merchant.
-        \item The merchant redeem the coins from the bank.
+        \item the customer sends the acknowledgment to the DC and decryption key to the merchant.
+        \item The merchant redeems the coins from the bank.
         \end{enumerate}
@@
 
-However, the protocol relies on strong assumptions, namely:
-
-\begin{itemize}
-    \item there exists trusted third party (TTP) and trusted delivery agent which do not misbehave or collude with any party;
+Besides the assumptions of the existence of TTP and trusted delivery agent (similar to the previous protocol~\cite{mohammedalarajFairnessPhysicalProducts2012}), the protocol also assumes:
+
+\begin{itemize}
     \item there exists an anonymous communication channel 
-    \item the customer's and merchant's banks enable confidential transactions, and both share commit-buffer where the value is locked until the transaction is finished;
+    \item the customer's and merchant's banks enable confidential transactions, and both share a commit buffer where the value is locked until the transaction is finished;
     \item all banks maintain a global list of coins' serial numbers to prevent double-spending problems;
@@
 
-The issue of TTPs in fair exchange protocols has been solved by the usage of decentralised networks, especially blockchain technology.
+The issue of TTPs in fair exchange protocols has been solved by the usage of decentralized networks, especially blockchain technology.
 
 The simplest example of blockchain-based fair exchange protocol is certified electronic mail protocol in which neither the sender can deny sending the mail, nor the receiver can deny receiving it.
-As the service is widely used in the paper world, achieving it for e-mails has not yet met the agreement across the scientific community.
-The main problem was the dependency of TTP, which significantly reduced the performance, security, and robustness of such protocols.
+As the service is widely used in the paper world, achieving it for e-mails has not yet met agreement across the scientific community.
+The main problem was the dependency on TTP, which significantly reduced the performance, security, and robustness of such protocols.
 The protocols that do not use TTP struggle with high computation and communication overhead~\cite{hinarejosSolutionSecureCertified2019}.
@@
 
-The idea behind certified e-mails and any other fair exchange protocols is following:
+The idea behind certified e-mails and any other fair exchange protocols is the following:
 \begin{enumerate}
-    \item The sender sends encrypted and signed message to the receiver.
+    \item The sender sends an encrypted and signed message to the receiver.
     \item The receiver returns a proof of delivery (a signature) of the encrypted message to the sender.
@@
 
-Next, both Alice and Bob, take their key shares, and encrypt each
+Next, both Alice and Bob, take their key shares and encrypt each
 \textit{i}-th key share using public key of \textit{i}-th mediator. As a result
@@
 
-In case of dispute, the decentralized network of mediators settle the conflict and grand one winning party, the other party secret key,
+In case of dispute, the decentralized network of mediators settles the conflict and grand one winning party, the other party secret key,
 letting him withdraw the funds.
@@
 
-Onchain smart-contract is used to coordinate the whole process and
+A smart-contract is used to coordinate the whole process and
 mediate communication between customers and delivery providers.
@@
 
-Bîrjoveanu, 2015~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} is the closest to our protocol, however it uses TTP and does not consider dispute between parties.
+Bîrjoveanu, 2015~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} is the closest to our protocol, however, it uses TTP and does not consider disputes between parties.
 
 Hinarejos et al., 2019~\cite{hinarejosSolutionSecureCertified2019} is the simplest protocol that replaces TTP with blockchain.
-However, it does not consider anonymity, dispute between parties nor physical material exchange.
-
-Meng et al., 2019~\cite{mengThemisDecentralizedEscrow2019} improves the previous protocol by the crownsource dispute resolution system. However it does not take anonimity into consideration.
-
-Altawy et al., 2017~\cite{altawyLelantosBlockchainBasedAnonymous2017} is a blockchain-based protocol that does not provide dispute resolution, but provides anonymous physical delivery by using onion routing and anonymous blockchain interaction assuming unlinkability between pseudonyms and real identities.
+However, it does not consider anonymity, disputes between parties nor physical material exchange.
+
+Meng et al., 2019~\cite{mengThemisDecentralizedEscrow2019} improves the previous protocol by the crowdsourced dispute resolution system. However, it does not take anonymity into consideration.
+
+Altawy et al., 2017~\cite{altawyLelantosBlockchainBasedAnonymous2017} is a blockchain-based protocol that does not provide dispute resolution but provides anonymous physical delivery by using onion routing and anonymous blockchain interaction assuming unlinkability between pseudonyms and real identities.
+
+The authors proposed many extensions to the protocol, namely, in ~\cite{birjoveanuPreservingAnonymityFair2018} they proposed a anonymous e-commerce protocol that govers complex transactions, in ~\cite{birjoveanuAnonymityComplexTransactions2019} they extend the anonimity for both customers and SPs, and in ~\cite{birjoveanuFairExchangeECommerce2020} they propose a protocol that supports chained transactions (involving multiple active intermediares).
+However none of them is relevant to our use case.
+
+We want the SP to remain public so that the anonymous customer can easily start a dispute.
+We assume just one package of physical materials.
+Moreover, the package is delivered from the customer to the SP, not the other way around — as it's the case for most e-commerce transactions.
 
 Our protocol achieves stronger anonymity guarantees.
-Namely, we achieve anonimity by using either cash or privacy-preserving blockchains.
-Moreover, our protocol does not require a customer to submit any transaction to the message board, which may be the weakest link in the anonymity of aforementioned protocols.
-
-Our protocol does not use its own delivery system. We assume that there is a way to anonymously deliver a package either via SP's drop box, or trusted party.
-
-Also, our protocol does not provide its own dispute resolution mechanism as Themis does.
+Namely, we achieve anonymity by using either cash or privacy-preserving blockchains.
+Moreover, our protocol does not require a customer to submit any transaction to the message board, which may be the weakest link in the anonymity of the aforementioned protocols.
+
+Our protocol does not use its own delivery system.
+We assume that there is a way to anonymously deliver a package either via SP's drop box, a customer's trusted party.
+The improvement of the protocol to support anonymous physical delivery via courier is discussed in Section~\ref{sec:anonymous-delivery}.
+
+Also, our protocol does not provide its own dispute-resolution mechanism as Themis does.
 However, we assume the existence of an abstract justice that accepts evidence and punishes the misbehaving party.
-It can be instantiated with either local court or police, or one of the blockchain
+%JS to warto podkreslic w dyskusji
+It can be instantiated with either the local court or police, or one of the blockchain
 dispute resolution services like Themis~\cite{mengThemisDecentralizedEscrow2019}, Kleros~\cite{bergollaKlerosSociolegalCase2022,gudkovCrowdArbitrationBlockchain2020}, Aragon Court\footnote{Aragon Court, Decentralized Dispute Resolution Protocol, https://aragon.org/aragon-court, (last visited Jan.
-10, 2023)}, LTO Network\footnote{LTO Network, 2019, https://lto.network/, (last visited Jan.
+10, 2023)}, LTO Network\footnote{LTO Network, a hybrid blockchain application development platform for securing, verifying, and exchanging enterprise information, https://lto.network/, (last visited Jan.
 17, 2023)}, and other Online Dispute Resolution platforms~\cite{allenGovernanceBlockchainDispute2019}.
 
-The comparision of the protocols is presented in table~\ref{tab:comparision}.
+The comparison of the protocols is presented in table~\ref{tab:comparision}.
 
@@
 \newcommand{\BC}{\cellcolor{green!50}BC}
-  \caption{Related work comparision}
+\caption{Comparision of related works}
 \label{tab:comparision}
 \setlength{\tabcolsep}{3pt}
+
+\ifx\JOURNAL\JOURNALIEEE
 \begin{tabular}{|p{40pt}|p{35pt}|p{40pt}|p{35pt}|p{30pt}|p{30pt}|}
+\else
+\begin{tabular}{|c|c|c|c|c|c|}
+\fi
 \hline
 Protocol & Fair exchange & Anonymity & Dispute resolution & Trust & Physical delivery \\
+\hline
+Alaraj, 2012~\cite{mohammedalarajFairnessPhysicalProducts2012} & \YES & \NO & \YES & \TTP & \YES \\
 \hline
@@
 The smart contract code encompasses the contract's specifications, hence the slogan \textit{code as a law}.
-Moreover, smart contracts are automatically executed merging together the gap of law and its enforcment by police~\cite{allenGovernanceBlockchainDispute2019}.
+Moreover, smart contracts are automatically executed merging together the gap between law and its enforcement by police~\cite{allenGovernanceBlockchainDispute2019}.
 However, the blockchain paradigm has its limitations.
@@
 Blockchain can assure the correctness of data existing only on the blockchain.
-The problem arises in the contact between blockchain and the real world, when we want the smart contract to decide based on some input from outside the blockchain.
-The technique of providing real-world data to the blockchain is called oracle.
+The problem arises in the contact between the blockchain and the real world when we want the smart contract to decide based on some input from outside the blockchain.
+The technique of providing real-world data to the blockchain is called an oracle.
 Oracle provides data based on a decentralized network of mediators; therefore, the trust is also decentralized~\cite{breidenbachChainlinkNextSteps2021}.
@@
 Some oracles provide the data like weather, soccer match result, stock
-price, train delay, election results, others—and they are the ones we
-are interested in—provide the settlement of a submitted dispute.
+price, train delay, election results, and others—and they are the ones we
+are interested in—providing the settlement of a submitted dispute.
 
@@
 Kleros~\cite{bergollaKlerosSociolegalCase2022} is a smart contract deployed on the Ethereum platform that mimics in a decentralized and autonomous way how the court works in real life.
-In Kleros, every process of a dispute like gathering evidence, selecting jurors, rewarding the winning party is automated by a set of smart contracts.
+In Kleros, every process of a dispute like gathering evidence, selecting jurors, and rewarding the winning party is automated by a set of smart contracts.
 Like Themis, the honesty of the agents voting in a case is achieved by game-theoretical economic incentives.
@@
 Such a decentralized, voluntary, and anonymous dispute resolution system might work for simple contracts violations like an eBay seller sending broken or wrong products or an Airbnb apartment being inadequate to the photos in the offer.
-However, it is hard to realize such decentralized evaluation of heath or legal services quality when expertise and privacy concerns are taken into account.
+However, it is hard to realize such a decentralized evaluation of health or legal services quality when expertise and privacy concerns are taken into account.
 Therefore, in our protocol, we take the more conservative approach and resolve disputes using local
@@
 
-In case of dispute, the customer can prove to justice (police or court) convincing evidence for the honesty of the customer and misbehaviour of the SP. 
+In case of dispute, the customer can prove to justice (police or court) convincing evidence for the honesty of the customer and the misbehavior of the SP. 
 Because the customer is anonymous, the SP can not start a dispute---there is no means to identify the customer.
@@
 To mitigate the issue, we designed the protocol so that the SP who follows the protocol is always in an advantaged position; therefore, she has no reason to start a dispute.
-On the other hand, the customer can start a dispute at any time of the protocol, but only the actual misbehaviour of the SP makes him win the case.
-
-Abstracting from the services the SP is providing, each party should be able to prove its honest behaviour in case of a dispute.
+On the other hand, the customer can start a dispute at any time of the protocol, but only the actual misbehavior of the SP makes him win the case.
+
+Abstracting from the services the SP is providing, each party should be able to prove its honest behavior in case of a dispute.
 We introduce three proofs that should be disclosed to justice in case of a dispute:
@@
     \item Proof of delivery ($\mathrm{PoD}$) is a confirmation issued by the SP to the customer that proves that the customer has delivered to the SP a complete (according to the SP requirements) package, and the SP accepted it.
-It consists of the current time, the deadline to pay for the transaction, the deadline to provide a result of the service, randomly generated number uniquely identifying the transaction, and the SP's signature guaranteeing non-repudiation.
+It consists of the current time, the deadline to pay for the transaction, the deadline to provide a result of the service, the randomly generated number uniquely identifying the transaction, and the SP's signature guaranteeing non-repudiation.
 The formal definition of the $\mathrm{PoD}$ is presented in section ~\ref{proof-of-delivery}.
@@
 It consists of a content identifier as specified in section ~\ref{storage-network}, the $\mathrm{nonce}$ uniquely identifying the transaction previously generated in $\mathrm{PoD}$, and the SP's signature guaranteeing authentication.
-The connection between $\mathrm{PoP}$ and the result is created by the content identifier ($\mathrm{cid}$) that uniquely identify the result (it is some kind of a hash of the result) such that the result can not be forged after the $\mathrm{PoP}$ has been published.
+The connection between $\mathrm{PoP}$ and the result is created by the content identifier ($\mathrm{cid}$) that uniquely identifies the result (it is some kind of a hash of the result) such that the result can not be forged after the $\mathrm{PoP}$ has been published.
 \end{enumerate}
@@
 \subsection{Message Board}\label{sec:message-board}
-The proof of provision that we coined for the purpose of this protocol is generally called the proof of existence~\cite{ProofExistenceOnline, crespoStamperyBlockchainTimestamping2017, ChainpointBlockchainProof}.
+The proof of provision that we coined for the purpose of this protocol is generally called the proof of existence~\cite{crespoStamperyBlockchainTimestamping2017}.
 
@@
 
-We need this functionality for two reasons: (1) communicate the existence of the result to the customer to whom the SP have no other communication medium as the customer stays anonymous; (2) let the SP to proof the publication of the result within the agreed with customer deadline.
+We need this functionality for two reasons: (1) communicate the existence of the result to the customer to whom the SP has no other communication medium as the customer stays anonymous; (2) let the SP proof the publication of the result within the agreed with customer deadline.
 
@@
 
-Depending on the context the platform of achieving it is called bulletin board~\cite{achenbachImprovedCoercionresistantElectronic2015}, trusted timestamping~\cite{gippDecentralizedTrustedTimestamping2015}, or message board~\cite{hinarejosSolutionSecureCertified2019}.
+Depending on the context the platform for achieving it is called bulletin board~\cite{achenbachImprovedCoercionresistantElectronic2015}, trusted timestamping~\cite{gippDecentralizedTrustedTimestamping2015}, or message board~\cite{hinarejosSolutionSecureCertified2019}.
 In this work, we call it a message board.
@@
 The multidisciplinary nature leads to ambiguous definitions~\cite{smithInformationPrivacyResearch2011}.
-For our work, we rely on more concrete definitions, i.e.~confidentality and anonymity.
-
-Confidentiality is the ability to hide the details of an action from others.
+For our work, we rely on more concrete definitions, i.e.~confidentality, and anonymity.
+
+Confidentiality is the ability to hide the details of action from others.
 Alternatively, we can say that the system guarantees confidentiality if, for all observers, everything they can say about the action is the fact that it happened and nothing more.
@@
 Some systems guarantee pseudonymity rather than anonymity.
-Pseudonymity allows users to hide their real identity behind the pseudonyms.
+Pseudonymity allows users to hide their real identity behind pseudonyms.
 Despite the whole system being transparent and allowing linking actions to pseudonyms, the system is considered anonymous as long as the link between pseudonyms and real identities is secret.
-This assumption is hard to satisfy in practice, as the KYC (Know Your Customer) and AML (Anti Money Laundering) regulations require users to reveal their real identity to cryptocurrencies exchanges, making the user's anonymity dependent on the security of the IT system.
+This assumption is hard to satisfy in practice, as the KYC (Know Your Customer) and AML (Anti Money Laundering) regulations require users to reveal their real identity to cryptocurrency exchanges, making the user's anonymity dependent on the security of the IT system.
 Moreover, some correlations can be inferred merely by the analysis of transactions \cite{androulakiEvaluatingUserPrivacy2013, oberStructureAnonymityBitcoin2013}.
 
-The figure ~\ref{fig:anonymity-diagram} ilustrate relations between these terms.
+Figure ~\ref{fig:anonymity-diagram} illustrates relations between these terms.
 
@@
 \caption{Let us assume Alice to be the customer willing to keep her identity anonymous and Bob to be the public SP.
-Alice controls two addresses, 1 and 2; the connection between her real identity and the first address has been compromised, and therefore the identification is possible; the connection between the second pseudonym is still unknown therefore anonymous.
+Alice controls two addresses, 1 and 2; the connection between her real identity and the first address has been compromised, and therefore the identification is possible; the connection between the second pseudonym is still unknown and therefore anonymous.
 Alice takes two actions; the first one from the compromised address and the second one from the anonymous one.
 The first action is confidential; therefore, even though the pseudonym has been compromised, the action can not be associated with Alice.
-The second action is transparent; therefore, Alice maintain her anonymity as long as the connection to the second pseudonym is concealed.}
+The second action is transparent; therefore, Alice maintains her anonymity as long as the connection to the second pseudonym is concealed.}
 
@@
 
-Examples of blockchains that natively support confidential transactions are: Monero~\cite{vansaberhagenCryptoNote2013} (via Ring Signatures~\cite{noetherRingSignatureConfidential2015} and Bulletproofs~\cite{moneroBulletproofsMoneropediaMonero, bunzBulletproofsShortProofs2018}), ZCash~\cite{ben-sassonZerocashDecentralizedAnonymous2014} (via zkSNARK~\cite{ben-sassonSNARKsVerifyingProgram2013}), and Grin~\cite{fuchsbauerAggregateCashSystems2019} (via Mimblewimble~\cite{jedusorMIMBLEWIMBLE2016}).
+Examples of blockchains that natively support confidential transactions are: Monero~\cite{vansaberhagenCryptoNote2013} (via Ring Signatures~\cite{noetherRingSignatureConfidential2015} and Bulletproofs~\cite{bunzBulletproofsShortProofs2018}), ZCash~\cite{ben-sassonZerocashDecentralizedAnonymous2014} (via zkSNARK~\cite{ben-sassonSNARKsVerifyingProgram2013}), and Grin~\cite{fuchsbauerAggregateCashSystems2019} (via Mimblewimble~\cite{jedusorMIMBLEWIMBLE2016}).
 
@@
 
-Depending on a cryptocurrency, the link can be created in different
+Depending on the cryptocurrency, the link can be created in different
 ways:
@@
 \item separate address: each transaction derives a new address uniquely associated with the transaction.
-Such addresses can be derived using Hierarchical Deterministic Wallets (BIP-32)\footnote{Bitcoin Improvement Proposals,Hierarchical Deterministic Wallets, \url{https://github.com/bitcoin/bips/blob/master/bip-0032.mediawiki}, (last visited Dec.
+Such addresses can be derived using Hierarchical Deterministic Wallets (BIP-32)\footnote{Bitcoin Improvement Proposals, Hierarchical Deterministic Wallets, \url{https://github.com/bitcoin/bips/blob/master/bip-0032.mediawiki}, (last visited Dec.
 03, 2022)}.
 \item memo: the payments are sent to one SP account but contain an extra field named ``memo'' filled with the unique number provided by the SP in $\mathrm{PoD}$.
-Each payment containing such value in the memo is considered to pay for the transaction.
+Each payment containing the such value in the memo is considered to pay for the transaction.
 In case of a dispute, revealing both the payment memo and the $\mathrm{PoD}$ proves the connection.
@@
 
-In case of a dispute, there must be a way to prove to the justice that the customer has paid for the transaction.
+In case of a dispute, there must be a way to prove to justice that the customer has paid for the transaction.
 As the proof of transaction is trivial in transparent and trackable blockchains, it gets more complicated when it comes to anonymous blockchains.
-Monero allows proving and checking payments via dedicated API \cite{MoneroHowProve}.
+Monero allows proving and checking payments via dedicated API\footnote{Monero, How to prove payment, \url{https://www.getmonero.org//resources/user-guides/prove-payment.html}, \LASTVISITED}.
 ZCash provides a mechanism called Payment Disclosure \cite{daviesIntroductionPaymentDisclosure2017}.
@@
 
-While most blockchains could provide the message board functionality, anonymous payments are not as prevalent.
-Especially a provable storage network is a functionality of a few specialized blockchains.
+While most blockchains could provide message board functionality, anonymous payments are not as prevalent. Especially a provable storage network is a functionality of a few specialized blockchains.
 
@@
 
-At the time of writing, we see the following technologies that fulfil the requirements of each role:
+At the time of writing, we see the following technologies that fulfill the requirements of each role:
 
@@
   Tornado Cash \cite{pertsevTornadoCashPrivacy2019}.
-\item Message board: Stampery \cite{crespoStamperyBlockchainTimestamping2017}, Proof of Existence
-  \cite{ProofExistenceOnline} (Bitcoin blockchain), Chainpoint
-  \cite{ChainpointBlockchainProof} (Bitcoin blockchain), or any other blockchain that
-  supports attaching extra data along the transaction.
+\item Message board: Open timestamps\footnote{Open timestamps, A timestamping proof standard, \url{https://opentimestamps.org}, \LASTVISITED}, Stampery \cite{crespoStamperyBlockchainTimestamping2017}, Bitcoin blockchain (Proof of Existence~\footnote{Proof of existence, An online service to prove the existence of documents, \url{https://docs.proofofexistence.com}, \LASTVISITED}, Chainpoint~\footnote{Chainpoint, Blockchain Proof and Anchoring Standar, \url{ https://chainpoint.org/}, \LASTVISITED}), Ethereum blockchain, or any other public blockchain that supports attaching extra data along the transaction.
 \item Storage network: IPFS \cite{benetIPFSContentAddressed2014}, Filecoin
@@
 \section{The Protocol}\label{sec:protocol}
-In this section we propose an abstract protocol for anonymous service provisioning without any assumptions about the underlying technologies.
+In this section, we propose an abstract protocol for anonymous service provisioning without any assumptions about the underlying technologies.
 We define the requirements for each role and leave the choice of the technology to the developer.
@@
         \item use common symmetric encryption $\mathrm{E}_\mathrm{key}(\cdot)$ and decryption $\mathrm{D}_\mathrm{key}(\cdot)$ operations.
-        \item have access to anonymous payments blockchain, message board, and storage network.
+        \item has access to anonymous payments blockchain, message board, and storage network.
     \end{itemize}
@@
 \noindent \textbf
-{Package}\label{package} is a physical container prepared by the customer encompassing all $\mathrm{materials}$ required by the SP to provide the service, randomly generated provision identifier used to anonymously track the provision throughout the protocol's steps, and the customer's public key $\mathrm{pk(C)}$ used to encrypt the result published on the public storage network.
+{Package}\label{package} is a physical container prepared by the customer encompassing all $\mathrm{materials}$ required by the SP to provide the service, a randomly generated provision identifier used to anonymously track the provision throughout the protocol's steps, and the customer's public key $\mathrm{pk(C)}$ used to encrypt the result published on the public storage network.
 
@@
 
-It is also an agreement between the customer and the SP, as it includes agreed upfront deadlines of actions, and a payment method.
+It is also an agreement between the customer and the SP, as it includes agreed upfront deadlines of actions and a payment method.
 
@@
 It protects the SP in case the customer unjustly starts a dispute after the result has been published.
-The connection between $\mathrm{PoP}$ and the result is made by the content identifier ($\mathrm{cid}$) uniquely identifing the result such that the result can not be forged after the $\mathrm{PoP}$ has been published.
+The connection between $\mathrm{PoP}$ and the result is made by the content identifier ($\mathrm{cid}$) uniquely identifying the result such that the result can not be forged after the $\mathrm{PoP}$ has been published.
 
@@
 \noindent \textbf
-{Result}\label{results} is assumed to be a document in PDF format, but any other format is allowed as long as it can be binary encoded and uploaded to sotrage network.
+{Result}\label{results} is assumed to be a document in PDF format, but any other format is allowed as long as it can be binary encoded and uploaded to the storage network.
 We refer to it symbolically as $\mathrm{result}$.
@@
 
-\begin{figure}[h!]
-\includegraphics[width=\linewidth]{anonser-protocol.png}
+\begin{figure}[ht!]
+\includegraphics[width=9cm]{anonser-protocol.png}
 \centering
@@
 The $\mathrm{provisionID}$ will be used to associate all actions related to the transaction throughout the protocol.
-The $\mathrm{provisionID}$ and $\mathrm{pk(C)}$ are encoded as a QR code, printed, and sticked to the package $\mathrm{pkg}$.
+The $\mathrm{provisionID}$ and $\mathrm{pk(C)}$ are encoded as a QR code, printed, and stuck to the package $\mathrm{pkg}$.
 The $\mathrm{sk(C)}$ is kept secret and used to decrypt the $\mathrm{result}$ at the end of the protocol.
@@
 As a result, $\mathrm{PoD}$ is created with predefined payment deadline $\mathrm{T}_\mathrm{pay}$, service provision deadline $\mathrm{T}_\mathrm{provide}$, and current time $\mathrm{T}_\mathrm{issue}$.
-Also $\mathrm{PoD}$ embodies the information whether the service has been paid in cash or should be paid by the customer using the anonymous blockchain account.
+Also, $\mathrm{PoD}$ embodies the information whether the service has been paid in cash or should be paid by the customer using the anonymous blockchain account.
 In the latter case, the SP's payment $\mathrm{address}$ is included in the $\mathrm{PoD}$.
@@
 
-Then, the $\mathrm{PoD}$ is published on the message board by the SP, commiting to the fact that the package $\mathrm{pkg}$ has been delivered, adn the SP can not reject receiving it.
+Then, the $\mathrm{PoD}$ is published on the message board by the SP, committing to the fact that the package $\mathrm{pkg}$ has been delivered, and the SP can not reject receiving it.
 If the provision has not been paid in cash, the SP waits for the customer to pay for the service on the specified in the $\mathrm{PoD}$ payment $\mathrm{address}$.
@@
 If the provision has not been paid in cash, the customer should pay for the transaction with the predefined anonymous payment blockchain (see section~\ref{payment-for-services}).
-
 In return, the customer receives the $\mathrm{attestation}$ that should be disclosed in case of a dispute.
@@
 After the service is finished, a result should be created. 
-Next, the result is encrypted using shared key derived from the customer's public key $\mathrm{pk(C)}$ and the SP's secret key $\mathrm{sk(S)}$ using Diffie-Hellman key exchange (DHKE) method.
-
-The encrypted result is then uploaded on the content addressable network (such as IPFS). In return the content identifier ($\mathrm{cid}$) is created.
+Next, the result is encrypted using a shared key derived from the customer's public key $\mathrm{pk(C)}$ and the SP's secret key $\mathrm{sk(S)}$ using Diffie-Hellman key exchange (DHKE) method.
+The encrypted result is then uploaded on the content addressable network (such as IPFS). In return, the content identifier ($\mathrm{cid}$) is created.
 
@@
 
-When the $\mathrm{result}$ is uploaded, the SP creates and publish on a message board a proof of provision consisting of $\mathrm{cid}$ along with $\mathrm{provisionID}$ and signature $\mathrm{sig}_\mathrm{SP}$.
+When the $\mathrm{result}$ is uploaded, the SP creates and publishes on a message board a proof of provision consisting of $\mathrm{cid}$ along with $\mathrm{provisionID}$ and signature $\mathrm{sig}_\mathrm{SP}$.
 
@@
 
-After delivering the package and paying for the transaction, the customer start listening to the message board and waits until the SP publishes the $\mathrm{PoP}$ for the $\mathrm{provisionID}$.
+After delivering the package and paying for the transaction, the customer starts listening to the message board and waits until the SP publishes the $\mathrm{PoP}$ for the $\mathrm{provisionID}$.
 
@@
 
-Having the $\mathrm{cid}$, the customer downloads and decrypts the $\mathrm{result}$ using shared key derived from the customer's secret key $\mathrm{sk(C)}$ and the SP's public key $\mathrm{pk(S)}$ using DHKE method.
+Having the $\mathrm{cid}$, the customer downloads and decrypts the $\mathrm{result}$ using a shared key derived from the customer's secret key $\mathrm{sk(C)}$ and the SP's public key $\mathrm{pk(S)}$ using DHKE method.
 The protocol ends.
@@
 \item Normal: taking actions prescribed by the protocol.
-\item Abnormal: everything that deviates from the designed steps of the protocol. For example, sending an arbitrary message, skipping or repeating steps, timing out.
+\item Abnormal: everything that deviates from the designed steps of the protocol. For example, sending an arbitrary message, skipping or repeating steps, and timing out.
 \end{enumerate}
@@
 To mitigate the issue, we designed the protocol so that the SP who follows the protocol is always in an advantaged position, and therefore has no reason to start a dispute.
-On the other hand, the customer can start a dispute at any time of the protocol, but only the actual misbehaviour of the SP makes him win the case.
+On the other hand, the customer can start a dispute at any time of the protocol, but only the actual misbehavior of the SP makes him win the case.
 
 \begin{definition}[Fairness] \label{def:fairness}
-A protocol achieve fariness iff 
+A protocol achieve fairness iff 
 \begin{equation*}
@@
 
-Below we listed assumptions we took for the analysis purpose.
+Below we list the assumptions we take for the analysis purpose.
 
@@
 \item Both parties start from a neutral position $\neutral$.
-\item After completing a transaction, both parties end up in advantaged positions (\plus{}). In other words, they have intrinsic motivation to initialize and complete the transaction.
+\item After completing a transaction, both parties end up in advantaged positions (\plus{}). In other words, they have an intrinsic motivation to initialize and complete the transaction.
 \item The protocol steps are atomic—there are no intermediate steps.
@@
 \item Both the customer and the SP are rational (selfish).
-They always prefer to go from the worst position (\minus{} or $\neutral${}) to a better position ($\neutral$ or \plus), but also risk a temporary worst position in favour of a later better position if and only if at any time they can get out of the worst position; in particular, at any time the customer can start a dispute and, if the SP has misbehaved, get out of disadvantaged position (\minus) to the neutral position ($\neutral$).
+They always prefer to go from the worst position (\minus{} or $\neutral${}) to a better position ($\neutral$ or \plus), but also risk a temporary worst position in favor of a later better position if and only if at any time they can get out of the worst position; in particular, at any time the customer can start a dispute and, if the SP has misbehaved, get out of disadvantaged position (\minus) to the neutral position ($\neutral$).
 \end{enumerate}
@@
 \begin{figure}[h!]
-\includegraphics[width=9cm]{formal-table-of-positions.png}
+\includegraphics[width=9cm]{model.png}
 \centering
@@
 
-The description of each step and the rationale of the outcome position is given in the Appendix~\ref{app:proof-of-fairness}.
+The detailed description of each step and the justification %JS proof lub justification ?
+of the outcome position is given in Appendix~\ref{app:proof-of-fairness}.
 
@@
 \begin{figure}[h!]
-\includegraphics[width=9cm]{formal-misbehaviour-path.png}
+\includegraphics[width=9cm]{misbehaviour.png}
 \centering
@@
 \begin{figure}[h!]
-\includegraphics[width=9cm]{formal-rational-path.png}
+\includegraphics[width=9cm]{rational.png}
 \centering
-\caption{Transitions of positions where where both the customer and the SP are behaving correctly}
+\caption{Transitions of positions where both the customer and the SP are following the protocol}
 \label{fig:rational}
@@
 
-Using the fariness definition~\ref{def:fairness} and the assumptions stated in Section~\ref{sec:assumptions}, our analysis indicates that the protocol achieves fairness.
+Using the fairness definition~\ref{def:fairness} and the assumptions stated in Section~\ref{sec:assumptions}, our analysis indicates that the protocol achieves fairness.
 
@@
 We use \texttt{MetaMask}\footnote{MetaMask, A crypto wallet \& gateway to blockchain apps, \url{https://metamask.io}, (last visited Dec.
-20, 2022)} browser extension for signing and submiting transactions to Ethereum's node.
+20, 2022)} browser extension for signing and submitting transactions to Ethereum's node.
 We use \texttt{monerod}\footnote{Monero, The Monero daemon \texttt{monerod}, \url{https://monerodocs.org/interacting/monerod-reference/}, (last visited Dec.
@@
 Moreover, Powergate is configured to use local Filecoin and IPFS networks.
-For Ethereum blockchain we use Truffle Ganache, which is a local Ethereum blockchain for development and testing purposes. 
+For Ethereum blockchain, we use Truffle Ganache, which is a local Ethereum blockchain for development and testing purposes. 
 Monero is configured to use the public stage network.
-We assume service provider offers only one type of service, which is offered for a fixed public price, hence we omit the type of service and price from the protocol.
+We assume the service provider offers only one type of service, which is offered for a fixed public price, hence we omit the type of service and price from the protocol.
 
@@
 
-Both the customer and the SP create a Monero wallets using \texttt{monero-wallet-cli} command-line tool.
-
-Service provider deploys the smart contract using the \texttt{truffle migrate --network development} command, which deploys the smart contract to the Ethereum blockchain.
+Both the customer and the SP create Monero wallets using \texttt{monero-wallet-cli} command-line tool.
+
+The service provider deploys the smart contract using the \texttt{truffle migrate --network development} command, which deploys the smart contract to the Ethereum blockchain.
 The webapp is configured to use the latest deployed smart contract address.
 
-Customer gets some testing Monero funds using \url{https://community.rino.io/faucet/stagenet/} faucet service.
-
-Next, the customer enable per-transaction proof generation (payment \texttt{attestation}) by setting \texttt{set store-tx-info 1} for his wallet.
-The proof generation is required to verify the payment in case of dispute.
-
-At this point both the customer and the SP are ready to start the protocol.
+The customer gets some testing Monero funds using \url{https://community.rino.io/faucet/stagenet/} faucet service.
+
+Next, the customer enables per-transaction proof generation (payment \texttt{attestation}) by setting \texttt{set store-tx-info 1} for his wallet.
+Proof generation is required to verify the payment in case of a dispute.
+
+At this point, both the customer and the SP are ready to start the protocol.
 
@@
 
-The customer and the SP are two different users of our prototype, but for simplicity they use the same machine and the same web application.
-
-Now we describe the experiments we performed to test our protocol.
-
-\begin{figure*}[ht]
-  \begin{center}
-  \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{anonser-experiment1.pdf}
-  \end{center}
-\end{figure*}
-\begin{figure*}[ht]
-  \begin{center}
-  \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{anonser-experiment2.pdf}
-  \end{center}
-\end{figure*}
+The customer and the SP are two different users of our prototype, but for simplicity, they use the same machine and the same web application.
+
+Figures \ref{fig:anonser-experiment1} and \ref{fig:anonser-experiment2} show the steps of the experiment. Their description is as follows:
 
@@
   \setcounter{enumi}{0}
-  \item[0.] The protocol starts with the customer opening the webapp and creating new provision. 
-The app generates random ECDSA (secp256k1) customer's keypair and random 32 bytes provisionID, then display QR code that encodes both the provisionID and the customer's public key. 
+  \item[0.] The protocol starts with the customer opening the webapp and creating a new provision. 
+The app generates a random ECDSA (secp256k1) customer's keypair and random 32 bytes provisionID, then display QR code that encodes both the provisionID and the customer's public key. 
 The customer's private key must be downloaded and provided later for the decryption of the results.
 
-  \item[1.] The customer prints the QR code, stick it on a package, and delivers the package to the SP either: in person, via trusted party, or delivery agency.
-
-  \item[2.1.] The SP opens the app, scans the QR code decoding the provisionID and the client's public key.
-
-  \item[2.2.] Since (in this experiment) the provision has not been paid in cash, the SP generate unique Monero payment address using \texttt{monero-wallet-cli integrated\_address} 
+  \item[1.] The customer prints the QR code, sticks it on a package and delivers the package to the SP either: in person, via a trusted party, or a delivery agency.
+
+  \item[2.1.] The SP opens the app, and scans the QR code decoding the provisionID and the client's public key.
+
+  \item[2.2.] Since (in this experiment) the provision has not been paid in cash, the SP generates a unique Monero payment address using \texttt{monero-wallet-cli integrated\_address} 
   \item[2.3.] The SP submits the proof of delivery to the Ethereum blockchain using MetaMask interface.
@@
   % Matching integrated address: 5LHmrsVsQM2Q2TgqufX4A5gKPpxy1czHULDyVc84omvnh1nQLVmqXk4VBuy8WnX1AXfKxDx7xuASAc6svkZqGVkL1XkUBWT7QejHymEaYM
-  \item[3.] The customer (using the webapp) check the transaction status on the Ethereum blockchain invoking \texttt{getProvision} with arguments \texttt{customerPubKey} and \texttt{provisionID}.
+  \item[3.] The customer (using the webapp) checks the transaction status on the Ethereum blockchain invoking \texttt{getProvision} with arguments \texttt{customerPubKey} and \texttt{provisionID}.
   % monero-wallet-cli --stagenet --wallet-file customer --password "" transfer 5LHmrsVsQM2Q2TgqufX4A5gKPpxy1czHULDyVc84omvnh1nQLVmqXk4VBuy8WnX1AXfKxDx7xuASAc6svkZqGVkL1XkUBWT7QejHymEaYM 1
@@
 
-  \item[4.] The customer (using the \texttt{monero-wallet-cli transfer}) sends the payment to the designated in the smart contract \texttt{paymentAddress} and stores the payment attestation (using \texttt{monero-wallet-cli get\_tex\_key <tx-id>}) in case of dispute.
-
-  \item[5.] Once SP notice the payment on Monero blockchain it starts providing the service and outputs the file \texttt{result.pdf}.
+  \item[4.] The customer (using the \texttt{monero-wallet-cli transfer}) sends the payment to the designated in the smart contract \texttt{paymentAddress} and stores the payment attestation (using \texttt{monero-wallet-cli get\_tex\_key <tx-id>}) in case of a dispute.
+
+  \item[5.] Once SP notices the payment on Monero blockchain it starts providing the service and outputs the file \texttt{result.pdf}.
 
   \item[6.] The SP uploads the file \texttt{result.pdf} on the Filecoin and IPFS networks using Powergate.
-In result, the SP gets the content identifier \texttt{cid}, and \texttt{dealID} and \texttt{minerID}.
+As a result, the SP gets the content identifier \texttt{cid}, and \texttt{dealID} and \texttt{minerID}.
 
@@
 
-  \item[8.] Meantime, the Customer subscribes to the Ethereum and waits until the SP publishes the Proof Of Provision.
- Once the Proof Of Provision is published the Customer downloads the result using either: IPFS network via \texttt{https://dweb.link/<cid>} or Lotus network using \texttt{lotus retreive <cid> <minerID>}.
-
-  \item[9.] Results are then decrypted using previously stored customer's private key.
-If everything is correct, the Customer is satisfied with the service and the protocol ends, otherwise the Customer can initiate a dispute.
+  \item[8.] Meantime, the Customer subscribes to Ethereum and waits until the SP publishes the Proof Of Provision.
+ Once the Proof Of Provision is published the Customer downloads the result using either: IPFS network via \texttt{https://dweb.link/<cid>} or Lotus network using \texttt{lotus retrieve <cid> <minerID>}.
+
+  \item[9.] Results are then decrypted using the previously stored customer's private key.
+If everything is correct, the Customer is satisfied with the service and the protocol ends, otherwise, the Customer can initiate a dispute.
 
@@
 
+\noindent%
+\begin{minipage}{\linewidth}% to keep image and caption on one page
+\makebox[\linewidth]{%        to center the image
+\includegraphics[height=0.95\textheight,keepaspectratio]{anonser-experiment1.pdf}}
+\captionof{figure}{Steps of the experiment, first part.}\label{fig:anonser-experiment1}%      only if needed  
+\end{minipage}
+
+\noindent%
+\begin{minipage}{\linewidth}% to keep image and caption on one page
+\makebox[\linewidth]{%        to center the image
+\includegraphics[height=0.95\textheight,keepaspectratio]{anonser-experiment2.pdf}}
+\captionof{figure}{Steps of the experiment, second part.}\label{fig:anonser-experiment2}%      only if needed  
+\end{minipage}
 \subsection{Results}
@@
 \paragraph{Fariness}
-As showed in Section~\ref{sec:steps} and Appendix~\ref{app:proof-of-fairness}, the protocol is fair.
-It is achieved by a undeniable hand-shake mechanism in which the SP first publishes $\mathrm{PoD}$ (step 2.) commiting to package delivery and deadlines of the service, and then the customer accepts it by paying for the service or not (step 3.).
-
-Once the payment is made, the SP stays in the advantaged position.
-Since he has agreed on the deadlines of the provision of the service, he is incentivised to provide the serice and publish the resutlts and PoP before the deadline (step 7.); because otherwise the customer—having all the evidences—can initiate a dispute and punish the SP, therefore rational parties will follow the protocol.
+As shown in Section~\ref{sec:steps} and Appendix~\ref{app:proof-of-fairness}, 
+the protocol is fair.
+It is achieved by an undeniable hand-shake mechanism in which the SP first publishes $\mathrm{PoD}$ (step 2.) committing to package delivery and deadlines of the service, and then the customer accepts it by paying for the service or not (step 3.).
+
+Once the payment is made, the SP stays in the advantaged position. Since he has agreed on the deadlines of the provision of the service, he is incentivized
+to provide the service and publish the results and PoP before the deadline (step 7.); otherwise the customer—having all the evidence—can initiate a dispute and punish the SP, therefore rational parties will follow the protocol.
 
@@
 We achieved anonymity by using anonymous payment methods such as cash or privacy-preserving payment blockchains (e.g.
-Monero), and decentralised storage networks like IPFS and Filecoin, allowing the customer to interact with the protocol without revealing his identity at any step of the protocol.
+Monero), and decentralized storage networks like IPFS and Filecoin, allowing the customer to interact with the protocol without revealing his identity at any step of the protocol.
 
@@
 In case of dispute, the SP can upload the content again, proving its availability.
-The SP has no motivation to proceed with this kind of misbehaviour other than putting the customer in a disadvantaged position caused by the lost dispute.}.
-However, the Filecoin network, which works as an incentivisation layer on top of IPFS, increases the content availability via economic incentivisations (i.e., punishment in case of lack of proof of storage of the content\footnote{Filecoin, Slashing, \url{https://docs.filecoin.io/storage-provider/rewards/slashing}, (last visited Jan.
+The SP has no motivation to proceed with this kind of misbehavior other than putting the customer in a disadvantaged position caused by the lost dispute.}.
+However, the Filecoin network, which works as an incentivization layer on top of IPFS, increases the content availability via economic incentivisation (i.e., punishment in case of lack of proof of storage of the content\footnote{Filecoin, Slashing, \url{https://docs.filecoin.io/storage-provider/rewards/slashing}, (last visited Jan.
 03, 2023)})~\cite{protocollabsFilecoinDecentralizedStorage2017}.
 
-The SP uploads the result on both IPFS and Filecoin networks (via Powergate) making the result available even in case of the SP stop serving the result from his node.
+The SP uploads the result on both IPFS and Filecoin networks (via Powergate) making the result available even in case of the SP stops serving the result from his node.
 
 \paragraph{Costs}
-Deploying smart contract and invoking functions on the Ethereum blockchain costs gas. The cost of gas is proportional to the amount of computation required to execute a transaction.
-
-Deploying smart contract consumed 1456577 gas.
+Deploying a smart contract and invoking functions on the Ethereum blockchain costs gas. The cost of gas is proportional to the amount of computation required to execute a transaction.
+
+Deploying a smart contract consumed 1456577 gas.
 Proof of delivery consumed 129649 gas.
@@
 
-In result, the cost of:
+In a result, the cost of:
 \begin{itemize}
@@
 
-Centralised justice is the biggest obstacle in achieving a system that complies with Web 3.0 postulates\footnote{Web3, \url{https://en.wikipedia.org/wiki/Web3}, (last visited Jan. 05, 2023)}.
-
-The possible directions for mitigation of such issues are to either (i) replace local justice with blockchain dispute resolution systems like proposed in Themis~\cite{mengThemisDecentralizedEscrow2019}, Kleros~\cite{bergollaKlerosSociolegalCase2022,gudkovCrowdArbitrationBlockchain2020}, Aragon Court\footnote{Aragon Court, Decentralized Dispute Resolution Protocol, https://aragon.org/aragon-court, (last visited Jan.
-10, 2023)}, LTO Network\footnote{LTO Network, 2019, https://lto.network/, (last visited Jan.
+Centralized justice is the biggest obstacle in achieving a system that complies with Web 3.0 postulates\footnote{Web3, \url{https://en.wikipedia.org/wiki/Web3}, (last visited Jan. 05, 2023)}.
+
+The possible directions for mitigation of such issues are to either (i) replace local justice with blockchain dispute resolution systems like those proposed in Themis~\cite{mengThemisDecentralizedEscrow2019}, Kleros~\cite{bergollaKlerosSociolegalCase2022,gudkovCrowdArbitrationBlockchain2020}, Aragon Court\footnote{Aragon Court, Decentralized Dispute Resolution Protocol, https://aragon.org/aragon-court, (last visited Jan.
+10, 2023)}, LTO Network\footnote{LTO Network, a hybrid blockchain application development platform for securing, verifying, and exchanging enterprise information, https://lto.network/, (last visited Jan.
 17, 2023)}, and other Online Dispute Resolution platforms~\cite{allenGovernanceBlockchainDispute2019}; or (ii) make it infeasible to provide incorrect results.
@@
 The experts would be incentivized to participate in the pool by the system of fees.
-They would be incentivized to vote honesty by the stake they would have to lock and reward/punishment they would get by judging correctly/incorrectly, where the correctness is determined by the quorum of votes.
+They would be incentivized to vote honestly by the stake they would have to lock and reward/punishment they would get by judging correctly/incorrectly, where the correctness is determined by the quorum of votes.
 
@@
 \subsection{Self-sovereign identities}
-Our research in the field showed that some jurisdictions require SPs to associate the diagnosis with the customer personal information.
-For example, in Poland all laboratories performing medical diagnostic tests, and collecting the material (except tests for HIV) are obligated to the unambiguous identification and verification of the identity of the patient from whom the material was collected~\footnote{Regulation of the Minister of Health of March 23, 2006 on quality standards for medical diagnostic and microbiological laboratories, \url{https://isap.sejm.gov.pl/isap.nsf/DocDetails.xsp?id=WDU20060610435}}.
+Our research in the field showed that some jurisdictions require SPs to associate the diagnosis with the customer's personal information.
+For example, in Poland, all laboratories performing medical diagnostic tests, and collecting the material (except tests for HIV) are obligated to the unambiguous identification and verification of the identity of the patient from whom the material was collected~\footnote{Regulation of the Minister of Health of March 23, 2006, on quality standards for medical diagnostic and microbiological laboratories, \url{https://isap.sejm.gov.pl/isap.nsf/DocDetails.xsp?id=WDU20060610435}}.
 
@@
 
-One promising solution would be to use Self-sovereign identities (SSI)~\cite{muhleSurveyEssentialComponents2018}, especially the verifable claims.
-A trusted authority (e.g., a government) would issue a one-time claim for a customer that would be accepted by the SP as a legitimate personal identificator.
+One promising solution would be to use Self-sovereign identities (SSI)~\cite{muhleSurveyEssentialComponents2018}, especially the verifiable claims.
+A trusted authority (e.g., a government) would issue a one-time claim for a customer that would be accepted by the SP as legitimate personal identification.
 The SP would associate the diagnosis result with the provided DID.
-The DID itself would not contain any personal information, therefore the SP would learn nothing about the customer identity besides the random-looking identificator.
-The DID could be deanonimised by the collaboration with the government.
-
-However, since SSI is relatively new technology and the government has not yet adopted it, we decided to postpone the discussion of this topic to the future work.
-
-\subsection{Anonymous delivery}\label{anonymous-delivery}
-
-We assumed the customer to deliver the package to the SP personally or via a trusted person.
-However, the system could be extended to support an anonymous delivery system as proposed in Lelantos~\cite{altawyLelantosBlockchainBasedAnonymous2017}.
-One modification to the protocol would be to publish $\mathrm{PoD}$ on the message board, similarly to $\mathrm{PoP}$.
+The DID itself would not contain any personal information, therefore the SP would learn nothing about the customer's identity besides the random-looking identification.
+The DID could be deanonimised by collaboration with the government.
+
+However, since SSI is a relatively new technology and the government has not yet adopted it, we decided to postpone the discussion of this topic to future work.
+
+\subsection{Anonymous delivery}\label{sec:anonymous-delivery}
+
+We assumed the customer to deliver the package to the SP anonymously via the SP's drop box, or via a trusted person.
+However since the delivery is from the anonymous customer to the public SP, achieving the anonymity of just the sender is much easier than the other way around as proposed in Lelantos~\cite{altawyLelantosBlockchainBasedAnonymous2017} or ~\cite{birjoveanuFairExchangeECommerce2020}.
 
 \section{Conclusions}\label{sec:conclusion}
-In this paper, we have proposed the protocol for service provision that simultaneously achieves anonymity, fairness, dispute resolution, TTP-less, and support physical materials.
-The protocol can be employed to provide services without collecting any personal information.
-Payments are handled by anonymous cryptocurrencies.
-The result of the service is published on a content-addressable p2p network like IPFS.
+In this work, we have focused on enabling service provision without the collection of personal data.
+Our aim was to enable services such as genetic tests, tests for paternity, venereal diseases, HIV, drugs, and steroids, or anonymous legal advice.
+
+We observed that the current state of the art is not sufficient to achieve the goal.
+Therefore, we have proposed a protocol for service provision that simultaneously achieves anonymity, fairness, dispute resolution, TTP-lessness, and supports physical materials.
+
+Payments are handled either in cash or anonymous cryptocurrencies.
+The result of the service is published on a content-addressable p2p network.
 The dispute can be settled by disclosing the collected proofs to justice.
-Using the definition~\ref{def:fairness} we showed that the protocol achieves fairness by the proof of delivery, payment attestation, and proof of provision published on the message board blockchain.
-Finally, we pinpointed further improvements like decentralized dispute resolution, provable availability of the result, paying with cash, and anonymous package delivery via courier.
+
+Using the definition~\ref{def:fairness} we showed that the protocol achieves fairness by the proof of delivery, payment attestation, and proof of provision published on the message board.
+
+Finally, we pinpointed further improvements like decentralized dispute resolution, self-sovereign identifiers, and anonymous package delivery via courier.
+
+%JS dodac acknowlegements
+
+\ifx\JOURNAL=IEEE
 
 \appendices
+\printbibliography
+\else
+
+\section*{Declaration of competing interest}
+The authors declare that they have no known competing financial interests or personal relationships that could have appeared to influence the work reported in this paper.
+
+\section*{Data availability}
+No data was used for the research described in the article.
+
+The prototype available at \url{https://anonser.stan.bar}.
+
+The source code available at \url{https://github.com/stanbar/anonymous-provision-of-services-via-blockchain}.
+
+\printbibliography
+\appendix
+\fi
+%JS za bibliografie tak by byl w calosci a nie przedzielony bibliografią
+%biogtafie na samym koncu
+
+%JS opis nie pasuje do rysunku - zaczyna sie od 1 a rysunek od 0
+%JS rysunek/schemat powinien byc zatytułowany, odnosniki do niego w tekscie opisujace co na nim jest
 
@@
 Below we describe each step and rationale of the outcome position.
-We use the notation introduced in Section~\ref{sec:fairness-model} to analise each position in the protocol and fariness Definition~\ref{def:fairness} to show the fairness of the protocol.
+We use the notation introduced in Section~\ref{sec:fairness-model} to analyze each position in the protocol and fairness Definition~\ref{def:fairness} to show the fairness of the protocol.
 
@@
 
-The protocol starts when the customer correctly execute the first step of the protocol, i.e., deliver the package to the SP.
+The protocol starts when the customer correctly executes the first step of the protocol, i.e., deliver the package to the SP.
 
@@
   \begin{itemize}
-    \item  \Pos{1}{c}{\normal}{\neutral}, the customer risked his materials but did not pay for the transaction therefore ends up in neutral position\footnote{One would argue that the customer has put effort into delivering the materials to the SP or that the materials are valuable.
-We assume that the materials without personal information is useless, and the effort to deliver the package is negligible.}.
-    \item \Pos{1}{s}{\normal}{\neutral}, the SP ends up in neutral position as she did not spend any resources and the package did not bring her any value.
+    \item  \Pos{1}{c}{\normal}{\neutral}, the customer risked his materials but did not pay for the transaction and therefore ends up in a neutral position\footnote{One would argue that the customer has put effort into delivering the materials to the SP or that the materials are valuable.
+We assume that the materials without personal information are useless, and the effort to deliver the package is negligible.}.
+    \item \Pos{1}{s}{\normal}{\neutral}, the SP ends up in a neutral position as she did not spend any resources and the package did not bring her any value.
   \end{itemize}
@@
       \item \Pos{2}{c}{\normal}{\neutral}, the customer remains in the neutral position as the PoD allows him to pay for the transaction but does not obligate him to anything.
-      \item \Pos{2}{s}{\normal}{\neutral}, the SP remains in the neutral position as the package has not brought her any value and she did not spend any resource to provide the service yet.
+      \item \Pos{2}{s}{\normal}{\neutral}, the SP remains in the neutral position as the package has not brought her any value and she did not spend any resources to provide the service yet.
     \end{itemize}
@@
     \item \Pos{2}{c}{\abnormal}{\neutral}, the customer remains in the neutral position as he is not obligated to agree with the incorrect $\mathrm{PoD}$.
-    \item \Pos{2}{s}{\abnormal}{\neutral}, the SP remains in the neutral position as the package has not brought her any value and she did not spend any resource to provide the service yet.
+    \item \Pos{2}{s}{\abnormal}{\neutral}, the SP remains in the neutral position as the package has not brought her any value and she did not spend any resources to provide the service yet.
   \end{itemize}
@@
   \item \CanDoAnything{SP}.
-  \item The customer can either wait (in case of the SP following the protocol), or abandon the transaction (in case of the SP acting abnormally).
+  \item The customer can either wait (in case of the SP following the protocol) or abandon the transaction (in case of the SP acting abnormally).
 In both cases the customer ends up in non-disadvantaged position \Pos{2}{c}{\normal}{\neutral} or \Pos{2}{c}{\abnormal}{\neutral}.
@@
     \item \Pos{4}{c}{\normal}{\minus}, the customer paid in advance.
-    \item \Pos{4}{s}{\normal}{\plus}, the SP received the payment, but has not spent his resources yet.
+    \item \Pos{4}{s}{\normal}{\plus}, the SP received the payment but has not spent his resources yet.
   \end{itemize}
@@
 
-\newcommand{\CustomerRiskTemporaryDisadvantagedPosition}[1]{The customer, following the 9th assumption described in Section~\ref{sec:assumptions}, risk the temporary disadvantaged position #1 in faviour of a later better position \Pos{9}{s}{\normal}{\plus}; meanwhile being able to get out of the disadvantaged position if the SP misbehave in one of the following steps.}
+\newcommand{\CustomerRiskTemporaryDisadvantagedPosition}[1]{The customer, following the 9th assumption described in Section~\ref{sec:assumptions}, risk the temporary disadvantaged position #1 in favor of a later better position \Pos{9}{s}{\normal}{\plus}; meanwhile being able to get out of the disadvantaged position if the SP misbehave in one of the following steps.}
 
@@
     \begin{itemize}
-      \item \Pos{7}{c}{\normal}{\minus}, the customer has not received the result. Therefore, he remains in the disadvantaged position. 
-      \item \Pos{7}{s}{\normal}{\plus}, the SP has published all evidences to prove her correct behaviour, therefore she remains in advantaged position fot the rest of the protocol.
+      \item \Pos{7}{c}{\normal}{\minus}, the customer has not received the result. Therefore, he remains in a disadvantaged position. 
+      \item \Pos{7}{s}{\normal}{\plus}, the SP has published all evidence to prove her correct behavior, therefore she remains in an advantaged position for the rest of the protocol.
     \end{itemize}
@@
   \begin{itemize}
-    \item \Pos{9}{c}{\normal}{\plus}, the customer got the result, therefore he terminate the protocol in advantaged position.
+    \item \Pos{9}{c}{\normal}{\plus}, the customer got the result, therefore he terminate the protocol in an advantaged position.
     \item \Pos{9}{s}{\normal}{\plus}, \RemainsIn{\sp}{advantaged}.
@@
   \begin{itemize}
-    \item \Pos{9}{c}{\abnormal}{\minus},the customer ends up in a disadvantaged position, as he ends up with the incorrect result.
+    \item \Pos{9}{c}{\abnormal}{\minus}, the customer ends up in a disadvantaged position, as he ends up with the incorrect result.
     \item \Pos{9}{s}{\abnormal}{\plus}, the SP ends up in the advantaged position as he received the payment but did not spend his resources.
@@
 \end{itemize}
-
-\bibliographystyle{IEEEtran}
-% argument is your BibTeX string definitions and bibliography database(s)
-\bibliography{bibliography}
-\EOD
-
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{stanislaw.jpg}}]{Stanis\L{}aw Bara{\'n}ski} received BEng in 2019 and MSc in 2020 in informatics at Gdańsk University of Technology.
-Currently, he is a PhD candidate at the Department of Computer Architecture, Faculty of Electronics, Telecommunications and Informatics, Gdansk University of Technology.
-
-His research interests include blockchains, applied cryptography, and secure computation; particularly the issue of blockchain-based internet voting, but also other areas that currently depend on trusted third parties.
-
-He likes to validate his ideas in practice, developing them up to the commercialization stage.
-He is the author of multiple software products that have reached success in the market.
-His blockchain-based internet voting project has been funded by the Stellar Community Fund for the most useful Stellar application.
-\end{IEEEbiography}
-
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{julian.jpg}}]{JULIAN SZYMA{\'N}SKI}  received the PhD degree in 2009 and DSc in 2020 at Gdańsk University of Technology.
-He is currently with the Department of Computer
-Architecture, Faculty of Electronics, Telecommunications and Informatics, Gdansk University of Technology.
-He addresses the problems of knowledge representation, methods of lexical knowledge acquisition, and linguistic data utilization.
-His research results find applications in web search engines and systems of automated text categorization.
-He manages research projects for processing the information in Wikipedia, where the main goal is to extract and structuralize textual knowledge and construct interfaces capable of communicating in natural language.
-Besides his research in information retrieval domain, he was involved in projects related to cognitive science.
-His mainstream of this research is building semantic memory models that improve natural language processing.
-He also worked on analyzing human emotions, by mining EEG signals.
-His results are implemented in the form of brain-machine interfaces for disabled people.
-He also works on analyzing data within the IoT domain and its secure storage on the blockchain.
-He is involved in project, where acquisition of data from sensors placed in beehives  allows one to predict apiary development and detect abnormalities.
-
-He was a committee member and reviewer in  many international
-conferences as well as served as guest editor preparing special issues of prestigious journals.
-
-\end{IEEEbiography}
-
-% \section{Appendix B: Smart contract code}\label{appendix-b-smart-contract-code}
-
-% \input{solidity-highlighting.tex}
-% \begin{lstlisting}[language=Solidity]
-% // SPDX-License-Identifier: MIT
-% pragma solidity >=0.4.22 <0.9.0;
-
-% contract AnonSer {
-%     struct Provision {
-%         uint256 issueTime;
-%         uint256 paymentDeadlineTime;
-%         uint256 provisionDeadlineTime;
-%         bool paidInCash;
-%         string paymentAddress;
-%         string cid;
-%         bool exist;
-%         uint256 dealId;
-%         string minerId;
-%     }
-
-%     mapping(bytes => mapping(bytes32 => Provision)) public provisions;
-
-%     address private _owner;
-
-%     event ProofOfDelivery(
-%         bytes indexed clientPubKey,
-%         bytes32 indexed provisionId,
-%         uint256 issueTime,
-%         uint256 paymentDeadlineTime,
-%         uint256 provisionDeadlineTime,
-%         bool paidInCash,
-%         string paymentAddress
-%     );
-
-%     constructor() {
-%         _owner = msg.sender;
-%     }
-
-%     modifier onlyOwner() {
-%         require(
-%             _owner == msg.sender,
-%             "Ownership Assertion: Caller of the function is not the owner."
-%         );
-%         _;
-%     }
-
-%     function proofOfDelivery(
-%         bytes memory clientPubKey,
-%         bytes32 provisionId,
-%         bool paidInCash,
-%         string memory paymentAddress
-%     ) public onlyOwner {
-%         if (provisions[clientPubKey][provisionId].exist) {
-%             revert("Provision already exists");
-%         }
-%         if (paidInCash && bytes(paymentAddress).length > 0) {
-%             revert("Payment address should be empty if paid in cash");
-%         }
-%         if (!paidInCash && bytes(paymentAddress).length == 0) {
-%             revert(
-%                 "Payment address should not be empty if didn't paid in cash"
-%             );
-%         }
-%         Provision memory provision = Provision({
-%             exist: true,
-%             issueTime: block.timestamp,
-%             paymentDeadlineTime: block.timestamp + 1 days,
-%             provisionDeadlineTime: block.timestamp + 8 days,
-%             paidInCash: paidInCash,
-%             paymentAddress: paymentAddress,
-%             dealId: 0,
-%             cid: "",
-%             minerId: ""
-%         });
-%         provisions[clientPubKey][provisionId] = provision;
-%         emit ProofOfDelivery(
-%             clientPubKey,
-%             provisionId,
-%             provision.issueTime,
-%             provision.paymentDeadlineTime,
-%             provision.provisionDeadlineTime,
-%             provision.paidInCash,
-%             provision.paymentAddress
-%         );
-%     }
-
-%     event ProofOfProvision(
-%         bytes indexed clientPubKey,
-%         bytes32 indexed provisionId,
-%         string cid,
-%         uint256 dealId,
-%         string minerId
-%     );
-
-%     function proofOfProvision(
-%         bytes memory clientPubKey,
-%         bytes32 provisionId,
-%         string memory cid,
-%         uint256 dealId,
-%         string memory minerId
-%     ) public onlyOwner {
-%         Provision storage provision = provisions[clientPubKey][provisionId];
-%         if (!provision.exist) {
-%             revert("Provision must be created with proof of delivery first");
-%         }
-
-%         provision.cid = cid;
-%         provision.dealId = dealId;
-%         provision.minerId = minerId;
-%         emit ProofOfProvision(clientPubKey, provisionId, cid, dealId, minerId);
-%     }
-
-%     function getProvision(bytes memory clientPubKey, bytes32 provisionId)
-%         public
-%         view
-%         returns (Provision memory)
-%     {
-%         return provisions[clientPubKey][provisionId];
-%     }
-% }
-% \end{lstlisting}
-
-\end{document}

### 2023-01-30 paper/ieee.tex
split the tex into subtexs

--- 2023-01-20 paper/access.tex
@@
 \documentclass{ieeeaccess}
+\usepackage{cite}
 
-\usepackage{cite}
 \usepackage{amsmath,amssymb,amsfonts}
@@
 \usepackage{textcomp}
+\usepackage{float}
 
@@
 \usepackage{xcolor,colortbl}
+\usepackage{scalerel}
 \newtheorem{theorem}{Theorem}
 \newtheorem{definition}{Definition}
-\usepackage{scalerel}
+
+\input{constants.tex}
 
@@
     T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+
 \begin{document}
+
 \history{Date of publication xxxx 00, 0000, date of current version xxxx 00, 0000.}
 \doi{10.1109/ACCESS.2022.0122113}
+\title{\TITLE}
 
-\title{Privacy-preserving physical delivery service provisioning using distributed networks}
-\author{\uppercase{Stanis\l{}aw Bara{\'n}ski} \authorrefmark{1},
-\uppercase{Julian Szyma{\'n}ski\authorrefmark{1} } 
- }
+\author{\uppercase{\STANLONG} \authorrefmark{1},
+\uppercase{\JULLONG{}} \authorrefmark{1}}
 
@@
 
-\markboth{S. Bara{\'n}ski, J. Szyma{\'n}ski : 
-Privacy-preserving physical delivery service provisioning using distributed networks}
-{S. Bara{\'n}ski, J. Szyma{\'n}ski : 
-Privacy-preserving physical delivery service provisioning using distributed networks}
+\markboth{\STAN{}, \JUL{} : \TITLE}
+{\STAN{}, \JUL{} : \TITLE}
 
@@
 \begin{abstract}
-Service providers like lawyers, laboratories, auditors, or banks, to provide services, require customers to submit data often associated with their personal information, exposing their customers to privacy risks.
-However, most service providers use personal information merely for logistic operations like payments and communication and could provide services anonymously if other means of logistics exist.
-We propose a anonymous fair exchange protocol for coordinating service provision using blockchain for both anonymous payments and proofs of existence and content-addressable network for results delivery.
-% Less important
-A service provider can employ our protocol to provide services without collecting personal information, enabling services currently based on unacceptable trust assumptions. 
-% Even less important
-Possible applications for this protocol include anonymous tests for drugs, venereal diseases, paternity, and steroids, or anonymous legal advice.
-We provide the fairness analysis and well as the implementation of the protocol. We discuss further extensions to an anonymous delivery system, and a decentralized conflict resolution system.
+  \ABSTRACT{}
 \end{abstract}
 
+\newcommand{\sep}{,}
 \begin{keywords}
-Anonymity, blockchain, fair-exchange, physical delivery, privacy, services
+Anonymity\sep{} blockchain\sep{} fair-exchange\sep{} physical delivery\sep{} privacy\sep{} services
 \end{keywords}
@@
 
-\section{Introduction}
-\label{sec:introduction}
-Service providers (SPs) like lawyers, laboratories, auditors, or banks, to provide services, require data that is often associated with the user identity.
+\def\JOURNALIEEE{IEEE}
+\def\JOURNALELS{ELS}
 
-Providing personal information exposes users to privacy risks, i.e. potential loss of control over personal information~\cite{smithInformationPrivacyResearch2011}.
+\def\JOURNAL{\JOURNALIEEE}
 
-Such personal information can be used deliberately or unintentionally
-(e.g., by theft) for insider disclosure, unauthorized access, or commercial gains.
-For example, by reselling it to marketers, financial institutions, other businesses, government agencies, or even cybercriminals.
-Which in turn can lead to profiled advertisements or criminal activities like identity theft or illegal tracking and surveillance~\cite{smithInformationPrivacyResearch2011}.
+\input{content}
 
-Important individuals like influencers, politicians, or celebrities are especially vulnerable to this kind of attack as exposure of their health records, purchase habits, or legal documents can threaten their reputation, position or be used for blackmailing.
-
-The privacy guarantee of the personal information is often based merely on trust assumptions and the security of the IT system.
-However, most SPs do not need personal information for any other reason than payment or communication, which should be considered secondary compared to actual service provision.
-
-It would be desirable for the user to keep its identity private while still receiving the service. This could lead to reduced trust that users have to put on SPs and less responsibility borne by SPs.
-
-Examples of services that would benefit from the anonymity property are:
-\begin{itemize}
-    \item Patients willing to take a test for drugs, venereal diseases, paternity or steroids have a strong incentive to keep the whole procedure private.
-Merely the fact that they took the test—without exposing the result—is suggestive enough to act as a premise in case of a conflict.
-
-Especially celebrities, politicians, and public figures are prone to this kind of problem as such precedent can negatively influence their future career.
-
-Currently, they have to risk that their personal details, materials, and results are stored securely and kept in private from any unauthorized actor (both curious employee and malicious attacker).
-
-Our protocol allows taking such tests anonymously, eliminating the strong trust assumption put on the laboratories and their IT
-systems.
-\item People willing to take risky business activities may be willing to receive the risk estimation and prediction of possible personal repercussions of such action.
-
-By exposing our identity we trust that the lawer will not use that information for harmful actions.
-
-Our protocol would allow taking such advice anonymously, eliminating the strong trust assumption put on the lawyers and their IT systems.
-\end{itemize}
-
-% We observe
-We observe that the issue of anonymous service provision can be seen as a problem of fair exchange where parties exchange some goods fairly, i.e., either both parties obtain the goods, or they both obtain nothing.
-
-In our case, the customer who wants to use the service, exchanges his materials and money with the SP for the result of the service.
-
-% Therefore we propose
-We propose a protocol for anonymously provisioning services that require the delivery of physical materials.
-A service provider employing our protocol can provide services without collecting any personal information from customers.
-
-In case of dispute, either due to exceeding deadlines or providing an incorrect result, the customer can disclose the whole interaction and prove to justice the misbehaviour of the SP.
-
-To achieve these objectives, we use:
-\begin{itemize}
-    \item Blockchain (aka message board), to achieve fairness, i.e., as a means for proving that certain actions took place at a certain moment without the trusted third party (TTP).
-    \item Anonymous payment methods, like cash or privacy-preserving cryptocurrencies, allowing customers to pay for the services anonymously.
-    \item Content-addressable decentralised storage network (e.g., IPFS) to anonymously provide results to customers together with provable storage netwrok (e.g., Filecoin) to guarantee that the results are available to the customer even in case of the SP deny of service.
-    \item Cryptography
-    \begin{itemize}
-        \item Symmetric encryption, to encrypt and decrypt results published on the public networks.
-        \item Public-key cryptography, and Diffie-Helman key exchange (DHKE) to derive shared secrets for symmetric encryption.
-        \item Digital signatures, to achieve authentication and non-repudiation of actions. 
-    \end{itemize}
-
-\end{itemize}
-
-%\paragraph{Contributions}
-We contribute to the state of the art by:
-
-\begin{itemize}
-\item proposing a novel protocol that:
-  \begin{itemize}
-  \item allows \textbf{anonymous} service provision, i.e., the service provider does not need to collect any personal information from the customer.
-  \item achieves \textbf{fairness} by carefully designing the protocol as an interactive non-cooperative game, in which the SP remains in advantageous position, and customer in disadvantageus with the option to start a dispute in case the SP misbehaviour.
-  \item \textbf{does not rely on centralized TTP}, but uses decentralized blockchain and distributed content-addressable storage network.
-  \item abstracts the customers from the blockchain technology used underneath, allowing the use of our protocol for \textbf{non-technical users}.
-  \item allows the \textbf{delivery of physical materials}, which was rarely addressed by other researchers or based on strong and unpractical assumptions.
-  \item guarantees the \textbf{remote availability of the results}, even in case of the SP denial of service.
-  \end{itemize} 
-\item Systemise often misused definitions of anonymity, pseudonymity, linkability, and traceability.
-\item Proposing a framework for analysing fairness analysis in fair-exchange protocols.
-\item Discuss the possible improvements to the protocol witht the use of secure computation, self-sovereign identities, zero-knowledge proofs, and blockchain-based dispute resolution mechanisms.
-\end{itemize}
-
-% Our protocol simultaneously provides five main properties:
-
-% \begin{itemize}
-% \item Anonymity: the customer stays anonymous to all external observers throughout the transaction.
-% \item Fairness: at each step of the protocol, both parties are incentivized to act accordingly to the protocol; otherwise, the misbehaving party ends up in a disadvantaged position.
-% \item Dispute resolution: at each step of the protocol, the customer can start a dispute and win the case if and only if the SP misbehaved.
-% \item Blockchain-obvious: the customer using our protocol does not need to interact with the blockchain directly; especially, he does not need to obtain funds and pay for the transaction fees, allowing the use of our protocol for non-technical users.
-% \item TTP-less: 
-% our protocol does not rely on a trusted third party to conduct transactions fairly.
-Only in case of a dispute, the centralised justice is involved, which can be instantiated either with courts and polices, or blockchain-based dispute resolution mechanisms as discussed in Section~\ref{sec:decentralised-justice}.
-% \item Physical materials: our protocol allows providing not only digital but also physical materials to the service provider.
-% \end{itemize}
-
-Some authors have proposed blockchain-based fair-exchange systems that could be adapted to service provision; however, to our best knowledge, we are the first to propose a system that satisfies all the properties stated above.
-Especially anonymity and physical materials delivery were rarely addressed together, and if so, the protocol was based on TTP and impractical assumptions on banking system~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} or did not address the conflict between parties~\cite{altawyLelantosBlockchainBasedAnonymous2017}.
-
-%\paragraph{Organisation}
-The remainder of this paper is organized as follows.
-In section~\ref{sec:related-works} we review related works. 
-Then, in section~\ref{sec:building-blocks} we discuss the building blocks of dispute resolution system, blockchain as a message board, fairness, payment for services, storage network, result availability, anonymity and confidentiality.
-Section~\ref{sec:protocol} describes how the protocol works in detail.
-Section~\ref{sec:fairness-analysis} provides a fairness analysis of the proposed protocol.
-In Section~\ref{sec:experiments} we present the implementation of the protocol and results of our experiments.
-Section~\ref{sec:discussion} discuss possible improvements in terms of crowd sourced dispute resolution or dispute avoidance, self-sovereign identities (SSI), and anonymous delivery.
-Finally, section~\ref{sec:conclusion} concludes the paper.
-
-\section{Related Works}\label{sec:related-works}
-In this section we review related works on fair exchange, anonymous, and physical delivery protocols. Then we outline the main differences between our protocol and the existing ones.
-
-\subsection{Fair exchange, anonymity, and physical products delivery} 
-\label{anonymity-and-fair-exchange-in-e-commerce-protocol-for-physical-products-delivery}
-
-The most common application of anonymous fair exchange protocols is e-commerce.
-The problem is that the customer wants to buy a product from a merchant, but does not want to reveal his identity to the merchant.
-The problem gets even more challenging when physical products are involved.
-
-Authors of~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} proposed a protocol for fair exchange of physical products and electronic payments, which guarantee both customer and merchant anonymity.
-They achieve it by introducing online TTPs that validate coins and provide fair exchange guarantees.
-
-The anonymity is ensured by assuming the existence of a source cabinet (SC), delivery cabinet (DC), and a trusted delivery agent who take a product from a SC and provide it to a DC.
-Both cabinets provide access to the product by passwords to conceal
-the identity of the customer and the merchant.
-
-The protocol works as follows: \begingroup
-\renewcommand{\labelenumii}{\arabic{enumii}.}
-
-\begin{enumerate}
-    \item Both parties agree on the purchase details.
-    \item The customer buys a digital coin from his bank and validates it with the TTP.
-    \item The customer sends the merchant the purchase order and the digital signature made by TTP on the encrypted coin.
-    \item The merchant post the product to the SC.
-    \item Delivery agent collects the product from the SC and posts it to the DC.
-    \item Customer collects the product from the DC using a password.
-    \item The customer checks if the product is the ordered one.
-    \begin{itemize}
-    \item[-] if yes 
-        \begin{enumerate}
-        \setcounter{enumii}{7}
-        \item the customer sends the acknowledge to the DC and decryption key to the merchant.
-        \item The merchant redeem the coins from the bank.
-        \end{enumerate}
-    \item[-] if no
-        \begin{enumerate}
-        \setcounter{enumii}{7}
-        \item the DC is equipped with a video camera that records the moment when the customer opens the package and lets the customer signal the invalidity of the product, and so, sending the encrypted recording to the TTP.
-        \item the dispute is settled via TTP, optionally letting each party reveal its identity.
-    \end{enumerate}
-    \end{itemize}
-\end{enumerate}
-\endgroup
-
-However, the protocol relies on strong assumptions, namely:
-
-\begin{itemize}
-    \item there exists trusted third party (TTP) and trusted delivery agent which do not misbehave or collude with any party;
-    \item there exists an anonymous communication channel 
-    \item the customer's and merchant's banks enable confidential transactions, and both share commit-buffer where the value is locked until the transaction is finished;
-    \item all banks maintain a global list of coins' serial numbers to prevent double-spending problems;
-    \item the SC and DC exist, and in both, the access is protected by a password;
-    \item the DC is equipped with a video camera that records the moment when the customer opens the package and provides a way to submit the video to TTP in case of a dispute;
-\end{itemize}
-
-\subsection{Fair exchange and blockchain}
-
-The issue of TTPs in fair exchange protocols has been solved by the usage of decentralised networks, especially blockchain technology.
-
-The simplest example of blockchain-based fair exchange protocol is certified electronic mail protocol in which neither the sender can deny sending the mail, nor the receiver can deny receiving it.
-As the service is widely used in the paper world, achieving it for e-mails has not yet met the agreement across the scientific community.
-The main problem was the dependency of TTP, which significantly reduced the performance, security, and robustness of such protocols.
-The protocols that do not use TTP struggle with high computation and communication overhead~\cite{hinarejosSolutionSecureCertified2019}.
-
-Authors of ~\cite{hinarejosSolutionSecureCertified2019} replaced the TTP with blockchain (concretely Bitcoin blockchain as a reference implementation) that acts as a secure, verifiable, and decentralized TTP.
-
-The idea behind certified e-mails and any other fair exchange protocols is following:
-\begin{enumerate}
-    \item The sender sends encrypted and signed message to the receiver.
-    \item The receiver returns a proof of delivery (a signature) of the encrypted message to the sender.
-    \item The sender publishes proof of delivery and the decryption key on a blockchain (or TTP in general).
-    \item The receiver decrypts the encrypted message using the published decryption key.
-\end{enumerate}
-
-The non-repudiation requirement is achieved by the receiver sending the proof of delivery prior to having access to the decrypted message and the sender publishing the decryption key together with the proof of delivery on the blockchain (or TTP) so that the receiver can deny neither receiving the message nor having access to the decryption key—because it is publicly available.
-
-In this case, the role of blockchain is to certify the existence of the decryption key at a certain time.
-
-\subsection{Fair-exchange, blockchain, and decentralized dispute resolution}
-\label{themis-towards-decentralized-escrow-of-cryptocurrencies-without-trusted-third-parties}
-
-Themis~\cite{mengThemisDecentralizedEscrow2019} is a fair exchange protocol that uses blockchain instead of TTP.
-It provides an escrow service for the secure exchange of cryptocurrencies and digital goods.
-Also, it provides a decentralized dispute resolution system for resolving conflicts.
-
-Two parties say, Alice and Bob, can create an escrow by generating
-2-of-2 (not 2-of-3 as it is other TTP-based systems) threshold account
-using Thresh-Key-Gen protocol. Alice and Bob generate secret keys
-\(x_A\) and \(x_B\) accordingly, the shared account public key becomes
-\(y = g^{x_A+x_B}\); only the access to both Alice's and Bob's secrets
-grants access to the shared account.
-
-Then, both Alice and Bob take their keys and split them into
-\(n=2t+1\) secret shares using Shamir Secret Shamir protocol, where
-\(n\) is the number of mediators that participate in the decentralized
-network and \(t+1\) becomes the threshold of a sufficient number of mediators to reconstruct the secret key.
-
-Next, both Alice and Bob, take their key shares, and encrypt each
-\textit{i}-th key share using public key of \textit{i}-th mediator. As a result
-Alice's secret \(x_A\) becomes \({c^A_1, c^A_2,...,c^A_n}\), and Bob's
-secret \(x_B\) becomes \({c^B_1, c^B_2,...,c^B_n}\), where
-\(c_i = E_{M_i}(P_i)\) is the encrypted \(i\)-th key share using
-\(i\)-th mediator public key \(M_i\).
-
-Next, both Alice and Bob exchange the sets of encrypted key shares with
-each other, and send funds to the escrow account.
-
-The escrow is secure as long as \(t+1\) of mediators does not collude,
-which would let them recreate both \(x_A\) and \(x_B\). To ensure
-that parties exchange actual key shares, they send witnesses
-generated with the Feldman VSS scheme and zero-knowledge proofs to guarantee the consistency between witnesses and key shares.
-
-In case of dispute, the decentralized network of mediators settle the conflict and grand one winning party, the other party secret key,
-letting him withdraw the funds.
-
-The monetary incentivization and reputation system guarantee the honesty of mediators.
-
-\subsection{Blockchain, anonymity, and physical delivery}\label{lelantos-a-blockchain-based-anonymous-physical-delivery-system}
-
-Lelantos~\cite{altawyLelantosBlockchainBasedAnonymous2017} is a blockchain-based anonymous
-physical delivery system.
-The protocol achieves anonymity by employing onion routing (similar to the Tor network) to connect physical delivery providers.
-The whole route from a merchant to a customer is split into multiple steps, and each step is undertaken by the different randomly selected delivery providers.
-As long as the delivery providers do not collude, a merchant neither can learn the identity nor destination address of the customer.
-
-Onchain smart-contract is used to coordinate the whole process and
-mediate communication between customers and delivery providers.
-
-However, since the system uses Ethereum, it achieves pseudonymity rather than anonymity (see section~\ref{sec:pseudo-anon}). Also, the protocol does not cover disputes between the parties.
-
-\subsection{Comparision}
-
-We considered only protocols that achieve fair exchange as it is the fundamental feature of such protocols.
-
-Bîrjoveanu, 2015~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} is the closest to our protocol, however it uses TTP and does not consider dispute between parties.
-
-Hinarejos et al., 2019~\cite{hinarejosSolutionSecureCertified2019} is the simplest protocol that replaces TTP with blockchain.
-However, it does not consider anonymity, dispute between parties nor physical material exchange.
-
-Meng et al., 2019~\cite{mengThemisDecentralizedEscrow2019} improves the previous protocol by the crownsource dispute resolution system. However it does not take anonimity into consideration.
-
-Altawy et al., 2017~\cite{altawyLelantosBlockchainBasedAnonymous2017} is a blockchain-based protocol that does not provide dispute resolution, but provides anonymous physical delivery by using onion routing and anonymous blockchain interaction assuming unlinkability between pseudonyms and real identities.
-
-Our protocol achieves stronger anonymity guarantees.
-Namely, we achieve anonimity by using either cash or privacy-preserving blockchains.
-Moreover, our protocol does not require a customer to submit any transaction to the message board, which may be the weakest link in the anonymity of aforementioned protocols.
-
-Our protocol does not use its own delivery system. We assume that there is a way to anonymously deliver a package either via SP's drop box, or trusted party.
-
-Also, our protocol does not provide its own dispute resolution mechanism as Themis does.
-However, we assume the existence of an abstract justice that accepts evidence and punishes the misbehaving party.
-It can be instantiated with either local court or police, or one of the blockchain
-dispute resolution services like Themis~\cite{mengThemisDecentralizedEscrow2019}, Kleros~\cite{bergollaKlerosSociolegalCase2022,gudkovCrowdArbitrationBlockchain2020}, Aragon Court\footnote{Aragon Court, Decentralized Dispute Resolution Protocol, https://aragon.org/aragon-court, (last visited Jan.
-10, 2023)}, LTO Network\footnote{LTO Network, 2019, https://lto.network/, (last visited Jan.
-17, 2023)}, and other Online Dispute Resolution platforms~\cite{allenGovernanceBlockchainDispute2019}.
-
-The comparision of the protocols is presented in table~\ref{tab:comparision}.
-
-\begin{table}
-  \newcommand{\YES}{\cellcolor{green!50}Yes}
-  \newcommand{\ID}{\cellcolor{green!25}Identity}
-  \newcommand{\PSEUDO}{\cellcolor{green!25}Pseudonym}
-  \newcommand{\ANON}{\cellcolor{green!50}Anonymity}
-  \newcommand{\NO}{\cellcolor{red!50}No}
-  \newcommand{\TTP}{\cellcolor{red!50}TTP}
-  \newcommand{\BC}{\cellcolor{green!50}BC}
-  \caption{Related work comparision}
-  \label{tab:comparision}
-  \setlength{\tabcolsep}{3pt}
-  \begin{tabular}{|p{40pt}|p{35pt}|p{40pt}|p{35pt}|p{30pt}|p{30pt}|}
-  \hline
-  Protocol & Fair exchange & Anonymity & Dispute resolution & Trust & Physical delivery \\
-  \hline
-  Bîrjoveanu, 2015~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} & \YES & \YES & \NO & \TTP & \YES \\
-  \hline
-  Hinarejos et al., 2019~\cite{hinarejosSolutionSecureCertified2019} & \YES & \NO & \NO & \BC & \NO \\
-  \hline
-  Themis~\cite{mengThemisDecentralizedEscrow2019} & \YES & \NO & \YES & \BC & \NO \\
-  \hline
-  Lelantos~\cite{altawyLelantosBlockchainBasedAnonymous2017} & \YES & \PSEUDO & \NO & \BC & \YES \\
-  \hline
-  This paper & \YES & \YES & \YES & \BC & \YES \\
-  \hline
-
-  \end{tabular}
-\end{table}
-
-\section{Building Blocks}\label{sec:building-blocks}
-\subsection{Dispute resolution system}
-
-Disputes are an inevitable part of all human transactions.
-Whether intentional or accidental, the system should prevent violation of agreed contract rules or local jurisdiction.
-The rules are specified by law and implemented by the police.
-
-The vision of smart contracts was to replace the legal contract with
-programmable and autonomous contracts.
-The smart contract code encompasses the contract's specifications, hence the slogan \textit{code as a law}.
-Moreover, smart contracts are automatically executed merging together the gap of law and its enforcment by police~\cite{allenGovernanceBlockchainDispute2019}.
-However, the blockchain paradigm has its limitations.
-
-Blockchain can assure the correctness of data existing only on the blockchain.
-The problem arises in the contact between blockchain and the real world, when we want the smart contract to decide based on some input from outside the blockchain.
-The technique of providing real-world data to the blockchain is called oracle.
-Oracle provides data based on a decentralized network of mediators; therefore, the trust is also decentralized~\cite{breidenbachChainlinkNextSteps2021}.
-
-Some oracles provide the data like weather, soccer match result, stock
-price, train delay, election results, others—and they are the ones we
-are interested in—provide the settlement of a submitted dispute.
-
-Themis~\cite{mengThemisDecentralizedEscrow2019} besides providing fair exchange protocol,
-also offers a semi-autonomous decentralized dispute resolution system that complies with the Web3 postulates of a decentralized web. Themis
-resolve disputes by a set of voluntary anonymous mediators participating
-in voting and deciding whether a party misbehaved. The honesty of
-mediators is achieved by the monetary incentivization and reputation
-system.
-
-Kleros~\cite{bergollaKlerosSociolegalCase2022} is a smart contract deployed on the Ethereum platform that mimics in a decentralized and autonomous way how the court works in real life.
-In Kleros, every process of a dispute like gathering evidence, selecting jurors, rewarding the winning party is automated by a set of smart contracts.
-Like Themis, the honesty of the agents voting in a case is achieved by game-theoretical economic incentives.
-
-Such a decentralized, voluntary, and anonymous dispute resolution system might work for simple contracts violations like an eBay seller sending broken or wrong products or an Airbnb apartment being inadequate to the photos in the offer.
-However, it is hard to realize such decentralized evaluation of heath or legal services quality when expertise and privacy concerns are taken into account.
-Therefore, in our protocol, we take the more conservative approach and resolve disputes using local
-justice system (police or court).
-
-Possible directions toward semi-autonomous decentralized resolution system are discussed in Section~\ref{sec:decentralised-justice}.
-
-\subsection{Fairness}\label{fairness}
-
-In case of dispute, the customer can prove to justice (police or court) convincing evidence for the honesty of the customer and misbehaviour of the SP. 
-Because the customer is anonymous, the SP can not start a dispute---there is no means to identify the customer.
-
-To mitigate the issue, we designed the protocol so that the SP who follows the protocol is always in an advantaged position; therefore, she has no reason to start a dispute.
-On the other hand, the customer can start a dispute at any time of the protocol, but only the actual misbehaviour of the SP makes him win the case.
-
-Abstracting from the services the SP is providing, each party should be able to prove its honest behaviour in case of a dispute.
-We introduce three proofs that should be disclosed to justice in case of a dispute:
-
-\begin{enumerate}
-    \item Proof of delivery ($\mathrm{PoD}$) is a confirmation issued by the SP to the customer that proves that the customer has delivered to the SP a complete (according to the SP requirements) package, and the SP accepted it.
-It consists of the current time, the deadline to pay for the transaction, the deadline to provide a result of the service, randomly generated number uniquely identifying the transaction, and the SP's signature guaranteeing non-repudiation.
-The formal definition of the $\mathrm{PoD}$ is presented in section ~\ref{proof-of-delivery}.
-
-    \item Payment $\mathrm{attestation}$ is confirmation that the customer has paid for the transaction at a certain time.
-The actual implementation depends on the particular cryptocurrency and is discussed further section~\ref{payment-for-services}.
-
-    \item Proof of provision ($\mathrm{PoP}$) is proof that the SP published the result at a certain time.
-It defends the SP in case the customer unjustly starts a dispute after the result has been published.
-It consists of a content identifier as specified in section ~\ref{storage-network}, the $\mathrm{nonce}$ uniquely identifying the transaction previously generated in $\mathrm{PoD}$, and the SP's signature guaranteeing authentication.
-The connection between $\mathrm{PoP}$ and the result is created by the content identifier ($\mathrm{cid}$) that uniquely identify the result (it is some kind of a hash of the result) such that the result can not be forged after the $\mathrm{PoP}$ has been published.
-\end{enumerate}
-
-\subsection{Message Board}\label{sec:message-board}
-The proof of provision that we coined for the purpose of this protocol is generally called the proof of existence~\cite{ProofExistenceOnline, crespoStamperyBlockchainTimestamping2017, ChainpointBlockchainProof}.
-
-The idea behind proof of existence is to certify that some information
-has existed at a certain moment, in such a way that nobody can
-undermine its existence, integrity, and ownership (also called the
-non-repudiation requirement).
-
-We need this functionality for two reasons: (1) communicate the existence of the result to the customer to whom the SP have no other communication medium as the customer stays anonymous; (2) let the SP to proof the publication of the result within the agreed with customer deadline.
-
-By publishing the $\mathrm{PoP}$ on the blockchain, the SP can not falsify the time at which the result has been provided because the block creation time proves that.
-Blockchain acts as a global clock that securely timestamps everything that gets into the block, so the $\mathrm{PoP}$ that was included in a block will be associated with the time when the block has been created.
-Moreover, since the blockchain is public, everyone (including justice) can be convinced that the SP indeed published the result at that time.
-
-Without such proof, there would be no other means to settle the conflict between the customer claiming the result has not been published and the SP claiming the result has been published within the deadline.
-
-Depending on the context the platform of achieving it is called bulletin board~\cite{achenbachImprovedCoercionresistantElectronic2015}, trusted timestamping~\cite{gippDecentralizedTrustedTimestamping2015}, or message board~\cite{hinarejosSolutionSecureCertified2019}.
-In this work, we call it a message board.
-
-We keep the protocol general enough to be implemented using any existing technology to provide message board service, assuming it is decentralized and supports subscribing for the upcoming proofs from a particular address.
-
-\subsection{Anonymity, pseudonomity, and confidentality}\label{sec:pseudo-anon}
-
-Privacy is a concept used in almost all social sciences like philosophy, psychology, sociology, and legal.
-The multidisciplinary nature leads to ambiguous definitions~\cite{smithInformationPrivacyResearch2011}.
-For our work, we rely on more concrete definitions, i.e.~confidentality and anonymity.
-
-Confidentiality is the ability to hide the details of an action from others.
-Alternatively, we can say that the system guarantees confidentiality if, for all observers, everything they can say about the action is the fact that it happened and nothing more.
-
-Anonymity is the ability to hide one identity from others.
-More precisely, the inability to correlate actions performed within the system with the user's identity.
-Alternatively, we can say that the system guarantees anonymity if, for all observers, the actions are equally likely to be associated with any user of the system.
-However, anonymity is a spectrum rather than a dichotomous classification.
-One method of quantifying the level of anonymity is \textit{k}-anonymity proposed in~\cite{sweeneyKanonymityModelProtecting2002}.
-It measures the user's anonymity by the number of other users from whom the user can not be distinguished.
-Concretely, the user is \textit{k}-anonymous if his actions are equally likely associated with \textit{k}-1 other users; the larger \textit{k}, the higher anonymity.
-
-Some anonymity techniques can be deployed on non-anonymous blockchains.
-The so-called mixers gather users into an \textit{anonymity set}, which then collude together to launder transactions in such a way that to an observer, the likelihood of the sender of each transaction is equiprobable for any user from the anonymity set.
-
-Some systems guarantee pseudonymity rather than anonymity.
-Pseudonymity allows users to hide their real identity behind the pseudonyms.
-Despite the whole system being transparent and allowing linking actions to pseudonyms, the system is considered anonymous as long as the link between pseudonyms and real identities is secret.
-This assumption is hard to satisfy in practice, as the KYC (Know Your Customer) and AML (Anti Money Laundering) regulations require users to reveal their real identity to cryptocurrencies exchanges, making the user's anonymity dependent on the security of the IT system.
-Moreover, some correlations can be inferred merely by the analysis of transactions \cite{androulakiEvaluatingUserPrivacy2013, oberStructureAnonymityBitcoin2013}.
-
-The figure ~\ref{fig:anonymity-diagram} ilustrate relations between these terms.
-
-\begin{figure}[h!]
-\includegraphics[width=9cm]{anonymity-diagram.png}
-\centering
-\caption{Let us assume Alice to be the customer willing to keep her identity anonymous and Bob to be the public SP.
-Alice controls two addresses, 1 and 2; the connection between her real identity and the first address has been compromised, and therefore the identification is possible; the connection between the second pseudonym is still unknown therefore anonymous.
-Alice takes two actions; the first one from the compromised address and the second one from the anonymous one.
-The first action is confidential; therefore, even though the pseudonym has been compromised, the action can not be associated with Alice.
-The second action is transparent; therefore, Alice maintain her anonymity as long as the connection to the second pseudonym is concealed.}
-
-\label{fig:anonymity-diagram}
-\end{figure}
-
-The privacy-preserving blockchains are the ones that maintain anonymity via untraceability and (ideally) unlikability, not via the assumption that the connection between an address (pseudonym) and the real identity is concealed.
-
-Examples of blockchains that natively support confidential transactions are: Monero~\cite{vansaberhagenCryptoNote2013} (via Ring Signatures~\cite{noetherRingSignatureConfidential2015} and Bulletproofs~\cite{moneroBulletproofsMoneropediaMonero, bunzBulletproofsShortProofs2018}), ZCash~\cite{ben-sassonZerocashDecentralizedAnonymous2014} (via zkSNARK~\cite{ben-sassonSNARKsVerifyingProgram2013}), and Grin~\cite{fuchsbauerAggregateCashSystems2019} (via Mimblewimble~\cite{jedusorMIMBLEWIMBLE2016}).
-
-Overly techniques that achieve anonymity on top of non-privacy-preserving blockchains are: Ethereum's Tornado Cash\cite{pertsevTornadoCashPrivacy2019} (via zkSNARK~\cite{grothSizePairingbasedNoninteractive2016} and MiMC~\cite{albrechtMiMCEfficientEncryption2016}), Bitcoin's Wasabi\footnote{Wasabi Wallet, Open-source, non-custodial Bitcoin Wallet for desktop, \url{https://wasabiwallet.io/}, (last visited Nov.
-28, 2022)} (via CoinJoin \cite{maxwellCoinJoinBitcoinPrivacy2013}).
-
-\subsection{Payment for services}\label{payment-for-services}
-Transactions between customers and SPs must be pegged to prevent proving one payment for multiple transactions. In other
-words, we need a mechanism that uniquely associates a payment with the corresponding transaction.
-
-Depending on a cryptocurrency, the link can be created in different
-ways:
-% continue reading from here
-\begin{itemize}
-
-\item separate address: each transaction derives a new address uniquely associated with the transaction.
-Such addresses can be derived using Hierarchical Deterministic Wallets (BIP-32)\footnote{Bitcoin Improvement Proposals,Hierarchical Deterministic Wallets, \url{https://github.com/bitcoin/bips/blob/master/bip-0032.mediawiki}, (last visited Dec.
-03, 2022)}.
-\item memo: the payments are sent to one SP account but contain an extra field named ``memo'' filled with the unique number provided by the SP in $\mathrm{PoD}$.
-Each payment containing such value in the memo is considered to pay for the transaction.
-In case of a dispute, revealing both the payment memo and the $\mathrm{PoD}$ proves the connection.
-\end{itemize}
-
-Both approaches have some advantages and disadvantages, but our protocol can abstract them away by treating them as some randomly generated unique number, often called \textit{nonce} (number once).
-The actual implementation depends on a particular blockchain.
-
-In case of a dispute, there must be a way to prove to the justice that the customer has paid for the transaction.
-As the proof of transaction is trivial in transparent and trackable blockchains, it gets more complicated when it comes to anonymous blockchains.
-Monero allows proving and checking payments via dedicated API \cite{MoneroHowProve}.
-ZCash provides a mechanism called Payment Disclosure \cite{daviesIntroductionPaymentDisclosure2017}.
-
-\subsection{Storage network}\label{storage-network}
-Once the SP finishes its service, she has to provide the result to the customer.
-The most natural approach would be to send the result via e-mail or some dedicated platform.
-However, since the customer wants to stay anonymous and so does not want to expose his e-mail address nor IP address.
-Moreover, the SP should prove that the result has been provided before the deadline, which brings us to the issue of proof of existence discussed in section ~\ref{sec:message-board}.
-
-One approach would be to post the result into a blockchain.
-However, storing data on a blockchain is very expensive.
-The most common workaround (\cite{shahidBlockchainBasedAgriFoodSupply2020, wangAuditableProtocolsFair2019, chenImprovedP2PFile2017}) is to publish the data on a content addressable peer-to-peer storage network like IPFS~\cite{benetIPFSContentAddressed2014}.
-Then, publish on the blockchain just the content identifier ($\mathrm{cid}$) that uniquely points to the content stored on IPFS.
-
-We take the same approach. Once the SP creates the result, she encrypts it using the previously provided encryption key and uploads it to the IPFS network.
-%TODO: write about DHKE encyption
-
-To increase anonymity, the customer should use standard techniques to hide its IP address, such as gateway, VPN, proxy, or onion routing.
-
-\subsection{Separation of concerns}
-We could use one blockchain to achieve all of these three roles: (i) anonymous payments, (ii) message board, (iii) storage network.
-
-While most blockchains could provide the message board functionality, anonymous payments are not as prevalent.
-Especially a provable storage network is a functionality of a few specialized blockchains.
-
-Instead of searching for one blockchain that provides all the functionalities, we allow the protocol to use separate blockchains for each role.
-If a suitable blockchain arises, it can play more than one role.
-
-At the time of writing, we see the following technologies that fulfil the requirements of each role:
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-
-\item Anonymous payments: Monero \cite{vansaberhagenCryptoNote2013}, ZCash
-  \cite{ben-sassonZerocashDecentralizedAnonymous2014}, Grin \cite{fuchsbauerAggregateCashSystems2019},
-  Tornado Cash \cite{pertsevTornadoCashPrivacy2019}.
-\item Message board: Stampery \cite{crespoStamperyBlockchainTimestamping2017}, Proof of Existence
-  \cite{ProofExistenceOnline} (Bitcoin blockchain), Chainpoint
-  \cite{ChainpointBlockchainProof} (Bitcoin blockchain), or any other blockchain that
-  supports attaching extra data along the transaction.
-\item Storage network: IPFS \cite{benetIPFSContentAddressed2014}, Filecoin
-  \cite{protocollabsFilecoinDecentralizedStorage2017}, or Ethereum's
-  Swarm\cite{teamSWARMStorageCommunication2021}.
-\end{enumerate}
-
-\section{The Protocol}\label{sec:protocol}
-In this section we propose an abstract protocol for anonymous service provisioning without any assumptions about the underlying technologies.
-We define the requirements for each role and leave the choice of the technology to the developer.
-Later in the paper (section~\ref{sec:experiments}) we describe our implementation used for conducting experiments.
-
-\subsection{Prerequisites}
-
-\begin{itemize}
-\item There exists PKI infrastructure:
-    \begin{itemize}
-        \item The customer and the SP have their key pairs consisting of secret key $\mathrm{sk}(\mathrm{party})$ and public key $\mathrm{pk}(\mathrm{party})$, where $\mathrm{party} \in \{\mathrm{C}, \mathrm{SP}\}$ for the customer and the SP.
-        \item Both the customer and the SP can create and verify digital signatures created by the customer $\mathrm{sig}_{\mathrm{sk}(\mathrm{C})}$ and the SP $\mathrm{sig}_{\mathrm{sk}(\mathrm{SP})}$.
-        \item The SP's public key $\mathrm{pk}(\mathrm{SP})$ is publicly known.
-    \end{itemize}
-
-\item Both the customer and the SP:
-    \begin{itemize}
-        \item use common symmetric encryption $\mathrm{E}_\mathrm{key}(\cdot)$ and decryption $\mathrm{D}_\mathrm{key}(\cdot)$ operations.
-        \item have access to anonymous payments blockchain, message board, and storage network.
-    \end{itemize}
-
-\item The SP:
-    \begin{itemize}
-        \item accepts packages from unknown customers.
-        \item accepts payments with anonymous cryptocurrencies as described in section~\ref{payment-for-services}.
-    \end{itemize}
-
-\item Justice:
-    \begin{itemize}
-        \item accepts as evidence in a dispute the $\mathrm{PoD}$, $\mathrm{PoP}$, and payment $\mathrm{attestation}$ as described in section~\ref{fairness}.
-    \end{itemize}
-
-\item Anonymous payments blockchain:
-    \begin{itemize}
-        \item supports anonymous, i.e., untraceable and (ideally) unlinkable transactions as specified in section~\ref{sec:pseudo-anon}.
-        \item supports uniquely identifying transaction either via separate address, memo field, or other similar mechanisms as described in section ~\ref{payment-for-services}. 
-    \end{itemize}
-
-\item Message Board:
-    \begin{itemize}
-        \item supports transactions of sizes up to $\mathrm{PoD}$ and $\mathrm{PoP}$.
-    \end{itemize}
-
-\item Storage network:
-    \begin{itemize}
-        \item allows for content retrieval via content identifier $\mathrm{cid}$ (usually a hash of the content).
-        \item allows for anonymous content retrieval.
-        \item guarantee that the content will be available for the duration of the agreement.
-    \end{itemize}
-\end{itemize}
-
-\subsection{Messages}\label{messages}
-In this section, we describe the messages exchanged between the parties of the protocol.
-
-\vspace{5mm}
-
-\noindent \textbf
-{Package}\label{package} is a physical container prepared by the customer encompassing all $\mathrm{materials}$ required by the SP to provide the service, randomly generated provision identifier used to anonymously track the provision throughout the protocol's steps, and the customer's public key $\mathrm{pk(C)}$ used to encrypt the result published on the public storage network.
-
-$$\mathrm{pkg} \equiv (\mathrm{materials}, \mathrm{provisionID}, \mathrm{pk(C)})$$
-
-where:
-
-\begin{itemize}
-
-\item $\mathrm{materials}$ - are the materials required to provide the service, for example, samples of urine, blood, stool, saliva; legal documents, CDs, emails, photos, bank statements; or any other kind of materials depending on the service.
-\item $\mathrm{provisionID}$ - a randomly generated provision identifier, used to anonymously track the provision throughout the protocol's steps.
-\item $\mathrm{pk(C)}$ - customer's public key used to encrypt the result published on the public storage network.
-\end{itemize}
-
-\noindent \textbf
-{Proof of delivery ($\mathrm{PoD}$)}\label{proof-of-delivery} is an attestation to the fact that the customer has delivered a correct (according to the SP requirements) package to the SP, and the SP has accepted it.
-
-It is also an agreement between the customer and the SP, as it includes agreed upfront deadlines of actions, and a payment method.
-
-$\mathrm{PoD}$ is published on the message board by the SP.
-
-\begin{eqnarray}
-\mathrm{PoD} & \equiv & (\begin{array}[t]{l}\mathrm{T}_\mathrm{issue}, \mathrm{T}_\mathrm{pay}, \mathrm{T}_\mathrm{provide},\\ \mathrm{address}, \mathrm{provisionID}, \mathrm{pk(C)}, \mathrm{sig}_\mathrm{SP} \; )\end{array}
-\end{eqnarray}
-
-% \begin{eqnarray}
-%   \quad L_{\mathrm{H}}(H) & \equiv & (\begin{array}[t]{l}H_{\mathrm{p}}, H_{\mathrm{o}}, H_{\mathrm{c}}, H_{\mathrm{r}}, H_{\mathrm{t}}, H_{\mathrm{e}}, H_{\mathrm{b}}, H_{\mathrm{d}},\\ H_{\mathrm{i}}, H_{\mathrm{l}}, H_{\mathrm{g}}, H_{\mathrm{s}}, H_{\mathrm{x}}, H_{\mathrm{m}}, H_{\mathrm{n}} \; )\end{array} \\
-%   \quad L_{\mathrm{B}}(B) & \equiv & \big( L_{\mathrm{H}}(B_{\mathrm{H}}), \widetilde{L}_{\mathrm{T}}^*(B_{\mathbf{T}}), L_{\mathrm{H}}^*(\hyperlink{ommer_block_headers_B__U}{B_{\mathbf{U}}}) \big)
-%   \end{eqnarray}
-
-where:
-
-\begin{itemize}
-
-\item $\mathrm{T}_\mathrm{issue}$ - time at which the $\mathrm{PoD}$ is issued.
-\item
-  $\mathrm{T}_\mathrm{pay}$ - deadline to pay for the transaction.
-\item
-  $\mathrm{T}_\mathrm{provide}$ - deadline to provide a result of the service.
-\item $\mathrm{address}$ - payment address of the SP's anonymous blockchain account.
-\item $\mathrm{provisionID}$ - the number uniquely identifying the transaction previously generated by the customer.
-\item $\mathrm{pk(C)}$ - customer's public key used to encrypt the result published on the public storage network.
-\item $\mathrm{sig}_\mathrm{SP}$ - the SP's signature guaranteeing non-repudiation.
-\end{itemize}
-
-also:
-\(\mathrm{T}_\mathrm{issue} < \mathrm{T}_\mathrm{pay} < \mathrm{T}_\mathrm{provide}\)
-
-\noindent \textbf
-{Proof of provision ($\mathrm{PoP}$)}\label{proof-of-provision} is proof that the SP published the result at a certain time.
-It protects the SP in case the customer unjustly starts a dispute after the result has been published.
-The connection between $\mathrm{PoP}$ and the result is made by the content identifier ($\mathrm{cid}$) uniquely identifing the result such that the result can not be forged after the $\mathrm{PoP}$ has been published.
-
-$\mathrm{PoP}$ is published on the message board by the SP.
-
-\begin{eqnarray}
-\mathrm{PoP} & \equiv & (\mathrm{cid}, \mathrm{provisionID}, \mathrm{sig}_\mathrm{SP})
-\end{eqnarray}
-
-where:
-
-\begin{itemize}
-
-\item $\mathrm{cid}$ - content identifier as specified in section~\ref{storage-network}.
-\item $\mathrm{provisionID}$ - the number uniquely identifying the transaction previously generated by the customer.
-\item $\mathrm{sig}_\mathrm{SP}$ - the SP's signature guaranteeing non-repudiation.
-\end{itemize}
-
-\noindent \textbf
-{Payment attestation}\label{payment-attestation} proves that the customer did the payment.
-Since the evidence depends on a particular blockchain (see section ~\ref{payment-for-services}), we refer to it symbolically as
-\(\mathrm{attestation}\).
-
-\noindent \textbf
-{Result}\label{results} is assumed to be a document in PDF format, but any other format is allowed as long as it can be binary encoded and uploaded to sotrage network.
-We refer to it symbolically as $\mathrm{result}$.
-
-\noindent \textbf
-{Content Identifier (cid)}\label{content-identifier-cid} is a term coined by IPFS\footnote{IPFS, Content addressing and CIDs, \url{https://docs.ipfs.tech/concepts/content-addressing}, (last visited Dec.
-01, 2022)}.
-However, since our protocol does not depend on this particular implementation of the storage network, we let the $\mathrm{cid}$ be any other identifier that securely and uniquely points to the content.
-
-\subsection{Protocol description}\label{protocol-description}
-
-In this section, we describe each step of the protocol, also shown in the figure~\ref{fig:protocol-diagram}.
-
-\begin{figure}[h!]
-\includegraphics[width=\linewidth]{anonser-protocol.png}
-\centering
-\caption{Messages exchanged in the protocol.}
-\label{fig:protocol-diagram}
-\end{figure}
-
-\noindent \textbf
-{Step 0.  Preparation}\label{step-0-preparation}
-
-The customer collects all the $\mathrm{materials}$ required by the SP, generates a random $\mathrm{provisionID}$ and a random keypair $(\mathrm{sk(C)},\mathrm{pk(C)})$.
-The $\mathrm{provisionID}$ will be used to associate all actions related to the transaction throughout the protocol.
-The $\mathrm{provisionID}$ and $\mathrm{pk(C)}$ are encoded as a QR code, printed, and sticked to the package $\mathrm{pkg}$.
-The $\mathrm{sk(C)}$ is kept secret and used to decrypt the $\mathrm{result}$ at the end of the protocol.
-
-\noindent \textbf
-{Step 1. Package delivery}\label{step-1-package-delivery}
-
-The protocol starts once the customer delivers package $\mathrm{pkg}$ to the SP and its content gets accepted.
-As a result, $\mathrm{PoD}$ is created with predefined payment deadline $\mathrm{T}_\mathrm{pay}$, service provision deadline $\mathrm{T}_\mathrm{provide}$, and current time $\mathrm{T}_\mathrm{issue}$.
-Also $\mathrm{PoD}$ embodies the information whether the service has been paid in cash or should be paid by the customer using the anonymous blockchain account.
-In the latter case, the SP's payment $\mathrm{address}$ is included in the $\mathrm{PoD}$.
-
-The digital signature $\mathrm{sig}_{\mathrm{sk}(\mathrm{SP})}$ on the $\mathrm{PoD}$ created with the SP's secret key $\mathrm{sk}(\mathrm{SP})$ guarantee non-repudiation.
-
-Symbolically: 
-\[
-\mathrm{PoD \gets delivery(pkg)}
-\]
-
-\noindent \textbf
-{Step 2. Proof of Delivery}\label{step-2-pod}
-
-Then, the $\mathrm{PoD}$ is published on the message board by the SP, commiting to the fact that the package $\mathrm{pkg}$ has been delivered, adn the SP can not reject receiving it.
-If the provision has not been paid in cash, the SP waits for the customer to pay for the service on the specified in the $\mathrm{PoD}$ payment $\mathrm{address}$.
-
-Symbolically: 
-\[
-\mathrm{publish(PoD)}
-\]
-
-\noindent \textbf
-{Step 3. Get Proof of Delivery}\label{step-3-get-pod}
-
-Once the package is delivered and the $\mathrm{PoD}$ is published, the customer can get the $\mathrm{PoD}$ from the message board and (if everything is correct) proceed with the protocol.
-
-Symbolically: 
-\[
-\mathrm{PoD \gets get(provisionID)}
-\]
-
-\noindent \textbf
-{Step 4. Payment}\label{step-4-payment}
-
-If the provision has not been paid in cash, the customer should pay for the transaction with the predefined anonymous payment blockchain (see section~\ref{payment-for-services}).
-
-In return, the customer receives the $\mathrm{attestation}$ that should be disclosed in case of a dispute.
-
-Symbolically: 
-\[
-\mathrm{attestation \gets payment(address)}
-\]
-
-\noindent \textbf
-{Step 5. Provision of service}\label{step-5-provision-of-service}
-
-Once the customer has paid for the transaction either in cash or using the anonymous blockchain, the SP can start providing the service.
-
-Symbolically: 
-\[
-\mathrm{result \gets provision(materials)}
-\]
-
-\noindent \textbf
-{Step 6. Upload result}\label{step-6-upload-result}
-
-After the service is finished, a result should be created. 
-Next, the result is encrypted using shared key derived from the customer's public key $\mathrm{pk(C)}$ and the SP's secret key $\mathrm{sk(S)}$ using Diffie-Hellman key exchange (DHKE) method.
-
-The encrypted result is then uploaded on the content addressable network (such as IPFS). In return the content identifier ($\mathrm{cid}$) is created.
-
-Symbolically: 
-\[
-\mathrm{cid \gets upload(E_{DHKE(sk(SP), pk(C))}(result))}
-\]
-
-\noindent \textbf
-{Step 7. Proof of provision}\label{step-7-proof-of-provision}
-
-When the $\mathrm{result}$ is uploaded, the SP creates and publish on a message board a proof of provision consisting of $\mathrm{cid}$ along with $\mathrm{provisionID}$ and signature $\mathrm{sig}_\mathrm{SP}$.
-
-Symbolically: 
-\[
-\mathrm{publish(PoP)}
-\]
-
-\noindent \textbf
-{Step 8. Get Proof of Provision}\label{step-8-get-proof-of-provision}
-
-After delivering the package and paying for the transaction, the customer start listening to the message board and waits until the SP publishes the $\mathrm{PoP}$ for the $\mathrm{provisionID}$.
-
-Symbolically: 
-\[
-\mathrm{cid \gets get(provisionID)}
-\]
-
-\noindent \textbf
-{Step 9. Download result}\label{step-9-download-result}
-
-Having the $\mathrm{cid}$, the customer downloads and decrypts the $\mathrm{result}$ using shared key derived from the customer's secret key $\mathrm{sk(C)}$ and the SP's public key $\mathrm{pk(S)}$ using DHKE method.
-The protocol ends.
-
-Symbolically: 
-\[
-\mathrm{result \gets D_{DHKE(sk(C), pk(SP))}(download(cid))}
-\]
-
-\section{Fairness analysis}\label{sec:fairness-analysis}
-We analyze the fairness of the protocol by representing it as an interactive non-cooperative game.
-
-\subsection{Model}\label{sec:fairness-model}
-We consider three positions:
-
-\begin{itemize}
-\item Neutral position (•): when a party has not spent nor gained anything of significant value (money, time, effort). For example, at the beginning of the protocol.
-\item Disadvantaged position (-): when a party has put a significant value without receiving an equivalent. For example, the customer has paid for a service in advance.
-\item Advantaged position (+): when a party would benefit if the transaction would halt at that step. For example, the SP has received payment before service provision.
-\end{itemize}
-
-There are many actions that each party can take, but we group them into two categories:
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-
-\item Normal: taking actions prescribed by the protocol.
-\item Abnormal: everything that deviates from the designed steps of the protocol. For example, sending an arbitrary message, skipping or repeating steps, timing out.
-\end{enumerate}
-
-Moreover, at any step of the protocol, the customer can start a dispute; therefore, another dimension with two positions has to be considered:
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-
-\item Agree: the customer agrees with the action and therefore does not start a dispute.
-\item Start a dispute: the customer disagrees with the action and therefore starts a dispute.
-\end{enumerate}
-
-As a result, in our analysis, we have to consider four different outcomes for each party of the protocol ($\mathrm{party \in \{c, s}\}$), for each step of the protocol ($\mathrm{step \in 1..9}$):
-
-\begin{itemize}
-
-\item
-  $\mathrm{\sigma_{step,party,n}}$: after following the protocol when the other party acted normally.
-\item
-  $\mathrm{\sigma_{step,party,d}}$: after a settled dispute when the other party acted normally.
-\item
-  $\mathrm{\sigma_{step,party,\overline{n}}}$: after not starting a dispute despite the other party has acted abnormally.
-\item
-  $\mathrm{\sigma_{step,party,\overline{d}}}$: after a settled dispute when the other party has acted abnormally.
-\end{itemize}
-
-The protocol terminates after the last step, after starting a dispute, or after a party has not completed its designated action in time.
-Therefore, all positions except $\mathrm{\sigma_n}$ are termination positions.
-
-Because the customer is anonymous, the SP can not start a dispute—there is no means to identify the customer.
-To mitigate the issue, we designed the protocol so that the SP who follows the protocol is always in an advantaged position, and therefore has no reason to start a dispute.
-On the other hand, the customer can start a dispute at any time of the protocol, but only the actual misbehaviour of the SP makes him win the case.
-
-\begin{definition}[Fairness] \label{def:fairness}
-A protocol achieve fariness iff 
-\begin{equation*}
-\begin{split}
-\forall_{party \in parties}\forall_{\mathrm{step} \in \mathrm{steps}} &\operatorname{can\ move}\\
-&\operatorname{to\ the\ non-disadvantaged\ position} 
-\end{split}
-\end{equation*}
-
-\end{definition}
-
-\subsection{Assumptions}\label{sec:assumptions}
-
-Below we listed assumptions we took for the analysis purpose.
-
-\begin{enumerate}
-\item Both parties start from a neutral position $\neutral$.
-\item After completing a transaction, both parties end up in advantaged positions (\plus{}). In other words, they have intrinsic motivation to initialize and complete the transaction.
-\item The protocol steps are atomic—there are no intermediate steps.
-\item The protocol can go only forward—there is no way of reverting any action.
-\item Repeating the first step starts a new transaction.
-Repeating any other step is considered abnormal and gets ignored.
-For example, paying for the invoice twice does not cause any effect on the curse of the protocol.
-\item Once published, the result is available to the customer on the storage network. The idea of guaranteeing it cryptographically is discussed in section~\ref{sec:discussion}.
-\item Winning the dispute leads to a neutral position ($\neutral$).
-\item Losing the dispute leads to a punishment greater than any reward, leading to a disadvantaged position (\minus{}).
-Hence, the rational customer will not start a dispute that he is unsure of winning.
-\item Both the customer and the SP are rational (selfish).
-They always prefer to go from the worst position (\minus{} or $\neutral${}) to a better position ($\neutral$ or \plus), but also risk a temporary worst position in favour of a later better position if and only if at any time they can get out of the worst position; in particular, at any time the customer can start a dispute and, if the SP has misbehaved, get out of disadvantaged position (\minus) to the neutral position ($\neutral$).
-\end{enumerate}
-
-\subsection{Steps}\label{sec:steps}
-
-Figure~\ref{fig:positions} shows the positions of each party after each possible action taken.
-
-\begin{figure}[h!]
-\includegraphics[width=9cm]{formal-table-of-positions.png}
-\centering
-\caption{Positions after each step of protocol}
-\label{fig:positions}
-\end{figure}
-
-The description of each step and the rationale of the outcome position is given in the Appendix~\ref{app:proof-of-fairness}.
-
-\subsection{Example scenarios}\label{example-scenarios}
-
-The figure~\ref{fig:misbehaviour} shows the transitions of positions when the SP tries to misbehave and does not execute service after receiving the payment.
-The customer reacts by starting a dispute and the protocol ends up neutral to the customer and disadvantaged to the SP positions.
-
-\begin{figure}[h!]
-\includegraphics[width=9cm]{formal-misbehaviour-path.png}
-\centering
-\caption{Transitions of positions where the SP is misbehaving and the customer starts a dispute}
-\label{fig:misbehaviour}
-\end{figure}
-
-Ultimately, the rational path for both parties is to follow the protocol as shown in the figure~\ref{fig:rational}.
-
-\begin{figure}[h!]
-\includegraphics[width=9cm]{formal-rational-path.png}
-\centering
-\caption{Transitions of positions where where both the customer and the SP are behaving correctly}
-\label{fig:rational}
-\end{figure}
-
-Using the fariness definition~\ref{def:fairness} and the assumptions stated in Section~\ref{sec:assumptions}, our analysis indicates that the protocol achieves fairness.
-
-\section{Experiments}\label{sec:experiments}
-
-\subsection*{Setup}
-
-We have developed a prototype of our protocol using the following technologies:
-
-\begin{itemize}
-  \item{Anonymous payments} — we use the Monero blockchain \cite{noetherRingSignatureConfidential2015}.
-  \item{Storage netowork} — we use the Powergate\footnote{Powergate, \url{https://github.com/textileio/powergate}, (last visited Dec. 20, 2022)}, which is a wrapper around Filecoin and IPFS.
-  \item{Message board} — we use the Ethereum blockchain \cite{woodEthereumSecureDecentralised2014}; concretely, Truffle Ganache\footnote{Truffle Ganache, \url{https://trufflesuite.com/ganache/}, (last visited Dec.
-20, 2022)} and Solidity language.
-  \item{Customer and SP} — we create client side web application (webapp) using \texttt{React}\footnote{React, A JavaScript library for building user interfaces, \url{https://reactjs.org}, (last visited Dec.
-20, 2022)} for creating UI, and \texttt{web3.js}\footnote{web3.js, A JavaScript library for building on Ethereum, \url{https://web3js.org}, (last visited Dec.
-20, 2022)} for interaction with Ethereum.
-We use \texttt{MetaMask}\footnote{MetaMask, A crypto wallet \& gateway to blockchain apps, \url{https://metamask.io}, (last visited Dec.
-20, 2022)} browser extension for signing and submiting transactions to Ethereum's node.
-We use \texttt{monerod}\footnote{Monero, The Monero daemon \texttt{monerod}, \url{https://monerodocs.org/interacting/monerod-reference/}, (last visited Dec.
-20, 2022)} network client and \texttt{monero-wallet-cli}\footnote{Monero, The CLI client for Monero, \url{https://monerodocs.org/interacting/monero-wallet-cli-reference/}, (last visited Dec.
-20, 2022)} command-line interface for interacting with Monero blockchain.
-\end{itemize}
-
-The prototype is available at \url{https://anonser.stan.bar}. The source code is available at \url{https://github.com/stanbar/anonymous-provision-of-services-via-blockchain}.
-
-We developed and tested our prototype in the following environment:
-
-\begin{itemize}
-  \item{OS} — Arch Linux 5.11.8
-  \item{Docker} — 20.10.5
-  \item{CPU} — Intel(R) Core(TM) i7-4790 (8) 4.00~GHz
-  \item{RAM} — 16 GB DDR3
-  \item{Storage} — Samsung PM85 256~GB SSD
-
-  \item{monerod and monero-wallet-cli} — v0.18.1.2
-  \item{Powergate} — v2.6.2
-  \item{Ganache} — v7.5.0
-  \item{Solidity} — v0.8.17
-  \item{ReactJS} — v18.0.25
-  \item{web3.js} — v1.8.1
-  \item{crypto-js} — v4.1.1
-\end{itemize}
-
-For simplicity, all components run on one, mentioned above, physical machine; and all processes are managed by Docker.
-
-Moreover, Powergate is configured to use local Filecoin and IPFS networks.
-For Ethereum blockchain we use Truffle Ganache, which is a local Ethereum blockchain for development and testing purposes. 
-Monero is configured to use the public stage network.
-We assume service provider offers only one type of service, which is offered for a fixed public price, hence we omit the type of service and price from the protocol.
-
-\subsection*{Preparation}
-
-Both the customer and the SP create a Monero wallets using \texttt{monero-wallet-cli} command-line tool.
-
-Service provider deploys the smart contract using the \texttt{truffle migrate --network development} command, which deploys the smart contract to the Ethereum blockchain.
-The webapp is configured to use the latest deployed smart contract address.
-
-Customer gets some testing Monero funds using \url{https://community.rino.io/faucet/stagenet/} faucet service.
-
-Next, the customer enable per-transaction proof generation (payment \texttt{attestation}) by setting \texttt{set store-tx-info 1} for his wallet.
-The proof generation is required to verify the payment in case of dispute.
-
-At this point both the customer and the SP are ready to start the protocol.
-
-\subsection*{Experiment}
-
-The customer and the SP are two different users of our prototype, but for simplicity they use the same machine and the same web application.
-
-Now we describe the experiments we performed to test our protocol.
-
-\begin{figure*}[ht]
-  \begin{center}
-  \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{anonser-experiment1.pdf}
-  \end{center}
-\end{figure*}
-\begin{figure*}[ht]
-  \begin{center}
-  \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{anonser-experiment2.pdf}
-  \end{center}
-\end{figure*}
-
-\begin{enumerate}
-  \setcounter{enumi}{0}
-  \item[0.] The protocol starts with the customer opening the webapp and creating new provision. 
-The app generates random ECDSA (secp256k1) customer's keypair and random 32 bytes provisionID, then display QR code that encodes both the provisionID and the customer's public key. 
-The customer's private key must be downloaded and provided later for the decryption of the results.
-
-  \item[1.] The customer prints the QR code, stick it on a package, and delivers the package to the SP either: in person, via trusted party, or delivery agency.
-
-  \item[2.1.] The SP opens the app, scans the QR code decoding the provisionID and the client's public key.
-
-  \item[2.2.] Since (in this experiment) the provision has not been paid in cash, the SP generate unique Monero payment address using \texttt{monero-wallet-cli integrated\_address} 
-  \item[2.3.] The SP submits the proof of delivery to the Ethereum blockchain using MetaMask interface.
-
-  % monero-wallet-cli --stagenet --wallet-file sp --password "" integrated_address
-  % Random payment ID: <2b6d65d7d48b7896>
-  % Matching integrated address: 5LHmrsVsQM2Q2TgqufX4A5gKPpxy1czHULDyVc84omvnh1nQLVmqXk4VBuy8WnX1AXfKxDx7xuASAc6svkZqGVkL1XkUBWT7QejHymEaYM
-  \item[3.] The customer (using the webapp) check the transaction status on the Ethereum blockchain invoking \texttt{getProvision} with arguments \texttt{customerPubKey} and \texttt{provisionID}.
-  % monero-wallet-cli --stagenet --wallet-file customer --password "" transfer 5LHmrsVsQM2Q2TgqufX4A5gKPpxy1czHULDyVc84omvnh1nQLVmqXk4VBuy8WnX1AXfKxDx7xuASAc6svkZqGVkL1XkUBWT7QejHymEaYM 1
-  % Transaction successfully submitted, transaction <7d89c04de458cfb76a811d5eb325075dec59f7a993c3bf7ce37f9e3a1630af65>
-  % monero-wallet-cli --stagenet --wallet-file customer --password "" get_tx_key 7d89c04de458cfb76a811d5eb325075dec59f7a993c3bf7ce37f9e3a1630af65
-  % Tx key: 1364dc848a752bf52011f4a63d98bcb16091cacd985713b6b5264b3ede6de40f
-
-  \item[4.] The customer (using the \texttt{monero-wallet-cli transfer}) sends the payment to the designated in the smart contract \texttt{paymentAddress} and stores the payment attestation (using \texttt{monero-wallet-cli get\_tex\_key <tx-id>}) in case of dispute.
-
-  \item[5.] Once SP notice the payment on Monero blockchain it starts providing the service and outputs the file \texttt{result.pdf}.
-
-  \item[6.] The SP uploads the file \texttt{result.pdf} on the Filecoin and IPFS networks using Powergate.
-In result, the SP gets the content identifier \texttt{cid}, and \texttt{dealID} and \texttt{minerID}.
-
-  \item[7.] The SP submits a Proof of Provision transaction to the Ethereum blockchain by invoking \texttt{proofOfProvision} with arguments \texttt{customer\-PubKey}, \texttt{provisionID}, \texttt{cid}, and \texttt{dealID}.
-
-  \item[8.] Meantime, the Customer subscribes to the Ethereum and waits until the SP publishes the Proof Of Provision.
- Once the Proof Of Provision is published the Customer downloads the result using either: IPFS network via \texttt{https://dweb.link/<cid>} or Lotus network using \texttt{lotus retreive <cid> <minerID>}.
-
-  \item[9.] Results are then decrypted using previously stored customer's private key.
-If everything is correct, the Customer is satisfied with the service and the protocol ends, otherwise the Customer can initiate a dispute.
-
-\end{enumerate}
-
-\subsection{Results}
-
-\paragraph{Fariness}
-As showed in Section~\ref{sec:steps} and Appendix~\ref{app:proof-of-fairness}, the protocol is fair.
-It is achieved by a undeniable hand-shake mechanism in which the SP first publishes $\mathrm{PoD}$ (step 2.) commiting to package delivery and deadlines of the service, and then the customer accepts it by paying for the service or not (step 3.).
-
-Once the payment is made, the SP stays in the advantaged position.
-Since he has agreed on the deadlines of the provision of the service, he is incentivised to provide the serice and publish the resutlts and PoP before the deadline (step 7.); because otherwise the customer—having all the evidences—can initiate a dispute and punish the SP, therefore rational parties will follow the protocol.
-
-Non-repudiation without TTP is achieved by using the blockchain and digital signatures.
-Blockchain guarantees that each change to the state of the smart contract is visible to everyone and only the SP is allowed to modify its state.
-
-\paragraph{Provable Results Availability}
-Content addressable networks such as IPFS can not guarantee the availability of the content\footnote{Nothing prevents the SP from publishing the result, receiving the $\mathrm{cid}$, publishing $\mathrm{PoP}$, and immediately after removing the result from the local storage.
-In case of dispute, the SP can upload the content again, proving its availability.
-The SP has no motivation to proceed with this kind of misbehaviour other than putting the customer in a disadvantaged position caused by the lost dispute.}.
-However, the Filecoin network, which works as an incentivisation layer on top of IPFS, increases the content availability via economic incentivisations (i.e., punishment in case of lack of proof of storage of the content)~\cite{protocollabsFilecoinDecentralizedStorage2017}.
-
-The SP uploads the result on both IPFS and Filecoin networks (via Powergate) making the result available even in case of the SP stop serving the result from his node.
-
-\paragraph{Anonymity}
-We achieved anonymity by using anonymous payment methods such as cash or privacy-preserving payment blockchains (e.g.
-Monero), and decentralised storage networks like IPFS and Filecoin, allowing the customer to interact with the protocol without revealing his identity at any step of the protocol.
-
-\paragraph{Costs}
-Deploying smart contract consumed 1456577 gas.
-Proof of delivery consumed 129649 gas.
-Proof of provision consumed 149130 gas.
-The price of gas at the time of the experiment (Jan.
-03, 2023) was $0.000000002227 \frac{\mathrm{ETH}}{\mathrm gas}$\footnote{Etherscan, Ethereum Gas Tracker, \url{https://etherscan.io/gastracker}, (last visited Jan.
-03, 2023)}, and the price of 1 $\mathrm{ETH}$ was $1261.97 \mathrm{USD}$.
-In result, the cost of 
-\begin{itemize}
-  \item deploying the smart contract was $0.000000002227 \frac{\mathrm{ETH}}{\mathrm gas} \cdot 1456577 \mathrm{gas} \cdot 1261.97 \frac{\mathrm{USD}}{\mathrm{ETH}} = 4.09 \mathrm{USD}$; 
-  \item Proof of delivery was $0.000000002227 \mathrm{\frac{ETH}{gas}} \cdot 129649 \mathrm{gas} \cdot 1261.97 \frac{\mathrm{USD}}{\mathrm{ETH}} = 0.29 \mathrm{USD}$; 
-  \item Proof of provision was $0.000000002227 \mathrm{\frac{ETH}{gas}} \cdot 149130 \mathrm{gas} \cdot 1261.97 \frac{\mathrm{USD}}{\mathrm{ETH}} = 0.33 \mathrm{USD}$.
-\end{itemize}
-
-\section{Discussion}
-\label{sec:discussion}
-
-\subsection{Justice}\label{sec:decentralised-justice}
-
-Centralised justice is the biggest obstacle in achieving a system that complies with Web 3.0 postulates\footnote{Web3, \url{https://en.wikipedia.org/wiki/Web3}, (last visited Jan. 05, 2023)}.
-
-The possible directions for mitigation of such issues are to either (i) replace local justice with blockchain dispute resolution systems like proposed in Themis~\cite{mengThemisDecentralizedEscrow2019}, Kleros~\cite{bergollaKlerosSociolegalCase2022,gudkovCrowdArbitrationBlockchain2020}, Aragon Court\footnote{Aragon Court, Decentralized Dispute Resolution Protocol, https://aragon.org/aragon-court, (last visited Jan.
-10, 2023)}, LTO Network\footnote{LTO Network, 2019, https://lto.network/, (last visited Jan.
-17, 2023)}, and other Online Dispute Resolution platforms~\cite{allenGovernanceBlockchainDispute2019}; or (ii) make it infeasible to provide incorrect results.
-
-The first approach is more feasible in the near future.
-It would require creating a large set of experts in a field that, in case of dispute, would receive all the proofs ($\mathrm{PoD}$, $\mathrm{PoP}$, payment $\mathrm{attestation}$ as well as any other proofs significant to the case) that could be queried by the experts in zero-knowledge fashion, i.e., they could ask a limited number of questions to the proofs and getting yes/no answers.
-The case would be fully confidential as they would not be able to query personal information.
-The experts would be incentivized to participate in the pool by the system of fees.
-They would be incentivized to vote honesty by the stake they would have to lock and reward/punishment they would get by judging correctly/incorrectly, where the correctness is determined by the quorum of votes.
-
-The second approach is more futuristic.
-Suppose that the service we are undertaking is fully computable.
-Then, it would be possible by employing proofs of correctness of computations~\cite{ben-sassonSNARKsVerifyingProgram2013} to enforce that only correct computations (hence correct services) are accepted.
-It would require the complete service examination to be computable, which is hard to achieve in settings where physical materials (like blood) are examined.
-Concretely, the problem canes down to ``How to represent blood digitally?''.
-If we could represent urine, blood, saliva, or any other physical material in a binary format and let the customer take a sample, discrete it, and send it to the SP, then the whole chain of integrity could be ensured.
-Therefore, incorrect service provision would be infeasible, and hence, disputes would be avoided.
-
-\subsection{Self-sovereign identities}
-Our research in the field showed that some jurisdictions require SPs to associate the diagnosis with the customer personal information.
-For example, in Poland all laboratories performing medical diagnostic tests, and collecting the material (except tests for HIV) are obligated to the unambiguous identification and verification of the identity of the patient from whom the material was collected~\footnote{Regulation of the Minister of Health of March 23, 2006 on quality standards for medical diagnostic and microbiological laboratories, \url{https://isap.sejm.gov.pl/isap.nsf/DocDetails.xsp?id=WDU20060610435}}.
-
-This conflicts with the main goal of our protocol, which is to prevent any identification information from being collected.
-
-One promising solution would be to use Self-sovereign identities (SSI)~\cite{muhleSurveyEssentialComponents2018}, especially the verifable claims.
-A trusted authority (e.g., a government) would issue a one-time claim for a customer that would be accepted by the SP as a legitimate personal identificator.
-The SP would associate the diagnosis result with the provided DID.
-The DID itself would not contain any personal information, therefore the SP would learn nothing about the customer identity besides the random-looking identificator.
-The DID could be deanonimised by the collaboration with the government.
-
-However, since SSI is relatively new technology and the government has not yet adopted it, we decided to postpone the discussion of this topic to the future work.
-
-\subsection{Anonymous delivery}\label{anonymous-delivery}
-
-We assumed the customer to deliver the package to the SP personally or via a trusted person.
-However, the system could be extended to support an anonymous delivery system as proposed in Lelantos~\cite{altawyLelantosBlockchainBasedAnonymous2017}.
-One modification to the protocol would be to publish $\mathrm{PoD}$ on the message board, similarly to $\mathrm{PoP}$.
-
-\section{Conclusions}\label{sec:conclusion}
-In this paper, we have proposed the protocol for service provision that simultaneously achieves anonymity, fairness, dispute resolution, TTP-less, and support physical materials.
-The protocol can be employed to provide services without collecting any personal information.
-Payments are handled by anonymous cryptocurrencies.
-The result of the service is published on a content-addressable p2p network like IPFS.
-The dispute can be settled by disclosing the collected proofs to justice.
-Using the definition~\ref{def:fairness} we showed that the protocol achieves fairness by the proof of delivery, payment attestation, and proof of provision published on the message board blockchain.
-Finally, we pinpointed further improvements like decentralized dispute resolution, provable availability of the result, paying with cash, and anonymous package delivery via courier.
-
-\appendices
-
-\section{Proof of fairness}\label{app:proof-of-fairness}
-Below we describe each step and rationale of the outcome position.
-We use the notation introduced in Section~\ref{sec:fairness-model} to analise each position in the protocol and fariness Definition~\ref{def:fairness} to show the fairness of the protocol.
-
-\newcommand{\AgreeablePath}{Agreeable path:}
-\newcommand{\DisputePath}{The \customer{} starts a dispute:}
-\newcommand{\Fairness}{Fairness:}
-\newcommand{\CustomerTurn}[0]{\expandafter\MakeUppercase \customer{} turn:}
-\newcommand{\SPTurn}[0]{\sp{} turn:}
-
-\newcommand{\CanFollowToOne}[2]{The #1 can follow the protocol to the non-disadvantaged position #2}
-\newcommand{\CanDoNothing}[1]{The #1 can do nothing and always ends up in the non-disadvantaged position}
-\newcommand{\CanDoAnything}[1]{The #1 can do anything and always ends up in the non-disadvantaged position}
-\newcommand{\Pos}[4]{$\operatorname{\sigma_{#1, #2, #3} = #4}$}
-\newcommand{\WinForTheSameReason}[1]{The #1 wins the dispute for the same reason}
-\newcommand{\LoseForTheSameReason}[1]{The #1 loses the dispute for the same reason}
-\newcommand{\ActedAbnormallyThen}[1]{The #1 acted abnormally, then:}
-\newcommand{\CustomerPaidButDidntGetResult}{the customer ends up in a disadvantaged position as he paid in advance but didn't receive the result}
-\newcommand{\SpReceivedThePayment}{the SP ends up in the advantaged position as she received the payment}
-
-\newcommand{\CustomerLosesBeforePayment}{The customer loses the dispute because the SP is not obligated to do anything until the transaction is paid}
-\newcommand{\CustomerLosesBeforePoP}{The customer loses the dispute because the SP still can publish the PoP within the agreed timeframe}
-
-\newcommand{\RemainsIn}[2]{The #1 remains in the #2 position}
-
-\subsubsection*{Step 1. \CustomerTurn{} Package delivery}\label{step-1-deliver-package}
-
-The protocol starts when the customer correctly execute the first step of the protocol, i.e., deliver the package to the SP.
-
-The case where the customer does not deliver the package is not considered as it is not a part of the protocol.
-
-\begin{itemize}
-\item \AgreeablePath
-  \begin{itemize}
-    \item  \Pos{1}{c}{\normal}{\neutral}, the customer risked his materials but did not pay for the transaction therefore ends up in neutral position\footnote{One would argue that the customer has put effort into delivering the materials to the SP or that the materials are valuable.
-We assume that the materials without personal information is useless, and the effort to deliver the package is negligible.}.
-    \item \Pos{1}{s}{\normal}{\neutral}, the SP ends up in neutral position as she did not spend any resources and the package did not bring her any value.
-  \end{itemize}
-\item \DisputePath
-  \begin{itemize}
-    \item \Pos{1}{c}{\dispute}{\minus}, \CustomerLosesBeforePayment{}.
-    \item \Pos{1}{s}{\dispute}{\neutral}, \WinForTheSameReason{SP}.
-  \end{itemize}
-\end{itemize}
-
-\Fairness
-
-\begin{itemize}
-  \item \CanFollowToOne{customer}{\Pos{1}{c}{n}{\neutral}}
-  \item \CanDoNothing{SP}
-\end{itemize}
-
-\subsubsection*{Step 2. \SPTurn{} Proof of Delivery}\label{step-2-proof-of-delivery}
-
-The SP publishes the PoD, then:
-
-\begin{itemize}
-  \item \AgreeablePath
-    \begin{itemize}
-      \item \Pos{2}{c}{\normal}{\neutral}, the customer remains in the neutral position as the PoD allows him to pay for the transaction but does not obligate him to anything.
-      \item \Pos{2}{s}{\normal}{\neutral}, the SP remains in the neutral position as the package has not brought her any value and she did not spend any resource to provide the service yet.
-    \end{itemize}
-
-  \item \DisputePath
-    \begin{itemize}
-      \item \Pos{2}{c}{\dispute}{\minus}, \CustomerLosesBeforePayment{}.
-      \item \Pos{2}{s}{\dispute}{\neutral}, \WinForTheSameReason{SP}.
-    \end{itemize}
-\end{itemize}
-
-\ActedAbnormallyThen{\sp}
-
-\begin{itemize}
-\item \AgreeablePath
-  \begin{itemize}
-    \item \Pos{2}{c}{\abnormal}{\neutral}, the customer remains in the neutral position as he is not obligated to agree with the incorrect $\mathrm{PoD}$.
-    \item \Pos{2}{s}{\abnormal}{\neutral}, the SP remains in the neutral position as the package has not brought her any value and she did not spend any resource to provide the service yet.
-  \end{itemize}
-\item \DisputePath
-  \begin{itemize}
-    \item \Pos{2}{c}{\abdispute}{\minus}, \CustomerLosesBeforePayment{}, not even to publish correct $\mathrm{PoD}$.
-    \item \Pos{2}{s}{\abdispute}{\neutral}, \WinForTheSameReason{SP}.
-  \end{itemize}
-\end{itemize}
-
-\Fairness
-
-\begin{itemize}
-  \item \CanDoAnything{SP}.
-  \item The customer can either wait (in case of the SP following the protocol), or abandon the transaction (in case of the SP acting abnormally).
-In both cases the customer ends up in non-disadvantaged position \Pos{2}{c}{\normal}{\neutral} or \Pos{2}{c}{\abnormal}{\neutral}.
-\end{itemize}
-
-\subsubsection*{Step 3. \CustomerTurn{} Get Proof of Delivery}\label{step-3-get-proof-of-delivery}
-
-The customer got the \PoD, then:
-
-\begin{itemize}
-\item \AgreeablePath
-  \begin{itemize}
-    \item \Pos{3}{c}{\normal}{\neutral}, \RemainsIn{customer}{neutral}.
-    \item \Pos{3}{s}{\normal}{\neutral}, \RemainsIn{SP}{neutral}.
-  \end{itemize}
-\item \DisputePath
-  \begin{itemize}
-    \item \Pos{3}{c}{\dispute}{\minus}, \CustomerLosesBeforePayment{}.
-    \item \Pos{3}{s}{\dispute}{\neutral}, \WinForTheSameReason{SP}.
-  \end{itemize}
-\end{itemize}
-
-\ActedAbnormallyThen{\customer}
-
-\begin{itemize}
-\item \AgreeablePath
-  \begin{itemize}
-    \item \Pos{3}{c}{\abnormal}{\neutral}, \RemainsIn{customer}{neutral}.
-    \item \Pos{3}{s}{\abnormal}{\neutral}, \RemainsIn{SP}{neutral}.
-  \end{itemize}
-\item \DisputePath
-  \begin{itemize}
-    \item \Pos{3}{c}{\abdispute}{\minus}, \CustomerLosesBeforePayment{}.
-    \item \Pos{3}{s}{\abdispute}{\neutral}, \WinForTheSameReason{SP}.
-  \end{itemize}
-\end{itemize}
-
-\Fairness
-
-\begin{itemize}
-  \item \CanFollowToOne{customer}{\Pos{3}{c}{\normal}{\neutral}}.
-  \item \CanDoNothing{SP}.
-\end{itemize}
-
-\subsubsection*{Step 4. \CustomerTurn{} Payment}
-
-The customer paid the transaction, then:
-
-\begin{itemize}
-\item \AgreeablePath
-  \begin{itemize}
-    \item \Pos{4}{c}{\normal}{\minus}, the customer paid in advance.
-    \item \Pos{4}{s}{\normal}{\plus}, the SP received the payment, but has not spent his resources yet.
-  \end{itemize}
-\item \DisputePath
-  \begin{itemize}
-    \item \Pos{4}{c}{\dispute}{\minus}, \CustomerLosesBeforePoP{}.
-    \item \Pos{4}{s}{\dispute}{\neutral}, \WinForTheSameReason{SP}.
-  \end{itemize}
-\end{itemize}
-
-\ActedAbnormallyThen{\customer}
-
-\begin{itemize}
-\item \AgreeablePath
-  \begin{itemize}
-    \item \Pos{4}{c}{\abnormal}{\neutral}, the customer ends up in the neutral position as he did not spend his funds.
-    \item \Pos{4}{s}{\abnormal}{\neutral}, the SP ends up in the neutral position as she neither received the payment nor spent her resources.
-  \end{itemize}
-\item \DisputePath
-  \begin{itemize}
-    \item \Pos{4}{c}{\abdispute}{\minus}, \CustomerLosesBeforePayment{}.
-    \item \Pos{4}{s}{\abdispute}{\neutral}, \WinForTheSameReason{SP}.
-  \end{itemize}
-\end{itemize}
-
-\Fairness
-
-\newcommand{\CustomerRiskTemporaryDisadvantagedPosition}[1]{The customer, following the 9th assumption described in Section~\ref{sec:assumptions}, risk the temporary disadvantaged position #1 in faviour of a later better position \Pos{9}{s}{\normal}{\plus}; meanwhile being able to get out of the disadvantaged position if the SP misbehave in one of the following steps.}
-
-\begin{itemize}
-  \item \CustomerRiskTemporaryDisadvantagedPosition{\Pos{4}{c}{\normal}{\minus}}.
-  \item \CanDoNothing{SP}.
-\end{itemize}
-
-\subsubsection*{Step 5. \SPTurn{} Provision of service}
-
-The \sp{} did the provision of service, then:
-
-\begin{itemize}
-\item \AgreeablePath
-  \begin{itemize}
-    \item \Pos{5}{c}{\normal}{\minus}, \RemainsIn{\customer}{disadvantaged} as he did not receive the result.
-    \item \Pos{5}{s}{\normal}{\plus}, \RemainsIn{\sp}{advantaged} as she received the payment.
-  \end{itemize}
-\item \DisputePath
-  \begin{itemize}
-    \item \Pos{5}{c}{\dispute}{\minus}, \CustomerLosesBeforePoP{}.
-    \item \Pos{5}{s}{\dispute}{\neutral}, \WinForTheSameReason{SP}.
-  \end{itemize}
-\end{itemize}
-
-\ActedAbnormallyThen{\sp}
-
-\begin{itemize}
-\item \AgreeablePath
-  \begin{itemize}
-    \item \Pos{5}{c}{\abnormal}{\minus}, \CustomerPaidButDidntGetResult{}. 
-    \item \Pos{5}{s}{\abnormal}{\plus}, \SpReceivedThePayment{}.
-  \end{itemize}
-\item \DisputePath
-  \begin{itemize}
-    \item \Pos{5}{c}{\abdispute}{\neutral} The customer wins the dispute because the SP did not provide the service within the time agreed upon in the \PoD{}, and so the SP will not be able to upload the result and publish the \PoP{} on time.
-    \item \Pos{5}{s}{\abdispute}{\minus}, \LoseForTheSameReason{SP}.
-  \end{itemize}
-\end{itemize}
-
-\Fairness
-\newcommand{\SPCanDoBothButFollowIsSafe}[1]{The SP can follow the protocol and move to the advantaged position \Pos{#1}{s}{\normal}{\plus}, or act abnormally (not provide the service) and also move to the advantaged position \Pos{#1}{s}{\abnormal}{\plus}; however, the second option puts her at risk of terminating the protocol at \Pos{#1}{s}{\abdispute}{\minus} if the customer is rational and starts a dispute; hence, the SP should choose the first option}
-
-\begin{itemize}
-  \item \CustomerRiskTemporaryDisadvantagedPosition{\Pos{5}{c}{\normal}{\minus}}.
-  \item \SPCanDoBothButFollowIsSafe{5}.
-\end{itemize}
-
-\subsubsection*{Step 6. \SPTurn{} Upload result}\label{step-6-publication-of-results}
-
-The SP uploaded the result on time, then:
-
-\begin{itemize}
-\item \AgreeablePath
-  \begin{itemize}
-    \item \Pos{6}{c}{\normal}{\minus}, \RemainsIn{\customer}{disadvantaged} as he did not receive the result.
-    \item \Pos{6}{s}{\normal}{\plus}, \RemainsIn{SP}{advantaged} as she received the payment.
-  \end{itemize}
-\item \DisputePath
-  \begin{itemize}
-    \item \Pos{6}{c}{\dispute}{\minus}, \CustomerLosesBeforePoP{}.
-    \item \Pos{6}{s}{\dispute}{\neutral}, \WinForTheSameReason{SP}.
-
-  \end{itemize}
-\end{itemize}
-
-\ActedAbnormallyThen{\sp}
-
-\begin{itemize}
-\item \AgreeablePath
-  \begin{itemize}
-    \item \Pos{6}{c}{\abnormal}{\minus}, \CustomerPaidButDidntGetResult{}.
-    \item \Pos{6}{s}{\abnormal}{\plus}, \SpReceivedThePayment{}.
-  \end{itemize}
-\item \DisputePath
-  \begin{itemize}
-    \item \Pos{6}{c}{\abdispute}{\neutral}, the customer wins the dispute because the SP did not upload the service within the time agreed upon in the \PoD{}, and so the SP will not be able to publish the \PoP{} on time.
-    \item \Pos{6}{s}{\abdispute}{\minus}, \LoseForTheSameReason{SP}.
-  \end{itemize}
-\end{itemize}
-
-\Fairness
-
-\begin{itemize}
-  \item \CustomerRiskTemporaryDisadvantagedPosition{\Pos{6}{c}{\normal}{\minus}}.
-  \item \SPCanDoBothButFollowIsSafe{6}.
-\end{itemize}
-
-\subsubsection*{Step 7. \SPTurn{} Proof of provision}\label{step-7-publication-of-proof-of-provision}
-
-The SP published \PoP{} on time, then:
-
-\newcommand{\CustomerLosesBecauseSPCanProveBeingCorrect}{the \customer{} loses the dispute as the \sp{} has published all evidences to prove her correct behaviour}
-
-\begin{itemize}
-  \item \AgreeablePath
-    \begin{itemize}
-      \item \Pos{7}{c}{\normal}{\minus}, the customer has not received the result. Therefore, he remains in the disadvantaged position. 
-      \item \Pos{7}{s}{\normal}{\plus}, the SP has published all evidences to prove her correct behaviour, therefore she remains in advantaged position fot the rest of the protocol.
-    \end{itemize}
-  \item \DisputePath
-    \begin{itemize}
-      \item \Pos{7}{c}{\dispute}{\minus}, \CustomerLosesBecauseSPCanProveBeingCorrect{}.
-      \item \Pos{7}{s}{\dispute}{\plus}, \WinForTheSameReason{SP}.
-    \end{itemize}
-\end{itemize}
-
-\ActedAbnormallyThen{\sp}
-
-\begin{itemize}
-\item \AgreeablePath
-  \begin{itemize}
-    \item \Pos{7}{c}{\abnormal}{\minus}, \CustomerPaidButDidntGetResult{}.
-    \item \Pos{7}{s}{\abnormal}{\plus}, \SpReceivedThePayment{}.
-  \end{itemize}
-\item \DisputePath
-  \begin{itemize}
-    \item \Pos{7}{c}{\abdispute}{\neutral}, the customer wins the dispute because the SP did not publish the correct \PoP{} on time.
-    \item \Pos{7}{s}{\abdispute}{\minus}, \LoseForTheSameReason{SP}.
-  \end{itemize}
-\end{itemize}
-
-\Fairness
-
-\begin{itemize}
-  \item \CustomerRiskTemporaryDisadvantagedPosition{\Pos{7}{c}{\normal}{\minus}}.
-  \item \SPCanDoBothButFollowIsSafe{7}.
-\end{itemize}
-
-\subsubsection*{Step 8. \CustomerTurn{} Get Proof of Provision}\label{step-8-pull-proof-of-provision}
-
-The customer got the \PoP{}, then:
-
-\begin{itemize}
-\item \AgreeablePath
-  \begin{itemize}
-    \item \Pos{8}{c}{\normal}{\minus}, the customer gets the \cid{}, but not the result yet.
-    \item \Pos{8}{s}{\normal}{\plus}, \RemainsIn{\sp}{advantaged}.
-  \end{itemize}
-\item \DisputePath
-
-  \begin{itemize}
-    \item \Pos{8}{c}{\dispute}{\minus}, \CustomerLosesBecauseSPCanProveBeingCorrect{}.
-    \item \Pos{8}{s}{\dispute}{\plus}, \WinForTheSameReason{SP}.
-  \end{itemize}
-\end{itemize}
-
-\ActedAbnormallyThen{\customer}
-
-\begin{itemize}
-\item \AgreeablePath
-  \begin{itemize}
-    \item \Pos{8}{c}{\abnormal}{\minus}, the customer paid for the transaction but does not have the access to $cid$, and hence, can not get the result from the storage network.
-    \item \Pos{8}{s}{\abnormal}{\plus}, \SpReceivedThePayment{}.
-  \end{itemize}
-\item \DisputePath
-  \begin{itemize}
-    \item \Pos{8}{c}{\abdispute}{\minus}, \CustomerLosesBecauseSPCanProveBeingCorrect{}
-    \item \Pos{8}{s}{\abdispute}{\neutral}, \WinForTheSameReason{SP}.
-  \end{itemize}
-\end{itemize}
-
-\Fairness
-
-\begin{itemize}
-  \item \CustomerRiskTemporaryDisadvantagedPosition{\Pos{8}{c}{\normal}{\minus}}.
-  \item \CanDoNothing{} \Pos{8}{s}{\normal}{\plus} or \Pos{8}{s}{\abnormal}{\plus}.
-\end{itemize}
-
-\subsubsection*{Step 9. \CustomerTurn{} Download result}\label{step-9-retrieval-of-results}
-
-The customer downloaded the result, then:
-
-\begin{itemize}
-\item \AgreeablePath
-  \begin{itemize}
-    \item \Pos{9}{c}{\normal}{\plus}, the customer got the result, therefore he terminate the protocol in advantaged position.
-    \item \Pos{9}{s}{\normal}{\plus}, \RemainsIn{\sp}{advantaged}.
-  \end{itemize}
-\item \DisputePath
-  \begin{itemize}
-    \item \Pos{9}{c}{\dispute}{\minus}, \CustomerLosesBecauseSPCanProveBeingCorrect{}.
-    \item \Pos{9}{s}{\dispute}{\plus}, \WinForTheSameReason{SP}.
-  \end{itemize}
-\end{itemize}
-
-\ActedAbnormallyThen{\customer}
-
-\begin{itemize}
-\item \AgreeablePath
-  \begin{itemize}
-    \item \Pos{9}{c}{\abnormal}{\minus},the customer ends up in a disadvantaged position, as he ends up with the incorrect result.
-    \item \Pos{9}{s}{\abnormal}{\plus}, the SP ends up in the advantaged position as he received the payment but did not spend his resources.
-  \end{itemize}
-\item \DisputePath
-  \begin{itemize}
-    \item \Pos{9}{c}{\abdispute}{\neutral}, the customer wins the case and ends up in the neutral position.
-    \item \Pos{9}{s}{\abdispute}{\minus}, the SP loses the case and ends up in the disadvantaged position.
-  \end{itemize}
-\end{itemize}
-
-\Fairness
-
-\begin{itemize}
-  \item \CanFollowToOne{\customer}{\Pos{9}{c}{\normal}{\plus}}.
-  \item \CanDoNothing{} \Pos{9}{s}{\normal}{\plus} or \Pos{9}{s}{\abnormal}{\plus}. 
-\end{itemize}
+\EOD
 
 \bibliographystyle{IEEEtran}
-% argument is your BibTeX string definitions and bibliography database(s)
+
+% Loading bibliography database
 \bibliography{bibliography}
-\EOD
 
 \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{stanislaw.jpg}}]{Stanis\L{}aw Bara{\'n}ski} received BEng in 2019 and MSc in 2020 in informatics at Gdańsk University of Technology.
-Currently, he is a PhD candidate at the Department of Computer Architecture, Faculty of Electronics, Telecommunications and Informatics, Gdansk University of Technology.
+Currently, he is a PhD student at the Department of Computer Architecture, Faculty of Electronics, Telecommunications and Informatics, Gdansk University of Technology.
 
@@
 He manages research projects for processing the information in Wikipedia, where the main goal is to extract and structuralize textual knowledge and construct interfaces capable of communicating in natural language.
-Besides his research in information retrieval domain, he was involved in projects related to cognitive science.
+Besides his research in the information retrieval domain, he was involved in projects related to cognitive science.
 His mainstream of this research is building semantic memory models that improve natural language processing.
@@
 He also works on analyzing data within the IoT domain and its secure storage on the blockchain.
-He is involved in project, where acquisition of data from sensors placed in beehives  allows one to predict apiary development and detect abnormalities.
+He is involved in the project, where acquisition of data from sensors placed in beehives  allows one to predict apiary development and detect abnormalities.
 
@@
 conferences as well as served as guest editor preparing special issues of prestigious journals. 
-
 \end{IEEEbiography}
 
-% \section{Appendix B: Smart contract code}\label{appendix-b-smart-contract-code}
-
-% \input{solidity-highlighting.tex}
-% \begin{lstlisting}[language=Solidity]
-% // SPDX-License-Identifier: MIT
-% pragma solidity >=0.4.22 <0.9.0;
-
-% contract AnonSer {
-%     struct Provision {
-%         uint256 issueTime;
-%         uint256 paymentDeadlineTime;
-%         uint256 provisionDeadlineTime;
-%         bool paidInCash;
-%         string paymentAddress;
-%         string cid;
-%         bool exist;
-%         uint256 dealId;
-%         string minerId;
-%     }
-
-%     mapping(bytes => mapping(bytes32 => Provision)) public provisions;
-
-%     address private _owner;
-
-%     event ProofOfDelivery(
-%         bytes indexed clientPubKey,
-%         bytes32 indexed provisionId,
-%         uint256 issueTime,
-%         uint256 paymentDeadlineTime,
-%         uint256 provisionDeadlineTime,
-%         bool paidInCash,
-%         string paymentAddress
-%     );
-
-%     constructor() {
-%         _owner = msg.sender;
-%     }
-
-%     modifier onlyOwner() {
-%         require(
-%             _owner == msg.sender,
-%             "Ownership Assertion: Caller of the function is not the owner."
-%         );
-%         _;
-%     }
-
-%     function proofOfDelivery(
-%         bytes memory clientPubKey,
-%         bytes32 provisionId,
-%         bool paidInCash,
-%         string memory paymentAddress
-%     ) public onlyOwner {
-%         if (provisions[clientPubKey][provisionId].exist) {
-%             revert("Provision already exists");
-%         }
-%         if (paidInCash && bytes(paymentAddress).length > 0) {
-%             revert("Payment address should be empty if paid in cash");
-%         }
-%         if (!paidInCash && bytes(paymentAddress).length == 0) {
-%             revert(
-%                 "Payment address should not be empty if didn't paid in cash"
-%             );
-%         }
-%         Provision memory provision = Provision({
-%             exist: true,
-%             issueTime: block.timestamp,
-%             paymentDeadlineTime: block.timestamp + 1 days,
-%             provisionDeadlineTime: block.timestamp + 8 days,
-%             paidInCash: paidInCash,
-%             paymentAddress: paymentAddress,
-%             dealId: 0,
-%             cid: "",
-%             minerId: ""
-%         });
-%         provisions[clientPubKey][provisionId] = provision;
-%         emit ProofOfDelivery(
-%             clientPubKey,
-%             provisionId,
-%             provision.issueTime,
-%             provision.paymentDeadlineTime,
-%             provision.provisionDeadlineTime,
-%             provision.paidInCash,
-%             provision.paymentAddress
-%         );
-%     }
-
-%     event ProofOfProvision(
-%         bytes indexed clientPubKey,
-%         bytes32 indexed provisionId,
-%         string cid,
-%         uint256 dealId,
-%         string minerId
-%     );
-
-%     function proofOfProvision(
-%         bytes memory clientPubKey,
-%         bytes32 provisionId,
-%         string memory cid,
-%         uint256 dealId,
-%         string memory minerId
-%     ) public onlyOwner {
-%         Provision storage provision = provisions[clientPubKey][provisionId];
-%         if (!provision.exist) {
-%             revert("Provision must be created with proof of delivery first");
-%         }
-
-%         provision.cid = cid;
-%         provision.dealId = dealId;
-%         provision.minerId = minerId;
-%         emit ProofOfProvision(clientPubKey, provisionId, cid, dealId, minerId);
-%     }
-
-%     function getProvision(bytes memory clientPubKey, bytes32 provisionId)
-%         public
-%         view
-%         returns (Provision memory)
-%     {
-%         return provisions[clientPubKey][provisionId];
-%     }
-% }
-% \end{lstlisting}
-
 \end{document}

### 2023-02-01 paper/highlights.tex
prepare els paper docs

\documentclass[preprint,3p]{elsarticle}

\input{constants.tex}
\begin{document}
\begin{titlepage}
   \begin{center}
       \vspace*{1cm}

       \begin{enumerate}
        \item We design a protocol for anonymous provision of privacy-sensitive services
        \item Privacy guarantee was achieved using anonymous payment methods
        \item We implemented demonstration of the practical application of the protocol
        \item The fairness of the protocol was proven
        \item The source code of the protocol has been made publicaly available
       \end{enumerate}

   \end{center}
\end{titlepage}
\end{document}

### 2023-02-01 paper/content.tex
add formal verification to discussion

@@
 In Section~\ref{sec:experiments} we present the implementation of the protocol and results of our experiments.
-Section~\ref{sec:discussion} discuss possible improvements in terms of crowd-sourced dispute resolution or dispute avoidance, self-sovereign identities (SSI), and anonymous delivery.
+Section~\ref{sec:discussion} discuss possible improvements in terms of crowd-sourced dispute resolution or dispute avoidance, self-sovereign identities (SSI), anonymous delivery, and formal verification.
 Finally, section~\ref{sec:conclusion} concludes the paper.
@@
 
-Two parties say, Alice and Bob, can create an escrow by generating
-2-of-2 (not 2-of-3 as it is other TTP-based systems) threshold account
-using Thresh-Key-Gen protocol. Alice and Bob generate secret keys
-\(x_A\) and \(x_B\) accordingly, the shared account public key becomes
-\(y = g^{x_A+x_B}\); only the access to both Alice's and Bob's secrets
-grants access to the shared account.
-
-Then, both Alice and Bob take their keys and split them into
-\(n=2t+1\) secret shares using Shamir Secret Shamir protocol, where
-\(n\) is the number of mediators that participate in the decentralized
-network and \(t+1\) becomes the threshold of a sufficient number of mediators to reconstruct the secret key.
-
-Next, both Alice and Bob, take their key shares and encrypt each
-\textit{i}-th key share using public key of \textit{i}-th mediator. As a result
-Alice's secret \(x_A\) becomes \({c^A_1, c^A_2,...,c^A_n}\), and Bob's
-secret \(x_B\) becomes \({c^B_1, c^B_2,...,c^B_n}\), where
-\(c_i = E_{M_i}(P_i)\) is the encrypted \(i\)-th key share using
-\(i\)-th mediator public key \(M_i\).
-
-Next, both Alice and Bob exchange the sets of encrypted key shares with
-each other, and send funds to the escrow account.
-
-The escrow is secure as long as \(t+1\) of mediators does not collude,
-which would let them recreate both \(x_A\) and \(x_B\). To ensure
-that parties exchange actual key shares, they send witnesses
-generated with the Feldman VSS scheme and zero-knowledge proofs to guarantee the consistency between witnesses and key shares.
-
-In case of dispute, the decentralized network of mediators settles the conflict and grand one winning party, the other party secret key,
-letting him withdraw the funds.
+The protocol works as follows:
+\begin{enumerate}
+    \item Alice and Bob generate a 2-of-2 threshold escrow account using Thresh-Key-Gen protocol and send funds to it.
+    \item Alice and Bob split their secret keys into \(n=2t+1\) secret shares using Shamir Secret Shamir protocol, where \(n\) is the number of mediators that participate in the decentralized network and \(t+1\) becomes the threshold of a sufficient number of mediators to reconstruct the secret key.
+    \item Alice and Bob encrypt each \textit{i}-th key share using public key of \textit{i}-th mediator.
+    \item Alice and Bob exchange the sets of encrypted key shares with each other and send funds to the escrow account.
+\end{enumerate}
+
+The escrow is secure as long as \(t+1\) of mediators does not collude, which would let them recreate both \(x_A\) and \(x_B\).
+
+To ensure that parties exchange actual key shares, they send witnesses generated with the Feldman VSS scheme and zero-knowledge proofs to guarantee the consistency between witnesses and key shares.
+
+In case of dispute, the decentralized network of mediators settles the conflict and grand one winning party the other party secret key, allowing it to withdraw the funds.
 
@@
 
-Hinarejos et al., 2019~\cite{hinarejosSolutionSecureCertified2019} is the simplest protocol that replaces TTP with blockchain.
-However, it does not consider anonymity, disputes between parties nor physical material exchange.
-
-Meng et al., 2019~\cite{mengThemisDecentralizedEscrow2019} improves the previous protocol by the crowdsourced dispute resolution system. However, it does not take anonymity into consideration.
-
-Altawy et al., 2017~\cite{altawyLelantosBlockchainBasedAnonymous2017} is a blockchain-based protocol that does not provide dispute resolution but provides anonymous physical delivery by using onion routing and anonymous blockchain interaction assuming unlinkability between pseudonyms and real identities.
-
-The authors proposed many extensions to the protocol, namely, in ~\cite{birjoveanuPreservingAnonymityFair2018} they proposed a anonymous e-commerce protocol that govers complex transactions, in ~\cite{birjoveanuAnonymityComplexTransactions2019} they extend the anonimity for both customers and SPs, and in ~\cite{birjoveanuFairExchangeECommerce2020} they propose a protocol that supports chained transactions (involving multiple active intermediares).
-However none of them is relevant to our use case.
-
+The authors proposed many extensions to the protocol, namely, in~\cite{birjoveanuPreservingAnonymityFair2018} they proposed an anonymous e-commerce protocol that governs complex transactions, in~\cite{birjoveanuAnonymityComplexTransactions2019} they extend the anonymity for both customers and SPs, and in~\cite{birjoveanuFairExchangeECommerce2020} they propose a protocol that supports chained transactions (involving multiple active intermediaries).
+However, none of them is relevant to our use case.
 We want the SP to remain public so that the anonymous customer can easily start a dispute.
@@
 Moreover, the package is delivered from the customer to the SP, not the other way around — as it's the case for most e-commerce transactions.
+
+Hinarejos et al., 2019~\cite{hinarejosSolutionSecureCertified2019} is the simplest protocol that replaces TTP with blockchain.
+However, it does not consider anonymity, disputes between parties nor physical material exchange.
+
+Meng et al., 2019~\cite{mengThemisDecentralizedEscrow2019} improves the previous protocol by the crowdsourced dispute resolution system. However, it does not take anonymity into consideration.
+
+Altawy et al., 2017~\cite{altawyLelantosBlockchainBasedAnonymous2017} is a blockchain-based protocol that does not provide dispute resolution but provides anonymous physical delivery by using onion routing and anonymous blockchain interaction assuming unlinkability between pseudonyms and real identities.
 
@@
 
-\subsection{Prerequisites}
+\subsection{Assumptions}
 
@@
 \subsection{Anonymous delivery}\label{sec:anonymous-delivery}
-
-We assumed the customer to deliver the package to the SP anonymously via the SP's drop box, or via a trusted person.
-However since the delivery is from the anonymous customer to the public SP, achieving the anonymity of just the sender is much easier than the other way around as proposed in Lelantos~\cite{altawyLelantosBlockchainBasedAnonymous2017} or ~\cite{birjoveanuFairExchangeECommerce2020}.
+We assume the customer being able to anonymously deliver the materials to the SP.
+The assumption is reasonable as the customer stays anonymous and the SP stays public.
+As a result, the customer can use any delivery service that does not require revealing the personal information, e.g., a trusted person, a drop box, or a post office.
+
+The protocols for e-commerce transactions can not rely on this assumption because the customer is the recipent of the package and the SP is the sender.
+Therefore, there arises the problem of hiding the customer's identity from the SP.
+The problem is not trivial as the SP needs to know the customer's address to deliver the package.
+The problem is discussed in~\cite{altawyLelantosBlockchainBasedAnonymous2017}.
+
+\subsection{Formal Verification}\label{sec:formal-verification}
+Following the work of~\cite{birjoveanuFormalVerificationMultiparty2022}, the security analysis of our protocol could be improved by the usage of tools for the automatic formal verification, e.g., AVISPA~\cite{armandoAVISPAToolAutomated2005}.
+It would require specifying the protocol using High-Level Protocol Specification Language (HLPSL)~\cite{chevalierHighLevelProtocol2004}.
+The specification would be then translated to the AVISPA's intermediate language and verified using the AVISPA's theorem prover.
+The verification would be performed by the AVISPA's model checker, which would check the protocol against the security properties.
 

### 2023-02-07 paper/constants.tex
update state abstract

@@
 
+\def\SINGLECOLUMN{SINGLE}
+\def\DOUBLECOLUMN{DOUBLE}
+\def\JOURNALIEEE{IEEE}
+\def\JOURNALELS{ELS}
+
 \newcommand\TITLE{Anonymous provision of privacy-sensitive services using distributed networks}
@@
 
-\newcommand\ABSTRACT{%
-Service providers like lawyers, laboratories, auditors, or banks, to provide services, require customers to submit data often associated with their personal information.
-This information puts suppliers at risk of breaking GDPR, CPAA, or other privacy regulations, and puts customers at risk of privacy violations.
+\newcommand\ABSTRACTPOL{%
+Swiadczenie wrazliwych uslug takich jak testy genetyczne, testy na rodzicielstwo, testy na choroby weneryczne, porady prawne, czy oszacowanie zdolnosci kredytowej, czesto wymaga dostarczenia danych zawierających dane osobiste.
 
-However, most service providers use personal information merely for logistic operations like payments and communication and could provide services anonymously if other means of logistics exist.
-We propose an anonymous protocol for coordinating service provision using blockchain for both anonymous payments and proofs of existence and content-addressable network for results delivery.
-% Less important
-Service providers may use our protocol to provide services without collecting personal information. Enabling provision of services that were previously limited by a high level of trust.
-% Even less important
-Possible applications for this protocol include anonymous genetic tests, tests for paternity, venereal diseases, HIV, drugs, and steroids, or anonymous legal advice.
+Przetwarzanie danych osobistych, szczególnie przy śwaidczeniu usług wykorzystujacych wrazliwe dane (np.
+health records, biological materials, or legal documents), naraza zarówno uzytkownikow jak i dostawcow uslug (SP) na ryzyko.
 
-Compared to other works, our protocol achieves stronger anonimity by accepting payments in either cash or privacy-preserving blockchains.
-It supports physical materials, dispute resolution, and does not require customers to submit any transaction to the message board, indicating higher practicality.
+SPs narazeni sa na zlamanie GDPR, CPAA, i innych prawnych regulacji, natomiast Klienci narazeni sa na utrate prywatnosci.
 
-We provide the fairness analysis and an implementation of the protocol using Ethereum as a message board, Monero as a privacy-preserving blockchain, and Powergate (IPFS and Filecoin) as a content-addressable network.
-We discuss further extensions to an anonymous delivery system, self-sovereign identifiers, and a decentralized conflict resolution system.
-%JS tu należałoby dodac kilka słów na temat rozwiazania i jak zostało ono zwalidowane czemu jest lepsze od innych
+Obserwujemy ze dane osobiste często wykorzystywane sa jedynie do celów logistycznych jak płatnosci czy komunikacja, i moglyby by być swiadczone anonimowo jeśli takie metody były by dostepne.
+
+W tej pracy proponujemy rozwiazanie pozwalajace na swiadczenie uslug bez zbierania danych osobistych.
+Wykorzystujemy anonimowe metody platnosci jak gotówka oraz anonimowe kryptowaluty, technologie blockchain do osiągniecia sprawiedliwosci, oraz rozproszone content-addressable storage networks do dostarczania wynikow.
+
+W porownaniu do innych rozwiazan, nasz protokol osiaga anonimowosc przy slabszych zalozeniach, wspiera fizyczne materialy, rozwiazywanie konfliktow, oraz w optymistycznym scenariuszu nie wymaga, aby uzytkownik wchodzil w interakcje z blockchainem, wykazujac lepsza praktycznosc.
+
+W pracy analizujemy sprawiedliwosc naszego protokolu, oraz implementujemy go przy uzyciu technologi Ethereum jako message board, Monero jako anonimowy sposób płatności, and Powergate (IPFS i Filecoin) jako content-addressable network.
+
+Rozpatrujemy dalsze rozszerzenia do anonimowych dostarczycieli, self-sovereign identifiers, oraz zdecentralizowanego rozwiazywania konfliktow.
+}
+
+\newcommand\ABSTRACT{
+Lawyers, laboratories, auditors or banks, in order to provide services, require data often containing sensitive personal information.
+
+Examples of sensitive services are genetic tests, parenthood tests, STD tests, credit score computation or legal advice.
+
+The processing of personal data, especially when providing services involving sensitive data like health records, biological materials, or legal documents, exposes both users and service providers (SP) to privacy risks.
+
+SPs are at risk of violating GDPR, CPAA, and other legal regulations, while customers are at risk of losing their privacy.
+
+We observe that personal data is often only used for logistical purposes, such as payments or communication, and could be provided anonymously if such methods were available.
+
+In this work, we propose a solution that allows the provision of services without the collection of personal data.
+We use anonymous payment methods such as cash and anonymous cryptocurrencies, blockchain technology to achieve fairness, and distributed content-addressable storage networks to deliver results.
+
+Compared to other solutions, our protocol achieves anonymity with weaker assumptions, supports physical materials and conflict resolution, and in conflict-free transactions does not require the customer to interact with the blockchain, demonstrating better practicality.
+
+In this work, we analyse the fairness of our protocol and implement it using Ethereum technology as a message board, Monero as an anonymous payment method, and Powergate (IPFS and Filecoin) as a decentralised storage network.
 }

### 2023-02-07 paper/content.tex
add support for two columns

@@
 \label{sec:introduction}
-Service providers (SPs) like lawyers, laboratories, auditors, or banks, to provide services, require data that is often associated with the user identity.
+Lawyers, laboratories, auditors or banks, in order to provide services, require data often containing sensitive personal information.
 
@@
 
-% SB START emphasise 
-The problem amplifies when personal information is linked to biological materials like DNA, saliva, or blood, or legal documents like contracts, or wills.
+The problem amplifies when personal information is linked to health records, or legal documents, or biological materials like DNA, saliva, or blood.
 
@@
 
-The privacy guarantee of personal information is often based merely on trust assumptions and the security of the IT system.
-However, most SPs do not need the personal information for any other reason than payment or communication, which should be considered secondary compared to actual service provision.
-
-It would be desirable for the user to keep his or her identity private while still receiving the service.
-This could lead to reduced trust that users have to put in SPs and less responsibility borne by SPs.
+The guarantee of privacy of personal data is often based solely on trust in the SPs' staff and the security of their IT systems.
+However, we observe that personal data is often only used for logistical purposes, such as payments or communications, and could be provided anonymously if such methods were available.
+
+It would be desirable for the customers to keep their identities private while still receiving the service.
+This could lead to reduced trust that customers have to put in SPs and less responsibility borne by SPs.
 
@@
 
-Especially %celebrities, politicians, and %js powtorka
-public figures are prone to this kind of problem as such precedent can negatively influence their future career.
-
 Currently, they have to risk that their personal details, materials, and results are stored securely and kept private from any unauthorized actor (both curious employees and malicious attackers).
 
-Our protocol allows taking such services anonymously, eliminating the strong trust assumption put on the service provider's (e.g., laboratory) IT system.
-\item People willing to take risky business activities may be willing to receive the risk estimation and prediction of possible personal repercussions of such action.
-
-By exposing our identity we trust that the lawyer will not use that information for harmful actions.
-
-Our protocol would allow taking such advice anonymously, eliminating the strong trust assumption put on the lawyers and their IT systems.
-\end{itemize}
-
-%SB GOAL
-In this work, we research the possibility of providing services without the collection of personal information.
+\item Individuals undertaking entrepreneurial activities may wish to obtain estimates of the risks and possible repercussions of the actions taken.
+
+By exposing their identity they trust that the lawyer will not use that information for harmful actions.
+\end{itemize}
+
+In this work we explore the possibilities of providing services anonymously.
 
@@
 
-Our review of the state of the art indicates that none of the current systems is sufficient to achieve the desired goal.
-Therefore, we propose a protocol for anonymously provisioning services that require the delivery of physical materials.
+Our review indicates that none of the current systems is sufficient to achieve the desired goal.
+We propose a anonymous protocol for provisioning serivces that require physical materials.
 In case of dispute, either due to exceeding deadlines or providing an incorrect result, the customer can disclose the whole interaction and prove to justice the misbehavior of the SP.
@@
 \begin{itemize}
-    \item Blockchain (aka message board), to achieve fairness, i.e., as a means for proving that certain actions took place at a certain moment without the trusted third party (TTP).
-    \item Anonymous payment methods, like cash or privacy-preserving cryptocurrencies, allow customers to pay for services anonymously.
-    \item Content-addressable decentralized storage network (e.g., IPFS) to anonymously provide results to customers together with a provable storage network (e.g., Filecoin) to guarantee that the results are available to the customer even in case of the SP denial of service.
-    \item Cryptography
-    \begin{itemize}
-        \item Symmetric encryption, to encrypt and decrypt results published on the public networks.
-        \item Public-key cryptography, and Diffie-Helman key exchange (DHKE) to derive shared secrets for symmetric encryption.
-        \item Digital signatures, to achieve authentication and non-repudiation of actions. 
+    \item \textbf{Blockchain} (aka message board), to achieve fairness, i.e., as a means for proving that certain actions took place at a certain time without the trusted third party (TTP).
+    \item \textbf{Anonymous payment methods}, like cash or anonymous cryptocurrencies, allowing customers to pay for services anonymously.
+    \item \textbf{Decentralized storage network} (e.g., IPFS) to anonymously provide results together with a provable storage network (e.g., Filecoin) to guarantee that the results are available to the customer even if the SP refuses to share the result.
+
+    \item Cryptography:
+    \begin{itemize}
+        \item \textbf{Symmetric encryption}, to encrypt and decrypt results published on the public networks.
+        \item \textbf{Public-key cryptography}, and \textbf{Diffie-Helman key exchange (DHKE)} to derive shared secrets for symmetric encryption.
+        \item \textbf{Digital signatures}, to achieve authentication and non-repudiation of actions. 
     \end{itemize}
@@
   \item allows \textbf{anonymous} service provision, i.e., the service provider does not need to collect any personal information from the customer.
-  \item achieves \textbf{fairness} by carefully designing the protocol as an interactive non-cooperative game, in which the SP remains in an advantageous position and the customer in a disadvantageous one with the option to start a dispute in case the SP misbehavior.
+  \item achieves \textbf{fairness} by carefully designing the protocol as an interactive non-cooperative game, in which the SP remains in an advantageous position and the customer in a disadvantageous position with an option to start a dispute in case a misbehaviour of SP.
   \item \textbf{does not rely on centralized TTP}, but uses decentralized blockchain and distributed content-addressable storage network.
-  \item abstracts the customers from the blockchain technology used underneath, allowing the use of our protocol for \textbf{non-technical users}.
+  \item In conflict-free transactions does not require customers to interact with the blockchain, achieving better \textbf{user-experience and practicality}.
   \item allows the \textbf{delivery of physical materials}, which was rarely addressed by other researchers or based on strong and unpractical assumptions.
@@
 \item Systemise often misused definitions of anonymity, pseudonymity, linkability, and traceability.
-\item Proposing a framework for analyzing fairness analysis in fair-exchange protocols.
-\item Discuss the possible improvements to the protocol with the use of secure computation, self-sovereign identities, zero-knowledge proofs, and blockchain-based dispute resolution mechanisms.
+\item Proposing a framework for analyzing fairness in fair-exchange protocols.
+\item Discuss the possible improvements to the protocol with the use of secure computation, self-sovereign identities, zero-knowledge proofs, and blockchain-based dispute resolution techniques.
 \end{itemize}
@@
 The rest of this paper is organized as follows.
-In section~\ref{sec:related-works} we review related works. 
-Then, in section~\ref{sec:building-blocks} we discuss the building blocks of a dispute resolution system, blockchain as a message board, fairness, payment for services, storage network, result availability, anonymity, and confidentiality.
-Section~\ref{sec:protocol} describes how the protocol works in detail.
+In Section~\ref{sec:related-works} we review related works. 
+Then, in Section~\ref{sec:building-blocks} we discuss the building blocks of a dispute resolution system, blockchain as a message board, fairness, anonymous payments, storage network, results availability, and anonymity.
+Section~\ref{sec:protocol} provides detailed description of the protocol.
 Section~\ref{sec:fairness-analysis} provides a fairness analysis of the proposed protocol.
@@
 Section~\ref{sec:discussion} discuss possible improvements in terms of crowd-sourced dispute resolution or dispute avoidance, self-sovereign identities (SSI), anonymous delivery, and formal verification.
-Finally, section~\ref{sec:conclusion} concludes the paper.
+Finally, Section~\ref{sec:conclusion} concludes the paper.
 
 \section{Related Works}\label{sec:related-works}
-In this section, we review related works on fair exchange, anonymous, and physical delivery protocols. Then we outline the main differences between our protocol and the existing ones.
+In this section, we review related works on fair exchange, anonymous, and physical delivery protocols. Then we outline the main differences between the protocols.
 
@@
 The most common application of fair exchange protocols is e-commerce.
-A typical transaction involves a seller and a buyer, who exchange money for a physical product such as a smartphone.
-To protect themselves, a seller would want to receive the funds prior to sending the product, while a buyer would want to receive the product prior to paying.
+A typical transaction involves a seller and a buyer who exchange money for a physical product.
+To protect themselves the seller want to receive the funds prior to sending the product, while the buyer want to receive the product prior to paying.
 The fairness of the protocol should guarantee that either both parties obtain the goods, or they both obtain nothing.
@@
 However, the protocol relies on strong assumptions, namely, the existence of a trusted third party (TTP) and trusted delivery agent which does not misbehave or collude with any party.
-
-\begin{itemize}
-    \item there exists a trusted third party (TTP) and trusted delivery agent which does not misbehave or collude with any party;
-\end{itemize}
 
@@
 
-\begin{table}
+\ifdefstring{\FORMAT}{\DOUBLECOLUMN}{\begin{table*}}{\begin{table}}
+% \ifx\FORMAT\DOUBLECOLUMN
+% \begin{table*}
+% \else
+% \begin{table}
+% \fi
+\centering
 \newcommand{\YES}{\cellcolor{green!50}Yes}
@@
 \newcommand{\BC}{\cellcolor{green!50}BC}
-\caption{Comparision of related works}
+\caption{Comparision of related works.}
 \label{tab:comparision}
@@
 
-\ifx\JOURNAL\JOURNALIEEE
-\begin{tabular}{|p{40pt}|p{35pt}|p{40pt}|p{35pt}|p{30pt}|p{30pt}|}
-\else
-\begin{tabular}{|c|c|c|c|c|c|}
-\fi
+\ifdefstring{\FORMAT}{\DOUBLECOLUMN}{\begin{tabular}{|c|c|c|c|c|c|}}{\begin{tabular}{|c|c|c|c|c|c|}}
+
+% \begin{tabular}{|p{40pt}|p{35pt}|p{40pt}|p{35pt}|p{30pt}|p{30pt}|}
+
 \hline
@@
 \end{tabular}
-\end{table}
+
+\ifdefstring{\FORMAT}{\DOUBLECOLUMN}
+{\end{table*}}
+{\end{table}}
 
@@
 
-Examples of blockchains that natively support confidential transactions are: Monero~\cite{vansaberhagenCryptoNote2013} (via Ring Signatures~\cite{noetherRingSignatureConfidential2015} and Bulletproofs~\cite{bunzBulletproofsShortProofs2018}), ZCash~\cite{ben-sassonZerocashDecentralizedAnonymous2014} (via zkSNARK~\cite{ben-sassonSNARKsVerifyingProgram2013}), and Grin~\cite{fuchsbauerAggregateCashSystems2019} (via Mimblewimble~\cite{jedusorMIMBLEWIMBLE2016}).
+Examples of blockchains that natively support confidential transactions are: Monero~\cite{vansaberhagenCryptoNote2013} (using Ring Signatures~\cite{noetherRingSignatureConfidential2015} or Bulletproofs~\cite{bunzBulletproofsShortProofs2018}), ZCash~\cite{ben-sassonZerocashDecentralizedAnonymous2014} (using zkSNARK~\cite{ben-sassonSNARKsVerifyingProgram2013}), Grin~\cite{fuchsbauerAggregateCashSystems2019} (using Mimblewimble~\cite{jedusorMIMBLEWIMBLE2016}), and IronFish~\footnote{IronFish, The Privacy Platform
+for web3, \url{https://ironfish.network}, \LASTVISITED} (using Sapling protocol~\cite{hopwoodZcashSaplingProtocol2022}).
 
@@
 The detailed description of each step and the justification %JS proof lub justification ?
-of the outcome position is given in Appendix~\ref{app:proof-of-fairness}.
+of the outcome positions is given in~\ref{app:proof-of-fairness}.
 
@@
 
+\ifx\FORMAT\SINGLECOLUMN
 \noindent%
@@
 \end{minipage}
+\else
+\begin{figure*}
+  \centering
+  \includegraphics[height=0.95\textheight,keepaspectratio]{anonser-experiment1.pdf}
+  \caption{Steps of the experiment, first part.}\label{fig:anonser-experiment1}
+\end{figure*}
+
+\begin{figure*}
+  \includegraphics[height=0.95\textheight,keepaspectratio]{anonser-experiment2.pdf}
+  \caption{Steps of the experiment, second part.}\label{fig:anonser-experiment2}
+\end{figure*}
+
+\fi
 \subsection{Results}

### 2023-02-20 paper/content.tex
improve the state of the art section

@@
 Authors of~\cite{mohammedalarajFairnessPhysicalProducts2012} proposed an protocol for fair-exchage involving physical materials delivery.
-The protocol assumes the existence of offline~\footnote{\textit{Offline} (also called \textit{optimistic}) TTP compared to \textit{online} TTP is in improvement which assumes the TTP being involved only in the case of a dispute between parties~\cite{rayFairExchangeEcommerce2002}.} TTP that is involved only in the case of a dispute.
+The protocol assumes the existence of an offline~\footnote{\textit{Offline} (also called \textit{optimistic}) TTP compared to \textit{online} TTP is in improvement which assumes the TTP being involved only in the case of a dispute between parties~\cite{rayFairExchangeEcommerce2002}.} TTP that is involved only in the event of a dispute.
 The protocol works as follows:
@@
 \item The buyer sends an encrypted payment to the seller along with the proof of validity.
-\item The seller validates the proof which convinces him that the decrypted payment will also be valid.
-\item The seller forwards the physical product to the delivery agent.
+\item The seller validates the proof, which convinces him that the decrypted payment will also be valid.
+\item The seller forwards the physical product to the trusted delivery agent (DA).
 \item The buyer verifies whether the product is the one he ordered.
@@
 
-However, the protocol relies on strong assumptions, namely, the existence of a trusted third party (TTP) and trusted delivery agent which does not misbehave or collude with any party.
+However, the protocol relies on strong assumptions, namely, the existence of a TTP and an DA, who does not misbehave or collude with either party.
 
@@
 
-In the previous protocol, the identities of both parties are known.
-There are however situations where the customer does not want to reveal his identity to the merchant.
-The problem gets even more challenging when physical products are involved.
-
-Authors of~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} proposed a protocol for the fair exchange of physical products and electronic payments, which guarantees both customer and merchant anonymity.
-They achieve it by introducing online TTPs that validate coins and provide fair exchange guarantees.
-
-The anonymity is ensured by assuming the existence of a source cabinet (SC), delivery cabinet (DC), and a trusted delivery agent who take a product from an SC and provide it to a DC.
-Both cabinets provide access to the product by passwords to conceal
-the identity of the customer and the merchant.
+In the previous protocol, both parties of the transaction are known to each other.
+However, there are situations in which the buyer would prefer not to disclose his identity to the seller.
+The situation becomes more challenging when the transaction involves physical products.
+
+Authors of~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} proposed a protocol involving physical products, which guarantees anonymity of both buyer and seller.
+They achieve it with the introduction of an online TTP that validates coins and guarantees fairness.
+
+Anonymity is ensured by assuming the existence of a source cabinet (SC), delivery cabinet (DC), and a trusted delivery agent (DA) who take a product from the SC and provide it to the DC.
+Both cabinets provide access to the product by passwords to conceal the identity of the buyer and the seller.
 
@@
     \item Both parties agree on the purchase details.
-    \item The customer buys a digital coin from his bank and validates it with the TTP.
-    \item The customer sends the merchant the purchase order and the digital signature made by TTP on the encrypted coin.
-    \item The merchant post the product to the SC.
-    \item Delivery agent collects the product from the SC and posts it to the DC.
-    \item Customer collects the product from the DC using a password.
-    \item The customer checks if the product is the ordered one.
+    \item The buyer buys a digital coin from his bank and validates it with the TTP.
+    \item The buyer sends to the seller the purchase order and the digital signature made by TTP on the encrypted coins.
+    \item The seller posts the product to the SC.
+    \item The DA collects the product from the SC and posts it to the DC.
+    \item The buyer collects the product from the DC using a password.
+    \item The buyer checks if the product is the ordered one.
     \begin{itemize}
@@
         \setcounter{enumii}{7}
-        \item the customer sends the acknowledgment to the DC and decryption key to the merchant.
-        \item The merchant redeems the coins from the bank.
+        \item The buyer sends the acknowledgment to the DC and decryption key to the seller.
+        \item The seller redeems the coins from the bank.
         \end{enumerate}
@@
         \setcounter{enumii}{7}
-        \item the DC is equipped with a video camera that records the moment when the customer opens the package and lets the customer signal the invalidity of the product, and so, sending the encrypted recording to the TTP.
-        \item the dispute is settled via TTP, optionally letting each party reveal its identity.
+        \item The DC is equipped with a video camera that records the moment when the buyer opens the package and lets the buyer signal the invalidity of the product, and so, sending the encrypted recording to the TTP.
+        \item The dispute is settled via TTP, optionally letting each party reveal its identity.
     \end{enumerate}
@@
 
-Besides the assumptions of the existence of TTP and trusted delivery agent (similar to the previous protocol~\cite{mohammedalarajFairnessPhysicalProducts2012}), the protocol also assumes:
-
-\begin{itemize}
-    \item there exists an anonymous communication channel 
-    \item the customer's and merchant's banks enable confidential transactions, and both share a commit buffer where the value is locked until the transaction is finished;
+Besides the assumptions of the existence of the TTP and DA (similar to the previous protocol~\cite{mohammedalarajFairnessPhysicalProducts2012}), the protocol also assumes:
+
+\begin{itemize}
+    \item the buyer's and seller's banks enable confidential transactions, and both share a commit buffer where the value is locked until the transaction is finished;
     \item all banks maintain a global list of coins' serial numbers to prevent double-spending problems;
-    \item the SC and DC exist, and in both, the access is protected by a password;
-    \item the DC is equipped with a video camera that records the moment when the customer opens the package and provides a way to submit the video to TTP in case of a dispute;
+    \item there exists an anonymous communication channel, and the SC and the DC protected by a passwords;
+    \item the DC is equipped with a video camera that records the moment when the buyer opens the package and provides a way to submit the video to TTP in case of a dispute;
 \end{itemize}
@@
 The protocol achieves anonymity by employing onion routing (similar to the Tor network) to connect physical delivery providers.
-The whole route from a merchant to a customer is split into multiple steps, and each step is undertaken by the different randomly selected delivery providers.
-As long as the delivery providers do not collude, a merchant neither can learn the identity nor destination address of the customer.
-
-A smart-contract is used to coordinate the whole process and
-mediate communication between customers and delivery providers.
+The whole route from a seller to a buyer is split into multiple steps, and each step is undertaken by the different randomly selected delivery providers.
+As long as the delivery providers do not collude, the seller neither can learn the identity nor destination address of the buyer.
+
+A smart-contract is used to coordinate the whole process and mediate communication between the buyer and delivery providers.
 
@@
 
-The authors proposed many extensions to the protocol, namely, in~\cite{birjoveanuPreservingAnonymityFair2018} they proposed an anonymous e-commerce protocol that governs complex transactions, in~\cite{birjoveanuAnonymityComplexTransactions2019} they extend the anonymity for both customers and SPs, and in~\cite{birjoveanuFairExchangeECommerce2020} they propose a protocol that supports chained transactions (involving multiple active intermediaries).
+The authors proposed many extensions to the protocol, namely, in~\cite{birjoveanuPreservingAnonymityFair2018} they proposed an anonymous e-commerce protocol that governs complex transactions, in~\cite{birjoveanuAnonymityComplexTransactions2019} they extend the anonymity for both buyers and sellers (in our case SPs), and in~\cite{birjoveanuFairExchangeECommerce2020} they proposed a protocol that supports chained transactions (involving multiple active intermediaries).
 However, none of them is relevant to our use case.
-We want the SP to remain public so that the anonymous customer can easily start a dispute.
+We want the SP to remain public so that the anonymous buyer can easily start a dispute.
 We assume just one package of physical materials.
-Moreover, the package is delivered from the customer to the SP, not the other way around — as it's the case for most e-commerce transactions.
+Moreover, the package is delivered from the buyer to the SP, not the other way around — as it's the case for most e-commerce transactions.
 
@@
 
-Altawy et al., 2017~\cite{altawyLelantosBlockchainBasedAnonymous2017} is a blockchain-based protocol that does not provide dispute resolution but provides anonymous physical delivery by using onion routing and anonymous blockchain interaction assuming unlinkability between pseudonyms and real identities.
+Altawy et al., 2017~\cite{altawyLelantosBlockchainBasedAnonymous2017} is a blockchain-based protocol that provides anonymous physical delivery by using onion routing and anonymous blockchain interaction assuming unlinkability between pseudonyms and real identities.
+However, it does not provide dispute resolution.
 
@@
 
-The comparison of the protocols is presented in table~\ref{tab:comparision}.
+The comparison of the protocols is presented in Table~\ref{tab:comparision}.
 

### 2023-03-01 paper/constants.tex
update title

@@
 
-\newcommand\TITLE{Anonymous provision of privacy-sensitive services using distributed networks}
-% \newcommand\TITLE{Privacy-preserving physical delivery service provisioning using distributed networks}
+\newcommand\TITLE{Anonymous provision of privacy-sensitive services using blockchain and decentralised storage}
 \newcommand\STANLONG{Stanis\l{}aw Bara{\'n}ski}
 \newcommand\JULLONG{Julian Szyma{\'n}ski}
+\newcommand\HIGILONG{Higinio Mora}
 \newcommand\STAN{S. Bara{\'n}ski}
 \newcommand\JUL{J. Szyma{\'n}ski}
-
-\newcommand\ABSTRACTPOL{%
-Swiadczenie wrazliwych uslug takich jak testy genetyczne, testy na rodzicielstwo, testy na choroby weneryczne, porady prawne, czy oszacowanie zdolnosci kredytowej, czesto wymaga dostarczenia danych zawierających dane osobiste.
-
-Przetwarzanie danych osobistych, szczególnie przy śwaidczeniu usług wykorzystujacych wrazliwe dane (np.
-health records, biological materials, or legal documents), naraza zarówno uzytkownikow jak i dostawcow uslug (SP) na ryzyko.
-
-SPs narazeni sa na zlamanie GDPR, CPAA, i innych prawnych regulacji, natomiast Klienci narazeni sa na utrate prywatnosci.
-
-Obserwujemy ze dane osobiste często wykorzystywane sa jedynie do celów logistycznych jak płatnosci czy komunikacja, i moglyby by być swiadczone anonimowo jeśli takie metody były by dostepne.
-
-W tej pracy proponujemy rozwiazanie pozwalajace na swiadczenie uslug bez zbierania danych osobistych.
-Wykorzystujemy anonimowe metody platnosci jak gotówka oraz anonimowe kryptowaluty, technologie blockchain do osiągniecia sprawiedliwosci, oraz rozproszone content-addressable storage networks do dostarczania wynikow.
-
-W porownaniu do innych rozwiazan, nasz protokol osiaga anonimowosc przy slabszych zalozeniach, wspiera fizyczne materialy, rozwiazywanie konfliktow, oraz w optymistycznym scenariuszu nie wymaga, aby uzytkownik wchodzil w interakcje z blockchainem, wykazujac lepsza praktycznosc.
-
-W pracy analizujemy sprawiedliwosc naszego protokolu, oraz implementujemy go przy uzyciu technologi Ethereum jako message board, Monero jako anonimowy sposób płatności, and Powergate (IPFS i Filecoin) jako content-addressable network.
-
-Rozpatrujemy dalsze rozszerzenia do anonimowych dostarczycieli, self-sovereign identifiers, oraz zdecentralizowanego rozwiazywania konfliktow.
-}
+\newcommand\HIGI{H. Mora}
 

### 2023-03-06 paper/content.tex
update paper

@@
 \label{sec:introduction}
-Lawyers, laboratories, auditors or banks, in order to provide services, require data often containing sensitive personal information.
+Diagnostic services such as paternity tests, doping tests, or venereal disease tests are performed at diagnostic centres that require clients to provide biological materials such as blood, urine, stool, or saliva.
+Unfortunately, to process transactions, clients are often forced to reveal their identities.
+Such a combination of personal data with biological materials exposes clients to significant privacy risks.
+
+Other examples of sensitive services are, legal services, such as legal advice that may require disclosure of the history of financial transactions and confidential legal documents.
+
+Banking services, such as credit scoring, may require sensitive personal data, such as medical records, and history of financial transactions.
 
 Providing personal information exposes users to privacy risks, i.e. potential loss of control over personal information~\cite{smithInformationPrivacyResearch2011}.
-%JS co może prowadzic do nieintencjonalnego naruszenia rodo  
-%SP dodałem na dole
 
 Such personal information can be used deliberately or accidently (e.g., by theft) 
-%JS kradzież to chyba inencjonalne
-%SB zmieniłem na accidentaly
 for insider disclosure, unauthorized access, or commercial gains. For example, by reselling it to marketers, financial institutions, other businesses, government agencies, or even cybercriminals. 
@@
 Both parties are affected as the client does not receive a diagnosis relevant to their health and the SP loses potential clients.
-% SB END emphasise
 
@@
 
-% We observe
 We observe that the issue of anonymous service provision can be seen as a problem of fair exchange where parties exchange some goods fairly, i.e., either both parties obtain the goods, or they both obtain nothing.
@@
 
-%\paragraph{Contributions}
-%We contribute to the state of the art by:
 The contribution of our paper is:
@@
 
-% Our protocol simultaneously provides five main properties:
-
-% \begin{itemize}
-% \item Anonymity: the customer stays anonymous to all external observers throughout the transaction.
-% \item Fairness: at each step of the protocol, both parties are incentivized to act accordingly to the protocol; otherwise, the misbehaving party ends up in a disadvantaged position.
-% \item Dispute resolution: at each step of the protocol, the customer can start a dispute and win the case if and only if the SP misbehaved.
-% \item Blockchain-obvious: the customer using our protocol does not need to interact with the blockchain directly; especially, he does not need to obtain funds and pay for the transaction fees, allowing the use of our protocol for non-technical users.
-% \item TTP-less: 
-% our protocol does not rely on a trusted third party to conduct transactions fairly.
-Only in case of a dispute, the centralised justice is involved, which can be instantiated either with courts and polices, or blockchain-based dispute resolution mechanisms as discussed in Section~\ref{sec:decentralised-justice}.
-% \item Physical materials: our protocol allows providing not only digital but also physical materials to the service provider.
-% \end{itemize}
-
 Some authors have proposed blockchain-based fair-exchange systems that could be adapted to service provision; however, to our best knowledge, we are the first to propose a system that satisfies all the properties stated above.
@@
 
-%\paragraph{Organisation}
 The rest of this paper is organized as follows.
@@
 The fairness of the protocol should guarantee that either both parties obtain the goods, or they both obtain nothing.
+
+To our best knowledge, the first system that allowed for fair exchange of physical products was proposed by Zhang et al.
+in 2006~\cite{zhangPracticalFairExchangeEPayment2006}.
+The protocol uses buyer's bank as TTP, and assumes no coalition between parties to achieve anonymity.
+Authors of
 
@@
 However, the protocol relies on strong assumptions, namely, the existence of a TTP and an DA, who does not misbehave or collude with either party.
-
-\subsection{Fair exchange, anonymity, and physical products delivery} 
+Also the fairness is obtained assuming resilient communication channels.
+
+\subsection{Fair exchange, anonymity, dispute resolution, and physical products delivery} 
 \label{anonymity-and-fair-exchange-in-e-commerce-protocol-for-physical-products-delivery}
@@
 They achieve it with the introduction of an online TTP that validates coins and guarantees fairness.
-
-Anonymity is ensured by assuming the existence of a source cabinet (SC), delivery cabinet (DC), and a trusted delivery agent (DA) who take a product from the SC and provide it to the DC.
-Both cabinets provide access to the product by passwords to conceal the identity of the buyer and the seller.
-
-The protocol works as follows: \begingroup
-\renewcommand{\labelenumii}{\arabic{enumii}.}
+Later, they proposed many extensions to the protocol, namely, in~\cite{birjoveanuPreservingAnonymityFair2018} they proposed an anonymous e-commerce protocol that governs complex transactions, in~\cite{birjoveanuAnonymityComplexTransactions2019} they extend the anonymity for both buyers and sellers (in our case SPs), and in~\cite{birjoveanuFairExchangeECommerce2020} they proposed a protocol that supports chained transactions (involving multiple active intermediaries).
+Finally in~\cite{birjoveanuTwoPartyECommerceProtocols2022} they proposed improved protocol named PPPDCP (Protocol with Physical Product Delivery Providing Customer's Privacy).
+
+Anonymity is ensured by using anonymous communication channel over Tor~\cite{dingledineTorSecondGenerationOnion2004} and blind signatures~\cite{chaumSecurityIdentificationTransaction1985}.
+Fair exchange, physical delivery, and dispute resolution is achieved using delivery cabinet (DC) under the seller's control (e.g.
+Amazon Locker) and offline TTP that intervenes only in the case of a dispute.
+
+The protocol works as follows:
 
 \begin{enumerate}
-    \item Both parties agree on the purchase details.
-    \item The buyer buys a digital coin from his bank and validates it with the TTP.
-    \item The buyer sends to the seller the purchase order and the digital signature made by TTP on the encrypted coins.
-    \item The seller posts the product to the SC.
+    \item The buyer buys a digital coin from his bank, blind signature is used to preserve customer's privacy.
+    \item The buyer sends to the seller the purchase details, address of DC, customer's bank signature, and some meta data to preserve the integrity of transaction, communication is done over Tor.
+    \item The seller request a redemption of the digital coin.
+    \item The seller posts the product to the DC via delivery serivice.
     \item The DA collects the product from the SC and posts it to the DC.
     \item The buyer collects the product from the DC using a password.
-    \item The buyer checks if the product is the ordered one.
-    \begin{itemize}
-    \item[-] if yes 
-        \begin{enumerate}
-        \setcounter{enumii}{7}
-        \item The buyer sends the acknowledgment to the DC and decryption key to the seller.
-        \item The seller redeems the coins from the bank.
+    \item The buyer checks if the product is the ordered one, if not, opens a dispute to TTP.
 \end{enumerate}
-    \item[-] if no
-        \begin{enumerate}
-        \setcounter{enumii}{7}
-        \item The DC is equipped with a video camera that records the moment when the buyer opens the package and lets the buyer signal the invalidity of the product, and so, sending the encrypted recording to the TTP.
-        \item The dispute is settled via TTP, optionally letting each party reveal its identity.
-    \end{enumerate}
-    \end{itemize}
-\end{enumerate}
-\endgroup
-
-Besides the assumptions of the existence of the TTP and DA (similar to the previous protocol~\cite{mohammedalarajFairnessPhysicalProducts2012}), the protocol also assumes:
+
+Besides the assumptions of the existence of the TTP, the protocol also assumes:
 
@@
     \item the buyer's and seller's banks enable confidential transactions, and both share a commit buffer where the value is locked until the transaction is finished;
-    \item all banks maintain a global list of coins' serial numbers to prevent double-spending problems;
+    \item banks maintain a global list of coins' serial numbers to prevent double-spending problems;
     \item there exists an anonymous communication channel, and the SC and the DC protected by a passwords;
@@
 
-However, since the system uses Ethereum, it achieves pseudonymity rather than anonymity (see section~\ref{sec:pseudo-anon}). Also, the protocol does not cover disputes between the parties.
+However, since the system uses Ethereum, it achieves pseudonymity rather than anonymity (see Section~\ref{sec:pseudo-anon}). Also, the protocol does not cover disputes between the parties.
 
@@
 
-Bîrjoveanu, 2015~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} is the closest to our protocol, however, it uses TTP and does not consider disputes between parties.
-
-The authors proposed many extensions to the protocol, namely, in~\cite{birjoveanuPreservingAnonymityFair2018} they proposed an anonymous e-commerce protocol that governs complex transactions, in~\cite{birjoveanuAnonymityComplexTransactions2019} they extend the anonymity for both buyers and sellers (in our case SPs), and in~\cite{birjoveanuFairExchangeECommerce2020} they proposed a protocol that supports chained transactions (involving multiple active intermediaries).
-However, none of them is relevant to our use case.
+Also, we didn't put much attention to the protocols for buying digital products as they are not relevant to our use case.
+The comprehensive analysis of such protocols is avaiable in~\cite{birjoveanuTwoPartyECommerceProtocols2022}.
+
+Altawy et al., 2017~\cite{altawyLelantosBlockchainBasedAnonymous2017} is a blockchain-based protocol that provides anonymous physical delivery by using onion routing and anonymous blockchain interaction assuming unlinkability between pseudonyms and real identities.
+However, it does not provide dispute resolution.
+
+Hinarejos et al., 2019~\cite{hinarejosSolutionSecureCertified2019} is the simplest protocol that replaces TTP with blockchain.
+However, it does not consider anonymity, disputes between parties nor physical material exchange.
+
+Meng et al., 2019~\cite{mengThemisDecentralizedEscrow2019} improves the previous protocol by the crowdsourced dispute resolution system. However, it does not take anonymity into consideration.
+
+Bîrjoveanu, 2022~\cite{birjoveanuTwoPartyECommerceProtocols2022} is the closest to our protocol, however, it is based on strong assumptions, namely, existence of TTP, banks supporting confidental transactions with commit buffers, and mantainng a global list of coins' serial numbers.
+
+Our protocol achieves anonymity by using either cash or privacy-preserving blockchains.
+Moreover, our protocol does not require a customer to submit any transaction to the message board, which in other protocols may be the weakest link in achieving the anonymity.
+
+Moreover, none of them directly address our use case.
 We want the SP to remain public so that the anonymous buyer can easily start a dispute.
@@
 
-Hinarejos et al., 2019~\cite{hinarejosSolutionSecureCertified2019} is the simplest protocol that replaces TTP with blockchain.
-However, it does not consider anonymity, disputes between parties nor physical material exchange.
-
-Meng et al., 2019~\cite{mengThemisDecentralizedEscrow2019} improves the previous protocol by the crowdsourced dispute resolution system. However, it does not take anonymity into consideration.
-
-Altawy et al., 2017~\cite{altawyLelantosBlockchainBasedAnonymous2017} is a blockchain-based protocol that provides anonymous physical delivery by using onion routing and anonymous blockchain interaction assuming unlinkability between pseudonyms and real identities.
-However, it does not provide dispute resolution.
-
-Our protocol achieves stronger anonymity guarantees.
-Namely, we achieve anonymity by using either cash or privacy-preserving blockchains.
-Moreover, our protocol does not require a customer to submit any transaction to the message board, which may be the weakest link in the anonymity of the aforementioned protocols.
-
-Our protocol does not use its own delivery system.
-We assume that there is a way to anonymously deliver a package either via SP's drop box, a customer's trusted party.
-The improvement of the protocol to support anonymous physical delivery via courier is discussed in Section~\ref{sec:anonymous-delivery}.
-
 Also, our protocol does not provide its own dispute-resolution mechanism as Themis does.
 However, we assume the existence of an abstract justice that accepts evidence and punishes the misbehaving party.
-%JS to warto podkreslic w dyskusji
 It can be instantiated with either the local court or police, or one of the blockchain
@@
 
+The notation \textit{Pseudonymity} means that the anonymity is based on the assumption that the pseudonym is not linked to the real identity; \textit{TTP} means that the protocol uses a trusted third party; \textit{BC} means that the protocol uses a public blockchain; \textit{YES*} means that the protocol provides the feature, but is based on strong or unpractical assumptions.
+
 \ifdefstring{\FORMAT}{\DOUBLECOLUMN}{\begin{table*}}{\begin{table}}
-% \ifx\FORMAT\DOUBLECOLUMN
-% \begin{table*}
-% \else
-% \begin{table}
-% \fi
 \centering
 \newcommand{\YES}{\cellcolor{green!50}Yes}
+\newcommand{\YESBUT}{\cellcolor{green!25}Yes*}
 \newcommand{\ID}{\cellcolor{green!25}Identity}
-\newcommand{\PSEUDO}{\cellcolor{green!25}Pseudonym}
+\newcommand{\PSEUDO}{\cellcolor{green!35}Pseudonym}
 \newcommand{\ANON}{\cellcolor{green!50}Anonymity}
@@
 \newcommand{\BC}{\cellcolor{green!50}BC}
+\newcommand{\BCBUT}{\cellcolor{green!35}BC*}
 \caption{Comparision of related works.}
@@
 
-% \begin{tabular}{|p{40pt}|p{35pt}|p{40pt}|p{35pt}|p{30pt}|p{30pt}|}
-
 \hline
@@
 \hline
-Alaraj, 2012~\cite{mohammedalarajFairnessPhysicalProducts2012} & \YES & \NO & \YES & \TTP & \YES \\
+Zhang et al. 2006~\cite{zhangPracticalFairExchangeEPayment2006} & \YES & \YESBUT & \YES & \TTP & \YES \\
 \hline
-Bîrjoveanu, 2015~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} & \YES & \YES & \NO & \TTP & \YES \\
+Alaraj, 2012~\cite{mohammedalarajFairnessPhysicalProducts2012} & \YESBUT & \NO & \YES & \TTP & \YES \\
+\hline
+Lelantos, 2017~\cite{altawyLelantosBlockchainBasedAnonymous2017} & \YES & \PSEUDO & \NO & \BC & \YES \\
 \hline
@@
 \hline
-Themis~\cite{mengThemisDecentralizedEscrow2019} & \YES & \NO & \YES & \BC & \NO \\
+Themis, 2019~\cite{mengThemisDecentralizedEscrow2019} & \YES & \NO & \YES & \BC & \NO \\
 \hline
-Lelantos~\cite{altawyLelantosBlockchainBasedAnonymous2017} & \YES & \PSEUDO & \NO & \BC & \YES \\
+PPPDCP, 2022~\cite{birjoveanuTwoPartyECommerceProtocols2022} & \YES & \YES & \YES & \TTP & \YES \\
 \hline
-This paper & \YES & \YES & \YES & \BC & \YES \\
+This paper & \YES & \YES & \YES & \BCBUT & \YES \\
 \hline
@@
 \section{Building Blocks}\label{sec:building-blocks}
+
+\subsection{Physical products}\label{sec:physical-products}
+The use cases we address in this paper use physical materials like blood, urine, hair, and other biological materials.
+This requirement, combined with the requirement of anonymity, is a challenging part of the fair-exchange protocols.
+The problem arises when the seller wants to sent the product to the buyer who wants to remain anonymous.
+Most of the existing protocols either assume the existence of trusted delivery agent~\cite{mohammedalarajFairnessPhysicalProducts2012,birjoveanuAnonymityFairexchangeEcommerce2015}, or use complex delivery mechanism similar to onion rounting involving multiple many delivery services~\cite{altawyLelantosBlockchainBasedAnonymous2017}.
+
+However, our use case is different in that the physical materials are transfered from the (anonymous) customer to the (public) SP.
+This, allows for siplification of the delivery process.
+We assume that there is a way to anonymously deliver a package without revealing the customer personal information either via SP's drop box, Parcel Locker services (e.g.
+Amazon Locker, InPost\footnote{InPost, Parcel locker service, \url{https://inpost.pl/en}, \LASTVISITED}), a customer's trusted party, of even post office.
+
 \subsection{Dispute resolution system}
+\label{sec:dispute-resolution}
 
@@
 price, train delay, election results, and others—and they are the ones we
-are interested in—providing the settlement of a submitted dispute.
+are interested in—provide the settlement of a submitted dispute.
 
@@
 However, it is hard to realize such a decentralized evaluation of health or legal services quality when expertise and privacy concerns are taken into account.
-Therefore, in our protocol, we take the more conservative approach and resolve disputes using local
-justice system (police or court).
+Therefore, in our protocol, we take a more conservative approach and resolve disputes by recording evidence on blockchain and then using the local justice system (police or court) to settle the conflict.
 
@@
 
-    \item Payment $\mathrm{attestation}$ is confirmation that the customer has paid for the transaction at a certain time.
-The actual implementation depends on the particular cryptocurrency and is discussed further section~\ref{payment-for-services}.
+    \item Payment $\mathrm{receipt}$ is confirmation that the customer has paid for the transaction at a certain time.
+The actual implementation depends on the particular cryptocurrency and is discussed further Section~\ref{payment-for-services}.
 
@@
 \subsection{Payment for services}\label{payment-for-services}
-Transactions between customers and SPs must be pegged to prevent proving one payment for multiple transactions. In other
-words, we need a mechanism that uniquely associates a payment with the corresponding transaction.
+Transactions between customers and SPs must be pegged to prevent reusing one payment for multiple transactions. 
+In other words, we need a mechanism that uniquely associates a payment with the corresponding transaction.
 
@@
 ways:
-% continue reading from here
-\begin{itemize}
-
-\item separate address: each transaction derives a new address uniquely associated with the transaction.
+
+\begin{itemize}
+
+\item separate address: each transaction uses an unique address associated with the transaction.
 Such addresses can be derived using Hierarchical Deterministic Wallets (BIP-32)\footnote{Bitcoin Improvement Proposals, Hierarchical Deterministic Wallets, \url{https://github.com/bitcoin/bips/blob/master/bip-0032.mediawiki}, (last visited Dec.
-03, 2022)}.
-\item memo: the payments are sent to one SP account but contain an extra field named ``memo'' filled with the unique number provided by the SP in $\mathrm{PoD}$.
-Each payment containing the such value in the memo is considered to pay for the transaction.
-In case of a dispute, revealing both the payment memo and the $\mathrm{PoD}$ proves the connection.
-\end{itemize}
-
-Both approaches have some advantages and disadvantages, but our protocol can abstract them away by treating them as some randomly generated unique number, often called \textit{nonce} (number once).
-The actual implementation depends on a particular blockchain.
+03, 2022)} and published on message board, to achieve non-repudiation.
+\item memo: the payments are sent to sigle SP account, but contain an extra field named ``memo'' filled with the unique indentifier $\textrm{provisionID}$. 
+\end{itemize}
+
+Each payment containing the $\textrm{provisionID}$ in the memo, or payment to the dedicated address is considered to pay for the transaction.
 
 In case of a dispute, there must be a way to prove to justice that the customer has paid for the transaction.
-As the proof of transaction is trivial in transparent and trackable blockchains, it gets more complicated when it comes to anonymous blockchains.
+As the proof of payment is trivial in transparent and trackable blockchains, it gets more complicated when it comes to anonymous blockchains.
 Monero allows proving and checking payments via dedicated API\footnote{Monero, How to prove payment, \url{https://www.getmonero.org//resources/user-guides/prove-payment.html}, \LASTVISITED}.
-ZCash provides a mechanism called Payment Disclosure \cite{daviesIntroductionPaymentDisclosure2017}.
+ZCash provides a mechanism called Payment Disclosure \footnote{Gareth Davies, An Introduction to Payment Disclosure in Zcash, \url{https://garethtdavies.medium.com/an-introduction-to-payment-disclosure-in-zcash-96748c209d49}, \LASTVISITED}.
+We call the proof of payment a \textit{payment recepit}.
 
@@
 The most natural approach would be to send the result via e-mail or some dedicated platform.
-However, since the customer wants to stay anonymous and so does not want to expose his e-mail address nor IP address.
-Moreover, the SP should prove that the result has been provided before the deadline, which brings us to the issue of proof of existence discussed in section ~\ref{sec:message-board}.
+However, the customer wants to stay anonymous and so does not want to expose his e-mail address nor IP address.
+Moreover, the SP should prove that the result has been provided before the deadline, which brings us to the issue of proof of existence discussed in Section ~\ref{sec:message-board}.
 
@@
 
-To increase anonymity, the customer should use standard techniques to hide its IP address, such as gateway, VPN, proxy, or onion routing.
+To increase anonymity, the customer should use standard techniques to hide its IP address, such as VPN, or proxy.
 
@@
 
-While most blockchains could provide message board functionality, anonymous payments are not as prevalent. Especially a provable storage network is a functionality of a few specialized blockchains.
+While most blockchains could provide message board functionality, anonymous payments are not as common. Especially a provable storage network is a functionality of a few specialized blockchains.
 
@@
 We define the requirements for each role and leave the choice of the technology to the developer.
-Later in the paper (section~\ref{sec:experiments}) we describe our implementation used for conducting experiments.
+Later in the paper (Section~\ref{sec:experiments}) we describe our implementation used to conduct an experiment.
 
@@
     \begin{itemize}
-        \item The customer and the SP have their key pairs consisting of secret key $\mathrm{sk}(\mathrm{party})$ and public key $\mathrm{pk}(\mathrm{party})$, where $\mathrm{party} \in \{\mathrm{C}, \mathrm{SP}\}$ for the customer and the SP.
+        \item The customer and the SP have their key pairs consisting of secret key $\mathrm{sk}(\mathrm{party})$ and public key $\mathrm{pk}(\mathrm{party})$, where $\mathrm{party} \in \{\mathrm{C}, \mathrm{SP}\}$ for the customer and the SP accordingly.
         \item Both the customer and the SP can create and verify digital signatures created by the customer $\mathrm{sig}_{\mathrm{sk}(\mathrm{C})}$ and the SP $\mathrm{sig}_{\mathrm{sk}(\mathrm{SP})}$.
@@
         \item use common symmetric encryption $\mathrm{E}_\mathrm{key}(\cdot)$ and decryption $\mathrm{D}_\mathrm{key}(\cdot)$ operations.
-        \item has access to anonymous payments blockchain, message board, and storage network.
+        \item have access to anonymous payments blockchain, message board, and storage network.
     \end{itemize}
@@
         \item accepts packages from unknown customers.
-        \item accepts payments with anonymous cryptocurrencies as described in section~\ref{payment-for-services}.
+        \item accepts payments with cash and anonymous cryptocurrencies as described in Section~\ref{payment-for-services}.
     \end{itemize}
@@
     \begin{itemize}
-        \item accepts as evidence in a dispute the $\mathrm{PoD}$, $\mathrm{PoP}$, and payment $\mathrm{attestation}$ as described in section~\ref{fairness}.
+        \item accepts as evidence in a dispute the $\mathrm{PoD}$, $\mathrm{PoP}$, and payment $\mathrm{receipt}$ as described in Section~\ref{fairness}.
     \end{itemize}
@@
     \begin{itemize}
-        \item supports anonymous, i.e., untraceable and (ideally) unlinkable transactions as specified in section~\ref{sec:pseudo-anon}.
-        \item supports uniquely identifying transaction either via separate address, memo field, or other similar mechanisms as described in section ~\ref{payment-for-services}. 
+        \item supports anonymous, i.e., untraceable and (ideally) unlinkable transactions as specified in Section~\ref{sec:pseudo-anon}.
+        \item supports uniquely identifying transactions via a dedicated address, memo field, or other similar mechanisms as described in Section ~\ref{payment-for-services}. 
     \end{itemize}
@@
 \noindent \textbf
-{Package}\label{package} is a physical container prepared by the customer encompassing all $\mathrm{materials}$ required by the SP to provide the service, a randomly generated provision identifier used to anonymously track the provision throughout the protocol's steps, and the customer's public key $\mathrm{pk(C)}$ used to encrypt the result published on the public storage network.
+{Package}\label{package} is a physical container prepared by the customer encompassing all $\mathrm{materials}$ required by the SP to provide the service.
 
@@
 \end{eqnarray}
-
-% \begin{eqnarray}
-%   \quad L_{\mathrm{H}}(H) & \equiv & (\begin{array}[t]{l}H_{\mathrm{p}}, H_{\mathrm{o}}, H_{\mathrm{c}}, H_{\mathrm{r}}, H_{\mathrm{t}}, H_{\mathrm{e}}, H_{\mathrm{b}}, H_{\mathrm{d}},\\ H_{\mathrm{i}}, H_{\mathrm{l}}, H_{\mathrm{g}}, H_{\mathrm{s}}, H_{\mathrm{x}}, H_{\mathrm{m}}, H_{\mathrm{n}} \; )\end{array} \\
-%   \quad L_{\mathrm{B}}(B) & \equiv & \big( L_{\mathrm{H}}(B_{\mathrm{H}}), \widetilde{L}_{\mathrm{T}}^*(B_{\mathbf{T}}), L_{\mathrm{H}}^*(\hyperlink{ommer_block_headers_B__U}{B_{\mathbf{U}}}) \big)
-%   \end{eqnarray}
 
@@
 also:
-\(\mathrm{T}_\mathrm{issue} < \mathrm{T}_\mathrm{pay} < \mathrm{T}_\mathrm{provide}\)
+\(\mathrm{T}_\mathrm{issue} \leq \mathrm{T}_\mathrm{pay} \leq \mathrm{T}_\mathrm{provide}\)
 
@@
 
-\item $\mathrm{cid}$ - content identifier as specified in section~\ref{storage-network}.
+\item $\mathrm{cid}$ - content identifier as specified in Section~\ref{storage-network}.
 \item $\mathrm{provisionID}$ - the number uniquely identifying the transaction previously generated by the customer.
@@
 \noindent \textbf
-{Payment attestation}\label{payment-attestation} proves that the customer did the payment.
-Since the evidence depends on a particular blockchain (see section ~\ref{payment-for-services}), we refer to it symbolically as
-\(\mathrm{attestation}\).
+{Payment receipt}\label{payment-receipt} proves that the customer did the payment.
+Since the evidence depends on a particular blockchain (see Section~\ref{payment-for-services}), we refer to it symbolically as
+$\mathrm{receipt}$.
 
@@
 
-In this section, we describe each step of the protocol, also shown in the figure~\ref{fig:protocol-diagram}.
+In this section, we describe each step of the protocol, also shown in the Figure~\ref{fig:protocol-diagram}.
 
@@
 
-If the provision has not been paid in cash, the customer should pay for the transaction with the predefined anonymous payment blockchain (see section~\ref{payment-for-services}).
-In return, the customer receives the $\mathrm{attestation}$ that should be disclosed in case of a dispute.
+If the provision has not been paid in cash, the customer should pay for the transaction with the predefined anonymous payment blockchain (see Section~\ref{payment-for-services}).
+In return, the customer receives the $\mathrm{receipt}$ that should be disclosed in case of a dispute.
 
@@
 \[
-\mathrm{attestation \gets payment(address)}
+\mathrm{receipt \gets payment(address)}
 \]
@@
 After the service is finished, a result should be created. 
-Next, the result is encrypted using a shared key derived from the customer's public key $\mathrm{pk(C)}$ and the SP's secret key $\mathrm{sk(S)}$ using Diffie-Hellman key exchange (DHKE) method.
+Next, the result is encrypted using a shared key derived from the customer's public key $\mathrm{pk(C)}$ and the SP's secret key $\mathrm{sk(S)}$ using Diffie-Hellman key exchange (DHKE) method~\cite{diffieNewDirectionsCryptography1976}.
 The encrypted result is then uploaded on the content addressable network (such as IPFS). In return, the content identifier ($\mathrm{cid}$) is created.
@@
 The protocol terminates after the last step, after starting a dispute, or after a party has not completed its designated action in time.
-Therefore, all positions except $\mathrm{\sigma_n}$ are termination positions.
+Therefore, all positions but $\mathrm{\sigma_n}$ are termination positions.
 
@@
 To mitigate the issue, we designed the protocol so that the SP who follows the protocol is always in an advantaged position, and therefore has no reason to start a dispute.
-On the other hand, the customer can start a dispute at any time of the protocol, but only the actual misbehavior of the SP makes him win the case.
+On the other hand, the customer can start a dispute at any time of the protocol, but only the actual misbehavior of the SP makes him win the conflict.
 
@@
 For example, paying for the invoice twice does not cause any effect on the curse of the protocol.
-\item Once published, the result is available to the customer on the storage network. The idea of guaranteeing it cryptographically is discussed in section~\ref{sec:discussion}.
+\item Once published, the result is available to the customer on the storage network. The idea of guaranteeing it cryptographically is discussed in Section~\ref{sec:discussion}.
 \item Winning the dispute leads to a neutral position ($\neutral$).
@@
 
-The detailed description of each step and the justification %JS proof lub justification ?
+The detailed description of each step and the justification
 of the outcome positions is given in~\ref{app:proof-of-fairness}.
@@
 
-The figure~\ref{fig:misbehaviour} shows the transitions of positions when the SP tries to misbehave and does not execute service after receiving the payment.
+The Figure~\ref{fig:misbehaviour} shows the transitions of positions when the SP tries to misbehave and does not execute service after receiving the payment.
 The customer reacts by starting a dispute and the protocol ends up neutral to the customer and disadvantaged to the SP positions.
@@
 \end{figure}
-the rational path for both parties is to follow the protocol as shown in the figure~\ref{fig:rational}.
+the rational path for both parties is to follow the protocol as shown in the Figure~\ref{fig:rational}.
 
@@
 
-We developed and tested our prototype in the following environment:
-
-\begin{itemize}
-  \item{OS} — Arch Linux 5.11.8
-  \item{Docker} — 20.10.5
-  \item{CPU} — Intel(R) Core(TM) i7-4790 (8) 4.00~GHz
-  \item{RAM} — 16 GB DDR3
-  \item{Storage} — Samsung PM85 256~GB SSD
-
-  \item{monerod and monero-wallet-cli} — v0.18.1.2
-  \item{Powergate} — v2.6.2
-  \item{Ganache} — v7.5.0
-  \item{Solidity} — v0.8.17
-  \item{ReactJS} — v18.0.25
-  \item{web3.js} — v1.8.1
-  \item{crypto-js} — v4.1.1
-\end{itemize}
+We developed and tested our prototype in the following environment: OS — Arch Linux 5.11.8; Docker — 20.10.5; CPU — Intel(R) Core(TM) i7-4790 (8) 4.00~GHz; RAM — 16 GB DDR3; Storage — Samsung PM85 256~GB SSD; monerod and monero-wallet-cli — v0.18.1.2; Powergate — v2.6.2; Ganache — v7.5.0; Solidity — v0.8.17; ReactJS — v18.0.25; web3.js — v1.8.1; crypto-js — v4.1.1.
 
@@
 
-The customer gets some testing Monero funds using \url{https://community.rino.io/faucet/stagenet/} faucet service.
-
-Next, the customer enables per-transaction proof generation (payment \texttt{attestation}) by setting \texttt{set store-tx-info 1} for his wallet.
+The customer gets some testing Monero funds using faucet service\footnote{Monero, faucet, \url{https://community.rino.io/faucet/stagenet/}, \LASTVISITED}.
+
+Next, the customer enables per-transaction proof generation (payment \texttt{receipt}) by setting \texttt{set store-tx-info 1} for his wallet.
 Proof generation is required to verify the payment in case of a dispute.
@@
 
-  \item[4.] The customer (using the \texttt{monero-wallet-cli transfer}) sends the payment to the designated in the smart contract \texttt{paymentAddress} and stores the payment attestation (using \texttt{monero-wallet-cli get\_tex\_key <tx-id>}) in case of a dispute.
+  \item[4.] The customer (using the \texttt{monero-wallet-cli transfer}) sends the payment to the designated in the smart contract \texttt{paymentAddress} and stores the payment receipt (using \texttt{monero-wallet-cli get\_tex\_key <tx-id>}) in case of a dispute.
 
@@
   \item[8.] Meantime, the Customer subscribes to Ethereum and waits until the SP publishes the Proof Of Provision.
- Once the Proof Of Provision is published the Customer downloads the result using either: IPFS network via \texttt{https://dweb.link/<cid>} or Lotus network using \texttt{lotus retrieve <cid> <minerID>}.
+ Once the Proof Of Provision is published the Customer downloads the result using either: IPFS network via \url{https://dweb.link/<cid>} or Lotus network using \texttt{lotus retrieve <cid> <minerID>}.
 
@@
 \noindent%
-\begin{minipage}{\linewidth}% to keep image and caption on one page
-\makebox[\linewidth]{%        to center the image
+\begin{minipage}{\linewidth}
+\makebox[\linewidth]{
 \includegraphics[height=0.95\textheight,keepaspectratio]{anonser-experiment1.pdf}}
-\captionof{figure}{Steps of the experiment, first part.}\label{fig:anonser-experiment1}%      only if needed  
+\captionof{figure}{Steps of the experiment, first part.}\label{fig:anonser-experiment1}
 \end{minipage}
@@
 \noindent%
-\begin{minipage}{\linewidth}% to keep image and caption on one page
-\makebox[\linewidth]{%        to center the image
+\begin{minipage}{\linewidth}
+\makebox[\linewidth]{
 \includegraphics[height=0.95\textheight,keepaspectratio]{anonser-experiment2.pdf}}
-\captionof{figure}{Steps of the experiment, second part.}\label{fig:anonser-experiment2}%      only if needed  
+\captionof{figure}{Steps of the experiment, second part.}\label{fig:anonser-experiment2}
 \end{minipage}
@@
 \paragraph{Fariness}
-As shown in Section~\ref{sec:steps} and Appendix~\ref{app:proof-of-fairness}, 
+As shown in Section~\ref{sec:steps} and~\ref{app:proof-of-fairness}, 
 the protocol is fair.
@@
 \paragraph{Anonymity}
-We achieved anonymity by using anonymous payment methods such as cash or privacy-preserving payment blockchains (e.g.
-Monero), and decentralized storage networks like IPFS and Filecoin, allowing the customer to interact with the protocol without revealing his identity at any step of the protocol.
+We achieved anonymity by using anonymous payment methods such as cash or privacy-preserving payment blockchains (e.g., Monero), and decentralized storage networks like IPFS and Filecoin, allowing the customer to interact with the protocol without revealing his identity at any step of the protocol.
 
@@
 \begin{itemize}
-  \item deploying the smart contract was $0.000000002227 \frac{\mathrm{ETH}}{\mathrm gas} \cdot 1456577 \mathrm{gas} \cdot 1261.97 \frac{\mathrm{USD}}{\mathrm{ETH}} = 4.09 \mathrm{USD}$; 
-  \item Proof of delivery was $0.000000002227 \mathrm{\frac{ETH}{gas}} \cdot 129649 \mathrm{gas} \cdot 1261.97 \frac{\mathrm{USD}}{\mathrm{ETH}} = 0.29 \mathrm{USD}$; 
-  \item Proof of provision was $0.000000002227 \mathrm{\frac{ETH}{gas}} \cdot 149130 \mathrm{gas} \cdot 1261.97 \frac{\mathrm{USD}}{\mathrm{ETH}} = 0.33 \mathrm{USD}$.
-\end{itemize}
-
-% Storing data in and retreiving data from Filecoin costs FIL cryptocurrency. Interacting with Filecoin is done via deals, which cost some FIL coins. 
-% Deals are made in a free market, where miners compete for the best price.
-
-% Selecting miners is not part of the Filecoin protocol. It is up to the customer to select the miners.
-
-% The list of all miners can be obtained by either quering Filecoin node or by visiting webpages like \url{https://filrep.io}.
-
-% Once we select a miner, we can use the \texttt{lotus} CLI to query it for the price of the deal.
-The price of the deal is determined by the miner and depends on the size of the payload, the duration of the deal, and the miner configuration.
-The price of the deal is denominated in FIL.
-% At the of the experiment (Jan.
-03, 2023) the price for one FIL coin was $5.28 \mathrm{USD}$\footnote{CoinMarketCap, Cryptocurrency Prices, \url{https://coinmarketcap.com/currencies/filecoin/}, (last visited Jan.
-03, 2023)}.
-% Because of the volatilaty of all the deal's parameters, the price is hard to predict.
-However, we can assume that the size of the result document is 1MiB, and the duration of the deal is 180 days (minimal duration), sector size is 256KiB,  and the miner price is .
-
-% Moreover, Filecoin allows publishing deals for free by using reputation based incentivisation layer\footnote{Filecoin, Filecoin Plus Overview, \url{https://docs.filecoin.io/store/filecoin-plus/overview/}, (last visited Jan.
-04, 2023)}.
-
-% Since the price is dynamic 
-% Each miner publishes the 
-% Deals are executed in a free market
+  \item Deploying the smart contract cost $0.000000002227 \frac{\mathrm{ETH}}{\mathrm gas} \cdot 1456577 \mathrm{gas} \cdot 1261.97 \frac{\mathrm{USD}}{\mathrm{ETH}} \approx 4.09 \mathrm{USD}$; 
+  \item Proof of delivery cost $0.000000002227 \mathrm{\frac{ETH}{gas}} \cdot 129649 \mathrm{gas} \cdot 1261.97 \frac{\mathrm{USD}}{\mathrm{ETH}} \approx 0.29 \mathrm{USD}$; 
+  \item Proof of provision cost $0.000000002227 \mathrm{\frac{ETH}{gas}} \cdot 149130 \mathrm{gas} \cdot 1261.97 \frac{\mathrm{USD}}{\mathrm{ETH}} \approx 0.33 \mathrm{USD}$.
+\end{itemize}
 
@@
 The first approach is more feasible in the near future.
-It would require creating a large set of experts in a field that, in case of dispute, would receive all the proofs ($\mathrm{PoD}$, $\mathrm{PoP}$, payment $\mathrm{attestation}$ as well as any other proofs significant to the case) that could be queried by the experts in zero-knowledge fashion, i.e., they could ask a limited number of questions to the proofs and getting yes/no answers.
+It would require creating a large set of experts in a field that, in case of dispute, would receive all the proofs ($\mathrm{PoD}$, $\mathrm{PoP}$, payment $\mathrm{receipt}$ as well as any other proofs significant to the case) that could be queried by the experts in zero-knowledge fashion, i.e., they could ask a limited number of questions to the proofs and getting yes/no answers.
 The case would be fully confidential as they would not be able to query personal information.
@@
 
-\subsection{Anonymous delivery}\label{sec:anonymous-delivery}
-We assume the customer being able to anonymously deliver the materials to the SP.
-The assumption is reasonable as the customer stays anonymous and the SP stays public.
-As a result, the customer can use any delivery service that does not require revealing the personal information, e.g., a trusted person, a drop box, or a post office.
-
-The protocols for e-commerce transactions can not rely on this assumption because the customer is the recipent of the package and the SP is the sender.
-Therefore, there arises the problem of hiding the customer's identity from the SP.
-The problem is not trivial as the SP needs to know the customer's address to deliver the package.
-The problem is discussed in~\cite{altawyLelantosBlockchainBasedAnonymous2017}.
-
 \subsection{Formal Verification}\label{sec:formal-verification}
@@
 
-Using the definition~\ref{def:fairness} we showed that the protocol achieves fairness by the proof of delivery, payment attestation, and proof of provision published on the message board.
+Using the definition~\ref{def:fairness} we showed that the protocol achieves fairness by the proof of delivery, payment receipt, and proof of provision published on the message board.
 
 Finally, we pinpointed further improvements like decentralized dispute resolution, self-sovereign identifiers, and anonymous package delivery via courier.
-
-%JS dodac acknowlegements
 
@@
 \fi
-%JS za bibliografie tak by byl w calosci a nie przedzielony bibliografią
-%biogtafie na samym koncu
-
-%JS opis nie pasuje do rysunku - zaczyna sie od 1 a rysunek od 0
-%JS rysunek/schemat powinien byc zatytułowany, odnosniki do niego w tekscie opisujace co na nim jest
 

### 2023-03-21 paper/contributions.tex
add contributions, coverletter and biographies

\documentclass[preprint,3p]{elsarticle}

\input{constants.tex}
\begin{document}
{\Large Contributions \par}

\vspace{2cm}

\textbf{\STANLONG}: Conceptualization, Methodology, Software, Validation, Formal analysis, Investigation, Resources, Data Curation, Writing - Original Draft, Writing - Review \& Editing, Visualization

\vspace{1cm}

\textbf{\JULLONG}: Supervision, Project administration, Funding acquisition, Writing - Original Draft, Writing - Review \& Editing

\vspace{1cm}

\textbf{\HIGILONG}: Validation, Writing - Review \& Editing, Methodology

\end{document}

### 2023-03-21 paper/coverletter.tex
add contributions, coverletter and biographies

\documentclass[preprint,3p]{elsarticle}

\input{constants.tex}
\begin{document}

Dear IEEE Access Editorial Board,

I am writing to submit my manuscript titled "\TITLE" for consideration in IEEE Access. The manuscript proposes a solution that enables service providers to offer sensitive services, such as legal advice, genetic testing, or STD tests, without collecting personal data, and therefore without violating data privacy regulations.

The proposed protocol uses blockchain technology to achieve fairness and anonymity, anonymous payment methods such as cash and cryptocurrencies, and distributed content-addressable storage networks to deliver results. The manuscript compares the proposed protocol with existing solutions and demonstrates its advantages, including weaker assumptions for anonymity, support for physical materials, and practicality.

The main contributions of the paper are as follows:
\begin{enumerate}
    \item We design a protocol for anonymous provision of privacy-sensitive services
    \item Privacy guarantee was achieved using anonymous payment methods
    \item We implemented demonstration of the practical application of the protocol
    \item The fairness of the protocol was proven
    \item The source code of the protocol has been made publicaly available
\end{enumerate}

Thank you for your time and consideration. I look forward to the opportunity to share my work with the IEEE Access community and contribute to the advancement of the field.

\noindent Sincerely,

\noindent Stanislaw Baranski

\end{document}

### 2023-03-21 paper/higinio-bio.tex
add contributions, coverletter and biographies

\documentclass[preprint,3p]{elsarticle}

\input{constants.tex}
\begin{document}
{Higinio Mora} received the B.S. degree in computer science engineering and the B.S. degree in business studies from the University of Alicante, Spain, in 1996 and 1997, respectively, and the Ph.D. degree in computer science from the University of Alicante in 2003. Since 2002, he has a member of the faculty of the Computer Technology and Computation Department, University of Alicante, where he is currently an Associate Professor and a Researcher with the Specialized Processors Architecture Laboratory. His research interests include computer modeling, computer architectures, high-performance computing, embedded systems, the Internet of Things, and cloud computing paradigm.
\end{document}

### 2023-03-21 paper/julian-bio.tex
add contributions, coverletter and biographies

--- 2023-01-30 paper/ieee.tex
@@
-\documentclass{ieeeaccess}
-\usepackage{cite}
-
-\usepackage{amsmath,amssymb,amsfonts}
-\usepackage{algorithmic}
-\usepackage{graphicx}
-\usepackage{textcomp}
-\usepackage{float}
-
-\usepackage{caption}
-\usepackage{url}
-\usepackage{listings}
-\usepackage{pdfpages}
-\usepackage[english]{babel}
-\usepackage{xcolor,colortbl}
-\usepackage{scalerel}
-\newtheorem{theorem}{Theorem}
-\newtheorem{definition}{Definition}
+\documentclass[preprint,3p]{elsarticle}
 
 \input{constants.tex}
-
-\newcommand{\plus}{+}
-\newcommand{\minus}{-}
-\newcommand\neutral[1][.75]{\mathbin{\ThisStyle{\vcenter{\hbox{%
-  \scalebox{#1}{$\SavedStyle\bullet$}}}}}%
-}
-
-\newcommand{\customer}{customer}
-\renewcommand{\sp}{SP}
-
-\newcommand{\normal}{n}
-\newcommand{\dispute}{d}
-\newcommand{\abnormal}{\overline{n}}
-\newcommand{\abdispute}{\overline{d}}
-
-\newcommand{\PoD}{$\mathrm{PoD}$}
-\newcommand{\PoP}{$\mathrm{PoP}$}
-\newcommand{\cid}{$\mathrm{cid}$}
-
-\newcommand{\floor}[1]{\left\lfloor #1 \right\rfloor}
-\newcommand{\ceil}[1]{\left\lceil #1 \right\rceil}
-
-\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
-    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
-
 \begin{document}
-
-\history{Date of publication xxxx 00, 0000, date of current version xxxx 00, 0000.}
-\doi{10.1109/ACCESS.2022.0122113}
-\title{\TITLE}
-
-\author{\uppercase{\STANLONG} \authorrefmark{1},
-\uppercase{\JULLONG{}} \authorrefmark{1}}
-
-\address[1]{Department of Electronic, Telecommunication and Informatics, Gdansk University of Technology, Narutowicza 11/12 Gdansk Poland (e-mail: stanislaw.baranski@pg.edu.pl, julian.szymanski@eti.pg.edu.pl}
-
-\tfootnote{The work has been supported partially by the founds of Department of Computer Architecture Faculty of Electronics, Telecommunications and Informatics, Gdańsk University of Technology.}
-
-\markboth{\STAN{}, \JUL{} : \TITLE}
-{\STAN{}, \JUL{} : \TITLE}
-
-\corresp{Corresponding author: Stanislaw Baranski (e-mail: stanislaw.baranski@pg.edu.pl).}
-
-\begin{abstract}
-  \ABSTRACT{}
-\end{abstract}
-
-\newcommand{\sep}{,}
-\begin{keywords}
-Anonymity\sep{} blockchain\sep{} fair-exchange\sep{} physical delivery\sep{} privacy\sep{} services
-\end{keywords}
-
-\titlepgskip=-21pt
-
-\maketitle
-
-\def\JOURNALIEEE{IEEE}
-\def\JOURNALELS{ELS}
-
-\def\JOURNAL{\JOURNALIEEE}
-
-\input{content}
-
-\EOD
-
-\bibliographystyle{IEEEtran}
-
-% Loading bibliography database
-\bibliography{bibliography}
-
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{stanislaw.jpg}}]{Stanis\L{}aw Bara{\'n}ski} received BEng in 2019 and MSc in 2020 in informatics at Gdańsk University of Technology.
-Currently, he is a PhD student at the Department of Computer Architecture, Faculty of Electronics, Telecommunications and Informatics, Gdansk University of Technology.
-
-His research interests include blockchains, applied cryptography, and secure computation; particularly the issue of blockchain-based internet voting, but also other areas that currently depend on trusted third parties.
-
-He likes to validate his ideas in practice, developing them up to the commercialization stage.
-He is the author of multiple software products that have reached success in the market.
-His blockchain-based internet voting project has been funded by the Stellar Community Fund for the most useful Stellar application.
-\end{IEEEbiography}
-
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{julian.jpg}}]{JULIAN SZYMA{\'N}SKI}  received the PhD degree in 2009 and DSc in 2020 at Gdańsk University of Technology.
+{Julian Szyma{\'n}ski}  received the PhD degree in 2009 and DSc in 2020 at Gdańsk University of Technology.
 He is currently with the Department of Computer
@@
 His research results find applications in web search engines and systems of automated text categorization.
-He manages research projects for processing the information in Wikipedia, where the main goal is to extract and structuralize textual knowledge and construct interfaces capable of communicating in natural language.
-Besides his research in the information retrieval domain, he was involved in projects related to cognitive science.
+He manages research projects for processing the information in Wikipedia.
 His mainstream of this research is building semantic memory models that improve natural language processing.
-He also worked on analyzing human emotions, by mining EEG signals.
-His results are implemented in the form of brain-machine interfaces for disabled people.
-He also works on analyzing data within the IoT domain and its secure storage on the blockchain.
-He is involved in the project, where acquisition of data from sensors placed in beehives  allows one to predict apiary development and detect abnormalities.
-
-He was a committee member and reviewer in  many international
-conferences as well as served as guest editor preparing special issues of prestigious journals. 
-\end{IEEEbiography}
-
 \end{document}

### 2023-03-21 paper/stanislaw-bio.tex
add contributions, coverletter and biographies

\documentclass[preprint,3p]{elsarticle}

\input{constants.tex}
\begin{document}
{Stanis\l{}aw Bara{\'n}ski} received BEng in 2019 and MSc in 2020 in informatics at the Gdańsk University of Technology. 
Currently, he is a PhD student at the Department of Computer Architecture, Faculty of Electronics, Telecommunications and Informatics, Gdańsk University of Technology.

His research interests include blockchains, applied cryptography, and secure computation; particularly the issue of blockchain-based internet voting, but also other protocols that currently depend on trusted third parties.

He likes to validate his ideas in practice, developing them up to the commercialization stage. He is the author of multiple software products that have reached success in the market.
\end{document}

### 2023-03-21 paper/content.tex
move footnotes to references

@@
 It can be instantiated with either the local court or police, or one of the blockchain
-dispute resolution services like Themis~\cite{mengThemisDecentralizedEscrow2019}, Kleros~\cite{bergollaKlerosSociolegalCase2022,gudkovCrowdArbitrationBlockchain2020}, Aragon Court\footnote{Aragon Court, Decentralized Dispute Resolution Protocol, https://aragon.org/aragon-court, (last visited Jan.
-10, 2023)}, LTO Network\footnote{LTO Network, a hybrid blockchain application development platform for securing, verifying, and exchanging enterprise information, https://lto.network/, (last visited Jan.
-17, 2023)}, and other Online Dispute Resolution platforms~\cite{allenGovernanceBlockchainDispute2019}.
+dispute resolution services like Themis~\cite{mengThemisDecentralizedEscrow2019}, Kleros~\cite{bergollaKlerosSociolegalCase2022,gudkovCrowdArbitrationBlockchain2020}, Aragon Court~\cite{aragonDecentralizedDisputeResolution}, LTO Network~\cite{ltonetworkNextGenBlockchainB2B,ltonetworkOnchainIdentitiesCredentials}, and other Online Dispute Resolution platforms~\cite{allenGovernanceBlockchainDispute2019}.
 
@@
 We assume that there is a way to anonymously deliver a package without revealing the customer personal information either via SP's drop box, Parcel Locker services (e.g.
-Amazon Locker, InPost\footnote{InPost, Parcel locker service, \url{https://inpost.pl/en}, \LASTVISITED}), a customer's trusted party, of even post office.
+Amazon Locker, InPost~\cite{inpostParcelLockerService}), a customer's trusted party, of even post office.
 
@@
 Themis~\cite{mengThemisDecentralizedEscrow2019} besides providing fair exchange protocol,
-also offers a semi-autonomous decentralized dispute resolution system that complies with the Web3 postulates of a decentralized web. Themis
-resolve disputes by a set of voluntary anonymous mediators participating
-in voting and deciding whether a party misbehaved. The honesty of
-mediators is achieved by the monetary incentivization and reputation
-system.
+also offers a semi-autonomous decentralized dispute resolution system that complies with the Web3 postulates of a decentralized web~\cite{ethereumWhatWeb3Why}.
+Themis resolve disputes by a set of voluntary anonymous mediators participating in voting and deciding whether a party misbehaved.
+The honesty of mediators is achieved by the monetary incentivization and reputation system.
 
@@
 
-Examples of blockchains that natively support confidential transactions are: Monero~\cite{vansaberhagenCryptoNote2013} (using Ring Signatures~\cite{noetherRingSignatureConfidential2015} or Bulletproofs~\cite{bunzBulletproofsShortProofs2018}), ZCash~\cite{ben-sassonZerocashDecentralizedAnonymous2014} (using zkSNARK~\cite{ben-sassonSNARKsVerifyingProgram2013}), Grin~\cite{fuchsbauerAggregateCashSystems2019} (using Mimblewimble~\cite{jedusorMIMBLEWIMBLE2016}), and IronFish~\footnote{IronFish, The Privacy Platform
-for web3, \url{https://ironfish.network}, \LASTVISITED} (using Sapling protocol~\cite{hopwoodZcashSaplingProtocol2022}).
-
-Overly techniques that achieve anonymity on top of non-privacy-preserving blockchains are: Ethereum's Tornado Cash\cite{pertsevTornadoCashPrivacy2019} (via zkSNARK~\cite{grothSizePairingbasedNoninteractive2016} and MiMC~\cite{albrechtMiMCEfficientEncryption2016}), Bitcoin's Wasabi\footnote{Wasabi Wallet, Open-source, non-custodial Bitcoin Wallet for desktop, \url{https://wasabiwallet.io/}, (last visited Nov.
-28, 2022)} (via CoinJoin \cite{maxwellCoinJoinBitcoinPrivacy2013}).
+Examples of blockchains that natively support confidential transactions are: Monero~\cite{vansaberhagenCryptoNote2013} (using Ring Signatures~\cite{noetherRingSignatureConfidential2015} or Bulletproofs~\cite{bunzBulletproofsShortProofs2018}), ZCash~\cite{ben-sassonZerocashDecentralizedAnonymous2014} (using zkSNARK~\cite{ben-sassonSNARKsVerifyingProgram2013}), Grin~\cite{fuchsbauerAggregateCashSystems2019} (using Mimblewimble~\cite{jedusorMIMBLEWIMBLE2016}), and IronFish~\cite{ironfishPrivateAnonymousEasy} (using Sapling protocol~\cite{hopwoodZcashSaplingProtocol2022}).
+
+Overly techniques that achieve anonymity on top of non-privacy-preserving blockchains are: Ethereum's Tornado Cash~\cite{pertsevTornadoCashPrivacy2019} (via zkSNARK~\cite{grothSizePairingbasedNoninteractive2016} and MiMC~\cite{albrechtMiMCEfficientEncryption2016}), Bitcoin's Wasabi~\cite{wasabiwalletBitcoinPrivacyWallet} (via CoinJoin~\cite{maxwellCoinJoinBitcoinPrivacy2013}).
 
@@
 \item separate address: each transaction uses an unique address associated with the transaction.
-Such addresses can be derived using Hierarchical Deterministic Wallets (BIP-32)\footnote{Bitcoin Improvement Proposals, Hierarchical Deterministic Wallets, \url{https://github.com/bitcoin/bips/blob/master/bip-0032.mediawiki}, (last visited Dec.
-03, 2022)} and published on message board, to achieve non-repudiation.
+Such addresses can be derived using Hierarchical Deterministic Wallets~\cite{wuilleBIP32HierarchicalDeterministic2012} and published on message board, to achieve non-repudiation.
 \item memo: the payments are sent to sigle SP account, but contain an extra field named ``memo'' filled with the unique indentifier $\textrm{provisionID}$. 
@@
 As the proof of payment is trivial in transparent and trackable blockchains, it gets more complicated when it comes to anonymous blockchains.
-Monero allows proving and checking payments via dedicated API\footnote{Monero, How to prove payment, \url{https://www.getmonero.org//resources/user-guides/prove-payment.html}, \LASTVISITED}.
-ZCash provides a mechanism called Payment Disclosure \footnote{Gareth Davies, An Introduction to Payment Disclosure in Zcash, \url{https://garethtdavies.medium.com/an-introduction-to-payment-disclosure-in-zcash-96748c209d49}, \LASTVISITED}.
+Monero allows proving and checking payments via dedicated API~\cite{moneroHowProvePayment}.
+ZCash provides a mechanism called Payment Disclosure~\cite{daviesIntroductionPaymentDisclosure2017}.
 We call the proof of payment a \textit{payment recepit}.
@@
   Tornado Cash \cite{pertsevTornadoCashPrivacy2019}.
-\item Message board: Open timestamps\footnote{Open timestamps, A timestamping proof standard, \url{https://opentimestamps.org}, \LASTVISITED}, Stampery \cite{crespoStamperyBlockchainTimestamping2017}, Bitcoin blockchain (Proof of Existence~\footnote{Proof of existence, An online service to prove the existence of documents, \url{https://docs.proofofexistence.com}, \LASTVISITED}, Chainpoint~\footnote{Chainpoint, Blockchain Proof and Anchoring Standar, \url{ https://chainpoint.org/}, \LASTVISITED}), Ethereum blockchain, or any other public blockchain that supports attaching extra data along the transaction.
-\item Storage network: IPFS \cite{benetIPFSContentAddressed2014}, Filecoin
-  \cite{protocollabsFilecoinDecentralizedStorage2017}, or Ethereum's
-  Swarm\cite{teamSWARMStorageCommunication2021}.
+\item Message board: Open timestamps~\cite{opentimestampsTimestampingProofStandard}, Stampery \cite{crespoStamperyBlockchainTimestamping2017}, Bitcoin blockchain (Proof of Existence~\cite{proofofexistenceWebApplicationProve}, Chainpoint~\cite{chainpointBlockchainProofAnchoring}), Ethereum blockchain, or any other public blockchain that supports attaching extra data along the transaction.
+\item Storage network: IPFS~\cite{benetIPFSContentAddressed2014}, Filecoin~\cite{protocollabsFilecoinDecentralizedStorage2017}, or Ethereum's
+  Swarm~\cite{teamSWARMStorageCommunication2021}.
 \end{enumerate}
@@
 \noindent \textbf
-{Content Identifier (cid)}\label{content-identifier-cid} is a term coined by IPFS\footnote{IPFS, Content addressing and CIDs, \url{https://docs.ipfs.tech/concepts/content-addressing}, (last visited Dec.
-01, 2022)}.
+{Content Identifier (cid)}\label{content-identifier-cid} is a term coined by IPFS~\cite{ipfsContentIdentifiersCIDs}.
 However, since our protocol does not depend on this particular implementation of the storage network, we let the $\mathrm{cid}$ be any other identifier that securely and uniquely points to the content.
@@
   \item{Anonymous payments} — we use the Monero blockchain \cite{noetherRingSignatureConfidential2015}.
-  \item{Storage netowork} — we use the Powergate\footnote{Powergate, \url{https://github.com/textileio/powergate}, (last visited Dec. 20, 2022)}, which is a wrapper around Filecoin and IPFS.
-  \item{Message board} — we use the Ethereum blockchain \cite{woodEthereumSecureDecentralised2014}; concretely, Truffle Ganache\footnote{Truffle Ganache, \url{https://trufflesuite.com/ganache/}, (last visited Dec.
-20, 2022)} and Solidity language.
-  \item{Customer and SP} — we create client side web application (webapp) using \texttt{React}\footnote{React, A JavaScript library for building user interfaces, \url{https://reactjs.org}, (last visited Dec.
-20, 2022)} for creating UI, and \texttt{web3.js}\footnote{web3.js, A JavaScript library for building on Ethereum, \url{https://web3js.org}, (last visited Dec.
-20, 2022)} for interaction with Ethereum.
-We use \texttt{MetaMask}\footnote{MetaMask, A crypto wallet \& gateway to blockchain apps, \url{https://metamask.io}, (last visited Dec.
-20, 2022)} browser extension for signing and submitting transactions to Ethereum's node.
-We use \texttt{monerod}\footnote{Monero, The Monero daemon \texttt{monerod}, \url{https://monerodocs.org/interacting/monerod-reference/}, (last visited Dec.
-20, 2022)} network client and \texttt{monero-wallet-cli}\footnote{Monero, The CLI client for Monero, \url{https://monerodocs.org/interacting/monero-wallet-cli-reference/}, (last visited Dec.
-20, 2022)} command-line interface for interacting with Monero blockchain.
+  \item{Storage netowork} — we use the Powergate~\cite{textilePowergate2023}, which is a wrapper around Filecoin and IPFS.
+  \item{Message board} — we use the Ethereum blockchain \cite{woodEthereumSecureDecentralised2014}; concretely, its local development version Truffle Ganache and Solidity language.
+  \item{Customer and SP} — we create client side web application (webapp) using \texttt{React.js} for creating UI, and \texttt{web3.js} library for interaction with Ethereum.
+We use \texttt{MetaMask} browser extension for signing and submitting transactions to Ethereum's node.
+We use \texttt{monerod} network client and \texttt{monero-wallet-cli} command-line interface for interacting with Monero blockchain.
 \end{itemize}
@@
 
-The customer gets some testing Monero funds using faucet service\footnote{Monero, faucet, \url{https://community.rino.io/faucet/stagenet/}, \LASTVISITED}.
+The customer gets some testing Monero funds using faucet service~\cite{rinoMoneroStagenetFaucet}.
 
@@
 The SP has no motivation to proceed with this kind of misbehavior other than putting the customer in a disadvantaged position caused by the lost dispute.}.
-However, the Filecoin network, which works as an incentivization layer on top of IPFS, increases the content availability via economic incentivisation (i.e., punishment in case of lack of proof of storage of the content\footnote{Filecoin, Slashing, \url{https://docs.filecoin.io/storage-provider/rewards/slashing}, (last visited Jan.
-03, 2023)})~\cite{protocollabsFilecoinDecentralizedStorage2017}.
+However, the Filecoin~\cite{protocollabsFilecoinDecentralizedStorage2017}, which works as an incentivization layer on top of IPFS, increases the content availability via economic incentivisation (i.e., punishment in case of lack of proof of storage of the content~\cite{filecoinSlashing}).
 
@@
 The price of gas at the time of the experiment (Jan.
-03, 2023) was $0.000000002227 \frac{\mathrm{ETH}}{\mathrm gas}$\footnote{Etherscan, Ethereum Gas Tracker, \url{https://etherscan.io/gastracker}, (last visited Jan.
-03, 2023)}, and the price of 1 $\mathrm{ETH}$ was $1261.97 \mathrm{USD}$.
+03, 2023, \url{https://etherscan.io/gastracker}) was $0.000000002227 \frac{\mathrm{ETH}}{\mathrm gas}$, and the price of 1 $\mathrm{ETH}$ was $1261.97 \mathrm{USD}$.
 
@@
 
-Centralized justice is the biggest obstacle in achieving a system that complies with Web 3.0 postulates\footnote{Web3, \url{https://en.wikipedia.org/wiki/Web3}, (last visited Jan. 05, 2023)}.
-
-The possible directions for mitigation of such issues are to either (i) replace local justice with blockchain dispute resolution systems like those proposed in Themis~\cite{mengThemisDecentralizedEscrow2019}, Kleros~\cite{bergollaKlerosSociolegalCase2022,gudkovCrowdArbitrationBlockchain2020}, Aragon Court\footnote{Aragon Court, Decentralized Dispute Resolution Protocol, https://aragon.org/aragon-court, (last visited Jan.
-10, 2023)}, LTO Network\footnote{LTO Network, a hybrid blockchain application development platform for securing, verifying, and exchanging enterprise information, https://lto.network/, (last visited Jan.
-17, 2023)}, and other Online Dispute Resolution platforms~\cite{allenGovernanceBlockchainDispute2019}; or (ii) make it infeasible to provide incorrect results.
+Centralized justice is the biggest obstacle in achieving a system that complies with Web3 postulates~\cite{ethereumWhatWeb3Why}.
+
+The possible directions for mitigation of such issues are to either (i) replace local justice with blockchain dispute resolution systems like those proposed in Themis~\cite{mengThemisDecentralizedEscrow2019}, Kleros~\cite{bergollaKlerosSociolegalCase2022,gudkovCrowdArbitrationBlockchain2020}, Aragon Court~\cite{aragonDecentralizedDisputeResolution}, LTO Network~\cite{ltonetworkNextGenBlockchainB2B}, and other Online Dispute Resolution platforms~\cite{allenGovernanceBlockchainDispute2019}; or (ii) make it infeasible to provide incorrect results.
 
@@
 Our research in the field showed that some jurisdictions require SPs to associate the diagnosis with the customer's personal information.
-For example, in Poland, all laboratories performing medical diagnostic tests, and collecting the material (except tests for HIV) are obligated to the unambiguous identification and verification of the identity of the patient from whom the material was collected~\footnote{Regulation of the Minister of Health of March 23, 2006, on quality standards for medical diagnostic and microbiological laboratories, \url{https://isap.sejm.gov.pl/isap.nsf/DocDetails.xsp?id=WDU20060610435}}.
+For example, in Poland, all laboratories performing medical diagnostic tests, and collecting the material (except tests for HIV) are obligated to the unambiguous identification and verification of the identity of the patient from whom the material was collected~\cite{ministerstwozdrowiaRegulationMinisterHealth2006}.
 

### 2023-04-05 paper/em.tex
add to electronic markets

--- 2023-03-21 paper/content.tex
@@
+\documentclass[sn-apa]{sn-jnl}
+
+\usepackage{multirow}%
+\usepackage{amsthm}%
+\usepackage{mathrsfs}%
+\usepackage[title]{appendix}%
+\usepackage{textcomp}%
+\usepackage{manyfoot}%
+\usepackage{booktabs}%
+\usepackage{algorithm}%
+\usepackage{algorithmicx}%
+\usepackage{algpseudocode}%
+
+\usepackage{amsmath,amssymb,amsfonts}
+\usepackage{algorithmic}
+\usepackage{graphicx}
+\usepackage{textcomp}
+\usepackage{float}
+\usepackage{etoolbox}
+
+\usepackage{caption}
+\usepackage{url}
+\usepackage{listings}
+\usepackage{pdfpages}
+\usepackage[english]{babel}
+\usepackage{xcolor,colortbl}
+\usepackage{scalerel}
+\newtheorem{theorem}{Theorem}
+\newtheorem{definition}{Definition}
+
+\newcommand{\customer}{customer}
+\renewcommand{\sp}{SP}
+
+\newcommand{\normal}{n}
+\newcommand{\dispute}{d}
+\newcommand{\abnormal}{\overline{n}}
+\newcommand{\abdispute}{\overline{d}}
+
+\newcommand{\PoD}{$\mathrm{PoD}$}
+\newcommand{\PoP}{$\mathrm{PoP}$}
+\newcommand{\cid}{$\mathrm{cid}$}
+
+\newcommand{\floor}[1]{\left\lfloor #1 \right\rfloor}
+\newcommand{\ceil}[1]{\left\lceil #1 \right\rceil}
+
+\newcommand{\plus}{+}
+\newcommand{\minus}{-}
+\newcommand\neutral[1][.75]{\mathbin{\ThisStyle{\vcenter{\hbox{%
+  \scalebox{#1}{$\SavedStyle\bullet$}}}}}%
+}
+
+\def\SINGLECOLUMN{SINGLE}
+\def\DOUBLECOLUMN{DOUBLE}
+\def\JOURNALIEEE{IEEE}
+\def\JOURNALELS{ELS}
+
+\newcommand\TITLE{Anonymous provision of privacy-sensitive services using blockchain and decentralised storage}
+\newcommand\STANLONG{Stanis\l{}aw Bara{\'n}ski}
+\newcommand\JULLONG{Julian Szyma{\'n}ski}
+\newcommand\HIGILONG{Higinio Mora}
+\newcommand\STAN{S. Bara{\'n}ski}
+\newcommand\JUL{J. Szyma{\'n}ski}
+\newcommand\HIGI{H. Mora}
+
+\newcommand\ABSTRACT{
+Lawyers, laboratories, auditors or banks, in order to provide services, require data often containing sensitive personal information.
+
+Examples of sensitive services are genetic tests, parenthood tests, STD tests, credit score computation or legal advice.
+
+The processing of personal data, especially when providing services involving sensitive data like health records, biological materials, or legal documents, exposes both users and service providers (SP) to privacy risks.
+
+SPs are at risk of violating GDPR, CPAA, and other legal regulations, while customers are at risk of losing their privacy.
+
+We observe that personal data is often only used for logistical purposes, such as payments or communication, and could be provided anonymously if such methods were available.
+
+We propose a solution that allows the provision of services without the collection of personal data.
+We use anonymous payment methods such as cash and anonymous cryptocurrencies, blockchain technology to achieve fairness, and distributed content-addressable storage networks to deliver results.
+
+Compared to other solutions, our protocol achieves anonymity with weaker assumptions, supports physical materials and conflict resolution, and in conflict-free transactions does not require the customer to interact with the blockchain, demonstrating better practicality.
+
+In this work, we analyse the fairness of our protocol and implement it using Ethereum technology as a message board, Monero as an anonymous payment method, and Powergate (IPFS and Filecoin) as a decentralised storage network.
+}
+
+\newcommand\ACKNOWLEDGEMENTS{
+The work has been supported partially by the founds of Department of Computer Architecture Faculty of Electronics, Telecommunications and Informatics, Gdańsk University of Technology.
+}
+
+\newcommand\LASTVISITED{(last visited Jan. 31, 2023)}
+
+\begin{document}
+
+\title[\TITLE]{\TITLE}
+
+% \author*[1]{\fnm{Stanis\l{}aw} \sur{Bara{\'n}ski}}\email{stanislaw.baranski@pg.edu.pl}
+
+% \author[1]{\fnm{Julian} \sur{Szyma{\'n}ski}}\email{julian.szymanski@pg.edu.pl}
+
+% \author[2]{\fnm{Higinio} \sur{Mora}}\email{hmora@dtic.ua.es}
+
+% \affil*[1]{\orgdiv{Department of Electronic, Telecommunication and Informatics}, \orgname{Gda{\'n}sk University of Technology}, \orgaddress{\street{Gabriela Narutowicza 11/12}, \city{Gda{\'n}sk}, \postcode{80-233}, \state{Pomorskie}, \country{Poland}}}
+
+% \affil[2]{\orgdiv{Department of Computer Science Technology and Computation}, \orgname{University of Alicante}, \orgaddress{\street{San Vicente del Raspeig}, \city{Alicante}, \postcode{03690}, \state{Alicante}, \country{Spain}}}
+
+\renewcommand{\sep}{,}
+
+\abstract{\ABSTRACT}
+
+\keywords{Anonymity\sep{} blockchain\sep{} diagnosis\sep{} e-commerce\sep{} fair-exchange\sep{} privacy}
+
+\maketitle
+
 \section{Introduction}
@@
 
-Providing personal information exposes users to privacy risks, i.e. potential loss of control over personal information~\cite{smithInformationPrivacyResearch2011}.
+Providing personal information exposes users to privacy risks, i.e. potential loss of control over personal information~\citep{smithInformationPrivacyResearch2011}.
 
@@
 for insider disclosure, unauthorized access, or commercial gains. For example, by reselling it to marketers, financial institutions, other businesses, government agencies, or even cybercriminals. 
-In turn, it can lead to an unintentional violation of the GDPR or CCPA, profiled advertisements or even criminal activities like identity theft or illegal tracking and surveillance~\cite{smithInformationPrivacyResearch2011}.
+In turn, it can lead to an unintentional violation of the GDPR or CCPA, profiled advertisements or even criminal activities like identity theft or illegal tracking and surveillance~\citep{smithInformationPrivacyResearch2011}.
 
@@
         \item \textbf{Symmetric encryption}, to encrypt and decrypt results published on the public networks.
-        \item \textbf{Public-key cryptography}, and \textbf{Diffie-Helman key exchange (DHKE)} to derive shared secrets for symmetric encryption.
+        \item \textbf{Diffie-Helman key exchange (DHKE)} to derive shared secrets for symmetric encryption.
         \item \textbf{Digital signatures}, to achieve authentication and non-repudiation of actions. 
@@
 Some authors have proposed blockchain-based fair-exchange systems that could be adapted to service provision; however, to our best knowledge, we are the first to propose a system that satisfies all the properties stated above.
-Especially anonymity and physical materials delivery were rarely addressed together, and if so, the protocol was based on TTP and impractical assumptions on banking system~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} or did not address the conflict between parties~\cite{altawyLelantosBlockchainBasedAnonymous2017}.
+Especially anonymity and physical materials delivery were rarely addressed together, and if so, the protocol was based on TTP and impractical assumptions on banking system~\citep{birjoveanuAnonymityFairexchangeEcommerce2015} or did not address the conflict between parties~\citep{altawyLelantosBlockchainBasedAnonymous2017}.
 
@@
 To our best knowledge, the first system that allowed for fair exchange of physical products was proposed by Zhang et al.
-in 2006~\cite{zhangPracticalFairExchangeEPayment2006}.
+in 2006~\citep{zhangPracticalFairExchangeEPayment2006}.
 The protocol uses buyer's bank as TTP, and assumes no coalition between parties to achieve anonymity.
@@
 
-Authors of~\cite{mohammedalarajFairnessPhysicalProducts2012} proposed an protocol for fair-exchage involving physical materials delivery.
-The protocol assumes the existence of an offline~\footnote{\textit{Offline} (also called \textit{optimistic}) TTP compared to \textit{online} TTP is in improvement which assumes the TTP being involved only in the case of a dispute between parties~\cite{rayFairExchangeEcommerce2002}.} TTP that is involved only in the event of a dispute.
+Authors of~\citep{mohammedalarajFairnessPhysicalProducts2012} proposed an protocol for fair-exchage involving physical materials delivery.
+The protocol assumes the existence of an offline~\footnote{\textit{Offline} (also called \textit{optimistic}) TTP compared to \textit{online} TTP is in improvement which assumes the TTP being involved only in the case of a dispute between parties~\citep{rayFairExchangeEcommerce2002}.} TTP that is involved only in the event of a dispute.
 The protocol works as follows:
@@
 
-Authors of~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} proposed a protocol involving physical products, which guarantees anonymity of both buyer and seller.
+Authors of~\citep{birjoveanuAnonymityFairexchangeEcommerce2015} proposed a protocol involving physical products, which guarantees anonymity of both buyer and seller.
 They achieve it with the introduction of an online TTP that validates coins and guarantees fairness.
-Later, they proposed many extensions to the protocol, namely, in~\cite{birjoveanuPreservingAnonymityFair2018} they proposed an anonymous e-commerce protocol that governs complex transactions, in~\cite{birjoveanuAnonymityComplexTransactions2019} they extend the anonymity for both buyers and sellers (in our case SPs), and in~\cite{birjoveanuFairExchangeECommerce2020} they proposed a protocol that supports chained transactions (involving multiple active intermediaries).
-Finally in~\cite{birjoveanuTwoPartyECommerceProtocols2022} they proposed improved protocol named PPPDCP (Protocol with Physical Product Delivery Providing Customer's Privacy).
-
-Anonymity is ensured by using anonymous communication channel over Tor~\cite{dingledineTorSecondGenerationOnion2004} and blind signatures~\cite{chaumSecurityIdentificationTransaction1985}.
+Later, they proposed many extensions to the protocol, namely, in~\citep{birjoveanuPreservingAnonymityFair2018} they proposed an anonymous e-commerce protocol that governs complex transactions, in~\citep{birjoveanuAnonymityComplexTransactions2019} they extend the anonymity for both buyers and sellers (in our case SPs), and in~\citep{birjoveanuFairExchangeECommerce2020} they proposed a protocol that supports chained transactions (involving multiple active intermediaries).
+Finally in~\citep{birjoveanuTwoPartyECommerceProtocols2022} they proposed improved protocol named PPPDCP (Protocol with Physical Product Delivery Providing Customer's Privacy).
+
+Anonymity is ensured by using anonymous communication channel over Tor~\citep{dingledineTorSecondGenerationOnion2004} and blind signatures~\citep{chaumSecurityIdentificationTransaction1985}.
 Fair exchange, physical delivery, and dispute resolution is achieved using delivery cabinet (DC) under the seller's control (e.g.
@@
 The main problem was the dependency on TTP, which significantly reduced the performance, security, and robustness of such protocols.
-The protocols that do not use TTP struggle with high computation and communication overhead~\cite{hinarejosSolutionSecureCertified2019}.
-
-Authors of ~\cite{hinarejosSolutionSecureCertified2019} replaced the TTP with blockchain (concretely Bitcoin blockchain as a reference implementation) that acts as a secure, verifiable, and decentralized TTP.
+The protocols that do not use TTP struggle with high computation and communication overhead~\citep{hinarejosSolutionSecureCertified2019}.
+
+Authors of ~\citep{hinarejosSolutionSecureCertified2019} replaced the TTP with blockchain (concretely Bitcoin blockchain as a reference implementation) that acts as a secure, verifiable, and decentralized TTP.
 
@@
 
-Themis~\cite{mengThemisDecentralizedEscrow2019} is a fair exchange protocol that uses blockchain instead of TTP.
+Themis~\citep{mengThemisDecentralizedEscrow2019} is a fair exchange protocol that uses blockchain instead of TTP.
 It provides an escrow service for the secure exchange of cryptocurrencies and digital goods.
@@
 
-Lelantos~\cite{altawyLelantosBlockchainBasedAnonymous2017} is a blockchain-based anonymous
+Lelantos~\citep{altawyLelantosBlockchainBasedAnonymous2017} is a blockchain-based anonymous
 physical delivery system.
@@
 Also, we didn't put much attention to the protocols for buying digital products as they are not relevant to our use case.
-The comprehensive analysis of such protocols is avaiable in~\cite{birjoveanuTwoPartyECommerceProtocols2022}.
-
-Altawy et al., 2017~\cite{altawyLelantosBlockchainBasedAnonymous2017} is a blockchain-based protocol that provides anonymous physical delivery by using onion routing and anonymous blockchain interaction assuming unlinkability between pseudonyms and real identities.
+The comprehensive analysis of such protocols is avaiable in~\citep{birjoveanuTwoPartyECommerceProtocols2022}.
+
+Altawy et al., 2017~\citep{altawyLelantosBlockchainBasedAnonymous2017} is a blockchain-based protocol that provides anonymous physical delivery by using onion routing and anonymous blockchain interaction assuming unlinkability between pseudonyms and real identities.
 However, it does not provide dispute resolution.
 
-Hinarejos et al., 2019~\cite{hinarejosSolutionSecureCertified2019} is the simplest protocol that replaces TTP with blockchain.
+Hinarejos et al., 2019~\citep{hinarejosSolutionSecureCertified2019} is the simplest protocol that replaces TTP with blockchain.
 However, it does not consider anonymity, disputes between parties nor physical material exchange.
 
-Meng et al., 2019~\cite{mengThemisDecentralizedEscrow2019} improves the previous protocol by the crowdsourced dispute resolution system. However, it does not take anonymity into consideration.
-
-Bîrjoveanu, 2022~\cite{birjoveanuTwoPartyECommerceProtocols2022} is the closest to our protocol, however, it is based on strong assumptions, namely, existence of TTP, banks supporting confidental transactions with commit buffers, and mantainng a global list of coins' serial numbers.
+Meng et al., 2019~\citep{mengThemisDecentralizedEscrow2019} improves the previous protocol by the crowdsourced dispute resolution system. However, it does not take anonymity into consideration.
+
+Bîrjoveanu, 2022~\citep{birjoveanuTwoPartyECommerceProtocols2022} is the closest to our protocol, however, it is based on strong assumptions, namely, existence of TTP, banks supporting confidental transactions with commit buffers, and mantainng a global list of coins' serial numbers.
 
@@
 It can be instantiated with either the local court or police, or one of the blockchain
-dispute resolution services like Themis~\cite{mengThemisDecentralizedEscrow2019}, Kleros~\cite{bergollaKlerosSociolegalCase2022,gudkovCrowdArbitrationBlockchain2020}, Aragon Court~\cite{aragonDecentralizedDisputeResolution}, LTO Network~\cite{ltonetworkNextGenBlockchainB2B,ltonetworkOnchainIdentitiesCredentials}, and other Online Dispute Resolution platforms~\cite{allenGovernanceBlockchainDispute2019}.
+dispute resolution services like Themis~\citep{mengThemisDecentralizedEscrow2019}, Kleros~\citep{bergollaKlerosSociolegalCase2022,gudkovCrowdArbitrationBlockchain2020}, Aragon Court~\citep{aragonDecentralizedDisputeResolution}, LTO Network~\citep{ltonetworkNextGenBlockchainB2B,ltonetworkOnchainIdentitiesCredentials}, and other Online Dispute Resolution platforms~\citep{allenGovernanceBlockchainDispute2019}.
 
@@
 
-\ifdefstring{\FORMAT}{\DOUBLECOLUMN}{\begin{table*}}{\begin{table}}
+\begin{table}
 \centering
@@
 
-\ifdefstring{\FORMAT}{\DOUBLECOLUMN}{\begin{tabular}{|c|c|c|c|c|c|}}{\begin{tabular}{|c|c|c|c|c|c|}}
+\begin{tabular}{|l|p{1.2cm}|l|p{1.3cm}|l|p{1.2cm}|}
 
 \hline
-Protocol & Fair exchange & Anonymity & Dispute resolution & Trust & Physical delivery \\
+Protocol & Fair \newline exchange & Anonymity & Dispute resolution & Trust & Physical \newline delivery \\
 \hline
-Zhang et al. 2006~\cite{zhangPracticalFairExchangeEPayment2006} & \YES & \YESBUT & \YES & \TTP & \YES \\
+\cite{zhangPracticalFairExchangeEPayment2006} & \YES & \YESBUT & \YES & \TTP & \YES \\
 \hline
-Alaraj, 2012~\cite{mohammedalarajFairnessPhysicalProducts2012} & \YESBUT & \NO & \YES & \TTP & \YES \\
+\cite{mohammedalarajFairnessPhysicalProducts2012} & \YESBUT & \NO & \YES & \TTP & \YES \\
 \hline
-Lelantos, 2017~\cite{altawyLelantosBlockchainBasedAnonymous2017} & \YES & \PSEUDO & \NO & \BC & \YES \\
+Lelantos~\citep{altawyLelantosBlockchainBasedAnonymous2017} & \YES & \PSEUDO & \NO & \BC & \YES \\
 \hline
-Hinarejos et al., 2019~\cite{hinarejosSolutionSecureCertified2019} & \YES & \NO & \NO & \BC & \NO \\
+\cite{hinarejosSolutionSecureCertified2019} & \YES & \NO & \NO & \BC & \NO \\
 \hline
-Themis, 2019~\cite{mengThemisDecentralizedEscrow2019} & \YES & \NO & \YES & \BC & \NO \\
+Themis~\citep{mengThemisDecentralizedEscrow2019} & \YES & \NO & \YES & \BC & \NO \\
 \hline
-PPPDCP, 2022~\cite{birjoveanuTwoPartyECommerceProtocols2022} & \YES & \YES & \YES & \TTP & \YES \\
+PPPDCP~\citep{birjoveanuTwoPartyECommerceProtocols2022} & \YES & \YES & \YES & \TTP & \YES \\
 \hline
@@
 
-\ifdefstring{\FORMAT}{\DOUBLECOLUMN}
-{\end{table*}}
-{\end{table}}
+\end{table}
 
@@
 The problem arises when the seller wants to sent the product to the buyer who wants to remain anonymous.
-Most of the existing protocols either assume the existence of trusted delivery agent~\cite{mohammedalarajFairnessPhysicalProducts2012,birjoveanuAnonymityFairexchangeEcommerce2015}, or use complex delivery mechanism similar to onion rounting involving multiple many delivery services~\cite{altawyLelantosBlockchainBasedAnonymous2017}.
+Most of the existing protocols either assume the existence of trusted delivery agent~\citep{mohammedalarajFairnessPhysicalProducts2012,birjoveanuAnonymityFairexchangeEcommerce2015}, or use complex delivery mechanism similar to onion rounting involving multiple many delivery services~\citep{altawyLelantosBlockchainBasedAnonymous2017}.
 
@@
 We assume that there is a way to anonymously deliver a package without revealing the customer personal information either via SP's drop box, Parcel Locker services (e.g.
-Amazon Locker, InPost~\cite{inpostParcelLockerService}), a customer's trusted party, of even post office.
+Amazon Locker, InPost~\citep{inpostParcelLockerService}), a customer's trusted party, of even post office.
 
@@
 The smart contract code encompasses the contract's specifications, hence the slogan \textit{code as a law}.
-Moreover, smart contracts are automatically executed merging together the gap between law and its enforcement by police~\cite{allenGovernanceBlockchainDispute2019}.
+Moreover, smart contracts are automatically executed merging together the gap between law and its enforcement by police~\citep{allenGovernanceBlockchainDispute2019}.
 However, the blockchain paradigm has its limitations.
@@
 The technique of providing real-world data to the blockchain is called an oracle.
-Oracle provides data based on a decentralized network of mediators; therefore, the trust is also decentralized~\cite{breidenbachChainlinkNextSteps2021}.
+Oracle provides data based on a decentralized network of mediators; therefore, the trust is also decentralized~\citep{breidenbachChainlinkNextSteps2021}.
 
@@
 
-Themis~\cite{mengThemisDecentralizedEscrow2019} besides providing fair exchange protocol,
-also offers a semi-autonomous decentralized dispute resolution system that complies with the Web3 postulates of a decentralized web~\cite{ethereumWhatWeb3Why}.
+Themis~\citep{mengThemisDecentralizedEscrow2019} besides providing fair exchange protocol,
+also offers a semi-autonomous decentralized dispute resolution system that complies with the Web3 postulates of a decentralized web~\citep{ethereumWhatWeb3Why2023}.
 Themis resolve disputes by a set of voluntary anonymous mediators participating in voting and deciding whether a party misbehaved.
@@
 
-Kleros~\cite{bergollaKlerosSociolegalCase2022} is a smart contract deployed on the Ethereum platform that mimics in a decentralized and autonomous way how the court works in real life.
+Kleros~\citep{bergollaKlerosSociolegalCase2022} is a smart contract deployed on the Ethereum platform that mimics in a decentralized and autonomous way how the court works in real life.
 In Kleros, every process of a dispute like gathering evidence, selecting jurors, and rewarding the winning party is automated by a set of smart contracts.
@@
 \subsection{Message Board}\label{sec:message-board}
-The proof of provision that we coined for the purpose of this protocol is generally called the proof of existence~\cite{crespoStamperyBlockchainTimestamping2017}.
+The proof of provision that we coined for the purpose of this protocol is generally called the proof of existence~\citep{crespoStamperyBlockchainTimestamping2017}.
 
@@
 
-Depending on the context the platform for achieving it is called bulletin board~\cite{achenbachImprovedCoercionresistantElectronic2015}, trusted timestamping~\cite{gippDecentralizedTrustedTimestamping2015}, or message board~\cite{hinarejosSolutionSecureCertified2019}.
+Depending on the context the platform for achieving it is called bulletin board~\citep{achenbachImprovedCoercionresistantElectronic2015}, trusted timestamping~\citep{gippDecentralizedTrustedTimestamping2015}, or message board~\citep{hinarejosSolutionSecureCertified2019}.
 In this work, we call it a message board.
@@
 Privacy is a concept used in almost all social sciences like philosophy, psychology, sociology, and legal.
-The multidisciplinary nature leads to ambiguous definitions~\cite{smithInformationPrivacyResearch2011}.
+The multidisciplinary nature leads to ambiguous definitions~\citep{smithInformationPrivacyResearch2011}.
 For our work, we rely on more concrete definitions, i.e.~confidentality, and anonymity.
@@
 However, anonymity is a spectrum rather than a dichotomous classification.
-One method of quantifying the level of anonymity is \textit{k}-anonymity proposed in~\cite{sweeneyKanonymityModelProtecting2002}.
+One method of quantifying the level of anonymity is \textit{k}-anonymity proposed in~\citep{sweeneyKanonymityModelProtecting2002}.
 It measures the user's anonymity by the number of other users from whom the user can not be distinguished.
@@
 
-Examples of blockchains that natively support confidential transactions are: Monero~\cite{vansaberhagenCryptoNote2013} (using Ring Signatures~\cite{noetherRingSignatureConfidential2015} or Bulletproofs~\cite{bunzBulletproofsShortProofs2018}), ZCash~\cite{ben-sassonZerocashDecentralizedAnonymous2014} (using zkSNARK~\cite{ben-sassonSNARKsVerifyingProgram2013}), Grin~\cite{fuchsbauerAggregateCashSystems2019} (using Mimblewimble~\cite{jedusorMIMBLEWIMBLE2016}), and IronFish~\cite{ironfishPrivateAnonymousEasy} (using Sapling protocol~\cite{hopwoodZcashSaplingProtocol2022}).
-
-Overly techniques that achieve anonymity on top of non-privacy-preserving blockchains are: Ethereum's Tornado Cash~\cite{pertsevTornadoCashPrivacy2019} (via zkSNARK~\cite{grothSizePairingbasedNoninteractive2016} and MiMC~\cite{albrechtMiMCEfficientEncryption2016}), Bitcoin's Wasabi~\cite{wasabiwalletBitcoinPrivacyWallet} (via CoinJoin~\cite{maxwellCoinJoinBitcoinPrivacy2013}).
+Examples of blockchains that natively support confidential transactions are: Monero~\citep{vansaberhagenCryptoNote2013} (using Ring Signatures~\citep{noetherRingSignatureConfidential2015} or Bulletproofs~\citep{bunzBulletproofsShortProofs2018}), ZCash~\citep{ben-sassonZerocashDecentralizedAnonymous2014} (using zkSNARK~\citep{ben-sassonSNARKsVerifyingProgram2013}), Grin~\citep{fuchsbauerAggregateCashSystems2019} (using Mimblewimble~\citep{jedusorMIMBLEWIMBLE2016}), and IronFish~\citep{ironfishPrivateAnonymousEasy} (using Sapling protocol~\citep{hopwoodZcashSaplingProtocol2022}).
+
+Overly techniques that achieve anonymity on top of non-privacy-preserving blockchains are: Ethereum's Tornado Cash~\citep{pertsevTornadoCashPrivacy2019} (via zkSNARK~\citep{grothSizePairingbasedNoninteractive2016} and MiMC~\citep{albrechtMiMCEfficientEncryption2016}), Bitcoin's Wasabi~\citep{wasabiwalletBitcoinPrivacyWallet} (via CoinJoin~\citep{maxwellCoinJoinBitcoinPrivacy2013}).
 
@@
 \item separate address: each transaction uses an unique address associated with the transaction.
-Such addresses can be derived using Hierarchical Deterministic Wallets~\cite{wuilleBIP32HierarchicalDeterministic2012} and published on message board, to achieve non-repudiation.
+Such addresses can be derived using Hierarchical Deterministic Wallets~\citep{wuilleBIP32HierarchicalDeterministic2012} and published on message board, to achieve non-repudiation.
 \item memo: the payments are sent to sigle SP account, but contain an extra field named ``memo'' filled with the unique indentifier $\textrm{provisionID}$. 
@@
 As the proof of payment is trivial in transparent and trackable blockchains, it gets more complicated when it comes to anonymous blockchains.
-Monero allows proving and checking payments via dedicated API~\cite{moneroHowProvePayment}.
-ZCash provides a mechanism called Payment Disclosure~\cite{daviesIntroductionPaymentDisclosure2017}.
+Monero allows proving and checking payments via dedicated API~\citep{moneroHowProvePayment}.
+ZCash provides a mechanism called Payment Disclosure~\citep{daviesIntroductionPaymentDisclosure2017}.
 We call the proof of payment a \textit{payment recepit}.
@@
 However, storing data on a blockchain is very expensive.
-The most common workaround (\cite{shahidBlockchainBasedAgriFoodSupply2020, wangAuditableProtocolsFair2019, chenImprovedP2PFile2017}) is to publish the data on a content addressable peer-to-peer storage network like IPFS~\cite{benetIPFSContentAddressed2014}.
+The most common workaround (\cite{shahidBlockchainBasedAgriFoodSupply2020, wangAuditableProtocolsFair2019, chenImprovedP2PFile2017}) is to publish the data on a content addressable peer-to-peer storage network like IPFS~\citep{benetIPFSContentAddressed2014}.
 Then, publish on the blockchain just the content identifier ($\mathrm{cid}$) that uniquely points to the content stored on IPFS.
@@
   Tornado Cash \cite{pertsevTornadoCashPrivacy2019}.
-\item Message board: Open timestamps~\cite{opentimestampsTimestampingProofStandard}, Stampery \cite{crespoStamperyBlockchainTimestamping2017}, Bitcoin blockchain (Proof of Existence~\cite{proofofexistenceWebApplicationProve}, Chainpoint~\cite{chainpointBlockchainProofAnchoring}), Ethereum blockchain, or any other public blockchain that supports attaching extra data along the transaction.
-\item Storage network: IPFS~\cite{benetIPFSContentAddressed2014}, Filecoin~\cite{protocollabsFilecoinDecentralizedStorage2017}, or Ethereum's
-  Swarm~\cite{teamSWARMStorageCommunication2021}.
+\item Message board: Open timestamps~\citep{opentimestampsTimestampingProofStandard}, Stampery \cite{crespoStamperyBlockchainTimestamping2017}, Bitcoin blockchain (Proof of Existence~\citep{proofofexistenceWebApplicationProve}, Chainpoint~\citep{chainpointBlockchainProofAnchoring}), Ethereum blockchain, or any other public blockchain that supports attaching extra data along the transaction.
+\item Storage network: IPFS~\citep{benetIPFSContentAddressed2014}, Filecoin~\citep{protocollabsFilecoinDecentralizedStorage2017}, or Ethereum's
+  Swarm~\citep{teamSWARMStorageCommunication2021}.
 \end{enumerate}
@@
 \begin{eqnarray}
-\mathrm{PoD} & \equiv & (\begin{array}[t]{l}\mathrm{T}_\mathrm{issue}, \mathrm{T}_\mathrm{pay}, \mathrm{T}_\mathrm{provide},\\ \mathrm{address}, \mathrm{provisionID}, \mathrm{pk(C)}, \mathrm{sig}_\mathrm{SP} \; )\end{array}
+\mathrm{PoD} & \equiv & (\begin{array}[t]{l}\mathrm{T}_\mathrm{issue}, \mathrm{T}_\mathrm{pay}, \mathrm{T}_\mathrm{provide}, \\\\ \mathrm{address}, \mathrm{provisionID}, \mathrm{pk(C)}, \mathrm{sig}_\mathrm{SP} \; )\end{array}
 \end{eqnarray}
@@
 \noindent \textbf
-{Content Identifier (cid)}\label{content-identifier-cid} is a term coined by IPFS~\cite{ipfsContentIdentifiersCIDs}.
+{Content Identifier (cid)}\label{content-identifier-cid} is a term coined by IPFS~\citep{ipfsContentIdentifiersCIDs}.
 However, since our protocol does not depend on this particular implementation of the storage network, we let the $\mathrm{cid}$ be any other identifier that securely and uniquely points to the content.
@@
 After the service is finished, a result should be created. 
-Next, the result is encrypted using a shared key derived from the customer's public key $\mathrm{pk(C)}$ and the SP's secret key $\mathrm{sk(S)}$ using Diffie-Hellman key exchange (DHKE) method~\cite{diffieNewDirectionsCryptography1976}.
+Next, the result is encrypted using a shared key derived from the customer's public key $\mathrm{pk(C)}$ and the SP's secret key $\mathrm{sk(S)}$ using Diffie-Hellman key exchange (DHKE) method~\citep{diffieNewDirectionsCryptography1976}.
 The encrypted result is then uploaded on the content addressable network (such as IPFS). In return, the content identifier ($\mathrm{cid}$) is created.
@@
 The detailed description of each step and the justification
-of the outcome positions is given in~\ref{app:proof-of-fairness}.
+of the outcome positions is given in Appendix~\ref{app:proof-of-fairness}.
 
@@
   \item{Anonymous payments} — we use the Monero blockchain \cite{noetherRingSignatureConfidential2015}.
-  \item{Storage netowork} — we use the Powergate~\cite{textilePowergate2023}, which is a wrapper around Filecoin and IPFS.
+  \item{Storage netowork} — we use the Powergate~\citep{textilePowergate2023}, which is a wrapper around Filecoin and IPFS.
   \item{Message board} — we use the Ethereum blockchain \cite{woodEthereumSecureDecentralised2014}; concretely, its local development version Truffle Ganache and Solidity language.
@@
 
-The prototype is available at \url{https://anonser.stan.bar}. The source code is available at \url{https://github.com/stanbar/anonymous-provision-of-services-via-blockchain}.
+The prototype is available at [blinded for review process]. The source code is available at [blinded for review process].
+
+% The prototype is available at \url{https://anonser.stan.bar}. The source code is available at \url{https://github.com/stanbar/anonymous-provision-of-services-via-blockchain}.
 
@@
 
-The customer gets some testing Monero funds using faucet service~\cite{rinoMoneroStagenetFaucet}.
+The customer gets some testing Monero funds using faucet service available at \url{https://community.rino.io/faucet/stagenet/}.
 
@@
 \paragraph{Fariness}
-As shown in Section~\ref{sec:steps} and~\ref{app:proof-of-fairness}, 
+As shown in Section~\ref{sec:steps} and Appendinx~\ref{app:proof-of-fairness}, 
 the protocol is fair.
@@
 The SP has no motivation to proceed with this kind of misbehavior other than putting the customer in a disadvantaged position caused by the lost dispute.}.
-However, the Filecoin~\cite{protocollabsFilecoinDecentralizedStorage2017}, which works as an incentivization layer on top of IPFS, increases the content availability via economic incentivisation (i.e., punishment in case of lack of proof of storage of the content~\cite{filecoinSlashing}).
+However, the Filecoin~\citep{protocollabsFilecoinDecentralizedStorage2017}, which works as an incentivization layer on top of IPFS, increases the content availability via economic incentivisation (i.e., punishment in case of lack of proof of storage of the content~\citep{filecoinSlashing}).
 
@@
 
-Centralized justice is the biggest obstacle in achieving a system that complies with Web3 postulates~\cite{ethereumWhatWeb3Why}.
-
-The possible directions for mitigation of such issues are to either (i) replace local justice with blockchain dispute resolution systems like those proposed in Themis~\cite{mengThemisDecentralizedEscrow2019}, Kleros~\cite{bergollaKlerosSociolegalCase2022,gudkovCrowdArbitrationBlockchain2020}, Aragon Court~\cite{aragonDecentralizedDisputeResolution}, LTO Network~\cite{ltonetworkNextGenBlockchainB2B}, and other Online Dispute Resolution platforms~\cite{allenGovernanceBlockchainDispute2019}; or (ii) make it infeasible to provide incorrect results.
+Centralized justice is the biggest obstacle in achieving a system that complies with Web3 postulates~\citep{ethereumWhatWeb3Why2023}.
+
+The possible directions for mitigation of such issues are to either (i) replace local justice with blockchain dispute resolution systems like those proposed in Themis~\citep{mengThemisDecentralizedEscrow2019}, Kleros~\citep{bergollaKlerosSociolegalCase2022,gudkovCrowdArbitrationBlockchain2020}, Aragon Court~\citep{aragonDecentralizedDisputeResolution}, LTO Network~\citep{ltonetworkNextGenBlockchainB2B}, and other Online Dispute Resolution platforms~\citep{allenGovernanceBlockchainDispute2019}; or (ii) make it infeasible to provide incorrect results.
 
@@
 Suppose that the service we are undertaking is fully computable.
-Then, it would be possible by employing proofs of correctness of computations~\cite{ben-sassonSNARKsVerifyingProgram2013} to enforce that only correct computations (hence correct services) are accepted.
+Then, it would be possible by employing proofs of correctness of computations~\citep{ben-sassonSNARKsVerifyingProgram2013} to enforce that only correct computations (hence correct services) are accepted.
 It would require the complete service examination to be computable, which is hard to achieve in settings where physical materials (like blood) are examined.
@@
 Our research in the field showed that some jurisdictions require SPs to associate the diagnosis with the customer's personal information.
-For example, in Poland, all laboratories performing medical diagnostic tests, and collecting the material (except tests for HIV) are obligated to the unambiguous identification and verification of the identity of the patient from whom the material was collected~\cite{ministerstwozdrowiaRegulationMinisterHealth2006}.
+For example, in Poland, all laboratories performing medical diagnostic tests, and collecting the material (except tests for HIV) are obligated to the unambiguous identification and verification of the identity of the patient from whom the material was collected~\citep{ministerstwozdrowiaRegulationMinisterHealth2006}.
 
@@
 
-One promising solution would be to use Self-sovereign identities (SSI)~\cite{muhleSurveyEssentialComponents2018}, especially the verifiable claims.
+One promising solution would be to use Self-sovereign identities (SSI)~\citep{muhleSurveyEssentialComponents2018}, especially the verifiable claims.
 A trusted authority (e.g., a government) would issue a one-time claim for a customer that would be accepted by the SP as legitimate personal identification.
@@
 \subsection{Formal Verification}\label{sec:formal-verification}
-Following the work of~\cite{birjoveanuFormalVerificationMultiparty2022}, the security analysis of our protocol could be improved by the usage of tools for the automatic formal verification, e.g., AVISPA~\cite{armandoAVISPAToolAutomated2005}.
-It would require specifying the protocol using High-Level Protocol Specification Language (HLPSL)~\cite{chevalierHighLevelProtocol2004}.
+Following the work of~\citep{birjoveanuFormalVerificationMultiparty2022}, the security analysis of our protocol could be improved by the usage of tools for the automatic formal verification, e.g., AVISPA~\citep{armandoAVISPAToolAutomated2005}.
+It would require specifying the protocol using High-Level Protocol Specification Language (HLPSL)~\citep{chevalierHighLevelProtocol2004}.
 The specification would be then translated to the AVISPA's intermediate language and verified using the AVISPA's theorem prover.
@@
 
-\ifx\JOURNAL=IEEE
-
-\appendices
-\printbibliography
-\else
-
 \section*{Declaration of competing interest}
@@
 
-The prototype available at \url{https://anonser.stan.bar}.
-
-The source code available at \url{https://github.com/stanbar/anonymous-provision-of-services-via-blockchain}.
-
-\printbibliography
-\appendix
-\fi
+%The prototype available at  \url{https://anonser.stan.bar}. 
+The prototype available at [blinded for review process].
+
+%The source code available at \url{https://github.com/stanbar/anonymous-provision-of-services-via-blockchain}.
+The source code available at [blinded for review process].
+
+\begin{appendices}
 
@@
 \end{itemize}
+
+\end{appendices}
+
+\bibliography{bibliography}
+
+\end{document}

### 2023-04-18 paper/content.tex
update IEEE paper

@@
 \hline
-Protocol & Fair exchange & Anonymity & Dispute resolution & Trust & Physical delivery \\
+Protocol & Fair \newline exchange & Anonymity & Dispute resolution & Trust & Physical \newline delivery \\
 \hline
-Zhang et al. 2006~\cite{zhangPracticalFairExchangeEPayment2006} & \YES & \YESBUT & \YES & \TTP & \YES \\
+\cite{zhangPracticalFairExchangeEPayment2006} (2006) & \YES & \YESBUT & \YES & \TTP & \YES \\
 \hline
-Alaraj, 2012~\cite{mohammedalarajFairnessPhysicalProducts2012} & \YESBUT & \NO & \YES & \TTP & \YES \\
+\cite{mohammedalarajFairnessPhysicalProducts2012} (2012) & \YESBUT & \NO & \YES & \TTP & \YES \\
 \hline
-Lelantos, 2017~\cite{altawyLelantosBlockchainBasedAnonymous2017} & \YES & \PSEUDO & \NO & \BC & \YES \\
+Lelantos~\cite{altawyLelantosBlockchainBasedAnonymous2017} (2017) & \YES & \PSEUDO & \NO & \BC & \YES \\
 \hline
-Hinarejos et al., 2019~\cite{hinarejosSolutionSecureCertified2019} & \YES & \NO & \NO & \BC & \NO \\
+\cite{hinarejosSolutionSecureCertified2019} (2019) & \YES & \NO & \NO & \BC & \NO \\
 \hline
-Themis, 2019~\cite{mengThemisDecentralizedEscrow2019} & \YES & \NO & \YES & \BC & \NO \\
+Themis~\cite{mengThemisDecentralizedEscrow2019} (2019) & \YES & \NO & \YES & \BC & \NO \\
 \hline
-PPPDCP, 2022~\cite{birjoveanuTwoPartyECommerceProtocols2022} & \YES & \YES & \YES & \TTP & \YES \\
+PPPDCP~\cite{birjoveanuTwoPartyECommerceProtocols2022} (2022) & \YES & \YES & \YES & \TTP & \YES \\
 \hline
@@
 Themis~\cite{mengThemisDecentralizedEscrow2019} besides providing fair exchange protocol,
-also offers a semi-autonomous decentralized dispute resolution system that complies with the Web3 postulates of a decentralized web~\cite{ethereumWhatWeb3Why}.
+also offers a semi-autonomous decentralized dispute resolution system that complies with the Web3 postulates of a decentralized web~\cite{ethereumWhatWeb3Why2023}.
 Themis resolve disputes by a set of voluntary anonymous mediators participating in voting and deciding whether a party misbehaved.
@@
 
-Centralized justice is the biggest obstacle in achieving a system that complies with Web3 postulates~\cite{ethereumWhatWeb3Why}.
+Centralized justice is the biggest obstacle in achieving a system that complies with Web3 postulates~\cite{ethereumWhatWeb3Why2023}.
 

### 2023-04-18 paper/ieee.tex
add support for two columns
update IEEE paper

@@
 \usepackage{float}
+\usepackage{etoolbox}
 
@@
 \newtheorem{definition}{Definition}
-
-\input{constants.tex}
-
-\newcommand{\plus}{+}
-\newcommand{\minus}{-}
-\newcommand\neutral[1][.75]{\mathbin{\ThisStyle{\vcenter{\hbox{%
-  \scalebox{#1}{$\SavedStyle\bullet$}}}}}%
-}
-
 \newcommand{\customer}{customer}
@@
 
+\newcommand{\plus}{+}
+\newcommand{\minus}{-}
+\newcommand\neutral[1][.75]{\mathbin{\ThisStyle{\vcenter{\hbox{%
+  \scalebox{#1}{$\SavedStyle\bullet$}}}}}%
+}
+
+\def\SINGLECOLUMN{SINGLE}
+\def\DOUBLECOLUMN{DOUBLE}
+\def\JOURNALIEEE{IEEE}
+\def\JOURNALELS{ELS}
+
+\newcommand\TITLE{Anonymous provision of privacy-sensitive services using blockchain and decentralised storage}
+\newcommand\STANLONG{Stanis\l{}aw Bara{\'n}ski}
+\newcommand\JULLONG{Julian Szyma{\'n}ski}
+\newcommand\HIGILONG{Higinio Mora}
+\newcommand\STAN{S. Bara{\'n}ski}
+\newcommand\JUL{J. Szyma{\'n}ski}
+\newcommand\HIGI{H. Mora}
+
+\newcommand\ABSTRACT{
+Lawyers, laboratories, auditors or banks, in order to provide services, require data often containing sensitive personal information.
+Examples of sensitive services are genetic tests, parenthood tests, STD tests, credit score computation or legal advice.
+
+The processing of personal data, especially when providing services involving sensitive data like health records, biological materials, or legal documents, exposes both users and service providers (SP) to privacy risks.
+SPs are at risk of violating GDPR, CPAA, and other legal regulations, while customers are at risk of losing their privacy.
+
+We observe that personal data is often only used for logistical purposes, such as payments or communication, and could be provided anonymously if such methods were available.
+
+We propose a solution that allows the provision of services without the collection of personal data.
+We use anonymous payment methods such as cash and anonymous cryptocurrencies, blockchain technology to achieve fairness, and distributed content-addressable storage networks to deliver results.
+
+Compared to other solutions, our protocol achieves anonymity with weaker assumptions, supports physical materials and conflict resolution, and in conflict-free transactions does not require the customer to interact with the blockchain, demonstrating better practicality.
+
+In this work, we analyse the fairness of our protocol and implement it using Ethereum technology as a message board, Monero as an anonymous payment method, and Powergate (IPFS and Filecoin) as a decentralised storage network.
+}
+
+\newcommand\ACKNOWLEDGEMENTS{
+The work has been supported partially by the founds of Department of Computer Architecture Faculty of Electronics, Telecommunications and Informatics, Gdańsk University of Technology.
+}
+
+\newcommand\LASTVISITED{(last visited Jan. 31, 2023)}
+
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 \history{Date of publication xxxx 00, 0000, date of current version xxxx 00, 0000.}
-\doi{10.1109/ACCESS.2022.0122113}
+\doi{10.1109/ACCESS.2023.0322000}
+
 \title{\TITLE}
@@
 \author{\uppercase{\STANLONG} \authorrefmark{1},
-\uppercase{\JULLONG{}} \authorrefmark{1}}
+\uppercase{\JULLONG{}} \authorrefmark{1},\uppercase{\HIGILONG{}} \authorrefmark{2} }
 
-\address[1]{Department of Electronic, Telecommunication and Informatics, Gdansk University of Technology, Narutowicza 11/12 Gdansk Poland (e-mail: stanislaw.baranski@pg.edu.pl, julian.szymanski@eti.pg.edu.pl}
+\address[1]{Department of Electronic, Telecommunication and Informatics, Gdansk University of Technology, Narutowicza 11/12 80-233 Gdansk Poland (e-mail: \{stanislaw.baranski\}\{julian.szymanski\}@pg.edu.pl)}
+
+\address[2]{Department of Computer Science Technology and Computation, University of Alicante, San Vicente del Raspeig, 03690 Alicante Spain (e-mail: hmora@ua.es)}
 
@@
 
-\markboth{\STAN{}, \JUL{} : \TITLE}
-{\STAN{}, \JUL{} : \TITLE}
+\markboth{\STAN{}, et. al. : \TITLE}
+{\STAN{}, et. al. : \TITLE}
 
@@
 \begin{keywords}
-Anonymity\sep{} blockchain\sep{} fair-exchange\sep{} physical delivery\sep{} privacy\sep{} services
+Anonymity\sep{} blockchain\sep{} diagnosis\sep{} e-commerce\sep{} fair-exchange\sep{} privacy\sep{} services
 \end{keywords}
@@
 \def\JOURNALELS{ELS}
+\def\SINGLECOLUMN{SINGLE}
+\def\DOUBLECOLUMN{DOUBLE}
 
 \def\JOURNAL{\JOURNALIEEE}
+\newcommand{\printbibliography}{
+\bibliographystyle{IEEEtran}
+\bibliography{bibliography}
+}
+\def\FORMAT{\DOUBLECOLUMN}
 
@@
 
-\bibliographystyle{IEEEtran}
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{stanislaw-front-glasses.png}}]{Stanis\l{}aw Bara{\'n}ski} received BEng in 2019 and MSc in 2020 in informatics at the Gdańsk University of Technology.
+Currently, he is a PhD student at the Department of Computer Architecture, Faculty of Electronics, Telecommunications and Informatics, Gdańsk University of Technology.
 
-% Loading bibliography database
-\bibliography{bibliography}
+His research interests include blockchains, applied cryptography, and secure computation; particularly the issue of blockchain-based internet voting, but also other protocols that currently depend on trusted third parties.
 
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{stanislaw.jpg}}]{Stanis\L{}aw Bara{\'n}ski} received BEng in 2019 and MSc in 2020 in informatics at Gdańsk University of Technology.
-Currently, he is a PhD student at the Department of Computer Architecture, Faculty of Electronics, Telecommunications and Informatics, Gdansk University of Technology.
-
-His research interests include blockchains, applied cryptography, and secure computation; particularly the issue of blockchain-based internet voting, but also other areas that currently depend on trusted third parties.
-
-He likes to validate his ideas in practice, developing them up to the commercialization stage.
-He is the author of multiple software products that have reached success in the market.
-His blockchain-based internet voting project has been funded by the Stellar Community Fund for the most useful Stellar application.
+He likes to validate his ideas in practice, developing them up to the commercialization stage. He is the author of multiple software products that have reached success in the market.
 \end{IEEEbiography}
@@
 
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{higinio.jpg}}]{Higinio Mora} received the B.S.
+degree in computer science engineering and the B.S.
+degree in business studies from the University of Alicante, Spain, in 1996 and 1997, respectively, and the Ph.D.
+degree in computer science from the University of Alicante in 2003.
+Since 2002, he has a member of the faculty of the Computer Technology and Computation Department, University of Alicante, where he is currently an Associate Professor and a Researcher with the Specialized Processors Architecture Laboratory.
+His research interests include computer modeling, computer architectures, high-performance computing, embedded systems, the Internet of Things, and cloud computing paradigm.
+\end{IEEEbiography}
+
 \end{document}

### 2023-06-15 paper/main.tex
prepare for IJIS journal

--- 2023-04-18 paper/content.tex
@@
+\documentclass[pdftex,twocolumn,epjc3]{svjour3} 
+\RequirePackage[T1]{fontenc}
+\smartqed  % flush right qed marks, e.g. at end of proof
+\RequirePackage{graphicx}
+\RequirePackage{mathptmx}      % use Times fonts if available on your TeX system
+\RequirePackage{flushend}
+\RequirePackage[numbers,sort&compress]{natbib}
+\RequirePackage[colorlinks,citecolor=blue,urlcolor=blue,linkcolor=blue]{hyperref}
+
+\journalname{Eur. Phys. J. C}
+
+\usepackage{amsmath,amssymb,amsfonts}
+\usepackage{algorithmic}
+\usepackage{graphicx}
+\usepackage{textcomp}
+\usepackage{float}
+\usepackage{etoolbox}
+
+\usepackage{url}
+\usepackage{listings}
+\usepackage{pdfpages}
+\usepackage[english]{babel}
+\usepackage{xcolor,colortbl}
+\usepackage{scalerel}
+\input{constants}
+
+\begin{document}
+
+\title{\TITLE}
+
+\author{\STANLONG\thanksref{e1,addr1}
+        \and \JULLONG{}\thanksref{e2,addr1}
+        \and \HIGILONG{}\thanksref{e3,addr2}
+}
+
+\thankstext{e1}{e-mail: stanislaw.baranski@pg.edu.pl}
+\thankstext{e2}{e-mail: julian.szymanski@pg.edu.pl}
+\thankstext{e3}{e-mail: hmora@ua.es}
+
+\institute{Department of Electronic, Telecommunication and Informatics, Gdansk University of Technology, Narutowicza 11/12 80-233 Gdansk Poland\label{addr1}
+          \and
+          Department of Computer Science Technology and Computation, University of Alicante, San Vicente del Raspeig, 03690 Alicante Spain \label{addr2}
+}
+
+\date{Received: date / Accepted: date}
+% The correct dates will be entered by the editor
+
+\maketitle
+
+\begin{abstract}
+  \ABSTRACT{}
+
+  \newcommand{\sep}{ \and }
+  \keywords{Anonymity\sep{} blockchain\sep{} diagnosis\sep{} e-commerce\sep{} fair-exchange\sep{} privacy\sep{} services}
+\end{abstract}
+
 \section{Introduction}
@@
 
-Providing personal information exposes users to privacy risks, i.e. potential loss of control over personal information~\cite{smithInformationPrivacyResearch2011}.
-
-Such personal information can be used deliberately or accidently (e.g., by theft) 
+Providing personal information exposes users to privacy risks, i.e. potential loss of control over personal information \cite{smithInformationPrivacyResearch2011}.
+
+Such personal information can be used deliberately or accidentally (e.g., by theft) 
 for insider disclosure, unauthorized access, or commercial gains. For example, by reselling it to marketers, financial institutions, other businesses, government agencies, or even cybercriminals. 
@@
   \end{itemize} 
-\item Systemise often misused definitions of anonymity, pseudonymity, linkability, and traceability.
+\item Systematise often misused definitions of anonymity, pseudonymity, linkability, and traceability.
 \item Proposing a framework for analyzing fairness in fair-exchange protocols.
@@
 The protocol uses buyer's bank as TTP, and assumes no coalition between parties to achieve anonymity.
-Authors of
-
-Authors of~\cite{mohammedalarajFairnessPhysicalProducts2012} proposed an protocol for fair-exchage involving physical materials delivery.
+
+Authors of~\cite{mohammedalarajFairnessPhysicalProducts2012} proposed an protocol for fair-exchange involving physical materials delivery.
 The protocol assumes the existence of an offline~\footnote{\textit{Offline} (also called \textit{optimistic}) TTP compared to \textit{online} TTP is in improvement which assumes the TTP being involved only in the case of a dispute between parties~\cite{rayFairExchangeEcommerce2002}.} TTP that is involved only in the event of a dispute.
@@
 \begin{enumerate}
-    \item The buyer buys a digital coin from his bank, blind signature is used to preserve customer's privacy.
+    \item The buyer buys a digital coin from his bank. Blind signature is used to preserve privacy.
     \item The buyer sends to the seller the purchase details, address of DC, customer's bank signature, and some meta data to preserve the integrity of transaction, communication is done over Tor.
@@
     \item The seller posts the product to the DC via delivery serivice.
-    \item The DA collects the product from the SC and posts it to the DC.
+    \item The DA collects the product from the seller's cabinet and posts it to the DC.
     \item The buyer collects the product from the DC using a password.
@@
     \item Alice and Bob generate a 2-of-2 threshold escrow account using Thresh-Key-Gen protocol and send funds to it.
-    \item Alice and Bob split their secret keys into \(n=2t+1\) secret shares using Shamir Secret Shamir protocol, where \(n\) is the number of mediators that participate in the decentralized network and \(t+1\) becomes the threshold of a sufficient number of mediators to reconstruct the secret key.
+    \item Alice and Bob split their secret keys into \(n=2t+1\) secret shares using Shamir Secret Sharing protocol, where \(n\) is the number of mediators that participate in the decentralized network and \(t+1\) becomes the threshold of a sufficient number of mediators to reconstruct the secret key.
     \item Alice and Bob encrypt each \textit{i}-th key share using public key of \textit{i}-th mediator.
@@
 
-Meng et al., 2019~\cite{mengThemisDecentralizedEscrow2019} improves the previous protocol by the crowdsourced dispute resolution system. However, it does not take anonymity into consideration.
-
-Bîrjoveanu, 2022~\cite{birjoveanuTwoPartyECommerceProtocols2022} is the closest to our protocol, however, it is based on strong assumptions, namely, existence of TTP, banks supporting confidental transactions with commit buffers, and mantainng a global list of coins' serial numbers.
+Meng et al., 2019~\cite{mengThemisDecentralizedEscrow2019} improves the previous protocol by the crowd-sourced dispute resolution system. However, it does not take anonymity into consideration.
+
+Bîrjoveanu, 2022~\cite{birjoveanuTwoPartyECommerceProtocols2022} is the closest to our protocol, however, it is based on strong assumptions, namely, existence of TTP, banks supporting confidential transactions with commit buffers, and maintaining a global list of coins' serial numbers.
 
@@
 
-\ifdefstring{\FORMAT}{\DOUBLECOLUMN}{\begin{table*}}{\begin{table}}
+{\begin{table*}
 \centering
@@
 \newcommand{\BC}{\cellcolor{green!50}BC}
-\newcommand{\BCBUT}{\cellcolor{green!35}BC*}
 \caption{Comparision of related works.}
@@
 
-\ifdefstring{\FORMAT}{\DOUBLECOLUMN}{\begin{tabular}{|c|c|c|c|c|c|}}{\begin{tabular}{|c|c|c|c|c|c|}}
-
-\hline
-Protocol & Fair \newline exchange & Anonymity & Dispute resolution & Trust & Physical \newline delivery \\
-\hline
+\begin{tabular}{cccccc}
+
+\noalign{\smallskip}\hline\noalign{\smallskip}
+Protocol & Fair exchange & Anonymity & Dispute resolution & Trust & Physical delivery \\
+\noalign{\smallskip}\hline\noalign{\smallskip}
 \cite{zhangPracticalFairExchangeEPayment2006} (2006) & \YES & \YESBUT & \YES & \TTP & \YES \\
-\hline
 \cite{mohammedalarajFairnessPhysicalProducts2012} (2012) & \YESBUT & \NO & \YES & \TTP & \YES \\
-\hline
 Lelantos~\cite{altawyLelantosBlockchainBasedAnonymous2017} (2017) & \YES & \PSEUDO & \NO & \BC & \YES \\
-\hline
 \cite{hinarejosSolutionSecureCertified2019} (2019) & \YES & \NO & \NO & \BC & \NO \\
-\hline
 Themis~\cite{mengThemisDecentralizedEscrow2019} (2019) & \YES & \NO & \YES & \BC & \NO \\
-\hline
 PPPDCP~\cite{birjoveanuTwoPartyECommerceProtocols2022} (2022) & \YES & \YES & \YES & \TTP & \YES \\
-\hline
-This paper & \YES & \YES & \YES & \BCBUT & \YES \\
-\hline
+This paper & \YES & \YES & \YES & \BC & \YES \\
+\noalign{\smallskip}\hline
 
@@
 
-\ifdefstring{\FORMAT}{\DOUBLECOLUMN}
-{\end{table*}}
-{\end{table}}
+\end{table*}
 
@@
 The problem arises when the seller wants to sent the product to the buyer who wants to remain anonymous.
-Most of the existing protocols either assume the existence of trusted delivery agent~\cite{mohammedalarajFairnessPhysicalProducts2012,birjoveanuAnonymityFairexchangeEcommerce2015}, or use complex delivery mechanism similar to onion rounting involving multiple many delivery services~\cite{altawyLelantosBlockchainBasedAnonymous2017}.
-
-However, our use case is different in that the physical materials are transfered from the (anonymous) customer to the (public) SP.
-This, allows for siplification of the delivery process.
+Most of the existing protocols either assume the existence of trusted delivery agent~\cite{mohammedalarajFairnessPhysicalProducts2012,birjoveanuAnonymityFairexchangeEcommerce2015}, or use complex delivery mechanism similar to onion routing involving multiple many delivery services~\cite{altawyLelantosBlockchainBasedAnonymous2017}.
+
+However, our use case is different in that the physical materials are transferred from the (anonymous) customer to the (public) SP.
+This, allows for simplification of the delivery process.
 We assume that there is a way to anonymously deliver a package without revealing the customer personal information either via SP's drop box, Parcel Locker services (e.g.
@@
 \begin{figure}[h!]
-\includegraphics[width=9cm]{anonymity-diagram.png}
+\includegraphics[width=\linewidth]{anonymity-diagram.png}
 \centering
@@
 
-\item $\mathrm{T}_\mathrm{issue}$ - time at which the $\mathrm{PoD}$ is issued.
+\item $\mathrm{T}_\mathrm{issue}$ - time at which the $\mathrm{PoD}$ is issued by the SP.
 \item
@@
 \item
-  $\mathrm{T}_\mathrm{provide}$ - deadline to provide a result of the service.
+  $\mathrm{T}_\mathrm{provide}$ - deadline to provide the result of the service, i.e. publish $\mathrm{PoP}$.
 \item $\mathrm{address}$ - payment address of the SP's anonymous blockchain account.
@@
 \begin{figure}[ht!]
-\includegraphics[width=9cm]{anonser-protocol.png}
+\includegraphics[width=\linewidth]{anonser-protocol.png}
 \centering
-\caption{Messages exchanged in the protocol.}
+\caption{Messages exchanged in the protocol. Solid arrows indicate requests and dashed arrows indicate responses.}
 \label{fig:protocol-diagram}
@@
 They always prefer to go from the worst position (\minus{} or $\neutral${}) to a better position ($\neutral$ or \plus), but also risk a temporary worst position in favor of a later better position if and only if at any time they can get out of the worst position; in particular, at any time the customer can start a dispute and, if the SP has misbehaved, get out of disadvantaged position (\minus) to the neutral position ($\neutral$).
+\item We assume that the Customer's materials without personal information are useless, and the effort to deliver the package is negligible, so that the Customer's first step does not lead to disadvantaged position.
+\item We assume the processing cost of publishing $\mathrm{PoD}$ is negligible and balance out the effort of delivering the package by the Customer.
 \end{enumerate}
@@
 \begin{figure}[h!]
-\includegraphics[width=9cm]{model.png}
+\includegraphics[width=\linewidth]{model.png}
 \centering
@@
 
-The Figure~\ref{fig:misbehaviour} shows the transitions of positions when the SP tries to misbehave and does not execute service after receiving the payment.
-The customer reacts by starting a dispute and the protocol ends up neutral to the customer and disadvantaged to the SP positions.
+The Figure~\ref{fig:misbehaviour} shows the transitions of positions when the SP tries to misbehave and does not execute service, and so does not publish $\mathrm{PoP}$ after receiving the payment.
+After the deadline $\mathrm{T}_\mathrm{provide}$ the SP can not publish valid $\mathrm{PoP}$ and so the Customer starts a dispute.
+The Customer wins the dispute as the SP is unable to proof the $\mathrm{PoP}$ was published before $\mathrm{T}_\mathrm{provide}$.
+The protocol ends up neutral to the customer and disadvantaged to the SP positions.
 
 \begin{figure}[h!]
-\includegraphics[width=9cm]{misbehaviour.png}
+\includegraphics[width=\linewidth]{misbehaviour.png}
 \centering
@@
 \begin{figure}[h!]
-\includegraphics[width=9cm]{rational.png}
+\includegraphics[width=\linewidth]{rational.png}
 \centering
@@
 However, the Filecoin~\cite{protocollabsFilecoinDecentralizedStorage2017}, which works as an incentivization layer on top of IPFS, increases the content availability via economic incentivisation (i.e., punishment in case of lack of proof of storage of the content~\cite{filecoinSlashing}).
-
-The SP uploads the result on both IPFS and Filecoin networks (via Powergate) making the result available even in case of the SP stops serving the result from his node.
+Compared to typical blockchain networks, Filecoin focuses on data storage and thus makes it cheaper than storing it on blockchains like Bitcoin or Ethereum.
+
+The SP uploads the result on both IPFS and Filecoin networks (via Powergate) making the result free in case of normal behaviour, and highly-available in case of the SP stops serving the result from his node.
 
@@
 
-\ifx\JOURNAL=IEEE
-
-\appendices
-\printbibliography
-\else
-
-\section*{Declaration of competing interest}
-The authors declare that they have no known competing financial interests or personal relationships that could have appeared to influence the work reported in this paper.
-
-\section*{Data availability}
-No data was used for the research described in the article.
-
-The prototype available at \url{https://anonser.stan.bar}.
-
-The source code available at \url{https://github.com/stanbar/anonymous-provision-of-services-via-blockchain}.
-
-\printbibliography
 \appendix
-\fi
 
@@
   \begin{itemize}
-    \item  \Pos{1}{c}{\normal}{\neutral}, the customer risked his materials but did not pay for the transaction and therefore ends up in a neutral position\footnote{One would argue that the customer has put effort into delivering the materials to the SP or that the materials are valuable.
-We assume that the materials without personal information are useless, and the effort to deliver the package is negligible.}.
+    \item  \Pos{1}{c}{\normal}{\neutral}, the customer risked his materials but did not pay for the transaction and therefore ends up in a neutral position (see Assumption 10.
+in Section \ref{sec:assumptions}).
     \item \Pos{1}{s}{\normal}{\neutral}, the SP ends up in a neutral position as she did not spend any resources and the package did not bring her any value.
@@
   \begin{itemize}
-    \item \Pos{2}{c}{\abnormal}{\neutral}, the customer remains in the neutral position as he is not obligated to agree with the incorrect $\mathrm{PoD}$.
+    \item \Pos{2}{c}{\abnormal}{\neutral}, the customer remains in the neutral position as he is not obligated\footnote{By not obligated we understand the situation where a party does not risk any resources by not taking the action} to agree with the incorrect $\mathrm{PoD}$.
     \item \Pos{2}{s}{\abnormal}{\neutral}, the SP remains in the neutral position as the package has not brought her any value and she did not spend any resources to provide the service yet.
@@
 \end{itemize}
+
+\bibliographystyle{spbasic}
+\bibliography{bibliography}
+
+\end{document}

### 2023-06-16 paper/main.tex
update privacy according to Solove taxonomy

@@
 By exposing their identity they trust that the lawyer will not use that information for harmful actions.
+\end{itemize}
+
+According to Solove's Taxonomy of privacy~\cite{soloveTaxonomyPrivacy2006}, our protocol aims to prevent the following privacy risks:
+\begin{itemize}
+    \item Identification, linking of information to a particular individual;
+    \item Secondary use, using personal information for a purpose other than the purpose it was collected; 
+    \item Breach of confidentiality, breaking a promise to keep a person's information confidential;
+    \item Disclosure, revealing truthful information about a person that impacts the ways others judge their character.
 \end{itemize}

### 2023-06-19 paper/main.tex
-m

--- 2023-06-15 paper/main.tex
@@
 \label{sec:introduction}
-Diagnostic services such as paternity tests, doping tests, or venereal disease tests are performed at diagnostic centres that require clients to provide biological materials such as blood, urine, stool, or saliva.
-Unfortunately, to process transactions, clients are often forced to reveal their identities.
-Such a combination of personal data with biological materials exposes clients to significant privacy risks.
-
-Other examples of sensitive services are, legal services, such as legal advice that may require disclosure of the history of financial transactions and confidential legal documents.
-
-Banking services, such as credit scoring, may require sensitive personal data, such as medical records, and history of financial transactions.
-
-Providing personal information exposes users to privacy risks, i.e. potential loss of control over personal information \cite{smithInformationPrivacyResearch2011}.
-
-Such personal information can be used deliberately or accidentally (e.g., by theft) 
-for insider disclosure, unauthorized access, or commercial gains. For example, by reselling it to marketers, financial institutions, other businesses, government agencies, or even cybercriminals. 
-In turn, it can lead to an unintentional violation of the GDPR or CCPA, profiled advertisements or even criminal activities like identity theft or illegal tracking and surveillance~\cite{smithInformationPrivacyResearch2011}.
-
-Public individuals like influencers, politicians, or celebrities are especially vulnerable to this kind of attack as exposure of their health records, purchase habits, or legal documents can threaten their reputation, position or be used for blackmailing.
-
-The problem amplifies when personal information is linked to health records, or legal documents, or biological materials like DNA, saliva, or blood.
-
-In such situations, customers may be reluctant to provide their personal information to the SP and thus resign from the service.
+Diagnostic services such as paternity tests, doping tests or venereal disease tests are carried out in diagnostic centres that require clients to provide biological material such as blood, urine, stool or saliva.
+Unfortunately, clients are often forced to reveal their identity in order to complete transactions.
+Such a combination of personal information with biological materials exposes clients to significant privacy risks.
+
+Other examples of sensitive services include anonymous complaints or legal services, such as legal advice, which may require disclosure of financial transaction history and confidential legal documents.
+Banking services, such as credit scoring, may require sensitive personal information, such as medical records and financial transaction history.
+
+Providing personal information exposes users to privacy risks, i.e. the potential loss of control over personal information \cite{smithInformationPrivacyResearch2011}.
+
+Such personal information can be used deliberately or by accident (e.g.
+theft) for insider disclosure, unauthorised access or commercial gain.
+For example, by reselling it to marketers, financial institutions, other businesses, government agencies or even cybercriminals.
+This, in turn, can lead to unintentional GDPR or CCPA breaches, profiled advertising, or even criminal activity such as identity theft or illegal tracking and surveillance~\cite{smithInformationPrivacyResearch2011}.
+
+Public figures such as influencers, politicians or celebrities are particularly vulnerable to this type of attack, as exposure of their health records, purchasing habits or legal documents can threaten their reputation, position or be used for blackmail.
+
+The problem is compounded when personal information is linked to health records, legal documents or biological materials such as DNA, saliva or blood.
+In such situations, clients may be reluctant to provide their personal information to the SP and therefore withdraw from the service.
 Both parties are harmed as the client does not receive a diagnosis relevant to their health and the SP loses potential clients.
-Both parties are affected as the client does not receive a diagnosis relevant to their health and the SP loses potential clients.
-
-The guarantee of privacy of personal data is often based solely on trust in the SPs' staff and the security of their IT systems.
-However, we observe that personal data is often only used for logistical purposes, such as payments or communications, and could be provided anonymously if such methods were available.
-
-It would be desirable for the customers to keep their identities private while still receiving the service.
-This could lead to reduced trust that customers have to put in SPs and less responsibility borne by SPs.
+
+The guarantee of privacy of personal data is often based solely on trust in the SP's staff and the security of their IT systems.
+However, we observe that personal data is often used only for logistical purposes, such as payment or communication, and could be provided anonymously if such methods were available.
+
+It would be desirable for customers to keep their identity private while still receiving the service.
+This could lead to a reduction in the trust that customers need to place in SPs and a reduction in the responsibility that SPs bear.
 
@@
 \begin{itemize}
-    \item Patients willing to take a test eg.: for drugs, venereal diseases, paternity or steroids have a strong incentive to keep the whole procedure private.
-Merely the fact that they took the test—without exposing the result—is suggestive enough to act as a premise in case of a conflict.
-
-Currently, they have to risk that their personal details, materials, and results are stored securely and kept private from any unauthorized actor (both curious employees and malicious attackers).
-
-\item Individuals undertaking entrepreneurial activities may wish to obtain estimates of the risks and possible repercussions of the actions taken.
-
-By exposing their identity they trust that the lawyer will not use that information for harmful actions.
-\end{itemize}
-
-In this work we explore the possibilities of providing services anonymously.
-
-We observe that the issue of anonymous service provision can be seen as a problem of fair exchange where parties exchange some goods fairly, i.e., either both parties obtain the goods, or they both obtain nothing.
-
-In our case, the customer who wants to use the service, exchanges his materials and money with the SP for the result of the service.
-
-Our review indicates that none of the current systems is sufficient to achieve the desired goal.
-We propose a anonymous protocol for provisioning serivces that require physical materials.
-In case of dispute, either due to exceeding deadlines or providing an incorrect result, the customer can disclose the whole interaction and prove to justice the misbehavior of the SP.
-
-To achieve these objectives, we use:
-\begin{itemize}
-    \item \textbf{Blockchain} (aka message board), to achieve fairness, i.e., as a means for proving that certain actions took place at a certain time without the trusted third party (TTP).
-    \item \textbf{Anonymous payment methods}, like cash or anonymous cryptocurrencies, allowing customers to pay for services anonymously.
-    \item \textbf{Decentralized storage network} (e.g., IPFS) to anonymously provide results together with a provable storage network (e.g., Filecoin) to guarantee that the results are available to the customer even if the SP refuses to share the result.
+    \item Patients who are willing to take a test, e.g.
+for drugs, STDs, paternity or steroids, have a strong incentive to keep the whole process private.
+The mere fact that they have taken the test—without revealing the result—is suggestive enough to be used as a premise in the event of a conflict.
+
+    Currently, they have to take the risk that their personal data, materials and results will be stored securely and kept secret from any unauthorised actor (both curious employees and malicious attackers).
+
+\item Individuals engaged in entrepreneurial activities may want to assess the risks and possible consequences of their actions.
+
+By revealing their identity, they trust that the lawyer will not use this information for harmful actions.
+\end{itemize}
+
+Using Solove's Taxonomy of Privacy~\cite{soloveTaxonomyPrivacy2006}, our protocol aims to prevent the following privacy risks:
+\begin{itemize}
+    \item \textbf{Breach of confidentiality}, breaking a promise to keep an individual's information confidential;
+    \item \textbf{Disclosure}, revealing true information about a person that affects the way others judge their character;
+    \item \textbf{Identification}, linking information to a specific individual;
+    \item \textbf{Secondary use}, using personal information for a purpose other than that for which they were collected.
+\end{itemize}
+
+We consider the following adversaries:
+\begin{itemize}
+    \item \textbf{Malicious insiders}: Individuals or entities with authorised access to the protocol's systems or data who may abuse their privileges to compromise customer privacy.
+This could include employees, contractors or service providers;
+    \item \textbf{Government agencies}: Depending on the jurisdiction and the nature of the protocol, government agencies may have legal powers or national security interests that could affect customer privacy.
+For example, the potential for surveillance, data requests or legal intervention;
+    \item \textbf{Malicious third-party services}: If the protocol relies on third party services or APIs, the privacy of customer data could be at risk if these services have inadequate security measures in place or if they engage in data sharing or tracking without the consent of the customer;
+    \item \textbf{Hackers and cybercriminals}: Individuals or organised groups with malicious intent who may exploit vulnerabilities in the protocol's implementation, infrastructure, or supporting systems to gain unauthorised access to customer information.
+\end{itemize}
+
+In this work we explore the possibilities of anonymous service provision and propose a protocol that preserves customer privacy even in the event of a successful attack.
+Under realistic operational assumptions, we believe that decoupling personal information from materials, payment and communication achieves a sufficient level of anonymity.
+
+However, a protocol that hides a customer's identity is difficult to secure and coordinate.
+In particular, conflicts between customers and service providers are difficult to resolve when there is no one to accuse.
+
+We observe that the problem of anonymous service provision can be seen as a problem of fair exchange, where parties exchange some goods fairly, i.e.
+either both parties obtain the goods, or they both obtain nothing.
+
+In our case, the customer who wants to use the service exchanges his materials and money with the SP for the result of the service.
+
+Our review shows that none of the current systems is sufficient to achieve the desired goal.
+We propose an anonymous protocol for the provision of services that require physical materials.
+In the event of a dispute, either due to missed deadlines or incorrect results, the customer can disclose the entire interaction, prove the SP's misbehaviour to justice, and win the dispute.
+
+To achieve this goal we use
+\begin{itemize}
+    \item \textbf{Blockchain}, to achieve fairness, i.e. as a means of proving that certain actions took place at a certain time without the Trusted Third Party (TTP).
+    \item \textbf{Anonymous payment methods}, such as cash or anonymous cryptocurrencies, which allow customers to pay for services anonymously.
+\item \textbf{Decentralised storage network} (e.g.
+IPFS) to provide results together with a provable storage network (e.g.
+Filecoin) to guarantee that the results are available to the customer even if the SP refuses to share the result.
 
@@
     \begin{itemize}
-        \item \textbf{Symmetric encryption}, to encrypt and decrypt results published on the public networks.
-        \item \textbf{Diffie-Helman key exchange (DHKE)} to derive shared secrets for symmetric encryption.
+        \item \textbf{Symmetric encryption}, to encrypt and decrypt the results published on the public networks.
+        \item \textbf{Diffie-Helman key exchange (DHKE)}, to derive shared secrets for symmetric encryption.
         \item \textbf{Digital signatures}, to achieve authentication and non-repudiation of actions. 
@@
 
+Figure~\ref{fig:protocol-overview} shows a simplified diagram of the protocol.
+
+\begin{figure}[h!]
+\includegraphics[width=\linewidth]{protocol-overview.pdf}
+\centering
+\caption{A simplified diagram of the protocol.
+The first step involves the delivery of the materials to the SP.
+The second step involves anonymous payment.
+The third step involves the delivery of the results to the customer.
+Each step is proven on the message board, protecting the fair party in a conflict situation.}
+
+\label{fig:protocol-overview}
+\end{figure}
+
+\paragraph{}
 The contribution of our paper is:
 \begin{itemize}
-\item proposing a novel protocol that:
-  \begin{itemize}
-  \item allows \textbf{anonymous} service provision, i.e., the service provider does not need to collect any personal information from the customer.
-  \item achieves \textbf{fairness} by carefully designing the protocol as an interactive non-cooperative game, in which the SP remains in an advantageous position and the customer in a disadvantageous position with an option to start a dispute in case a misbehaviour of SP.
-  \item \textbf{does not rely on centralized TTP}, but uses decentralized blockchain and distributed content-addressable storage network.
-  \item In conflict-free transactions does not require customers to interact with the blockchain, achieving better \textbf{user-experience and practicality}.
-  \item allows the \textbf{delivery of physical materials}, which was rarely addressed by other researchers or based on strong and unpractical assumptions.
+\item we propose a protocol that upon a realistic operational and threat model:
+  \begin{itemize}
+  \item allows \textbf{anonymous} service provision involving \textbf{physical materials}, i.e., the service provider does not need to collect any personal information from the customer;
+  \item achieves \textbf{fairness} by the use of blockchain and cryptographic proofs. We model the protocol as an interactive non-cooperative game and show fairness at each of its steps.
+  \item \textbf{does not rely on a centralised TTP}, but uses a decentralised blockchain and a distributed content-addressable storage network;
+  \item in conflict-free transactions does not require customers to interact with the blockchain, achieving better \textbf{user experience and practicality};
   \item guarantees the \textbf{remote availability of the results}, even in case of the SP denial of service.
   \end{itemize} 
-\item Systematise often misused definitions of anonymity, pseudonymity, linkability, and traceability.
-\item Proposing a framework for analyzing fairness in fair-exchange protocols.
-\item Discuss the possible improvements to the protocol with the use of secure computation, self-sovereign identities, zero-knowledge proofs, and blockchain-based dispute resolution techniques.
-\end{itemize}
-
-Some authors have proposed blockchain-based fair-exchange systems that could be adapted to service provision; however, to our best knowledge, we are the first to propose a system that satisfies all the properties stated above.
-Especially anonymity and physical materials delivery were rarely addressed together, and if so, the protocol was based on TTP and impractical assumptions on banking system~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} or did not address the conflict between parties~\cite{altawyLelantosBlockchainBasedAnonymous2017}.
-
-The rest of this paper is organized as follows.
+\item We implement a working prototype of the protocol and provide open source code.
+\item We systematise often misused definitions of anonymity, pseudonymity, linkability and traceability.
+\item We propose a framework for analysing fairness in fair exchange protocols and use it to prove the fairness of our protocol.
+\item We discuss possible improvements to the protocol using secure computation, self-sovereign identities, zero-knowledge proofs, and blockchain-based dispute resolution techniques.
+\end{itemize}
+
+Some authors have proposed blockchain-based fair exchange systems that could be adapted to service provision; however, to the best of our knowledge, we are the first to propose a system that satisfies all of the above properties.
+In particular, anonymity and physical delivery have rarely been addressed together, and if so, the protocol was based on TTP and impractical assumptions about the banking system~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} or did not address the conflict between parties~\cite{altawyLelantosBlockchainBasedAnonymous2017}.
+
+The rest of this paper is organised as follows.
 In Section~\ref{sec:related-works} we review related works. 
-Then, in Section~\ref{sec:building-blocks} we discuss the building blocks of a dispute resolution system, blockchain as a message board, fairness, anonymous payments, storage network, results availability, and anonymity.
-Section~\ref{sec:protocol} provides detailed description of the protocol.
+Then in Section~\ref{sec:building-blocks} we discuss the building blocks of a dispute resolution system, blockchain as a message board, fairness, anonymous payments, storage network, availability of results and anonymity.
+Section~\ref{sec:protocol} provides a detailed description of the protocol.
 Section~\ref{sec:fairness-analysis} provides a fairness analysis of the proposed protocol.
-In Section~\ref{sec:experiments} we present the implementation of the protocol and results of our experiments.
-Section~\ref{sec:discussion} discuss possible improvements in terms of crowd-sourced dispute resolution or dispute avoidance, self-sovereign identities (SSI), anonymous delivery, and formal verification.
+Section~\ref{sec:experiments} presents the implementation of the protocol and the results of our experiments.
+Section~\ref{sec:discussion} discusses possible improvements in terms of crowdsourced dispute resolution or dispute avoidance, self-sovereign identities (SSIs), anonymous delivery, and formal verification.
 Finally, Section~\ref{sec:conclusion} concludes the paper.
@@
 The most common application of fair exchange protocols is e-commerce.
-A typical transaction involves a seller and a buyer who exchange money for a physical product.
-To protect themselves the seller want to receive the funds prior to sending the product, while the buyer want to receive the product prior to paying.
+A typical transaction involves a seller and a buyer exchanging money for a physical product.
+To protect themselves, the seller wants to receive the funds before sending the product, while the buyer wants to receive the product before paying.
 The fairness of the protocol should guarantee that either both parties obtain the goods, or they both obtain nothing.
 
-To our best knowledge, the first system that allowed for fair exchange of physical products was proposed by Zhang et al.
+To the best of our knowledge, the first system allowing fair exchange of physical products was proposed by Zhang et al.
 in 2006~\cite{zhangPracticalFairExchangeEPayment2006}.
-The protocol uses buyer's bank as TTP, and assumes no coalition between parties to achieve anonymity.
-
-Authors of~\cite{mohammedalarajFairnessPhysicalProducts2012} proposed an protocol for fair-exchange involving physical materials delivery.
-The protocol assumes the existence of an offline~\footnote{\textit{Offline} (also called \textit{optimistic}) TTP compared to \textit{online} TTP is in improvement which assumes the TTP being involved only in the case of a dispute between parties~\cite{rayFairExchangeEcommerce2002}.} TTP that is involved only in the event of a dispute.
-The protocol works as follows:
+The protocol uses the buyer's bank as the TTP and assumes no coalition between the parties to achieve anonymity.
+
+The authors of~\cite{mohammedalarajFairnessPhysicalProducts2012} proposed a protocol for fair exchange involving the delivery of physical materials.
+The protocol assumes the existence of an offline~\footnote{\textit{Offline} (also called \textit{optimistic}) TTP compared to \textit{online} TTP which assumes the TTP is only involved in the case of a dispute between parties~\cite{rayFairExchangeEcommerce2002}.} TTP only gets involved in the event of a dispute.
+The protocol works as follows
 \begin{enumerate}
-\item The buyer sends an encrypted payment to the seller along with the proof of validity.
-\item The seller validates the proof, which convinces him that the decrypted payment will also be valid.
-\item The seller forwards the physical product to the trusted delivery agent (DA).
-\item The buyer verifies whether the product is the one he ordered.
-\item The buyer creates a proof of delivery and sends it along with the decryption key to the seller.
+\item The buyer sends an encrypted payment to the seller along with proof of validity.
+\item The seller validates the proof, which convinces him that the decrypted payment is also valid.
+\item The seller forwards the physical product to the trusted Delivery Agent (DA).
+\item The buyer verifies that the product is the one ordered.
+\item The buyer creates a proof of delivery and sends it to the seller along with the decryption key.
 \end{enumerate}
 
-However, the protocol relies on strong assumptions, namely, the existence of a TTP and an DA, who does not misbehave or collude with either party.
-Also the fairness is obtained assuming resilient communication channels.
+However, the protocol relies on strong assumptions, namely the existence of a TTP and a DA that do not misbehave or collude with either party.
+Fairness is also achieved by assuming resilient communication channels.
 
@@
 The situation becomes more challenging when the transaction involves physical products.
-
-Authors of~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} proposed a protocol involving physical products, which guarantees anonymity of both buyer and seller.
-They achieve it with the introduction of an online TTP that validates coins and guarantees fairness.
-Later, they proposed many extensions to the protocol, namely, in~\cite{birjoveanuPreservingAnonymityFair2018} they proposed an anonymous e-commerce protocol that governs complex transactions, in~\cite{birjoveanuAnonymityComplexTransactions2019} they extend the anonymity for both buyers and sellers (in our case SPs), and in~\cite{birjoveanuFairExchangeECommerce2020} they proposed a protocol that supports chained transactions (involving multiple active intermediaries).
-Finally in~\cite{birjoveanuTwoPartyECommerceProtocols2022} they proposed improved protocol named PPPDCP (Protocol with Physical Product Delivery Providing Customer's Privacy).
-
-Anonymity is ensured by using anonymous communication channel over Tor~\cite{dingledineTorSecondGenerationOnion2004} and blind signatures~\cite{chaumSecurityIdentificationTransaction1985}.
-Fair exchange, physical delivery, and dispute resolution is achieved using delivery cabinet (DC) under the seller's control (e.g.
-Amazon Locker) and offline TTP that intervenes only in the case of a dispute.
-
-The protocol works as follows:
+In the previous protocol, both parties to the transaction are known to each other.
+However, there are situations where the buyer would prefer not to reveal his identity to the seller.
+The situation becomes more difficult when the transaction involves physical products.
+
+The authors of~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} proposed a protocol for physical products that guarantees the anonymity of both buyer and seller.
+They achieve this by introducing an online TTP that validates coins and guarantees fairness.
+Later they proposed many extensions to the protocol, namely in~\cite{birjoveanuPreservingAnonymityFair2018} they proposed an anonymous e-commerce protocol that governs complex transactions, in~\cite{birjoveanuAnonymityComplexTransactions2019} they extend anonymity for both buyers and sellers (in our case SPs), and in~\cite{birjoveanuFairExchangeECommerce2020} they proposed a protocol that supports chained transactions (involving multiple active intermediaries).
+Finally, in~\cite{birjoveanuTwoPartyECommerceProtocols2022} they proposed an improved protocol called PPPDCP (Protocol with Physical Product Delivery Providing Customer's Privacy).
+
+Anonymity is ensured by using an anonymous communication channel over Tor~\cite{dingledineTorSecondGenerationOnion2004} and blind signatures~\cite{chaumSecurityIdentificationTransaction1985}.
+Fair exchange, physical delivery and dispute resolution are achieved using a Delivery Cabinet (DC) under the control of the seller (e.g.
+Amazon Locker) and an offline TTP that only intervenes in the event of a dispute.
+
+The protocol works as follows
 
 \begin{enumerate}
-    \item The buyer buys a digital coin from his bank. Blind signature is used to preserve privacy.
-    \item The buyer sends to the seller the purchase details, address of DC, customer's bank signature, and some meta data to preserve the integrity of transaction, communication is done over Tor.
-    \item The seller request a redemption of the digital coin.
-    \item The seller posts the product to the DC via delivery serivice.
-    \item The DA collects the product from the seller's cabinet and posts it to the DC.
+    \item The buyer buys a digital coin from their bank. A blind signature is used to ensure privacy.
+    \item The buyer sends the seller the purchase details, the address of the DC, the signature of the customer's bank and some metadata to preserve the integrity of the transaction, communication is done over Tor.
+    \item The seller requests redemption of the digital coin.
+    \item The seller posts the product to the DC via the delivery service.
+    \item The Delivery Agent (DA) collects the product from the seller's locker and posts it to the DC.
     \item The buyer collects the product from the DC using a password.
-    \item The buyer checks if the product is the ordered one, if not, opens a dispute to TTP.
+    \item The buyer verifies that the product is the one ordered, if not, opens a dispute with TTP.
 \end{enumerate}
@@
 \begin{itemize}
-    \item the buyer's and seller's banks enable confidential transactions, and both share a commit buffer where the value is locked until the transaction is finished;
-    \item banks maintain a global list of coins' serial numbers to prevent double-spending problems;
-    \item there exists an anonymous communication channel, and the SC and the DC protected by a passwords;
-    \item the DC is equipped with a video camera that records the moment when the buyer opens the package and provides a way to submit the video to TTP in case of a dispute;
+    \item The buyer's and seller's banks allow confidential transactions, and both share a commit buffer where the value is locked until the transaction is complete;
+    \item The banks maintain a global list of coin serial numbers to prevent problems with double spending;
+    \item there is an anonymous communication channel and the SC and DC are password protected;
+    \item The DC is equipped with a video camera that records the moment the buyer opens the package and provides a means to submit the video to TTP in the event of a dispute;
 \end{itemize}
@@
 \subsection{Fair exchange and blockchain}
-
-The issue of TTPs in fair exchange protocols has been solved by the usage of decentralized networks, especially blockchain technology.
-
-The simplest example of blockchain-based fair exchange protocol is certified electronic mail protocol in which neither the sender can deny sending the mail, nor the receiver can deny receiving it.
-As the service is widely used in the paper world, achieving it for e-mails has not yet met agreement across the scientific community.
-The main problem was the dependency on TTP, which significantly reduced the performance, security, and robustness of such protocols.
-The protocols that do not use TTP struggle with high computation and communication overhead~\cite{hinarejosSolutionSecureCertified2019}.
-
-Authors of ~\cite{hinarejosSolutionSecureCertified2019} replaced the TTP with blockchain (concretely Bitcoin blockchain as a reference implementation) that acts as a secure, verifiable, and decentralized TTP.
-
-The idea behind certified e-mails and any other fair exchange protocols is the following:
+The problem of TTPs in fair exchange protocols has been solved by the use of decentralised networks, in particular blockchain technology.
+
+The simplest example of a blockchain-based fair exchange protocol is the certified email protocol, where neither the sender can deny sending the email nor the recipient can deny receiving it.
+As this service is widely used in the paper world, achieving it for emails has not yet been agreed upon by the scientific community.
+The main problem has been the reliance on TTP, which significantly reduces the performance, security and robustness of such protocols.
+The protocols that do not use TTP suffer from high computational and communication overhead~\cite{hinarejosSolutionSecureCertified2019}.
+
+The authors of ~\cite{hinarejosSolutionSecureCertified2019} have replaced TTP with blockchain (specifically the bitcoin blockchain as a reference implementation), which acts as a secure, verifiable and decentralised TTP.
+
+The idea behind certified email and any other fair exchange protocol is as follows:
 \begin{enumerate}
-    \item The sender sends an encrypted and signed message to the receiver.
-    \item The receiver returns a proof of delivery (a signature) of the encrypted message to the sender.
-    \item The sender publishes proof of delivery and the decryption key on a blockchain (or TTP in general).
-    \item The receiver decrypts the encrypted message using the published decryption key.
+    \item The sender sends an encrypted and signed message to the recipient.
+    \item The recipient returns a proof of delivery (a signature) of the encrypted message to the sender.
+    \item The sender publishes the proof of delivery and the decryption key on a blockchain (or TTP in general).
+    \item The recipient decrypts the encrypted message using the published decryption key.
 \end{enumerate}
 
-The non-repudiation requirement is achieved by the receiver sending the proof of delivery prior to having access to the decrypted message and the sender publishing the decryption key together with the proof of delivery on the blockchain (or TTP) so that the receiver can deny neither receiving the message nor having access to the decryption key—because it is publicly available.
-
-In this case, the role of blockchain is to certify the existence of the decryption key at a certain time.
+The non-repudiation requirement is achieved by the receiver sending the proof of delivery before having access to the decrypted message, and the sender publishing the decryption key together with the proof of delivery on the blockchain (or TTP), so that the receiver cannot deny having received the message or having access to the decryption key—because it is publicly available.
+
+In this case, the role of the blockchain is to certify the existence of the decryption key at a given point in time.
 
@@
 \label{themis-towards-decentralized-escrow-of-cryptocurrencies-without-trusted-third-parties}
-
 Themis~\cite{mengThemisDecentralizedEscrow2019} is a fair exchange protocol that uses blockchain instead of TTP.
 It provides an escrow service for the secure exchange of cryptocurrencies and digital goods.
-Also, it provides a decentralized dispute resolution system for resolving conflicts.
+It also provides a decentralised dispute resolution system for resolving conflicts.
 
@@
 \begin{enumerate}
-    \item Alice and Bob generate a 2-of-2 threshold escrow account using Thresh-Key-Gen protocol and send funds to it.
-    \item Alice and Bob split their secret keys into \(n=2t+1\) secret shares using Shamir Secret Sharing protocol, where \(n\) is the number of mediators that participate in the decentralized network and \(t+1\) becomes the threshold of a sufficient number of mediators to reconstruct the secret key.
-    \item Alice and Bob encrypt each \textit{i}-th key share using public key of \textit{i}-th mediator.
-    \item Alice and Bob exchange the sets of encrypted key shares with each other and send funds to the escrow account.
+    \item Alice and Bob create a 2-of-2 threshold escrow account using the Thresh-Key-Gen protocol and send funds to it.
+\item Alice and Bob split their secret keys into \(n=2t+1\) secret shares using Shamir Secret Sharing protocol, where \(n\) is the number of mediators participating in the decentralised network and \(t+1\) is the threshold for a sufficient number of mediators to reconstruct the secret key.
+    \item Alice and Bob encrypt each \textit{i}-th key share with the public key of \textit{i}-th mediator.
+\item Alice and Bob exchange the sets of encrypted key shares and send funds to the escrow account.
 \end{enumerate}
 
-The escrow is secure as long as \(t+1\) of mediators does not collude, which would let them recreate both \(x_A\) and \(x_B\).
-
-To ensure that parties exchange actual key shares, they send witnesses generated with the Feldman VSS scheme and zero-knowledge proofs to guarantee the consistency between witnesses and key shares.
-
-In case of dispute, the decentralized network of mediators settles the conflict and grand one winning party the other party secret key, allowing it to withdraw the funds.
-
-The monetary incentivization and reputation system guarantee the honesty of mediators.
+The escrow is secure as long as \(t+1\) of the mediators do not collude, which would allow them to reconstruct both \(x_A\) and \(x_B\).
+
+To ensure that the parties exchange real key shares, they send witnesses generated using the Feldman VSS scheme and zero-knowledge proofs to guarantee consistency between witnesses and key shares.
+
+In the event of a dispute, the decentralised network of mediators resolves the conflict and grants the winning party the other party's secret key, allowing it to withdraw the funds.
+
+The financial incentives and the reputation system guarantee the honesty of the mediators.
 
@@
 
-Lelantos~\cite{altawyLelantosBlockchainBasedAnonymous2017} is a blockchain-based anonymous
-physical delivery system.
-The protocol achieves anonymity by employing onion routing (similar to the Tor network) to connect physical delivery providers.
-The whole route from a seller to a buyer is split into multiple steps, and each step is undertaken by the different randomly selected delivery providers.
-As long as the delivery providers do not collude, the seller neither can learn the identity nor destination address of the buyer.
-
-A smart-contract is used to coordinate the whole process and mediate communication between the buyer and delivery providers.
-
-However, since the system uses Ethereum, it achieves pseudonymity rather than anonymity (see Section~\ref{sec:pseudo-anon}). Also, the protocol does not cover disputes between the parties.
+Lelantos~\cite{altawyLelantosBlockchainBasedAnonymous2017} is a blockchain-based anonymous physical delivery system.
+The protocol achieves anonymity by using onion routing (similar to the Tor network) to connect physical delivery providers.
+The entire path from a seller to a buyer is divided into multiple steps, and each step is performed by randomly selected delivery providers.
+As long as the couriers do not collude, the seller cannot learn the identity or destination address of the buyer.
+
+A smart contract is used to coordinate the whole process and mediate communication between the buyer and the delivery providers.
+
+However, because the system uses Ethereum, it achieves pseudonymity rather than anonymity (see section~\ref{sec:pseudo-anon}). Also, the protocol does not cover disputes between the parties.
 
@@
 
-We considered only protocols that achieve fair exchange as it is the fundamental feature of such protocols.
-
-Also, we didn't put much attention to the protocols for buying digital products as they are not relevant to our use case.
-The comprehensive analysis of such protocols is avaiable in~\cite{birjoveanuTwoPartyECommerceProtocols2022}.
-
-Altawy et al., 2017~\cite{altawyLelantosBlockchainBasedAnonymous2017} is a blockchain-based protocol that provides anonymous physical delivery by using onion routing and anonymous blockchain interaction assuming unlinkability between pseudonyms and real identities.
+We only considered protocols that achieve fair exchange, as this is the fundamental feature of such protocols.
+
+We also didn't focus on protocols for buying digital products, as they are not relevant to our use case.
+A more comprehensive analysis of such protocols is available in~\cite{birjoveanuTwoPartyECommerceProtocols2022}.
+
+Altawy et al.
+2017~\cite{altawyLelantosBlockchainBasedAnonymous2017} is a blockchain-based protocol that provides anonymous physical delivery using onion routing and anonymous blockchain interaction, assuming unlinkability between pseudonyms and real identities.
 However, it does not provide dispute resolution.
 
-Hinarejos et al., 2019~\cite{hinarejosSolutionSecureCertified2019} is the simplest protocol that replaces TTP with blockchain.
-However, it does not consider anonymity, disputes between parties nor physical material exchange.
-
-Meng et al., 2019~\cite{mengThemisDecentralizedEscrow2019} improves the previous protocol by the crowd-sourced dispute resolution system. However, it does not take anonymity into consideration.
-
-Bîrjoveanu, 2022~\cite{birjoveanuTwoPartyECommerceProtocols2022} is the closest to our protocol, however, it is based on strong assumptions, namely, existence of TTP, banks supporting confidential transactions with commit buffers, and maintaining a global list of coins' serial numbers.
+Hinarejos et al.
+2019~\cite{hinarejosSolutionSecureCertified2019} is the simplest protocol that replaces TTP with blockchain.
+However, it does not take into account anonymity, disputes between parties, or the exchange of physical material.
+
+Meng et al. 2019~\cite{mengThemisDecentralizedEscrow2019} improves the previous protocol through the crowd-sourced dispute resolution system. However, it does not take anonymity into account.
+
+Bîrjoveanu, 2022~\cite{birjoveanuTwoPartyECommerceProtocols2022} is the closest to our protocol, but it is based on strong assumptions, namely the existence of TTP, banks supporting confidential transactions with commit buffers, and maintaining a global list of coin serial numbers.
 
 Our protocol achieves anonymity by using either cash or privacy-preserving blockchains.
-Moreover, our protocol does not require a customer to submit any transaction to the message board, which in other protocols may be the weakest link in achieving the anonymity.
-
-Moreover, none of them directly address our use case.
+In addition, our protocol does not require a customer to submit a transaction to the bulletin board, which may be the weakest link in achieving anonymity in other protocols.
+
+Furthermore, none of them directly address our use case.
 We want the SP to remain public so that the anonymous buyer can easily start a dispute.
-We assume just one package of physical materials.
-Moreover, the package is delivered from the buyer to the SP, not the other way around — as it's the case for most e-commerce transactions.
-
-Also, our protocol does not provide its own dispute-resolution mechanism as Themis does.
+We assume a single package of physical materials.
+Also, the package is delivered from the buyer to the SP, not the other way around–as in most e-commerce transactions.
+
+Also, our protocol does not have its own dispute resolution mechanism, as Themis does.
 However, we assume the existence of an abstract justice that accepts evidence and punishes the misbehaving party.
-It can be instantiated with either the local court or police, or one of the blockchain
-dispute resolution services like Themis~\cite{mengThemisDecentralizedEscrow2019}, Kleros~\cite{bergollaKlerosSociolegalCase2022,gudkovCrowdArbitrationBlockchain2020}, Aragon Court~\cite{aragonDecentralizedDisputeResolution}, LTO Network~\cite{ltonetworkNextGenBlockchainB2B,ltonetworkOnchainIdentitiesCredentials}, and other Online Dispute Resolution platforms~\cite{allenGovernanceBlockchainDispute2019}.
+This can be instantiated either with the local court or police, or with one of the blockchain's
+dispute resolution services such as Themis~\cite{mengThemisDecentralizedEscrow2019}, Kleros~\cite{bergollaKlerosSociolegalCase2022,gudkovCrowdArbitrationBlockchain2020}, Aragon Court~\cite{aragonDecentralizedDisputeResolution}, LTO Network~\cite{ltonetworkNextGenBlockchainB2B,ltonetworkOnchainIdentitiesCredentials}, and other Online Dispute Resolution platforms~\cite{allenGovernanceBlockchainDispute2019}.
 
@@
 
-The notation \textit{Pseudonymity} means that the anonymity is based on the assumption that the pseudonym is not linked to the real identity; \textit{TTP} means that the protocol uses a trusted third party; \textit{BC} means that the protocol uses a public blockchain; \textit{YES*} means that the protocol provides the feature, but is based on strong or unpractical assumptions.
+The notation \textit{Pseudonymity} means that the anonymity is based on the assumption that the pseudonym is not linked to the real identity; \textit{TTP} means that the protocol uses a trusted third party; \textit{BC} means that the protocol uses a public blockchain; \textit{YES*} means that the protocol provides the feature but is based on strong or impractical assumptions.
 
@@
 \subsection{Physical products}\label{sec:physical-products}
-The use cases we address in this paper use physical materials like blood, urine, hair, and other biological materials.
-This requirement, combined with the requirement of anonymity, is a challenging part of the fair-exchange protocols.
-The problem arises when the seller wants to sent the product to the buyer who wants to remain anonymous.
-Most of the existing protocols either assume the existence of trusted delivery agent~\cite{mohammedalarajFairnessPhysicalProducts2012,birjoveanuAnonymityFairexchangeEcommerce2015}, or use complex delivery mechanism similar to onion routing involving multiple many delivery services~\cite{altawyLelantosBlockchainBasedAnonymous2017}.
+The use cases discussed in this paper use physical materials such as blood, urine, hair and other biological materials.
+This requirement, combined with the need for anonymity, is a challenging part of fair exchange protocols.
+The problem arises when the seller wants to send the product to the buyer who wants to remain anonymous.
+Most of the existing protocols either assume the existence of a trusted delivery agent~\cite{mohammedalarajFairnessPhysicalProducts2012,birjoveanuAnonymityFairexchangeEcommerce2015}, or use a complex delivery mechanism similar to onion routing involving multiple many delivery services~\cite{altawyLelantosBlockchainBasedAnonymous2017}.
 
 However, our use case is different in that the physical materials are transferred from the (anonymous) customer to the (public) SP.
-This, allows for simplification of the delivery process.
-We assume that there is a way to anonymously deliver a package without revealing the customer personal information either via SP's drop box, Parcel Locker services (e.g.
-Amazon Locker, InPost~\cite{inpostParcelLockerService}), a customer's trusted party, of even post office.
+This allows a simplification of the delivery process.
+We assume that there is a way to deliver a package anonymously without revealing the customer's personal information, either via the SP's drop box, parcel locker services (e.g.
+Amazon Locker, InPost~\cite{inpostParcelLockerService}), a customer's trusted Delivery Agent, or even the post office.
 
@@
 \label{sec:dispute-resolution}
-
 Disputes are an inevitable part of all human transactions.
-Whether intentional or accidental, the system should prevent violation of agreed contract rules or local jurisdiction.
-The rules are specified by law and implemented by the police.
+Whether intentional or accidental, the system should prevent violations of agreed contract rules or local jurisdiction.
+The rules are set by law and enforced by the police.
 
@@
 programmable and autonomous contracts.
-The smart contract code encompasses the contract's specifications, hence the slogan \textit{code as a law}.
-Moreover, smart contracts are automatically executed merging together the gap between law and its enforcement by police~\cite{allenGovernanceBlockchainDispute2019}.
+The code of the smart contract contains the specifications of the contract, hence the slogan \textit{code as law}.
+In addition, smart contracts are executed automatically, bridging the gap between law and its enforcement by police~\cite{allenGovernanceBlockchainDispute2019}.
 However, the blockchain paradigm has its limitations.
 
-Blockchain can assure the correctness of data existing only on the blockchain.
-The problem arises in the contact between the blockchain and the real world when we want the smart contract to decide based on some input from outside the blockchain.
-The technique of providing real-world data to the blockchain is called an oracle.
-Oracle provides data based on a decentralized network of mediators; therefore, the trust is also decentralized~\cite{breidenbachChainlinkNextSteps2021}.
-
-Some oracles provide the data like weather, soccer match result, stock
-price, train delay, election results, and others—and they are the ones we
-are interested in—provide the settlement of a submitted dispute.
-
-Themis~\cite{mengThemisDecentralizedEscrow2019} besides providing fair exchange protocol,
-also offers a semi-autonomous decentralized dispute resolution system that complies with the Web3 postulates of a decentralized web~\cite{ethereumWhatWeb3Why2023}.
-Themis resolve disputes by a set of voluntary anonymous mediators participating in voting and deciding whether a party misbehaved.
-The honesty of mediators is achieved by the monetary incentivization and reputation system.
-
-Kleros~\cite{bergollaKlerosSociolegalCase2022} is a smart contract deployed on the Ethereum platform that mimics in a decentralized and autonomous way how the court works in real life.
-In Kleros, every process of a dispute like gathering evidence, selecting jurors, and rewarding the winning party is automated by a set of smart contracts.
-Like Themis, the honesty of the agents voting in a case is achieved by game-theoretical economic incentives.
-
-Such a decentralized, voluntary, and anonymous dispute resolution system might work for simple contracts violations like an eBay seller sending broken or wrong products or an Airbnb apartment being inadequate to the photos in the offer.
-However, it is hard to realize such a decentralized evaluation of health or legal services quality when expertise and privacy concerns are taken into account.
-Therefore, in our protocol, we take a more conservative approach and resolve disputes by recording evidence on blockchain and then using the local justice system (police or court) to settle the conflict.
-
-Possible directions toward semi-autonomous decentralized resolution system are discussed in Section~\ref{sec:decentralised-justice}.
+Blockchains can only guarantee the correctness of the data and calculations that exist on the blockchain.
+The problem arises when we want the smart contract to make decisions based on some input from outside the blockchain.
+The technique for providing real-world data to the blockchain is called \textit{oracle}.
+An oracle provides data based on a decentralised network of mediators, so the trust is also decentralised~\cite{breidenbachChainlinkNextSteps2021}.
+
+Some oracles provide data such as weather, football results, stock prices, train delays, election results and others-and these are the ones we are interested in-provide the resolution of a submitted dispute.
+
+Themis~\cite{mengThemisDecentralizedEscrow2019} not only provides a fair exchange protocol, it also provides a semi-autonomous decentralised dispute resolution system that complies with the Web3 postulates of a decentralised Web~\cite{ethereumWhatWeb3Why2023}.
+Themis resolves disputes through a set of voluntary, anonymous mediators who take part in voting and decide whether a party has misbehaved.
+The honesty of the mediators is achieved through a monetary incentive and reputation system.
+
+Kleros~\cite{bergollaKlerosSociolegalCase2022} is a smart contract deployed on the Ethereum platform that mimics, in a decentralised and autonomous way, how the court works in real life.
+In Kleros, every process of a dispute, such as gathering evidence, selecting jurors and rewarding the winning party, is automated by a set of smart contracts.
+As in Themis, the honesty of the agents voting in a case is achieved through game-theoretic economic incentives.
+
+Such a decentralised, voluntary and anonymous dispute resolution system might work for simple breaches of contract, such as an eBay seller sending broken or wrong products, or an Airbnb apartment that does not match the photos in the listing.
+However, it is difficult to implement such a decentralised assessment of the quality of health or legal services when expertise and privacy concerns are taken into account.
+Therefore, our protocol takes a more conservative approach and resolves disputes by recording evidence on the blockchain and then using the local justice system (police or courts) to resolve the conflict.
+
+Possible directions towards a semi-autonomous decentralised resolution system are discussed in Section~\ref{sec:decentralised-justice}.
 
@@
 
-In case of dispute, the customer can prove to justice (police or court) convincing evidence for the honesty of the customer and the misbehavior of the SP. 
-Because the customer is anonymous, the SP can not start a dispute---there is no means to identify the customer.
-
-To mitigate the issue, we designed the protocol so that the SP who follows the protocol is always in an advantaged position; therefore, she has no reason to start a dispute.
-On the other hand, the customer can start a dispute at any time of the protocol, but only the actual misbehavior of the SP makes him win the case.
-
-Abstracting from the services the SP is providing, each party should be able to prove its honest behavior in case of a dispute.
-We introduce three proofs that should be disclosed to justice in case of a dispute:
+In the event of a dispute, the customer can provide convincing evidence of the customer's honesty and the SP's misbehaviour to the judicial authorities (police or court). 
+Because the customer is anonymous, the SP cannot start a dispute - there is no way to identify the customer.
+
+To mitigate this problem, we have designed the protocol in such a way that the SP who follows the protocol is always in an advantageous position and therefore has no reason to start a dispute.
+On the other hand, the customer can start a dispute at any point in the protocol, but only the actual misbehaviour of the SP will allow him to win the case.
+
+Abstracting from the services provided by the SP, each party should be able to prove its honest behaviour in case of a dispute.
+We present three pieces of evidence that should be disclosed to the judiciary in the event of a dispute:
 
 \begin{enumerate}
-    \item Proof of delivery ($\mathrm{PoD}$) is a confirmation issued by the SP to the customer that proves that the customer has delivered to the SP a complete (according to the SP requirements) package, and the SP accepted it.
-It consists of the current time, the deadline to pay for the transaction, the deadline to provide a result of the service, the randomly generated number uniquely identifying the transaction, and the SP's signature guaranteeing non-repudiation.
-The formal definition of the $\mathrm{PoD}$ is presented in section ~\ref{proof-of-delivery}.
-
-    \item Payment $\mathrm{receipt}$ is confirmation that the customer has paid for the transaction at a certain time.
-The actual implementation depends on the particular cryptocurrency and is discussed further Section~\ref{payment-for-services}.
-
-    \item Proof of provision ($\mathrm{PoP}$) is proof that the SP published the result at a certain time.
-It defends the SP in case the customer unjustly starts a dispute after the result has been published.
-It consists of a content identifier as specified in section ~\ref{storage-network}, the $\mathrm{nonce}$ uniquely identifying the transaction previously generated in $\mathrm{PoD}$, and the SP's signature guaranteeing authentication.
-The connection between $\mathrm{PoP}$ and the result is created by the content identifier ($\mathrm{cid}$) that uniquely identifies the result (it is some kind of a hash of the result) such that the result can not be forged after the $\mathrm{PoP}$ has been published.
+    \item Proof of Delivery ($\mathrm{PoD}$) is a confirmation issued by the SP to the customer proving that the customer has delivered a complete (according to the SP's requirements) package to the SP and that the SP has accepted it.
+It consists of i) the current time, ii) the deadline to pay for the transaction, iii) the deadline to provide a result of the service, iv) the transaction identifier ($\textrm{provisionID}$) randomly generated by the customer, v) and the signature of the SP guaranteeing non-repudiation.
+The formal definition of $\mathrm{PoD}$ is given in Section~\ref{proof-of-delivery}.
+
+    \item Payment $\mathrm{receipt}$ is the confirmation that the customer has paid for the transaction at some point in time.
+The actual implementation depends on the cryptocurrency and is discussed further in Section~\ref{payment-for-services}.
+
+    \item Proof of Provision ($\mathrm{PoP}$) is the proof that the SP has published the result at a given time.
+It defends the SP in case the customer unjustifiably starts a dispute after the result has been published.
+It consists of i) a content identifier (as specified in Section ~\ref{storage-network}), ii) the $\textrm{provisionID}$ that uniquely identifies the transaction, and iii) the SP's signature that guarantees authentication.
+The link between $\mathrm{PoP}$ and the results is provided by the content identifier ($\mathrm{cid}$) that uniquely identifies the result (it is a kind of hash of the result), so that the result cannot be forged after the $\mathrm{PoP}$ is published.
 \end{enumerate}
@@
 \subsection{Message Board}\label{sec:message-board}
-The proof of provision that we coined for the purpose of this protocol is generally called the proof of existence~\cite{crespoStamperyBlockchainTimestamping2017}.
-
-The idea behind proof of existence is to certify that some information
-has existed at a certain moment, in such a way that nobody can
-undermine its existence, integrity, and ownership (also called the
-non-repudiation requirement).
-
-We need this functionality for two reasons: (1) communicate the existence of the result to the customer to whom the SP has no other communication medium as the customer stays anonymous; (2) let the SP proof the publication of the result within the agreed with customer deadline.
-
-By publishing the $\mathrm{PoP}$ on the blockchain, the SP can not falsify the time at which the result has been provided because the block creation time proves that.
-Blockchain acts as a global clock that securely timestamps everything that gets into the block, so the $\mathrm{PoP}$ that was included in a block will be associated with the time when the block has been created.
-Moreover, since the blockchain is public, everyone (including justice) can be convinced that the SP indeed published the result at that time.
-
-Without such proof, there would be no other means to settle the conflict between the customer claiming the result has not been published and the SP claiming the result has been published within the deadline.
-
-Depending on the context the platform for achieving it is called bulletin board~\cite{achenbachImprovedCoercionresistantElectronic2015}, trusted timestamping~\cite{gippDecentralizedTrustedTimestamping2015}, or message board~\cite{hinarejosSolutionSecureCertified2019}.
-In this work, we call it a message board.
-
-We keep the protocol general enough to be implemented using any existing technology to provide message board service, assuming it is decentralized and supports subscribing for the upcoming proofs from a particular address.
+The Proof of Provision ($\mathrm{PoP}$) that we have coined for the purposes of this protocol is commonly called Proof of Existence~\cite{crespoStamperyBlockchainTimestamping2017}.
+
+The idea behind Proof of Existence is to certify that a piece of information existed at a certain point in time, in such a way that nobody can undermine its existence, integrity or ownership (also called the non-repudiation property).
+
+We need this functionality for two reasons: (1) to communicate the existence of the results to the customer, to whom the SP has no other means of communication, since the customer remains anonymous; (2) to let the SP prove the publication of the result within the deadline agreed with the customer.
+
+By publishing the $\mathrm{PoP}$ on the blockchain, the SP cannot falsify the time at which the results were provided, as the block creation time proves it.
+The blockchain acts as a global clock that securely timestamps everything that goes into the block, so the $\mathrm{PoP}$ included in a block is associated with the time the block was created.
+Moreover, since the blockchain is public, anyone (including the judiciary) can be convinced that the SP did indeed publish the result at that time.
+
+Without such proof, there would be no other way to resolve the conflict between the customer claiming that the results were not published and the SP claiming that the results were published on time.
+
+Depending on the context, the platform for achieving this is called bulletin board~\cite{achenbachImprovedCoercionresistantElectronic2015}, trusted timestamping~\cite{gippDecentralizedTrustedTimestamping2015}, or message board~\cite{hinarejosSolutionSecureCertified2019}.
+In this paper we call it a message board.
+
+We keep the protocol general enough to be implemented using any existing technology to provide a message board service, provided it is decentralised and supports subscribing to upcoming proofs from a given address.
 
@@
 
-Privacy is a concept used in almost all social sciences like philosophy, psychology, sociology, and legal.
-The multidisciplinary nature leads to ambiguous definitions~\cite{smithInformationPrivacyResearch2011}.
-For our work, we rely on more concrete definitions, i.e.~confidentality, and anonymity.
-
-Confidentiality is the ability to hide the details of action from others.
-Alternatively, we can say that the system guarantees confidentiality if, for all observers, everything they can say about the action is the fact that it happened and nothing more.
-
-Anonymity is the ability to hide one identity from others.
-More precisely, the inability to correlate actions performed within the system with the user's identity.
+Privacy is a concept used in almost all social sciences such as philosophy, psychology, sociology and law.
+This multidisciplinary nature leads to ambiguous definitions~\cite{smithInformationPrivacyResearch2011}.
+For our work we rely on more concrete definitions, i.e.~confidentiality and anonymity.
+
+Confidentiality is the ability to hide the details of actions from others.
+Alternatively, we can say that the system guarantees confidentiality if, for all observers, all they can say about the action is the fact that it happened and nothing more.
+
+Anonymity is the ability to hide one's identity from others.
+More specifically, it is the inability to correlate actions taken within the system with the identity of the user.
 Alternatively, we can say that the system guarantees anonymity if, for all observers, the actions are equally likely to be associated with any user of the system.
 However, anonymity is a spectrum rather than a dichotomous classification.
-One method of quantifying the level of anonymity is \textit{k}-anonymity proposed in~\cite{sweeneyKanonymityModelProtecting2002}.
-It measures the user's anonymity by the number of other users from whom the user can not be distinguished.
-Concretely, the user is \textit{k}-anonymous if his actions are equally likely associated with \textit{k}-1 other users; the larger \textit{k}, the higher anonymity.
-
-Some anonymity techniques can be deployed on non-anonymous blockchains.
-The so-called mixers gather users into an \textit{anonymity set}, which then collude together to launder transactions in such a way that to an observer, the likelihood of the sender of each transaction is equiprobable for any user from the anonymity set.
-
-Some systems guarantee pseudonymity rather than anonymity.
-Pseudonymity allows users to hide their real identity behind pseudonyms.
-Despite the whole system being transparent and allowing linking actions to pseudonyms, the system is considered anonymous as long as the link between pseudonyms and real identities is secret.
-This assumption is hard to satisfy in practice, as the KYC (Know Your Customer) and AML (Anti Money Laundering) regulations require users to reveal their real identity to cryptocurrency exchanges, making the user's anonymity dependent on the security of the IT system.
-Moreover, some correlations can be inferred merely by the analysis of transactions \cite{androulakiEvaluatingUserPrivacy2013, oberStructureAnonymityBitcoin2013}.
-
-Figure ~\ref{fig:anonymity-diagram} illustrates relations between these terms.
+One method of quantifying the level of anonymity is the \textit{k}-anonymity proposed in~\cite{sweeneyKanonymityModelProtecting2002}.
+It measures the user's anonymity by the number of other users from whom the user is indistinguishable.
+Specifically, the user is \textit{k}-anonymous if his actions are equally likely to be associated with \textit{k}-1 other users; the larger the \textit{k}, the greater the anonymity.
+
+Some anonymity techniques can be used on non-anonymous blockchains.
+The so-called mixers gather users into an anonymity set who then collude to launder transactions in such a way that, to an observer, the likelihood of the sender of each transaction being any user from the anonymity set is equiprobable.
+
+Some systems provide pseudonymity rather than anonymity.
+Pseudonymity allows users to hide their real identities behind pseudonyms.
+Although the whole system is transparent and allows actions to be linked to pseudonyms, the system is considered anonymous as long as the link between pseudonyms and real identities is secret.
+This assumption is difficult to meet in practice, as KYC (Know Your Customer) and AML (Anti Money Laundering) regulations require users to reveal their real identities to cryptocurrency exchanges, exposing users' privacy to government agencies, malicious insiders and cyber criminals.
+In addition, some correlations can be inferred simply by analysing transactions~\cite{androulakiEvaluatingUserPrivacy2013, oberStructureAnonymityBitcoin2013}.
+
+Figure~\ref{fig:anonymity-diagram} illustrates the relationships between these terms.
 
@@
 \centering
-\caption{Let us assume Alice to be the customer willing to keep her identity anonymous and Bob to be the public SP.
-Alice controls two addresses, 1 and 2; the connection between her real identity and the first address has been compromised, and therefore the identification is possible; the connection between the second pseudonym is still unknown and therefore anonymous.
-Alice takes two actions; the first one from the compromised address and the second one from the anonymous one.
-The first action is confidential; therefore, even though the pseudonym has been compromised, the action can not be associated with Alice.
-The second action is transparent; therefore, Alice maintains her anonymity as long as the connection to the second pseudonym is concealed.}
+\caption{Suppose Alice is the client who wants to keep her identity anonymous and Bob is the public SP.
+Alice controls two addresses 1 and 2; the link between her real identity and the first address has been compromised and therefore identification is possible; the link to the second pseudonym is still unknown and therefore anonymous.
+Alice takes two actions, the first from the compromised address and the second from the anonymous address.
+The first action is confidential; therefore, even though the pseudonym has been compromised, the action cannot be associated with Alice.
+The second action is transparent, so Alice maintains her anonymity as long as the link to the second pseudonym is concealed.}
 
@@
 \end{figure}
-
-The privacy-preserving blockchains are the ones that maintain anonymity via untraceability and (ideally) unlikability, not via the assumption that the connection between an address (pseudonym) and the real identity is concealed.
-
-Examples of blockchains that natively support confidential transactions are: Monero~\cite{vansaberhagenCryptoNote2013} (using Ring Signatures~\cite{noetherRingSignatureConfidential2015} or Bulletproofs~\cite{bunzBulletproofsShortProofs2018}), ZCash~\cite{ben-sassonZerocashDecentralizedAnonymous2014} (using zkSNARK~\cite{ben-sassonSNARKsVerifyingProgram2013}), Grin~\cite{fuchsbauerAggregateCashSystems2019} (using Mimblewimble~\cite{jedusorMIMBLEWIMBLE2016}), and IronFish~\cite{ironfishPrivateAnonymousEasy} (using Sapling protocol~\cite{hopwoodZcashSaplingProtocol2022}).
-
-Overly techniques that achieve anonymity on top of non-privacy-preserving blockchains are: Ethereum's Tornado Cash~\cite{pertsevTornadoCashPrivacy2019} (via zkSNARK~\cite{grothSizePairingbasedNoninteractive2016} and MiMC~\cite{albrechtMiMCEfficientEncryption2016}), Bitcoin's Wasabi~\cite{wasabiwalletBitcoinPrivacyWallet} (via CoinJoin~\cite{maxwellCoinJoinBitcoinPrivacy2013}).
+The privacy-preserving blockchains are those that maintain anonymity through untraceability and (ideally) unlikability - not by assuming that the link between an address (pseudonym) and real identity is hidden.
+
+Examples of blockchains that natively support confidential transactions include Monero~\cite{vansaberhagenCryptoNote2013} (using Ring Signatures~\cite{noetherRingSignatureConfidential2015} or Bulletproofs~\cite{bunzBulletproofsShortProofs2018}), ZCash~\cite{ben-sassonZerocashDecentralizedAnonymous2014} (using zkSNARK~\cite{ben-sassonSNARKsVerifyingProgram2013}), Grin~\cite{fuchsbauerAggregateCashSystems2019} (using Mimblewimble~\cite{jedusorMIMBLEWIMBLE2016}), and IronFish~\cite{ironfishPrivateAnonymousEasy} (using Sapling protocol~\cite{hopwoodZcashSaplingProtocol2022}).
+
+Overly techniques that achieve anonymity on top of non-privacy preserving blockchains are Ethereum's Tornado Cash~\cite{pertsevTornadoCashPrivacy2019} (via zkSNARK~\cite{grothSizePairingbasedNoninteractive2016} and MiMC~\cite{albrechtMiMCEfficientEncryption2016}), Bitcoin's Wasabi~\cite{wasabiwalletBitcoinPrivacyWallet} (via CoinJoin~\cite{maxwellCoinJoinBitcoinPrivacy2013}).
 
 \subsection{Payment for services}\label{payment-for-services}
-Transactions between customers and SPs must be pegged to prevent reusing one payment for multiple transactions. 
-In other words, we need a mechanism that uniquely associates a payment with the corresponding transaction.
-
-Depending on the cryptocurrency, the link can be created in different
-ways:
-
-\begin{itemize}
-
-\item separate address: each transaction uses an unique address associated with the transaction.
-Such addresses can be derived using Hierarchical Deterministic Wallets~\cite{wuilleBIP32HierarchicalDeterministic2012} and published on message board, to achieve non-repudiation.
-\item memo: the payments are sent to sigle SP account, but contain an extra field named ``memo'' filled with the unique indentifier $\textrm{provisionID}$. 
-\end{itemize}
-
-Each payment containing the $\textrm{provisionID}$ in the memo, or payment to the dedicated address is considered to pay for the transaction.
-
-In case of a dispute, there must be a way to prove to justice that the customer has paid for the transaction.
-As the proof of payment is trivial in transparent and trackable blockchains, it gets more complicated when it comes to anonymous blockchains.
-Monero allows proving and checking payments via dedicated API~\cite{moneroHowProvePayment}.
+Transactions between customers and SPs need to be linked to prevent the reuse of a payment for multiple transactions.
+In other words, we need a mechanism that uniquely links the payment to the corresponding transaction.
+
+Depending on the cryptocurrency, this link can be established in different ways:
+
+\begin{itemize}
+\item separate address: each transaction uses a unique address associated with the transaction.
+Such addresses can be derived using Hierarchical Deterministic Wallets~\cite{wuilleBIP32HierarchicalDeterministic2012} and published on the message board to achieve non-repudiation.
+\item memo: payments are sent to a single SP account, but contain an extra field called ``memo'' filled with the unique identifier $\textrm{provisionID}$. 
+\end{itemize}
+
+Any payment that contains $\textrm{provisionID}$ in the memo or is sent to the designated address will be considered payment for the transaction.
+
+In the event of a dispute, there must be a way to prove to the courts that the customer has paid for the transaction.
+As proof of payment is trivial in transparent and traceable blockchains, it becomes more complicated when it comes to anonymous blockchains.
+Monero allows payments to be proven and verified via a dedicated API~\cite{moneroHowProvePayment}.
 ZCash provides a mechanism called Payment Disclosure~\cite{daviesIntroductionPaymentDisclosure2017}.

### 2023-06-20 paper/main.tex
-m

@@
 \usepackage{scalerel}
-\input{constants}
+
+\newcommand{\customer}{customer}
+\renewcommand{\sp}{SP}
+
+\newcommand{\normal}{n}
+\newcommand{\dispute}{d}
+\newcommand{\abnormal}{\overline{n}}
+\newcommand{\abdispute}{\overline{d}}
+
+\newcommand{\PoD}{$\mathrm{PoD}$}
+\newcommand{\PoP}{$\mathrm{PoP}$}
+\newcommand{\cid}{$\mathrm{cid}$}
+
+\newcommand{\floor}[1]{\left\lfloor #1 \right\rfloor}
+\newcommand{\ceil}[1]{\left\lceil #1 \right\rceil}
+
+\newcommand{\plus}{+}
+\newcommand{\minus}{-}
+\newcommand\neutral[1][.75]{\mathbin{\ThisStyle{\vcenter{\hbox{%
+  \scalebox{#1}{$\SavedStyle\bullet$}}}}}%
+}
+
+\def\SINGLECOLUMN{SINGLE}
+\def\DOUBLECOLUMN{DOUBLE}
+\def\JOURNALIEEE{IEEE}
+\def\JOURNALELS{ELS}
+
+\newcommand\TITLE{Anonymous provision of privacy-sensitive services using blockchain and decentralised storage}
+\newcommand\STANLONG{Stanis\l{}aw Bara{\'n}ski}
+\newcommand\JULLONG{Julian Szyma{\'n}ski}
+\newcommand\HIGILONG{Higinio Mora}
+\newcommand\STAN{S. Bara{\'n}ski}
+\newcommand\JUL{J. Szyma{\'n}ski}
+\newcommand\HIGI{H. Mora}
+
+\newcommand\ABSTRACT{
+Lawyers, laboratories, auditors or banks often need data containing sensitive personal information to provide their services.
+Examples of sensitive services include genetic testing, paternity testing, STD testing, credit scoring or legal advice.
+
+The processing of personal data, especially when providing services involving sensitive data such as health records, biological material or legal documents, exposes both users and service providers (SPs) to privacy risks.
+SPs are at risk of violating GDPR, CPAA and other legal regulations, while customers are at risk of losing their privacy.
+
+We observe that personal data is often only used for logistical purposes, such as payment or communication, and could be provided anonymously if such methods were available.
+
+We present a solution that allows services to be provided without collecting personal data.
+We use anonymous payment methods such as cash and anonymous cryptocurrencies, blockchain to achieve fairness, and distributed content-addressable storage networks to deliver results.
+
+Compared to other solutions, our protocol achieves anonymity with weaker assumptions, supports physical materials and conflict resolution, and does not require the customer to interact with the blockchain in conflict-free transactions, demonstrating better practicality.
+
+In this work, we analyse the fairness of our protocol and implement it using Ethereum technology as a message board, Monero as an anonymous payment method, and Powergate (IPFS and Filecoin) as a decentralised storage network.
+}
+
+\newcommand\ACKNOWLEDGEMENTS{
+The work has been supported partially by the founds of Department of Computer Architecture Faculty of Electronics, Telecommunications and Informatics, Gdańsk University of Technology.
+}
+
+\newcommand\LASTVISITED{(last visited Jan. 31, 2023)}
 
@@
 We propose an anonymous protocol for the provision of services that require physical materials.
-In the event of a dispute, either due to missed deadlines or incorrect results, the customer can disclose the entire interaction, prove the SP's misbehaviour to justice, and win the dispute.
+In the event of a dispute, either due to missed deadlines or incorrect results, the customer can disclose the entire interaction, prove the SP's misbehaviour to the Dispute Resolution Service, and win the dispute.
 
@@
 Also, our protocol does not have its own dispute resolution mechanism, as Themis does.
-However, we assume the existence of an abstract justice that accepts evidence and punishes the misbehaving party.
-This can be instantiated either with the local court or police, or with one of the blockchain's
-dispute resolution services such as Themis~\cite{mengThemisDecentralizedEscrow2019}, Kleros~\cite{bergollaKlerosSociolegalCase2022,gudkovCrowdArbitrationBlockchain2020}, Aragon Court~\cite{aragonDecentralizedDisputeResolution}, LTO Network~\cite{ltonetworkNextGenBlockchainB2B,ltonetworkOnchainIdentitiesCredentials}, and other Online Dispute Resolution platforms~\cite{allenGovernanceBlockchainDispute2019}.
+However, we assume the existence of an abstract Dispute Resolution Service that accepts evidence and punishes the misbehaving party.
+This can be instantiated either with the local court or police, or with one of the blockchain's dispute resolution services such as Themis~\cite{mengThemisDecentralizedEscrow2019}, Kleros~\cite{bergollaKlerosSociolegalCase2022,gudkovCrowdArbitrationBlockchain2020}, Aragon Court~\cite{aragonDecentralizedDisputeResolution}, LTO Network~\cite{ltonetworkNextGenBlockchainB2B,ltonetworkOnchainIdentitiesCredentials}, and other Online Dispute Resolution platforms~\cite{allenGovernanceBlockchainDispute2019}.
 
@@
 \subsection{Storage network}\label{storage-network}
-Once the SP finishes its service, she has to provide the result to the customer.
-The most natural approach would be to send the result via e-mail or some dedicated platform.
-However, the customer wants to stay anonymous and so does not want to expose his e-mail address nor IP address.
-Moreover, the SP should prove that the result has been provided before the deadline, which brings us to the issue of proof of existence discussed in Section ~\ref{sec:message-board}.
-
-One approach would be to post the result into a blockchain.
+Once the SP has completed its service, it needs to deliver the result to the customer.
+The most natural approach would be to send the result via email or a dedicated platform.
+However, the customer wants to remain anonymous and does not want to reveal his email address or IP address.
+Furthermore, the SP needs to prove that the result was delivered before the deadline, which brings us to the issue of proof of existence discussed in Section~\ref{sec:message-board}.
+
+One approach would be to post the result to a blockchain.
 However, storing data on a blockchain is very expensive.
-The most common workaround (\cite{shahidBlockchainBasedAgriFoodSupply2020, wangAuditableProtocolsFair2019, chenImprovedP2PFile2017}) is to publish the data on a content addressable peer-to-peer storage network like IPFS~\cite{benetIPFSContentAddressed2014}.
-Then, publish on the blockchain just the content identifier ($\mathrm{cid}$) that uniquely points to the content stored on IPFS.
-
-We take the same approach. Once the SP creates the result, she encrypts it using the previously provided encryption key and uploads it to the IPFS network.
-%TODO: write about DHKE encyption
-
-To increase anonymity, the customer should use standard techniques to hide its IP address, such as VPN, or proxy.
+The most common workaround (\cite{shahidBlockchainBasedAgriFoodSupply2020, wangAuditableProtocolsFair2019, chenImprovedP2PFile2017}) is to publish the data on a content addressable peer-to-peer storage network such as IPFS~\cite{benetIPFSContentAddressed2014}.
+Then publish only the content identifier ($\mathrm{cid}$) on the blockchain, which uniquely points to the content stored on IPFS.
+
+We follow the same approach. Once the SP has produced the result, it encrypts it using the previously provided encryption key and uploads it to the IPFS network.
+
+We also use Filecoin to guarantee that the results are available to the customer even if the SP refuses to share the result (see Section ~\ref{sec:provable-results-availability}).
+
+To increase anonymity, the customer should use standard techniques to hide their IP address, such as VPN or proxy.
 
 \subsection{Separation of concerns}
-We could use one blockchain to achieve all of these three roles: (i) anonymous payments, (ii) message board, (iii) storage network.
-
-While most blockchains could provide message board functionality, anonymous payments are not as common. Especially a provable storage network is a functionality of a few specialized blockchains.
-
-Instead of searching for one blockchain that provides all the functionalities, we allow the protocol to use separate blockchains for each role.
-If a suitable blockchain arises, it can play more than one role.
-
-At the time of writing, we see the following technologies that fulfill the requirements of each role:
+We could use a single blockchain to achieve all three of these roles: i) anonymous payments, ii) message board, and iii) storage network.
+
+While most blockchains could provide message board functionality, anonymous payments are not as common. In particular, a verifiable storage network is a feature of a few specialised blockchains.
+
+Rather than searching for a single blockchain to provide all functionalities, we allow the protocol to use separate blockchains for each role.
+If a suitable blockchain emerges, it can play more than one role.
+
+At the time of writing, we see the following technologies fulfilling the requirements of each role:
 
@@
 \section{The Protocol}\label{sec:protocol}
-In this section, we propose an abstract protocol for anonymous service provisioning without any assumptions about the underlying technologies.
-We define the requirements for each role and leave the choice of the technology to the developer.
-Later in the paper (Section~\ref{sec:experiments}) we describe our implementation used to conduct an experiment.
+In this section, we propose an abstract protocol for anonymous service provisioning that makes no assumptions about the underlying technologies.
+We define the requirements for each role and leave the choice of technology to the developer.
+Later in the paper (Section~\ref{sec:experiments}) we describe our implementation, which we use to conduct an experiment.
 
@@
 
-\item Justice:
+\item Dispute Resolution Service:
     \begin{itemize}
@@
 
-\item Anonymous payments blockchain:
-    \begin{itemize}
-        \item supports anonymous, i.e., untraceable and (ideally) unlinkable transactions as specified in Section~\ref{sec:pseudo-anon}.
-        \item supports uniquely identifying transactions via a dedicated address, memo field, or other similar mechanisms as described in Section ~\ref{payment-for-services}. 
+\item Anonymous Payments Blockchain:
+    \begin{itemize}
+        \item supports anonymous, i.e., untraceable and (ideally) unlinkable transactions as described in Section~\ref{sec:pseudo-anon}.
+        \item supports uniquely identifiable transactions via a dedicated address, memo field, or other similar mechanisms as described in Section ~\ref{payment-for-services}. 
     \end{itemize}
@@
 
-\item Storage network:
-    \begin{itemize}
-        \item allows for content retrieval via content identifier $\mathrm{cid}$ (usually a hash of the content).
-        \item allows for anonymous content retrieval.
-        \item guarantee that the content will be available for the duration of the agreement.
+\item Storage Network:
+    \begin{itemize}
+        \item allows content to be retrieved using a content identifier $\mathrm{cid}$ (usually a hash of the content).
+        \item allows content to be retrieved anonymously.
+        \item guarantees that the content will be available for the duration of the agreement.
     \end{itemize}
@@
 \noindent \textbf
-{Package}\label{package} is a physical container prepared by the customer encompassing all $\mathrm{materials}$ required by the SP to provide the service.
+{Package}\label{package} is a physical container prepared by the customer encompassing all the $\mathrm{materials}$ required by the SP to provide the service.
 
@@
 
-\item $\mathrm{materials}$ - are the materials required to provide the service, for example, samples of urine, blood, stool, saliva; legal documents, CDs, emails, photos, bank statements; or any other kind of materials depending on the service.
-\item $\mathrm{provisionID}$ - a randomly generated provision identifier, used to anonymously track the provision throughout the protocol's steps.
-\item $\mathrm{pk(C)}$ - customer's public key used to encrypt the result published on the public storage network.
+\item $\mathrm{materials}$ - are the materials required to provide the service, for example, samples of urine, blood, stool, saliva; legal documents, CDs, emails, photos, bank statements; or any other type of material depending on the service.
+\item $\mathrm{provisionID}$ - a randomly generated provision identifier, used to anonymously track the provision through all steps of the protocol.
+\item $\mathrm{pk(C)}$ - the customer's public key used to encrypt the results published to the public storage network.
 \end{itemize}
@@
 \noindent \textbf
-{Proof of delivery ($\mathrm{PoD}$)}\label{proof-of-delivery} is an attestation to the fact that the customer has delivered a correct (according to the SP requirements) package to the SP, and the SP has accepted it.
-
-It is also an agreement between the customer and the SP, as it includes agreed upfront deadlines of actions and a payment method.
-
-$\mathrm{PoD}$ is published on the message board by the SP.
+{Proof of Delivery ($\mathrm{PoD}$)}\label{proof-of-delivery} is a confirmation that the customer has delivered a correct (according to the SP's requirements) package to the SP and that the SP has accepted it.
+
+It is also an agreement between the customer and the SP, as it includes agreed-upon deadlines for actions and a method of payment.
+
+The $\mathrm{PoD}$ is published on the message board by the SP.
 
@@
 \item
-  $\mathrm{T}_\mathrm{pay}$ - deadline to pay for the transaction.
+  $\mathrm{T}_\mathrm{pay}$ - deadline for paying the transaction.
 \item
-  $\mathrm{T}_\mathrm{provide}$ - deadline to provide the result of the service, i.e. publish $\mathrm{PoP}$.
+  $\mathrm{T}_\mathrm{provide}$ - deadline to provide the result of the service, i.e. to publish $\mathrm{PoP}$.
 \item $\mathrm{address}$ - payment address of the SP's anonymous blockchain account.
-\item $\mathrm{provisionID}$ - the number uniquely identifying the transaction previously generated by the customer.
-\item $\mathrm{pk(C)}$ - customer's public key used to encrypt the result published on the public storage network.
-\item $\mathrm{sig}_\mathrm{SP}$ - the SP's signature guaranteeing non-repudiation.
+\item $\mathrm{provisionID}$ - the number that uniquely identifies the transaction previously generated by the customer.
+\item $\mathrm{pk(C)}$ - the public key of the client used to encrypt the result published on the public storage network.
+\item $\mathrm{sig}_\mathrm{SP}$ - the SP's signature to ensure non-repudiation.
 \end{itemize}
@@
 {Proof of provision ($\mathrm{PoP}$)}\label{proof-of-provision} is proof that the SP published the result at a certain time.
-It protects the SP in case the customer unjustly starts a dispute after the result has been published.
-The connection between $\mathrm{PoP}$ and the result is made by the content identifier ($\mathrm{cid}$) uniquely identifying the result such that the result can not be forged after the $\mathrm{PoP}$ has been published.
-
-$\mathrm{PoP}$ is published on the message board by the SP.
+It protects the SP in case the customer unjustifiably starts a dispute after the results have been published.
+The link between $\mathrm{PoP}$ and the results is made by the content identifier ($\mathrm{cid}$), which uniquely identifies the results so that the result cannot be forged after the $\mathrm{PoP}$ has been published.
+
+The $\mathrm{PoP}$ is published on the message board by the SP.
 
@@
 
-\item $\mathrm{cid}$ - content identifier as specified in Section~\ref{storage-network}.
-\item $\mathrm{provisionID}$ - the number uniquely identifying the transaction previously generated by the customer.
-\item $\mathrm{sig}_\mathrm{SP}$ - the SP's signature guaranteeing non-repudiation.
+\item $\mathrm{cid}$ - the content identifier as specified in Section~\ref{storage-network}.
+\item $\mathrm{provisionID}$ - The number that uniquely identifies the transaction previously created by the customer.
+\item $\mathrm{sig}_\mathrm{SP}$ - the signature of the SP, which guarantees non-repudiation.
 \end{itemize}
@@
 \noindent \textbf
-{Payment receipt}\label{payment-receipt} proves that the customer did the payment.
-Since the evidence depends on a particular blockchain (see Section~\ref{payment-for-services}), we refer to it symbolically as
-$\mathrm{receipt}$.
+{Payment-receipt}\label{payment-receipt} proves that the customer made the payment.
+Since the proof depends on a specific blockchain (see Section~\ref{payment-for-services}), we symbolically refer to it as $\mathrm{receipt}$.
 
 \noindent \textbf
-{Result}\label{results} is assumed to be a document in PDF format, but any other format is allowed as long as it can be binary encoded and uploaded to the storage network.
-We refer to it symbolically as $\mathrm{result}$.
+{Results}\label{results} is assumed to be a document in PDF format, but any other format is acceptable as long as it can be binary encoded and uploaded to the storage network.
+We symbolically refer to it as $\mathrm{results}$.
 
@@
 
-In this section, we describe each step of the protocol, also shown in the Figure~\ref{fig:protocol-diagram}.
+In this section we describe each step of the protocol, also shown in Figure~\ref{fig:protocol-diagram}.
 
@@
 
-The customer collects all the $\mathrm{materials}$ required by the SP, generates a random $\mathrm{provisionID}$ and a random keypair $(\mathrm{sk(C)},\mathrm{pk(C)})$.
-The $\mathrm{provisionID}$ will be used to associate all actions related to the transaction throughout the protocol.
-The $\mathrm{provisionID}$ and $\mathrm{pk(C)}$ are encoded as a QR code, printed, and stuck to the package $\mathrm{pkg}$.
-The $\mathrm{sk(C)}$ is kept secret and used to decrypt the $\mathrm{result}$ at the end of the protocol.
+The customer collects all $\mathrm{materials}$ required by the SP, generates a random $\mathrm{provisionID}$ and a random keypair $(\mathrm{sk(C)},\mathrm{pk(C)})$.
+The $\mathrm{provisionID}$ is used to connect all actions associated with the transaction throughout the protocol.
+The $\mathrm{provisionID}$ and $\mathrm{pk(C)}$ are encoded as a QR code, printed and attached to the $\mathrm{pkg}$ package.
+The $\mathrm{sk(C)}$ is kept secret and is used to decrypt the $\mathrm{result}$ at the end of the protocol.
 
 \noindent \textbf
-{Step 1. Package delivery}\label{step-1-package-delivery}
-
-The protocol starts once the customer delivers package $\mathrm{pkg}$ to the SP and its content gets accepted.
-As a result, $\mathrm{PoD}$ is created with predefined payment deadline $\mathrm{T}_\mathrm{pay}$, service provision deadline $\mathrm{T}_\mathrm{provide}$, and current time $\mathrm{T}_\mathrm{issue}$.
-Also, $\mathrm{PoD}$ embodies the information whether the service has been paid in cash or should be paid by the customer using the anonymous blockchain account.
-In the latter case, the SP's payment $\mathrm{address}$ is included in the $\mathrm{PoD}$.
-
-The digital signature $\mathrm{sig}_{\mathrm{sk}(\mathrm{SP})}$ on the $\mathrm{PoD}$ created with the SP's secret key $\mathrm{sk}(\mathrm{SP})$ guarantee non-repudiation.
+{Step 1. Package Delivery}\label{step-1-package-delivery}
+
+The protocol starts when the customer delivers the package $\mathrm{pkg}$ to the SP and its content is accepted.
+As a result, $\mathrm{PoD}$ is created with a predefined payment deadline $\mathrm{T}_\mathrm{pay}$, service provision deadline $\mathrm{T}_\mathrm{provide}$ and current time $\mathrm{T}_\mathrm{issue}$.
+In addition, $\mathrm{PoD}$ embodies information on whether the service was paid for in cash or whether the customer should pay using the anonymous blockchain account.
+In the latter case, the SP's payment $\mathrm{address}$ is included in $\mathrm{PoD}$.
+
+The digital signature $\mathrm{sig}_{\mathrm{sk}(\mathrm{SP})}$ on the $\mathrm{PoD}$, created with the SP's secret key $\mathrm{sk}(\mathrm{SP})$, guarantees non-repudiation.
 
@@
 
-Then, the $\mathrm{PoD}$ is published on the message board by the SP, committing to the fact that the package $\mathrm{pkg}$ has been delivered, and the SP can not reject receiving it.
-If the provision has not been paid in cash, the SP waits for the customer to pay for the service on the specified in the $\mathrm{PoD}$ payment $\mathrm{address}$.
+Then, the $\mathrm{PoD}$ is published on the message board by the SP, committing to the fact that the package $\mathrm{pkg}$ has been delivered, and the SP cannot reject receiving it.
+If the provision has not been paid in cash, the SP waits for the customer to pay for the service at the payment $\mathrm{address}$ specified in the $\mathrm{PoD}$.
 
@@
 
-Once the package is delivered and the $\mathrm{PoD}$ is published, the customer can get the $\mathrm{PoD}$ from the message board and (if everything is correct) proceed with the protocol.
+Once the package has been delivered and the $\mathrm{PoD}$ has been published, the customer can retrieve the $\mathrm{PoD}$ from the message board and (if everything is correct) proceed with the protocol.
 
@@
 
-If the provision has not been paid in cash, the customer should pay for the transaction with the predefined anonymous payment blockchain (see Section~\ref{payment-for-services}).
-In return, the customer receives the $\mathrm{receipt}$ that should be disclosed in case of a dispute.
+If the provision was not paid in cash, the customer should pay for the transaction using the predefined anonymous payment blockchain (see Section~\ref{payment-for-services}).
+In return, the customer receives the $\mathrm{receipt}$, which should be disclosed in case of dispute.
 
@@
 \noindent \textbf
-{Step 5. Provision of service}\label{step-5-provision-of-service}
-
-Once the customer has paid for the transaction either in cash or using the anonymous blockchain, the SP can start providing the service.
+{Step 5. Provision of Service}\label{step-5-provision-of-service}
+
+Once the customer has paid for the transaction, either in cash or via the anonymous blockchain, the SP can begin to provide the service.
 
@@
 
-After the service is finished, a result should be created. 
-Next, the result is encrypted using a shared key derived from the customer's public key $\mathrm{pk(C)}$ and the SP's secret key $\mathrm{sk(S)}$ using Diffie-Hellman key exchange (DHKE) method~\cite{diffieNewDirectionsCryptography1976}.
-The encrypted result is then uploaded on the content addressable network (such as IPFS). In return, the content identifier ($\mathrm{cid}$) is created.
+When the service is complete, a result should be generated. 
+Next, the result is encrypted using a shared key derived from the customer's public key $\mathrm{pk(C)}$ and the SP's secret key $\mathrm{sk(S)}$ using the Diffie-Hellman key exchange (DHKE) method~\cite{diffieNewDirectionsCryptography1976}.
+The encrypted result is then uploaded to the content addressable network (such as IPFS). In return, the content identifier ($\mathrm{cid}$) is created.
 
@@
 \noindent \textbf
-{Step 7. Proof of provision}\label{step-7-proof-of-provision}
+{Step 7. Proof of Provision}\label{step-7-proof-of-provision}
 
@@
 
-Having the $\mathrm{cid}$, the customer downloads and decrypts the $\mathrm{result}$ using a shared key derived from the customer's secret key $\mathrm{sk(C)}$ and the SP's public key $\mathrm{pk(S)}$ using DHKE method.
+Having the $\mathrm{cid}$, the customer downloads and decrypts the $\mathrm{result}$ using a shared key derived from the customer's secret key $\mathrm{sk(C)}$ and the SP's public key $\mathrm{pk(S)}$ using the DHKE method.
 The protocol ends.
@@
 \section{Fairness analysis}\label{sec:fairness-analysis}
-We analyze the fairness of the protocol by representing it as an interactive non-cooperative game.
+We analyse the fairness of the protocol by representing it as an interactive non-cooperative game.
 
@@
 \begin{itemize}
-\item Neutral position (•): when a party has not spent nor gained anything of significant value (money, time, effort). For example, at the beginning of the protocol.
-\item Disadvantaged position (-): when a party has put a significant value without receiving an equivalent. For example, the customer has paid for a service in advance.
-\item Advantaged position (+): when a party would benefit if the transaction would halt at that step. For example, the SP has received payment before service provision.
+\item Neutral position (•): when a party has neither spent nor gained anything of significant value (money, time, effort). For example, at the beginning of the protocol.
+\item Disadvantaged position (-): when a party has put a significant value without receiving an equivalent. For example, the customer has paid in advance for a service.
+\item Advantaged position (+): when a party would benefit if the transaction was stopped at this step. For example, the SP has received payment before the service has been provided.
 \end{itemize}
@@
 \item Normal: taking actions prescribed by the protocol.
-\item Abnormal: everything that deviates from the designed steps of the protocol. For example, sending an arbitrary message, skipping or repeating steps, and timing out.
+\item Abnormal: anything that deviates from the intended steps of the protocol. For example, sending an arbitrary message, skipping or repeating steps, or timing out.
 \end{enumerate}
 
-Moreover, at any step of the protocol, the customer can start a dispute; therefore, another dimension with two positions has to be considered:
+In addition, at each step of the protocol, the customer can start a dispute, so another dimension with two positions must be taken into account:
 
@@
 
-As a result, in our analysis, we have to consider four different outcomes for each party of the protocol ($\mathrm{party \in \{c, s}\}$), for each step of the protocol ($\mathrm{step \in 1..9}$):
+As a result, in our analysis we need to consider four different outcomes for each party of the protocol ($\mathrm{party \in \{C, SP}\}$), for each step of the protocol ($\mathrm{step \in 1..9}$):
 
@@
 
-The protocol terminates after the last step, after starting a dispute, or after a party has not completed its designated action in time.
-Therefore, all positions but $\mathrm{\sigma_n}$ are termination positions.
-
-Because the customer is anonymous, the SP can not start a dispute—there is no means to identify the customer.
-To mitigate the issue, we designed the protocol so that the SP who follows the protocol is always in an advantaged position, and therefore has no reason to start a dispute.
-On the other hand, the customer can start a dispute at any time of the protocol, but only the actual misbehavior of the SP makes him win the conflict.
+The protocol terminates after the last step, after starting a dispute, or after a party fails to complete its designated action in time.
+Therefore, all positions except $\mathrm{\sigma_n}$ are termination positions.
+
+Because the customer is anonymous, the SP cannot start a dispute - there is no way to identify the customer.
+To mitigate this problem, we designed the protocol so that the SP who follows the protocol is always in an advantageous position and therefore has no reason to start a dispute.
+On the other hand, the customer can start a dispute at any time during the protocol, but only the actual misbehaviour of the SP will make him win the conflict.
 
 \begin{definition}[Fairness] \label{def:fairness}
-A protocol achieve fairness iff 
+A protocol achieves fairness iff 
 \begin{equation*}
@@
 \forall_{party \in parties}\forall_{\mathrm{step} \in \mathrm{steps}} &\operatorname{can\ move}\\
-&\operatorname{to\ the\ non-disadvantaged\ position} 
+&\operatorname{to the\ non-disadvantaged\ position} 
 \end{split}
@@
 \begin{enumerate}
-\item Both parties start from a neutral position $\neutral$.
-\item After completing a transaction, both parties end up in advantaged positions (\plus{}). In other words, they have an intrinsic motivation to initialize and complete the transaction.
-\item The protocol steps are atomic—there are no intermediate steps.
-\item The protocol can go only forward—there is no way of reverting any action.
+\item Both parties start from a neutral position ($\neutral$).
+\item After completing a transaction, both parties end up in an advantageous position (\plus{}). In other words, they have an intrinsic motivation to initialise and complete the transaction.
+\item The protocol steps are atomic - there are no intermediate steps.
+\item The protocol can only go forward - there is no way to undo any action.
 \item Repeating the first step starts a new transaction.
-Repeating any other step is considered abnormal and gets ignored.
-For example, paying for the invoice twice does not cause any effect on the curse of the protocol.
-\item Once published, the result is available to the customer on the storage network. The idea of guaranteeing it cryptographically is discussed in Section~\ref{sec:discussion}.
-\item Winning the dispute leads to a neutral position ($\neutral$).
-\item Losing the dispute leads to a punishment greater than any reward, leading to a disadvantaged position (\minus{}).
-Hence, the rational customer will not start a dispute that he is unsure of winning.
-\item Both the customer and the SP are rational (selfish).
-They always prefer to go from the worst position (\minus{} or $\neutral${}) to a better position ($\neutral$ or \plus), but also risk a temporary worst position in favor of a later better position if and only if at any time they can get out of the worst position; in particular, at any time the customer can start a dispute and, if the SP has misbehaved, get out of disadvantaged position (\minus) to the neutral position ($\neutral$).
-\item We assume that the Customer's materials without personal information are useless, and the effort to deliver the package is negligible, so that the Customer's first step does not lead to disadvantaged position.
-\item We assume the processing cost of publishing $\mathrm{PoD}$ is negligible and balance out the effort of delivering the package by the Customer.
+Repeating any other step is considered abnormal and is ignored.
+For example, paying the invoice twice has no effect on the curse of the protocol.
+\item Once published, the result is available to the customer on the storage network. 
+\item Winning the dispute results in a neutral position ($\neutral$).
+\item Losing the dispute results in a penalty greater than any reward, leading to a disadvantaged position (\minus{}).
+Therefore, the rational customer will not start a dispute that he is not sure he can win.
+\item Both the customer and the SP are rational.
+They always prefer to go from the worst position (\minus{} or $\neutral${}) to a better position ($\neutral$ or \plus), but they are willing to risk a temporary worst position in favour of a later better position if and only if they can always get out of the worst position; in particular, the customer can always start a dispute and, if the SP has misbehaved, get out of the disadvantaged position (\minus) to the neutral position ($\neutral$).
+\item We assume that the customer's materials without personal information are useless and the effort to deliver the package is negligible, so the customer's first step does not lead to a disadvantaged position.
+\item We assume that the processing cost of publishing $\mathrm{PoD}$ is negligible and compensates for the customer's effort in delivering the package.
 \end{enumerate}
@@
 \centering
-\caption{Positions after each step of protocol}
+\caption{Positions after each step of the protocol}
 \label{fig:positions}
@@
 
-The detailed description of each step and the justification
-of the outcome positions is given in Appendix~\ref{app:proof-of-fairness}.
+The detailed description of each step and the rationale for the outcome of the result positions is given in Appendix~\ref{app:proof-of-fairness}.
 
 \subsection{Example scenarios}\label{example-scenarios}
-
-The Figure~\ref{fig:misbehaviour} shows the transitions of positions when the SP tries to misbehave and does not execute service, and so does not publish $\mathrm{PoP}$ after receiving the payment.
-After the deadline $\mathrm{T}_\mathrm{provide}$ the SP can not publish valid $\mathrm{PoP}$ and so the Customer starts a dispute.
-The Customer wins the dispute as the SP is unable to proof the $\mathrm{PoP}$ was published before $\mathrm{T}_\mathrm{provide}$.
-The protocol ends up neutral to the customer and disadvantaged to the SP positions.
+The Figure~\ref{fig:misbehaviour} shows the transitions of positions when the SP tries to misbehave and does not perform the service and therefore does not publish $\mathrm{PoP}$ after receiving the payment.
+After the deadline $\mathrm{T}_\mathrm{provide}$ the SP cannot publish valid $\mathrm{PoP}$ and so the customer starts a dispute.
+The customer wins the dispute because the SP cannot prove that the $\mathrm{PoP}$ was published before $\mathrm{T}_\mathrm{provide}$.
+The protocol ends up neutral for the customer and disadvantageous for the SP's positions.
 
@@
 \end{figure}
-the rational path for both parties is to follow the protocol as shown in the Figure~\ref{fig:rational}.
+
+The rational course for both parties is to follow the protocol shown in Figure~\ref{fig:rational}.
 
@@
 \centering
-\caption{Transitions of positions where both the customer and the SP are following the protocol}
+\caption{Transitions of positions where both the customer and the SP follow the protocol}
 \label{fig:rational}
@@
 
-Using the fairness definition~\ref{def:fairness} and the assumptions stated in Section~\ref{sec:assumptions}, our analysis indicates that the protocol achieves fairness.
+Using the definition of fairness~\ref{def:fairness} and the assumptions listed in Section~\ref{sec:assumptions}, our analysis shows that the protocol achieves fairness.
 
@@
 \begin{itemize}
-  \item{Anonymous payments} — we use the Monero blockchain \cite{noetherRingSignatureConfidential2015}.
-  \item{Storage netowork} — we use the Powergate~\cite{textilePowergate2023}, which is a wrapper around Filecoin and IPFS.
-  \item{Message board} — we use the Ethereum blockchain \cite{woodEthereumSecureDecentralised2014}; concretely, its local development version Truffle Ganache and Solidity language.
-  \item{Customer and SP} — we create client side web application (webapp) using \texttt{React.js} for creating UI, and \texttt{web3.js} library for interaction with Ethereum.
-We use \texttt{MetaMask} browser extension for signing and submitting transactions to Ethereum's node.
-We use \texttt{monerod} network client and \texttt{monero-wallet-cli} command-line interface for interacting with Monero blockchain.
-\end{itemize}
-
-The prototype is available at [blinded for review process]. The source code is available at [blinded for review process].
+  \item{Anonymous Payments} - we use the Monero blockchain \cite{noetherRingSignatureConfidential2015}.
+  \item{Storage Network} - we use the Powergate~\cite{textilePowergate2023}, which is a wrapper around Filecoin and IPFS.
+  \item{Message Board} - we use the Ethereum blockchain~\cite{woodEthereumSecureDecentralised2014}; specifically, its local development version Truffle Ganache and the Solidity language.
+\item{Customer and SP} - we create client-side web application (webapp) using \texttt{React.js} and \texttt{web3.js} library for interaction with Ethereum.
+We use \texttt{MetaMask} browser extension to sign and submit transactions to the Ethereum node.
+We use \texttt{monerod} network client and \texttt{monero-wallet-cli} command line interface to interact with the Monero blockchain.
+\end{itemize}
+
+The prototype is available at \url{https://anonser.stan.bar}. The source code is available at \url{https://github.com/stanbar/anonymous-provision-of-services-via-blockchain}.
 
@@
 Moreover, Powergate is configured to use local Filecoin and IPFS networks.
-For Ethereum blockchain, we use Truffle Ganache, which is a local Ethereum blockchain for development and testing purposes. 
+For the Ethereum blockchain, we use Truffle Ganache, which is a local Ethereum blockchain for development and testing purposes. 
 Monero is configured to use the public stage network.
-We assume the service provider offers only one type of service, which is offered for a fixed public price, hence we omit the type of service and price from the protocol.
+We assume that the service provider offers only one type of service at a fixed public price, so we omit the service type and price from the protocol.
 
@@
 
-Both the customer and the SP create Monero wallets using \texttt{monero-wallet-cli} command-line tool.
-
-The service provider deploys the smart contract using the \texttt{truffle migrate --network development} command, which deploys the smart contract to the Ethereum blockchain.
-The webapp is configured to use the latest deployed smart contract address.
-
-The customer gets some testing Monero funds using faucet service available at \url{https://community.rino.io/faucet/stagenet/}.
-
-Next, the customer enables per-transaction proof generation (payment \texttt{receipt}) by setting \texttt{set store-tx-info 1} for his wallet.
-Proof generation is required to verify the payment in case of a dispute.
-
-At this point, both the customer and the SP are ready to start the protocol.
+Both the customer and the SP create Monero wallets using the \texttt{monero-wallet-cli} command line tool.
+
+The SP deploys the smart contract using the \texttt{truffle migrate --network development} command, which deploys the smart contract to the Ethereum blockchain.
+The web application is configured to use the last deployed smart contract address.
+
+The customer receives some test Monero funds using the Faucet service available at \url{https://community.rino.io/faucet/stagenet/}.
+
+Next, the customer enables per-transaction proof generation (payment \texttt{receipt}) by setting \texttt{set store-tx-info 1} for their wallet.
+This is required to verify the payment in the event of a dispute.
+
+At this point both the customer and the SP are ready to start the protocol.
 
@@
 
-Figures \ref{fig:anonser-experiment1} and \ref{fig:anonser-experiment2} show the steps of the experiment. Their description is as follows:
+Figure~\ref{fig:anonser-experiment1} and Figure~\ref{fig:anonser-experiment2} show the steps of the experiment. Their description is as follows:
 
@@
   \item[0.] The protocol starts with the customer opening the webapp and creating a new provision.
-The app generates a random ECDSA (secp256k1) customer's keypair and random 32 bytes provisionID, then display QR code that encodes both the provisionID and the customer's public key. 
-The customer's private key must be downloaded and provided later for the decryption of the results.
-
-  \item[1.] The customer prints the QR code, sticks it on a package and delivers the package to the SP either: in person, via a trusted party, or a delivery agency.
-
-  \item[2.1.] The SP opens the app, and scans the QR code decoding the provisionID and the client's public key.
-
-  \item[2.2.] Since (in this experiment) the provision has not been paid in cash, the SP generates a unique Monero payment address using \texttt{monero-wallet-cli integrated\_address} 
-  \item[2.3.] The SP submits the proof of delivery to the Ethereum blockchain using MetaMask interface.
+The application generates a random ECDSA (secp256k1) customer keypair and a random 32-byte provisionID, and then displays a QR code that encodes both the provisionID and the customer's public key. 
+The customer's private key must be downloaded and provided later to decrypt the results.
+
+  \item[1.] The customer prints the QR code, sticks it on a parcel and delivers the parcel to the SP either via the SP's drop box, parcel locker services (e.g.
+Amazon Locker, InPost~\cite{inpostParcelLockerService}), a customer's trusted delivery agent or the post office.
+
+  \item[2.1.] The SP opens the app and scans the QR code, which decodes the provisionID and the customer's public key.
+
+  \item[2.2.] Since (in this experiment) the provision was not paid in cash, the SP generates a unique Monero payment address using \texttt{monero-wallet-cli integrated\_address}. 
+  \item[2.3.] The SP submits the Proof of Delivery to the Ethereum blockchain using the MetaMask interface.
 
@@
   % Matching integrated address: 5LHmrsVsQM2Q2TgqufX4A5gKPpxy1czHULDyVc84omvnh1nQLVmqXk4VBuy8WnX1AXfKxDx7xuASAc6svkZqGVkL1XkUBWT7QejHymEaYM
-  \item[3.] The customer (using the webapp) checks the transaction status on the Ethereum blockchain invoking \texttt{getProvision} with arguments \texttt{customerPubKey} and \texttt{provisionID}.
+  \item[3.] The customer (using the webapp) checks the transaction status on the Ethereum blockchain by calling \texttt{getProvision} with arguments \texttt{customerPubKey} and \texttt{provisionID}.
   % monero-wallet-cli --stagenet --wallet-file customer --password "" transfer 5LHmrsVsQM2Q2TgqufX4A5gKPpxy1czHULDyVc84omvnh1nQLVmqXk4VBuy8WnX1AXfKxDx7xuASAc6svkZqGVkL1XkUBWT7QejHymEaYM 1
@@
 
-  \item[4.] The customer (using the \texttt{monero-wallet-cli transfer}) sends the payment to the designated in the smart contract \texttt{paymentAddress} and stores the payment receipt (using \texttt{monero-wallet-cli get\_tex\_key <tx-id>}) in case of a dispute.
-
-  \item[5.] Once SP notices the payment on Monero blockchain it starts providing the service and outputs the file \texttt{result.pdf}.
-
-  \item[6.] The SP uploads the file \texttt{result.pdf} on the Filecoin and IPFS networks using Powergate.
-As a result, the SP gets the content identifier \texttt{cid}, and \texttt{dealID} and \texttt{minerID}.
-
-  \item[7.] The SP submits a Proof of Provision transaction to the Ethereum blockchain by invoking \texttt{proofOfProvision} with arguments \texttt{customer\-PubKey}, \texttt{provisionID}, \texttt{cid}, and \texttt{dealID}.
-
-  \item[8.] Meantime, the Customer subscribes to Ethereum and waits until the SP publishes the Proof Of Provision.
- Once the Proof Of Provision is published the Customer downloads the result using either: IPFS network via \url{https://dweb.link/<cid>} or Lotus network using \texttt{lotus retrieve <cid> <minerID>}.
-
-  \item[9.] Results are then decrypted using the previously stored customer's private key.
-If everything is correct, the Customer is satisfied with the service and the protocol ends, otherwise, the Customer can initiate a dispute.
+  \item[4.] The customer sends the payment (using \texttt{monero-wallet-cli transfer}) to the \texttt{paymentAddress} specified in the smart contract and stores the payment receipt (using \texttt{monero-wallet-cli get\_tex\_key <tx-id>}) in case of a dispute.
+  \item[5.] Once the SP notices the payment on the Monero blockchain, it starts providing the service and outputs the file \texttt{result.pdf}.
+
+  \item[6.] The SP uploads the file \texttt{result.pdf} to the IPFS and Filecoin networks using Powergate.
+As a result, the SP receives the content identifier \texttt{cid}, as well as \texttt{dealID} and \texttt{minerID}.
+
+  \item[7.] The SP submits a Proof of Provision transaction to the Ethereum blockchain by calling \texttt{proofOfProvision} with arguments \texttt{customer\-PubKey}, \texttt{provisionID}, \texttt{cid} and \texttt{dealID}.
+
+  \item[8.] Meanwhile, the customer subscribes to Ethereum and waits for the SP to publish the Proof of Provision.
+ Once the Proof Of Provision is published, the customer downloads the result using either the IPFS network using \url{https://dweb.link/<cid>} or Lotus network using \texttt{lotus retrieve <cid> <minerID>}.
+
+  \item[9.] The results are then decrypted using the customer's previously stored private key.
+If everything is correct, the customer is satisfied with the service and the protocol ends, otherwise the customer can initiate a dispute.
 
@@
 \includegraphics[height=0.95\textheight,keepaspectratio]{anonser-experiment1.pdf}}
-\captionof{figure}{Steps of the experiment, first part.}\label{fig:anonser-experiment1}
+\captionof{figure}{The steps of the experiment, the first part.}\label{fig:anonser-experiment1}
 \end{minipage}
@@
 \includegraphics[height=0.95\textheight,keepaspectratio]{anonser-experiment2.pdf}}
-\captionof{figure}{Steps of the experiment, second part.}\label{fig:anonser-experiment2}
+\captionof{figure}{The steps of the experiment, the second part.}\label{fig:anonser-experiment2}
 \end{minipage}
@@
   \includegraphics[height=0.95\textheight,keepaspectratio]{anonser-experiment1.pdf}
-  \caption{Steps of the experiment, first part.}\label{fig:anonser-experiment1}
+  \caption{The steps of the experiment, the first part.}\label{fig:anonser-experiment1}
 \end{figure*}
@@
   \includegraphics[height=0.95\textheight,keepaspectratio]{anonser-experiment2.pdf}
-  \caption{Steps of the experiment, second part.}\label{fig:anonser-experiment2}
+  \caption{The steps of the experiment, the second part.}\label{fig:anonser-experiment2}
 \end{figure*}
@@
 the protocol is fair.
-It is achieved by an undeniable hand-shake mechanism in which the SP first publishes $\mathrm{PoD}$ (step 2.) committing to package delivery and deadlines of the service, and then the customer accepts it by paying for the service or not (step 3.).
-
-Once the payment is made, the SP stays in the advantaged position. Since he has agreed on the deadlines of the provision of the service, he is incentivized
-to provide the service and publish the results and PoP before the deadline (step 7.); otherwise the customer—having all the evidence—can initiate a dispute and punish the SP, therefore rational parties will follow the protocol.
-
-Non-repudiation without TTP is achieved by using the blockchain and digital signatures.
-Blockchain guarantees that each change to the state of the smart contract is visible to everyone and only the SP is allowed to modify its state.
+It is achieved by an undeniable hand-shake mechanism in which the SP first publishes $\mathrm{PoD}$ (step 2.), committing to package delivery and service deadlines, and then the customer accepts it by paying for the service or not (step 3.).
+
+Once the payment is made, the SP remains in the advantageous position.
+Having agreed on the service delivery times, the SP is incentivised to to deliver the service and publish the results and the PoP before the deadline (step 7.); otherwise, the customer - having all the evidence - can initiate a dispute and punish the SP, so rational parties will follow the protocol.
+
+Non-repudiation without TTP is achieved through the use of blockchain and digital signatures.
+The blockchain guarantees that any change to the state of the smart contract is visible to everyone, and only the SP is allowed to change its state.
 
 \paragraph{Anonymity}
-We achieved anonymity by using anonymous payment methods such as cash or privacy-preserving payment blockchains (e.g., Monero), and decentralized storage networks like IPFS and Filecoin, allowing the customer to interact with the protocol without revealing his identity at any step of the protocol.
-
-\paragraph{Provable Results Availability}
-Content addressable networks such as IPFS can not guarantee the availability of the content\footnote{Nothing prevents the SP from publishing the result, receiving the $\mathrm{cid}$, publishing $\mathrm{PoP}$, and immediately after removing the result from the local storage.
-In case of dispute, the SP can upload the content again, proving its availability.
-The SP has no motivation to proceed with this kind of misbehavior other than putting the customer in a disadvantaged position caused by the lost dispute.}.
-However, the Filecoin~\cite{protocollabsFilecoinDecentralizedStorage2017}, which works as an incentivization layer on top of IPFS, increases the content availability via economic incentivisation (i.e., punishment in case of lack of proof of storage of the content~\cite{filecoinSlashing}).
-Compared to typical blockchain networks, Filecoin focuses on data storage and thus makes it cheaper than storing it on blockchains like Bitcoin or Ethereum.
-
-The SP uploads the result on both IPFS and Filecoin networks (via Powergate) making the result free in case of normal behaviour, and highly-available in case of the SP stops serving the result from his node.
+We achieve anonymity by decoupling personal information from materials, payment and communication.
+We used anonymous payment methods such as cash or privacy-preserving payment blockchains (e.g.
+Monero) and decentralised storage networks such as IPFS and Filecoin, allowing the customer to interact with the protocol without revealing their identity at any stage of the protocol.
+
+\paragraph{Provable Results Availability}\label{sec:provable-results-availability}
+Content addressable networks such as IPFS cannot guarantee the availability of the content\footnote{Nothing prevents the SP from publishing the result, receiving the $\mathrm{cid}$, publishing $\mathrm{PoP}$, and immediately removing the result from local storage.
+In the event of a dispute, the SP can re-upload the content to prove its availability.
+The SP has no motivation to proceed with this kind of misbehaviour other than to put the customer in a disadvantageous position caused by the lost dispute.} However, Filecoin~\cite{protocollabsFilecoinDecentralizedStorage2017}, which acts as an incentivisation layer on top of IPFS, increases content availability through economic incentivisation (i.e.
+punishment in case of lack of proof of content storage~\cite{filecoinSlashing}).
+Compared to typical blockchain networks, Filecoin focuses on data storage, making it cheaper than storing it on blockchains like Bitcoin or Ethereum.
+
+The SP uploads the result to both the IPFS and Filecoin networks (via Powergate), making access to the results free in the case of normal behaviour, and highly available in the case that the SP stops serving the result from its node.
 
@@
 
-Although our experiment was conducted on testnet, the amount of gas is the same on mainnet.
+Although our experiment was conducted on the testnet, the amount of gas is the same on the mainnet.
 
@@
 
-\subsection{Justice}\label{sec:decentralised-justice}
-
-Centralized justice is the biggest obstacle in achieving a system that complies with Web3 postulates~\cite{ethereumWhatWeb3Why2023}.
-
-The possible directions for mitigation of such issues are to either (i) replace local justice with blockchain dispute resolution systems like those proposed in Themis~\cite{mengThemisDecentralizedEscrow2019}, Kleros~\cite{bergollaKlerosSociolegalCase2022,gudkovCrowdArbitrationBlockchain2020}, Aragon Court~\cite{aragonDecentralizedDisputeResolution}, LTO Network~\cite{ltonetworkNextGenBlockchainB2B}, and other Online Dispute Resolution platforms~\cite{allenGovernanceBlockchainDispute2019}; or (ii) make it infeasible to provide incorrect results.
+\subsection{Dispute Resolution Service}\label{sec:decentralised-justice}
+Centralised Dispute Resolution Service is the biggest obstacle to the realisation of a system that is compliant with the Web3 postulates~\cite{ethereumWhatWeb3Why2023}.
+
+Possible directions for mitigating such problems are either (i) replacing local justice with blockchain dispute resolution systems, such as those proposed in Themis~\cite{mengThemisDecentralizedEscrow2019}, Kleros~\cite{bergollaKlerosSociolegalCase2022, gudkovCrowdArbitrationBlockchain2020}, Aragon Court~\cite{aragonDecentralizedDisputeResolution}, LTO Network~\cite{ltonetworkNextGenBlockchainB2B}, and other Online Dispute Resolution platforms~\cite{allenGovernanceBlockchainDispute2019}; or (ii) make it infeasible to provide incorrect results.
 
 The first approach is more feasible in the near future.
-It would require creating a large set of experts in a field that, in case of dispute, would receive all the proofs ($\mathrm{PoD}$, $\mathrm{PoP}$, payment $\mathrm{receipt}$ as well as any other proofs significant to the case) that could be queried by the experts in zero-knowledge fashion, i.e., they could ask a limited number of questions to the proofs and getting yes/no answers.
-The case would be fully confidential as they would not be able to query personal information.
-The experts would be incentivized to participate in the pool by the system of fees.
-They would be incentivized to vote honestly by the stake they would have to lock and reward/punishment they would get by judging correctly/incorrectly, where the correctness is determined by the quorum of votes.
-
-The second approach is more futuristic.
-Suppose that the service we are undertaking is fully computable.
-Then, it would be possible by employing proofs of correctness of computations~\cite{ben-sassonSNARKsVerifyingProgram2013} to enforce that only correct computations (hence correct services) are accepted.
-It would require the complete service examination to be computable, which is hard to achieve in settings where physical materials (like blood) are examined.
-Concretely, the problem canes down to ``How to represent blood digitally?''.
-If we could represent urine, blood, saliva, or any other physical material in a binary format and let the customer take a sample, discrete it, and send it to the SP, then the whole chain of integrity could be ensured.
-Therefore, incorrect service provision would be infeasible, and hence, disputes would be avoided.
+It would require the creation of a large set of experts in a field who, in the case of a dispute, would receive all the proofs ($\mathrm{PoD}$, $\mathrm{PoP}$, payment $\mathrm{receipt}$ as well as any other proofs relevant to the case) that could be queried by the experts in a zero-knowledge fashion, i.e.
+they could ask a limited number of questions of the proofs and get yes/no answers.
+The case would be completely confidential as they would not be able to query any personal information.
+Experts would be incentivised to participate in the pool by the fee system.
+They would be incentivised to vote honestly by the stake they would have to lock and the reward/punishment they would receive for a correct/incorrect judgement, correctness being determined by the quorum of votes.
+
+The second is more futuristic.
+Let us assume that the service we are performing is fully computable.
+Then it would be possible to use proofs of correctness of computations~\cite{ben-sassonSNARKsVerifyingProgram2013} to enforce that only correct computations (and hence correct services) are accepted.
+This would require the entire service verification to be computable, which is difficult to achieve in settings where physical materials (such as blood) are examined.
+Specifically, the problem boils down to ``How to represent blood digitally?'' If we could represent urine, blood, saliva or any other physical material in a binary format and let the customer take a sample, discrete it and send it to the SP, then the whole chain of integrity could be ensured.
+This would make it impossible to provide the wrong service and therefore avoid disputes.
 
 \subsection{Self-sovereign identities}
-Our research in the field showed that some jurisdictions require SPs to associate the diagnosis with the customer's personal information.
-For example, in Poland, all laboratories performing medical diagnostic tests, and collecting the material (except tests for HIV) are obligated to the unambiguous identification and verification of the identity of the patient from whom the material was collected~\cite{ministerstwozdrowiaRegulationMinisterHealth2006}.
-
-This conflicts with the main goal of our protocol, which is to prevent any identification information from being collected.
-
-One promising solution would be to use Self-sovereign identities (SSI)~\cite{muhleSurveyEssentialComponents2018}, especially the verifiable claims.
-A trusted authority (e.g., a government) would issue a one-time claim for a customer that would be accepted by the SP as legitimate personal identification.
+Our research in this area has shown that some jurisdictions require SPs to link the diagnosis to the customer's personal data.
+For example, in Poland, all laboratories performing medical diagnostic tests and collecting the material (except for HIV tests) are required to uniquely identify and verify the identity of the patient from whom the material was collected~\cite{ministerstwozdrowiaRegulationMinisterHealth2006}.
+
+This conflicts with the main aim of our protocol, which is to prevent the collection of any identifying information.
+
+A promising solution would be to use self-sovereign identities (SSIs)~\cite{muhleSurveyEssentialComponents2018}, especially the verifiable claims.
+A trusted authority (e.g.
+a government) would issue a one-time claim for a customer, which would be accepted by the SP as a legitimate personal identification.
 The SP would associate the diagnosis result with the provided DID.
-The DID itself would not contain any personal information, therefore the SP would learn nothing about the customer's identity besides the random-looking identification.
-The DID could be deanonimised by collaboration with the government.
-
-However, since SSI is a relatively new technology and the government has not yet adopted it, we decided to postpone the discussion of this topic to future work.
+The DID itself would contain no personal information, so the SP would learn nothing about the customer's identity beyond the random-looking identification.
+The DID could be de-anonymised in cooperation with the government.
+
+However, as SSI is a relatively new technology and the government has not yet adopted it, we decided to leave the discussion of this topic for future work.
 
 \subsection{Formal Verification}\label{sec:formal-verification}
-Following the work of~\cite{birjoveanuFormalVerificationMultiparty2022}, the security analysis of our protocol could be improved by the usage of tools for the automatic formal verification, e.g., AVISPA~\cite{armandoAVISPAToolAutomated2005}.
-It would require specifying the protocol using High-Level Protocol Specification Language (HLPSL)~\cite{chevalierHighLevelProtocol2004}.
-The specification would be then translated to the AVISPA's intermediate language and verified using the AVISPA's theorem prover.
-The verification would be performed by the AVISPA's model checker, which would check the protocol against the security properties.
+Following the work of~\cite{birjoveanuFormalVerificationMultiparty2022}, the security analysis of our protocol could be improved by using automatic formal verification tools, such as AVISPA~\cite{armandoAVISPAToolAutomated2005}.
+It would require the specification of the protocol using the High-Level Protocol Specification Language (HLPSL)~\cite{chevalierHighLevelProtocol2004}.
+The specification would then be translated into the AVISPA intermediate language and verified using the AVISPA theorem prover.
+The verification would be performed by the AVISPA model checker, which would check the protocol against the security properties.
 
 \section{Conclusions}\label{sec:conclusion}
-In this work, we have focused on enabling service provision without the collection of personal data.
-Our aim was to enable services such as genetic tests, tests for paternity, venereal diseases, HIV, drugs, and steroids, or anonymous legal advice.
-
-We observed that the current state of the art is not sufficient to achieve the goal.
-Therefore, we have proposed a protocol for service provision that simultaneously achieves anonymity, fairness, dispute resolution, TTP-lessness, and supports physical materials.
-
-Payments are handled either in cash or anonymous cryptocurrencies.
+In this work, we have focused on enabling the provision of services without the collection of personal data.
+Our aim was to enable services such as genetic testing, testing for paternity, venereal diseases, HIV, drugs and steroids, or anonymous legal advice.
+
+We found that the current state of the art was not sufficient to achieve this goal.
+We have therefore proposed a service delivery protocol that simultaneously achieves anonymity, fairness, dispute resolution, TTP-lessness and supports physical materials.
+
+Payments are made in either cash or anonymous cryptocurrencies.
 The result of the service is published on a content-addressable p2p network.
-The dispute can be settled by disclosing the collected proofs to justice.
-
-Using the definition~\ref{def:fairness} we showed that the protocol achieves fairness by the proof of delivery, payment receipt, and proof of provision published on the message board.
-
-Finally, we pinpointed further improvements like decentralized dispute resolution, self-sovereign identifiers, and anonymous package delivery via courier.
+The dispute can be resolved by submitting the collected evidence to the dispute resolution service.
+
+Using the definition~\ref{def:fairness}, we showed that the protocol achieves fairness by publishing proof of delivery, proof of payment, and proof of provisioning on the message board.
+
+Finally, we identified other improvements such as decentralised dispute resolution, self-sovereign identifiers, and anonymous courier delivery.
+
+\section*{Data availability}
+No data was used for the research described in the article.
+
+The prototype is available at \url{https://anonser.stan.bar}.
+
+The source code is available at \url{https://github.com/stanbar/anonymous-provision-of-services-via-blockchain}.
 
@@
 \section{Proof of fairness}\label{app:proof-of-fairness}
-Below we describe each step and rationale of the outcome position.
-We use the notation introduced in Section~\ref{sec:fairness-model} to analyze each position in the protocol and fairness Definition~\ref{def:fairness} to show the fairness of the protocol.
+Below we describe each step and the reasoning behind the outcome position.
+We use the notation introduced in Section~\ref{sec:fairness-model} to analyse each position in the protocol and the fairness Definition~\ref{def:fairness} to show the fairness of the protocol.
 
@@
 \newcommand{\ActedAbnormallyThen}[1]{The #1 acted abnormally, then:}
-\newcommand{\CustomerPaidButDidntGetResult}{the customer ends up in a disadvantaged position as he paid in advance but didn't receive the result}
-\newcommand{\SpReceivedThePayment}{the SP ends up in the advantaged position as she received the payment}
-
-\newcommand{\CustomerLosesBeforePayment}{The customer loses the dispute because the SP is not obligated to do anything until the transaction is paid}
-\newcommand{\CustomerLosesBeforePoP}{The customer loses the dispute because the SP still can publish the PoP within the agreed timeframe}
+\newcommand{\CustomerPaidButDidntGetResult}{The customer ends up in a disadvantageous position, because he has paid in advance, but hasn't received the result}
+\newcommand{\SpReceivedThePayment}{The SP ends up in the advantageous position, having received the payment}
+
+\newcommand{\CustomerLosesBeforePayment}{The customer loses the dispute because the SP is not obliged to do anything until the transaction is paid}
+\newcommand{\CustomerLosesBeforePoP}{The customer loses the dispute because the SP is still able to publish the PoP within the agreed timeframe}
 
@@
 
-The protocol starts when the customer correctly executes the first step of the protocol, i.e., deliver the package to the SP.
-
-The case where the customer does not deliver the package is not considered as it is not a part of the protocol.
+The protocol starts when the customer correctly completes the first step of the protocol, i.e. delivers the package to the SP.
+
+The case where the customer does not deliver the package is not considered as it is not part of the protocol.
 
@@
     \begin{itemize}
-      \item \Pos{2}{c}{\normal}{\neutral}, the customer remains in the neutral position as the PoD allows him to pay for the transaction but does not obligate him to anything.
-      \item \Pos{2}{s}{\normal}{\neutral}, the SP remains in the neutral position as the package has not brought her any value and she did not spend any resources to provide the service yet.
+      \item \Pos{2}{c}{\normal}{\neutral}, the customer remains in the neutral position as the PoD allows him to pay for the transaction but does not oblige him to do anything.
+      \item \Pos{2}{s}{\normal}{\neutral}, the SP remains in the neutral position as the package has not brought her any value and she has not spent any resources to provide the service.
     \end{itemize}
@@
   \begin{itemize}
-    \item \Pos{2}{c}{\abnormal}{\neutral}, the customer remains in the neutral position as he is not obligated\footnote{By not obligated we understand the situation where a party does not risk any resources by not taking the action} to agree with the incorrect $\mathrm{PoD}$.
-    \item \Pos{2}{s}{\abnormal}{\neutral}, the SP remains in the neutral position as the package has not brought her any value and she did not spend any resources to provide the service yet.
+    \item \Pos{2}{c}{\abnormal}{\neutral}, the customer remains in the neutral position as he is not obliged\footnote{By not obliged we understand the situation where a party does not risk any resources by not taking the action} to agree with the incorrect $\mathrm{PoD}$.
+    \item \Pos{2}{s}{\abnormal}{\neutral}, the SP remains in the neutral position as the package has not brought her any value and she has not spent any resources to provide the service.
   \end{itemize}
@@
   \item \CanDoAnything{SP}.
-  \item The customer can either wait (in case of the SP following the protocol) or abandon the transaction (in case of the SP acting abnormally).
-In both cases the customer ends up in non-disadvantaged position \Pos{2}{c}{\normal}{\neutral} or \Pos{2}{c}{\abnormal}{\neutral}.
+  \item customer can either wait (if the SP is following the protocol) or abandon the transaction (if the SP is acting abnormally).
+In both cases the customer ends up in a non-disadvantaged position \Pos{2}{c}{\normal}{\neutral} or \Pos{2}{c}{\abnormal}{\neutral}.
 \end{itemize}
@@
   \begin{itemize}
-    \item \Pos{4}{c}{\normal}{\minus}, the customer paid in advance.
-    \item \Pos{4}{s}{\normal}{\plus}, the SP received the payment but has not spent his resources yet.
+    \item \Pos{4}{c}{\normal}{\minus}, the customer has paid in advance.
+    \item \Pos{4}{s}{\normal}{\plus}, the SP has received the payment but has not spent his resources yet.
   \end{itemize}
@@
   \begin{itemize}
-    \item \Pos{4}{c}{\abnormal}{\neutral}, the customer ends up in the neutral position as he did not spend his funds.
+    \item \Pos{4}{c}{\abnormal}{\neutral}, the customer ends up in the neutral position as he has not spent his funds.
     \item \Pos{4}{s}{\abnormal}{\neutral}, the SP ends up in the neutral position as she neither received the payment nor spent her resources.
@@
 
-\newcommand{\CustomerRiskTemporaryDisadvantagedPosition}[1]{The customer, following the 9th assumption described in Section~\ref{sec:assumptions}, risk the temporary disadvantaged position #1 in favor of a later better position \Pos{9}{s}{\normal}{\plus}; meanwhile being able to get out of the disadvantaged position if the SP misbehave in one of the following steps.}
+\newcommand{\CustomerRiskTemporaryDisadvantagedPosition}[1]{The customer, following the 9th assumption described in Section~\ref{sec:assumptions}, risks the temporary disadvantaged position #1 in favour of a later better position \Pos{9}{s}{\normal}{\plus}; in the meantime, he can get out of the disadvantaged position if the SP misbehaves in any of the following steps.}
 
@@
   \begin{itemize}
-    \item \Pos{5}{c}{\normal}{\minus}, \RemainsIn{\customer}{disadvantaged} as he did not receive the result.
-    \item \Pos{5}{s}{\normal}{\plus}, \RemainsIn{\sp}{advantaged} as she received the payment.
+    \item \Pos{5}{c}{\normal}{\minus}, \RemainsIn{\customer}{disadvantaged} as he hasn't received the result.
+    \item \Pos{5}{s}{\normal}{\plus}, \RemainsIn{\sp}{advantaged} as she has received the payment.
   \end{itemize}
@@
   \begin{itemize}
-    \item \Pos{5}{c}{\abdispute}{\neutral} The customer wins the dispute because the SP did not provide the service within the time agreed upon in the \PoD{}, and so the SP will not be able to upload the result and publish the \PoP{} on time.
+    \item \Pos{5}{c}{\abdispute}{\neutral} The customer wins the dispute because the SP has not provided the service within the time agreed in the \PoD{}, and therefore the SP is unable to upload the result and publish the \PoP{} on time.
     \item \Pos{5}{s}{\abdispute}{\minus}, \LoseForTheSameReason{SP}.
@@
   \begin{itemize}
-    \item \Pos{6}{c}{\normal}{\minus}, \RemainsIn{\customer}{disadvantaged} as he did not receive the result.
-    \item \Pos{6}{s}{\normal}{\plus}, \RemainsIn{SP}{advantaged} as she received the payment.
+    \item \Pos{6}{c}{\normal}{\minus}, \RemainsIn{\customer}{disadvantaged} as he has not received the result.
+    \item \Pos{6}{s}{\normal}{\plus}, \RemainsIn{SP}{advantaged} as she has received the payment.
       \end{itemize}
@@
   \begin{itemize}
-    \item \Pos{6}{c}{\abdispute}{\neutral}, the customer wins the dispute because the SP did not upload the service within the time agreed upon in the \PoD{}, and so the SP will not be able to publish the \PoP{} on time.
-    \item \Pos{6}{s}{\abdispute}{\minus}, \LoseForTheSameReason{SP}.
+    \item \Pos{6}{c}{\abdispute}{\neutral}, the customer wins the dispute because the SP has not uploaded the service within the time agreed in the \PoD{} and the SP will not be able to publish the \PoP{} on time.
+    \Pos{6}{s}{\abdispute}{\minus}, \LoseForTheSameReason{SP}.
   \end{itemize}
@@
       \item \Pos{7}{c}{\normal}{\minus}, the customer has not received the result. Therefore, he remains in a disadvantaged position. 
-      \item \Pos{7}{s}{\normal}{\plus}, the SP has published all evidence to prove her correct behavior, therefore she remains in an advantaged position for the rest of the protocol.
+      \item \Pos{7}{s}{\normal}{\plus}, the SP has published all the evidence to prove her correct behaviour, so she remains in an advantageous position for the rest of the protocol.
     \end{itemize}
@@
   \begin{itemize}
-    \item \Pos{8}{c}{\abnormal}{\minus}, the customer paid for the transaction but does not have the access to $cid$, and hence, can not get the result from the storage network.
+    \item \Pos{8}{c}{\abnormal}{\minus}, the customer has paid for the transaction but does not have access to the $cid$ and therefore cannot get the result from the storage network.
     \item \Pos{8}{s}{\abnormal}{\plus}, \SpReceivedThePayment{}.
@@
   \begin{itemize}
-    \item \Pos{9}{c}{\normal}{\plus}, the customer got the result, therefore he terminate the protocol in an advantaged position.
+    \item \Pos{9}{c}{\normal}{\plus}, The customer has received the result, therefore he finishes the protocol in an advantaged position.
     \item \Pos{9}{s}{\normal}{\plus}, \RemainsIn{\sp}{advantaged}.
@@
     \item \Pos{9}{c}{\abnormal}{\minus}, the customer ends up in a disadvantaged position, as he ends up with the incorrect result.
-    \item \Pos{9}{s}{\abnormal}{\plus}, the SP ends up in the advantaged position as he received the payment but did not spend his resources.
+    \item \Pos{9}{s}{\abnormal}{\plus}, the SP ends up in the advantageous position of having received the payment but not having spent his resources.
   \end{itemize}

### 2023-10-25 paper/main.tex
update related works according to reviewer

@@
 \section{Related Works}\label{sec:related-works}
-In this section, we review related works on fair exchange, anonymous, and physical delivery protocols. Then we outline the main differences between the protocols.
-
-\subsection{Fair exchange, physical delivery}
-The most common application of fair exchange protocols is e-commerce.
-A typical transaction involves a seller and a buyer exchanging money for a physical product.
-To protect themselves, the seller wants to receive the funds before sending the product, while the buyer wants to receive the product before paying.
-The fairness of the protocol should guarantee that either both parties obtain the goods, or they both obtain nothing.
-
-To the best of our knowledge, the first system allowing fair exchange of physical products was proposed by Zhang et al.
-in 2006~\cite{zhangPracticalFairExchangeEPayment2006}.
-The protocol uses the buyer's bank as the TTP and assumes no coalition between the parties to achieve anonymity.
-
-The authors of~\cite{mohammedalarajFairnessPhysicalProducts2012} proposed a protocol for fair exchange involving the delivery of physical materials.
-The protocol assumes the existence of an offline~\footnote{\textit{Offline} (also called \textit{optimistic}) TTP compared to \textit{online} TTP which assumes the TTP is only involved in the case of a dispute between parties~\cite{rayFairExchangeEcommerce2002}.} TTP only gets involved in the event of a dispute.
-The protocol works as follows
-\begin{enumerate}
-\item The buyer sends an encrypted payment to the seller along with proof of validity.
-\item The seller validates the proof, which convinces him that the decrypted payment is also valid.
-\item The seller forwards the physical product to the trusted Delivery Agent (DA).
-\item The buyer verifies that the product is the one ordered.
-\item The buyer creates a proof of delivery and sends it to the seller along with the decryption key.
-\end{enumerate}
-
-However, the protocol relies on strong assumptions, namely the existence of a TTP and a DA that do not misbehave or collude with either party.
-Fairness is also achieved by assuming resilient communication channels.
-
-\subsection{Fair exchange, anonymity, dispute resolution, and physical products delivery} 
-\label{anonymity-and-fair-exchange-in-e-commerce-protocol-for-physical-products-delivery}
-
-In the previous protocol, both parties of the transaction are known to each other.
-However, there are situations in which the buyer would prefer not to disclose his identity to the seller.
-The situation becomes more challenging when the transaction involves physical products.
-In the previous protocol, both parties to the transaction are known to each other.
-However, there are situations where the buyer would prefer not to reveal his identity to the seller.
-The situation becomes more difficult when the transaction involves physical products.
-
-The authors of~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} proposed a protocol for physical products that guarantees the anonymity of both buyer and seller.
-They achieve this by introducing an online TTP that validates coins and guarantees fairness.
-Later they proposed many extensions to the protocol, namely in~\cite{birjoveanuPreservingAnonymityFair2018} they proposed an anonymous e-commerce protocol that governs complex transactions, in~\cite{birjoveanuAnonymityComplexTransactions2019} they extend anonymity for both buyers and sellers (in our case SPs), and in~\cite{birjoveanuFairExchangeECommerce2020} they proposed a protocol that supports chained transactions (involving multiple active intermediaries).
-Finally, in~\cite{birjoveanuTwoPartyECommerceProtocols2022} they proposed an improved protocol called PPPDCP (Protocol with Physical Product Delivery Providing Customer's Privacy).
-
-Anonymity is ensured by using an anonymous communication channel over Tor~\cite{dingledineTorSecondGenerationOnion2004} and blind signatures~\cite{chaumSecurityIdentificationTransaction1985}.
-Fair exchange, physical delivery and dispute resolution are achieved using a Delivery Cabinet (DC) under the control of the seller (e.g.
-Amazon Locker) and an offline TTP that only intervenes in the event of a dispute.
-
-The protocol works as follows
-
-\begin{enumerate}
-    \item The buyer buys a digital coin from their bank. A blind signature is used to ensure privacy.
-    \item The buyer sends the seller the purchase details, the address of the DC, the signature of the customer's bank and some metadata to preserve the integrity of the transaction, communication is done over Tor.
-    \item The seller requests redemption of the digital coin.
-    \item The seller posts the product to the DC via the delivery service.
-    \item The Delivery Agent (DA) collects the product from the seller's locker and posts it to the DC.
-    \item The buyer collects the product from the DC using a password.
-    \item The buyer verifies that the product is the one ordered, if not, opens a dispute with TTP.
-\end{enumerate}
-
-Besides the assumptions of the existence of the TTP, the protocol also assumes:
-
-\begin{itemize}
-    \item The buyer's and seller's banks allow confidential transactions, and both share a commit buffer where the value is locked until the transaction is complete;
-    \item The banks maintain a global list of coin serial numbers to prevent problems with double spending;
-    \item there is an anonymous communication channel and the SC and DC are password protected;
-    \item The DC is equipped with a video camera that records the moment the buyer opens the package and provides a means to submit the video to TTP in the event of a dispute;
-\end{itemize}
-
-\subsection{Fair exchange and blockchain}
-The problem of TTPs in fair exchange protocols has been solved by the use of decentralised networks, in particular blockchain technology.
-
-The simplest example of a blockchain-based fair exchange protocol is the certified email protocol, where neither the sender can deny sending the email nor the recipient can deny receiving it.
-As this service is widely used in the paper world, achieving it for emails has not yet been agreed upon by the scientific community.
-The main problem has been the reliance on TTP, which significantly reduces the performance, security and robustness of such protocols.
-The protocols that do not use TTP suffer from high computational and communication overhead~\cite{hinarejosSolutionSecureCertified2019}.
-
-The authors of ~\cite{hinarejosSolutionSecureCertified2019} have replaced TTP with blockchain (specifically the bitcoin blockchain as a reference implementation), which acts as a secure, verifiable and decentralised TTP.
-
-The idea behind certified email and any other fair exchange protocol is as follows:
-\begin{enumerate}
-    \item The sender sends an encrypted and signed message to the recipient.
-    \item The recipient returns a proof of delivery (a signature) of the encrypted message to the sender.
-    \item The sender publishes the proof of delivery and the decryption key on a blockchain (or TTP in general).
-    \item The recipient decrypts the encrypted message using the published decryption key.
-\end{enumerate}
-
-The non-repudiation requirement is achieved by the receiver sending the proof of delivery before having access to the decrypted message, and the sender publishing the decryption key together with the proof of delivery on the blockchain (or TTP), so that the receiver cannot deny having received the message or having access to the decryption key—because it is publicly available.
-
-In this case, the role of the blockchain is to certify the existence of the decryption key at a given point in time.
-
-\subsection{Fair-exchange, blockchain, and decentralized dispute resolution}
-\label{themis-towards-decentralized-escrow-of-cryptocurrencies-without-trusted-third-parties}
-Themis~\cite{mengThemisDecentralizedEscrow2019} is a fair exchange protocol that uses blockchain instead of TTP.
-It provides an escrow service for the secure exchange of cryptocurrencies and digital goods.
-It also provides a decentralised dispute resolution system for resolving conflicts.
-
-The protocol works as follows:
-\begin{enumerate}
-    \item Alice and Bob create a 2-of-2 threshold escrow account using the Thresh-Key-Gen protocol and send funds to it.
-\item Alice and Bob split their secret keys into \(n=2t+1\) secret shares using Shamir Secret Sharing protocol, where \(n\) is the number of mediators participating in the decentralised network and \(t+1\) is the threshold for a sufficient number of mediators to reconstruct the secret key.
-    \item Alice and Bob encrypt each \textit{i}-th key share with the public key of \textit{i}-th mediator.
-\item Alice and Bob exchange the sets of encrypted key shares and send funds to the escrow account.
-\end{enumerate}
-
-The escrow is secure as long as \(t+1\) of the mediators do not collude, which would allow them to reconstruct both \(x_A\) and \(x_B\).
-
-To ensure that the parties exchange real key shares, they send witnesses generated using the Feldman VSS scheme and zero-knowledge proofs to guarantee consistency between witnesses and key shares.
-
-In the event of a dispute, the decentralised network of mediators resolves the conflict and grants the winning party the other party's secret key, allowing it to withdraw the funds.
-
-The financial incentives and the reputation system guarantee the honesty of the mediators.
-
-\subsection{Blockchain, anonymity, and physical delivery}\label{lelantos-a-blockchain-based-anonymous-physical-delivery-system}
-
-Lelantos~\cite{altawyLelantosBlockchainBasedAnonymous2017} is a blockchain-based anonymous physical delivery system.
-The protocol achieves anonymity by using onion routing (similar to the Tor network) to connect physical delivery providers.
-The entire path from a seller to a buyer is divided into multiple steps, and each step is performed by randomly selected delivery providers.
-As long as the couriers do not collude, the seller cannot learn the identity or destination address of the buyer.
-
-A smart contract is used to coordinate the whole process and mediate communication between the buyer and the delivery providers.
-
-However, because the system uses Ethereum, it achieves pseudonymity rather than anonymity (see section~\ref{sec:pseudo-anon}). Also, the protocol does not cover disputes between the parties.
-
-\subsection{Comparision}
+This section reviews key protocols in fair exchange, anonymity, and physical delivery, highlighting their primary features and differences.
+
+The most common application of fair exchange protocols
+is e-commerce. A typical transaction involves a seller and
+a buyer exchanging money for a physical product. To pro-
+tect themselves, the seller wants to receive the funds before
+sending the product, while the buyer wants to receive the
+product before paying. The fairness of the protocol should
+guarantee that either both parties obtain the goods, or they
+both obtain nothing.
+Early systems like the one by Zhang et al.
+(2006)\cite{zhangPracticalFairExchangeEPayment2006} and Mohammedalaraj (2012)\cite{mohammedalarajFairnessPhysicalProducts2012} introduced Trusted Third Parties (TTPs) and Delivery Agents (DAs) to ensure fairness, and relied on strong assumptions about non-collusion and resilient communication channels.
+
+Protocols like those proposed by Bîrjoveanu et al.
+(2015-2022)~\cite{birjoveanuAnonymityFairexchangeEcommerce2015, birjoveanuPreservingAnonymityFair2018, birjoveanuAnonymityComplexTransactions2019, birjoveanuFairExchangeECommerce2020, birjoveanuTwoPartyECommerceProtocols2022} focus on anonymity in transactions involving physical products.
+These protocols utilize TTPs, anonymous communication channels like Tor, and cryptographic techniques like blind signatures to ensure privacy and fairness.
+However, they depend on the existence of TTPs and secure, confidential transaction systems between banks.
+
+Blockchain technology offers solutions to the TTP dependency in fair exchange protocols.
+Hinarejos et al.
+(2019)\cite{hinarejosSolutionSecureCertified2019} demonstrated a blockchain-based protocol for certified email, replacing TTP with a decentralized, verifiable system.
+Themis (Meng et al., 2019)\cite{mengThemisDecentralizedEscrow2019} further advanced this by incorporating a decentralized dispute resolution mechanism, though it does not address anonymity.
+
+Lelantos (Altawy et al., 2017)~\cite{altawyLelantosBlockchainBasedAnonymous2017} is a notable example of a blockchain-based system providing anonymous physical delivery.
+It uses onion routing and smart contracts to ensure anonymity, although it only achieves pseudonymity and lacks a dispute resolution mechanism.
+
+\paragraph{Comparison and Our Approach}
 
@@
 
-Our protocol achieves anonymity by using either cash or privacy-preserving blockchains.
-In addition, our protocol does not require a customer to submit a transaction to the bulletin board, which may be the weakest link in achieving anonymity in other protocols.
-
-Furthermore, none of them directly address our use case.
-We want the SP to remain public so that the anonymous buyer can easily start a dispute.
-We assume a single package of physical materials.
-Also, the package is delivered from the buyer to the SP, not the other way around–as in most e-commerce transactions.
-
-Also, our protocol does not have its own dispute resolution mechanism, as Themis does.
-However, we assume the existence of an abstract Dispute Resolution Service that accepts evidence and punishes the misbehaving party.
-This can be instantiated either with the local court or police, or with one of the blockchain's dispute resolution services such as Themis~\cite{mengThemisDecentralizedEscrow2019}, Kleros~\cite{bergollaKlerosSociolegalCase2022,gudkovCrowdArbitrationBlockchain2020}, Aragon Court~\cite{aragonDecentralizedDisputeResolution}, LTO Network~\cite{ltonetworkNextGenBlockchainB2B,ltonetworkOnchainIdentitiesCredentials}, and other Online Dispute Resolution platforms~\cite{allenGovernanceBlockchainDispute2019}.
-
-The comparison of the protocols is presented in Table~\ref{tab:comparision}.
-
-The notation \textit{Pseudonymity} means that the anonymity is based on the assumption that the pseudonym is not linked to the real identity; \textit{TTP} means that the protocol uses a trusted third party; \textit{BC} means that the protocol uses a public blockchain; \textit{YES*} means that the protocol provides the feature but is based on strong or impractical assumptions.
+Our protocol differs from existing ones by focusing on anonymity and fair exchange without relying on TTPs or complex banking systems.
+It achieves anonymity by using either cash or privacy-preserving blockchains.
+In addition, our protocol does not require a customer to submit a transaction to the bulletin board simplifying the transaction process while maintaining anonymity and fairness.
+
+Unlike most protocols, our system is designed for transactions where the package is delivered from the buyer to the Service Provider (SP), and we assume a generic Dispute Resolution Service for handling conflicts .
+
+To provide a clearer understanding of how our protocol compares with existing work, Table~\ref{tab:comparision} presents a summary of key features and differences among the discussed protocols.
 
@@
 \newcommand{\BC}{\cellcolor{green!50}BC}
-\caption{Comparision of related works.}
+\caption{Comparison of related works.
+The notation \textit{Pseudonymity} means that the anonymity is based on the assumption that the pseudonym is not linked to the real identity; \textit{TTP} means that the protocol uses a trusted third party; \textit{BC} means that the protocol uses a public blockchain; \textit{YES*} means that the protocol provides the feature but is based on strong or impractical assumptions.}
 \label{tab:comparision}
@@
 
-The prototype is available at \url{https://anonser.stan.bar}. The source code is available at \url{https://github.com/stanbar/anonymous-provision-of-services-via-blockchain}.
+The prototype is available at \url{https://anonser.stan.bar}. The source code is available at \url{https://github.com/stanbar/anonser}.
 
@@
 
-Using the definition~\ref{def:fairness}, we showed that the protocol achieves fairness by publishing proof of delivery, proof of payment, and proof of provisioning on the message board.
+Using the Definition~\ref{def:fairness}, we showed that the protocol achieves fairness by publishing proof of delivery, proof of payment, and proof of provisioning on the message board.
 
@@
 
-\section*{Data availability}
+\paragraph{Data availability}
 No data was used for the research described in the article.
-
 The prototype is available at \url{https://anonser.stan.bar}. 
-
-The source code is available at \url{https://github.com/stanbar/anonymous-provision-of-services-via-blockchain}.
+The source code is available at \url{https://github.com/stanbar/anonser}.
+
+\section*{Declarations}
+
+\paragraph{Conflict of interest} The authors declare that they have no competing interests.
+The authors certify that they have no affiliations with or involvement in any organisation or entity with any financial interest or non-financial interest in the subject matter or materials discussed in this manuscript.
+
+\paragraph{Ethical approval} This article does not contain any studies with human participants or animals performed by any of the authors
 

### 2023-10-27 paper/main.tex
add pseudocodes and change sk and pk notation

@@
 \usepackage{amsmath,amssymb,amsfonts}
-\usepackage{algorithmic}
+\usepackage{algorithm}
+\usepackage{algpseudocode}
 \usepackage{graphicx}
@@
 \usepackage{etoolbox}
-
 \usepackage{url}
@@
     \begin{itemize}
-        \item The customer and the SP have their key pairs consisting of secret key $\mathrm{sk}(\mathrm{party})$ and public key $\mathrm{pk}(\mathrm{party})$, where $\mathrm{party} \in \{\mathrm{C}, \mathrm{SP}\}$ for the customer and the SP accordingly.
-        \item Both the customer and the SP can create and verify digital signatures created by the customer $\mathrm{sig}_{\mathrm{sk}(\mathrm{C})}$ and the SP $\mathrm{sig}_{\mathrm{sk}(\mathrm{SP})}$.
-        \item The SP's public key $\mathrm{pk}(\mathrm{SP})$ is publicly known.
+        \item The customer and the SP have their key pairs consisting of secret key $\mathrm{sk}_\mathrm{party}$ and public key $\mathrm{pk}_\mathrm{party}$, where $\mathrm{party} \in \{\mathrm{C}, \mathrm{SP}\}$ for the customer and the SP accordingly.
+        \item Both the customer and the SP can create and verify digital signatures created by the customer $\mathrm{sig}_{\mathrm{sk}_\mathrm{C}}$ and the SP $\mathrm{sig}_{\mathrm{sk}_\mathrm{SP}}$.
+        \item The SP's public key $\mathrm{pk}_\mathrm{SP}$ is publicly known.
     \end{itemize}
@@
 
-$$\mathrm{pkg} \equiv (\mathrm{materials}, \mathrm{provisionID}, \mathrm{pk(C)})$$
+$$\mathrm{pkg} \equiv (\mathrm{materials}, \mathrm{provisionID}, \mathrm{pk_C})$$
 
@@
 \item $\mathrm{provisionID}$ - a randomly generated provision identifier, used to anonymously track the provision through all steps of the protocol.
-\item $\mathrm{pk(C)}$ - the customer's public key used to encrypt the results published to the public storage network.
+\item $\mathrm{pk_C}$ - the customer's public key used to encrypt the results published to the public storage network.
 \end{itemize}
@@
 \begin{eqnarray}
-\mathrm{PoD} & \equiv & (\begin{array}[t]{l}\mathrm{T}_\mathrm{issue}, \mathrm{T}_\mathrm{pay}, \mathrm{T}_\mathrm{provide}, \\\\ \mathrm{address}, \mathrm{provisionID}, \mathrm{pk(C)}, \mathrm{sig}_\mathrm{SP} \; )\end{array}
+\mathrm{PoD} & \equiv & (\begin{array}[t]{l}\mathrm{pk_C}, \mathrm{provisionID},  \mathrm{sig}_\mathrm{SP}, \mathrm{paymentAddress}, \\\\ 
+\mathrm{T}_\mathrm{issue}, \mathrm{T}_\mathrm{pay}, \mathrm{T}_\mathrm{provide}\; )\end{array}
 \end{eqnarray}
@@
 \begin{itemize}
-
+\item $\mathrm{pk_C}$ - the public key of the client used to encrypt the result published on the public storage network.
+\item $\mathrm{provisionID}$ - the number that uniquely identifies the transaction previously generated by the customer.
+\item $\mathrm{sig}_\mathrm{SP}$ - the SP's signature to ensure non-repudiation.
+\item $\mathrm{paymentAddress}$ - payment address of the SP's anonymous blockchain account.
 \item $\mathrm{T}_\mathrm{issue}$ - time at which the $\mathrm{PoD}$ is issued by the SP.
@@
   $\mathrm{T}_\mathrm{provide}$ - deadline to provide the result of the service, i.e. to publish $\mathrm{PoP}$.
-\item $\mathrm{address}$ - payment address of the SP's anonymous blockchain account.
-\item $\mathrm{provisionID}$ - the number that uniquely identifies the transaction previously generated by the customer.
-\item $\mathrm{pk(C)}$ - the public key of the client used to encrypt the result published on the public storage network.
-\item $\mathrm{sig}_\mathrm{SP}$ - the SP's signature to ensure non-repudiation.
 \end{itemize}
@@
 
-The customer collects all $\mathrm{materials}$ required by the SP, generates a random $\mathrm{provisionID}$ and a random keypair $(\mathrm{sk(C)},\mathrm{pk(C)})$.
+The customer collects all $\mathrm{materials}$ required by the SP, generates a random $\mathrm{provisionID}$ and a random keypair $(\mathrm{sk_C},\mathrm{pk_C})$.
 The $\mathrm{provisionID}$ is used to connect all actions associated with the transaction throughout the protocol.
-The $\mathrm{provisionID}$ and $\mathrm{pk(C)}$ are encoded as a QR code, printed and attached to the $\mathrm{pkg}$ package.
-The $\mathrm{sk(C)}$ is kept secret and is used to decrypt the $\mathrm{result}$ at the end of the protocol.
+The $\mathrm{provisionID}$ and $\mathrm{pk_C}$ are encoded as a QR code, printed and attached to the $\mathrm{pkg}$ package.
+The $\mathrm{sk_C}$ is kept secret and is used to decrypt the $\mathrm{result}$ at the end of the protocol.
 
@@
 
-The digital signature $\mathrm{sig}_{\mathrm{sk}(\mathrm{SP})}$ on the $\mathrm{PoD}$, created with the SP's secret key $\mathrm{sk}(\mathrm{SP})$, guarantees non-repudiation.
+The digital signature $\mathrm{sig}_{\mathrm{sk}_\mathrm{SP}}$ on the $\mathrm{PoD}$, created with the SP's secret key $\mathrm{sk}_\mathrm{SP}$, guarantees non-repudiation.
 
@@
 
+The Algorithm~\ref{alg:proofOfDelivery} presents the process of processing the PoD and recording it on-chain.
+
+\begin{algorithm}
+\caption{Algorithm for Registering Proof of Delivery}
+\label{alg:proofOfDelivery}
+\begin{algorithmic}[1]
+\Function{proofOfDelivery}{$pk_C$, $provisionId$, $sig_{SP}$, $paidInCash$, $paymentAddress$, $paymentWindow$, $provisionWindow$}
+    \State Verify $sig_{SP}$
+    \If{provisions[$pk_C$][$provisionId$].exist}
+        \State \Return Error("Provision already exists")
+    \EndIf
+
+    \If{$paidInCash = \text{TRUE} \oplus paymentAddress$ is not empty}
+        \State \Return Error("Inconsistent payment method and address")
+    \EndIf
+
+    \State $\mathrm{T}_\mathrm{issue} \gets$ block.timestamp
+    \State $\mathrm{T}_\mathrm{pay} \gets \mathrm{T}_\mathrm{issue} + paymentWindow$
+    \State $\mathrm{T}_\mathrm{provide} \gets \mathrm{T}_\mathrm{issue} + provisionWindow$
+
+    \State $provision \gets \left\{ \mathrm{T}_\mathrm{issue}, paymentDeadlineTime, \right.$
+    \State \hspace{\algorithmicindent}$\left. \mathrm{T}_\mathrm{pay}, \mathrm{T}_\mathrm{provide}, paidInCash, paymentAddress \right\}$
+    \State provisions[$pk_C$][$provisionId$] $\gets provision$
+\EndFunction
+\end{algorithmic}
+\end{algorithm}
+
 \noindent \textbf
@@
 \[
-\mathrm{PoD \gets get(provisionID)}
+\mathrm{PoD \gets get(pk_C, provisionID)}
 \]
@@
 \[
-\mathrm{receipt \gets payment(address)}
+\mathrm{receipt \gets payment(paymentAddress)}
 \]
@@
 When the service is complete, a result should be generated. 
-Next, the result is encrypted using a shared key derived from the customer's public key $\mathrm{pk(C)}$ and the SP's secret key $\mathrm{sk(S)}$ using the Diffie-Hellman key exchange (DHKE) method~\cite{diffieNewDirectionsCryptography1976}.
+Next, the result is encrypted using a shared key derived from the customer's public key $\mathrm{pk_C}$ and the SP's secret key $\mathrm{sk(SP)}$ using the Diffie-Hellman key exchange (DHKE) method~\cite{diffieNewDirectionsCryptography1976}.
 The encrypted result is then uploaded to the content addressable network (such as IPFS). In return, the content identifier ($\mathrm{cid}$) is created.
@@
 \[
-\mathrm{cid \gets upload(E_{DHKE(sk(SP), pk(C))}(result))}
+\mathrm{cid \gets upload(E_{DHKE(sk_{SP}, pk_C)}(result))}
 \]
@@
 
+The Algorithm~\ref{alg:proofOfProvision} presents the process of processing the PoP and recording it on-chain.
+
+\begin{algorithm}
+\caption{Algorithm for Registering Proof of Provision}
+\label{alg:proofOfProvision}
+\begin{algorithmic}[1]
+\Function{proofOfProvision}{$pk_C$, $provisionId$, $cid$}
+    \State $provision \gets$ provisions[$pk_C$][$provisionId$]
+    \If{not $provision$.exist}
+        \State \Return Error("Provision must be created with proof of delivery first")
+    \EndIf
+
+    \State Update $provision$ with $\{cid\}$
+\EndFunction
+\end{algorithmic}
+\end{algorithm}
+
 \noindent \textbf
@@
 \[
-\mathrm{cid \gets get(provisionID)}
+\mathrm{cid \gets get(pk_C, provisionID)}
 \]
@@
 
-Having the $\mathrm{cid}$, the customer downloads and decrypts the $\mathrm{result}$ using a shared key derived from the customer's secret key $\mathrm{sk(C)}$ and the SP's public key $\mathrm{pk(S)}$ using the DHKE method.
+Having the $\mathrm{cid}$, the customer downloads and decrypts the $\mathrm{result}$ using a shared key derived from the customer's secret key $\mathrm{sk_C}$ and the SP's public key $\mathrm{pk_{SP}}$ using the DHKE method.
 The protocol ends.
@@
 \[
-\mathrm{result \gets D_{DHKE(sk(C), pk(SP))}(download(cid))}
+\mathrm{result \gets D_{DHKE(sk_C, pk_{SP})}(download(cid))}
 \]
@@
 \begin{itemize}
-\item Neutral position (•): when a party has neither spent nor gained anything of significant value (money, time, effort). For example, at the beginning of the protocol.
-\item Disadvantaged position (-): when a party has put a significant value without receiving an equivalent. For example, the customer has paid in advance for a service.
-\item Advantaged position (+): when a party would benefit if the transaction was stopped at this step. For example, the SP has received payment before the service has been provided.
+\item \textbf{Neutral position ($\neutral{}$)}: when a party has neither spent nor gained anything of significant value (money, time, effort). For example, at the beginning of the protocol.
+\item \textbf{Disadvantaged position ($\minus{}$)}: when a party has put a significant value without receiving an equivalent. For example, the customer has paid in advance for a service.
+\item \textbf{Advantaged position ($\plus{}$)}: when a party would benefit if the transaction was stopped at this step. For example, the SP has received payment before the service has been provided.
 \end{itemize}
@@
 
-\item Normal: taking actions prescribed by the protocol.
-\item Abnormal: anything that deviates from the intended steps of the protocol. For example, sending an arbitrary message, skipping or repeating steps, or timing out.
+\item \textbf{Normal}: taking actions prescribed by the protocol.
+\item \textbf{Abnormal}: anything that deviates from the intended steps of the protocol. For example, sending an arbitrary message, skipping or repeating steps, or timing out.
 \end{enumerate}
@@
 
-\item Agree: the customer agrees with the action and therefore does not start a dispute.
-\item Start a dispute: the customer disagrees with the action and therefore starts a dispute.
+\item \textbf{Agree}: the customer agrees with the action and therefore does not start a dispute.
+\item \textbf{Start a dispute}: the customer disagrees with the action and therefore starts a dispute.
 \end{enumerate}
@@
 \begin{enumerate}
-\item Both parties start from a neutral position ($\neutral$).
+\item Both parties start from a neutral position ($\neutral${}).
 \item After completing a transaction, both parties end up in an advantageous position (\plus{}). In other words, they have an intrinsic motivation to initialise and complete the transaction.
@@
 \item Once published, the result is available to the customer on the storage network. 
-\item Winning the dispute results in a neutral position ($\neutral$).
+\item Winning the dispute results in a neutral position ($\neutral${}).
 \item Losing the dispute results in a penalty greater than any reward, leading to a disadvantaged position (\minus{}).
@@
 \item Both the customer and the SP are rational.
-They always prefer to go from the worst position (\minus{} or $\neutral${}) to a better position ($\neutral$ or \plus), but they are willing to risk a temporary worst position in favour of a later better position if and only if they can always get out of the worst position; in particular, the customer can always start a dispute and, if the SP has misbehaved, get out of the disadvantaged position (\minus) to the neutral position ($\neutral$).
+They always prefer to go from the worst position (\minus{} or $\neutral${}) to a better position ($\neutral${} or \plus), but they are willing to risk a temporary worst position in favour of a later better position if and only if they can always get out of the worst position; in particular, the customer can always start a dispute and, if the SP has misbehaved, get out of the disadvantaged position (\minus) to the neutral position ($\neutral${}).
 \item We assume that the customer's materials without personal information are useless and the effort to deliver the package is negligible, so the customer's first step does not lead to a disadvantaged position.
@@
 \centering
-\caption{Positions after each step of the protocol}
+\caption{Visual representation of the fairness of the protocol.
+The figure shows the game-theoretic outcomes of each party after each possible actions taken.
+Symbol $\neutral${} represents neutral outcome, \minus{} represents disadvantaged outcome, and \plus{} represents advantaged outcome, where the order relation holds \minus{} < $\neutral${} < \plus{}.}
 \label{fig:positions}
@@
 
-The detailed description of each step and the rationale for the outcome of the result positions is given in Appendix~\ref{app:proof-of-fairness}.
+The detailed description of each step and the rationale for the outcome is given in Appendix~\ref{app:proof-of-fairness}.
 
@@
 \centering
-\caption{Transitions of positions where the SP is misbehaving and the customer starts a dispute}
+\caption{Transitions of positions where the SP is misbehaving and the customer starts a dispute.}
 \label{fig:misbehaviour}
@@
 \centering
-\caption{Transitions of positions where both the customer and the SP follow the protocol}
+\caption{Transitions of positions where both the customer and the SP follow the protocol.}
 \label{fig:rational}
@@
 
-Figure~\ref{fig:anonser-experiment1} and Figure~\ref{fig:anonser-experiment2} show the steps of the experiment. Their description is as follows:
+The experiment was conducted as follows:
 
@@
 
-\ifx\FORMAT\SINGLECOLUMN
-\noindent%
-\begin{minipage}{\linewidth}
-\makebox[\linewidth]{
-\includegraphics[height=0.95\textheight,keepaspectratio]{anonser-experiment1.pdf}}
-\captionof{figure}{The steps of the experiment, the first part.}\label{fig:anonser-experiment1}
-\end{minipage}
-
-\noindent%
-\begin{minipage}{\linewidth}
-\makebox[\linewidth]{
-\includegraphics[height=0.95\textheight,keepaspectratio]{anonser-experiment2.pdf}}
-\captionof{figure}{The steps of the experiment, the second part.}\label{fig:anonser-experiment2}
-\end{minipage}
-\else
-\begin{figure*}
-  \centering
-  \includegraphics[height=0.95\textheight,keepaspectratio]{anonser-experiment1.pdf}
-  \caption{The steps of the experiment, the first part.}\label{fig:anonser-experiment1}
-\end{figure*}
-
-\begin{figure*}
-  \includegraphics[height=0.95\textheight,keepaspectratio]{anonser-experiment2.pdf}
-  \caption{The steps of the experiment, the second part.}\label{fig:anonser-experiment2}
-\end{figure*}
-
-\fi
 \subsection{Results}

### 2023-10-27 paper/main.tex
improve introduction with additional background

@@
 
-Providing personal information exposes users to privacy risks, i.e. the potential loss of control over personal information \cite{smithInformationPrivacyResearch2011}.
-
-Such personal information can be used deliberately or by accident (e.g.
-theft) for insider disclosure, unauthorised access or commercial gain.
-For example, by reselling it to marketers, financial institutions, other businesses, government agencies or even cybercriminals.
-This, in turn, can lead to unintentional GDPR or CCPA breaches, profiled advertising, or even criminal activity such as identity theft or illegal tracking and surveillance~\cite{smithInformationPrivacyResearch2011}.
+Providing personal information exposes users to a myriad of privacy risks, ranging from the potential loss of control over personal information to more severe threats like identity theft, data breaches, and unsanctioned monitoring.
+Such sensitive information is highly valuable to a potential attacker as it can be exploited for insider leaks, unauthorized entry, or financial profit.
+For instance, this data might be sold to marketers, banks, other corporations, government bodies, or cybercriminals.
+Consequently, this could unintentionally violate regulations like GDPR or CCPA, result in targeted advertising, or lead to crimes such as identity theft or unlawful tracking and surveillance~\cite{smithInformationPrivacyResearch2011}.
 
@@
 
-The problem is compounded when personal information is linked to health records, legal documents or biological materials such as DNA, saliva or blood.
+The problem is amplified when personal information is linked to health records, legal documents or biological materials such as DNA, saliva or blood.
 In such situations, clients may be reluctant to provide their personal information to the SP and therefore withdraw from the service.
-Both parties are harmed as the client does not receive a diagnosis relevant to their health and the SP loses potential clients.
-
-The guarantee of privacy of personal data is often based solely on trust in the SP's staff and the security of their IT systems.
-However, we observe that personal data is often used only for logistical purposes, such as payment or communication, and could be provided anonymously if such methods were available.
+\textbf{Both parties are harmed as the client does not receive a diagnosis relevant to their health and the SP loses potential clients.}
+
+In the majority of healthcare system, the critical data managed typically resides in the Electronic Medical Records (EMRs), which is consistently regarded as confidential information requiring robust security measures~\cite{jinReviewSecurePrivacypreserving2019}~\cite{keshtaSecurityPrivacyElectronic2021}.
+
+Mantaining the privacy of health data seems to be open and active area of reserach in the field of Privacy-Preserving Data Mining (PPDM) ~\cite{nareshPrivacyPreservingData2023,linPPSFOpensourcePrivacypreserving2018,hewagePrivacypreservingDataStream2023}.
+The recent reserach in this area focuses on employing methods of anonymisation and hiding sensitive information of the EMRs~\cite{hamdiEnhancingSecurityPrivacy2023, sharmaPrivacyPreservingData2019, wuHidingSensitiveInformation2021}, or securing the interaction between patient and Healthcare system~\cite{zhangPrivacyProtectionTelecare2016, mehmoodAnonymousAuthenticationScheme2018, khasimImprovedFastSecure2022}.
+
+However, in our study, we focus on the possibility of carrying out services without revealing any personal information — solving the problem of privacy at a much earlier stage.
 

### 2023-10-31 paper/main.tex
add background references

@@
 In such situations, clients may be reluctant to provide their personal information to the SP and therefore withdraw from the service.
-\textbf{Both parties are harmed as the client does not receive a diagnosis relevant to their health and the SP loses potential clients.}
+\textbf{Both parties are harmed as the client does not receive a diagnosis relevant to their health and the SP loses potential clients.}~\cite{klitzmanExclusionGeneticInformation2010,blackPresymptomaticTestingConfidentiality2021}
 
@@
 
-Mantaining the privacy of health data seems to be open and active area of reserach in the field of Privacy-Preserving Data Mining (PPDM) ~\cite{nareshPrivacyPreservingData2023,linPPSFOpensourcePrivacypreserving2018,hewagePrivacypreservingDataStream2023}.
-The recent reserach in this area focuses on employing methods of anonymisation and hiding sensitive information of the EMRs~\cite{hamdiEnhancingSecurityPrivacy2023, sharmaPrivacyPreservingData2019, wuHidingSensitiveInformation2021}, or securing the interaction between patient and Healthcare system~\cite{zhangPrivacyProtectionTelecare2016, mehmoodAnonymousAuthenticationScheme2018, khasimImprovedFastSecure2022}.
-
-However, in our study, we focus on the possibility of carrying out services without revealing any personal information — solving the problem of privacy at a much earlier stage.
+Maintaining the privacy of health data seems to be open and active area of research in the field of Privacy-Preserving Data Mining (PPDM) ~\cite{nareshPrivacyPreservingData2023,linPPSFOpensourcePrivacypreserving2018,hewagePrivacypreservingDataStream2023}.
+The recent research in this area focuses on employing methods of anonymisation and hiding sensitive information of the EMRs~\cite{hamdiEnhancingSecurityPrivacy2023, sharmaPrivacyPreservingData2019, wuHidingSensitiveInformation2021}, or securing the interaction between patient and Healthcare system~\cite{zhangPrivacyProtectionTelecare2016, mehmoodAnonymousAuthenticationScheme2018, khasimImprovedFastSecure2022}.
+
+Authors of~\cite{blackPresymptomaticTestingConfidentiality2021} highlight that after their organisation adopted Electronic Medical Record (EMR) systems, they could no longer promise the same confidentiality assurances.
+
+Klitzman~\cite{klitzmanExclusionGeneticInformation2010} investigated exclusion of genetic information from the EMR, as patients often do not trust the institutions and withhold genetic tests from physicians, assuming the information will be entered into their EMR.
+He acknowledged that this may impede continuity of care.
+
+Klitzman~\cite{klitzmanExclusionGeneticInformation2010} examined exclusion of genetic data from EMR, noting that patients frequently distrust healthcare facilities and choose not to share their genetic test results with doctors, fearing that this information might be recorded in their EMR.
+
+In our study, we focus on the possibility of carrying out services without revealing any personal information — solving the problem of privacy at a much earlier stage, before any personal information gets into EMR system.
 
@@
 \begin{itemize}
-    \item Patients who are willing to take a test, e.g.
+    \item \textbf{Confidentiality in Medical Testing}: Patients who are willing to take a test, e.g.
 for drugs, STDs, paternity or steroids, have a strong incentive to keep the whole process private.
@@
 
-\item Individuals engaged in entrepreneurial activities may want to assess the risks and possible consequences of their actions.
-
+\item \textbf{Anonymity in Legal Consultations for Entrepreneurs}: Individuals engaged in entrepreneurial activities may want to assess the risks and possible consequences of their actions.
 By revealing their identity, they trust that the lawyer will not use this information for harmful actions.
-\end{itemize}
-
-Using Solove's Taxonomy of Privacy~\cite{soloveTaxonomyPrivacy2006}, our protocol aims to prevent the following privacy risks:
-\begin{itemize}
-    \item \textbf{Breach of confidentiality}, breaking a promise to keep an individual's information confidential;
-    \item \textbf{Disclosure}, revealing true information about a person that affects the way others judge their character;
-    \item \textbf{Identification}, linking information to a specific individual;
-    \item \textbf{Secondary use}, using personal information for a purpose other than that for which they were collected.
-\end{itemize}
-
-We consider the following adversaries:
-\begin{itemize}
-    \item \textbf{Malicious insiders}: Individuals or entities with authorised access to the protocol's systems or data who may abuse their privileges to compromise customer privacy.
-This could include employees, contractors or service providers;
-    \item \textbf{Government agencies}: Depending on the jurisdiction and the nature of the protocol, government agencies may have legal powers or national security interests that could affect customer privacy.
-For example, the potential for surveillance, data requests or legal intervention;
-    \item \textbf{Malicious third-party services}: If the protocol relies on third party services or APIs, the privacy of customer data could be at risk if these services have inadequate security measures in place or if they engage in data sharing or tracking without the consent of the customer;
-    \item \textbf{Hackers and cybercriminals}: Individuals or organised groups with malicious intent who may exploit vulnerabilities in the protocol's implementation, infrastructure, or supporting systems to gain unauthorised access to customer information.
-\end{itemize}
+\item \textbf{Whistleblowing Platforms}: Employees or citizens witnessing unethical or illegal activities within organizations can report these anonymously without fear of reprisal, job loss, or social stigma, thereby promoting a more transparent and accountable society.
+\item \textbf{Sexual Health and Reproductive Services}: People seeking advice or services related to sexual health, contraception, or abortion might prefer anonymity due to the sensitive nature of these topics and potential societal judgment.
+\item \textbf{Substance Abuse Rehabilitation Services}: Individuals seeking help for substance abuse might avoid treatment due to the stigma or potential legal implications.
+Anonymity can facilitate access to necessary health services without fear of personal or professional consequences.
+\end{itemize}
+
+Using Solove's Taxonomy of Privacy~\cite{soloveTaxonomyPrivacy2006}, our protocol aims to prevent the following privacy risks: Breach of confidentiality, Disclosure, Identification, and Secondary use.
+We consider the following adversaries: Malicious insiders, Government agencies, Malicious third-party services, Hackers and cybercriminals.
 
 In this work we explore the possibilities of anonymous service provision and propose a protocol that preserves customer privacy even in the event of a successful attack.
-Under realistic operational assumptions, we believe that decoupling personal information from materials, payment and communication achieves a sufficient level of anonymity.
+Under realistic operational assumptions, we show that \textbf{decoupling personal information from materials, payment and communication achieves a sufficient level of anonymity}.
 

### 2023-10-31 paper/main.tex
unify customer and client terms

@@
 
-\newcommand{\customer}{customer}
 \renewcommand{\sp}{SP}
@@
 \label{sec:introduction}
-Diagnostic services such as paternity tests, doping tests or venereal disease tests are carried out in diagnostic centres that require clients to provide biological material such as blood, urine, stool or saliva.
-Unfortunately, clients are often forced to reveal their identity in order to complete transactions.
-Such a combination of personal information with biological materials exposes clients to significant privacy risks.
+Diagnostic services such as paternity tests, doping tests or venereal disease tests are carried out in diagnostic centres that require customers to provide biological material such as blood, urine, stool or saliva.
+Unfortunately, customers are often forced to reveal their identity in order to complete transactions.
+Such a combination of personal information with biological materials exposes customers to significant privacy risks.
 
@@
 The problem is amplified when personal information is linked to health records, legal documents or biological materials such as DNA, saliva or blood.
-In such situations, clients may be reluctant to provide their personal information to the SP and therefore withdraw from the service.
-\textbf{Both parties are harmed as the client does not receive a diagnosis relevant to their health and the SP loses potential clients.}~\cite{klitzmanExclusionGeneticInformation2010,blackPresymptomaticTestingConfidentiality2021}
+In such situations, customers may be reluctant to provide their personal information to the SP and therefore withdraw from the service.
+\textbf{Both parties are harmed as the customer does not receive a diagnosis relevant to their health and the SP loses potential customers.}~\cite{klitzmanExclusionGeneticInformation2010,blackPresymptomaticTestingConfidentiality2021}
 
@@
 
-    Currently, they have to take the risk that their personal data, materials and results will be stored securely and kept secret from any unauthorised actor (both curious employees and malicious attackers).
+    Currently, they have to take the risk that their personal data, materials and results will be stored securely and kept secret from any unauthorised actor (both curious employees and malicious attackers)~\cite{klitzmanExclusionGeneticInformation2010, blackPresymptomaticTestingConfidentiality2021}.
 
@@
 \item \textbf{Sexual Health and Reproductive Services}: People seeking advice or services related to sexual health, contraception, or abortion might prefer anonymity due to the sensitive nature of these topics and potential societal judgment.
-\item \textbf{Substance Abuse Rehabilitation Services}: Individuals seeking help for substance abuse might avoid treatment due to the stigma or potential legal implications.
-Anonymity can facilitate access to necessary health services without fear of personal or professional consequences.
 \end{itemize}
@@
 
-In this work we explore the possibilities of anonymous service provision and propose a protocol that preserves customer privacy even in the event of a successful attack.
+In this work we explore the possibilities of anonymous service provision and propose a protocol that preserves the customer's privacy even in the event of a successful attack.
 Under realistic operational assumptions, we show that \textbf{decoupling personal information from materials, payment and communication achieves a sufficient level of anonymity}.
 
-However, a protocol that hides a customer's identity is difficult to secure and coordinate.
-In particular, conflicts between customers and service providers are difficult to resolve when there is no one to accuse.
+However, a protocol that hides the customer's identity is difficult to secure and coordinate.
+In particular, conflicts between customers and service providers are difficult to resolve when there is subject to accuse.
 
@@
 The second step involves anonymous payment.
-The third step involves the delivery of the results to the customer.
+The third step involves the delivery of the result to the customer.
 Each step is proven on the message board, protecting the fair party in a conflict situation.}
@@
 It achieves anonymity by using either cash or privacy-preserving blockchains.
-In addition, our protocol does not require a customer to submit a transaction to the bulletin board simplifying the transaction process while maintaining anonymity and fairness.
+In addition, our protocol does not require the customer to submit a transaction to the bulletin board simplifying the transaction process while maintaining anonymity and fairness.
 
@@
 The problem arises when the seller wants to send the product to the buyer who wants to remain anonymous.
-Most of the existing protocols either assume the existence of a trusted delivery agent~\cite{mohammedalarajFairnessPhysicalProducts2012,birjoveanuAnonymityFairexchangeEcommerce2015}, or use a complex delivery mechanism similar to onion routing involving multiple many delivery services~\cite{altawyLelantosBlockchainBasedAnonymous2017}.
+Most of the existing protocols either assume the existence of a trusted delivery agent~\cite{mohammedalarajFairnessPhysicalProducts2012,birjoveanuAnonymityFairexchangeEcommerce2015}, or use a complex delivery mechanism similar to onion routing involving multiple delivery services~\cite{altawyLelantosBlockchainBasedAnonymous2017}.
 
@@
 We assume that there is a way to deliver a package anonymously without revealing the customer's personal information, either via the SP's drop box, parcel locker services (e.g.
-Amazon Locker, InPost~\cite{inpostParcelLockerService}), a customer's trusted Delivery Agent, or even the post office.
+Amazon Locker, InPost), the customer's trusted Delivery Agent, or even the post office.
 
@@
 To mitigate this problem, we have designed the protocol in such a way that the SP who follows the protocol is always in an advantageous position and therefore has no reason to start a dispute.
-On the other hand, the customer can start a dispute at any point in the protocol, but only the actual misbehaviour of the SP will allow him to win the case.
-
-Abstracting from the services provided by the SP, each party should be able to prove its honest behaviour in case of a dispute.
-We present three pieces of evidence that should be disclosed to the judiciary in the event of a dispute:
+On the other hand, the customer can start a dispute at any point in the protocol, but only the actual misbehaviour of the SP will lead to win the case.
+
+Abstracting from the services provided by the SP, each party should be able to prove its honest behaviour in the event of a dispute.
+We propose three pieces of evidence that should be disclosed to the judiciary in the event of a dispute:
 
 \begin{enumerate}
-    \item Proof of Delivery ($\mathrm{PoD}$) is a confirmation issued by the SP to the customer proving that the customer has delivered a complete (according to the SP's requirements) package to the SP and that the SP has accepted it.
-It consists of i) the current time, ii) the deadline to pay for the transaction, iii) the deadline to provide a result of the service, iv) the transaction identifier ($\textrm{provisionID}$) randomly generated by the customer, v) and the signature of the SP guaranteeing non-repudiation.
+    \item \textbf{Proof of Delivery ($\textrm{PoD}$)} is a confirmation issued by the SP to the customer proving that the customer has delivered a complete (according to the SP's requirements) package to the SP and that the SP has accepted it.
 The formal definition of $\mathrm{PoD}$ is given in Section~\ref{proof-of-delivery}.
 
-    \item Payment $\mathrm{receipt}$ is the confirmation that the customer has paid for the transaction at some point in time.
-The actual implementation depends on the cryptocurrency and is discussed further in Section~\ref{payment-for-services}.
-
-    \item Proof of Provision ($\mathrm{PoP}$) is the proof that the SP has published the result at a given time.
-It defends the SP in case the customer unjustifiably starts a dispute after the result has been published.
-It consists of i) a content identifier (as specified in Section ~\ref{storage-network}), ii) the $\textrm{provisionID}$ that uniquely identifies the transaction, and iii) the SP's signature that guarantees authentication.
-The link between $\mathrm{PoP}$ and the results is provided by the content identifier ($\mathrm{cid}$) that uniquely identifies the result (it is a kind of hash of the result), so that the result cannot be forged after the $\mathrm{PoP}$ is published.
+    \item \textbf{Payment $\textrm{receipt}$} is the confirmation that the customer has paid for the transaction at some point in time.
+The actual implementation depends on the cryptocurrency (or cash) and is discussed further in Section~\ref{payment-for-services}.
+
+    \item \textbf{Proof of Provision ($\textrm{PoP}$)} is the proof that the SP has published the result at a given time.
+It protects the SP in the event the customer unjustifiably starts a dispute after the result has been published.
+The formal definition of $\mathrm{PoP}$ is given in Section~\ref{proof-of-provision}.
 \end{enumerate}
@@
 \subsection{Message Board}\label{sec:message-board}
-The Proof of Provision ($\mathrm{PoP}$) that we have coined for the purposes of this protocol is commonly called Proof of Existence~\cite{crespoStamperyBlockchainTimestamping2017}.
-
-The idea behind Proof of Existence is to certify that a piece of information existed at a certain point in time, in such a way that nobody can undermine its existence, integrity or ownership (also called the non-repudiation property).
-
-We need this functionality for two reasons: (1) to communicate the existence of the results to the customer, to whom the SP has no other means of communication, since the customer remains anonymous; (2) to let the SP prove the publication of the result within the deadline agreed with the customer.
+The term Proof of Provision ($\mathrm{PoP}$) that we have coined for the purposes of this protocol is often referred to as Proof of Existence~\cite{crespoStamperyBlockchainTimestamping2017}.
+
+Its concept is to certify the existence, integrity and ownership of a particular information at a certain point in time (non-repudiation property).
+
+We use this feature for two purposes: (1) to inform the customer about the existence of the results, with whom the SP cannot communicate via any other means, since the customer remains anonymous; (2) to allow the SP to prove the publication of the results within the deadline agreed with the customer.
 
 By publishing the $\mathrm{PoP}$ on the blockchain, the SP cannot falsify the time at which the results were provided, as the block creation time proves it.
-The blockchain acts as a global clock that securely timestamps everything that goes into the block, so the $\mathrm{PoP}$ included in a block is associated with the time the block was created.
-Moreover, since the blockchain is public, anyone (including the judiciary) can be convinced that the SP did indeed publish the result at that time.
+The blockchain acts as a global clock that securely timestamps all data included in the block, so the $\mathrm{PoP}$ included in a block is associated with the time the block was created.
+Also, since the blockchain is public, anyone (including the judiciary) can be convinced that the service provider indeed released the result at that time.
 
@@
 \centering
-\caption{Suppose Alice is the client who wants to keep her identity anonymous and Bob is the public SP.
+\caption{Suppose Alice is the customer who wants to keep her identity anonymous and Bob is the public SP.
 Alice controls two addresses 1 and 2; the link between her real identity and the first address has been compromised and therefore identification is possible; the link to the second pseudonym is still unknown and therefore anonymous.
@@
 \begin{itemize}
-\item $\mathrm{pk_C}$ - the public key of the client used to encrypt the result published on the public storage network.
+\item $\mathrm{pk_C}$ - the public key of the customer used to encrypt the result published on the public storage network.
 \item $\mathrm{provisionID}$ - the number that uniquely identifies the transaction previously generated by the customer.
@@
   \item[1.] The customer prints the QR code, sticks it on a parcel and delivers the parcel to the SP either via the SP's drop box, parcel locker services (e.g.
-Amazon Locker, InPost~\cite{inpostParcelLockerService}), a customer's trusted delivery agent or the post office.
+Amazon Locker, InPost~\cite{inpostParcelLockerService}), the customer's trusted delivery agent or the post office.
 
@@
 A trusted authority (e.g.
-a government) would issue a one-time claim for a customer, which would be accepted by the SP as a legitimate personal identification.
+a government) would issue a one-time claim for the customer, which would be accepted by the SP as a legitimate personal identification.
 The SP would associate the diagnosis result with the provided DID.
@@
 \newcommand{\AgreeablePath}{Agreeable path:}
-\newcommand{\DisputePath}{The \customer{} starts a dispute:}
+\newcommand{\DisputePath}{The customer starts a dispute:}
 \newcommand{\Fairness}{Fairness:}
-\newcommand{\CustomerTurn}[0]{\expandafter\MakeUppercase \customer{} turn:}
+\newcommand{\CustomerTurn}[0]{\expandafter\MakeUppercase customer turn:}
 \newcommand{\SPTurn}[0]{\sp{} turn:}
@@
 
-\ActedAbnormallyThen{\customer}
+\ActedAbnormallyThen{Customer}
 
@@
   \begin{itemize}
-    \item \Pos{5}{c}{\normal}{\minus}, \RemainsIn{\customer}{disadvantaged} as he hasn't received the result.
+    \item \Pos{5}{c}{\normal}{\minus}, \RemainsIn{Customer}{disadvantaged} as he hasn't received the result.
     \item \Pos{5}{s}{\normal}{\plus}, \RemainsIn{\sp}{advantaged} as she has received the payment.
@@
   \begin{itemize}
-    \item \Pos{6}{c}{\normal}{\minus}, \RemainsIn{\customer}{disadvantaged} as he has not received the result.
+    \item \Pos{6}{c}{\normal}{\minus}, \RemainsIn{Customer}{disadvantaged} as he has not received the result.
     \item \Pos{6}{s}{\normal}{\plus}, \RemainsIn{SP}{advantaged} as she has received the payment.
@@
 
-\newcommand{\CustomerLosesBecauseSPCanProveBeingCorrect}{the \customer{} loses the dispute as the \sp{} has published all evidences to prove her correct behaviour}
+\newcommand{\CustomerLosesBecauseSPCanProveBeingCorrect}{the customer loses the dispute as the \sp{} has published all evidences to prove her correct behaviour}
 
@@
 \begin{itemize}
-  \item \CanFollowToOne{\customer}{\Pos{9}{c}{\normal}{\plus}}.
+  \item \CanFollowToOne{Customer}{\Pos{9}{c}{\normal}{\plus}}.
   \item \CanDoNothing{} \Pos{9}{s}{\normal}{\plus} or \Pos{9}{s}{\abnormal}{\plus}. 

### 2023-10-31 paper/main.tex
fix introduction and PoD pseudocode

@@
 Authors of~\cite{blackPresymptomaticTestingConfidentiality2021} highlight that after their organisation adopted Electronic Medical Record (EMR) systems, they could no longer promise the same confidentiality assurances.
-
-Klitzman~\cite{klitzmanExclusionGeneticInformation2010} investigated exclusion of genetic information from the EMR, as patients often do not trust the institutions and withhold genetic tests from physicians, assuming the information will be entered into their EMR.
-He acknowledged that this may impede continuity of care.
 
@@
     \If{$paidInCash = \text{TRUE} \oplus paymentAddress$ is not empty}
-        \State \Return Error("Inconsistent payment method and address")
+        \State \Return Error("Pay in cash or specify paymentAddress")
     \EndIf
@@
     \EndIf
-
     \State Update $provision$ with $\{cid\}$
+    \State provisions[$pk_C$][$provisionId$] $\gets$ $provision$
 \EndFunction

### 2023-11-06 paper/main.tex
improve the results

@@
 
-\paragraph{Fariness}
-As shown in Section~\ref{sec:steps} and~\ref{app:proof-of-fairness}, 
-the protocol is fair.
-It is achieved by an undeniable hand-shake mechanism in which the SP first publishes $\mathrm{PoD}$ (step 2.), committing to package delivery and service deadlines, and then the customer accepts it by paying for the service or not (step 3.).
-
-Once the payment is made, the SP remains in the advantageous position.
-Having agreed on the service delivery times, the SP is incentivised to to deliver the service and publish the results and the PoP before the deadline (step 7.); otherwise, the customer - having all the evidence - can initiate a dispute and punish the SP, so rational parties will follow the protocol.
-
-Non-repudiation without TTP is achieved through the use of blockchain and digital signatures.
-The blockchain guarantees that any change to the state of the smart contract is visible to everyone, and only the SP is allowed to change its state.
+\paragraph{Fairness}
+Fairness within the protocol was demonstrated, as detailed in Section~\ref{sec:steps} and ~\ref{app:proof-of-fairness}.
+This was achieved through an undeniable handshake mechanism, where the SP first commits to the package delivery and service deadlines by publishing the PoD (as outlined in step 2).
+The customer then acknowledges this commitment and accepts the terms by proceeding with the payment for the service (step 3).
+
+Once payment is confirmed, the SP is incentivized to fulfill the service obligations.
+The SP must deliver the service and publish both the results and the PoP before the agreed deadline (step 7).
+Failure to do so allows the customer, equipped with all necessary evidence, to initiate a dispute and potentially penalize the SP.
+This mechanism ensures that rational parties are motivated to adhere to the protocol.
+
+The protocol also ensures non-repudiation without the need for a TTP by employing blockchain technology and digital signatures.
+The blockchain provides a transparent and immutable record, ensuring that any changes to the smart contract's state are publicly visible and can only be made by the SP.
 
 \paragraph{Anonymity}
-We achieve anonymity by decoupling personal information from materials, payment and communication.
-We used anonymous payment methods such as cash or privacy-preserving payment blockchains (e.g.
-Monero) and decentralised storage networks such as IPFS and Filecoin, allowing the customer to interact with the protocol without revealing their identity at any stage of the protocol.
+Anonymity was achieved through the decoupling of personal information from transactional elements such as materials, payment, and communication.
+Anonymous payment methods were employed, including cash and privacy-focused cryptocurrencies like Monero, which obscure the details of transactions.
+Decentralized storage networks, namely IPFS and Filecoin, were also utilized to enhance privacy.
+These networks enabled the storage and retrieval of information without the need to disclose the customer's identity, ensuring that customers could engage with the protocol anonymously at every stage.
 
 \paragraph{Provable Results Availability}\label{sec:provable-results-availability}
-Content addressable networks such as IPFS cannot guarantee the availability of the content\footnote{Nothing prevents the SP from publishing the result, receiving the $\mathrm{cid}$, publishing $\mathrm{PoP}$, and immediately removing the result from local storage.
-In the event of a dispute, the SP can re-upload the content to prove its availability.
-The SP has no motivation to proceed with this kind of misbehaviour other than to put the customer in a disadvantageous position caused by the lost dispute.} However, Filecoin~\cite{protocollabsFilecoinDecentralizedStorage2017}, which acts as an incentivisation layer on top of IPFS, increases content availability through economic incentivisation (i.e.
-punishment in case of lack of proof of content storage~\cite{filecoinSlashing}).
-Compared to typical blockchain networks, Filecoin focuses on data storage, making it cheaper than storing it on blockchains like Bitcoin or Ethereum.
-
-The SP uploads the result to both the IPFS and Filecoin networks (via Powergate), making access to the results free in the case of normal behaviour, and highly available in the case that the SP stops serving the result from its node.
+The availability of the result is guaranteed by the usage of Filecoin~\cite{protocollabsFilecoinDecentralizedStorage2017}, which operates as an incentivization layer on top of IPFS.
+Filecoin enhances content availability by economically penalizing the lack of proof of content storage~\cite{filecoinSlashing}.
+
+In our protocol, the SP is responsible for uploading the result to both the IPFS and Filecoin networks (utilizing Powergate), which ensures free access to the results under normal operational circumstances.
+This dual-network approach also ensures high availability of the results, even if the SP ceases to host the content on their node.
 
 \paragraph{Costs}
-Deploying a smart contract and invoking functions on the Ethereum blockchain costs gas. The cost of gas is proportional to the amount of computation required to execute a transaction.
-
-Deploying a smart contract consumed 1456577 gas.
-Proof of delivery consumed 129649 gas.
-Proof of provision consumed 149130 gas.
-
-Although our experiment was conducted on the testnet, the amount of gas is the same on the mainnet.
-
-The cost of gas is denominated in $\mathrm{ETH}$.
-The price of gas at the time of the experiment (Jan.
-03, 2023, \url{https://etherscan.io/gastracker}) was $0.000000002227 \frac{\mathrm{ETH}}{\mathrm gas}$, and the price of 1 $\mathrm{ETH}$ was $1261.97 \mathrm{USD}$.
-
-In a result, the cost of:
-\begin{itemize}
-  \item Deploying the smart contract cost $0.000000002227 \frac{\mathrm{ETH}}{\mathrm gas} \cdot 1456577 \mathrm{gas} \cdot 1261.97 \frac{\mathrm{USD}}{\mathrm{ETH}} \approx 4.09 \mathrm{USD}$; 
-  \item Proof of delivery cost $0.000000002227 \mathrm{\frac{ETH}{gas}} \cdot 129649 \mathrm{gas} \cdot 1261.97 \frac{\mathrm{USD}}{\mathrm{ETH}} \approx 0.29 \mathrm{USD}$; 
-  \item Proof of provision cost $0.000000002227 \mathrm{\frac{ETH}{gas}} \cdot 149130 \mathrm{gas} \cdot 1261.97 \frac{\mathrm{USD}}{\mathrm{ETH}} \approx 0.33 \mathrm{USD}$.
-\end{itemize}
+The deployment and operation of smart contracts on the Ethereum blockchain incur gas fees, which are proportional to the computational resources required for transaction execution.
+The following outlines the gas consumption and associated costs for each operation within our protocol, based on the testnet metrics which are analogous to the mainnet:
+
+\begin{itemize}
+    \item \textbf{Smart Contract Deployment}: Consumed 1,456,577 gas units.
+    \item \textbf{Proof of Delivery}: Consumed 129,649 gas units.
+    \item \textbf{Proof of Provision}: Consumed 149,130 gas units.
+\end{itemize}
+
+The cost of gas is denominated in ETH, and the price per unit of gas at the time of the experiment (January 3, 2023) was 0.000000002227 ETH/gas, with the ETH price being \$1,261.97 USD\footnote{Etherscan Gas Tracker, \url{https://etherscan.io/gastracker}}.
+The customer is responsible only for covering the payment transaction fee.
+For transactions using Monero, the fee was approximately 0.000304 XMR at the time of the experiment, with the price of Monero being \$150 USD per XMR\footnote{Cryptocurrency statistics, \url{https://bitinfocharts.com}}.
+
+The incurred costs were as follows:
+
+\begin{itemize}
+    \item \textbf{Deploying the Smart Contract}: \( 0.000000002227 \frac{\text{ETH}}{\text{gas}} \times 1,456,577 \, \text{gas} \times 1,261.97 \frac{\text{USD}}{\text{ETH}} \approx 4.09 \, \text{USD} \).
+This is a one-time cost, paid by the SP.
+
+    \item \textbf{Proof of Delivery}: \( 0.000000002227 \frac{\text{ETH}}{\text{gas}} \times 129,649 \, \text{gas} \times 1,261.97 \frac{\text{USD}}{\text{ETH}} \approx 0.29 \, \text{USD} \).
+This fee is paid once per transaction, paid by the SP.
+
+    \item \textbf{Payment}: \( 0.000304 \, \text{XMR} \times 150 \frac{\text{USD}}{\text{XMR}} \approx 0.0456 \, \text{USD} \).  This fee is paid once per transaction, paid by the customer.
+
+    \item \textbf{Proof of Provision}: \( 0.000000002227 \frac{\text{ETH}}{\text{gas}} \times 149,130 \, \text{gas} \times 1,261.97 \frac{\text{USD}}{\text{ETH}} \approx 0.33 \, \text{USD} \).
+This fee is paid once per transaction, paid by the SP.
+\end{itemize}
+
+Additionally, our protocol's interaction with the Filecoin network introduces costs in FIL cryptocurrency for data storage and retrieval.
+These costs are determined through market-driven deals with miners.
+Deal prices, quoted in FIL, are influenced by various factors including data size, storage duration, and miner policies.
+The dynamic nature of these parameters means that costs can fluctuate, making precise predictions challenging.
+However, for our experiment, we leveraged Filecoin's reputation-based incentivisation layer to publish deals at no cost\footnote{Filecoin, Filecoin Plus Overview, \url{https://docs.filecoin.io/store/filecoin-plus/overview/}, (last visited Jan.
+04, 2023)}.
+
+\paragraph{Performance Evaluation Metrics}
+
+To provide a comprehensive performance evaluation of our protocol, we have analyzed the following metrics for each of the blockchain networks:
+
+\begin{itemize}
+    \item \textbf{Ethereum Network}:
+    \begin{itemize}
+        \item \textbf{Block Time}: Approximately 13-15 seconds.
+        \item \textbf{Transaction Throughput}: Ranges between 15-30 transactions per second (TPS).
+        \item \textbf{Transaction Latency}: Approximately 6 minutes.
+    \end{itemize}
+
+    \item \textbf{Monero Network}:
+    \begin{itemize}
+        \item \textbf{Block Time}: Approximately 2 minutes.
+        \item \textbf{Transaction Throughput}: Approximately 4 TPS.
+        \item \textbf{Transaction Latency}: Approximately under 20 minutes.
+    \end{itemize}
+
+    \item \textbf{Filecoin Network}:
+    \begin{itemize}
+        \item \textbf{Block Time}: Approximately 30 seconds.
+        \item \textbf{Transaction Throughput}: Not explicitly stated.
+The network is optimized for storage operations rather than transaction processing, with the throughput being primarily dependent on the storage and retrieval deal proposals.
+        \item \textbf{Transaction Latency}: Storage deal transactions take approximately 5-10 minutes for a 1 MiB file.
+    \end{itemize}
+\end{itemize}
+
+These metrics are crucial for understanding the scalability and efficiency of the blockchain networks in question and provide insight into their suitability for various applications within our protocol.
 

### 2023-11-08 paper/main.tex
improve fairness analysis

@@
 
-\section{Fairness analysis}\label{sec:fairness-analysis}
-We analyse the fairness of the protocol by representing it as an interactive non-cooperative game.
+\section{Fairness Analysis}\label{sec:fairness-analysis}
+Our protocol's fairness is assessed through its representation as an interactive non-cooperative game, examining the strategic interactions between the service provider (SP) and the customer.
 
 \subsection{Model}\label{sec:fairness-model}
-We consider three positions:
-
-\begin{itemize}
-\item \textbf{Neutral position ($\neutral{}$)}: when a party has neither spent nor gained anything of significant value (money, time, effort). For example, at the beginning of the protocol.
-\item \textbf{Disadvantaged position ($\minus{}$)}: when a party has put a significant value without receiving an equivalent. For example, the customer has paid in advance for a service.
-\item \textbf{Advantaged position ($\plus{}$)}: when a party would benefit if the transaction was stopped at this step. For example, the SP has received payment before the service has been provided.
-\end{itemize}
-
-There are many actions that each party can take, but we group them into two categories:
+We define three distinct positions to represent the state of each party within the protocol:
+
+\begin{itemize}
+\item \textbf{Neutral Position ($\neutral{}$)}: A party's state when no significant resources (money, time, effort) have been expended or acquired.
+\item \textbf{Disadvantaged Position ($\minus{}$)}: A party's state when it has invested resources without receiving a commensurate return, like a customer who has prepaid for a service.
+\item \textbf{Advantaged position ($\plus{}$)}: A scenario where halting the transaction would result in a benefit for a party, for instance, if the SP has been paid but has not yet provided the service.
+\end{itemize}
+
+The actions of each party are categorized as follows:
+
+\begin{enumerate}
+\item \textbf{Normal}: Those that adhere to the protocol's prescribed steps.
+\item \textbf{Abnormal}: Any deviation from the protocol's prescribed steps, such as sending irrelevant messages, skipping steps, or exceeding time limits.
+\end{enumerate}
+
+Additionally, the customer has the option to initiate a dispute at any protocol step, introducing another strategic layer:
 
@@
 \def\labelenumi{\arabic{enumi}.}
-
-\item \textbf{Normal}: taking actions prescribed by the protocol.
-\item \textbf{Abnormal}: anything that deviates from the intended steps of the protocol. For example, sending an arbitrary message, skipping or repeating steps, or timing out.
+\item \textbf{Agree}: The customer consents to the action and refrains from disputing.
+\item \textbf{Start a dispute}: The customer contests the action and initiates a dispute.
 \end{enumerate}
 
-In addition, at each step of the protocol, the customer can start a dispute, so another dimension with two positions must be taken into account:
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-
-\item \textbf{Agree}: the customer agrees with the action and therefore does not start a dispute.
-\item \textbf{Start a dispute}: the customer disagrees with the action and therefore starts a dispute.
-\end{enumerate}
-
-As a result, in our analysis we need to consider four different outcomes for each party of the protocol ($\mathrm{party \in \{C, SP}\}$), for each step of the protocol ($\mathrm{step \in 1..9}$):
-
-\begin{itemize}
-
-\item
-  $\mathrm{\sigma_{step,party,n}}$: after following the protocol when the other party acted normally.
-\item
-  $\mathrm{\sigma_{step,party,d}}$: after a settled dispute when the other party acted normally.
-\item
-  $\mathrm{\sigma_{step,party,\overline{n}}}$: after not starting a dispute despite the other party has acted abnormally.
-\item
-  $\mathrm{\sigma_{step,party,\overline{d}}}$: after a settled dispute when the other party has acted abnormally.
-\end{itemize}
-
-The protocol terminates after the last step, after starting a dispute, or after a party fails to complete its designated action in time.
-Therefore, all positions except $\mathrm{\sigma_n}$ are termination positions.
-
-Because the customer is anonymous, the SP cannot start a dispute - there is no way to identify the customer.
-To mitigate this problem, we designed the protocol so that the SP who follows the protocol is always in an advantageous position and therefore has no reason to start a dispute.
-On the other hand, the customer can start a dispute at any time during the protocol, but only the actual misbehaviour of the SP will make him win the conflict.
+Consequently, our analysis must account for four potential outcomes for each party at every protocol step ($\mathrm{party \in \{C, SP}\}$, $\mathrm{step \in 1..9}$):
+
+\begin{itemize}
+\item $\mathrm{\sigma_{step,party,n}}$: The outcome after adhering to the protocol with the other party acting normally.
+\item $\mathrm{\sigma_{step,party,d}}$: The outcome following a resolved dispute with the other party acting normally.
+\item $\mathrm{\sigma_{step,party,\overline{n}}}$: The outcome when no dispute is raised despite the other party's abnormal actions.
+\item $\mathrm{\sigma_{step,party,\overline{d}}}$: The outcome after a resolved dispute with the other party acting abnormally.
+\end{itemize}
+
+The protocol concludes after the final step, if a dispute is initiated, or if a party fails to perform its required action within the designated timeframe.
+Hence, all positions except $\mathrm{\sigma_n}$ signify the end of the protocol.
+
+The anonymity of the customer prevents the SP from initiating a dispute.
+To address this, the protocol is designed in such a way that an SP who adheres to the protocol remains in an advantageous position, eliminating the incentive to dispute.
+Conversely, the customer can dispute at any time, but only proven misbehavior of the SP will result in a successful dispute.
 
 \begin{definition}[Fairness] \label{def:fairness}
-A protocol achieves fairness iff 
+A protocol is considered fair iff 
 \begin{equation*}
@@
 \forall_{party \in parties}\forall_{\mathrm{step} \in \mathrm{steps}} &\operatorname{can\ move}\\
-&\operatorname{to the\ non-disadvantaged\ position} 
+&\operatorname{to\ the\ non-disadvantaged\ position} 
 \end{split}
@@
 
-Below we list the assumptions we take for the analysis purpose.
+For the purpose of our analysis, we operate under the following assumptions:
 
 \begin{enumerate}
-\item Both parties start from a neutral position ($\neutral${}).
-\item After completing a transaction, both parties end up in an advantageous position (\plus{}). In other words, they have an intrinsic motivation to initialise and complete the transaction.
-\item The protocol steps are atomic - there are no intermediate steps.
-\item The protocol can only go forward - there is no way to undo any action.
-\item Repeating the first step starts a new transaction.
-Repeating any other step is considered abnormal and is ignored.
-For example, paying the invoice twice has no effect on the curse of the protocol.
-\item Once published, the result is available to the customer on the storage network. 
-\item Winning the dispute results in a neutral position ($\neutral${}).
-\item Losing the dispute results in a penalty greater than any reward, leading to a disadvantaged position (\minus{}).
-Therefore, the rational customer will not start a dispute that he is not sure he can win.
-\item Both the customer and the SP are rational.
-They always prefer to go from the worst position (\minus{} or $\neutral${}) to a better position ($\neutral${} or \plus), but they are willing to risk a temporary worst position in favour of a later better position if and only if they can always get out of the worst position; in particular, the customer can always start a dispute and, if the SP has misbehaved, get out of the disadvantaged position (\minus) to the neutral position ($\neutral${}).
-\item We assume that the customer's materials without personal information are useless and the effort to deliver the package is negligible, so the customer's first step does not lead to a disadvantaged position.
-\item We assume that the processing cost of publishing $\mathrm{PoD}$ is negligible and compensates for the customer's effort in delivering the package.
+\item Both parties start from a neutral position ($\neutral{}$), implying no initial advantage or disadvantage.
+\item Upon successful transaction completion, both parties attain an advantageous position (\plus{}), indicating mutual benefit and motivation to engage in and complete the transaction.
+\item The steps within the protocol are atomic, meaning they are indivisible and have no intermediate states.
+\item The protocol is unidirectional; actions taken cannot be reversed or undone.
+\item The protocol can only be restarted by repeating the first step.
+Any repetition of subsequent steps is considered abnormal and will be disregarded.
+For example, a double payment does not change the course of the protocol.
+\item Once the service result is published, it becomes accessible to the customer via the storage network.
+\item A successful dispute resolution restores the disputing party to a neutral position ($\neutral{}$).
+\item Losing a dispute incurs a penalty that exceeds any potential gain, resulting in a disadvantaged position (\minus{}). This discourages frivolous or uncertain disputes.
+\item Both the customer and the SP are rational actors who prefer to move from a less advantageous to a more advantageous position.
+However, they may temporarily accept a less advantageous position if it leads to a subsequent advantageous state, as long as there is an escape route from the less advantageous position.
+Specifically, the client can initiate a dispute to move from a disadvantaged (\minus{}) to a neutral ($\neutral{}$) position if the SP fails to comply with the protocol.
+\item The customer's materials, without personal information, have no value and the effort to deliver the package is considered minimal.
+Thus, the customer's first step does not lead to a disadvantaged position.
+\item The cost of publishing the Proof of Delivery (PoD) is negligible and is offset by the customer's effort in delivering the package.
 \end{enumerate}
@@
 
-Figure~\ref{fig:positions} shows the positions of each party after each possible action taken.
+The fairness of our protocol is visually represented in Figure~\ref{fig:positions}, which illustrates the positions of each party following each possible action within the protocol.
 
@@
 \caption{Visual representation of the fairness of the protocol.
-The figure shows the game-theoretic outcomes of each party after each possible actions taken.
-Symbol $\neutral${} represents neutral outcome, \minus{} represents disadvantaged outcome, and \plus{} represents advantaged outcome, where the order relation holds \minus{} < $\neutral${} < \plus{}.}
+This figure shows the outcomes for each party after various actions.
+The symbols used are $\neutral{}$ for a neutral outcome, \minus{} for a disadvantaged outcome, and \plus{} for an advantaged outcome.
+The order relation is defined as \minus{} < $\neutral{}$ < \plus{}.}
 \label{fig:positions}
@@
 
-The detailed description of each step and the rationale for the outcome is given in Appendix~\ref{app:proof-of-fairness}.
+The detailed description of each step and the reasoning for the outcomes is given in~\ref{app:proof-of-fairness}.
 
 \subsection{Example scenarios}\label{example-scenarios}
-The Figure~\ref{fig:misbehaviour} shows the transitions of positions when the SP tries to misbehave and does not perform the service and therefore does not publish $\mathrm{PoP}$ after receiving the payment.
-After the deadline $\mathrm{T}_\mathrm{provide}$ the SP cannot publish valid $\mathrm{PoP}$ and so the customer starts a dispute.
-The customer wins the dispute because the SP cannot prove that the $\mathrm{PoP}$ was published before $\mathrm{T}_\mathrm{provide}$.
-The protocol ends up neutral for the customer and disadvantageous for the SP's positions.
+This section illustrates two key scenarios using figures to demonstrate the transitions of positions between the customer and the SP under different conditions.
 
@@
 \centering
-\caption{Transitions of positions where the SP is misbehaving and the customer starts a dispute.}
+\caption{Transitions of positions in a scenario where the SP misbehaves by not performing the service and failing to publish $\mathrm{PoP}$ after receiving payment.
+This leads to the customer initiating a dispute.}
 \label{fig:misbehaviour}
@@
 
-The rational course for both parties is to follow the protocol shown in Figure~\ref{fig:rational}.
+In the first scenario (Figure~\ref{fig:misbehaviour}), the SP attempts to misbehave by not delivering the service and consequently not publishing the Proof of Provision ($\mathrm{PoP}$) after receiving payment.
+If the SP fails to publish a valid $\mathrm{PoP}$ by the deadline $\mathrm{T}_\mathrm{provide}$, the customer is justified in starting a dispute.
+The customer is likely to win this dispute as the SP cannot prove the timely publication of $\mathrm{PoP}$.
+This scenario results in a neutral outcome for the customer and a disadvantageous outcome for the SP.
 
@@
 \centering
-\caption{Transitions of positions where both the customer and the SP follow the protocol.}
+\caption{Transitions of positions in a scenario where both the customer and the SP adhere to the protocol.}
 \label{fig:rational}
@@
 
-Using the definition of fairness~\ref{def:fairness} and the assumptions listed in Section~\ref{sec:assumptions}, our analysis shows that the protocol achieves fairness.
+The second scenario (Figure~\ref{fig:rational}) represents the rational and intended course of action, where both the customer and the SP follow the protocol as designed.
+This scenario is crucial as it demonstrates the protocol functioning optimally, leading to a fair outcome for both parties.
+
+By applying the definition of fairness from Section~\ref{def:fairness} and considering the assumptions outlined in Section~\ref{sec:assumptions}, our analysis confirms that the protocol achieves fairness under these scenarios (see ~\ref{app:proof-of-fairness} for detailed description).
 
@@
 
-\subsection*{Setup}
-
-We have developed a prototype of our protocol using the following technologies:
-
-\begin{itemize}
-  \item{Anonymous Payments} - we use the Monero blockchain \cite{noetherRingSignatureConfidential2015}.
-  \item{Storage Network} - we use the Powergate~\cite{textilePowergate2023}, which is a wrapper around Filecoin and IPFS.
-  \item{Message Board} - we use the Ethereum blockchain~\cite{woodEthereumSecureDecentralised2014}; specifically, its local development version Truffle Ganache and the Solidity language.
-\item{Customer and SP} - we create client-side web application (webapp) using \texttt{React.js} and \texttt{web3.js} library for interaction with Ethereum.
-We use \texttt{MetaMask} browser extension to sign and submit transactions to the Ethereum node.
-We use \texttt{monerod} network client and \texttt{monero-wallet-cli} command line interface to interact with the Monero blockchain.
-\end{itemize}
-
-The prototype is available at \url{https://anonser.stan.bar}. The source code is available at \url{https://github.com/stanbar/anonser}.
-
-% The prototype is available at \url{https://anonser.stan.bar}. The source code is available at \url{https://github.com/stanbar/anonymous-provision-of-services-via-blockchain}.
-
-We developed and tested our prototype in the following environment: OS — Arch Linux 5.11.8; Docker — 20.10.5; CPU — Intel(R) Core(TM) i7-4790 (8) 4.00~GHz; RAM — 16 GB DDR3; Storage — Samsung PM85 256~GB SSD; monerod and monero-wallet-cli — v0.18.1.2; Powergate — v2.6.2; Ganache — v7.5.0; Solidity — v0.8.17; ReactJS — v18.0.25; web3.js — v1.8.1; crypto-js — v4.1.1.
-
-For simplicity, all components run on one, mentioned above, physical machine; and all processes are managed by Docker.
+\subsection*{Setup, Preparation, and Experiment}
+
+Our protocol's prototype was developed using a suite of technologies designed to ensure anonymity and security:
+
+\begin{itemize}
+  \item \textbf{Anonymous Payments:} Utilization of the Monero blockchain for secure transactions.
+  \item \textbf{Storage Network:} Powergate serves as an interface for Filecoin and IPFS, facilitating decentralized storage.
+  \item \textbf{Message Board:} The Ethereum blockchain, accessed via a local development version Truffle Ganache and Solidity, acts as a public ledger.
+  \item \textbf{Customer and SP Interface:} A client-side web application built with \texttt{React.js} and \texttt{web3.js}, with \texttt{MetaMask} for Ethereum transactions and \texttt{monero-wallet-cli} for Monero interactions.
+\end{itemize}
+
+We used the following tools to create the experiment:
+\texttt{monerod} and \texttt{monero-wallet-cli} - v0.18.1.2; \texttt{Powergate} - v2.6.2; \texttt{Ganache} - v7.5.0; \texttt{Solidity} - v0.8.17; \texttt{ReactJS} - v18.0.25; \texttt{web3.js} - v1.8.1; \texttt{crypto-js} - v4.1.1.
+
+For simplicity, all components run on one physical machine; and all processes are managed by Docker.
 
@@
 
-\subsection*{Preparation}
-
-Both the customer and the SP create Monero wallets using the \texttt{monero-wallet-cli} command line tool.
-
-The SP deploys the smart contract using the \texttt{truffle migrate --network development} command, which deploys the smart contract to the Ethereum blockchain.
-The web application is configured to use the last deployed smart contract address.
-
-The customer receives some test Monero funds using the Faucet service available at \url{https://community.rino.io/faucet/stagenet/}.
-
-Next, the customer enables per-transaction proof generation (payment \texttt{receipt}) by setting \texttt{set store-tx-info 1} for their wallet.
-This is required to verify the payment in the event of a dispute.
-
-At this point both the customer and the SP are ready to start the protocol.
-
-\subsection*{Experiment}
-
-The customer and the SP are two different users of our prototype, but for simplicity, they use the same machine and the same web application.
-
-The experiment was conducted as follows:
+The prototype is available at \url{https://anonser.stan.bar}. The source code is available at \url{https://github.com/stanbar/anonser}.
+
+In preparation for the experiment, both the customer and the SP set up their Monero wallets using the \texttt{monero-wallet-cli}.
+The SP deploys the smart contract to the Ethereum blockchain with the \texttt{truffle migrate --network development} command, and the web application is then configured to interact with this newly deployed contract.
+
+The customer acquires test Monero funds from a Faucet service and configures their wallet to generate transaction proofs, essential for dispute resolution.
+
+With preparations complete, the experiment proceeds as follows:
 
 \begin{enumerate}
-  \setcounter{enumi}{0}
-  \item[0.] The protocol starts with the customer opening the webapp and creating a new provision.
-The application generates a random ECDSA (secp256k1) customer keypair and a random 32-byte provisionID, and then displays a QR code that encodes both the provisionID and the customer's public key. 
-The customer's private key must be downloaded and provided later to decrypt the results.
-
-  \item[1.] The customer prints the QR code, sticks it on a parcel and delivers the parcel to the SP either via the SP's drop box, parcel locker services (e.g.
-Amazon Locker, InPost~\cite{inpostParcelLockerService}), the customer's trusted delivery agent or the post office.
-
-  \item[2.1.] The SP opens the app and scans the QR code, which decodes the provisionID and the customer's public key.
-
-  \item[2.2.] Since (in this experiment) the provision was not paid in cash, the SP generates a unique Monero payment address using \texttt{monero-wallet-cli integrated\_address}. 
-  \item[2.3.] The SP submits the Proof of Delivery to the Ethereum blockchain using the MetaMask interface.
-
-  % monero-wallet-cli --stagenet --wallet-file sp --password "" integrated_address
-  % Random payment ID: <2b6d65d7d48b7896>
-  % Matching integrated address: 5LHmrsVsQM2Q2TgqufX4A5gKPpxy1czHULDyVc84omvnh1nQLVmqXk4VBuy8WnX1AXfKxDx7xuASAc6svkZqGVkL1XkUBWT7QejHymEaYM
-  \item[3.] The customer (using the webapp) checks the transaction status on the Ethereum blockchain by calling \texttt{getProvision} with arguments \texttt{customerPubKey} and \texttt{provisionID}.
-  % monero-wallet-cli --stagenet --wallet-file customer --password "" transfer 5LHmrsVsQM2Q2TgqufX4A5gKPpxy1czHULDyVc84omvnh1nQLVmqXk4VBuy8WnX1AXfKxDx7xuASAc6svkZqGVkL1XkUBWT7QejHymEaYM 1
-  % Transaction successfully submitted, transaction <7d89c04de458cfb76a811d5eb325075dec59f7a993c3bf7ce37f9e3a1630af65>
-  % monero-wallet-cli --stagenet --wallet-file customer --password "" get_tx_key 7d89c04de458cfb76a811d5eb325075dec59f7a993c3bf7ce37f9e3a1630af65
-  % Tx key: 1364dc848a752bf52011f4a63d98bcb16091cacd985713b6b5264b3ede6de40f
-
-  \item[4.] The customer sends the payment (using \texttt{monero-wallet-cli transfer}) to the \texttt{paymentAddress} specified in the smart contract and stores the payment receipt (using \texttt{monero-wallet-cli get\_tex\_key <tx-id>}) in case of a dispute.
-  \item[5.] Once the SP notices the payment on the Monero blockchain, it starts providing the service and outputs the file \texttt{result.pdf}.
-
-  \item[6.] The SP uploads the file \texttt{result.pdf} to the IPFS and Filecoin networks using Powergate.
-As a result, the SP receives the content identifier \texttt{cid}, as well as \texttt{dealID} and \texttt{minerID}.
-
-  \item[7.] The SP submits a Proof of Provision transaction to the Ethereum blockchain by calling \texttt{proofOfProvision} with arguments \texttt{customer\-PubKey}, \texttt{provisionID}, \texttt{cid} and \texttt{dealID}.
-
-  \item[8.] Meanwhile, the customer subscribes to Ethereum and waits for the SP to publish the Proof of Provision.
- Once the Proof Of Provision is published, the customer downloads the result using either the IPFS network using \url{https://dweb.link/<cid>} or Lotus network using \texttt{lotus retrieve <cid> <minerID>}.
-
-  \item[9.] The results are then decrypted using the customer's previously stored private key.
-If everything is correct, the customer is satisfied with the service and the protocol ends, otherwise the customer can initiate a dispute.
+  \item The customer begins by creating a new provision in the webapp, which generates a unique ECDSA keypair and provisionID.
+The corresponding QR code is printed and attached to the parcel for delivery.
+
+  \item The parcel is delivered to the SP through a chosen delivery method, such as a secure drop box or locker service.
+
+  \item Upon receipt, the SP scans the QR code to retrieve the provisionID and customer's public key.
+
+  \item Since (in this experiment) the provision was not paid in cash, the SP generates a unique Monero payment address using \texttt{monero-wallet-cli integrated\_address}.
+
+  \item The SP submits the PoD to the Ethereum blockchain using the MetaMask interface.
+
+    \item The customer checks the transaction status on the Ethereum blockchain by calling \texttt{getProvision} with arguments \texttt{customerPubKey} and \texttt{provisionID}
+
+    \item The customer sends the payment (using \texttt{monero-wallet-cli transfer}) to the \texttt{paymentAddress} specified in the smart contract and stores the payment receipt using \texttt{monero-wallet-cli get\_tex\_key <tx-id>}.
+
+    \item Upon payment confirmation, the SP provides the service, resulting in a \texttt{result.pdf} file.
+
+  \item This file is uploaded to IPFS and Filecoin, granting the SP a \texttt{cid}, \texttt{dealID}, and \texttt{minerID}.
+
+  \item A PoP is submitted to the Ethereum blockchain by the SP.
+
+    \item Meanwhile, the customer subscribes to Ethereum and waits for the SP to publish the PoP.
+Upon noticing the PoP, the customer retrieves the result using either one of the public gateways\footnote{IPFS Public Gateway Checker, \url{https://ipfs.github.io/public-gateway-checker/}, (last visited Jan.
+04, 2023)} like \url{https://cf-ipfs.com/ipfs/<cid>} or Lotus network using \texttt{lotus} \texttt{retrieve} \texttt{<cid>} \texttt{<minerID>}.
+
+  \item The results are then decrypted using the customer's previously stored private key.
+If the customer is satisfied with the service the protocol ends; otherwise, the customer may initiate a dispute process.
 
@@
 \paragraph{Fairness}
-Fairness within the protocol was demonstrated, as detailed in Section~\ref{sec:steps} and ~\ref{app:proof-of-fairness}.
+As shown in Section~\ref{sec:steps} and ~\ref{app:proof-of-fairness}, the protocol is fair.
 This was achieved through an undeniable handshake mechanism, where the SP first commits to the package delivery and service deadlines by publishing the PoD (as outlined in step 2).
@@
 \paragraph{Anonymity}
-Anonymity was achieved through the decoupling of personal information from transactional elements such as materials, payment, and communication.
-Anonymous payment methods were employed, including cash and privacy-focused cryptocurrencies like Monero, which obscure the details of transactions.
-Decentralized storage networks, namely IPFS and Filecoin, were also utilized to enhance privacy.
-These networks enabled the storage and retrieval of information without the need to disclose the customer's identity, ensuring that customers could engage with the protocol anonymously at every stage.
+Anonymity was secured by breaking the link between personal data and transactional elements, including materials, payments, and communications.
+We utilized anonymous payment methods such as cash and privacy-centric cryptocurrencies like Monero, to conceal transactional details.
+Furthermore, we leveraged decentralized storage networks like IPFS and Filecoin, which facilitate the anonymous storage and retrieval of data.
+This approach guaranteed that customer interactions with the protocol remained confidential at every stage.
 
@@
 \subsection{Dispute Resolution Service}\label{sec:decentralised-justice}
-Centralised Dispute Resolution Service is the biggest obstacle to the realisation of a system that is compliant with the Web3 postulates~\cite{ethereumWhatWeb3Why2023}.
-
-Possible directions for mitigating such problems are either (i) replacing local justice with blockchain dispute resolution systems, such as those proposed in Themis~\cite{mengThemisDecentralizedEscrow2019}, Kleros~\cite{bergollaKlerosSociolegalCase2022, gudkovCrowdArbitrationBlockchain2020}, Aragon Court~\cite{aragonDecentralizedDisputeResolution}, LTO Network~\cite{ltonetworkNextGenBlockchainB2B}, and other Online Dispute Resolution platforms~\cite{allenGovernanceBlockchainDispute2019}; or (ii) make it infeasible to provide incorrect results.
-
-The first approach is more feasible in the near future.
-It would require the creation of a large set of experts in a field who, in the case of a dispute, would receive all the proofs ($\mathrm{PoD}$, $\mathrm{PoP}$, payment $\mathrm{receipt}$ as well as any other proofs relevant to the case) that could be queried by the experts in a zero-knowledge fashion, i.e.
-they could ask a limited number of questions of the proofs and get yes/no answers.
-The case would be completely confidential as they would not be able to query any personal information.
-Experts would be incentivised to participate in the pool by the fee system.
-They would be incentivised to vote honestly by the stake they would have to lock and the reward/punishment they would receive for a correct/incorrect judgement, correctness being determined by the quorum of votes.
-
-The second is more futuristic.
-Let us assume that the service we are performing is fully computable.
-Then it would be possible to use proofs of correctness of computations~\cite{ben-sassonSNARKsVerifyingProgram2013} to enforce that only correct computations (and hence correct services) are accepted.
-This would require the entire service verification to be computable, which is difficult to achieve in settings where physical materials (such as blood) are examined.
-Specifically, the problem boils down to ``How to represent blood digitally?'' If we could represent urine, blood, saliva or any other physical material in a binary format and let the customer take a sample, discrete it and send it to the SP, then the whole chain of integrity could be ensured.
-This would make it impossible to provide the wrong service and therefore avoid disputes.
-
-\subsection{Self-sovereign identities}
-Our research in this area has shown that some jurisdictions require SPs to link the diagnosis to the customer's personal data.
-For example, in Poland, all laboratories performing medical diagnostic tests and collecting the material (except for HIV tests) are required to uniquely identify and verify the identity of the patient from whom the material was collected~\cite{ministerstwozdrowiaRegulationMinisterHealth2006}.
-
-This conflicts with the main aim of our protocol, which is to prevent the collection of any identifying information.
-
-A promising solution would be to use self-sovereign identities (SSIs)~\cite{muhleSurveyEssentialComponents2018}, especially the verifiable claims.
-A trusted authority (e.g.
-a government) would issue a one-time claim for the customer, which would be accepted by the SP as a legitimate personal identification.
-The SP would associate the diagnosis result with the provided DID.
-The DID itself would contain no personal information, so the SP would learn nothing about the customer's identity beyond the random-looking identification.
-The DID could be de-anonymised in cooperation with the government.
-
-However, as SSI is a relatively new technology and the government has not yet adopted it, we decided to leave the discussion of this topic for future work.
+The central challenge in achieving a Web3-compliant system lies in the centralization of dispute resolution services~\cite{ethereumWhatWeb3Why2023}.
+To address this, we consider two potential solutions: the integration of blockchain-based dispute resolution systems and the development of mechanisms to ensure the infeasibility of incorrect service provision.
+
+Blockchain-based dispute resolution platforms such as Themis~\cite{mengThemisDecentralizedEscrow2019}, Kleros~\cite{bergollaKlerosSociolegalCase2022, gudkovCrowdArbitrationBlockchain2020}, Aragon Court~\cite{aragonDecentralizedDisputeResolution}, LTO Network~\cite{ltonetworkNextGenBlockchainB2B}, and other Online Dispute Resolution (ODR) systems~\cite{allenGovernanceBlockchainDispute2019} offer a promising direction.
+These systems could employ a pool of field experts who, in the event of a dispute, would examine the proofs (e.g., $\mathrm{PoD}$, $\mathrm{PoP}$, payment $\mathrm{receipt}$) in a confidential, zero-knowledge context, providing verdicts without access to personal data.
+Expert participation and honest adjudication would be encouraged through a system of fees, stakes, and rewards.
+
+The second, more visionary approach involves ensuring service correctness through computational proofs, such as zkSNARKs~\cite{ben-sassonSNARKsVerifyingProgram2013}, which could validate the accuracy of services that are fully computable.
+This method, however, faces significant challenges in representing physical materials like blood or saliva digitally—a prerequisite for end-to-end service verification and the elimination of disputes.
+
+\subsection{Self-sovereign Identities}
+In our exploration of privacy-preserving protocols, we encountered regulatory requirements that mandate the linking of diagnostic results to patient identities, as is the case in Poland~\cite{ministerstwozdrowiaRegulationMinisterHealth2006}.
+Such regulations present a direct challenge to our protocol's objective of anonymity.
+
+The concept of self-sovereign identities (SSIs) and verifiable claims offers a potential resolution~\cite{muhleSurveyEssentialComponents2018}.
+Under this system, a trusted entity, such as a government body, could issue a one-time, verifiable claim to the customer.
+Service providers would accept this claim as valid identification, linking diagnostic results to a Decentralized Identifier (DID) that holds no personal data.
+While this ensures the SP cannot deduce the customer's identity, the DID could be traced back to the individual by the issuing authority if necessary.
+
+Given the early stage of SSI technology and its current lack of governmental adoption, we recognize the need for further research and development in this area.
 
@@
 Following the work of~\cite{birjoveanuFormalVerificationMultiparty2022}, the security analysis of our protocol could be improved by using automatic formal verification tools, such as AVISPA~\cite{armandoAVISPAToolAutomated2005}.
-It would require the specification of the protocol using the High-Level Protocol Specification Language (HLPSL)~\cite{chevalierHighLevelProtocol2004}.
-The specification would then be translated into the AVISPA intermediate language and verified using the AVISPA theorem prover.
-The verification would be performed by the AVISPA model checker, which would check the protocol against the security properties.
+This process would involve formulating the protocol in the High-Level Protocol Specification Language (HLPSL)~\cite{chevalierHighLevelProtocol2004}, followed by its translation into AVISPA's intermediate format.
+Subsequently, AVISPA's tools would rigorously assess the protocol's adherence to established security properties through automated theorem proving and model checking techniques.
 
 \section{Conclusions}\label{sec:conclusion}
-In this work, we have focused on enabling the provision of services without the collection of personal data.
-Our aim was to enable services such as genetic testing, testing for paternity, venereal diseases, HIV, drugs and steroids, or anonymous legal advice.
-
-We found that the current state of the art was not sufficient to achieve this goal.
-We have therefore proposed a service delivery protocol that simultaneously achieves anonymity, fairness, dispute resolution, TTP-lessness and supports physical materials.
-
-Payments are made in either cash or anonymous cryptocurrencies.
-The result of the service is published on a content-addressable p2p network.
-The dispute can be resolved by submitting the collected evidence to the dispute resolution service.
-
-Using the Definition~\ref{def:fairness}, we showed that the protocol achieves fairness by publishing proof of delivery, proof of payment, and proof of provisioning on the message board.
-
-Finally, we identified other improvements such as decentralised dispute resolution, self-sovereign identifiers, and anonymous courier delivery.
+
+This study has been dedicated to the development of a protocol that facilitates the provision of services while preserving the anonymity of the user.
+Our protocol is particularly applicable to services requiring a high degree of confidentiality, such as genetic testing, paternity determination, and anonymous legal consultation.
+
+We found that the current state of the art was not sufficient to achieve this goal, so we have designed and implemented a novel protocol that ensures user anonymity, fairness in service delivery, and a mechanism for dispute resolution without the need for a trusted third party.
+This protocol leverages anonymous payment systems, such as cash or privacy-focused cryptocurrencies, and utilizes peer-to-peer networks for the dissemination of service results.
+
+Through rigorous definition and analysis, we have demonstrated that our protocol meets the criteria for fairness, as outlined in Definition~\ref{def:fairness}.
+It does so by systematically publishing proofs of delivery, payment, and provisioning, ensuring a transparent and equitable process for all parties involved.
+
+In closing, we have pinpointed several avenues for future enhancement, including the integration of decentralized dispute resolution systems, the application of self-sovereign identity (SSI) frameworks, and the exploration of anonymous physical delivery methods.
+These areas present exciting opportunities for further research and development towards the realization of fully anonymous service provision in the digital age.
 
@@
 \bibliography{bibliography}
-
-\end{document}

### 2023-11-14 paper/main.tex
update protocol's assumptions

@@
 \RequirePackage{flushend}
+\usepackage[htt]{hyphenat}
 \RequirePackage[numbers,sort&compress]{natbib}
@@
 \section{The Protocol}\label{sec:protocol}
-In this section, we propose an abstract protocol for anonymous service provisioning that makes no assumptions about the underlying technologies.
-We define the requirements for each role and leave the choice of technology to the developer.
-Later in the paper (Section~\ref{sec:experiments}) we describe our implementation, which we use to conduct an experiment.
+This section outlines an abstract protocol for anonymous service provisioning, designed to be technology-agnostic.
+It specifies the requirements for each role, allowing developers flexibility in technology selection.
+The implementation details and experimental validation of this protocol are discussed in Section~\ref{sec:experiments}.
 
 \subsection{Assumptions}
-
-\begin{itemize}
-\item There exists PKI infrastructure:
-    \begin{itemize}
-        \item The customer and the SP have their key pairs consisting of secret key $\mathrm{sk}_\mathrm{party}$ and public key $\mathrm{pk}_\mathrm{party}$, where $\mathrm{party} \in \{\mathrm{C}, \mathrm{SP}\}$ for the customer and the SP accordingly.
-        \item Both the customer and the SP can create and verify digital signatures created by the customer $\mathrm{sig}_{\mathrm{sk}_\mathrm{C}}$ and the SP $\mathrm{sig}_{\mathrm{sk}_\mathrm{SP}}$.
-        \item The SP's public key $\mathrm{pk}_\mathrm{SP}$ is publicly known.
-    \end{itemize}
-
-\item Both the customer and the SP:
-    \begin{itemize}
-        \item use common symmetric encryption $\mathrm{E}_\mathrm{key}(\cdot)$ and decryption $\mathrm{D}_\mathrm{key}(\cdot)$ operations.
-        \item have access to anonymous payments blockchain, message board, and storage network.
-    \end{itemize}
-
-\item The SP:
-    \begin{itemize}
-        \item accepts packages from unknown customers.
-        \item accepts payments with cash and anonymous cryptocurrencies as described in Section~\ref{payment-for-services}.
-    \end{itemize}
-
-\item Dispute Resolution Service:
-    \begin{itemize}
-        \item accepts as evidence in a dispute the $\mathrm{PoD}$, $\mathrm{PoP}$, and payment $\mathrm{receipt}$ as described in Section~\ref{fairness}.
-    \end{itemize}
-
-\item Anonymous Payments Blockchain:
-    \begin{itemize}
-        \item supports anonymous, i.e., untraceable and (ideally) unlinkable transactions as described in Section~\ref{sec:pseudo-anon}.
-        \item supports uniquely identifiable transactions via a dedicated address, memo field, or other similar mechanisms as described in Section ~\ref{payment-for-services}. 
-    \end{itemize}
-
-\item Message Board:
-    \begin{itemize}
-        \item supports transactions of sizes up to $\mathrm{PoD}$ and $\mathrm{PoP}$.
-    \end{itemize}
-
-\item Storage Network:
-    \begin{itemize}
-        \item allows content to be retrieved using a content identifier $\mathrm{cid}$ (usually a hash of the content).
-        \item allows content to be retrieved anonymously.
-        \item guarantees that the content will be available for the duration of the agreement.
-    \end{itemize}
-\end{itemize}
+The protocol is based on several key assumptions, each critical to its functionality and security:
+
+\begin{itemize}
+
+\item \textbf{Cryptography and Public Key Infrastructure (PKI)}:
+    \begin{itemize}
+        \item The service provider (SP) possesses a key pair consisting of a secret key ($\mathrm{sk}_\mathrm{SP}$) and a publicly known public key ($\mathrm{pk}_\mathrm{SP}$).
+        \item Digital signatures created by the SP ($\mathrm{sig}_{\mathrm{sk}_\mathrm{SP}}$) can be verified using the publicly accessible $\mathrm{pk}_\mathrm{SP}$.
+        \item The customer remains anonymous and does not require a publicly known key pair, ensuring their privacy and anonymity in the protocol.
+
+        \item Both parties utilize standard symmetric encryption ($\mathrm{E}_\mathrm{key}(\cdot)$) and decryption ($\mathrm{D}_\mathrm{key}(\cdot)$) methods.
+    \end{itemize}
+
+\item \textbf{Service Provider (SP) Requirements}:
+    \begin{itemize}
+        \item The SP is willing to accept packages from unidentified customers.
+        \item Payments are accepted via cash or anonymous cryptocurrencies, as detailed in Section~\ref{payment-for-services}.
+    \end{itemize}
+
+\item \textbf{Anonymous Payments Blockchain}:
+    \begin{itemize}
+        \item Facilitates anonymous transactions that are untraceable and ideally unlinkable.
+        \item Allows transactions to be uniquely identified through dedicated addresses, memo fields, or similar mechanisms (see Section~\ref{payment-for-services}).
+    \end{itemize}
+
+\item \textbf{Message Board}:
+    \begin{itemize}
+        \item Capable of handling transaction sizes up to $\mathrm{PoD}$ and $\mathrm{PoP}$.
+    \end{itemize}
+
+\item \textbf{Storage Network}:
+    \begin{itemize}
+        \item Enables content retrieval using a content identifier ($\mathrm{cid}$), typically a hash of the content.
+        \item Ensures anonymous access to content.
+        \item Provides a guarantee of content availability for the agreed duration.
+    \end{itemize}
+
+\item \textbf{Dispute Resolution Service}:
+    \begin{itemize}
+        \item Recognizes $\mathrm{PoD}$ (Proof of Delivery), $\mathrm{PoP}$ (Proof of Provision), and payment receipts as valid evidence in disputes (see Section~\ref{fairness}).
+    \end{itemize}
+\end{itemize}
+
+This protocol framework sets the stage for a secure, anonymous, and fair service provisioning system.
+It balances the needs for privacy and accountability, ensuring that both the customer and the SP can engage in transactions with confidence in the system's integrity and fairness.
 

### 2023-11-15 paper/main.tex
update protocols messages

@@
 \subsection{Messages}\label{messages}
-In this section, we describe the messages exchanged between the parties of the protocol.
+This subsection details the messages exchanged between the parties in the protocol.
 
@@
 
-\noindent \textbf
-{Package}\label{package} is a physical container prepared by the customer encompassing all the $\mathrm{materials}$ required by the SP to provide the service.
+\noindent \textbf{Package}\label{package} is a physical container prepared by the customer containing all the $\mathrm{materials}$ required by the SP to provide the service.
 
@@
 where:
-
-\begin{itemize}
-
-\item $\mathrm{materials}$ - are the materials required to provide the service, for example, samples of urine, blood, stool, saliva; legal documents, CDs, emails, photos, bank statements; or any other type of material depending on the service.
-\item $\mathrm{provisionID}$ - a randomly generated provision identifier, used to anonymously track the provision through all steps of the protocol.
-\item $\mathrm{pk_C}$ - the customer's public key used to encrypt the results published to the public storage network.
-\end{itemize}
-
-\noindent \textbf
-{Proof of Delivery ($\mathrm{PoD}$)}\label{proof-of-delivery} is a confirmation that the customer has delivered a correct (according to the SP's requirements) package to the SP and that the SP has accepted it.
-
-It is also an agreement between the customer and the SP, as it includes agreed-upon deadlines for actions and a method of payment.
-
-The $\mathrm{PoD}$ is published on the message board by the SP.
+\begin{itemize}
+\item $\mathrm{materials}$ - Materials required for the service provision, such as biological samples, legal documents or other relevant items.
+\item $\mathrm{provisionID}$ - A unique identifier generated by the customer to anonymously track the provision through all protocol steps.
+\item $\mathrm{pk_C}$ - The customer's public key for encrypting results to be published to the public storage network.
+\end{itemize}
+
+\noindent \textbf{Proof of Delivery ($\mathrm{PoD}$)}\label{proof-of-delivery} confirms the correct delivery of the package to the SP and its acceptance.
+
+It is also an agreement between the customer and the SP as it contains agreed deadlines for actions and a payment method.
 
 \begin{eqnarray}
-\mathrm{PoD} & \equiv & (\begin{array}[t]{l}\mathrm{pk_C}, \mathrm{provisionID},  \mathrm{sig}_\mathrm{SP}, \mathrm{paymentAddress}, \\\\ 
+\mathrm{PoD} & \equiv & (\begin{array}[t]{l}\mathrm{pk_C}, \mathrm{provisionID},   \mathrm{paymentAddress},
+\mathrm{sig}_\mathrm{SP}, \\\\ 
 \mathrm{T}_\mathrm{issue}, \mathrm{T}_\mathrm{pay}, \mathrm{T}_\mathrm{provide}\; )\end{array}
@@
 where:
-
-\begin{itemize}
-\item $\mathrm{pk_C}$ - the public key of the customer used to encrypt the result published on the public storage network.
-\item $\mathrm{provisionID}$ - the number that uniquely identifies the transaction previously generated by the customer.
-\item $\mathrm{sig}_\mathrm{SP}$ - the SP's signature to ensure non-repudiation.
-\item $\mathrm{paymentAddress}$ - payment address of the SP's anonymous blockchain account.
-\item $\mathrm{T}_\mathrm{issue}$ - time at which the $\mathrm{PoD}$ is issued by the SP.
-\item
-  $\mathrm{T}_\mathrm{pay}$ - deadline for paying the transaction.
-\item
-  $\mathrm{T}_\mathrm{provide}$ - deadline to provide the result of the service, i.e. to publish $\mathrm{PoP}$.
+\begin{itemize}
+\item $\mathrm{pk_C}$ - Customer's public key.
+\item $\mathrm{provisionID}$ - Unique transaction identifier.
+\item $\mathrm{sig}_\mathrm{SP}$ - SP's digital signature.
+\item $\mathrm{paymentAddress}$ - SP's anonymous payment address.
+\item $\mathrm{T}_\mathrm{issue}$ - Time of $\mathrm{PoD}$ issuance.
+\item $\mathrm{T}_\mathrm{pay}$ - Payment deadline.
+\item $\mathrm{T}_\mathrm{provide}$ - Deadline for service provision, i.e. to publish $\mathrm{PoP}$.
 \end{itemize}
@@
 
-\noindent \textbf
-{Proof of provision ($\mathrm{PoP}$)}\label{proof-of-provision} is proof that the SP published the result at a certain time.
-It protects the SP in case the customer unjustifiably starts a dispute after the results have been published.
+\noindent \textbf{Proof of Provision ($\mathrm{PoP}$)}\label{proof-of-provision} verifies the SP's publication of results at a specific time, protecting the SP against unjustified disputes.
+
 The link between $\mathrm{PoP}$ and the results is made by the content identifier ($\mathrm{cid}$), which uniquely identifies the results so that the result cannot be forged after the $\mathrm{PoP}$ has been published.
-
-The $\mathrm{PoP}$ is published on the message board by the SP.
 
@@
 where:
-
-\begin{itemize}
-
-\item $\mathrm{cid}$ - the content identifier as specified in Section~\ref{storage-network}.
-\item $\mathrm{provisionID}$ - The number that uniquely identifies the transaction previously created by the customer.
-\item $\mathrm{sig}_\mathrm{SP}$ - the signature of the SP, which guarantees non-repudiation.
+\begin{itemize}
+\item $\mathrm{cid}$ - Content identifier as specified in Section~\ref{storage-network}.
+\item $\mathrm{provisionID}$ - Unique transaction identifier.
+\item $\mathrm{sig}_\mathrm{SP}$ - SP's digital signature.
 \end{itemize}
@@
 
-\noindent \textbf
-{Results}\label{results} is assumed to be a document in PDF format, but any other format is acceptable as long as it can be binary encoded and uploaded to the storage network.
-We symbolically refer to it as $\mathrm{results}$.
-
-\noindent \textbf
-{Content Identifier (cid)}\label{content-identifier-cid} is a term coined by IPFS~\cite{ipfsContentIdentifiersCIDs}.
-However, since our protocol does not depend on this particular implementation of the storage network, we let the $\mathrm{cid}$ be any other identifier that securely and uniquely points to the content.
+\noindent \textbf{Results}\label{results} are typically in PDF format, but any binary-encodable format acceptable for the storage network can be used, symbolically referred to as $\mathrm{results}$.
+
+\noindent \textbf{Content Identifier (cid)}\label{content-identifier-cid} is a term from IPFS~\cite{ipfsContentIdentifiersCIDs}.
+However, the protocol allows for any secure and unique identifier for content referencing.
 

### 2023-11-22 paper/main.tex
update protocol steps

@@
 
-\subsection{Protocol description}\label{protocol-description}
-
-In this section we describe each step of the protocol, also shown in Figure~\ref{fig:protocol-diagram}.
+\subsection{Protocol Description}\label{protocol-description}
+
+This section outlines each step of the protocol, also shown in Figure~\ref{fig:protocol-diagram}.
 
@@
 
-\noindent \textbf
-{Step 0.  Preparation}\label{step-0-preparation}
-
-The customer collects all $\mathrm{materials}$ required by the SP, generates a random $\mathrm{provisionID}$ and a random keypair $(\mathrm{sk_C},\mathrm{pk_C})$.
-The $\mathrm{provisionID}$ is used to connect all actions associated with the transaction throughout the protocol.
-The $\mathrm{provisionID}$ and $\mathrm{pk_C}$ are encoded as a QR code, printed and attached to the $\mathrm{pkg}$ package.
-The $\mathrm{sk_C}$ is kept secret and is used to decrypt the $\mathrm{result}$ at the end of the protocol.
-
-\noindent \textbf
-{Step 1. Package Delivery}\label{step-1-package-delivery}
-
-The protocol starts when the customer delivers the package $\mathrm{pkg}$ to the SP and its content is accepted.
-As a result, $\mathrm{PoD}$ is created with a predefined payment deadline $\mathrm{T}_\mathrm{pay}$, service provision deadline $\mathrm{T}_\mathrm{provide}$ and current time $\mathrm{T}_\mathrm{issue}$.
-In addition, $\mathrm{PoD}$ embodies information on whether the service was paid for in cash or whether the customer should pay using the anonymous blockchain account.
-In the latter case, the SP's payment $\mathrm{address}$ is included in $\mathrm{PoD}$.
-
-The digital signature $\mathrm{sig}_{\mathrm{sk}_\mathrm{SP}}$ on the $\mathrm{PoD}$, created with the SP's secret key $\mathrm{sk}_\mathrm{SP}$, guarantees non-repudiation.
+\noindent \textbf{Step 0. Preparation}\label{step-0-preparation}
+
+The customer prepares the $\mathrm{materials}$ required by the SP, generates a random $\mathrm{provisionID}$, and a keypair $(\mathrm{sk_C},\mathrm{pk_C})$.
+The $\mathrm{provisionID}$ and $\mathrm{pk_C}$ are encoded as a QR code, attached to the $\mathrm{pkg}$.
+The $\mathrm{sk_C}$ is kept secret for decrypting the $\mathrm{result}$ later.
+
+\noindent \textbf{Step 1. Package Delivery}\label{step-1-package-delivery}
+
+The protocol initiates when the customer delivers $\mathrm{pkg}$ to the SP.
+The SP creates $\mathrm{PoD}$ with deadlines $\mathrm{T}_\mathrm{pay}$, $\mathrm{T}_\mathrm{provide}$, and $\mathrm{T}_\mathrm{issue}$.
+The $\mathrm{PoD}$ also specifies the payment method (cash or blockchain address).
+The SP's digital signature $\mathrm{sig}_{\mathrm{sk}_\mathrm{SP}}$ on $\mathrm{PoD}$ ensures non-repudiation.
 
@@
 \]
-
-\noindent \textbf
-{Step 2. Proof of Delivery}\label{step-2-pod}
-
-Then, the $\mathrm{PoD}$ is published on the message board by the SP, committing to the fact that the package $\mathrm{pkg}$ has been delivered, and the SP cannot reject receiving it.
-If the provision has not been paid in cash, the SP waits for the customer to pay for the service at the payment $\mathrm{address}$ specified in the $\mathrm{PoD}$.
+% TODO continute from here
+
+\noindent \textbf{Step 2. Proof of Delivery}\label{step-2-pod}
+
+The SP publishes $\mathrm{PoD}$ on the message board, confirming receipt of $\mathrm{pkg}$. If not paid in cash, the SP awaits payment at the specified address in $\mathrm{PoD}$.
 
@@
 
-The Algorithm~\ref{alg:proofOfDelivery} presents the process of processing the PoD and recording it on-chain.
+The Algorithm~\ref{alg:proofOfDelivery} presents the process of processing the $\mathrm{PoD}$ and recording it on-chain.
 
@@
 \begin{algorithmic}[1]
-\Function{proofOfDelivery}{$pk_C$, $provisionId$, $sig_{SP}$, $paidInCash$, $paymentAddress$, $paymentWindow$, $provisionWindow$}
+\Function{proofOfDelivery}{$pk_C$, $provisionId$, $paidInCash$, $paymentAddress$, $paymentWindow$, $provisionWindow$, $sig_{SP}$}
     \State Verify $sig_{SP}$
-    \If{provisions[$pk_C$][$provisionId$].exist}
+    \If{provisions[$pk_C$][$provisionId$] is not empty}
         \State \Return Error("Provision already exists")
@@
 
-\noindent \textbf
-{Step 3. Get Proof of Delivery}\label{step-3-get-pod}
-
-Once the package has been delivered and the $\mathrm{PoD}$ has been published, the customer can retrieve the $\mathrm{PoD}$ from the message board and (if everything is correct) proceed with the protocol.
+\noindent \textbf{Step 3. Get Proof of Delivery}\label{step-3-get-pod}
+
+The customer retrieves $\mathrm{PoD}$ from the message board and verifies its correctness.
 
@@
 
-\noindent \textbf
-{Step 4. Payment}\label{step-4-payment}
-
-If the provision was not paid in cash, the customer should pay for the transaction using the predefined anonymous payment blockchain (see Section~\ref{payment-for-services}).
-In return, the customer receives the $\mathrm{receipt}$, which should be disclosed in case of dispute.
+\noindent \textbf{Step 4. Payment}\label{step-4-payment}
+
+If not paid in cash, the customer pays via the anonymous blockchain, receiving a $\mathrm{receipt}$.
 
@@
 
-\noindent \textbf
-{Step 5. Provision of Service}\label{step-5-provision-of-service}
-
-Once the customer has paid for the transaction, either in cash or via the anonymous blockchain, the SP can begin to provide the service.
+\noindent \textbf{Step 5. Provision of Service}\label{step-5-provision-of-service}
+
+Upon payment confirmation, the SP begins service provision.
 
@@
 
-\noindent \textbf
-{Step 6. Upload result}\label{step-6-upload-result}
-
-When the service is complete, a result should be generated. 
-Next, the result is encrypted using a shared key derived from the customer's public key $\mathrm{pk_C}$ and the SP's secret key $\mathrm{sk(SP)}$ using the Diffie-Hellman key exchange (DHKE) method~\cite{diffieNewDirectionsCryptography1976}.
-The encrypted result is then uploaded to the content addressable network (such as IPFS). In return, the content identifier ($\mathrm{cid}$) is created.
+\noindent \textbf{Step 6. Upload Result}\label{step-6-upload-result}
+
+The SP encrypts the $\mathrm{result}$ using $\mathrm{E_{DHKE(sk_{SP}, pk_C)}}$ and uploads it to the storage network, receiving a $\mathrm{cid}$.
 
@@
 
-\noindent \textbf
-{Step 7. Proof of Provision}\label{step-7-proof-of-provision}
-
-When the $\mathrm{result}$ is uploaded, the SP creates and publishes on a message board a proof of provision consisting of $\mathrm{cid}$ along with $\mathrm{provisionID}$ and signature $\mathrm{sig}_\mathrm{SP}$.
+\noindent \textbf{Step 7. Proof of Provision}\label{step-7-proof-of-provision}
+
+The SP publishes $\mathrm{PoP}$ on the message board, including $\mathrm{cid}$ and $\mathrm{provisionID}$.
 
@@
 
-The Algorithm~\ref{alg:proofOfProvision} presents the process of processing the PoP and recording it on-chain.
+The Algorithm~\ref{alg:proofOfProvision} presents the process of processing the $\mathrm{PoP}$ and recording it on-chain.
 
@@
 \begin{algorithmic}[1]
-\Function{proofOfProvision}{$pk_C$, $provisionId$, $cid$}
+\Function{proofOfProvision}{$pk_C$, $provisionId$, $cid$, $sig_{SP}$}
+    \State Verify $sig_{SP}$
     \State $provision \gets$ provisions[$pk_C$][$provisionId$]
@@
 
-\noindent \textbf
-{Step 8. Get Proof of Provision}\label{step-8-get-proof-of-provision}
-
-After delivering the package and paying for the transaction, the customer starts listening to the message board and waits until the SP publishes the $\mathrm{PoP}$ for the $\mathrm{provisionID}$.
+\noindent \textbf{Step 8. Get Proof of Provision}\label{step-8-get-proof-of-provision}
+
+The customer monitors the message board for the SP's $\mathrm{PoP}$.
 
@@
 
-\noindent \textbf
-{Step 9. Download result}\label{step-9-download-result}
-
-Having the $\mathrm{cid}$, the customer downloads and decrypts the $\mathrm{result}$ using a shared key derived from the customer's secret key $\mathrm{sk_C}$ and the SP's public key $\mathrm{pk_{SP}}$ using the DHKE method.
-The protocol ends.
+\noindent \textbf{Step 9. Download Result}\label{step-9-download-result}
+
+The customer downloads and decrypts the $\mathrm{result}$ using $\mathrm{D_{DHKE(sk_C, pk_{SP})}}$.
 
@@
 \bibliography{bibliography}
+
+\end{document}

### 2023-11-28 paper/main.tex
apply changes suggested by reviewers

@@
 \RequirePackage[T1]{fontenc}
-\smartqed  % flush right qed marks, e.g. at end of proof
+\smartqed
 \RequirePackage{graphicx}
-\RequirePackage{mathptmx}      % use Times fonts if available on your TeX system
+\RequirePackage{mathptmx}
 \RequirePackage{flushend}
@@
 \RequirePackage[numbers,sort&compress]{natbib}
-\RequirePackage[colorlinks,citecolor=blue,urlcolor=blue,linkcolor=blue]{hyperref}
 
@@
 \usepackage{algpseudocode}
-\usepackage{graphicx}
 \usepackage{textcomp}
@@
 
+\RequirePackage[colorlinks,citecolor=blue,urlcolor=blue,linkcolor=blue]{hyperref}
+
 \renewcommand{\sp}{SP}
@@
 \begin{abstract}
-  \ABSTRACT{}
-
+\begin{sloppypar}
+Lawyers, laboratories, auditors or banks often need data containing sensitive personal information to provide their services.
+Examples of sensitive services include genetic testing, paternity testing, STD testing, credit scoring or legal advice.
+\end{sloppypar}
+
+The processing of personal data, especially when providing services involving sensitive data such as health records, biological material or legal documents, exposes both users and service providers (SPs) to privacy risks.
+SPs are at risk of violating GDPR, CPAA and other legal regulations, while customers are at risk of losing their privacy.
+
+We observe that personal data is often only used for logistical purposes, such as payment or communication, and could be provided anonymously if such methods were available.
+
+We present a solution that allows services to be provided without collecting personal data.
+We use anonymous payment methods such as cash and anonymous cryptocurrencies, blockchain to achieve fairness, and distributed content-addressable storage networks to deliver results.
+
+\begin{sloppypar}
+Compared to other solutions, our protocol achieves anonymity with weaker assumptions, supports physical materials and conflict resolution, and does not require the customer to interact with the blockchain in conflict-free transactions, demonstrating better practicality.
+\end{sloppypar}
+
+In this work, we analyse the fairness of our protocol and implement it using Ethereum technology as a message board, Monero as an anonymous payment method, and Powergate (IPFS and Filecoin) as a decentralised storage network.
   \newcommand{\sep}{ \and }
@@
 
+\begin{sloppypar}
 Other examples of sensitive services include anonymous complaints or legal services, such as legal advice, which may require disclosure of financial transaction history and confidential legal documents.
 Banking services, such as credit scoring, may require sensitive personal information, such as medical records and financial transaction history.
+\end{sloppypar}
 
@@
 
+\begin{sloppypar}
 Authors of~\cite{blackPresymptomaticTestingConfidentiality2021} highlight that after their organisation adopted Electronic Medical Record (EMR) systems, they could no longer promise the same confidentiality assurances.
+\end{sloppypar}
 
@@
 
+\begin{sloppypar}
 Examples of services that would benefit from the anonymity property are:
+\end{sloppypar}
+
 \begin{itemize}
@@
 
+\begin{sloppypar}
 \item \textbf{Anonymity in Legal Consultations for Entrepreneurs}: Individuals engaged in entrepreneurial activities may want to assess the risks and possible consequences of their actions.
 By revealing their identity, they trust that the lawyer will not use this information for harmful actions.
+\end{sloppypar}
+
+\begin{sloppypar}
 \item \textbf{Whistleblowing Platforms}: Employees or citizens witnessing unethical or illegal activities within organizations can report these anonymously without fear of reprisal, job loss, or social stigma, thereby promoting a more transparent and accountable society.
+\end{sloppypar}
+
+\begin{sloppypar}
 \item \textbf{Sexual Health and Reproductive Services}: People seeking advice or services related to sexual health, contraception, or abortion might prefer anonymity due to the sensitive nature of these topics and potential societal judgment.
+\end{sloppypar}
+
 \end{itemize}
@@
 
+\begin{sloppypar}
 In this work we explore the possibilities of anonymous service provision and propose a protocol that preserves the customer's privacy even in the event of a successful attack.
 Under realistic operational assumptions, we show that \textbf{decoupling personal information from materials, payment and communication achieves a sufficient level of anonymity}.
+\end{sloppypar}
 
@@
 
+\begin{sloppypar}
 Our review shows that none of the current systems is sufficient to achieve the desired goal.
@@
 In the event of a dispute, either due to missed deadlines or incorrect results, the customer can disclose the entire interaction, prove the SP's misbehaviour to the Dispute Resolution Service, and win the dispute.
+\end{sloppypar}
 
@@
         \item \textbf{Symmetric encryption}, to encrypt and decrypt the results published on the public networks.
+        \begin{sloppypar}
         \item \textbf{Diffie-Helman key exchange (DHKE)}, to derive shared secrets for symmetric encryption.
         \item \textbf{Digital signatures}, to achieve authentication and non-repudiation of actions. 
+        \end{sloppypar}
     \end{itemize}
@@
 
-\paragraph{}
-The contribution of our paper is:
-\begin{itemize}
-\item we propose a protocol that upon a realistic operational and threat model:
-  \begin{itemize}
-  \item allows \textbf{anonymous} service provision involving \textbf{physical materials}, i.e., the service provider does not need to collect any personal information from the customer;
-  \item achieves \textbf{fairness} by the use of blockchain and cryptographic proofs. We model the protocol as an interactive non-cooperative game and show fairness at each of its steps.
-  \item \textbf{does not rely on a centralised TTP}, but uses a decentralised blockchain and a distributed content-addressable storage network;
-  \item in conflict-free transactions does not require customers to interact with the blockchain, achieving better \textbf{user experience and practicality};
-  \item guarantees the \textbf{remote availability of the results}, even in case of the SP denial of service.
-  \end{itemize} 
-\item We implement a working prototype of the protocol and provide open source code.
-\item We systematise often misused definitions of anonymity, pseudonymity, linkability and traceability.
-\item We propose a framework for analysing fairness in fair exchange protocols and use it to prove the fairness of our protocol.
-\item We discuss possible improvements to the protocol using secure computation, self-sovereign identities, zero-knowledge proofs, and blockchain-based dispute resolution techniques.
-\end{itemize}
+The contribution of our paper is multifaceted and significant in advancing blockchain-based fair exchange systems:
+
+\begin{sloppypar}
+\begin{itemize}
+    \item We propose a protocol based on a realistic operational and threat model that:
+    \begin{itemize}
+        \item Enables \textbf{anonymous service provision} involving physical materials, eliminating the need for service providers to collect personal information from customers.
+        \item Achieves \textbf{fairness} through blockchain technology and cryptographic proofs, modeled as an interactive non-cooperative game, ensuring fairness at each step.
+        \item Operates without a centralized Trusted Third Party (TTP), leveraging a decentralized blockchain and a distributed content-addressable storage network.
+        \item Enhances \textbf{user experience and practicality} in conflict-free transactions by eliminating the need for customer interaction with the blockchain.
+        \item Ensures \textbf{remote availability of results}, even in cases of service provider denial.
+    \end{itemize}
+    \item Our implementation includes a working prototype with open-source code, demonstrating the practical applicability of our protocol.
+    \item We clarify often misused concepts such as anonymity, pseudonymity, linkability, and traceability, providing a clearer framework for understanding these critical aspects.
+    \item A novel framework for analyzing fairness in fair exchange protocols is introduced, and we use it to validate the fairness of our protocol.
+    \item We discuss potential enhancements using advanced technologies like secure computation, self-sovereign identities, zero-knowledge proofs, and blockchain-based dispute resolution, paving the way for future research and development.
+\end{itemize}
+\end{sloppypar}
 
@@
 
-The rest of this paper is organised as follows.
-In Section~\ref{sec:related-works} we review related works. 
+\begin{sloppypar}
+The rest of this paper is organised as follows. In Section~\ref{sec:related-works} we review related works. 
 Then in Section~\ref{sec:building-blocks} we discuss the building blocks of a dispute resolution system, blockchain as a message board, fairness, anonymous payments, storage network, availability of results and anonymity.
@@
 Finally, Section~\ref{sec:conclusion} concludes the paper.
+\end{sloppypar}
 
 \section{Related Works}\label{sec:related-works}
+\begin{sloppypar}
 This section reviews key protocols in fair exchange, anonymity, and physical delivery, highlighting their primary features and differences.
+\end{sloppypar}
 
@@
 is e-commerce. A typical transaction involves a seller and
-a buyer exchanging money for a physical product. To pro-
+a customer exchanging money for a physical product. To pro-
 tect themselves, the seller wants to receive the funds before
-sending the product, while the buyer wants to receive the
+sending the product, while the customer wants to receive the
 product before paying. The fairness of the protocol should
@@
 
+\begin{sloppypar}
 Protocols like those proposed by Bîrjoveanu et al.
@@
 Themis (Meng et al., 2019)\cite{mengThemisDecentralizedEscrow2019} further advanced this by incorporating a decentralized dispute resolution mechanism, though it does not address anonymity.
+\end{sloppypar}
 
@@
 
+\begin{sloppypar}
 We also didn't focus on protocols for buying digital products, as they are not relevant to our use case.
 A more comprehensive analysis of such protocols is available in~\cite{birjoveanuTwoPartyECommerceProtocols2022}.
+\end{sloppypar}
 
@@
 
-Unlike most protocols, our system is designed for transactions where the package is delivered from the buyer to the Service Provider (SP), and we assume a generic Dispute Resolution Service for handling conflicts .
+Unlike most protocols, our system is designed for transactions where the package is delivered from the customer to the Service Provider (SP), and we assume a generic Dispute Resolution Service for handling conflicts .
 
@@
 
-{\begin{table*}
+\begin{table*}
 \centering
@@
 
-\subsection{Physical products}\label{sec:physical-products}
-The use cases discussed in this paper use physical materials such as blood, urine, hair and other biological materials.
-This requirement, combined with the need for anonymity, is a challenging part of fair exchange protocols.
-The problem arises when the seller wants to send the product to the buyer who wants to remain anonymous.
-Most of the existing protocols either assume the existence of a trusted delivery agent~\cite{mohammedalarajFairnessPhysicalProducts2012,birjoveanuAnonymityFairexchangeEcommerce2015}, or use a complex delivery mechanism similar to onion routing involving multiple delivery services~\cite{altawyLelantosBlockchainBasedAnonymous2017}.
-
-However, our use case is different in that the physical materials are transferred from the (anonymous) customer to the (public) SP.
-This allows a simplification of the delivery process.
-We assume that there is a way to deliver a package anonymously without revealing the customer's personal information, either via the SP's drop box, parcel locker services (e.g.
-Amazon Locker, InPost), the customer's trusted Delivery Agent, or even the post office.
-
-\subsection{Dispute resolution system}
+\subsection{Physical Products}\label{sec:physical-products}
+In the realm of fair exchange protocols involving physical materials, existing solutions often rely on trusted intermediaries~\cite{mohammedalarajFairnessPhysicalProducts2012, birjoveanuAnonymityFairexchangeEcommerce2015} or complex delivery systems~\cite{altawyLelantosBlockchainBasedAnonymous2017} to maintain anonymity.
+These methods, while effective, can be cumbersome and less practical for certain use cases.
+
+In our context, the process is reversed as the physical materials are transferred from an anonymous customer to a publicly known Service Provider (SP).
+This unique setup allows for a simplification of the delivery process.
+We propose several methods to facilitate anonymous delivery without compromising the customer's personal information:
+
+\begin{itemize}
+    \item \textbf{SP's Drop Box:} Utilizing a secure drop box provided by the SP, where customers can leave their packages without revealing their identity.
+
+    \item \textbf{Parcel Locker Services:} Leveraging existing locker services (e.g., Amazon Locker, InPost) that offer a degree of anonymity and security in package delivery.
+
+    \item \textbf{Trusted Delivery Agent:} The customer may employ a trusted individual or service to deliver the package to the SP, ensuring the customer's anonymity.
+
+    \item \textbf{Postal Services:} Traditional postal services can be used, provided that they do not require personal identification or return addresses that could compromise anonymity.
+\end{itemize}
+
+\subsection{Dispute Resolution System}
 \label{sec:dispute-resolution}
-Disputes are an inevitable part of all human transactions.
-Whether intentional or accidental, the system should prevent violations of agreed contract rules or local jurisdiction.
-The rules are set by law and enforced by the police.
-
-The vision of smart contracts was to replace the legal contract with
-programmable and autonomous contracts.
-The code of the smart contract contains the specifications of the contract, hence the slogan \textit{code as law}.
-In addition, smart contracts are executed automatically, bridging the gap between law and its enforcement by police~\cite{allenGovernanceBlockchainDispute2019}.
-However, the blockchain paradigm has its limitations.
-
-Blockchains can only guarantee the correctness of the data and calculations that exist on the blockchain.
-The problem arises when we want the smart contract to make decisions based on some input from outside the blockchain.
-The technique for providing real-world data to the blockchain is called \textit{oracle}.
-An oracle provides data based on a decentralised network of mediators, so the trust is also decentralised~\cite{breidenbachChainlinkNextSteps2021}.
-
-Some oracles provide data such as weather, football results, stock prices, train delays, election results and others-and these are the ones we are interested in-provide the resolution of a submitted dispute.
-
-Themis~\cite{mengThemisDecentralizedEscrow2019} not only provides a fair exchange protocol, it also provides a semi-autonomous decentralised dispute resolution system that complies with the Web3 postulates of a decentralised Web~\cite{ethereumWhatWeb3Why2023}.
-Themis resolves disputes through a set of voluntary, anonymous mediators who take part in voting and decide whether a party has misbehaved.
-The honesty of the mediators is achieved through a monetary incentive and reputation system.
-
-Kleros~\cite{bergollaKlerosSociolegalCase2022} is a smart contract deployed on the Ethereum platform that mimics, in a decentralised and autonomous way, how the court works in real life.
-In Kleros, every process of a dispute, such as gathering evidence, selecting jurors and rewarding the winning party, is automated by a set of smart contracts.
-As in Themis, the honesty of the agents voting in a case is achieved through game-theoretic economic incentives.
-
-Such a decentralised, voluntary and anonymous dispute resolution system might work for simple breaches of contract, such as an eBay seller sending broken or wrong products, or an Airbnb apartment that does not match the photos in the listing.
-However, it is difficult to implement such a decentralised assessment of the quality of health or legal services when expertise and privacy concerns are taken into account.
-Therefore, our protocol takes a more conservative approach and resolves disputes by recording evidence on the blockchain and then using the local justice system (police or courts) to resolve the conflict.
-
-Possible directions towards a semi-autonomous decentralised resolution system are discussed in Section~\ref{sec:decentralised-justice}.
+\begin{sloppypar}
+Disputes are common in transactions, and systems are needed to make sure rules and laws are followed.
+Traditionally, this involves legal contracts and law enforcement.
+With blockchain technology, smart contracts offer a new way by putting contract details into code and automatically enforcing them~\cite{allenGovernanceBlockchainDispute2019}.
+\end{sloppypar}
+
+A challenge with blockchain is dealing with outside information, which is where \textit{oracles} come in.
+They feed real-world data into the blockchain~\cite{breidenbachChainlinkNextSteps2021}.
+This is important for dispute resolution systems like Themis~\cite{mengThemisDecentralizedEscrow2019} and Kleros~\cite{bergollaKlerosSociolegalCase2022}, which use decentralized networks to make fair decisions.
+However, these systems might struggle with complex disputes that need special knowledge and privacy.
+
+Our protocol takes a more traditional approach.
+It uses blockchain to keep track of evidence but relies on local legal systems (like police or courts) to solve disputes.
+This way, we balance the use of technology with the need for detailed understanding in complicated service disputes.
+We talk more about exploring decentralized, partly automated systems in Section~\ref{sec:decentralised-justice}.
 
 \subsection{Fairness}\label{fairness}
-
-In the event of a dispute, the customer can provide convincing evidence of the customer's honesty and the SP's misbehaviour to the judicial authorities (police or court). 
-Because the customer is anonymous, the SP cannot start a dispute - there is no way to identify the customer.
-
-To mitigate this problem, we have designed the protocol in such a way that the SP who follows the protocol is always in an advantageous position and therefore has no reason to start a dispute.
-On the other hand, the customer can start a dispute at any point in the protocol, but only the actual misbehaviour of the SP will lead to win the case.
-
-Abstracting from the services provided by the SP, each party should be able to prove its honest behaviour in the event of a dispute.
-We propose three pieces of evidence that should be disclosed to the judiciary in the event of a dispute:
+In our protocol, disputes are resolved by providing evidence to judicial authorities (police or courts).
+As the customer remains anonymous, the SP cannot initiate a dispute due to the inability to identify the customer.
+Our protocol is designed to favor the SP who adheres to the protocol, thus removing the need to initiate disputes.
+Conversely, customers can initiate disputes, but only SP misbehavior will result in a successful claim.
+
+We outline three key pieces of evidence for dispute resolution:
 
 \begin{enumerate}
-    \item \textbf{Proof of Delivery ($\textrm{PoD}$)} is a confirmation issued by the SP to the customer proving that the customer has delivered a complete (according to the SP's requirements) package to the SP and that the SP has accepted it.
-The formal definition of $\mathrm{PoD}$ is given in Section~\ref{proof-of-delivery}.
-
-    \item \textbf{Payment $\textrm{receipt}$} is the confirmation that the customer has paid for the transaction at some point in time.
-The actual implementation depends on the cryptocurrency (or cash) and is discussed further in Section~\ref{payment-for-services}.
-
-    \item \textbf{Proof of Provision ($\textrm{PoP}$)} is the proof that the SP has published the result at a given time.
-It protects the SP in the event the customer unjustifiably starts a dispute after the result has been published.
-The formal definition of $\mathrm{PoP}$ is given in Section~\ref{proof-of-provision}.
+    \item \textbf{Proof of Delivery ($\textrm{PoD}$)}: Issued by the SP, this confirms the customer's delivery of a complete package as per SP's requirements.
+The detailed definition is in Section~\ref{proof-of-delivery}.
+
+    \item \textbf{Payment $\textrm{receipt}$}: This confirms the customer's payment for the service.
+Its format varies based on the payment method (cryptocurrency or cash) and is further discussed in Section~\ref{payment-for-services}.
+
+    \item \textbf{Proof of Provision ($\textrm{PoP}$)}: This shows that the SP has published the service result at a specific time, protecting the SP against unjustified disputes by the customer.
+The detailed definition is in Section~\ref{proof-of-provision}.
 \end{enumerate}
@@
 \subsection{Message Board}\label{sec:message-board}
-The term Proof of Provision ($\mathrm{PoP}$) that we have coined for the purposes of this protocol is often referred to as Proof of Existence~\cite{crespoStamperyBlockchainTimestamping2017}.
-
-Its concept is to certify the existence, integrity and ownership of a particular information at a certain point in time (non-repudiation property).
-
-We use this feature for two purposes: (1) to inform the customer about the existence of the results, with whom the SP cannot communicate via any other means, since the customer remains anonymous; (2) to allow the SP to prove the publication of the results within the deadline agreed with the customer.
-
-By publishing the $\mathrm{PoP}$ on the blockchain, the SP cannot falsify the time at which the results were provided, as the block creation time proves it.
-The blockchain acts as a global clock that securely timestamps all data included in the block, so the $\mathrm{PoP}$ included in a block is associated with the time the block was created.
-Also, since the blockchain is public, anyone (including the judiciary) can be convinced that the service provider indeed released the result at that time.
-
-Without such proof, there would be no other way to resolve the conflict between the customer claiming that the results were not published and the SP claiming that the results were published on time.
-
-Depending on the context, the platform for achieving this is called bulletin board~\cite{achenbachImprovedCoercionresistantElectronic2015}, trusted timestamping~\cite{gippDecentralizedTrustedTimestamping2015}, or message board~\cite{hinarejosSolutionSecureCertified2019}.
-In this paper we call it a message board.
-
-We keep the protocol general enough to be implemented using any existing technology to provide a message board service, provided it is decentralised and supports subscribing to upcoming proofs from a given address.
-
-\subsection{Anonymity, pseudonomity, and confidentality}\label{sec:pseudo-anon}
-
-Privacy is a concept used in almost all social sciences such as philosophy, psychology, sociology and law.
-This multidisciplinary nature leads to ambiguous definitions~\cite{smithInformationPrivacyResearch2011}.
-For our work we rely on more concrete definitions, i.e.~confidentiality and anonymity.
-
-Confidentiality is the ability to hide the details of actions from others.
-Alternatively, we can say that the system guarantees confidentiality if, for all observers, all they can say about the action is the fact that it happened and nothing more.
-
-Anonymity is the ability to hide one's identity from others.
-More specifically, it is the inability to correlate actions taken within the system with the identity of the user.
-Alternatively, we can say that the system guarantees anonymity if, for all observers, the actions are equally likely to be associated with any user of the system.
-However, anonymity is a spectrum rather than a dichotomous classification.
-One method of quantifying the level of anonymity is the \textit{k}-anonymity proposed in~\cite{sweeneyKanonymityModelProtecting2002}.
-It measures the user's anonymity by the number of other users from whom the user is indistinguishable.
-Specifically, the user is \textit{k}-anonymous if his actions are equally likely to be associated with \textit{k}-1 other users; the larger the \textit{k}, the greater the anonymity.
-
-Some anonymity techniques can be used on non-anonymous blockchains.
-The so-called mixers gather users into an anonymity set who then collude to launder transactions in such a way that, to an observer, the likelihood of the sender of each transaction being any user from the anonymity set is equiprobable.
-
-Some systems provide pseudonymity rather than anonymity.
-Pseudonymity allows users to hide their real identities behind pseudonyms.
-Although the whole system is transparent and allows actions to be linked to pseudonyms, the system is considered anonymous as long as the link between pseudonyms and real identities is secret.
-This assumption is difficult to meet in practice, as KYC (Know Your Customer) and AML (Anti Money Laundering) regulations require users to reveal their real identities to cryptocurrency exchanges, exposing users' privacy to government agencies, malicious insiders and cyber criminals.
-In addition, some correlations can be inferred simply by analysing transactions~\cite{androulakiEvaluatingUserPrivacy2013, oberStructureAnonymityBitcoin2013}.
-
-Figure~\ref{fig:anonymity-diagram} illustrates the relationships between these terms.
+The platform for issuing and publishing these proofs is a critical aspect of the protocol.
+Referred to by various terms like bulletin board~\cite{achenbachImprovedCoercionresistantElectronic2015}, trusted timestamping~\cite{gippDecentralizedTrustedTimestamping2015}, or message board~\cite{hinarejosSolutionSecureCertified2019}, this platform serves as a decentralized, public ledger that securely timestamps and records each proof.
+By leveraging blockchain technology, the platform ensures that the proofs are tamper-proof and verifiable by any third party, including judicial authorities.
+
+This approach of using a decentralized message board for publishing proofs provides several advantages:
+\begin{itemize}
+    \item It establishes an immutable record of actions and agreements between the anonymous customer and the service provider.
+    \begin{sloppypar}
+    \item It enables transparent verification of the timeline of events, crucial for dispute resolution.
+    \end{sloppypar}
+    \item It offers a universally accessible platform for checking the authenticity and integrity of the transaction-related proofs.
+\end{itemize}
+
+The protocol is designed to be adaptable, allowing for implementation with any decentralized technology capable of providing a message board service and supporting subscription to proofs from specific addresses.
+
+\subsection{Anonymity, Pseudonymity, and Confidentiality}\label{sec:pseudo-anon}
+
+\begin{sloppypar}
+Privacy, a multifaceted concept in social sciences, is often ambiguously defined~\cite{smithInformationPrivacyResearch2011}.
+In our context, we focus on more concrete aspects: confidentiality, anonymity and pseudonymity.
+\end{sloppypar}
+
+\textbf{Confidentiality} refers to the ability to conceal the details of actions within a system.
+A system guarantees confidentiality if observers can only ascertain that an action occurred, without additional information.
+
+\textbf{Anonymity} involves hiding one's identity within a system.
+It's the inability to link actions to a user's identity.
+Anonymity is a spectrum, quantifiable by \textit{k}-anonymity~\cite{sweeneyKanonymityModelProtecting2002}, where a user is \textit{k}-anonymous if their actions are indistinguishable from \textit{k}-1 other users.
+The larger the \textit{k}, the greater the anonymity.
+
+\begin{sloppypar}
+\textbf{Pseudonymity} differs from anonymity.
+Users operate under pseudonyms, and while actions can be linked to these pseudonyms, the system remains anonymous as long as the real identities behind these pseudonyms are concealed.
+However, this assumption is challenging due to KYC (Know Your Customer) and AML (Anti Money Laundering) regulations, which require users to reveal their real identities to cryptocurrency exchanges or other on-ramping services.
+This exposure of users' privacy to government agencies, malicious insiders, and cybercriminals complicates the maintenance of true anonymity and raises concerns about transaction analysis~\cite{androulakiEvaluatingUserPrivacy2013, oberStructureAnonymityBitcoin2013}.
+
+Figure~\ref{fig:anonymity-diagram} illustrates these concepts.
+Alice, wanting anonymity, controls two addresses.
+The first address's link to her identity is compromised, but the second remains anonymous.
+Her actions from these addresses demonstrate the nuances of confidentiality and anonymity.
+\end{sloppypar}
+
+In the realm of blockchain technologies, the concepts of anonymity and confidentiality are achieved through different mechanisms, depending on whether the blockchain is privacy-preserving or not.
+We outline these differences as follows:
+
+\begin{sloppypar}
+\begin{enumerate}
+    \item \textbf{Privacy-Preserving Blockchains:} These blockchains inherently support both anonymity and confidentiality through advanced cryptographic techniques, ensuring that both user identities and transaction details are obscured.
+    \begin{itemize}
+        \item \textbf{Examples:}
+        \begin{itemize}
+            \item \textbf{Monero:} Utilizes Ring Signatures and Bulletproofs~\cite{vansaberhagenCryptoNote2013, noetherRingSignatureConfidential2015, bunzBulletproofsShortProofs2018}.
+            \item \textbf{ZCash:} Employs zkSNARKs for private transactions~\cite{ben-sassonZerocashDecentralizedAnonymous2014}.
+            \item \textbf{Grin} and \textbf{IronFish:} Use Mimblewimble and the Sapling protocol, respectively~\cite{jedusorMIMBLEWIMBLE2016,fuchsbauerAggregateCashSystems2019, hopwoodZcashSaplingProtocol2022, ironfishPrivateAnonymousEasy}.
+        \end{itemize}
+    \end{itemize}
+
+    \item \textbf{Non-privacy-preserving Blockchains:} These blockchains, such as Bitcoin and Ethereum, do not natively support strong privacy features.
+However, anonymity can be enhanced through the use of mixers and other privacy tools.
+    \begin{itemize}
+        \item \textbf{Examples:}
+        \begin{itemize}
+            \item \textbf{Tornado Cash} (Ethereum): Implements zkSNARKs and MiMC for enhanced privacy~\cite{grothSizePairingbasedNoninteractive2016,pertsevTornadoCashPrivacy2019}.
+            \item \textbf{Wasabi Wallet} (Bitcoin): Uses CoinJoin to mix transactions~\cite{maxwellCoinJoinBitcoinPrivacy2013,wasabiwalletBitcoinPrivacyWallet}.
+        \end{itemize}
+    \end{itemize}
+\end{enumerate}
+\end{sloppypar}
 
@@
 \centering
-\caption{Suppose Alice is the customer who wants to keep her identity anonymous and Bob is the public SP.
-Alice controls two addresses 1 and 2; the link between her real identity and the first address has been compromised and therefore identification is possible; the link to the second pseudonym is still unknown and therefore anonymous.
-Alice takes two actions, the first from the compromised address and the second from the anonymous address.
-The first action is confidential; therefore, even though the pseudonym has been compromised, the action cannot be associated with Alice.
-The second action is transparent, so Alice maintains her anonymity as long as the link to the second pseudonym is concealed.}
-
+\caption{Consider a scenario where Alice is an anonymous customer and Bob is a public Service Provider (SP).
+Alice controls two addresses, labeled 1 and 2.
+The link (represented by a red line) between Alice's real identity and address 1 has been compromised, making identification possible.
+However, the link to address 2 remains unknown, preserving anonymity.
+Alice performs two actions, A and B.
+Action A originates from the compromised address 1, while action B is from the anonymous address 2.
+Action A is confidential, meaning that despite the compromised pseudonym, the nature of the action remains undisclosed.
+Action B is transparent, but it cannot be linked to Alice as long as the connection to pseudonym 2 remains hidden.}
 \label{fig:anonymity-diagram}
 \end{figure}
-The privacy-preserving blockchains are those that maintain anonymity through untraceability and (ideally) unlikability - not by assuming that the link between an address (pseudonym) and real identity is hidden.
-
-Examples of blockchains that natively support confidential transactions include Monero~\cite{vansaberhagenCryptoNote2013} (using Ring Signatures~\cite{noetherRingSignatureConfidential2015} or Bulletproofs~\cite{bunzBulletproofsShortProofs2018}), ZCash~\cite{ben-sassonZerocashDecentralizedAnonymous2014} (using zkSNARK~\cite{ben-sassonSNARKsVerifyingProgram2013}), Grin~\cite{fuchsbauerAggregateCashSystems2019} (using Mimblewimble~\cite{jedusorMIMBLEWIMBLE2016}), and IronFish~\cite{ironfishPrivateAnonymousEasy} (using Sapling protocol~\cite{hopwoodZcashSaplingProtocol2022}).
-
-Overly techniques that achieve anonymity on top of non-privacy preserving blockchains are Ethereum's Tornado Cash~\cite{pertsevTornadoCashPrivacy2019} (via zkSNARK~\cite{grothSizePairingbasedNoninteractive2016} and MiMC~\cite{albrechtMiMCEfficientEncryption2016}), Bitcoin's Wasabi~\cite{wasabiwalletBitcoinPrivacyWallet} (via CoinJoin~\cite{maxwellCoinJoinBitcoinPrivacy2013}).
-
-\subsection{Payment for services}\label{payment-for-services}
-Transactions between customers and SPs need to be linked to prevent the reuse of a payment for multiple transactions.
-In other words, we need a mechanism that uniquely links the payment to the corresponding transaction.
-
-Depending on the cryptocurrency, this link can be established in different ways:
-
-\begin{itemize}
-\item separate address: each transaction uses a unique address associated with the transaction.
-Such addresses can be derived using Hierarchical Deterministic Wallets~\cite{wuilleBIP32HierarchicalDeterministic2012} and published on the message board to achieve non-repudiation.
-\item memo: payments are sent to a single SP account, but contain an extra field called ``memo'' filled with the unique identifier $\textrm{provisionID}$. 
-\end{itemize}
-
-Any payment that contains $\textrm{provisionID}$ in the memo or is sent to the designated address will be considered payment for the transaction.
-
-In the event of a dispute, there must be a way to prove to the courts that the customer has paid for the transaction.
-As proof of payment is trivial in transparent and traceable blockchains, it becomes more complicated when it comes to anonymous blockchains.
-Monero allows payments to be proven and verified via a dedicated API~\cite{moneroHowProvePayment}.
-ZCash provides a mechanism called Payment Disclosure~\cite{daviesIntroductionPaymentDisclosure2017}.
-We call the proof of payment a \textit{payment recepit}.
-
-\subsection{Storage network}\label{storage-network}
-Once the SP has completed its service, it needs to deliver the result to the customer.
-The most natural approach would be to send the result via email or a dedicated platform.
-However, the customer wants to remain anonymous and does not want to reveal his email address or IP address.
-Furthermore, the SP needs to prove that the result was delivered before the deadline, which brings us to the issue of proof of existence discussed in Section~\ref{sec:message-board}.
-
-One approach would be to post the result to a blockchain.
-However, storing data on a blockchain is very expensive.
-The most common workaround (\cite{shahidBlockchainBasedAgriFoodSupply2020, wangAuditableProtocolsFair2019, chenImprovedP2PFile2017}) is to publish the data on a content addressable peer-to-peer storage network such as IPFS~\cite{benetIPFSContentAddressed2014}.
-Then publish only the content identifier ($\mathrm{cid}$) on the blockchain, which uniquely points to the content stored on IPFS.
-
-We follow the same approach. Once the SP has produced the result, it encrypts it using the previously provided encryption key and uploads it to the IPFS network.
-
-We also use Filecoin to guarantee that the results are available to the customer even if the SP refuses to share the result (see Section ~\ref{sec:provable-results-availability}).
-
-To increase anonymity, the customer should use standard techniques to hide their IP address, such as VPN or proxy.
-
-\subsection{Separation of concerns}
-We could use a single blockchain to achieve all three of these roles: i) anonymous payments, ii) message board, and iii) storage network.
-
-While most blockchains could provide message board functionality, anonymous payments are not as common. In particular, a verifiable storage network is a feature of a few specialised blockchains.
-
-Rather than searching for a single blockchain to provide all functionalities, we allow the protocol to use separate blockchains for each role.
-If a suitable blockchain emerges, it can play more than one role.
-
-At the time of writing, we see the following technologies fulfilling the requirements of each role:
+
+\subsection{Payment for Services}\label{payment-for-services}
+
+\begin{sloppypar}
+In transactions between customers and service providers (SPs), it is crucial to establish a unique link between the payment and the corresponding transaction to prevent the reuse of a payment for multiple transactions.
+This link can be established in various ways depending on the cryptocurrency used:
+\end{sloppypar}
+
+\begin{sloppypar}
+\begin{itemize}
+    \item \textbf{Separate Address:} Each transaction utilizes a unique address associated with it.
+These addresses can be generated using Hierarchical Deterministic Wallets~\cite{wuilleBIP32HierarchicalDeterministic2012} and published on the message board to ensure non-repudiation.
+    \item \textbf{Memo:} Payments are sent to a single SP account but include an extra field called ``memo,'' filled with the unique identifier $\textrm{provisionID}$.
+\end{itemize}
+\end{sloppypar}
+
+Any payment that contains $\textrm{provisionID}$ in the memo or is sent to the designated address is recognized as payment for the transaction.
+
+\begin{sloppypar}
+In the event of a dispute, it is necessary to demonstrate to the courts that the customer has paid for the transaction.
+While proving payment is straightforward in transparent and traceable blockchains, it becomes more complex in anonymous blockchains.
+Monero, for instance, allows payments to be proven and verified through a dedicated API~\cite{moneroHowProvePayment}, and ZCash offers a mechanism known as Payment Disclosure~\cite{daviesIntroductionPaymentDisclosure2017}.
+We refer to this proof of payment as a \textit{payment receipt}.
+\end{sloppypar}
+
+\subsection{Storage Network}\label{storage-network}
+
+Upon completing its service, the service provider (SP) faces the challenge of delivering the result to the customer while maintaining the customer's anonymity.
+The customer, wishing to remain anonymous, cannot reveal their email address or IP address.
+Additionally, the SP must prove that the result was delivered before a specified deadline, aligning with the concept of proof of existence discussed in Section~\ref{sec:message-board}.
+
+\begin{sloppypar}
+A common solution is to utilize a content addressable peer-to-peer storage network for data storage, as direct blockchain storage is prohibitively expensive.
+This approach is widely adopted in various applications~\cite{shahidBlockchainBasedAgriFoodSupply2020, wangAuditableProtocolsFair2019, chenImprovedP2PFile2017}.
+Specifically, data is stored on a network like IPFS~\cite{benetIPFSContentAddressed2014}, and only the content identifier ($\mathrm{cid}$) that uniquely points to the content on IPFS is published on the blockchain.
+\end{sloppypar}
+
+Following this methodology, the SP encrypts the result using the encryption key provided by the customer and uploads it to the IPFS network.
+To ensure the availability of the results, even in cases where the SP is unwilling to share them, we incorporate Filecoin as detailed in Section~\ref{sec:provable-results-availability}.
+
+To further enhance anonymity, customers are advised to use standard techniques such as VPNs or proxies to conceal their IP addresses.
+
+\subsection{Separation of Concerns}\label{sec:separation-of-concerns}
+
+\begin{sloppypar}
+The protocol we propose could potentially utilize a single blockchain to fulfill three distinct roles: (i) facilitating anonymous payments, (ii) serving as a message board, and (iii) acting as a storage network.
+However, while most blockchains can provide message board functionality, anonymous payments and a verifiable storage network are less common features, often limited to specialized blockchains.
+
+Instead of relying on a single blockchain to provide all functionalities, our protocol is designed to be flexible, allowing the use of separate blockchains for each specific role.
+This approach provides the freedom to choose the best technology available for each function.
+In the future, if a blockchain emerges that can efficiently handle multiple roles, it can be integrated into the protocol.
+
+As of the current state of blockchain technology, we identify the following platforms as suitable candidates for each role:
 
 \begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-
-\item Anonymous payments: Monero \cite{vansaberhagenCryptoNote2013}, ZCash
-  \cite{ben-sassonZerocashDecentralizedAnonymous2014}, Grin \cite{fuchsbauerAggregateCashSystems2019},
-  Tornado Cash \cite{pertsevTornadoCashPrivacy2019}.
-\item Message board: Open timestamps~\cite{opentimestampsTimestampingProofStandard}, Stampery \cite{crespoStamperyBlockchainTimestamping2017}, Bitcoin blockchain (Proof of Existence~\cite{proofofexistenceWebApplicationProve}, Chainpoint~\cite{chainpointBlockchainProofAnchoring}), Ethereum blockchain, or any other public blockchain that supports attaching extra data along the transaction.
-\item Storage network: IPFS~\cite{benetIPFSContentAddressed2014}, Filecoin~\cite{protocollabsFilecoinDecentralizedStorage2017}, or Ethereum's
-  Swarm~\cite{teamSWARMStorageCommunication2021}.
+    \item \textbf{Anonymous Payments:} Technologies such as Monero~\cite{vansaberhagenCryptoNote2013}, ZCash~\cite{ben-sassonZerocashDecentralizedAnonymous2014}, Grin~\cite{fuchsbauerAggregateCashSystems2019}, and Tornado Cash~\cite{pertsevTornadoCashPrivacy2019} offer robust solutions for anonymous transactions.
+    \item \textbf{Message Board:} Various platforms can be utilized for this purpose, including Open timestamps~\cite{opentimestampsTimestampingProofStandard}, Stampery~\cite{crespoStamperyBlockchainTimestamping2017}, and the Bitcoin blockchain with services like Proof of Existence~\cite{proofofexistenceWebApplicationProve} and Chainpoint~\cite{chainpointBlockchainProofAnchoring}.
+The Ethereum blockchain, along with other public blockchains that support attaching extra data to transactions, are also viable options.
+    \item \textbf{Storage Network:} For decentralized storage solutions, IPFS~\cite{benetIPFSContentAddressed2014}, Filecoin~\cite{protocollabsFilecoinDecentralizedStorage2017}, and Ethereum's Swarm~\cite{teamSWARMStorageCommunication2021} are among the leading technologies.
 \end{enumerate}
+\end{sloppypar}
 
@@
 
+\begin{sloppypar}
 This protocol framework sets the stage for a secure, anonymous, and fair service provisioning system.
 It balances the needs for privacy and accountability, ensuring that both the customer and the SP can engage in transactions with confidence in the system's integrity and fairness.
+\end{sloppypar}
 
@@
 \noindent \textbf{Package}\label{package} is a physical container prepared by the customer containing all the $\mathrm{materials}$ required by the SP to provide the service.
-
-$$\mathrm{pkg} \equiv (\mathrm{materials}, \mathrm{provisionID}, \mathrm{pk_C})$$
-
+\[\mathrm{pkg} \equiv (\mathrm{materials}, \mathrm{provisionID}, \mathrm{pk_C})\]
 where:
@@
 It is also an agreement between the customer and the SP as it contains agreed deadlines for actions and a payment method.
-
-\begin{eqnarray}
+\begin{eqnarray*}
 \mathrm{PoD} & \equiv & (\begin{array}[t]{l}\mathrm{pk_C}, \mathrm{provisionID},   \mathrm{paymentAddress},
@@
 \mathrm{T}_\mathrm{issue}, \mathrm{T}_\mathrm{pay}, \mathrm{T}_\mathrm{provide}\; )\end{array}
-\end{eqnarray}
-
+\end{eqnarray*}
 where:
@@
 \item $\mathrm{provisionID}$ - Unique transaction identifier.
+\item $\mathrm{paymentAddress}$ - SP's anonymous payment address.
 \item $\mathrm{sig}_\mathrm{SP}$ - SP's digital signature.
-\item $\mathrm{paymentAddress}$ - SP's anonymous payment address.
 \item $\mathrm{T}_\mathrm{issue}$ - Time of $\mathrm{PoD}$ issuance.
 \item $\mathrm{T}_\mathrm{pay}$ - Payment deadline.
-\item $\mathrm{T}_\mathrm{provide}$ - Deadline for service provision, i.e. to publish $\mathrm{PoP}$.
+\item $\mathrm{T}_\mathrm{provide}$ - Service provision deadline.
 \end{itemize}
@@
 The link between $\mathrm{PoP}$ and the results is made by the content identifier ($\mathrm{cid}$), which uniquely identifies the results so that the result cannot be forged after the $\mathrm{PoP}$ has been published.
-
-\begin{eqnarray}
+\begin{eqnarray*}
 \mathrm{PoP} & \equiv & (\mathrm{cid}, \mathrm{provisionID}, \mathrm{sig}_\mathrm{SP})
-\end{eqnarray}
+\end{eqnarray*}
 
@@
 
+\begin{sloppypar}
 \noindent \textbf{Results}\label{results} are typically in PDF format, but any binary-encodable format acceptable for the storage network can be used, symbolically referred to as $\mathrm{results}$.
+\end{sloppypar}
 
@@
 
+\begin{sloppypar}
 Consequently, our analysis must account for four potential outcomes for each party at every protocol step ($\mathrm{party \in \{C, SP}\}$, $\mathrm{step \in 1..9}$):
+\end{sloppypar}
 
@@
 
-\subsection*{Setup, Preparation, and Experiment}
-
 Our protocol's prototype was developed using a suite of technologies designed to ensure anonymity and security:
@@
 \begin{itemize}
+\begin{sloppypar}
   \item \textbf{Anonymous Payments:} Utilization of the Monero blockchain for secure transactions.
+\end{sloppypar}
   \item \textbf{Storage Network:} Powergate serves as an interface for Filecoin and IPFS, facilitating decentralized storage.
@@
 
+\begin{sloppypar}
 In preparation for the experiment, both the customer and the SP set up their Monero wallets using the \texttt{monero-wallet-cli}.
 The SP deploys the smart contract to the Ethereum blockchain with the \texttt{truffle migrate --network development} command, and the web application is then configured to interact with this newly deployed contract.
+\end{sloppypar}
 
@@
 \begin{enumerate}
-  \item The customer begins by creating a new provision in the webapp, which generates a unique ECDSA keypair and provisionID.
+  \setcounter{enumi}{-1}
+  \item \textbf{Setup:} The customer begins by creating a new provision in the webapp, which generates a unique ECDSA keypair and provisionID.
 The corresponding QR code is printed and attached to the parcel for delivery.
 
-  \item The parcel is delivered to the SP through a chosen delivery method, such as a secure drop box or locker service.
-
-  \item Upon receipt, the SP scans the QR code to retrieve the provisionID and customer's public key.
-
-  \item Since (in this experiment) the provision was not paid in cash, the SP generates a unique Monero payment address using \texttt{monero-wallet-cli integrated\_address}.
-
-  \item The SP submits the PoD to the Ethereum blockchain using the MetaMask interface.
-
-    \item The customer checks the transaction status on the Ethereum blockchain by calling \texttt{getProvision} with arguments \texttt{customerPubKey} and \texttt{provisionID}
-
-    \item The customer sends the payment (using \texttt{monero-wallet-cli transfer}) to the \texttt{paymentAddress} specified in the smart contract and stores the payment receipt using \texttt{monero-wallet-cli get\_tex\_key <tx-id>}.
-
-    \item Upon payment confirmation, the SP provides the service, resulting in a \texttt{result.pdf} file.
-
-  \item This file is uploaded to IPFS and Filecoin, granting the SP a \texttt{cid}, \texttt{dealID}, and \texttt{minerID}.
-
-  \item A PoP is submitted to the Ethereum blockchain by the SP.
-
-    \item Meanwhile, the customer subscribes to Ethereum and waits for the SP to publish the PoP.
-Upon noticing the PoP, the customer retrieves the result using either one of the public gateways\footnote{IPFS Public Gateway Checker, \url{https://ipfs.github.io/public-gateway-checker/}, (last visited Jan.
+  \item  \textbf{Package Delivery:}  The parcel is delivered to the SP through a chosen delivery method, such as a secure drop box or locker service.
+Upon receipt, the SP scans the QR code to retrieve the provisionID and customer's public key.
+Since (in this experiment) the provision was not paid in cash, the SP generates a unique Monero payment address using \texttt{monero-wallet-cli integrated\_address}.
+As a result, the PoD is prepared.
+
+  \item \textbf{Proof of Delivery:} Then, the SP submits the PoD to the Ethereum blockchain using the MetaMask interface.
+
+    \item \textbf{Get Proof of Delivery:} The customer checks the transaction status on the Ethereum blockchain by calling \texttt{getProvision} with arguments \texttt{customerPubKey} and \texttt{provisionID}
+
+    \begin{sloppypar}
+    \item \textbf{Payment:} The customer sends the payment (using \texttt{monero-wallet-cli transfer}) to the \texttt{paymentAddress} specified in the smart contract and stores the payment receipt using \texttt{monero-wallet-cli get\_tex\_key <tx-id>}.
+    \end{sloppypar}
+
+    \item \textbf{Provision of Service:} Upon payment confirmation, the SP provides the service, resulting in a \texttt{result.pdf} file.
+
+  \item \textbf{Upload result:} This file is uploaded to IPFS and Filecoin, granting the SP a \texttt{cid}, \texttt{dealID}, and \texttt{minerID}.
+
+  \item \textbf{Proof of Provision:} A PoP is submitted to the Ethereum blockchain by the SP.
+
+    \item \textbf{Get Proof of Provision:} Meanwhile, the customer subscribes to Ethereum and waits for the SP to publish the PoP.
+
+  \item \textbf{Download result:} Upon noticing the PoP, the customer retrieves the result using either one of the public gateways\footnote{IPFS Public Gateway Checker, \url{https://ipfs.github.io/public-gateway-checker/}, (last visited Jan.
 04, 2023)} like \url{https://cf-ipfs.com/ipfs/<cid>} or Lotus network using \texttt{lotus} \texttt{retrieve} \texttt{<cid>} \texttt{<minerID>}.
-
-  \item The results are then decrypted using the customer's previously stored private key.
+The result is then decrypted using the customer's previously stored private key.
 If the customer is satisfied with the service the protocol ends; otherwise, the customer may initiate a dispute process.
@@
 \paragraph{Anonymity}
+\begin{sloppypar}
 Anonymity was secured by breaking the link between personal data and transactional elements, including materials, payments, and communications.
@@
 This approach guaranteed that customer interactions with the protocol remained confidential at every stage.
+\end{sloppypar}
 
@@
 The incurred costs were as follows:
-
+\begin{sloppypar}
 \begin{itemize}
@@
 \end{itemize}
+\end{sloppypar}
 
@@
 \subsection{Dispute Resolution Service}\label{sec:decentralised-justice}
+
+\begin{sloppypar}
 The central challenge in achieving a Web3-compliant system lies in the centralization of dispute resolution services~\cite{ethereumWhatWeb3Why2023}.
 To address this, we consider two potential solutions: the integration of blockchain-based dispute resolution systems and the development of mechanisms to ensure the infeasibility of incorrect service provision.
+\end{sloppypar}
 
@@
 
+\begin{sloppypar}
 Through rigorous definition and analysis, we have demonstrated that our protocol meets the criteria for fairness, as outlined in Definition~\ref{def:fairness}.
 It does so by systematically publishing proofs of delivery, payment, and provisioning, ensuring a transparent and equitable process for all parties involved.
+\end{sloppypar}
 
@@
 
+\begin{sloppypar}
 \section{Proof of fairness}\label{app:proof-of-fairness}
@@
 
+\end{sloppypar}
+
 \bibliographystyle{spbasic}
-\bibliography{bibliography}
-
+\bibliography{bibliography-betterbibtex}
 \end{document}

### 2023-11-28 paper/pre-revision.tex
add pre-revision paper

\documentclass[pdftex,twocolumn,epjc3]{svjour3} 
\RequirePackage[T1]{fontenc}
\smartqed  % flush right qed marks, e.g. at end of proof
\RequirePackage{graphicx}
\RequirePackage{mathptmx}      % use Times fonts if available on your TeX system
\RequirePackage{flushend}
\RequirePackage[numbers,sort&compress]{natbib}
\RequirePackage[colorlinks,citecolor=blue,urlcolor=blue,linkcolor=blue]{hyperref}

\journalname{Eur. Phys. J. C}

\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{float}
\usepackage{etoolbox}

\usepackage{url}
\usepackage{listings}
\usepackage{pdfpages}
\usepackage[english]{babel}
\usepackage{xcolor,colortbl}
\usepackage{scalerel}

\newcommand{\customer}{customer}
\renewcommand{\sp}{SP}

\newcommand{\normal}{n}
\newcommand{\dispute}{d}
\newcommand{\abnormal}{\overline{n}}
\newcommand{\abdispute}{\overline{d}}

\newcommand{\PoD}{$\mathrm{PoD}$}
\newcommand{\PoP}{$\mathrm{PoP}$}
\newcommand{\cid}{$\mathrm{cid}$}

\newcommand{\floor}[1]{\left\lfloor #1 \right\rfloor}
\newcommand{\ceil}[1]{\left\lceil #1 \right\rceil}

\newcommand{\plus}{+}
\newcommand{\minus}{-}
\newcommand\neutral[1][.75]{\mathbin{\ThisStyle{\vcenter{\hbox{%
  \scalebox{#1}{$\SavedStyle\bullet$}}}}}%
}

\def\SINGLECOLUMN{SINGLE}
\def\DOUBLECOLUMN{DOUBLE}
\def\JOURNALIEEE{IEEE}
\def\JOURNALELS{ELS}

\newcommand\TITLE{Anonymous provision of privacy-sensitive services using blockchain and decentralised storage}
\newcommand\STANLONG{Stanis\l{}aw Bara{\'n}ski}
\newcommand\JULLONG{Julian Szyma{\'n}ski}
\newcommand\HIGILONG{Higinio Mora}
\newcommand\STAN{S. Bara{\'n}ski}
\newcommand\JUL{J. Szyma{\'n}ski}
\newcommand\HIGI{H. Mora}

\newcommand\ABSTRACT{
Lawyers, laboratories, auditors or banks often need data containing sensitive personal information to provide their services. Examples of sensitive services include genetic testing, paternity testing, STD testing, credit scoring or legal advice.

The processing of personal data, especially when providing services involving sensitive data such as health records, biological material or legal documents, exposes both users and service providers (SPs) to privacy risks. SPs are at risk of violating GDPR, CPAA and other legal regulations, while customers are at risk of losing their privacy.

We observe that personal data is often only used for logistical purposes, such as payment or communication, and could be provided anonymously if such methods were available.

We present a solution that allows services to be provided without collecting personal data. We use anonymous payment methods such as cash and anonymous cryptocurrencies, blockchain to achieve fairness, and distributed content-addressable storage networks to deliver results.

Compared to other solutions, our protocol achieves anonymity with weaker assumptions, supports physical materials and conflict resolution, and does not require the customer to interact with the blockchain in conflict-free transactions, demonstrating better practicality.

In this work, we analyse the fairness of our protocol and implement it using Ethereum technology as a message board, Monero as an anonymous payment method, and Powergate (IPFS and Filecoin) as a decentralised storage network.
}

\newcommand\ACKNOWLEDGEMENTS{
The work has been supported partially by the founds of Department of Computer Architecture Faculty of Electronics, Telecommunications and Informatics, Gdańsk University of Technology.
}

\newcommand\LASTVISITED{(last visited Jan. 31, 2023)}

\begin{document}

\title{\TITLE}

\author{\STANLONG\thanksref{e1,addr1}
        \and \JULLONG{}\thanksref{e2,addr1}
        \and \HIGILONG{}\thanksref{e3,addr2}
}

\thankstext{e1}{e-mail: stanislaw.baranski@pg.edu.pl}
\thankstext{e2}{e-mail: julian.szymanski@pg.edu.pl}
\thankstext{e3}{e-mail: hmora@ua.es}

\institute{Department of Electronic, Telecommunication and Informatics, Gdansk University of Technology, Narutowicza 11/12 80-233 Gdansk Poland\label{addr1}
          \and
          Department of Computer Science Technology and Computation, University of Alicante, San Vicente del Raspeig, 03690 Alicante Spain \label{addr2}
}

\date{Received: date / Accepted: date}
% The correct dates will be entered by the editor

\maketitle

\begin{abstract}
  \ABSTRACT{}

  \newcommand{\sep}{ \and }
  \keywords{Anonymity\sep{} blockchain\sep{} diagnosis\sep{} e-commerce\sep{} fair-exchange\sep{} privacy\sep{} services}
\end{abstract}

\section{Introduction}
\label{sec:introduction}
Diagnostic services such as paternity tests, doping tests or venereal disease tests are carried out in diagnostic centres that require clients to provide biological material such as blood, urine, stool or saliva. Unfortunately, clients are often forced to reveal their identity in order to complete transactions. Such a combination of personal information with biological materials exposes clients to significant privacy risks.

Other examples of sensitive services include anonymous complaints or legal services, such as legal advice, which may require disclosure of financial transaction history and confidential legal documents. Banking services, such as credit scoring, may require sensitive personal information, such as medical records and financial transaction history.

Providing personal information exposes users to privacy risks, i.e. the potential loss of control over personal information \cite{smithInformationPrivacyResearch2011}.

Such personal information can be used deliberately or by accident (e.g. theft) for insider disclosure, unauthorised access or commercial gain. For example, by reselling it to marketers, financial institutions, other businesses, government agencies or even cybercriminals. 
This, in turn, can lead to unintentional GDPR or CCPA breaches, profiled advertising, or even criminal activity such as identity theft or illegal tracking and surveillance~\cite{smithInformationPrivacyResearch2011}.

Public figures such as influencers, politicians or celebrities are particularly vulnerable to this type of attack, as exposure of their health records, purchasing habits or legal documents can threaten their reputation, position or be used for blackmail.

The problem is compounded when personal information is linked to health records, legal documents or biological materials such as DNA, saliva or blood.
In such situations, clients may be reluctant to provide their personal information to the SP and therefore withdraw from the service. Both parties are harmed as the client does not receive a diagnosis relevant to their health and the SP loses potential clients.

The guarantee of privacy of personal data is often based solely on trust in the SP's staff and the security of their IT systems. However, we observe that personal data is often used only for logistical purposes, such as payment or communication, and could be provided anonymously if such methods were available.

It would be desirable for customers to keep their identity private while still receiving the service. This could lead to a reduction in the trust that customers need to place in SPs and a reduction in the responsibility that SPs bear.

Examples of services that would benefit from the anonymity property are:
\begin{itemize}
    \item Patients who are willing to take a test, e.g. for drugs, STDs, paternity or steroids, have a strong incentive to keep the whole process private. The mere fact that they have taken the test—without revealing the result—is suggestive enough to be used as a premise in the event of a conflict.

    Currently, they have to take the risk that their personal data, materials and results will be stored securely and kept secret from any unauthorised actor (both curious employees and malicious attackers).

\item Individuals engaged in entrepreneurial activities may want to assess the risks and possible consequences of their actions.

By revealing their identity, they trust that the lawyer will not use this information for harmful actions.
\end{itemize}

Using Solove's Taxonomy of Privacy~\cite{soloveTaxonomyPrivacy2006}, our protocol aims to prevent the following privacy risks:
\begin{itemize}
    \item \textbf{Breach of confidentiality}, breaking a promise to keep an individual's information confidential;
    \item \textbf{Disclosure}, revealing true information about a person that affects the way others judge their character;
    \item \textbf{Identification}, linking information to a specific individual;
    \item \textbf{Secondary use}, using personal information for a purpose other than that for which they were collected.
\end{itemize}

We consider the following adversaries:
\begin{itemize}
    \item \textbf{Malicious insiders}: Individuals or entities with authorised access to the protocol's systems or data who may abuse their privileges to compromise customer privacy. This could include employees, contractors or service providers;
    \item \textbf{Government agencies}: Depending on the jurisdiction and the nature of the protocol, government agencies may have legal powers or national security interests that could affect customer privacy. For example, the potential for surveillance, data requests or legal intervention;
    \item \textbf{Malicious third-party services}: If the protocol relies on third party services or APIs, the privacy of customer data could be at risk if these services have inadequate security measures in place or if they engage in data sharing or tracking without the consent of the customer;
    \item \textbf{Hackers and cybercriminals}: Individuals or organised groups with malicious intent who may exploit vulnerabilities in the protocol's implementation, infrastructure, or supporting systems to gain unauthorised access to customer information.
\end{itemize}

In this work we explore the possibilities of anonymous service provision and propose a protocol that preserves customer privacy even in the event of a successful attack. Under realistic operational assumptions, we believe that decoupling personal information from materials, payment and communication achieves a sufficient level of anonymity.

However, a protocol that hides a customer's identity is difficult to secure and coordinate. In particular, conflicts between customers and service providers are difficult to resolve when there is no one to accuse.

We observe that the problem of anonymous service provision can be seen as a problem of fair exchange, where parties exchange some goods fairly, i.e. either both parties obtain the goods, or they both obtain nothing.

In our case, the customer who wants to use the service exchanges his materials and money with the SP for the result of the service.

Our review shows that none of the current systems is sufficient to achieve the desired goal. We propose an anonymous protocol for the provision of services that require physical materials. In the event of a dispute, either due to missed deadlines or incorrect results, the customer can disclose the entire interaction, prove the SP's misbehaviour to the Dispute Resolution Service, and win the dispute.

To achieve this goal we use
\begin{itemize}
    \item \textbf{Blockchain}, to achieve fairness, i.e. as a means of proving that certain actions took place at a certain time without the Trusted Third Party (TTP).
    \item \textbf{Anonymous payment methods}, such as cash or anonymous cryptocurrencies, which allow customers to pay for services anonymously.
\item \textbf{Decentralised storage network} (e.g. IPFS) to provide results together with a provable storage network (e.g. Filecoin) to guarantee that the results are available to the customer even if the SP refuses to share the result.

    \item Cryptography:
    \begin{itemize}
        \item \textbf{Symmetric encryption}, to encrypt and decrypt the results published on the public networks.
        \item \textbf{Diffie-Helman key exchange (DHKE)}, to derive shared secrets for symmetric encryption.
        \item \textbf{Digital signatures}, to achieve authentication and non-repudiation of actions. 
    \end{itemize}

\end{itemize}

Figure~\ref{fig:protocol-overview} shows a simplified diagram of the protocol.

\begin{figure}[h!]
\includegraphics[width=\linewidth]{protocol-overview.pdf}
\centering
\caption{A simplified diagram of the protocol. The first step involves the delivery of the materials to the SP. The second step involves anonymous payment. The third step involves the delivery of the results to the customer. Each step is proven on the message board, protecting the fair party in a conflict situation.}

\label{fig:protocol-overview}
\end{figure}

\paragraph{}
The contribution of our paper is:
\begin{itemize}
\item we propose a protocol that upon a realistic operational and threat model:
  \begin{itemize}
  \item allows \textbf{anonymous} service provision involving \textbf{physical materials}, i.e., the service provider does not need to collect any personal information from the customer;
  \item achieves \textbf{fairness} by the use of blockchain and cryptographic proofs. We model the protocol as an interactive non-cooperative game and show fairness at each of its steps.
  \item \textbf{does not rely on a centralised TTP}, but uses a decentralised blockchain and a distributed content-addressable storage network;
  \item in conflict-free transactions does not require customers to interact with the blockchain, achieving better \textbf{user experience and practicality};
  \item guarantees the \textbf{remote availability of the results}, even in case of the SP denial of service.
  \end{itemize} 
\item We implement a working prototype of the protocol and provide open source code.
\item We systematise often misused definitions of anonymity, pseudonymity, linkability and traceability.
\item We propose a framework for analysing fairness in fair exchange protocols and use it to prove the fairness of our protocol.
\item We discuss possible improvements to the protocol using secure computation, self-sovereign identities, zero-knowledge proofs, and blockchain-based dispute resolution techniques.
\end{itemize}

Some authors have proposed blockchain-based fair exchange systems that could be adapted to service provision; however, to the best of our knowledge, we are the first to propose a system that satisfies all of the above properties. In particular, anonymity and physical delivery have rarely been addressed together, and if so, the protocol was based on TTP and impractical assumptions about the banking system~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} or did not address the conflict between parties~\cite{altawyLelantosBlockchainBasedAnonymous2017}.

The rest of this paper is organised as follows.
In Section~\ref{sec:related-works} we review related works. 
Then in Section~\ref{sec:building-blocks} we discuss the building blocks of a dispute resolution system, blockchain as a message board, fairness, anonymous payments, storage network, availability of results and anonymity.
Section~\ref{sec:protocol} provides a detailed description of the protocol.
Section~\ref{sec:fairness-analysis} provides a fairness analysis of the proposed protocol.
Section~\ref{sec:experiments} presents the implementation of the protocol and the results of our experiments.
Section~\ref{sec:discussion} discusses possible improvements in terms of crowdsourced dispute resolution or dispute avoidance, self-sovereign identities (SSIs), anonymous delivery, and formal verification.
Finally, Section~\ref{sec:conclusion} concludes the paper.

\section{Related Works}\label{sec:related-works}
In this section, we review related works on fair exchange, anonymous, and physical delivery protocols. Then we outline the main differences between the protocols.

\subsection{Fair exchange, physical delivery}
The most common application of fair exchange protocols is e-commerce. A typical transaction involves a seller and a buyer exchanging money for a physical product. To protect themselves, the seller wants to receive the funds before sending the product, while the buyer wants to receive the product before paying. The fairness of the protocol should guarantee that either both parties obtain the goods, or they both obtain nothing.

To the best of our knowledge, the first system allowing fair exchange of physical products was proposed by Zhang et al. in 2006~\cite{zhangPracticalFairExchangeEPayment2006}. The protocol uses the buyer's bank as the TTP and assumes no coalition between the parties to achieve anonymity.

The authors of~\cite{mohammedalarajFairnessPhysicalProducts2012} proposed a protocol for fair exchange involving the delivery of physical materials. The protocol assumes the existence of an offline~\footnote{\textit{Offline} (also called \textit{optimistic}) TTP compared to \textit{online} TTP which assumes the TTP is only involved in the case of a dispute between parties~\cite{rayFairExchangeEcommerce2002}.} TTP only gets involved in the event of a dispute. The protocol works as follows 
\begin{enumerate}
\item The buyer sends an encrypted payment to the seller along with proof of validity.
\item The seller validates the proof, which convinces him that the decrypted payment is also valid.
\item The seller forwards the physical product to the trusted Delivery Agent (DA).
\item The buyer verifies that the product is the one ordered.
\item The buyer creates a proof of delivery and sends it to the seller along with the decryption key.
\end{enumerate}

However, the protocol relies on strong assumptions, namely the existence of a TTP and a DA that do not misbehave or collude with either party. Fairness is also achieved by assuming resilient communication channels.

\subsection{Fair exchange, anonymity, dispute resolution, and physical products delivery} 
\label{anonymity-and-fair-exchange-in-e-commerce-protocol-for-physical-products-delivery}

In the previous protocol, both parties of the transaction are known to each other. However, there are situations in which the buyer would prefer not to disclose his identity to the seller. The situation becomes more challenging when the transaction involves physical products.
In the previous protocol, both parties to the transaction are known to each other. However, there are situations where the buyer would prefer not to reveal his identity to the seller. The situation becomes more difficult when the transaction involves physical products.

The authors of~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} proposed a protocol for physical products that guarantees the anonymity of both buyer and seller. They achieve this by introducing an online TTP that validates coins and guarantees fairness. Later they proposed many extensions to the protocol, namely in~\cite{birjoveanuPreservingAnonymityFair2018} they proposed an anonymous e-commerce protocol that governs complex transactions, in~\cite{birjoveanuAnonymityComplexTransactions2019} they extend anonymity for both buyers and sellers (in our case SPs), and in~\cite{birjoveanuFairExchangeECommerce2020} they proposed a protocol that supports chained transactions (involving multiple active intermediaries). Finally, in~\cite{birjoveanuTwoPartyECommerceProtocols2022} they proposed an improved protocol called PPPDCP (Protocol with Physical Product Delivery Providing Customer's Privacy).

Anonymity is ensured by using an anonymous communication channel over Tor~\cite{dingledineTorSecondGenerationOnion2004} and blind signatures~\cite{chaumSecurityIdentificationTransaction1985}. Fair exchange, physical delivery and dispute resolution are achieved using a Delivery Cabinet (DC) under the control of the seller (e.g. Amazon Locker) and an offline TTP that only intervenes in the event of a dispute.

The protocol works as follows

\begin{enumerate}
    \item The buyer buys a digital coin from their bank. A blind signature is used to ensure privacy.
    \item The buyer sends the seller the purchase details, the address of the DC, the signature of the customer's bank and some metadata to preserve the integrity of the transaction, communication is done over Tor.
    \item The seller requests redemption of the digital coin.
    \item The seller posts the product to the DC via the delivery service.
    \item The Delivery Agent (DA) collects the product from the seller's locker and posts it to the DC.
    \item The buyer collects the product from the DC using a password.
    \item The buyer verifies that the product is the one ordered, if not, opens a dispute with TTP.
\end{enumerate}

Besides the assumptions of the existence of the TTP, the protocol also assumes:

\begin{itemize}
    \item The buyer's and seller's banks allow confidential transactions, and both share a commit buffer where the value is locked until the transaction is complete;
    \item The banks maintain a global list of coin serial numbers to prevent problems with double spending;
    \item there is an anonymous communication channel and the SC and DC are password protected;
    \item The DC is equipped with a video camera that records the moment the buyer opens the package and provides a means to submit the video to TTP in the event of a dispute;
\end{itemize}

\subsection{Fair exchange and blockchain}
The problem of TTPs in fair exchange protocols has been solved by the use of decentralised networks, in particular blockchain technology.

The simplest example of a blockchain-based fair exchange protocol is the certified email protocol, where neither the sender can deny sending the email nor the recipient can deny receiving it. As this service is widely used in the paper world, achieving it for emails has not yet been agreed upon by the scientific community. The main problem has been the reliance on TTP, which significantly reduces the performance, security and robustness of such protocols. The protocols that do not use TTP suffer from high computational and communication overhead~\cite{hinarejosSolutionSecureCertified2019}.

The authors of ~\cite{hinarejosSolutionSecureCertified2019} have replaced TTP with blockchain (specifically the bitcoin blockchain as a reference implementation), which acts as a secure, verifiable and decentralised TTP.

The idea behind certified email and any other fair exchange protocol is as follows:
\begin{enumerate}
    \item The sender sends an encrypted and signed message to the recipient.
    \item The recipient returns a proof of delivery (a signature) of the encrypted message to the sender.
    \item The sender publishes the proof of delivery and the decryption key on a blockchain (or TTP in general).
    \item The recipient decrypts the encrypted message using the published decryption key.
\end{enumerate}

The non-repudiation requirement is achieved by the receiver sending the proof of delivery before having access to the decrypted message, and the sender publishing the decryption key together with the proof of delivery on the blockchain (or TTP), so that the receiver cannot deny having received the message or having access to the decryption key—because it is publicly available.

In this case, the role of the blockchain is to certify the existence of the decryption key at a given point in time.

\subsection{Fair-exchange, blockchain, and decentralized dispute resolution}
\label{themis-towards-decentralized-escrow-of-cryptocurrencies-without-trusted-third-parties}
Themis~\cite{mengThemisDecentralizedEscrow2019} is a fair exchange protocol that uses blockchain instead of TTP. It provides an escrow service for the secure exchange of cryptocurrencies and digital goods. It also provides a decentralised dispute resolution system for resolving conflicts.

The protocol works as follows:
\begin{enumerate}
    \item Alice and Bob create a 2-of-2 threshold escrow account using the Thresh-Key-Gen protocol and send funds to it.
\item Alice and Bob split their secret keys into \(n=2t+1\) secret shares using Shamir Secret Sharing protocol, where \(n\) is the number of mediators participating in the decentralised network and \(t+1\) is the threshold for a sufficient number of mediators to reconstruct the secret key.
    \item Alice and Bob encrypt each \textit{i}-th key share with the public key of \textit{i}-th mediator.
\item Alice and Bob exchange the sets of encrypted key shares and send funds to the escrow account.
\end{enumerate}

The escrow is secure as long as \(t+1\) of the mediators do not collude, which would allow them to reconstruct both \(x_A\) and \(x_B\).

To ensure that the parties exchange real key shares, they send witnesses generated using the Feldman VSS scheme and zero-knowledge proofs to guarantee consistency between witnesses and key shares.

In the event of a dispute, the decentralised network of mediators resolves the conflict and grants the winning party the other party's secret key, allowing it to withdraw the funds.

The financial incentives and the reputation system guarantee the honesty of the mediators.

\subsection{Blockchain, anonymity, and physical delivery}\label{lelantos-a-blockchain-based-anonymous-physical-delivery-system}

Lelantos~\cite{altawyLelantosBlockchainBasedAnonymous2017} is a blockchain-based anonymous physical delivery system. The protocol achieves anonymity by using onion routing (similar to the Tor network) to connect physical delivery providers. The entire path from a seller to a buyer is divided into multiple steps, and each step is performed by randomly selected delivery providers. As long as the couriers do not collude, the seller cannot learn the identity or destination address of the buyer.

A smart contract is used to coordinate the whole process and mediate communication between the buyer and the delivery providers.

However, because the system uses Ethereum, it achieves pseudonymity rather than anonymity (see section~\ref{sec:pseudo-anon}). Also, the protocol does not cover disputes between the parties.

\subsection{Comparision}

We only considered protocols that achieve fair exchange, as this is the fundamental feature of such protocols.

We also didn't focus on protocols for buying digital products, as they are not relevant to our use case. A more comprehensive analysis of such protocols is available in~\cite{birjoveanuTwoPartyECommerceProtocols2022}.

Altawy et al. 2017~\cite{altawyLelantosBlockchainBasedAnonymous2017} is a blockchain-based protocol that provides anonymous physical delivery using onion routing and anonymous blockchain interaction, assuming unlinkability between pseudonyms and real identities. However, it does not provide dispute resolution.

Hinarejos et al. 2019~\cite{hinarejosSolutionSecureCertified2019} is the simplest protocol that replaces TTP with blockchain. However, it does not take into account anonymity, disputes between parties, or the exchange of physical material.

Meng et al. 2019~\cite{mengThemisDecentralizedEscrow2019} improves the previous protocol through the crowd-sourced dispute resolution system. However, it does not take anonymity into account.

Bîrjoveanu, 2022~\cite{birjoveanuTwoPartyECommerceProtocols2022} is the closest to our protocol, but it is based on strong assumptions, namely the existence of TTP, banks supporting confidential transactions with commit buffers, and maintaining a global list of coin serial numbers.

Our protocol achieves anonymity by using either cash or privacy-preserving blockchains. In addition, our protocol does not require a customer to submit a transaction to the bulletin board, which may be the weakest link in achieving anonymity in other protocols.

Furthermore, none of them directly address our use case. We want the SP to remain public so that the anonymous buyer can easily start a dispute. We assume a single package of physical materials. Also, the package is delivered from the buyer to the SP, not the other way around–as in most e-commerce transactions.

Also, our protocol does not have its own dispute resolution mechanism, as Themis does. However, we assume the existence of an abstract Dispute Resolution Service that accepts evidence and punishes the misbehaving party. 
This can be instantiated either with the local court or police, or with one of the blockchain's dispute resolution services such as Themis~\cite{mengThemisDecentralizedEscrow2019}, Kleros~\cite{bergollaKlerosSociolegalCase2022,gudkovCrowdArbitrationBlockchain2020}, Aragon Court~\cite{aragonDecentralizedDisputeResolution}, LTO Network~\cite{ltonetworkNextGenBlockchainB2B,ltonetworkOnchainIdentitiesCredentials}, and other Online Dispute Resolution platforms~\cite{allenGovernanceBlockchainDispute2019}.

The comparison of the protocols is presented in Table~\ref{tab:comparision}.

The notation \textit{Pseudonymity} means that the anonymity is based on the assumption that the pseudonym is not linked to the real identity; \textit{TTP} means that the protocol uses a trusted third party; \textit{BC} means that the protocol uses a public blockchain; \textit{YES*} means that the protocol provides the feature but is based on strong or impractical assumptions.

\begin{table*}
\centering
\newcommand{\YES}{\cellcolor{green!50}Yes}
\newcommand{\YESBUT}{\cellcolor{green!25}Yes*}
\newcommand{\ID}{\cellcolor{green!25}Identity}
\newcommand{\PSEUDO}{\cellcolor{green!35}Pseudonym}
\newcommand{\ANON}{\cellcolor{green!50}Anonymity}
\newcommand{\NO}{\cellcolor{red!50}No}
\newcommand{\TTP}{\cellcolor{red!50}TTP}
\newcommand{\BC}{\cellcolor{green!50}BC}
\caption{Comparision of related works.}
\label{tab:comparision}
\setlength{\tabcolsep}{3pt}

\begin{tabular}{cccccc}

\noalign{\smallskip}\hline\noalign{\smallskip}
Protocol & Fair exchange & Anonymity & Dispute resolution & Trust & Physical delivery \\
\noalign{\smallskip}\hline\noalign{\smallskip}
\cite{zhangPracticalFairExchangeEPayment2006} (2006) & \YES & \YESBUT & \YES & \TTP & \YES \\
\cite{mohammedalarajFairnessPhysicalProducts2012} (2012) & \YESBUT & \NO & \YES & \TTP & \YES \\
Lelantos~\cite{altawyLelantosBlockchainBasedAnonymous2017} (2017) & \YES & \PSEUDO & \NO & \BC & \YES \\
\cite{hinarejosSolutionSecureCertified2019} (2019) & \YES & \NO & \NO & \BC & \NO \\
Themis~\cite{mengThemisDecentralizedEscrow2019} (2019) & \YES & \NO & \YES & \BC & \NO \\
PPPDCP~\cite{birjoveanuTwoPartyECommerceProtocols2022} (2022) & \YES & \YES & \YES & \TTP & \YES \\
This paper & \YES & \YES & \YES & \BC & \YES \\
\noalign{\smallskip}\hline

\end{tabular}

\end{table*}

\section{Building Blocks}\label{sec:building-blocks}

\subsection{Physical products}\label{sec:physical-products}
The use cases discussed in this paper use physical materials such as blood, urine, hair and other biological materials.
This requirement, combined with the need for anonymity, is a challenging part of fair exchange protocols. The problem arises when the seller wants to send the product to the buyer who wants to remain anonymous. Most of the existing protocols either assume the existence of a trusted delivery agent~\cite{mohammedalarajFairnessPhysicalProducts2012,birjoveanuAnonymityFairexchangeEcommerce2015}, or use a complex delivery mechanism similar to onion routing involving multiple many delivery services~\cite{altawyLelantosBlockchainBasedAnonymous2017}.

However, our use case is different in that the physical materials are transferred from the (anonymous) customer to the (public) SP. This allows a simplification of the delivery process. We assume that there is a way to deliver a package anonymously without revealing the customer's personal information, either via the SP's drop box, parcel locker services (e.g. Amazon Locker, InPost~\cite{inpostParcelLockerService}), a customer's trusted Delivery Agent, or even the post office.

\subsection{Dispute resolution system}
\label{sec:dispute-resolution}
Disputes are an inevitable part of all human transactions. Whether intentional or accidental, the system should prevent violations of agreed contract rules or local jurisdiction. The rules are set by law and enforced by the police.

The vision of smart contracts was to replace the legal contract with
programmable and autonomous contracts. The code of the smart contract contains the specifications of the contract, hence the slogan \textit{code as law}. In addition, smart contracts are executed automatically, bridging the gap between law and its enforcement by police~\cite{allenGovernanceBlockchainDispute2019}. However, the blockchain paradigm has its limitations.

Blockchains can only guarantee the correctness of the data and calculations that exist on the blockchain. The problem arises when we want the smart contract to make decisions based on some input from outside the blockchain. The technique for providing real-world data to the blockchain is called \textit{oracle}. An oracle provides data based on a decentralised network of mediators, so the trust is also decentralised~\cite{breidenbachChainlinkNextSteps2021}.

Some oracles provide data such as weather, football results, stock prices, train delays, election results and others-and these are the ones we are interested in-provide the resolution of a submitted dispute.

Themis~\cite{mengThemisDecentralizedEscrow2019} not only provides a fair exchange protocol, it also provides a semi-autonomous decentralised dispute resolution system that complies with the Web3 postulates of a decentralised Web~\cite{ethereumWhatWeb3Why2023}. Themis resolves disputes through a set of voluntary, anonymous mediators who take part in voting and decide whether a party has misbehaved. The honesty of the mediators is achieved through a monetary incentive and reputation system.

Kleros~\cite{bergollaKlerosSociolegalCase2022} is a smart contract deployed on the Ethereum platform that mimics, in a decentralised and autonomous way, how the court works in real life. In Kleros, every process of a dispute, such as gathering evidence, selecting jurors and rewarding the winning party, is automated by a set of smart contracts. As in Themis, the honesty of the agents voting in a case is achieved through game-theoretic economic incentives.

Such a decentralised, voluntary and anonymous dispute resolution system might work for simple breaches of contract, such as an eBay seller sending broken or wrong products, or an Airbnb apartment that does not match the photos in the listing. However, it is difficult to implement such a decentralised assessment of the quality of health or legal services when expertise and privacy concerns are taken into account. Therefore, our protocol takes a more conservative approach and resolves disputes by recording evidence on the blockchain and then using the local justice system (police or courts) to resolve the conflict.

Possible directions towards a semi-autonomous decentralised resolution system are discussed in Section~\ref{sec:decentralised-justice}.

\subsection{Fairness}\label{fairness}

In the event of a dispute, the customer can provide convincing evidence of the customer's honesty and the SP's misbehaviour to the judicial authorities (police or court). 
Because the customer is anonymous, the SP cannot start a dispute - there is no way to identify the customer.

To mitigate this problem, we have designed the protocol in such a way that the SP who follows the protocol is always in an advantageous position and therefore has no reason to start a dispute. On the other hand, the customer can start a dispute at any point in the protocol, but only the actual misbehaviour of the SP will allow him to win the case.

Abstracting from the services provided by the SP, each party should be able to prove its honest behaviour in case of a dispute. We present three pieces of evidence that should be disclosed to the judiciary in the event of a dispute:

\begin{enumerate}
    \item Proof of Delivery ($\mathrm{PoD}$) is a confirmation issued by the SP to the customer proving that the customer has delivered a complete (according to the SP's requirements) package to the SP and that the SP has accepted it. It consists of i) the current time, ii) the deadline to pay for the transaction, iii) the deadline to provide a result of the service, iv) the transaction identifier ($\textrm{provisionID}$) randomly generated by the customer, v) and the signature of the SP guaranteeing non-repudiation. The formal definition of $\mathrm{PoD}$ is given in Section~\ref{proof-of-delivery}.

    \item Payment $\mathrm{receipt}$ is the confirmation that the customer has paid for the transaction at some point in time. The actual implementation depends on the cryptocurrency and is discussed further in Section~\ref{payment-for-services}.

    \item Proof of Provision ($\mathrm{PoP}$) is the proof that the SP has published the result at a given time. It defends the SP in case the customer unjustifiably starts a dispute after the result has been published. It consists of i) a content identifier (as specified in Section ~\ref{storage-network}), ii) the $\textrm{provisionID}$ that uniquely identifies the transaction, and iii) the SP's signature that guarantees authentication. The link between $\mathrm{PoP}$ and the results is provided by the content identifier ($\mathrm{cid}$) that uniquely identifies the result (it is a kind of hash of the result), so that the result cannot be forged after the $\mathrm{PoP}$ is published.
\end{enumerate}

\subsection{Message Board}\label{sec:message-board}
The Proof of Provision ($\mathrm{PoP}$) that we have coined for the purposes of this protocol is commonly called Proof of Existence~\cite{crespoStamperyBlockchainTimestamping2017}.

The idea behind Proof of Existence is to certify that a piece of information existed at a certain point in time, in such a way that nobody can undermine its existence, integrity or ownership (also called the non-repudiation property).

We need this functionality for two reasons: (1) to communicate the existence of the results to the customer, to whom the SP has no other means of communication, since the customer remains anonymous; (2) to let the SP prove the publication of the result within the deadline agreed with the customer.

By publishing the $\mathrm{PoP}$ on the blockchain, the SP cannot falsify the time at which the results were provided, as the block creation time proves it. The blockchain acts as a global clock that securely timestamps everything that goes into the block, so the $\mathrm{PoP}$ included in a block is associated with the time the block was created. Moreover, since the blockchain is public, anyone (including the judiciary) can be convinced that the SP did indeed publish the result at that time.

Without such proof, there would be no other way to resolve the conflict between the customer claiming that the results were not published and the SP claiming that the results were published on time.

Depending on the context, the platform for achieving this is called bulletin board~\cite{achenbachImprovedCoercionresistantElectronic2015}, trusted timestamping~\cite{gippDecentralizedTrustedTimestamping2015}, or message board~\cite{hinarejosSolutionSecureCertified2019}. In this paper we call it a message board.

We keep the protocol general enough to be implemented using any existing technology to provide a message board service, provided it is decentralised and supports subscribing to upcoming proofs from a given address.

\subsection{Anonymity, pseudonomity, and confidentality}\label{sec:pseudo-anon}

Privacy is a concept used in almost all social sciences such as philosophy, psychology, sociology and law. This multidisciplinary nature leads to ambiguous definitions~\cite{smithInformationPrivacyResearch2011}. For our work we rely on more concrete definitions, i.e.~confidentiality and anonymity.

Confidentiality is the ability to hide the details of actions from others. Alternatively, we can say that the system guarantees confidentiality if, for all observers, all they can say about the action is the fact that it happened and nothing more.

Anonymity is the ability to hide one's identity from others. More specifically, it is the inability to correlate actions taken within the system with the identity of the user. Alternatively, we can say that the system guarantees anonymity if, for all observers, the actions are equally likely to be associated with any user of the system. However, anonymity is a spectrum rather than a dichotomous classification. One method of quantifying the level of anonymity is the \textit{k}-anonymity proposed in~\cite{sweeneyKanonymityModelProtecting2002}. It measures the user's anonymity by the number of other users from whom the user is indistinguishable. Specifically, the user is \textit{k}-anonymous if his actions are equally likely to be associated with \textit{k}-1 other users; the larger the \textit{k}, the greater the anonymity.

Some anonymity techniques can be used on non-anonymous blockchains. The so-called mixers gather users into an anonymity set who then collude to launder transactions in such a way that, to an observer, the likelihood of the sender of each transaction being any user from the anonymity set is equiprobable.

Some systems provide pseudonymity rather than anonymity. Pseudonymity allows users to hide their real identities behind pseudonyms. Although the whole system is transparent and allows actions to be linked to pseudonyms, the system is considered anonymous as long as the link between pseudonyms and real identities is secret. This assumption is difficult to meet in practice, as KYC (Know Your Customer) and AML (Anti Money Laundering) regulations require users to reveal their real identities to cryptocurrency exchanges, exposing users' privacy to government agencies, malicious insiders and cyber criminals. In addition, some correlations can be inferred simply by analysing transactions~\cite{androulakiEvaluatingUserPrivacy2013, oberStructureAnonymityBitcoin2013}.

Figure~\ref{fig:anonymity-diagram} illustrates the relationships between these terms.

\begin{figure}[h!]
\includegraphics[width=\linewidth]{anonymity-diagram.png}
\centering
\caption{Suppose Alice is the client who wants to keep her identity anonymous and Bob is the public SP. Alice controls two addresses 1 and 2; the link between her real identity and the first address has been compromised and therefore identification is possible; the link to the second pseudonym is still unknown and therefore anonymous. Alice takes two actions, the first from the compromised address and the second from the anonymous address. The first action is confidential; therefore, even though the pseudonym has been compromised, the action cannot be associated with Alice. The second action is transparent, so Alice maintains her anonymity as long as the link to the second pseudonym is concealed.}

\label{fig:anonymity-diagram}
\end{figure}
The privacy-preserving blockchains are those that maintain anonymity through untraceability and (ideally) unlikability - not by assuming that the link between an address (pseudonym) and real identity is hidden.

Examples of blockchains that natively support confidential transactions include Monero~\cite{vansaberhagenCryptoNote2013} (using Ring Signatures~\cite{noetherRingSignatureConfidential2015} or Bulletproofs~\cite{bunzBulletproofsShortProofs2018}), ZCash~\cite{ben-sassonZerocashDecentralizedAnonymous2014} (using zkSNARK~\cite{ben-sassonSNARKsVerifyingProgram2013}), Grin~\cite{fuchsbauerAggregateCashSystems2019} (using Mimblewimble~\cite{jedusorMIMBLEWIMBLE2016}), and IronFish~\cite{ironfishPrivateAnonymousEasy} (using Sapling protocol~\cite{hopwoodZcashSaplingProtocol2022}).

Overly techniques that achieve anonymity on top of non-privacy preserving blockchains are Ethereum's Tornado Cash~\cite{pertsevTornadoCashPrivacy2019} (via zkSNARK~\cite{grothSizePairingbasedNoninteractive2016} and MiMC~\cite{albrechtMiMCEfficientEncryption2016}), Bitcoin's Wasabi~\cite{wasabiwalletBitcoinPrivacyWallet} (via CoinJoin~\cite{maxwellCoinJoinBitcoinPrivacy2013}).

\subsection{Payment for services}\label{payment-for-services}
Transactions between customers and SPs need to be linked to prevent the reuse of a payment for multiple transactions. In other words, we need a mechanism that uniquely links the payment to the corresponding transaction.

Depending on the cryptocurrency, this link can be established in different ways:

\begin{itemize}
\item separate address: each transaction uses a unique address associated with the transaction. Such addresses can be derived using Hierarchical Deterministic Wallets~\cite{wuilleBIP32HierarchicalDeterministic2012} and published on the message board to achieve non-repudiation.
\item memo: payments are sent to a single SP account, but contain an extra field called ``memo'' filled with the unique identifier $\textrm{provisionID}$. 
\end{itemize}

Any payment that contains $\textrm{provisionID}$ in the memo or is sent to the designated address will be considered payment for the transaction.

In the event of a dispute, there must be a way to prove to the courts that the customer has paid for the transaction. As proof of payment is trivial in transparent and traceable blockchains, it becomes more complicated when it comes to anonymous blockchains. Monero allows payments to be proven and verified via a dedicated API~\cite{moneroHowProvePayment}. ZCash provides a mechanism called Payment Disclosure~\cite{daviesIntroductionPaymentDisclosure2017}. We call the proof of payment a \textit{payment recepit}.

\subsection{Storage network}\label{storage-network}
Once the SP has completed its service, it needs to deliver the result to the customer. The most natural approach would be to send the result via email or a dedicated platform. However, the customer wants to remain anonymous and does not want to reveal his email address or IP address. Furthermore, the SP needs to prove that the result was delivered before the deadline, which brings us to the issue of proof of existence discussed in Section~\ref{sec:message-board}.

One approach would be to post the result to a blockchain. However, storing data on a blockchain is very expensive. The most common workaround (\cite{shahidBlockchainBasedAgriFoodSupply2020, wangAuditableProtocolsFair2019, chenImprovedP2PFile2017}) is to publish the data on a content addressable peer-to-peer storage network such as IPFS~\cite{benetIPFSContentAddressed2014}. Then publish only the content identifier ($\mathrm{cid}$) on the blockchain, which uniquely points to the content stored on IPFS.

We follow the same approach. Once the SP has produced the result, it encrypts it using the previously provided encryption key and uploads it to the IPFS network.

We also use Filecoin to guarantee that the results are available to the customer even if the SP refuses to share the result (see Section ~\ref{sec:provable-results-availability}).

To increase anonymity, the customer should use standard techniques to hide their IP address, such as VPN or proxy.

\subsection{Separation of concerns}
We could use a single blockchain to achieve all three of these roles: i) anonymous payments, ii) message board, and iii) storage network.

While most blockchains could provide message board functionality, anonymous payments are not as common. In particular, a verifiable storage network is a feature of a few specialised blockchains.

Rather than searching for a single blockchain to provide all functionalities, we allow the protocol to use separate blockchains for each role. If a suitable blockchain emerges, it can play more than one role.

At the time of writing, we see the following technologies fulfilling the requirements of each role:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}

\item Anonymous payments: Monero \cite{vansaberhagenCryptoNote2013}, ZCash
  \cite{ben-sassonZerocashDecentralizedAnonymous2014}, Grin \cite{fuchsbauerAggregateCashSystems2019},
  Tornado Cash \cite{pertsevTornadoCashPrivacy2019}.
\item Message board: Open timestamps~\cite{opentimestampsTimestampingProofStandard}, Stampery \cite{crespoStamperyBlockchainTimestamping2017}, Bitcoin blockchain (Proof of Existence~\cite{proofofexistenceWebApplicationProve}, Chainpoint~\cite{chainpointBlockchainProofAnchoring}), Ethereum blockchain, or any other public blockchain that supports attaching extra data along the transaction.
\item Storage network: IPFS~\cite{benetIPFSContentAddressed2014}, Filecoin~\cite{protocollabsFilecoinDecentralizedStorage2017}, or Ethereum's
  Swarm~\cite{teamSWARMStorageCommunication2021}.
\end{enumerate}

\section{The Protocol}\label{sec:protocol}
In this section, we propose an abstract protocol for anonymous service provisioning that makes no assumptions about the underlying technologies. We define the requirements for each role and leave the choice of technology to the developer. Later in the paper (Section~\ref{sec:experiments}) we describe our implementation, which we use to conduct an experiment.

\subsection{Assumptions}

\begin{itemize}
\item There exists PKI infrastructure:
    \begin{itemize}
        \item The customer and the SP have their key pairs consisting of secret key $\mathrm{sk}(\mathrm{party})$ and public key $\mathrm{pk}(\mathrm{party})$, where $\mathrm{party} \in \{\mathrm{C}, \mathrm{SP}\}$ for the customer and the SP accordingly.
        \item Both the customer and the SP can create and verify digital signatures created by the customer $\mathrm{sig}_{\mathrm{sk}(\mathrm{C})}$ and the SP $\mathrm{sig}_{\mathrm{sk}(\mathrm{SP})}$.
        \item The SP's public key $\mathrm{pk}(\mathrm{SP})$ is publicly known.
    \end{itemize}

\item Both the customer and the SP:
    \begin{itemize}
        \item use common symmetric encryption $\mathrm{E}_\mathrm{key}(\cdot)$ and decryption $\mathrm{D}_\mathrm{key}(\cdot)$ operations.
        \item have access to anonymous payments blockchain, message board, and storage network.
    \end{itemize}

\item The SP:
    \begin{itemize}
        \item accepts packages from unknown customers.
        \item accepts payments with cash and anonymous cryptocurrencies as described in Section~\ref{payment-for-services}.
    \end{itemize}

\item Dispute Resolution Service:
    \begin{itemize}
        \item accepts as evidence in a dispute the $\mathrm{PoD}$, $\mathrm{PoP}$, and payment $\mathrm{receipt}$ as described in Section~\ref{fairness}.
    \end{itemize}

\item Anonymous Payments Blockchain:
    \begin{itemize}
        \item supports anonymous, i.e., untraceable and (ideally) unlinkable transactions as described in Section~\ref{sec:pseudo-anon}.
        \item supports uniquely identifiable transactions via a dedicated address, memo field, or other similar mechanisms as described in Section ~\ref{payment-for-services}. 
    \end{itemize}

\item Message Board:
    \begin{itemize}
        \item supports transactions of sizes up to $\mathrm{PoD}$ and $\mathrm{PoP}$.
    \end{itemize}

\item Storage Network:
    \begin{itemize}
        \item allows content to be retrieved using a content identifier $\mathrm{cid}$ (usually a hash of the content).
        \item allows content to be retrieved anonymously.
        \item guarantees that the content will be available for the duration of the agreement.
    \end{itemize}
\end{itemize}

\subsection{Messages}\label{messages}
In this section, we describe the messages exchanged between the parties of the protocol.

\vspace{5mm}

\noindent \textbf
{Package}\label{package} is a physical container prepared by the customer encompassing all the $\mathrm{materials}$ required by the SP to provide the service.

$$\mathrm{pkg} \equiv (\mathrm{materials}, \mathrm{provisionID}, \mathrm{pk(C)})$$

where:

\begin{itemize}

\item $\mathrm{materials}$ - are the materials required to provide the service, for example, samples of urine, blood, stool, saliva; legal documents, CDs, emails, photos, bank statements; or any other type of material depending on the service.
\item $\mathrm{provisionID}$ - a randomly generated provision identifier, used to anonymously track the provision through all steps of the protocol.
\item $\mathrm{pk(C)}$ - the customer's public key used to encrypt the results published to the public storage network.
\end{itemize}

\noindent \textbf
{Proof of Delivery ($\mathrm{PoD}$)}\label{proof-of-delivery} is a confirmation that the customer has delivered a correct (according to the SP's requirements) package to the SP and that the SP has accepted it.

It is also an agreement between the customer and the SP, as it includes agreed-upon deadlines for actions and a method of payment.

The $\mathrm{PoD}$ is published on the message board by the SP.

\begin{eqnarray}
\mathrm{PoD} & \equiv & (\begin{array}[t]{l}\mathrm{T}_\mathrm{issue}, \mathrm{T}_\mathrm{pay}, \mathrm{T}_\mathrm{provide}, \\\\ \mathrm{address}, \mathrm{provisionID}, \mathrm{pk(C)}, \mathrm{sig}_\mathrm{SP} \; )\end{array}
\end{eqnarray}

where:

\begin{itemize}

\item $\mathrm{T}_\mathrm{issue}$ - time at which the $\mathrm{PoD}$ is issued by the SP.
\item
  $\mathrm{T}_\mathrm{pay}$ - deadline for paying the transaction.
\item
  $\mathrm{T}_\mathrm{provide}$ - deadline to provide the result of the service, i.e. to publish $\mathrm{PoP}$.
\item $\mathrm{address}$ - payment address of the SP's anonymous blockchain account.
\item $\mathrm{provisionID}$ - the number that uniquely identifies the transaction previously generated by the customer.
\item $\mathrm{pk(C)}$ - the public key of the client used to encrypt the result published on the public storage network.
\item $\mathrm{sig}_\mathrm{SP}$ - the SP's signature to ensure non-repudiation.
\end{itemize}

also:
\(\mathrm{T}_\mathrm{issue} \leq \mathrm{T}_\mathrm{pay} \leq \mathrm{T}_\mathrm{provide}\)

\noindent \textbf
{Proof of provision ($\mathrm{PoP}$)}\label{proof-of-provision} is proof that the SP published the result at a certain time. It protects the SP in case the customer unjustifiably starts a dispute after the results have been published. The link between $\mathrm{PoP}$ and the results is made by the content identifier ($\mathrm{cid}$), which uniquely identifies the results so that the result cannot be forged after the $\mathrm{PoP}$ has been published.

The $\mathrm{PoP}$ is published on the message board by the SP.

\begin{eqnarray}
\mathrm{PoP} & \equiv & (\mathrm{cid}, \mathrm{provisionID}, \mathrm{sig}_\mathrm{SP})
\end{eqnarray}

where:

\begin{itemize}

\item $\mathrm{cid}$ - the content identifier as specified in Section~\ref{storage-network}.
\item $\mathrm{provisionID}$ - The number that uniquely identifies the transaction previously created by the customer.
\item $\mathrm{sig}_\mathrm{SP}$ - the signature of the SP, which guarantees non-repudiation.
\end{itemize}

\noindent \textbf
{Payment-receipt}\label{payment-receipt} proves that the customer made the payment. Since the proof depends on a specific blockchain (see Section~\ref{payment-for-services}), we symbolically refer to it as $\mathrm{receipt}$.

\noindent \textbf
{Results}\label{results} is assumed to be a document in PDF format, but any other format is acceptable as long as it can be binary encoded and uploaded to the storage network. We symbolically refer to it as $\mathrm{results}$.

\noindent \textbf
{Content Identifier (cid)}\label{content-identifier-cid} is a term coined by IPFS~\cite{ipfsContentIdentifiersCIDs}. However, since our protocol does not depend on this particular implementation of the storage network, we let the $\mathrm{cid}$ be any other identifier that securely and uniquely points to the content.

\subsection{Protocol description}\label{protocol-description}

In this section we describe each step of the protocol, also shown in Figure~\ref{fig:protocol-diagram}.

\begin{figure}[ht!]
\includegraphics[width=\linewidth]{anonser-protocol.png}
\centering
\caption{Messages exchanged in the protocol. Solid arrows indicate requests and dashed arrows indicate responses.}
\label{fig:protocol-diagram}
\end{figure}

\noindent \textbf
{Step 0.  Preparation}\label{step-0-preparation}

The customer collects all $\mathrm{materials}$ required by the SP, generates a random $\mathrm{provisionID}$ and a random keypair $(\mathrm{sk(C)},\mathrm{pk(C)})$. The $\mathrm{provisionID}$ is used to connect all actions associated with the transaction throughout the protocol. The $\mathrm{provisionID}$ and $\mathrm{pk(C)}$ are encoded as a QR code, printed and attached to the $\mathrm{pkg}$ package. The $\mathrm{sk(C)}$ is kept secret and is used to decrypt the $\mathrm{result}$ at the end of the protocol.

\noindent \textbf
{Step 1. Package Delivery}\label{step-1-package-delivery}

The protocol starts when the customer delivers the package $\mathrm{pkg}$ to the SP and its content is accepted. As a result, $\mathrm{PoD}$ is created with a predefined payment deadline $\mathrm{T}_\mathrm{pay}$, service provision deadline $\mathrm{T}_\mathrm{provide}$ and current time $\mathrm{T}_\mathrm{issue}$. In addition, $\mathrm{PoD}$ embodies information on whether the service was paid for in cash or whether the customer should pay using the anonymous blockchain account. In the latter case, the SP's payment $\mathrm{address}$ is included in $\mathrm{PoD}$.

The digital signature $\mathrm{sig}_{\mathrm{sk}(\mathrm{SP})}$ on the $\mathrm{PoD}$, created with the SP's secret key $\mathrm{sk}(\mathrm{SP})$, guarantees non-repudiation.

Symbolically: 
\[
\mathrm{PoD \gets delivery(pkg)}
\]

\noindent \textbf
{Step 2. Proof of Delivery}\label{step-2-pod}

Then, the $\mathrm{PoD}$ is published on the message board by the SP, committing to the fact that the package $\mathrm{pkg}$ has been delivered, and the SP cannot reject receiving it. If the provision has not been paid in cash, the SP waits for the customer to pay for the service at the payment $\mathrm{address}$ specified in the $\mathrm{PoD}$.

Symbolically: 
\[
\mathrm{publish(PoD)}
\]

\noindent \textbf
{Step 3. Get Proof of Delivery}\label{step-3-get-pod}

Once the package has been delivered and the $\mathrm{PoD}$ has been published, the customer can retrieve the $\mathrm{PoD}$ from the message board and (if everything is correct) proceed with the protocol.

Symbolically: 
\[
\mathrm{PoD \gets get(provisionID)}
\]

\noindent \textbf
{Step 4. Payment}\label{step-4-payment}

If the provision was not paid in cash, the customer should pay for the transaction using the predefined anonymous payment blockchain (see Section~\ref{payment-for-services}).
In return, the customer receives the $\mathrm{receipt}$, which should be disclosed in case of dispute.

Symbolically: 
\[
\mathrm{receipt \gets payment(address)}
\]

\noindent \textbf
{Step 5. Provision of Service}\label{step-5-provision-of-service}

Once the customer has paid for the transaction, either in cash or via the anonymous blockchain, the SP can begin to provide the service.

Symbolically: 
\[
\mathrm{result \gets provision(materials)}
\]

\noindent \textbf
{Step 6. Upload result}\label{step-6-upload-result}

When the service is complete, a result should be generated. 
Next, the result is encrypted using a shared key derived from the customer's public key $\mathrm{pk(C)}$ and the SP's secret key $\mathrm{sk(S)}$ using the Diffie-Hellman key exchange (DHKE) method~\cite{diffieNewDirectionsCryptography1976}.
The encrypted result is then uploaded to the content addressable network (such as IPFS). In return, the content identifier ($\mathrm{cid}$) is created.

Symbolically: 
\[
\mathrm{cid \gets upload(E_{DHKE(sk(SP), pk(C))}(result))}
\]

\noindent \textbf
{Step 7. Proof of Provision}\label{step-7-proof-of-provision}

When the $\mathrm{result}$ is uploaded, the SP creates and publishes on a message board a proof of provision consisting of $\mathrm{cid}$ along with $\mathrm{provisionID}$ and signature $\mathrm{sig}_\mathrm{SP}$.

Symbolically: 
\[
\mathrm{publish(PoP)}
\]

\noindent \textbf
{Step 8. Get Proof of Provision}\label{step-8-get-proof-of-provision}

After delivering the package and paying for the transaction, the customer starts listening to the message board and waits until the SP publishes the $\mathrm{PoP}$ for the $\mathrm{provisionID}$.

Symbolically: 
\[
\mathrm{cid \gets get(provisionID)}
\]

\noindent \textbf
{Step 9. Download result}\label{step-9-download-result}

Having the $\mathrm{cid}$, the customer downloads and decrypts the $\mathrm{result}$ using a shared key derived from the customer's secret key $\mathrm{sk(C)}$ and the SP's public key $\mathrm{pk(S)}$ using the DHKE method. The protocol ends.

Symbolically: 
\[
\mathrm{result \gets D_{DHKE(sk(C), pk(SP))}(download(cid))}
\]

\section{Fairness analysis}\label{sec:fairness-analysis}
We analyse the fairness of the protocol by representing it as an interactive non-cooperative game.

\subsection{Model}\label{sec:fairness-model}
We consider three positions:

\begin{itemize}
\item Neutral position (•): when a party has neither spent nor gained anything of significant value (money, time, effort). For example, at the beginning of the protocol.
\item Disadvantaged position (-): when a party has put a significant value without receiving an equivalent. For example, the customer has paid in advance for a service.
\item Advantaged position (+): when a party would benefit if the transaction was stopped at this step. For example, the SP has received payment before the service has been provided.
\end{itemize}

There are many actions that each party can take, but we group them into two categories:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}

\item Normal: taking actions prescribed by the protocol.
\item Abnormal: anything that deviates from the intended steps of the protocol. For example, sending an arbitrary message, skipping or repeating steps, or timing out.
\end{enumerate}

In addition, at each step of the protocol, the customer can start a dispute, so another dimension with two positions must be taken into account:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}

\item Agree: the customer agrees with the action and therefore does not start a dispute.
\item Start a dispute: the customer disagrees with the action and therefore starts a dispute.
\end{enumerate}

As a result, in our analysis we need to consider four different outcomes for each party of the protocol ($\mathrm{party \in \{C, SP}\}$), for each step of the protocol ($\mathrm{step \in 1..9}$):

\begin{itemize}

\item
  $\mathrm{\sigma_{step,party,n}}$: after following the protocol when the other party acted normally.
\item
  $\mathrm{\sigma_{step,party,d}}$: after a settled dispute when the other party acted normally.
\item
  $\mathrm{\sigma_{step,party,\overline{n}}}$: after not starting a dispute despite the other party has acted abnormally.
\item
  $\mathrm{\sigma_{step,party,\overline{d}}}$: after a settled dispute when the other party has acted abnormally.
\end{itemize}

The protocol terminates after the last step, after starting a dispute, or after a party fails to complete its designated action in time. Therefore, all positions except $\mathrm{\sigma_n}$ are termination positions.

Because the customer is anonymous, the SP cannot start a dispute - there is no way to identify the customer. To mitigate this problem, we designed the protocol so that the SP who follows the protocol is always in an advantageous position and therefore has no reason to start a dispute. On the other hand, the customer can start a dispute at any time during the protocol, but only the actual misbehaviour of the SP will make him win the conflict.

\begin{definition}[Fairness] \label{def:fairness}
A protocol achieves fairness iff 
\begin{equation*}
\begin{split}
\forall_{party \in parties}\forall_{\mathrm{step} \in \mathrm{steps}} &\operatorname{can\ move}\\
&\operatorname{to the\ non-disadvantaged\ position} 
\end{split}
\end{equation*}

\end{definition}

\subsection{Assumptions}\label{sec:assumptions}

Below we list the assumptions we take for the analysis purpose.

\begin{enumerate}
\item Both parties start from a neutral position ($\neutral$).
\item After completing a transaction, both parties end up in an advantageous position (\plus{}). In other words, they have an intrinsic motivation to initialise and complete the transaction.
\item The protocol steps are atomic - there are no intermediate steps.
\item The protocol can only go forward - there is no way to undo any action.
\item Repeating the first step starts a new transaction. Repeating any other step is considered abnormal and is ignored. For example, paying the invoice twice has no effect on the curse of the protocol.
\item Once published, the result is available to the customer on the storage network. 
\item Winning the dispute results in a neutral position ($\neutral$).
\item Losing the dispute results in a penalty greater than any reward, leading to a disadvantaged position (\minus{}). Therefore, the rational customer will not start a dispute that he is not sure he can win.
\item Both the customer and the SP are rational. They always prefer to go from the worst position (\minus{} or $\neutral${}) to a better position ($\neutral$ or \plus), but they are willing to risk a temporary worst position in favour of a later better position if and only if they can always get out of the worst position; in particular, the customer can always start a dispute and, if the SP has misbehaved, get out of the disadvantaged position (\minus) to the neutral position ($\neutral$).
\item We assume that the customer's materials without personal information are useless and the effort to deliver the package is negligible, so the customer's first step does not lead to a disadvantaged position.
\item We assume that the processing cost of publishing $\mathrm{PoD}$ is negligible and compensates for the customer's effort in delivering the package.
\end{enumerate}

\subsection{Steps}\label{sec:steps}

Figure~\ref{fig:positions} shows the positions of each party after each possible action taken.

\begin{figure}[h!]
\includegraphics[width=\linewidth]{model.png}
\centering
\caption{Positions after each step of the protocol}
\label{fig:positions}
\end{figure}

The detailed description of each step and the rationale for the outcome of the result positions is given in Appendix~\ref{app:proof-of-fairness}.

\subsection{Example scenarios}\label{example-scenarios}
The Figure~\ref{fig:misbehaviour} shows the transitions of positions when the SP tries to misbehave and does not perform the service and therefore does not publish $\mathrm{PoP}$ after receiving the payment. After the deadline $\mathrm{T}_\mathrm{provide}$ the SP cannot publish valid $\mathrm{PoP}$ and so the customer starts a dispute. The customer wins the dispute because the SP cannot prove that the $\mathrm{PoP}$ was published before $\mathrm{T}_\mathrm{provide}$. The protocol ends up neutral for the customer and disadvantageous for the SP's positions.

\begin{figure}[h!]
\includegraphics[width=\linewidth]{misbehaviour.png}
\centering
\caption{Transitions of positions where the SP is misbehaving and the customer starts a dispute}
\label{fig:misbehaviour}
\end{figure}

The rational course for both parties is to follow the protocol shown in Figure~\ref{fig:rational}.

\begin{figure}[h!]
\includegraphics[width=\linewidth]{rational.png}
\centering
\caption{Transitions of positions where both the customer and the SP follow the protocol}
\label{fig:rational}
\end{figure}

Using the definition of fairness~\ref{def:fairness} and the assumptions listed in Section~\ref{sec:assumptions}, our analysis shows that the protocol achieves fairness.

\section{Experiments}\label{sec:experiments}

\subsection*{Setup}

We have developed a prototype of our protocol using the following technologies:

\begin{itemize}
  \item{Anonymous Payments} - we use the Monero blockchain \cite{noetherRingSignatureConfidential2015}.
  \item{Storage Network} - we use the Powergate~\cite{textilePowergate2023}, which is a wrapper around Filecoin and IPFS.
  \item{Message Board} - we use the Ethereum blockchain~\cite{woodEthereumSecureDecentralised2014}; specifically, its local development version Truffle Ganache and the Solidity language.
\item{Customer and SP} - we create client-side web application (webapp) using \texttt{React.js} and \texttt{web3.js} library for interaction with Ethereum. We use \texttt{MetaMask} browser extension to sign and submit transactions to the Ethereum node. We use \texttt{monerod} network client and \texttt{monero-wallet-cli} command line interface to interact with the Monero blockchain.
\end{itemize}

The prototype is available at \url{https://anonser.stan.bar}. The source code is available at \url{https://github.com/stanbar/anonymous-provision-of-services-via-blockchain}.

% The prototype is available at \url{https://anonser.stan.bar}. The source code is available at \url{https://github.com/stanbar/anonymous-provision-of-services-via-blockchain}.

We developed and tested our prototype in the following environment: OS — Arch Linux 5.11.8; Docker — 20.10.5; CPU — Intel(R) Core(TM) i7-4790 (8) 4.00~GHz; RAM — 16 GB DDR3; Storage — Samsung PM85 256~GB SSD; monerod and monero-wallet-cli — v0.18.1.2; Powergate — v2.6.2; Ganache — v7.5.0; Solidity — v0.8.17; ReactJS — v18.0.25; web3.js — v1.8.1; crypto-js — v4.1.1.

For simplicity, all components run on one, mentioned above, physical machine; and all processes are managed by Docker.

Moreover, Powergate is configured to use local Filecoin and IPFS networks.
For the Ethereum blockchain, we use Truffle Ganache, which is a local Ethereum blockchain for development and testing purposes. 
Monero is configured to use the public stage network.
We assume that the service provider offers only one type of service at a fixed public price, so we omit the service type and price from the protocol.

\subsection*{Preparation}

Both the customer and the SP create Monero wallets using the \texttt{monero-wallet-cli} command line tool.

The SP deploys the smart contract using the \texttt{truffle migrate --network development} command, which deploys the smart contract to the Ethereum blockchain. The web application is configured to use the last deployed smart contract address.

The customer receives some test Monero funds using the Faucet service available at \url{https://community.rino.io/faucet/stagenet/}.

Next, the customer enables per-transaction proof generation (payment \texttt{receipt}) by setting \texttt{set store-tx-info 1} for their wallet. This is required to verify the payment in the event of a dispute.

At this point both the customer and the SP are ready to start the protocol.

\subsection*{Experiment}

The customer and the SP are two different users of our prototype, but for simplicity, they use the same machine and the same web application.

Figure~\ref{fig:anonser-experiment1} and Figure~\ref{fig:anonser-experiment2} show the steps of the experiment. Their description is as follows:

\begin{enumerate}
  \setcounter{enumi}{0}
  \item[0.] The protocol starts with the customer opening the webapp and creating a new provision.
The application generates a random ECDSA (secp256k1) customer keypair and a random 32-byte provisionID, and then displays a QR code that encodes both the provisionID and the customer's public key. 
The customer's private key must be downloaded and provided later to decrypt the results.

  \item[1.] The customer prints the QR code, sticks it on a parcel and delivers the parcel to the SP either via the SP's drop box, parcel locker services (e.g. Amazon Locker, InPost~\cite{inpostParcelLockerService}), a customer's trusted delivery agent or the post office.

  \item[2.1.] The SP opens the app and scans the QR code, which decodes the provisionID and the customer's public key.

  \item[2.2.] Since (in this experiment) the provision was not paid in cash, the SP generates a unique Monero payment address using \texttt{monero-wallet-cli integrated\_address}. 
  \item[2.3.] The SP submits the Proof of Delivery to the Ethereum blockchain using the MetaMask interface.

  % monero-wallet-cli --stagenet --wallet-file sp --password "" integrated_address
  % Random payment ID: <2b6d65d7d48b7896>
  % Matching integrated address: 5LHmrsVsQM2Q2TgqufX4A5gKPpxy1czHULDyVc84omvnh1nQLVmqXk4VBuy8WnX1AXfKxDx7xuASAc6svkZqGVkL1XkUBWT7QejHymEaYM
  \item[3.] The customer (using the webapp) checks the transaction status on the Ethereum blockchain by calling \texttt{getProvision} with arguments \texttt{customerPubKey} and \texttt{provisionID}.
  % monero-wallet-cli --stagenet --wallet-file customer --password "" transfer 5LHmrsVsQM2Q2TgqufX4A5gKPpxy1czHULDyVc84omvnh1nQLVmqXk4VBuy8WnX1AXfKxDx7xuASAc6svkZqGVkL1XkUBWT7QejHymEaYM 1
  % Transaction successfully submitted, transaction <7d89c04de458cfb76a811d5eb325075dec59f7a993c3bf7ce37f9e3a1630af65>
  % monero-wallet-cli --stagenet --wallet-file customer --password "" get_tx_key 7d89c04de458cfb76a811d5eb325075dec59f7a993c3bf7ce37f9e3a1630af65
  % Tx key: 1364dc848a752bf52011f4a63d98bcb16091cacd985713b6b5264b3ede6de40f

  \item[4.] The customer sends the payment (using \texttt{monero-wallet-cli transfer}) to the \texttt{paymentAddress} specified in the smart contract and stores the payment receipt (using \texttt{monero-wallet-cli get\_tex\_key <tx-id>}) in case of a dispute.
  \item[5.] Once the SP notices the payment on the Monero blockchain, it starts providing the service and outputs the file \texttt{result.pdf}.

  \item[6.] The SP uploads the file \texttt{result.pdf} to the IPFS and Filecoin networks using Powergate. As a result, the SP receives the content identifier \texttt{cid}, as well as \texttt{dealID} and \texttt{minerID}.

  \item[7.] The SP submits a Proof of Provision transaction to the Ethereum blockchain by calling \texttt{proofOfProvision} with arguments \texttt{customer\-PubKey}, \texttt{provisionID}, \texttt{cid} and \texttt{dealID}.

  \item[8.] Meanwhile, the customer subscribes to Ethereum and waits for the SP to publish the Proof of Provision.
 Once the Proof Of Provision is published, the customer downloads the result using either the IPFS network using \url{https://dweb.link/<cid>} or Lotus network using \texttt{lotus retrieve <cid> <minerID>}.

  \item[9.] The results are then decrypted using the customer's previously stored private key. If everything is correct, the customer is satisfied with the service and the protocol ends, otherwise the customer can initiate a dispute.

\end{enumerate}

\ifx\FORMAT\SINGLECOLUMN
\noindent%
\begin{minipage}{\linewidth}
\makebox[\linewidth]{
\includegraphics[height=0.95\textheight,keepaspectratio]{anonser-experiment1.pdf}}
\captionof{figure}{The steps of the experiment, the first part.}\label{fig:anonser-experiment1}
\end{minipage}

\noindent%
\begin{minipage}{\linewidth}
\makebox[\linewidth]{
\includegraphics[height=0.95\textheight,keepaspectratio]{anonser-experiment2.pdf}}
\captionof{figure}{The steps of the experiment, the second part.}\label{fig:anonser-experiment2}
\end{minipage}
\else
\begin{figure*}
  \centering
  \includegraphics[height=0.95\textheight,keepaspectratio]{anonser-experiment1.pdf}
  \caption{The steps of the experiment, the first part.}\label{fig:anonser-experiment1}
\end{figure*}

\begin{figure*}
  \includegraphics[height=0.95\textheight,keepaspectratio]{anonser-experiment2.pdf}
  \caption{The steps of the experiment, the second part.}\label{fig:anonser-experiment2}
\end{figure*}

\fi
\subsection{Results}

\paragraph{Fariness}
As shown in Section~\ref{sec:steps} and~\ref{app:proof-of-fairness}, 
the protocol is fair. It is achieved by an undeniable hand-shake mechanism in which the SP first publishes $\mathrm{PoD}$ (step 2.), committing to package delivery and service deadlines, and then the customer accepts it by paying for the service or not (step 3.).

Once the payment is made, the SP remains in the advantageous position. Having agreed on the service delivery times, the SP is incentivised to to deliver the service and publish the results and the PoP before the deadline (step 7.); otherwise, the customer - having all the evidence - can initiate a dispute and punish the SP, so rational parties will follow the protocol.

Non-repudiation without TTP is achieved through the use of blockchain and digital signatures. The blockchain guarantees that any change to the state of the smart contract is visible to everyone, and only the SP is allowed to change its state.

\paragraph{Anonymity}
We achieve anonymity by decoupling personal information from materials, payment and communication. We used anonymous payment methods such as cash or privacy-preserving payment blockchains (e.g. Monero) and decentralised storage networks such as IPFS and Filecoin, allowing the customer to interact with the protocol without revealing their identity at any stage of the protocol.

\paragraph{Provable Results Availability}\label{sec:provable-results-availability}
Content addressable networks such as IPFS cannot guarantee the availability of the content\footnote{Nothing prevents the SP from publishing the result, receiving the $\mathrm{cid}$, publishing $\mathrm{PoP}$, and immediately removing the result from local storage. In the event of a dispute, the SP can re-upload the content to prove its availability. The SP has no motivation to proceed with this kind of misbehaviour other than to put the customer in a disadvantageous position caused by the lost dispute.} However, Filecoin~\cite{protocollabsFilecoinDecentralizedStorage2017}, which acts as an incentivisation layer on top of IPFS, increases content availability through economic incentivisation (i.e. punishment in case of lack of proof of content storage~\cite{filecoinSlashing}). Compared to typical blockchain networks, Filecoin focuses on data storage, making it cheaper than storing it on blockchains like Bitcoin or Ethereum.

The SP uploads the result to both the IPFS and Filecoin networks (via Powergate), making access to the results free in the case of normal behaviour, and highly available in the case that the SP stops serving the result from its node.

\paragraph{Costs}
Deploying a smart contract and invoking functions on the Ethereum blockchain costs gas. The cost of gas is proportional to the amount of computation required to execute a transaction.

Deploying a smart contract consumed 1456577 gas.
Proof of delivery consumed 129649 gas.
Proof of provision consumed 149130 gas.

Although our experiment was conducted on the testnet, the amount of gas is the same on the mainnet.

The cost of gas is denominated in $\mathrm{ETH}$. The price of gas at the time of the experiment (Jan. 03, 2023, \url{https://etherscan.io/gastracker}) was $0.000000002227 \frac{\mathrm{ETH}}{\mathrm gas}$, and the price of 1 $\mathrm{ETH}$ was $1261.97 \mathrm{USD}$.

In a result, the cost of:
\begin{itemize}
  \item Deploying the smart contract cost $0.000000002227 \frac{\mathrm{ETH}}{\mathrm gas} \cdot 1456577 \mathrm{gas} \cdot 1261.97 \frac{\mathrm{USD}}{\mathrm{ETH}} \approx 4.09 \mathrm{USD}$; 
  \item Proof of delivery cost $0.000000002227 \mathrm{\frac{ETH}{gas}} \cdot 129649 \mathrm{gas} \cdot 1261.97 \frac{\mathrm{USD}}{\mathrm{ETH}} \approx 0.29 \mathrm{USD}$; 
  \item Proof of provision cost $0.000000002227 \mathrm{\frac{ETH}{gas}} \cdot 149130 \mathrm{gas} \cdot 1261.97 \frac{\mathrm{USD}}{\mathrm{ETH}} \approx 0.33 \mathrm{USD}$.
\end{itemize}

\section{Discussion}
\label{sec:discussion}

\subsection{Dispute Resolution Service}\label{sec:decentralised-justice}
Centralised Dispute Resolution Service is the biggest obstacle to the realisation of a system that is compliant with the Web3 postulates~\cite{ethereumWhatWeb3Why2023}.

Possible directions for mitigating such problems are either (i) replacing local justice with blockchain dispute resolution systems, such as those proposed in Themis~\cite{mengThemisDecentralizedEscrow2019}, Kleros~\cite{bergollaKlerosSociolegalCase2022, gudkovCrowdArbitrationBlockchain2020}, Aragon Court~\cite{aragonDecentralizedDisputeResolution}, LTO Network~\cite{ltonetworkNextGenBlockchainB2B}, and other Online Dispute Resolution platforms~\cite{allenGovernanceBlockchainDispute2019}; or (ii) make it infeasible to provide incorrect results.

The first approach is more feasible in the near future. It would require the creation of a large set of experts in a field who, in the case of a dispute, would receive all the proofs ($\mathrm{PoD}$, $\mathrm{PoP}$, payment $\mathrm{receipt}$ as well as any other proofs relevant to the case) that could be queried by the experts in a zero-knowledge fashion, i.e. they could ask a limited number of questions of the proofs and get yes/no answers. The case would be completely confidential as they would not be able to query any personal information. Experts would be incentivised to participate in the pool by the fee system. They would be incentivised to vote honestly by the stake they would have to lock and the reward/punishment they would receive for a correct/incorrect judgement, correctness being determined by the quorum of votes.

The second is more futuristic. Let us assume that the service we are performing is fully computable. Then it would be possible to use proofs of correctness of computations~\cite{ben-sassonSNARKsVerifyingProgram2013} to enforce that only correct computations (and hence correct services) are accepted. This would require the entire service verification to be computable, which is difficult to achieve in settings where physical materials (such as blood) are examined. Specifically, the problem boils down to ``How to represent blood digitally?'' If we could represent urine, blood, saliva or any other physical material in a binary format and let the customer take a sample, discrete it and send it to the SP, then the whole chain of integrity could be ensured. This would make it impossible to provide the wrong service and therefore avoid disputes.

\subsection{Self-sovereign identities}
Our research in this area has shown that some jurisdictions require SPs to link the diagnosis to the customer's personal data. For example, in Poland, all laboratories performing medical diagnostic tests and collecting the material (except for HIV tests) are required to uniquely identify and verify the identity of the patient from whom the material was collected~\cite{ministerstwozdrowiaRegulationMinisterHealth2006}.

This conflicts with the main aim of our protocol, which is to prevent the collection of any identifying information.

A promising solution would be to use self-sovereign identities (SSIs)~\cite{muhleSurveyEssentialComponents2018}, especially the verifiable claims. A trusted authority (e.g. a government) would issue a one-time claim for a customer, which would be accepted by the SP as a legitimate personal identification. The SP would associate the diagnosis result with the provided DID. The DID itself would contain no personal information, so the SP would learn nothing about the customer's identity beyond the random-looking identification. The DID could be de-anonymised in cooperation with the government.

However, as SSI is a relatively new technology and the government has not yet adopted it, we decided to leave the discussion of this topic for future work.

\subsection{Formal Verification}\label{sec:formal-verification}
Following the work of~\cite{birjoveanuFormalVerificationMultiparty2022}, the security analysis of our protocol could be improved by using automatic formal verification tools, such as AVISPA~\cite{armandoAVISPAToolAutomated2005}. It would require the specification of the protocol using the High-Level Protocol Specification Language (HLPSL)~\cite{chevalierHighLevelProtocol2004}. The specification would then be translated into the AVISPA intermediate language and verified using the AVISPA theorem prover. The verification would be performed by the AVISPA model checker, which would check the protocol against the security properties.

\section{Conclusions}\label{sec:conclusion}
In this work, we have focused on enabling the provision of services without the collection of personal data. Our aim was to enable services such as genetic testing, testing for paternity, venereal diseases, HIV, drugs and steroids, or anonymous legal advice.

We found that the current state of the art was not sufficient to achieve this goal. We have therefore proposed a service delivery protocol that simultaneously achieves anonymity, fairness, dispute resolution, TTP-lessness and supports physical materials.

Payments are made in either cash or anonymous cryptocurrencies. The result of the service is published on a content-addressable p2p network. The dispute can be resolved by submitting the collected evidence to the dispute resolution service.

Using the definition~\ref{def:fairness}, we showed that the protocol achieves fairness by publishing proof of delivery, proof of payment, and proof of provisioning on the message board.

Finally, we identified other improvements such as decentralised dispute resolution, self-sovereign identifiers, and anonymous courier delivery.

\section*{Data availability}
No data was used for the research described in the article.

The prototype is available at \url{https://anonser.stan.bar}.

The source code is available at \url{https://github.com/stanbar/anonymous-provision-of-services-via-blockchain}.

\appendix

\section{Proof of fairness}\label{app:proof-of-fairness}
Below we describe each step and the reasoning behind the outcome position.
We use the notation introduced in Section~\ref{sec:fairness-model} to analyse each position in the protocol and the fairness Definition~\ref{def:fairness} to show the fairness of the protocol.

\newcommand{\AgreeablePath}{Agreeable path:}
\newcommand{\DisputePath}{The \customer{} starts a dispute:}
\newcommand{\Fairness}{Fairness:}
\newcommand{\CustomerTurn}[0]{\expandafter\MakeUppercase \customer{} turn:}
\newcommand{\SPTurn}[0]{\sp{} turn:}

\newcommand{\CanFollowToOne}[2]{The #1 can follow the protocol to the non-disadvantaged position #2}
\newcommand{\CanDoNothing}[1]{The #1 can do nothing and always ends up in the non-disadvantaged position}
\newcommand{\CanDoAnything}[1]{The #1 can do anything and always ends up in the non-disadvantaged position}
\newcommand{\Pos}[4]{$\operatorname{\sigma_{#1, #2, #3} = #4}$}
\newcommand{\WinForTheSameReason}[1]{The #1 wins the dispute for the same reason}
\newcommand{\LoseForTheSameReason}[1]{The #1 loses the dispute for the same reason}
\newcommand{\ActedAbnormallyThen}[1]{The #1 acted abnormally, then:}
\newcommand{\CustomerPaidButDidntGetResult}{The customer ends up in a disadvantageous position, because he has paid in advance, but hasn't received the result}
\newcommand{\SpReceivedThePayment}{The SP ends up in the advantageous position, having received the payment}

\newcommand{\CustomerLosesBeforePayment}{The customer loses the dispute because the SP is not obliged to do anything until the transaction is paid}
\newcommand{\CustomerLosesBeforePoP}{The customer loses the dispute because the SP is still able to publish the PoP within the agreed timeframe}

\newcommand{\RemainsIn}[2]{The #1 remains in the #2 position}

\subsubsection*{Step 1. \CustomerTurn{} Package delivery}\label{step-1-deliver-package}

The protocol starts when the customer correctly completes the first step of the protocol, i.e. delivers the package to the SP.

The case where the customer does not deliver the package is not considered as it is not part of the protocol.

\begin{itemize}
\item \AgreeablePath
  \begin{itemize}
    \item  \Pos{1}{c}{\normal}{\neutral}, the customer risked his materials but did not pay for the transaction and therefore ends up in a neutral position (see Assumption 10. in Section \ref{sec:assumptions}).
    \item \Pos{1}{s}{\normal}{\neutral}, the SP ends up in a neutral position as she did not spend any resources and the package did not bring her any value.
  \end{itemize}
\item \DisputePath
  \begin{itemize}
    \item \Pos{1}{c}{\dispute}{\minus}, \CustomerLosesBeforePayment{}.
    \item \Pos{1}{s}{\dispute}{\neutral}, \WinForTheSameReason{SP}.
  \end{itemize}
\end{itemize}

\Fairness

\begin{itemize}
  \item \CanFollowToOne{customer}{\Pos{1}{c}{n}{\neutral}}
  \item \CanDoNothing{SP}
\end{itemize}

\subsubsection*{Step 2. \SPTurn{} Proof of Delivery}\label{step-2-proof-of-delivery}

The SP publishes the PoD, then:

\begin{itemize}
  \item \AgreeablePath
    \begin{itemize}
      \item \Pos{2}{c}{\normal}{\neutral}, the customer remains in the neutral position as the PoD allows him to pay for the transaction but does not oblige him to do anything.
      \item \Pos{2}{s}{\normal}{\neutral}, the SP remains in the neutral position as the package has not brought her any value and she has not spent any resources to provide the service.
    \end{itemize}

  \item \DisputePath
    \begin{itemize}
      \item \Pos{2}{c}{\dispute}{\minus}, \CustomerLosesBeforePayment{}.
      \item \Pos{2}{s}{\dispute}{\neutral}, \WinForTheSameReason{SP}.
    \end{itemize}
\end{itemize}

\ActedAbnormallyThen{\sp}

\begin{itemize}
\item \AgreeablePath
  \begin{itemize}
    \item \Pos{2}{c}{\abnormal}{\neutral}, the customer remains in the neutral position as he is not obliged\footnote{By not obliged we understand the situation where a party does not risk any resources by not taking the action} to agree with the incorrect $\mathrm{PoD}$.
    \item \Pos{2}{s}{\abnormal}{\neutral}, the SP remains in the neutral position as the package has not brought her any value and she has not spent any resources to provide the service.
  \end{itemize}
\item \DisputePath
  \begin{itemize}
    \item \Pos{2}{c}{\abdispute}{\minus}, \CustomerLosesBeforePayment{}, not even to publish correct $\mathrm{PoD}$.
    \item \Pos{2}{s}{\abdispute}{\neutral}, \WinForTheSameReason{SP}.
  \end{itemize}
\end{itemize}

\Fairness

\begin{itemize}
  \item \CanDoAnything{SP}.
  \item customer can either wait (if the SP is following the protocol) or abandon the transaction (if the SP is acting abnormally). In both cases the customer ends up in a non-disadvantaged position \Pos{2}{c}{\normal}{\neutral} or \Pos{2}{c}{\abnormal}{\neutral}.
\end{itemize}

\subsubsection*{Step 3. \CustomerTurn{} Get Proof of Delivery}\label{step-3-get-proof-of-delivery}

The customer got the \PoD, then:

\begin{itemize}
\item \AgreeablePath
  \begin{itemize}
    \item \Pos{3}{c}{\normal}{\neutral}, \RemainsIn{customer}{neutral}.
    \item \Pos{3}{s}{\normal}{\neutral}, \RemainsIn{SP}{neutral}.
  \end{itemize}
\item \DisputePath
  \begin{itemize}
    \item \Pos{3}{c}{\dispute}{\minus}, \CustomerLosesBeforePayment{}.
    \item \Pos{3}{s}{\dispute}{\neutral}, \WinForTheSameReason{SP}.
  \end{itemize}
\end{itemize}

\ActedAbnormallyThen{\customer}

\begin{itemize}
\item \AgreeablePath
  \begin{itemize}
    \item \Pos{3}{c}{\abnormal}{\neutral}, \RemainsIn{customer}{neutral}.
    \item \Pos{3}{s}{\abnormal}{\neutral}, \RemainsIn{SP}{neutral}.
  \end{itemize}
\item \DisputePath
  \begin{itemize}
    \item \Pos{3}{c}{\abdispute}{\minus}, \CustomerLosesBeforePayment{}.
    \item \Pos{3}{s}{\abdispute}{\neutral}, \WinForTheSameReason{SP}.
  \end{itemize}
\end{itemize}

\Fairness

\begin{itemize}
  \item \CanFollowToOne{customer}{\Pos{3}{c}{\normal}{\neutral}}.
  \item \CanDoNothing{SP}.
\end{itemize}

\subsubsection*{Step 4. \CustomerTurn{} Payment}

The customer paid the transaction, then:

\begin{itemize}
\item \AgreeablePath
  \begin{itemize}
    \item \Pos{4}{c}{\normal}{\minus}, the customer has paid in advance.
    \item \Pos{4}{s}{\normal}{\plus}, the SP has received the payment but has not spent his resources yet.
  \end{itemize}
\item \DisputePath
  \begin{itemize}
    \item \Pos{4}{c}{\dispute}{\minus}, \CustomerLosesBeforePoP{}.
    \item \Pos{4}{s}{\dispute}{\neutral}, \WinForTheSameReason{SP}.
  \end{itemize}
\end{itemize}

\ActedAbnormallyThen{\customer}

\begin{itemize}
\item \AgreeablePath
  \begin{itemize}
    \item \Pos{4}{c}{\abnormal}{\neutral}, the customer ends up in the neutral position as he has not spent his funds.
    \item \Pos{4}{s}{\abnormal}{\neutral}, the SP ends up in the neutral position as she neither received the payment nor spent her resources.
  \end{itemize}
\item \DisputePath
  \begin{itemize}
    \item \Pos{4}{c}{\abdispute}{\minus}, \CustomerLosesBeforePayment{}.
    \item \Pos{4}{s}{\abdispute}{\neutral}, \WinForTheSameReason{SP}.
  \end{itemize}
\end{itemize}

\Fairness

\newcommand{\CustomerRiskTemporaryDisadvantagedPosition}[1]{The customer, following the 9th assumption described in Section~\ref{sec:assumptions}, risks the temporary disadvantaged position #1 in favour of a later better position \Pos{9}{s}{\normal}{\plus}; in the meantime, he can get out of the disadvantaged position if the SP misbehaves in any of the following steps.}

\begin{itemize}
  \item \CustomerRiskTemporaryDisadvantagedPosition{\Pos{4}{c}{\normal}{\minus}}.
  \item \CanDoNothing{SP}.
\end{itemize}

\subsubsection*{Step 5. \SPTurn{} Provision of service}

The \sp{} did the provision of service, then:

\begin{itemize}
\item \AgreeablePath
  \begin{itemize}
    \item \Pos{5}{c}{\normal}{\minus}, \RemainsIn{\customer}{disadvantaged} as he hasn't received the result.
    \item \Pos{5}{s}{\normal}{\plus}, \RemainsIn{\sp}{advantaged} as she has received the payment.
  \end{itemize}
\item \DisputePath
  \begin{itemize}
    \item \Pos{5}{c}{\dispute}{\minus}, \CustomerLosesBeforePoP{}.
    \item \Pos{5}{s}{\dispute}{\neutral}, \WinForTheSameReason{SP}.
  \end{itemize}
\end{itemize}

\ActedAbnormallyThen{\sp}

\begin{itemize}
\item \AgreeablePath
  \begin{itemize}
    \item \Pos{5}{c}{\abnormal}{\minus}, \CustomerPaidButDidntGetResult{}. 
    \item \Pos{5}{s}{\abnormal}{\plus}, \SpReceivedThePayment{}.
  \end{itemize}
\item \DisputePath
  \begin{itemize}
    \item \Pos{5}{c}{\abdispute}{\neutral} The customer wins the dispute because the SP has not provided the service within the time agreed in the \PoD{}, and therefore the SP is unable to upload the result and publish the \PoP{} on time.
    \item \Pos{5}{s}{\abdispute}{\minus}, \LoseForTheSameReason{SP}.
  \end{itemize}
\end{itemize}

\Fairness
\newcommand{\SPCanDoBothButFollowIsSafe}[1]{The SP can follow the protocol and move to the advantaged position \Pos{#1}{s}{\normal}{\plus}, or act abnormally (not provide the service) and also move to the advantaged position \Pos{#1}{s}{\abnormal}{\plus}; however, the second option puts her at risk of terminating the protocol at \Pos{#1}{s}{\abdispute}{\minus} if the customer is rational and starts a dispute; hence, the SP should choose the first option}

\begin{itemize}
  \item \CustomerRiskTemporaryDisadvantagedPosition{\Pos{5}{c}{\normal}{\minus}}.
  \item \SPCanDoBothButFollowIsSafe{5}.
\end{itemize}

\subsubsection*{Step 6. \SPTurn{} Upload result}\label{step-6-publication-of-results}

The SP uploaded the result on time, then:

\begin{itemize}
\item \AgreeablePath
  \begin{itemize}
    \item \Pos{6}{c}{\normal}{\minus}, \RemainsIn{\customer}{disadvantaged} as he has not received the result.
    \item \Pos{6}{s}{\normal}{\plus}, \RemainsIn{SP}{advantaged} as she has received the payment.
      \end{itemize}
\item \DisputePath
  \begin{itemize}
    \item \Pos{6}{c}{\dispute}{\minus}, \CustomerLosesBeforePoP{}.
    \item \Pos{6}{s}{\dispute}{\neutral}, \WinForTheSameReason{SP}.

  \end{itemize}
\end{itemize}

\ActedAbnormallyThen{\sp}

\begin{itemize}
\item \AgreeablePath
  \begin{itemize}
    \item \Pos{6}{c}{\abnormal}{\minus}, \CustomerPaidButDidntGetResult{}.
    \item \Pos{6}{s}{\abnormal}{\plus}, \SpReceivedThePayment{}.
  \end{itemize}
\item \DisputePath
  \begin{itemize}
    \item \Pos{6}{c}{\abdispute}{\neutral}, the customer wins the dispute because the SP has not uploaded the service within the time agreed in the \PoD{} and the SP will not be able to publish the \PoP{} on time.
    \Pos{6}{s}{\abdispute}{\minus}, \LoseForTheSameReason{SP}.
  \end{itemize}
\end{itemize}

\Fairness

\begin{itemize}
  \item \CustomerRiskTemporaryDisadvantagedPosition{\Pos{6}{c}{\normal}{\minus}}.
  \item \SPCanDoBothButFollowIsSafe{6}.
\end{itemize}

\subsubsection*{Step 7. \SPTurn{} Proof of provision}\label{step-7-publication-of-proof-of-provision}

The SP published \PoP{} on time, then:

\newcommand{\CustomerLosesBecauseSPCanProveBeingCorrect}{the \customer{} loses the dispute as the \sp{} has published all evidences to prove her correct behaviour}

\begin{itemize}
  \item \AgreeablePath
    \begin{itemize}
      \item \Pos{7}{c}{\normal}{\minus}, the customer has not received the result. Therefore, he remains in a disadvantaged position. 
      \item \Pos{7}{s}{\normal}{\plus}, the SP has published all the evidence to prove her correct behaviour, so she remains in an advantageous position for the rest of the protocol.
    \end{itemize}
  \item \DisputePath
    \begin{itemize}
      \item \Pos{7}{c}{\dispute}{\minus}, \CustomerLosesBecauseSPCanProveBeingCorrect{}.
      \item \Pos{7}{s}{\dispute}{\plus}, \WinForTheSameReason{SP}.
    \end{itemize}
\end{itemize}

\ActedAbnormallyThen{\sp}

\begin{itemize}
\item \AgreeablePath
  \begin{itemize}
    \item \Pos{7}{c}{\abnormal}{\minus}, \CustomerPaidButDidntGetResult{}.
    \item \Pos{7}{s}{\abnormal}{\plus}, \SpReceivedThePayment{}.
  \end{itemize}
\item \DisputePath
  \begin{itemize}
    \item \Pos{7}{c}{\abdispute}{\neutral}, the customer wins the dispute because the SP did not publish the correct \PoP{} on time.
    \item \Pos{7}{s}{\abdispute}{\minus}, \LoseForTheSameReason{SP}.
  \end{itemize}
\end{itemize}

\Fairness

\begin{itemize}
  \item \CustomerRiskTemporaryDisadvantagedPosition{\Pos{7}{c}{\normal}{\minus}}.
  \item \SPCanDoBothButFollowIsSafe{7}.
\end{itemize}

\subsubsection*{Step 8. \CustomerTurn{} Get Proof of Provision}\label{step-8-pull-proof-of-provision}

The customer got the \PoP{}, then:

\begin{itemize}
\item \AgreeablePath
  \begin{itemize}
    \item \Pos{8}{c}{\normal}{\minus}, the customer gets the \cid{}, but not the result yet.
    \item \Pos{8}{s}{\normal}{\plus}, \RemainsIn{\sp}{advantaged}.
  \end{itemize}
\item \DisputePath

  \begin{itemize}
    \item \Pos{8}{c}{\dispute}{\minus}, \CustomerLosesBecauseSPCanProveBeingCorrect{}.
    \item \Pos{8}{s}{\dispute}{\plus}, \WinForTheSameReason{SP}.
  \end{itemize}
\end{itemize}

\ActedAbnormallyThen{\customer}

\begin{itemize}
\item \AgreeablePath
  \begin{itemize}
    \item \Pos{8}{c}{\abnormal}{\minus}, the customer has paid for the transaction but does not have access to the $cid$ and therefore cannot get the result from the storage network.
    \item \Pos{8}{s}{\abnormal}{\plus}, \SpReceivedThePayment{}.
  \end{itemize}
\item \DisputePath
  \begin{itemize}
    \item \Pos{8}{c}{\abdispute}{\minus}, \CustomerLosesBecauseSPCanProveBeingCorrect{}
    \item \Pos{8}{s}{\abdispute}{\neutral}, \WinForTheSameReason{SP}.
  \end{itemize}
\end{itemize}

\Fairness

\begin{itemize}
  \item \CustomerRiskTemporaryDisadvantagedPosition{\Pos{8}{c}{\normal}{\minus}}.
  \item \CanDoNothing{} \Pos{8}{s}{\normal}{\plus} or \Pos{8}{s}{\abnormal}{\plus}.
\end{itemize}

\subsubsection*{Step 9. \CustomerTurn{} Download result}\label{step-9-retrieval-of-results}

The customer downloaded the result, then:

\begin{itemize}
\item \AgreeablePath
  \begin{itemize}
    \item \Pos{9}{c}{\normal}{\plus}, The customer has received the result, therefore he finishes the protocol in an advantaged position.
    \item \Pos{9}{s}{\normal}{\plus}, \RemainsIn{\sp}{advantaged}.
  \end{itemize}
\item \DisputePath
  \begin{itemize}
    \item \Pos{9}{c}{\dispute}{\minus}, \CustomerLosesBecauseSPCanProveBeingCorrect{}.
    \item \Pos{9}{s}{\dispute}{\plus}, \WinForTheSameReason{SP}.
  \end{itemize}
\end{itemize}

\ActedAbnormallyThen{\customer}

\begin{itemize}
\item \AgreeablePath
  \begin{itemize}
    \item \Pos{9}{c}{\abnormal}{\minus}, the customer ends up in a disadvantaged position, as he ends up with the incorrect result.
    \item \Pos{9}{s}{\abnormal}{\plus}, the SP ends up in the advantageous position of having received the payment but not having spent his resources.
  \end{itemize}
\item \DisputePath
  \begin{itemize}
    \item \Pos{9}{c}{\abdispute}{\neutral}, the customer wins the case and ends up in the neutral position.
    \item \Pos{9}{s}{\abdispute}{\minus}, the SP loses the case and ends up in the disadvantaged position.
  \end{itemize}
\end{itemize}

\Fairness

\begin{itemize}
  \item \CanFollowToOne{\customer}{\Pos{9}{c}{\normal}{\plus}}.
  \item \CanDoNothing{} \Pos{9}{s}{\normal}{\plus} or \Pos{9}{s}{\abnormal}{\plus}. 
\end{itemize}

\bibliographystyle{spbasic}
\bibliography{bibliography-betterbibtex}

\end{document}

### 2024-06-03 paper/main.tex
update the fairness and costs suggestions

@@
 \label{sec:introduction}
-Diagnostic services such as paternity tests, doping tests or venereal disease tests are carried out in diagnostic centres that require customers to provide biological material such as blood, urine, stool or saliva.
-Unfortunately, customers are often forced to reveal their identity in order to complete transactions.
-Such a combination of personal information with biological materials exposes customers to significant privacy risks.
-
-\begin{sloppypar}
-Other examples of sensitive services include anonymous complaints or legal services, such as legal advice, which may require disclosure of financial transaction history and confidential legal documents.
-Banking services, such as credit scoring, may require sensitive personal information, such as medical records and financial transaction history.
-\end{sloppypar}
-
-Providing personal information exposes users to a myriad of privacy risks, ranging from the potential loss of control over personal information to more severe threats like identity theft, data breaches, and unsanctioned monitoring.
-Such sensitive information is highly valuable to a potential attacker as it can be exploited for insider leaks, unauthorized entry, or financial profit.
-For instance, this data might be sold to marketers, banks, other corporations, government bodies, or cybercriminals.
-Consequently, this could unintentionally violate regulations like GDPR or CCPA, result in targeted advertising, or lead to crimes such as identity theft or unlawful tracking and surveillance~\cite{smithInformationPrivacyResearch2011}.
-
-Public figures such as influencers, politicians or celebrities are particularly vulnerable to this type of attack, as exposure of their health records, purchasing habits or legal documents can threaten their reputation, position or be used for blackmail.
-
-The problem is amplified when personal information is linked to health records, legal documents or biological materials such as DNA, saliva or blood.
+Diagnostic services such as paternity tests, doping tests, or venereal disease tests require customers to provide biological material such as blood, urine, stool, or saliva.
+Unfortunately, customers often have to reveal their identity to complete transactions, exposing them to significant privacy risks.
+
+Other examples of sensitive services include anonymous complaints or legal services, like legal advice, which may require disclosure of financial transaction history and confidential legal documents.
+Banking services, such as credit scoring, may require sensitive personal information like medical records and financial transaction history.
+
+Providing personal information exposes users to a myriad of privacy risks, ranging from the potential loss of control over personal information to severe threats like identity theft, data breaches, and unsanctioned monitoring.
+Sensitive information is valuable to attackers, leading to potential unauthorized uses.
+This situation could unintentionally violate regulations like GDPR or CCPA, result in targeted advertising, or lead to crimes like identity theft or unlawful tracking and surveillance~\cite{smithInformationPrivacyResearch2011}.
+
+Public figures such as influencers, politicians, or celebrities are particularly vulnerable to this type of attack, as exposure of their health records, purchasing habits, or legal documents can threaten their reputation, position, or be used for blackmail.
+
+The problem is amplified when personal information is linked to health records, legal documents, or biological materials such as DNA, saliva, or blood.
 In such situations, customers may be reluctant to provide their personal information to the SP and therefore withdraw from the service.
-\textbf{Both parties are harmed as the customer does not receive a diagnosis relevant to their health and the SP loses potential customers.}~\cite{klitzmanExclusionGeneticInformation2010,blackPresymptomaticTestingConfidentiality2021}
-
-In the majority of healthcare system, the critical data managed typically resides in the Electronic Medical Records (EMRs), which is consistently regarded as confidential information requiring robust security measures~\cite{jinReviewSecurePrivacypreserving2019}~\cite{keshtaSecurityPrivacyElectronic2021}.
-
-Maintaining the privacy of health data seems to be open and active area of research in the field of Privacy-Preserving Data Mining (PPDM) ~\cite{nareshPrivacyPreservingData2023,linPPSFOpensourcePrivacypreserving2018,hewagePrivacypreservingDataStream2023}.
-The recent research in this area focuses on employing methods of anonymisation and hiding sensitive information of the EMRs~\cite{hamdiEnhancingSecurityPrivacy2023, sharmaPrivacyPreservingData2019, wuHidingSensitiveInformation2021}, or securing the interaction between patient and Healthcare system~\cite{zhangPrivacyProtectionTelecare2016, mehmoodAnonymousAuthenticationScheme2018, khasimImprovedFastSecure2022}.
-
-\begin{sloppypar}
+Both parties are harmed as the customer does not receive a diagnosis relevant to their health and the SP loses potential customers~\cite{klitzmanExclusionGeneticInformation2010,blackPresymptomaticTestingConfidentiality2021}.
+
+In the majority of healthcare systems, the critical data managed typically resides in the Electronic Medical Records (EMRs), which is consistently regarded as confidential information requiring robust security measures~\cite{jinReviewSecurePrivacypreserving2019,keshtaSecurityPrivacyElectronic2021}.
+
+Maintaining the privacy of health data seems to be an open and active area of research in the field of Privacy-Preserving Data Mining (PPDM)~\cite{nareshPrivacyPreservingData2023,linPPSFOpensourcePrivacypreserving2018,hewagePrivacypreservingDataStream2023}.
+Recent research in this area focuses on employing methods of anonymization and hiding sensitive information of the EMRs~\cite{hamdiEnhancingSecurityPrivacy2023, sharmaPrivacyPreservingData2019, wuHidingSensitiveInformation2021}, or securing the interaction between patient and Healthcare system~\cite{zhangPrivacyProtectionTelecare2016, mehmoodAnonymousAuthenticationScheme2018, khasimImprovedFastSecure2022}.
+
 Authors of~\cite{blackPresymptomaticTestingConfidentiality2021} highlight that after their organisation adopted Electronic Medical Record (EMR) systems, they could no longer promise the same confidentiality assurances.
-\end{sloppypar}
-
-Klitzman~\cite{klitzmanExclusionGeneticInformation2010} examined exclusion of genetic data from EMR, noting that patients frequently distrust healthcare facilities and choose not to share their genetic test results with doctors, fearing that this information might be recorded in their EMR.
-
-In our study, we focus on the possibility of carrying out services without revealing any personal information — solving the problem of privacy at a much earlier stage, before any personal information gets into EMR system.
+
+Klitzman~\cite{klitzmanExclusionGeneticInformation2010} examined the exclusion of genetic data from EMR, noting that patients frequently distrust healthcare facilities and choose not to share their genetic test results with doctors, fearing that this information might be recorded in their EMR.
+
+In our study, we focus on the possibility of carrying out services without revealing any personal information — solving the problem of privacy at a much earlier stage, before any personal information gets into the EMR system.
 
@@
 
-\begin{sloppypar}
 Examples of services that would benefit from the anonymity property are:
-\end{sloppypar}
 
@@
   \item \textbf{Confidentiality in Medical Testing}: Patients who are willing to take a test, e.g.
-for drugs, STDs, paternity or steroids, have a strong incentive to keep the whole process private.
+for drugs, STDs, paternity, or steroids, have a strong incentive to keep the whole process private.
 The mere fact that they have taken the test—without revealing the result—is suggestive enough to be used as a premise in the event of a conflict.
-
-    Currently, they have to take the risk that their personal data, materials and results will be stored securely and kept secret from any unauthorised actor (both curious employees and malicious attackers)~\cite{klitzmanExclusionGeneticInformation2010, blackPresymptomaticTestingConfidentiality2021}.
-
-\begin{sloppypar}
+Currently, they have to take the risk that their personal data, materials, and results will be stored securely and kept secret from any unauthorized actor (both curious employees and malicious attackers)~\cite{klitzmanExclusionGeneticInformation2010, blackPresymptomaticTestingConfidentiality2021}.
+
   \item \textbf{Anonymity in Legal Consultations for Entrepreneurs}: Individuals engaged in entrepreneurial activities may want to assess the risks and possible consequences of their actions.
 By revealing their identity, they trust that the lawyer will not use this information for harmful actions.
-\end{sloppypar}
-
-\begin{sloppypar}
+
   \item \textbf{Whistleblowing Platforms}: Employees or citizens witnessing unethical or illegal activities within organizations can report these anonymously without fear of reprisal, job loss, or social stigma, thereby promoting a more transparent and accountable society.
-\end{sloppypar}
-
-\begin{sloppypar}
+
   \item \textbf{Sexual Health and Reproductive Services}: People seeking advice or services related to sexual health, contraception, or abortion might prefer anonymity due to the sensitive nature of these topics and potential societal judgment.
-\end{sloppypar}
-
 \end{itemize}
@@
 Using Solove's Taxonomy of Privacy~\cite{soloveTaxonomyPrivacy2006}, our protocol aims to prevent the following privacy risks: Breach of confidentiality, Disclosure, Identification, and Secondary use.
-We consider the following adversaries: Malicious insiders, Government agencies, Malicious third-party services, Hackers and cybercriminals.
-
-\begin{sloppypar}
-In this work we explore the possibilities of anonymous service provision and propose a protocol that preserves the customer's privacy even in the event of a successful attack.
-Under realistic operational assumptions, we show that \textbf{decoupling personal information from materials, payment and communication achieves a sufficient level of anonymity}.
-\end{sloppypar}
+We consider the following adversaries: Malicious insiders, Government agencies, Malicious third-party services, Hackers, and cybercriminals.
+
+In this work, we explore the possibilities of anonymous service provision and propose a protocol that preserves the customer's privacy even in the event of a successful attack.
+Under realistic operational assumptions, we show that decoupling personal information from materials, payment, and communication achieves a sufficient level of anonymity.
 
 However, a protocol that hides the customer's identity is difficult to secure and coordinate.
-In particular, conflicts between customers and service providers are difficult to resolve when there is subject to accuse.
-
-We observe that the problem of anonymous service provision can be seen as a problem of fair exchange, where parties exchange some goods fairly, i.e.
-either both parties obtain the goods, or they both obtain nothing.
+In particular, conflicts between customers and service providers are difficult to resolve when there is no subject to accuse.
+
+We observe that the problem of anonymous service provision can be seen as a problem of fair exchange, where parties exchange some goods fairly, i.e., either both parties obtain the goods, or they both obtain nothing.
 
@@
 
-\begin{sloppypar}
 Our review shows that none of the current systems is sufficient to achieve the desired goal.
@@
 In the event of a dispute, either due to missed deadlines or incorrect results, the customer can disclose the entire interaction, prove the SP's misbehaviour to the Dispute Resolution Service, and win the dispute.
-\end{sloppypar}
-
-To achieve this goal we use
-\begin{itemize}
-    \item \textbf{Blockchain}, to achieve fairness, i.e. as a means of proving that certain actions took place at a certain time without the Trusted Third Party (TTP).
+
+To achieve this goal we use:
+\begin{itemize}
+  \item \textbf{Blockchain}, to achieve fairness, i.e., as a means of proving that certain actions took place at a certain time without the Trusted Third Party (TTP).
   \item \textbf{Anonymous payment methods}, such as cash or anonymous cryptocurrencies, which allow customers to pay for services anonymously.
-    \item \textbf{Decentralised storage network} (e.g.
-IPFS) to provide results together with a provable storage network (e.g.
-Filecoin) to guarantee that the results are available to the customer even if the SP refuses to share the result.
-
+  \item \textbf{Decentralised storage network} (e.g., IPFS) to provide results together with a provable storage network (e.g., Filecoin) to guarantee that the results are available to the customer even if the SP refuses to share the result.
   \item Cryptography:
@@
     \item \textbf{Symmetric encryption}, to encrypt and decrypt the results published on the public networks.
-        \begin{sloppypar}
-        \item \textbf{Diffie-Helman key exchange (DHKE)}, to derive shared secrets for symmetric encryption.
+    \item \textbf{Diffie-Hellman key exchange (DHKE)}, to derive shared secrets for symmetric encryption.
     \item \textbf{Digital signatures}, to achieve authentication and non-repudiation of actions.
-        \end{sloppypar}
-    \end{itemize}
-
+  \end{itemize}
 \end{itemize}
@@
 
-\begin{sloppypar}
 \begin{itemize}
@@
 \end{itemize}
-\end{sloppypar}
 
@@
 
-\begin{sloppypar}
-The rest of this paper is organised as follows. In Section~\ref{sec:related-works} we review related works. 
+The rest of this paper is organised as follows.
+In Section~\ref{sec:related-works} we review related works.
 Then in Section~\ref{sec:building-blocks} we discuss the building blocks of a dispute resolution system, blockchain as a message board, fairness, anonymous payments, storage network, availability of results and anonymity.
@@
 Finally, Section~\ref{sec:conclusion} concludes the paper.
-\end{sloppypar}
 
@@
 \begin{sloppypar}
-Consequently, our analysis must account for four potential outcomes for each party at every protocol step ($\mathrm{party \in \{C, SP}\}$, $\mathrm{step \in 1..9}$):
+Consequently, our analysis must account for four potential outcomes for each party at every protocol step ($\mathrm{party \in \{C, SP\} }$, $\mathrm{step \in 1..9}$):
 \end{sloppypar}
@@
 \begin{definition}[Fairness] \label{def:fairness}
-A protocol is considered fair iff 
-\begin{equation*}
-\begin{split}
-\forall_{party \in parties}\forall_{\mathrm{step} \in \mathrm{steps}} &\operatorname{can\ move}\\
-&\operatorname{to\ the\ non-disadvantaged\ position} 
-\end{split}
-\end{equation*}
-
+Let $\mathrm{parties} = \{ C, SP \}$, $\mathrm{steps} = 1..9$, and \( M_{\mathrm{s, p}} = \{ 
+\mathrm{\sigma_{s+1,p,\normal}}, 
+\mathrm{\sigma_{s+1,p,\abnormal}}, 
+\mathrm{\sigma_{s+1,p,\dispute}}, 
+\mathrm{\sigma_{s+1,p,\abdispute}}
+\} \) be the set of all possible moves that a party $p$ can make at a step $s$.
+
+% TODO: describe that we include also the further steps because the protocol can be continued after a dispute
+% The customer, following the 9th assumption described in
+% Section 5.2, risks the temporary disadvantaged position
+% σ4,c,n = - in favour of a later better position σ9,s,n = +;
+% in the meantime, he can get out of the disadvantaged position 
+% if the SP misbehaves in any of the following steps
+
+A protocol is considered fair if and only if, for every party involved and at every step of the protocol, there exists a move that allows the party to move to a non-disadvantaged position.
+\begin{equation}
+\forall_{\mathrm{p} \in \mathrm{parties}} \forall_{\mathrm{s} \in \mathrm{steps}} \exists \sigma \in M_{\mathrm{s, p}} \text{ such that } \sigma \neq -
+\end{equation}
 \end{definition}
+
+% TODO: write something at the end of the equatyion as it's usualy done in the math papers
 
@@
 The deployment and operation of smart contracts on the Ethereum blockchain incur gas fees, which are proportional to the computational resources required for transaction execution.
-The following outlines the gas consumption and associated costs for each operation within our protocol, based on the testnet metrics which are analogous to the mainnet:
-
-\begin{itemize}
-    \item \textbf{Smart Contract Deployment}: Consumed 1,456,577 gas units.
-    \item \textbf{Proof of Delivery}: Consumed 129,649 gas units.
-    \item \textbf{Proof of Provision}: Consumed 149,130 gas units.
-\end{itemize}
+The following outlines the gas consumption and associated costs for each operation within our protocol, based on the testnet metrics, which are analogous to the mainnet:
 
@@
 The customer is responsible only for covering the payment transaction fee.
-For transactions using Monero, the fee was approximately 0.000304 XMR at the time of the experiment, with the price of Monero being \$150 USD per XMR\footnote{Cryptocurrency statistics, \url{https://bitinfocharts.com}}.
-
-The incurred costs were as follows:
-\begin{sloppypar}
-\begin{itemize}
-    \item \textbf{Deploying the Smart Contract}: \( 0.000000002227 \frac{\text{ETH}}{\text{gas}} \times 1,456,577 \, \text{gas} \times 1,261.97 \frac{\text{USD}}{\text{ETH}} \approx 4.09 \, \text{USD} \).
-This is a one-time cost, paid by the SP.
-
-    \item \textbf{Proof of Delivery}: \( 0.000000002227 \frac{\text{ETH}}{\text{gas}} \times 129,649 \, \text{gas} \times 1,261.97 \frac{\text{USD}}{\text{ETH}} \approx 0.29 \, \text{USD} \).
-This fee is paid once per transaction, paid by the SP.
-
-    \item \textbf{Payment}: \( 0.000304 \, \text{XMR} \times 150 \frac{\text{USD}}{\text{XMR}} \approx 0.0456 \, \text{USD} \).  This fee is paid once per transaction, paid by the customer.
-
-    \item \textbf{Proof of Provision}: \( 0.000000002227 \frac{\text{ETH}}{\text{gas}} \times 149,130 \, \text{gas} \times 1,261.97 \frac{\text{USD}}{\text{ETH}} \approx 0.33 \, \text{USD} \).
-This fee is paid once per transaction, paid by the SP.
-\end{itemize}
-\end{sloppypar}
+For transactions using Monero, the fee was approx.
+0.000304 XMR at the time of the experiment, with the price of Monero being \$150 USD per XMR\footnote{Cryptocurrency statistics, \url{https://bitinfocharts.com}}.
+
+The incurred costs are summarized in Table~\ref{table:costs}:
+
+\begin{table}[h!]
+\centering
+\caption{Incurred Costs for Protocol Operations}
+\label{table:costs}
+\begin{tabular}{|l|l|l|}
+\hline
+\textbf{Operation}            & \textbf{Gas Units} & \textbf{Cost (USD)} \\ \hline
+Smart Contract Deployment     & 1,456,577          & 4.09                \\ \hline
+Proof of Delivery             & 129,649            & 0.29                \\ \hline
+Payment (Monero)              & -                  & 0.0456              \\ \hline
+Proof of Provision            & 149,130            & 0.33                \\ \hline
+\end{tabular}
+\end{table}
 
@@
 
-To provide a comprehensive performance evaluation of our protocol, we have analyzed the following metrics for each of the blockchain networks:
-
-\begin{itemize}
-    \item \textbf{Ethereum Network}:
-    \begin{itemize}
-        \item \textbf{Block Time}: Approximately 13-15 seconds.
-        \item \textbf{Transaction Throughput}: Ranges between 15-30 transactions per second (TPS).
-        \item \textbf{Transaction Latency}: Approximately 6 minutes.
-    \end{itemize}
-
-    \item \textbf{Monero Network}:
-    \begin{itemize}
-        \item \textbf{Block Time}: Approximately 2 minutes.
-        \item \textbf{Transaction Throughput}: Approximately 4 TPS.
-        \item \textbf{Transaction Latency}: Approximately under 20 minutes.
-    \end{itemize}
-
-    \item \textbf{Filecoin Network}:
-    \begin{itemize}
-        \item \textbf{Block Time}: Approximately 30 seconds.
-        \item \textbf{Transaction Throughput}: Not explicitly stated.
-The network is optimized for storage operations rather than transaction processing, with the throughput being primarily dependent on the storage and retrieval deal proposals.
-        \item \textbf{Transaction Latency}: Storage deal transactions take approximately 5-10 minutes for a 1 MiB file.
-    \end{itemize}
-\end{itemize}
+To provide a comprehensive performance evaluation of our protocol, we have analyzed the following metrics for each of the blockchain networks, as summarized in Table~\ref{table:performance}:
+
+\begin{table}[h!]
+\centering
+\caption{Performance Evaluation Metrics}
+\label{table:performance}
+\begin{tabular}{|l|l|l|l|}
+\hline
+\textbf{Network}     & \textbf{Block Time} & \textbf{Tx Throughput} & \textbf{Tx Latency} \\ \hline
+Ethereum             & 13-15 sec       & 15-30 TPS                       & \textasciitilde{}6 min      \\ \hline
+Monero               & \textasciitilde{}2 min & \textasciitilde{}4 TPS             & \textasciitilde{}20 min \\ \hline
+Filecoin             & 30 s & N/A\footnotemark{}            & 5-10 min \\ 
+& & & for 1 MiB file \\ \hline
+\end{tabular}
+\end{table}
+
+\footnotetext{The network is optimized for storage operations rather than transaction processing, with the throughput being primarily dependent on the storage and retrieval deal proposals.}
 
 These metrics are crucial for understanding the scalability and efficiency of the blockchain networks in question and provide insight into their suitability for various applications within our protocol.
-
 \section{Discussion}
@@
 \begin{itemize}
-  \item \CustomerRiskTemporaryDisadvantagedPosition{\Pos{4}{c}{\normal}{\minus}}.
+  \item \CustomerRiskTemporaryDisadvantagedPosition{\Pos{4}{c}{\normal}{\minus}}
   \item \CanDoNothing{SP}.
@@
 \begin{itemize}
-  \item \CustomerRiskTemporaryDisadvantagedPosition{\Pos{5}{c}{\normal}{\minus}}.
+  \item \CustomerRiskTemporaryDisadvantagedPosition{\Pos{5}{c}{\normal}{\minus}}
   \item \SPCanDoBothButFollowIsSafe{5}.
@@
 \begin{itemize}
-  \item \CustomerRiskTemporaryDisadvantagedPosition{\Pos{6}{c}{\normal}{\minus}}.
+  \item \CustomerRiskTemporaryDisadvantagedPosition{\Pos{6}{c}{\normal}{\minus}}
   \item \SPCanDoBothButFollowIsSafe{6}.
@@
 \begin{itemize}
-  \item \CustomerRiskTemporaryDisadvantagedPosition{\Pos{7}{c}{\normal}{\minus}}.
+  \item \CustomerRiskTemporaryDisadvantagedPosition{\Pos{7}{c}{\normal}{\minus}}
   \item \SPCanDoBothButFollowIsSafe{7}.
@@
 \begin{itemize}
-  \item \CustomerRiskTemporaryDisadvantagedPosition{\Pos{8}{c}{\normal}{\minus}}.
+  \item \CustomerRiskTemporaryDisadvantagedPosition{\Pos{8}{c}{\normal}{\minus}}
   \item \CanDoNothing{} \Pos{8}{s}{\normal}{\plus} or \Pos{8}{s}{\abnormal}{\plus}.

### 2024-06-05 paper/main.tex
update paper

@@
 
-\newcommand{\normal}{n}
-\newcommand{\dispute}{d}
-\newcommand{\abnormal}{\overline{n}}
-\newcommand{\abdispute}{\overline{d}}
+\newcommand{\normal}{\mathrm{n}}
+\newcommand{\dispute}{\mathrm{d}}
+\newcommand{\abnormal}{\overline{\mathrm{n}}}
+\newcommand{\abdispute}{\overline{\mathrm{d}}}
 
@@
 \label{sec:introduction}
-Diagnostic services such as paternity tests, doping tests, or venereal disease tests require customers to provide biological material such as blood, urine, stool, or saliva.
-Unfortunately, customers often have to reveal their identity to complete transactions, exposing them to significant privacy risks.
-
-Other examples of sensitive services include anonymous complaints or legal services, like legal advice, which may require disclosure of financial transaction history and confidential legal documents.
-Banking services, such as credit scoring, may require sensitive personal information like medical records and financial transaction history.
-
-Providing personal information exposes users to a myriad of privacy risks, ranging from the potential loss of control over personal information to severe threats like identity theft, data breaches, and unsanctioned monitoring.
-Sensitive information is valuable to attackers, leading to potential unauthorized uses.
-This situation could unintentionally violate regulations like GDPR or CCPA, result in targeted advertising, or lead to crimes like identity theft or unlawful tracking and surveillance~\cite{smithInformationPrivacyResearch2011}.
-
-Public figures such as influencers, politicians, or celebrities are particularly vulnerable to this type of attack, as exposure of their health records, purchasing habits, or legal documents can threaten their reputation, position, or be used for blackmail.
-
-The problem is amplified when personal information is linked to health records, legal documents, or biological materials such as DNA, saliva, or blood.
-In such situations, customers may be reluctant to provide their personal information to the SP and therefore withdraw from the service.
-Both parties are harmed as the customer does not receive a diagnosis relevant to their health and the SP loses potential customers~\cite{klitzmanExclusionGeneticInformation2010,blackPresymptomaticTestingConfidentiality2021}.
-
-In the majority of healthcare systems, the critical data managed typically resides in the Electronic Medical Records (EMRs), which is consistently regarded as confidential information requiring robust security measures~\cite{jinReviewSecurePrivacypreserving2019,keshtaSecurityPrivacyElectronic2021}.
-
-Maintaining the privacy of health data seems to be an open and active area of research in the field of Privacy-Preserving Data Mining (PPDM)~\cite{nareshPrivacyPreservingData2023,linPPSFOpensourcePrivacypreserving2018,hewagePrivacypreservingDataStream2023}.
-Recent research in this area focuses on employing methods of anonymization and hiding sensitive information of the EMRs~\cite{hamdiEnhancingSecurityPrivacy2023, sharmaPrivacyPreservingData2019, wuHidingSensitiveInformation2021}, or securing the interaction between patient and Healthcare system~\cite{zhangPrivacyProtectionTelecare2016, mehmoodAnonymousAuthenticationScheme2018, khasimImprovedFastSecure2022}.
-
-Authors of~\cite{blackPresymptomaticTestingConfidentiality2021} highlight that after their organisation adopted Electronic Medical Record (EMR) systems, they could no longer promise the same confidentiality assurances.
-
-Klitzman~\cite{klitzmanExclusionGeneticInformation2010} examined the exclusion of genetic data from EMR, noting that patients frequently distrust healthcare facilities and choose not to share their genetic test results with doctors, fearing that this information might be recorded in their EMR.
-
-In our study, we focus on the possibility of carrying out services without revealing any personal information — solving the problem of privacy at a much earlier stage, before any personal information gets into the EMR system.
-
-It would be desirable for customers to keep their identity private while still receiving the service.
-This could lead to a reduction in the trust that customers need to place in SPs and a reduction in the responsibility that SPs bear.
-
-Examples of services that would benefit from the anonymity property are:
-
-\begin{itemize}
-  \item \textbf{Confidentiality in Medical Testing}: Patients who are willing to take a test, e.g.
-for drugs, STDs, paternity, or steroids, have a strong incentive to keep the whole process private.
-The mere fact that they have taken the test—without revealing the result—is suggestive enough to be used as a premise in the event of a conflict.
-Currently, they have to take the risk that their personal data, materials, and results will be stored securely and kept secret from any unauthorized actor (both curious employees and malicious attackers)~\cite{klitzmanExclusionGeneticInformation2010, blackPresymptomaticTestingConfidentiality2021}.
-
-  \item \textbf{Anonymity in Legal Consultations for Entrepreneurs}: Individuals engaged in entrepreneurial activities may want to assess the risks and possible consequences of their actions.
-By revealing their identity, they trust that the lawyer will not use this information for harmful actions.
-
-  \item \textbf{Whistleblowing Platforms}: Employees or citizens witnessing unethical or illegal activities within organizations can report these anonymously without fear of reprisal, job loss, or social stigma, thereby promoting a more transparent and accountable society.
-
-  \item \textbf{Sexual Health and Reproductive Services}: People seeking advice or services related to sexual health, contraception, or abortion might prefer anonymity due to the sensitive nature of these topics and potential societal judgment.
-\end{itemize}
-
-Using Solove's Taxonomy of Privacy~\cite{soloveTaxonomyPrivacy2006}, our protocol aims to prevent the following privacy risks: Breach of confidentiality, Disclosure, Identification, and Secondary use.
-We consider the following adversaries: Malicious insiders, Government agencies, Malicious third-party services, Hackers, and cybercriminals.
-
-In this work, we explore the possibilities of anonymous service provision and propose a protocol that preserves the customer's privacy even in the event of a successful attack.
-Under realistic operational assumptions, we show that decoupling personal information from materials, payment, and communication achieves a sufficient level of anonymity.
-
+\begin{sloppypar}
+Sensitive diagnostic services such as paternity tests, doping tests, and venereal disease tests require customers to provide biological material like blood, urine, stool, or saliva, which often necessitates revealing their identity.
+This exposure poses significant privacy risks.
+Similarly, other sensitive services include anonymous complaints, legal services requiring financial and confidential disclosures, and banking services needing personal information like medical records and financial histories.
+The necessity to provide personal information exposes users to risks such as loss of control over their information, identity theft, data breaches, and unauthorized monitoring, which can lead to severe consequences like GDPR or CCPA violations, targeted advertising, or unlawful tracking and surveillance~\cite{smithInformationPrivacyResearch2011}.
+\end{sloppypar}
+
+\begin{sloppypar}
+Public figures, including influencers, politicians, and celebrities, are particularly vulnerable as the exposure of their health records, purchasing habits, or legal documents can be detrimental to their reputation or used for blackmail.
+This problem intensifies when personal information is linked to sensitive records or biological materials, causing customers to withdraw from services due to privacy concerns.
+This withdrawal negatively impacts both the customer, who does not receive needed services, and the service provider (SP), who loses potential clients~\cite{klitzmanExclusionGeneticInformation2010,blackPresymptomaticTestingConfidentiality2021}.
+\end{sloppypar}
+
+\begin{sloppypar}
+In healthcare systems, critical data typically resides in Electronic Medical Records (EMRs), regarded as confidential and requiring robust security measures~\cite{jinReviewSecurePrivacypreserving2019,keshtaSecurityPrivacyElectronic2021}.
+Privacy-preserving data mining (PPDM) remains an active research area, focusing on anonymization methods and securing patient-healthcare interactions~\cite{nareshPrivacyPreservingData2023,linPPSFOpensourcePrivacypreserving2018,hewagePrivacypreservingDataStream2023}.
+Studies indicate that adopting EMRs can compromise confidentiality~\cite{blackPresymptomaticTestingConfidentiality2021}, and exclusion of genetic data from EMRs often results from patient distrust~\cite{klitzmanExclusionGeneticInformation2010}.
+\end{sloppypar}
+
+\begin{sloppypar}
+Our study explores providing services without revealing personal information, addressing privacy concerns before data enters EMR systems.
+Maintaining customer anonymity while delivering services reduces the trust required from customers and the responsibility borne by SPs.
+Key participants in this model include customers, SPs, and dispute resolution services.
+Examples of services benefiting from anonymity include:
+\begin{itemize}
+  \item \textbf{Confidentiality in Medical Testing}: Patients undergoing tests for drugs, STDs, paternity, or steroids benefit from keeping the process private to avoid suggestive implications.
+  \item \textbf{Anonymity in Legal Consultations for Entrepreneurs}: Entrepreneurs assessing risks may prefer anonymous consultations to prevent misuse of disclosed information.
+  \item \textbf{Whistleblowing Platforms}: Anonymous reporting of unethical or illegal activities promotes transparency and accountability without fear of reprisal.
+  \item \textbf{Sexual Health and Reproductive Services}: Individuals seeking advice on sensitive topics like sexual health, contraception, or abortion prefer anonymity due to potential societal judgment.
+\end{itemize}
+\end{sloppypar}
+
+\begin{sloppypar}
+Using Solove's Taxonomy of Privacy~\cite{soloveTaxonomyPrivacy2006}, our protocol aims to prevent privacy risks such as breach of confidentiality, disclosure, identification, and secondary use.
+We consider adversaries like malicious insiders, government agencies, third-party services, hackers, and cybercriminals.
+Our proposed protocol decouples personal information from materials, payment, and communication, achieving anonymity even during attacks.
+\end{sloppypar}
+
+\begin{sloppypar}
 However, a protocol that hides the customer's identity is difficult to secure and coordinate.
 In particular, conflicts between customers and service providers are difficult to resolve when there is no subject to accuse.
-
-We observe that the problem of anonymous service provision can be seen as a problem of fair exchange, where parties exchange some goods fairly, i.e., either both parties obtain the goods, or they both obtain nothing.
-
-In our case, the customer who wants to use the service exchanges his materials and money with the SP for the result of the service.
-
-Our review shows that none of the current systems is sufficient to achieve the desired goal.
-We propose an anonymous protocol for the provision of services that require physical materials.
-In the event of a dispute, either due to missed deadlines or incorrect results, the customer can disclose the entire interaction, prove the SP's misbehaviour to the Dispute Resolution Service, and win the dispute.
-
-To achieve this goal we use:
+\end{sloppypar}
+
+\begin{sloppypar}
+We frame anonymous service provision as a fair exchange problem, ensuring that either both parties obtain the goods or neither does.
+Our review indicates that current systems do not meet our goals.
+We propose an anonymous protocol for services requiring physical materials, with dispute resolution capabilities.
+If disputes arise, customers can disclose interactions and prove SP misbehavior.
+\end{sloppypar}
+
+\begin{sloppypar}
+To achieve this, we use:
 \begin{itemize}
   \item \textbf{Blockchain}, to achieve fairness, i.e., as a means of proving that certain actions took place at a certain time without the Trusted Third Party (TTP).
-  \item \textbf{Anonymous payment methods}, such as cash or anonymous cryptocurrencies, which allow customers to pay for services anonymously.
+  \item \textbf{Anonymous payment methods}, like cash or cryptocurrencies, for anonymous transactions.
   \item \textbf{Decentralised storage network} (e.g., IPFS) to provide results together with a provable storage network (e.g., Filecoin) to guarantee that the results are available to the customer even if the SP refuses to share the result.
-  \item Cryptography:
-  \begin{itemize}
-    \item \textbf{Symmetric encryption}, to encrypt and decrypt the results published on the public networks.
-    \item \textbf{Diffie-Hellman key exchange (DHKE)}, to derive shared secrets for symmetric encryption.
-    \item \textbf{Digital signatures}, to achieve authentication and non-repudiation of actions.
-  \end{itemize}
-\end{itemize}
-
-Figure~\ref{fig:protocol-overview} shows a simplified diagram of the protocol.
+  \item Cryptographic techniques, including symmetric encryption, Diffie-Hellman key exchange, and digital signatures for security and authentication.
+\end{itemize}
+\end{sloppypar}
+
+\begin{sloppypar}
+Figure~\ref{fig:protocol-overview} illustrates a simplified protocol diagram. The contribution of our paper is multifaceted and significant in advancing blockchain-based fair exchange systems:
+\begin{itemize}
+  \item We propose a protocol based on a realistic operational and threat model that:
+  \begin{itemize}
+    \item Enables \textbf{anonymous service provision} involving physical materials, eliminating the need for service providers to collect personal information from customers.
+    \item Achieves \textbf{fairness} through blockchain technology and cryptographic proofs, modeled as an interactive non-cooperative game, ensuring fairness at each step.
+    \item Operates without a centralized Trusted Third Party (TTP), leveraging a decentralized blockchain and a distributed content-addressable storage network.
+    \item Enhances \textbf{user experience and practicality} in conflict-free transactions by eliminating the need for customer interaction with the blockchain.
+    \item Ensures \textbf{remote availability of results}, even in cases of service provider denial.
+  \end{itemize}
+  \item Our implementation includes a working prototype with open-source code, demonstrating the practical applicability of our protocol.
+  \item We clarify often misused concepts such as anonymity, pseudonymity, linkability, and traceability, providing a clearer framework for understanding these critical aspects.
+  \item A novel framework for analyzing fairness in fair exchange protocols is introduced and used to validate the fairness.
+  \item We discuss potential enhancements using advanced technologies like secure computation, self-sovereign identities, zero-knowledge proofs, and blockchain-based dispute resolution.
+\end{itemize}
+Some authors have proposed blockchain-based fair exchange systems that could be adapted to service provision; however, to the best of our knowledge, we are the first to propose a system that satisfies all of the above properties.
+In particular, anonymity and physical delivery have rarely been addressed together, and if so, the protocol was based on TTP and impractical assumptions about the banking system~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} or did not address the conflict between parties~\cite{altawyLelantosBlockchainBasedAnonymous2017}.
+\end{sloppypar}
+
+The rest of this paper is organised as follows.
+In Section~\ref{sec:related-works} we review related works.
+Then in Section~\ref{sec:building-blocks} we discuss the building blocks of a dispute resolution system, blockchain as a message board, fairness, anonymous payments, storage network, availability of results and anonymity.
+Section~\ref{sec:protocol} provides a detailed description of the protocol.
+Section~\ref{sec:fairness-analysis} provides a fairness analysis of the proposed protocol.
+Section~\ref{sec:experiments} presents the implementation of the protocol and the results of our experiments.
+Section~\ref{sec:discussion} discusses possible improvements in terms of crowdsourced dispute resolution or dispute avoidance, self-sovereign identities (SSIs), anonymous delivery, and formal verification.
+Finally, Section~\ref{sec:conclusion} concludes the paper.
 
@@
 
-The contribution of our paper is multifaceted and significant in advancing blockchain-based fair exchange systems:
-
-\begin{itemize}
-  \item We propose a protocol based on a realistic operational and threat model that:
-  \begin{itemize}
-    \item Enables \textbf{anonymous service provision} involving physical materials, eliminating the need for service providers to collect personal information from customers.
-    \item Achieves \textbf{fairness} through blockchain technology and cryptographic proofs, modeled as an interactive non-cooperative game, ensuring fairness at each step.
-    \item Operates without a centralized Trusted Third Party (TTP), leveraging a decentralized blockchain and a distributed content-addressable storage network.
-    \item Enhances \textbf{user experience and practicality} in conflict-free transactions by eliminating the need for customer interaction with the blockchain.
-    \item Ensures \textbf{remote availability of results}, even in cases of service provider denial.
-  \end{itemize}
-  \item Our implementation includes a working prototype with open-source code, demonstrating the practical applicability of our protocol.
-  \item We clarify often misused concepts such as anonymity, pseudonymity, linkability, and traceability, providing a clearer framework for understanding these critical aspects.
-  \item A novel framework for analyzing fairness in fair exchange protocols is introduced, and we use it to validate the fairness of our protocol.
-  \item We discuss potential enhancements using advanced technologies like secure computation, self-sovereign identities, zero-knowledge proofs, and blockchain-based dispute resolution, paving the way for future research and development.
-\end{itemize}
-
-Some authors have proposed blockchain-based fair exchange systems that could be adapted to service provision; however, to the best of our knowledge, we are the first to propose a system that satisfies all of the above properties.
-In particular, anonymity and physical delivery have rarely been addressed together, and if so, the protocol was based on TTP and impractical assumptions about the banking system~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} or did not address the conflict between parties~\cite{altawyLelantosBlockchainBasedAnonymous2017}.
-
-The rest of this paper is organised as follows.
-In Section~\ref{sec:related-works} we review related works.
-Then in Section~\ref{sec:building-blocks} we discuss the building blocks of a dispute resolution system, blockchain as a message board, fairness, anonymous payments, storage network, availability of results and anonymity.
-Section~\ref{sec:protocol} provides a detailed description of the protocol.
-Section~\ref{sec:fairness-analysis} provides a fairness analysis of the proposed protocol.
-Section~\ref{sec:experiments} presents the implementation of the protocol and the results of our experiments.
-Section~\ref{sec:discussion} discusses possible improvements in terms of crowdsourced dispute resolution or dispute avoidance, self-sovereign identities (SSIs), anonymous delivery, and formal verification.
-Finally, Section~\ref{sec:conclusion} concludes the paper.
-
-\section{Related Works}\label{sec:related-works}
-\begin{sloppypar}
-This section reviews key protocols in fair exchange, anonymity, and physical delivery, highlighting their primary features and differences.
-\end{sloppypar}
-
-The most common application of fair exchange protocols
-is e-commerce. A typical transaction involves a seller and
-a customer exchanging money for a physical product. To pro-
-tect themselves, the seller wants to receive the funds before
-sending the product, while the customer wants to receive the
-product before paying. The fairness of the protocol should
-guarantee that either both parties obtain the goods, or they
-both obtain nothing.
-Early systems like the one by Zhang et al.
-(2006)\cite{zhangPracticalFairExchangeEPayment2006} and Mohammedalaraj (2012)\cite{mohammedalarajFairnessPhysicalProducts2012} introduced Trusted Third Parties (TTPs) and Delivery Agents (DAs) to ensure fairness, and relied on strong assumptions about non-collusion and resilient communication channels.
-
-\begin{sloppypar}
-Protocols like those proposed by Bîrjoveanu et al.
+\section{Related works}\label{sec:related-works}
+\begin{sloppypar}
+This section reviews the main protocols for fair exchange, anonymity and physical delivery, highlighting their main features and differences.
+\end{sloppypar}
+
+The most common application of fair exchange protocols is in e-commerce. In a typical transaction, a seller and a customer exchange money for a physical product.
+To protect themselves, the seller wants to receive the funds before sending the product, while the customer wants to receive the product before paying.
+The fairness of the protocol should ensure that either both parties receive the goods or neither receives anything.
+Early systems, such as those by Zhang et al.
+(2006)\cite{zhangPracticalFairExchangeEPayment2006} and Mohammedalaraj (2012)\cite{mohammedalarajFairnessPhysicalProducts2012}, introduced Trusted Third Parties (TTPs) and Delivery Agents (DAs) to ensure fairness and relied on strong assumptions about non-collusion and resilient communication channels.
+
+\begin{sloppypar}
+Protocols such as those proposed by Bîrjoveanu et al.
 (2015-2022)~\cite{birjoveanuAnonymityFairexchangeEcommerce2015, birjoveanuPreservingAnonymityFair2018, birjoveanuAnonymityComplexTransactions2019, birjoveanuFairExchangeECommerce2020, birjoveanuTwoPartyECommerceProtocols2022} focus on anonymity in transactions involving physical products.
-These protocols utilize TTPs, anonymous communication channels like Tor, and cryptographic techniques like blind signatures to ensure privacy and fairness.
-However, they depend on the existence of TTPs and secure, confidential transaction systems between banks.
-
-Blockchain technology offers solutions to the TTP dependency in fair exchange protocols.
+These protocols use TTPs, anonymous communication channels like Tor, and cryptographic techniques like blind signatures to ensure privacy and fairness.
+However, they rely on the existence of TTPs and secure, confidential transaction systems between banks.
+\end{sloppypar}
+
+Blockchain technology offers solutions to TTP dependency in fair exchange protocols.
 Hinarejos et al.
-(2019)\cite{hinarejosSolutionSecureCertified2019} demonstrated a blockchain-based protocol for certified email, replacing TTP with a decentralized, verifiable system.
-Themis (Meng et al., 2019)\cite{mengThemisDecentralizedEscrow2019} further advanced this by incorporating a decentralized dispute resolution mechanism, though it does not address anonymity.
-\end{sloppypar}
-
-Lelantos (Altawy et al., 2017)~\cite{altawyLelantosBlockchainBasedAnonymous2017} is a notable example of a blockchain-based system providing anonymous physical delivery.
+(2019)\cite{hinarejosSolutionSecureCertified2019} demonstrated a blockchain-based protocol for certified email that replaces TTP with a decentralized, verifiable system.
+Themis (Meng et al., 2019)\cite{mengThemisDecentralizedEscrow2019} took this further by incorporating a decentralized dispute resolution mechanism, although it does not address anonymity.
+
+Lelantos (Altawy et al., 2017)~\cite{altawyLelantosBlockchainBasedAnonymous2017} is a notable example of a blockchain-based system that provides anonymous physical delivery.
 It uses onion routing and smart contracts to ensure anonymity, although it only achieves pseudonymity and lacks a dispute resolution mechanism.
 
-\paragraph{Comparison and Our Approach}
-
-We only considered protocols that achieve fair exchange, as this is the fundamental feature of such protocols.
+\paragraph{Comparison and our approach}
+
+We have only considered protocols that achieve fair exchange, as this is the fundamental feature of such protocols.
 
@@
 Altawy et al.
-2017~\cite{altawyLelantosBlockchainBasedAnonymous2017} is a blockchain-based protocol that provides anonymous physical delivery using onion routing and anonymous blockchain interaction, assuming unlinkability between pseudonyms and real identities.
+2017~\cite{altawyLelantosBlockchainBasedAnonymous2017} is a blockchain-based protocol that uses onion routing and anonymous blockchain interaction to provide anonymous physical delivery, assuming unlinkability between pseudonyms and real identities.
 However, it does not provide dispute resolution.
@@
 
-Meng et al. 2019~\cite{mengThemisDecentralizedEscrow2019} improves the previous protocol through the crowd-sourced dispute resolution system. However, it does not take anonymity into account.
+Meng et al. 2019~\cite{mengThemisDecentralizedEscrow2019} improves on the previous protocol through a crowdsourced dispute resolution system. However, it does not consider anonymity.
 
@@
 
-Our protocol differs from existing ones by focusing on anonymity and fair exchange without relying on TTPs or complex banking systems.
+Our protocol differs from existing ones in that it focuses on anonymity and fair exchange without relying on TTPs or complex banking systems.
 It achieves anonymity by using either cash or privacy-preserving blockchains.
-In addition, our protocol does not require the customer to submit a transaction to the bulletin board simplifying the transaction process while maintaining anonymity and fairness.
-
-Unlike most protocols, our system is designed for transactions where the package is delivered from the customer to the Service Provider (SP), and we assume a generic Dispute Resolution Service for handling conflicts .
-
-To provide a clearer understanding of how our protocol compares with existing work, Table~\ref{tab:comparision} presents a summary of key features and differences among the discussed protocols.
+In addition, our protocol does not require the customer to submit a transaction to the bulletin board, simplifying the transaction process while maintaining anonymity and fairness.
+
+Unlike most protocols, our system is designed for transactions where the package is delivered from the customer to the service provider (SP), and we assume a generic dispute resolution service to handle conflicts.
+
+To provide a clearer understanding of how our protocol compares to existing work, Table~\ref{tab:comparison} provides a summary of the key features and differences between the protocols discussed.
 
@@
 The notation \textit{Pseudonymity} means that the anonymity is based on the assumption that the pseudonym is not linked to the real identity; \textit{TTP} means that the protocol uses a trusted third party; \textit{BC} means that the protocol uses a public blockchain; \textit{YES*} means that the protocol provides the feature but is based on strong or impractical assumptions.}
-\label{tab:comparision}
+\label{tab:comparison}
 \setlength{\tabcolsep}{3pt}
@@
 In the realm of fair exchange protocols involving physical materials, existing solutions often rely on trusted intermediaries~\cite{mohammedalarajFairnessPhysicalProducts2012, birjoveanuAnonymityFairexchangeEcommerce2015} or complex delivery systems~\cite{altawyLelantosBlockchainBasedAnonymous2017} to maintain anonymity.
-These methods, while effective, can be cumbersome and less practical for certain use cases.
-
-In our context, the process is reversed as the physical materials are transferred from an anonymous customer to a publicly known Service Provider (SP).
+While these methods are effective, they can be cumbersome and less practical for certain use cases.
+
+In our context, the process is reversed, as the physical materials are transferred from an anonymous customer to a publicly known service provider (SP).
 This unique setup allows for a simplification of the delivery process.
@@
 
-    \item \textbf{Parcel Locker Services:} Leveraging existing locker services (e.g., Amazon Locker, InPost) that offer a degree of anonymity and security in package delivery.
-
-    \item \textbf{Trusted Delivery Agent:} The customer may employ a trusted individual or service to deliver the package to the SP, ensuring the customer's anonymity.
-
-    \item \textbf{Postal Services:} Traditional postal services can be used, provided that they do not require personal identification or return addresses that could compromise anonymity.
+    \item \textbf{Parcel Locker Services:} Leverage existing locker services (e.g. Amazon Locker, InPost) that provide a level of anonymity and security for package delivery.
+
+    \item \textbf{Trusted Delivery Agent:} The customer can use a trusted individual or service to deliver the package to the SP, ensuring the customer's anonymity.
+
+    \item \textbf{Postal Services:} Traditional postal services may be used, provided they do not require personal identification or return addresses that could compromise anonymity.
 \end{itemize}
@@
 \begin{sloppypar}
-Disputes are common in transactions, and systems are needed to make sure rules and laws are followed.
-Traditionally, this involves legal contracts and law enforcement.
-With blockchain technology, smart contracts offer a new way by putting contract details into code and automatically enforcing them~\cite{allenGovernanceBlockchainDispute2019}.
-\end{sloppypar}
-
-A challenge with blockchain is dealing with outside information, which is where \textit{oracles} come in.
+Disputes are common in transactions, and systems are needed to ensure that rules and laws are followed.
+Traditionally, this has involved legal contracts and law enforcement.
+With blockchain technology, smart contracts offer a new way by putting contract details into code and enforcing them automatically~\cite{allenGovernanceBlockchainDispute2019}.
+\end{sloppypar}
+
+One challenge with blockchain is dealing with external information, which is where \textit{oracles} come in.
 They feed real-world data into the blockchain~\cite{breidenbachChainlinkNextSteps2021}.
 This is important for dispute resolution systems like Themis~\cite{mengThemisDecentralizedEscrow2019} and Kleros~\cite{bergollaKlerosSociolegalCase2022}, which use decentralized networks to make fair decisions.
-However, these systems might struggle with complex disputes that need special knowledge and privacy.
+However, these systems may struggle with complex disputes that require special knowledge and privacy.
 
 Our protocol takes a more traditional approach.
-It uses blockchain to keep track of evidence but relies on local legal systems (like police or courts) to solve disputes.
-This way, we balance the use of technology with the need for detailed understanding in complicated service disputes.
-We talk more about exploring decentralized, partly automated systems in Section~\ref{sec:decentralised-justice}.
+It uses the blockchain to keep track of evidence, but relies on local legal systems (such as police or courts) to resolve disputes.
+In this way, we balance the use of technology with the need for detailed understanding in complicated service disputes.
+We talk more about exploring decentralized, partially automated systems in Section~\ref{sec:decentralised-justice}.
 
@@
 As the customer remains anonymous, the SP cannot initiate a dispute due to the inability to identify the customer.
-Our protocol is designed to favor the SP who adheres to the protocol, thus removing the need to initiate disputes.
-Conversely, customers can initiate disputes, but only SP misbehavior will result in a successful claim.
+Our protocol is designed to favour the SP who adheres to the protocol, thus eliminating the need to initiate disputes.
+Conversely, customers can initiate disputes, but only misbehavior by the SP will result in a successful claim.
 
@@
 \begin{enumerate}
-    \item \textbf{Proof of Delivery ($\textrm{PoD}$)}: Issued by the SP, this confirms the customer's delivery of a complete package as per SP's requirements.
-The detailed definition is in Section~\ref{proof-of-delivery}.
-
-    \item \textbf{Payment $\textrm{receipt}$}: This confirms the customer's payment for the service.
-Its format varies based on the payment method (cryptocurrency or cash) and is further discussed in Section~\ref{payment-for-services}.
-
-    \item \textbf{Proof of Provision ($\textrm{PoP}$)}: This shows that the SP has published the service result at a specific time, protecting the SP against unjustified disputes by the customer.
-The detailed definition is in Section~\ref{proof-of-provision}.
+  \item \textbf{Proof of Delivery ($\textrm{PoD}$)}: Issued by the SP to confirm that the customer has delivered a complete package in accordance with the SP's requirements.
+The detailed definition is given in Section~\ref{proof-of-delivery}.
+
+  \item \textbf{Payment $\textrm{receipt}$}: This confirms that the customer has paid for the service.
+Its format varies depending on the payment method (cryptocurrency or cash) and is discussed further in Section~\ref{payment-for-services}.
+
+  \item \textbf{Proof of Provision ($\textrm{PoP}$)}: This shows that the SP has published the service result at a certain time, thus protecting the SP against unjustified disputes from the customer.
+The detailed definition is given in Section~\ref{proof-of-provision}.
 \end{enumerate}
@@
 The platform for issuing and publishing these proofs is a critical aspect of the protocol.
-Referred to by various terms like bulletin board~\cite{achenbachImprovedCoercionresistantElectronic2015}, trusted timestamping~\cite{gippDecentralizedTrustedTimestamping2015}, or message board~\cite{hinarejosSolutionSecureCertified2019}, this platform serves as a decentralized, public ledger that securely timestamps and records each proof.
-By leveraging blockchain technology, the platform ensures that the proofs are tamper-proof and verifiable by any third party, including judicial authorities.
-
-This approach of using a decentralized message board for publishing proofs provides several advantages:
-\begin{itemize}
-    \item It establishes an immutable record of actions and agreements between the anonymous customer and the service provider.
-    \begin{sloppypar}
-    \item It enables transparent verification of the timeline of events, crucial for dispute resolution.
-    \end{sloppypar}
-    \item It offers a universally accessible platform for checking the authenticity and integrity of the transaction-related proofs.
+Known by various names such as bulletin board~\cite{achenbachImprovedCoercionresistantElectronic2015}, trusted timestamping~\cite{gippDecentralizedTrustedTimestamping2015}, or message board~\cite{hinarejosSolutionSecureCertified2019}, this platform serves as a decentralized, public ledger that securely timestamps and records each proof.
+By using blockchain technology, the platform ensures that the proofs are tamper-proof and verifiable by any third party, including judicial authorities.
+
+This approach of using a decentralized message board to publish proofs has several advantages:
+\begin{itemize}
+  \item It creates an immutable record of the actions and agreements between the anonymous customer and the service provider.
+  \item It allows transparent verification of the timeline of events, which is critical for dispute resolution.
+\item It provides a universally accessible platform for verifying the authenticity and integrity of transaction-related proofs.
 \end{itemize}
@@
 In the realm of blockchain technologies, the concepts of anonymity and confidentiality are achieved through different mechanisms, depending on whether the blockchain is privacy-preserving or not.
-We outline these differences as follows:
+We outline these differences below:
 
@@
 \begin{enumerate}
-    \item \textbf{Privacy-Preserving Blockchains:} These blockchains inherently support both anonymity and confidentiality through advanced cryptographic techniques, ensuring that both user identities and transaction details are obscured.
-    \begin{itemize}
-        \item \textbf{Examples:}
-        \begin{itemize}
-            \item \textbf{Monero:} Utilizes Ring Signatures and Bulletproofs~\cite{vansaberhagenCryptoNote2013, noetherRingSignatureConfidential2015, bunzBulletproofsShortProofs2018}.
-            \item \textbf{ZCash:} Employs zkSNARKs for private transactions~\cite{ben-sassonZerocashDecentralizedAnonymous2014}.
-            \item \textbf{Grin} and \textbf{IronFish:} Use Mimblewimble and the Sapling protocol, respectively~\cite{jedusorMIMBLEWIMBLE2016,fuchsbauerAggregateCashSystems2019, hopwoodZcashSaplingProtocol2022, ironfishPrivateAnonymousEasy}.
-        \end{itemize}
-    \end{itemize}
-
-    \item \textbf{Non-privacy-preserving Blockchains:} These blockchains, such as Bitcoin and Ethereum, do not natively support strong privacy features.
+    \item \textbf{Privacy preserving blockchains:} These blockchains inherently support both anonymity and confidentiality through advanced cryptographic techniques, ensuring that both user identities and transaction details are obscured.
+Examples:
+      \begin{itemize}
+          \item \textbf{Monero:} Uses ring signatures and bulletproofs~\cite{vansaberhagenCryptoNote2013, noetherRingSignatureConfidential2015, bunzBulletproofsShortProofs2018}.
+          \item \textbf{ZCash:} Uses zkSNARKs for private transactions~\cite{ben-sassonZerocashDecentralizedAnonymous2014}.
+          \item \textbf{Grin} and \textbf{IronFish:} Use Mimblewimble and the Sapling protocol respectively~\cite{jedusorMIMBLEWIMBLE2016,fuchsbauerAggregateCashSystems2019, hopwoodZcashSaplingProtocol2022, ironfishPrivateAnonymousEasy}.
+    \end{itemize}
+
+    \item \textbf{Non-privacy preserving blockchains:} These blockchains, such as Bitcoin and Ethereum, do not natively support strong privacy features.
 However, anonymity can be enhanced through the use of mixers and other privacy tools.
-    \begin{itemize}
-        \item \textbf{Examples:}
+Examples:
     \begin{itemize}
@@
           \item \textbf{Wasabi Wallet} (Bitcoin): Uses CoinJoin to mix transactions~\cite{maxwellCoinJoinBitcoinPrivacy2013,wasabiwalletBitcoinPrivacyWallet}.
-        \end{itemize}
     \end{itemize}
@@
 \centering
-\caption{Consider a scenario where Alice is an anonymous customer and Bob is a public Service Provider (SP).
-Alice controls two addresses, labeled 1 and 2.
-The link (represented by a red line) between Alice's real identity and address 1 has been compromised, making identification possible.
+\caption{Consider a scenario where Alice is an anonymous customer and Bob is a public service provider (SP).
+Alice controls two addresses, labelled 1 and 2.
+The link (shown as a red line) between Alice's real identity and address 1 has been compromised, allowing identification.
 However, the link to address 2 remains unknown, preserving anonymity.
 Alice performs two actions, A and B.
-Action A originates from the compromised address 1, while action B is from the anonymous address 2.
+Action A is from the compromised address 1, while action B is from the anonymous address 2.
 Action A is confidential, meaning that despite the compromised pseudonym, the nature of the action remains undisclosed.
-Action B is transparent, but it cannot be linked to Alice as long as the connection to pseudonym 2 remains hidden.}
+Action B is transparent, but it cannot be linked to Alice as long as the connection to nickname 2 remains hidden.}
 \label{fig:anonymity-diagram}
@@
 
-\subsection{Payment for Services}\label{payment-for-services}
-
-\begin{sloppypar}
-In transactions between customers and service providers (SPs), it is crucial to establish a unique link between the payment and the corresponding transaction to prevent the reuse of a payment for multiple transactions.
+\subsection{Paying for services}\label{payment-for-services}
+
+\begin{sloppypar}
+In transactions between customers and service providers (SPs), it is essential to establish a unique link between the payment and the corresponding transaction in order to prevent the reuse of a payment for multiple transactions.
 This link can be established in various ways depending on the cryptocurrency used:
@@
 \begin{itemize}
-    \item \textbf{Separate Address:} Each transaction utilizes a unique address associated with it.
+    \item \textbf{Separate address:} Each transaction uses a unique address associated with it.
 These addresses can be generated using Hierarchical Deterministic Wallets~\cite{wuilleBIP32HierarchicalDeterministic2012} and published on the message board to ensure non-repudiation.
-    \item \textbf{Memo:} Payments are sent to a single SP account but include an extra field called ``memo,'' filled with the unique identifier $\textrm{provisionID}$.
-\end{itemize}
-\end{sloppypar}
-
-Any payment that contains $\textrm{provisionID}$ in the memo or is sent to the designated address is recognized as payment for the transaction.
+    \item \textbf{Memo:} Payments are sent to a single SP account but contain an extra field called ``memo'' filled with the unique identifier $\textrm{provisionID}$.
+\end{itemize}
+\end{sloppypar}
+
+Any payment that contains $\textrm{provisionID}$ in the memo or is sent to the specified address will be recognized as payment for the transaction.
 
@@
 \begin{enumerate}
-\item \textbf{Normal}: Those that adhere to the protocol's prescribed steps.
-\item \textbf{Abnormal}: Any deviation from the protocol's prescribed steps, such as sending irrelevant messages, skipping steps, or exceeding time limits.
+\item \textbf{Normal} ($\normal{}$): Those that adhere to the protocol's prescribed steps.
+\item \textbf{Abnormal} ($\abnormal{}$): Any deviation from the protocol's prescribed steps, such as sending irrelevant messages, skipping steps, or exceeding time limits.
 \end{enumerate}
@@
 \def\labelenumi{\arabic{enumi}.}
-\item \textbf{Agree}: The customer consents to the action and refrains from disputing.
-\item \textbf{Start a dispute}: The customer contests the action and initiates a dispute.
+\item \textbf{Agree} ($\normal{}$ or $\abnormal{}$): The customer consents to the action and refrains from disputing.
+\item \textbf{Start a dispute} ($\dispute{}$ or $\abdispute{}$): The customer contests the action and initiates a dispute.
 \end{enumerate}
@@
 \begin{sloppypar}
-Consequently, our analysis must account for four potential outcomes for each party at every protocol step ($\mathrm{party \in \{C, SP\} }$, $\mathrm{step \in 1..9}$):
-\end{sloppypar}
-
-\begin{itemize}
-\item $\mathrm{\sigma_{step,party,n}}$: The outcome after adhering to the protocol with the other party acting normally.
-\item $\mathrm{\sigma_{step,party,d}}$: The outcome following a resolved dispute with the other party acting normally.
-\item $\mathrm{\sigma_{step,party,\overline{n}}}$: The outcome when no dispute is raised despite the other party's abnormal actions.
-\item $\mathrm{\sigma_{step,party,\overline{d}}}$: The outcome after a resolved dispute with the other party acting abnormally.
+Consequently, our analysis must account for four potential $\mathrm{action} \in \{ \normal{}, \abnormal{}, \dispute{}, \abdispute{} \}$, for each $\mathrm{party \in \{C, SP\} }$, at every protocol step $\mathrm{step \in 1..9}$:
+\end{sloppypar}
+
+\begin{itemize}
+\item $\mathrm{\sigma_{step,party,\normal{}}}$: The outcome after adhering to the protocol with the other party acting normally.
+\item $\mathrm{\sigma_{step,party,\dispute{}}}$: The outcome following a resolved dispute with the other party acting normally.
+\item $\mathrm{\sigma_{step,party,\abnormal{}}}$: The outcome when no dispute is raised despite the other party's abnormal actions.
+\item $\mathrm{\sigma_{step,party,\abdispute{}}}$: The outcome after a resolved dispute with the other party acting abnormally.
 \end{itemize}
@@
 The protocol concludes after the final step, if a dispute is initiated, or if a party fails to perform its required action within the designated timeframe.
-Hence, all positions except $\mathrm{\sigma_n}$ signify the end of the protocol.
+Hence, all positions except $\mathrm{\sigma_{step, party, n}}$ for $\mathrm{step} \in 1..8$ signify the end of the protocol.
 
@@
 \begin{definition}[Fairness] \label{def:fairness}
-Let $\mathrm{parties} = \{ C, SP \}$, $\mathrm{steps} = 1..9$, and \( M_{\mathrm{s, p}} = \{ 
-\mathrm{\sigma_{s+1,p,\normal}}, 
-\mathrm{\sigma_{s+1,p,\abnormal}}, 
-\mathrm{\sigma_{s+1,p,\dispute}}, 
-\mathrm{\sigma_{s+1,p,\abdispute}}
-\} \) be the set of all possible moves that a party $p$ can make at a step $s$.
-
-% TODO: describe that we include also the further steps because the protocol can be continued after a dispute
-% The customer, following the 9th assumption described in
-% Section 5.2, risks the temporary disadvantaged position
-% σ4,c,n = - in favour of a later better position σ9,s,n = +;
-% in the meantime, he can get out of the disadvantaged position 
-% if the SP misbehaves in any of the following steps
-
-A protocol is considered fair if and only if, for every party involved and at every step of the protocol, there exists a move that allows the party to move to a non-disadvantaged position.
+Let $\mathrm{parties} = \{ C, SP \}$, $\mathrm{steps} = 1..9$, $\mathrm{actions} = \{ \normal{}, \abnormal{}, \dispute{}, \abdispute{} \}$, and 
+\[
+M_{\sigma_\mathrm{s,p,a}} = 
+\begin{cases} 
+\{ \mathrm{\sigma_{s+1,p,\normal}}, \mathrm{\sigma_{s+1,p,\abnormal}}, \mathrm{\sigma_{s,p,\dispute}}, \mathrm{\sigma_{s,p,\abdispute}} \} & \text{if } s < 9, a = \normal{} \\
+\{ \mathrm{\sigma_{s,p,a}} \} & \text{otherwise} 
+\end{cases}
+\]
+represent the set of all possible positions a party $\mathrm{p}$ can move to at step $\mathrm{s}$ by taking action $\mathrm{a}$, from position $\sigma_\mathrm{s,p,a}$.
+The second case in $M_{\sigma_\mathrm{s,p,a}}$ represents the termination position.
+
+A protocol is considered fair if, at every step, both the customer and the service provider have the option  to move to or stay in a non-disadvantaged position.
+
 \begin{equation}
-\forall_{\mathrm{p} \in \mathrm{parties}} \forall_{\mathrm{s} \in \mathrm{steps}} \exists \sigma \in M_{\mathrm{s, p}} \text{ such that } \sigma \neq -
+\forall_{\mathrm{p} \in \mathrm{parties}} \forall_{\mathrm{s} \in \mathrm{steps}} \forall_{\mathrm{a} \in \mathrm{actions}} \exists \sigma \in M_{\sigma_\mathrm{s, p, a}} \text{ such that } \sigma \neq -
 \end{equation}
 \end{definition}
-
-% TODO: write something at the end of the equatyion as it's usualy done in the math papers
 

### 2024-06-06 paper/main.tex
update paper

@@
 
-\section{Related works}\label{sec:related-works}
+\section{Related Works}\label{sec:related-works}
 \begin{sloppypar}
@@
 
+\begin{sloppypar}
 One challenge with blockchain is dealing with external information, which is where \textit{oracles} come in.
@@
 However, these systems may struggle with complex disputes that require special knowledge and privacy.
+\end{sloppypar}
 
@@
 Action A is confidential, meaning that despite the compromised pseudonym, the nature of the action remains undisclosed.
-Action B is transparent, but it cannot be linked to Alice as long as the connection to nickname 2 remains hidden.}
+Action B is transparent, but it cannot be linked to Alice as long as the connection to pseudonym 2 remains hidden.}
 \label{fig:anonymity-diagram}
@@
 \begin{sloppypar}
-In the event of a dispute, it is necessary to demonstrate to the courts that the customer has paid for the transaction.
+In the event of a dispute, it is necessary to prove to the courts that the customer has paid for the transaction.
 While proving payment is straightforward in transparent and traceable blockchains, it becomes more complex in anonymous blockchains.
-Monero, for instance, allows payments to be proven and verified through a dedicated API~\cite{moneroHowProvePayment}, and ZCash offers a mechanism known as Payment Disclosure~\cite{daviesIntroductionPaymentDisclosure2017}.
+Monero, for example, allows payments to be proven and verified through a dedicated API~\cite{moneroHowProvePayment}, and ZCash provides a mechanism known as Payment Disclosure~\cite{daviesIntroductionPaymentDisclosure2017}.
 We refer to this proof of payment as a \textit{payment receipt}.
@@
 
-Upon completing its service, the service provider (SP) faces the challenge of delivering the result to the customer while maintaining the customer's anonymity.
-The customer, wishing to remain anonymous, cannot reveal their email address or IP address.
-Additionally, the SP must prove that the result was delivered before a specified deadline, aligning with the concept of proof of existence discussed in Section~\ref{sec:message-board}.
-
-\begin{sloppypar}
-A common solution is to utilize a content addressable peer-to-peer storage network for data storage, as direct blockchain storage is prohibitively expensive.
-This approach is widely adopted in various applications~\cite{shahidBlockchainBasedAgriFoodSupply2020, wangAuditableProtocolsFair2019, chenImprovedP2PFile2017}.
-Specifically, data is stored on a network like IPFS~\cite{benetIPFSContentAddressed2014}, and only the content identifier ($\mathrm{cid}$) that uniquely points to the content on IPFS is published on the blockchain.
-\end{sloppypar}
-
-Following this methodology, the SP encrypts the result using the encryption key provided by the customer and uploads it to the IPFS network.
-To ensure the availability of the results, even in cases where the SP is unwilling to share them, we incorporate Filecoin as detailed in Section~\ref{sec:provable-results-availability}.
-
-To further enhance anonymity, customers are advised to use standard techniques such as VPNs or proxies to conceal their IP addresses.
+Upon completion of the service, the Service Provider (SP) faces the challenge of delivering the result to the customer while maintaining the customer's anonymity.
+The customer who wishes to remain anonymous cannot reveal their email address or IP address.
+In addition, the SP must prove that the result was delivered before a specified deadline, according to the concept of proof of existence discussed in section~\ref{sec:message-board}.
+
+\begin{sloppypar}
+A common solution is to use a content addressable peer-to-peer storage network for data storage, as direct blockchain storage is prohibitively expensive.
+This approach has been widely adopted in various applications~\cite{shahidBlockchainBasedAgriFoodSupply2020, wangAuditableProtocolsFair2019, chenImprovedP2PFile2017}.
+Specifically, data is stored on a network such as IPFS~\cite{benetIPFSContentAddressed2014}, and only the content identifier ($\mathrm{cid}$) that uniquely points to the content on IPFS is published on the blockchain.
+\end{sloppypar}
+
+Following this methodology, the SP encrypts the result using the encryption key provided by the client and uploads it to the IPFS network.
+To ensure the availability of the results, even in cases where the SP is unwilling to share them, we integrate Filecoin as described in Section~\ref{sec:provable-results-availability}.
+
+To further increase anonymity, customers are advised to use standard techniques such as VPNs or proxies to hide their IP addresses.
 
@@
 \begin{sloppypar}
-The protocol we propose could potentially utilize a single blockchain to fulfill three distinct roles: (i) facilitating anonymous payments, (ii) serving as a message board, and (iii) acting as a storage network.
-However, while most blockchains can provide message board functionality, anonymous payments and a verifiable storage network are less common features, often limited to specialized blockchains.
-
-Instead of relying on a single blockchain to provide all functionalities, our protocol is designed to be flexible, allowing the use of separate blockchains for each specific role.
-This approach provides the freedom to choose the best technology available for each function.
+The protocol we propose could potentially use a single blockchain to fulfil three different roles: i) facilitating anonymous payments, ii) serving as a message board, and iii) acting as a storage network.
+However, while most blockchains can provide message board functionality, anonymous payments and a verifiable storage network are less common features and are often limited to specialized blockchains.
+
+Rather than relying on a single blockchain to provide all functionalities, our protocol is designed to be flexible, allowing the use of separate blockchains for each specific role.
+This approach provides the freedom to choose the best available technology for each function.
 In the future, if a blockchain emerges that can efficiently handle multiple roles, it can be integrated into the protocol.
 
-As of the current state of blockchain technology, we identify the following platforms as suitable candidates for each role:
-
+Based on the current state of blockchain technology, we identify the following platforms as suitable candidates for each role:
 \begin{enumerate}
-    \item \textbf{Anonymous Payments:} Technologies such as Monero~\cite{vansaberhagenCryptoNote2013}, ZCash~\cite{ben-sassonZerocashDecentralizedAnonymous2014}, Grin~\cite{fuchsbauerAggregateCashSystems2019}, and Tornado Cash~\cite{pertsevTornadoCashPrivacy2019} offer robust solutions for anonymous transactions.
-    \item \textbf{Message Board:} Various platforms can be utilized for this purpose, including Open timestamps~\cite{opentimestampsTimestampingProofStandard}, Stampery~\cite{crespoStamperyBlockchainTimestamping2017}, and the Bitcoin blockchain with services like Proof of Existence~\cite{proofofexistenceWebApplicationProve} and Chainpoint~\cite{chainpointBlockchainProofAnchoring}.
-The Ethereum blockchain, along with other public blockchains that support attaching extra data to transactions, are also viable options.
-    \item \textbf{Storage Network:} For decentralized storage solutions, IPFS~\cite{benetIPFSContentAddressed2014}, Filecoin~\cite{protocollabsFilecoinDecentralizedStorage2017}, and Ethereum's Swarm~\cite{teamSWARMStorageCommunication2021} are among the leading technologies.
+  \item \textbf{Anonymous payments:} Technologies such as Monero~\cite{vansaberhagenCryptoNote2013}, ZCash~\cite{ben-sassonZerocashDecentralizedAnonymous2014}, Grin~\cite{fuchsbauerAggregateCashSystems2019} and Tornado Cash~\cite{pertsevTornadoCashPrivacy2019} provide robust solutions for anonymous transactions.
+  \item \textbf{Message Board:} Several platforms can be used for this purpose, including Open Timestamps~\cite{opentimestampsTimestampingProofStandard}, Stampery~\cite{crespoStamperyBlockchainTimestamping2017} and the Bitcoin blockchain with services like Proof of Existence~\cite{proofofexistenceWebApplicationProve} and Chainpoint~\cite{chainpointBlockchainProofAnchoring}.
+The Ethereum blockchain and other public blockchains that support attaching extra data to transactions are also viable options.
+  \item \textbf{Storage Network:} For decentralized storage solutions, IPFS~\cite{benetIPFSContentAddressed2014}, Filecoin~\cite{protocollabsFilecoinDecentralizedStorage2017} and Ethereum's Swarm~\cite{teamSWARMStorageCommunication2021} are among the leading technologies.
 \end{enumerate}
@@
 \section{The Protocol}\label{sec:protocol}
-This section outlines an abstract protocol for anonymous service provisioning, designed to be technology-agnostic.
-It specifies the requirements for each role, allowing developers flexibility in technology selection.
-The implementation details and experimental validation of this protocol are discussed in Section~\ref{sec:experiments}.
+This section outlines an abstract protocol for anonymous service provisioning that is designed to be technology agnostic.
+It specifies the requirements for each role, allowing developers flexibility in technology choice.
+Implementation details and experimental validation of this protocol are discussed in Section~\ref{sec:experiments}.
 
@@
 \begin{itemize}
-
   \item \textbf{Cryptography and Public Key Infrastructure (PKI)}:
   \begin{itemize}
-        \item The service provider (SP) possesses a key pair consisting of a secret key ($\mathrm{sk}_\mathrm{SP}$) and a publicly known public key ($\mathrm{pk}_\mathrm{SP}$).
-        \item Digital signatures created by the SP ($\mathrm{sig}_{\mathrm{sk}_\mathrm{SP}}$) can be verified using the publicly accessible $\mathrm{pk}_\mathrm{SP}$.
-        \item The customer remains anonymous and does not require a publicly known key pair, ensuring their privacy and anonymity in the protocol.
-
-        \item Both parties utilize standard symmetric encryption ($\mathrm{E}_\mathrm{key}(\cdot)$) and decryption ($\mathrm{D}_\mathrm{key}(\cdot)$) methods.
+      \item The service provider (SP) has a key pair consisting of a secret key ($\mathrm{sk}_\mathrm{SP}$) and a publicly known public key ($\mathrm{pk}_\mathrm{SP}$).
+      \item Digital signatures created by the SP ($\mathrm{sig}_{\mathrm{sk}_\mathrm{SP}}$) can be verified using the public $\mathrm{pk}_\mathrm{SP}$.
+      \item The customer remains anonymous and does not require a publicly known key pair, thus ensuring their privacy and anonymity in the protocol.
+
+    \begin{sloppypar}
+      \item Both parties use standard symmetric encryption ($\mathrm{E}_\mathrm{key}(\cdot)$) and decryption ($\mathrm{D}_\mathrm{key}(\cdot)$) methods.
+    \end{sloppypar}
 \end{itemize}
@@
       \item The SP is willing to accept packages from unidentified customers.
-        \item Payments are accepted via cash or anonymous cryptocurrencies, as detailed in Section~\ref{payment-for-services}.
+      \item Payments are accepted in cash or anonymous cryptocurrencies, as detailed in Section~\ref{payment-for-services}.
    \end{itemize}
@@
       \item Facilitates anonymous transactions that are untraceable and ideally unlinkable.
-        \item Allows transactions to be uniquely identified through dedicated addresses, memo fields, or similar mechanisms (see Section~\ref{payment-for-services}).
+      \item Allows transactions to be uniquely identified through dedicated addresses, memo fields or similar mechanisms (see Section~\ref{payment-for-services}).
   \end{itemize}
@@
   \begin{itemize}
-        \item Enables content retrieval using a content identifier ($\mathrm{cid}$), typically a hash of the content.
+      \item Enables content to be retrieved using a content identifier ($\mathrm{cid}$), typically a hash of the content.
       \item Ensures anonymous access to content.
-        \item Provides a guarantee of content availability for the agreed duration.
+      \item Guarantees that the content will be available for an agreed period of time.
   \end{itemize}
@@
 \end{itemize}
-
-\begin{sloppypar}
-This protocol framework sets the stage for a secure, anonymous, and fair service provisioning system.
-It balances the needs for privacy and accountability, ensuring that both the customer and the SP can engage in transactions with confidence in the system's integrity and fairness.
-\end{sloppypar}
 
@@
 \]
-% TODO continute from here
 
@@
 \section{Fairness Analysis}\label{sec:fairness-analysis}
-Our protocol's fairness is assessed through its representation as an interactive non-cooperative game, examining the strategic interactions between the service provider (SP) and the customer.
+The fairness of our protocol is assessed by representing it as an interactive non-cooperative game, examining the strategic interactions between the service provider (SP) and the customer.
 
@@
 \begin{itemize}
-\item \textbf{Neutral Position ($\neutral{}$)}: A party's state when no significant resources (money, time, effort) have been expended or acquired.
-\item \textbf{Disadvantaged Position ($\minus{}$)}: A party's state when it has invested resources without receiving a commensurate return, like a customer who has prepaid for a service.
-\item \textbf{Advantaged position ($\plus{}$)}: A scenario where halting the transaction would result in a benefit for a party, for instance, if the SP has been paid but has not yet provided the service.
+\item \textbf{Neutral Position ($\neutral{}$)}: The state of a party when no significant resources (money, time, effort) have been expended or acquired.
+\item \textbf{Disadvantaged Position ($\minus{}$)}: The state of a party when it has invested resources without receiving a commensurate return, like a customer who has paid in advance for a service.
+\item \textbf{Advantaged position ($\plus{}$)}: A scenario where stopping the transaction would result in a benefit to one party, e.g. where the SP has been paid but has not yet delivered the service.
 \end{itemize}
@@
 \begin{enumerate}
-\item \textbf{Normal} ($\normal{}$): Those that adhere to the protocol's prescribed steps.
+\item \textbf{Normal} ($\normal{}$): Those who adhere to the prescribed steps of the protocol.
 \item \textbf{Abnormal} ($\abnormal{}$): Any deviation from the protocol's prescribed steps, such as sending irrelevant messages, skipping steps, or exceeding time limits.
@@
 \item \textbf{Agree} ($\normal{}$ or $\abnormal{}$): The customer consents to the action and refrains from disputing.
-\item \textbf{Start a dispute} ($\dispute{}$ or $\abdispute{}$): The customer contests the action and initiates a dispute.
+\item \textbf{Start a dispute} ($\dispute{}$ or $\abdispute{}$): The customer opposes the action and initiates a dispute.
 \end{enumerate}
@@
 \begin{sloppypar}
-Consequently, our analysis must account for four potential $\mathrm{action} \in \{ \normal{}, \abnormal{}, \dispute{}, \abdispute{} \}$, for each $\mathrm{party \in \{C, SP\} }$, at every protocol step $\mathrm{step \in 1..9}$:
+  Consequently, our analysis needs to consider four possible $\mathrm{action} \in \{ \normal{}, \abnormal{}, \dispute{}, \abdispute{} \}$, for each $\mathrm{party \in \{C, SP\} }$, at every protocol step $\mathrm{step \in 1..9}$:
 \end{sloppypar}
@@
 
-The protocol concludes after the final step, if a dispute is initiated, or if a party fails to perform its required action within the designated timeframe.
-Hence, all positions except $\mathrm{\sigma_{step, party, n}}$ for $\mathrm{step} \in 1..8$ signify the end of the protocol.
+\begin{sloppypar}
+The protocol ends after the final step, if a dispute is initiated, or if a party fails to take the required action within the specified timeframe.
+Therefore, all positions except $\mathrm{\sigma_{step, party, n}}$ for $\mathrm{step} \in 1..8$ indicate the end of the protocol.
+\end{sloppypar}
 
@@
 
-A protocol is considered fair if, at every step, both the customer and the service provider have the option  to move to or stay in a non-disadvantaged position.
+A protocol is said to be fair if, at each step, both the customer and the service provider have the option to move to or remain in a non-disadvantaged position.
 
@@
 \item Both parties start from a neutral position ($\neutral{}$), implying no initial advantage or disadvantage.
-\item Upon successful transaction completion, both parties attain an advantageous position (\plus{}), indicating mutual benefit and motivation to engage in and complete the transaction.
-\item The steps within the protocol are atomic, meaning they are indivisible and have no intermediate states.
+\item Upon successful completion of the transaction, both parties reach an advantageous position (\plus{}), indicating mutual benefit and motivation to initiate and complete the transaction.
+\item The steps within the protocol are atomic, i.e. they are indivisible and have no intermediate states.
 \item The protocol is unidirectional; actions taken cannot be reversed or undone.
@@
 For example, a double payment does not change the course of the protocol.
-\item Once the service result is published, it becomes accessible to the customer via the storage network.
+\item Once the result of the service is published, it becomes available to the customer via the storage network.
 \item A successful dispute resolution restores the disputing party to a neutral position ($\neutral{}$).
@@
 
-The fairness of our protocol is visually represented in Figure~\ref{fig:positions}, which illustrates the positions of each party following each possible action within the protocol.
+The fairness of our protocol is visually represented in Figure~\ref{fig:positions}, which shows the positions of each party after each possible action within the protocol.
 
@@
 
-The detailed description of each step and the reasoning for the outcomes is given in~\ref{app:proof-of-fairness}.
+The detailed description of each step and the reasoning behind the outcomes is given in~\ref{app:proof-of-fairness}.
 
 \subsection{Example scenarios}\label{example-scenarios}
-This section illustrates two key scenarios using figures to demonstrate the transitions of positions between the customer and the SP under different conditions.
+This section illustrates two key scenarios using figures to show the transitions of positions between the customer and the SP under different conditions.
 
@@
 \centering
-\caption{Transitions of positions in a scenario where the SP misbehaves by not performing the service and failing to publish $\mathrm{PoP}$ after receiving payment.
+\caption{Transitions of positions in a scenario where the SP misbehaves by failing to perform the service and publish $\mathrm{PoP}$ after receiving payment.
 This leads to the customer initiating a dispute.}
@@
 
-Our protocol's prototype was developed using a suite of technologies designed to ensure anonymity and security:
-
-\begin{itemize}
-\begin{sloppypar}
-  \item \textbf{Anonymous Payments:} Utilization of the Monero blockchain for secure transactions.
+The prototype of our protocol has been developed using a number of technologies designed to ensure anonymity and security:
+\begin{itemize}
+\begin{sloppypar}
+  \item \textbf{Anonymous Payments:} Use of the Monero blockchain for secure transactions.
 \end{sloppypar}
@@
 \begin{sloppypar}
-Anonymity was secured by breaking the link between personal data and transactional elements, including materials, payments, and communications.
-We utilized anonymous payment methods such as cash and privacy-centric cryptocurrencies like Monero, to conceal transactional details.
+Anonymity was ensured by breaking the link between personal data and transactional elements, including materials, payments, and communications.
+We used anonymous payment methods such as cash and privacy-centric cryptocurrencies like Monero, to conceal transactional details.
 Furthermore, we leveraged decentralized storage networks like IPFS and Filecoin, which facilitate the anonymous storage and retrieval of data.
@@
 
-\begin{table}[h!]
+\begin{table}
+\caption{Incurred Costs for Protocol Operations}
 \centering
-\caption{Incurred Costs for Protocol Operations}
 \label{table:costs}
-\begin{tabular}{|l|l|l|}
+\begin{tabular}{lrr}
 \hline
-\textbf{Operation}            & \textbf{Gas Units} & \textbf{Cost (USD)} \\ \hline
-Smart Contract Deployment     & 1,456,577          & 4.09                \\ \hline
-Proof of Delivery             & 129,649            & 0.29                \\ \hline
-Payment (Monero)              & -                  & 0.0456              \\ \hline
-Proof of Provision            & 149,130            & 0.33                \\ \hline
+\textbf{Operation}            & \textbf{Gas Units} & \textbf{Cost (USD)} \\
+\hline
+Smart Contract Deployment     & 1,456,577          & 4.09                \\
+Proof of Delivery             & 129,649            & 0.29                \\
+Payment (Monero)              & -                  & 0.0456              \\
+Proof of Provision            & 149,130            & 0.33                \\
+\hline
 \end{tabular}
@@
 \label{table:performance}
-\begin{tabular}{|l|l|l|l|}
+\begin{tabular}{lrrr}
 \hline
 \textbf{Network}     & \textbf{Block Time} & \textbf{Tx Throughput} & \textbf{Tx Latency} \\ \hline
-Ethereum             & 13-15 sec       & 15-30 TPS                       & \textasciitilde{}6 min      \\ \hline
-Monero               & \textasciitilde{}2 min & \textasciitilde{}4 TPS             & \textasciitilde{}20 min \\ \hline
-Filecoin             & 30 s & N/A\footnotemark{}            & 5-10 min \\ 
-& & & for 1 MiB file \\ \hline
+Ethereum             & 13-15 sec       & 15-30 TPS                       & \textasciitilde{}6 min      \\
+Monero               & \textasciitilde{}2 min & \textasciitilde{}4 TPS             & \textasciitilde{}20 min \\
+Filecoin             & 30 sec & N/A\footnotemark{}            & 5-10 min  \\ 
+\hline
 \end{tabular}

### 2024-06-10 paper/main.tex
update to the reviewer requests

@@
 \begin{sloppypar}
-We frame anonymous service provision as a fair exchange problem, ensuring that either both parties obtain the goods or neither does.
-Our review indicates that current systems do not meet our goals.
-We propose an anonymous protocol for services requiring physical materials, with dispute resolution capabilities.
+We frame anonymous service provision as a fair exchange problem, ensuring that either both parties (customer and service provider) get the goods or neither.
+In our case, the parties exchange money and sensitive (possibly physical) materials for a service result.
+Our review shows that current systems do not achieve our goals.
+We propose an anonymous protocol for services that require physical materials, with dispute resolution capabilities.
 If disputes arise, customers can disclose interactions and prove SP misbehavior.
@@
 
+\begin{sloppypar}
 We have only considered protocols that achieve fair exchange, as this is the fundamental feature of such protocols.
-
-\begin{sloppypar}
 We also didn't focus on protocols for buying digital products, as they are not relevant to our use case.
@@
 However, it does not provide dispute resolution.
-
 Hinarejos et al.
@@
 However, it does not take into account anonymity, disputes between parties, or the exchange of physical material.
-
 Meng et al. 2019~\cite{mengThemisDecentralizedEscrow2019} improves on the previous protocol through a crowdsourced dispute resolution system. However, it does not consider anonymity.
-
 Bîrjoveanu, 2022~\cite{birjoveanuTwoPartyECommerceProtocols2022} is the closest to our protocol, but it is based on strong assumptions, namely the existence of TTP, banks supporting confidential transactions with commit buffers, and maintaining a global list of coin serial numbers.
@@
 
-Unlike most protocols, our system is designed for transactions where the package is delivered from the customer to the service provider (SP), and we assume a generic dispute resolution service to handle conflicts.
-
-To provide a clearer understanding of how our protocol compares to existing work, Table~\ref{tab:comparison} provides a summary of the key features and differences between the protocols discussed.
+Table~\ref{tab:comparison} provides a summary of the key features and differences between the protocols discussed.
 
@@
     \item \textbf{Privacy preserving blockchains:} These blockchains inherently support both anonymity and confidentiality through advanced cryptographic techniques, ensuring that both user identities and transaction details are obscured.
-Examples:
-      \begin{itemize}
-          \item \textbf{Monero:} Uses ring signatures and bulletproofs~\cite{vansaberhagenCryptoNote2013, noetherRingSignatureConfidential2015, bunzBulletproofsShortProofs2018}.
-          \item \textbf{ZCash:} Uses zkSNARKs for private transactions~\cite{ben-sassonZerocashDecentralizedAnonymous2014}.
-          \item \textbf{Grin} and \textbf{IronFish:} Use Mimblewimble and the Sapling protocol respectively~\cite{jedusorMIMBLEWIMBLE2016,fuchsbauerAggregateCashSystems2019, hopwoodZcashSaplingProtocol2022, ironfishPrivateAnonymousEasy}.
-    \end{itemize}
-
+Examples include \textbf{Monero}, which uses ring signatures and bulletproofs~\cite{vansaberhagenCryptoNote2013, noetherRingSignatureConfidential2015, bunzBulletproofsShortProofs2018}, \textbf{ZCash}, which uses zkSNARKs for private transactions~\cite{ben-sassonZerocashDecentralizedAnonymous2014}, and \textbf{Grin} and \textbf{IronFish}, which use Mimblewimble and the Sapling protocol respectively~\cite{jedusorMIMBLEWIMBLE2016,fuchsbauerAggregateCashSystems2019, hopwoodZcashSaplingProtocol2022, ironfishPrivateAnonymousEasy}.
     \item \textbf{Non-privacy preserving blockchains:} These blockchains, such as Bitcoin and Ethereum, do not natively support strong privacy features.
 However, anonymity can be enhanced through the use of mixers and other privacy tools.
-Examples:
-    \begin{itemize}
-          \item \textbf{Tornado Cash} (Ethereum): Implements zkSNARKs and MiMC for enhanced privacy~\cite{grothSizePairingbasedNoninteractive2016,pertsevTornadoCashPrivacy2019}.
-          \item \textbf{Wasabi Wallet} (Bitcoin): Uses CoinJoin to mix transactions~\cite{maxwellCoinJoinBitcoinPrivacy2013,wasabiwalletBitcoinPrivacyWallet}.
-    \end{itemize}
+Examples include \textbf{Tornado Cash} (Ethereum), which implements zkSNARKs and MiMC for enhanced privacy~\cite{grothSizePairingbasedNoninteractive2016,pertsevTornadoCashPrivacy2019}, and \textbf{Wasabi Wallet} (Bitcoin), which uses CoinJoin to mix transactions~\cite{maxwellCoinJoinBitcoinPrivacy2013,wasabiwalletBitcoinPrivacyWallet}.
 \end{enumerate}
@@
 
-\begin{itemize}
+\begin{enumerate}
 \item $\mathrm{\sigma_{step,party,\normal{}}}$: The outcome after adhering to the protocol with the other party acting normally.
@@
 \item $\mathrm{\sigma_{step,party,\abdispute{}}}$: The outcome after a resolved dispute with the other party acting abnormally.
-\end{itemize}
+\end{enumerate}
 
@@
 represent the set of all possible positions a party $\mathrm{p}$ can move to at step $\mathrm{s}$ by taking action $\mathrm{a}$, from position $\sigma_\mathrm{s,p,a}$.
-The second case in $M_{\sigma_\mathrm{s,p,a}}$ represents the termination position.
+The second case in $M_{\sigma_\mathrm{s,p,a}}$ represents the termination positions.
 
@@
 For simplicity, all components run on one physical machine; and all processes are managed by Docker. 
-
 Moreover, Powergate is configured to use local Filecoin and IPFS networks.
@@
 
-\begin{sloppypar}
 In preparation for the experiment, both the customer and the SP set up their Monero wallets using the \texttt{monero-wallet-cli}.
 The SP deploys the smart contract to the Ethereum blockchain with the \texttt{truffle migrate --network development} command, and the web application is then configured to interact with this newly deployed contract.
-\end{sloppypar}
-
 The customer acquires test Monero funds from a Faucet service and configures their wallet to generate transaction proofs, essential for dispute resolution.
-
 With preparations complete, the experiment proceeds as follows:

### 2024-08-07 paper/main.tex
reviewer1 suggestions

@@
 \def\JOURNALELS{ELS}
-
 \newcommand\TITLE{Anonymous provision of privacy-sensitive services using blockchain and decentralised storage}
@@
 The processing of personal data, especially when providing services involving sensitive data such as health records, biological material or legal documents, exposes both users and service providers (SPs) to privacy risks.
-SPs are at risk of violating GDPR, CPAA and other legal regulations, while customers are at risk of losing their privacy.
-
-We observe that personal data is often only used for logistical purposes, such as payment or communication, and could be provided anonymously if such methods were available.
+SPs are at risk of violating General Data Protection Regulation (GDPR), Consumer Protection Act (CPA) and other legal regulations, while customers are at risk of losing their privacy.
+
+We observe that personal data is often only used for logistical purposes, such as communication, and could be provided anonymously if such methods were available.
 
@@
 
-The processing of personal data, especially when providing services involving sensitive data such as health records, biological material or legal documents, exposes both users and service providers (SPs) to privacy risks.
-SPs are at risk of violating GDPR, CPAA and other legal regulations, while customers are at risk of losing their privacy.
+Processing personal data, especially for services involving sensitive information such as health records, biological materials, or legal documents, exposes both users and service providers (SPs) to privacy risks.
+SPs are at risk of violating General Data Protection Regulation (GDPR), Consumer Protection Act (CPA) and other legal regulations, while customers are at risk of losing their privacy.
 
@@
 \begin{sloppypar}
-Sensitive diagnostic services such as paternity tests, doping tests, and venereal disease tests require customers to provide biological material like blood, urine, stool, or saliva, which often necessitates revealing their identity.
+Sensitive diagnostic services such as paternity tests, doping tests, and venereal disease tests require customers to provide biological material such as blood, urine, stool, or saliva, which often necessitates revealing their identity.
 This exposure poses significant privacy risks.
-Similarly, other sensitive services include anonymous complaints, legal services requiring financial and confidential disclosures, and banking services needing personal information like medical records and financial histories.
-The necessity to provide personal information exposes users to risks such as loss of control over their information, identity theft, data breaches, and unauthorized monitoring, which can lead to severe consequences like GDPR or CCPA violations, targeted advertising, or unlawful tracking and surveillance~\cite{smithInformationPrivacyResearch2011}.
+Similarly, other sensitive services include anonymous complaints, legal services requiring financial and confidential disclosures, and banking services needing personal information such as medical records and financial histories.
+The necessity to provide personal information exposes users to risks such as loss of control over their information, identity theft, data breaches, and unauthorized monitoring, which can lead to severe consequences such as GDPR or CPA violations, targeted advertising, or unlawful tracking and surveillance~\cite{smithInformationPrivacyResearch2011}.
 \end{sloppypar}

### 2024-08-08 paper/main.tex
add paragraph on public vs permissioned blockchains

@@
 The protocol is designed to be adaptable, allowing for implementation with any decentralized technology capable of providing a message board service and supporting subscription to proofs from specific addresses.
+
+The choice between permissioned and permissionless blockchain touches on an ideological dispute about freedom and trust.
+The use of permissioned blockchain is recommended in domain-specific applications, such as closed consortia between distrustful parties.
+All the referenced protocols we've found use a public blockchain, suggesting that the fair exchange problem is allegedly not one of them.
+The public blockchain offers the irreplaceable qualities of total decentralisation, transparency, openness, no infrastructure maintenance costs (only transaction costs) and a different but arguably higher level of security (for networks with a high number of validators).
+In addition, protocols designed for public blockchains have a higher degree of generality and can be implemented in any private or permissioned blockchain.
+Therefore, for the rest of the paper, we only consider public networks.
 

### 2024-08-09 paper/main.tex
add Provable Results Availability

@@
 
+\begin{sloppypar}
 The choice between permissioned and permissionless blockchain touches on an ideological dispute about freedom and trust.
@@
 Therefore, for the rest of the paper, we only consider public networks.
+\end{sloppypar}
 
@@
 
-\begin{sloppypar}
-A common solution is to use a content addressable peer-to-peer storage network for data storage, as direct blockchain storage is prohibitively expensive.
+Even though the result does not contain private information (because the input data did not have it) we acknowledge the danger of storing on a distributed immutable record as blockchain.
+
+\begin{sloppypar}
+A common solution is to use a content addressable peer-to-peer storage network for data storage.
 This approach has been widely adopted in various applications~\cite{shahidBlockchainBasedAgriFoodSupply2020, wangAuditableProtocolsFair2019, chenImprovedP2PFile2017}.
@@
 Following this methodology, the SP encrypts the result using the encryption key provided by the client and uploads it to the IPFS network.
-To ensure the availability of the results, even in cases where the SP is unwilling to share them, we integrate Filecoin as described in Section~\ref{sec:provable-results-availability}.
+
+The result is stored on public network so it is accessible to anyone with the cid address.
+However, the result is encrypted, so even if downloaded by third party it doesn't get access to the file unless it obtains the client's or SP's private key.
 
 To further increase anonymity, customers are advised to use standard techniques such as VPNs or proxies to hide their IP addresses.
+
+\subsection{Provable Results Availability}
+
+The demand-driven and opportunistic nature of IPFS storage means that the results may not be available indefinitely.
+
+To ensure the availability of the results, we see two approaches.
+One involves fraud proofs, where an user which can not access the results invoke oracle service like Chainlink Request~\cite{breidenbachChainlinkNextSteps2021, ChainlinkMakeGET} which proves the content unavailability, and so pentalise the SP.
+
+The other approach is to integrate Filecoin as a decentralised pinning service to ensure the results are available for a defined period.
+
+Filecoin enhances content availability on the IPFS network by economically penalizing the lack of proof of content storage~\cite{filecoinSlashing}.
+
+The content availability is therefore economically guaranteed for the duration of the Filecoin contract.
+
+Then, a file that is not further paid for in the Filecoin network is naturally deleted from the network as there is not incentive to keep it.
+
+In this paper we explore the second approach and leave the first for future work.
 
@@
 \noindent \textbf{Package}\label{package} is a physical container prepared by the customer containing all the $\mathrm{materials}$ required by the SP to provide the service.
-\[\mathrm{pkg} \equiv (\mathrm{materials}, \mathrm{provisionID}, \mathrm{pk_C})\]
+\begin{equation}
+\mathrm{pkg} \equiv (\mathrm{materials}, \mathrm{provisionID}, \mathrm{pk_C})
+\end{equation}
 where:
@@
 It is also an agreement between the customer and the SP as it contains agreed deadlines for actions and a payment method.
-\begin{eqnarray*}
+\begin{eqnarray}
 \mathrm{PoD} & \equiv & (\begin{array}[t]{l}\mathrm{pk_C}, \mathrm{provisionID},   \mathrm{paymentAddress},
@@
 \mathrm{T}_\mathrm{issue}, \mathrm{T}_\mathrm{pay}, \mathrm{T}_\mathrm{provide}\; )\end{array}
-\end{eqnarray*}
+\end{eqnarray}
 where:
@@
 The link between $\mathrm{PoP}$ and the results is made by the content identifier ($\mathrm{cid}$), which uniquely identifies the results so that the result cannot be forged after the $\mathrm{PoP}$ has been published.
-\begin{eqnarray*}
-\mathrm{PoP} & \equiv & (\mathrm{cid}, \mathrm{provisionID}, \mathrm{sig}_\mathrm{SP})
-\end{eqnarray*}
+\begin{equation}
+\mathrm{PoP} \equiv (\mathrm{cid}, \mathrm{provisionID}, \mathrm{sig}_\mathrm{SP})
+\end{equation}
 
@@
 Let $\mathrm{parties} = \{ C, SP \}$, $\mathrm{steps} = 1..9$, $\mathrm{actions} = \{ \normal{}, \abnormal{}, \dispute{}, \abdispute{} \}$, and
-\[
+
+\begin{equation}
 M_{\sigma_\mathrm{s,p,a}} = 
@@
 \end{cases}
-\]
+\end{equation}
 represent the set of all possible positions a party $\mathrm{p}$ can move to at step $\mathrm{s}$ by taking action $\mathrm{a}$, from position $\sigma_\mathrm{s,p,a}$.
@@
 
+\subsection{Ethical and Regulatory Considerations}
+
+The core objective of our protocol is to facilitate anonymous access to services without necessitating the disclosure of personal information, which naturally raises concerns regarding regulatory compliance, particularly with Know Your Customer (KYC), Anti-Money Laundering (AML), and regulations concerning Politically Exposed Persons (PEP).
+
+Our approach is explicitly designed to integrate with services that inherently comply with applicable local and international regulations.
+This integration ensures that while our protocol itself operates under the premise of anonymity, it does not facilitate illegal activities or contravene established legal frameworks.
+Specifically, the services that would utilize our protocol are those not primarily involved in financial transactions or money transmission, thereby not falling directly under the stringent requirements of financial regulations such as KYC and AML.
+
+We acknowledge that the use of anonymous payment methods, such as cryptocurrencies like Monero, might raise suspicions due to their common association with privacy and potential misuse.
+However, it is important to note that Monero is just one of several anonymous payment methods that could be utilized with our protocol.
+Our design is versatile enough to support a variety of payment mechanisms, both blockchain-based and non-blockchain-based.
+
+\begin{sloppypar}
+For instance, we could employ the Ethereum network and utilize privacy mixers to ensure private payments.
+Nevertheless, privacy mixers have drawn scrutiny from regulators because they are increasingly used by malicious actors to obscure the origins of funds illicitly.
+A notable example is Tornado Cash, the largest privacy mixer to date, which has faced sanctions across significant portions of the Ethereum network.
+Ongoing research into compliant privacy mixers, such as the Voluntary Reveal Approach proposed in~\cite{dotanHazeCompliantPrivacy2023}, seeks to address these concerns.
+This approach involves Proofs of Innocence required before a user can access the system and incorporates oracles for monitoring sanctioned addresses—currently maintained on the Ethereum blockchain by Chainalysis~\cite{ChainalysisOracleSanctions}.
+\end{sloppypar}
+
 \section{Conclusions}\label{sec:conclusion}

### 2024-08-12 paper/main.tex
update dispute and anonimity

@@
 Traditionally, this has involved legal contracts and law enforcement.
-With blockchain technology, smart contracts offer a new way by putting contract details into code and enforcing them automatically~\cite{allenGovernanceBlockchainDispute2019}.
+With blockchain technology, smart contracts offer a new way by putting the details of a contract into code and enforcing it through a consensus mechanism.~\cite{allenGovernanceBlockchainDispute2019}.
 \end{sloppypar}
@@
 
-\subsection{Example scenarios}\label{example-scenarios}
-This section illustrates two key scenarios using figures to show the transitions of positions between the customer and the SP under different conditions.
+\subsection{Analyse scenarios}\label{example-scenarios}
+This section illustrates two scenarios using figures to show the transitions of positions between the customer and the SP under different conditions.
 
@@
 
-In the first scenario (Figure~\ref{fig:misbehaviour}), the SP attempts to misbehave by not delivering the service and consequently not publishing the Proof of Provision ($\mathrm{PoP}$) after receiving payment.
-If the SP fails to publish a valid $\mathrm{PoP}$ by the deadline $\mathrm{T}_\mathrm{provide}$, the customer is justified in starting a dispute.
+\paragraph{Dispute}
+In the first scenario (Figure~\ref{fig:misbehaviour}), (1) the customer initialise the transaction and delivers the material to the SP, (2) who validates the materials and publish the Proof of Delivery ($\mathrm{PoD}$) on blockchain.
+(3) The customer validates the existence of PoD on blockchain and (4) pay for the transaction using one of the specified payment method.
+(5) The SP misbehaves by not delivering the service and consequently not publishing the Proof of Provision ($\mathrm{PoP}$) after having received the payment.
+Once the agreed deadline $\mathrm{T}_\mathrm{provide}$ pass the position moves to the Abnormal column and the customer is in disadvantage position and the SP is in advantage position.
+However, the customer is justified in starting a dispute, by collecting all the evidences, i.e., Proof of Delivery ($\mathrm{PoD}$) from Message Board, payment $\mathrm{recipt}$, and delivering them to the Dispute Resolution Service.
 The customer is likely to win this dispute as the SP cannot prove the timely publication of $\mathrm{PoP}$.
@@
 
+\paragraph{Agreement}
 The second scenario (Figure~\ref{fig:rational}) represents the rational and intended course of action, where both the customer and the SP follow the protocol as designed.
@@
 
-Blockchain-based dispute resolution platforms such as Themis~\cite{mengThemisDecentralizedEscrow2019}, Kleros~\cite{bergollaKlerosSociolegalCase2022, gudkovCrowdArbitrationBlockchain2020}, Aragon Court~\cite{aragonDecentralizedDisputeResolution}, LTO Network~\cite{ltonetworkNextGenBlockchainB2B}, and other Online Dispute Resolution (ODR) systems~\cite{allenGovernanceBlockchainDispute2019} offer a promising direction.
-These systems could employ a pool of field experts who, in the event of a dispute, would examine the proofs (e.g., $\mathrm{PoD}$, $\mathrm{PoP}$, payment $\mathrm{receipt}$) in a confidential, zero-knowledge context, providing verdicts without access to personal data.
+Blockchain-based dispute resolution platforms such as  Kleros~\cite{bergollaKlerosSociolegalCase2022, gudkovCrowdArbitrationBlockchain2020}, Themis~\cite{mengThemisDecentralizedEscrow2019}, Aragon Court~\cite{AragonWhitepaper2023,aragonDecentralizedDisputeResolution}, LTO Network~\cite{ltonetworkNextGenBlockchainB2B}, and other Online Dispute Resolution (ODR) systems~\cite{allenGovernanceBlockchainDispute2019} offer a promising direction.
+These systems could employ a pool of field experts who, in the event of a dispute, would examine the smart contract, proofs ( $\mathrm{PoD}$, $\mathrm{PoP}$, payment $\mathrm{receipt}$) and providing verdicts.
 Expert participation and honest adjudication would be encouraged through a system of fees, stakes, and rewards.
+At the time of writing Kleros is the most successful protocol for the disputes resolution, claiminng to employ 716 jurors and having resolved 1645 disputes.
 

### 2024-08-12 paper/main.tex
update lose of anonimity in case of dispute

@@
 
+In the event of a dispute, the customer may lose their anonymity due to local policy enforcement that requires identification.
+To maintain anonymity in the event of a dispute, the anonymous dispute resolution service would have to be used.
+We discuss this further in section~\ref{sec:decentralised-justice}.
+
 \paragraph{Provable Results Availability}\label{sec:provable-results-availability}
@@
 
-Blockchain-based dispute resolution platforms such as  Kleros~\cite{bergollaKlerosSociolegalCase2022, gudkovCrowdArbitrationBlockchain2020}, Themis~\cite{mengThemisDecentralizedEscrow2019}, Aragon Court~\cite{AragonWhitepaper2023,aragonDecentralizedDisputeResolution}, LTO Network~\cite{ltonetworkNextGenBlockchainB2B}, and other Online Dispute Resolution (ODR) systems~\cite{allenGovernanceBlockchainDispute2019} offer a promising direction.
-These systems could employ a pool of field experts who, in the event of a dispute, would examine the smart contract, proofs ( $\mathrm{PoD}$, $\mathrm{PoP}$, payment $\mathrm{receipt}$) and providing verdicts.
-Expert participation and honest adjudication would be encouraged through a system of fees, stakes, and rewards.
-At the time of writing Kleros is the most successful protocol for the disputes resolution, claiminng to employ 716 jurors and having resolved 1645 disputes.
+Blockchain-based dispute resolution platforms such as  Kleros~\cite{bergollaKlerosSociolegalCase2022, nappertDecentralizedJusticeReinventing2020, gudkovCrowdArbitrationBlockchain2020}, Themis~\cite{mengThemisDecentralizedEscrow2019}, Aragon Court~\cite{AragonWhitepaper2023,aragonDecentralizedDisputeResolution}, LTO Network~\cite{ltonetworkNextGenBlockchainB2B}, and other Online Dispute Resolution (ODR) systems~\cite{allenGovernanceBlockchainDispute2019, lingwallShouldCodeBe2019} offer a promising direction.
+These systems could employ a pool of field experts who, in the event of a dispute, would examine the smart contract, the proofs ( $\mathrm{PoD}$, $\mathrm{PoP}$, payment $\mathrm{receipt}$) and provide verdicts.
+Expert participation and honest verdicts are encouraged through a system of fees, stakes and rewards.
+At the time of writing Kleros is the most successful platform for resolving consumer disputes in e-commerce or collaborative economy.
+It has received funding from the Commission's European Innovation Council~\cite{CommissionEuropeanInnovation2020}.
+The protocol claims to have resolved 1645 disputes, employing 716 jurors and rewarding them with 401 ETH.
+Kleros allows integration with new protocols and we leave it to future work.
 

### 2024-08-12 paper/main.tex
update fairnesss section

@@
 Traditionally, this has involved legal contracts and law enforcement.
-With blockchain technology, smart contracts offer a new way by putting the details of a contract into code and enforcing it through a consensus mechanism.~\cite{allenGovernanceBlockchainDispute2019}.
+With blockchain technology, smart contracts offer a new way by putting the details of a contract into code and enforcing it through a consensus mechanism.~\cite{allenGovernanceBlockchainDispute2019,lingwallShouldCodeBe2019}.
 \end{sloppypar}
@@
 They feed real-world data into the blockchain~\cite{breidenbachChainlinkNextSteps2021}.
-This is important for dispute resolution systems like Themis~\cite{mengThemisDecentralizedEscrow2019} and Kleros~\cite{bergollaKlerosSociolegalCase2022}, which use decentralized networks to make fair decisions.
-However, these systems may struggle with complex disputes that require special knowledge and privacy.
+This is important for dispute resolution systems like Kleros~\cite{bergollaKlerosSociolegalCase2022, nappertDecentralizedJusticeReinventing2020, gudkovCrowdArbitrationBlockchain2020} or Themis~\cite{mengThemisDecentralizedEscrow2019}, which use decentralized networks to make fair decisions.
+Such arbitration services employ a pool of local experts who would
+In the event of a dispute, they would examine the smart contract and all the evidence to provide verdicts back to the blockchain.
+The SP would be required to lock a certain amount of funds into the protocol, which would be cut in the event of misbehaviour.
+However, these systems may struggle with complex disputes that require specialised knowledge and privacy.
 \end{sloppypar}
@@
 It has received funding from the Commission's European Innovation Council~\cite{CommissionEuropeanInnovation2020}.
-The protocol claims to have resolved 1645 disputes, employing 716 jurors and rewarding them with 401 ETH.
+The protocol claims to have resolved 1645 disputes, employing 716 jurors and rewarding them with 401 ETH~\cite{KlerosHomepage}.
 Kleros allows integration with new protocols and we leave it to future work.

### 2024-08-14 paper/main.tex
update comparision table

@@
 \newcommand{\TTP}{\cellcolor{red!50}TTP}
+\newcommand{\OffTTP}{\cellcolor{orange!50}Offline TTP}
+\newcommand{\OffBC}{\cellcolor{yellow!50}BC \& Offline TTP}
 \newcommand{\BC}{\cellcolor{green!50}BC}
 \caption{Comparison of related works.
-The notation \textit{Pseudonymity} means that the anonymity is based on the assumption that the pseudonym is not linked to the real identity; \textit{TTP} means that the protocol uses a trusted third party; \textit{BC} means that the protocol uses a public blockchain; \textit{YES*} means that the protocol provides the feature but is based on strong or impractical assumptions.}
+Category Definitions: \textit{E-commerce:} Secure online transactions for physical goods; \textit{Private Delivery System:} Methods ensuring fair and anonymous delivery of physical products; \textit{Certified email:} Secure exchange of certified electronic mail with proof of receipt; \textit{Digital escrow:} Decentralized escrow services for secure digital currency transactions.
+The notation \textit{Pseudonymity} means that the anonymity is based on the assumption that the pseudonym is not linked to the real identity; \textit{TTP} means that the protocol relies on a trusted third party in every transaction; \textit{Offline TTP} means that the protocol relies on a trusted third party only to resolve disputes; \textit{BC} means that the protocol uses a public blockchain; \textit{YES*} means that the protocol provides the feature but is based on strong or impractical assumptions.}
 \label{tab:comparison}
@@
 
-\begin{tabular}{cccccc}
+\begin{tabular}{ccccccc}
 
 \noalign{\smallskip}\hline\noalign{\smallskip}
-Protocol & Fair exchange & Anonymity & Dispute resolution & Trust & Physical delivery \\
+Protocol & Scenario & Fair exchange & Anonymity & Dispute resolution & Trust & Physical delivery \\
 \noalign{\smallskip}\hline\noalign{\smallskip}
-\cite{zhangPracticalFairExchangeEPayment2006} (2006) & \YES & \YESBUT & \YES & \TTP & \YES \\
-\cite{mohammedalarajFairnessPhysicalProducts2012} (2012) & \YESBUT & \NO & \YES & \TTP & \YES \\
-Lelantos~\cite{altawyLelantosBlockchainBasedAnonymous2017} (2017) & \YES & \PSEUDO & \NO & \BC & \YES \\
-\cite{hinarejosSolutionSecureCertified2019} (2019) & \YES & \NO & \NO & \BC & \NO \\
-Themis~\cite{mengThemisDecentralizedEscrow2019} (2019) & \YES & \NO & \YES & \BC & \NO \\
-PPPDCP~\cite{birjoveanuTwoPartyECommerceProtocols2022} (2022) & \YES & \YES & \YES & \TTP & \YES \\
-This paper & \YES & \YES & \YES & \BC & \YES \\
+Zhang et al. \cite{zhangPracticalFairExchangeEPayment2006} (2006) & E-commerce & \YES & \YESBUT & \YES & \TTP & \YES  \\
+Alaraj et al.\cite{mohammedalarajFairnessPhysicalProducts2012} (2012) & E-commerce & \YESBUT & \NO & \YES & \OffTTP & \YES \\
+Lelantos~\cite{altawyLelantosBlockchainBasedAnonymous2017} (2017) & Private Delivery System & \YES & \PSEUDO & \NO & \BC & \YES \\
+Hinarejos et al.\cite{hinarejosSolutionSecureCertified2019} (2019) & Certified email & \YES & \NO & \NO & \BC & \NO \\
+Themis~\cite{mengThemisDecentralizedEscrow2019} (2019) & Digital escrow & \YES & \NO & \YES & \BC & \NO \\
+PPPDCP~\cite{birjoveanuTwoPartyECommerceProtocols2022} (2022) & E-commerce & \YES & \YES & \YES & \TTP & \YES \\
+This paper & E-commerce & \YES & \YES & \YES & \OffBC & \YES \\
 \noalign{\smallskip}\hline

### 2024-08-15 paper/main.tex
improve the fairness anaylsis

@@
 
-\section{Fairness Analysis}\label{sec:fairness-analysis}
-The fairness of our protocol is assessed by representing it as an interactive non-cooperative game, examining the strategic interactions between the service provider (SP) and the customer.
-
-\subsection{Model}\label{sec:fairness-model}
+\section{Fair Exchange Analysis}\label{sec:fairness-analysis}
+
+Fair exchange protocols involve two parties trading items with each other, where each party holds an item to trade and expects to receive a specific item in return.
+These protocols operate even when the parties do not necessarily trust each other.
+A key goal of fair exchange protocols is to ensure that a dishonest participant cannot exploit the situation to gain an advantage over an honest participant.
+Specifically, these protocols must meet the following requirements~\cite{asokanFairnessElectronicCommerce1998, liuFairnessCryptocurrencyPayments2018}:
+\begin{enumerate}
+
+    \item \textbf{R1, Fairness}: Fairness can be defined in two ways:\begin{itemize}
+        \item \textbf{R1a Strong fairness}: Upon protocol completion, either both participants receive their desired items (successful exchange) or neither does (exchange fails).
+        \begin{sloppypar}
+        \item \textbf{R1b Weak fairness}: When strong fairness is not achievable, an honest participant can demonstrate to an external arbiter that the other party has received (or still can receive) the expected item.
+        \end{sloppypar}
+    \end{itemize}
+
+    \item \textbf{R2, Timeliness}: An honest participant can be assured that the exchange will conclude (either successfully or unsuccessfully) within a specified timeframe, regardless of the other participant's behavior.
+At the end of the protocol, the outcome is final from the honest participant's perspective (e.g., the fairness ensured by the protocol remains consistent).
+
+    \item \textbf{R3, Effectiveness}: The protocol guarantees successful completion of the exchange if both participants act correctly and agree to trade.
+
+\end{enumerate}
+
+\subsection{Weak fairness}
+
+Our protocol relies on an external arbiter to resolve disputes and so, by definition, it can achieve only \textbf{R1b Weak Fairness}.
+The weak fairness of our protocol is assessed by representing it as an interactive non-cooperative game, examining the strategic interactions between the service provider (SP) and the customer.
+
+\subsubsection{Model}\label{sec:fairness-model}
 We define three distinct positions to represent the state of each party within the protocol:
@@
 
-\begin{definition}[Fairness] \label{def:fairness}
+\begin{definition}[Weak Fairness] \label{def:fairness}
 Let $\mathrm{parties} = \{ C, SP \}$, $\mathrm{steps} = 1..9$, $\mathrm{actions} = \{ \normal{}, \abnormal{}, \dispute{}, \abdispute{} \}$, and
@@
 
-\subsection{Assumptions}\label{sec:assumptions}
+\subsubsection{Assumptions}\label{sec:assumptions}
 
@@
 
-\subsection{Steps}\label{sec:steps}
+\subsubsection{Steps}\label{sec:steps}
 
@@
 
-\subsection{Analyse scenarios}\label{example-scenarios}
-This section illustrates two scenarios using figures to show the transitions of positions between the customer and the SP under different conditions.
+% By applying the definition of fairness from Section~\ref{def:fairness} and considering the assumptions outlined in Section~\ref{sec:assumptions}, our analysis confirms that the protocol achieves fairness under these scenarios (see ~\ref{app:proof-of-fairness} for detailed description).
+
+\subsection{Timeliness}
+The timeliness of the protocol is achieved through the use of blockchain.
+Assuming an honest majority, the blockchain acts as a global, immutable and undeniable clock that timestamps each action and moves the protocol forward.
+Every step must be recorded on the blockchain, once the transaction is recorded it's undeniable.
+
+Both parties agree to the timelines $\mathrm{T}_\mathrm{issue}$, $\mathrm{T}_\mathrm{pay}$, $\mathrm{T}_\mathrm{provide}$ and so any breach of the timelines is undeniably conclusive.
+The blockchain continuously creates blocks at a probabilistic rate.
+If a party hasn't fulfilled its step within a time window, it can't publish a transaction in a previous block.
+Consequently, the protocol cannot move from a completed to a non-completed state, nor can it hang in a non-completed position as the timelines push it forward, thus fulfilling the \textbf{R2, Timeliness} requirement.
+
+% TODO: finish this train of thought
+% TODO: The transaction actually can hang out if one party voliate and the other doesn't start a dispute. We would have to add a period of time where the dispute is 
+% An honest participant can be assured that the exchange will conclude (either successfully or unsuccessfully) within a specified timeframe, regardless of the other participant's behavior.
+At the end of the protocol, the outcome is final from the honest participant's perspective (e.g., the fairness ensured by the protocol remains consistent).
+
+\subsection{Effectiveness}
+
+\begin{figure}[h!]
+\includegraphics[width=\linewidth]{rational.png}
+\centering
+\caption{Transitions of positions in a scenario where both the customer and the SP adhere to the protocol.}
+\label{fig:rational}
+\end{figure}
+
+The first scenario (Figure~\ref{fig:rational}) represents the rational and intended course of action, where both the client and the SP follow the protocol as designed.
+This scenario is crucial as it shows that parties who act correctly (normally and agreeably) will eventually succeed and thus \textbf{R3, Effectiveness} is achieved.
+
+\subsection{Dispute scenario}\label{sec:example-scenarios}
 
@@
 
-\paragraph{Dispute}
-In the first scenario (Figure~\ref{fig:misbehaviour}), (1) the customer initialise the transaction and delivers the material to the SP, (2) who validates the materials and publish the Proof of Delivery ($\mathrm{PoD}$) on blockchain.
-(3) The customer validates the existence of PoD on blockchain and (4) pay for the transaction using one of the specified payment method.
-(5) The SP misbehaves by not delivering the service and consequently not publishing the Proof of Provision ($\mathrm{PoP}$) after having received the payment.
-Once the agreed deadline $\mathrm{T}_\mathrm{provide}$ pass the position moves to the Abnormal column and the customer is in disadvantage position and the SP is in advantage position.
-However, the customer is justified in starting a dispute, by collecting all the evidences, i.e., Proof of Delivery ($\mathrm{PoD}$) from Message Board, payment $\mathrm{recipt}$, and delivering them to the Dispute Resolution Service.
+In the second scenario (Figure~\ref{fig:misbehaviour}), (1) the customer initialises the transaction and delivers the material to the SP, (2) who validates the material and publishes the Proof of Delivery ($\mathrm{PoD}$) on blockchain.
+(3) The customer validates the existence of the PoD on the blockchain, and (4) pays for the transaction using one of the specified payment methods.
+(5) The SP misbehaves by not provisioning the service and consequently not publishing the Proof of Provision ($\mathrm{PoP}$) after receiving the payment.
+Once the agreed $\mathrm{T}_\mathrm{provide}$ deadline has passed, the position moves to the Abnormal column and the customer is in a disadvantaged position and the SP is in an advantaged position.
+However, the customer is justified in starting a dispute by collecting all the evidence, i.e.
+Proof of Delivery ($\mathrm{PoD}$) from the message board, payment $\mathrm{recipt}$, and submitting it to the dispute resolution service.
 The customer is likely to win this dispute as the SP cannot prove the timely publication of $\mathrm{PoP}$.
-This scenario results in a neutral outcome for the customer and a disadvantageous outcome for the SP.
-
-\begin{figure}[h!]
-\includegraphics[width=\linewidth]{rational.png}
-\centering
-\caption{Transitions of positions in a scenario where both the customer and the SP adhere to the protocol.}
-\label{fig:rational}
-\end{figure}
-
-\paragraph{Agreement}
-The second scenario (Figure~\ref{fig:rational}) represents the rational and intended course of action, where both the customer and the SP follow the protocol as designed.
-This scenario is crucial as it demonstrates the protocol functioning optimally, leading to a fair outcome for both parties.
-
-By applying the definition of fairness from Section~\ref{def:fairness} and considering the assumptions outlined in Section~\ref{sec:assumptions}, our analysis confirms that the protocol achieves fairness under these scenarios (see ~\ref{app:proof-of-fairness} for detailed description).
+This scenario results in a neutral outcome for the customer and a disadvantaged outcome for the SP.
 
@@
 Furthermore, we leveraged decentralized storage networks like IPFS and Filecoin, which facilitate the anonymous storage and retrieval of data.
-This approach guaranteed that customer interactions with the protocol remained confidential at every stage.
-\end{sloppypar}
-
-In the event of a dispute, the customer may lose their anonymity due to local policy enforcement that requires identification.
-To maintain anonymity in the event of a dispute, the anonymous dispute resolution service would have to be used.
-We discuss this further in section~\ref{sec:decentralised-justice}.
+This approach guaranteed that, in the dispute-free transaction, customer interactions with the protocol remained confidential at every stage.
+
+Depending on the specific use case, the anonymity of the customer may be lost if the resolution of the dispute (e.g.
+by the police) involves the identification of the customer.
+However, even if the Dispute Resolution Service identifies the customer, the customer's identity won't be disclosed to the SP, which is the main goal of the protocol.
+
+To maintain anonymity in the event of a dispute,
+Online Dispute Resolution systems~\cite{allenGovernanceBlockchainDispute2019, lingwallShouldCodeBe2019} such as  Kleros~\cite{bergollaKlerosSociolegalCase2022, nappertDecentralizedJusticeReinventing2020, gudkovCrowdArbitrationBlockchain2020} should be used, where only the customer's pseudonym is revealed and anonymous evidence can be provided in zero-knowledge proofs.
+We discuss this further in Section~\ref{sec:decentralised-justice}.
+\end{sloppypar}
 

### 2024-08-16 paper/main.tex
update reviewer suggestions

@@
 \begin{sloppypar}
-Compared to other solutions, our protocol achieves anonymity with weaker assumptions, supports physical materials and conflict resolution, and does not require the customer to interact with the blockchain in conflict-free transactions, demonstrating better practicality.
-\end{sloppypar}
-
-In this work, we analyse the fairness of our protocol and implement it using Ethereum technology as a message board, Monero as an anonymous payment method, and Powergate (IPFS and Filecoin) as a decentralised storage network.
+Compared to other solutions, our protocol achieves anonymity with weaker assumptions, supports physical materials and conflict resolution, and does not require the customer to interact with the trusted arbiter in conflict-free transactions, demonstrating better practicality.
+\end{sloppypar}
+
+We analyse the fairness of our protocol and implement it using Ethereum technology as a message board, Monero as an anonymous payment method, and Powergate (IPFS and Filecoin) as a decentralised storage network.
   \newcommand{\sep}{ \and }
@@
 In our case, the parties exchange money and sensitive (possibly physical) materials for a service result.
-Our review shows that current systems do not achieve our goals.
+Our review of existing systems reveals that none fully meet our requirements.
 We propose an anonymous protocol for services that require physical materials, with dispute resolution capabilities.
 If disputes arise, customers can disclose interactions and prove SP misbehavior.
+\end{sloppypar}
+
+\begin{sloppypar}
+Our protocol is specifically designed for the commerce sector, particularly for service providers who handle sensitive and potentially physical materials provided by customers, such as biological samples, legal documents, or financial records.
+This includes applications in anonymous genetic testing, forensic analysis, and confidential research studies where personal data and physical materials must be handled with utmost privacy.
+Additionally, the protocol is beneficial for discreet services such as substance testing, private counseling, and therapy, as well as in sectors like industrial testing, environmental analysis, and intellectual property verification, where anonymity and secure handling of physical materials are crucial.
+These services span across industries such as healthcare, legal services, environmental science, and industrial compliance, highlighting the protocol's versatility in ensuring both privacy and compliance with legal regulations.
+By addressing the unique challenges of transactions involving physical materials, our approach ensures that these services can be delivered securely and fairly, even when the customer's identity remains protected.
 \end{sloppypar}
@@
 
-It is also an agreement between the customer and the SP as it contains agreed deadlines for actions and a payment method.
+It is also an agreement between the customer and the SP as it contains the description of the expected item~\footnote{We follow the assumption from~\cite{asokanFairnessElectronicCommerce1998} that there exists a string that describes the desired item in "sufficient" detail so that during the dispute the arbitrator can decide whether the provided result is as agreed.}, agreed deadlines for actions and a payment method.
 \begin{eqnarray}
-\mathrm{PoD} & \equiv & (\begin{array}[t]{l}\mathrm{pk_C}, \mathrm{provisionID},   \mathrm{paymentAddress},
-\mathrm{sig}_\mathrm{SP}, \\\\ 
-\mathrm{T}_\mathrm{issue}, \mathrm{T}_\mathrm{pay}, \mathrm{T}_\mathrm{provide}\; )\end{array}
+\mathrm{PoD} & \equiv & (\begin{array}[t]{l}\mathrm{pk_C}, \mathrm{provisionID},    \mathrm{itemDescription}, \\\\ 
+\mathrm{paymentAddress}, \mathrm{T}_\mathrm{issue}, \mathrm{T}_\mathrm{pay}, \mathrm{T}_\mathrm{provide}, \mathrm{sig}_\mathrm{SP} \; )\end{array}
 \end{eqnarray}
@@
 \item $\mathrm{provisionID}$ - Unique transaction identifier.
+\item $\mathrm{itemDescription}$ - Hash of the description of the expected item.
 \item $\mathrm{paymentAddress}$ - SP's anonymous payment address.
-\item $\mathrm{sig}_\mathrm{SP}$ - SP's digital signature.
+
 \item $\mathrm{T}_\mathrm{issue}$ - Time of $\mathrm{PoD}$ issuance.
@@
 \item $\mathrm{T}_\mathrm{provide}$ - Service provision deadline.
+\item $\mathrm{sig}_\mathrm{SP}$ - SP's digital signature.
 \end{itemize}
@@
 The SP creates $\mathrm{PoD}$ with deadlines $\mathrm{T}_\mathrm{pay}$, $\mathrm{T}_\mathrm{provide}$, and $\mathrm{T}_\mathrm{issue}$.
-The $\mathrm{PoD}$ also specifies the payment method (cash or blockchain address).
+The $\mathrm{PoD}$ also specifies the description of the item $itemDescription$, and payment method (cash or blockchain address).
 The SP's digital signature $\mathrm{sig}_{\mathrm{sk}_\mathrm{SP}}$ on $\mathrm{PoD}$ ensures non-repudiation.
@@
 \begin{algorithmic}[1]
-\Function{proofOfDelivery}{$pk_C$, $provisionId$, $paidInCash$, $paymentAddress$, $paymentWindow$, $provisionWindow$, $sig_{SP}$}
+\Function{proofOfDelivery}{$pk_C$, $provisionId$, $itemDescription$, $paidInCash$, $paymentAddress$, $paymentWindow$, $provisionWindow$, $sig_{SP}$}
     \State Verify $sig_{SP}$
@@
 
-    \State $provision \gets \left\{ \mathrm{T}_\mathrm{issue}, paymentDeadlineTime, \right.$
-    \State \hspace{\algorithmicindent}$\left. \mathrm{T}_\mathrm{pay}, \mathrm{T}_\mathrm{provide}, paidInCash, paymentAddress \right\}$
+    \State $provision \gets \left\{ \mathrm{T}_\mathrm{issue}, \mathrm{T}_\mathrm{pay}, \mathrm{T}_\mathrm{provide} \right.$
+    \State \hspace{\algorithmicindent}$\left. itemDescription, paidInCash, paymentAddress \right\}$
     \State provisions[$pk_C$][$provisionId$] $\gets provision$
@@
 
-The customer retrieves $\mathrm{PoD}$ from the message board and verifies its correctness.
+The customer retrieves $\mathrm{PoD}$ from the message board and verifies payment details, $itemDescription$ and time windows ($\mathrm{T}_\mathrm{issue}$, $\mathrm{T}_\mathrm{pay}$, $\mathrm{T}_\mathrm{provide}$).
 
@@
 \subsection{Weak fairness}
-
-Our protocol relies on an external arbiter to resolve disputes and so, by definition, it can achieve only \textbf{R1b Weak Fairness}.
-The weak fairness of our protocol is assessed by representing it as an interactive non-cooperative game, examining the strategic interactions between the service provider (SP) and the customer.
+Here we show that with the use of an external arbitrator (Dispute Resolution Service), either both parties receive their desired items at the end of the protocol, or neither receives anything.
+That is, the customer gets $result$ and the SP gets $payment$, or neither gets anything.
+This is how \textbf{R1b Weak Fairness} is achieved.
+
+First, we represent the protocol as an interactive non-cooperative game and analyse the strategic interactions between the service provider (SP) and the customer.
+We then show that successful completions result in both parties receiving desired items, and all unsuccessful completions result in both parties receiving nothing.
+We also extend the definition to include penalties for misbehaviour, which discourages frivolous or uncertain disputes.
 
@@
 Conversely, the customer can dispute at any time, but only proven misbehavior of the SP will result in a successful dispute.
-
-\begin{definition}[Weak Fairness] \label{def:fairness}
-Let $\mathrm{parties} = \{ C, SP \}$, $\mathrm{steps} = 1..9$, $\mathrm{actions} = \{ \normal{}, \abnormal{}, \dispute{}, \abdispute{} \}$, and
-
-\begin{equation}
-M_{\sigma_\mathrm{s,p,a}} = 
-\begin{cases} 
-\{ \mathrm{\sigma_{s+1,p,\normal}}, \mathrm{\sigma_{s+1,p,\abnormal}}, \mathrm{\sigma_{s,p,\dispute}}, \mathrm{\sigma_{s,p,\abdispute}} \} & \text{if } s < 9, a = \normal{} \\
-\{ \mathrm{\sigma_{s,p,a}} \} & \text{otherwise} 
-\end{cases}
-\end{equation}
-represent the set of all possible positions a party $\mathrm{p}$ can move to at step $\mathrm{s}$ by taking action $\mathrm{a}$, from position $\sigma_\mathrm{s,p,a}$.
+The Algorithm~\ref{alg:disputeResolution} presents the process of dispute resolution.
+
+\begin{algorithm}
+\caption{Algorithm for Dispute Resolution}
+\label{alg:disputeResolution}
+\begin{algorithmic}[1]
+\Function{Dispute Resolution}{$pk_C$, $provisionId$, $receipt$, $result$}
+
+    \State $provision$ $\gets$ $provisions$[$pk_C$][$provisionId$]
+    \If{Time dispute}
+    \State Verify $provision$.$paidInCash$ OR  (valid $receipt$ AND $receipt$.time < $provision$.$\mathrm{T}_\mathrm{pay}$)
+    \State Verify not $provision$.$cid$ and $provision$.$provisionTime$ > $provision$.$\mathrm{T}_\mathrm{provide}$
+    \State \Return The Customer wins the dispute because the SP has not provided the PoP on the agreed time.
+    \EndIf
+    \If{Result dispute}
+        \State $provision$.$cid$ $\equiv$ $result$
+        \State $provision$.$itemDescription$ $\not\equiv$ $result$
+        \State \Return The Customer wins the dispute because the SP has not provided the desired result.
+    \EndIf
+\EndFunction
+\end{algorithmic}
+\end{algorithm}
+
+% \begin{definition}[Weak Fairness] \label{def:fairness}
+% Let $\mathrm{parties} = \{ C, SP \}$, $\mathrm{steps} = 1..9$, $\mathrm{actions} = \{ \normal{}, \abnormal{}, \dispute{}, \abdispute{} \}$, and
+
+% \begin{equation}
+% M_{\sigma_\mathrm{s,p,a}} = 
+% \begin{cases} 
+% \{ \mathrm{\sigma_{s+1,p,\normal}}, \mathrm{\sigma_{s+1,p,\abnormal}}, \mathrm{\sigma_{s,p,\dispute}}, \mathrm{\sigma_{s,p,\abdispute}} \} & \text{if } s < 9, a = \normal{} \\
+% \{ \mathrm{\sigma_{s,p,a}} \} & \text{otherwise} 
+% \end{cases}
+% \end{equation}
+% represent the set of all possible positions a party $\mathrm{p}$ can move to at step $\mathrm{s}$ by taking action $\mathrm{a}$, from position $\sigma_\mathrm{s,p,a}$.
 The second case in $M_{\sigma_\mathrm{s,p,a}}$ represents the termination positions.
 
-A protocol is said to be fair if, at each step, both the customer and the service provider have the option to move to or remain in a non-disadvantaged position.
-
-\begin{equation}
-\forall_{\mathrm{p} \in \mathrm{parties}} \forall_{\mathrm{s} \in \mathrm{steps}} \forall_{\mathrm{a} \in \mathrm{actions}} \exists \sigma \in M_{\sigma_\mathrm{s, p, a}} \text{ such that } \sigma \neq -
-\end{equation}
-\end{definition}
+% A protocol is said to be fair if, at each step, both the customer and the service provider have the option to move to or remain in a non-disadvantaged position.
+
+% \begin{equation}
+% \forall_{\mathrm{p} \in \mathrm{parties}} \forall_{\mathrm{s} \in \mathrm{steps}} \forall_{\mathrm{a} \in \mathrm{actions}} \exists \sigma \in M_{\sigma_\mathrm{s, p, a}} \text{ such that } \sigma \neq -
+% \end{equation}
+% \end{definition}
 
@@
 
-\subsubsection{Steps}\label{sec:steps}
-
-The fairness of our protocol is visually represented in Figure~\ref{fig:positions}, which shows the positions of each party after each possible action within the protocol.
+\subsection{Proofs}\label{sec:proofs}
+
+\begin{theorem}
+The proposed protocol satisfies the security requirement of \textbf{R1b Weak fairness}.  
+\end{theorem}
+
+\begin{proof} 
+The positions of each party after each action within our protocol are visually represented in Figure~\ref{fig:positions}.
+The detailed description of each step and the reasoning behind the outcomes is given in~\ref{app:proof-of-fairness}.
 
@@
 
-The detailed description of each step and the reasoning behind the outcomes is given in~\ref{app:proof-of-fairness}.
-
-% By applying the definition of fairness from Section~\ref{def:fairness} and considering the assumptions outlined in Section~\ref{sec:assumptions}, our analysis confirms that the protocol achieves fairness under these scenarios (see ~\ref{app:proof-of-fairness} for detailed description).
-
-\subsection{Timeliness}
+Following the definition of \textbf{R1b Weak fairness} it's sufficient to show that, with the use of an external arbitrator (Dispute Resolution Service), the protocol completes either with both parties getting the desired items (advantaged positions), or neither does (neutral or disadvantaged).
+The protocol (successfully) completes at the last normal agreement step ($\sigma_{9,n}$), and (unsuccessfully), after starting a dispute ($\sigma_{\dispute}$ or $\sigma_{\abdispute}$). 
+We consider only honest (rational) customer, and so it will always starts a dispute after the SP misbehaves, and so it will never settle at abnormal agreement positions ($\sigma_{\abnormal}$, as that would be irrational.
+
+\end{proof}
+
+\begin{theorem}
+The proposed protocol satisfies the security requirement of \textbf{R2, Timeliness}.  
+\end{theorem}
+
+\begin{proof}
+
 The timeliness of the protocol is achieved through the use of blockchain.
-Assuming an honest majority, the blockchain acts as a global, immutable and undeniable clock that timestamps each action and moves the protocol forward.
+Assuming an honest majority, the blockchain acts as a global, immutable and undeniable clock that timestamps every action and moves the protocol forward.
 Every step must be recorded on the blockchain, once the transaction is recorded it's undeniable.
@@
 The blockchain continuously creates blocks at a probabilistic rate.
-If a party hasn't fulfilled its step within a time window, it can't publish a transaction in a previous block.
-Consequently, the protocol cannot move from a completed to a non-completed state, nor can it hang in a non-completed position as the timelines push it forward, thus fulfilling the \textbf{R2, Timeliness} requirement.
+If a party hasn't completed its step within a time window, it can't publish a transaction in a previous block.
+Consequently, the protocol cannot move from a completed to an uncompleted state, nor can it hang in an uncompleted position, as the blocks produced move the parties' states out of the agreed timelines, thus fulfilling the \textbf{R2, Timeliness} requirement.
+\end{proof}
 
@@
 At the end of the protocol, the outcome is final from the honest participant's perspective (e.g., the fairness ensured by the protocol remains consistent).
-
-\subsection{Effectiveness}
 
@@
 \end{figure}
+
+\begin{theorem}
+The proposed protocol satisfies the security requirement of \textbf{R2, Effectiveness}.  
+\end{theorem}
 
@@
 \paragraph{Fairness}
-As shown in Section~\ref{sec:steps} and ~\ref{app:proof-of-fairness}, the protocol is fair.
+As shown in Section~\ref{sec:proofs} the protocol is fair.
 This was achieved through an undeniable handshake mechanism, where the SP first commits to the package delivery and service deadlines by publishing the PoD (as outlined in step 2).
@@
 Below we describe each step and the reasoning behind the outcome position.
-We use the notation introduced in Section~\ref{sec:fairness-model} to analyse each position in the protocol and the fairness Definition~\ref{def:fairness} to show the fairness of the protocol.
+We use the notation introduced in Section~\ref{sec:fairness-model} to analyse each position in the protocol and to show the fairness of the protocol.
 

### 2024-08-21 paper/main.tex
update bibliography

@@
 
-The prototype is available at \url{https://anonser.stan.bar}. The source code is available at \url{https://github.com/stanbar/anonser}.
+The source code is available at \url{https://github.com/stanbar/anonser}.
 
@@
 At the time of writing Kleros is the most successful platform for resolving consumer disputes in e-commerce or collaborative economy.
-It has received funding from the Commission's European Innovation Council~\cite{CommissionEuropeanInnovation2020}.
+It has received funding from the Commission's European Innovation Council~\cite{europeancommissionCommissionEuropeanInnovation2020}.
 The protocol claims to have resolved 1645 disputes, employing 716 jurors and rewarding them with 401 ETH~\cite{KlerosHomepage}.
@@
 Ongoing research into compliant privacy mixers, such as the Voluntary Reveal Approach proposed in~\cite{dotanHazeCompliantPrivacy2023}, seeks to address these concerns.
-This approach involves Proofs of Innocence required before a user can access the system and incorporates oracles for monitoring sanctioned addresses—currently maintained on the Ethereum blockchain by Chainalysis~\cite{ChainalysisOracleSanctions}.
+This approach involves Proofs of Innocence required before a user can access the system and incorporates oracles for monitoring sanctioned addresses—currently maintained on the Ethereum blockchain by Chainalysis~\cite{chainalysisChainalysisOracleSanctions}.
 \end{sloppypar}
@@
 \begin{sloppypar}
-Through rigorous definition and analysis, we have demonstrated that our protocol meets the criteria for fairness, as outlined in Definition~\ref{def:fairness}.
+Through rigorous definition and analysis, we have demonstrated that our protocol meets the criteria for fair-exchange protocol, as shown in in Section~\ref{sec:fairness-analysis}.
 It does so by systematically publishing proofs of delivery, payment, and provisioning, ensuring a transparent and equitable process for all parties involved.
@@
 No data was used for the research described in the article.
-The prototype is available at \url{https://anonser.stan.bar}. 
 The source code is available at \url{https://github.com/stanbar/anonser}.
